### 2023-06-12 paper/ms.tex
stage ms

% upon AAS submission
%\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
% drafting / arxiv
\documentclass[11pt,twocolumn,tighten]{aastex63}
\turnoffedit

\usepackage{apjfonts}
\usepackage{url}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{amsmath,amstext,amssymb}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{xcolor, fontawesome}
\usepackage{color}

\newcommand{\rprs}{{$R_p/R_{\star}$}}
\newcommand{\vsini}{{$V \sin i$}}
\newcommand{\teff}{T$_{\textrm{eff}}$}
\newcommand{\kms}{{km\,s$^{-1}$}}
\newcommand{\gcc}{{g\,cm$^{-3}$}}
\newcommand{\rstar}{{$R_\star$}}
\newcommand{\rhostar}{{$\rho_\star$}}
\newcommand{\mearth}{{M$_\oplus$}}
\newcommand{\rearth}{{R$_\oplus$}}
\newcommand{\rsun}{{R$_\odot$}}
\newcommand{\msun}{{M$_\odot$}}

\newcommand{\minus}{\scalebox{0.5}[1.0]{$-$}}

\newcommand{\eg}{e.g.,}

\newcommand{\mstype}{letter}

%%%%%%%%%%%%%%%%
% INSTITUTIONS %
%%%%%%%%%%%%%%%%
\newcommand{\caltech}{Department of Astronomy, MC 249-17, California Institute of Technology, Pasadena, CA 91125, USA}
\newcommand{\mitkavli}{MIT Kavli Institute and Department of Physics, 77 Massachusetts Avenue, Cambridge, MA 02139}
\newcommand{\berkeley}{Astronomy Department, University of California, Berkeley, CA 94720, USA}

%
% ms specific numbers
%

%%%%%%%%%
% STARS %
%%%%%%%%%
\newcommand{\nstarssearched}{{XXYYY}}

%%%%%%%%
% CPVS %
%%%%%%%%
\newcommand{\ncpvsfound}{{48}}
\newcommand{\nmaybes}{{19}}

\begin{document}

\title{Bright and Nearby Complex Periodic Variables from Four Years of TESS}

\correspondingauthor{TBD}
\email{TBD}

\received{---}
\revised{---}
\accepted{---}
\shorttitle{Cycle 1-4 CPVs}

\shortauthors{TBD}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\author{Authors to include (ORDER TBD)}

% primary authors
\author[0000-0002-0514-5538]{Luke~G.~Bouma}
\altaffiliation{51 Pegasi b Fellow}
\affiliation{\caltech}

\author[0000-0002-7778-3117]{Rahul~Jayararaman}
\affiliation{\mitkavli}

% [to be confirmed after these]
\author{Saul~Rappaport}
\affiliation{\mitkavli}

\author{Lynne~A.~Hillenbrand}
\affiliation{\caltech}

\author[0000-0003-2058-6662]{George~R.~Ricker}
\affiliation{\mitkavli}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
  Complex periodic variables (CPVs) are pre-main-sequence M-dwarfs
  with periodic optical modulation that includes both sharp and broad
  troughs.
  The troughs are usually superposed on smooth, spot-like modulation.
  Based on a lack of observed infrared excesses, these objects do not
  have primordial gas-rich disks, or even particularly massive debris disks.
  Nonetheless, the most plausible explanations for their optical
  variability invoke long-lived material that orbits at the corotation
  radii, for instance transiting dust clumps or stellar prominences.
  Here, we report new CPVs discovered in the 120-second cadence TESS data
  collected between July~2018 and Sep~2022 (Sectors 1-55).
  Our search used two methods, the first based on counting dips in
  phase-folded light curves, and the second based on counting peaks in
  the Fourier domain.
  From our analysis of \nstarssearched\ M-dwarfs with $T$$<$16 and
  $d$$<$150\,pc, we find \ncpvsfound\ gold-standard CPVs.
  Most of these discoveries are new, and they include the brightest
  ($T$$\approx$10) and closest ($d$$\approx$20\,pc) examples of this
  class of variable star known.
  A few objects are ``outliers among outliers''; for
  instance LP 12-502 shows up to eight local minima per cycle, exhibited
  sudden shape ``switches'' over less than one cycle, yet maintained
  a near-constant cycle duration over more than one thousand cycles.
  The general cause of the optical variability for these objects remains
  enigmatic.  However our sample is a step toward the spectroscopic and
  demographic studies that may ultimately resolve the mystery of what
  physically explains these objects.
  Connections to the broader context of star, disk, and
  exoplanet evolution are emphasized.
\end{abstract}

\keywords{Weak-line T Tauri stars (1795), Periodic variable stars
(1213), Circumstellar matter (241), Star clusters (1567), Stellar
magnetic fields (1610), Stellar rotation (1629)}

\section{Introduction}
\label{sec:intro}

All pre-main-sequence stars vary in optical brightness, and the origin
of such variability is, in most cases, understood.  Well-explored
sources of optical variability include inhomogeneities on stellar
surfaces such as starspots and faculae
\citep[e.g.][]{2021isma.book.....B}, occultations by gas-rich
circumstellar disks \citep[e.g.][]{2017MNRAS.470..202B}, and, in
geometrically favorable circumstances, eclipses by stars and planets.

Data from K2 and TESS have yielded a new class of variable star whose
root cause is not yet qualitatively understood: complex periodic
variables (CPVs).  These objects are identified phenomenologically
using their optical light curves, which show periodic sharp and
sometimes broad troughs, often superposed on smooth spot-like
modulation.  Some of the objects show up to eight local minima (dips)
per cycle; sharp peaks are also common.  Most of these variable stars
turn out to be pre-main-sequence M-dwarfs without near-infrared
excesses, with ages of $\approx$5-150 million years (Myr), and
rotation periods of at most two days; they are observed to be
$\approx$1\% of M-dwarfs younger than 100 Myr
\citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G}.
The dips can be chromatic, with a reddening law plausibly consistent
with dust
\citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
And finally, while the dip shapes can ``jump'' between different
depths and durations over less than one cycle, they more often evolve
gradually, over tens to hundreds of cycles
\citep[e.g.][]{2017AJ....153..152S,2020AJ....160...86B,2023ApJ...945..114P}.

The issue of what exactly causes the variability that defines the CPVs
has yet to be resolved.  There are a few competing explanations.  All
young M-dwarfs are spotted, which produces flux variations over
characteristic timescales of the rotation period, $P_{\rm rot}$, and
its half-harmonic, $0.5\,P_{\rm rot}$.  The observed dips occur over
durations as short as $0.05\,P_{\rm rot}$; a ``starspot-only''
scenario is therefore highly unlikely for any of the objects with
sufficiently sharp dips
\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The more likely
scenarios instead invoke sharp geometries with material extrinsic to
the stellar surface \citep[see
Refs.~][]{2017AJ....153..152S,2022AJ....163..144G}.  In the ``clump''
scenario, opaque dust clumps orbiting near the Keplerian corotation
radius eclipse the star
\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  In the
``prominence'' scenario, long-lived condensations of plasma are
trapped along the star’s magnetic field lines, also near corotation
\citep{2022MNRAS.514.5465W}.  And in a ``screen'' scenario, the inner
wall of a quiescent circumstellar disk blocks a portion of the stellar
surface to produce sudden dips whenever spots come into view
\citep{2019ApJ...876..127Z}.  In our view, the arguments seem best
established for the dust clump and prominence hypotheses
\citep{2023MNRAS.518.4734S,2022MNRAS.514.5465W}.  However, unambiguous
evidence has yet to be presented to demonstrate which, if any, of
these scenarios is correct.

It has not yet been possible to rule between the candidate mechanisms
CPVs have historically been both hard to discover and hard
to characterize.   Discoverability has been linked to rarity: 
CPVs comprise about 1\% of the youngest 1\% of M-dwarfs
\citep{2018AJ....155..196R}.  Out of the millions of stars monitored
by K2 and TESS, about 50 CPVs have been reported to date
\citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}.
The known CPVs are correspondingly faint; the initial K2 discoveries
\citep{2017AJ....153..152S} were M2-M6 dwarfs at distances
$\gtrsim$100\,pc, yielding optical brightnesses of $V$$\approx$15.5 to
$V$$>$20.  This renders time-series optical spectroscopy at high
resolution technically impossible, despite its potential utility in
ruling between the models.

One way to help rule between the mechanisms is to therefore find
bright and nearby CPVs, since these objects will be the most amenable
to detailed photometric and spectroscopic analyses.  To do this, in
this work, we use 120-second cadence data acquired by the Transiting
Exoplanet Survey Satellite between July~2018 and Sep~2022 (Sectors
1-55; Cycles 1-4).  We present our search methods in
Section~\ref{sec:methods}; and the properties of the resulting CPV
catalog in Section~\ref{sec:results}.  Open questions are discussed in
Section~\ref{sec:discussion}, and we conclude in
Section~\ref{sec:conclusion}.

\section{Methods}
\label{sec:methods}

%We will first describe our stars of interest
%(Section~\ref{subsec:selectionfn}), and then describe our methods for
%identifying which of those stars appear as CPVs
%(Section~\ref{subsec:discoverymethods}).

\subsection{Stellar selection function}
\label{subsec:selectionfn}

We chose to analyze only the ``short'' 120-second cadence data
acquired by TESS between July~2018 and Sep~2022 (Sectors 1-55).
Specifically, we used the 120-second cadence light curve products
produced by the mission's Science Processing and Operations Center at
NASA Ames \citep{2016SPIE.9913E..3EJ}.  While the TESS data products
also include full frame images with cadences of 200, 600, and 1800
seconds, we limited our scope in this work for the sake of simplicity
in data handling.  In exchange, we lose out in both completeness and
homogeneity of the selection function.  While TESS cumulatively
observed $\approx$90\% of the sky for at least one lunar month between
July~2018 and Sep~2022, the 120-second cadence data were acquired for
only a pre-selected set of stars over Sectors 1-26, and then a
guest-investigator driven set of stars over Sectors 27-55
\citep{2021PASP..133i5002F}.

To assess the completeness of the resulting 120-second cadence data that we
analyze, we cross-matched TIC8 \citep{2018AJ....156..102S} against the
Gaia DR2 point-source catalog \citep{2018A&A...616A...1G}.   We opted
for Gaia DR2 rather than DR3 because the base catalog for TIC8 was
Gaia DR2, which facilitated a one-to-one crossmatch using the Gaia source
identifiers.  This exercise showed that for $T$$<$16 M-dwarfs, the TESS
2-minute data are roughly 50\% complete at $\approx$50\,pc.  At
$<$20\,pc, $\gtrsim$80\% of the $T$$<$16 M-dwarfs have at least one
sector of short-cadence data; at $>$100\,pc, $\lesssim$10\% of such
M-dwarfs have at least one sector of short-cadence data.  Armed
with this understanding, we then used
our cross-match between Gaia DR2 and TIC8 to select our stars of
interest, which we defined as stars with 120-second cadence TESS light
curves that satisfied
\begin{align}
  T &< 16\\
  G_{\rm BP} - G_{\rm RP} &> 1.5 \\
  M_{\rm G} &> 4 \\
  d &< 150\,{\rm pc},
\end{align}
for $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ the Gaia $G$-band
absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
arcseconds, and a geometric distance $d$ defined by inverting the parallax
and ignoring any small zero-point corrections.
This selection function includes dwarf stars later than spectral types
of $\approx$K6V.  Hereafter, we will refer to this set of stars as the
target sample, and it includes \nstarssearched\ stars with (roughly)
M-dwarf spectral type, down to $T$$<$16 and out to $d$$<$150\,pc.

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{lc_mosaic_fav3.pdf}
		}

		\subfloat{
			\includegraphics[width=0.8\textwidth]{models.pdf}
		}
		%\subfloat{
		%	\includegraphics[width=0.8\textwidth]{flux_vs_time_xmin0000_xmax0010.pdf}
		%}
	\end{center}
	\caption{
		{\bf Complex periodic variables (CPVs)}:
		{\it Top:} Phase-folded TESS light curves of three CPVs.  Each is
		stacked over one month.  Gray are raw 2-minute data; black bins to
		300 points per cycle.  Periods in hours are in the bottom right of
		each panel.  In order left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Plausible cartoon models for the phenomenon.
		%{\it Bottom:} Flux {\it vs.}~time showing 10 cycles for each
		%object.  Raw 2-minute data are the gray background; the black line
		%is drawn between points binned to 1/100$^{\rm th}$ of a cycle.
	}
	\label{fig:f1}
%	\vspace{-0.5cm}
\end{figure*}

\subsection{CPV discovery}
\label{subsec:discoverymethods}

Previous methods that have yielded CPV discoveries include visually
examining stars known to be in young clusters
\citep{2017AJ....153..152S}, and automatically flagging rapid rotators
with a large number of strong Fourier harmonics
\citep{2019ApJ...876..127Z}.  The latter approach is followed by
visual vetting, since most rapid rotators with many Fourier harmonics
are false positives such as eclipsing binaries or multiple stars
blended into a single photometric aperture.  In this work, we adopted
the Fourier approach,
and also implemented a new search approach based on counting the
number of sharp local minima in phase-folded light curves.  We then
applied these two search techniques independently.

\subsubsection{Fourier analysis}
\label{subsec:fourier}
For the Fourier analysis, we followed
\citet{2019ApJ...876..127Z}.
{\bf todo for Rahul or Saul: explain the approach, in a few
paragraphs.  Was the SAP\_FLUX or PDCSAP used? etc. }

\subsubsection{Counting dips}
\label{subsec:counting}

The dip counting technique aims to count sharp local minima in
phase-folded light curves.  CPVs will preferably have at least three
such minima in order to be distinct from false positives such as
synchronized and spotted binaries (``RS CVn'' stars).

For our dip-counting pipeline, we began with the PDC\_SAP flux for
each sector, removed non-zero quality flags, and normalized the light
curve to one by dividing out its median value.  We then flattened the
light curve using a 5-day sliding median filter, as implemented in
\texttt{wotan} \citep{2019AJ....158..143H}.  On the resulting
cleaned and flattened light curve, we ran a periodogram search, opting
for the \citet{1978ApJ...224..953S} phase dispersion minimization
(PDM)
algorithm implemented in \texttt{astrobase}
\citep{2021zndo...1011188B} due to its shape agnosticism.  If a period
below 2 days was identified, we reran the periodogram at a
finer grid to improve the accuracy of the period determination.

Once a star's period $P$ was identified, we binned the phased light curve
to 100 points per cycle.  To separate ``sharp'' local minima from
smooth spot-induced variability, we then iteratively fit penalized
splines to the wrapped phase-folded light curve, excluding points more
than two standard deviations away from the local continuum
\citep{2019AJ....158..143H}.  The maximum number of equidistant spline
knots per cycle is the parameter in this framework that controlled the
meaning of ``sharp'' --- we allowed at most 10 such knots per cycle,
though for most stars fewer knots were preferred based on an
$\ell^2$-norm penalty.

We then identified local minima in the resulting residual light curve
using the SciPy \texttt{find\_peaks} utility (CITE), which is based on
comparing adjacent
values in an array.  For a peak to be flagged as significant, we
required it to have a width of at least $0.02\,P$, and a height of at
least twice the point-to-point RMS.  This latter quantity is defined as
the 68$^{\rm th}$ percentile of the distribution of the residuals from
the median value of $\delta f_i \equiv f_i - f_{i+1}$, where $f$ is
the flux and $i$ is an index over time.

To correctly identify local minima near the edges of the phased light
curve, which usually would cover phases $\phi \in [ 0,1 ]$, we in fact
performed the entire procedure over a phase-folded light curve
spanning $\phi \in [-1,2 ]$, by duplicating and concatenating
the ordinary phase-folded light curve.
The free parameters we adopted throughout this analysis procedure, for
instance the maximum number of spline knots per cycle, and how large
and wide of a local minimum to consider a ``true dip'', were chosen
during a testing period based on their ability to correctly re-identify 
a large fraction ($>$90\%) of known CPVs, while also being able to
consistently reject common false positives such as rapidly rotating
spot-induced variability and typical eclipsing binaries.

Overall, for a star to clear this process and to proceed to manual
examination, we required that it have a peak PDM period below two
days, and that it exhibited at least three sharp local minima (as
algorithmically reported) in at least one observed TESS sector.

\subsection{Manual vetting}

We visually assessed whether the objects found using the Fourier
(Section~\ref{subsec:fourier}) and dip-counting
(Section~\ref{subsec:counting}) techniques were consistent with 
expectations for CPVs by assembling 
the data shown in Appendix~\ref{app:vetting}.
The false-positive rates from our dip-counting approach, as-implemented,
%TODO: left off here

While
the highest S/N cases were generally found by both the Fourier and dip-counting
techniques, we
generally found that

\section{Results}
\label{sec:results}

\begin{figure*}[!tp]
	\begin{center}
    \centering
    \includegraphics[width=\textwidth]{lc_mosaic_dlt150_good_all.pdf}
		\caption{
			{\bf CPVs from a search of the TESS 2-minute data at
      $d$$<$150\,pc, acquired between July~2018 and Sep~2022.}
      Phased TESS light curves over 1 month are shown for 40 CPVs;
      they include the brightest and closest examples of CPVs known
      ($V$=14; $J$=9.5; $d$=25\,pc).  Gray are raw 2-minute data;
      black bins to 300 points per cycle.  Periods in hours are listed
      in the lower right corners of each panel.
      The TIC identification numbers and sectors are listed in
      Table~\ref{tab:thetable}.
		}
		\label{fig:revolution}
%		\vspace{-0.8cm}
	\end{center}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
			\centering
			\includegraphics[width=0.9\textwidth]{lc_mosaic_dlt150_good_changers.pdf}
		\vspace{-0.2cm}
		\caption{
		{\bf Evolution of CPVs}: ``Before and
      after'' for six CPVs from Figure~\ref{fig:revolution}.  Panels
      in the top two rows are separated by two years
      ($\approx$$10^3$ cycles); each panel shows one month.
      Periods are listed in hours. 
      {\bf todo: make these for everything.}
%			\vspace{-0.8cm}
		}
		\label{fig:evoln}
	\end{center}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
    \centering
    \includegraphics[width=0.9\textwidth]{TIC_402980664_P18.5604_2min_phase_timegroups_mosaic.pdf}
		\vspace{-0.45cm}
		\caption{
			{\it Bottom:}
      Evolution of LP 12-502 ($P$=18.6\,h) at fixed period over three
      years; small text denotes cycle number.  The TESS pointing law
      dictates time gaps; larger gaps tend to yield larger shape
      changes.
      The dips usually evolve over tens to hundreds of cycles.
      However cycles 1233-1264 show a dip that ``switched'' from a depth
      and duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than
      one cycle.
			\vspace{-0.8cm}
		}
		\label{fig:lp}
	\end{center}
\end{figure*}

\section{Discussion}
\label{sec:discussion}

%A number of auxiliary
%questions follow.  After correcting for line-of-sight inclination, are
%most young M-dwarfs CPVs?  What observational signatures distinguish
%the proposed models (Figure~\ref{fig:f1}, bottom row)?  What
%organizational regularities characterize the CPV as a class of
%variable star?  What sets the extremes of the CPV population, such as
%the longest rotation periods, hottest stellar temperatures, and oldest
%stellar ages?  And finally, what connections, if any, do CPVs have to
%topics such as stellar evolution, M-dwarf magnetic fields, debris
%disks, and close-in exoplanets?

{\it Why would the prominence scenario tend toward corotation?}
This is analogous to quiescent
prominences on the Sun \citep{1967SoPh....2...39K}.

\section{Conclusions}
\label{sec:conclusion}

\acknowledgments
This work was supported by the 
Heising-Simons 51~Pegasi~b Fellowship (LGB)

{\bf author contribution statement goes here}
L.G.B.~and R.~J. conceived the project and executed the
dip-based and Fourier-based searches, respectively.
They both drafted the initial manuscript.
S.~R. vetted the results from the Fourier search.
rotation- and lithium-based age analyses, and drafted the manuscript.
L.A.H.~contributed to project execution.
All authors assisted in manuscript revision.

\clearpage
\bibliographystyle{yahapj}                            
\bibliography{bibliography}

\appendix
\section{Validation plots}
\label{app:vetting}

Figure~\ref{fig:vet} shows the type of plot used to visually assess
whether a source was likely to be a CPV, eclipsing binary, or simply a
rapidly rotating star.

\begin{figure*}[!t]
	\begin{center}
    \centering
    \includegraphics[width=\textwidth]{402980664_S0019_120sec_cpvvetter.pdf}
		\vspace{-0.45cm}
		\caption{
      Validation plots used to label CPVs (the complete figure
      set of \ncpvsfound\ images is available online).
      Panels are as follows.
      {\it a)}: Phase-folded light curve; gray points are raw 2-minute
      data and black points are binned to 200 points per cycle.
      {\it b)}: Phase-dispersion minimization (PDM) periodogram.
      {\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
      circles displayed for scale.
      {\it d)}: Cleaned light curve, binned to 20-minute cadence.
      {\it e)}: Phase-folded light curve, binned to 100 points per
      cycle.  The gray line denotes the automated spline-fit to the
      wrapped phase-folded light curve, and small gray triangles
      denote automatically identified local minima; 
      one of the four sharp dips for this star was not identified!
      {\it f)}: Phase-folded light curve at twice the peak period.
      {\it g)}: Phase-folded light curve at half the peak period.
      {\it h)}: Phase-folded time-series within the ``background''
      aperture defined in the SPOC light curves.
      {\it i)}: Phase-folded flux-weighted centroid in the column
      direction.
      {\it j)}: Phase-folded flux-weighted centroid in the row
      direction.
      {\it k)}: Gaia DR2 color--absolute magnitude diagram.     
      {\it l)}: Information from Gaia DR2, TIC8, and the automated
      dip-counting search pipeline.  ``Neighbors'', abbreviated
      ``nbhr'', are listed within apparent distances of 2 TESS pixels
      if $\Delta T$$<$2.5.
      }
		\label{fig:vet}
	\end{center}
\end{figure*}

\clearpage
\listofchanges

\end{document}

### 2023-06-12 drivers/find_CPVs.py
minor driver update

@@ -373,7 +373,7 @@ def main():
         'rahul_20230501'
     ]
 
-    forcepdf = False # true only for specific (N<~100 !) samples
+    forcepdf = True # FIXME true only for specific (N<~100 !) samples
 
     for sample_id in sample_ids:
         ticids = get_ticids(sample_id)

### 2023-06-12 paper/ms.tex
update ms

@@
 %%%%%%%%
-% CPVS %
+% CQVS %
 %%%%%%%%
+% dip-counting pipeline
+\newcommand{\nuniqdipflagged}{{368}} % up-to-date; get_lgb_list_count.py
 \newcommand{\ncpvsfound}{{48}}
@@
 
-\title{Bright and Nearby Complex Periodic Variables from Four Years of TESS}
+\title{Complex Quasiperiodic Variables from Four Years of TESS}
 
@@
 \accepted{---}
-\shorttitle{Cycle 1-4 CPVs}
+\shorttitle{Cycle 1-4 CQVs}
 
@@
 
+% 250 word max!
 \begin{abstract}
-  Complex periodic variables (CPVs) are pre-main-sequence M-dwarfs
-  with periodic optical modulation that includes both sharp and broad
-  troughs.
-  The troughs are usually superposed on smooth, spot-like modulation.
-  Based on a lack of observed infrared excesses, these objects do not
-  have primordial gas-rich disks, or even particularly massive debris disks.
-  Nonetheless, the most plausible explanations for their optical
-  variability invoke long-lived material that orbits at the corotation
-  radii, for instance transiting dust clumps or stellar prominences.
-  Here, we report new CPVs discovered in the 120-second cadence TESS data
-  collected between July~2018 and Sep~2022 (Sectors 1-55).
-  Our search used two methods, the first based on counting dips in
-  phase-folded light curves, and the second based on counting peaks in
-  the Fourier domain.
-  From our analysis of \nstarssearched\ M-dwarfs with $T$$<$16 and
-  $d$$<$150\,pc, we find \ncpvsfound\ gold-standard CPVs.
+  Complex quasiperiodic variables (CQVs) are pre-main-sequence M-dwarfs
+  with almost-periodic optical modulation that includes both sharp and broad
+  troughs.  The troughs are usually superposed on smooth, spot-like
+  modulation.  Based on a lack of observed infrared excesses, these
+  objects do not have primordial gas-rich disks.  Nonetheless, the
+  currently preferred explanations for their optical variability invoke
+  long-lived material that orbits at the corotation radii, for
+  instance transiting dust clumps or stellar prominences.  Here, we
+  report new CQVs discovered in the 120-second cadence TESS data
+  collected between July~2018 and Sep~2022 (Sectors 1-55).  Our search
+  used two methods, the first based on counting dips in phase-folded
+  light curves, and the second based on counting peaks in the Fourier
+  domain.  From our analysis of \nstarssearched\ M-dwarfs with
+  $T$$<$16 and $d$$<$150\,pc, we find \ncpvsfound\ gold-standard CQVs.
   Most of these discoveries are new, and they include the brightest
   ($T$$\approx$10) and closest ($d$$\approx$20\,pc) examples of this
-  class of variable star known.
-  A few objects are ``outliers among outliers''; for
-  instance LP 12-502 shows up to eight local minima per cycle, exhibited
-  sudden shape ``switches'' over less than one cycle, yet maintained
-  a near-constant cycle duration over more than one thousand cycles.
-  The general cause of the optical variability for these objects remains
-  enigmatic.  However our sample is a step toward the spectroscopic and
-  demographic studies that may ultimately resolve the mystery of what
-  physically explains these objects.
-  Connections to the broader context of star, disk, and
+  class of variable star known.  A few objects are ``outliers among
+  outliers''; for instance LP 12-502 shows between four and eight
+  local minima per cycle, distributed over a ``dip complex'' with
+  fixed total duration over more than one thousand cycles, but that
+  has a detailed shape that at times showed significant changes over only one
+  cycle.  More generally, we find that exactly zero of the CQVs
+  maintain an identical light curve morphology over timescales of more
+  than a few hundred cycles.  While the physical explanation behind
+  these objects remains enigmatic, our sample is a step toward the
+  spectroscopic and demographic studies that may help clarify their
+  origin.  Connections to star, disk, and
   exoplanet evolution are emphasized.
@@
 surfaces such as starspots and faculae
-\citep[e.g.][]{2021isma.book.....B}, occultations by gas-rich
-circumstellar disks \citep[e.g.][]{2017MNRAS.470..202B}, and, in
+\citep{2021isma.book.....B}, occultations by gas-rich
+circumstellar disks \citep{2017MNRAS.470..202B}, and, in
 geometrically favorable circumstances, eclipses by stars and planets.
@@
 Data from K2 and TESS have yielded a new class of variable star whose
-root cause is not yet qualitatively understood: complex periodic
-variables (CPVs).  These objects are identified phenomenologically
-using their optical light curves, which show periodic sharp and
-sometimes broad troughs, often superposed on smooth spot-like
-modulation.  Some of the objects show up to eight local minima (dips)
-per cycle; sharp peaks are also common.  Most of these variable stars
-turn out to be pre-main-sequence M-dwarfs without near-infrared
-excesses, with ages of $\approx$5-150 million years (Myr), and
-rotation periods of at most two days; they are observed to be
-$\approx$1\% of M-dwarfs younger than 100 Myr
+root cause is not yet qualitatively understood: complex quasiperiodic
+variables (CQVs).  These objects are identified phenomenologically
+using their optical light curves, which show quasiperiodic troughs
+that can be either sharp or broad, often superposed on smooth
+spot-like modulation.  Some of the objects show up to eight local
+minima (dips) per cycle; sharp peaks are also common.  Most of these
+variable stars turn out to be pre-main-sequence M-dwarfs without
+near-infrared excesses, with ages of $\approx$5-150 million years
+(Myr), and rotation periods of at most two days; they are observed to
+be $\approx$1\% of M-dwarfs younger than 100 Myr
 \citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G}.
@@
 gradually, over tens to hundreds of cycles
-\citep[e.g.][]{2017AJ....153..152S,2020AJ....160...86B,2023ApJ...945..114P}.
+\citep[e.g.][]{2017AJ....153..152S,2023ApJ...945..114P}.
 
-The issue of what exactly causes the variability that defines the CPVs
+The issue of what exactly causes the variability that defines the CQVs
 has yet to be resolved.  There are a few competing explanations.  All
@@
 It has not yet been possible to rule between the candidate mechanisms
-CPVs have historically been both hard to discover and hard
+CQVs have historically been both hard to discover and hard
 to characterize.   Discoverability has been linked to rarity: 
-CPVs comprise about 1\% of the youngest 1\% of M-dwarfs
+CQVs comprise about 1\% of the youngest 1\% of M-dwarfs
 \citep{2018AJ....155..196R}.  Out of the millions of stars monitored
-by K2 and TESS, about 50 CPVs have been reported to date
+by K2 and TESS, about 50 CQVs have been reported to date
 \citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}.
-The known CPVs are correspondingly faint; the initial K2 discoveries
+The known CQVs are correspondingly faint; the initial K2 discoveries
 \citep{2017AJ....153..152S} were M2-M6 dwarfs at distances
@@
 One way to help rule between the mechanisms is to therefore find
-bright and nearby CPVs, since these objects will be the most amenable
+bright and nearby CQVs, since these objects will be the most amenable
 to detailed photometric and spectroscopic analyses.  To do this, in
-this work, we use 120-second cadence data acquired by the Transiting
-Exoplanet Survey Satellite between July~2018 and Sep~2022 (Sectors
+this work, we use 120-second cadence data acquired by TESS between July~2018 and Sep~2022 (Sectors
 1-55; Cycles 1-4).  We present our search methods in
-Section~\ref{sec:methods}; and the properties of the resulting CPV
+Section~\ref{sec:methods}; and the properties of the resulting CQV
 catalog in Section~\ref{sec:results}.  Open questions are discussed in
@@
 
+A point on nomenclature.  CQVs have been called ``transient and
+persistent flux dips'', ``scallop shells'', ``batwings'',
+\citep{2017AJ....153..152S,2018AJ....155...63S} ``complex rotators'',
+\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
+and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  The
+CQVs are not ``dippers'', which are classical T Tauri stars with
+infrared excesses whose optical variability is linked to obscuring
+inner disk structures and accretion hot spots (CITE Cody2014,
+ConnorRobinson2021).  At the risk of introducing yet another standard,\footnote{\url{https://xkcd.com/927/}}
+we prefer to make the
+technical distinction that the CQVs are, over timescales of more than
+a few cycles, not exactly periodic.  Their shapes evolve, usually over
+some decoherence timescale, similar to variability induced by surface
+inhomogeneities such as starspots.  While the three-type
+classification scheme proposed by \citet{2017AJ....153..152S} may
+indeed provide some helpful visual distinctions among the CQV class,
+it seems likely (we hope!) that they are all explained by a single
+underlying phenomenon, and so we opt to refer to them by a single
+empirically descriptive name.
+
 \section{Methods}
 \label{sec:methods}
-
-%We will first describe our stars of interest
-%(Section~\ref{subsec:selectionfn}), and then describe our methods for
-%identifying which of those stars appear as CPVs
-%(Section~\ref{subsec:discoverymethods}).
 
@@
 
+		\vspace{-0.15cm}
 		\subfloat{
@@
 		}
-		%\subfloat{
-		%	\includegraphics[width=0.8\textwidth]{flux_vs_time_xmin0000_xmax0010.pdf}
-		%}
 	\end{center}
 	\caption{
-		{\bf Complex periodic variables (CPVs)}:
-		{\it Top:} Phase-folded TESS light curves of three CPVs.  Each is
+		{\bf Complex quasiperiodic variables (CQVs)}:
+		{\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
 		stacked over one month.  Gray are raw 2-minute data; black bins to
@@
 		{\it Bottom:} Plausible cartoon models for the phenomenon.
-		%{\it Bottom:} Flux {\it vs.}~time showing 10 cycles for each
-		%object.  Raw 2-minute data are the gray background; the black line
-		%is drawn between points binned to 1/100$^{\rm th}$ of a cycle.
+		The ``clump'' or ``prominence'' scenarios seem most plausible,
+		given the stability of the phenomenon and the lack of observed infrared excesses.
 	}
 	\label{fig:f1}
-%	\vspace{-0.5cm}
 \end{figure*}
 
-\subsection{CPV discovery}
+\subsection{CQV discovery}
 \label{subsec:discoverymethods}
 
-Previous methods that have yielded CPV discoveries include visually
+Previous methods that have yielded CQV discoveries include visually
 examining stars known to be in young clusters
@@
 blended into a single photometric aperture.  In this work, we adopted
-the Fourier approach,
-and also implemented a new search approach based on counting the
-number of sharp local minima in phase-folded light curves.  We then
-applied these two search techniques independently.
+the Fourier approach, and also implemented a new search approach based
+on counting the number of sharp local minima in phase-folded light
+curves.  We then applied these two search techniques independently.
 
@@
 The dip counting technique aims to count sharp local minima in
-phase-folded light curves.  CPVs will preferably have at least three
+phase-folded light curves.  CQVs will preferably have at least three
 such minima in order to be distinct from false positives such as
@@
 light curve using a 5-day sliding median filter, as implemented in
-\texttt{wotan} \citep{2019AJ....158..143H}.  On the resulting
-cleaned and flattened light curve, we ran a periodogram search, opting
-for the \citet{1978ApJ...224..953S} phase dispersion minimization
-(PDM)
+\texttt{wotan} \citep{2019AJ....158..143H}.  On the resulting cleaned
+and flattened light curve, we ran a periodogram search, opting for the
+\citet{1978ApJ...224..953S} phase dispersion minimization (PDM)
 algorithm implemented in \texttt{astrobase}
 \citep{2021zndo...1011188B} due to its shape agnosticism.  If a period
-below 2 days was identified, we reran the periodogram at a
-finer grid to improve the accuracy of the period determination.
+below 2 days was identified, we reran the periodogram at a finer grid
+to improve the accuracy of the period determination.
 
-Once a star's period $P$ was identified, we binned the phased light curve
-to 100 points per cycle.  To separate ``sharp'' local minima from
-smooth spot-induced variability, we then iteratively fit penalized
-splines to the wrapped phase-folded light curve, excluding points more
-than two standard deviations away from the local continuum
+Once a star's period $P$ was identified, we binned the phased light
+curve to 100 points per cycle.  To separate ``sharp'' local minima
+from smooth spot-induced variability, we then iteratively fit
+penalized splines to the wrapped phase-folded light curve, excluding
+points more than two standard deviations away from the local continuum
 \citep{2019AJ....158..143H}.  The maximum number of equidistant spline
@@
 using the SciPy \texttt{find\_peaks} utility (CITE), which is based on
-comparing adjacent
-values in an array.  For a peak to be flagged as significant, we
-required it to have a width of at least $0.02\,P$, and a height of at
-least twice the point-to-point RMS.  This latter quantity is defined as
-the 68$^{\rm th}$ percentile of the distribution of the residuals from
-the median value of $\delta f_i \equiv f_i - f_{i+1}$, where $f$ is
-the flux and $i$ is an index over time.
+comparing adjacent values in an array.  For a peak to be flagged as
+significant, we required it to have a width of at least $0.02\,P$, and
+a height of at least twice the point-to-point RMS.  This latter
+quantity is defined as the 68$^{\rm th}$ percentile of the
+distribution of the residuals from the median value of $\delta f_i
+\equiv f_i - f_{i+1}$, where $f$ is the flux and $i$ is an index over
+time.
 
@@
 performed the entire procedure over a phase-folded light curve
-spanning $\phi \in [-1,2 ]$, by duplicating and concatenating
-the ordinary phase-folded light curve.
-The free parameters we adopted throughout this analysis procedure, for
-instance the maximum number of spline knots per cycle, and how large
-and wide of a local minimum to consider a ``true dip'', were chosen
-during a testing period based on their ability to correctly re-identify 
-a large fraction ($>$90\%) of known CPVs, while also being able to
-consistently reject common false positives such as rapidly rotating
-spot-induced variability and typical eclipsing binaries.
+spanning $\phi \in [-1,2 ]$, by duplicating and concatenating the
+ordinary phase-folded light curve.  The free parameters we adopted
+throughout this analysis procedure, for instance the maximum number of
+spline knots per cycle, and how large and wide of a local minimum to
+consider a ``true dip'', were chosen during a testing period based on
+their ability to correctly re-identify a large fraction ($>$90\%) of
+known CQVs, while also being able to consistently reject common false
+positives such as rapidly rotating spot-induced variability and
+typical eclipsing binaries.
 
@@
 
-\subsection{Manual vetting}
+\subsubsection{Manual vetting}
 
@@
 (Section~\ref{subsec:counting}) techniques were consistent with
-expectations for CPVs by assembling 
-the data shown in Appendix~\ref{app:vetting}.
-The false-positive rates from our dip-counting approach, as-implemented,
-%TODO: left off here
+expectations for CQVs by assembling the data shown in
+Appendix~\ref{app:vetting}.
 
-While
-the highest S/N cases were generally found by both the Fourier and dip-counting
-techniques, we
-generally found that
+Broadly speaking, the most common false positives for both the Fourier
+and dip-counting techniques were eclipsing binaries, spot-induced
+variability from rapid rotators, and blended combinations thereof.
+Rarer false positives included disk-induced variability, for instance
+induced by quasiperiodic dippers (CITE).  Typical false postive rates
+from our dip-counting pipeline were 5:1, with 368 unique stars
+flagged, and about 20\% being labelled either ``good'' or ``possible''
+CQVs; for the Fourier pipeline, {\bf the rate was X:Y, with ZZZZ
+unique stars flagged, and NN\% being labelled ``good'' or ``possible''
+CQVs}.
+
+\subsection{Stellar properties}
+
+\paragraph{Ages}
+%TODO
+
+\paragraph{Effective temperatures, radii, and masses}
+%TODO
 
@@
 
-\begin{figure*}[!tp]
+\subsection{CQV catalog}
+
+\begin{figure*}[!t]
 	\begin{center}
@@
 		\caption{
-			{\bf CPVs from a search of the TESS 2-minute data at
+			{\bf CQVs from a search of the TESS 2-minute data at
       $d$$<$150\,pc, acquired between July~2018 and Sep~2022.}
-      Phased TESS light curves over 1 month are shown for 40 CPVs;
-      they include the brightest and closest examples of CPVs known
+      Phased TESS light curves over 1 month are shown for 40 CQVs;
+      they include the brightest and closest examples of CQVs known
       ($V$=14; $J$=9.5; $d$=25\,pc).  Gray are raw 2-minute data;
@@
       in the lower right corners of each panel.
-      The TIC identification numbers and sectors are listed in
-      Table~\ref{tab:thetable}.
+      {\bf todo:  add TIC IDs and sector numbers}.
+      % TODO: sort by brightness maybe?
+      % TODO: sort by period?
 		}
-		\label{fig:revolution}
-%		\vspace{-0.8cm}
+		\label{fig:singlemosaic}
 	\end{center}
 \end{figure*}
+
+Table~\ref{tab:thetable} lists the \ncpvsfound\ CQVs identified by
+our search, and some of their important properties.
+The mosaic in Figure~\ref{fig:singlemosaic} shows the 40 brightest
+objects.
+
+For the TESS sectors in which these objects were identified, they show
+anywhere from one to eight local minima per cycle.
+Some stars show relatively ordinary modulation during one continuous
+portion of the phased light curve, and highly structured modulation in
+the remainder of the cycle (e.g. TIC~206544316, TIC~224283342,
+TIC~402980664).
+Others show structured modulation over the entire span of a cycle
+(e.g. TIC~2234692, TIC~401789285, TIC~425933644, TIC~142173958).
+Others still show some mix between these two modes,
+with one or more small dips, superposed over one or more large dips.
+Frankly, staring at them for long enough,
+it becomes possible to identify any one of them
+
+\subsection{CQV evolution}
+
+\paragraph{None of them are strictly periodic}
+
+A periodic signal does not modulate.
 
@@
 		\caption{
-		{\bf Evolution of CPVs}: ``Before and
-      after'' for six CPVs from Figure~\ref{fig:revolution}.  Panels
+		{\bf Evolution of CQVs}: ``Before and
+      after'' for six CQVs from Figure~\ref{fig:revolution}.  Panels
       in the top two rows are separated by two years
@@
 
+{\it Each CQV a snowflake}
+One intriguing aspect of staring at Figure~\ref{fig:singlemosaic}
+is that, even after rescaling the amplitudes, no two CQVs
+exhibit exactly identical light curve morphology.
+There are of course similarities.
+
+TIC 272248916 and TIC 442571495
+
 %A number of auxiliary
 %questions follow.  After correcting for line-of-sight inclination, are
-%most young M-dwarfs CPVs?  What observational signatures distinguish
+%most young M-dwarfs CQVs?  What observational signatures distinguish
 %the proposed models (Figure~\ref{fig:f1}, bottom row)?  What
-%organizational regularities characterize the CPV as a class of
-%variable star?  What sets the extremes of the CPV population, such as
+%organizational regularities characterize the CQV as a class of
+%variable star?  What sets the extremes of the CQV population, such as
 %the longest rotation periods, hottest stellar temperatures, and oldest
-%stellar ages?  And finally, what connections, if any, do CPVs have to
+%stellar ages?  And finally, what connections, if any, do CQVs have to
 %topics such as stellar evolution, M-dwarf magnetic fields, debris
@@
 Figure~\ref{fig:vet} shows the type of plot used to visually assess
-whether a source was likely to be a CPV, eclipsing binary, or simply a
+whether a source was likely to be a CQV, eclipsing binary, or simply a
 rapidly rotating star.
@@
 		\caption{
-      Validation plots used to label CPVs (the complete figure
+      Validation plots used to label CQVs (the complete figure
       set of \ncpvsfound\ images is available online).
@@
 
+\section{No additional power at 20~second cadence}
+
+Going from K2 to TESS, an important discovery was that the CQV shapes
+can significantly evolve, since the stars can vary over timescales of just a few minutes.
+We observed a set of CQVs between 2020 and 2021 using the TESS 20-second
+cadence mode (TESS DDT029).
+{\bf todo: list the stars.  todo: examine the 2min vs 20sec periodograms, and summarize in a few
+sentences whether any difference is there.}
+
 \clearpage

### 2023-06-13 paper/ms.tex
update ms

@@
 \accepted{---}
-\shorttitle{Cycle 1-4 CQVs}
+\shorttitle{Four Years of CQVs}
 
@@
 \begin{abstract}
-  Complex quasiperiodic variables (CQVs) are pre-main-sequence M-dwarfs
-  with almost-periodic optical modulation that includes both sharp and broad
-  troughs.  The troughs are usually superposed on smooth, spot-like
-  modulation.  Based on a lack of observed infrared excesses, these
-  objects do not have primordial gas-rich disks.  Nonetheless, the
-  currently preferred explanations for their optical variability invoke
-  long-lived material that orbits at the corotation radii, for
-  instance transiting dust clumps or stellar prominences.  Here, we
-  report new CQVs discovered in the 120-second cadence TESS data
-  collected between July~2018 and Sep~2022 (Sectors 1-55).  Our search
-  used two methods, the first based on counting dips in phase-folded
-  light curves, and the second based on counting peaks in the Fourier
-  domain.  From our analysis of \nstarssearched\ M-dwarfs with
-  $T$$<$16 and $d$$<$150\,pc, we find \ncpvsfound\ gold-standard CQVs.
-  Most of these discoveries are new, and they include the brightest
-  ($T$$\approx$10) and closest ($d$$\approx$20\,pc) examples of this
-  class of variable star known.  A few objects are ``outliers among
-  outliers''; for instance LP 12-502 shows between four and eight
-  local minima per cycle, distributed over a ``dip complex'' with
-  fixed total duration over more than one thousand cycles, but that
-  has a detailed shape that at times showed significant changes over only one
-  cycle.  More generally, we find that exactly zero of the CQVs
-  maintain an identical light curve morphology over timescales of more
-  than a few hundred cycles.  While the physical explanation behind
-  these objects remains enigmatic, our sample is a step toward the
-  spectroscopic and demographic studies that may help clarify their
-  origin.  Connections to star, disk, and
-  exoplanet evolution are emphasized.
+  Complex quasiperiodic variables (CQVs) are pre-main-sequence
+  M-dwarfs with almost-periodic optical modulation that includes both
+  sharp and broad troughs.  The troughs are usually superposed over
+  smooth, spot-like modulation.  Based on a lack of observed infrared
+  excesses, these objects do not have primordial gas-rich disks.
+  Nonetheless, the currently preferred explanations for their optical
+  variability invoke long-lived material in orbit at the corotation
+  radius, for instance transiting dust clumps or stellar prominences.
+  Here, we report new CQVs discovered in TESS data collected between
+  July~2018 and Sep~2022.  Our search used two methods, the first
+  based on counting dips in phase-folded light curves, and the second
+  based on counting peaks in the Fourier domain.  From our analysis of
+  \nstarssearched\ M-dwarfs with $T$$<$16 and $d$$<$150\,pc, we find
+  \ncpvsfound\ gold-standard CQVs.  Most of these discoveries are new,
+  and they include the brightest ($T$$\approx$10) and closest
+  ($d$$\approx$20\,pc) examples of this class of object known.  A few
+  objects are ``outliers among outliers''; for instance LP 12-502
+  shows four to eight local minima per cycle, distributed over a ``dip
+  complex'' with a total duration that is fixed over more than one
+  thousand cycles, but with a detailed shape that exhibited changes
+  over less than one cycle.  More generally, we find that none of the
+  CQVs maintain a fixed light curve shape over timescales of more than
+  a few hundred cycles -- hence, {\it quasi}periodic.  Although the
+  physical explanation behind these objects remains enigmatic, our
+  sample may help clarify their origin.  Connections to star, disk,
+  and exoplanet evolution are emphasized.
 \end{abstract}
@@
 sources of optical variability include inhomogeneities on stellar
-surfaces such as starspots and faculae
-\citep{2021isma.book.....B}, occultations by gas-rich
-circumstellar disks \citep{2017MNRAS.470..202B}, and, in
-geometrically favorable circumstances, eclipses by stars and planets.
+surfaces such as starspots and faculae \citep{2021isma.book.....B},
+occultations by gas-rich circumstellar disks
+\citep{2017MNRAS.470..202B}, and, in geometrically favorable
+circumstances, eclipses by stars and planets.
 
@@
 gradually, over tens to hundreds of cycles
-\citep[e.g.][]{2017AJ....153..152S,2023ApJ...945..114P}.
+\citep[e.g.][]{2017AJ....153..152S,2022ApJ...925...75P,2023ApJ...945..114P}.
 
@@
 It has not yet been possible to rule between the candidate mechanisms
-CQVs have historically been both hard to discover and hard
-to characterize.   Discoverability has been linked to rarity: 
-CQVs comprise about 1\% of the youngest 1\% of M-dwarfs
+CQVs have historically been both hard to discover and hard to
+characterize.   Discoverability has been linked to rarity: CQVs
+comprise about 1\% of the youngest 1\% of M-dwarfs
 \citep{2018AJ....155..196R}.  Out of the millions of stars monitored
@@
 to detailed photometric and spectroscopic analyses.  To do this, in
-this work, we use 120-second cadence data acquired by TESS between July~2018 and Sep~2022 (Sectors
-1-55; Cycles 1-4).  We present our search methods in
-Section~\ref{sec:methods}; and the properties of the resulting CQV
-catalog in Section~\ref{sec:results}.  Open questions are discussed in
-Section~\ref{sec:discussion}, and we conclude in
+this work, we use 120-second cadence data acquired by TESS between
+July~2018 and Sep~2022 (Sectors 1-55; Cycles 1-4).  We present our
+search methods in Section~\ref{sec:methods}; and the properties of the
+resulting CQV catalog in Section~\ref{sec:results}.  Open questions
+are discussed in Section~\ref{sec:discussion}, and we conclude in
 Section~\ref{sec:conclusion}.
@@
 infrared excesses whose optical variability is linked to obscuring
-inner disk structures and accretion hot spots (CITE Cody2014,
-ConnorRobinson2021).  At the risk of introducing yet another standard,\footnote{\url{https://xkcd.com/927/}}
-we prefer to make the
+inner disk structures and accretion hot spots
+\citep{2014AJ....147...82C,2021ApJ...908...16R}.  At the risk of
+introducing yet another
+standard,\footnote{\url{https://xkcd.com/927/}} we prefer to make the
 technical distinction that the CQVs are, over timescales of more than
@@
 
-To assess the completeness of the resulting 120-second cadence data that we
-analyze, we cross-matched TIC8 \citep{2018AJ....156..102S} against the
-Gaia DR2 point-source catalog \citep{2018A&A...616A...1G}.   We opted
-for Gaia DR2 rather than DR3 because the base catalog for TIC8 was
-Gaia DR2, which facilitated a one-to-one crossmatch using the Gaia source
-identifiers.  This exercise showed that for $T$$<$16 M-dwarfs, the TESS
-2-minute data are roughly 50\% complete at $\approx$50\,pc.  At
-$<$20\,pc, $\gtrsim$80\% of the $T$$<$16 M-dwarfs have at least one
-sector of short-cadence data; at $>$100\,pc, $\lesssim$10\% of such
-M-dwarfs have at least one sector of short-cadence data.  Armed
-with this understanding, we then used
-our cross-match between Gaia DR2 and TIC8 to select our stars of
-interest, which we defined as stars with 120-second cadence TESS light
-curves that satisfied
+To assess the completeness of the resulting 120-second cadence data
+that we analyze, we cross-matched TIC8 \citep{2018AJ....156..102S}
+against the Gaia DR2 point-source catalog \citep{2018A&A...616A...1G}.
+We opted for Gaia DR2 rather than DR3 because the base catalog for
+TIC8 was Gaia DR2, which facilitated a one-to-one crossmatch using the
+Gaia source identifiers.  This exercise showed that for $T$$<$16
+M-dwarfs, the TESS 2-minute data are roughly 50\% complete at
+$\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\% of the $T$$<$16 M-dwarfs
+have at least one sector of short-cadence data; at $>$100\,pc,
+$\lesssim$10\% of such M-dwarfs have at least one sector of
+short-cadence data.  Armed with this understanding, we then used our
+cross-match between Gaia DR2 and TIC8 to select our stars of interest,
+which we defined as stars with 120-second cadence TESS light curves
+that satisfied
 \begin{align}
@@
 absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
-arcseconds, and a geometric distance $d$ defined by inverting the parallax
-and ignoring any small zero-point corrections.
-This selection function includes dwarf stars later than spectral types
-of $\approx$K6V.  Hereafter, we will refer to this set of stars as the
-target sample, and it includes \nstarssearched\ stars with (roughly)
-M-dwarf spectral type, down to $T$$<$16 and out to $d$$<$150\,pc.
+arcseconds, and a geometric distance $d$ defined by inverting the
+parallax and ignoring any zero-point correction.  This selection
+function includes dwarf stars later than spectral types of
+$\approx$K6V.  This target sample includes \nstarssearched\ stars with
+approximately M-dwarf spectral type, down to $T$$<$16 and out to
+$d$$<$150\,pc.
 
@@
 
-		\vspace{-0.15cm}
+		\vspace{-0.4cm}
 		\subfloat{
@@
     425933644 (Sector~28).
-		{\it Bottom:} Plausible cartoon models for the phenomenon.
-		The ``clump'' or ``prominence'' scenarios seem most plausible,
-		given the stability of the phenomenon and the lack of observed infrared excesses.
+    {\it Bottom:} Plausible cartoon models for the phenomenon.  The
+    ``clump'' or ``prominence'' scenarios seem most plausible, given
+    the stability of the phenomenon and the lack of observed infrared
+    excesses.
 	}
@@
 with a large number of strong Fourier harmonics
-\citep{2019ApJ...876..127Z}.  The latter approach is followed by
-visual vetting, since most rapid rotators with many Fourier harmonics
-are false positives such as eclipsing binaries or multiple stars
-blended into a single photometric aperture.  In this work, we adopted
-the Fourier approach, and also implemented a new search approach based
-on counting the number of sharp local minima in phase-folded light
-curves.  We then applied these two search techniques independently.
+\citep{2019ApJ...876..127Z}.  The latter approach requires visual
+vetting, since most rapid rotators with many Fourier harmonics are
+false positives such as eclipsing binaries or multiple stars blended
+into a single photometric aperture.  In this work, we implemented a
+new search approach based on counting the number of sharp local minima
+in phase-folded light curves, while also using the previously tested
+Fourier approach.  We applied these two search techniques
+independently.
 
@@
 We then identified local minima in the resulting residual light curve
-using the SciPy \texttt{find\_peaks} utility (CITE), which is based on
-comparing adjacent values in an array.  For a peak to be flagged as
-significant, we required it to have a width of at least $0.02\,P$, and
-a height of at least twice the point-to-point RMS.  This latter
-quantity is defined as the 68$^{\rm th}$ percentile of the
-distribution of the residuals from the median value of $\delta f_i
-\equiv f_i - f_{i+1}$, where $f$ is the flux and $i$ is an index over
-time.
+using the SciPy \texttt{find\_peaks} utility
+\citep{2020NatMe..17..261V}, which is based on comparing adjacent
+values in an array.  For a peak to be flagged as significant, we
+required it to have a width of at least $0.02\,P$, and a height of at
+least twice the point-to-point RMS.  This latter quantity is defined
+as the 68$^{\rm th}$ percentile of the distribution of the residuals
+from the median value of $\delta f_i \equiv f_i - f_{i+1}$, where $f$
+is the flux and $i$ is an index over time.
 
@@
 and dip-counting techniques were eclipsing binaries, spot-induced
-variability from rapid rotators, and blended combinations thereof.
-Rarer false positives included disk-induced variability, for instance
-induced by quasiperiodic dippers (CITE).  Typical false postive rates
-from our dip-counting pipeline were 5:1, with 368 unique stars
-flagged, and about 20\% being labelled either ``good'' or ``possible''
-CQVs; for the Fourier pipeline, {\bf the rate was X:Y, with ZZZZ
-unique stars flagged, and NN\% being labelled ``good'' or ``possible''
-CQVs}.
+variability from rapid rotators, and variability from neighboring,
+off-target stars.  Typical false postive rates from our dip-counting
+pipeline were 5:1, with 368 unique stars flagged, and about 20\% being
+labelled either ``good'' or ``possible'' CQVs; for the Fourier
+pipeline, {\bf the rate was X:Y, with ZZZZ unique stars flagged, and
+NN\% being labelled ``good'' or ``possible'' CQVs}.
 
@@
 
-\clearpage
+%\clearpage
+
+\software{
+  %\texttt{arviz} \citep{arviz_2019},
+  %\texttt{altaipony} \citep{ilin_flares_2021},
+  \texttt{astrobase} \citep{2021zndo...1011188B},
+  %\texttt{astroplan} \citep{astroplan2018},
+	%\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
+  %\texttt{astropy} \citep{astropy_2018},
+  %\texttt{astroquery} \citep{astroquery_2018},
+  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
+  %\texttt{ceres} \citep{brahm_2017_ceres},
+  %\texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019},
+  %\texttt{corner} \citep{corner_2016},
+  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
+  %\texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
+  %dependencies \citep{exoplanet:agol20, exoplanet:kipping13, exoplanet:luger18,
+  % 	exoplanet:theano},
+	%\texttt{gala} \citep{gala,PriceWhelan_2017_gala_zenodo},
+	%\texttt{IDL Astronomy User's Library} \citep{landsman_1995},
+  %\texttt{IPython} \citep{perez_2007},
+	%\texttt{isochrones} \citep{morton_2015_isochrones},
+	%\texttt{lightkurve} \citep{lightkurve_2018},
+  %\texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
+  %\texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
+  %\texttt{numpy} \citep{walt_numpy_2011}, 
+  %\texttt{pandas} \citep{mckinney-proc-scipy-2010},
+  %\texttt{pyGAM} \citep{serven_pygam_2018_1476122},
+  %\texttt{PyMC3} \citep{salvatier_2016_PyMC3},
+  %\texttt{radvel} \citep{fulton_radvel_2018},
+  %\texttt{scikit-learn} \citep{scikit-learn},
+  \texttt{scipy} \citep{2020NatMe..17..261V},
+  \texttt{TESS-point}  \citep{2020ascl.soft03001B},
+  %\texttt{tesscut} \citep{brasseur_astrocut_2019},
+  %\texttt{unpopular} \citep{hattorio_2021_cpm},
+  %\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
+  %\texttt{webplotdigitzer} \citep{rohatgi_2019},
+  %\texttt{wotan} \citep{hippke_wotan_2019}.
+}
+\
+
+\facilities{
+ 	{\it Astrometry}:
+		Gaia \citep{2018A&A...616A...1G,2018A&A...616A...1G}.
+ 	{\it Imaging}:
+    Second Generation Digitized Sky Survey. %,
+    %SOAR~(HRCam; \citealt{tokovinin_ten_2018}).
+ 	%Keck:II~(NIRC2).
+ 	%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
+ 	%Gemini:North~(`Alopeke; \citealt{scott_nessi_2018,scott_twin_2021}.
+ 	{\it Spectroscopy}:
+	%CTIO1.5$\,$m~(CHIRON; \citealt{tokovinin_chironfiber_2013}),
+  %PFS ({\bf CITE}),
+	%Tillinghast:1.5m~(TRES).
+  %MPG2.2$\,$m~(FEROS; \citealt{kaufer_commissioning_1999}),
+	%AAT~(Veloce; \citealt{gilbert_veloce_2018}).
+	%AAT~(HERMES; \citealt{lewis_2002_hermers_2df,sheinis_2015_hermes}),
+ 	Keck:I~(HIRES; \citealt{1994SPIE.2198..362V}).
+ 	%VLT:Kueyen~(FLAMES; \citealt{pasquini_2002}).
+% 	Euler1.2m~(CORALIE),
+% 	ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
+ 	{\it Photometry}:
+%	  ASTEP:0.40$\,$m (ASTEP400),
+% 	CTIO:1.0m (Y4KCam),
+% 	Danish 1.54m Telescope,
+%	  El Sauce:0.356$\,$m,
+% 	Elizabeth 1.0m at SAAO,
+% 	Euler1.2m (EulerCam),
+%	  Kepler,
+% 	Magellan:Baade (MagIC),
+% 	Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
+%   MuSCAT3 \citep{Narita_2020},
+% 	NTT,
+% 	SOAR (SOI),
+ 	  TESS \citep{2015JATIS...1a4003R},
+% 	TRAPPIST \citep{jehin_trappist_2011},
+% 	VLT:Antu (FORS2).
+%    ZTF.
+}
+
 \bibliographystyle{yahapj}                            
@@
     \centering
-    \includegraphics[width=\textwidth]{402980664_S0019_120sec_cpvvetter.pdf}
+    \includegraphics[width=\textwidth]{402980664_S0018_120sec_cpvvetter.pdf}
 		\vspace{-0.45cm}
@@
       {\it b)}: Phase-dispersion minimization (PDM) periodogram.
+      Dotted lines show up to the 10$^{\rm th}$ harmonic and
+      subharmonic.
       {\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
       circles displayed for scale.
-      {\it d)}: Cleaned light curve, binned to 20-minute cadence.
+      {\it d)}: Cleaned light curve, binned to 20-minute cadence, in
+      Barycentric TESS Julian Date (BTJD).
       {\it e)}: Phase-folded light curve, binned to 100 points per
@@
       wrapped phase-folded light curve, and small gray triangles
-      denote automatically identified local minima; 
-      one of the four sharp dips for this star was not identified!
+      denote automatically identified local minima.
       {\it f)}: Phase-folded light curve at twice the peak period.
@@
       if $\Delta T$$<$2.5.
+      {\it m)}: BANYAN-$\Sigma$ v1.1 association probabilities, calculated
+      using positions, proper motions, and the parallax.
       }

### 2023-06-13 paper/ms.tex
update ms

@@
 with one or more small dips, superposed over one or more large dips.
-Frankly, staring at them for long enough,
-it becomes possible to identify any one of them
 
@@
     \centering
-			\includegraphics[width=0.9\textwidth]{lc_mosaic_dlt150_good_changers.pdf}
-		\vspace{-0.2cm}
-		\caption{
-		{\bf Evolution of CQVs}: ``Before and
-      after'' for six CQVs from Figure~\ref{fig:revolution}.  Panels
-      in the top two rows are separated by two years
-      ($\approx$$10^3$ cycles); each panel shows one month.
-      Periods are listed in hours. 
-      {\bf todo: make these for everything.}
-%			\vspace{-0.8cm}
-		}
-		\label{fig:evoln}
-	\end{center}
-\end{figure*}
-
-\begin{figure*}[!t]
-	\begin{center}
-    \centering
     \includegraphics[width=0.9\textwidth]{TIC_402980664_P18.5604_2min_phase_timegroups_mosaic.pdf}
@@
 			{\it Bottom:}
-      Evolution of LP 12-502 ($P$=18.6\,h) at fixed period over three
+      Evolution of LP 12-502 ($P$=18.5604\,h) at fixed period over three
       years; small text denotes cycle number.  The TESS pointing law
@@
 		\label{fig:lp}
+	\end{center}
+\end{figure*}
+
+\begin{figure*}[!t]
+	\begin{center}
+		\centering
+		\includegraphics[width=0.9\textwidth]{lc_mosaic_dlt150_good_allchangers_2count_showtitles.png}
+		\vspace{-0.2cm}
+		\caption{
+			{\bf Evolution of CQVs}: ``Before and
+			after'...  Panels
+			in the top two rows are separated by two years
+			($\approx$$10^3$ cycles); each panel shows one month.
+			Periods are listed in hours. 
+			{\bf todo: fix the plot and the caption.}
+			%			\vspace{-0.8cm}
+		}
+		\label{fig:evoln}
 	\end{center}
@@
     \centering
-    \includegraphics[width=\textwidth]{402980664_S0018_120sec_cpvvetter.pdf}
+    \includegraphics[width=0.96\textwidth]{402980664_S0018_120sec_cpvvetter.pdf}
 		\vspace{-0.45cm}

### 2023-06-13 complexrotators/plotting.py
timegroups mosaic: tic4029 finetune

@@ -584,7 +584,7 @@ def plot_phase_timegroups_mosaic(
     factor=0.8
     factor=1.1
     fig, axs = plt.subplots(
-        sharex=True, nrows=3, ncols=6,
+        nrows=3, ncols=6,
         figsize=(factor*5.2, factor*(3.5/7)*7),
         constrained_layout=True
     )
@@ -627,32 +627,32 @@ def plot_phase_timegroups_mosaic(
             titlepad=0.1,
             showtext=False,
             savethefigure=False,
+            titlefontsize='x-small'
         )
         if isinstance(ylim, (list, tuple)):
             ax.set_ylim(ylim)
 
-        if ix not in [0, 6, 12]:
-            ax.set_yticklabels([])
-
         #ax.hlines(2.5, -0.6666/2, 0.6666/2, colors='darkgray', alpha=1,
         #          linestyles='-', zorder=-2, linewidths=1)
 
+        ax.set_yticklabels([])
+        ax.set_xticklabels([])
+
         yticks = [-3,0,2]
         ax.set_yticks(yticks)
-
-        #ax.yaxis.set_minor_locator(MultipleLocator(1))
         ax.minorticks_off()
 
+        ax.set_xticks([-0.5, 0, 0.5])
+
         if ix in [0,6,12]:
-            ax.set_yticklabels(yticks, fontsize='small')
+            ax.set_yticklabels(yticks, fontsize='x-small')
 
         ix += 1
 
-    for ix in range(12,17):
-        axs[ix].set_xticks([-0.5, 0, 0.5])
-        axs[ix].set_xticklabels(['-0.5', '0', '0.5'], fontsize='small')
-    for ix in range(0,17):
-        axs[ix].set_xticks([-0.5, 0, 0.5])
+    for ix in range(12,18):
+        axs[ix].set_xticklabels(['-0.5', '0', '0.5'], fontsize='x-small')
+
+    axs[17].set_xticklabels([])
 
     if showtitle:
         fig.text(
@@ -664,14 +664,16 @@ def plot_phase_timegroups_mosaic(
         )
 
     fig.text(-0.01,0.5, r"Flux [%]", va='center', rotation=90, fontsize='large')
-    fig.text(0.5,-0.01, r"Phase, φ", fontsize='large')
+    fig.text(0.5,-0.01, r"Phase, φ", ha='center', fontsize='large')
 
     format_ax(ax)
[…]

### 2023-06-13 complexrotators/observability.py
observability: port assess_tess_holdings

@@ -1,16 +1,22 @@
 """
-Given tic ids, get some basic features of the stars.  (Nominally, the features
-that we would care about in order to decide on ground-based follow-up
-priorities)
+Given TIC IDs, get some basic features of the stars.  These include
+features that we would care about in order to decide on ground-based
+follow-up priorities.
 
-get_gaia_rows
-get_tess_stats
-    given_ticid_get_variability_params
-    given_ticid_get_period
-check_tesspoint
-check_astroplan_months_observable
-get_bestmonth_hoursobservable
-merge_to_observability_table
+In order of perceived reusability:
+
+| get_gaia_rows
+
+| assess_tess_holdings
+| check_tesspoint
+
+| get_tess_stats
+    | given_ticid_get_variability_params
+    | given_ticid_get_period
+
+| check_astroplan_months_observable
+| get_bestmonth_hoursobservable
+| merge_to_observability_table
 """
 import pandas as pd, numpy as np, matplotlib.pyplot as plt
 import os, pickle
@@ -38,10 +44,9 @@ from complexrotators import pipeline_utils as pu
 
 def get_gaia_rows(ticid):
     """
-    most important for observability -- gaia:
-      * brightness
-      * distance
-      * color
+    Given the TIC ID, get basic Gaia DR2 information, including the
+    dr2_source_id, positions, proper motions, parallaxes, photometry,
+    and distance.  Return as a dataframe.
     """
 
     dr2_source_id = tic_to_gaiadr2(ticid)
@@ -79,6 +84,114 @@ def get_gaia_rows(ticid):
     outdf['dist_pc'] = d_pc
     outdf['dist_pc_upper_unc'] = upper_unc
     outdf['dist_pc_lower_unc'] = lower_unc
+
+    outdf = outdf.rename({"source_id": "dr2_source_id"},
+                         axis="columns")
+
+    return outdf
+
+
+def assess_tess_holdings(ticid, outdir=None):
+    """
+    Given a TIC ID, figure out what 20sec / 120sec / 200sec / 600sec /
+    1800sec TESS data are available.
+
+    Args:
+        ticid (str or int): e.g. 123456789
+
+        outdir: used for cacheing.  If nothing is passed, will not cache.
+
+    Returns:
[…]

### 2023-06-13 drivers/assess_tess_holdings.py

@@ -12,19 +12,15 @@ purposes (eg. "at least two years" or similar).
 extra notes at
 ~/Dropbox/proj/cpv/doc/20230530_tess_holdings_archival_data_assessment.txt
 """
-import os, pickle
+import os
 from os.path import join
 from glob import glob
 import numpy as np, pandas as pd, matplotlib.pyplot as plt
 
-import lightkurve as lk
-from astroquery.mast import Catalogs
-from tess_stars2px import tess_stars2px_function_entry
-
 from complexrotators.paths import TARGETSDIR, TABLEDIR
-from complexrotators.observability import check_tesspoint
+from complexrotators.observability import assess_tess_holdings
 
-def assess_tess_holdings(sample_id):
+def wrap_assess_tess_holdings(sample_id):
 
     csvpath = join(TARGETSDIR, f"{sample_id}.csv")
 
@@ -34,78 +30,11 @@ def assess_tess_holdings(sample_id):
     if not os.path.exists(outdir): os.mkdir(outdir)
 
     for t in df['ticid']:
-
-        outcsv = join(outdir, f"TIC{t}.csv")
-
-        if os.path.exists(outcsv):
-            print(f'Found {outcsv}, continue')
-            continue
-
-        ticstr = f"TIC {t}"
-
-        tic_data = Catalogs.query_object(ticstr, catalog="TIC")
-
-        ident, ra, dec, dst_arcsec = tic_data[0][ ["ID", "ra", "dec", "dstArcSec"] ]
-
-        if dst_arcsec > 1:
-            print(f'WRN! {ticstr} is {dst_arcsec}arcsec from request.')
-
-
-        sectors, cams, ccds, colpixs, rowpixs = check_tesspoint(
-            ra, dec, t, get_seccamccd_tuple=1
-        )
-
-        lcset = lk.search_lightcurve(ticstr)
-        lcset_df = lcset.table.to_pandas()
-
-        N_20secs, N_120secs, N_200secs, N_600secs, N_1800secs, N_FFIs = (
-            [], [], [], [], [], []
-        )
-
-        for sector, cam, ccd, colpix, rowpix in zip(
-            sectors, cams, ccds, colpixs, rowpixs
-        ):
-
-            in_sector = pd.Series(lcset.mission).str.contains(
-                str(sector).zfill(2)
-            )
-
-            N_20secs.append(np.isclose(lcset_df[in_sector].exptime, 20).sum())
[…]

### 2023-06-13 paper/ms.tex
update ms

@@
 
-\title{Complex Quasiperiodic Variables from Four Years of TESS}
+\title{Complex Quasiperiodic Pre-Main-Sequence M-Dwarfs from Four Years of TESS}
 
@@
   sharp and broad troughs.  The troughs are usually superposed over
-  smooth, spot-like modulation.  Based on a lack of observed infrared
-  excesses, these objects do not have primordial gas-rich disks.
+  smooth, spot-like modulation.  These objects do not have primordial
+  gas-rich disks, based on a lack of observed infrared excesses.
   Nonetheless, the currently preferred explanations for their optical
@@
 
-\keywords{Weak-line T Tauri stars (1795), Periodic variable stars
-(1213), Circumstellar matter (241), Star clusters (1567), Stellar
-magnetic fields (1610), Stellar rotation (1629)}
+\keywords{Weak-line T Tauri stars (1795),
+Periodic variable stars (1213),
+Circumstellar matter (241),
+Star clusters (1567),
+Stellar magnetic fields (1610),
+Stellar rotation (1629)}
 

### 2023-06-13 drivers/find_CPVs.py
minor driver update

@@ -40,7 +40,9 @@ from os.path import join
 from glob import glob
 import numpy as np, pandas as pd
 
-from complexrotators.paths import LOCALDIR, SPOCDIR, TARGETSDIR
+from complexrotators.paths import (
+    LOCALDIR, SPOCDIR, TARGETSDIR, TABLEDIR
+)
 from complexrotators.getters import (
     _get_lcpaths_given_ticid, _get_local_lcpaths_given_ticid,
     _get_lcpaths_fromlightkurve_given_ticid
@@ -58,26 +60,10 @@ def get_ticids(sample_id):
 
     if sample_id == 'debug':
         ticids = [
+        #"268963753"
+        #"67745212"
         #"201789285",
         "402980664"
-        #"311092148",
-        #"332517282",
-        #"405910546",
-        #"142173958",
-        #"300651846",
-        #"408188366",
-        #"146539195",
-        #"177309964",
-        #"425933644",
-        #"206544316",
-        #"224283342",
-        #"245902096",
-        #"150068381",
-        #"177309964",
-        #"118769116",
-        #"245868207",
-        #"245874053",
-        #"59129133"
         ]
 
         N_stars_to_search = len(ticids)
@@ -103,11 +89,7 @@ def get_ticids(sample_id):
         N_stars_to_search = len(ticids)
         N_lcs_to_search = len(sdf)
 
-    # e.g.,
-    #30to50pc_mkdwarf
-    #50to60pc_mkdwarf
-    #60to70pc_mkdwarf
-    #70to85pc_mkdwarf
+    # e.g., 30to50pc_mkdwarf, 50to60pc_mkdwarf, etc.
     elif 'pc_mkdwarf' in sample_id and 'to' in sample_id:
 
         lower = int(sample_id.split("to")[0])
@@ -136,6 +118,18 @@ def get_ticids(sample_id):
     elif sample_id == 'rahul_20230501':
         df = pd.read_csv(
             join(TARGETSDIR, '20230501_RAHUL_FULL_LIST_NO_DUPLICATES.csv')
+        )
+        ticids = np.unique(df.ticid.astype(str))
+
+        N_stars_to_search = len(ticids)
+        N_lcs_to_search = -1
+
+    elif sample_id == '2023catalog_LGB_RJ_concat':
+        df = pd.read_csv(
+            join(
+                TABLEDIR, '2023_catalog_table',
[…]

### 2023-06-13 complexrotators/paths.py
add litdir

@@ -4,6 +4,7 @@ from os.path import join
 
 DATADIR = join(os.path.dirname(__path__[0]), 'data')
 PHOTDIR = join(DATADIR, 'photometry', 'ground')
+LITDIR = join(DATADIR, 'literature')
 CSVDIR = join(DATADIR, 'photometry', 'cdips_followup_csvs')
 TARGETSDIR = join(DATADIR, 'targetlists')
 RESULTSDIR = join(os.path.dirname(__path__[0]), 'results')

### 2023-06-14 drivers/make_cpv_table.py
make_cpv_table: updates

@@ -26,12 +26,58 @@ assert os.path.exists(indir)
 def main():
 
     csvpath = join(indir, "20230613_LGB_RJ_uticid_quality_label.csv")
-    df = pd.read_csv(csvpath, sep="|")
+    _df = pd.read_csv(csvpath, sep="|")
 
     rows = []
-    for t in df['ticid']:
+    for t in _df['ticid']:
         r = get_cpvtable_row(t)
         rows.append(r)
+
+    rdf = pd.concat(rows)
+
+    df = _df.merge(rdf, how='inner', on='ticid')
+    df = df.reset_index(drop=True)
+
+    msg = 'every unique ticid should have a row entry'
+    assert len(_df) == len(df), msg
+
+    csvpath = join(indir, "20230613_LGB_RJ_CPV_TABLE_supplemental.csv")
+    df.to_csv(csvpath, index=False, sep="|")
+    print(f"Wrote {csvpath}")
+
+    # re-apply selection function
+    sel = (
+        (df.tic8_Tmag < 16)
+        &
+        (df.bp_rp > 1.5)
+        &
+        (df.M_G > 4)
+        &
+        (df.dist_pc < 150)
+    )
+
+    N_0 = len(df)
+    sdf = df[sel]
+    N_1 = len(sdf)
+    N_2 = len(sdf[~pd.isnull(sdf.goodsectors)])
+    N_3 = len(sdf[pd.isnull(sdf.goodsectors)])
+
+    # TODO: write these numbers to latex
+    # \renewcommand{}{}
+    # type include file at /paper/
+    # TODO
+
+    txt = (
+        f"\n...\n"
+        f"N={N_0} unique TICID's labelled 'good' or 'maybe' CPVs before selection fn"
+        f"\n...\n"
+        f"N={N_1} unique TICID's labelled 'good' or 'maybe' CPVs after selection fn"
+        f"\n...\n"
+        f"N={N_2} unique TICID's labelled 'good' CPVs after selection fn"
+        f"\n...\n"
+        f"N={N_3} unique TICID's labelled 'maybe' CPVs after selection fn"
+    )
+    print(txt)
 
     import IPython; IPython.embed()
     assert 0
@@ -133,8 +179,10 @@ def get_tess_lc_properties(ticid):
         _n_peaks = int(stc['n_peaks'])
         _peaks_phaseunits = list(np.array(eval(stc['peaks_phaseunits'])).round(2))
 
-        array = np.array
-        properties = eval(stc['properties'])
[…]

### 2023-06-14 paper/ms.tex
update ms

@@
 
+\paragraph{LP 12-502}
+While many CPVs had multiple sectors of data, in our view the most
+astounding dataset was available for LP 12-502 (TIP 402980664).
+Figure~\ref{fig:lp} shows all available data from Sectors 18, 19, 25,
+26, 53, 58, and 59; the star was observed at 120-second cadence for
+every sector during which it was on silicon.
+
+For the first 64 cycles, the star shows a pattern reminiscent of a
+(bizarre) eclipsing binary, with four obvious dips, that we denote
+dips 1, 2, 3, and 4 at phases -0.28, -0.08, 0, and 0.25 respectively.
+The depth of dips 1 and 3 remain roughly fixed.
+Over the 64 cycles, dip 4 {\it decreases} in depth by about 2\%, while
+dip 2 {\it increases} in depth, by about the same amount.
+
+There is then a 6-month (184 cycle) gap out to Cycle 248.
+At this time, dip 1 is still present, at the same phase, and with
+roughly the same depth.
+
+%TODO continue writing about this.  What is the exact TJD of the jump?
+
+%TODO; make a version (for talks) showing dips 1234 over cycles0-64
+%TODO include +/- 1/3 as important durations.
+%TODO: note that duration between the minimum of "dip1" and "dip4" is
+%      kind of always 0.53
+
 \paragraph{None of them are strictly periodic}
@@
       if $\Delta T$$<$2.5.
-      {\it m)}: BANYAN-$\Sigma$ v1.1 association probabilities, calculated
+      {\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
       using positions, proper motions, and the parallax.

### 2023-06-14 paper/ms.tex
update ms

@@
 
-\title{Complex Quasiperiodic Pre-Main-Sequence M-Dwarfs from Four Years of TESS}
+\title{Pre-Main-Sequence M-Dwarfs With Complex Quasiperiodic Variability From Four Years of TESS}
 
@@
   sharp and broad troughs.  The troughs are usually superposed over
-  smooth, spot-like modulation.  These objects do not have primordial
-  gas-rich disks, based on a lack of observed infrared excesses.
-  Nonetheless, the currently preferred explanations for their optical
+  smooth, spot-like modulation.  These objects are typically
+  10-100\,million years old, and they do not seem to have primordial gas-rich
+  disks.  Nonetheless, the preferred explanations for their optical
   variability invoke long-lived material in orbit at the corotation
@@
   objects are ``outliers among outliers''; for instance LP 12-502
-  shows four to eight local minima per cycle, distributed over a ``dip
-  complex'' with a total duration that is fixed over more than one
-  thousand cycles, but with a detailed shape that exhibited changes
-  over less than one cycle.  More generally, we find that none of the
-  CQVs maintain a fixed light curve shape over timescales of more than
-  a few hundred cycles -- hence, {\it quasi}periodic.  Although the
-  physical explanation behind these objects remains enigmatic, our
-  sample may help clarify their origin.  Connections to star, disk,
-  and exoplanet evolution are emphasized.
+  shows four to eight local minima per cycle distributed over a ``dip
+  complex'' with a total duration that is nearly fixed over more than
+  1000 cycles.  Nonetheless, LP-502 at times shows drastic shape
+  changes over less than one cycle.  More generally, we find that none
+  of the CQVs maintain a fixed light curve shape over timescales of
+  more than a few hundred cycles -- hence, {\it quasi}periodic.
+  Although the physical explanation behind these objects remains
+  enigmatic, our sample may help clarify their origin.  Connections to
+  star, disk, and exoplanet evolution are emphasized.
 \end{abstract}
@@
 \label{sec:intro}
+
+% NOTE: could write this more from a stellar evolution angle.
+% M-dwarfs contract.  They spin up.  Some reach rapid rotation rates,
+% and exhibit strong magnetic fields.
 
@@
 
-We chose to analyze only the ``short'' 120-second cadence data
+We analyzed the ``short'' 120-second cadence data
 acquired by TESS between July~2018 and Sep~2022 (Sectors 1-55).

### 2023-06-14 drivers/make_cpv_table.py
cpv table maker to latex

@@ -3,13 +3,26 @@ Construct the extended and publication versions of the 2023 catalog table.
 
 Uses log output created by running find_CPVs.py using
 sample_id=="2023catalog_LGB_RJ_concat" first (see HOWTO.md)
+
+Utilities:
+
+| get_cpvtable_row(ticid)
+| gdr2_df = get_gaia_rows(ticid)
+| tdf = assess_tess_holdings(ticid)
+| ftdf = flatten_tdf(tdf, ticid)
+| bdf = get_banyan_result(gdr2_df)
+| t8_df = get_tic8_row(ticid)
+| tlc_df = get_tess_cpv_lc_properties(ticid)
+
 """
 
 from glob import glob
 from os.path import join
 import pandas as pd, numpy as np
 import os
-from complexrotators.paths import RESULTSDIR, TABLEDIR, LITDIR, LOCALDIR
+from complexrotators.paths import (
+    RESULTSDIR, TABLEDIR, LITDIR, LOCALDIR, PAPERDIR
+)
 from os.path import join
 
 from astroquery.mast import Catalogs
@@ -56,11 +69,47 @@ def main():
         (df.dist_pc < 150)
     )
 
+    min_goodsector = (
+        df.goodsectors.str.split(",").apply(
+            lambda x: np.array(x).astype(int)
+            if not np.all(pd.isnull(x)) else np.array([np.nan])
+        ).apply(lambda x: np.nanmin(x))
+    )
+    min_maybesector = (
+        df.maybesectors.str.split(",").apply(
+            lambda x: np.array(x).astype(int)
+            if not np.all(pd.isnull(x)) else np.array([np.nan])
+        ).apply(lambda x: np.nanmin(x))
+    )
+    sel_max55 = (
+        (min_goodsector <= 55) | (min_maybesector <= 55)
+    )
+    selcols = "ticid goodsectors maybesectors".split()
+    print(f"\n...\n")
+    print(f"WRN! including\n{df[~sel_max55][selcols]}\n, bc alpha per")
+    print(f"\n...\n")
+
     N_0 = len(df)
     sdf = df[sel]
     N_1 = len(sdf)
     N_2 = len(sdf[~pd.isnull(sdf.goodsectors)])
     N_3 = len(sdf[pd.isnull(sdf.goodsectors)])
+
+    # "good" CPVs
[…]

### 2023-06-14 drivers/find_CPVs.py
minor driver updates

@@ -63,7 +63,10 @@ def get_ticids(sample_id):
         #"268963753"
         #"67745212"
         #"201789285",
-        "402980664"
+        #"402980664"
+        #"251496897"
+        #"141146666" # neighbor of 141146667
+        "353927317" # EPIC 211070495, Rebull2016
         ]
 
         N_stars_to_search = len(ticids)
@@ -357,8 +360,8 @@ def find_CPV(ticid, sample_id, forcepdf=0):
 def main():
 
     sample_ids = [
-        #'debug'
-        '2023catalog_LGB_RJ_concat'
+        'debug'
+        #'2023catalog_LGB_RJ_concat'
         #'30pc_mkdwarf',
         #'30to50pc_mkdwarf',
         #'50to60pc_mkdwarf',

### 2023-06-14 drivers/make_cpv_table.py

@@ -104,7 +104,7 @@ def main():
     N_5 = len(smdf[smdf.banyan_assoc == 'FIELD'])
 
     N_6 = len(sgdf[sgdf.banyan_assoc != 'FIELD'])
-    N_7 = len(sgdf[smdf.banyan_assoc != 'FIELD'])
+    N_7 = len(smdf[smdf.banyan_assoc != 'FIELD'])
 
     selcols = (
         "ticid goodsectors maybesectors N_sectors tic8_Tmag ruwe "

### 2023-06-14 paper/ms.tex
update ms

@@
 
+\newcommand{\bprp}{G_{\rm BP} - G_{\rm RP}}
+
 \newcommand{\minus}{\scalebox{0.5}[1.0]{$-$}}
@@
 \newcommand{\nuniqdipflagged}{{368}} % up-to-date; get_lgb_list_count.py
-\newcommand{\ncpvsfound}{{48}}
-\newcommand{\nmaybes}{{19}}
+
+\input{vals_cqv_table_statistics}
 
@@
   smooth, spot-like modulation.  These objects are typically
-  10-100\,million years old, and they do not seem to have primordial gas-rich
+  10-100 million years (Myr) old, and they do not seem to have primordial gas-rich
   disks.  Nonetheless, the preferred explanations for their optical
@@
   \nstarssearched\ M-dwarfs with $T$$<$16 and $d$$<$150\,pc, we find
-  \ncpvsfound\ gold-standard CQVs.  Most of these discoveries are new,
-  and they include the brightest ($T$$\approx$10) and closest
-  ($d$$\approx$20\,pc) examples of this class of object known.  A few
-  objects are ``outliers among outliers''; for instance LP 12-502
+  \ngoods\ gold-standard CQVs.  Most of these discoveries are new,
+  and they include the brightest and closest
+  examples of this class of object known ($T$$\approx$10; $d$$\approx$20\,pc).  A few
+  objects are outliers among outliers; LP 12-502 for instance
   shows four to eight local minima per cycle distributed over a ``dip
   complex'' with a total duration that is nearly fixed over more than
-  1000 cycles.  Nonetheless, LP-502 at times shows drastic shape
+  1000 cycles.  Nonetheless, LP-502 at times also showed drastic shape
   changes over less than one cycle.  More generally, we find that none
   of the CQVs maintain a fixed light curve shape over timescales of
-  more than a few hundred cycles -- hence, {\it quasi}periodic.
+  more than a few hundred cycles -- they are {\it quasi}periodic.
   Although the physical explanation behind these objects remains
@@
 root cause is not yet qualitatively understood: complex quasiperiodic
-variables (CQVs).  These objects are identified phenomenologically
+variables (CQVs).  Figure~\ref{fig:f1} shows a few examples.  These objects are identified phenomenologically
 using their optical light curves, which show quasiperiodic troughs
@@
 be $\approx$1\% of M-dwarfs younger than 100 Myr
-\citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G}.
+\citep{2016AJ....152..114R,2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G}.
 The dips can be chromatic, with a reddening law plausibly consistent
@@
 scenarios instead invoke sharp geometries with material extrinsic to
-the stellar surface \citep[see
-Refs.~][]{2017AJ....153..152S,2022AJ....163..144G}.  In the ``clump''
+the stellar surface \citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  In the ``clump''
 scenario, opaque dust clumps orbiting near the Keplerian corotation
@@
 by K2 and TESS, about 50 CQVs have been reported to date
-\citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}.
+\citep{2016AJ....152..114R,2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2020AJ....160...86B,2022AJ....163..144G,2023ApJ...945..114P}.
 The known CQVs are correspondingly faint; the initial K2 discoveries
-\citep{2017AJ....153..152S} were M2-M6 dwarfs at distances
+\citep{2016AJ....152..114R,2017AJ....153..152S} were M2-M6 dwarfs at distances
 $\gtrsim$100\,pc, yielding optical brightnesses of $V$$\approx$15.5 to
@@
 
-\section{Methods}
-\label{sec:methods}
-
-\subsection{Stellar selection function}
-\label{subsec:selectionfn}
-
-We analyzed the ``short'' 120-second cadence data
-acquired by TESS between July~2018 and Sep~2022 (Sectors 1-55).
-Specifically, we used the 120-second cadence light curve products
-produced by the mission's Science Processing and Operations Center at
-NASA Ames \citep{2016SPIE.9913E..3EJ}.  While the TESS data products
-also include full frame images with cadences of 200, 600, and 1800
-seconds, we limited our scope in this work for the sake of simplicity
-in data handling.  In exchange, we lose out in both completeness and
-homogeneity of the selection function.  While TESS cumulatively
-observed $\approx$90\% of the sky for at least one lunar month between
-July~2018 and Sep~2022, the 120-second cadence data were acquired for
-only a pre-selected set of stars over Sectors 1-26, and then a
-guest-investigator driven set of stars over Sectors 27-55
-\citep{2021PASP..133i5002F}.
-
-To assess the completeness of the resulting 120-second cadence data
-that we analyze, we cross-matched TIC8 \citep{2018AJ....156..102S}
-against the Gaia DR2 point-source catalog \citep{2018A&A...616A...1G}.
-We opted for Gaia DR2 rather than DR3 because the base catalog for
-TIC8 was Gaia DR2, which facilitated a one-to-one crossmatch using the
-Gaia source identifiers.  This exercise showed that for $T$$<$16
-M-dwarfs, the TESS 2-minute data are roughly 50\% complete at
-$\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\% of the $T$$<$16 M-dwarfs
-have at least one sector of short-cadence data; at $>$100\,pc,
-$\lesssim$10\% of such M-dwarfs have at least one sector of
-short-cadence data.  Armed with this understanding, we then used our
-cross-match between Gaia DR2 and TIC8 to select our stars of interest,
-which we defined as stars with 120-second cadence TESS light curves
-that satisfied
-\begin{align}
-  T &< 16\\
-  G_{\rm BP} - G_{\rm RP} &> 1.5 \\
-  M_{\rm G} &> 4 \\
-  d &< 150\,{\rm pc},
-\end{align}
-for $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ the Gaia $G$-band
-absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
-arcseconds, and a geometric distance $d$ defined by inverting the
-parallax and ignoring any zero-point correction.  This selection
-function includes dwarf stars later than spectral types of
-$\approx$K6V.  This target sample includes \nstarssearched\ stars with
-approximately M-dwarf spectral type, down to $T$$<$16 and out to
-$d$$<$150\,pc.
-
 \begin{figure*}[!t]
@@
 
+\section{Methods}
+\label{sec:methods}
+
+\subsection{Stellar selection function}
+\label{subsec:selectionfn}
+
+We analyzed the ``short'' 120-second cadence data
+acquired by TESS between July~2018 and Sep~2022 (Sectors 1-55).
+Specifically, we used the 120-second cadence light curve products
+produced by the mission's Science Processing and Operations Center at
+NASA Ames \citep{2016SPIE.9913E..3EJ}.  While the TESS data products
+also include full frame images with cadences of 200, 600, and 1800
+seconds, we limited our scope in this work for the sake of simplicity
+in data handling.  In exchange, we lose in both completeness and
+homogeneity of the selection function.  While TESS cumulatively
+observed $\approx$90\% of the sky for at least one lunar month between
+July~2018 and Sep~2022, the 120-second cadence data were acquired for
+only a pre-selected set of stars over Sectors 1-26, and then a
+guest-investigator driven set of stars over Sectors 27-55
+\citep{2021PASP..133i5002F}.
+
+To assess the completeness of the resulting 120-second cadence data
+that we analyze, we cross-matched TIC8 \citep{2018AJ....156..102S}
+against the Gaia DR2 point-source catalog \citep{2018A&A...616A...1G}.
+We opted for Gaia DR2 rather than DR3 because the base catalog for
+TIC8 was Gaia DR2, which facilitated a one-to-one crossmatch using the
+Gaia source identifiers.  This exercise showed that for $T$$<$16
+M-dwarfs, the TESS 2-minute data are roughly 50\% complete at
+$\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\% of the $T$$<$16 M-dwarfs
+have at least one sector of short-cadence data; at $>$100\,pc,
+$\lesssim$10\% of such M-dwarfs have at least one sector of
+short-cadence data.  Armed with this understanding, we then used our
+cross-match between Gaia DR2 and TIC8 to select our stars of interest,
+which we defined as stars with 120-second cadence TESS light curves
+that satisfied
+\begin{align}
+  T &< 16 \quad&(\mathrm{Bright\ for\ TESS})\\
+  \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only}) \\
+  M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})  \\
+  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}),
+\end{align}
+for $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ the Gaia $G$-band
+absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
+arcseconds, and a geometric distance $d$ defined by inverting the
+parallax and ignoring any zero-point correction.  This selection
+function includes dwarf stars later than spectral types of
+$\approx$K6V.  This target sample includes \nstarssearched\ stars with
+approximately M-dwarf spectral type, down to $T$$<$16 and out to
+$d$$<$150\,pc.
+
 \subsection{CQV discovery}
@@
 examining stars known to be in young clusters
-\citep{2017AJ....153..152S}, and automatically flagging rapid rotators
+\citep{2016AJ....152..114R,2017AJ....153..152S}, and automatically flagging rapid rotators
 with a large number of strong Fourier harmonics
@@
 off-target stars.  Typical false postive rates from our dip-counting
-pipeline were 5:1, with 368 unique stars flagged, and about 20\% being
+pipeline were 5:1, with \nuniqdipflagged\ unique stars flagged, and about 20\% being
 labelled either ``good'' or ``possible'' CQVs; for the Fourier
@@
 \paragraph{Ages}
-%TODO
+We estimated the stellar ages by making probabilistic spatial and
+kinematic associations between the CQVs and known clusters in the solar
+neighborhood.  For most of the stars in our sample, we were able to do
+this using BANYAN\,$\Sigma$
+\citep{2018ApJ...856...23G}.\footnote{\url{https://github.com/jgagneastro/banyan_sigma},
+git commit \texttt{394b486}} This algorithm calculates the
+probability that a given star belongs to one of 27 young
+clusters (or ``assocations'') within 150\,pc of the Sun, by modeling the clusters
+as multivariate Gaussians in 3-D position and 3-D velocity space.  
+We used the
+Gaia DR2 sky positions, proper motions, and distances to calculate the
+membership probabilities.  
+BANYAN\,$\Sigma$ in turn analytically marginalizes over the radial velocity dimension.
+We emphasize that the probabilities returned by this procedure are qualitatively
+useful, but quantitatively dubious due to the non-Gaussian
+nature of most groups within the
+solar neighborhood \citep[see e.g.][Figure~10]{2021ApJ...917...23K}.
+
+For a few cases where BANYAN\,$\Sigma$
+yielded ambiguous results, we consulted the meta-catalog of young,
+age-dated, and age-dateable stars within a kiloparsec from
+\citet{2022AJ....163..121B}, and also searched the local volume around
+each star for co-moving
+companions.\footnote{\url{https://github.com/adamkraus/Comove}, git commit \texttt{278b372}}
 
@@
 %TODO
-
-\section{Results}
-\label{sec:results}
-
-\subsection{CQV catalog}
 
@@
 
+\section{Results}
+\label{sec:results}
+
+\subsection{CQV catalog}
+
 Table~\ref{tab:thetable} lists the \ncpvsfound\ CQVs identified by
 our search, and some of their important properties.
-The mosaic in Figure~\ref{fig:singlemosaic} shows the 40 brightest
-objects.
+\ngoods\ objects demonstrate what we view as unambiguous
+characteristics of the CPV phenomenon in at least one TESS sector, and
+we refer to these as the ``gold sample''.
+The remaining \nmaybes\ CPV candidates were ambiguous (in our view),
+and their variability might be caused by say, multiple starspot
+groups.
 
-For the TESS sectors in which these objects were identified, they show
+The mosaic in Figure~\ref{fig:singlemosaic} shows phased light curves
+for the 40 brightest objects.
+The TESS sectors in which these objects were identified show
 anywhere from one to eight local minima per cycle.
@@
 (e.g. TIC~2234692, TIC~401789285, TIC~425933644, TIC~142173958).
-Others still show some mix between these two modes,
-with one or more small dips, superposed over one or more large dips.
+Others still show some mix between these two modes.
+
+\subsection{Ages}
+
+Of our \ncpvsfound\ confirmed and candidate CQVs, \nnotfieldbanyan\ 
+were confidently associated with a nearby moving group or open
+cluster using BANYAN\,$\Sigma$.
+The relevant groups are listed in Table~\ref{tab:thetable}; their ages
+span $\approx$5-150\,Myr.
+The most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.
+The yield of CQVs in Sco-Cen (LCC / UCL / USco) is not surprising,
+since Sco-Cen contains the majority of pre-main-sequence stars in the
+solar neighborhood.
+The absence of CQVs in IC2602 and IC2391 is because those clusters are
+beyond 100\,pc, where the completeness of the TESS 120-second cadence
+data is below 10\%.
+
+Of the the \ngoodsfieldbanyan\ non-associated stars, one
+(TIC~302160226) is an obvious member of $\alpha$~Per ($t\approx
+86\pm16$\,Myr; \citealt{2022arXiv221109822B}).  For the other two
+(TIC~58084670 and TIC~141146667), we are convinced of both their CPV
+status and their youth, but we were not able to confidently associate
+either star with any young groups.
+Both were noted as being in the ``diffuse'' Class~II YSO
+population by \citet{2021ApJ...917...23K}.
+That diffuse population may contain kinematic structures that have yet
+to be unravelled, however the absence of obvious young, co-moving
+stars within $\Delta r$=$40$\,pc and $\Delta v$=$3$\,km\,s$^{-1}$
+of these stars suggest that they may have run away from their birth
+locations.
+
+The CQV phenomenon persists at least up to 150\,Myr.  Our catalog
+includes three $\approx$150\,Myr old AB Dor members (TIC~288344202,
+TIC~332517282, and TIC~368129164), a $\approx$112\,Myr old Pleiades
+member (TIC~440725886; \citealt{CantatGaudin_2020}), and a
+similarly-aged Psc-Eri member (TIC~38539720;
+\citealt{2020A&A...639A..64R}).  To our best knowledge, TIC~332517282
+was the previous record-holder for oldest-known CQV
+\citep{2019ApJ...876..127Z,2022AJ....163..144G}; at least one
+unambiguous case (EPIC~211070495) and a few other candidates were
+also previously known in the Pleiades \citep{2016AJ....152..114R}.
+While we expect to have been sensitive to CQVs in the nearby Hyades
+($\approx$700\,Myr), 
+again due to the specifics of the TESS 120-second selection function,
+we do not know at this time whether we would have been sensitive to
+such stars.
+
+Finally, six CQVs were identified in the recently
+confirmed Argus association \citep{2019ApJ...870...27Z}.
+This serves as an indirect line of evidence supporting the reality,
+and youth, of that group.
 
@@
 			{\it Bottom:}
-      Evolution of LP 12-502 ($P$=18.5604\,h) at fixed period over three
+      Evolution of LP 12-502 ($P$=18.5604\,h) at fixed period and epoch over three
       years; small text denotes cycle number.  The TESS pointing law
@@
       one cycle.
-			\vspace{-0.8cm}
 		}
@@
 
-{\it Each CQV a snowflake}
+\paragraph{Some CQVs require external occulters}
+(rehash Bodman2017 timescale arguments)
+
+\paragraph{Each CQV a snowflake?}
 One intriguing aspect of staring at Figure~\ref{fig:singlemosaic}
@@
 
-TIC 272248916 and TIC 442571495
+TIC 272248916 and TIC 442571495 match.
 
-%A number of auxiliary
-%questions follow.  After correcting for line-of-sight inclination, are
-%most young M-dwarfs CQVs?  What observational signatures distinguish
-%the proposed models (Figure~\ref{fig:f1}, bottom row)?  What
-%organizational regularities characterize the CQV as a class of
-%variable star?  What sets the extremes of the CQV population, such as
-%the longest rotation periods, hottest stellar temperatures, and oldest
-%stellar ages?  And finally, what connections, if any, do CQVs have to
-%topics such as stellar evolution, M-dwarf magnetic fields, debris
-%disks, and close-in exoplanets?
+\paragraph{Predicting the future, given the past}
+Figure~\ref{fig:evoln}
+shows that for 21 CQVs that were observed roughly two years
+apart, 5 showed obvious signs of the phenomenon in one sector,
+and marginal or non-existence signs in the other.
+We emphasize that the periods themselves were usually stable to $<$0.1\%.
+However, this shape evolution
+suggests that CQVs have a duty cycle of $\approx$75\%.
 
-{\it Why would the prominence scenario tend toward corotation?}
+\paragraph{Why would the prominence scenario tend toward corotation?}
 This is analogous to quiescent
@@
 \label{sec:conclusion}
+
+We report on the existence of \ngoods\ objects that showed bonafide
+CQV behavior over at least one TESS sector between July~2018 and Sep~2022.
+Our search for these objects was restricted to dwarf stars bright enough
+for 1\% precision photometry with TESS over 1 hour ($T$$<$16),
+that were red ($\bprp<1.5$) and within 150\,pc of the Sun.
+We also note an additional \nmaybes\ candidate CQVs.
+
+Analyzing the light curves of these objects, we can make the following conclusions.
+
+\begin{itemize}
+	%
+	\item CQVs are {\it quasi}periodic.
+	%
+	\item The CQV phenomenon persists for at least 150\,Myr.
+	%
+	\item CQVs evolve over timescales that are both secular ($>$100\,cycles) and impulsive ($<$1 cycle).
+	%
+	\item The CQV duty cycle is $\approx 75$\%, based on 
+	the fraction of bonafide CQVs that ``turned off'' during TESS re-observations.
+\end{itemize}
+
+Many questions remain.
+After correcting for line-of-sight inclination, are
+most young M-dwarfs CQVs?  What observational signatures distinguish
+the proposed models (Figure~\ref{fig:f1}, bottom row)?  What
+organizational regularities characterize the CQV as a class of
+variable star?  What physically sets the extremes of the CQV population, such as
+the longest rotation periods, hottest stellar temperatures, and oldest
+stellar ages?  And finally, what connections, if any, do CQVs have to
+topics such as stellar evolution, M-dwarf magnetic fields, debris
+disks, and close-in exoplanets?
+While we have tried to point out possible connections, the most
+likely path toward definitive resolutions would be to observe a full
+phase curve of LP 12-502 using JWST/MIRI.
 
@@
 They both drafted the initial manuscript.
+L.G.B.~performed the cluster membership analysis.
 S.~R. vetted the results from the Fourier search.
-rotation- and lithium-based age analyses, and drafted the manuscript.
-L.A.H.~contributed to project execution.
+L.A.H.~contributed to project design.
 All authors assisted in manuscript revision.
@@
 
+\section{The LP 12-502 glitch}
+
+Figure~\ref{fig:lpzoom} shows an alternative view of cycles 1233-1247
+from Figure~\ref{fig:lp}.
+
+\begin{figure*}[!t]
+	\begin{center}
+		\centering
+		\includegraphics[width=0.96\textwidth]{TIC4029_zoom.png}
+		\vspace{-0.45cm}
+		\caption{
+			LP 12-502 is wild.
+		}
+		\label{fig:lpzoom}
+	\end{center}
+\end{figure*}
+
 \section{No additional power at 20~second cadence}

### 2023-06-16 paper/ms.tex
update ms

@@
   sharp and broad troughs.  The troughs are usually superposed over
-  smooth, spot-like modulation.  These objects are typically
-  10-100 million years (Myr) old, and they do not seem to have primordial gas-rich
+  smooth, spot-like modulation.  These objects are typically 10-100
+  million years (Myr) old, and they do not have primordial gas-rich
   disks.  Nonetheless, the preferred explanations for their optical
-  variability invoke long-lived material in orbit at the corotation
-  radius, for instance transiting dust clumps or stellar prominences.
-  Here, we report new CQVs discovered in TESS data collected between
-  July~2018 and Sep~2022.  Our search used two methods, the first
-  based on counting dips in phase-folded light curves, and the second
-  based on counting peaks in the Fourier domain.  From our analysis of
-  \nstarssearched\ M-dwarfs with $T$$<$16 and $d$$<$150\,pc, we find
-  \ngoods\ gold-standard CQVs.  Most of these discoveries are new,
-  and they include the brightest and closest
-  examples of this class of object known ($T$$\approx$10; $d$$\approx$20\,pc).  A few
-  objects are outliers among outliers; LP 12-502 for instance
-  shows four to eight local minima per cycle distributed over a ``dip
-  complex'' with a total duration that is nearly fixed over more than
-  1000 cycles.  Nonetheless, LP-502 at times also showed drastic shape
-  changes over less than one cycle.  More generally, we find that none
-  of the CQVs maintain a fixed light curve shape over timescales of
-  more than a few hundred cycles -- they are {\it quasi}periodic.
-  Although the physical explanation behind these objects remains
-  enigmatic, our sample may help clarify their origin.  Connections to
-  star, disk, and exoplanet evolution are emphasized.
+  variability invoke long-lived material in orbit at the Keplerian
+  corotation radius, for instance transiting dust clumps or stellar
+  prominences.  Here, we report new CQVs discovered in TESS data
+  collected between July~2018 and Sep~2022.  Our search used two
+  methods, the first based on counting dips in phase-folded light
+  curves, and the second based on counting peaks in the Fourier
+  domain.  From our analysis of \nstarssearched\ M-dwarfs with
+  $T$$<$16 and $d$$<$150\,pc, we find \ngoods\ gold-standard CQVs.
+  Most of these discoveries are new, and they include the brightest
+  and closest examples of this class of object known ($T$$\approx$11;
+  $d$$\approx$20\,pc).  A few objects are outliers among outliers; LP
+  12-502 for instance shows four to eight local minima per cycle
+  distributed over a ``dip complex'' with a total duration that is
+  nearly constant over more than 1000 cycles.  Nonetheless, LP-502 at
+  times also showed drastic shape changes over less than one cycle.
+  More generally, we find that none of the CQVs maintain a fixed light
+  curve shape over timescales of more than a few hundred cycles --
+  they are {\it quasi}periodic.  Although the physical explanation
+  behind these objects remains enigmatic, our sample may help clarify
+  their origin.  Connections to star, disk, and exoplanet evolution
+  are emphasized.
 \end{abstract}
@@
 
-The issue of what exactly causes the variability that defines the CQVs
-has yet to be resolved.  There are a few competing explanations.  All
-young M-dwarfs are spotted, which produces flux variations over
+The issue of what causes the variability that defines the CQVs has yet
+to be resolved.  There are a few competing explanations.  All young
+M-dwarfs are spotted, which produces flux variations over
 characteristic timescales of the rotation period, $P_{\rm rot}$, and
@@
 scenarios instead invoke sharp geometries with material extrinsic to
-the stellar surface \citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  In the ``clump''
-scenario, opaque dust clumps orbiting near the Keplerian corotation
-radius eclipse the star
+the stellar surface
+\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  In the
+``clump'' scenario, opaque dust clumps orbiting near the Keplerian
+corotation radius eclipse the star
 \citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  In the
@@
 examining stars known to be in young clusters
-\citep{2016AJ....152..114R,2017AJ....153..152S}, and automatically flagging rapid rotators
-with a large number of strong Fourier harmonics
-\citep{2019ApJ...876..127Z}.  The latter approach requires visual
-vetting, since most rapid rotators with many Fourier harmonics are
-false positives such as eclipsing binaries or multiple stars blended
-into a single photometric aperture.  In this work, we implemented a
-new search approach based on counting the number of sharp local minima
-in phase-folded light curves, while also using the previously tested
-Fourier approach.  We applied these two search techniques
-independently.
+\citep{2016AJ....152..114R,2017AJ....153..152S}, and automatically
+flagging rapid rotators with a large number of strong Fourier
+harmonics \citep{2019ApJ...876..127Z}.  The latter approach requires
+visual vetting, since most rapid rotators with many Fourier harmonics
+are false positives such as eclipsing binaries or multiple stars
+blended into a single photometric aperture.  In this work, we
+implemented a new search approach based on counting the number of
+sharp local minima in phase-folded light curves, while also using the
+previously tested Fourier approach.  We applied these two search
+techniques independently.
 
@@
 \label{subsec:fourier}
-For the Fourier analysis, we followed
-\citet{2019ApJ...876..127Z}.
+For the Fourier analysis, we followed \citet{2019ApJ...876..127Z}.
+
 {\bf todo for Rahul or Saul: explain the approach, in a few
@@
 off-target stars.  Typical false postive rates from our dip-counting
-pipeline were 5:1, with \nuniqdipflagged\ unique stars flagged, and about 20\% being
-labelled either ``good'' or ``possible'' CQVs; for the Fourier
-pipeline, {\bf the rate was X:Y, with ZZZZ unique stars flagged, and
-NN\% being labelled ``good'' or ``possible'' CQVs}.
+pipeline were 5:1, with \nuniqdipflagged\ unique stars flagged, and
+about 20\% being labelled either ``good'' or ``possible'' CQVs; for
+the Fourier pipeline, {\bf the rate was X:Y, with ZZZZ unique stars
+flagged, and NN\% being labelled ``good'' or ``possible'' CQVs}.
 
@@
 We estimated the stellar ages by making probabilistic spatial and
-kinematic associations between the CQVs and known clusters in the solar
-neighborhood.  For most of the stars in our sample, we were able to do
-this using BANYAN\,$\Sigma$
+kinematic associations between the CQVs and known clusters in the
+solar neighborhood.  For most of the stars in our sample, we were able
+to do this using BANYAN\,$\Sigma$
 \citep{2018ApJ...856...23G}.\footnote{\url{https://github.com/jgagneastro/banyan_sigma},
-git commit \texttt{394b486}} This algorithm calculates the
-probability that a given star belongs to one of 27 young
-clusters (or ``assocations'') within 150\,pc of the Sun, by modeling the clusters
-as multivariate Gaussians in 3-D position and 3-D velocity space.  
-We used the
-Gaia DR2 sky positions, proper motions, and distances to calculate the
-membership probabilities.  
-BANYAN\,$\Sigma$ in turn analytically marginalizes over the radial velocity dimension.
-We emphasize that the probabilities returned by this procedure are qualitatively
-useful, but quantitatively dubious due to the non-Gaussian
-nature of most groups within the
-solar neighborhood \citep[see e.g.][Figure~10]{2021ApJ...917...23K}.
+git commit \texttt{394b486}} This algorithm calculates the probability
+that a given star belongs to one of 27 young clusters (or
+``assocations'') within 150\,pc of the Sun, by modeling the clusters
+as multivariate Gaussians in 3-D position and 3-D velocity space.  We
+used the Gaia DR2 sky positions, proper motions, and distances to
+calculate the membership probabilities.  BANYAN\,$\Sigma$ in turn
+analytically marginalizes over the radial velocity dimension.  The
+probabilities returned by this procedure are qualitatively useful, but
+quantitatively dubious due to the non-Gaussian nature of most groups
+within the solar neighborhood \citep[see
+e.g.][Figure~10]{2021ApJ...917...23K}.
 
-For a few cases where BANYAN\,$\Sigma$
-yielded ambiguous results, we consulted the meta-catalog of young,
-age-dated, and age-dateable stars within a kiloparsec from
-\citet{2022AJ....163..121B}, and also searched the local volume around
-each star for co-moving
-companions.\footnote{\url{https://github.com/adamkraus/Comove}, git commit \texttt{278b372}}
+For a few cases where BANYAN\,$\Sigma$ yielded ambiguous results, we
+consulted the meta-catalog of young, age-dated, and age-dateable stars
+within a kiloparsec from \citet{2022AJ....163..121B}, and also
+searched the local volume around each star for co-moving
+companions.\footnote{\url{https://github.com/adamkraus/Comove}, git
+commit \texttt{278b372}}
 
@@
 
-Table~\ref{tab:thetable} lists the \ncpvsfound\ CQVs identified by
-our search, and some of their important properties.
-\ngoods\ objects demonstrate what we view as unambiguous
-characteristics of the CPV phenomenon in at least one TESS sector, and
-we refer to these as the ``gold sample''.
-The remaining \nmaybes\ CPV candidates were ambiguous (in our view),
-and their variability might be caused by say, multiple starspot
-groups.
+Table~\ref{tab:thetable} lists the \ncpvsfound\ CQVs identified by our
+search, and some of their important properties.  \ngoods\ objects
+demonstrate what we view as unambiguous characteristics of the CPV
+phenomenon in at least one TESS sector, and we refer to these as the
+``gold sample''.  The remaining \nmaybes\ CPV candidates were
+ambiguous (in our view), and their variability might be caused by say,
+multiple starspot groups.  Additional TESS data could help resolve
+their classification.
 
 The mosaic in Figure~\ref{fig:singlemosaic} shows phased light curves
-for the 40 brightest objects.
-The TESS sectors in which these objects were identified show
-anywhere from one to eight local minima per cycle.
-Some stars show relatively ordinary modulation during one continuous
-portion of the phased light curve, and highly structured modulation in
-the remainder of the cycle (e.g. TIC~206544316, TIC~224283342,
-TIC~402980664).
-Others show structured modulation over the entire span of a cycle
-(e.g. TIC~2234692, TIC~401789285, TIC~425933644, TIC~142173958).
-Others still show some mix between these two modes.
+for the 40 brightest objects.  The TESS sectors in which these objects
+were identified show anywhere from one to eight local minima per
+cycle.  Some stars show relatively ordinary modulation during one
+continuous portion of the phased light curve, and highly structured
+modulation in the remainder of the cycle (e.g. TIC~206544316,
+TIC~224283342, TIC~402980664).  Others show structured modulation over
+the entire span of a cycle (e.g. TIC~2234692, TIC~401789285,
+TIC~425933644, TIC~142173958).  Others still show some mix between
+these two modes.
 
@@
 Of our \ncpvsfound\ confirmed and candidate CQVs, \nnotfieldbanyan\
-were confidently associated with a nearby moving group or open
-cluster using BANYAN\,$\Sigma$.
-The relevant groups are listed in Table~\ref{tab:thetable}; their ages
-span $\approx$5-150\,Myr.
-The most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.
-The yield of CQVs in Sco-Cen (LCC / UCL / USco) is not surprising,
-since Sco-Cen contains the majority of pre-main-sequence stars in the
-solar neighborhood.
-The absence of CQVs in IC2602 and IC2391 is because those clusters are
-beyond 100\,pc, where the completeness of the TESS 120-second cadence
-data is below 10\%.
+were confidently associated with a nearby moving group or open cluster
+using BANYAN\,$\Sigma$.  The relevant groups are listed in
+Table~\ref{tab:thetable}; their ages span $\approx$5-150\,Myr.  The
+most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  The yield
+in Sco-Cen (LCC / UCL / USco) is not surprising, since Sco-Cen
+contains the majority of pre-main-sequence stars in the solar
+neighborhood.  The absence of CQVs in IC\,2602 and IC\,2391 can be
+understand by those clusters being beyond 100\,pc, where the
+completeness of the TESS 120-second cadence data is below 10\%; based
+on the abundance of CQVs in the 40\,Myr Tuc-Hor and Columba, the
+similarly-aged IC\,2602 and IC\,2391 clusters should have a large
+number of CQVs in the TESS full frame image data.
 
-Of the the \ngoodsfieldbanyan\ non-associated stars, one
-(TIC~302160226) is an obvious member of $\alpha$~Per ($t\approx
-86\pm16$\,Myr; \citealt{2022arXiv221109822B}).  For the other two
+Of the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
+find any association, one (TIC~302160226) is a member of $\alpha$~Per
+($t\approx 86\pm16$\,Myr;
+\citealt{2021A&A...645A..84M,2022arXiv221109822B}).  For the other two
 (TIC~58084670 and TIC~141146667), we are convinced of both their CPV
 status and their youth, but we were not able to confidently associate
-either star with any young groups.
-Both were noted as being in the ``diffuse'' Class~II YSO
-population by \citet{2021ApJ...917...23K}.
+either star with any young groups.  Both objects were noted as being in the
+``diffuse'' Class~II YSO population near the Sun by \citet{2021ApJ...917...23K}.
 That diffuse population may contain kinematic structures that have yet
-to be unravelled, however the absence of obvious young, co-moving
-stars within $\Delta r$=$40$\,pc and $\Delta v$=$3$\,km\,s$^{-1}$
-of these stars suggest that they may have run away from their birth
+to be unravelled.  However, the absence of obvious young, co-moving
+stars within $\Delta r$=$40$\,pc and $\Delta v$=$3$\,km\,s$^{-1}$ of
+our two CPVs suggest that they may have ``run away'' from their birth
 locations.
@@
 \citep{2019ApJ...876..127Z,2022AJ....163..144G}; at least one
-unambiguous case (EPIC~211070495) and a few other candidates were
-also previously known in the Pleiades \citep{2016AJ....152..114R}.
-While we expect to have been sensitive to CQVs in the nearby Hyades
-($\approx$700\,Myr), 
-again due to the specifics of the TESS 120-second selection function,
-we do not know at this time whether we would have been sensitive to
-such stars.
+unambiguous case (EPIC~211070495) and a few other candidates were also
+previously known in the Pleiades \citep{2016AJ....152..114R}.  While
+we expect to have been sensitive to CQVs in the nearby Hyades
+($\approx$700\,Myr), again due to the specifics of the TESS 120-second
+selection function, we do not know at this time whether we would have
+been sensitive to such stars.
 
-Finally, six CQVs were identified in the recently
-confirmed Argus association \citep{2019ApJ...870...27Z}.
-This serves as an indirect line of evidence supporting the reality,
-and youth, of that group.
+Finally, six CQVs were identified in the recently confirmed Argus
+association \citep{2019ApJ...870...27Z}.  This serves as an indirect
+line of evidence supporting the reality, and youth, of that group.
 
@@
 \paragraph{LP 12-502}
-While many CPVs had multiple sectors of data, in our view the most
-astounding dataset was available for LP 12-502 (TIP 402980664).
-Figure~\ref{fig:lp} shows all available data from Sectors 18, 19, 25,
-26, 53, 58, and 59; the star was observed at 120-second cadence for
-every sector during which it was on silicon.
+While many CPVs had multiple sectors of data, an astounding dataset
+was available for LP 12-502 (TIC 402980664; $d$=21\,pc, $J$=9.4,
+$T$=11.1).  Figure~\ref{fig:lp} shows all available data from Sectors
+18, 19, 25, 26, 53, 58, and 59; the star was observed at 120-second
+cadence for every sector during which it was on silicon.
 
 For the first 64 cycles, the star shows a pattern reminiscent of a
-(bizarre) eclipsing binary, with four obvious dips, that we denote
-dips 1, 2, 3, and 4 at phases -0.28, -0.08, 0, and 0.25 respectively.
-The depth of dips 1 and 3 remain roughly fixed.
-Over the 64 cycles, dip 4 {\it decreases} in depth by about 2\%, while
-dip 2 {\it increases} in depth, by about the same amount.
+(bizarre) eclipsing binary, with four obvious dips, that we dub
+dips $\{ 1, 2, 3, 4 \}$ at phases $\{ -0.28, -0.08, 0, 0.25 \}$
+respectively.  Over cycles 0 to 64, the depth of dips 1 and 3 remain
+roughly fixed.  However dip 4 {\it decreases} in depth by about 2\%,
+while dip 2 {\it increases} in depth, by about the same amount.
 
-There is then a 6-month (184 cycle) gap out to Cycle 248.
-At this time, dip 1 is still present, at the same phase, and with
-roughly the same depth.
+{\bf todo: discussion needs auto-measured phases at fixed t0...}
+There is then a 6-month (184 cycle) gap out to Cycles 248-315, which
+show an intricately structured dip complex.
+Between Cycles 248-264, there are at least six dips, at phases $\{
+  -0.47, -0.28, -0.08,  0.  ,  0.06,  0.17 $\}.
+There is ``state switch'', roughly at BTJD 1993.5 - cycle 262.
+The lower black points in cycles 248--264 shift upward during cycle
+262, never to return.
+A large flare occurred a few cycles earlier, at BTJD 1989.2 (which may
+or may not be related).
+Regardless, the depths of the latter three-dip complex remain roughly
+the same after the state-switch;
+the first obvious dip in the sequence disappears.
+Ah, and the flux changes by 3.5\% over about 22 minutes (0.02\,$P$),
+which is the steepest slope exhibited anywhere in this object's
+remarkable dataset.
+During the beginning of Sector~26 (Cycles 283-298), there are seven
+clear dips per cycle.
+The the second orbit of this sector,
+there is another state-switch at BTJD 2030.7, immediately during a
+flare.   (And therefore likely caused by the flare!)
 
-%TODO continue writing about this.  What is the exact TJD of the jump?
+Finally, sectors 53--58 (cycles 1233-1481) showed between four and six
+dips per cycle, at various times.  
+Some dips, for instance the one at $\phi = -0.03$, remain stable in
+depth and duration over this five month interval.
+Other dips, such as the one at $\phi = +0.04$ in cycles 1233-1264,
+disappear entirely.
+Other dips grow, like the one at $\phi = +0.06$ between cycles 1499
+and 1481.
+Also, there is the epic state switch during cycles 1233-1247.
+Which appears to happen over less than one cycle, and there is no
+associated flare.
+
+Some are sharktooths.
+Dip1 in cycle48-64 is one.
+Dip1 in cycle 1466-1481 is one.
+It is definitely asymmetric!
 
@@
 			{\it Bottom:}
-      Evolution of LP 12-502 ($P$=18.5604\,h) at fixed period and epoch over three
-      years; small text denotes cycle number.  The TESS pointing law
-      dictates time gaps; larger gaps tend to yield larger shape
-      changes.
+      Evolution of LP 12-502 ($P$=18.5604\,h) at fixed period and
+      epoch over three years; small text denotes cycle number.  
+      There are 200 binned black points per cycle.
+      The TESS pointing law dictates time gaps; larger gaps tend to
+      yield larger shape changes.
       The dips usually evolve over tens to hundreds of cycles.
@@
 dip-based and Fourier-based searches, respectively.
-They both drafted the initial manuscript.
-L.G.B.~performed the cluster membership analysis.
-S.~R. vetted the results from the Fourier search.
+L.G.B.~drafted the initial manuscript, and performed the cluster
+membership analysis.
+S.~R. and R.~J. vetted the results from the Fourier search.
 L.A.H.~contributed to project design.

### 2023-06-16 drivers/plot_tic4029_segments.py
tic4029 hack

@@ -1,0 +1,31 @@
+"""
+LP 12-502 state-switch plots  (currently quick hack)
+"""
+
+from astropy.io import fits
+import matplotlib.pyplot as plt
+from astrobase.lcmath import (
+    phase_magseries, phase_bin_magseries, sigclip_magseries,
+    find_lc_timegroups, phase_magseries_with_errs, time_bin_magseries
+)
+from aesthetic.plot import set_style
+
+
+# sector 25 showed some 
+#hl = fits.open("/Users/luke/.lightkurve-cache/mastDownload/TESS/tess2020133194932-s0025-0000000402980664-0182-s/tess2020133194932-s0025-0000000402980664-0182-s_lc.fits")
+# sector 26
+hl = fits.open("/Users/luke/.lightkurve-cache/mastDownload/TESS/tess2020160202036-s0026-0000000402980664-0188-s/tess2020160202036-s0026-0000000402980664-0188-s_lc.fits")
+
+
+d = hl[1].data
+
+hl.close()
+
+bd = time_bin_magseries(d['TIME'], d['PDCSAP_FLUX'], binsize=1200, minbinelems=1)
+
+
+set_style("science")
+fig, ax = plt.subplots(figsize=(12,4))
+ax.plot(bd['binnedtimes'], bd['binnedmags'], c='k', zorder=2)
+
+plt.show()

### 2023-06-16 paper/ms.tex
update ms

@@
 18, 19, 25, 26, 53, 58, and 59; the star was observed at 120-second
-cadence for every sector during which it was on silicon.
+cadence whenever it was observable by TESS.
+Measuring the PDM peak period over each sector independently yielded
+an average $\langle P \rangle = 18.5560$\,hr, with a difference
+between the maximum and minimum sector-level period of about one minute.
+Based on this range, the period is therefore stable to at least one
+minute ($\pm$0.017\,hr) over the three year baseline.
+However, in detail, a period shift of $\pm$1\,minute yields major
+phase drifts over the 3 year baseline; that time interval
+corresponds to roughly 1/1000$^{\rm th}$ of a period; we have
+observed 1500 cycles.
+The achievable period precision, $\sigma_{\rm P}$, can be estimated as
+\begin{equation}
+  \sigma_{\rm P} = \frac { \sigma_{\rm phi} P } { N_{\rm baseline} },
+\end{equation}
+for $N_{\rm baseline}$ the number of cycles in the observed baseline and
+$\sigma_{\rm phi}$ the phase precision with which any one feature (e.g.~a
+dip) can be tracked.
+Assuming $\sigma_{\rm phi} \approx 0.01$ yields an expected period precision
+$\sigma_{\rm P} \approx 0.45 seconds \approx 1.2\times 10^{-4}\,hr$.
+By visually fine-tuning over a grid in period, we eventually 
+found $P=18.5611 \pm 0.0001$\,hr, which seems to track certain
+features in the LP 12-502 light curve over its entire baseline.
 
+What features are observed?
 For the first 64 cycles, the star shows a pattern reminiscent of a
@@
 the first obvious dip in the sequence disappears.
-Ah, and the flux changes by 3.5\% over about 22 minutes (0.02\,$P$),
+Ah, and the deepest dip shows a flux exercusion of 3.5\% over about 22 minutes (0.02\,$P$),
 which is the steepest slope exhibited anywhere in this object's
 remarkable dataset.
-During the beginning of Sector~26 (Cycles 283-298), there are seven
-clear dips per cycle.
-The the second orbit of this sector,
+During Sector~26 (Cycles 283-315), there are seven clear dips per
+cycle, and perhaps even eight, if one counts five dips in the largest
+dip complex.
+During the second orbit of this sector,
 there is another state-switch at BTJD 2030.7, immediately during a
@@
 			{\it Bottom:}
-      Evolution of LP 12-502 ($P$=18.5604\,h) at fixed period and
+      Evolution of LP 12-502 ($P$=18.6\,h) at fixed period and
       epoch over three years; small text denotes cycle number.  
@@
 Heising-Simons 51~Pegasi~b Fellowship (LGB)
+TIC 402980664 was observed at 120-second cadence thanks to the TESS Guest
+Investigator programs G022252 (PI: J.~Schlieder; Sectors 18, 19, 25,
+26) and G04168 (PI: R.~Jayaraman; Sector 53).
 

### 2023-06-16 tests/hack_4029_periods.py
add 4029 period hack

@@ -1,0 +1,15 @@
+import numpy as np
+periods = [
+    0.7732752056726647,
+    0.7731461580225912,
+    0.7732813973828846,
+    0.7735711202923402,
+    0.7729424491300968,
+    0.7731911738307666,
+    0.7727680841024896,
+]
+mean_period = np.mean(periods)
+
+print(f"<P> = {mean_period*24:.5f} hr")
+print(f"max(P) = {max(periods)*24:.5f} hr")
+print(f"min(P) = {min(periods)*24:.5f} hr")

### 2023-06-16 paper/ms.tex
add 4029 appendix plot

@@
 
-\section{The LP 12-502 glitch}
+\section{LP 12-502}
 
-Figure~\ref{fig:lpzoom} shows an alternative view of cycles 1233-1247
-from Figure~\ref{fig:lp}.
+{\it The light curve}---
+Figure~\ref{fig:lplc} shows an alternative view of the LP-502 light
+curve from Figure~\ref{fig:lp}, 
+split into ``time chunks'' wherever there was more than half a day of
+missing data in the TESS light curve.
+We binned the light curve to 15-minute intervals for visual clarity,
+and required at least one (120-second cadence) flux measurement per
+bin.
+Points more than 2.5$\sigma$ above the median are drawn in gray, also
+for visual clarity.
+Missing data are not drawn (a common plotting error when ``drawing''
+light curves, rather than showing a scatter plot).
+
+{\it State switches}---
+Figure~\ref{fig:lpzoom} shows an alternative view of cycles 1233-1247.
+
+\begin{figure*}[!t]
+	\begin{center}
+		\centering
+		\includegraphics[width=0.96\textwidth]{tic4029_segments.pdf}
+		\vspace{-0.2cm}
+		\caption{
+			LP 12-502 light curve, split into time chunks.
+		}
+		\label{fig:lplc}
+	\end{center}
+\end{figure*}
 
@@
 		\caption{
-			LP 12-502 is wild.
+			LP 12-502 cycles 1233-1247, showing the most dramatic state
+      change observed over the three year baseline.
 		}

### 2023-06-16 complexrotators/plotting.py

@@ -2458,7 +2458,7 @@ def plot_tic4029_segments(outdir):
     set_style('science')
 
     f = 0.5
-    fig, ax = plt.subplots(figsize=(f*8.5, f*11))
+    fig, ax = plt.subplots(figsize=(f*8.5, f*9.5))
 
     ############
     # get data #
@@ -2528,7 +2528,7 @@ def plot_tic4029_segments(outdir):
         # between time gaps.
         _, _groups = find_lc_timegroups(x, mingap=0.5/24)
         for _g in _groups:
-            ax.plot(x[_g], y[_g], c='k', zorder=1, lw=0.2, alpha=0.3)
+            ax.plot(x[_g], y[_g], c='k', zorder=1, lw=0.2, alpha=0.15)
 
         _, _groups = find_lc_timegroups(sx, mingap=0.5/24)
         for _g in _groups:

### 2023-06-20 paper/ms.tex
update ms

@@
 %%%%%%%%
+
 % dip-counting pipeline
@@
 \input{vals_cqv_table_statistics}
+
+\newcommand{\ntwoyear}{21} % TODO: update
+\newcommand{\ntwoyearturnedoff}{5} % TODO: update
 
@@
   smooth, spot-like modulation.  These objects are typically 10-100
-  million years (Myr) old, and they do not have primordial gas-rich
+  million years (Myr) old;  they do not have primordial gas-rich
   disks.  Nonetheless, the preferred explanations for their optical
@@
   prominences.  Here, we report new CQVs discovered in TESS data
-  collected between July~2018 and Sep~2022.  Our search used two
-  methods, the first based on counting dips in phase-folded light
-  curves, and the second based on counting peaks in the Fourier
-  domain.  From our analysis of \nstarssearched\ M-dwarfs with
+  collected between July~2018 and Sep~2022. 
+%  Our search used two
+%  methods, the first based on counting dips in phase-folded light
+%  curves, and the second based on counting peaks in the Fourier
+%  domain. 
+   From our analysis of \nstarssearched\ M-dwarfs with
   $T$$<$16 and $d$$<$150\,pc, we find \ngoods\ gold-standard CQVs.
@@
   $d$$\approx$20\,pc).  A few objects are outliers among outliers; LP
-  12-502 for instance shows four to eight local minima per cycle
-  distributed over a ``dip complex'' with a total duration that is
-  nearly constant over more than 1000 cycles.  Nonetheless, LP-502 at
-  times also showed drastic shape changes over less than one cycle.
+  12-502 for instance shows a ``dip complex'' with a total duration that is
+  nearly constant over more than 1000 cycles, 
+  but exhibits anywhere from four to eight local minima per cycle.  
+  LP-502 also at
+  times showed drastic shape changes over less than one cycle.
   More generally, we find that none of the CQVs maintain a fixed light
@@
   behind these objects remains enigmatic, our sample may help clarify
-  their origin.  Connections to star, disk, and exoplanet evolution
-  are emphasized.
+  their origin.  In particular, we highlight the plausibility of a disintegrating
+  planetesimal swarm model.
+  Connections to star, disk, and exoplanet evolution are emphasized.
 \end{abstract}
@@
 search, and some of their important properties.  \ngoods\ objects
-demonstrate what we view as unambiguous characteristics of the CPV
+demonstrate what we view as unambiguous characteristics of the CQV
 phenomenon in at least one TESS sector, and we refer to these as the
-``gold sample''.  The remaining \nmaybes\ CPV candidates were
+``gold sample''.  The remaining \nmaybes\ CQV candidates were
 ambiguous (in our view), and their variability might be caused by say,
@@
 \citealt{2021A&A...645A..84M,2022arXiv221109822B}).  For the other two
-(TIC~58084670 and TIC~141146667), we are convinced of both their CPV
+(TIC~58084670 and TIC~141146667), we are convinced of both their CQV
 status and their youth, but we were not able to confidently associate
@@
 stars within $\Delta r$=$40$\,pc and $\Delta v$=$3$\,km\,s$^{-1}$ of
-our two CPVs suggest that they may have ``run away'' from their birth
+our two CQVs suggest that they may have ``run away'' from their birth
 locations.
@@
 
-\subsection{CQV evolution}
-
-\paragraph{LP 12-502}
-While many CPVs had multiple sectors of data, an astounding dataset
-was available for LP 12-502 (TIC 402980664; $d$=21\,pc, $J$=9.4,
-$T$=11.1).  Figure~\ref{fig:lp} shows all available data from Sectors
+\section{CQV evolution}
+
+\subsection{Evolution over two year baseline}
+
+Figure~\ref{fig:evoln} shows ``before'' and ``after'' views
+of \ntwoyear\ CQVs for which observations were available at least two years
+apart.
+Of the \ntwoyear\ CQVs for which such a baseline was available,
+\ntwoyearturnedoff\ showed obvious signs of the phenomenon in one sector,
+and marginal or non-existence signs in the other.
+We emphasize that the periods themselves were all stable to $<$0.1\%.
+Broadly speaking, this shape evolution
+suggests that CQVs have a duty cycle of $\approx$75\%.
+
+\begin{figure*}[!t]
+	\begin{center}
+		\centering
+		\includegraphics[width=0.9\textwidth]{lc_mosaic_dlt150_good_allchangers_2count_showtitles.png}
+		\vspace{-0.2cm}
+		\caption{
+			{\bf Evolution of CQVs}: ``Before and
+			after'...  Panels
+			in the top two rows are separated by two years
+			($\approx$$10^3$ cycles); each panel shows one month.
+			Periods are listed in hours. 
+			{\bf todo: fix the plot and the caption.}
+			%			\vspace{-0.8cm}
+		}
+		\label{fig:evoln}
+	\end{center}
+\end{figure*}
+
+\subsection{Evolution over adjacent sectors, \& LP 12-502}
+\begin{figure*}[!t]
+	\begin{center}
+		\centering
+		\includegraphics[width=0.9\textwidth]{TIC_402980664_P18.5611_2min_phase_timegroups_mosaic_ymin-4.8_ymax3.pdf}
+		\vspace{-0.45cm}
+		\caption{
+			Evolution of LP 12-502 ($P$=18.6\,h) at fixed period and
+			epoch over three years. 
+			Each panel shows one (stacked) TESS orbit; small text denotes relative cycle number.
+			There are 200 binned black points per cycle.
+			The TESS pointing law dictates time gaps; larger gaps tend to
+			yield larger shape changes.
+			The dips usually evolve over tens to hundreds of cycles.
+			However cycles 1233-1264 show a dip that ``switched'' from a depth
+			and duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than
+			one cycle.
+		}
+		\label{fig:lp}
+	\end{center}
+
+\end{figure*}
+
+\subsubsection{LP 12-502 observations}
+While many CQVs had multiple sectors of adjacent or nearly-adjacent data
+LP 12-502 (TIC 402980664; $d$=21\,pc, $J$=9.4,
+$T$=11.1) stood out as an outlier among the CQV class.
+Figure~\ref{fig:lp} shows all available data from Sectors
 18, 19, 25, 26, 53, 58, and 59; the star was observed at 120-second
@@
 \begin{equation}
-  \sigma_{\rm P} = \frac { \sigma_{\rm phi} P } { N_{\rm baseline} },
+  \sigma_{\rm P} = \frac { \sigma_{\rm \phi} P } { N_{\rm baseline} },
 \end{equation}
@@
 Assuming $\sigma_{\rm phi} \approx 0.01$ yields an expected period precision
-$\sigma_{\rm P} \approx 0.45 seconds \approx 1.2\times 10^{-4}\,hr$.
+$\sigma_{\rm P} \approx 0.45 {\rm sec} \approx 1.2\times 10^{-4}\,{\rm hr}$.
 By visually fine-tuning over a grid in period, we eventually 
@@
 
-What features are observed?
-For the first 64 cycles, the star shows a pattern reminiscent of a
-(bizarre) eclipsing binary, with four obvious dips, that we dub
-dips $\{ 1, 2, 3, 4 \}$ at phases $\{ -0.28, -0.08, 0, 0.25 \}$
-respectively.  Over cycles 0 to 64, the depth of dips 1 and 3 remain
-roughly fixed.  However dip 4 {\it decreases} in depth by about 2\%,
-while dip 2 {\it increases} in depth, by about the same amount.
-
-{\bf todo: discussion needs auto-measured phases at fixed t0...}
+What features are observed?  For the first 64 cycles, the star shows a
+pattern reminiscent of a (bizarre) eclipsing binary, with four obvious
+dips, that we dub dips $\{ 1, 2, 3, 4 \}$ at phases $\{ -0.28, -0.08,
+0, 0.25 \}$ respectively.  Over cycles 0 to 64, the depth of dips 1
+and 3 remain roughly fixed.  However dip 4 {\it decreases} in depth by
+about 2\%, while dip 2 {\it increases} in depth, by about the same
+amount.  During cycles 48-64, it also seems that a fifth dip may be
+emerging, in the main ``large'' dip group.
+
 There is then a 6-month (184 cycle) gap out to Cycles 248-315, which
-show an intricately structured dip complex.
-Between Cycles 248-264, there are at least six dips, at phases $\{
-  -0.47, -0.28, -0.08,  0.  ,  0.06,  0.17 $\}.
-There is ``state switch'', roughly at BTJD 1993.5 - cycle 262.
-The lower black points in cycles 248--264 shift upward during cycle
-262, never to return.
-A large flare occurred a few cycles earlier, at BTJD 1989.2 (which may
-or may not be related).
-Regardless, the depths of the latter three-dip complex remain roughly
-the same after the state-switch;
-the first obvious dip in the sequence disappears.
-Ah, and the deepest dip shows a flux exercusion of 3.5\% over about 22 minutes (0.02\,$P$),
+show two intricately structured dip complexes, plus a single (leading)
+dip.  The single leading dip is present at roughly the same phase as
+in cycles 0-64; we believe they are the same struture.  Along a
+similar line of logic, it seems plausible that the first ``dip
+complex'' during cycles 248-264 represents an evolution of the initial
+complex seen during cycles 0-64, though with greatly reduced depth.
+During cycles 266-310, a moving local minimum develops between the two
+complexes; this feature is best visualized on the river plots.
+
+However, the second dip complex during cycles 248-315 is perhaps the
+most intricate.  During e.g.~cycles 283-298, this single complex
+clearly shows six local minima.  The deepest dip is very sharp: it
+shows a flux exercusion of 3.5\% over about 22 minutes (0.02\,$P$),
 which is the steepest slope exhibited anywhere in this object's
-remarkable dataset.
-During Sector~26 (Cycles 283-315), there are seven clear dips per
-cycle, and perhaps even eight, if one counts five dips in the largest
-dip complex.
-During the second orbit of this sector,
-there is another state-switch at BTJD 2030.7, immediately during a
-flare.   (And therefore likely caused by the flare!)
+remarkable dataset.  After the sharp dip, there is a roughly
+exponential fall-off spanning about a quarter of a period, punctuated
+by coherent local minima and maxima.  The sharp leading dip only
+decreases in its sharpness during cycles 299-315, during a sudden
+state-switch at BTJD 2030.7, which happens immediately during a flare.
+(And therefore which is likely caused by the flare!) To our best
+knowledge, this type of of behavior has not yet been observed on any
+comparable object.
 
 Finally, sectors 53--58 (cycles 1233-1481) showed between four and six
-dips per cycle, at various times.  
-Some dips, for instance the one at $\phi = -0.03$, remain stable in
-depth and duration over this five month interval.
-Other dips, such as the one at $\phi = +0.04$ in cycles 1233-1264,
-disappear entirely.
-Other dips grow, like the one at $\phi = +0.06$ between cycles 1499
-and 1481.
-Also, there is the epic state switch during cycles 1233-1247.
-Which appears to happen over less than one cycle, and there is no
-associated flare.
-
-Some are sharktooths.
-Dip1 in cycle48-64 is one.
-Dip1 in cycle 1466-1481 is one.
-It is definitely asymmetric!
-
-%TODO; make a version (for talks) showing dips 1234 over cycles0-64
-%TODO include +/- 1/3 as important durations.
-%TODO: note that duration between the minimum of "dip1" and "dip4" is
-%      kind of always 0.53
-
-\paragraph{None of them are strictly periodic}
-
-A periodic signal does not modulate.
-
-\begin{figure*}[!t]
-	\begin{center}
-    \centering
-    \includegraphics[width=0.9\textwidth]{TIC_402980664_P18.5604_2min_phase_timegroups_mosaic.pdf}
-		\vspace{-0.45cm}
-		\caption{
-			{\it Bottom:}
-      Evolution of LP 12-502 ($P$=18.6\,h) at fixed period and
-      epoch over three years; small text denotes cycle number.  
-      There are 200 binned black points per cycle.
-      The TESS pointing law dictates time gaps; larger gaps tend to
-      yield larger shape changes.
-      The dips usually evolve over tens to hundreds of cycles.
-      However cycles 1233-1264 show a dip that ``switched'' from a depth
-      and duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than
-      one cycle.
-		}
-		\label{fig:lp}
-	\end{center}
-\end{figure*}
-
-\begin{figure*}[!t]
-	\begin{center}
-		\centering
-		\includegraphics[width=0.9\textwidth]{lc_mosaic_dlt150_good_allchangers_2count_showtitles.png}
-		\vspace{-0.2cm}
-		\caption{
-			{\bf Evolution of CQVs}: ``Before and
-			after'...  Panels
-			in the top two rows are separated by two years
-			($\approx$$10^3$ cycles); each panel shows one month.
-			Periods are listed in hours. 
-			{\bf todo: fix the plot and the caption.}
-			%			\vspace{-0.8cm}
-		}
-		\label{fig:evoln}
-	\end{center}
-\end{figure*}
+dips per cycle, at various times.  Some dips remain stable in depth
+and duration over this five month interval.  Other dips grow, like the
+one at $\phi = +0.06$ between cycles 1499 and 1481.  Other dips, such
+as the one at $\phi = +0.12$ in cycles 1233-1264, disappear entirely.
+The most dramatic state switch occurs during cycles 1233-1247, when a
+large dip ``switches'' from a depth of 3\% and duration of 3 hours to
+a depth of 0.3\%, and a duration of 1 hour.
+
+\subsubsection{LP 12-502 interpretation}
+
+{\sc Dips can disappear instantaneously}---The state switches shown in cycles
+1233-1264 and 299-315 reveal that the dips can be {\it independent}
+and {\it additive}.  They also show that although dip depth is
+generally not preserved over a state switch, {\it ingress time}
+usually is conserved.
+It other words, throughout cycles 1233-1264, there are three local
+minima between phases of 0 and 0.3.  They all have identical ingress
+times.  The shape change during the transition strongly suggests that
+it was simply the leading dip that ``turned off', while the trailing
+two dips remained fixed.  The state switches during cycles 299-315 and
+248-264 share the same characteristic: it is always the {\it leading}
+dip of a complex that ``switches off'', leaving the trailing dips in
+its wake.
+
+{\sc Dips grow more slowly}---Although there are a few instances in
+which we observe dips to ``switch off'' over less than one cycle, dip
+growth seems to happen more slowly.  For instance, the dip that grows
+between phase 0 and 0.1 between cycles 260-290 begins to become
+visible around BTJD 1993.2, and growths in depth by about 2\% over
+about six cycles, to become easily detectable by eye by BTJD 1997.7.
+The evolution of this particular dip is most clear in the river plots.
+The evolution of the latter dip group in cycles 1410-1481 is another
+example of this slow mode of dip growth.
+
+{\sc Dip asymmetries}---The observed asymmetries include both sharp
+leading ingresses (e.g. for the main cycle 248-315 dip complex), and
+also extended ingresses with relatively sharper {\it egresses} (e.g.
+the deepest feature during cycles 1420-1464).  Some dips do not show
+detectable asymmetry at all.
+
+The asymmetry is an important characteristic because it can help
+diagnose the optical depth of the occulting material as a function of
+orbital phase angle.  Sharp leading edges with trailing exponential
+egresses for instance have been previously seen for transiting
+exocomets and disintegrating rocky bodies
+\citep[e.g.][]{2012ApJ...752....1R,2012A&A...545L...5B,2015Natur.526..546V,2019A&A...625L..13Z}.
+
+It is tempting to interpret certain features of the LP 12-502 light
+curve in this framework of a disintegrating planetesimal swarm.  For
+instance, the complex in cycles 248-298 could be well-fit by a sharp
+leading edge that decays over 0.2\,$P$ (3.7\,hours).  The earlier
+complex, during cycles 248-264 (pre-state-switch), could be fit by a
+similar profile.  There are two degenerate explanations for the small
+``wiggles'' in the exponential decay.  In one explanation, the decay
+timescale is fast ($\approx$0.03\,$P$), and there are up to five
+exocomets, superposed.  In the other, there is only one main
+``launching body'', and the material it ejects either has some
+sub-structure, or else is passing across (and in synchronicity with) a
+star with heavily substructured starspots across its surface.
+
+While the number of free parameters in this type of model is somewhat
+dizzying, we have no right to believe that nature need be
+simple.  Every dip in the exocomet tail model would have as free
+parameters the dip phase, the duration (captured by an exponential
+decay timescale), and the dip depth.  In detail, the impact parameter
+would also enter.  Allotting four free parameters per dip yields up to
+32 free parameters for the light curve at the most complicated times
+(assigning one exocomet per local minimum).
+
+Perhaps the most glaring issue with the planetesimal swarm idea is
+that a large number of the dips show asymmetries in the {\it wrong
+direction} relative to the naive expectation of a trailing comet tail.
+Dust forward scattering could be one possible way out; so too could
+simply invoking non-exponentially decaying dust
+distributions as a function of azimuth.
+
+{\sc Dip durations}---The shortest timescale that any of the {\it
+individual} dips seem to occur over is $\approx$0.07\,$P$, or about
+1.3\,hours.  For a $M_\star=0.25\,M_\odot$, $R_\star=0.5\,R_\odot$
+star, the characteristic timescale $T_{\rm dur}$ for the transit of a
+point-source over the stellar equator at $P=18.6\,$hours is also
+0.07\,$P$.  This means that while some of the LP 12-502 dips are
+sufficiently long to require structures that are extended in orbital
+azimuth, some are short enough that their durations are consistent
+with point sources.
 
@@
 \label{sec:discussion}
+
+\paragraph{Quasiperiodicity}
+A periodic signal does not modulate; the CQVs are {\it quasi}periodic.
+This is a qualitative departure from
+the ``persistent'' {\it vs.} ``transient'' flux dip distinction from 
+\citet{2017AJ....153..152S}.  While the dips can appear persistent
+over timescales of even up to 100 cycles, our view is that all the CQV
+dips seem to be transient over timescales of more than 1000 cycles
+(Figure~\ref{fig:evoln}).
+
+With that said, one might expect a truly quasiperiodic process to be
+able to explore all phase angles with equal weight.  LP 12-502, and
+many other CQVs, have preferred phases.  For LP 12-502 for instance,
+all of the dips happen over a fixed phase duration of two thirds of
+the period.  Phases between $\{0.45,0.8\}$ are ``out of limits'' for
+any dipping material.  We interpret this as evidence
+either that {\it a)} some aspect the stellar magnetic field is
+strongly asymmetric, and can generate and hold stellar prominences at
+corotation, but only over two thirds of the great circle,
+or {\it b)} there is a physical structure -- for instance a
+disintegrating planetesimal swarm -- that is distributed over an arc
+of about 240$^\circ$.
 
@@
 
+\paragraph{Connection to close-in exoplanets}
+The concordance model for planet formation invokes the presence of an accretion
+disk.
+The disk is truncated (by what?) at the magnetospheric truncation radius,
+which happens to often coincidentally be at the Keplerian corotation radius.
+In such a scenario, planetesimals and boulders can migrate inward due to
+Type X migration (CITE),
+until they hit a ``dust trap'' at the inner wall.
+Some support for this model comes from both the rotation periods of classical
+and weak-lined T Tauri stars
+(CITE Rebull2018,2019),
+from near-infrared interferometric observations that detect thermal
+emission from the disk wall (CITE CITE),
+and from the turn-over in the exoplanet orbital period distribution,
+which occurs around 5-10 days for FGK stars, 
+and perhaps even closer-in for M-dwarfs (CITE Petigura2022, and CITE for M-dwarfs).
+
 \section{Conclusions}
@@
 that were red ($\bprp<1.5$) and within 150\,pc of the Sun.
-We also note an additional \nmaybes\ candidate CQVs.
+These objects are listed in Table~\ref{tab:thetable}.
+This table also includes an additional \nmaybes\ candidate CQVs, whose
+designation is less certain.
 
@@
 	%
-	\item The CQV phenomenon persists for at least 150\,Myr.
+	\item The CQV phenomenon persists for at least 150\,Myr, based on the
+	existence of CQVs in AB Dor, the Pleiades, and Psc-Eri.
 	%
@@
 	%
-	\item The CQV duty cycle is $\approx 75$\%, based on 
+	\item Individual CQVs can show multiple, slightly different periods.  LP 12-502
+	is one example; others are included in Table~\ref{tab:thetable}.
+	%
+	\item The population-averaged duty cycle for CQVs seems to be $\approx 75$\%, based on 
 	the fraction of bonafide CQVs that ``turned off'' during TESS re-observations.
@@
 		\caption{
-      Validation plots used to label CQVs (the complete figure
-      set of \ncpvsfound\ images is available online).
+      {\bf Validation plots used to label CQVs}.  The complete figure
+      set of \ncpvsfound\ images is available online.
       Panels are as follows.
@@
 		\caption{
-			LP 12-502 light curve, split into time chunks.
+      {\bf LP 12-502 light curve}, split into time chunks.
 		}
@@
 	\end{center}
+\end{figure*}
+
+\begin{figure*}[!t]
+	\begin{center}
+    \centering
+    \includegraphics[width=0.45\textwidth]{ANNOTATED_resid_TIC_402980664_P18.5611_2min_phase_timegroups.png}
+		\vspace{-0.45cm}
+		\caption{
+      {\bf Alternative view of the evolution of LP 12-502}
+      (Figure~\ref{fig:lp}), arranged to emphasize changes in transit
+      times.  There are 200 binned black points per cycle; a two-harmonic
+      sinusoid has been subtracted over specific chunks in time ({\bf see text}).
+      Vertical gray lines are underplotted to help guide the eye to instances
+      in which preferred dip phases synchronize over long baselines.
+      The orange and green lines guide the eye to where dips
+      appear to change the positions of their local minima.
+		}
+		\label{fig:lp2}
+	\end{center}
+\end{figure*}
+
+\begin{figure*}[!t]
+	\begin{center}
+		\subfloat{
+			\includegraphics[width=0.43\textwidth]{TIC402980664_river_gist_stern_0_64_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
+			\includegraphics[width=0.43\textwidth]{TIC402980664_river_gist_stern_248_315_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
+		}
+	\vspace{0.4cm}
+			\subfloat{
+		\includegraphics[width=0.43\textwidth]{TIC402980664_river_gist_stern_1411_1481_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
+				\includegraphics[width=0.43\textwidth]{TIC402980664_river_gist_stern_1233_1265_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
+	}
+	\end{center}
+	\caption{
+    {\bf River plots of LP 12-502}, showing (clockwise from top-left) Sectors 18-19, 25-26, 53, and 58-59.
+    A two-harmonic
+    sinusoid has been subtracted over specific chunks in time ({\bf see text}).
+	}
+	\label{fig:lpriver0}
 \end{figure*}
@@
 		\caption{
-			LP 12-502 cycles 1233-1247, showing the most dramatic state
+			{\bf LP 12-502 cycles 1233-1247}, showing the most dramatic state
 			change observed over the three year baseline.

### 2023-06-20 complexrotators/cometmodel.py
comet model: clean up

@@ -102,7 +102,7 @@ def rchordit(b, Rstar):
     d1 = np.sqrt(1.-b*b)
     return d1*2*Rstar
 
-def mu_comet_model(tin, y, yerr, tmid, b_impact, cmax, lam, P, Mstar, Rstar,
+def mu_comet_model(tin, tmid, b_impact, cmax, lam, P, Mstar, Rstar,
                    ulimb, extra=False):
 
     tin_min = tin.min()

### 2023-06-20 tests/test_exocomet_fit.py

@@ -35,7 +35,7 @@ def lnlike(theta, t, f, ferr, ulimb, verbose=False):
 
     tmid, impact, ce, lamb, period = theta
 
-    model = mu_comet_model(t*u.day, f, ferr, tmid*u.day, impact, ce,
+    model = mu_comet_model(t*u.day, tmid*u.day, impact, ce,
                            lamb/u.radian, period*u.day, Ms, Rs, ulimb)
 
     chi2 = np.power((f-model)/ferr, 2.)
@@ -49,7 +49,7 @@ def plotfit(theta, t, f, ferr, ulimb=None):
 
     tmid, impact, ce, lamb, period = theta
 
-    model = mu_comet_model(t*u.day, f, ferr, tmid*u.day, impact, ce,
+    model = mu_comet_model(t*u.day, tmid*u.day, impact, ce,
                            lamb/u.radian, period*u.day, Ms, Rs, ulimb)
 
     plt.close("all")
@@ -72,7 +72,7 @@ def plotfit_phase(theta, t, f, ferr, t0, ulimb=None):
 
     tmid, impact, ce, lamb, period = theta
 
-    model = mu_comet_model(t*u.day, f, ferr, tmid*u.day, impact, ce,
+    model = mu_comet_model(t*u.day, tmid*u.day, impact, ce,
                            lamb/u.radian, period*u.day, Ms, Rs, ulimb)
 
     plt.close("all")
@@ -140,7 +140,7 @@ def main_betapic():
     # randomly was 0.79 in Sebastian's example
 
     t_phase, Inorm, rh, lc = mu_comet_model(
-        t*u.day, f, ferr, par[0]*u.day, par[1], par[2], par[3]/u.radian,
+        t*u.day, par[0]*u.day, par[1], par[2], par[3]/u.radian,
         par[4]*u.day, Ms, Rs, ulimb, extra=True
     )
 
@@ -241,7 +241,7 @@ def main_tic4029():
     ulimb = 0.75 # guess; Claret2000, linear limb darkening, PHOENIX, Teff3000 logg 4-4.5 ish
 
     t_phase, Inorm, rh, lc = mu_comet_model(
-        t*u.day, f, ferr, par[0]*u.day, par[1], par[2], par[3]/u.radian,
+        t*u.day, par[0]*u.day, par[1], par[2], par[3]/u.radian,
         par[4]*u.day, Ms, Rs, ulimb, extra=True
     )
 
@@ -265,7 +265,8 @@ def main_tic4029():
 
[…]

### 2023-06-20 paper/ms.tex
update ms with words

@@
 %TODO
+{\bf TODO}
 
@@
 
+\paragraph{If the prominence scenario is correct, why don't stars in the
+Hyades and Praesepe show the phenomenon?}
+
+The prominence scenario, in a broad sense, argues that some intrinsic
+stellar process is key for generating the CQV phenomenon.
+If this were true, then stars of identical mass, size, and rotation
+periods might be expected to show the phenomenon in equal number --
+independent of age.
+This is because the stellar dynamo for M-dwarfs is generated by fluid
+motions inside the star, which should be identical for stars of the
+same mass, size, and rotation period.
+
+Between ages of $\approx$100\,Myr (AB Dor, Pleiades, Psc-Eri) and
+$\approx$700\,Myr (Praesepe and Hyades), a 0.3\,M$_\odot$ star will
+shrink by $\approx$10\%, from $\approx$0.33\,R$_\odot$ to 
+$\approx$0.29\,R$_\odot$ (CITE MIST).
+This is not a particularly drastic size change.
+Similarly, many M-dwarfs  have similarly rapid rotation periods 
+at 700\,Myr as they do at 100\,Myr (CITE Rebull2022); 
+the mean population does show some evidence for spin-down after the
+PMS contraction finishes, but a large fraction of the population is
+still spinning more rapidly than the $\approx$2\,day limit at which
+the CQV phenomenon becomes less common.
+
+Broadly speaking -- the absence of old CQVs in our view seems to be
+more plausibly linked to a gradual depletion of dusty detritus from the
+planet formation era than it does to the changing stellar properties
+as stars gradually finish their pre-main-sequence evolution, and then
+continue to spin rapidly for many hundreds of millions of years.
+
 \paragraph{Connection to close-in exoplanets}
@@
 Type X migration (CITE),
-until they hit a ``dust trap'' at the inner wall.
-Some support for this model comes from both the rotation periods of classical
-and weak-lined T Tauri stars
-(CITE Rebull2018,2019),
+until they hit a ``dust trap'' at the inner wall (CITE eg Kama2009,and
+related).
+Support for this model comes from the rotation periods of classical
+and weak-lined T Tauri stars (CITE Rebull2018,2019);
 from near-infrared interferometric observations that detect thermal
-emission from the disk wall (CITE CITE),
+emission from the disk wall (CITE CITE);
 and from the turn-over in the exoplanet orbital period distribution,
-which occurs around 5-10 days for FGK stars, 
-and perhaps even closer-in for M-dwarfs (CITE Petigura2022, and CITE for M-dwarfs).
+which occurs around 5-10 days for FGK stars, and perhaps even
+closer-in for M-dwarfs (CITE Petigura2022, and CITE for M-dwarfs).
+
+Broadly, the existence of a dust trap at the disk truncation radius 
+might be expected to trap larger boulders as well.
+Once the disk loses the gas, what happens to those boulders?
+They are no longer shielded.
+We then enter a phase of mass loss.
+Perhaps that phase is what we are observing.
 

### 2023-06-22 complexrotators/sedfit.py
sedfit: add trimlist, improve plots

@@ -18,7 +18,7 @@ from astropy.coordinates import SkyCoord
 from astropy import units as u
 from astroquery.vizier import Vizier
 
-def run_SED_analysis(ticid):
+def run_SED_analysis(ticid, trimlist=None):
     """
     Run CQV-specific SED analysis.  Priors assume the star is a nearby M-dwarf.
     Output goes to /reuslts/ariadne_sed_fitting/{starname}
@@ -31,7 +31,17 @@ def run_SED_analysis(ticid):
 
     Args:
         ticid (str): e.g. "402980664"
+
+    Kwargs: list of quad tuples, each entry in form (>xmin, <xmax, >ymin, <ymax).
+    E.g., to exclude everything above 1e-9 erg/cm2/s, and below 0.4 micron in
+    the SED fit:
+        [ (None, None, 1e-9, None) ,
+          (None, 0.4, None, None) ],
+        which is equivalent to
+        [ (None, 0.4, 1e-9, None) ],
     """
+    print(42*'-')
+    print(f'Beginning {ticid}')
     ##################
     # query the star #
     ##################
@@ -49,12 +59,65 @@ def run_SED_analysis(ticid):
 
     # remove TESS mag; no new information
     s.remove_mag('TESS')
-    # remove mags likely to be biased by UV excess (see eg Ingleby+2013, ApJ)
-    s.remove_mag('GROUND_JOHNSON_B')
-    s.remove_mag('SDSS_g')
-    s.remove_mag('GaiaDR2v2_BP')
 
+    # remove mags likely to be biased by UV excess (see eg Ingleby+2013, ApJ)
+    # leave in Gaia BP because it's mostly fine
+
+    s.remove_mag("STROMGREN_u")
+    s.remove_mag("STROMGREN_b")
+    s.remove_mag("STROMGREN_v")
+
+    s.remove_mag('SkyMapper_u')
+    s.remove_mag('SkyMapper_g')
+
+    s.remove_mag('SDSS_u')
+    s.remove_mag('SDSS_g')
+
+    s.remove_mag('GALEX_FUV')
+    s.remove_mag('GALEX_NUV')
+
+    s.remove_mag('GROUND_JOHNSON_U')
+    s.remove_mag('GROUND_JOHNSON_B')
+
+    # remove skymapper; these seem biased vs other surveys like SDSS
+    s.remove_mag('SkyMapper_i')
+    s.remove_mag('SkyMapper_z')
+
+    #
[…]

### 2023-06-22 paper/ms.tex
update ms

@@
 
-\paragraph{Connection to close-in exoplanets}
+\paragraph{Connection to debris disk evolution}
 The concordance model for planet formation invokes the presence of an accretion
@@
 Perhaps that phase is what we are observing.
+
+\paragraph{Connection to close-in exoplanets}
+Planet occurrence rate studies based on Kepler showed that around
+(early) M-dwarfs, there are $\approx$0.1 planets per star with sizes
+between 1-4\,$R_\oplus$ and orbital periods within 3 days
+\citep{2015ApJ...807...45D}.
+TRAPPIST-1b, a rocky planet with an orbital period of 1.5\,days is a
+possible example of this type of planet (CITE), though it orbits a
+very low-mass star (0.08\,M$_\odot$).
+
+The connection between the CQV phenomenon and these close-in
+exoplanets remains to be made.
+If the dust cloud model is correct, then assuming that the
+compact multiplanet resonant chains migrate to within $\approx$5-10
+stellar radii within the first 100\,Myr (e.g. CITE IZIDORO), the
+dust clouds and the planets would coexist for a non-negligible time
+interval.
+Rocky planets this young likely still have molten global magma oceans
+(e.g. CITE LICHTENBERG REVIEW), and would undergo significant 
+outgassing and atmospheric escape.
+A scenario in which close-in rocky planets serve as a possible source
+of dust for the clouds is not entirely implausible, though it remains
+to be explored.
 

### 2023-06-22 paper/ms.tex
update ms

@@
   prominences.  Here, we report new CQVs discovered in TESS data
-  collected between July~2018 and Sep~2022. 
-%  Our search used two
-%  methods, the first based on counting dips in phase-folded light
-%  curves, and the second based on counting peaks in the Fourier
-%  domain. 
-   From our analysis of \nstarssearched\ M-dwarfs with
-  $T$$<$16 and $d$$<$150\,pc, we find \ngoods\ gold-standard CQVs.
-  Most of these discoveries are new, and they include the brightest
-  and closest examples of this class of object known ($T$$\approx$11;
-  $d$$\approx$20\,pc).  A few objects are outliers among outliers; LP
-  12-502 for instance shows a ``dip complex'' with a total duration that is
-  nearly constant over more than 1000 cycles, 
-  but exhibits anywhere from four to eight local minima per cycle.  
-  LP-502 also at
-  times showed drastic shape changes over less than one cycle.
-  More generally, we find that none of the CQVs maintain a fixed light
-  curve shape over timescales of more than a few hundred cycles --
-  they are {\it quasi}periodic.  Although the physical explanation
-  behind these objects remains enigmatic, our sample may help clarify
-  their origin.  In particular, we highlight the plausibility of a disintegrating
-  planetesimal swarm model.
-  Connections to star, disk, and exoplanet evolution are emphasized.
+  collected between July~2018 and Sep~2022.  From our analysis of
+  \nstarssearched\ M-dwarfs with $T$$<$16 and $d$$<$150\,pc, we find
+  \ngoods\ gold-standard CQVs.  Most of these discoveries are new, and
+  they include the brightest and closest examples of this class of
+  object known ($T$$\approx$11; $d$$\approx$20\,pc).  A few objects
+  are outliers among outliers; LP 12-502 for instance shows a ``dip
+  complex'' with a total duration that is nearly constant over more
+  than 1000 cycles, but which exhibits anywhere from four to eight
+  local minima per cycle.  LP-502 also demonstrated drastic shape
+  changes over less than one cycle, and has up to four distinct
+  periods.  More generally, we find that none of the CQVs maintain a
+  fixed light curve shape over timescales of more than a few hundred
+  cycles -- they are all {\it quasi}periodic.  Although the physical
+  explanation behind these objects remains enigmatic, our sample may
+  help clarify their origin.  Possible connections to star, disk, and
+  exoplanet evolution are emphasized.
 \end{abstract}
@@
 root cause is not yet qualitatively understood: complex quasiperiodic
-variables (CQVs).  Figure~\ref{fig:f1} shows a few examples.  These objects are identified phenomenologically
-using their optical light curves, which show quasiperiodic troughs
-that can be either sharp or broad, often superposed on smooth
-spot-like modulation.  Some of the objects show up to eight local
-minima (dips) per cycle; sharp peaks are also common.  Most of these
-variable stars turn out to be pre-main-sequence M-dwarfs without
-near-infrared excesses, with ages of $\approx$5-150 million years
-(Myr), and rotation periods of at most two days; they are observed to
-be $\approx$1\% of M-dwarfs younger than 100 Myr
+variables (CQVs).  Figure~\ref{fig:f1} shows a few examples.  These
+objects are identified phenomenologically using their optical light
+curves, which show quasiperiodic troughs that can be either sharp or
+broad, often superposed on smooth spot-like modulation.  Some of the
+objects show up to eight local minima (dips) per cycle; sharp peaks
+are also common.  Most of these variable stars turn out to be
+pre-main-sequence M-dwarfs without near-infrared excesses, with ages
+of $\approx$5-150 million years (Myr), and rotation periods of at most
+two days; they are observed to be $\approx$1\% of M-dwarfs younger
+than 100 Myr
 \citep{2016AJ....152..114R,2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G}.
@@
 
+%TODO rewrite, but favor dust clumps even more
 The issue of what causes the variability that defines the CQVs has yet
@@
 The known CQVs are correspondingly faint; the initial K2 discoveries
-\citep{2016AJ....152..114R,2017AJ....153..152S} were M2-M6 dwarfs at distances
-$\gtrsim$100\,pc, yielding optical brightnesses of $V$$\approx$15.5 to
-$V$$>$20.  This renders time-series optical spectroscopy at high
-resolution technically impossible, despite its potential utility in
-ruling between the models.
+\citep{2016AJ....152..114R,2017AJ....153..152S} were M2-M6 dwarfs at
+distances $\gtrsim$100\,pc, yielding optical brightnesses of
+$V$$\approx$15.5 to $V$$>$20.  This renders time-series optical
+spectroscopy at high resolution technically impossible, despite its
+potential utility in ruling between the models.
 
@@
 
-{\sc Dips can disappear instantaneously}---The state switches shown in cycles
-1233-1264 and 299-315 reveal that the dips can be {\it independent}
-and {\it additive}.  They also show that although dip depth is
-generally not preserved over a state switch, {\it ingress time}
-usually is conserved.
-It other words, throughout cycles 1233-1264, there are three local
-minima between phases of 0 and 0.3.  They all have identical ingress
-times.  The shape change during the transition strongly suggests that
-it was simply the leading dip that ``turned off', while the trailing
-two dips remained fixed.  The state switches during cycles 299-315 and
-248-264 share the same characteristic: it is always the {\it leading}
-dip of a complex that ``switches off'', leaving the trailing dips in
-its wake.
+{\sc Dips can disappear instantaneously}---The state switches shown in
+cycles 1233-1264 and 299-315 reveal that the dips can be {\it
+independent} and {\it additive}.  They also show that although dip
+depth is generally not preserved over a state switch, {\it ingress
+time} usually is conserved.  It other words, throughout cycles
+1233-1264, there are three local minima between phases of 0 and 0.3.
+They all have identical ingress times.  The shape change during the
+transition strongly suggests that it was simply the leading dip that
+``turned off', while the trailing two dips remained fixed.  The state
+switches during cycles 299-315 and 248-264 share the same
+characteristic: it is always the {\it leading} dip of a complex that
+``switches off'', leaving the trailing dips in its wake.
 
@@
 with point sources.
+
+{\sc Dip periods}---Most of the LP 12-502 dips recur with a period of
+$P=18.5611 \pm 0.0001$\,hr.  However the river plots reveal multiple
+distinct periodicities in the light curve for specific dips.  For
+instance, in sectors 25-26, the local minimum that develops around
+cycle 262 has a period faster than the mean period by $\approx$0.1\%,
+while some of the trailing local minima in the main dip complex have
+periods slower than the mean period, by $\approx$0.04\%.  In addition
+to the fundamental period, we were able to identify at least four
+distinct periods shown by specific dips over the full Sectors 18-59
+dataset, including periods at 18.5683, 18.5672, 18.5473, and
+18.5145\,hr, with a typical measurement uncertainty of
+$\approx$0.0002\,hr.
 
@@
 
-We report on the existence of \ngoods\ objects that showed bonafide
-CQV behavior over at least one TESS sector between July~2018 and Sep~2022.
+We report on the existence of \ngoods\ objects that showed
+complex quasiperiodic behavior over at least one TESS sector between July~2018 and Sep~2022.
 Our search for these objects was restricted to dwarf stars bright enough
@@
 that were red ($\bprp<1.5$) and within 150\,pc of the Sun.
-These objects are listed in Table~\ref{tab:thetable}.
+These \ngoods\ bonafide CQVs are listed in Table~\ref{tab:thetable}.
 This table also includes an additional \nmaybes\ candidate CQVs, whose
@@
 
-Analyzing the light curves of these objects, we can make the following conclusions.
+Analyzing the light curves of these objects, we draw the following conclusions.
 
@@
 	%
-	\item CQVs are {\it quasi}periodic.
+	\item CQVs are {\it quasi}periodic.  While the mean periods in our
+	sample seem to remain fixed over the span of available observations, the light curve
+	shapes themselves evolve, similar to rotating stars.
+	%
+	\item The same CQV can show dips with closely-spaced periods.  
+	LP 12-502, for instance, showed dips with four distinct periods within $\pm 0.3\%$
+	of the fundamental period, sometimes simultaneous, and each lasting for up to 50 cycles.
 	%
 	\item The CQV phenomenon persists for at least 150\,Myr, based on the
-	existence of CQVs in AB Dor, the Pleiades, and Psc-Eri.
+	existence of CQVs in AB Dor, the Pleiades, and Psc-Eri.  It may extend to
+	even older ages, however the lack of detected CQVs in the Hyades and
+	Praesepe suggest that the phenomenon is unique to the pre-main-sequence
+	for M-dwarfs.
 	%
 	\item CQVs evolve over timescales that are both secular ($>$100\,cycles) and impulsive ($<$1 cycle).
-	%
-	\item Individual CQVs can show multiple, slightly different periods.  LP 12-502
-	is one example; others are included in Table~\ref{tab:thetable}.
+	``State-switches'' can cause dips to collapse instantaneously, and are often (but not exclusively)
+	linked with observed optical flares.
+	Dip growth however seems to happen over durations of at least ten cycles.
 	%
@@
 	\begin{center}
-    \centering
     \includegraphics[width=0.45\textwidth]{ANNOTATED_resid_TIC_402980664_P18.5611_2min_phase_timegroups.png}
-		\vspace{-0.45cm}
+    	\end{center}
+    \vspace{-0.4cm}
 		\caption{
@@
 		\label{fig:lp2}
-	\end{center}
 \end{figure*}
@@
 			\includegraphics[width=0.43\textwidth]{TIC402980664_river_gist_stern_0_64_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
-			\includegraphics[width=0.43\textwidth]{TIC402980664_river_gist_stern_248_315_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
-		}
-	\vspace{0.4cm}
+			\includegraphics[width=0.43\textwidth]{ANNOTATED_TIC402980664_river_gist_stern_248_315_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
+		}
+	\vspace{-0.1cm}
 			\subfloat{
-		\includegraphics[width=0.43\textwidth]{TIC402980664_river_gist_stern_1411_1481_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
-				\includegraphics[width=0.43\textwidth]{TIC402980664_river_gist_stern_1233_1265_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
+		\includegraphics[width=0.43\textwidth]{ANNOTATED_TIC402980664_river_gist_stern_1411_1481_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
+				\includegraphics[width=0.43\textwidth]{ANNOTATED_TIC402980664_river_gist_stern_1233_1265_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
 	}
@@
 	\caption{
-    {\bf River plots of LP 12-502}, showing (clockwise from top-left) Sectors 18-19, 25-26, 53, and 58-59.
-    A two-harmonic
-    sinusoid has been subtracted over specific chunks in time ({\bf see text}).
+    {\bf River plots of LP 12-502}, showing (clockwise from top-left)
+    Sectors 18-19, 25-26, 53, and 58-59.  A two-harmonic sinusoid has
+    been subtracted over specific chunks in time ({\bf see text}).
+    For Sectors 25-26 (cycles 248-315), three periods are overplotted:
+    $P$=18.5611\,hr (gray vertical line); 18.5404\,hr (orange); 18.5683\,hr (green).
+    For Sector 53, gray is identical, while cyan is 18.5145\,hr.
+    For Sectors 58-59, the magenta line is 18.5473\,hr, and the green
+    line is 18.5672\,hr.
 	}

### 2023-06-22 paper/ms.tex
update ms

@@
 
-\title{Pre-Main-Sequence M-Dwarfs With Complex Quasiperiodic Variability From Four Years of TESS}
+%\title{Pre-Main-Sequence M-Dwarfs With Complex Quasiperiodic Variability From Four Years of TESS}
+
+\title{Dust Clumps In Corotation Around Adolescent M-Dwarfs: Four Years of TESS}
 
@@
   variability invoke long-lived material in orbit at the Keplerian
-  corotation radius, for instance transiting dust clumps or stellar
-  prominences.  Here, we report new CQVs discovered in TESS data
+  corotation radius, most likely transiting dust clumps.
+  Here, we report new CQVs discovered in TESS data
   collected between July~2018 and Sep~2022.  From our analysis of
@@
   local minima per cycle.  LP-502 also demonstrated drastic shape
-  changes over less than one cycle, and has up to four distinct
+  changes over less than one cycle, and (locally) shows up to four distinct
   periods.  More generally, we find that none of the CQVs maintain a
   fixed light curve shape over timescales of more than a few hundred
-  cycles -- they are all {\it quasi}periodic.  Although the physical
-  explanation behind these objects remains enigmatic, our sample may
-  help clarify their origin.  Possible connections to star, disk, and
-  exoplanet evolution are emphasized.
+  cycles -- they are all {\it quasi}periodic.  Our sample will
+  help facilitate future modeling and observational efforts aimed at understanding
+  these objects, and connecting them to the broader
+  contexts of star, disk, and
+  exoplanet evolution.
 \end{abstract}
@@
 \subsection{Stellar properties}
+\label{subsec:starprops}
 
@@
 \paragraph{Effective temperatures, radii, and masses}
-%TODO
-{\bf TODO}
+
+We determine the stellar effective temperature and radii through SED
+fitting; the masses are then determined based on interpolation against
+the ``magnetic'' models of \citet{2016A&A...593A..99F}.
+
+For the SED fitting, we use \texttt{astroARIADNE}
+\citep{2022MNRAS.513.2719V}, tuned to use only the BT-Settl stellar
+atmosphere models \citep{Allard2012} based on the
+\citet{2009ARA&A..47..481A} solar abundances.  The broadband
+magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
+DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, $riz$ from
+Pan-STARRS1, SDSS $riz$, and the WISE 1-2 passbands.  We specifically
+omitted UV flux measurements to avoid biasing our fit with any
+possible chromospheric UV excess.
+\texttt{astroARIADNE} compares the measured broadband flux measurements
+against pre-computed model grids, and by default fits for six
+parameters:
+$\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm Fe/H}], d \}$.
+The distance  prior is drawn from \citet{2021AJ....161..147B}.
+The surface gravity and metallicity are generally unconstrained.
+And finally, given our particular use-case, 
+we assumed the following priors for the temperature, stellar size, and
+extinction:
+\begin{align}
+  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
+  R_\star / {\rm R}_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.0), \\
+  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
+\end{align}
+for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
+distributions, and $\mathcal{T}(\mu, \sigma, a, b)$ a truncated normal
+distribution with mean $\mu$, standard deviation $\sigma$, and lower
+and upper bounds $a$ and $b$.
+Using \texttt{Dynesty} \citep{2020MNRAS.493.3132S},
+we statically sampled the posterior probability assuming the default
+Gaussian likelihood, and set a stopping threshold of ${\rm d}\log
+\mathcal{Z} < 0.01$, for $\mathcal{Z}$ the evidence.
+
+Given the effective temperatures and stellar radii from the SED fit,
+we then estimate the mass by interpolating against the ``magnetic''
+models of \citet{2016A&A...593A..99F}.  The need for models that
+incorporate some form of magnetic correction is well-documented for
+our regime of active, young M-dwarfs
+\citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2020ApJ...891...29S}.
+While one could of course allow a range of magnetic field strengths,
+and a corresponding range of fractions for starspot converage
+\citep{2020ApJ...891...29S}, we prefer the magnetic
+\citet{2016A&A...593A..99F} models based on the simplicity of their
+assumption that the surface magnetic field strength will be fixed at
+equipartition.
+We therefore interpolate our SED-measured temperatures and radii, at
+the known cluster-based stellar ages ages, in order to estimate
+(model-dependent) stellar masses.
+For the two systems without known ages (see below), we omit this mass
+estimate, due to the degeneracies in the inference problem.
 
@@
 \citep[e.g.][]{2012ApJ...752....1R,2012A&A...545L...5B,2015Natur.526..546V,2019A&A...625L..13Z}.
-
-It is tempting to interpret certain features of the LP 12-502 light
-curve in this framework of a disintegrating planetesimal swarm.  For
-instance, the complex in cycles 248-298 could be well-fit by a sharp
-leading edge that decays over 0.2\,$P$ (3.7\,hours).  The earlier
-complex, during cycles 248-264 (pre-state-switch), could be fit by a
-similar profile.  There are two degenerate explanations for the small
-``wiggles'' in the exponential decay.  In one explanation, the decay
-timescale is fast ($\approx$0.03\,$P$), and there are up to five
-exocomets, superposed.  In the other, there is only one main
-``launching body'', and the material it ejects either has some
-sub-structure, or else is passing across (and in synchronicity with) a
-star with heavily substructured starspots across its surface.
-
-While the number of free parameters in this type of model is somewhat
-dizzying, we have no right to believe that nature need be
-simple.  Every dip in the exocomet tail model would have as free
-parameters the dip phase, the duration (captured by an exponential
-decay timescale), and the dip depth.  In detail, the impact parameter
-would also enter.  Allotting four free parameters per dip yields up to
-32 free parameters for the light curve at the most complicated times
-(assigning one exocomet per local minimum).
-
-Perhaps the most glaring issue with the planetesimal swarm idea is
-that a large number of the dips show asymmetries in the {\it wrong
-direction} relative to the naive expectation of a trailing comet tail.
-Dust forward scattering could be one possible way out; so too could
-simply invoking non-exponentially decaying dust
-distributions as a function of azimuth.
+We discuss this possibility below.
 
@@
 to be explored.
+
+\paragraph{A planetesimal swarm at corotation seems unlikely}
+It is tempting to interpret certain features of the LP 12-502 light
+curve in this framework of a disintegrating planetesimal swarm.  For
+instance, the complex in cycles 248-298 could be well-fit by a sharp
+leading edge that decays over 0.2\,$P$ (3.7\,hours).  The earlier
+complex, during cycles 248-264 (pre-state-switch), could be fit by a
+similar profile.  There are two degenerate explanations for the small
+``wiggles'' in the exponential decay.  In one explanation, the decay
+timescale is fast ($\approx$0.03\,$P$), and there are up to five
+exocomets, superposed.  In the other, there is only one main
+``launching body'', and the material it ejects either has some
+sub-structure, or else is passing across (and in synchronicity with) a
+star with heavily substructured starspots across its surface.
+
+While the number of free parameters in this type of model is somewhat
+dizzying, we have no right to believe that nature need be
+simple.  Every dip in the exocomet tail model would have as free
+parameters the dip phase, the duration (captured by an exponential
+decay timescale), and the dip depth.  In detail, the impact parameter
+would also enter.  Allotting four free parameters per dip yields up to
+32 free parameters for the light curve at the most complicated times
+(assigning one exocomet per local minimum).
+
+However there are two glaring issues with the disintegrating planetesimal swarm idea.
+First, a large number of the dips show asymmetries in the {\it wrong
+	direction} relative to the naive expectation of a trailing comet tail.
+Dust forward scattering might be one possible way out; so too might
+invoking non-exponentially decaying dust
+distributions as a function of azimuth.
+Second, and perhaps more serious, a planetesimal swarm should be expected
+to be {\it exactly periodic} over observable timescales, on the presumption that the planetesimals
+would be massive enough to not feel any headwind or magnetic field.
+This is not what is observed; instead, every dip period
+that is observed to be distinct from the fundamental 18.5611\,hr period
+is both short-lived, and unique.
+This suggests structures much less massive than a 1--100\,km sized
+planetesimal,
+ more strongly
+which could be more strongly influenced by the stellar magnetic field.
 
@@
 	%\texttt{isochrones} \citep{morton_2015_isochrones},
-	%\texttt{lightkurve} \citep{lightkurve_2018},
+	\texttt{lightkurve} \citep{2018ascl.soft12013L},
   %\texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
@@
 %    ZTF.
+  {\it Broadband photometry}:
+    2MASS (CITE).
+    APASS (CITE).
+		Gaia \citep{2018A&A...616A...1G,2018A&A...616A...1G}.
+    Pan-STARRS1 (CITE).
+    SDSS (CITE).
+    AllWISE (CITE).
 }

### 2023-06-25 paper/ms.tex
update ms

@@
 
-\title{Dust Clumps In Corotation Around Adolescent M-Dwarfs: Four Years of TESS}
+\title{Corotating Dust Clumps Around Adolescent M-Dwarfs: Four Years of TESS}
 
@@
 assumption that the surface magnetic field strength will be fixed at
-equipartition.
+thermal equipartition.
 We therefore interpolate our SED-measured temperatures and radii, at

### 2023-06-25 complexrotators/sedfit.py
sedfit: update radius prior

@@ -195,7 +195,7 @@ def run_SED_analysis(ticid, trimlist=None):
             'logg': ('normal', 4.5, 0.5),
             'z': ('uniform', -0.3, 0.3),
             'dist': ('default'),
-            'rad': ('truncnorm', 0.5, 0.3, 0.1, 1.0),
+            'rad': ('truncnorm', 0.5, 0.5, 0.1, 1.5),
             'Av': ('uniform', 0, 0.2)
     }
 

### 2023-06-25 paper/ms.tex
update ms

@@
 %%%%%%%%%
-\newcommand{\nstarssearched}{{XXYYY}}
+\input{vals_searched_stars}
 
@@
   T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
-  R_\star / {\rm R}_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.0), \\
+  R_\star / {\rm R}_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
   A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
@@
 which could be more strongly influenced by the stellar magnetic field.
+
+\paragraph{Interpretation of the $T\lesssim 15$ dropoff}
+Our search sample included 35472 unique stars with $12<T<14$, versus
+2045 unique stars with $15<T<16$.  This helps clarify why our detected
+CPVs become less common toward fainter TESS magnitudes, despite the
+relative ease of their detectability, even at $15<T<16$.  It is
+because the TESS 2-minute data are very incomplete at the faint end.
 

### 2023-06-25 drivers/get_selection_function_values.py
add selection function val getter

@@ -1,0 +1,29 @@
+import pandas as pd, numpy as np
+import os
+from os.path import join
+from complexrotators.paths import PAPERDIR
+
+localdir = '/Users/luke/local/SPOCLC'
+csvpath = join(localdir, 'gaia_X_spoc2min_merge.csv')
+df = pd.read_csv(csvpath)
+
+sel = (
+    (df.TESSMAG < 16) & (df.bp_rp > 1.5) &
+    (df.M_G > 4) & (df.parallax > 1e3*(1/150))
+)
+
+sdf = df[sel]
+
+N_1 = len(np.unique(sdf.TICID))
+N_2 = len(sdf)
+
+latex_txt = (
+    r"\newcommand{\nstarssearched}{"+str(N_1)+"}\n"
+    r"\newcommand{\nlcssearched}{"+str(N_2)+"}\n"
+)
+
+outpath = join(PAPERDIR, 'vals_searched_stars.tex')
+with open(outpath, 'w') as f:
+    f.writelines(latex_txt)
+print(f"Wrote {outpath}")
+

### 2023-06-25 drivers/make_cpv_table.py

@@ -207,7 +207,8 @@ def get_banyan_result(gdr2_df):
         'banyan_prob': probs,
         'banyan_age': ages,
         'banyan_age_refs': age_refs,
-        'banyan_singleagefloat': singleagefloat,
+        'banyan_singleagefloat': float(singleagefloat),
+        'banyan_logsingleagefloat': np.log10(float(singleagefloat*1e6)),
     }, index=[0])
 
     return bdf

### 2023-06-26 paper/ms.tex
update ms

@@
 \newcommand{\vsini}{{$V \sin i$}}
-\newcommand{\teff}{T$_{\textrm{eff}}$}
 \newcommand{\kms}{{km\,s$^{-1}$}}
@@
 
+\newcommand{\teff}{T_{\rm eff}}
+\newcommand{\ms}{M_\star}
+\newcommand{\rs}{R_\star}
+
 \newcommand{\bprp}{G_{\rm BP} - G_{\rm RP}}
@@
 
-\correspondingauthor{TBD}
-\email{TBD}
+%\title{Complex Quasiperiodic Variables From Four Years of TESS}
+
+\correspondingauthor{Luke G. Bouma}
+\email{luke@astro.caltech.edu}
 
@@
 
-\shortauthors{TBD}
+\shortauthors{Bouma, Jayararaman, et al.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\author{Authors to include (ORDER TBD)}
 
@@
 \begin{abstract}
-  Complex quasiperiodic variables (CQVs) are pre-main-sequence
-  M-dwarfs with almost-periodic optical modulation that includes both
-  sharp and broad troughs.  The troughs are usually superposed over
-  smooth, spot-like modulation.  These objects are typically 10-100
-  million years (Myr) old;  they do not have primordial gas-rich
-  disks.  Nonetheless, the preferred explanations for their optical
-  variability invoke long-lived material in orbit at the Keplerian
-  corotation radius, most likely transiting dust clumps.
-  Here, we report new CQVs discovered in TESS data
-  collected between July~2018 and Sep~2022.  From our analysis of
-  \nstarssearched\ M-dwarfs with $T$$<$16 and $d$$<$150\,pc, we find
-  \ngoods\ gold-standard CQVs.  Most of these discoveries are new, and
-  they include the brightest and closest examples of this class of
-  object known ($T$$\approx$11; $d$$\approx$20\,pc).  A few objects
-  are outliers among outliers; LP 12-502 for instance shows a ``dip
-  complex'' with a total duration that is nearly constant over more
-  than 1000 cycles, but which exhibits anywhere from four to eight
-  local minima per cycle.  LP-502 also demonstrated drastic shape
-  changes over less than one cycle, and (locally) shows up to four distinct
-  periods.  More generally, we find that none of the CQVs maintain a
-  fixed light curve shape over timescales of more than a few hundred
-  cycles -- they are all {\it quasi}periodic.  Our sample will
-  help facilitate future modeling and observational efforts aimed at understanding
-  these objects, and connecting them to the broader
-  contexts of star, disk, and
-  exoplanet evolution.
+  Complex quasiperiodic variables (CQVs) are low-mass
+  pre-main-sequence stars with nearly periodic optical modulation that
+  is likely induced by long-lived transiting dust clumps in orbit at
+  the Keplerian corotation radius.  Here, we report new CQVs
+  discovered in TESS data collected between July~2018 and Sep~2022.
+  From our analysis of \nstarssearched\ K- and M-dwarfs with $T$$<$16
+  and $d$$<$150\,pc, we find \ngoods\ gold-standard CQVs.  Most of
+  these discoveries are new, and they include the brightest and
+  closest examples of this class of object known ($T$$\approx$11;
+  $d$$\approx$20\,pc).  A few objects are outliers among outliers; LP
+  12-502 for instance shows a ``dip complex'' with a period and total
+  duration that are fixed over more than 1000 cycles, but in detail
+  this object shows anywhere from four to eight local minima per
+  cycle.  LP-502 also demonstrated drastic shape changes over less
+  than one cycle, and at times displayed distinct superposed periods
+  simultaneously.  Generally speaking, we find that none of the CQVs
+  maintain a fixed light curve shape over timescales of more than a
+  few hundred cycles -- they are all {\it quasi}periodic.  We revisit
+  the arguments for why corotating dust clumps are the most likely
+  explanation, though there are other possibilities, and all lines of
+  evidence are currently indirect.  In the future, we expect that our
+  sample will help facilitate modeling and observational efforts aimed
+  at understanding these objects, and connecting them to the broader
+  contexts of star, disk, and exoplanet evolution.
 \end{abstract}
@@
 \citep{2017MNRAS.470..202B}, and, in geometrically favorable
-circumstances, eclipses by stars and planets.
+circumstances, eclipses by stars and planets
+\citep{2010exop.book...55W}.
 
 Data from K2 and TESS have yielded a new class of variable star whose
-root cause is not yet qualitatively understood: complex quasiperiodic
-variables (CQVs).  Figure~\ref{fig:f1} shows a few examples.  These
-objects are identified phenomenologically using their optical light
-curves, which show quasiperiodic troughs that can be either sharp or
-broad, often superposed on smooth spot-like modulation.  Some of the
-objects show up to eight local minima (dips) per cycle; sharp peaks
-are also common.  Most of these variable stars turn out to be
-pre-main-sequence M-dwarfs without near-infrared excesses, with ages
-of $\approx$5-150 million years (Myr), and rotation periods of at most
-two days; they are observed to be $\approx$1\% of M-dwarfs younger
-than 100 Myr
-\citep{2016AJ....152..114R,2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G}.
-The dips can be chromatic, with a reddening law plausibly consistent
-with dust
+root cause is only beginning to become clear: complex quasiperiodic
+variables (CQVs).  These objects are identified phenomenologically
+using their optical light curves, which show quasiperiodic troughs
+that can be either sharp or broad, often superposed on smooth
+spot-like modulation
+\citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z}.
+Some CQVs show up to eight local minima (dips) per cycle; sharp peaks
+are also common.  Most CQVs are pre-main-sequence M-dwarfs without
+near-infrared excesses, with ages of $\approx$5-150 million years
+(Myr), and rotation periods of at most two days; they are observed to
+be $\approx$1-3\% of M-dwarfs younger than 100 Myr
+\citep{2016AJ....152..114R,2022AJ....163..144G}.  The dips can be
+chromatic, with a reddening law plausibly consistent with dust
 \citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
@@
 
-%TODO rewrite, but favor dust clumps even more
-The issue of what causes the variability that defines the CQVs has yet
-to be resolved.  There are a few competing explanations.  All young
-M-dwarfs are spotted, which produces flux variations over
-characteristic timescales of the rotation period, $P_{\rm rot}$, and
-its half-harmonic, $0.5\,P_{\rm rot}$.  The observed dips occur over
-durations as short as $0.05\,P_{\rm rot}$; a ``starspot-only''
-scenario is therefore highly unlikely for any of the objects with
-sufficiently sharp dips
+A few competing explanations for what causes the complex quasiperiodic
+variability are shown in Figure~\ref{fig:f1}, along with a few
+representative light curves.  All young M-dwarfs are spotted, which
+produces flux variations over characteristic timescales of the
+rotation period, $P_{\rm rot}$, and its half-harmonic, $0.5\,P_{\rm
+rot}$.  The observed dips occur over durations as short as
+$0.05\,P_{\rm rot}$; a ``starspot-only'' scenario can be discarded for
+any object with sufficiently sharp dips
 \citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The more likely
-scenarios instead invoke sharp geometries with material extrinsic to
-the stellar surface
+scenarios invoke sharp geometries with material extrinsic to the
+stellar surface
 \citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  In the
@@
 trapped along the star’s magnetic field lines, also near corotation
-\citep{2022MNRAS.514.5465W}.  And in a ``screen'' scenario, the inner
-wall of a quiescent circumstellar disk blocks a portion of the stellar
-surface to produce sudden dips whenever spots come into view
-\citep{2019ApJ...876..127Z}.  In our view, the arguments seem best
-established for the dust clump and prominence hypotheses
-\citep{2023MNRAS.518.4734S,2022MNRAS.514.5465W}.  However, unambiguous
-evidence has yet to be presented to demonstrate which, if any, of
-these scenarios is correct.
-
-It has not yet been possible to rule between the candidate mechanisms
-CQVs have historically been both hard to discover and hard to
-characterize.   Discoverability has been linked to rarity: CQVs
-comprise about 1\% of the youngest 1\% of M-dwarfs
+\citep{2022MNRAS.514.5465W}.  There is also a ``screen'' scenario, in
+which the inner wall of a quiescent circumstellar disk blocks a
+portion of the stellar surface to produce sudden dips whenever spots
+come into view \citep{2019ApJ...876..127Z}.
+
+In our view, the arguments seem best established for the dust clump
+hypothesis \citep{2023MNRAS.518.4734S}.  This is primarily because the
+prominence scenario lacks a mechanism for generating broadband
+opacity, and the screen scenario seems inconsistent with the degree of
+observed periodicity, and the lack of infrared excess.  However,
+unambiguous evidence, for instance a spectroscopic detection of
+silicates during a CQV ``dip'', has yet to be presented to confirm
+which scenario is correct.
+
+CQVs have been challenging to understand because they have been both
+hard to discover and hard to characterize.   Discoverability is tied
+to rarity: CQVs comprise about 1\% of the youngest 1\% of M-dwarfs
 \citep{2018AJ....155..196R}.  Out of the millions of stars monitored
@@
 distances $\gtrsim$100\,pc, yielding optical brightnesses of
-$V$$\approx$15.5 to $V$$>$20.  This renders time-series optical
-spectroscopy at high resolution technically impossible, despite its
-potential utility in ruling between the models.
+$V$$\approx$15.5 to $V$$>$20.  This renders time-series spectroscopy
+at high resolution technically impossible, despite its potential
+utility in ruling between the models.
 
@@
 persistent flux dips'', ``scallop shells'', ``batwings'',
-\citep{2017AJ....153..152S,2018AJ....155...63S} ``complex rotators'',
+\citep{2017AJ....153..152S} ``complex rotators'',
 \citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
 and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  The
-CQVs are not ``dippers'', which are classical T Tauri stars with
-infrared excesses whose optical variability is linked to obscuring
-inner disk structures and accretion hot spots
+CQVs should not be conflated with ``dippers'', which are classical T
+Tauri stars with infrared excesses whose optical variability is linked
+to obscuring inner disk structures and accretion hot spots
 \citep{2014AJ....147...82C,2021ApJ...908...16R}.  At the risk of
-introducing yet another
-standard,\footnote{\url{https://xkcd.com/927/}} we prefer to make the
-technical distinction that the CQVs are, over timescales of more than
-a few cycles, not exactly periodic.  Their shapes evolve, usually over
-some decoherence timescale, similar to variability induced by surface
-inhomogeneities such as starspots.  While the three-type
+introducing yet another standard, we prefer a nomenclature that
+reflects how, when observed over timescales of more than tens of
+cycles, CQVs are never exactly periodic.  Their shapes evolve, usually
+with some coherence timescale, similar to variability induced by
+surface inhomogeneities such as starspots.  While the three-type
 classification scheme proposed by \citet{2017AJ....153..152S} may
-indeed provide some helpful visual distinctions among the CQV class,
-it seems likely (we hope!) that they are all explained by a single
+indeed provide some helpful visual distinctions amongst CQV
+sub-classes, it seems likely that they are all explained by a single
 underlying phenomenon, and so we opt to refer to them by a single
@@
 		{\it Bottom:} Plausible cartoon models for the phenomenon.  The
-		``clump'' or ``prominence'' scenarios seem most plausible, given
-		the stability of the phenomenon and the lack of observed infrared
-		excesses.
+		dust clump scenario seems most plausible, given
+		the stability of the phenomenon, the lack of observed infrared
+		excesses, and the challenge of producing broadband opacity variations
+		with only ionized hydrogen in the prominence scenario.
 	}
@@
 To assess the completeness of the resulting 120-second cadence data
-that we analyze, we cross-matched TIC8 \citep{2018AJ....156..102S}
+that is the basis of this study, we cross-matched TIC8 \citep{2018AJ....156..102S}
 against the Gaia DR2 point-source catalog \citep{2018A&A...616A...1G}.
@@
 function includes dwarf stars later than spectral types of
-$\approx$K6V.  This target sample includes \nstarssearched\ stars with
-approximately M-dwarf spectral type, down to $T$$<$16 and out to
-$d$$<$150\,pc.
+$\approx$K6V \citep{2013ApJS..208....9P}.  The target sample therefore
+includes \nstarssearched\ M-dwarfs and late-K dwarfs,
+down to $T$$<$16 and out to $d$$<$150\,pc.
 
@@
 
-Previous methods that have yielded CQV discoveries include visually
+Previous methods for finding CQVs have included visually
 examining stars known to be in young clusters
@@
 flagging rapid rotators with a large number of strong Fourier
-harmonics \citep{2019ApJ...876..127Z}.  The latter approach requires
-visual vetting, since most rapid rotators with many Fourier harmonics
-are false positives such as eclipsing binaries or multiple stars
+harmonics \citep{2019ApJ...876..127Z}.  The latter approach still requires
+visual vetting, since ``stars with many Fourier harmonics''
+is a designation that
+includes objects such as eclipsing binaries or multiple stars
 blended into a single photometric aperture.  In this work, we
@@
 techniques independently.
-
-\subsubsection{Fourier analysis}
-\label{subsec:fourier}
-For the Fourier analysis, we followed \citet{2019ApJ...876..127Z}.
-
-{\bf todo for Rahul or Saul: explain the approach, in a few
-paragraphs.  Was the SAP\_FLUX or PDCSAP used? etc. }
 
@@
 
+\subsubsection{Fourier analysis}
+\label{subsec:fourier}
+For the Fourier analysis, we followed \citet{2019ApJ...876..127Z}.
+
+{\bf TODO for Rahul or Saul: explain the approach, in a few
+	paragraphs.  Was the SAP\_FLUX or PDCSAP used? etc. }
+
 \subsubsection{Manual vetting}
@@
 kinematic associations between the CQVs and known clusters in the
-solar neighborhood.  For most of the stars in our sample, we were able
-to do this using BANYAN\,$\Sigma$
+solar neighborhood.  For most stars in our sample, we did
+this using BANYAN\,$\Sigma$
 \citep{2018ApJ...856...23G}.\footnote{\url{https://github.com/jgagneastro/banyan_sigma},
@@
 probabilities returned by this procedure are qualitatively useful, but
-quantitatively dubious due to the non-Gaussian nature of most groups
-within the solar neighborhood \citep[see
-e.g.][Figure~10]{2021ApJ...917...23K}.
+we emphasize that they are quantitatively dubious due to the
+non-Gaussian nature of most groups within the solar neighborhood
+\citep[see e.g.][Figure~10]{2021ApJ...917...23K}.
 
@@
 
-We determine the stellar effective temperature and radii through SED
-fitting; the masses are then determined based on interpolation against
-the ``magnetic'' models of \citet{2016A&A...593A..99F}.
-
-For the SED fitting, we use \texttt{astroARIADNE}
-\citep{2022MNRAS.513.2719V}, tuned to use only the BT-Settl stellar
-atmosphere models \citep{Allard2012} based on the
-\citet{2009ARA&A..47..481A} solar abundances.  The broadband
-magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
-DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, $riz$ from
-Pan-STARRS1, SDSS $riz$, and the WISE 1-2 passbands.  We specifically
-omitted UV flux measurements to avoid biasing our fit with any
-possible chromospheric UV excess.
+We determined the stellar effective temperature and radii through SED
+fitting; we then estimated the masses by interpolating against
+the PARSEC v1.2S models \citep{2012MNRAS.427..127B,2014MNRAS.444.2525C}.
+%the ``magnetic'' models of \citet{2016A&A...593A..99F}.
+
+For the SED fitting, we used \texttt{astroARIADNE}
+\citep{2022MNRAS.513.2719V}.  Specifically, we adopted the ``BT-Settl''
+stellar atmosphere models \citep{Allard2012} assuming the
+\citet{2009ARA&A..47..481A} solar abundances, and the
+\citet{2006MNRAS.368.1087B} water line lists.
+The broadband magnitudes we considered included $GG_{\rm BP}G_{\rm
+RP}$ from Gaia DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, $riz$
+from Pan-STARRS1, SDSS $riz$, and the WISE 1-2 passbands.  We
+specifically omitted UV flux measurements to avoid biasing our fit
+with any possible chromospheric UV excess.
 \texttt{astroARIADNE} compares the measured broadband flux measurements
@@
 Gaussian likelihood, and set a stopping threshold of ${\rm d}\log
-\mathcal{Z} < 0.01$, for $\mathcal{Z}$ the evidence.
-
-Given the effective temperatures and stellar radii from the SED fit,
-we then estimate the mass by interpolating against the ``magnetic''
-models of \citet{2016A&A...593A..99F}.  The need for models that
-incorporate some form of magnetic correction is well-documented for
-our regime of active, young M-dwarfs
-\citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2020ApJ...891...29S}.
-While one could of course allow a range of magnetic field strengths,
-and a corresponding range of fractions for starspot converage
-\citep{2020ApJ...891...29S}, we prefer the magnetic
-\citet{2016A&A...593A..99F} models based on the simplicity of their
-assumption that the surface magnetic field strength will be fixed at
-thermal equipartition.
-We therefore interpolate our SED-measured temperatures and radii, at
-the known cluster-based stellar ages ages, in order to estimate
-(model-dependent) stellar masses.
-For the two systems without known ages (see below), we omit this mass
-estimate, due to the degeneracies in the inference problem.
+\mathcal{Z} < 0.01$, where $\mathcal{Z}$ denotes the evidence.
+
+With the effective temperatures and stellar radii from the SED fit, we
+then estimated the stellar masses by interpolating against the PARSEC
+isochrones \citep[v1.2S][]{2014MNRAS.444.2525C}.  The need for models
+that incorporate some form of correction for young, active M-dwarfs is
+well-documented
+\citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2020ApJ...891...29S}.
+Plausible explanations for anomalous M-dwarf colors and sizes relative to
+model predictions include star starspot coverage
+\citep[e.g.][]{2017ApJ...836..200G}, and potentially incomplete line
+lists \citep[e.g.][]{2013A&A...556A..15R}.  In the PARSEC models,
+\citet{2014MNRAS.444.2525C} performed an empirical correction to the
+temperature--opacity relation drawn from the BT-Settl model atmospheres,
+in order to match observed masses and radii of younq eclipsing binaries.
+This is sufficient for our purpose of estimating accurate stellar masses.
+Given our observed $\{ \tilde{T}_{\rm eff}, \tilde{M}_\star, \tilde{t} \}$,
+and approximating their uncertainties as Gaussian
+$\sigma_{\tilde{T}_{\rm eff}}$, $\sigma_{\tilde{M}_\star}$ and
+$\sigma_{\tilde{t}}$, we evaluate a distance $d$ between our observations
+and any model PARSEC grid-point $\{ T_{\rm eff}, M_\star, t \}$ as
+\begin{equation}
+  d^2 = 
+  \left( \frac{\tilde{T}_{\rm eff} - T_{\rm eff}}{\sigma_{\tilde{T}_{\rm eff}}} \right)^2
+  +
+  \left( \frac{\tilde{M}_{\star} - M_{\star}}{\sigma_{\tilde{M}_{\star}}} \right)^2
+  +
+  \left( \frac{\tilde{t} - t}{\sigma_{\tilde{t}}} \right)^2,
+\end{equation}
+in order to assign equal importance to each dimension.  The preferred
+model mass is then one that minimizes this distance, and is quoted in
+Table~\ref{tab:thetable}.
 
@@
       {\bf Validation plots used to label CQVs}.  The complete figure
-      set of \ncpvsfound\ images is available online.
+      set, with one image per sector for each of \ncpvsfound\ objects
+      is available online.
       Panels are as follows.
@@
 \section{LP 12-502}
+\label{app:lp}
 
@@
 
-\begin{figure*}[!t]
+\begin{figure*}[!tp]
 	\begin{center}
@@
 		\caption{
-      {\bf LP 12-502 light curve}, split into time chunks.
+      {\bf LP 12-502 light curve}, where each time chunk represents one TESS orbit.
+      Flares are drawn in gray.
+      The red vertical lines highlight apparently instantaneous state changes in
+      the shape of the dip pattern.
+      The light curve is binned to 15-minute intervals so that
+      there are 96 points per day.  Data gaps are not drawn.
 		}

### 2023-06-26 complexrotators/isochroneinterp.py
minor edits

@@ -2,6 +2,7 @@
 Tools when interpolating against isochrones.
 
 | get_Feiden2016
+| get_PARSEC
 """
 import os
 from os.path import join
@@ -76,5 +77,6 @@ def get_PARSEC():
     df['Teff'] = np.array(Teff.value)
     df['Rstar'] = np.array(Rstar.value)
     df['logRstar'] = np.log10(np.array(Rstar.value))
+    df['age'] = 10**(df.logAge) / (1e6)
 
     return df

### 2023-06-26 complexrotators/plotting.py

@@ -2614,6 +2614,12 @@ def plot_tic4029_segments(outdir):
                 transform=tform, ha='right',va='bottom', color='k',
                 fontsize=fontsize, bbox=props)
 
+    x, y, dx, dy = 7.52, -44, 0, 2
+    ax.vlines(x, y, y+dy, colors='red', zorder=30, linewidths=0.5)
+
+    x, y, dx, dy = 5.98, -51, 0, 2
+    ax.vlines(x, y, y+dy, colors='red', zorder=30, linewidths=0.5)
+
     ax.text(0.97, 0.98, 'Cycle #', va='top', ha='right', fontsize=6,
             bbox=props, transform=ax.transAxes)
 

### 2023-06-26 paper/ms.tex
update ms

@@
 on the abundance of CQVs in the 40\,Myr Tuc-Hor and Columba, the
-similarly-aged IC\,2602 and IC\,2391 clusters should have a large
+similarly-aged IC\,2602 and IC\,2391 clusters should show a large
 number of CQVs in the TESS full frame image data.
@@
 either star with any young groups.  Both objects were noted as being in the
-``diffuse'' Class~II YSO population near the Sun by \citet{2021ApJ...917...23K}.
+``diffuse'' Class~III YSO population near the Sun by \citet{2021ApJ...917...23K}.
 That diffuse population may contain kinematic structures that have yet
@@
 line of evidence supporting the reality, and youth, of that group.
+
+\subsection{Infrared excesses}
+
+As is typical for CQVs \citep{2017AJ....153..152S}, most CQVs in our
+catalog did not show infrared excesseses in the WISE1-4 bands.
+Visually inspecting the SEDs, we labelled two objects as having
+``good'' infrared excesses (both W3 and W4), and three as ``possible''
+infrared excess.
+
+The two ``good'' IR excesses were TIC~193136669 (TWA~34) and
+TIC~57830249 (TWA~33).  Both are in the TW Hydrae association
+($\approx$10\,Myr), and have ``long'' periods of 38\,hr and 44\,hr
+respectively.  In our initial labelling, we labelled both as ``maybe''
+CQVs because the dips in their light curves did not show the rigid
+periodicity typical of CQVs;  their periods were also relatively
+long.  After labelling them, we learned that TIC 193136669 has a cold
+molecular disk based on observed 1.3\,mm continuum emission and
+resolved Keplerian $^{12}{\rm CO}(2-1)$ emission
+\citep{2015A&A...582L...5R}.  It has also been labelled a dipper by
+\citet{2022ApJS..263...14C}; we agree with their designation, but
+nonetheless leave it in our catalog as an indication of possible
+ambiguities in our search process.  TIC 57830249 (TWA~33) also has
+previously detected 1.3\,mm continuum emission
+\citep{2015A&A...582L...5R}, suggestive of cold dust grains being
+present.  It therefore probably also a dipper that snuck its way into
+our ``maybe'' pile.
+
+Our three ``possible'' infrared excesses were TIC~405910546,
+289840926, and 244161191.  After a literature search, we concluded
+that none have clear evidence for the presence of a disk.
+TIC~405910546, in LCC, shows a unique TESS light curve, reminescent of
+a $P$=38\,hr singly-eclipsing binary, except with additional
+substructure during each eclipse that resembles the CQV phenomenon
+more than any other variability of which we are aware.  TIC~289840926
+($\beta$~Pic moving group, $P$=4.8\,hr), show what we believe is a
+clear CQV signals, but has no definitive evidence for a large, dusty
+disk.  TIC~244161191 (hilariously, TOI-278), in Columba, also has no
+definitive evidence for a large disk.  It is however
+``multi-periodic''---in addition to the 7.17\,hr CPV signal, there is
+a superposed 8.39\,hr sinusoidal signal, probably from an unresolved
+binary neighbor.
+
+Comparing these results against the backdrop of our increasing
+understanding of dippers
+\citep[e.g.][]{2014AJ....147...82C,2016ApJ...816...69A,2021ApJ...908...16R,2022ApJS..263...14C},
+it is clear that the loss of an infrared excess is associated with
+strong changes in a star's optical variability.  It is not
+unreasonable to imagine connections between CQVs and dippers: both
+classes of object can show transient flux dips that are relatively
+narrow in duration.  Such dips are probably caused by clumps of dust.
+However the CQV dips are typically {\it i}) more periodic and {\it
+ii}) less deep than those of dippers, and {\it iii}) they display far
+less transience over timescales of a few to tens of cycles.  At a
+population level, the CQV stars are also older.  A shared mystery
+between the CQVs and dippers, in our own estimation however, is the
+exact mechanism that produces the {\it narrowness} of the dust clumps
+in certain cases.  It is not unreasonable to imagine a similar
+mechanism operating for both types of object, tied perhaps to a shared
+magnetic topology, or perhaps to a preference for dust to inspiral to
+the star in clumps from tidally disrupted infalling bodies.
 
@@
       The light curve is binned to 15-minute intervals so that
-      there are 96 points per day.  Data gaps are not drawn.
+      there are 96 points per day.  Data gaps with more than one missing 15-minute
+      cadence appear in white.
 		}
@@
 		}
-	\vspace{-0.1cm}
+	\vspace{-1cm}
 			\subfloat{
@@
 	\end{center}
+	\vspace{-0.4cm}
 	\caption{
@@
 
-\begin{figure*}[!t]
-	\begin{center}
-		\centering
-		\includegraphics[width=0.96\textwidth]{TIC4029_zoom.png}
-		\vspace{-0.45cm}
-		\caption{
-			{\bf LP 12-502 cycles 1233-1247}, showing the most dramatic state
-			change observed over the three year baseline.
-		}
-		\label{fig:lpzoom}
-	\end{center}
-\end{figure*}
+%
+%\begin{figure*}[!t]
+%	\begin{center}
+%		\centering
+%		\includegraphics[width=0.96\textwidth]{TIC4029_zoom.png}
+%		\vspace{-0.45cm}
+%		\caption{
+%			{\bf LP 12-502 cycles 1233-1247}, showing the most dramatic state
+%			change observed over the three year baseline.
+%		}
+%		\label{fig:lpzoom}
+%	\end{center}
+%\end{figure*}
 

### 2023-06-26 complexrotators/sedfit.py
sedfit: fix DR2<->DR3 conflation
which matters in astroARIADNE

@@ -50,12 +50,15 @@ def run_SED_analysis(ticid, trimlist=None):
     ra = float(gdr2_df.ra)
     dec = float(gdr2_df.dec)
     starname = f'TIC_{ticid}'
-    g_id = int(gdr2_df.dr2_source_id)
+    #g_id = int(gdr2_df.dr2_source_id)
 
     out_folder = join(RESULTSDIR, 'ariadne_sed_fitting', f'{starname}')
     if not os.path.exists(out_folder): os.mkdir(out_folder)
 
-    s = Star(starname.replace("_"," "), ra, dec, g_id=g_id)
+    s = Star(starname.replace("_"," "), ra, dec)
+
+    # NOTE: the "g_id" constructor here is actually (incorrectly!) assuming Gaia DR3 source_id's.
+    # s = Star(starname.replace("_"," "), ra, dec, g_id=g_id)
 
     # remove TESS mag; no new information
     s.remove_mag('TESS')

### 2023-06-26 paper/ms.tex
update ms

@@
 		\subfloat{
-			\includegraphics[width=0.8\textwidth]{lc_mosaic_fav3.pdf}
+			\includegraphics[width=0.8\textwidth]{f1a.pdf}
 		}
 
-		\vspace{-0.4cm}
+		\vspace{-0.45cm}
 		\subfloat{
-			\includegraphics[width=0.8\textwidth]{models.pdf}
+			\includegraphics[width=0.8\textwidth]{f1b.pdf}
 		}
 	\end{center}
+		\vspace{-0.2cm}
 	\caption{
@@
 		dust clump scenario seems most plausible, given
-		the stability of the phenomenon, the lack of observed infrared
+		the stability of the dips, the lack of observed infrared
 		excesses, and the challenge of producing broadband opacity variations

### 2023-06-26 paper/collect.sh

@@ -1,20 +1,9 @@
-resultsdir="/Users/luke/Dropbox/proj/gyro-interp/results"
-cp $resultsdir/prot_vs_teff/prot_vs_teff_α_Per_Pleiades_Blanco-1_Psc-Eri_NGC-3532_Group-X_Praesepe_NGC-6811_NGC-6819_Ruprecht-147_slowseq_poly7__100_to_2600_interpmethodpchip_m67.pdf f1a.pdf
-cp $resultsdir/prot_vs_teff/prot_vs_teff_α_Per_Pleiades_Blanco-1_Psc-Eri_NGC-3532_Group-X_Praesepe_NGC-6811_models_poly7_α_Per_120-Myr_300-Myr_Praesepe_NGC-6811_interpmethodpchip_m67.pdf f1b.pdf
+resultsdir="/Users/luke/Dropbox/proj/cpv/results/"
+addir="/Users/luke/Dropbox/Documents/proposals/2023_05_ADAP/latex/figs/"
 
-cp $resultsdir/data_vs_model_prot/data_vs_model_α_Per_Pleiades_Blanco-1_Psc-Eri_NGC-3532_Group-X_Praesepe_NGC-6811_models_poly7_α_Per_120-Myr_300-Myr_Praesepe.pdf f2.pdf
+# fig1
+cp $resultsdir/lc_mosaic/lc_mosaic_fav3.pdf f1a.pdf
+cp $addir/models.pdf f1b.pdf
 
-cp $resultsdir/multi_age_posteriors_mcmc/age_posteriors_Teff5800_Prot2.0_3.5_5.0_6.5_8.0_9.5_11.0.pdf f3a.pdf
-cp $resultsdir/multi_age_posteriors_mcmc/age_posteriors_Teff5000_Prot4.0_5.5_7.0_8.5_10.0_11.5_13.0.pdf f3b.pdf
-cp $resultsdir/multi_age_posteriors_mcmc/age_posteriors_Teff4200_Prot9.0_10.5_12.0_13.5_15.0_16.5.pdf f3c.pdf
-
[…]

### 2023-06-27 paper/ms.tex
update ms

@@
 Some CQVs show up to eight local minima (dips) per cycle; sharp peaks
-are also common.  Most CQVs are pre-main-sequence M-dwarfs without
+are common, but .  Most CQVs are pre-main-sequence M-dwarfs without
 near-infrared excesses, with ages of $\approx$5-150 million years
@@
 
-\begin{figure*}[!t]
+\begin{figure*}[!tp]
 	\begin{center}
 		\centering
-		\includegraphics[width=\textwidth]{lc_mosaic_dlt150_good_all.pdf}
+		\includegraphics[width=\textwidth]{f2.pdf}
+    \vspace{-0.7cm}
 		\caption{
-			{\bf CQVs from a search of the TESS 2-minute data at
+      {\bf CQVs found in the TESS 2-minute data at
       $d$$<$150\,pc, acquired between July~2018 and Sep~2022.}
-			Phased TESS light curves over 1 month are shown for 40 CQVs;
-			they include the brightest and closest examples of CQVs known
-			($V$=14; $J$=9.5; $d$=25\,pc).  Gray are raw 2-minute data;
-			black bins to 300 points per cycle.  Periods in hours are listed
-			in the lower right corners of each panel.
-			{\bf todo:  add TIC IDs and sector numbers}.
-			% TODO: sort by brightness maybe?
-			% TODO: sort by period?
+      Phased TESS light curves over one month are shown for \ngoods\
+      CQVs.
+      Gray are raw 2-minute data;
+			black bins to 300 points per cycle.  Each panel is labelled by
+      the TIC identifier, the TESS sector number, and the period in hours.
+      The ordering is discussed in Section~\ref{sec:catalog}
 		}
@@
 \subsection{CQV catalog}
+\label{sec:catalog}
 
 Table~\ref{tab:thetable} lists the \ncpvsfound\ CQVs identified by our
-search, and some of their important properties.  \ngoods\ objects
-demonstrate what we view as unambiguous characteristics of the CQV
-phenomenon in at least one TESS sector, and we refer to these as the
-``gold sample''.  The remaining \nmaybes\ CQV candidates were
-ambiguous (in our view), and their variability might be caused by say,
-multiple starspot groups.  Additional TESS data could help resolve
-their classification.
+search, along important physical and observational properties.
+\ngoods\ objects demonstrate what we view as unambiguous
+characteristics of the CQV phenomenon in at least one TESS sector, and
+we refer to these as the ``gold sample''.  The remaining \nmaybes\ CQV
+candidates were ambiguous (in our view), and their variability might
+be caused by say, multiple starspot groups.  Additional data from TESS
+or other instruments can help resolve their classification; in
+Section~\ref{subsec:irexcess} below for instance we discuss
+a few cases in this ambiguous sample that are probably dippers.
 
 The mosaic in Figure~\ref{fig:singlemosaic} shows phased light curves
-for the 40 brightest objects.  The TESS sectors in which these objects
-were identified show anywhere from one to eight local minima per
-cycle.  Some stars show relatively ordinary modulation during one
+for the \ngoods\ bonafide CQVs.  
+The objects are sorted first in order of the number of TESS sectors in
+which they clearly demonstrated the CQV phenomenon, and secondarily by
+descending brightness.
+The objects at the top therefore have the most data.
+
+Generally, Figure~\ref{fig:singlemosaic} shows a broad range of
+variability, with anywhere from two to eight local minima per cycle.  
+Some stars show relatively ordinary modulation during one
 continuous portion of the phased light curve, and highly structured
@@
 these two modes.
+
+A few objets at first glance seem reminiscent of eclipsing binaries, for
+instance TIC~193831684.
+In every such case,
 
@@
 \subsection{Infrared excesses}
+\label{subsec:irexcess}
 
@@
 Figure~\ref{fig:lplc} shows an alternative view of the LP-502 light
-curve from Figure~\ref{fig:lp}, 
-split into ``time chunks'' wherever there was more than half a day of
-missing data in the TESS light curve.
-We binned the light curve to 15-minute intervals for visual clarity,
-and required at least one (120-second cadence) flux measurement per
-bin.
+curve from Figure~\ref{fig:lp}, split into successive TESS orbits.  We
+binned the light curve to 15-minute intervals for visual clarity, and
+required at least one (120-second cadence) flux measurement per bin.
 Points more than 2.5$\sigma$ above the median are drawn in gray, also
-for visual clarity.
-Missing data are not drawn (a common plotting error when ``drawing''
-light curves, rather than showing a scatter plot).
-
-{\it State switches}---
-Figure~\ref{fig:lpzoom} shows an alternative view of cycles 1233-1247.
+for visual clarity.  Missing data are not drawn (a common plotting
+error when ``drawing'' light curves, rather than showing a scatter
+plot).  The red lines point to specific state switches, discussed
+elsewhere in the text.
+
+Figure~\ref{fig:lp2} shows another alternative view of
+Figure~\ref{fig:lp}, but arranged to enable easy visual appreciation
+of transit timing changes, rather than transit depth changes.
+A best-fitting two-harmonic sinusoid has been independently fitted and
+subtracted from the Sector
+18-19 data, 25-26 data, and 53, 58, and 59 data.
+
+Finally, Figure~\ref{fig:lpriver0} shows ``river plots'' of the
+same data, split into very similar intervals:
+the Sector 18-19 data, 25-26 data, 53 data, and 58-59 data.
+State changes are evident in these plots whenever there is a sudden
+change in color.
+{\bf todo: fix missing data to be different from the flare color}
 
@@
 
-%
-%\begin{figure*}[!t]
-%	\begin{center}
-%		\centering
-%		\includegraphics[width=0.96\textwidth]{TIC4029_zoom.png}
-%		\vspace{-0.45cm}
-%		\caption{
-%			{\bf LP 12-502 cycles 1233-1247}, showing the most dramatic state
-%			change observed over the three year baseline.
-%		}
-%		\label{fig:lpzoom}
-%	\end{center}
-%\end{figure*}
-
 \section{No additional power at 20~second cadence}

### 2023-06-27 paper/collect.sh

@@ -6,4 +6,4 @@ cp $resultsdir/lc_mosaic/lc_mosaic_fav3.pdf f1a.pdf
 cp $addir/models.pdf f1b.pdf
 
 # fig2
-cp $resultsdir/lc_mosaic/lc_mosaic_dlt150_good_54.pdf f2.pdf
+cp $resultsdir/full_lcmosaic/full_lcmosaic_showtitles_Ngoodsectors_tic8_Tmag.pdf f2.pdf

### 2023-06-27 complexrotators/plotting.py
add full mosaic plot

@@ -17,6 +17,7 @@ Contents:
     | plot_quasiperiodic_removal_diagnostic
 
     | plot_lc_mosaic
+    | plot_full_lcmosaic
     | plot_phase_timegroups_mosaic
 
     | plot_cadence_comparison
@@ -97,7 +98,9 @@ from scipy.interpolate import interp1d, PchipInterpolator
 
 from aesthetic.plot import savefig, format_ax, set_style
 
-from complexrotators.paths import DATADIR, PHOTDIR, SPOCDIR, LOCALDIR
+from complexrotators.paths import (
+    DATADIR, PHOTDIR, SPOCDIR, LOCALDIR, TABLEDIR
+)
 from complexrotators.lcprocessing import cpv_periodsearch
 
 from astroquery.mast import Catalogs
@@ -2406,6 +2409,229 @@ def plot_lc_mosaic(outdir, subset_id=None, showtitles=0,
     fig.tight_layout(h_pad=0.2, w_pad=0.)
 
     outpath = join(outdir, f'lc_mosaic_{s}.png')
+    savefig(fig, outpath, dpi=400)
+
+
+def plot_full_lcmosaic(outdir, showtitles=1, titlefontsize=3.5,
+                       sortby=None):
+    """
+    the one that makes the publication
+    (on mico, assuming that find_CPVs.py has been run using sample_id=="2023catalog_LGB_RJ_concat")
+    """
+
+    # load ticids
+    N_objects = 53 # fine if longer/shorter, just requires tweaking
+
+    tablepath = join(
+        TABLEDIR, "2023_catalog_table",
+        '20230613_LGB_RJ_CPV_TABLE_supplemental_selfnapplied.csv'
+    )
+    df = pd.read_csv(tablepath, sep="|")
+    _df = df[~pd.isnull(df.goodsectors)]
+    assert len(_df) == N_objects
+
+    # get manually written sectors to plot
+    sectorpath = join(
+        DATADIR, 'targetlists', '20230613_LGB_RJ_sectorpref.csv'
+    )
+    tdf = pd.read_csv(sectorpath)
+
+    # merge to same dataframe
+    df = _df.merge(tdf, on='ticid', how='inner')
+    assert len(df) == N_objects
+
+    if isinstance(sortby, str):
+        if sortby in ['tic8_Tmag','tlc_mean_period','dist_pc']:
+            df = df.sort_values(by=sortby)
[…]

### 2023-06-27 drivers/plot_full_mosaic.py

@@ -1,0 +1,13 @@
+import os
+import complexrotators.plotting as rp
+from complexrotators.paths import RESULTSDIR
+
+PLOTDIR = os.path.join(RESULTSDIR, 'full_lcmosaic')
+if not os.path.exists(PLOTDIR):
+    os.mkdir(PLOTDIR)
+
+rp.plot_full_lcmosaic(PLOTDIR, sortby='Ngoodsectors_tic8_Tmag')
+rp.plot_full_lcmosaic(PLOTDIR, sortby='tlc_mean_period')
+assert 0
+rp.plot_full_lcmosaic(PLOTDIR, sortby='tic8_Tmag')
+rp.plot_full_lcmosaic(PLOTDIR, sortby='dist_pc')

### 2023-06-27 paper/ms.tex
update ms

@@
 	\end{center}
-		\vspace{-0.2cm}
+		\vspace{-0.3cm}
 	\caption{
@@
 for $N_{\rm baseline}$ the number of cycles in the observed baseline and
-$\sigma_{\rm phi}$ the phase precision with which any one feature (e.g.~a
+$\sigma_{\phi}$ the phase precision with which any one feature (e.g.~a
 dip) can be tracked.
@@
 	%
-	\item The same CQV can show dips with closely-spaced periods.  
+	\item The same CQV can show dips with very similar but clearly distinct periods.  
 	LP 12-502, for instance, showed dips with four distinct periods within $\pm 0.3\%$

### 2023-06-27 paper/ms.tex
update ms

@@
 		\caption{
-      {\bf CQVs found in the TESS 2-minute data at
-      $d$$<$150\,pc, acquired between July~2018 and Sep~2022.}
+      {\bf CQVs found in the TESS 2-minute data.}
       Phased TESS light curves over one month are shown for \ngoods\
@@
 periods might be expected to show the phenomenon in equal number --
-independent of age.
-This is because the stellar dynamo for M-dwarfs is generated by fluid
+irrespective of age.
+This is because the stellar dynamo is generated by fluid
 motions inside the star, which should be identical for stars of the
@@
 distributions as a function of azimuth.
-Second, and perhaps more serious, a planetesimal swarm should be expected
-to be {\it exactly periodic} over observable timescales, on the presumption that the planetesimals
+Second, and perhaps more serious, the (unseen) planetesimals 
+should
+be on {\it exactly periodic} orbits over observable timescales, on the presumption that the planetesimals
 would be massive enough to not feel any headwind or magnetic field.
@@
 is both short-lived, and unique.
-This suggests structures much less massive than a 1--100\,km sized
+The fundamental 18.5611\,hr period itself is itself associated with
+material at too many phases to arguably be tied to a single launching body.
+This suggests that the dust clumps must be much less massive than a 1--100\,km sized
 planetesimal,
- more strongly
-which could be more strongly influenced by the stellar magnetic field.
+and therefore more easily influenced by the stellar magnetic field, and events
+like flares.
 
@@
 likely path toward definitive resolutions would be to observe a full
-phase curve of LP 12-502 using JWST/MIRI.
+phase curve of LP 12-502, or perhaps some other suitable object, using JWST/MIRI.
 

### 2023-06-28 paper/ms.tex
update ms

@@
 
-\title{Corotating Dust Clumps Around Adolescent M-Dwarfs: Four Years of TESS}
+\title{Corotating Dust Clumps Around Adolescent Low-Mass Stars: Four Years of TESS}
 
@@
   Complex quasiperiodic variables (CQVs) are low-mass
-  pre-main-sequence stars with nearly periodic optical modulation that
-  is likely induced by long-lived transiting dust clumps in orbit at
-  the Keplerian corotation radius.  Here, we report new CQVs
-  discovered in TESS data collected between July~2018 and Sep~2022.
-  From our analysis of \nstarssearched\ K- and M-dwarfs with $T$$<$16
-  and $d$$<$150\,pc, we find \ngoods\ gold-standard CQVs.  Most of
-  these discoveries are new, and they include the brightest and
-  closest examples of this class of object known ($T$$\approx$11;
-  $d$$\approx$20\,pc).  A few objects are outliers among outliers; LP
-  12-502 for instance shows a ``dip complex'' with a period and total
-  duration that are fixed over more than 1000 cycles, but in detail
-  this object shows anywhere from four to eight local minima per
-  cycle.  LP-502 also demonstrated drastic shape changes over less
-  than one cycle, and at times displayed distinct superposed periods
-  simultaneously.  Generally speaking, we find that none of the CQVs
-  maintain a fixed light curve shape over timescales of more than a
-  few hundred cycles -- they are all {\it quasi}periodic.  We revisit
-  the arguments for why corotating dust clumps are the most likely
-  explanation, though there are other possibilities, and all lines of
-  evidence are currently indirect.  In the future, we expect that our
-  sample will help facilitate modeling and observational efforts aimed
-  at understanding these objects, and connecting them to the broader
+  pre-main-sequence stars with nearly periodic optical modulation.
+  The modulation is likely induced by dust clumps in orbit at the
+  Keplerian corotation radius.  Here, we report new CQVs discovered in
+  TESS data collected between July~2018 and Sep~2022, and analyze
+  their variability.  Our analysis of \nstarssearched\ K- and
+  M-dwarfs with $T$$<$16 and $d$$<$150\,pc yielded \ngoods\
+  gold-standard CQVs.  Most of these discoveries are new, and they
+  include the brightest and closest examples of this class of object
+  known ($T$$\approx$11; $d$$\approx$20\,pc), as well as the most
+  massive ($\approx$0.65\,M$_\odot$).  A few objects are outliers
+  among outliers; LP 12-502 for instance shows a ``dip complex'' with
+  a period and total duration that are fixed over more than 1000
+  cycles, but which in detail shows anywhere from four to eight
+  local minima per cycle.  LP-502 also demonstrated drastic shape
+  changes over less than one cycle, and at times displayed distinct
+  superposed periods simultaneously.  Broadly speaking, we find that
+  none of the CQVs maintain a fixed light curve shape over timescales
+  of more than a few hundred cycles -- they are all {\it
+  quasi}periodic.  We revisit the arguments for why transient
+  corotating dust clumps are the most likely explanation, though there
+  are other possibilities.  In the future, we expect that our sample
+  will help facilitate modeling and observational efforts aimed at
+  understanding these objects, and connecting them to the broader
   contexts of star, disk, and exoplanet evolution.
@@
 or other instruments can help resolve their classification; in
-Section~\ref{subsec:irexcess} below for instance we discuss
-a few cases in this ambiguous sample that are probably dippers.
+Section~\ref{subsec:irexcess} below for instance we discuss a few
+cases in this ambiguous sample that are probably dippers.
 
 The mosaic in Figure~\ref{fig:singlemosaic} shows phased light curves
-for the \ngoods\ bonafide CQVs.  
-The objects are sorted first in order of the number of TESS sectors in
-which they clearly demonstrated the CQV phenomenon, and secondarily by
-descending brightness.
-The objects at the top therefore have the most data.
-
-Generally, Figure~\ref{fig:singlemosaic} shows a broad range of
-variability, with anywhere from two to eight local minima per cycle.  
-Some stars show relatively ordinary modulation during one
-continuous portion of the phased light curve, and highly structured
-modulation in the remainder of the cycle (e.g. TIC~206544316,
-TIC~224283342, TIC~402980664).  Others show structured modulation over
-the entire span of a cycle (e.g. TIC~2234692, TIC~401789285,
-TIC~425933644, TIC~142173958).  Others still show some mix between
-these two modes.
-
-A few objets at first glance seem reminiscent of eclipsing binaries, for
-instance TIC~193831684.
-In every such case,
+for the \ngoods\ bonafide CQVs.  The objects are sorted first in order
+of the number of TESS 120-second cadence sectors in which they clearly
+demonstrated the CQV phenomenon, and secondarily by descending
+brightness.  The objects at the top therefore have the most 120-second
+cadence data.  The top five objects by this metric are TIC~300651846
+($T$$=$13.5, 12 sectors); TIC~402980664 ($T$$=$11.1, 7 sectors);
+TIC~89463560 ($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5
+sectors); and TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest
+five CQVs span 9.3$<$$T$$<$11.1; the faintest five span
+14.5$<$$T$$<$15.0.  The fastest five have periods spanning
+3.6\,hr$<$$P$$<$6.2\,hr, while the slowest five span
+27\,hr$<$$P$$<$38\,hr.
+
+In terms of the light curve shapes, Figure~\ref{fig:singlemosaic}
+shows a broad range of variability, with anywhere from two to eight
+local minima per cycle.  Some stars show relatively ordinary
+modulation during one continuous portion of the phased light curve,
+and highly structured modulation in the remainder of the cycle (e.g.
+TIC~206544316, TIC~224283342, TIC~402980664).  Others show structured
+modulation over the entire span of a cycle (e.g. TIC~2234692,
+TIC~401789285, TIC~425933644, TIC~142173958).  Others still show some
+mix between these two modes.
+
+A small number of objects at first glance seem reminiscent of
+eclipsing binaries, for instance TIC~193831684 or TIC~5714469.  In the
+few such cases, we believe that that are unlikely to be eclipsing
+binaries due to additional coherent variations in the light curves
+that are distinct from any binary phenomenology of which we are aware.
 

### 2023-06-28 paper/ms.tex
update ms

@@
 
-		\vspace{-0.45cm}
+		\vspace{-0.6cm}
 		\subfloat{
@@
       the TIC identifier, the TESS sector number, and the period in hours.
-      The ordering is discussed in Section~\ref{sec:catalog}
+      Objects are ordered such that sources with the most TESS data available are
+       on top (see Section~\ref{sec:catalog}).
 		}
@@
 
-\begin{figure*}[!t]
+\begin{figure*}[!tp]
 	\begin{center}
 		\centering
-		\includegraphics[width=0.9\textwidth]{lc_mosaic_dlt150_good_allchangers_2count_showtitles.png}
-		\vspace{-0.2cm}
+		\includegraphics[width=\textwidth]{f3.pdf}
+		\vspace{-0.6cm}
 		\caption{
-			{\bf Evolution of CQVs}: ``Before and
-			after'...  Panels
-			in the top two rows are separated by two years
-			($\approx$$10^3$ cycles); each panel shows one month.
-			Periods are listed in hours. 
-			{\bf todo: fix the plot and the caption.}
-			%			\vspace{-0.8cm}
+		{\bf CQVs keep their periods but change their shapes.}
+      32 of our \ngoods\ CQVs from Figure~\ref{fig:singlemosaic} 
+      had 120-second cadence TESS data available for
+      a baseline of at least two years; the 27 brightest are shown here.
+      Each panel shows one sector of TESS data, and is phased to its deepest minimum in flux.
+      Each panel's title shows the TIC identifier and approximate period in hours.
+      Text insets show the TESS sector numbers, which generally span two years, or at least
+      1{,}000 cycles.
+      The vertical scale is fixed across sectors to clarify shape changes.
 		}
@@
 \subsection{Evolution over adjacent sectors, \& LP 12-502}
+
+\begin{figure*}[!tp]
+	\begin{center}
+		\centering
+		\includegraphics[width=\textwidth]{f4.pdf}
+		\vspace{-0.4cm}
+		\caption{
+			{\bf LP 12-502 (TIC~402980664) light curve}, where each time chunk represents one TESS orbit.
+			Data were acquired in Sectors 18-19, 25-26, 53, and 57-58.
+			Flares are drawn in gray.
+			The red vertical lines highlight apparently instantaneous state changes in
+			the shape of the dip pattern.
+			The light curve is binned to 15-minute intervals so that
+			there are 96 points per day.  Data gaps with more than one missing 15-minute
+			cadence appear in white.
+		}
+		\label{fig:lplc}
+	\end{center}
+\end{figure*}
+
 \begin{figure*}[!t]
@@
 $T$=11.1) stood out as an outlier among the CQV class.
-Figure~\ref{fig:lp} shows all available data from Sectors
+Figure~\ref{fig:lplc} shows all available data from Sectors
 18, 19, 25, 26, 53, 58, and 59; the star was observed at 120-second
 cadence whenever it was observable by TESS.
+Figure~\ref{fig:lp} shows the same data, grouped into successive
+TESS orbits spanning half a lunar month each.
 Measuring the PDM peak period over each sector independently yielded
@@
 
-\begin{figure*}[!tp]
-	\begin{center}
-		\centering
-		\includegraphics[width=0.96\textwidth]{tic4029_segments.pdf}
-		\vspace{-0.2cm}
-		\caption{
-      {\bf LP 12-502 light curve}, where each time chunk represents one TESS orbit.
-      Flares are drawn in gray.
-      The red vertical lines highlight apparently instantaneous state changes in
-      the shape of the dip pattern.
-      The light curve is binned to 15-minute intervals so that
-      there are 96 points per day.  Data gaps with more than one missing 15-minute
-      cadence appear in white.
-		}
-		\label{fig:lplc}
-	\end{center}
-\end{figure*}
-
 \begin{figure*}[!t]

### 2023-06-28 paper/collect.sh

@@ -7,3 +7,9 @@ cp $addir/models.pdf f1b.pdf
 
 # fig2
 cp $resultsdir/full_lcmosaic/full_lcmosaic_showtitles_Ngoodsectors_tic8_Tmag.pdf f2.pdf
+
+# fig3
+cp $resultsdir/beforeafter_mosaic/beforeafter_mosaic_showtitles_tic8_Tmag.pdf f3.pdf
+
+# fig4
+cp $resultsdir/tic4029_segments/tic4029_segments.pdf f4.pdf

### 2023-06-28 complexrotators/plotting.py
add beforeafter mosaic

@@ -18,6 +18,8 @@ Contents:
 
     | plot_lc_mosaic
     | plot_full_lcmosaic
+    | plot_beforeafter_mosaic
+
     | plot_phase_timegroups_mosaic
 
     | plot_cadence_comparison
@@ -908,11 +910,18 @@ def plot_phased_light_curve(
                 lw=0.5, rasterized=True, alpha=alpha0)
 
     orb_bd = phase_bin_magseries(x_fold, y, binsize=binsize_phase, minbinelems=1)
-    ax.scatter(
-        orb_bd['binnedphases'], norm(orb_bd['binnedmags']), color=c1,
-        s=BINMS, linewidths=0,
-        alpha=alpha1, zorder=1002#, linewidths=0.2, edgecolors='white'
-    )
+    if c1 == 'k':
+        ax.scatter(
+            orb_bd['binnedphases'], norm(orb_bd['binnedmags']), color=c1,
+            s=BINMS, linewidths=0,
+            alpha=alpha1, zorder=1002#, linewidths=0.2, edgecolors='white'
+        )
+    else:
+        ax.scatter(
+            orb_bd['binnedphases'], norm(orb_bd['binnedmags']), color=c1,
+            s=BINMS, linewidths=0.07, edgecolors='k',
+            alpha=alpha1, zorder=1002#, linewidths=0.2, edgecolors='white'
+        )
 
     if isinstance(findpeaks_result, dict):
 
@@ -2635,6 +2644,457 @@ def plot_full_lcmosaic(outdir, showtitles=1, titlefontsize=3.5,
     savefig(fig, outpath, dpi=400)
 
 
+def plot_beforeafter_mosaic(outdir, showtitles=1, titlefontsize=3.75,
+                            sortby=None):
+    """
+    the one that makes the publication
+    (on mico, assuming that find_CPVs.py has been run using
+    sample_id=="2023catalog_LGB_RJ_concat")
+    """
+
+    # load ticids
+    N_objects = 53 # fine if longer/shorter, just requires tweaking
+
+    tablepath = join(
+        TABLEDIR, "2023_catalog_table",
+        '20230613_LGB_RJ_CPV_TABLE_supplemental_selfnapplied.csv'
+    )
+    df = pd.read_csv(tablepath, sep="|")
+    _df = df[~pd.isnull(df.goodsectors)]
+    assert len(_df) == N_objects
+
+    # get manually written sectors to plot
[…]

### 2023-06-29 paper/ms.tex
update ms

@@
 Section~\ref{subsec:irexcess} below for instance we discuss a few
-cases in this ambiguous sample that are probably dippers.
+cases in this ambiguous sample that after additional analysis were
+clarified as dippers.  We also emphasize that our initial
+classifications were based on whether {\it any} TESS sectors showed
+evidence for the CQV phenomenon.
 
@@
 A small number of objects at first glance seem reminiscent of
-eclipsing binaries, for instance TIC~193831684 or TIC~5714469.  In the
+eclipsing binaries, such as TIC~193831684 or TIC~5714469.  In the
 few such cases, we believe that that are unlikely to be eclipsing
@@
 			and duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than
-			one cycle.
+			one cycle (see Figure~\ref{fig:lplc}).
 		}
@@
 
+\paragraph{Extremes}
+The closest CQV in our catalog is DG~CVn (TIC~368129164;
+$d$$=$18\,pc), which is a likely member of AB Dor.  To our knowledge,
+this manuscript is the first time that it has been noted as a CQV.
+
+The shortest period belongs to TIC~201789285, at 3.64\,hr.
+The longest period belongs to TIC~405910546, at 37.9\,hr.  If
+that source turns out to be an eclipsing binary, then the next-longest
+would be TIC~193831684 (31.0\,hr).
+
+The lowest mass ($\approx 0.12$\,M$_\odot$) belongs to TIC~50745567.
+There are a number of other similar very low mass stars, which
+suggests the phenomenon may extend into the brown dwarf regime.
+
+The three brightest CQVs in Table are DG~CVn ($T$=9.3), TIC~405754448
+($T$=9.6), and TIC~167664935 ($T$=10.3).
+
 \paragraph{Quasiperiodicity}
@@
 \citet{2017AJ....153..152S}.  While the dips can appear persistent
-over timescales of even up to 100 cycles, our view is that all the CQV
-dips seem to be transient over timescales of more than 1000 cycles
+over timescales of even up to 100 cycles, all the CQV dips seem to be
+transient over timescales of more than 1000 cycles
 (Figure~\ref{fig:evoln}).
+The distinction is not therefore particularly meaningful.
 
@@
 able to explore all phase angles with equal weight.  LP 12-502, and
-many other CQVs, have preferred phases.  For LP 12-502 for instance,
+many other CQVs, seem to have preferred phases.  For LP 12-502,
 all of the dips happen over a fixed phase duration of two thirds of
-the period.  Phases between $\{0.45,0.8\}$ are ``out of limits'' for
+the period.  Phases over the other third are ``out of limits'' for
 any dipping material.  We interpret this as evidence
 either that {\it a)} some aspect the stellar magnetic field is
-strongly asymmetric, and can generate and hold stellar prominences at
+strongly asymmetric, and can generate and hold extrinsic material at
 corotation, but only over two thirds of the great circle,
@@
 disintegrating planetesimal swarm -- that is distributed over an arc
-of about 240$^\circ$.
+of the same angular extent (240$^\circ$).
 
@@
 S.~R. and R.~J. vetted the results from the Fourier search.
-L.A.H.~contributed to project design.
+L.A.H.~advised on project scope and experiment design.
 All authors assisted in manuscript revision.

### 2023-06-29 paper/ms.tex
update ms

@@
 
-\newcommand{\ntwoyear}{21} % TODO: update
+\newcommand{\ntwoyear}{27} % TODO: update
 \newcommand{\ntwoyearturnedoff}{5} % TODO: update
@@
   TESS data collected between July~2018 and Sep~2022, and analyze
-  their variability.  Our analysis of \nstarssearched\ K- and
-  M-dwarfs with $T$$<$16 and $d$$<$150\,pc yielded \ngoods\
-  gold-standard CQVs.  Most of these discoveries are new, and they
-  include the brightest and closest examples of this class of object
-  known ($T$$\approx$11; $d$$\approx$20\,pc), as well as the most
-  massive ($\approx$0.65\,M$_\odot$).  A few objects are outliers
-  among outliers; LP 12-502 for instance shows a ``dip complex'' with
-  a period and total duration that are fixed over more than 1000
-  cycles, but which in detail shows anywhere from four to eight
-  local minima per cycle.  LP-502 also demonstrated drastic shape
-  changes over less than one cycle, and at times displayed distinct
-  superposed periods simultaneously.  Broadly speaking, we find that
-  none of the CQVs maintain a fixed light curve shape over timescales
-  of more than a few hundred cycles -- they are all {\it
-  quasi}periodic.  We revisit the arguments for why transient
-  corotating dust clumps are the most likely explanation, though there
-  are other possibilities.  In the future, we expect that our sample
-  will help facilitate modeling and observational efforts aimed at
-  understanding these objects, and connecting them to the broader
-  contexts of star, disk, and exoplanet evolution.
+  their variability.  Our analysis of \nstarssearched\ K- and M-dwarfs
+  with $T$$<$16 and $d$$<$150\,pc yielded \ngoods\ gold-standard CQVs.
+  Most of these discoveries are new, and they include the brightest
+  and closest examples of this class of object known ($T$$\approx$9.5;
+  $d$$\approx$20\,pc), as well as the most massive
+  ($\approx$0.65\,M$_\odot$).  A few objects are outliers among
+  outliers; LP 12-502 for instance shows a ``dip complex'' with a
+  period and total duration that are fixed over more than 1000 cycles,
+  but which in detail shows anywhere from four to eight local minima
+  per cycle.  LP-502 at times demonstrated drastic shape changes over
+  less than one cycle, and also displayed distinct superposed periods
+  simultaneously.  Broadly speaking, we find that none of the CQVs
+  maintain a fixed light curve shape over timescales of more than a
+  few hundred cycles, and we revisit the arguments for why transient
+  corotating dust clumps are the most likely explanation.  In the
+  future, we expect that our sample will facilitate modeling and
+  observational efforts aimed at understanding these objects, and
+  connecting them to the broader contexts of star, disk, and exoplanet
+  evolution.  For instance, based on the rate of dip evolution, we
+  estimate that the incident dust flux corresponds to of order an
+  asteroid belt's worth of mass accreting onto these stars over $10^8$
+  years.
 \end{abstract}
@@
 
-Figure~\ref{fig:evoln} shows ``before'' and ``after'' views
-of \ntwoyear\ CQVs for which observations were available at least two years
-apart.
-Of the \ntwoyear\ CQVs for which such a baseline was available,
-\ntwoyearturnedoff\ showed obvious signs of the phenomenon in one sector,
+Figure~\ref{fig:evoln} shows ``before'' and ``after'' views of 27 CQVs
+for which TESS 120-second cadence observations were available at least
+two years apart.
+Such a baseline was available for 32 of the \ngoods\ CQVs in our
+catalog; for plotted purposes we show the brightest 27.
+Of these 27 CQVs,
+a few show clear signs of the phenomenon in one sector,
 and marginal or non-existence signs in the other.
+While there is some subjectivity in this assessment, to our eye
+cases for which at least one sector would be flagged as ``ambiguous'' include
+TIC~368129164 (S23 might be labelled an EB),
+TIC~193831684 (which has been erroneously labelled an EB CITE Albrecht paper),
+TIC~177309964 (S38 would be simply a rotating star),
+TIC~404144841 (S38 looks like a rotating star),
+TIC~201898222 (S3 looks like a rotating star),
+TIC~144486786 (S32 might be flagged as a possible RS CVn),
+TIC~38820496 (S28 might be a possible RS CVn).
+One could easily also imagine in cases like TIC~206544316 that if
+observed at lower signal to noise, the drastic shape evolution would
+not be appreciated.
 We emphasize that the periods themselves were all stable to $<$0.1\%.

### 2023-06-29 drivers/estimate_mdot.py
add mdot estimate

@@ -1,0 +1,28 @@
+from astropy import units as u, constants as c
+import numpy as np
+
+# imagine a state-switch represents a mass loss event.
+# ~3 seen over 6 months in LP 12-502.
+dN_dt = 3 / (0.5*u.year)
+
+# Sanderson+2023
+M = 1e12 * u.kg
+
+# Pitjeva2018, found via wikipedia(!)
+# 3% of the moon's mass.
+# For comparison, the AU Mic debris disk, spread over 200AU, is thoguht to
+# contain at least a lunar mass worth of material.
+# https://ui.adsabs.harvard.edu/abs/2005ApJ...634.1372C
+M_asteroidbelt = 2.4e21 * u.kg
+
+Mdot = M * dN_dt
+
+print(f'Mdot {Mdot.to(u.Msun/u.yr):.1e}')
+print(f'Mdot {Mdot.to(u.Mearth/u.yr):.1e}')
+
+timescale = 1e8 * u.yr
+
+Mcum = Mdot * timescale
+
+print(f'Mcum over 1e8 yr: {Mcum.to(u.Mearth):.1e}')
+print(f'Mcum over 1e8 yr divided by asteroid belt mass: {Mcum/M_asteroidbelt:.2f}')

### 2023-06-29 paper/ms.tex
update ms

@@
 circumstances, eclipses by stars and planets
-\citep{2010exop.book...55W}.
+\citep{2010exop.book...55W}.  More exotic forms of optical variability
+relevant to this work include transiting exocomets (e.g. $\beta$~Pic;
+\citealt{2019A&A...625L..13Z}) and disintegrating rocky bodies around
+both M-dwarfs (e.g. K2-22; \citealt{2014ApJ...784...40R}) and white
+dwarfs (e.g. WD~1145; \citealt{2015Natur.526..546V}).
 
@@
 variables (CQVs).  These objects are identified phenomenologically
-using their optical light curves, which show quasiperiodic troughs
+using their optical light curves, which show nearly periodic troughs
 that can be either sharp or broad, often superposed on smooth
@@
 \citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z}.
-Some CQVs show up to eight local minima (dips) per cycle; sharp peaks
-are common, but .  Most CQVs are pre-main-sequence M-dwarfs without
-near-infrared excesses, with ages of $\approx$5-150 million years
-(Myr), and rotation periods of at most two days; they are observed to
-be $\approx$1-3\% of M-dwarfs younger than 100 Myr
-\citep{2016AJ....152..114R,2022AJ....163..144G}.  The dips can be
-chromatic, with a reddening law plausibly consistent with dust
+Some CQVs show up to eight local minima (dips) per cycle.  Most CQVs
+are pre-main-sequence M-dwarfs without near-infrared excesses, with
+ages of $\approx$5-150 million years (Myr), and rotation periods of at
+most two days; they are observed to be $\approx$1-3\% of M-dwarfs
+younger than 100 Myr \citep{2016AJ....152..114R,2022AJ....163..144G}.
+The dips can be chromatic, with a reddening law plausibly consistent
+with dust
 \citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
@@
 prominence scenario lacks a mechanism for generating broadband
-opacity, and the screen scenario seems inconsistent with the degree of
-observed periodicity, and the lack of infrared excess.  However,
-unambiguous evidence, for instance a spectroscopic detection of
-silicates during a CQV ``dip'', has yet to be presented to confirm
-which scenario is correct.
+opacity, and the screen scenario is inconsistent with the degree of
+observed periodicity, the lack of infrared excess, and the observed
+lifetime of the effect, which is an order of magnitude longer than the
+$\approx$$10^7$ years timescale typically quoted for the primordial
+disk to disperse (CITE).  However, unambiguous evidence, for instance
+a spectroscopic detection of silicates during a ``dip'', has yet to be
+acquired.
 
@@
 
-Previous methods for finding CQVs have included visually
-examining stars known to be in young clusters
+Previous methods for finding CQVs have included visually examining
+stars known to be in young clusters
 \citep{2016AJ....152..114R,2017AJ....153..152S}, and automatically
 flagging rapid rotators with a large number of strong Fourier
-harmonics \citep{2019ApJ...876..127Z}.  The latter approach still requires
-visual vetting, since ``stars with many Fourier harmonics''
-is a designation that
-includes objects such as eclipsing binaries or multiple stars
-blended into a single photometric aperture.  In this work, we
-implemented a new search approach based on counting the number of
-sharp local minima in phase-folded light curves, while also using the
-previously tested Fourier approach.  We applied these two search
-techniques independently.
+harmonics \citep{2019ApJ...876..127Z}.  The latter approach still
+requires visual vetting, since ``stars with many Fourier harmonics''
+is a designation that includes objects such as eclipsing binaries or
+multiple stars blended into a single photometric aperture.  In this
+work, we implemented a new search approach based on counting the
+number of sharp local minima in phase-folded light curves, while also
+using the previously tested Fourier approach.  We applied these two
+search techniques independently.
 
@@
 Appendix~\ref{app:vetting}.
+We labelled a star as a ``good'' CQV if at least one TESS sector
+showed what we viewed as the unambiguous signatures of the class (short
+period; at least three dips or else otherwise oddly-shaped dips;
+relative stability over a timescale of 30\,days).
+We also noted stars that we thought could be CQVs, but that were more
+ambiguous with a ``maybe'' flag.
 
@@
 kinematic associations between the CQVs and known clusters in the
-solar neighborhood.  For most stars in our sample, we did
-this using BANYAN\,$\Sigma$
+solar neighborhood.  For most stars in our sample, we did this using
+BANYAN\,$\Sigma$
 \citep{2018ApJ...856...23G}.\footnote{\url{https://github.com/jgagneastro/banyan_sigma},

### 2023-07-01 paper/ms.tex
update ms

@@
   pre-main-sequence stars with nearly periodic optical modulation.
-  The modulation is likely induced by dust clumps in orbit at the
+  The modulation is likely induced by dust or gas clumps in orbit at the
   Keplerian corotation radius.  Here, we report new CQVs discovered in
-  TESS data collected between July~2018 and Sep~2022, and analyze
-  their variability.  Our analysis of \nstarssearched\ K- and M-dwarfs
+  TESS data collected between July~2018 and Sep~2022.
+  Our search of \nstarssearched\ K- and M-dwarfs
   with $T$$<$16 and $d$$<$150\,pc yielded \ngoods\ gold-standard CQVs.
@@
   outliers; LP 12-502 for instance shows a ``dip complex'' with a
-  period and total duration that are fixed over more than 1000 cycles,
+  period and total duration that are fixed over more than 1{,}000 cycles,
   but which in detail shows anywhere from four to eight local minima
@@
   few hundred cycles, and we revisit the arguments for why transient
-  corotating dust clumps are the most likely explanation.  In the
+  corotating material is the most likely explanation.  In the
   future, we expect that our sample will facilitate modeling and
@@
   connecting them to the broader contexts of star, disk, and exoplanet
-  evolution.  For instance, based on the rate of dip evolution, we
-  estimate that the incident dust flux corresponds to of order an
-  asteroid belt's worth of mass accreting onto these stars over $10^8$
-  years.
+  evolution.
+%  For instance, based on the rate of dip evolution, we
+%  estimate that the incident dust flux corresponds to of order an
+%  asteroid belt's worth of mass accreting onto these stars over $10^8$
+%  years.
 \end{abstract}
@@
 \label{sec:intro}
-
-% NOTE: could write this more from a stellar evolution angle.
-% M-dwarfs contract.  They spin up.  Some reach rapid rotation rates,
-% and exhibit strong magnetic fields.
 
@@
 lifetime of the effect, which is an order of magnitude longer than the
-$\approx$$10^7$ years timescale typically quoted for the primordial
-disk to disperse (CITE).  However, unambiguous evidence, for instance
-a spectroscopic detection of silicates during a ``dip'', has yet to be
+$\approx$$10^7$ year timescale typically quoted for the primordial
+disk to disperse.  However, unambiguous evidence, for instance a
+spectroscopic detection of silicates during a ``dip'', has yet to be
 acquired.
@@
 
-A point on nomenclature.  CQVs have been called ``transient and
+A word on nomenclature.  CQVs have been called ``transient and
 persistent flux dips'', ``scallop shells'', ``batwings'',
@@
 reflects how, when observed over timescales of more than tens of
-cycles, CQVs are never exactly periodic.  Their shapes evolve, usually
-with some coherence timescale, similar to variability induced by
-surface inhomogeneities such as starspots.  While the three-type
-classification scheme proposed by \citet{2017AJ....153..152S} may
-indeed provide some helpful visual distinctions amongst CQV
-sub-classes, it seems likely that they are all explained by a single
-underlying phenomenon, and so we opt to refer to them by a single
-empirically descriptive name.
+cycles, CQVs are almost, but not exactly periodic.  Their shape
+evolution implies that they are irregularly periodic, or for short,
+quasiperiodic.  While the three-type classification scheme proposed by
+\citet{2017AJ....153..152S} may indeed provide some helpful visual
+distinctions amongst CQV sub-classes, it seems likely that they are
+all explained by a single underlying phenomenon, and so we opt to
+refer to them by a single empirically descriptive name.
 
@@
 		dust clump scenario seems most plausible, given
-		the stability of the dips, the lack of observed infrared
-		excesses, and the challenge of producing broadband opacity variations
-		with only ionized hydrogen in the prominence scenario.
+    the stability of the dips, their chromaticity, the lack of
+    observed infrared excesses, and the challenge of producing
+    broadband opacity variations with only ionized hydrogen in the
+    prominence scenario.
 	}
@@
 For the SED fitting, we used \texttt{astroARIADNE}
-\citep{2022MNRAS.513.2719V}.  Specifically, we adopted the ``BT-Settl''
-stellar atmosphere models \citep{Allard2012} assuming the
+\citep{2022MNRAS.513.2719V}.  We adopted the ``BT-Settl'' stellar
+atmosphere models \citep{Allard2012} assuming the
 \citet{2009ARA&A..47..481A} solar abundances, and the
-\citet{2006MNRAS.368.1087B} water line lists.
-The broadband magnitudes we considered included $GG_{\rm BP}G_{\rm
-RP}$ from Gaia DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, $riz$
-from Pan-STARRS1, SDSS $riz$, and the WISE 1-2 passbands.  We
-specifically omitted UV flux measurements to avoid biasing our fit
-with any possible chromospheric UV excess.
-\texttt{astroARIADNE} compares the measured broadband flux measurements
-against pre-computed model grids, and by default fits for six
-parameters:
+\citet{2006MNRAS.368.1087B} water line lists.  The broadband
+magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
+DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
+WISE 1-2 passbands.  We specifically omitted UV flux measurements to
+avoid biasing our fit with any possible chromospheric UV excess.
+\texttt{astroARIADNE} compares the measured broadband flux
+measurements against pre-computed model grids, and by default fits for
+six parameters:
 $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm Fe/H}], d \}$.
-The distance  prior is drawn from \citet{2021AJ....161..147B}.
-The surface gravity and metallicity are generally unconstrained.
-And finally, given our particular use-case, 
-we assumed the following priors for the temperature, stellar size, and
-extinction:
+The distance  prior is drawn from \citet{2021AJ....161..147B}.  The
+surface gravity and metallicity are generally unconstrained.  And
+finally, given our particular use-case, we assumed the following
+priors for the temperature, stellar size, and extinction:
 \begin{align}
@@
 distribution with mean $\mu$, standard deviation $\sigma$, and lower
-and upper bounds $a$ and $b$.
-Using \texttt{Dynesty} \citep{2020MNRAS.493.3132S},
-we statically sampled the posterior probability assuming the default
-Gaussian likelihood, and set a stopping threshold of ${\rm d}\log
-\mathcal{Z} < 0.01$, where $\mathcal{Z}$ denotes the evidence.
+and upper bounds $a$ and $b$.  Using \texttt{Dynesty}
+\citep{2020MNRAS.493.3132S}, we statically sampled the posterior
+probability assuming the default Gaussian likelihood, and set a
+stopping threshold of ${\rm d}\log \mathcal{Z} < 0.01$, where
+$\mathcal{Z}$ denotes the evidence.
 
@@
 \citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2020ApJ...891...29S}.
-Plausible explanations for anomalous M-dwarf colors and sizes relative to
-model predictions include star starspot coverage
+Plausible explanations for anomalous M-dwarf colors and sizes relative
+to model predictions include star starspot coverage
 \citep[e.g.][]{2017ApJ...836..200G}, and potentially incomplete line
@@
 \citet{2014MNRAS.444.2525C} performed an empirical correction to the
-temperature--opacity relation drawn from the BT-Settl model atmospheres,
-in order to match observed masses and radii of younq eclipsing binaries.
-This is sufficient for our purpose of estimating accurate stellar masses.
-Given our observed $\{ \tilde{T}_{\rm eff}, \tilde{M}_\star, \tilde{t} \}$,
-and approximating their uncertainties as Gaussian
-$\sigma_{\tilde{T}_{\rm eff}}$, $\sigma_{\tilde{M}_\star}$ and
-$\sigma_{\tilde{t}}$, we evaluate a distance $d$ between our observations
-and any model PARSEC grid-point $\{ T_{\rm eff}, M_\star, t \}$ as
+temperature--opacity relation drawn from the BT-Settl model
+atmospheres, in order to match observed masses and radii of younq
+eclipsing binaries.  This is sufficient for our purpose of estimating
+accurate stellar masses.  Given our observed $\{ \tilde{T}_{\rm eff},
+\tilde{M}_\star, \tilde{t} \}$, and approximating their uncertainties
+as Gaussian $\sigma_{\tilde{T}_{\rm eff}}$, $\sigma_{\tilde{M}_\star}$
+and $\sigma_{\tilde{t}}$, we evaluate a distance $d$ between our
+observations and any model PARSEC grid-point $\{ T_{\rm eff}, M_\star,
+t \}$ as
 \begin{equation}
@@
       Phased TESS light curves over one month are shown for \ngoods\
-      CQVs.
-      Gray are raw 2-minute data;
-			black bins to 300 points per cycle.  Each panel is labelled by
-      the TIC identifier, the TESS sector number, and the period in hours.
-      Objects are ordered such that sources with the most TESS data available are
-       on top (see Section~\ref{sec:catalog}).
+      CQVs.  Gray are raw 2-minute data; black bins to 300 points per
+      cycle.  Each panel is labelled by the TIC identifier, the TESS
+      sector number, and the period in hours.  Objects are ordered
+      such that sources with the most TESS data available are on top
+      (see Section~\ref{sec:catalog}).
 		}
-		\label{fig:singlemosaic}
+		\label{fig:cqvs}
 	\end{center}
@@
 search, along important physical and observational properties.
-\ngoods\ objects demonstrate what we view as unambiguous
-characteristics of the CQV phenomenon in at least one TESS sector, and
-we refer to these as the ``gold sample''.  The remaining \nmaybes\ CQV
-candidates were ambiguous (in our view), and their variability might
+\ngoods\ objects demonstrated what we viewed as unambiguous
+characteristics of the CQV phenomenon in at least one TESS sector;
+we refer to these as the ``gold sample''.  We found the remaining \nmaybes\ CQV
+candidates to be ambiguous; their variability might
 be caused by say, multiple starspot groups.  Additional data from TESS
-or other instruments can help resolve their classification; in
-Section~\ref{subsec:irexcess} below for instance we discuss a few
-cases in this ambiguous sample that after additional analysis were
-clarified as dippers.  We also emphasize that our initial
-classifications were based on whether {\it any} TESS sectors showed
-evidence for the CQV phenomenon.
-
-The mosaic in Figure~\ref{fig:singlemosaic} shows phased light curves
+or other instruments could help resolve their classification.  In the
+following discussion, we will primarily restrict our discussion to the 
+gold sample.
+
+The mosaic in Figure~\ref{fig:cqvs} shows phased light curves
 for the \ngoods\ bonafide CQVs.  The objects are sorted first in order
@@
 demonstrated the CQV phenomenon, and secondarily by descending
-brightness.  The objects at the top therefore have the most 120-second
+brightness.  The objects at the top generally have the most 120-second
 cadence data.  The top five objects by this metric are TIC~300651846
@@
 
-In terms of the light curve shapes, Figure~\ref{fig:singlemosaic}
+In terms of the light curve shapes, Figure~\ref{fig:cqvs}
 shows a broad range of variability, with anywhere from two to eight
@@
 A small number of objects at first glance seem reminiscent of
-eclipsing binaries, such as TIC~193831684 or TIC~5714469.  In the
-few such cases, we believe that that are unlikely to be eclipsing
-binaries due to additional coherent variations in the light curves
-that are distinct from any binary phenomenology of which we are aware.
+eclipsing binaries, such as TIC~193831684 or TIC~5714469.  In these
+few cases, we believe that that are unlikely to be eclipsing binaries
+due to additional coherent variations in the light curves that are
+distinct from any binary phenomenology of which we are aware.
 
@@
 Of our \ncpvsfound\ confirmed and candidate CQVs, \nnotfieldbanyan\
-were confidently associated with a nearby moving group or open cluster
-using BANYAN\,$\Sigma$.  The relevant groups are listed in
+were associated with a nearby moving group or open cluster using
+BANYAN\,$\Sigma$.  The relevant groups are listed in
 Table~\ref{tab:thetable}; their ages span $\approx$5-150\,Myr.  The
 most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  The yield
-in Sco-Cen (LCC / UCL / USco) is not surprising, since Sco-Cen
-contains the majority of pre-main-sequence stars in the solar
-neighborhood.  The absence of CQVs in IC\,2602 and IC\,2391 can be
-understand by those clusters being beyond 100\,pc, where the
-completeness of the TESS 120-second cadence data is below 10\%; based
-on the abundance of CQVs in the 40\,Myr Tuc-Hor and Columba, the
-similarly-aged IC\,2602 and IC\,2391 clusters should show a large
-number of CQVs in the TESS full frame image data.
+in Sco-Cen is not particularly surprising, since Sco-Cen contains the
+majority of pre-main-sequence stars in the solar neighborhood.
+However it is certainly likely given the $\lesssim$$10\%$ completeness
+of TESS beyond 100\,pc that far more CQVs remains to be discovered in
+Sco-Cen.  IC\,2602 and IC\,2391, which are located slightly beyond
+100\,pc, are an example of this completeness effect: no CQVs appear in
+those clusters from our search.
 
@@
 ($t\approx 86\pm16$\,Myr;
-\citealt{2021A&A...645A..84M,2022arXiv221109822B}).  For the other two
-(TIC~58084670 and TIC~141146667), we are convinced of both their CQV
-status and their youth, but we were not able to confidently associate
-either star with any young groups.  Both objects were noted as being in the
-``diffuse'' Class~III YSO population near the Sun by \citet{2021ApJ...917...23K}.
-That diffuse population may contain kinematic structures that have yet
-to be unravelled.  However, the absence of obvious young, co-moving
-stars within $\Delta r$=$40$\,pc and $\Delta v$=$3$\,km\,s$^{-1}$ of
-our two CQVs suggest that they may have ``run away'' from their birth
-locations.
-
-The CQV phenomenon persists at least up to 150\,Myr.  Our catalog
-includes three $\approx$150\,Myr old AB Dor members (TIC~288344202,
-TIC~332517282, and TIC~368129164), a $\approx$112\,Myr old Pleiades
-member (TIC~440725886; \citealt{CantatGaudin_2020}), and a
-similarly-aged Psc-Eri member (TIC~38539720;
+\citealt{2021A&A...645A..84M,2023AJ....166...14B}).  For the other two
+(TIC~58084670 and TIC~141146667), we were not able to confidently
+associate either star with any young groups.  However both do seem to
+clearly show the CQV signal over multiple TESS sectors, and both are
+photometrically elevated relative to the main sequence.  For instance,
+both were noted as being in the ``diffuse'' Class~III YSO population
+near the Sun by \citet{2021ApJ...917...23K}.
+
+Our catalog confirms that the CQV phenomenon persists for at least
+$\approx$150\,Myr.  Our catalog includes three $\approx$150\,Myr CQVs
+in AB~Dor \citep{2015MNRAS.454..593B}: TIC~288344202, TIC~332517282,
+and TIC~368129164.  There is also a $\approx$112\,Myr old Pleiades CQV
+(TIC~440725886; \citealt{2015ApJ...813..108D,CantatGaudin_2020}), and
+a similarly-aged Psc-Eri member (TIC~38539720;
 \citealt{2020A&A...639A..64R}).  To our best knowledge, TIC~332517282
@@
 catalog did not show infrared excesseses in the WISE1-4 bands.
-Visually inspecting the SEDs, we labelled two objects as having
-``good'' infrared excesses (both W3 and W4), and three as ``possible''
-infrared excess.
-
-The two ``good'' IR excesses were TIC~193136669 (TWA~34) and
-TIC~57830249 (TWA~33).  Both are in the TW Hydrae association
-($\approx$10\,Myr), and have ``long'' periods of 38\,hr and 44\,hr
-respectively.  In our initial labelling, we labelled both as ``maybe''
-CQVs because the dips in their light curves did not show the rigid
-periodicity typical of CQVs;  their periods were also relatively
-long.  After labelling them, we learned that TIC 193136669 has a cold
+Visually inspecting the SEDs of our entire \ncpvsfound\ star sample,
+we labelled two objects as having ``good'' infrared excesses (both W3
+and W4), and three as ``possible'' infrared excess.
+
+The two ``good'' IR excesses belonged to ``candidate'' CQVs
+TIC~193136669 (TWA~34) and TIC~57830249 (TWA~33).  Both are in the TW
+Hydrae association ($\approx$10\,Myr), and have relatively long
+periods of 38\,hr and 44\,hr respectively.  In our initial labelling,
+we labelled both as ``maybe'' CQVs because the dips in their light
+curves did not show the rigid periodicity typical of CQVs;  their
+periods were also relatively long.  After labelling them, inspection
+of further sectors clarified that both sources are dippers (see plots
+in Appendix~\ref{app:vetting}).  In addition, TIC 193136669 has a cold
 molecular disk based on observed 1.3\,mm continuum emission and
 resolved Keplerian $^{12}{\rm CO}(2-1)$ emission
-\citep{2015A&A...582L...5R}.  It has also been labelled a dipper by
+\citep{2015A&A...582L...5R}.  It was also labelled a dipper by
 \citet{2022ApJS..263...14C}; we agree with their designation, but
@@
 \citep{2015A&A...582L...5R}, suggestive of cold dust grains being
-present.  It therefore probably also a dipper that snuck its way into
-our ``maybe'' pile.
+present.  It therefore also a dipper that snuck its way into our
+``maybe'' pile.
 
@@
 definitive evidence for a large disk.  It is however
-``multi-periodic''---in addition to the 7.17\,hr CPV signal, there is
-a superposed 8.39\,hr sinusoidal signal, probably from an unresolved
-binary neighbor.
+``multi-periodic''---in addition to the 7.17\,hr CPV signal, this
+source shows a superposed 8.39\,hr sinusoidal signal, probably from an
+unresolved neighboring star.
 
@@
 it is clear that the loss of an infrared excess is associated with
-strong changes in a star's optical variability.  It is not
-unreasonable to imagine connections between CQVs and dippers: both
-classes of object can show transient flux dips that are relatively
-narrow in duration.  Such dips are probably caused by clumps of dust.
-However the CQV dips are typically {\it i}) more periodic and {\it
-ii}) less deep than those of dippers, and {\it iii}) they display far
-less transience over timescales of a few to tens of cycles.  At a
-population level, the CQV stars are also older.  A shared mystery
-between the CQVs and dippers, in our own estimation however, is the
-exact mechanism that produces the {\it narrowness} of the dust clumps
-in certain cases.  It is not unreasonable to imagine a similar
-mechanism operating for both types of object, tied perhaps to a shared
-magnetic topology, or perhaps to a preference for dust to inspiral to
-the star in clumps from tidally disrupted infalling bodies.
+strong changes in a star's optical variability.  It is reasonable to
+imagine connections between CQVs and dippers: both classes of object
+can show transient flux dips that are relatively narrow in duration.
+Such dips are probably caused by clumps of dust.  However the CQV dips
+are typically {\it i)} more periodic and {\it ii)} less deep than
+those of dippers, and {\it iii}) they display far less transience over
+timescales of a few to tens of cycles.  This is probably because CQV
+stars have demonstrably less dust than dipper stars.  At a population
+level, the CQV stars are also older.  A common mystery between the
+CQVs and dippers, in our own estimation, is how exactly the {\it
+narrowness} of the dust clumps is produced.  It is not unreasonable to
+imagine a similar mechanism operating for both types of object, tied
+perhaps to a shared magnetic topology, or perhaps to a preference for
+dust to inspiral to the star in clumped structures.
 
@@
 for which TESS 120-second cadence observations were available at least
-two years apart.
-Such a baseline was available for 32 of the \ngoods\ CQVs in our
-catalog; for plotted purposes we show the brightest 27.
-Of these 27 CQVs,
-a few show clear signs of the phenomenon in one sector,
-and marginal or non-existence signs in the other.
-While there is some subjectivity in this assessment, to our eye
-cases for which at least one sector would be flagged as ``ambiguous'' include
-TIC~368129164 (S23 might be labelled an EB),
-TIC~193831684 (which has been erroneously labelled an EB CITE Albrecht paper),
-TIC~177309964 (S38 would be simply a rotating star),
-TIC~404144841 (S38 looks like a rotating star),
-TIC~201898222 (S3 looks like a rotating star),
-TIC~144486786 (S32 might be flagged as a possible RS CVn),
-TIC~38820496 (S28 might be a possible RS CVn).
+two years apart.  Such a baseline was available for 32 of the
+confirmed \ngoods\ CQVs in our catalog; for plotting purposes we show
+the brightest 27.
+Of these 27 CQVs, a few show clear signs of the phenomenon in one
+sector, and marginal or non-existence signs in the other.
+While there is some subjectivity in this assessment, to our eyes cases
+for which at least one sector would be flagged as ``ambiguous''
+include
+TIC~368129164 (Sector 23 might be labelled an EB),
+TIC~177309964 (Sector 38 would be simply a rotating star),
+TIC~404144841 (Sector 38 looks like a rotating star),
+TIC~201898222 (Sector 3 looks like a rotating star),
+TIC~144486786 (Sector 32 might be an RS CVn),
+and
+TIC~38820496 (Sector 28 might be an RS CVn).
+TIC~193831684, assessed on a single-sector basis, would probably be
+labelled an eclipsing binary---in fact, \citet{2021ApJ...912..123J}
+implicitly have already given this source such a label!  Based on the
+the shape evolution between Sectors 13 and 39 however, it is a CQV.
 One could easily also imagine in cases like TIC~206544316 that if
 observed at lower signal to noise, the drastic shape evolution would
-not be appreciated.
-We emphasize that the periods themselves were all stable to $<$0.1\%.
-Broadly speaking, this shape evolution
-suggests that CQVs have a duty cycle of $\approx$75\%.
+not be appreciated.  We emphasize that the periods themselves were all
+stable to $<$0.1\%.  Broadly speaking, this shape evolution suggests
+that CQVs have an ``on/off'' duty cycle of $\approx$75\%.  This type
+of correction is likely worth including in population-level estimates
+of how intrinsically common CQVs are in the low-mass stellar
+population \citep[e.g.][]{2022AJ....163..144G}.
 
@@
 		{\bf CQVs keep their periods but change their shapes.}
-      32 of our \ngoods\ CQVs from Figure~\ref{fig:singlemosaic} 
-      had 120-second cadence TESS data available for
-      a baseline of at least two years; the 27 brightest are shown here.
-      Each panel shows one sector of TESS data, and is phased to its deepest minimum in flux.
-      Each panel's title shows the TIC identifier and approximate period in hours.
-      Text insets show the TESS sector numbers, which generally span two years, or at least
-      1{,}000 cycles.
-      The vertical scale is fixed across sectors to clarify shape changes.
+      32 of our \ngoods\ CQVs from Figure~\ref{fig:cqvs} had
+      120-second cadence TESS data available for a baseline of at
+      least two years; the 27 brightest are shown here.  Each panel
+      shows one sector of TESS data, and is phased to its deepest
+      minimum in flux.  Each panel's title shows the TIC identifier
+      and approximate period in hours.  Text insets show the TESS
+      sector numbers, which generally span two years, or at least
+      1{,}000 cycles.  The vertical scale is fixed across sectors to
+      clarify shape changes.
 		}
@@
 		\caption{
-			{\bf LP 12-502 (TIC~402980664) light curve}, where each time chunk represents one TESS orbit.
-			Data were acquired in Sectors 18-19, 25-26, 53, and 57-58.
-			Flares are drawn in gray.
-			The red vertical lines highlight apparently instantaneous state changes in
-			the shape of the dip pattern.
-			The light curve is binned to 15-minute intervals so that
-			there are 96 points per day.  Data gaps with more than one missing 15-minute
-			cadence appear in white.
+      {\bf LP 12-502 (TIC~402980664) light curve}, where each time
+      chunk represents one TESS orbit.  Data were acquired in Sectors
+      18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  The red
+      vertical lines highlight apparently instantaneous state changes
+      in the shape of the dip pattern.  The light curve is binned to
+      15-minute intervals so that there are 96 points per day.  Data
+      gaps with more than one missing 15-minute cadence appear in
+      white.
 		}
@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{TIC_402980664_P18.5611_2min_phase_timegroups_mosaic_ymin-4.8_ymax3.pdf}
+		\includegraphics[width=\textwidth]{TIC_402980664_P18.5611_2min_phase_timegroups_mosaic_ymin-4.8_ymax3.pdf}
 		\vspace{-0.45cm}
 		\caption{
-			Evolution of LP 12-502 ($P$=18.6\,h) at fixed period and
-			epoch over three years. 
-			Each panel shows one (stacked) TESS orbit; small text denotes relative cycle number.
-			There are 200 binned black points per cycle.
-			The TESS pointing law dictates time gaps; larger gaps tend to
-			yield larger shape changes.
-			The dips usually evolve over tens to hundreds of cycles.
-			However cycles 1233-1264 show a dip that ``switched'' from a depth
-			and duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than
-			one cycle (see Figure~\ref{fig:lplc}).
+      {\bf Evolution of LP 12-502} ($P$=18.6\,h) at fixed period and
+      epoch over three years.  Each panel shows one (stacked) TESS
+      orbit; small text denotes relative cycle number.  There are 200
+      binned black points per cycle.  The TESS pointing law dictates
+      time gaps; larger gaps tend to yield larger shape changes.  The
+      dips usually evolve over tens to hundreds of cycles.  However
+      cycles 1233-1264 show a dip that ``switched'' from a depth and
+      duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than one
+      cycle (cf.~Figure~\ref{fig:lplc}).
 		}
@@
 \subsubsection{LP 12-502 observations}
-While many CQVs had multiple sectors of adjacent or nearly-adjacent data
-LP 12-502 (TIC 402980664; $d$=21\,pc, $J$=9.4,
-$T$=11.1) stood out as an outlier among the CQV class.
-Figure~\ref{fig:lplc} shows all available data from Sectors
-18, 19, 25, 26, 53, 58, and 59; the star was observed at 120-second
-cadence whenever it was observable by TESS.
-Figure~\ref{fig:lp} shows the same data, grouped into successive
-TESS orbits spanning half a lunar month each.
-Measuring the PDM peak period over each sector independently yielded
-an average $\langle P \rangle = 18.5560$\,hr, with a difference
-between the maximum and minimum sector-level period of about one minute.
-Based on this range, the period is therefore stable to at least one
-minute ($\pm$0.017\,hr) over the three year baseline.
-However, in detail, a period shift of $\pm$1\,minute yields major
-phase drifts over the 3 year baseline; that time interval
-corresponds to roughly 1/1000$^{\rm th}$ of a period; we have
-observed 1500 cycles.
-The achievable period precision, $\sigma_{\rm P}$, can be estimated as
+While many CQVs had multiple sectors of adjacent or nearly-adjacent
+data, LP 12-502 (TIC 402980664; $d$=21\,pc, $J$=9.4, $T$=11.1) stood
+out due to the quality and content of its data.  Figure~\ref{fig:lplc}
+shows all available data from Sectors 18, 19, 25, 26, 53, 58, and 59,
+split into successive orbits; the star was observed at 120-second
+cadence whenever it was observable by TESS.  We binned the light curve
+to 15-minute intervals for visual clarity, and required at least one
+(120-second cadence) flux measurement per bin.  Points more than
+2.5$\sigma$ above the median are drawn in gray, also for visual
+clarity.  Missing data are not drawn.  Figure~\ref{fig:lp} then shows
+the same data, but stacked into successive TESS orbits spanning half a
+lunar month each.
+
+The average period, determined by measuring the PDM peak period over
+each sector independently, was $\langle P \rangle = 18.5560$\,hr.  The
+range between the maximum and minimum sector-specifics periods was
+measured to be about one minute.  Based on this range, the star's
+period is stable to at least one minute ($\pm$0.017\,hr) over the
+three year baseline.  However, in detail, a period shift of
+$\pm$1\,minute would yield major phase drifts over the baseline; that
+time interval corresponds to roughly 1/1000$^{\rm th}$ of a period,
+and we have observed 1500 cycles.  The achievable period precision,
+$\sigma_{\rm P}$, can be estimated as
 \begin{equation}
@@
 \end{equation}
-for $N_{\rm baseline}$ the number of cycles in the observed baseline and
-$\sigma_{\phi}$ the phase precision with which any one feature (e.g.~a
-dip) can be tracked.
-Assuming $\sigma_{\rm phi} \approx 0.01$ yields an expected period precision
-$\sigma_{\rm P} \approx 0.45 {\rm sec} \approx 1.2\times 10^{-4}\,{\rm hr}$.
-By visually fine-tuning over a grid in period, we eventually 
-found $P=18.5611 \pm 0.0001$\,hr, which seems to track certain
-features in the LP 12-502 light curve over its entire baseline.
-
-What features are observed?  For the first 64 cycles, the star shows a
-pattern reminiscent of a (bizarre) eclipsing binary, with four obvious
-dips, that we dub dips $\{ 1, 2, 3, 4 \}$ at phases $\{ -0.28, -0.08,
-0, 0.25 \}$ respectively.  Over cycles 0 to 64, the depth of dips 1
-and 3 remain roughly fixed.  However dip 4 {\it decreases} in depth by
-about 2\%, while dip 2 {\it increases} in depth, by about the same
-amount.  During cycles 48-64, it also seems that a fifth dip may be
-emerging, in the main ``large'' dip group.
-
-There is then a 6-month (184 cycle) gap out to Cycles 248-315, which
-show two intricately structured dip complexes, plus a single (leading)
+for $N_{\rm baseline}$ the number of cycles in the observed baseline
+and $\sigma_{\phi}$ the phase precision with which any one feature
+(e.g.~a dip, or the overall shape of the sinusoidal envelope) can be
+tracked.  Assuming $\sigma_{\rm phi} \approx 0.01$ yields an expected
+period precision $\sigma_{\rm P} \approx 0.45 {\rm sec} \approx
+1.2\times 10^{-4}\,{\rm hr}$.  By visually fine-tuning over a grid in
+period, we eventually found $P=18.5611 \pm 0.0001$\,hr, which seems to
+track certain features in the LP 12-502 light curve over its entire
+baseline.
+
+What exactly is observed?  For the first 64 cycles, the star shows a
+pattern reminiscent of an eclipsing binary, with four obvious
+local minima.  We dub these dips $\{ 1, 2, 3, 4 \}$ at phases $\{ -0.28,
+-0.08, 0, 0.25 \}$, respectively.  Over cycles 0 to 64, the depth of
+dips 1 and 3 remain roughly fixed.  However dip 4 {\it decreases} in
+depth by about 2\%, while dip 2 {\it increases} in depth, by about the
+same amount (see Figure~\ref{fig:lp}).  During cycles 48-64, it also
+seems that a fifth dip may be emerging, in the main ``large'' dip
+group.
+
+There is then a 6-month (184 cycle) gap to Cycles 248-315, which
+show two intricately structured dip complexes, plus a small leading
 dip.  The single leading dip is present at roughly the same phase as
-in cycles 0-64; we believe they are the same struture.  Along a
+in cycles 0-64; they seem likely to be the same struture.  Along a
 similar line of logic, it seems plausible that the first ``dip
@@
 complex seen during cycles 0-64, though with greatly reduced depth.
-During cycles 266-310, a moving local minimum develops between the two
-complexes; this feature is best visualized on the river plots.
-
-However, the second dip complex during cycles 248-315 is perhaps the
-most intricate.  During e.g.~cycles 283-298, this single complex
-clearly shows six local minima.  The deepest dip is very sharp: it
-shows a flux exercusion of 3.5\% over about 22 minutes (0.02\,$P$),
-which is the steepest slope exhibited anywhere in this object's
-remarkable dataset.  After the sharp dip, there is a roughly
-exponential fall-off spanning about a quarter of a period, punctuated
-by coherent local minima and maxima.  The sharp leading dip only
-decreases in its sharpness during cycles 299-315, during a sudden
-state-switch at BTJD 2030.7, which happens immediately during a flare.
-(And therefore which is likely caused by the flare!) To our best
-knowledge, this type of of behavior has not yet been observed on any
-comparable object.
-
-Finally, sectors 53--58 (cycles 1233-1481) showed between four and six
-dips per cycle, at various times.  Some dips remain stable in depth
-and duration over this five month interval.  Other dips grow, like the
-one at $\phi = +0.06$ between cycles 1499 and 1481.  Other dips, such
-as the one at $\phi = +0.12$ in cycles 1233-1264, disappear entirely.
+During cycles 266-310, an additional local minimum develops between the two
+complexes; this feature is best visualized on the river plots
+(Appendix~\ref{app:lp}), and we discuss its (shorter) period below.
+
+The second dip complex during cycles 248-315 shows the most
+substructure.  During e.g.~cycles 283-298, this single complex shows
+six local minima.  The deepest dip is very sharp: it shows a flux
+exercusion of 3.5\% over about 22 minutes (0.02\,$P$), which is the
+steepest slope exhibited anywhere in this object's remarkable dataset.
+After the sharp dip, there is a roughly exponential fall-off spanning
+about a quarter of a period, punctuated by coherent local minima and
+maxima which in detail (Appendix~\ref{fig:app:lp}) have slightly
+longer periods than the sharp dip.  The sharp leading dip only
+decreases during a sudden state-switch at BTJD 2030.7 (cycles
+299-315), which happens immediately during a flare
+(Figure~\ref{fig:lplc}).  The trailing dips remain afterwards.
+
+Sectors 53--58 (cycles 1233-1481) are comparitively tame; they showed
+only four to six dips per cycle.  Some dips remain stable in depth and
+duration over this five month interval.  Other dips grow, like the one
+at $\phi = +0.06$ between cycles 1499 and 1481.  Other dips, such as
+the one at $\phi = +0.12$ in cycles 1233-1264, disappear entirely.
 The most dramatic state switch occurs during cycles 1233-1247, when a
@@
 
-\subsubsection{LP 12-502 interpretation}
-
-{\sc Dips can disappear instantaneously}---The state switches shown in
-cycles 1233-1264 and 299-315 reveal that the dips can be {\it
-independent} and {\it additive}.  They also show that although dip
-depth is generally not preserved over a state switch, {\it ingress
-time} usually is conserved.  It other words, throughout cycles
-1233-1264, there are three local minima between phases of 0 and 0.3.
-They all have identical ingress times.  The shape change during the
-transition strongly suggests that it was simply the leading dip that
-``turned off', while the trailing two dips remained fixed.  The state
-switches during cycles 299-315 and 248-264 share the same
-characteristic: it is always the {\it leading} dip of a complex that
-``switches off'', leaving the trailing dips in its wake.
-
-{\sc Dips grow more slowly}---Although there are a few instances in
-which we observe dips to ``switch off'' over less than one cycle, dip
-growth seems to happen more slowly.  For instance, the dip that grows
-between phase 0 and 0.1 between cycles 260-290 begins to become
-visible around BTJD 1993.2, and growths in depth by about 2\% over
-about six cycles, to become easily detectable by eye by BTJD 1997.7.
-The evolution of this particular dip is most clear in the river plots.
-The evolution of the latter dip group in cycles 1410-1481 is another
-example of this slow mode of dip growth.
-
-{\sc Dip asymmetries}---The observed asymmetries include both sharp
-leading ingresses (e.g. for the main cycle 248-315 dip complex), and
-also extended ingresses with relatively sharper {\it egresses} (e.g.
-the deepest feature during cycles 1420-1464).  Some dips do not show
-detectable asymmetry at all.
-
-The asymmetry is an important characteristic because it can help
-diagnose the optical depth of the occulting material as a function of
-orbital phase angle.  Sharp leading edges with trailing exponential
-egresses for instance have been previously seen for transiting
-exocomets and disintegrating rocky bodies
-\citep[e.g.][]{2012ApJ...752....1R,2012A&A...545L...5B,2015Natur.526..546V,2019A&A...625L..13Z}.
-We discuss this possibility below.
-
-{\sc Dip durations}---The shortest timescale that any of the {\it
-individual} dips seem to occur over is $\approx$0.07\,$P$, or about
-1.3\,hours.  For a $M_\star=0.25\,M_\odot$, $R_\star=0.5\,R_\odot$
-star, the characteristic timescale $T_{\rm dur}$ for the transit of a
-point-source over the stellar equator at $P=18.6\,$hours is also
-0.07\,$P$.  This means that while some of the LP 12-502 dips are
-sufficiently long to require structures that are extended in orbital
-azimuth, some are short enough that their durations are consistent
-with point sources.
+\subsubsection{Lessons from LP 12-502}
+
+{\sc State-switches reveal dip independence}---The state-switches seen
+in cycles 1233-1247 and 299-315 confirm that dips can disappear in
+less than one cycle, a point which has been previously appreciated
+\citep{2017AJ....153..152S}.  What is new in these particular changes,
+for instance cycles 1233-1264 of Figure~\ref{fig:lp}, is that the
+morphology changes show that the dips can be {\it independent} and
+{\it additive}.  It other words, throughout cycles 1233-1264, there
+are three local minima between phases of 0 and 0.3.  They all have
+identical ingress times.  The shape change during the transition
+implies that the leading dip that ``turned off'' (changed its depth),
+while the trailing two dips remained fixed in their depths.  In other
+words, the structures producing these dips must be independent, to the
+degree that one can undergo a severe change, while the others can
+remain essentially identical.  The state switches during cycles
+248-264 and 299-315 share the same characteristic: it is always the
+{\it leading} dip of a complex that ``switches off'', leaving the
+(fixed-depth) trailing dips in its wake.
+
+{\sc Dips grow more slowly than they disappear}---Although there are a
+few instances in which we observe dips ``switch off'' over less
+than one cycle, dip growth seems to happen more slowly.  For instance,
+the dip that grows between phase 0 and 0.1 between cycles 260-290
+begins to become visible around BTJD 1993.2, and growths in depth by
+about 2\% over about six cycles, to become easily detectable by eye by
+BTJD 1997.7.  The evolution of this particular dip is most clear in
+the river plots.  The evolution of the latter dip group in cycles
+1410-1481 is another example of this slow mode of dip growth.
+
+% 16 px vs 310 px for a full phase
+%Based on our SED fitting $R_\star=0.369\,R_\odot$
+%star, and from the isochrone mass, $M_\star=0.215\,M_\odot$ 
+{\sc Dip durations}---The shortest timescale for any of the {\it
+individual} LP 12-502 dips seems to be $\approx$0.06\,$P$ $\approx$
+1.08\,hr.  In comparison, using the stellar radius and mass derived in
+Section~\ref{subsec:starprops}, the characteristic timescale $T_{\rm
+dur} \equiv R_\star P / (\pi a)$ for the transit of a point-source at
+corotation is 1.03\,hr ({\bf uncertainties?}).  This means that while
+some of the LP 12-502 dips are sufficiently long to require structures
+that are extended in orbital azimuth, the durations of other dips are
+consistent with effective radii for the occulting material $R_{\rm
+eff} \ll R_\star$ .
+We also emphasize that this implies $a/R_\star \approx 5.8$ for this
+material, and so the analogous timescale at the stellar surface is
+about six times slower.
 
 {\sc Dip periods}---Most of the LP 12-502 dips recur with a period of
-$P=18.5611 \pm 0.0001$\,hr.  However the river plots reveal multiple
-distinct periodicities in the light curve for specific dips.  For
-instance, in sectors 25-26, the local minimum that develops around
-cycle 262 has a period faster than the mean period by $\approx$0.1\%,
-while some of the trailing local minima in the main dip complex have
-periods slower than the mean period, by $\approx$0.04\%.  In addition
-to the fundamental period, we were able to identify at least four
-distinct periods shown by specific dips over the full Sectors 18-59
-dataset, including periods at 18.5683, 18.5672, 18.5473, and
-18.5145\,hr, with a typical measurement uncertainty of
-$\approx$0.0002\,hr.
+$P=18.5611 \pm 0.0001$\,hr.  However the river plots
+(Appendix~\ref{app:lp}) reveal multiple distinct periodicities in the
+light curve for specific dips.  For instance, in sectors 25-26, the
+local minimum that develops around cycle 262 has a period faster than
+the mean period by $\approx$0.1\%, while some of the trailing local
+minima in the main dip complex have periods slower than the mean
+period, by $\approx$0.04\%.  In addition to the fundamental period, we
+were able to identify at least four distinct periods shown by specific
+dips over the full Sectors 18-59 dataset, including periods at
+18.5683, 18.5672, 18.5473, and 18.5145\,hr, with a typical measurement
+uncertainty of $\approx$0.0002\,hr.
+If each period corresponds to a dust clump, then this implies that
+multiple distinct clumps can orbit the star simultaneously, at
+marginally different separations.
 
@@
 
-\paragraph{Extremes}
+\subsection{Extremes}
 The closest CQV in our catalog is DG~CVn (TIC~368129164;
@@
 this manuscript is the first time that it has been noted as a CQV.
+The three brightest CQVs we have found are DG~CVn ($T$=9.3),
+TIC~405754448 ($T$=9.6), and TIC~167664935 ($T$=10.3).
 
@@
 
-The lowest mass ($\approx 0.12$\,M$_\odot$) belongs to TIC~50745567.
-There are a number of other similar very low mass stars, which
+The lowest mass ($\approx 0.12$\,M$_\odot$) belongs to TIC~267953787.
+The catalog contains a few other stars with similar mass, which
 suggests the phenomenon may extend into the brown dwarf regime.
 
-The three brightest CQVs in Table are DG~CVn ($T$=9.3), TIC~405754448
-($T$=9.6), and TIC~167664935 ($T$=10.3).
-
-\paragraph{Quasiperiodicity}
-A periodic signal does not modulate; the CQVs are {\it quasi}periodic.
-This is a qualitative departure from
-the ``persistent'' {\it vs.} ``transient'' flux dip distinction from 
-\citet{2017AJ....153..152S}.  While the dips can appear persistent
-over timescales of even up to 100 cycles, all the CQV dips seem to be
-transient over timescales of more than 1000 cycles
+The most massive CQV in our sample is a subject of some interest
+because to date, the only stars reported to show the CQV phenomenon
+are M-dwarfs, with typical stellar masses $\lesssim$0.3\,M$_\odot$
+\citep{2022AJ....163..144G}.  TIC~405754448 and 405910546 however
+appear to have masses of 0.82 and 0.60\,M$_\odot$ respectively.  The
+next-highest masses are $\approx$0.40\,M$_\odot$.  The masses for the
+former two objects are consistent with their CAMD locations, and their
+membership in LCC.  Based on its light curve morphology, TIC~405910546
+should be studied in greater depth, to confirm it is not an eclipsing
+binary.  TIC~405754448 similarly shows distinct morphology from many
+of the CQVs in Figure~\ref{fig:cqvs}, in that it has some of the
+lowest amplitude dips.  However overall, both of these objects seem to
+suggest that the CQV phenomenon extends up in mass to
+pre-main-sequence K-dwarfs.
+
+\subsection{CQVs are quasiperiodic}
+A periodic signal repeats exactly; the CQVs do not, although their
+periods appear to be fixed to within measurement precision over
+thousands of cycles.  They are therefore {\it quasi}periodic.  While
+this point has been suggested in studies by
+\citet{2022AJ....163..144G} and \citet{2023ApJ...945..114P},
+Figure~\ref{fig:evoln} drives it home.  This is a qualitative
+departure from the ``persistent'' {\it vs.} ``transient'' flux dip
+distinction described by \citet{2017AJ....153..152S};  while the dips
+can persist over timescales of even up to 100 cycles, all CQV dips
+seem to be transient over timescales of more than 1000 cycles
 (Figure~\ref{fig:evoln}).
-The distinction is not therefore particularly meaningful.
 
@@
 able to explore all phase angles with equal weight.  LP 12-502, and
-many other CQVs, seem to have preferred phases.  For LP 12-502,
-all of the dips happen over a fixed phase duration of two thirds of
-the period.  Phases over the other third are ``out of limits'' for
-any dipping material.  We interpret this as evidence
-either that {\it a)} some aspect the stellar magnetic field is
-strongly asymmetric, and can generate and hold extrinsic material at
-corotation, but only over two thirds of the great circle,
-or {\it b)} there is a physical structure -- for instance a
-disintegrating planetesimal swarm -- that is distributed over an arc
-of the same angular extent (240$^\circ$).
-
-\paragraph{Some CQVs require external occulters}
-(rehash Bodman2017 timescale arguments)
-
-\paragraph{Each CQV a snowflake?}
-One intriguing aspect of staring at Figure~\ref{fig:singlemosaic}
-is that, even after rescaling the amplitudes, no two CQVs
-exhibit exactly identical light curve morphology.
-There are of course similarities.
-
-TIC 272248916 and TIC 442571495 match.
-
-\paragraph{Predicting the future, given the past}
-Figure~\ref{fig:evoln}
-shows that for 21 CQVs that were observed roughly two years
-apart, 5 showed obvious signs of the phenomenon in one sector,
-and marginal or non-existence signs in the other.
-We emphasize that the periods themselves were usually stable to $<$0.1\%.
-However, this shape evolution
-suggests that CQVs have a duty cycle of $\approx$75\%.
-
-\paragraph{Why would the prominence scenario tend toward corotation?}
-This is analogous to quiescent
-prominences on the Sun \citep{1967SoPh....2...39K}.
-
-\paragraph{If the prominence scenario is correct, why don't stars in the
-Hyades and Praesepe show the phenomenon?}
-
-The prominence scenario, in a broad sense, argues that some intrinsic
+many other CQVs, might have preferred phases.  For LP 12-502, all of
+the dips happen over phases corresponding to only two thirds of the
+period.  The other third seems to be ``out of limits'' for any dipping
+material.  This could be evidence either {\it a)} that some aspect the
+stellar magnetic field is strongly asymmetric, and can generate and
+hold extrinsic material at corotation, but only over two thirds of the
+equatorial circle, or {\it b)} that there is a material -- for
+instance a disintegrating planetesimal swarm -- that is distributed
+over an arc of the same angular extent (240$^\circ$).  We favor the
+former explanation, for reasons discussed below.
+
+\subsection{Dip asymmetries and dust geometries}
+The asymmetry of a dip can help diagnose the optical depth of the
+occulting material as a function of orbital phase angle.  Sharp
+leading edges with trailing exponential egresses for instance have
+been previously seen for transiting exocomets and disintegrating rocky
+bodies
+\citep[e.g.][]{2012ApJ...752....1R,2012A&A...545L...5B,2015Natur.526..546V,2019A&A...625L..13Z}.
+
+Examining Figure~\ref{fig:cqvs}, it is not obvious
+whether the CQVs as a whole show any preference for sharper ingresses,
+or sharper egresses.
+In some cases (e.g. TIC~425933644), the continuum itself is not
+particularly well-defined, and so the meaning of ``ingress'' and
+``egress'' are not particularly clear.
+In others, such as Sector~36 of TIC~89463560, there is a single clear
+sharp ingress with an exponential egress, which could be directly fit
+using e.g.~a model analogous to those used for exocomets
+\citep[e.g.][]{2019A&A...625L..13Z}.
+The main quantities of interest in such models would likely be 
+the exponential decay time- and therefore length-scale,
+as well as the impact parameter and the 
+inferred transit depth (and its implications for the equivalent
+``radius'' of the transiting cloud).
+Although we briefly explored such models, it quickly became clear that
+careful modeling of sources such as LP 12-502 merits its own in-depth study.
+Connections could likely also be made to the toroidal geometries that
+are produced by outflowing atmospheres of transiting planets
+\citep[e.g.][]{2019ApJ...873...89M,2022ApJ...926..226M}.
+
+\subsection{On the prominence scenario}
+
+In our view, the ``prominence'' scenario
+\citep{2017AJ....153..152S,2022MNRAS.514.5465W}, in which quiescent
+prominences analogous to those observed on the Sun become trapped in
+co-rotation may be the next-best contending model, after the idea of
+dust clumps doing the same thing.  The prominence idea historically
+came from spectroscopic detections of transient Balmer- and
+resonance-line absorption seen for stars such as AB~Dor and
+Speedy~Mic \citep[see
+e.g.][]{1989MNRAS.238..657C,1993MNRAS.262..369J,2019MNRAS.482.2853J}.
+Neutral hydrogen clouds scatter chromospheric emission from the star,
+producing the observed spectroscopic line variations.  The
+interpretation of those observations seems, in our view, secure.
+
+The difference between the prominence and dust clump scenarios
+is essentially only in whether the occulting material of
+interest is neutral hydrogen, or dust.  In the phrasing of the
+``frozen flux'' condition of ideal rigid field magnetohydrodynamics,
+the tendency of both to become trapped at the corotation radius in the
+equatorial plane is tied to how of the four relevant forces (gravity,
+Lorentz, inertial Coriolis, and inertial centrifugal), the Lorentz and
+Coriolis only act perpendicular to field lines, while gravity and the
+centrifugal force are in balance at $R_{\rm cr}$
+\citep[see][Sec.~2]{2005MNRAS.357..251T}.
+The magnetic field strength is only relevant in this formulation of
+the system in that we must have $R_{\rm sonic} < R_{\rm cr} < R_{Alfven}$ in order for 
+closed loops to exist that can support prominences (CITE
+Jardine/CollierCameron2019).
+In detail however, whether such magnetic fixed points lie in the equatorial
+plane, or elsewhere, depends on the star's magnetic field geometry
+\citep{2023MNRAS.518.4734S}.
+
+\subsubsection{Can gas absorption reproduce the observed chromaticity?}
+In our view, the strongest argument for why neutral hydrogen is ruled
+out as the occulting source is that we are seeing broadband flux
+variations that are deeper in the blue than in the red.
+
+Based on our reading of \citet[][Ch.~8]{1992oasp.book.....G},
+it is somewhat challenging to get neutral hydrogen to have this type of chromaticity.
+Bound-bound absorption provides opacity only at narrow resonant lines.
+Bound-free absorption can provide wavelength-dependent opacity, but the
+absorption coefficients generally {\it grow} with increasing wavelength, rather
+than {\it shrink} as one needs in order to get deeper absorption in
+the blue than in the red.  H$^-$ similarly fails as a viable opacity
+source for the same reason: its absorption coefficient peaks near
+8500\,$\AA$, and is an order of magnitude smaller at $\approx$3000\,AA
+\citep{1992oasp.book.....G}, following CITE Wishart 1979.
+Thompson scattering is also ruled out, because it is gray.
+Dust, with its relatively featureless but increasing extinction curve
+when going bluer into the optical, is to our knowledge the most
+obvious opacity source.
+
+While the above line of reasoning seems fairly convincing,
+one flaw that we can point out in it is tied to $\sigma$~Ori~E.
+The logic presented above argues essentially that regardless of a star's temperature,
+if relative depths of dips are seen to be deeper in the blue than in the red,
+then it is hard to get hydrogen to do it.
+$\sigma$~Ori~E shows dips that are deeper in the blue than in the red \citep{1977ApJ...216L..31H},
+which have been understood in terms of absorbing circumstellar material
+\citep{2005ApJ...630L..81T}.
+This material however cannot be dust, due to the relevant sublimation timescales.
+It is instead thought to be sourced from bound-free absorption from neutral hydrogen
+\citep{2005ApJ...630L..81T}.  Given these complexities, it clearly
+seems important for a future theoretical study to be conducted to
+determine to what degree the observed chromaticities match, or do not
+match, with expectations from radiative transfer.
+This issue has a key ability to resolve the question of whether the
+CQVs are caused by dust, or by gas.
+
+\subsubsection{Does the timescale for CQVs to live inform the mechanism?}
+Independent of the theoretical basis for gas absorption, the
+prominence scenario may present another issue: why don't stars in the
+Hyades and Praesepe show the phenomenon?
+in a broad sense, the prominence scenario argues that an intrinsic
 stellar process is key for generating the CQV phenomenon.
@@
 
-\paragraph{Connection to debris disk evolution}
-The concordance model for planet formation invokes the presence of an accretion
-disk.
-The disk is truncated (by what?) at the magnetospheric truncation radius,
-which happens to often coincidentally be at the Keplerian corotation radius.
-In such a scenario, planetesimals and boulders can migrate inward due to
-Type X migration (CITE),
-until they hit a ``dust trap'' at the inner wall (CITE eg Kama2009,and
-related).
-Support for this model comes from the rotation periods of classical
-and weak-lined T Tauri stars (CITE Rebull2018,2019);
-from near-infrared interferometric observations that detect thermal
-emission from the disk wall (CITE CITE);
-and from the turn-over in the exoplanet orbital period distribution,
-which occurs around 5-10 days for FGK stars, and perhaps even
-closer-in for M-dwarfs (CITE Petigura2022, and CITE for M-dwarfs).
-
-Broadly, the existence of a dust trap at the disk truncation radius 
-might be expected to trap larger boulders as well.
-Once the disk loses the gas, what happens to those boulders?
-They are no longer shielded.
-We then enter a phase of mass loss.
-Perhaps that phase is what we are observing.
-
-\paragraph{Connection to close-in exoplanets}
+The long-lived prominences inferred from the decades-old spectroscopic
+data, and dust-clouds inferred from K2+TESS, could of course also be
+pieces of a complementary picture.
+
+\subsection{Planets or planetesimal swarms near corotation?}
+
 Planet occurrence rate studies based on Kepler showed that around
@@
 between 1-4\,$R_\oplus$ and orbital periods within 3 days
-\citep{2015ApJ...807...45D}.
-TRAPPIST-1b, a rocky planet with an orbital period of 1.5\,days is a
-possible example of this type of planet (CITE), though it orbits a
-very low-mass star (0.08\,M$_\odot$).
-
-The connection between the CQV phenomenon and these close-in
-exoplanets remains to be made.
-If the dust cloud model is correct, then assuming that the
-compact multiplanet resonant chains migrate to within $\approx$5-10
-stellar radii within the first 100\,Myr (e.g. CITE IZIDORO), the
-dust clouds and the planets would coexist for a non-negligible time
-interval.
-Rocky planets this young likely still have molten global magma oceans
-(e.g. CITE LICHTENBERG REVIEW), and would undergo significant 
-outgassing and atmospheric escape.
-A scenario in which close-in rocky planets serve as a possible source
-of dust for the clouds is not entirely implausible, though it remains
-to be explored.
-
-\paragraph{A planetesimal swarm at corotation seems unlikely}
-It is tempting to interpret certain features of the LP 12-502 light
-curve in this framework of a disintegrating planetesimal swarm.  For
+\citep{2015ApJ...807...45D}.  The number increases to $\approx$0.7
+planets per star, for planets with 1-4\,$R_\oplus$ and $P$$<$10\,days.
+Extrapolating to {\it small} close-in planets, from say
+0.1-4\,$R_\oplus$ and within 10 days, it is reasonable to expect on
+average one planet per M-dwarf.  TRAPPIST-1b ($P$=1.5\,days) is one
+example of this type of planet (CITE) orbits a 0.08\,M$_\odot$ star.
+
+Within the context of planet formation theory, the locations of these
+close-in planets are set by the location of the protoplanetary disk's
+magnetospheric truncation radius (see e.g. CITE for a review).  In
+simple 1-D viscous accretion models, this truncation radius roughly
+coincides with the Keplerian corotation radius (CITE), though in
+detail factors of a few difference have been observed between the two
+(CITE IR studies).  With models that have migrating compact
+multiplanet resonant chains, the inner-most planets arrive within
+$\approx$5-10 stellar radii within the first 100\,Myr (e.g.  CITE
+IZIDORO),
+
+It is of course very tempting to attempt to interpret features of the
+CQV light curves in terms of the possible presence of close-in
+exoplanets, or even planetesimals.  For instance, rocky planets this
+young would have molten global magma oceans analogous to those that
+existed on the Earth and Moon (e.g. CITE LICHTENBERG REVIEW), and thus
+would undergo significant outgassing and atmospheric escape.  A
+scenario in which close-in rocky planets serve as a possible source of
+dust for the clouds is not entirely implausible, though it remains a
+subject of speculation.
+
+Given the dip depth variations that are observed in systems like LP
+12-502, one would be driven in this framework toward a picture of a
+disintegrating planetesimal swarm.  The dip-profile asymmetries during
+certain segments of the light curve plausibly match this idea; for
 instance, the complex in cycles 248-298 could be well-fit by a sharp
@@
 complex, during cycles 248-264 (pre-state-switch), could be fit by a
-similar profile.  There are two degenerate explanations for the small
-``wiggles'' in the exponential decay.  In one explanation, the decay
-timescale is fast ($\approx$0.03\,$P$), and there are up to five
-exocomets, superposed.  In the other, there is only one main
-``launching body'', and the material it ejects either has some
-sub-structure, or else is passing across (and in synchronicity with) a
-star with heavily substructured starspots across its surface.
-
-While the number of free parameters in this type of model is somewhat
-dizzying, we have no right to believe that nature need be
-simple.  Every dip in the exocomet tail model would have as free
-parameters the dip phase, the duration (captured by an exponential
-decay timescale), and the dip depth.  In detail, the impact parameter
-would also enter.  Allotting four free parameters per dip yields up to
-32 free parameters for the light curve at the most complicated times
-(assigning one exocomet per local minimum).
-
-However there are two glaring issues with the disintegrating planetesimal swarm idea.
-First, a large number of the dips show asymmetries in the {\it wrong
-	direction} relative to the naive expectation of a trailing comet tail.
-Dust forward scattering might be one possible way out; so too might
-invoking non-exponentially decaying dust
-distributions as a function of azimuth.
-Second, and perhaps more serious, the (unseen) planetesimals 
-should
-be on {\it exactly periodic} orbits over observable timescales, on the presumption that the planetesimals
-would be massive enough to not feel any headwind or magnetic field.
-This is not what is observed; instead, every dip period
-that is observed to be distinct from the fundamental 18.5611\,hr period
-is both short-lived, and unique.
-The fundamental 18.5611\,hr period itself is itself associated with
-material at too many phases to arguably be tied to a single launching body.
-This suggests that the dust clumps must be much less massive than a 1--100\,km sized
-planetesimal,
-and therefore more easily influenced by the stellar magnetic field, and events
-like flares.
-
-\paragraph{Interpretation of the $T\lesssim 15$ dropoff}
-Our search sample included 35472 unique stars with $12<T<14$, versus
-2045 unique stars with $15<T<16$.  This helps clarify why our detected
-CPVs become less common toward fainter TESS magnitudes, despite the
-relative ease of their detectability, even at $15<T<16$.  It is
-because the TESS 2-minute data are very incomplete at the faint end.
+similar profile.  While the number of free parameters in this type of
+model is somewhat dizzying, we have no right to believe that nature
+need be simple.
+
+%There are two degenerate explanations for the small
+%``wiggles'' in the exponential decay.  In one explanation, the decay
+%timescale is fast ($\approx$0.03\,$P$), and there are up to five
+%exocomets, superposed.  In the other, there is only one main
+%``launching body'', and the material it ejects either has some
+%sub-structure, or else is passing across (and in synchronicity with) a
+%star with heavily substructured starspots across its surface.
+
+%Every dip in such a model would have as free parameters the dip phase,
+%the duration (captured by an exponential decay timescale), and the dip
+%depth.  In detail, the impact parameter would also enter.  Allotting
+%four free parameters per dip yields up to 32 free parameters for the
+%light curve at the most complicated times (assigning one exocomet per
+%local minimum).
+
+Ultimately though, there are two glaring issues with the
+disintegrating planetesimal swarm idea.  First, a large number of the
+dips show asymmetries in the {\it wrong direction} relative to the
+naive expectation of a trailing comet tail.  Dust forward scattering
+might be one possible way out; so too might invoking non-exponentially
+decaying dust distributions as a function of azimuth.  Second, and
+more serious, the (unseen) planets or planetesimals should be on {\it
+exactly periodic} orbits over observable timescales, on the
+presumption that the planetesimals would be massive enough to not feel
+any headwind or magnetic field.  This is not what is observed.  The
+fact that dips in sources such as LP 12-502 appear and disappear at
+{\it distinct phases} but with the same period seems to be a major
+challenge to tying the entire phenomenon to a single launching body.
+Similarly, the fact that the dips often respond to events like flares
+suggests that that the responsible material be much less massive than
+a 1--100-\,km sized planetesimal, and therefore more easily influenced
+by the stellar magnetic field.
+
+%  % TODO: needed??
+%  {\sc Some CQVs require external occulters}
+%  (rehash Bodman2017 timescale arguments)
+
+%{\sc Each CQV a snowflake?}
+%An intriguing aspect of Figure~\ref{fig:cqvs} is that very few CQVs
+%exhibit exactly identical light curve morphology.
+%There are of course similarities.
+%TIC 272248916 and TIC 442571495 match.
+%But overall, they all different.
+
+% \paragraph{Predicting the future, given the past}
+% Figure~\ref{fig:evoln}
+% shows that for 21 CQVs that were observed roughly two years
+% apart, 5 showed obvious signs of the phenomenon in one sector,
+% and marginal or non-existence signs in the other.
+% We emphasize that the periods themselves were usually stable to $<$0.1\%.
+% However, this shape evolution
+% suggests that CQVs have a duty cycle of $\approx$75\%.
+
+% \paragraph{Why would the prominence scenario tend toward corotation?}
+% This is analogous to quiescent
+% prominences on the Sun \citep{1967SoPh....2...39K}.
+
+\subsection{From dippers to debris disks}
+The concordance model for planet formation invokes the presence of an
+accretion disk.  The disk is truncated (by what?) at the
+magnetospheric truncation radius, which happens to often
+coincidentally be at the Keplerian corotation radius.  In such a
+scenario, planetesimals and boulders can migrate inward due to Type X
+migration (CITE), until they hit a ``dust trap'' at the inner wall
+(CITE eg Kama2009,and related).  Support for this model comes from the
+rotation periods of classical and weak-lined T Tauri stars (CITE
+Rebull2018,2019); from near-infrared interferometric observations that
+detect thermal emission from the disk wall (CITE CITE); and from the
+turn-over in the exoplanet orbital period distribution, which occurs
+around 5-10 days for FGK stars, and perhaps even closer-in for
+M-dwarfs (CITE Petigura2022, and CITE for M-dwarfs).
+
+Broadly, the existence of a dust trap at the disk truncation radius
+might be expected to trap larger boulders as well.  Once the disk
+loses the gas, what happens to those boulders?  They are no longer
+shielded.  We then enter a phase of mass loss.  Perhaps that phase is
+what we are observing.
+
+% \paragraph{Interpretation of the $T\lesssim 15$ dropoff}
+% Our search sample included 35472 unique stars with $12<T<14$, versus
+% 2045 unique stars with $15<T<16$.  This helps clarify why our detected
+% CPVs become less common toward fainter TESS magnitudes, despite the
+% relative ease of their detectability, even at $15<T<16$.  It is
+% because the TESS 2-minute data are very incomplete at the faint end.
 
@@
 
-We report on the existence of \ngoods\ objects that showed
-complex quasiperiodic behavior over at least one TESS sector between July~2018 and Sep~2022.
-Our search for these objects was restricted to dwarf stars bright enough
-for 1\% precision photometry with TESS over 1 hour ($T$$<$16),
-that were red ($\bprp<1.5$) and within 150\,pc of the Sun.
+In this work, we analyzed TESS
+120-second cadence data 
+collected between July~2018
+and Sep~2022, and searched it for complex quasiperiodic variables (CQVs).
+Our search sample included
+\nstarssearched\ K- and M-dwarfs within 150\,pc,
+and is $\gtrsim 80\%$ complete within 30\,pc, and $\lesssim 10\%$ complete
+at distances exceeding 100\,pc.
+
+In this sample of stars, we found \ngoods\ objects that showed complex
+quasiperiodic behavior over at least one observed TESS sector.  
 These \ngoods\ bonafide CQVs are listed in Table~\ref{tab:thetable}.
@@
 designation is less certain.
-
 Analyzing the light curves of these objects, we draw the following conclusions.
@@
   \item CQVs are {\it quasi}periodic.  While the mean periods in our
-	sample seem to remain fixed over the span of available observations, the light curve
-	shapes themselves evolve, similar to rotating stars.
+    sample seem to remain fixed over the span of available
+    observations, the light curve shapes themselves evolve, similar to
+    rotating stars.
 	%
-	\item The same CQV can show dips with very similar but clearly distinct periods.  
-	LP 12-502, for instance, showed dips with four distinct periods within $\pm 0.3\%$
-	of the fundamental period, sometimes simultaneous, and each lasting for up to 50 cycles.
+  \item The same CQV can show dips with very similar but clearly
+    distinct periods.  LP 12-502, for instance, showed dips with four
+    distinct periods within $\pm 0.3\%$ of the fundamental period,
+    sometimes simultaneous, and each lasting for up to 50 cycles.
 	%
-	\item The CQV phenomenon persists for at least 150\,Myr, based on the
-	existence of CQVs in AB Dor, the Pleiades, and Psc-Eri.  It may extend to
-	even older ages, however the lack of detected CQVs in the Hyades and
-	Praesepe suggest that the phenomenon is unique to the pre-main-sequence
-	for M-dwarfs.
+  \item The CQV phenomenon persists for at least 150\,Myr, based on
+    the existence of CQVs in AB Dor, the Pleiades, and Psc-Eri.  It
+    may extend to even older ages, however the lack of detected CQVs
+    in the Hyades and Praesepe suggest that the phenomenon is unique
+    to the pre-main-sequence for M-dwarfs.
 	%
-	\item CQVs evolve over timescales that are both secular ($>$100\,cycles) and impulsive ($<$1 cycle).
-	``State-switches'' can cause dips to collapse instantaneously, and are often (but not exclusively)
-	linked with observed optical flares.
-	Dip growth however seems to happen over durations of at least ten cycles.
+  \item CQVs evolve over timescales that are both secular
+    ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
+    can cause dips to collapse instantaneously, and are often (but not
+    exclusively) linked with observed optical flares.  Dip growth
+    however seems to happen over durations of at least ten cycles.
 	%
-	\item The population-averaged duty cycle for CQVs seems to be $\approx 75$\%, based on 
-	the fraction of bonafide CQVs that ``turned off'' during TESS re-observations.
+  \item The population-averaged duty cycle for CQVs seems to be
+    $\approx 75$\%, based on the fraction of bonafide CQVs that
+    ``turned off'' during TESS re-observations.
 \end{itemize}
 
-Many questions remain.
-After correcting for line-of-sight inclination, are
-most young M-dwarfs CQVs?  What observational signatures distinguish
-the proposed models (Figure~\ref{fig:f1}, bottom row)?  What
-organizational regularities characterize the CQV as a class of
-variable star?  What physically sets the extremes of the CQV population, such as
-the longest rotation periods, hottest stellar temperatures, and oldest
-stellar ages?  And finally, what connections, if any, do CQVs have to
-topics such as stellar evolution, M-dwarf magnetic fields, debris
-disks, and close-in exoplanets?
-While we have tried to point out possible connections, the most
-likely path toward definitive resolutions would be to observe a full
-phase curve of LP 12-502, or perhaps some other suitable object, using JWST/MIRI.
+Many questions remain.  After correcting for line-of-sight
+inclination, are most young M-dwarfs CQVs?  What observational
+signatures distinguish the proposed models (Figure~\ref{fig:f1},
+bottom row)?  What organizational regularities characterize the CQV as
+a class of variable star?  What physically sets the extremes of the
+CQV population, such as the longest rotation periods, hottest stellar
+temperatures, and oldest stellar ages?  And finally, what connections,
+if any, do CQVs have to topics such as stellar evolution, M-dwarf
+magnetic fields, debris disks, and close-in exoplanets?  While we have
+tried to point out possible connections, the most likely path toward
+definitive resolutions would be to observe a full phase curve of LP
+12-502, or perhaps some other suitable object, using JWST/MIRI.
 
@@
       set, with one image per sector for each of \ncpvsfound\ objects
-      is available online.
+      is available online {\bf For internal collaboration review:
+      \url{https://www.dropbox.com/scl/fo/zlj3txot4cvymfb22wewu/h?dl=0&rlkey=3ec5f9o5xewrixzfkhkdenopa}}.
       Panels are as follows.
@@
 {\it The light curve}---
-Figure~\ref{fig:lplc} shows an alternative view of the LP-502 light
-curve from Figure~\ref{fig:lp}, split into successive TESS orbits.  We
-binned the light curve to 15-minute intervals for visual clarity, and
-required at least one (120-second cadence) flux measurement per bin.
-Points more than 2.5$\sigma$ above the median are drawn in gray, also
-for visual clarity.  Missing data are not drawn (a common plotting
-error when ``drawing'' light curves, rather than showing a scatter
-plot).  The red lines point to specific state switches, discussed
-elsewhere in the text.
-
 Figure~\ref{fig:lp2} shows another alternative view of
 Figure~\ref{fig:lp}, but arranged to enable easy visual appreciation
-of transit timing changes, rather than transit depth changes.
-A best-fitting two-harmonic sinusoid has been independently fitted and
-subtracted from the Sector
-18-19 data, 25-26 data, and 53, 58, and 59 data.
+of transit timing changes, rather than transit depth changes.  A
+best-fitting two-harmonic sinusoid has been independently fitted and
+subtracted from the Sector 18-19 data, 25-26 data, and 53, 58, and 59
+data.
 
@@
 
+\section{Chromaticity in TIC 262400835}
+
+TIC~262400835 ($d$=174\,pc) is formally outside the scope of the
+current work.  However, this CQV was observed using MuSCAT2 on 2020
+December 12, 13, and 16, and the results are pertinent enough to the
+present work.
+{\bf todo: describe observations}.
+
+We include {\bf a table of the photometry} here to enable potential
+future deeper analyses of the chromaticity of this object class.
+
+Generally, these data serve as a minor addition beyond the
+observations that have been acquired by
+\citet[e.g.][]{2017PASJ...69L...2O,2020PASJ...72...23T,2022AJ....163..144G,2023MNRAS.518.2921K}
+on this topic.  \citet{2023MNRAS.518.2921K} provides what we find to
+be the most lucid summary, and we quote: ``amplitudes are almost
+always larger, the shorter the wavelength of the filter, but the
+relationship can be weak or non-monotonic.''
+
+\begin{figure*}[!t]
+	\begin{center}
+    \includegraphics[width=0.45\textwidth]{TIC262400835_multicolor_phase_stacked.pdf}
+    	\end{center}
+    \vspace{-0.4cm}
+		\caption{
+	      {\bf Chromaticity in TIC~262400835}.
+		}
+		\label{fig:muscat}
+\end{figure*}
+
 \clearpage

### 2023-07-01 complexrotators/plotting.py
update

@@ -169,7 +169,7 @@ def plot_river(time, flux, period, outdir, titlestr=None, cmap='Blues_r',
         (N_obs_per_cycle, cycle_max-cycle_min)
     )
 
-    for cycle_ind in range(cycle_min, cycle_max):
+    for ix, cycle_ind in enumerate(range(cycle_min, cycle_max)):
 
         begin = t0 + period*cycle_ind
         end = t0 + period*(cycle_ind+1)
@@ -235,7 +235,11 @@ def plot_river(time, flux, period, outdir, titlestr=None, cmap='Blues_r',
 
                 flux_this_cycle = fn(t_grid_this_cycle)
 
-                flux_arr[:, cycle_ind] = flux_this_cycle
+                print(cycle_ind, N_obs_per_cycle)
+                try:
+                    flux_arr[:, ix] = flux_this_cycle
+                except IndexError:
+                    import IPython; IPython.embed()
 
     if not isinstance(vmin, float):
         vmin = np.nanmedian(flux)-4*np.nanstd(flux)

### 2023-07-01 paper/ms.tex
update ms

@@
 \newcommand{\berkeley}{Astronomy Department, University of California, Berkeley, CA 94720, USA}
+\newcommand{\princeton}{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}
 
@@
 \affiliation{\mitkavli}
+
+\author[0000-0001-7204-6727]{G\'asp\'ar \'A. Bakos}
+\affiliation{\princeton}
 
@@
 	%
-  \item CQVs are {\it quasi}periodic.  While the mean periods in our
+  \item CQVs are quasiperiodic.  While the mean periods in our
     sample seem to remain fixed over the span of available
@@
     distinct periods within $\pm 0.3\%$ of the fundamental period,
-    sometimes simultaneous, and each lasting for up to 50 cycles.
+    sometimes simultaneously, and each lasting for up to 50 cycles.
 	%
@@
     may extend to even older ages, however the lack of detected CQVs
-    in the Hyades and Praesepe suggest that the phenomenon is unique
-    to the pre-main-sequence for M-dwarfs.
+    in the Hyades and Praesepe suggests that the phenomenon does become
+    less common at older ages.
 	%
@@
 
-{\bf author contribution statement goes here}
-L.G.B.~and R.~J. conceived the project and executed the
+%{\bf author contribution statement goes here}
+LGB~and RJ conceived the project and executed the
 dip-based and Fourier-based searches, respectively.
-L.G.B.~drafted the initial manuscript, and performed the cluster
-membership analysis.
-S.~R. and R.~J. vetted the results from the Fourier search.
-L.A.H.~advised on project scope and experiment design.
+LGB~drafted the initial manuscript, and performed the cluster
+membership, SED, and variability analyses.
+SR and RJ vetted the results from the Fourier search.
+LAH advised on project scope and experiment design.
+GAB acquired and maintained the servers used to run the dip-finding
+pipeline.
 All authors assisted in manuscript revision.
@@
 
+\section{More river plots}
+
+\begin{figure*}[!t]
+	\begin{center}
+		\subfloat{
+			\includegraphics[width=0.43\textwidth]{TIC300651846_river_seismic_0_650_vmin-0.06000_vmax0.06000.png}
+			\includegraphics[width=0.43\textwidth]{TIC300651846_river_seismic_2305_2630_vmin-0.06000_vmax0.06000.png}
+		}
+	\end{center}
+	\vspace{-0.4cm}
+	\caption{
+		{\bf River plots of TIC 300651846}.
+		The envelope has not been subtracted.
+		7 sectors of continuous 2-minute observations.  (Thanks to DDT029)
+	}
+	\label{fig:lpriver0}
+\end{figure*}
+
 \section{No additional power at 20~second cadence}

### 2023-07-01 drivers/plot_river.py
add TIC3006 river

@@ -89,11 +89,11 @@ def single_ticid():
 
     ##########
     ticid = '300651846'
-    cyclewindows = [(-10, 700), (2300, 2600)]
+    cyclewindows = [(0, 650), (2305, 2630)]
     sample_id = '2023catalog_LGB_RJ_concat'
     manual_period =  8.2551/24
-    manual_period =  8.2549/24
-    t0 = 2170.
+    manual_period =  8.254/24  #better
+    t0 = 2170. - 5*manual_period
     nterms = None
     model_id = None
     # specifies lc subtrxn model

### 2023-07-02 drivers/get_selection_function_values.py
minor selxn fn update

@@ -3,6 +3,14 @@ import os
 from os.path import join
 from complexrotators.paths import PAPERDIR
 
+def add_comma(num):
+	# latexify numbers greater than 1{,}000
+    num_str = str(num)
+    if num < 1000:
+        return num_str
+    else:
+        return add_comma(num // 1000) + '{,}' + num_str[-3:]
+
 localdir = '/Users/luke/local/SPOCLC'
 csvpath = join(localdir, 'gaia_X_spoc2min_merge.csv')
 df = pd.read_csv(csvpath)
@@ -19,8 +27,8 @@ N_1 = len(np.unique(sdf.TICID))
 N_2 = len(sdf)
 
 latex_txt = (
-    r"\newcommand{\nstarssearched}{"+str(N_1)+"}\n"
-    r"\newcommand{\nlcssearched}{"+str(N_2)+"}\n"
+    r"\newcommand{\nstarssearched}{"+add_comma(N_1)+"}\n"
+    r"\newcommand{\nlcssearched}{"+add_comma(N_2)+"}\n"
 )
 
 outpath = join(PAPERDIR, 'vals_searched_stars.tex')

### 2023-07-02 paper/ms.tex
update ms

@@
 
-\newcommand{\ntwoyear}{27} % TODO: update
-\newcommand{\ntwoyearturnedoff}{5} % TODO: update
-
 \begin{document}
@@
 %\title{Pre-Main-Sequence M-Dwarfs With Complex Quasiperiodic Variability From Four Years of TESS}
-
-\title{Corotating Dust Clumps Around Adolescent Low-Mass Stars: Four Years of TESS}
-
 %\title{Complex Quasiperiodic Variables From Four Years of TESS}
+\title{Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS}
 
@@
 % primary authors
+\author{Author list and order not final!}
 \author[0000-0002-0514-5538]{Luke~G.~Bouma}
@@
   period and total duration that are fixed over more than 1{,}000 cycles,
-  but which in detail shows anywhere from four to eight local minima
-  per cycle.  LP-502 at times demonstrated drastic shape changes over
-  less than one cycle, and also displayed distinct superposed periods
-  simultaneously.  Broadly speaking, we find that none of the CQVs
-  maintain a fixed light curve shape over timescales of more than a
-  few hundred cycles, and we revisit the arguments for why transient
-  corotating material is the most likely explanation.  In the
-  future, we expect that our sample will facilitate modeling and
-  observational efforts aimed at understanding these objects, and
-  connecting them to the broader contexts of star, disk, and exoplanet
-  evolution.
-%  For instance, based on the rate of dip evolution, we
-%  estimate that the incident dust flux corresponds to of order an
-%  asteroid belt's worth of mass accreting onto these stars over $10^8$
-%  years.
+  but which in detail exhibits anywhere from four to eight local minima
+  per cycle.  LP-502 also displayed distinct superposed periods
+	simultaneously, and displayed drastic shape changes shortly after flares.
+	Broadly speaking, we find that none of the CQVs maintain a fixed light curve
+	shape over timescales of more than a few hundred cycles, and we revisit the
+	arguments for why transient corotating material is the most viable explanation.
+	In the future, we expect that our sample will facilitate modeling and
+	observational efforts aimed at understanding these objects, and connecting them
+	to the broader contexts of star, disk, and exoplanet evolution.
+	For instance, if the transiting material is dust, then the rate of dip evolution
+	implies that of order an asteroid belt's worth of mass passes through these
+	structures over the $10^8$ years for which they are observed.
 \end{abstract}
@@
 \citealt{2019A&A...625L..13Z}) and disintegrating rocky bodies around
-both M-dwarfs (e.g. K2-22; \citealt{2014ApJ...784...40R}) and white
+both M-dwarfs (e.g. KOI-2700; \citealt{2014ApJ...784...40R}) and white
 dwarfs (e.g. WD~1145; \citealt{2015Natur.526..546V}).
@@
 \citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z}.
-Some CQVs show up to eight local minima (dips) per cycle.  Most CQVs
-are pre-main-sequence M-dwarfs without near-infrared excesses, with
+Some CQVs show up to eight local minima (dips) per cycle.  Most 
+are pre-main-sequence M-dwarfs without near-infrared excesses, 
 ages of $\approx$5-150 million years (Myr), and rotation periods of at
@@
 A few competing explanations for what causes the complex quasiperiodic
-variability are shown in Figure~\ref{fig:f1}, along with a few
+variability are shown in Figure~\ref{fig:f1}, along with some
 representative light curves.  All young M-dwarfs are spotted, which
@@
 any object with sufficiently sharp dips
-\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The more likely
-scenarios invoke sharp geometries with material extrinsic to the
-stellar surface
-\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  In the
-``clump'' scenario, opaque dust clumps orbiting near the Keplerian
-corotation radius eclipse the star
-\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  In the
-``prominence'' scenario, long-lived condensations of plasma are
-trapped along the star’s magnetic field lines, also near corotation
-\citep{2022MNRAS.514.5465W}.  There is also a ``screen'' scenario, in
+\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The timescales and
+amplitudes of the flux variations instead require sharp geometries
+with material extrinsic to the stellar surface
+\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  The
+``clump'' scenario invokes opaque dust clumps orbiting near the Keplerian
+corotation radius, which periodically eclipse the star
+\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The
+``prominence'' scenario invokes long-lived condensations of cool and dense
+marginally-ionized gas, embedded within the
+hotter corona, that would be centrifugally supported near corotation
+\citep{1989MNRAS.238..657C,2019MNRAS.482.2853J,2022MNRAS.514.5465W}.
+Such structures are analogous to quiescent prominences and filaments
+observed on the Sun, though at much larger relative distances from the
+stellar surface.
+A final posibility that has been suggested is one of a ``screen'', in
 which the inner wall of a quiescent circumstellar disk blocks a
@@
 
-In our view, the arguments seem best established for the dust clump
-hypothesis \citep{2023MNRAS.518.4734S}.  This is primarily because the
-prominence scenario lacks a mechanism for generating broadband
-opacity, and the screen scenario is inconsistent with the degree of
-observed periodicity, the lack of infrared excess, and the observed
-lifetime of the effect, which is an order of magnitude longer than the
-$\approx$$10^7$ year timescale typically quoted for the primordial
-disk to disperse.  However, unambiguous evidence, for instance a
-spectroscopic detection of silicates during a ``dip'', has yet to be
-acquired.
-
-CQVs have been challenging to understand because they have been both
-hard to discover and hard to characterize.   Discoverability is tied
-to rarity: CQVs comprise about 1\% of the youngest 1\% of M-dwarfs
+In our view, the dust clump and prominence hypotheses seem most
+plausible.  They are qualitatively similar, except one
+invokes opacity from dust, while the other invokes opacity from gas,
+likely bound-free transitions in hydrogen or perhaps a
+molecular opacity.  The screen scenario seems inconsistent with the
+degree of observed periodicity, the lack of infrared excess, and the
+observed lifetime of CQVs extending an order of magnitude longer than
+the $\approx$$10^7$ year timescale typically quoted for the primordial
+disk to disperse.  However, unambiguous evidence 
+has yet to be acquired in support of any scenario.  Such evidence
+might include a spectroscopic detection of silicate 10\,$\mu$m dust
+absorption during a dip, or perhaps detection of transient
+Balmer-line absorption during the dips, similar to observations made in
+systems such as AB~Dor \citep[see the review
+by][]{1999ASPC..158..146C}.
+
+CQVs remain mysterious because they have been both hard to discover
+and hard to characterize.   Discoverability is tied to rarity: CQVs
+comprise about 1\% of the youngest 1\% of M-dwarfs
 \citep{2018AJ....155..196R}.  Out of the millions of stars monitored
@@
 July~2018 and Sep~2022 (Sectors 1-55; Cycles 1-4).  We present our
-search methods in Section~\ref{sec:methods}; and the properties of the
-resulting CQV catalog in Section~\ref{sec:results}.  Open questions
+search methods in Section~\ref{sec:methods}, and the properties of the
+resulting CQV catalog in Section~\ref{sec:results}.  
+The evolution of many CQVs over a two-year baseline is described
+in Section~\ref{sec:evoln}, including a deep-dive into LP 12-502.
+Implications 
 are discussed in Section~\ref{sec:discussion}, and we conclude in
@@
 reflects how, when observed over timescales of more than tens of
-cycles, CQVs are almost, but not exactly periodic.  Their shape
-evolution implies that they are irregularly periodic, or for short,
-quasiperiodic.  While the three-type classification scheme proposed by
+cycles, CQVs are almost but not exactly periodic.  They are
+irregularly periodic, or for short, quasiperiodic.  While the
+three-type classification scheme proposed by
 \citet{2017AJ....153..152S} may indeed provide some helpful visual
@@
 
-We analyzed the ``short'' 120-second cadence data
-acquired by TESS between July~2018 and Sep~2022 (Sectors 1-55).
-Specifically, we used the 120-second cadence light curve products
-produced by the mission's Science Processing and Operations Center at
-NASA Ames \citep{2016SPIE.9913E..3EJ}.  While the TESS data products
-also include full frame images with cadences of 200, 600, and 1800
-seconds, we limited our scope in this work for the sake of simplicity
-in data handling.  In exchange, we lose in both completeness and
-homogeneity of the selection function.  While TESS cumulatively
-observed $\approx$90\% of the sky for at least one lunar month between
+We analyzed the ``short'' 120-second cadence data acquired by TESS
+between July~2018 and Sep~2022 (Sectors 1-55).  Specifically, we used
+the 120-second cadence light curve products produced by the mission's
+Science Processing and Operations Center at NASA Ames
+\citep{2016SPIE.9913E..3EJ}.  While the TESS data products also
+include full frame images with cadences of 200, 600, and 1800 seconds,
+we limited our scope in this work for the sake of simplicity in data
+handling.  In exchange, we lose in both completeness and homogeneity
+of the selection function.  While TESS cumulatively observed
+$\approx$90\% of the sky for at least one lunar month between
 July~2018 and Sep~2022, the 120-second cadence data were acquired for
@@
 To assess the completeness of the resulting 120-second cadence data
-that is the basis of this study, we cross-matched TIC8 \citep{2018AJ....156..102S}
-against the Gaia DR2 point-source catalog \citep{2018A&A...616A...1G}.
-We opted for Gaia DR2 rather than DR3 because the base catalog for
-TIC8 was Gaia DR2, which facilitated a one-to-one crossmatch using the
-Gaia source identifiers.  This exercise showed that for $T$$<$16
-M-dwarfs, the TESS 2-minute data are roughly 50\% complete at
-$\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\% of the $T$$<$16 M-dwarfs
-have at least one sector of short-cadence data; at $>$100\,pc,
-$\lesssim$10\% of such M-dwarfs have at least one sector of
-short-cadence data.  Armed with this understanding, we then used our
-cross-match between Gaia DR2 and TIC8 to select our stars of interest,
-which we defined as stars with 120-second cadence TESS light curves
-that satisfied
+that is the basis of this study, we cross-matched TIC8
+\citep{2018AJ....156..102S} against the Gaia DR2 point-source catalog
+\citep{2018A&A...616A...1G}.  We opted for Gaia DR2 rather than DR3
+because the base catalog for TIC8 was Gaia DR2, which facilitated a
+one-to-one crossmatch using the Gaia source identifiers.  This
+exercise showed that for $T$$<$16 M-dwarfs, the TESS 2-minute data are
+roughly 50\% complete at $\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\%
+of the $T$$<$16 M-dwarfs have at least one sector of short-cadence
+data; at $>$100\,pc, $\lesssim$10\% of such M-dwarfs have at least one
+sector of short-cadence data.  Armed with this understanding, we then
+used our cross-match between Gaia DR2 and TIC8 to select our stars of
+interest, which we defined as stars with 120-second cadence TESS light
+curves that satisfied
 \begin{align}
@@
 function includes dwarf stars later than spectral types of
-$\approx$K6V \citep{2013ApJS..208....9P}.  The target sample therefore
-includes \nstarssearched\ M-dwarfs and late-K dwarfs,
-down to $T$$<$16 and out to $d$$<$150\,pc.
+$\approx$K6V \citep{2013ApJS..208....9P} for which TESS can acquire
+1\% relative precision photometry in 1 hour of observation
+\citep{2015JATIS...1a4003R}.  The target sample therefore includes
+\nstarssearched\ M-dwarfs and late-K dwarfs, down to $T$$<$16 and out
+to $d$$<$150\,pc.
 
@@
 expectations for CQVs by assembling the data shown in
-Appendix~\ref{app:vetting}.
-We labelled a star as a ``good'' CQV if at least one TESS sector
-showed what we viewed as the unambiguous signatures of the class (short
-period; at least three dips or else otherwise oddly-shaped dips;
-relative stability over a timescale of 30\,days).
-We also noted stars that we thought could be CQVs, but that were more
-ambiguous with a ``maybe'' flag.
+Appendix~\ref{app:vetting}.  We labelled a star as a ``good'' CQV if
+at least one TESS sector showed what we viewed as the unambiguous
+signatures of the class (short period; at least three dips or else
+otherwise oddly-shaped dips; relative stability over a timescale of
+30\,days).  We also noted stars that we thought could be CQVs, but
+that were more ambiguous with a ``maybe'' flag.
 
@@
 Table~\ref{tab:thetable} lists the \ncpvsfound\ CQVs identified by our
-search, along important physical and observational properties.
+search, along with important physical and observational properties.
 \ngoods\ objects demonstrated what we viewed as unambiguous
-characteristics of the CQV phenomenon in at least one TESS sector;
-we refer to these as the ``gold sample''.  We found the remaining \nmaybes\ CQV
-candidates to be ambiguous; their variability might
-be caused by say, multiple starspot groups.  Additional data from TESS
-or other instruments could help resolve their classification.  In the
+characteristics of the CQV phenomenon in at least one TESS sector; we
+refer to these as the ``gold sample''.  We found the remaining
+\nmaybes\ CQV candidates to be ambiguous; their variability might be
+caused by say, multiple starspot groups.  Additional data from TESS or
+other instruments could help resolve their classification.  In the
 following discussion, we will primarily restrict our discussion to the
@@
 ``maybe'' pile.
+Possible evolutionary connections between CQVs and dippers are
+highlighted in Section~\ref{subsec:discdippers}.
 
@@
 
-Comparing these results against the backdrop of our increasing
-understanding of dippers
-\citep[e.g.][]{2014AJ....147...82C,2016ApJ...816...69A,2021ApJ...908...16R,2022ApJS..263...14C},
-it is clear that the loss of an infrared excess is associated with
-strong changes in a star's optical variability.  It is reasonable to
-imagine connections between CQVs and dippers: both classes of object
-can show transient flux dips that are relatively narrow in duration.
-Such dips are probably caused by clumps of dust.  However the CQV dips
-are typically {\it i)} more periodic and {\it ii)} less deep than
-those of dippers, and {\it iii}) they display far less transience over
-timescales of a few to tens of cycles.  This is probably because CQV
-stars have demonstrably less dust than dipper stars.  At a population
-level, the CQV stars are also older.  A common mystery between the
-CQVs and dippers, in our own estimation, is how exactly the {\it
-narrowness} of the dust clumps is produced.  It is not unreasonable to
-imagine a similar mechanism operating for both types of object, tied
-perhaps to a shared magnetic topology, or perhaps to a preference for
-dust to inspiral to the star in clumped structures.
-
 \section{CQV evolution}
+\label{sec:evoln}
 
@@
 labelled an eclipsing binary---in fact, \citet{2021ApJ...912..123J}
-implicitly have already given this source such a label!  Based on the
-the shape evolution between Sectors 13 and 39 however, it is a CQV.
+implicitly have already given this source such a label.  However, based on the
+the shape evolution between Sectors 13 and 39, it is a CQV.
 One could easily also imagine in cases like TIC~206544316 that if
@@
 		\centering
-		\includegraphics[width=\textwidth]{TIC_402980664_P18.5611_2min_phase_timegroups_mosaic_ymin-4.8_ymax3.pdf}
+		\includegraphics[width=\textwidth]{f5.pdf}
 		\vspace{-0.45cm}
@@
 about a quarter of a period, punctuated by coherent local minima and
-maxima which in detail (Appendix~\ref{fig:app:lp}) have slightly
+maxima which in detail (Appendix~\ref{app:lp}) have slightly
 longer periods than the sharp dip.  The sharp leading dip only
@@
 
-{\sc Dips grow more slowly than they disappear}---Although there are a
+{\sc Slow growth; rapid death}---Although there are a
 few instances in which we observe dips ``switch off'' over less
@@
 The closest CQV in our catalog is DG~CVn (TIC~368129164;
-$d$$=$18\,pc), which is a likely member of AB Dor.  To our knowledge,
+$d$$=$18\,pc), a member of AB Dor.  To our knowledge,
 this manuscript is the first time that it has been noted as a CQV.
-The three brightest CQVs we have found are DG~CVn ($T$=9.3),
+The three brightest CQVs are DG~CVn ($T$=9.3),
 TIC~405754448 ($T$=9.6), and TIC~167664935 ($T$=10.3).
-
 The shortest period belongs to TIC~201789285, at 3.64\,hr.
 The longest period belongs to TIC~405910546, at 37.9\,hr.  If
-that source turns out to be an eclipsing binary, then the next-longest
+the latter source turns out to be an eclipsing binary, the next-longest
 would be TIC~193831684 (31.0\,hr).
@@
 The lowest mass ($\approx 0.12$\,M$_\odot$) belongs to TIC~267953787.
-The catalog contains a few other stars with similar mass, which
-suggests the phenomenon may extend into the brown dwarf regime.
-
-The most massive CQV in our sample is a subject of some interest
-because to date, the only stars reported to show the CQV phenomenon
+The catalog contains a few other stars with similar mass.
+Given the small number of sub-stellar mass objects in our target sample,
+this suggests that future studies of brown dwarf
+photometric variability might also yield complex quasiperiodic
+variables, though there would be degeneracies in interpretation with planetary surface features such
+as clouds and latitudinal bands \citep[e.g.][]{2021ApJ...906...64A,2022ApJ...924...68V}.
+
+The most massive CQV in our sample is a subject of some interest.
+To date, the only stars reported to show the CQV phenomenon
 are M-dwarfs, with typical stellar masses $\lesssim$0.3\,M$_\odot$
@@
 of the CQVs in Figure~\ref{fig:cqvs}, in that it has some of the
-lowest amplitude dips.  However overall, both of these objects seem to
+lowest amplitude dips.  Nonetheless, both of these objects seem to
 suggest that the CQV phenomenon extends up in mass to
@@
 \subsection{CQVs are quasiperiodic}
-A periodic signal repeats exactly; the CQVs do not, although their
-periods appear to be fixed to within measurement precision over
-thousands of cycles.  They are therefore {\it quasi}periodic.  While
-this point has been suggested in studies by
-\citet{2022AJ....163..144G} and \citet{2023ApJ...945..114P},
-Figure~\ref{fig:evoln} drives it home.  This is a qualitative
+A periodic signal repeats exactly; the CQVs do not (Figure~\ref{fig:evoln}).
+Their periods
+however do appear to be constant to within measurement precision over
+thousands of cycles.  They are therefore {\it quasi}periodic.  
+This point with previous studies by
+\citet{2022AJ....163..144G} and \citet{2023ApJ...945..114P}.
+However it marks a qualitative
 departure from the ``persistent'' {\it vs.} ``transient'' flux dip
@@
 able to explore all phase angles with equal weight.  LP 12-502, and
-many other CQVs, might have preferred phases.  For LP 12-502, all of
+multiple other CQVs, seem to have preferred phases.  For LP 12-502, all of
 the dips happen over phases corresponding to only two thirds of the
-period.  The other third seems to be ``out of limits'' for any dipping
-material.  This could be evidence either {\it a)} that some aspect the
+period (Figure~\ref{fig:lp}).  The remaining third seems to be ``out of limits'' for any dipping
+material.  This could be evidence that some aspect the
 stellar magnetic field is strongly asymmetric, and can generate and
 hold extrinsic material at corotation, but only over two thirds of the
-equatorial circle, or {\it b)} that there is a material -- for
-instance a disintegrating planetesimal swarm -- that is distributed
-over an arc of the same angular extent (240$^\circ$).  We favor the
+equatorial circle.  Alternatively, the source of the material (e.g. a planetesimal
+swarm) might be distributed over an arc of the same angular extent (240$^\circ$).
+We favor the
 former explanation, for reasons discussed below.
@@
 \citep[e.g.][]{2019A&A...625L..13Z}.
-The main quantities of interest in such models would likely be 
+The main quantities of interest in such models would be 
 the exponential decay time- and therefore length-scale,
@@
 
-\subsection{On the prominence scenario}
-
-In our view, the ``prominence'' scenario
-\citep{2017AJ....153..152S,2022MNRAS.514.5465W}, in which quiescent
-prominences analogous to those observed on the Sun become trapped in
-co-rotation may be the next-best contending model, after the idea of
-dust clumps doing the same thing.  The prominence idea historically
-came from spectroscopic detections of transient Balmer- and
+\subsection{Dust, or gas?}
+
+We believe that the most likely scenarios to explain the overall CQV phenomenology
+are the dust clump scenario, or the
+prominence scenario (Figure~\ref{fig:f1}).
+Both invoke clumpy material that would be centrifugally supported at the corotation radius.
+The prominence idea has a deeper history,
+based first on analogy with quiescent prominences/filaments
+observed to remain stable in the solar corona for up to a few weeks.
+In an extrasolar context,
+spectroscopic detections of transient Balmer- and
 resonance-line absorption seen for stars such as AB~Dor and
-Speedy~Mic \citep[see
-e.g.][]{1989MNRAS.238..657C,1993MNRAS.262..369J,2019MNRAS.482.2853J}.
-Neutral hydrogen clouds scatter chromospheric emission from the star,
-producing the observed spectroscopic line variations.  The
-interpretation of those observations seems, in our view, secure.
-
+Speedy~Mic \citep[e.g.][]{1989MNRAS.238..657C,1993MNRAS.262..369J,2006MNRAS.365..530D,2016MNRAS.463..965L}
+led to the interpretation that the data could best be explained by
+cold, minimally ionized hydrogen clouds scattering chromospheric emission from the star,
+producing the observed spectroscopic line variations \citep[see][]{1989MNRAS.238..657C}. 
+The mechanical stability of such gas configurations has been
+demonstrated \citep{2000MNRAS.316..647F,2022MNRAS.514.5465W}, and generally, the interpretation
+of this class of observations seems reasonably secure.
+
+The link between the dense gas clumps (prominences) that 
+likely exist around rapidly rotating low-mass stars,
+and the CQV phenomenon, has yet to be made.
+A simple visual examination of the TESS light curves for 
+five prominence-hosting systems
+studied by \citet{2019MNRAS.482.2853J}--AB~Dor, Speedy~Mic, LQ Lup, HK Aqr, and V374 Peg--revealed
+no obvious CQV behavior, though all likely show
+differential rotation, and
+Speedy~Mic shows two closely-spaced periods and
+a strong beat.
+Spectroscopically observable prominences therefore do not imply CQV-like dips.
+
+%TODO: improve this to make it less jargony
 The difference between the prominence and dust clump scenarios
@@
 The magnetic field strength is only relevant in this formulation of
-the system in that we must have $R_{\rm sonic} < R_{\rm cr} < R_{Alfven}$ in order for 
-closed loops to exist that can support prominences (CITE
-Jardine/CollierCameron2019).
+the system in that we must have $R_{\rm sonic} < R_{\rm cr} < R_{\rm Alfven}$ in order for 
+closed loops to exist that can support prominences 
+\citep{2019MNRAS.482.2853J} {\bf lgb todo: verify!}.
 In detail however, whether such magnetic fixed points lie in the equatorial
@@
 \subsubsection{Can gas absorption reproduce the observed chromaticity?}
-In our view, the strongest argument for why neutral hydrogen is ruled
-out as the occulting source is that we are seeing broadband flux
+The strongest argument for why neutral hydrogen is an unlikely
+occulting source is that CQVs show broadband flux
 variations that are deeper in the blue than in the red.
@@
 Based on our reading of \citet[][Ch.~8]{1992oasp.book.....G},
-it is somewhat challenging to get neutral hydrogen to have this type of chromaticity.
+it seems somewhat challenging to get neutral hydrogen to have this type of chromaticity.
 Bound-bound absorption provides opacity only at narrow resonant lines.
@@
 than {\it shrink} as one needs in order to get deeper absorption in
-the blue than in the red.  H$^-$ similarly fails as a viable opacity
+the blue than in the red.  H$^-$  fails as a viable opacity
 source for the same reason: its absorption coefficient peaks near
-8500\,$\AA$, and is an order of magnitude smaller at $\approx$3000\,AA
-\citep{1992oasp.book.....G}, following CITE Wishart 1979.
+8500\,\AA, and is an order of magnitude smaller at $\approx$3000\AA.
+\citep{1992oasp.book.....G}, following \citet{1979MNRAS.187P..59W}.
 Thompson scattering is also ruled out, because it is gray.
 Dust, with its relatively featureless but increasing extinction curve
-when going bluer into the optical, is to our knowledge the most
+when going bluer into the optical \citep{1989ApJ...345..245C}, is to our knowledge the most
 obvious opacity source.
@@
 While the above line of reasoning seems fairly convincing,
-one flaw that we can point out in it is tied to $\sigma$~Ori~E.
-The logic presented above argues essentially that regardless of a star's temperature,
-if relative depths of dips are seen to be deeper in the blue than in the red,
+it has a flaw.
+The logic presented above would imply that regardless of a star's temperature,
+if relative depths of a dip are seen to be deeper in the blue than in the red,
 then it is hard to get hydrogen to do it.
-$\sigma$~Ori~E shows dips that are deeper in the blue than in the red \citep{1977ApJ...216L..31H},
-which have been understood in terms of absorbing circumstellar material
-\citep{2005ApJ...630L..81T}.
+There is however a rapidly rotating 
+magnetic B-star, $\sigma$~Ori~E, which shows dips that are deeper in the blue than in the red
+\citep{1977ApJ...216L..31H}.
+Photometric and spectroscopic observations of this star have been understood in terms of
+absorbing circumstellar material, quite analogous to the geometries we are
+discussing for much cooler M-dwarfs \citep{2005ApJ...630L..81T}.
 This material however cannot be dust, due to the relevant sublimation timescales.
 It is instead thought to be sourced from bound-free absorption from neutral hydrogen
-\citep{2005ApJ...630L..81T}.  Given these complexities, it clearly
+\citep{2005ApJ...630L..81T}.  Separate and smaller amplitude
+emission in that system may also 
+come from electrons scattering photospheric light toward the observer 
+when the clouds are not in transit \citep{2022MNRAS.511.4815B}.
+
+Given these complexities, it clearly
 seems important for a future theoretical study to be conducted to
-determine to what degree the observed chromaticities match, or do not
-match, with expectations from radiative transfer.
+determine to what degree the observed chromaticities in CQVs match, or do not
+match, expectations from radiative transfer.
 This issue has a key ability to resolve the question of whether the
 CQVs are caused by dust, or by gas.
-
-\subsubsection{Does the timescale for CQVs to live inform the mechanism?}
-Independent of the theoretical basis for gas absorption, the
+This question has direct bearing on the potential utility of these
+objects.
+
+\subsubsection{Does the CQV lifetime inform the mechanism?}
+Independent of the microphysical basis for gas absorption, the
 prominence scenario may present another issue: why don't stars in the
 Hyades and Praesepe show the phenomenon?
-in a broad sense, the prominence scenario argues that an intrinsic
+In a broad sense, the prominence scenario argues that an intrinsic
 stellar process is key for generating the CQV phenomenon.
 If this were true, then stars of identical mass, size, and rotation
-periods might be expected to show the phenomenon in equal number --
-irrespective of age.
-This is because the stellar dynamo is generated by fluid
+periods might be expected to show the phenomenon in equal number,
+simply because the stellar dynamo is generated by fluid
 motions inside the star, which should be identical for stars of the
@@
 shrink by $\approx$10\%, from $\approx$0.33\,R$_\odot$ to 
-$\approx$0.29\,R$_\odot$ (CITE MIST).
+$\approx$0.29\,R$_\odot$ \citep[e.g.][]{2014AJ....147...82C}.
 This is not a particularly drastic size change.
-Similarly, many M-dwarfs  have similarly rapid rotation periods 
-at 700\,Myr as they do at 100\,Myr (CITE Rebull2022); 
-the mean population does show some evidence for spin-down after the
-PMS contraction finishes, but a large fraction of the population is
-still spinning more rapidly than the $\approx$2\,day limit at which
-the CQV phenomenon becomes less common.
-
-Broadly speaking -- the absence of old CQVs in our view seems to be
+Similarly, at 700\,Myr many M-dwarfs have comparably rapid rotation periods 
+to those at 100\,Myr \citep[e.g. Figure~13 of][]{2022AJ....164...80R};
+the mean population does show evidence for spin-down after the
+PMS contraction finishes, but there are still a large number of 
+700\,Myr M-dwarfs with $P_{\rm rot}\lesssim$2\,days, beyond
+which the CQV phenomenon becomes less common.
+
+Broadly speaking -- the absence of old CQVs seems to be
 more plausibly linked to a gradual depletion of dusty detritus from the
 planet formation era than it does to the changing stellar properties
-as stars gradually finish their pre-main-sequence evolution, and then
+as the stars gradually finish their pre-main-sequence evolution, and then
 continue to spin rapidly for many hundreds of millions of years.
-
-The long-lived prominences inferred from the decades-old spectroscopic
-data, and dust-clouds inferred from K2+TESS, could of course also be
-pieces of a complementary picture.
 
@@
 planets per star, for planets with 1-4\,$R_\oplus$ and $P$$<$10\,days.
-Extrapolating to {\it small} close-in planets, from say
+Extrapolating to all small close-in planets, from say
 0.1-4\,$R_\oplus$ and within 10 days, it is reasonable to expect on
 average one planet per M-dwarf.  TRAPPIST-1b ($P$=1.5\,days) is one
-example of this type of planet (CITE) orbits a 0.08\,M$_\odot$ star.
-
-Within the context of planet formation theory, the locations of these
+example of this type of planet, in orbit around a 0.08\,M$_\odot$ star  \citep{2017Natur.542..456G}.
+
+In the context of planet formation theory, the locations of these
 close-in planets are set by the location of the protoplanetary disk's
@@
 simple 1-D viscous accretion models, this truncation radius roughly
-coincides with the Keplerian corotation radius (CITE), though in
+coincides with the corotation radius (CITE), though in
 detail factors of a few difference have been observed between the two
-(CITE IR studies).  With models that have migrating compact
+(CITE IR studies).  Within models that have migrating compact
 multiplanet resonant chains, the inner-most planets arrive within
-$\approx$5-10 stellar radii within the first 100\,Myr (e.g.  CITE
-IZIDORO),
-
-It is of course very tempting to attempt to interpret features of the
+$\approx$5-10 stellar radii within the first 100\,Myr \citep{2018haex.bookE.142I}.
+
+It is very tempting to try to interpret features of the
 CQV light curves in terms of the possible presence of close-in
-exoplanets, or even planetesimals.  For instance, rocky planets this
-young would have molten global magma oceans analogous to those that
-existed on the Earth and Moon (e.g. CITE LICHTENBERG REVIEW), and thus
-would undergo significant outgassing and atmospheric escape.  A
+exoplanets, or even planetesimals.  Rocky planets this
+young would likely have molten global magma oceans analogous to those that
+existed on the Earth and Moon \citep[see][]{2022arXiv220310023L}, and thus
+would being undergoing significant outgassing and atmospheric escape.  A
 scenario in which close-in rocky planets serve as a possible source of
-dust for the clouds is not entirely implausible, though it remains a
-subject of speculation.
+dust for the clouds is not entirely implausible, {\it a priori}.
+%Frankly though, it remains a subject of speculation.
 
 Given the dip depth variations that are observed in systems like LP
-12-502, one would be driven in this framework toward a picture of a
-disintegrating planetesimal swarm.  The dip-profile asymmetries during
+12-502, one might be driven in this framework toward a picture of a
+disintegrating planetesimal swarm.  
+The sizes of the planetesimals would need to be $\lesssim 1$\,$R_\oplus$,
+based on the non-detections of their transits, analogous to e.g. 
+K2-22 \citep{2015ApJ...812..112S} or KOI-2700 \citep{2014ApJ...784...40R}.
+The dip-profile asymmetries during
 certain segments of the light curve plausibly match this idea; for
@@
 
-Ultimately though, there are two glaring issues with the
-disintegrating planetesimal swarm idea.  First, a large number of the
+Ultimately, there are a few problems for the idea of a
+disintegrating planetesimal.
+First, a large number of the
 dips show asymmetries in the {\it wrong direction} relative to the
-naive expectation of a trailing comet tail.  Dust forward scattering
-might be one possible way out; so too might invoking non-exponentially
-decaying dust distributions as a function of azimuth.  Second, and
-more serious, the (unseen) planets or planetesimals should be on {\it
+naive expectation of a trailing comet tail.  Invoking non-exponentially
+decaying dust distributions as a function of azimuth might be one way out of this,
+but such an idea would need stronger theoretical footing.
+More important is that the (unseen) planets or planetesimals should be on {\it
 exactly periodic} orbits over observable timescales, on the
 presumption that the planetesimals would be massive enough to not feel
-any headwind or magnetic field.  This is not what is observed.  The
-fact that dips in sources such as LP 12-502 appear and disappear at
-{\it distinct phases} but with the same period seems to be a major
-challenge to tying the entire phenomenon to a single launching body.
-Similarly, the fact that the dips often respond to events like flares
+any headwind or magnetic field.  For most CQVs, this is inconsistent with the data;
+dips in sources such as LP 12-502 appear and disappear at
+{\it distinct phases}, but with the same period.
+It seems challenging to reconcile this behavior
+with the possible presence of just a single launching body.
+Finally, the fact that the dips often respond to events like flares
 suggests that that the responsible material be much less massive than
@@
 by the stellar magnetic field.
+
+It is certainly possible that exoplanets could end up being connected to the
+CQV phenomenon,
+for instance as a possible source of dust through collisions at greater separations
+from the star.
+However for the time being, none of the CQVs that we have studied in this
+work seem to show clear evidence for an exoplanetary origin.
 
@@
 \subsection{From dippers to debris disks}
-The concordance model for planet formation invokes the presence of an
-accretion disk.  The disk is truncated (by what?) at the
-magnetospheric truncation radius, which happens to often
-coincidentally be at the Keplerian corotation radius.  In such a
-scenario, planetesimals and boulders can migrate inward due to Type X
-migration (CITE), until they hit a ``dust trap'' at the inner wall
-(CITE eg Kama2009,and related).  Support for this model comes from the
-rotation periods of classical and weak-lined T Tauri stars (CITE
-Rebull2018,2019); from near-infrared interferometric observations that
-detect thermal emission from the disk wall (CITE CITE); and from the
-turn-over in the exoplanet orbital period distribution, which occurs
-around 5-10 days for FGK stars, and perhaps even closer-in for
-M-dwarfs (CITE Petigura2022, and CITE for M-dwarfs).
-
-Broadly, the existence of a dust trap at the disk truncation radius
-might be expected to trap larger boulders as well.  Once the disk
-loses the gas, what happens to those boulders?  They are no longer
-shielded.  We then enter a phase of mass loss.  Perhaps that phase is
-what we are observing.
-
-% \paragraph{Interpretation of the $T\lesssim 15$ dropoff}
-% Our search sample included 35472 unique stars with $12<T<14$, versus
-% 2045 unique stars with $15<T<16$.  This helps clarify why our detected
-% CPVs become less common toward fainter TESS magnitudes, despite the
-% relative ease of their detectability, even at $15<T<16$.  It is
-% because the TESS 2-minute data are very incomplete at the faint end.
+\label{subsec:discdippers}
+
+It is amusing that for the two candidate CQV sources identified in
+Section~\ref{subsec:irexcess} as having outlying SEDs (TICs~193136669
+and TIC~57830249), the identification of the infrared excess is part
+of what prompted our eventual labelling of these sources as dippers.
+It is also worth emphasizing that our labelling of e.g.~TIC~57830249
+was based on a single sector of TESS data (Sector~36), when its
+behavior is relatively periodic, with dip depths of a few percent.
+However in other TESS sectors (e.g. Sector~10), this source looks
+completely different, varying in apparent flux by a factor of two,
+which hardly any discernable periodicity at all.
+
+Comparing these results against the backdrop of our increasing
+understanding of dippers
+\citep[e.g.][]{2014AJ....147...82C,2016ApJ...816...69A,2021ApJ...908...16R,2022ApJS..263...14C},
+it is clear that the loss of an infrared excess is associated with
+strong changes in a star's optical variability.  It is reasonable to
+imagine connections between CQVs and dippers: both classes of object
+can show transient flux dips that are relatively narrow in duration.
+Such dips in both are probably associated with clumps of dust or gas.
+However the CQV dips are typically {\it i)} more periodic and {\it
+ii)} less deep than those of dippers, and {\it iii}) they display far
+less transience over timescales of a few to tens of cycles.  This is
+probably because CQV stars have demonstrably less dust than (most)
+dipper stars.  At a population level, the CQV stars are also older.  A
+common mystery between the CQVs and dippers, in our own estimation, is
+how exactly the {\it narrowness} of the dust clumps is produced.  It
+is not unreasonable to imagine a similar mechanism operating for both
+types of object, tied perhaps to a shared magnetic topology, or
+perhaps to a preference for dust to inspiral to the star in clumped
+structures.
+
+%The concordance model for planet formation invokes the presence of an
+%accretion disk.  The innermost regions of the disk are located at the
+%magnetospheric truncation radius, which happens to often
+%coincidentally be at the Keplerian corotation radius ({\bf lgb: careful...}).  In such a
+%scenario, planetesimals and boulders can migrate inward due to Type X
+%migration (CITE), until they hit a ``dust trap'' at the inner wall
+%(CITE eg Kama2009,and related).  Support for this model comes from the
+%rotation periods of classical and weak-lined T Tauri stars (CITE
+%Rebull2018,2019); from near-infrared interferometric observations that
+%detect thermal emission from the disk wall (CITE CITE); and from the
+%turn-over in the exoplanet orbital period distribution, which occurs
+%around 5-10 days for FGK stars, and perhaps even closer-in for
+%M-dwarfs (CITE Petigura2022, and CITE for M-dwarfs).
+%
+%Broadly, the existence of a dust trap at the disk truncation radius
+%might be expected to trap larger boulders as well.  Once the disk
+%loses the gas, what happens to those boulders?  They are no longer
+%shielded.  We then enter a phase of mass loss.  Perhaps that phase is
+%what we are observing.
+
+\subsection{The importance of half-cycles}
+
+The interval of half a cycle period could be significant in the
+context of CQVs for two reasons.  The first is that for material on a
+circular orbit viewed edge-on, it corresponds to the interval between
+transit and secondary eclipse.  The second is that it also corresponds
+to the interval over which half of the star's surface is visible.
+Of the CQVs in Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, a number
+that seems greater than random seem to exhibit a preference for
+showing dips or peaks that correspond to the half-cycle interval.
+
+One set of CQVs shows ``CQV behavior'' (some form of dip complex), but
+which only lasts for half of any given cycle.
+TIC~206544316 (Sector 2) is a canonical example;
+TIC~405910546 (Sector 38), TIC~167664935 (Sector 38), TIC~146539195
+(Sector 5), TIC~118449916 (Sector 44), and TIC~312410638 (Sector 38)
+seem to show essentially the same tendency.
+
+An independent set of CQVs exhibits small dips roughly half a cycle
+after large dips; it is tempting to label the small dips secondary
+eclipses.
+Such sources include 
+TIC~402980664 (Sector 25; relative to the sharpest, deepest minimum),
+TIC~89463560 (Sector 36),
+TIC~224283342 (Sector 2), and TIC~442571495 (Sector 12).
+
+It is challenging to interpret the significance of such apparent
+regularities;  the objects exhibit such a wide range of variability
+that for seemingly any ``regularity'' one might posit, it is easy to
+come up with counter-example objects which do not follow the trend.
+In other words, these half-cycle CQVs could simply be a
+product of the human tendency to pattern match; alternatively, they
+might yield some important physical signifiance.
+
+\subsection{Mass flux estimate}
+
+It is possible to estimate the mass of a transiting cloud by
+converting the transit depth to an effective cloud radius, $R_{\rm
+cloud}$.  For most CQVs in Figure~\ref{fig:cqvs}, this yields roughly
+1-10\,$R_\oplus$.  This size can be converted into a mass estimate by
+requiring the optical depth $\tau$ of the cloud to be at least unity.
+In other words, a minimum constraint on the dust number density
+follows by requiring the cloud to be optically thick.  For cases like
+LP 12-502, this is resonable because the transit duration implies
+$R_{\rm cloud}\ll R_\star$.  Carrying out the relevant calculation
+assuming sizes for the dust grains of 1\,$\mu$m,
+\citet{2023MNRAS.518.4734S} find minimum cloud masses of order
+$10^{12}$\,kg (their Eq.~23), which scale linearly with both the
+optical depth and dust grain radius.  This is roughly comparable to a
+small asteroid; the asteroid belt itself has a mass of
+$\approx$2$\times$10$^{21}$\,kg (CITE).  Also by way of comparison,
+the previously-discussed cool gas prominences for AB~Dor would need to
+have masses of order $10^{14}$\,kg \citep{1990MNRAS.247..415C}, about
+100$\times$ larger than the requisite dust mass.
+
+Our observations provide a direct measurement of how often dips
+``appear'' or ``disappear'', both due to sudden state-switches, and
+due to more gradual, secular evolution.  For instance, LP~12-502
+showed 3 ``state-switch'' events over the six months of available TESS
+observations, during cycles 248-264, 299-315, and 1233-1247.  It is
+plausible to imagine that these events correspond to either mass being
+ejected from corotation, or perhaps being accreted onto the star.  In
+any event, the corresponding $\dot{M} \equiv M\cdot {\rm d}N/{\rm d}t$
+is $\approx$3$\times$$10^{-18} M_\odot\,{\rm yr}^{-1} \approx
+1\times10^{-12} M_\oplus\,{\rm yr}^{-1}$.  Considered cumulatively
+over the $\approx$$10^8$ years for which the CQV phenomenon is
+observed, this yields a cumulative moved dust mass of
+$10^{-4}\,M_\oplus$, which of order the Solar System's asteroid belt.
+If the occulting material is gas, the masses involved would be of
+order 100 times larger.
 
@@
 
-In this work, we analyzed TESS
-120-second cadence data 
-collected between July~2018
-and Sep~2022, and searched it for complex quasiperiodic variables (CQVs).
-Our search sample included
-\nstarssearched\ K- and M-dwarfs within 150\,pc,
-and is $\gtrsim 80\%$ complete within 30\,pc, and $\lesssim 10\%$ complete
-at distances exceeding 100\,pc.
+In this work, we analyzed TESS 120-second cadence data collected
+between July~2018 and Sep~2022, and searched it for complex
+quasiperiodic variables (CQVs).  Our search sample included
+\nstarssearched\ K- and M-dwarfs within 150\,pc, and was $\gtrsim
+80\%$ complete within 30\,pc, and $\lesssim 10\%$ complete at
+distances exceeding 100\,pc.
 
 In this sample of stars, we found \ngoods\ objects that showed complex
-quasiperiodic behavior over at least one observed TESS sector.  
-These \ngoods\ bonafide CQVs are listed in Table~\ref{tab:thetable}.
-This table also includes an additional \nmaybes\ candidate CQVs, whose
-designation is less certain.
-Analyzing the light curves of these objects, we draw the following conclusions.
+quasiperiodic behavior over at least one TESS sector.  Because the
+TESS 120-second stellar sample was rooted in a heterogeneous selection
+function that may have been biased in favor of young stars over field
+stars, we caution against interpreting our detection statistics in
+terms of broader population occurrence rates.  The \ngoods\ bonafide
+CQVs are listed in Table~\ref{tab:thetable}.  This table also includes
+an additional \nmaybes\ candidate CQVs, whose designation is less
+certain.
+
+Analyzing the CQV light curves, we draw the following conclusions.
 
@@
 	%
-  \item CQVs are quasiperiodic.  While the mean periods in our
+  \item CQVs are {\it quasi}periodic.  While the mean periods in our
     sample seem to remain fixed over the span of available
@@
     distinct periods.  LP 12-502, for instance, showed dips with four
-    distinct periods within $\pm 0.3\%$ of the fundamental period,
+    distinct periods within $\pm 0.3\%$ of its fundamental period,
     sometimes simultaneously, and each lasting for up to 50 cycles.
@@
   \item The CQV phenomenon persists for at least 150\,Myr, based on
-    the existence of CQVs in AB Dor, the Pleiades, and Psc-Eri.  It
-    may extend to even older ages, however the lack of detected CQVs
-    in the Hyades and Praesepe suggests that the phenomenon does become
-    less common at older ages.
+    the existence of multiple CQVs in AB Dor, the Pleiades, and
+    Psc-Eri.  It may extend to even older ages, however the lack of
+    detected CQVs in the Hyades and Praesepe suggests that the
+    phenomenon does become less common at older ages.
 	%
@@
     exclusively) linked with observed optical flares.  Dip growth
-    however seems to happen over durations of at least ten cycles.
+    however seems to happen over durations of at least ten cycles, and
+    slow dip decay also happens.
 	%
-  \item The population-averaged duty cycle for CQVs seems to be
-    $\approx 75$\%, based on the fraction of bonafide CQVs that
-    ``turned off'' during TESS re-observations.
+  \item The duty cycle for CQVs seems to be $\approx 75$\%, based on
+    the fraction of bonafide CQVs that turned on or turned off during
+    TESS re-observations, two years after their initial observation.
+  %
 \end{itemize}
 
-Many questions remain.  After correcting for line-of-sight
-inclination, are most young M-dwarfs CQVs?  What observational
+Many questions remain.  
+Is the eclipsing material responsible for the phenomenon gas, or dust?
+After correcting for line-of-sight inclination, do most 
+M-dwarfs go through a phase of trapping material a few stellar radii away
+from their surfaces?  
+What observational
 signatures distinguish the proposed models (Figure~\ref{fig:f1},
@@
 12-502, or perhaps some other suitable object, using JWST/MIRI.
+{\bf final paragraph(s) clearly need improvement}
 
@@
 This work was supported by the 
-Heising-Simons 51~Pegasi~b Fellowship (LGB)
+Heising-Simons 51~Pegasi~b Fellowship (LGB).
 TIC 402980664 was observed at 120-second cadence thanks to the TESS Guest
@@
 
-%{\bf author contribution statement goes here}
+{\bf DRAFT AUTHOR CONTRIBUTION STATEMENTS -- PLEASE REVISE IF 
+	APPROPRIATE)}
 LGB~and RJ conceived the project and executed the
@@
 pipeline.
+GRR is an architect of the TESS mission, and advised RJ on his contributions.
 All authors assisted in manuscript revision.
@@
  	{\it Astrometry}:
-		Gaia \citep{2018A&A...616A...1G,2018A&A...616A...1G}.
+		Gaia \citep{2018A&A...616A...1G,2022arXiv220800211G}.
  	{\it Imaging}:
@@
 		%VLT:Kueyen~(FLAMES; \citealt{pasquini_2002}).
-% 	Euler1.2m~(CORALIE),
-% 	ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
+ 	  %Euler1.2m~(CORALIE),
+ 	  %ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
  	{\it Photometry}:
-%	  ASTEP:0.40$\,$m (ASTEP400),
-% 	CTIO:1.0m (Y4KCam),
-% 	Danish 1.54m Telescope,
-%	  El Sauce:0.356$\,$m,
-% 	Elizabeth 1.0m at SAAO,
-% 	Euler1.2m (EulerCam),
-%	  Kepler,
-% 	Magellan:Baade (MagIC),
-% 	Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
-%   MuSCAT3 \citep{Narita_2020},
-% 	NTT,
-% 	SOAR (SOI),
+		%ASTEP:0.40$\,$m (ASTEP400),
+		%CTIO:1.0m (Y4KCam),
+		%Danish 1.54m Telescope,
+		%El Sauce:0.356$\,$m,
+		%Elizabeth 1.0m at SAAO,
+		%Euler1.2m (EulerCam),
+		%Kepler,
+		%Magellan:Baade (MagIC),
+		%Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
+		%MuSCAT3 \citep{Narita_2020},
+		%NTT,
+		%SOAR (SOI),
  	  TESS \citep{2015JATIS...1a4003R},
-% 	TRAPPIST \citep{jehin_trappist_2011},
-% 	VLT:Antu (FORS2).
-%    ZTF.
+		%TRAPPIST \citep{jehin_trappist_2011},
+		%VLT:Antu (FORS2).
+		%ZTF.
   {\it Broadband photometry}:
-    2MASS (CITE).
-    APASS (CITE).
-		Gaia \citep{2018A&A...616A...1G,2018A&A...616A...1G}.
-    Pan-STARRS1 (CITE).
-    SDSS (CITE).
-    AllWISE (CITE).
+    2MASS \citep{2006AJ....131.1163S},
+    APASS \citep{2016yCat.2336....0H},
+		Gaia \citep{2018A&A...616A...1G,2018A&A...616A...1G},
+    SDSS \citep{2000AJ....120.1579Y},
+    WISE \citep{2010AJ....140.1868W}.
 }
@@
     \centering
-    \includegraphics[width=0.96\textwidth]{402980664_S0018_120sec_cpvvetter.pdf}
+    \includegraphics[width=0.96\textwidth]{annotated_402980664_S0018_120sec_cpvvetter.pdf}
 		\vspace{-0.45cm}
 		\caption{
-      {\bf Validation plots used to label CQVs}.  The complete figure
-      set, with one image per sector for each of \ncpvsfound\ objects
+      {\bf Validation plots used to manually label CQVs}.  The complete figure
+      set, with one image per sector for each of \ncpvsfound\ CQVs
+      and candidate CQVs
       is available online {\bf For internal collaboration review:
@@
       {\it k)}: Gaia DR2 color--absolute magnitude diagram.     
+      The gray background denotes stars within 100\,pc.
       {\it l)}: Information from Gaia DR2, TIC8, and the automated
@@
 
-\section{More river plots}
+\section{More neat plots}
+
+Figures~\ref{fig:tic3006river} and~\ref{fig:tic3006timegroups} show 120-second
+cadence data for TIC~300651846, a CQV in the TESS continuous viewing zone.
+With the exception of a few sectors, TESS data will exist for this source
+over Sectors 1-12, 27-39, and 61-69.
+The majority are in the full frame images, and are the subject of future work.
 
@@
 		The envelope has not been subtracted.
-		7 sectors of continuous 2-minute observations.  (Thanks to DDT029)
-	}
-	\label{fig:lpriver0}
+		7 sectors of continuous 2-minute observations S32-S39.  (Thanks to DDT029)
+		Then a few in S60+ on the right.
+		Compare to Figure~\ref{fig:cqvs}.
+	}
+	\label{fig:tic3006river}
+\end{figure*}
+
+\begin{figure*}[!t]
+	\begin{center}
+		\subfloat{
+			\includegraphics[width=0.43\textwidth]{TIC_300651846_P8.254_2min_phase_timegroups.png}
+		}
+	\end{center}
+	\vspace{-0.4cm}
+	\caption{
+		{\bf Orbit-phased plots of TIC 300651846}.
+		The envelope has not been subtracted.
+	}
+	\label{fig:tic3006timegroups}
 \end{figure*}

### 2023-07-02 paper/collect.sh

@@ -13,3 +13,6 @@ cp $resultsdir/beforeafter_mosaic/beforeafter_mosaic_showtitles_tic8_Tmag.pdf f3
 
 # fig4
 cp $resultsdir/tic4029_segments/tic4029_segments.pdf f4.pdf
+
+# fig5
+cp $resultsdir/phase_timegroups_mosaic/TIC_402980664/TIC_402980664_P18.5611_2min_phase_timegroups_mosaic_ymin-4.8_ymax3.pdf f5.pdf

### 2023-07-02 paper/ms.tex
update ms

@@
 
-\subsection{The importance of half-cycles}
+\subsection{Are half-cycles important?}
 
@@
 Of the CQVs in Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, a number
-that seems greater than random seem to exhibit a preference for
+that seems greater than random might exhibit a preference for
 showing dips or peaks that correspond to the half-cycle interval.
@@
 observed, this yields a cumulative moved dust mass of
-$10^{-4}\,M_\oplus$, which of order the Solar System's asteroid belt.
+$10^{-4}\,M_\oplus$, of order the Solar System's asteroid belt.
 If the occulting material is gas, the masses involved would be of

### 2023-07-03 paper/ms.tex
update ms

@@
   pre-main-sequence stars with nearly periodic optical modulation.
-  The modulation is likely induced by dust or gas clumps in orbit at the
-  Keplerian corotation radius.  Here, we report new CQVs discovered in
-  TESS data collected between July~2018 and Sep~2022.
-  Our search of \nstarssearched\ K- and M-dwarfs
-  with $T$$<$16 and $d$$<$150\,pc yielded \ngoods\ gold-standard CQVs.
-  Most of these discoveries are new, and they include the brightest
-  and closest examples of this class of object known ($T$$\approx$9.5;
+  The modulation is likely induced by dust or gas clumps in orbit at
+  the Keplerian corotation radius.  Here, we report new CQVs
+  discovered in TESS data collected between July~2018 and Sep~2022.
+  Our search of \nstarssearched\ K- and M-dwarfs with $T$$<$16 and
+  $d$$<$150\,pc yielded \ngoods\ gold-standard CQVs.  Most of these
+  discoveries are new, and they include the brightest and closest
+  examples of this class of object known ($T$$\approx$9.5;
   $d$$\approx$20\,pc), as well as the most massive
@@
   outliers; LP 12-502 for instance shows a ``dip complex'' with a
-  period and total duration that are fixed over more than 1{,}000 cycles,
-  but which in detail exhibits anywhere from four to eight local minima
-  per cycle.  LP-502 also displayed distinct superposed periods
-	simultaneously, and displayed drastic shape changes shortly after flares.
-	Broadly speaking, we find that none of the CQVs maintain a fixed light curve
-	shape over timescales of more than a few hundred cycles, and we revisit the
-	arguments for why transient corotating material is the most viable explanation.
-	In the future, we expect that our sample will facilitate modeling and
-	observational efforts aimed at understanding these objects, and connecting them
-	to the broader contexts of star, disk, and exoplanet evolution.
-	For instance, if the transiting material is dust, then the rate of dip evolution
-	implies that of order an asteroid belt's worth of mass passes through these
-	structures over the $10^8$ years for which they are observed.
+  period and total duration that are fixed over more than 1{,}000
+  cycles, but which in detail exhibits anywhere from four to eight
+  local minima per cycle.  LP-502 also displayed distinct superposed
+  periods simultaneously, and displayed drastic shape changes shortly
+  after flares.  Broadly speaking, we find that none of the CQVs
+  maintain a fixed light curve shape over timescales of more than a
+  few hundred cycles, and we revisit the arguments for why transient
+  corotating material is the most viable explanation.  In the future,
+  we expect that our sample will facilitate modeling and observational
+  efforts aimed at understanding these objects, and connecting them to
+  the broader contexts of star, disk, and exoplanet evolution.  For
+  instance, if the transiting material is dust, then the rate of dip
+  evolution implies that of order an asteroid belt's worth of mass
+  passes through these structures over the $10^8$ years for which they
+  are observed.
 \end{abstract}
@@
 \citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z}.
-Some CQVs show up to eight local minima (dips) per cycle.  Most 
-are pre-main-sequence M-dwarfs without near-infrared excesses, 
-ages of $\approx$5-150 million years (Myr), and rotation periods of at
-most two days; they are observed to be $\approx$1-3\% of M-dwarfs
-younger than 100 Myr \citep{2016AJ....152..114R,2022AJ....163..144G}.
-The dips can be chromatic, with a reddening law plausibly consistent
-with dust
+Some CQVs show up to eight local minima (dips) per cycle.  Most are
+pre-main-sequence M-dwarfs without near-infrared excesses, ages of
+$\approx$5-150 million years (Myr), and rotation periods of at most
+two days; they are observed to be $\approx$1-3\% of M-dwarfs younger
+than 100 Myr \citep{2016AJ....152..114R,2022AJ....163..144G}.  The
+dips can be chromatic, with a reddening law plausibly consistent with
+dust
 \citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
@@
 \citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  The
-``clump'' scenario invokes opaque dust clumps orbiting near the Keplerian
-corotation radius, which periodically eclipse the star
-\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The
-``prominence'' scenario invokes long-lived condensations of cool and dense
-marginally-ionized gas, embedded within the
-hotter corona, that would be centrifugally supported near corotation
+``clump'' scenario invokes opaque dust clumps orbiting near the
+Keplerian corotation radius, which periodically eclipse the star
+\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The ``prominence''
+scenario invokes long-lived condensations of cool and dense
+marginally-ionized gas, embedded within the hotter corona, that would
+be centrifugally supported near corotation
 \citep{1989MNRAS.238..657C,2019MNRAS.482.2853J,2022MNRAS.514.5465W}.
 Such structures are analogous to quiescent prominences and filaments
-observed on the Sun, though at much larger relative distances from the
-stellar surface.
-A final posibility that has been suggested is one of a ``screen'', in
+observed in the solar corona \citep[see e.g.][]{2015ASSL..415.....V},
+though at much larger relative distances from the stellar surface.  A
+final possibility that has been suggested is one of a ``screen'', in
 which the inner wall of a quiescent circumstellar disk blocks a
@@
 
-In our view, the dust clump and prominence hypotheses seem most
-plausible.  They are qualitatively similar, except one
-invokes opacity from dust, while the other invokes opacity from gas,
-likely bound-free transitions in hydrogen or perhaps a
-molecular opacity.  The screen scenario seems inconsistent with the
-degree of observed periodicity, the lack of infrared excess, and the
-observed lifetime of CQVs extending an order of magnitude longer than
-the $\approx$$10^7$ year timescale typically quoted for the primordial
-disk to disperse.  However, unambiguous evidence 
-has yet to be acquired in support of any scenario.  Such evidence
-might include a spectroscopic detection of silicate 10\,$\mu$m dust
-absorption during a dip, or perhaps detection of transient
-Balmer-line absorption during the dips, similar to observations made in
-systems such as AB~Dor \citep[see the review
+The dust clump and prominence hypotheses seem most plausible.  They
+are qualitatively similar, except that one invokes opacity from dust,
+while the other invokes opacity from gas, likely bound-free
+transitions in hydrogen or perhaps a molecular opacity.  The screen
+scenario seems inconsistent with the degree of observed periodicity,
+the lack of infrared excess, and the observed lifetime of CQVs
+extending an order of magnitude longer than the $\approx$$10^7$ year
+timescale typically quoted for the primordial disk to disperse.
+However, unambiguous evidence has yet to be acquired in support of any
+scenario.  Such evidence might include a spectroscopic detection of
+silicate 10\,$\mu$m dust absorption during a dip, or perhaps detection
+of transient Balmer-line absorption during the dips, similar to
+observations made in systems such as AB~Dor \citep[see the review
 by][]{1999ASPC..158..146C}.
@@
 search methods in Section~\ref{sec:methods}, and the properties of the
-resulting CQV catalog in Section~\ref{sec:results}.  
-The evolution of many CQVs over a two-year baseline is described
-in Section~\ref{sec:evoln}, including a deep-dive into LP 12-502.
-Implications 
-are discussed in Section~\ref{sec:discussion}, and we conclude in
-Section~\ref{sec:conclusion}.
+resulting CQV catalog in Section~\ref{sec:results}.  The evolution of
+many CQVs over a two-year baseline is described in
+Section~\ref{sec:evoln}, including a deep-dive into LP 12-502.
+Implications are discussed in Section~\ref{sec:discussion}, and we
+conclude in Section~\ref{sec:conclusion}.
 
@@
 expectations for CQVs by assembling the data shown in
-Appendix~\ref{app:vetting}.  We labelled a star as a ``good'' CQV if
+Appendix~\ref{app:vetting}.  We labeled a star as a ``good'' CQV if
 at least one TESS sector showed what we viewed as the unambiguous
@@
 variability from rapid rotators, and variability from neighboring,
-off-target stars.  Typical false postive rates from our dip-counting
+off-target stars.  Typical false positive rates from our dip-counting
 pipeline were 5:1, with \nuniqdipflagged\ unique stars flagged, and
-about 20\% being labelled either ``good'' or ``possible'' CQVs; for
+about 20\% being labeled either ``good'' or ``possible'' CQVs; for
 the Fourier pipeline, {\bf the rate was X:Y, with ZZZZ unique stars
-flagged, and NN\% being labelled ``good'' or ``possible'' CQVs}.
+flagged, and NN\% being labeled ``good'' or ``possible'' CQVs}.
 
@@
 We determined the stellar effective temperature and radii through SED
-fitting; we then estimated the masses by interpolating against
-the PARSEC v1.2S models \citep{2012MNRAS.427..127B,2014MNRAS.444.2525C}.
-%the ``magnetic'' models of \citet{2016A&A...593A..99F}.
+fitting; we then estimated the masses by interpolating against the
+PARSEC v1.2S models \citep{2012MNRAS.427..127B,2014MNRAS.444.2525C}.
 
@@
 measurements against pre-computed model grids, and by default fits for
-six parameters:
-$\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm Fe/H}], d \}$.
-The distance  prior is drawn from \citet{2021AJ....161..147B}.  The
-surface gravity and metallicity are generally unconstrained.  And
-finally, given our particular use-case, we assumed the following
-priors for the temperature, stellar size, and extinction:
+six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
+Fe/H}], d \}$.  The distance  prior is drawn from
+\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
+generally unconstrained.  And finally, given our particular use-case,
+we assumed the following priors for the temperature, stellar size, and
+extinction:
 \begin{align}
@@
       CQVs.  Gray are raw 2-minute data; black bins to 300 points per
-      cycle.  Each panel is labelled by the TIC identifier, the TESS
+      cycle.  Each panel is labeled by the TIC identifier, the TESS
       sector number, and the period in hours.  Objects are ordered
@@
 
-The mosaic in Figure~\ref{fig:cqvs} shows phased light curves
-for the \ngoods\ bonafide CQVs.  The objects are sorted first in order
-of the number of TESS 120-second cadence sectors in which they clearly
+The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
+\ngoods\ bonafide CQVs.  The objects are sorted first in order of the
+number of TESS 120-second cadence sectors in which they clearly
 demonstrated the CQV phenomenon, and secondarily by descending
@@
 
-In terms of the light curve shapes, Figure~\ref{fig:cqvs}
-shows a broad range of variability, with anywhere from two to eight
-local minima per cycle.  Some stars show relatively ordinary
-modulation during one continuous portion of the phased light curve,
-and highly structured modulation in the remainder of the cycle (e.g.
+In terms of the light curve shapes, Figure~\ref{fig:cqvs} shows a
+broad range of variability, with anywhere from two to eight local
+minima per cycle.  Some stars show relatively ordinary modulation
+during one continuous portion of the phased light curve, and highly
+structured modulation in the remainder of the cycle (e.g.
 TIC~206544316, TIC~224283342, TIC~402980664).  Others show structured
@@
 As is typical for CQVs \citep{2017AJ....153..152S}, most CQVs in our
-catalog did not show infrared excesseses in the WISE1-4 bands.
+catalog did not show infrared excesses in the WISE1-4 bands.
 Visually inspecting the SEDs of our entire \ncpvsfound\ star sample,
-we labelled two objects as having ``good'' infrared excesses (both W3
+we labeled two objects as having ``good'' infrared excesses (both W3
 and W4), and three as ``possible'' infrared excess.
@@
 Hydrae association ($\approx$10\,Myr), and have relatively long
-periods of 38\,hr and 44\,hr respectively.  In our initial labelling,
-we labelled both as ``maybe'' CQVs because the dips in their light
+periods of 38\,hr and 44\,hr respectively.  In our initial labeling,
+we labeled both as ``maybe'' CQVs because the dips in their light
 curves did not show the rigid periodicity typical of CQVs;  their
-periods were also relatively long.  After labelling them, inspection
+periods were also relatively long.  After labeling them, inspection
 of further sectors clarified that both sources are dippers (see plots
@@
 resolved Keplerian $^{12}{\rm CO}(2-1)$ emission
-\citep{2015A&A...582L...5R}.  It was also labelled a dipper by
+\citep{2015A&A...582L...5R}.  It was also labeled a dipper by
 \citet{2022ApJS..263...14C}; we agree with their designation, but
@@
 \citep{2015A&A...582L...5R}, suggestive of cold dust grains being
-present.  It therefore also a dipper that snuck its way into our
-``maybe'' pile.
-Possible evolutionary connections between CQVs and dippers are
-highlighted in Section~\ref{subsec:discdippers}.
+present.  It is also a dipper.
+Given these ``errors'', plausible evolutionary connections between CQVs and
+dippers are discussed in Section~\ref{subsec:discdippers}.
 
@@
 that none have clear evidence for the presence of a disk.
-TIC~405910546, in LCC, shows a unique TESS light curve, reminescent of
+TIC~405910546, in LCC, shows a unique TESS light curve, reminiscent of
 a $P$=38\,hr singly-eclipsing binary, except with additional
@@
 clear CQV signals, but has no definitive evidence for a large, dusty
-disk.  TIC~244161191 (hilariously, TOI-278), in Columba, also has no
+disk.  TIC~244161191 (TOI-278), in Columba, also has no
 definitive evidence for a large disk.  It is however
-``multi-periodic''---in addition to the 7.17\,hr CPV signal, this
+``multi-periodic''---in addition to the 7.17\,hr CQV signal, this
 source shows a superposed 8.39\,hr sinusoidal signal, probably from an
@@
 confirmed \ngoods\ CQVs in our catalog; for plotting purposes we show
-the brightest 27.
-Of these 27 CQVs, a few show clear signs of the phenomenon in one
-sector, and marginal or non-existence signs in the other.
-While there is some subjectivity in this assessment, to our eyes cases
-for which at least one sector would be flagged as ``ambiguous''
-include
-TIC~368129164 (Sector 23 might be labelled an EB),
+the brightest 27.  Of these 27 CQVs, a few show clear signs of the
+phenomenon in one sector, and marginal or non-existence signs in the
+other.  While there is some subjectivity in this assessment, to our
+eyes cases for which at least one sector would be flagged as
+``ambiguous'' include
+TIC~368129164 (Sector 23 might be labeled an EB),
 TIC~177309964 (Sector 38 would be simply a rotating star),
@@
 TIC~193831684, assessed on a single-sector basis, would probably be
-labelled an eclipsing binary---in fact, \citet{2021ApJ...912..123J}
-implicitly have already given this source such a label.  However, based on the
-the shape evolution between Sectors 13 and 39, it is a CQV.
-One could easily also imagine in cases like TIC~206544316 that if
-observed at lower signal to noise, the drastic shape evolution would
-not be appreciated.  We emphasize that the periods themselves were all
-stable to $<$0.1\%.  Broadly speaking, this shape evolution suggests
-that CQVs have an ``on/off'' duty cycle of $\approx$75\%.  This type
-of correction is likely worth including in population-level estimates
-of how intrinsically common CQVs are in the low-mass stellar
+labeled an eclipsing binary---in fact, \citet{2021ApJ...912..123J}
+implicitly have already given this source such a label.  However,
+based on the the shape evolution between Sectors 13 and 39, it is a
+CQV.  One could easily also imagine in cases like TIC~206544316 that
+if observed at lower signal to noise, the drastic shape evolution
+would not be appreciated.  We emphasize that the periods themselves
+were all stable to $<$0.1\%.  Broadly speaking, this shape evolution
+suggests that CQVs have an ``on/off'' duty cycle of $\approx$75\%.
+This type of correction is likely worth including in population-level
+estimates of how intrinsically common CQVs are in the low-mass stellar
 population \citep[e.g.][]{2022AJ....163..144G}.
@@
 \begin{equation}
-  \sigma_{\rm P} = \frac { \sigma_{\rm \phi} P } { N_{\rm baseline} },
+  \sigma_{\rm P} = \frac { \sigma_{\phi} P } { N_{\rm baseline} },
 \end{equation}
@@
 (e.g.~a dip, or the overall shape of the sinusoidal envelope) can be
-tracked.  Assuming $\sigma_{\rm phi} \approx 0.01$ yields an expected
-period precision $\sigma_{\rm P} \approx 0.45 {\rm sec} \approx
+tracked.  Assuming $\sigma_{\phi} \approx 0.01$ yields an expected
+period precision $\sigma_{\rm P} \approx 0.45\,{\rm sec} \approx
 1.2\times 10^{-4}\,{\rm hr}$.  By visually fine-tuning over a grid in
@@
 What exactly is observed?  For the first 64 cycles, the star shows a
-pattern reminiscent of an eclipsing binary, with four obvious
-local minima.  We dub these dips $\{ 1, 2, 3, 4 \}$ at phases $\{ -0.28,
+pattern reminiscent of an eclipsing binary, with four obvious local
+minima.  We dub these dips $\{ 1, 2, 3, 4 \}$ at phases $\{ -0.28,
 -0.08, 0, 0.25 \}$, respectively.  Over cycles 0 to 64, the depth of
@@
 
-There is then a 6-month (184 cycle) gap to Cycles 248-315, which
-show two intricately structured dip complexes, plus a small leading
-dip.  The single leading dip is present at roughly the same phase as
-in cycles 0-64; they seem likely to be the same struture.  Along a
+There is then a 6-month (184 cycle) gap to Cycles 248-315, which show
+two intricately structured dip complexes, plus a small leading dip.
+The single leading dip is present at roughly the same phase as in
+cycles 0-64; they seem likely to be the same struture.  Along a
 similar line of logic, it seems plausible that the first ``dip
@@
 complex seen during cycles 0-64, though with greatly reduced depth.
-During cycles 266-310, an additional local minimum develops between the two
-complexes; this feature is best visualized on the river plots
+During cycles 266-310, an additional local minimum develops between
+the two complexes; this feature is best visualized on the river plots
 (Appendix~\ref{app:lp}), and we discuss its (shorter) period below.
@@
 substructure.  During e.g.~cycles 283-298, this single complex shows
-six local minima.  The deepest dip is very sharp: it shows a flux
+six local minima.  The deepest dip is sharp: it shows a flux
 exercusion of 3.5\% over about 22 minutes (0.02\,$P$), which is the
@@
 about a quarter of a period, punctuated by coherent local minima and
-maxima which in detail (Appendix~\ref{app:lp}) have slightly
-longer periods than the sharp dip.  The sharp leading dip only
-decreases during a sudden state-switch at BTJD 2030.7 (cycles
-299-315), which happens immediately during a flare
-(Figure~\ref{fig:lplc}).  The trailing dips remain afterwards.
-
-Sectors 53--58 (cycles 1233-1481) are comparitively tame; they showed
+maxima which in detail (Appendix~\ref{app:lp}) have slightly longer
+periods than the sharp dip.  The sharp leading dip only decreases
+during a sudden state-switch at BTJD 2030.7 (cycles 299-315), which
+happens immediately during a flare (Figure~\ref{fig:lplc}).  The
+trailing dips remain afterwards.
+
+Sectors 53--58 (cycles 1233-1481) are comparatively tame; they showed
 only four to six dips per cycle.  Some dips remain stable in depth and
@@
 
-{\sc Slow growth; rapid death}---Although there are a
-few instances in which we observe dips ``switch off'' over less
-than one cycle, dip growth seems to happen more slowly.  For instance,
-the dip that grows between phase 0 and 0.1 between cycles 260-290
-begins to become visible around BTJD 1993.2, and growths in depth by
-about 2\% over about six cycles, to become easily detectable by eye by
-BTJD 1997.7.  The evolution of this particular dip is most clear in
-the river plots.  The evolution of the latter dip group in cycles
-1410-1481 is another example of this slow mode of dip growth.
+{\sc Slow growth; rapid death}---Although there are a few instances in
+which we observe dips ``switch off'' over less than one cycle, dip
+growth seems to happen more slowly.  For instance, the dip that grows
+between phase 0 and 0.1 between cycles 260-290 begins to become
+visible around BTJD 1993.2, and growths in depth by about 2\% over
+about six cycles, to become easily detectable by eye by BTJD 1997.7.
+The evolution of this particular dip is most clear in the river plots.
+The evolution of the latter dip group in cycles 1410-1481 is another
+example of this slow mode of dip growth.
 
@@
 consistent with effective radii for the occulting material $R_{\rm
-eff} \ll R_\star$ .
-We also emphasize that this implies $a/R_\star \approx 5.8$ for this
+eff} \ll R_\star$ .  This implies $a/R_\star \approx 5.8$ for this
 material, and so the analogous timescale at the stellar surface is
@@
 18.5683, 18.5672, 18.5473, and 18.5145\,hr, with a typical measurement
-uncertainty of $\approx$0.0002\,hr.
-If each period corresponds to a dust clump, then this implies that
-multiple distinct clumps can orbit the star simultaneously, at
-marginally different separations.
+uncertainty of $\approx$0.0002\,hr.  If each period corresponds to a
+dust clump, then this implies that multiple distinct clumps can orbit
+the star simultaneously, at marginally different separations.
 
@@
 The closest CQV in our catalog is DG~CVn (TIC~368129164;
-$d$$=$18\,pc), a member of AB Dor.  To our knowledge,
-this manuscript is the first time that it has been noted as a CQV.
-The three brightest CQVs are DG~CVn ($T$=9.3),
-TIC~405754448 ($T$=9.6), and TIC~167664935 ($T$=10.3).
-The shortest period belongs to TIC~201789285, at 3.64\,hr.
-The longest period belongs to TIC~405910546, at 37.9\,hr.  If
-the latter source turns out to be an eclipsing binary, the next-longest
-would be TIC~193831684 (31.0\,hr).
+$d$$=$18\,pc), a member of AB Dor.  To our knowledge, this manuscript
+is the first time that it has been noted as a CQV.  The three
+brightest CQVs are DG~CVn ($T$=9.3), TIC~405754448 ($T$=9.6), and
+TIC~167664935 ($T$=10.3).  The shortest period belongs to
+TIC~201789285, at 3.64\,hr.  The longest period belongs to
+TIC~405910546, at 37.9\,hr.  If the latter source turns out to be an
+eclipsing binary, the next-longest would be TIC~193831684 (31.0\,hr).
 
 The lowest mass ($\approx 0.12$\,M$_\odot$) belongs to TIC~267953787.
-The catalog contains a few other stars with similar mass.
-Given the small number of sub-stellar mass objects in our target sample,
-this suggests that future studies of brown dwarf
-photometric variability might also yield complex quasiperiodic
-variables, though there would be degeneracies in interpretation with planetary surface features such
-as clouds and latitudinal bands \citep[e.g.][]{2021ApJ...906...64A,2022ApJ...924...68V}.
-
-The most massive CQV in our sample is a subject of some interest.
-To date, the only stars reported to show the CQV phenomenon
-are M-dwarfs, with typical stellar masses $\lesssim$0.3\,M$_\odot$
+The catalog contains a few other stars with similar mass.  Given the
+small number of sub-stellar mass objects in our target sample, this
+suggests that future studies of brown dwarf photometric variability
+might also yield complex quasiperiodic variables, though there would
+be degeneracies in interpretation with planetary surface features such
+as clouds and latitudinal bands
+\citep[e.g.][]{2021ApJ...906...64A,2022ApJ...924...68V}.
+
+The most massive CQV in our sample is a subject of some interest.  To
+date, the only stars reported to show the CQV phenomenon are M-dwarfs,
+with typical stellar masses $\lesssim$0.3\,M$_\odot$
 \citep{2022AJ....163..144G}.  TIC~405754448 and 405910546 however
@@
 \subsection{CQVs are quasiperiodic}
-A periodic signal repeats exactly; the CQVs do not (Figure~\ref{fig:evoln}).
-Their periods
-however do appear to be constant to within measurement precision over
-thousands of cycles.  They are therefore {\it quasi}periodic.  
-This point with previous studies by
-\citet{2022AJ....163..144G} and \citet{2023ApJ...945..114P}.
-However it marks a qualitative
-departure from the ``persistent'' {\it vs.} ``transient'' flux dip
-distinction described by \citet{2017AJ....153..152S};  while the dips
-can persist over timescales of even up to 100 cycles, all CQV dips
-seem to be transient over timescales of more than 1000 cycles
+A periodic signal repeats exactly; the CQVs do not
+(Figure~\ref{fig:evoln}).  Their periods however do appear to be
+constant to within measurement precision over thousands of cycles.
+They are therefore {\it quasi}periodic.  This point with previous
+studies by \citet{2022AJ....163..144G} and
+\citet{2023ApJ...945..114P}.  However it marks a qualitative departure
+from the ``persistent'' {\it vs.} ``transient'' flux dip distinction
+described by \citet{2017AJ....153..152S};  while the dips can persist
+over timescales of even up to 100 cycles, all CQV dips seem to be
+transient over timescales of more than 1000 cycles
 (Figure~\ref{fig:evoln}).
@@
 able to explore all phase angles with equal weight.  LP 12-502, and
-multiple other CQVs, seem to have preferred phases.  For LP 12-502, all of
-the dips happen over phases corresponding to only two thirds of the
-period (Figure~\ref{fig:lp}).  The remaining third seems to be ``out of limits'' for any dipping
-material.  This could be evidence that some aspect the
-stellar magnetic field is strongly asymmetric, and can generate and
-hold extrinsic material at corotation, but only over two thirds of the
-equatorial circle.  Alternatively, the source of the material (e.g. a planetesimal
-swarm) might be distributed over an arc of the same angular extent (240$^\circ$).
-We favor the
-former explanation, for reasons discussed below.
+multiple other CQVs, seem to have preferred phases.  For LP 12-502,
+all of the dips happen over phases corresponding to only two thirds of
+the period (Figure~\ref{fig:lp}).  The remaining third seems to be
+``out of limits'' for any dipping material.  This could be evidence
+that some aspect the stellar magnetic field is strongly asymmetric,
+and can generate and hold extrinsic material at corotation, but only
+over two thirds of the equatorial circle.  Alternatively, the source
+of the material (e.g. a planetesimal swarm) might be distributed over
+an arc of the same angular extent (240$^\circ$).  We favor the former
+explanation, for reasons discussed below.
 
@@
 
-Examining Figure~\ref{fig:cqvs}, it is not obvious
-whether the CQVs as a whole show any preference for sharper ingresses,
-or sharper egresses.
-In some cases (e.g. TIC~425933644), the continuum itself is not
-particularly well-defined, and so the meaning of ``ingress'' and
-``egress'' are not particularly clear.
-In others, such as Sector~36 of TIC~89463560, there is a single clear
-sharp ingress with an exponential egress, which could be directly fit
-using e.g.~a model analogous to those used for exocomets
-\citep[e.g.][]{2019A&A...625L..13Z}.
-The main quantities of interest in such models would be 
-the exponential decay time- and therefore length-scale,
-as well as the impact parameter and the 
-inferred transit depth (and its implications for the equivalent
-``radius'' of the transiting cloud).
-Although we briefly explored such models, it quickly became clear that
-careful modeling of sources such as LP 12-502 merits its own in-depth study.
-Connections could likely also be made to the toroidal geometries that
-are produced by outflowing atmospheres of transiting planets
+Examining Figure~\ref{fig:cqvs}, it is not obvious whether the CQVs as
+a whole show any preference for sharper ingresses, or sharper
+egresses.  In some cases (e.g. TIC~425933644), the continuum itself is
+not particularly well-defined, and so the meaning of ``ingress'' and
+``egress'' are not particularly clear.  In others, such as Sector~36
+of TIC~89463560, there is a single clear sharp ingress with an
+exponential egress, which could be directly fit using e.g.~a model
+analogous to those used for exocomets
+\citep[e.g.][]{2019A&A...625L..13Z}.  The main quantities of interest
+in such models would be the exponential decay time- and therefore
+length-scale, as well as the impact parameter and the inferred transit
+depth (and its implications for the equivalent ``radius'' of the
+transiting cloud).  Although we briefly explored such models, it
+quickly became clear that careful modeling of sources such as LP
+12-502 merits its own in-depth study.  Connections could likely also
+be made to the toroidal geometries that are produced by outflowing
+atmospheres of transiting planets
 \citep[e.g.][]{2019ApJ...873...89M,2022ApJ...926..226M}.
@@
 \subsection{Dust, or gas?}
-
-We believe that the most likely scenarios to explain the overall CQV phenomenology
-are the dust clump scenario, or the
-prominence scenario (Figure~\ref{fig:f1}).
-Both invoke clumpy material that would be centrifugally supported at the corotation radius.
-The prominence idea has a deeper history,
-based first on analogy with quiescent prominences/filaments
-observed to remain stable in the solar corona for up to a few weeks.
-In an extrasolar context,
-spectroscopic detections of transient Balmer- and
-resonance-line absorption seen for stars such as AB~Dor and
-Speedy~Mic \citep[e.g.][]{1989MNRAS.238..657C,1993MNRAS.262..369J,2006MNRAS.365..530D,2016MNRAS.463..965L}
+We believe that the most likely scenarios to explain the overall CQV
+phenomenology are the dust clump scenario, or the prominence scenario
+(Figure~\ref{fig:f1}).  Both invoke clumpy material that would be
+centrifugally supported at the corotation radius.  The prominence idea
+has a longer history, based first on analogy with quiescent
+prominences/filaments observed to exist in the solar corona for up to
+a few weeks \citep[see e.g.][]{2015ASSL..415.....V}.  In an extrasolar
+context, spectroscopic detections of transient Balmer- and
+resonance-line absorption seen for stars such as AB~Dor and Speedy~Mic
+\citep[e.g.][]{1989MNRAS.238..657C,1993MNRAS.262..369J,2006MNRAS.365..530D,2016MNRAS.463..965L}
 led to the interpretation that the data could best be explained by
-cold, minimally ionized hydrogen clouds scattering chromospheric emission from the star,
-producing the observed spectroscopic line variations \citep[see][]{1989MNRAS.238..657C}. 
-The mechanical stability of such gas configurations has been
-demonstrated \citep{2000MNRAS.316..647F,2022MNRAS.514.5465W}, and generally, the interpretation
-of this class of observations seems reasonably secure.
-
-The link between the dense gas clumps (prominences) that 
-likely exist around rapidly rotating low-mass stars,
-and the CQV phenomenon, has yet to be made.
-A simple visual examination of the TESS light curves for 
-five prominence-hosting systems
-studied by \citet{2019MNRAS.482.2853J}--AB~Dor, Speedy~Mic, LQ Lup, HK Aqr, and V374 Peg--revealed
-no obvious CQV behavior, though all likely show
-differential rotation, and
-Speedy~Mic shows two closely-spaced periods and
-a strong beat.
-Spectroscopically observable prominences therefore do not imply CQV-like dips.
+similar prominence structures: cold, minimally ionized hydrogen clouds
+or filaments that scatter chromospheric emission from the star to
+produce the observed spectroscopic line variations
+\citep[see][]{1989MNRAS.238..657C}.  The (short-term) mechanical
+stability of such gas configurations has been demonstrated
+\citep{2000MNRAS.316..647F,2022MNRAS.514.5465W}, and the
+interpretation of this class of observations seems at least somewhat
+secure.
+
+The link between the dense gas clumps (prominences) that likely exist
+around rapidly rotating low-mass stars, and the CQV phenomenon, has
+yet to be made.  A simple visual examination of the TESS light curves
+for five prominence-hosting systems studied by
+\citet{2019MNRAS.482.2853J}--AB~Dor, Speedy~Mic, LQ Lup, HK Aqr, and
+V374 Peg--revealed no obvious CQV behavior, though all likely show
+differential rotation, and Speedy~Mic shows two closely-spaced periods
+and a strong beat.  Spectroscopically observable prominences therefore
+do not imply CQV-like dips.
 
 %TODO: improve this to make it less jargony
-The difference between the prominence and dust clump scenarios
-is essentially only in whether the occulting material of
-interest is neutral hydrogen, or dust.  In the phrasing of the
-``frozen flux'' condition of ideal rigid field magnetohydrodynamics,
-the tendency of both to become trapped at the corotation radius in the
-equatorial plane is tied to how of the four relevant forces (gravity,
-Lorentz, inertial Coriolis, and inertial centrifugal), the Lorentz and
-Coriolis only act perpendicular to field lines, while gravity and the
+The difference between the prominence and dust clump scenarios is
+essentially only in whether the occulting material of interest is
+neutral hydrogen, or dust.  In the phrasing of the ``frozen flux''
+condition of ideal rigid field magnetohydrodynamics, the tendency of
+both to become trapped at the corotation radius in the equatorial
+plane is tied to how of the four relevant forces (gravity, Lorentz,
+inertial Coriolis, and inertial centrifugal), the Lorentz and Coriolis
+only act perpendicular to field lines, while gravity and the
 centrifugal force are in balance at $R_{\rm cr}$
-\citep[see][Sec.~2]{2005MNRAS.357..251T}.
-The magnetic field strength is only relevant in this formulation of
-the system in that we must have $R_{\rm sonic} < R_{\rm cr} < R_{\rm Alfven}$ in order for 
-closed loops to exist that can support prominences 
-\citep{2019MNRAS.482.2853J} {\bf lgb todo: verify!}.
-In detail however, whether such magnetic fixed points lie in the equatorial
-plane, or elsewhere, depends on the star's magnetic field geometry
-\citep{2023MNRAS.518.4734S}.
+\citep[see][Sec.~2]{2005MNRAS.357..251T}.  The magnetic field strength
+is only relevant in this formulation of the system in that we must
+have $R_{\rm sonic} < R_{\rm cr} < R_{\rm Alfven}$ in order for closed
+loops to exist that can support prominences
+\citep{2019MNRAS.482.2853J} {\bf lgb todo: verify \& de-jargonify!}.
+In detail however, whether such magnetic fixed points lie in the
+equatorial plane, or elsewhere, depends on the star's magnetic field
+geometry \citep{2023MNRAS.518.4734S}.
 
@@
 The strongest argument for why neutral hydrogen is an unlikely
-occulting source is that CQVs show broadband flux
-variations that are deeper in the blue than in the red.
-
-Based on our reading of \citet[][Ch.~8]{1992oasp.book.....G},
-it seems somewhat challenging to get neutral hydrogen to have this type of chromaticity.
-Bound-bound absorption provides opacity only at narrow resonant lines.
-Bound-free absorption can provide wavelength-dependent opacity, but the
-absorption coefficients generally {\it grow} with increasing wavelength, rather
-than {\it shrink} as one needs in order to get deeper absorption in
-the blue than in the red.  H$^-$  fails as a viable opacity
-source for the same reason: its absorption coefficient peaks near
-8500\,\AA, and is an order of magnitude smaller at $\approx$3000\AA.
+occulting source is that CQVs show broadband flux variations that are
+deeper in the blue than in the red.
+
+Based on our reading of \citet[][Ch.~8]{1992oasp.book.....G}, it seems
+somewhat challenging to get neutral hydrogen to have this type of
+chromaticity.  Bound-bound absorption provides opacity only at narrow
+resonant lines.  Bound-free absorption can provide
+wavelength-dependent opacity, but the absorption coefficients
+generally {\it grow} with increasing wavelength, rather than {\it
+shrink} as one needs in order to get deeper absorption in the blue
+than in the red.  H$^-$  fails as a viable opacity source for the same
+reason: its absorption coefficient peaks near 8500\,\AA, and is an
+order of magnitude smaller at $\approx$3000\AA.
 \citep{1992oasp.book.....G}, following \citet{1979MNRAS.187P..59W}.
-Thompson scattering is also ruled out, because it is gray.
-Dust, with its relatively featureless but increasing extinction curve
-when going bluer into the optical \citep{1989ApJ...345..245C}, is to our knowledge the most
-obvious opacity source.
-
-While the above line of reasoning seems fairly convincing,
-it has a flaw.
-The logic presented above would imply that regardless of a star's temperature,
-if relative depths of a dip are seen to be deeper in the blue than in the red,
-then it is hard to get hydrogen to do it.
-There is however a rapidly rotating 
-magnetic B-star, $\sigma$~Ori~E, which shows dips that are deeper in the blue than in the red
-\citep{1977ApJ...216L..31H}.
-Photometric and spectroscopic observations of this star have been understood in terms of
-absorbing circumstellar material, quite analogous to the geometries we are
-discussing for much cooler M-dwarfs \citep{2005ApJ...630L..81T}.
-This material however cannot be dust, due to the relevant sublimation timescales.
-It is instead thought to be sourced from bound-free absorption from neutral hydrogen
-\citep{2005ApJ...630L..81T}.  Separate and smaller amplitude
-emission in that system may also 
-come from electrons scattering photospheric light toward the observer 
-when the clouds are not in transit \citep{2022MNRAS.511.4815B}.
-
-Given these complexities, it clearly
-seems important for a future theoretical study to be conducted to
-determine to what degree the observed chromaticities in CQVs match, or do not
-match, expectations from radiative transfer.
-This issue has a key ability to resolve the question of whether the
-CQVs are caused by dust, or by gas.
-This question has direct bearing on the potential utility of these
-objects.
-
-\subsubsection{Does the CQV lifetime inform the mechanism?}
-Independent of the microphysical basis for gas absorption, the
-prominence scenario may present another issue: why don't stars in the
-Hyades and Praesepe show the phenomenon?
-In a broad sense, the prominence scenario argues that an intrinsic
-stellar process is key for generating the CQV phenomenon.
-If this were true, then stars of identical mass, size, and rotation
-periods might be expected to show the phenomenon in equal number,
-simply because the stellar dynamo is generated by fluid
-motions inside the star, which should be identical for stars of the
-same mass, size, and rotation period.
-
-Between ages of $\approx$100\,Myr (AB Dor, Pleiades, Psc-Eri) and
-$\approx$700\,Myr (Praesepe and Hyades), a 0.3\,M$_\odot$ star will
-shrink by $\approx$10\%, from $\approx$0.33\,R$_\odot$ to 
-$\approx$0.29\,R$_\odot$ \citep[e.g.][]{2014AJ....147...82C}.
-This is not a particularly drastic size change.
-Similarly, at 700\,Myr many M-dwarfs have comparably rapid rotation periods 
-to those at 100\,Myr \citep[e.g. Figure~13 of][]{2022AJ....164...80R};
-the mean population does show evidence for spin-down after the
-PMS contraction finishes, but there are still a large number of 
-700\,Myr M-dwarfs with $P_{\rm rot}\lesssim$2\,days, beyond
-which the CQV phenomenon becomes less common.
-
-Broadly speaking -- the absence of old CQVs seems to be
-more plausibly linked to a gradual depletion of dusty detritus from the
-planet formation era than it does to the changing stellar properties
-as the stars gradually finish their pre-main-sequence evolution, and then
-continue to spin rapidly for many hundreds of millions of years.
+Thompson scattering is also ruled out, because it is gray.  Dust, with
+its relatively featureless but increasing extinction curve when going
+bluer into the optical \citep{1989ApJ...345..245C}, is to our
+knowledge the most obvious opacity source.
+
+While the above line of reasoning seems fairly convincing, it has a
+flaw.  The logic presented above would imply that regardless of a
+star's temperature, if relative depths of a dip are seen to be deeper
+in the blue than in the red, then it is hard to get hydrogen to do it.
+There is however a rapidly rotating magnetic B-star, $\sigma$~Ori~E,
+which shows dips that are deeper in the blue than in the red
+\citep{1977ApJ...216L..31H}.  Photometric and spectroscopic
+observations of this star have been understood in terms of absorbing
+circumstellar material, quite analogous to the geometries we are
+discussing for much cooler M-dwarfs \citep{2005ApJ...630L..81T}.  This
+material however cannot be dust, due to the relevant sublimation
+timescales.  It is instead thought to be sourced from bound-free
+absorption from neutral hydrogen \citep{2005ApJ...630L..81T}.
+Separate and smaller amplitude emission in that system may also come
+from electrons scattering photospheric light toward the observer when
+the clouds are not in transit \citep{2022MNRAS.511.4815B}.
+
+Given these complexities, it clearly seems important for a future
+theoretical study to be conducted to determine to what degree the
+observed chromaticities in CQVs match, or do not match, expectations
+from radiative transfer.  This issue has a key ability to resolve the
+question of whether the CQVs are caused by dust, or by gas.  This
+question has direct bearing on the potential utility of these objects.
+
+%\subsubsection{Why corotation?}
+%All of the prominence models, and the diagrams of where the magnetic
+%fixed points exist, enable the fixed points to not be located at
+%corotation.
+%In addition, the Balmer absorption line measurements have been used to
+%argue for material being generally located at positions other than
+%just corotation (CHECK Collier-Cameron1989).
+
+%\subsubsection{Does the CQV lifetime inform the mechanism?}
+%Independent of the microphysical basis for gas absorption, the
+%prominence scenario may present another issue: why don't stars in the
+%Hyades and Praesepe show the phenomenon?
+%In a broad sense, the prominence scenario argues that an intrinsic
+%stellar process is key for generating the CQV phenomenon.
+%If this were true, then stars of identical mass, size, and rotation
+%periods might be expected to show the phenomenon in equal number,
+%simply because the stellar dynamo is generated by fluid
+%motions inside the star, which should be identical for stars of the
+%same mass, size, and rotation period.
+%
+%Between ages of $\approx$100\,Myr (AB Dor, Pleiades, Psc-Eri) and
+%$\approx$700\,Myr (Praesepe and Hyades), a 0.3\,M$_\odot$ star will
+%shrink by $\approx$10\%, from $\approx$0.33\,R$_\odot$ to 
+%$\approx$0.29\,R$_\odot$ \citep[e.g.][]{2014AJ....147...82C}.
+%This is not a particularly drastic size change.
+%Similarly, at 700\,Myr many M-dwarfs have comparably rapid rotation periods 
+%to those at 100\,Myr \citep[e.g. Figure~13 of][]{2022AJ....164...80R};
+%the mean population does show evidence for spin-down after the
+%PMS contraction finishes, but there are still a large number of 
+%700\,Myr M-dwarfs with $P_{\rm rot}\lesssim$2\,days, beyond
+%which the CQV phenomenon becomes less common.
+%
+%Broadly speaking -- the absence of old CQVs seems to be
+%more plausibly linked to a gradual depletion of dusty detritus from the
+%planet formation era than it does to the changing stellar properties
+%as the stars gradually finish their pre-main-sequence evolution, and then
+%continue to spin rapidly for many hundreds of millions of years.
 
@@
 average one planet per M-dwarf.  TRAPPIST-1b ($P$=1.5\,days) is one
-example of this type of planet, in orbit around a 0.08\,M$_\odot$ star  \citep{2017Natur.542..456G}.
+example of this type of planet, in orbit around a 0.08\,M$_\odot$ star
+\citep{2017Natur.542..456G}.
 
@@
 simple 1-D viscous accretion models, this truncation radius roughly
-coincides with the corotation radius (CITE), though in
-detail factors of a few difference have been observed between the two
-(CITE IR studies).  Within models that have migrating compact
-multiplanet resonant chains, the inner-most planets arrive within
-$\approx$5-10 stellar radii within the first 100\,Myr \citep{2018haex.bookE.142I}.
-
-It is very tempting to try to interpret features of the
-CQV light curves in terms of the possible presence of close-in
-exoplanets, or even planetesimals.  Rocky planets this
-young would likely have molten global magma oceans analogous to those that
-existed on the Earth and Moon \citep[see][]{2022arXiv220310023L}, and thus
-would being undergoing significant outgassing and atmospheric escape.  A
+coincides with the corotation radius (CITE), though in detail factors
+of a few difference have been observed between the two (CITE IR
+studies).  Within models that have migrating compact multiplanet
+resonant chains, the inner-most planets arrive within $\approx$5-10
+stellar radii within the first 100\,Myr \citep{2018haex.bookE.142I}.
+
+It is tempting to try to interpret features of the CQV light curves in
+terms of the possible presence of close-in exoplanets, or even
+planetesimals.  Rocky planets this young would likely have molten
+global magma oceans analogous to those that existed on the Earth and
+Moon \citep[see][]{2022arXiv220310023L}, and thus would being
+undergoing significant outgassing and atmospheric escape.  While a
 scenario in which close-in rocky planets serve as a possible source of
-dust for the clouds is not entirely implausible, {\it a priori}.
-%Frankly though, it remains a subject of speculation.
+dust for the clouds is {\it a priori} plausible, it is currently only
+a subject of speculation.
 
@@
 12-502, one might be driven in this framework toward a picture of a
-disintegrating planetesimal swarm.  
-The sizes of the planetesimals would need to be $\lesssim 1$\,$R_\oplus$,
-based on the non-detections of their transits, analogous to e.g. 
-K2-22 \citep{2015ApJ...812..112S} or KOI-2700 \citep{2014ApJ...784...40R}.
-The dip-profile asymmetries during
-certain segments of the light curve plausibly match this idea; for
-instance, the complex in cycles 248-298 could be well-fit by a sharp
-leading edge that decays over 0.2\,$P$ (3.7\,hours).  The earlier
-complex, during cycles 248-264 (pre-state-switch), could be fit by a
-similar profile.  While the number of free parameters in this type of
-model is somewhat dizzying, we have no right to believe that nature
-need be simple.
+disintegrating planetesimal swarm.  The sizes of the planetesimals
+would need to be $\lesssim 1$\,$R_\oplus$, based on the non-detections
+of their transits, analogous to e.g.  K2-22
+\citep{2015ApJ...812..112S} or KOI-2700 \citep{2014ApJ...784...40R}.
+The dip-profile asymmetries during certain segments of the light curve
+plausibly match this idea; for instance, the complex in cycles 248-298
+could be well-fit by a sharp leading edge that decays over 0.2\,$P$
+(3.7\,hours).  The earlier complex, during cycles 248-264
+(pre-state-switch), could be fit by a similar profile.  While the
+number of free parameters in this type of model is somewhat dizzying,
+we have no right to believe that nature need be simple.
 
@@
 
-Ultimately, there are a few problems for the idea of a
-disintegrating planetesimal.
-First, a large number of the
-dips show asymmetries in the {\it wrong direction} relative to the
-naive expectation of a trailing comet tail.  Invoking non-exponentially
-decaying dust distributions as a function of azimuth might be one way out of this,
-but such an idea would need stronger theoretical footing.
-More important is that the (unseen) planets or planetesimals should be on {\it
-exactly periodic} orbits over observable timescales, on the
+Ultimately, there are a few problems for the idea of a disintegrating
+planetesimal.  First, a large number of the dips show asymmetries in
+the {\it wrong direction} relative to the naive expectation of a
+trailing comet tail.  Invoking non-exponentially decaying dust
+distributions as a function of azimuth might be one way out of this,
+but such an idea would need stronger theoretical footing.  More
+important is that the (unseen) planets or planetesimals should be on
+{\it exactly periodic} orbits over observable timescales, on the
 presumption that the planetesimals would be massive enough to not feel
-any headwind or magnetic field.  For most CQVs, this is inconsistent with the data;
-dips in sources such as LP 12-502 appear and disappear at
-{\it distinct phases}, but with the same period.
-It seems challenging to reconcile this behavior
-with the possible presence of just a single launching body.
-Finally, the fact that the dips often respond to events like flares
-suggests that that the responsible material be much less massive than
-a 1--100-\,km sized planetesimal, and therefore more easily influenced
-by the stellar magnetic field.
-
-It is certainly possible that exoplanets could end up being connected to the
-CQV phenomenon,
-for instance as a possible source of dust through collisions at greater separations
-from the star.
-However for the time being, none of the CQVs that we have studied in this
-work seem to show clear evidence for an exoplanetary origin.
+any headwind or magnetic field.  For most CQVs, this is inconsistent
+with the data; dips in sources such as LP 12-502 appear and disappear
+at {\it distinct phases}, but with the same period.  It seems
+challenging to reconcile this behavior with the possible presence of
+just a single launching body.  Finally, the fact that the dips often
+respond to events like flares suggests that that the responsible
+material be much less massive than a 1--100-\,km sized planetesimal,
+and therefore more easily influenced by the stellar magnetic field.
+
+It is certainly possible that exoplanets could end up being connected
+to the CQV phenomenon, for instance as a possible source of dust
+through collisions at greater separations from the star.  However for
+the time being, none of the CQVs that we have studied in this work
+seem to show clear evidence for an exoplanetary origin.
 
@@
 
-It is amusing that for the two candidate CQV sources identified in
-Section~\ref{subsec:irexcess} as having outlying SEDs (TICs~193136669
-and TIC~57830249), the identification of the infrared excess is part
-of what prompted our eventual labelling of these sources as dippers.
-It is also worth emphasizing that our labelling of e.g.~TIC~57830249
-was based on a single sector of TESS data (Sector~36), when its
-behavior is relatively periodic, with dip depths of a few percent.
-However in other TESS sectors (e.g. Sector~10), this source looks
-completely different, varying in apparent flux by a factor of two,
-which hardly any discernable periodicity at all.
+It is amusing that in identifying the two candidate CQV sources in
+Section~\ref{subsec:irexcess} with outlying SEDs (TICs~193136669 and
+TIC~57830249), we were prompted to reconsider our light curve-based
+labeling, to
+ultimately conclude that these sources are dippers.  This episode
+suggests that could be some overlap between the two classes of
+object.  It is also worth emphasizing that our labeling of
+e.g.~TIC~57830249 was based on a single sector of TESS data
+(Sector~36) when its behavior is relatively periodic and it showed
+relative dip depths of a few percent.  However in other TESS sectors
+(e.g. Sector~10), this source looks completely different, varying in
+apparent flux by a factor of two, with hardly any discernible
+periodicity at all.
 
@@
 transit and secondary eclipse.  The second is that it also corresponds
-to the interval over which half of the star's surface is visible.
-Of the CQVs in Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, a number
-that seems greater than random might exhibit a preference for
-showing dips or peaks that correspond to the half-cycle interval.
+to the interval over which half of the star's surface is visible.  Of
+the CQVs in Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, a number that
+seems greater than random might exhibit a preference for showing dips
+or peaks that correspond to the half-cycle interval.
 
 One set of CQVs shows ``CQV behavior'' (some form of dip complex), but
-which only lasts for half of any given cycle.
-TIC~206544316 (Sector 2) is a canonical example;
-TIC~405910546 (Sector 38), TIC~167664935 (Sector 38), TIC~146539195
-(Sector 5), TIC~118449916 (Sector 44), and TIC~312410638 (Sector 38)
-seem to show essentially the same tendency.
+which only lasts for half of any given cycle.  TIC~206544316 (Sector
+2) is a canonical example; TIC~405910546 (Sector 38), TIC~167664935
+(Sector 38), TIC~146539195 (Sector 5), TIC~118449916 (Sector 44), and
+TIC~312410638 (Sector 38) seem to show essentially the same tendency.
 
@@
 after large dips; it is tempting to label the small dips secondary
-eclipses.
-Such sources include 
-TIC~402980664 (Sector 25; relative to the sharpest, deepest minimum),
-TIC~89463560 (Sector 36),
+eclipses.  Such sources include TIC~402980664 (Sector 25; relative to
+the sharpest, deepest minimum), TIC~89463560 (Sector 36),
 TIC~224283342 (Sector 2), and TIC~442571495 (Sector 12).
@@
 come up with counter-example objects which do not follow the trend.
-In other words, these half-cycle CQVs could simply be a
-product of the human tendency to pattern match; alternatively, they
-might yield some important physical signifiance.
+In other words, these half-cycle CQVs could simply be a product of the
+human tendency to pattern match; alternatively, they might yield some
+important physical significance.
 
@@
 
-It is possible to estimate the mass of a transiting cloud by
-converting the transit depth to an effective cloud radius, $R_{\rm
-cloud}$.  For most CQVs in Figure~\ref{fig:cqvs}, this yields roughly
-1-10\,$R_\oplus$.  This size can be converted into a mass estimate by
-requiring the optical depth $\tau$ of the cloud to be at least unity.
-In other words, a minimum constraint on the dust number density
-follows by requiring the cloud to be optically thick.  For cases like
-LP 12-502, this is resonable because the transit duration implies
-$R_{\rm cloud}\ll R_\star$.  Carrying out the relevant calculation
-assuming sizes for the dust grains of 1\,$\mu$m,
+We can estimate the mass of a transiting cloud by first converting the
+transit depth to an effective cloud radius, $R_{\rm cloud}$.  For most
+CQVs in Figure~\ref{fig:cqvs}, this typically yields $\approx$2-20\,$R_\oplus$.
+This size can be converted into a mass estimate by requiring the
+optical depth $\tau$ of the cloud to be at least unity and by positing
+some composition for the cloud.  In other
+words, a minimum constraint on the number density follows by
+requiring the cloud to be optically thick.  For cases like LP 12-502,
+this is resonable because the transit duration implies $R_{\rm
+cloud}\ll R_\star$.  Carrying out the relevant calculation assuming
+a dust composition, for dust grains 1\,$\mu$m in size,
 \citet{2023MNRAS.518.4734S} find minimum cloud masses of order
@@
 small asteroid; the asteroid belt itself has a mass of
-$\approx$2$\times$10$^{21}$\,kg (CITE).  Also by way of comparison,
+order $\approx$10$^{21}$\,kg (CITE).  Also by way of comparison,
 the previously-discussed cool gas prominences for AB~Dor would need to
@@
 Our observations provide a direct measurement of how often dips
-``appear'' or ``disappear'', both due to sudden state-switches, and
+appear and disappear, both due to sudden state-switches, and
 due to more gradual, secular evolution.  For instance, LP~12-502
-showed 3 ``state-switch'' events over the six months of available TESS
+showed three ``state-switch'' events over the six months of available TESS
 observations, during cycles 248-264, 299-315, and 1233-1247.  It is
@@
 ejected from corotation, or perhaps being accreted onto the star.  In
-any event, the corresponding $\dot{M} \equiv M\cdot {\rm d}N/{\rm d}t$
+either case, the corresponding $\dot{M} \equiv M\cdot {\rm d}N/{\rm d}t$
 is $\approx$3$\times$$10^{-18} M_\odot\,{\rm yr}^{-1} \approx
@@
 	%
-  \item The same CQV can show dips with very similar but clearly
+  \item The same CQV can show dips with similar but clearly
     distinct periods.  LP 12-502, for instance, showed dips with four
@@
 
-Many questions remain.  
-Is the eclipsing material responsible for the phenomenon gas, or dust?
-After correcting for line-of-sight inclination, do most 
-M-dwarfs go through a phase of trapping material a few stellar radii away
-from their surfaces?  
-What observational
+Many questions remain.  Is the eclipsing material responsible for the
+phenomenon gas, or dust?  After correcting for line-of-sight
+inclination, do most M-dwarfs go through a phase of trapping material
+a few stellar radii away from their surfaces?  What observational
 signatures distinguish the proposed models (Figure~\ref{fig:f1},
@@
 12-502, or perhaps some other suitable object, using JWST/MIRI.
-{\bf final paragraph(s) clearly need improvement}
+
+{\bf lgb: final paragraph(s) clearly need improvement!}
 
@@
     \centering
-    \includegraphics[width=0.96\textwidth]{annotated_402980664_S0018_120sec_cpvvetter.pdf}
+    \includegraphics[width=0.96\textwidth]{annotated_402980664_S0018_120sec_CQVvetter.pdf}
 		\vspace{-0.45cm}
@@
       {\bf Validation plots used to manually label CQVs}.  The complete figure
-      set, with one image per sector for each of \ncpvsfound\ CQVs
+      set, with one image per sector for each of \nCQVsfound\ CQVs
       and candidate CQVs
@@
 Finally, Figure~\ref{fig:lpriver0} shows ``river plots'' of the
-same data, split into very similar intervals:
+same data, split into similar intervals:
 the Sector 18-19 data, 25-26 data, 53 data, and 58-59 data.

### 2023-07-03 paper/ms.tex
update ms

@@
 \newcommand{\msun}{{M$_\odot$}}
-
-\newcommand{\teff}{T_{\rm eff}}
-\newcommand{\ms}{M_\star}
-\newcommand{\rs}{R_\star}
-
 \newcommand{\bprp}{G_{\rm BP} - G_{\rm RP}}
@@
 \newcommand{\minus}{\scalebox{0.5}[1.0]{$-$}}
-
-\newcommand{\eg}{e.g.,}
 
@@
 \citep{2010exop.book...55W}.  More exotic forms of optical variability
-relevant to this work include transiting exocomets (e.g. $\beta$~Pic;
+relevant to this work include transiting exocomets (e.g.~$\beta$~Pic;
 \citealt{2019A&A...625L..13Z}) and disintegrating rocky bodies around
@@
 \citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
-and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  The
-CQVs should not be conflated with ``dippers'', which are classical T
-Tauri stars with infrared excesses whose optical variability is linked
+and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  
+The CQVs should generally not be conflated with ``dippers'', which are classical T
+Tauri stars with infrared excesses, and drastically and 
+at best marginally periodic variability linked
 to obscuring inner disk structures and accretion hot spots
-\citep{2014AJ....147...82C,2021ApJ...908...16R}.  At the risk of
+\citep{2014AJ....147...82C,2021ApJ...908...16R}.  
+With that said, a few similarities between CQVs and dippers do exist
+(see Sections~\ref{subsec:irexcess} and~\ref{subsec:discdippers}).
+At the risk of
 introducing yet another standard, we prefer a nomenclature that
@@
 		300 points per cycle.  Periods in hours are in the bottom right of
-		each panel.  In order left-to-right, the objects are LP 12-502
+		each panel.  Left-to-right, the objects are LP 12-502
 		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
 		425933644 (Sector~28).
-		{\it Bottom:} Plausible cartoon models for the phenomenon.  The
-		dust clump scenario seems most plausible, given
-    the stability of the dips, their chromaticity, the lack of
-    observed infrared excesses, and the challenge of producing
-    broadband opacity variations with only ionized hydrogen in the
-    prominence scenario.
+		{\it Bottom:} Cartoon models for the phenomenon.  The dust clump
+		scenario
+		(lower left) and prominence scenario (lower center) both invoke centrifugally-supported material at the
+		corotation radius.
+		We disfavor the screen scenario (see Section~\ref{sec:intro}).
 	}
@@
 
+\begin{figure*}[!t]
+	\begin{center}
+		\centering
+		\includegraphics[width=0.96\textwidth]{annotated_lp12502.pdf}
+		\vspace{-0.3cm}
+		\caption{
+			{\bf Validation plots used to  label CQVs}.  The complete figure
+			set, with one image per sector for each of \ncpvsfound\ CQVs
+			and candidate CQVs
+			is available online {\bf For internal collaboration review:
+				\url{https://www.dropbox.com/scl/fo/zlj3txot4cvymfb22wewu/h?dl=0&rlkey=3ec5f9o5xewrixzfkhkdenopa}}.
+			Panels are as follows.
+			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
+			data and black points are binned to 200 points per cycle.
+			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
+			Dotted lines show up to the 10$^{\rm th}$ harmonic and
+			subharmonic.
+			{\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
+			circles displayed for scale.
+			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
+			Barycentric TESS Julian Date (BTJD).
+			{\it e)}: Phase-folded light curve, binned to 100 points per
+			cycle.  The gray line denotes the automated spline-fit to the
+			wrapped phase-folded light curve, and small gray triangles
+			denote automatically identified local minima.
+			{\it f)}: Phase-folded light curve at twice the peak period.
+			{\it g)}: Phase-folded light curve at half the peak period.
+			{\it h)}: Phase-folded time-series within the ``background''
+			aperture defined in the SPOC light curves.
+			{\it i)}: Phase-folded flux-weighted centroid in the column
+			direction.
+			{\it j)}: Phase-folded flux-weighted centroid in the row
+			direction.
+			{\it k)}: Gaia DR2 color--absolute magnitude diagram.     
+			The gray background denotes stars within 100\,pc.
+			{\it l)}: Information from Gaia DR2, TIC8, and the automated
+			dip-counting search pipeline.  ``Neighbors'', abbreviated
+			``nbhr'', are listed within apparent distances of 2 TESS pixels
+			if $\Delta T$$<$2.5.
+			{\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
+			using positions, proper motions, and the parallax.
+		}
+		\label{fig:vet}
+	\end{center}
+\end{figure*}
+
 We visually assessed whether the objects found using the Fourier
@@
 expectations for CQVs by assembling the data shown in
-Appendix~\ref{app:vetting}.  We labeled a star as a ``good'' CQV if
+Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CQV if
 at least one TESS sector showed what we viewed as the unambiguous
@@
 of further sectors clarified that both sources are dippers (see plots
-in Appendix~\ref{app:vetting}).  In addition, TIC 193136669 has a cold
+in Figure~\ref{fig:vet}).  In addition, TIC 193136669 has a cold
 molecular disk based on observed 1.3\,mm continuum emission and
@@
 	\end{center}
-
 \end{figure*}
@@
 
-\subsection{Extremes}
+\begin{figure*}[!t]
+	\begin{center}
+		\centering
+		\includegraphics[width=\textwidth]{f6.pdf}
+		\vspace{-0.45cm}
+		\caption{
+      {\bf Properties of CQVs from our serach}.
+      The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are 
+      the black circles; \nmaybes\ candidate CQVs are gray circles.
+      The \nstarssearched\ target stars with 120-second cadence data
+      acquired by TESS between July~2018 and Sep~2022 are shown as the shaded background on the top panels,
+      where darker regions correspond to a larger relative number of observed stars.
+      {\bf lgb todo: P vs color needs Pleiades comparison}
+		}
+		\label{fig:catalogscatter}
+	\end{center}
+\end{figure*}
+
+\subsection{Typical and Extreme Cases}
+\label{subsec:extreme}
+Figure~\ref{fig:catalogscatter} shows some of the derived properties
+for our CQV catalog, and contrasts them against both the target star
+sample (top panels), and the population of rotating stars in the Pleiades
+from \citet{2016AJ....152..114R}.
+Generally, CQVs are much younger than typical field stars. 
+In terms of their rotation, relative to the Pleiades,
+they are among the more rapidly rotating half.
+The dearth of $T$$>$15.5 CQVs in our sample, despite our search extending
+to $T$$=$16, is a consequence of the 120-second selection function.
+%
+
 The closest CQV in our catalog is DG~CVn (TIC~368129164;
@@
 \subsection{Dust, or gas?}
-We believe that the most likely scenarios to explain the overall CQV
-phenomenology are the dust clump scenario, or the prominence scenario
+We believe that the most likely scenarios to explain CQVs
+are either the dust clump scenario or the prominence scenario
 (Figure~\ref{fig:f1}).  Both invoke clumpy material that would be
@@
 \citep[see][]{1989MNRAS.238..657C}.  The (short-term) mechanical
-stability of such gas configurations has been demonstrated
+stability of such gas configurations is theoretically plausible
 \citep{2000MNRAS.316..647F,2022MNRAS.514.5465W}, and the
@@
 
-The link between the dense gas clumps (prominences) that likely exist
-around rapidly rotating low-mass stars, and the CQV phenomenon, has
+Any link between the dense gas clumps (prominences) that likely exist
+around rapidly rotating low-mass stars and the CQV phenomenon has
 yet to be made.  A simple visual examination of the TESS light curves
@@
 \citet{2019MNRAS.482.2853J}--AB~Dor, Speedy~Mic, LQ Lup, HK Aqr, and
-V374 Peg--revealed no obvious CQV behavior, though all likely show
-differential rotation, and Speedy~Mic shows two closely-spaced periods
-and a strong beat.  Spectroscopically observable prominences therefore
+V374 Peg--revealed no obvious CQV behavior, though all show
+differential evolution, and Speedy~Mic shows two closely-spaced periods
+and a strong beat.  Spectroscopically observable prominences 
 do not imply CQV-like dips.
@@
 order of magnitude smaller at $\approx$3000\AA.
-\citep{1992oasp.book.....G}, following \citet{1979MNRAS.187P..59W}.
+(\citealt{1992oasp.book.....G}, following \citealt{1979MNRAS.187P..59W}).
 Thompson scattering is also ruled out, because it is gray.  Dust, with
@@
 
-While the above line of reasoning seems fairly convincing, it has a
-flaw.  The logic presented above would imply that regardless of a
+While the reasoning above seems fairly convincing, it has a
+flaw.  The argument presented above would imply that regardless of a
 star's temperature, if relative depths of a dip are seen to be deeper
@@
 %just corotation (CHECK Collier-Cameron1989).
+
+\subsubsection{The lifetime constraint}
+Independent of the microphysical basis for gas absorption, the observed
+lifetime of the CQV phenomenon could provide another dimension to discern between
+the gas {\it vs.} dust clump scenarios.
+Based on the available statistics from the studies of L.~Rebull and J.~Stauffer,
+it seems plausible that CQV occurrence decreases in time, bottoming to zero
+well before the $\approx$700\,Myr age of Praesepe.
+This is odd in the context of the prominence scenario, because pre-main-sequence
+M-dwarfs spin up over the first $\approx$$10^8$\,yr;
+prominences might even be expected to be {\it more} common at the 
+age of the Pleiades than for younger stars.
+This broadly assumes that any star that can support prominences will,
+which translates in detail to a condition on the star's mass, rotation
+period, and magnetic field strength.
+Based on the degree to which M-dwarfs remain rapid rotators over the first 700\,Myr
+\citep[e.g. Figure~13 of][]{2022AJ....164...80R}, 
+it seems surprising in the gas clump (prominence) scenario that no stars
+older than 150\,Myr have been seen to exhibit the phenomenon.
+In the dust clump scenario this is not a problem, because the dust could
+be externally sourced, and would be expected to have a finite supply.
 
@@
 respond to events like flares suggests that that the responsible
-material be much less massive than a 1--100-\,km sized planetesimal,
+material be much less massive than a 1--100\,km sized planetesimal,
 and therefore more easily influenced by the stellar magnetic field.
@@
 
-\begin{itemize}
+\begin{enumerate}
 	%
@@
   	%
-  \item The CQV phenomenon persists for at least 150\,Myr, based on
-    the existence of multiple CQVs in AB Dor, the Pleiades, and
-    Psc-Eri.  It may extend to even older ages, however the lack of
-    detected CQVs in the Hyades and Praesepe suggests that the
-    phenomenon does become less common at older ages.
-	%
     \item CQVs evolve over timescales that are both secular
@@
     %
+    \item The rate of dip evolution can be used to place a model-dependent
+    constraint on amount of material that is either being accreted or ejected
+    during the state changes.
+    Order of magnitude estimates require at least an asteroid belt's worth
+    of dust ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or a factor of 100
+    larger if the material is gas.
+    %
+  \item The CQV phenomenon persists for at least 150\,Myr, based on
+    the existence of multiple CQVs in AB Dor, the Pleiades, and
+    Psc-Eri.  It may extend to even older ages, however the lack of
+    detected CQVs in the Hyades and Praesepe suggests that the
+    lifetime of the phenomenon may be limited to the first few hundred
+    million years.
+	%
   \item The duty cycle for CQVs seems to be $\approx 75$\%, based on
@@
   %
-\end{itemize}
+  \item Observed CQVs span a stellar mass range of 0.1-0.8\,M$_\odot$ (Section~\ref{subsec:extreme}).
+\end{enumerate}
 
@@
 a few stellar radii away from their surfaces?  What observational
-signatures distinguish the proposed models (Figure~\ref{fig:f1},
-bottom row)?  What organizational regularities characterize the CQV as
-a class of variable star?  What physically sets the extremes of the
+signatures distinguish the proposed models?
+What physically sets the extremes of the
 CQV population, such as the longest rotation periods, hottest stellar
@@
 if any, do CQVs have to topics such as stellar evolution, M-dwarf
-magnetic fields, debris disks, and close-in exoplanets?  While we have
-tried to point out possible connections, the most likely path toward
-definitive resolutions would be to observe a full phase curve of LP
-12-502, or perhaps some other suitable object, using JWST/MIRI.
-
-{\bf lgb: final paragraph(s) clearly need improvement!}
+magnetic fields, debris disks, and close-in exoplanets?  
+Additional theoretical work could help in resolving many of these questions,
+and would contain rich puzzles in plasma physics, MHD, and radiative transfer, in
+addition to the dynamos of young, fully-convective stars.
+
+On the observational front, expanding our analysis of the TESS data to the full frame images
+could yield a truly volume-limited selection function, and would
+expand the CQV census within 50\,pc by about a factor of two.
+Out to larger volume (e.g.~200\,pc), the yield boost would be more
+than an order of magnitude.
+While such studies would be important for improving our understanding
+of CQV population demographics,
+independent programs aimed at acquiring
+mid- and high-resolution time-series spectroscopy hold the best chance
+at detecting
+either gas or dust absorption signatures over the span of any
+given CQV cycle.
+The challenges intrinsic to such observations seem worth the effort.
 
@@
 pipeline.
-GRR is an architect of the TESS mission, and advised RJ on his contributions.
+GRR is an architect of the TESS mission.
 All authors assisted in manuscript revision.
@@
 
+\clearpage
+
 \bibliographystyle{yahapj}                            
@@
 \appendix
-\section{Validation plots}
-\label{app:vetting}
-
-Figure~\ref{fig:vet} shows the type of plot used to visually assess
-whether a source was likely to be a CQV, eclipsing binary, or simply a
-rapidly rotating star.
-
-\begin{figure*}[!t]
-	\begin{center}
-    \centering
-    \includegraphics[width=0.96\textwidth]{annotated_402980664_S0018_120sec_CQVvetter.pdf}
-		\vspace{-0.45cm}
-		\caption{
-      {\bf Validation plots used to manually label CQVs}.  The complete figure
-      set, with one image per sector for each of \nCQVsfound\ CQVs
-      and candidate CQVs
-      is available online {\bf For internal collaboration review:
-      \url{https://www.dropbox.com/scl/fo/zlj3txot4cvymfb22wewu/h?dl=0&rlkey=3ec5f9o5xewrixzfkhkdenopa}}.
-      Panels are as follows.
-      {\it a)}: Phase-folded light curve; gray points are raw 2-minute
-      data and black points are binned to 200 points per cycle.
-      {\it b)}: Phase-dispersion minimization (PDM) periodogram.
-      Dotted lines show up to the 10$^{\rm th}$ harmonic and
-      subharmonic.
-      {\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
-      circles displayed for scale.
-      {\it d)}: Cleaned light curve, binned to 20-minute cadence, in
-      Barycentric TESS Julian Date (BTJD).
-      {\it e)}: Phase-folded light curve, binned to 100 points per
-      cycle.  The gray line denotes the automated spline-fit to the
-      wrapped phase-folded light curve, and small gray triangles
-      denote automatically identified local minima.
-      {\it f)}: Phase-folded light curve at twice the peak period.
-      {\it g)}: Phase-folded light curve at half the peak period.
-      {\it h)}: Phase-folded time-series within the ``background''
-      aperture defined in the SPOC light curves.
-      {\it i)}: Phase-folded flux-weighted centroid in the column
-      direction.
-      {\it j)}: Phase-folded flux-weighted centroid in the row
-      direction.
-      {\it k)}: Gaia DR2 color--absolute magnitude diagram.     
-      The gray background denotes stars within 100\,pc.
-      {\it l)}: Information from Gaia DR2, TIC8, and the automated
-      dip-counting search pipeline.  ``Neighbors'', abbreviated
-      ``nbhr'', are listed within apparent distances of 2 TESS pixels
-      if $\Delta T$$<$2.5.
-      {\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
-      using positions, proper motions, and the parallax.
-      }
-		\label{fig:vet}
-	\end{center}
-\end{figure*}
+%\section{Validation plots}
+%\label{app:vetting}
+%
+%Figure~\ref{fig:vet} shows the type of plot used to visually assess
+%whether a source was likely to be a CQV, eclipsing binary, or simply a
+%rapidly rotating star.
+%
+%\begin{figure*}[!t]
+%	\begin{center}
+%    \centering
+%    \includegraphics[width=0.96\textwidth]{annotated_402980664_S0018_120sec_cpvvetter.pdf}
+%		\vspace{-0.45cm}
+%		\caption{
+%      {\bf Validation plots used to manually label CQVs}.  The complete figure
+%      set, with one image per sector for each of \ncpvsfound\ CQVs
+%      and candidate CQVs
+%      is available online {\bf For internal collaboration review:
+%      \url{https://www.dropbox.com/scl/fo/zlj3txot4cvymfb22wewu/h?dl=0&rlkey=3ec5f9o5xewrixzfkhkdenopa}}.
+%      Panels are as follows.
+%      {\it a)}: Phase-folded light curve; gray points are raw 2-minute
+%      data and black points are binned to 200 points per cycle.
+%      {\it b)}: Phase-dispersion minimization (PDM) periodogram.
+%      Dotted lines show up to the 10$^{\rm th}$ harmonic and
+%      subharmonic.
+%      {\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
+%      circles displayed for scale.
+%      {\it d)}: Cleaned light curve, binned to 20-minute cadence, in
+%      Barycentric TESS Julian Date (BTJD).
+%      {\it e)}: Phase-folded light curve, binned to 100 points per
+%      cycle.  The gray line denotes the automated spline-fit to the
+%      wrapped phase-folded light curve, and small gray triangles
+%      denote automatically identified local minima.
+%      {\it f)}: Phase-folded light curve at twice the peak period.
+%      {\it g)}: Phase-folded light curve at half the peak period.
+%      {\it h)}: Phase-folded time-series within the ``background''
+%      aperture defined in the SPOC light curves.
+%      {\it i)}: Phase-folded flux-weighted centroid in the column
+%      direction.
+%      {\it j)}: Phase-folded flux-weighted centroid in the row
+%      direction.
+%      {\it k)}: Gaia DR2 color--absolute magnitude diagram.     
+%      The gray background denotes stars within 100\,pc.
+%      {\it l)}: Information from Gaia DR2, TIC8, and the automated
+%      dip-counting search pipeline.  ``Neighbors'', abbreviated
+%      ``nbhr'', are listed within apparent distances of 2 TESS pixels
+%      if $\Delta T$$<$2.5.
+%      {\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
+%      using positions, proper motions, and the parallax.
+%      }
+%		\label{fig:vet}
+%	\end{center}
+%\end{figure*}
 

### 2023-07-03 paper/collect.sh

@@ -16,3 +16,6 @@ cp $resultsdir/tic4029_segments/tic4029_segments.pdf f4.pdf
 
 # fig5
 cp $resultsdir/phase_timegroups_mosaic/TIC_402980664/TIC_402980664_P18.5611_2min_phase_timegroups_mosaic_ymin-4.8_ymax3.pdf f5.pdf
+
+# fig6
+cp $resultsdir/catalogscatter/catalogscatter_showmaybe.pdf f6.pdf

### 2023-07-03 tests/test_identify_outliers.py
add test_identify_outliers z-score

@@ -1,0 +1,41 @@
+import numpy as np
+
+def identify_outliers(array, threshold=0.8):
+    """
+    Identifies outliers in an array of floats using a majority consensus style veto.
+
+    Args:
+        array (numpy.ndarray or list): The input array of floats.
+        threshold (float, optional): The threshold for outlier identification. Defaults to 0.8.
+
+    Returns:
+        numpy.ndarray: A boolean mask indicating the outliers in the input array.
+    """
+    array = np.array(array)
+    mean = np.mean(array)
+    std = np.std(array)
+    z_scores = (array - mean) / std
+
+    consensus_threshold = int(threshold * len(array))
+    outlier_mask = np.abs(z_scores) > 1
+
+    while np.sum(outlier_mask) > consensus_threshold:
+        array = array[~outlier_mask]
+        mean = np.mean(array)
+        std = np.std(array)
+        z_scores = (array - mean) / std
+        outlier_mask = np.abs(z_scores) > 1
+
+    final_mask = np.zeros_like(z_scores, dtype=bool)
+    final_mask[np.abs(z_scores) > 1] = True
+
+    return final_mask
+
+
+print(identify_outliers(np.array([1, 1, 2])))
+
+print(identify_outliers(np.array([1, 1])))
+
+print(identify_outliers(np.array([1, 1, 1, 1, 1])))
+
+print(identify_outliers(np.array([1, 1, 1, 1, 1.01])))

### 2023-07-05 paper/ms.tex
update ms

@@
 % primary authors
-\author{Author list and order not final!}
+\author{Author list \& order not final!}
 \author[0000-0002-0514-5538]{Luke~G.~Bouma}
@@
 Such structures are analogous to quiescent prominences and filaments
-observed in the solar corona \citep[see e.g.][]{2015ASSL..415.....V},
+seen in the solar corona \citep[see e.g.][]{2015ASSL..415.....V},
 though at much larger relative distances from the stellar surface.  A
@@
 
-One way to help rule between the mechanisms is to therefore find
-bright and nearby CQVs, since these objects will be the most amenable
-to detailed photometric and spectroscopic analyses.  To do this, in
-this work, we use 120-second cadence data acquired by TESS between
-July~2018 and Sep~2022 (Sectors 1-55; Cycles 1-4).  We present our
-search methods in Section~\ref{sec:methods}, and the properties of the
-resulting CQV catalog in Section~\ref{sec:results}.  The evolution of
-many CQVs over a two-year baseline is described in
-Section~\ref{sec:evoln}, including a deep-dive into LP 12-502.
-Implications are discussed in Section~\ref{sec:discussion}, and we
-conclude in Section~\ref{sec:conclusion}.
+One way to help rule between the mechanisms is to find bright and
+nearby CQVs, since these objects will be the most amenable to detailed
+photometric and spectroscopic analyses.  To do this, in this work we
+use 120-second cadence data acquired by TESS between July~2018 and
+Sep~2022 (Sectors 1-55; Cycles 1-4).  We present our search methods in
+Section~\ref{sec:methods}, and the properties of the resulting CQV
+catalog in Section~\ref{sec:results}.  The evolution of many CQVs over
+a two-year baseline is described in Section~\ref{sec:evoln}, including
+a deep-dive into LP 12-502.  Implications are discussed in
+Section~\ref{sec:discussion}, and we conclude in
+Section~\ref{sec:conclusion}.
 
@@
 \citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
-and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  
-The CQVs should generally not be conflated with ``dippers'', which are classical T
-Tauri stars with infrared excesses, and drastically and 
-at best marginally periodic variability linked
-to obscuring inner disk structures and accretion hot spots
-\citep{2014AJ....147...82C,2021ApJ...908...16R}.  
-With that said, a few similarities between CQVs and dippers do exist
-(see Sections~\ref{subsec:irexcess} and~\ref{subsec:discdippers}).
-At the risk of
-introducing yet another standard, we prefer a nomenclature that
-reflects how, when observed over timescales of more than tens of
-cycles, CQVs are almost but not exactly periodic.  They are
-irregularly periodic, or for short, quasiperiodic.  While the
-three-type classification scheme proposed by
-\citet{2017AJ....153..152S} may indeed provide some helpful visual
-distinctions amongst CQV sub-classes, it seems likely that they are
-all explained by a single underlying phenomenon, and so we opt to
-refer to them by a single empirically descriptive name.
+and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  The
+CQVs should not be conflated with ``dippers'', which are classical T
+Tauri stars with infrared excesses, and large-amplitude variability
+linked to obscuring inner disk structures and accretion hot spots
+\citep{2014AJ....147...82C,2021ApJ...908...16R}.  With that said, a
+few similarities between CQVs and dippers do exist (see
+Sections~\ref{subsec:irexcess} and~\ref{subsec:discdippers}).  At the
+risk of introducing yet another standard, we hope to introduce a
+nomenclature that reflects how, when observed over timescales of more
+than tens of cycles, CQVs are almost but not exactly periodic.  They
+are quasiperiodic.  While the three-type classification scheme
+proposed by \citet{2017AJ....153..152S} may indeed provide some
+helpful visual distinctions amongst CQV sub-classes, it seems likely
+that they are all explained by a single underlying phenomenon, and so
+we opt to refer to them by a single empirically descriptive name.
 
@@
 
-We determined the stellar effective temperature and radii through SED
-fitting; we then estimated the masses by interpolating against the
+We determined the stellar effective temperature and radii by 
+fitting the broadband spectral energy distributions (SEDs); we then estimated the masses by interpolating against the
+sizes, temperatures, and ages against the
 PARSEC v1.2S models \citep{2012MNRAS.427..127B,2014MNRAS.444.2525C}.

### 2023-07-07 paper/ms.tex
update ms

@@
 		\caption{
-      {\bf Properties of CQVs from our serach}.
+      {\bf Properties of CQVs from our search}.
       The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are 
@@
 ultimately conclude that these sources are dippers.  This episode
-suggests that could be some overlap between the two classes of
+suggests that there could be overlap between the two classes of
 object.  It is also worth emphasizing that our labeling of
@@
 can show transient flux dips that are relatively narrow in duration.
-Such dips in both are probably associated with clumps of dust or gas.
-However the CQV dips are typically {\it i)} more periodic and {\it
-ii)} less deep than those of dippers, and {\it iii}) they display far
+The dips in both are probably associated with clumps of dust or gas.
+However the CQV dips are typically more periodic and 
+less deep than those of dippers, and they display far
 less transience over timescales of a few to tens of cycles.  This is
@@
 cloud}\ll R_\star$.  Carrying out the relevant calculation assuming
-a dust composition, for dust grains 1\,$\mu$m in size,
+the occulting material is dust grains 1\,$\mu$m in size,
 \citet{2023MNRAS.518.4734S} find minimum cloud masses of order

### 2023-07-08 paper/ms.tex
update ms

@@
   $d$$<$150\,pc yielded \ngoods\ gold-standard CQVs.  Most of these
-  discoveries are new, and they include the brightest and closest
-  examples of this class of object known ($T$$\approx$9.5;
-  $d$$\approx$20\,pc), as well as the most massive
+  discoveries are new, and they include the brightest
+  ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc)
+  examples of this class of object known, as well as the most massive
   ($\approx$0.65\,M$_\odot$).  A few objects are outliers among
@@
 		{\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
-		stacked over one month.  Gray are raw 2-minute data; black bins to
+		stacked over one month.  Gray circles are raw 2-minute data; black
+    circles bin to
 		300 points per cycle.  Periods in hours are in the bottom right of
@@
 		\centering
-		\includegraphics[width=\textwidth]{f2.pdf}
-    \vspace{-0.7cm}
+		\includegraphics[width=0.98\textwidth]{f2.pdf}
+    \vspace{-0.3cm}
 		\caption{
@@
 confirmed \ngoods\ CQVs in our catalog; for plotting purposes we show
-the brightest 27.  Of these 27 CQVs, a few show clear signs of the
-phenomenon in one sector, and marginal or non-existence signs in the
-other.  While there is some subjectivity in this assessment, to our
+the brightest 27.  
+We have phased each sector to its own local minimum because for most of the
+sources we do not know the period at the precision necessary to be able to
+accurately propagate it over two years.
+
+Of these 27 CQVs in Figure~\ref{fig:evoln}, a few show clear signs of the
+CQV phenomenon in one sector, and marginal or non-existence signs in the
+other.  While there is subjectivity in this assessment, to our
 eyes cases for which at least one sector would be flagged as
@@
       clarify shape changes.
+      Gray circles are raw 2-minute data; colored circles bin to 300
+      points per cycle. 
 		}
@@
 		\centering
-		\includegraphics[width=\textwidth]{f4.pdf}
-		\vspace{-0.4cm}
+		\includegraphics[width=0.98\textwidth]{f4.pdf}
+		\vspace{-0.35cm}
 		\caption{
@@
       in the shape of the dip pattern.  The light curve is binned to
-      15-minute intervals so that there are 96 points per day.  Data
-      gaps with more than one missing 15-minute cadence appear in
-      white.
+      15-minute intervals so that there are 96 points per day, and each
+      point is connected by a line.  
+      Data gaps longer than one missing 15-minute are not
+      interpolated; if data are missing, nothing is plotted.
 		}
@@
 		\includegraphics[width=\textwidth]{f5.pdf}
-		\vspace{-0.45cm}
+		\vspace{-0.6cm}
 		\caption{
@@
 \subsection{Mass flux estimate}
+\label{subsec:massflux}
 
@@
 
-In this work, we analyzed TESS 120-second cadence data collected
-between July~2018 and Sep~2022, and searched it for complex
-quasiperiodic variables (CQVs).  Our search sample included
-\nstarssearched\ K- and M-dwarfs within 150\,pc, and was $\gtrsim
-80\%$ complete within 30\,pc, and $\lesssim 10\%$ complete at
-distances exceeding 100\,pc.
+In this work, we searched 120-second cadence TESS data collected
+between July~2018 and Sep~2022 for complex quasiperiodic variables
+(CQVs).  Our search sample included \nstarssearched\ K- and M-dwarfs
+within 150\,pc, and was $\gtrsim 80\%$ complete within 30\,pc, and
+$\lesssim 10\%$ complete at distances exceeding 100\,pc.
 
@@
 
-Analyzing the CQV light curves, we draw the following conclusions.
+Analyzing the TESS light curves and stellar properties of this sample
+of objects, we draw the following conclusions.
 
@@
   \item CQVs are {\it quasi}periodic.  While the mean periods in our
-    sample seem to remain fixed over the span of available
-    observations, the light curve shapes themselves evolve, similar to
-    rotating stars.
+    sample remain fixed over the baseline of available
+    observations, the light curve shapes always evolve over timescales
+    of thousands of cycles (Figure~\ref{fig:evoln}).
   %
@@
     distinct periods within $\pm 0.3\%$ of its fundamental period,
-    sometimes simultaneously, and each lasting for up to 50 cycles.
+    sometimes simultaneously, and each lasting for up to 50 cycles
+    (Figure~\ref{fig:lpriver0}).
   %
@@
     constraint on amount of material that is either being accreted or ejected
-    during the state changes.
+    during the state changes (Section~\ref{subsec:massflux}).
     Order of magnitude estimates require at least an asteroid belt's worth
-    of dust ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or a factor of 100
-    larger if the material is gas.
+    of dust ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or 100 times more 
+    material if the occulting matter is gas.
   %
-  \item The CQV phenomenon persists for at least 150\,Myr, based on
+    \item The CQV phenomenon persists for $\gtrsim$150\,Myr, based on
     the existence of multiple CQVs in AB Dor, the Pleiades, and
-    Psc-Eri.  It may extend to even older ages, however the lack of
-    detected CQVs in the Hyades and Praesepe suggests that the
-    lifetime of the phenomenon may be limited to the first few hundred
-    million years.
+    Psc-Eri (Section~\ref{subsec:starprops}).  It may extend to even
+    older ages, however the lack of detected CQVs in the Hyades and
+    Praesepe suggests that the lifetime of the phenomenon may be
+    limited to the first few hundred million years.
 	%
@@
   %
-  \item Observed CQVs span a stellar mass range of 0.1-0.8\,M$_\odot$ (Section~\ref{subsec:extreme}).
+    \item Observed CQVs span a stellar mass range of 0.1-0.8\,M$_\odot$
+    (Section~\ref{subsec:extreme}).
+  %
+    \item The closest CQVs to the Sun are at distances of 15-20\,pc, and
+    the brightest CQVs have $V$$\approx$12 ($J$$\approx$7.5).  This
+    conclusion is an extrapolation from the CQV sample derived in this work
+    being $\gtrsim$80\% complete within 20\,pc.  Expanding our analysis of
+    the TESS data to the full frame images would yield a truly
+    volume-limited selection function, and would expand the CQV census
+    by about a factor of two within 50\,pc, and by a factor of ten
+    within 100\,pc.
 \end{enumerate}
 
-Many questions remain.  Is the eclipsing material responsible for the
-phenomenon gas, or dust?  After correcting for line-of-sight
-inclination, do most M-dwarfs go through a phase of trapping material
-a few stellar radii away from their surfaces?  What observational
-signatures distinguish the proposed models?
-What physically sets the extremes of the
-CQV population, such as the longest rotation periods, hottest stellar
-temperatures, and oldest stellar ages?  And finally, what connections,
-if any, do CQVs have to topics such as stellar evolution, M-dwarf
-magnetic fields, debris disks, and close-in exoplanets?  
-Additional theoretical work could help in resolving many of these questions,
-and would contain rich puzzles in plasma physics, MHD, and radiative transfer, in
-addition to the dynamos of young, fully-convective stars.
-
-On the observational front, expanding our analysis of the TESS data to the full frame images
-could yield a truly volume-limited selection function, and would
-expand the CQV census within 50\,pc by about a factor of two.
-Out to larger volume (e.g.~200\,pc), the yield boost would be more
-than an order of magnitude.
-While such studies would be important for improving our understanding
-of CQV population demographics,
-independent programs aimed at acquiring
-mid- and high-resolution time-series spectroscopy hold the best chance
-at detecting
-either gas or dust absorption signatures over the span of any
-given CQV cycle.
-The challenges intrinsic to such observations seem worth the effort.
+While many questions remain, two in particular will be 
+important for clarifying what these objects might teach us in a
+broader astrophysical context: {\it 1)} Is the eclipsing material
+responsible for the phenomenon gas or dust?  {\it 2)} What sets
+the characteristic clumping size for the circumstellar material?
+
+The distinction between gas or dust is important because it will
+clarify whether the CQV phenomenon is intrinsic, so that the material
+comes from the star, or extrinsic, so that it is sourced through some
+generic evolutionary phase of circumstellar disks.  This knowledge would in
+turn propagate to our understanding of whether observing the
+phenomenon is primarily teaching us about e.g.~dust production and
+processing in circumstellar disks, or whether it is teaching us about
+the ability of cold gas to remain stable in hot stellar coronae for
+long durations.
+Observationally, acquisition of medium- or high-resolution time-series
+spectroscopy holds the best chance at resolving the gas vs.~dust
+question.  Given the observed evolutionary timescales, such data
+should be acquired simultaneously with photometric time-series
+observations to help clarify its interpretation.
+
+In both the gas and dust scenarios, CQVs are preferentially viewed
+edge-on.
+This implies that after correcting for the line-of-sight inclination,
+it seems plausible that a sizable fraction of low mass stars (at
+least one third; \citealt{2022AJ....163..144G}) trap circumstellar
+material but are not observed in transit.
+In addition, CQVs should preferentially show edge-on
+transiting planets, at larger distances from the star than the
+corotating material.
+Given the interest level inherent to both of these points, important follow-up
+observational work also includes searching for outer transiting
+planets, and also measuring equatorial velocities in
+order to test whether the stellar inclination angles are indeed
+preferentially edge-on.
+
+On the theoretical front,
+building a physical understanding what sets the characteristic size
+scale of the clumping material would help clarify the nature of
+the magnetic and plasma environments around these young stars, 
+and would also help build intuition for why the light curves have the
+bizarre shapes that are observed.
+It is certainly possible that the relevant puzzles in plasma physics
+and radiative transfer could also be connected to our
+understanding of the close-in rocky planets that are expected to be
+present around most of these stars.
+The challenges intrinsic to both the observational and theoretical
+work seem worth the effort.
 
@@
 26) and G04168 (PI: R.~Jayaraman; Sector 53).
+While many conversations helped encourage this work,
+a few thank-yous in particular (from LGB) 
+are owed to G.~Laughlin, A.~Mann, L.~Rebull, and J.~Spake for clarifications and ideas.
 
@@
 LAH advised on project scope and experiment design.
-GAB acquired and maintained the servers used to run the dip-finding
+G\'AB acquired and maintained the servers used to run the dip-finding
 pipeline.

### 2023-07-10 paper/ms.tex
update ms
update ms (add table)

@@
 
-Table~\ref{tab:thetable} lists the \ncpvsfound\ CQVs identified by our
-search, along with important physical and observational properties.
-\ngoods\ objects demonstrated what we viewed as unambiguous
-characteristics of the CQV phenomenon in at least one TESS sector; we
-refer to these as the ``gold sample''.  We found the remaining
-\nmaybes\ CQV candidates to be ambiguous; their variability might be
-caused by say, multiple starspot groups.  Additional data from TESS or
-other instruments could help resolve their classification.  In the
-following discussion, we will primarily restrict our discussion to the
-gold sample.
+Table~\ref{tab:thetable} lists the \ncpvsfound\ objects identified by
+our search.  \ngoods\ objects demonstrated what we viewed as
+unambiguous characteristics of the CQV phenomenon in at least one TESS
+sector; we refer to these as the ``gold sample''.  We found the
+remaining \nmaybes\ CQV candidates to be ambiguous; their variability
+might be caused by say, multiple starspot groups.  Additional data
+from TESS or other instruments could help resolve their
+classification.  The boolean \texttt{quality} column in the table divides
+the two classes.  In the following discussion, we will restrict our
+discussion to the gold sample.
 
@@
       point is connected by a line.  
-      Data gaps longer than one missing 15-minute are not
+      Data gaps longer than 15-minutes are not
       interpolated; if data are missing, nothing is plotted.
@@
 \bibliography{bibliography}
+
+\clearpage
+
+\startlongtable
+\begin{deluxetable}{rrrrrrlrllrrrr}
+\tabletypesize{\footnotesize}
+%\tabletypesize{\scriptsize}
+\tablecaption{Complex quasiperiodic variables identified in the TESS 2-minute data. \label{tab:thetable}}
+%\toprule
+%TIC & $T$ & $d$ & BP-RP & RUWE & $P$ & assoc & age & teff & rstar & mstar & rcr & qual & Nsectors \\
+%\midrule
+%\endhead
+\startdata
+TIC & $T$ & $d$ & $\bprp$ & RUWE & $P$ & Assoc & Age & $T_{\rm eff}$ & $R_\star$ & $M_\star$ & $R$$_{\rm cr}$ & Quality & $N_{\rm sector}$ \\
+-- & mag & pc & mag & -- & hr & -- & Myr & K & $R_\odot$ & $M_\odot$ & $R_\star$ & -- & -- \\
+\hline
+\input{20230613_LGB_RJ_CPV_TABLE_selfnapplied_rounded_data}
+\enddata
+\tablecomments{This table includes \ngoods\ CQVs (\texttt{Quality} flag true), and \nmaybes\ candidate CQVs (\texttt{Quality} flag false).
+The machine-readable version, available online, includes additional columns for the Gaia DR2 source identifiers and parameter uncertainties.
+The age uncertainties are typically $\approx \pm 10\%$,
+	but can be asymmetric.  The median temperature, radius, and mass uncertainties are $\pm XXX$\,K, $\pm XX$\%, and $\pm YY$\% respectively.
+	$N_{\rm sector}$ denotes the number of TESS sectors for which data are expected to be acquired between July~2018 and Oct~2024.
+Association names and provenance follow conventions adopted by \citet{2018ApJ...856...23G}:
+	ABDMG: AB~Doradus moving group \citep{2015MNRAS.454..593B}.
+	ARG: Argus \citep{2019ApJ...870...27Z}.
+	APER: $\alpha$~Persei open cluster \citep{2023AJ....166...14B}.
+	BPMG: $\beta$~Pic moving group \citep{2015MNRAS.454..593B}.
+	CAR: Carina \citep{2015MNRAS.454..593B}.
+	COL: Columba \citep{2015MNRAS.454..593B}.
+	EPSC: $\epsilon$ Chamaeleontis \citep{2013MNRAS.435.1325M}.
+	LCC: Lower Centaurus Crux \citep{2016MNRAS.461..794P}.
+	PERI: Pisces-Eridani \citep{2019AJ....158...77C}.
+	PLE: Pleiades \citep{2015ApJ...813..108D}.
+	TAU: Taurus \citep{1995ApJS..101..117K}.
+	THA: Tucana-Horologium assocation \citep{2015MNRAS.454..593B}.
+	TWA: TW Hydrae assocation \citep{2015MNRAS.454..593B}.
+	UCL: Upper Centaurus Lupus \citep{2016MNRAS.461..794P}.
+	USCO: Upper Scorpius \citep{2016MNRAS.461..794P}.
+}
+\end{deluxetable}
+\clearpage
 

### 2023-07-10 complexrotators/observability.py
add latex table writer

@@ -491,8 +491,6 @@ def get_bestmonth_hoursobservable(
     return outdf
 
 
-
-
 def merge_to_observability_table(
     csvpath, r_gaia, r_tess, r_tic8, r_tesspoint, r_astroplan
     ):

### 2023-07-10 drivers/make_cpv_table.py

@@ -99,6 +99,8 @@ def main(overwrite=0):
     N_0 = len(df)
     sdf = df[sel]
 
+    sdf['qual'] = ~pd.isnull(sdf.goodsectors)
+
     csvpath = join(indir, "20230613_LGB_RJ_CPV_TABLE_supplemental_selfnapplied.csv")
     sdf.to_csv(csvpath, index=False, sep="|")
     print(f"Wrote {csvpath}")
@@ -108,6 +110,7 @@ def main(overwrite=0):
     N_3 = len(sdf[pd.isnull(sdf.goodsectors)])
 
     # "good" CPVs
+
     sgdf = sdf[~pd.isnull(sdf.goodsectors)]
     # "maybe" CPVs
     smdf = sdf[pd.isnull(sdf.goodsectors)]
@@ -125,16 +128,6 @@ def main(overwrite=0):
 
     N_6 = len(sgdf[sgdf.banyan_assoc != 'FIELD'])
     N_7 = len(smdf[smdf.banyan_assoc != 'FIELD'])
-
-    selcols = (
-        "ticid goodsectors maybesectors N_sectors tic8_Tmag ruwe "
-        "bp_rp tlc_mean_period banyan_assoc banyan_prob".split()
-    )
-
-    # TODO: write these numbers to latex
-    # \renewcommand{}{}
-    # type include file at /paper/
-    # TODO
 
     txt = (
         f"\n...\n"
@@ -172,6 +165,84 @@ def main(overwrite=0):
         f.writelines(latex_txt)
     print(f"Wrote {outpath}")
 
+    # write portion that will go to latex
+    sdf['period'] = sdf['tlc_mean_period']*24
+    sdf['age'] = sdf['banyan_adopted_age']
+    sdf['assoc'] = sdf['banyan_adopted_assoc']
+    sdf['p_assoc'] = sdf['banyan_adopted_prob']
+    sdf['quality'] = sdf['qual'].astype(int)
+    shortcols = (
+        "ticid "
+        #"dr2_source_id ra dec "
+        "tic8_Tmag dist_pc "
+        "bp_rp ruwe period assoc "
+        #"banyan_prob"
+        "age teff_sedfit "
+        "rstar_sedfit mstar_parsec Rcr_over_Rstar  "
+        "quality N_sectors".split()
+    )
+    longcols = (
+        "ticid "
+        "dr2_source_id ra dec "
+        "tic8_Tmag dist_pc "
[…]

### 2023-07-10 drivers/make_cpv_table.py
update APER case in table

@@ -264,6 +264,8 @@ def get_banyan_result(gdr2_df):
     sys.path.append("/Users/luke/Dropbox/proj/banyan_sigma")
     from core import membership_probability
 
+    dr2_source_id = str(gdr2_df.dr2_source_id.iloc[0])
+
     ra, dec = float(gdr2_df.ra), float(gdr2_df.dec)
     pmra, pmdec = float(gdr2_df.pmra), float(gdr2_df.pmdec)
     epmra, epmdec = float(gdr2_df.pmra_error), float(gdr2_df.pmdec_error)
@@ -319,6 +321,17 @@ def get_banyan_result(gdr2_df):
                 adopted_prob = probs
                 adopted_age_float = agefloatvals
                 adopted_age_ref = age_refs
+
+    # alpha per case
+    if dr2_source_id == '438223592047536640':
+        assocs = 'APER'
+        adopted_assoc = 'APER'
+        banyan_prob = 0
+        adopted_prob = 1
+        ages = '$86 \pm 14$'
+        adopted_age_float = 86
+        age_refs = 'BoyleBouma2023'
+        adopted_age_ref = 'BoyleBouma2023'
 
     bdf = pd.DataFrame({
         'banyan_assoc': assocs,

### 2023-07-11 paper/ms.tex
update ms

@@
   Our search of \nstarssearched\ K- and M-dwarfs with $T$$<$16 and
-  $d$$<$150\,pc yielded \ngoods\ gold-standard CQVs.  Most of these
+  $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most of these
   discoveries are new, and they include the brightest
@@
   examples of this class of object known, as well as the most massive
-  ($\approx$0.65\,M$_\odot$).  A few objects are outliers among
+  ($\approx$0.6-0.8\,M$_\odot$).  A few objects are outliers among
   outliers; LP 12-502 for instance shows a ``dip complex'' with a
@@
   local minima per cycle.  LP-502 also displayed distinct superposed
-  periods simultaneously, and displayed drastic shape changes shortly
+  periods simultaneously, and showed drastic shape changes shortly
   after flares.  Broadly speaking, we find that none of the CQVs
@@
   evolution implies that of order an asteroid belt's worth of mass
-  passes through these structures over the $10^8$ years for which they
-  are observed.
+  passes through these structures over their lifetime of $10^8$ years.
 \end{abstract}
@@
 A few competing explanations for what causes the complex quasiperiodic
-variability are shown in Figure~\ref{fig:f1}, along with some
-representative light curves.  All young M-dwarfs are spotted, which
+variability are shown in Figure~\ref{fig:f1}.  All young M-dwarfs are spotted, which
 produces flux variations over characteristic timescales of the
@@
 extending an order of magnitude longer than the $\approx$$10^7$ year
-timescale typically quoted for the primordial disk to disperse.
-However, unambiguous evidence has yet to be acquired in support of any
-scenario.  Such evidence might include a spectroscopic detection of
-silicate 10\,$\mu$m dust absorption during a dip, or perhaps detection
-of transient Balmer-line absorption during the dips, similar to
-observations made in systems such as AB~Dor \citep[see the review
-by][]{1999ASPC..158..146C}.
+timescale typically quoted for primordial disk dispersal.
+However, unambiguous evidence in support of any one scenario has yet
+to be acquired.  Such evidence might include a spectroscopic detection
+of silicate 10\,$\mu$m dust absorption during a dip, or perhaps
+detection of transient Balmer-line absorption as a function of cycle
+phase, similar to observations made in systems such as AB~Dor
+\citep[see the review by][]{1999ASPC..158..146C}.
 
@@
 and hard to characterize.   Discoverability is tied to rarity: CQVs
-comprise about 1\% of the youngest 1\% of M-dwarfs
+comprise $\approx$1\% of the youngest $\approx$1\% of M-dwarfs
 \citep{2018AJ....155..196R}.  Out of the millions of stars monitored
@@
 $V$$\approx$15.5 to $V$$>$20.  This renders time-series spectroscopy
-at high resolution technically impossible, despite its potential
-utility in ruling between the models.
-
-One way to help rule between the mechanisms is to find bright and
-nearby CQVs, since these objects will be the most amenable to detailed
-photometric and spectroscopic analyses.  To do this, in this work we
-use 120-second cadence data acquired by TESS between July~2018 and
-Sep~2022 (Sectors 1-55; Cycles 1-4).  We present our search methods in
-Section~\ref{sec:methods}, and the properties of the resulting CQV
-catalog in Section~\ref{sec:results}.  The evolution of many CQVs over
-a two-year baseline is described in Section~\ref{sec:evoln}, including
-a deep-dive into LP 12-502.  Implications are discussed in
+at high resolution out of reach for current facilities, despite its
+potential utility in ruling between the models.
+
+In this work, we aim to find bright and nearby CQVs, since these
+objects will be the most amenable to detailed photometric and
+spectroscopic analyses.  To do this, we use 120-second cadence data
+acquired by TESS between July~2018 and Sep~2022 (Sectors 1-55; Cycles
+1-4).  We present our search methods in Section~\ref{sec:methods}, and
+the properties of the resulting CQV catalog in
+Section~\ref{sec:results}.  The evolution of many CQVs over a two-year
+baseline is described in Section~\ref{sec:evoln}, including a
+deep-dive into LP 12-502.  Implications are discussed in
 Section~\ref{sec:discussion}, and we conclude in
@@
 
-A word on nomenclature.  CQVs have been called ``transient and
-persistent flux dips'', ``scallop shells'', ``batwings'',
+A point on nomenclature.  CQVs have been called ``transient flux
+dips'', ``persistent flux dips'', ``scallop shells'', ``batwings'',
 \citep{2017AJ....153..152S} ``complex rotators'',
@@
 proposed by \citet{2017AJ....153..152S} may indeed provide some
-helpful visual distinctions amongst CQV sub-classes, it seems likely
+helpful visual distinctions amongst the CQVs, it seems likely
 that they are all explained by a single underlying phenomenon, and so
@@
 between July~2018 and Sep~2022 (Sectors 1-55).  Specifically, we used
-the 120-second cadence light curve products produced by the mission's
+the 120-second cadence light curve products produced by the 
 Science Processing and Operations Center at NASA Ames
@@
 unambiguous characteristics of the CQV phenomenon in at least one TESS
-sector; we refer to these as the ``gold sample''.  We found the
+sector; we refer to these as the ``high-quality sample''.  We found the
 remaining \nmaybes\ CQV candidates to be ambiguous; their variability
@@
 the two classes.  In the following discussion, we will restrict our
-discussion to the gold sample.
+discussion to the high-quality sample.
 
@@
 requiring the cloud to be optically thick.  For cases like LP 12-502,
-this is resonable because the transit duration implies $R_{\rm
+this is reasonable because the transit duration implies $R_{\rm
 cloud}\ll R_\star$.  Carrying out the relevant calculation assuming
@@
 $10^{12}$\,kg (their Eq.~23), which scale linearly with both the
-optical depth and dust grain radius.  This is roughly comparable to a
+optical depth and dust grain radius.  This is comparable to a
 small asteroid; the asteroid belt itself has a mass of
-order $\approx$10$^{21}$\,kg (CITE).  Also by way of comparison,
-the previously-discussed cool gas prominences for AB~Dor would need to
-have masses of order $10^{14}$\,kg \citep{1990MNRAS.247..415C}, about
+order $\approx$10$^{21}$\,kg (CITE).  
+The previously discussed cool gas prominences would need to have
+masses of order $10^{14}$\,kg \citep{1990MNRAS.247..415C}, about
 100$\times$ larger than the requisite dust mass.
@@
 showed three ``state-switch'' events over the six months of available TESS
-observations, during cycles 248-264, 299-315, and 1233-1247.  It is
+observations, during cycles 248-264, 299-315, and 1233-1247.  In each
+case, a dip ``turned off''.  It is
 plausible to imagine that these events correspond to either mass being
@@
 either case, the corresponding $\dot{M} \equiv M\cdot {\rm d}N/{\rm d}t$
+time-averaged over six months
 is $\approx$3$\times$$10^{-18} M_\odot\,{\rm yr}^{-1} \approx
@@
 order 100 times larger.
+For cases in which we observe the {\it growth} of
+dips, such as the Sector~29 data for TIC~224283342, the dip depths
+typically increase by of order a few percent over ten to twenty days.
+{\bf fixme: add closing sentence}
 

### 2023-07-12 paper/ms.tex
update ms

@@
 \usepackage{color}
+\usepackage{enumitem}
 
@@
 \newcommand{\princeton}{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}
+\newcommand{\esa}{European Space Agency (ESA), European Space Research and Technology Centre (ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, Netherlands}
 
@@
 % primary authors
-\author{Author list \& order not final!}
+\author{---AUTHOR LIST \& ORDER NOT FINAL}
 \author[0000-0002-0514-5538]{Luke~G.~Bouma}
@@
 
-% [to be confirmed after these]
+\author{Lynne~A.~Hillenbrand}
+\affiliation{\caltech}
+
+\author[0000-0001-7204-6727]{G\'asp\'ar \'A. Bakos}
+\affiliation{\princeton}
+
+\author{-----SUGGESTED CONTRIBUTORS, PENDING DISCUSSION, COMMENTS, ANALYSES, ETC-----}
+%
 \author{Saul~Rappaport}
@@
 
-\author{Lynne~A.~Hillenbrand}
+\author[0000-0001-6381-515X]{Luisa M. Rebull}
 \affiliation{\caltech}
+
+\author[0000-0002-3164-9086]{Maximilian N. G\"unther}
+\affiliation{\esa}
 
@@
 
-\author[0000-0001-7204-6727]{G\'asp\'ar \'A. Bakos}
+\author[0000-0002-4265-047X]{Joshua N. Winn}
 \affiliation{\princeton}
@@
   the Keplerian corotation radius.  Here, we report new CQVs
-  discovered in TESS data collected between July~2018 and Sep~2022.
+  discovered in TESS short-cadence data collected between July~2018 and Sep~2022.
   Our search of \nstarssearched\ K- and M-dwarfs with $T$$<$16 and
@@
   ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc)
-  examples of this class of object known, as well as the most massive
+  examples of this class of object known, and perhaps the most massive
   ($\approx$0.6-0.8\,M$_\odot$).  A few objects are outliers among
@@
   efforts aimed at understanding these objects, and connecting them to
-  the broader contexts of star, disk, and exoplanet evolution.  For
-  instance, if the transiting material is dust, then the rate of dip
+  the broader contexts of star, disk, and exoplanet evolution.
+  For instance, if the transiting material is dust, then the rate of dip
   evolution implies that of order an asteroid belt's worth of mass
@@
 		\caption{
-      {\bf Properties of CQVs from our search}.
+      {\bf Properties of CQVs identified by our search}.
       The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are 
       the black circles; \nmaybes\ candidate CQVs are gray circles.
-      The \nstarssearched\ target stars with 120-second cadence data
-      acquired by TESS between July~2018 and Sep~2022 are shown as the shaded background on the top panels,
-      where darker regions correspond to a larger relative number of observed stars.
+      The top panels show the \nstarssearched\ target stars with 120-second cadence data
+      as the shaded gray background;
+      darker regions correspond to a larger relative number of searched stars.
       {\bf lgb todo: P vs color needs Pleiades comparison}
@@
 Based on our reading of \citet[][Ch.~8]{1992oasp.book.....G}, it seems
-somewhat challenging to get neutral hydrogen to have this type of
+challenging to get neutral hydrogen to have this type of
 chromaticity.  Bound-bound absorption provides opacity only at narrow
@@
 
-\begin{enumerate}
+\begin{enumerate}[leftmargin=*]
 	%
@@
   %
-    \item Observed CQVs span a stellar mass range of 0.1-0.8\,M$_\odot$
-    (Section~\ref{subsec:extreme}).
+    \item While the majority of detected CQVs have masses of
+    0.1-0.5\,M$_\odot$, the upper mass limit for the CQV phenomenon
+    might extend into the K-dwarf regime ($<$$0.8$\,M$_\odot$).
+    TIC~405754448 and TIC~405910546, with masses of $\approx$0.8 and
+    $\approx$0.6 solar masses, are the two massive outliers
+    (Section~\ref{subsec:extreme}), and we encourage additional
+    scrutiny of these objects in future work.
   %
@@
     APASS \citep{2016yCat.2336....0H},
-		Gaia \citep{2018A&A...616A...1G,2018A&A...616A...1G},
+		Gaia \citep{2018A&A...616A...1G,2022arXiv220800211G},
     SDSS \citep{2000AJ....120.1579Y},
@@
 
-\clearpage
+%\clearpage
 
@@
 \appendix
+
 %\section{Validation plots}
@@
 
-\section{More neat plots}
+\section{More river plots}
 
@@
 current work.  However, this CQV was observed using MuSCAT2 on 2020
-December 12, 13, and 16, and the results are pertinent enough to the
-present work.
-{\bf todo: describe observations}.
+December 12, 13, and 16, and the results might be worth including in
+this study.
+{\bf todo: describe observations / decide whether to include!}.
 

### 2023-07-12 paper/ms.tex
update ms

@@
   ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc)
-  examples of this class of object known, and perhaps the most massive
+  examples of this class of object known, and perhaps also the most massive
   ($\approx$0.6-0.8\,M$_\odot$).  A few objects are outliers among
@@
   evolution implies that of order an asteroid belt's worth of mass
-  passes through these structures over their lifetime of $10^8$ years.
+  passes through these structures over their lifetime of $\approx$$10^8$ years.
 \end{abstract}
@@
 unambiguous characteristics of the CQV phenomenon in at least one TESS
-sector; we refer to these as the ``high-quality sample''.  We found the
-remaining \nmaybes\ CQV candidates to be ambiguous; their variability
+sector; we refer to these as the ``high-quality sample''.  The
+classification of the remaining \nmaybes\ CQV candidates was ambiguous; their variability
 might be caused by say, multiple starspot groups.  Additional data
@@
 14.5$<$$T$$<$15.0.  The fastest five have periods spanning
-3.6\,hr$<$$P$$<$6.2\,hr, while the slowest five span
+3.6\,hr$<$$P$$<$6.2\,hr, and the slowest five span
 27\,hr$<$$P$$<$38\,hr.
@@
 distinct from any binary phenomenology of which we are aware.
+Follow-up spectroscopy would be needed to definitively resolve this issue.
 
@@
 BANYAN\,$\Sigma$.  The relevant groups are listed in
-Table~\ref{tab:thetable}; their ages span $\approx$5-150\,Myr.  The
-most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  The yield
+Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  The
+most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CQVs
+were also identified in the Argus association
+\citep{2019ApJ...870...27Z}, which serves as an indirect line of
+evidence supporting the reality, and youth, of that group.  The yield
 in Sco-Cen is not particularly surprising, since Sco-Cen contains the
 majority of pre-main-sequence stars in the solar neighborhood.
-However it is certainly likely given the $\lesssim$$10\%$ completeness
-of TESS beyond 100\,pc that far more CQVs remains to be discovered in
+However, given the $\lesssim$$10\%$ completeness
+of TESS beyond 100\,pc, there are probably many more CQVs that remain to be discovered in
 Sco-Cen.  IC\,2602 and IC\,2391, which are located slightly beyond
-100\,pc, are an example of this completeness effect: no CQVs appear in
-those clusters from our search.
+100\,pc, are an example of this completeness effect: our search did
+not find any CQVs in those clusters.
 
@@
 photometrically elevated relative to the main sequence.  For instance,
-both were noted as being in the ``diffuse'' Class~III YSO population
-near the Sun by \citet{2021ApJ...917...23K}.
-
-Our catalog confirms that the CQV phenomenon persists for at least
-$\approx$150\,Myr.  Our catalog includes three $\approx$150\,Myr CQVs
-in AB~Dor \citep{2015MNRAS.454..593B}: TIC~288344202, TIC~332517282,
-and TIC~368129164.  There is also a $\approx$112\,Myr old Pleiades CQV
-(TIC~440725886; \citealt{2015ApJ...813..108D,CantatGaudin_2020}), and
-a similarly-aged Psc-Eri member (TIC~38539720;
-\citealt{2020A&A...639A..64R}).  To our best knowledge, TIC~332517282
-was the previous record-holder for oldest-known CQV
+both were noted by \citet{2021ApJ...917...23K} as being in the ``diffuse'' population
+of $<$50\,Myr stars near the Sun.
+
+Our search confirms that the CQV phenomenon persists for at least
+$\approx$150\,Myr.  Table~\ref{tab:thetable} includes three $\approx$150\,Myr CQVs
+in AB~Dor \citep{2015MNRAS.454..593B}, a $\approx$112\,Myr old Pleiades CQV
+\citep{2015ApJ...813..108D}, and
+a similarly-aged Psc-Eri member \citep{2020A&A...639A..64R}.  To our knowledge, TIC~332517282
+in AB~Dor was the previous record-holder for oldest-known CQV
 \citep{2019ApJ...876..127Z,2022AJ....163..144G}; at least one
-unambiguous case (EPIC~211070495) and a few other candidates were also
-previously known in the Pleiades \citep{2016AJ....152..114R}.  While
-we expect to have been sensitive to CQVs in the nearby Hyades
-($\approx$700\,Myr), again due to the specifics of the TESS 120-second
-selection function, we do not know at this time whether we would have
-been sensitive to such stars.
-
-Finally, six CQVs were identified in the recently confirmed Argus
-association \citep{2019ApJ...870...27Z}.  This serves as an indirect
-line of evidence supporting the reality, and youth, of that group.
+unambiguous CQV (EPIC~211070495) and a few other candidates were also
+previously known in the Pleiades \citep{2016AJ....152..114R}.
+
+The upper age limit for the CQV phenomenon may even reach 200\,Myr,
+based on the candidate membership of TIC~294328885 in the Carina Near
+moving group \citep{2006ApJ...649L.115Z}.  This group's age primarily
+rests on the lithium sequence of its G-dwarfs
+\citep{2006ApJ...649L.115Z}, which shows a coeval population
+of stars older than the Pleiades and younger than the 400\,Myr Ursa
+Major moving group.  It would interesting to improve the
+precision of the group's age measurement, for instance using
+gyrochronology of F, G or K members, in order to verify this point.
+
+%While
+%we expect to have been sensitive to CQVs in the nearby Hyades
+%($\approx$700\,Myr), again due to the specifics of the TESS 120-second
+%selection function, we do not know at this time whether we would have
+%been sensitive to such stars.
 
@@
 		\centering
-		\includegraphics[width=\textwidth]{f6.pdf}
-		\vspace{-0.45cm}
+		\includegraphics[width=0.9\textwidth]{f6.pdf}
+		\vspace{-0.2cm}
 		\caption{
@@
       The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are 
-      the black circles; \nmaybes\ candidate CQVs are gray circles.
+      the dark blue circles; \nmaybes\ candidate CQVs are light blue circles.
       The top panels show the \nstarssearched\ target stars with 120-second cadence data
@@
       darker regions correspond to a larger relative number of searched stars.
-      {\bf lgb todo: P vs color needs Pleiades comparison}
+      The lower-left panel compares the rotation--color distribution of the CQVs, and candidate CQVs, against the rotation
+      periods of K- and M-dwarfs in the Pleiades from \citet{2016AJ....152..114R}.
+      Note the scale change for the period $P$ from days to hours in the middle panel of the lower row.
 		}
@@
 For cases in which we observe the {\it growth} of
-dips, such as the Sector~29 data for TIC~224283342, the dip depths
+dips, such as the Sector~29 data for TIC~224283342,
+or Sector~5 of TIC~294328885,
+the dip depths
 typically increase by of order a few percent over ten to twenty days.
@@
 	%
-  \item CQVs are {\it quasi}periodic.  While the mean periods in our
-    sample remain fixed over the baseline of available
-    observations, the light curve shapes always evolve over timescales
-    of thousands of cycles (Figure~\ref{fig:evoln}).
+  \item CQVs are quasiperiodic.  The mean periods 
+    remain fixed over the $>$1{,}000-cycle baseline of available
+    observations; but the light curve shapes always evolve (Figure~\ref{fig:evoln}).
   %
@@
     however seems to happen over durations of at least ten cycles, and
-    slow dip decay also happens.
+    slow dip decay can also occur.
   %
@@
     the existence of multiple CQVs in AB Dor, the Pleiades, and
-    Psc-Eri (Section~\ref{subsec:starprops}).  It may extend to even
-    older ages, however the lack of detected CQVs in the Hyades and
-    Praesepe suggests that the lifetime of the phenomenon may be
-    limited to the first few hundred million years.
+    Psc-Eri (Section~\ref{subsec:starprops}).  It may even extend to
+    200\,Myr, based on the one CQV we found in the Carina Near
+    moving group (TIC~294328885; $\approx$200\,Myr).  The lack of
+    detected CQVs in the Hyades and Praesepe suggests that the
+    lifetime of the phenomenon is likely limited to the first few
+    hundred million years.
 	%
@@
 	BPMG: $\beta$~Pic moving group \citep{2015MNRAS.454..593B}.
-	CAR: Carina \citep{2015MNRAS.454..593B}.
+  CARN: Carina Near moving group \citep{2006ApJ...649L.115Z}.
 	COL: Columba \citep{2015MNRAS.454..593B}.

### 2023-07-12 complexrotators/plotting.py
minor plot update

@@ -3432,7 +3432,7 @@ def plot_catalogscatter(outdir, showmaybe=0):
             df_plei = df_plei[df_plei.flag_benchmark_period]
             ax.scatter(
                 df_plei['dr2_bp_rp'], df_plei['Prot'], c='darkgray', s=3,
-                linewidths=0, zorder=-1
+                linewidths=0, zorder=-1, alpha=0.7
             )
             ax.text(0.97,0.97, 'CQVs', transform=ax.transAxes,
                     ha='right',va='top', color='C0', fontsize='small')

### 2023-07-12 drivers/make_cpv_table.py
table driver tweak

@@ -123,10 +123,10 @@ def main(overwrite=0):
         assert num <= 10
         return units[num]
 
-    N_4 = num2word(len(sgdf[sgdf.banyan_assoc == 'FIELD']))
+    N_4 = num2word(len(sgdf[sgdf.banyan_assoc == 'FIELD']) + 1)
     N_5 = len(smdf[smdf.banyan_assoc == 'FIELD'])
 
-    N_6 = len(sgdf[sgdf.banyan_assoc != 'FIELD'])
+    N_6 = len(sgdf[sgdf.banyan_assoc != 'FIELD']) + 1
     N_7 = len(smdf[smdf.banyan_assoc != 'FIELD'])
 
     txt = (

### 2023-07-12 paper/ms.tex
update catalogscatter plot

@@
 		\includegraphics[width=0.9\textwidth]{f6.pdf}
-		\vspace{-0.2cm}
+		\vspace{-0.1cm}
 		\caption{
@@
       the dark blue circles; \nmaybes\ candidate CQVs are light blue circles.
-      The top panels show the \nstarssearched\ target stars with 120-second cadence data
+      The top panels show the \nstarssearched\ target stars with 120-second cadence TESS data
       as the shaded gray background;
       darker regions correspond to a larger relative number of searched stars.
-      The lower-left panel compares the rotation--color distribution of the CQVs, and candidate CQVs, against the rotation
+      The lower-left panel compares the rotation--color distribution of CQVs against the rotation
       periods of K- and M-dwarfs in the Pleiades from \citet{2016AJ....152..114R}.
-      Note the scale change for the period $P$ from days to hours in the middle panel of the lower row.
+      The lower-middle panel plots the derived corotation radii
+      $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in units of stellar radii against the measured
+      CQV periods, in units of hours.
 		}

### 2023-07-12 complexrotators/plotting.py

@@ -3356,7 +3356,8 @@ def plot_catalogscatter(outdir, showmaybe=0):
         ('tlc_mean_period', 'bp_rp', '$P$ [days]', '$G_{\mathrm{BP}}-G_{\mathrm{RP}}$ [mag]', 'log', 'linear'),
         #('rstar_sedfit', 'teff_sedfit', '$R_{\! \star}$ [$R_\odot$]', '$T_\mathrm{eff}$ [K]', 'linear', 'linear'),
         #('ruwe', 'bp_rp', 'RUWE', '$G_{\mathrm{BP}}-G_{\mathrm{RP}}$ [mag]', 'log', 'linear'),
-        ('tlc_mean_period', 'Rcr_over_Rstar', '$P$ [hours]', '$R_{\mathrm{cr}}/R_{\! \star}$', 'log', 'linear'),
+        #('tlc_mean_period', 'Rcr_over_Rstar', '$P$ [hours]', '$R_{\mathrm{cr}}/R_{\! \star}$', 'log', 'linear'),
+        ('Rcr_over_Rstar', 'tlc_mean_period',  '$R_{\mathrm{cr}}/R_{\! \star}$', '$P$ [hours]', 'linear', 'log'),
         ('banyan_adopted_age', 'mstar_parsec', 'Age [Myr]', '$M_{\! \star}$ [$M_\odot$]', 'log', 'linear'),
         #('rstar_sedfit', 'banyan_singleagefloat', '$R_{\! \star}$ [$R_\odot$]', 'Age [Myr]', 'linear', 'log'),
     ]
@@ -3443,10 +3444,9 @@ def plot_catalogscatter(outdir, showmaybe=0):
                     ha='right',va='top', color='darkgray', fontsize='small')
 
 
-        if ykey == 'tlc_mean_period' and xkey == 'Rcr_over_Rstar':
-            f = 24
-            f0 = f
-            f1 = f
+        fx = 1
+        if xkey == 'tlc_mean_period' and ykey == 'Rcr_over_Rstar':
+            fx = 24
 
         elif ykey == 'banyan_adopted_age':
             np.random.seed(42)
@@ -3463,11 +3463,11 @@ def plot_catalogscatter(outdir, showmaybe=0):
             f1 = 1
 
         ax.scatter(
-            df[xkey], f0*df[ykey], c='C0', s=6, linewidths=0, zorder=10
[…]

### 2023-07-14 paper/ms.tex
update ms

@@
 		\centering
-		\includegraphics[width=0.98\textwidth]{f2.pdf}
+		\includegraphics[width=0.98\textwidth]{f3.pdf}
     \vspace{-0.3cm}
@@
 
-The upper age limit for the CQV phenomenon may even reach 200\,Myr,
-based on the candidate membership of TIC~294328885 in the Carina Near
-moving group \citep{2006ApJ...649L.115Z}.  This group's age primarily
-rests on the lithium sequence of its G-dwarfs
-\citep{2006ApJ...649L.115Z}, which shows a coeval population
-of stars older than the Pleiades and younger than the 400\,Myr Ursa
-Major moving group.  It would interesting to improve the
-precision of the group's age measurement, for instance using
-gyrochronology of F, G or K members, in order to verify this point.
+%FIXME it'd be useful to get an RV for this one...
+The upper age limit for CQVs may even pass 200\,Myr, based on the
+candidate membership of TIC~294328887 in the Carina Near moving group
+\citep{2006ApJ...649L.115Z}.  This group's $200 \pm 50$\,Myr age
+primarily rests on the lithium sequence of its G-dwarfs
+\citep{2006ApJ...649L.115Z}, which shows a coeval population of stars
+older than the Pleiades and younger than the 400\,Myr Ursa Major
+moving group.  The formal BANYAN-$\Sigma$ membership probability is
+however somewhat low, perhaps due to a
+
+It would interesting to perform independent tests of
+the group's age, for instance using gyrochronology of F, G or K
+members, in order to verify this .
 
@@
 		\centering
-		\includegraphics[width=\textwidth]{f3.pdf}
+		\includegraphics[width=\textwidth]{f4.pdf}
 		\vspace{-0.6cm}
@@
 		\centering
-		\includegraphics[width=0.98\textwidth]{f4.pdf}
+		\includegraphics[width=0.98\textwidth]{f5.pdf}
 		\vspace{-0.35cm}
@@
 		\centering
-		\includegraphics[width=\textwidth]{f5.pdf}
+		\includegraphics[width=\textwidth]{f6.pdf}
 		\vspace{-0.6cm}
@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{f6.pdf}
+		\includegraphics[width=0.9\textwidth]{f7.pdf}
 		\vspace{-0.1cm}
@@
     200\,Myr, based on the one CQV we found in the Carina Near
-    moving group (TIC~294328885; $\approx$200\,Myr).  The lack of
+    moving group (TIC~294328887; $\approx$200\,Myr).  The lack of
     detected CQVs in the Hyades and Praesepe suggests that the
@@
 \acknowledgments
-This work was supported by the 
-Heising-Simons 51~Pegasi~b Fellowship (LGB).
-TIC 402980664 was observed at 120-second cadence thanks to the TESS Guest
+LGB gratefully acknowledges support from the
+Heising-Simons 51~Pegasi~b Fellowship.
+While many conversations helped encourage this work,
+a few thank-yous in particular (from LGB) 
+are owed to G.~Laughlin, A.~Mann, and J.~Spake for clarifications and ideas.
+This paper relies on data collected by the TESS mission, which are publicly available from the Mikulski Archive for Space Telescopes (MAST).
+Funding for the TESS mission is provided by NASA’s Science Mission Directorate.
+TIC 402980664 in particular was observed at 120-second cadence thanks to the TESS Guest
 Investigator programs G022252 (PI: J.~Schlieder; Sectors 18, 19, 25,
 26) and G04168 (PI: R.~Jayaraman; Sector 53).
-While many conversations helped encourage this work,
-a few thank-yous in particular (from LGB) 
-are owed to G.~Laughlin, A.~Mann, L.~Rebull, and J.~Spake for clarifications and ideas.
 
@@
 %\tabletypesize{\scriptsize}
-\tablecaption{Complex quasiperiodic variables identified in the TESS 2-minute data. \label{tab:thetable}}
+\tablecaption{Complex quasiperiodic variables identified in the TESS
+  2-minute data. {\bf For internal review, full versions are available
+  here
+  \url{https://www.dropbox.com/scl/fo/twn4s9ckbevf75jqhtoy1/h?rlkey=t5cn8cx2uoc2ptdm9e570kp1b&dl=0}} \label{tab:thetable}}
 %\toprule

### 2023-07-14 paper/collect.sh

@@ -6,16 +6,16 @@ cp $resultsdir/lc_mosaic/lc_mosaic_fav3.pdf f1a.pdf
 cp $addir/models.pdf f1b.pdf
 
 # fig2
-cp $resultsdir/full_lcmosaic/full_lcmosaic_showtitles_Ngoodsectors_tic8_Tmag.pdf f2.pdf
+cp $resultsdir/full_lcmosaic/full_lcmosaic_showtitles_Ngoodsectors_tic8_Tmag.pdf f3.pdf
 
 # fig3
-cp $resultsdir/beforeafter_mosaic/beforeafter_mosaic_showtitles_tic8_Tmag.pdf f3.pdf
+cp $resultsdir/beforeafter_mosaic/beforeafter_mosaic_showtitles_tic8_Tmag.pdf f4.pdf
 
 # fig4
-cp $resultsdir/tic4029_segments/tic4029_segments.pdf f4.pdf
+cp $resultsdir/tic4029_segments/tic4029_segments.pdf f5.pdf
 
 # fig5
-cp $resultsdir/phase_timegroups_mosaic/TIC_402980664/TIC_402980664_P18.5611_2min_phase_timegroups_mosaic_ymin-4.8_ymax3.pdf f5.pdf
+cp $resultsdir/phase_timegroups_mosaic/TIC_402980664/TIC_402980664_P18.5611_2min_phase_timegroups_mosaic_ymin-4.8_ymax3.pdf f6.pdf
 
 # fig6
-cp $resultsdir/catalogscatter/catalogscatter_showmaybe.pdf f6.pdf
+cp $resultsdir/catalogscatter/catalogscatter_showmaybe.pdf f7.pdf

### 2023-07-15 paper/ms.tex
update ms

@@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% MS TODO's
+%
+% * find/replace "centrifugally supported" with something less
+% jargony, and more physically meaningful.  (read CR89)
+%
+% * "Bound-free absorption can provide
+%   wavelength-dependent opacity, but the absorption coefficients
+%   generally {\it grow} with increasing wavelength, rather than {\it
+%   shrink} as one needs in order to get deeper absorption in the blue
+%   than in the red."
+%   --> Isn't this statement wavelength dependent????
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 % upon AAS submission
@@
 \newcommand{\rearth}{{R$_\oplus$}}
-\newcommand{\rsun}{{R$_\odot$}}
-\newcommand{\msun}{{M$_\odot$}}
+\newcommand{\rsun}{{$R_\odot$}}
+\newcommand{\msun}{{$M_\odot$}}
 \newcommand{\bprp}{G_{\rm BP} - G_{\rm RP}}
@@
   ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc)
-  examples of this class of object known, and perhaps also the most massive
-  ($\approx$0.6-0.8\,M$_\odot$).  A few objects are outliers among
-  outliers; LP 12-502 for instance shows a ``dip complex'' with a
+  examples of this class of object known, and probably also the most massive
+  ($\approx$0.6-0.8\,$M_\odot$) and oldest ($\approx$200\,Myr).  A few objects are outliers among
+  outliers; LP 12-502 for instance shows a recurring ``dip complex'' with a
   period and total duration that are fixed over more than 1{,}000
   cycles, but which in detail exhibits anywhere from four to eight
-  local minima per cycle.  LP-502 also displayed distinct superposed
+  local minima per cycle.  LP 12-502 also displayed distinct superposed
   periods simultaneously, and showed drastic shape changes shortly
@@
 baseline is described in Section~\ref{sec:evoln}, including a
-deep-dive into LP 12-502.  Implications are discussed in
-Section~\ref{sec:discussion}, and we conclude in
+deep-dive into LP 12-502.  We describe a few implications in
+Section~\ref{sec:discussion}, and conclude in
 Section~\ref{sec:conclusion}.
@@
 To correctly identify local minima near the edges of the phased light
-curve, which usually would cover phases $\phi \in [ 0,1 ]$, we in fact
+curve, which usually would cover phases $\phi \in [ 0,1 ]$, we 
 performed the entire procedure over a phase-folded light curve
@@
 spline knots per cycle, and how large and wide of a local minimum to
-consider a ``true dip'', were chosen during a testing period based on
+consider a ``true dip'', were chosen during testing based on
 their ability to correctly re-identify a large fraction ($>$90\%) of
@@
 
-Overall, for a star to clear this process and to proceed to manual
+Overall, for a star to proceed to manual
 examination, we required that it have a peak PDM period below two
@@
 			set, with one image per sector for each of \ncpvsfound\ CQVs
-			and candidate CQVs
+			and CQV candidates
 			is available online {\bf For internal collaboration review:
@@
 
-We visually assessed whether the objects found using the Fourier
-(Section~\ref{subsec:fourier}) and dip-counting
-(Section~\ref{subsec:counting}) techniques were consistent with
+We visually assessed whether the objects found using the dip-counting
+(Section~\ref{subsec:counting}) and Fourier
+(Section~\ref{subsec:fourier}) techniques were consistent with
 expectations for CQVs by assembling the data shown in
-Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CQV if
-at least one TESS sector showed what we viewed as the unambiguous
-signatures of the class (short period; at least three dips or else
-otherwise oddly-shaped dips; relative stability over a timescale of
-30\,days).  We also noted stars that we thought could be CQVs, but
-that were more ambiguous with a ``maybe'' flag.
+Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CQV if at least
+one TESS sector showed what we viewed as the unambiguous signatures of
+the class (short period; at least three dips or else otherwise
+oddly-shaped dips; relative stability over a timescale of 30\,days).
+We independently noted stars that we thought could be CQVs, but that were more
+ambiguous.
 
@@
 probabilities returned by this procedure are qualitatively useful, but
-we emphasize that they are quantitatively dubious due to the
+should be assessed with caution due to the
 non-Gaussian nature of most groups within the solar neighborhood
@@
 For the SED fitting, we used \texttt{astroARIADNE}
-\citep{2022MNRAS.513.2719V}.  We adopted the ``BT-Settl'' stellar
+\citep{2022MNRAS.513.2719V}.  We adopted the BT-Settl stellar
 atmosphere models \citep{Allard2012} assuming the
@@
   T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
-  R_\star / {\rm R}_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
+  R_\star / R_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
   A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
@@
 Plausible explanations for anomalous M-dwarf colors and sizes relative
-to model predictions include star starspot coverage
+to model predictions include starspot coverage
 \citep[e.g.][]{2017ApJ...836..200G}, and potentially incomplete line
@@
 atmospheres, in order to match observed masses and radii of younq
-eclipsing binaries.  This is sufficient for our purpose of estimating
-accurate stellar masses.  Given our observed $\{ \tilde{T}_{\rm eff},
+eclipsing binaries.  This is sufficient for our goal of estimating
+stellar masses.  Given our observed $\{ \tilde{T}_{\rm eff},
 \tilde{M}_\star, \tilde{t} \}$, and approximating their uncertainties
@@
 sector; we refer to these as the ``high-quality sample''.  The
-classification of the remaining \nmaybes\ CQV candidates was ambiguous; their variability
-might be caused by say, multiple starspot groups.  Additional data
+classification of the remaining \nmaybes\ CQV candidates was ambiguous.  Additional data
 from TESS or other instruments could help resolve their
 classification.  The boolean \texttt{quality} column in the table divides
-the two classes.  In the following discussion, we will restrict our
+the two classes.  In the following, we will restrict our
 discussion to the high-quality sample.
@@
 The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
-\ngoods\ bonafide CQVs.  The objects are sorted first in order of the
+\ngoods\ CQVs.  The objects are sorted first in order of the
 number of TESS 120-second cadence sectors in which they clearly
 demonstrated the CQV phenomenon, and secondarily by descending
-brightness.  The objects at the top generally have the most 120-second
-cadence data.  The top five objects by this metric are TIC~300651846
+brightness.  The top five objects by this metric are TIC~300651846
 ($T$$=$13.5, 12 sectors); TIC~402980664 ($T$$=$11.1, 7 sectors);
@@
 minima per cycle.  Some stars show relatively ordinary modulation
-during one continuous portion of the phased light curve, and highly
+during one portion of the phased light curve, and highly
 structured modulation in the remainder of the cycle (e.g.
@@
 modulation over the entire span of a cycle (e.g. TIC~2234692,
-TIC~401789285, TIC~425933644, TIC~142173958).  Others still show some
+TIC~401789285, TIC~425933644, TIC~142173958).  Others show some
 mix between these two modes.
@@
 distinct from any binary phenomenology of which we are aware.
-Follow-up spectroscopy would be needed to definitively resolve this issue.
 
@@
 majority of pre-main-sequence stars in the solar neighborhood.
-However, given the $\lesssim$$10\%$ completeness
-of TESS beyond 100\,pc, there are probably many more CQVs that remain to be discovered in
-Sco-Cen.  IC\,2602 and IC\,2391, which are located slightly beyond
-100\,pc, are an example of this completeness effect: our search did
-not find any CQVs in those clusters.
+However, given the $\lesssim$$10\%$ completeness of TESS beyond
+100\,pc, there are probably many more CQVs that remain to be
+discovered in Sco-Cen.  
+%IC\,2602 and IC\,2391, which are located slightly beyond
+%100\,pc, are an example of this completeness effect: our search did
+%not find any CQVs in those clusters.
 
@@
 moving group.  The formal BANYAN-$\Sigma$ membership probability is
-however somewhat low, perhaps due to a
-
-It would interesting to perform independent tests of
-the group's age, for instance using gyrochronology of F, G or K
-members, in order to verify this .
-
-%While
-%we expect to have been sensitive to CQVs in the nearby Hyades
-%($\approx$700\,Myr), again due to the specifics of the TESS 120-second
-%selection function, we do not know at this time whether we would have
-%been sensitive to such stars.
+however somewhat low, perhaps due to the missing radial velocity.
+This could be relatively easily resolved by acquiring even a
+medium-resolution spectrum.
+An independent assessment of the group's kinematics using Gaia data,
+and its rotation sequence using TESS, could lend further credence in
+such an analysis.
 
@@
 
-The two ``good'' IR excesses belonged to ``candidate'' CQVs
+The two ``good'' IR excesses belonged to ``ambiguous'' CQVs
 TIC~193136669 (TWA~34) and TIC~57830249 (TWA~33).  Both are in the TW
@@
 periods of 38\,hr and 44\,hr respectively.  In our initial labeling,
-we labeled both as ``maybe'' CQVs because the dips in their light
+we labeled both as ``ambiguous'' CQVs because the dips in their light
 curves did not show the rigid periodicity typical of CQVs;  their
@@
 of further sectors clarified that both sources are dippers (see plots
-in Figure~\ref{fig:vet}).  In addition, TIC 193136669 has a cold
+in Figure~\ref{fig:vet}).  Independently, TIC 193136669 has a cold
 molecular disk based on observed 1.3\,mm continuum emission and
@@
 present.  It is also a dipper.
-Given these ``errors'', plausible evolutionary connections between CQVs and
-dippers are discussed in Section~\ref{subsec:discdippers}.
+Section~\ref{subsec:discdippers} highlights plausible evolutionary
+connections between CQVs and dippers in light of these
+``misclassifications'' .
 
@@
 more than any other variability of which we are aware.  TIC~289840926
-($\beta$~Pic moving group, $P$=4.8\,hr), show what we believe is a
-clear CQV signals, but has no definitive evidence for a large, dusty
+($\beta$~Pic moving group, $P$=4.8\,hr), shows what we believe is a
+clear CQV signal, but has no definitive evidence for a large, dusty
 disk.  TIC~244161191 (TOI-278), in Columba, also has no
@@
 sources we do not know the period at the precision necessary to be able to
-accurately propagate it over two years.
+accurately propagate an ephemeris over two years.
 
 Of these 27 CQVs in Figure~\ref{fig:evoln}, a few show clear signs of the
-CQV phenomenon in one sector, and marginal or non-existence signs in the
+CQV phenomenon in one sector, and marginal or non-existent signs in the
 other.  While there is subjectivity in this assessment, to our
@@
 based on the the shape evolution between Sectors 13 and 39, it is a
-CQV.  One could easily also imagine in cases like TIC~206544316 that
-if observed at lower signal to noise, the drastic shape evolution
-would not be appreciated.  We emphasize that the periods themselves
-were all stable to $<$0.1\%.  Broadly speaking, this shape evolution
-suggests that CQVs have an ``on/off'' duty cycle of $\approx$75\%.
+CQV.  
+Based on the fraction of sources overall that ``turned off'', the
+observed shape evolution implies that CQVs have a duty cycle of
+$\approx$75\%.
 This type of correction is likely worth including in population-level
@@
 each sector independently, was $\langle P \rangle = 18.5560$\,hr.  The
-range between the maximum and minimum sector-specifics periods was
+range between the maximum and minimum sector-specific periods was
 measured to be about one minute.  Based on this range, the star's
@@
 depth by about 2\%, while dip 2 {\it increases} in depth, by about the
-same amount (see Figure~\ref{fig:lp}).  During cycles 48-64, it also
-seems that a fifth dip may be emerging, in the main ``large'' dip
-group.
+same amount (see Figure~\ref{fig:lp}).  During cycles 48-64, a fifth
+dip may also be emerging, in the main ``large'' dip group.
 
@@
 two intricately structured dip complexes, plus a small leading dip.
-The single leading dip is present at roughly the same phase as in
-cycles 0-64; they seem likely to be the same struture.  Along a
+The single leading dip is present at the same phase as in
+cycles 0-64, and is therefore likely to be the same struture.  Along a
 similar line of logic, it seems plausible that the first ``dip
@@
 substructure.  During e.g.~cycles 283-298, this single complex shows
-six local minima.  The deepest dip is sharp: it shows a flux
-exercusion of 3.5\% over about 22 minutes (0.02\,$P$), which is the
-steepest slope exhibited anywhere in this object's remarkable dataset.
-After the sharp dip, there is a roughly exponential fall-off spanning
-about a quarter of a period, punctuated by coherent local minima and
-maxima which in detail (Appendix~\ref{app:lp}) have slightly longer
-periods than the sharp dip.  The sharp leading dip only decreases
-during a sudden state-switch at BTJD 2030.7 (cycles 299-315), which
-happens immediately during a flare (Figure~\ref{fig:lplc}).  The
-trailing dips remain afterwards.
+six local minima.  The deepest dip is sharp: it shows a flux excursion
+of 3.5\% over about 22 minutes (0.02\,$P$), which is the steepest
+slope exhibited anywhere in the LP~12-502 remarkable dataset.  After
+the sharp dip, there is a roughly exponential fall-off spanning about
+a quarter of a period, punctuated by coherent local minima and maxima
+which in detail (Appendix~\ref{app:lp}) have slightly longer periods
+than the sharp dip.  The sharp leading dip only decreases in depth
+following a sudden state-switch at BTJD 2030.7 (cycles 299-315), which
+happens during a flare (Figure~\ref{fig:lplc}).  The trailing dips
+remain thereafter.
 
@@
 less than one cycle, a point which has been previously appreciated
-\citep{2017AJ....153..152S}.  What is new in these particular changes,
-for instance cycles 1233-1264 of Figure~\ref{fig:lp}, is that the
-morphology changes show that the dips can be {\it independent} and
-{\it additive}.  It other words, throughout cycles 1233-1264, there
-are three local minima between phases of 0 and 0.3.  They all have
-identical ingress times.  The shape change during the transition
-implies that the leading dip that ``turned off'' (changed its depth),
-while the trailing two dips remained fixed in their depths.  In other
-words, the structures producing these dips must be independent, to the
-degree that one can undergo a severe change, while the others can
+\citep{2017AJ....153..152S}.  What is new in these particular changes
+is that the morphology changes show that the dips can be {\it
+independent} and {\it additive}.  For example, throughout cycles
+1233-1264, there are three local minima between phases of 0 and 0.3.
+They all have identical ingress times.  The shape change during the
+transition implies that the leading dip that ``turned off'' (reduced
+its depth and duration), while the trailing two dips remained fixed.
+In other words, the structures producing these dips are independent to
+the degree that one can undergo a severe change while the others
 remain essentially identical.  The state switches during cycles
@@
 {\sc Slow growth; rapid death}---Although there are a few instances in
-which we observe dips ``switch off'' over less than one cycle, dip
+which we observe dips switch off over less than one cycle, dip
 growth seems to happen more slowly.  For instance, the dip that grows
@@
 %star, and from the isochrone mass, $M_\star=0.215\,M_\odot$ 
-{\sc Dip durations}---The shortest timescale for any of the {\it
-individual} LP 12-502 dips seems to be $\approx$0.06\,$P$ $\approx$
+{\sc Dip durations}---The shortest dip duration for any of the
+individual LP 12-502 dips seems to be $\approx$0.06\,$P$ $\approx$
 1.08\,hr.  In comparison, using the stellar radius and mass derived in
@@
 consistent with effective radii for the occulting material $R_{\rm
-eff} \ll R_\star$ .  This implies $a/R_\star \approx 5.8$ for this
+eff} \ll R_\star$.  This implies $a/R_\star \approx 5.8$ for this
 material, and so the analogous timescale at the stellar surface is
@@
       The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are 
-      the dark blue circles; \nmaybes\ candidate CQVs are light blue circles.
+      the dark blue circles; \nmaybes\ ambiguous CQV candidates are light blue circles.
       The top panels show the \nstarssearched\ target stars with 120-second cadence TESS data
@@
 
-\subsection{Typical and Extreme Cases}
+\subsection{Typical and extreme CQVs}
 \label{subsec:extreme}
@@
 In terms of their rotation, relative to the Pleiades,
-they are among the more rapidly rotating half.
+they are among the more rapidly rotating half of M-dwarfs.
 The dearth of $T$$>$15.5 CQVs in our sample, despite our search extending
-to $T$$=$16, is a consequence of the 120-second selection function.
-%
+to $T$$=$16, is a consequence of the 120-second selection function,
+not detection sensitivity.
 
@@
 
-The lowest mass ($\approx 0.12$\,M$_\odot$) belongs to TIC~267953787.
+The lowest mass ($\approx 0.12$\,$M_\odot$) belongs to TIC~267953787.
 The catalog contains a few other stars with similar mass.  Given the
@@
 suggests that future studies of brown dwarf photometric variability
-might also yield complex quasiperiodic variables, though there would
+might also yield complex quasiperiodic variables, though there could
 be degeneracies in interpretation with planetary surface features such
@@
 date, the only stars reported to show the CQV phenomenon are M-dwarfs,
-with typical stellar masses $\lesssim$0.3\,M$_\odot$
+with typical stellar masses $\lesssim$0.3\,$M_\odot$
 \citep{2022AJ....163..144G}.  TIC~405754448 and 405910546 however
-appear to have masses of 0.82 and 0.60\,M$_\odot$ respectively.  The
-next-highest masses are $\approx$0.40\,M$_\odot$.  The masses for the
+appear to have masses of 0.82 and 0.60\,$M_\odot$ respectively.  The
+next-highest masses are $\approx$0.40\,$M_\odot$.  The masses for the
 former two objects are consistent with their CAMD locations, and their
@@
 A periodic signal repeats exactly; the CQVs do not
-(Figure~\ref{fig:evoln}).  Their periods however do appear to be
-constant to within measurement precision over thousands of cycles.
-They are therefore {\it quasi}periodic.  This point with previous
+(Figure~\ref{fig:evoln}).  While their periods appear to remain
+constant to within measurement precision over thousands of cycles, the
+light curve shapes evolve over 10 to 1{,}000 cycles.
+They are therefore {\it quasi}periodic.  This observation is consistent
 studies by \citet{2022AJ....163..144G} and
@@
 from the ``persistent'' {\it vs.} ``transient'' flux dip distinction
-described by \citet{2017AJ....153..152S};  while the dips can persist
-over timescales of even up to 100 cycles, all CQV dips seem to be
-transient over timescales of more than 1000 cycles
+described by \citet{2017AJ....153..152S};  since all CQV dips seem to
+be transient over timescales of more than 1{,}000 cycles
 (Figure~\ref{fig:evoln}).
@@
 able to explore all phase angles with equal weight.  LP 12-502, and
-multiple other CQVs, seem to have preferred phases.  For LP 12-502,
+perhaps other CQVs, seem to have preferred phases.  For LP 12-502,
 all of the dips happen over phases corresponding to only two thirds of
@@
 
-Examining Figure~\ref{fig:cqvs}, it is not obvious whether the CQVs as
+Examining Figure~\ref{fig:cqvs}, it is not obvious whether CQVs as
 a whole show any preference for sharper ingresses, or sharper
 egresses.  In some cases (e.g. TIC~425933644), the continuum itself is
-not particularly well-defined, and so the meaning of ``ingress'' and
-``egress'' are not particularly clear.  In others, such as Sector~36
+not well-defined, and so the meaning of ``ingress'' and
+``egress'' are not clear.  In others, such as Sector~36
 of TIC~89463560, there is a single clear sharp ingress with an
@@
 12-502 merits its own in-depth study.  Connections could likely also
-be made to the toroidal geometries that are produced by outflowing
+be made to the toroidal geometries that can be produced by outflowing
 atmospheres of transiting planets
@@
 centrifugally supported at the corotation radius.  The prominence idea
-has a longer history, based first on analogy with quiescent
+has a longer history, based on analogy with quiescent
 prominences/filaments observed to exist in the solar corona for up to
-a few weeks \citep[see e.g.][]{2015ASSL..415.....V}.  In an extrasolar
+a few weeks \citep[see][]{2015ASSL..415.....V}.  In an extrasolar
 context, spectroscopic detections of transient Balmer- and
@@
 led to the interpretation that the data could best be explained by
-similar prominence structures: cold, minimally ionized hydrogen clouds
+similar structures: cold, minimally ionized hydrogen clouds
 or filaments that scatter chromospheric emission from the star to
 produce the observed spectroscopic line variations
-\citep[see][]{1989MNRAS.238..657C}.  The (short-term) mechanical
+\citep[see][]{1989MNRAS.238..657C}.  The short-term mechanical
 stability of such gas configurations is theoretically plausible
@@
 Thompson scattering is also ruled out, because it is gray.  Dust, with
-its relatively featureless but increasing extinction curve when going
-bluer into the optical \citep{1989ApJ...345..245C}, is to our
-knowledge the most obvious opacity source.
+its larger absorption cross-section in the blue than the red
+\citep{1989ApJ...345..245C}, is to our knowledge the most obvious
+opacity source.
 
@@
 observations of this star have been understood in terms of absorbing
-circumstellar material, quite analogous to the geometries we are
+circumstellar material, analogous to the geometries we are
 discussing for much cooler M-dwarfs \citep{2005ApJ...630L..81T}.  This
-material however cannot be dust, due to the relevant sublimation
-timescales.  It is instead thought to be sourced from bound-free
+material however is unlikely to be dust, due to the relevant sublimation
+timescales.  The opacity is instead thought to be sourced from bound-free
 absorption from neutral hydrogen \citep{2005ApJ...630L..81T}.
@@
 the gas {\it vs.} dust clump scenarios.
-Based on the available statistics from the studies of L.~Rebull and J.~Stauffer,
+Based on the available statistics from the studies by L.~Rebull and J.~Stauffer,
 it seems plausible that CQV occurrence decreases in time, bottoming to zero
@@
 older than 150\,Myr have been seen to exhibit the phenomenon.
-In the dust clump scenario this is not a problem, because the dust could
-be externally sourced, and would be expected to have a finite supply.
+In the dust clump scenario this is not a problem, because if the dust
+were externally sourced, it would be expected to have a finite supply.
 
@@
 planets per star, for planets with 1-4\,$R_\oplus$ and $P$$<$10\,days.
-Extrapolating to all small close-in planets, from say
+Extrapolating to all small close-in planets, with say
 0.1-4\,$R_\oplus$ and within 10 days, it is reasonable to expect on
 average one planet per M-dwarf.  TRAPPIST-1b ($P$=1.5\,days) is one
-example of this type of planet, in orbit around a 0.08\,M$_\odot$ star
+example of this type of planet, in orbit around a 0.08\,$M_\odot$ star
 \citep{2017Natur.542..456G}.
@@
 
-It is tempting to try to interpret features of the CQV light curves in
-terms of the possible presence of close-in exoplanets, or even
-planetesimals.  Rocky planets this young would likely have molten
-global magma oceans analogous to those that existed on the Earth and
-Moon \citep[see][]{2022arXiv220310023L}, and thus would being
-undergoing significant outgassing and atmospheric escape.  While a
-scenario in which close-in rocky planets serve as a possible source of
-dust for the clouds is {\it a priori} plausible, it is currently only
-a subject of speculation.
-
-Given the dip depth variations that are observed in systems like LP
-12-502, one might be driven in this framework toward a picture of a
-disintegrating planetesimal swarm.  The sizes of the planetesimals
+Given this context, it is tempting to try to interpret features of the
+CQV light curves in terms of the possible presence of close-in
+exoplanets, or even planetesimals.  Rocky planets this young would
+likely have molten global magma oceans analogous to those that existed
+on the Earth and Moon \citep[see][]{2022arXiv220310023L}, and thus
+would be undergoing significant outgassing and atmospheric escape.
+However while a scenario in which close-in rocky planets or
+planetesimals serve as a possible source of dust for the clouds is
+{\it a priori} plausible, any evidence in support of such a picture
+currently seems ambiguous at best.
+
+In systems like LP 12-502, the observed dip depth variations would
+necessarily drive one toward a picture of a disintegrating
+planetesimal swarm, rather than just a single planetesimal.  
+While the
+number of free parameters in this type of model is somewhat dizzying,
+we have no right to believe that nature need be simple.
+The need for a swarm rather than just one launching body would
+be driven by the observation that we see dips appear and disappear at
+many {\it different phases}, but with roughly the same period.
+The observed changing dip depths in response to flares would be
+understood through the planetesimal outflow rates being stalled by
+changes in the local magnetic field or coronal plasma density.
+The sizes of these purported planetesimals
 would need to be $\lesssim 1$\,$R_\oplus$, based on the non-detections
@@
 \citep{2015ApJ...812..112S} or KOI-2700 \citep{2014ApJ...784...40R}.
-The dip-profile asymmetries during certain segments of the light curve
-plausibly match this idea; for instance, the complex in cycles 248-298
-could be well-fit by a sharp leading edge that decays over 0.2\,$P$
-(3.7\,hours).  The earlier complex, during cycles 248-264
-(pre-state-switch), could be fit by a similar profile.  While the
-number of free parameters in this type of model is somewhat dizzying,
-we have no right to believe that nature need be simple.
+Typical sizes of bodies in the asteroid belt for instance span
+hundreds of meters to a few kilometers.
+
+The planetesimal swarm model would also predict that certain orbital
+phases would produce recurrent dips if observed over sufficiently long
+timescales, since the launching planetesimal would be massive enough
+to remain in orbit, and similar to say K2-22 would stochastically
+eject material.  While the regularity of the dip phases of LP~12-502
+over the existing baseline (Figure~\ref{fig:lp2}) might agree with
+this prediction, 
+for most other CQVs (Figure~\ref{fig:evoln}) the data seem likely to
+be in tension with this expectation.
+
+There are a few additional problems for the idea of a disintegrating
+planetesimal swarm.  First, many of the dips show asymmetries in
+the wrong direction relative to the naive expectation of a
+trailing comet tail.  Invoking non-exponentially decaying dust
+distributions as a function of azimuth might be one way out of this,
+but such an idea would need stronger theoretical footing.  
+Dynamical stability would be a separate concern:
+in a model in which any new dip is ``explained'' by invoking a new
+planetesimal, one might eventually pack the corotation radius to a
+degree where instability over short timescales would be guranteed.
+
+It is certainly possible that exoplanets or exoplanetesimals could end
+up being connected to the CQV phenomenon, for instance as a possible
+source of dust through collisions at greater separations from the
+star.  However for the time being, none of the CQVs that we have
+studied in this work seem to show clear evidence for this type of
+origin scenario.
+
+%The dip-profile asymmetries during certain segments of the light curve
+%plausibly match this idea; for instance, the complex in cycles 248-298
+%could be well-fit by a sharp leading edge that decays over 0.2\,$P$
+%(3.7\,hours).  The earlier complex, during cycles 248-264
+%(pre-state-switch), could be fit by a similar profile.
 
@@
 
-Ultimately, there are a few problems for the idea of a disintegrating
-planetesimal.  First, a large number of the dips show asymmetries in
-the {\it wrong direction} relative to the naive expectation of a
-trailing comet tail.  Invoking non-exponentially decaying dust
-distributions as a function of azimuth might be one way out of this,
-but such an idea would need stronger theoretical footing.  More
-important is that the (unseen) planets or planetesimals should be on
-{\it exactly periodic} orbits over observable timescales, on the
-presumption that the planetesimals would be massive enough to not feel
-any headwind or magnetic field.  For most CQVs, this is inconsistent
-with the data; dips in sources such as LP 12-502 appear and disappear
-at {\it distinct phases}, but with the same period.  It seems
-challenging to reconcile this behavior with the possible presence of
-just a single launching body.  Finally, the fact that the dips often
-respond to events like flares suggests that that the responsible
-material be much less massive than a 1--100\,km sized planetesimal,
-and therefore more easily influenced by the stellar magnetic field.
-
-It is certainly possible that exoplanets could end up being connected
-to the CQV phenomenon, for instance as a possible source of dust
-through collisions at greater separations from the star.  However for
-the time being, none of the CQVs that we have studied in this work
-seem to show clear evidence for an exoplanetary origin.
+%It seems
+%challenging to reconcile this behavior with the possible presence of
+%just a single launching body.  Finally, the fact that the dips often
+%respond to events like flares suggests that that the responsible
+%material be much less massive than a 1--100\,km sized planetesimal,
+%and therefore more easily influenced by the stellar magnetic field.
 
@@
 
-It is amusing that in identifying the two candidate CQV sources in
+It is amusing that in identifying the two ambiguous CQV sources in
 Section~\ref{subsec:irexcess} with outlying SEDs (TICs~193136669 and
@@
 ultimately conclude that these sources are dippers.  This episode
-suggests that there could be overlap between the two classes of
-object.  It is also worth emphasizing that our labeling of
+suggests that there could be overlap between CQVs and dippers.  It is also worth emphasizing that our labeling of
 e.g.~TIC~57830249 was based on a single sector of TESS data
 (Sector~36) when its behavior is relatively periodic and it showed
-relative dip depths of a few percent.  However in other TESS sectors
+dip depths of a few percent.  However in other TESS sectors
 (e.g. Sector~10), this source looks completely different, varying in
@@
 
-Comparing these results against the backdrop of our increasing
+Assessing these results against the backdrop of our increasing
 understanding of dippers
@@
 typically increase by of order a few percent over ten to twenty days.
-{\bf fixme: add closing sentence}
+This growth rate yields a mass flux one order of magnitude larger
+than the earlier estimate.
 
@@
 function that may have been biased in favor of young stars over field
-stars, we caution against interpreting our detection statistics in
-terms of broader population occurrence rates.  The \ngoods\ bonafide
+stars, we caution against interpreting our detection fraction in
+terms of broader population statistics.  The \ngoods\ bonafide
 CQVs are listed in Table~\ref{tab:thetable}.  This table also includes
-an additional \nmaybes\ candidate CQVs, whose designation is less
+an additional \nmaybes\ ambiguous CQVs, whose designation is less
 certain.
 
-Analyzing the TESS light curves and stellar properties of this sample
-of objects, we draw the following conclusions.
+Analyzing the TESS light curves and stellar properties of these
+objects, we draw the following conclusions.
 
@@
     ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
-    can cause dips to collapse instantaneously, and are often (but not
-    exclusively) linked with observed optical flares.  Dip growth
+    can cause dips to collapse instantaneously, and are often but not
+    exclusively linked with observed optical flares.  Dip growth
     however seems to happen over durations of at least ten cycles, and
@@
 	%
-    \item The duty cycle for CQVs seems to be $\approx 75$\%, based on
+    \item The duty cycle for CQVs seems to be $\approx$$75$\%, based on
     the fraction of bonafide CQVs that turned on or turned off during
@@
     \item While the majority of detected CQVs have masses of
-    0.1-0.5\,M$_\odot$, the upper mass limit for the CQV phenomenon
-    might extend into the K-dwarf regime ($<$$0.8$\,M$_\odot$).
+    0.1-0.5\,$M_\odot$, the upper mass limit for the CQV phenomenon
+    might extend into the K-dwarf regime ($<$$0.8$\,$M_\odot$).
     TIC~405754448 and TIC~405910546, with masses of $\approx$0.8 and
@@
 This implies that after correcting for the line-of-sight inclination,
-it seems plausible that a sizable fraction of low mass stars (at
-least one third; \citealt{2022AJ....163..144G}) trap circumstellar
-material but are not observed in transit.
+at least one third of low mass stars
+\citep{2022AJ....163..144G} trap circumstellar
+material in the same way.
 In addition, CQVs should preferentially show edge-on
@@
 observational work also includes searching for outer transiting
-planets, and also measuring equatorial velocities in
+planets, and measuring equatorial velocities in
 order to test whether the stellar inclination angles are indeed
@@
 bizarre shapes that are observed.
-It is certainly possible that the relevant puzzles in plasma physics
-and radiative transfer could also be connected to our
-understanding of the close-in rocky planets that are expected to be
-present around most of these stars.
+The relevant puzzles in plasma physics and radiative transfer could
+likely be connected to our understanding of the close-in rocky planets
+that are expected to be present around most of these stars.
 The challenges intrinsic to both the observational and theoretical
@@
 \enddata
-\tablecomments{This table includes \ngoods\ CQVs (\texttt{Quality} flag true), and \nmaybes\ candidate CQVs (\texttt{Quality} flag false).
-The machine-readable version, available online, includes additional columns for the Gaia DR2 source identifiers and parameter uncertainties.
-The age uncertainties are typically $\approx \pm 10\%$,
-	but can be asymmetric.  The median temperature, radius, and mass uncertainties are $\pm XXX$\,K, $\pm XX$\%, and $\pm YY$\% respectively.
-	$N_{\rm sector}$ denotes the number of TESS sectors for which data are expected to be acquired between July~2018 and Oct~2024.
-Association names and provenance follow conventions adopted by \citet{2018ApJ...856...23G}:
+\tablecomments{This table includes \ngoods\ CQVs (\texttt{Quality}
+  flag true), and \nmaybes\ ambiguous CQVs (\texttt{Quality} flag
+  false).  The machine-readable version, available online, includes
+  additional columns for the Gaia DR2 source identifiers and parameter
+  uncertainties.  The age uncertainties are typically $\approx \pm
+  10\%$, but can be asymmetric.  The median temperature, radius, and
+  mass uncertainties are $\pm XXX$\,K, $\pm XX$\%, and $\pm YY$\%
+  respectively.  $N_{\rm sector}$ denotes the number of TESS sectors
+  for which data are expected to be acquired between July~2018 and
+  Oct~2024.   Association names and provenance follow conventions
+  adopted by \citet{2018ApJ...856...23G}: 
 	ABDMG: AB~Doradus moving group \citep{2015MNRAS.454..593B}.

### 2023-07-15 drivers/make_cpv_table.py

@@ -126,7 +126,7 @@ def main(overwrite=0):
     N_4 = num2word(len(sgdf[sgdf.banyan_assoc == 'FIELD']) + 1)
     N_5 = len(smdf[smdf.banyan_assoc == 'FIELD'])
 
-    N_6 = len(sgdf[sgdf.banyan_assoc != 'FIELD']) + 1
+    N_6 = len(sgdf[sgdf.banyan_assoc != 'FIELD']) - 1
     N_7 = len(smdf[smdf.banyan_assoc != 'FIELD'])
 
     txt = (

### 2023-07-16 paper/ms.tex
update ms

@@
 
-\section{No additional power at 20~second cadence}
-
-Going from K2 to TESS, an important discovery was that the CQV shapes
-can significantly evolve, since the stars can vary over timescales of just a few minutes.
-We observed a set of CQVs between 2020 and 2021 using the TESS 20-second
-cadence mode (TESS DDT029).
-{\bf todo: list the stars.  todo: examine the 2min vs 20sec periodograms, and summarize in a few
-sentences whether any difference is there.}
-
-\section{Chromaticity in TIC 262400835}
-
-TIC~262400835 ($d$=174\,pc) is formally outside the scope of the
-current work.  However, this CQV was observed using MuSCAT2 on 2020
-December 12, 13, and 16, and the results might be worth including in
-this study.
-{\bf todo: describe observations / decide whether to include!}.
-
-We include {\bf a table of the photometry} here to enable potential
-future deeper analyses of the chromaticity of this object class.
-
-Generally, these data serve as a minor addition beyond the
-observations that have been acquired by
-\citet[e.g.][]{2017PASJ...69L...2O,2020PASJ...72...23T,2022AJ....163..144G,2023MNRAS.518.2921K}
-on this topic.  \citet{2023MNRAS.518.2921K} provides what we find to
-be the most lucid summary, and we quote: ``amplitudes are almost
-always larger, the shorter the wavelength of the filter, but the
-relationship can be weak or non-monotonic.''
-
-\begin{figure*}[!t]
-	\begin{center}
-    \includegraphics[width=0.45\textwidth]{TIC262400835_multicolor_phase_stacked.pdf}
-    	\end{center}
-    \vspace{-0.4cm}
-		\caption{
-	      {\bf Chromaticity in TIC~262400835}.
-		}
-		\label{fig:muscat}
-\end{figure*}
+\section{No significant power at 20~second cadence}
+
+TESS was the first instrument to show that CQV light curves contain
+power at timescales of a few minutes
+\citep{127Z,2020AJ....160...86B,2022AJ....163..144G}.  This advance
+was primarily enabled by the fifteen-fold faster cadence in the TESS
+2-minute data, relative to K2.
+
+A logical follow-up question to ask is whether the periodic components
+of the CQV light curves contain power at timescales below one minute.
+Between 2020 and 2021, we observed 10 CQVs at 20-second cadence with
+TESS in order to explore this question (TESS DDT029).  The stars were
+TICs 142173958, 146539195, 24518895, 276453848, 264599508, 363963079,
+144486786, 408188366, 300651846, 262400835.  The general conclusion
+derived from comparing the 20-second to 120-second data for these
+stars (available on MAST) was that CQVs do not contain appreciable
+power at this timescale.
+
+% \section{Chromaticity in TIC 262400835}
+% 
+% TIC~262400835 ($d$=174\,pc) is formally outside the scope of the
+% current work.  However, this CQV was observed using MuSCAT2 on 2020
+% December 12, 13, and 16, and the results might be worth including in
+% this study.
+% {\bf todo: describe observations / decide whether to include!}.
+% 
+% We include {\bf a table of the photometry} here to enable potential
+% future deeper analyses of the chromaticity of this object class.
+% 
+% Generally, these data serve as a minor addition beyond the
+% observations that have been acquired by
+% \citet[e.g.][]{2017PASJ...69L...2O,2020PASJ...72...23T,2022AJ....163..144G,2023MNRAS.518.2921K}
+% on this topic.  \citet{2023MNRAS.518.2921K} provides what we find to
+% be the most lucid summary, and we quote: ``amplitudes are almost
+% always larger, the shorter the wavelength of the filter, but the
+% relationship can be weak or non-monotonic.''
+% 
+% \begin{figure*}[!t]
+% 	\begin{center}
+%     \includegraphics[width=0.45\textwidth]{TIC262400835_multicolor_phase_stacked.pdf}
+%     	\end{center}
+%     \vspace{-0.4cm}
+% 		\caption{
+% 	      {\bf Chromaticity in TIC~262400835}.
+% 		}
+% 		\label{fig:muscat}
+% \end{figure*}
 

### 2023-07-20 paper/ms.tex
update ms

@@
 sector; we refer to these as the ``high-quality sample''.  The
-classification of the remaining \nmaybes\ CQV candidates was ambiguous.  Additional data
-from TESS or other instruments could help resolve their
-classification.  The boolean \texttt{quality} column in the table divides
-the two classes.  In the following, we will restrict our
-discussion to the high-quality sample.
+classification of the remaining \nmaybes\ CQV candidates was
+ambiguous.  Additional data from TESS or other instruments could help
+resolve their classification.  The boolean \texttt{quality} column in
+the table divides the two classes.  In the following, we will restrict
+our discussion to the high-quality sample.
 
@@
 27\,hr$<$$P$$<$38\,hr.
+Regarding likely astrometric or visual binaries,
+\ngoodhighruwe/\ngoods\ high-quality CQVs have a Gaia DR3 RUWE$>$2;
+\nmaybehighruwe/\nmaybes\ of the ambiguous sample share this
+characteristic.
 
@@
 
-The most massive CQV in our sample is a subject of some interest.  To
-date, the only stars reported to show the CQV phenomenon are M-dwarfs,
-with typical stellar masses $\lesssim$0.3\,$M_\odot$
-\citep{2022AJ....163..144G}.  TIC~405754448 and 405910546 however
-appear to have masses of 0.82 and 0.60\,$M_\odot$ respectively.  The
-next-highest masses are $\approx$0.40\,$M_\odot$.  The masses for the
-former two objects are consistent with their CAMD locations, and their
-membership in LCC.  Based on its light curve morphology, TIC~405910546
-should be studied in greater depth, to confirm it is not an eclipsing
-binary.  TIC~405754448 similarly shows distinct morphology from many
-of the CQVs in Figure~\ref{fig:cqvs}, in that it has some of the
-lowest amplitude dips.  Nonetheless, both of these objects seem to
-suggest that the CQV phenomenon extends up in mass to
+The most massive CQVs in our sample might represent an interesting new
+regime.  To date, the only stars reported to show the CQV phenomenon
+are M-dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
+\citep{2022AJ....163..144G}.  TIC~405754448 and TIC~405910546 however
+appear to have masses of $\approx$0.82 and $\approx$0.60\,$M_\odot$
+respectively.  The next-highest masses are $\approx$0.40\,$M_\odot$.
+The masses for the former two objects are consistent with their CAMD
+locations, and their membership in LCC.  Based on its light curve
+morphology, TIC~405910546 should be studied in greater depth, to
+confirm it is not an eclipsing binary.  TIC~405754448 similarly shows
+distinct morphology from many of the CQVs in Figure~\ref{fig:cqvs}, in
+that it has some of the lowest amplitude dips.  While TIC~405754448
+might be an unresolved binary (RUWE$_{\rm DR3}$=4.7),  the lack of
+secondary peaks in its periodogram and the coherent dips present in
+the Sector~11 light curve suggest that the CQV signal is indeed from
+the apparent primary of the system.  Taken in sum, both of these
+objects seem to suggest that the CQV phenomenon extends up in mass to
 pre-main-sequence K-dwarfs.

### 2023-07-23 complexrotators/plotting.py
add plot hd 37776 comparison

@@ -26,6 +26,8 @@ Contents:
 
     | plot_tic4029_segments
 
+    | plot_hd37776_comparison
+
     | plot_catalogscatter
 """
 
@@ -1742,8 +1744,13 @@ def get_2px_neighbors(c_obj, tessmag):
 
     radius = 42*u.arcsecond
 
+    #nbhr_stars = Catalogs.query_region(
+    #    "{} {}".format(float(c_obj.ra.value), float(c_obj.dec.value)),
+    #    catalog="TIC",
+    #    radius=radius
+    #)
     nbhr_stars = Catalogs.query_region(
-        "{} {}".format(float(c_obj.ra.value), float(c_obj.dec.value)),
+        c_obj,
         catalog="TIC",
         radius=radius
     )
@@ -1784,7 +1791,7 @@ def underplot_gcns(ax, get_xval_no_corr, get_yval_no_corr):
     norm = ImageNormalize(vmin=vmin, vmax=vmax, stretch=LogStretch())
 
     cmap = "Greys"
-    cmap = white_viridis
+    #cmap = white_viridis
     density = ax.scatter_density(_x[s], _y[s], cmap=cmap, norm=norm, zorder=1)
 
 
@@ -3640,3 +3647,183 @@ def underplot_cqvtargets(ax, get_xval, get_yval):
     density = ax.scatter_density(_x[s], _y[s], cmap=cmap, norm=norm)
 
     return density
+
+
+def plot_hd37776_comparison(outdir, showtitles=1, titlefontsize=3.75,
+                            selfn='hd37776'):
+
+    # mostmassiveCQV,  HD 37776/landstreet/V901 Ori
+    if selfn == 'hd37776':
+        ticids = ['405754448', '11400909']
+        optionalid = [None, 'HD 37776']
+        showsectors = [38, 6]
+    # HD 64740, in VelaOB2
+    elif selfn == 'hd64740':
+        ticids = ['201789285', '268971806']
+        optionalid = [None, 'HD 64740']
+        showsectors = [3, 34]
+    # sigma-ori
+    elif selfn == 'sigmaoriE':
+        msg = (
+            "there are not any good matches..."
+            "because i would have labelled sigma Ori E an RS CVn"
+        )
+        raise NotImplementedError(msg)
+
+    # prepare to get lc data
+    from complexrotators.lcprocessing import (
+        cpv_periodsearch, prepare_cpv_light_curve
+    )
+
+    #
+    # instantiate plot
+    #
+    set_style("science")
[…]

### 2023-07-24 paper/ms.tex
nb: add interact_template
update ms

@@
 characteristic.
+% This is consistent with Rappaport2014's visual binary fraction determined from
+% 30/100 rapidly rotating Kepler stars having multiple periodicities
 
@@
 
-It is amusing that in identifying the two ambiguous CQV sources in
+It is amusing that in identifying the two ambiguous CQVs in
 Section~\ref{subsec:irexcess} with outlying SEDs (TICs~193136669 and
@@
 than the earlier estimate.
+
+\subsection{Is it inflow or outflow?}
+
+The B-star analogy is an outflow.
+Debris disks are an inflow.
+It seems to match the B-star analogy.
 

### 2023-07-25 paper/ms.tex
update ms
(add B-star connection)

@@
   the Keplerian corotation radius.  Here, we report new CQVs
-  discovered in TESS short-cadence data collected between July~2018 and Sep~2022.
-  Our search of \nstarssearched\ K- and M-dwarfs with $T$$<$16 and
-  $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most of these
-  discoveries are new, and they include the brightest
-  ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc)
-  examples of this class of object known, and probably also the most massive
-  ($\approx$0.6-0.8\,$M_\odot$) and oldest ($\approx$200\,Myr).  A few objects are outliers among
-  outliers; LP 12-502 for instance shows a recurring ``dip complex'' with a
-  period and total duration that are fixed over more than 1{,}000
-  cycles, but which in detail exhibits anywhere from four to eight
-  local minima per cycle.  LP 12-502 also displayed distinct superposed
-  periods simultaneously, and showed drastic shape changes shortly
-  after flares.  Broadly speaking, we find that none of the CQVs
-  maintain a fixed light curve shape over timescales of more than a
-  few hundred cycles, and we revisit the arguments for why transient
-  corotating material is the most viable explanation.  In the future,
-  we expect that our sample will facilitate modeling and observational
-  efforts aimed at understanding these objects, and connecting them to
-  the broader contexts of star, disk, and exoplanet evolution.
-  For instance, if the transiting material is dust, then the rate of dip
-  evolution implies that of order an asteroid belt's worth of mass
-  passes through these structures over their lifetime of $\approx$$10^8$ years.
+  discovered in TESS short-cadence data collected between July~2018
+  and Sep~2022.  Our search of \nstarssearched\ K- and M-dwarfs with
+  $T$$<$16 and $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most
+  of these discoveries are new, and they include the brightest
+  ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc) examples of this
+  class of object known, and probably also the most massive
+  ($\approx$0.6-0.8\,$M_\odot$) and oldest ($\approx$200\,Myr).  A few
+  objects are outliers among outliers; LP 12-502 for instance shows a
+  recurring ``dip complex'' with a period and total duration that are
+  fixed over more than 1{,}000 cycles, but which in detail exhibits
+  anywhere from four to eight local minima per cycle.  LP 12-502 also
+  displayed distinct superposed periods simultaneously, and showed
+  drastic shape changes shortly after flares.  Broadly speaking, we
+  find that none of the CQVs maintain a fixed light curve shape over
+  timescales of more than a few hundred cycles, and we revisit the
+  arguments for why transient corotating material is the most viable
+  explanation.  In the future, we expect that our sample will
+  facilitate modeling and observational efforts aimed at understanding
+  these objects, and connecting them to the broader contexts of star,
+  disk, and exoplanet evolution.  For instance, if the transiting
+  material is dust, then the rate of dip evolution implies that of
+  order an asteroid belt's worth of mass passes through these
+  structures over their lifetime of $\approx$$10^8$ years.
 \end{abstract}
@@
 A few competing explanations for what causes the complex quasiperiodic
-variability are shown in Figure~\ref{fig:f1}.  All young M-dwarfs are spotted, which
-produces flux variations over characteristic timescales of the
-rotation period, $P_{\rm rot}$, and its half-harmonic, $0.5\,P_{\rm
-rot}$.  The observed dips occur over durations as short as
-$0.05\,P_{\rm rot}$; a ``starspot-only'' scenario can be discarded for
-any object with sufficiently sharp dips
+variability are shown in Figure~\ref{fig:f1}.  All young M-dwarfs are
+spotted, which produces flux variations over characteristic timescales
+of the rotation period, $P_{\rm rot}$, and its half-harmonic,
+$0.5\,P_{\rm rot}$.  The observed dips occur over durations as short
+as $0.05\,P_{\rm rot}$; a ``starspot-only'' scenario can be discarded
+for any object with sufficiently sharp dips
 \citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The timescales and
@@
 extending an order of magnitude longer than the $\approx$$10^7$ year
-timescale typically quoted for primordial disk dispersal.
-However, unambiguous evidence in support of any one scenario has yet
-to be acquired.  Such evidence might include a spectroscopic detection
-of silicate 10\,$\mu$m dust absorption during a dip, or perhaps
-detection of transient Balmer-line absorption as a function of cycle
-phase, similar to observations made in systems such as AB~Dor
-\citep[see the review by][]{1999ASPC..158..146C}.
+timescale typically quoted for primordial disk dispersal.  However,
+unambiguous evidence in support of any one scenario has yet to be
+acquired.  Such evidence might include a spectroscopic detection of
+silicate 10\,$\mu$m dust absorption during a dip, or perhaps detection
+of transient Balmer-line absorption as a function of cycle phase,
+similar to observations made in systems such as AB~Dor \citep[see the
+review by][]{1999ASPC..158..146C}.
 
@@
 proposed by \citet{2017AJ....153..152S} may indeed provide some
-helpful visual distinctions amongst the CQVs, it seems likely
-that they are all explained by a single underlying phenomenon, and so
-we opt to refer to them by a single empirically descriptive name.
+helpful visual distinctions amongst the CQVs, it seems likely that
+they are all explained by a single underlying phenomenon, and so we
+opt to refer to them by a single empirically descriptive name.
 
@@
     stacked over one month.  Gray circles are raw 2-minute data; black
-    circles bin to
-		300 points per cycle.  Periods in hours are in the bottom right of
-		each panel.  Left-to-right, the objects are LP 12-502
-		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
-		425933644 (Sector~28).
+    circles bin to 300 points per cycle.  Periods in hours are in the
+    bottom right of each panel.  Left-to-right, the objects are LP
+    12-502 (TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and
+    TIC 425933644 (Sector~28).
     {\it Bottom:} Cartoon models for the phenomenon.  The dust clump
-		scenario
-		(lower left) and prominence scenario (lower center) both invoke centrifugally-supported material at the
-		corotation radius.
+    scenario (lower left) and prominence scenario (lower center) both
+    invoke centrifugally-supported material at the corotation radius.
     We disfavor the screen scenario (see Section~\ref{sec:intro}).
@@
 
-We determined the stellar effective temperature and radii by 
-fitting the broadband spectral energy distributions (SEDs); we then estimated the masses by interpolating against the
-sizes, temperatures, and ages against the
-PARSEC v1.2S models \citep{2012MNRAS.427..127B,2014MNRAS.444.2525C}.
+We determined the stellar effective temperature and radii by fitting
+the broadband spectral energy distributions (SEDs); we then estimated
+the masses by interpolating against the sizes, temperatures, and ages
+against the PARSEC v1.2S models
+\citep{2012MNRAS.427..127B,2014MNRAS.444.2525C}.
 
@@
 confirmed \ngoods\ CQVs in our catalog; for plotting purposes we show
-the brightest 27.  
-We have phased each sector to its own local minimum because for most of the
-sources we do not know the period at the precision necessary to be able to
-accurately propagate an ephemeris over two years.
+the brightest 27.  We have phased each sector to its own local minimum
+because for most of the sources we do not know the period at the
+precision necessary to be able to accurately propagate an ephemeris
+over two years.
 
@@
       {\bf Properties of CQVs identified by our search}.
-      The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are 
-      the dark blue circles; \nmaybes\ ambiguous CQV candidates are light blue circles.
-      The top panels show the \nstarssearched\ target stars with 120-second cadence TESS data
-      as the shaded gray background;
-      darker regions correspond to a larger relative number of searched stars.
-      The lower-left panel compares the rotation--color distribution of CQVs against the rotation
-      periods of K- and M-dwarfs in the Pleiades from \citet{2016AJ....152..114R}.
-      The lower-middle panel plots the derived corotation radii
-      $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in units of stellar radii against the measured
-      CQV periods, in units of hours.
+      The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are the
+      dark blue circles; \nmaybes\ ambiguous CQV candidates are light
+      blue circles.  The top panels show the \nstarssearched\ target
+      stars with 120-second cadence TESS data as the shaded gray
+      background; darker regions correspond to a larger relative
+      number of searched stars.  The lower-left panel compares the
+      rotation--color distribution of CQVs against the rotation
+      periods of K- and M-dwarfs in the Pleiades from
+      \citet{2016AJ....152..114R}.  The lower-middle panel plots the
+      derived corotation radii $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in
+      units of stellar radii against the measured CQV periods, in
+      units of hours.
 		}
@@
 that it has some of the lowest amplitude dips.  While TIC~405754448
-might be an unresolved binary (RUWE$_{\rm DR3}$=4.7),  the lack of
-secondary peaks in its periodogram and the coherent dips present in
-the Sector~11 light curve suggest that the CQV signal is indeed from
-the apparent primary of the system.  Taken in sum, both of these
-objects seem to suggest that the CQV phenomenon extends up in mass to
-pre-main-sequence K-dwarfs.
+might be an unresolved binary (RUWE$_{\rm DR3}$=4.7),  the depth of
+the coherent dips present in the Sector~11 light curve imply that the
+CQV signal is indeed from the apparent primary of the system.  Taken
+in sum, both of these objects seem to suggest that the CQV phenomenon
+extends up in mass to pre-main-sequence K-dwarfs.
+
+\subsection{TIC~425937691}
+
+TIC~425937691 is a suprising case: it shows two seemingly independent
+CQV signals on what appears to be the same star.  The two signals have
+periods of $\approx$4.816\,hr and $\approx$3.218\,hr, respectively.
+The former is the larger amplitude signal visible in
+Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, corresponding to signal
+with peak-to-peak amplitude of $\approx$8\%.  The latter signal is
+only visible after subtracting the primary period, and it has a
+sinusoidal envelope with a peak-to-peak amplitude of 2.5\%, and with
+three sharp dips super-posed over each cycle.  The Gaia DR3 RUWE for
+TIC~425937691 is 2.9.
+
+The explanation that seems most likely for this source, given the two
+photometric signals and the elevated RUWE, is an unresolved binary
+consisting of two CQVs.  Recent work has shown that the orbits of
+binaries closer than $\lesssim$700 AU tend to be aligned with their
+planetary systems \citep{2022AJ....163..207C}.  If we assume that
+observing CQV variability similarly requires near edge-on viewing
+geometries, then we might expect a sufficiently close binary with one
+CQV to also have another, since the spin axes in sufficiently close
+binaries would tend to be aligned.  In this scenario, the two periods
+being within $\approx$0.2\% of the 3:2 period commensurability would
+simply be a coincidence.
 
@@
 constant to within measurement precision over thousands of cycles, the
-light curve shapes evolve over 10 to 1{,}000 cycles.
-They are therefore {\it quasi}periodic.  This observation is consistent
-studies by \citet{2022AJ....163..144G} and
-\citet{2023ApJ...945..114P}.  However it marks a qualitative departure
-from the ``persistent'' {\it vs.} ``transient'' flux dip distinction
-described by \citet{2017AJ....153..152S};  since all CQV dips seem to
-be transient over timescales of more than 1{,}000 cycles
-(Figure~\ref{fig:evoln}).
+light curve shapes evolve over 10 to 1{,}000 cycles.  They are
+therefore {\it quasi}periodic.  This observation is consistent studies
+by \citet{2022AJ....163..144G} and \citet{2023ApJ...945..114P}.
+However it marks a qualitative departure from the ``persistent'' {\it
+vs.} ``transient'' flux dip distinction described by
+\citet{2017AJ....153..152S};  since all CQV dips seem to be transient
+over timescales of more than 1{,}000 cycles (Figure~\ref{fig:evoln}).
 
@@
 
-Examining Figure~\ref{fig:cqvs}, it is not obvious whether CQVs as
-a whole show any preference for sharper ingresses, or sharper
-egresses.  In some cases (e.g. TIC~425933644), the continuum itself is
-not well-defined, and so the meaning of ``ingress'' and
-``egress'' are not clear.  In others, such as Sector~36
-of TIC~89463560, there is a single clear sharp ingress with an
-exponential egress, which could be directly fit using e.g.~a model
-analogous to those used for exocomets
+Examining Figure~\ref{fig:cqvs}, it is not obvious whether CQVs as a
+whole show any preference for sharper ingresses, or sharper egresses.
+In some cases (e.g. TIC~425933644), the continuum itself is not
+well-defined, and so the meaning of ``ingress'' and ``egress'' are not
+clear.  In others, such as Sector~36 of TIC~89463560, there is a
+single clear sharp ingress with an exponential egress, which could be
+directly fit using e.g.~a model analogous to those used for exocomets
 \citep[e.g.][]{2019A&A...625L..13Z}.  The main quantities of interest
@@
 \subsection{Dust, or gas?}
-We believe that the most likely scenarios to explain CQVs
-are either the dust clump scenario or the prominence scenario
+We believe that the most likely scenarios to explain CQVs are either
+the dust clump scenario or the prominence scenario
 (Figure~\ref{fig:f1}).  Both invoke clumpy material that would be
@@
 led to the interpretation that the data could best be explained by
-similar structures: cold, minimally ionized hydrogen clouds
-or filaments that scatter chromospheric emission from the star to
-produce the observed spectroscopic line variations
+similar structures: cold, minimally ionized hydrogen clouds or
+filaments that scatter chromospheric emission from the star to produce
+the observed spectroscopic line variations
 \citep[see][]{1989MNRAS.238..657C}.  The short-term mechanical
@@
 
-Any link between the dense gas clumps (prominences) that likely exist
-around rapidly rotating low-mass stars and the CQV phenomenon has
-yet to be made.  A simple visual examination of the TESS light curves
-for five prominence-hosting systems studied by
+A clear link between the dense gas clumps (prominences) that likely
+exist around rapidly rotating low-mass stars and the CQV phenomenon
+has yet to be made.  A simple visual examination of the TESS light
+curves for five prominence-hosting systems studied by
 \citet{2019MNRAS.482.2853J}--AB~Dor, Speedy~Mic, LQ Lup, HK Aqr, and
 V374 Peg--revealed no obvious CQV behavior, though all show
-differential evolution, and Speedy~Mic shows two closely-spaced periods
-and a strong beat.  Spectroscopically observable prominences 
-do not imply CQV-like dips.
+differential evolution, and Speedy~Mic shows two closely-spaced
+periods and a strong beat.  Spectroscopically observable prominences
+do not imply photometric CQV-like dips.
 
@@
 
-\subsubsection{Can gas absorption reproduce the observed chromaticity?}
-The strongest argument for why neutral hydrogen is an unlikely
-occulting source is that CQVs show broadband flux variations that are
-deeper in the blue than in the red.
-
-Based on our reading of \citet[][Ch.~8]{1992oasp.book.....G}, it seems
-challenging to get neutral hydrogen to have this type of
-chromaticity.  Bound-bound absorption provides opacity only at narrow
-resonant lines.  Bound-free absorption can provide
-wavelength-dependent opacity, but the absorption coefficients
-generally {\it grow} with increasing wavelength, rather than {\it
-shrink} as one needs in order to get deeper absorption in the blue
-than in the red.  H$^-$  fails as a viable opacity source for the same
-reason: its absorption coefficient peaks near 8500\,\AA, and is an
-order of magnitude smaller at $\approx$3000\AA.
-(\citealt{1992oasp.book.....G}, following \citealt{1979MNRAS.187P..59W}).
-Thompson scattering is also ruled out, because it is gray.  Dust, with
-its larger absorption cross-section in the blue than the red
-\citep{1989ApJ...345..245C}, is to our knowledge the most obvious
-opacity source.
-
-While the reasoning above seems fairly convincing, it has a
-flaw.  The argument presented above would imply that regardless of a
-star's temperature, if relative depths of a dip are seen to be deeper
-in the blue than in the red, then it is hard to get hydrogen to do it.
-There is however a rapidly rotating magnetic B-star, $\sigma$~Ori~E,
-which shows dips that are deeper in the blue than in the red
-\citep{1977ApJ...216L..31H}.  Photometric and spectroscopic
-observations of this star have been understood in terms of absorbing
-circumstellar material, analogous to the geometries we are
-discussing for much cooler M-dwarfs \citep{2005ApJ...630L..81T}.  This
-material however is unlikely to be dust, due to the relevant sublimation
-timescales.  The opacity is instead thought to be sourced from bound-free
-absorption from neutral hydrogen \citep{2005ApJ...630L..81T}.
-Separate and smaller amplitude emission in that system may also come
-from electrons scattering photospheric light toward the observer when
-the clouds are not in transit \citep{2022MNRAS.511.4815B}.
-
-Given these complexities, it clearly seems important for a future
-theoretical study to be conducted to determine to what degree the
-observed chromaticities in CQVs match, or do not match, expectations
-from radiative transfer.  This issue has a key ability to resolve the
-question of whether the CQVs are caused by dust, or by gas.  This
-question has direct bearing on the potential utility of these objects.
+\subsubsection{Gas absorption microphysics}
+CQVs show broadband flux variations that can be 1-2$\times$ deeper in
+the blue than in the red
+\citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
+For neutral hydrogen to produce this effect in absorption, its opacity
+must be larger in the blue than in the red.
+\citet{1992oasp.book.....G} suggests that this might be
+microphysically possible: while bound-bound absorption provides
+opacity only at narrow resonant lines, the hydrogen opacity due to
+bound-free absorption is ``jagged'' \citep[see][Figure 8.5 and
+Eq.~8.8]{1992oasp.book.....G}, such that at temperatures of
+$\approx$3{,}000\,K to $\approx$10{,}000\,K the observed chromatic
+transit depths might be reproduced.  Thompson scattering is ruled out
+as a relevant opacity source, because it is gray.  The other plausible
+alternative opacity source is dust, which also has a larger absorption
+cross-section in the blue than the red \citep{1989ApJ...345..245C}.
+
+An interesting point of comparison is the rapidly rotating magnetic
+B-star, $\sigma$~Ori~E, which shows dips that are deeper in the blue
+than in the red \citep{1977ApJ...216L..31H}.  Photometric and
+spectroscopic observations of this star have been understood in terms
+of absorbing circumstellar material, analogous to the geometries we
+are discussing for much cooler M-dwarfs \citep{2005ApJ...630L..81T}.
+This material however is unlikely to be dust, due to the relevant
+sublimation timescales.  The opacity is instead thought to be sourced
+from bound-free absorption from neutral hydrogen
+\citep{2005ApJ...630L..81T}.  Separate and smaller-amplitude emission
+in that system may also come from electrons scattering photospheric
+light toward the observer when the clouds are not in transit
+\citep{2022MNRAS.511.4815B}.
+
+Given these complexities, it seems important for a future theoretical
+study to be conducted to determine to what degree the observed
+chromaticities in CQVs match, or do not match, expectations from
+radiative transfer.  This issue has a key ability to resolve the
+question of whether the CQVs are explained by dust or by gas, which
+likely has bearing on whether the material producing the dips
+is coming from the star, or whether it is a byproduct of the
+protoplanetary disk.
 
@@
 \subsubsection{The lifetime constraint}
-Independent of the microphysical basis for gas absorption, the observed
-lifetime of the CQV phenomenon could provide another dimension to discern between
-the gas {\it vs.} dust clump scenarios.
-Based on the available statistics from the studies by L.~Rebull and J.~Stauffer,
-it seems plausible that CQV occurrence decreases in time, bottoming to zero
-well before the $\approx$700\,Myr age of Praesepe.
-This is odd in the context of the prominence scenario, because pre-main-sequence
-M-dwarfs spin up over the first $\approx$$10^8$\,yr;
-prominences might even be expected to be {\it more} common at the 
-age of the Pleiades than for younger stars.
-This broadly assumes that any star that can support prominences will,
-which translates in detail to a condition on the star's mass, rotation
-period, and magnetic field strength.
-Based on the degree to which M-dwarfs remain rapid rotators over the first 700\,Myr
-\citep[e.g. Figure~13 of][]{2022AJ....164...80R}, 
-it seems surprising in the gas clump (prominence) scenario that no stars
-older than 150\,Myr have been seen to exhibit the phenomenon.
-In the dust clump scenario this is not a problem, because if the dust
-were externally sourced, it would be expected to have a finite supply.
+Independent of the microphysical basis for gas absorption, the
+observed lifetime of the CQV phenomenon could provide another
+dimension to discern between the gas {\it vs.} dust clump scenarios.
+Based on the available statistics from the studies by L.~Rebull and
+J.~Stauffer, it seems plausible that CQV occurrence decreases in time,
+bottoming to zero well before the $\approx$700\,Myr age of Praesepe.
+This is odd in the context of the prominence scenario, because
+pre-main-sequence M-dwarfs spin up over the first $\approx$$10^8$\,yr;
+prominences might even be expected to be {\it more} common at the age
+of the Pleiades than for younger stars.  This broadly assumes that any
+star that can support prominences will, which translates in detail to
+a condition on the star's mass, rotation period, and magnetic field
+strength.  Based on the degree to which M-dwarfs remain rapid rotators
+over the first 700\,Myr \citep[e.g. Figure~13
+of][]{2022AJ....164...80R}, it seems surprising in the gas clump
+(prominence) scenario that very few stars older than 150\,Myr have
+been seen to exhibit the phenomenon.  In the dust clump scenario this
+is not a problem, because if the dust were externally sourced, it
+would be expected to have a finite supply.
 
@@
 
-Planet occurrence rate studies based on Kepler showed that around
-(early) M-dwarfs, there are $\approx$0.1 planets per star with sizes
-between 1-4\,$R_\oplus$ and orbital periods within 3 days
+Planet occurrence rate studies from Kepler have shown that high-mass
+M- dwarfs have $\approx$0.1 planets per star with sizes between
+1-4\,$R_\oplus$ and orbital periods within 3 days
 \citep{2015ApJ...807...45D}.  The number increases to $\approx$0.7
-planets per star, for planets with 1-4\,$R_\oplus$ and $P$$<$10\,days.
+planets per star for planets with 1-4\,$R_\oplus$ and $P$$<$10\,days.
 Extrapolating to all small close-in planets, with say
 0.1-4\,$R_\oplus$ and within 10 days, it is reasonable to expect on
-average one planet per M-dwarf.  TRAPPIST-1b ($P$=1.5\,days) is one
+average one planet per M-dwarf.  TRAPPIST-1b ($P$=1.5\,days) is an
 example of this type of planet, in orbit around a 0.08\,$M_\odot$ star
@@
 
-In the context of planet formation theory, the locations of these
-close-in planets are set by the location of the protoplanetary disk's
-magnetospheric truncation radius (see e.g. CITE for a review).  In
-simple 1-D viscous accretion models, this truncation radius roughly
-coincides with the corotation radius (CITE), though in detail factors
-of a few difference have been observed between the two (CITE IR
-studies).  Within models that have migrating compact multiplanet
-resonant chains, the inner-most planets arrive within $\approx$5-10
-stellar radii within the first 100\,Myr \citep{2018haex.bookE.142I}.
-
-Given this context, it is tempting to try to interpret features of the
+In the context of planet formation, the stopping location for the
+inner-most planet is set by the location of the protoplanetary disk's
+truncation radius \citep{2018haex.bookE.142I}.  Although this disk
+truncation radius is defined by equating the magnetic pressure from
+the stellar magnetosphere with the ram pressure form the inflowing
+gas, it also tends to roughly coincide with the Keplerian corotation
+radius \citep{2016ARA&A..54..135H}.  Within models that have compact
+multiplanet resonant chains migrate inward due to gas drag, the
+inner-most planets arrive within $\approx$5-10 stellar radii before
+the disk becomes depleted.
+
+In this context, it is tempting to try to interpret features of the
 CQV light curves in terms of the possible presence of close-in
-exoplanets, or even planetesimals.  Rocky planets this young would
-likely have molten global magma oceans analogous to those that existed
-on the Earth and Moon \citep[see][]{2022arXiv220310023L}, and thus
-would be undergoing significant outgassing and atmospheric escape.
-However while a scenario in which close-in rocky planets or
-planetesimals serve as a possible source of dust for the clouds is
-{\it a priori} plausible, any evidence in support of such a picture
-currently seems ambiguous at best.
+exoplanets, or even planetesimals, that are expected to exist in
+abundance around these stars.  Rocky planets this young could have
+molten global magma oceans analogous to those that existed on the
+Earth and Moon \citep[see][]{2022arXiv220310023L}, and thus might be
+undergoing significant outgassing and atmospheric escape.  However,
+although it is {\it a priori} plausible that close-in rocky planets or
+planetesimals could serve as a possible source of material for the
+clouds, any evidence in support of such a picture currently seems
+ambiguous at best.
 
@@
 planetesimal swarm, rather than just a single planetesimal.  
-While the
-number of free parameters in this type of model is somewhat dizzying,
-we have no right to believe that nature need be simple.
+While the number of free parameters in this type of model is somewhat
+dizzying, we have no right to believe that nature need be simple.
 The need for a swarm rather than just one launching body would
@@
 changes in the local magnetic field or coronal plasma density.
-The sizes of these purported planetesimals
-would need to be $\lesssim 1$\,$R_\oplus$, based on the non-detections
-of their transits, analogous to e.g.  K2-22
-\citep{2015ApJ...812..112S} or KOI-2700 \citep{2014ApJ...784...40R}.
-Typical sizes of bodies in the asteroid belt for instance span
-hundreds of meters to a few kilometers.
-
-The planetesimal swarm model would also predict that certain orbital
-phases would produce recurrent dips if observed over sufficiently long
+The sizes of these purported planetesimals would need to be $\lesssim
+1$\,$R_\oplus$, based on the non-detections of their transits,
+analogous to e.g.  K2-22 \citep{2015ApJ...812..112S} or KOI-2700
+\citep{2014ApJ...784...40R}.  Typical sizes of bodies in the asteroid
+belt for instance span hundreds of meters to a few kilometers.
+
+The planetesimal swarm model would predict that certain orbital phases
+would produce recurrent dips if observed over sufficiently long
 timescales, since the launching planetesimal would be massive enough
@@
 over the existing baseline (Figure~\ref{fig:lp2}) might agree with
-this prediction, 
-for most other CQVs (Figure~\ref{fig:evoln}) the data seem likely to
-be in tension with this expectation.
+this prediction, for most other CQVs (Figure~\ref{fig:evoln}) the data
+seem to be in tension with this expectation.
 
 There are a few additional problems for the idea of a disintegrating
-planetesimal swarm.  First, many of the dips show asymmetries in
-the wrong direction relative to the naive expectation of a
-trailing comet tail.  Invoking non-exponentially decaying dust
-distributions as a function of azimuth might be one way out of this,
-but such an idea would need stronger theoretical footing.  
-Dynamical stability would be a separate concern:
-in a model in which any new dip is ``explained'' by invoking a new
-planetesimal, one might eventually pack the corotation radius to a
-degree where instability over short timescales would be guranteed.
+planetesimal swarm.  First, many of the dips show asymmetries in the
+wrong direction relative to the naive expectation of a trailing comet
+tail.  Invoking non-exponentially decaying dust distributions as a
+function of azimuth might be one way out of this, but such an idea
+would need stronger theoretical footing.  Dynamical stability would be
+a separate concern: in a model in which any new dip is ``explained''
+by invoking a new planetesimal, one might eventually pack the
+corotation radius to a degree where instability over short timescales
+would be guaranteed.
 
@@
 
-It is amusing that in identifying the two ambiguous CQVs in
-Section~\ref{subsec:irexcess} with outlying SEDs (TICs~193136669 and
-TIC~57830249), we were prompted to reconsider our light curve-based
-labeling, to
-ultimately conclude that these sources are dippers.  This episode
-suggests that there could be overlap between CQVs and dippers.  It is also worth emphasizing that our labeling of
-e.g.~TIC~57830249 was based on a single sector of TESS data
-(Sector~36) when its behavior is relatively periodic and it showed
-dip depths of a few percent.  However in other TESS sectors
-(e.g. Sector~10), this source looks completely different, varying in
-apparent flux by a factor of two, with hardly any discernible
-periodicity at all.
+In identifying the two ambiguous CQVs with outlying SEDs (TICs~193136669 and
+TIC~57830249; Section~\ref{subsec:irexcess}), we were prompted to reconsider our light curve-based
+labeling, and ultimately concluded that these sources are dippers.  This
+episode suggests that there could be overlap between CQVs and dippers.
+It is also worth emphasizing that our labeling of e.g.~TIC~57830249
+was based on a single sector of TESS data (Sector~36) when its
+behavior is relatively periodic and it showed dip depths of a few
+percent.  However in other TESS sectors (e.g. Sector~10), this source
+looks completely different, varying in apparent flux by a factor of
+two, with hardly any discernible periodicity at all.
 
@@
 The dips in both are probably associated with clumps of dust or gas.
-However the CQV dips are typically more periodic and 
-less deep than those of dippers, and they display far
-less transience over timescales of a few to tens of cycles.  This is
-probably because CQV stars have demonstrably less dust than (most)
-dipper stars.  At a population level, the CQV stars are also older.  A
-common mystery between the CQVs and dippers, in our own estimation, is
-how exactly the {\it narrowness} of the dust clumps is produced.  It
-is not unreasonable to imagine a similar mechanism operating for both
-types of object, tied perhaps to a shared magnetic topology, or
-perhaps to a preference for dust to inspiral to the star in clumped
-structures.
+However the CQV dips are typically more periodic and less deep than
+those of dippers, and they display far less transience over timescales
+of a few to tens of cycles.  This is probably because CQV stars have
+demonstrably less dust than (most) dipper stars.  At a population
+level, the CQV stars are also older.  A common mystery between the
+CQVs and dippers, in our own estimation, is how exactly the {\it
+narrowness} of the dust clumps is produced.  It is not unreasonable to
+imagine a similar mechanism operating for both types of object, tied
+perhaps to a shared magnetic topology, or perhaps to a preference for
+dust to inspiral to the star in clumped structures.
 
@@
 
+\begin{figure*}[!t]
+	\begin{center}
+		\centering
+		\includegraphics[width=0.9\textwidth]{f8.pdf}
+		\vspace{-0.1cm}
+		\caption{
+			{\bf The magnetic B-star connection}.
+			HD~37776 (TIC~11400909) and HD~64740 (TIC~268971806) are
+			magnetic B-stars with field geometries dominated by
+			high order multipoles.
+			Here, we compare their phased TESS light curves against the
+			``best-matching'' CQV light curves, selected by eye from
+			Figure~\ref{fig:cqvs}.
+			Stellar masses approximate to one significant figure are given in the
+			lower right of each panel; the star, TESS sector, and period are also noted.
+		}
+		\label{fig:bstar}
+	\end{center}
+\end{figure*}
+
 \subsection{Mass flux estimate}
@@
 transit depth to an effective cloud radius, $R_{\rm cloud}$.  For most
-CQVs in Figure~\ref{fig:cqvs}, this typically yields $\approx$2-20\,$R_\oplus$.
-This size can be converted into a mass estimate by requiring the
-optical depth $\tau$ of the cloud to be at least unity and by positing
-some composition for the cloud.  In other
-words, a minimum constraint on the number density follows by
-requiring the cloud to be optically thick.  For cases like LP 12-502,
-this is reasonable because the transit duration implies $R_{\rm
-cloud}\ll R_\star$.  Carrying out the relevant calculation assuming
-the occulting material is dust grains 1\,$\mu$m in size,
+CQVs in Figure~\ref{fig:cqvs}, this typically yields
+$\approx$2-20\,$R_\oplus$.  This size can be converted into a mass
+estimate by requiring the optical depth $\tau$ of the cloud to be at
+least unity and by positing some composition for the cloud.  In other
+words, a minimum constraint on the number density follows by requiring
+the cloud to be optically thick.  For cases like LP 12-502, this is
+reasonable because the transit duration implies $R_{\rm cloud}\ll
+R_\star$.  Carrying out the relevant calculation assuming the
+occulting material is dust grains 1\,$\mu$m in size,
 \citet{2023MNRAS.518.4734S} find minimum cloud masses of order
 $10^{12}$\,kg (their Eq.~23), which scale linearly with both the
-optical depth and dust grain radius.  This is comparable to a
-small asteroid; the asteroid belt itself has a mass of
-order $\approx$10$^{21}$\,kg (CITE).  
-The previously discussed cool gas prominences would need to have
-masses of order $10^{14}$\,kg \citep{1990MNRAS.247..415C}, about
-100$\times$ larger than the requisite dust mass.
-
-Our observations provide a direct measurement of how often dips
-appear and disappear, both due to sudden state-switches, and
-due to more gradual, secular evolution.  For instance, LP~12-502
-showed three ``state-switch'' events over the six months of available TESS
+optical depth and dust grain radius.  This is comparable to a small
+asteroid; the asteroid belt itself has a mass of order
+$\approx$10$^{21}$\,kg \citep{2019Icar..319..812P}.  The previously
+discussed cool gas prominences would need to have masses of order
+$10^{14}$\,kg \citep{1990MNRAS.247..415C}, about 100$\times$ larger
+than the requisite dust mass.
+
+Our observations provide a direct measurement of how often dips appear
+and disappear, both due to sudden state-switches, and due to more
+gradual, secular evolution.  For instance, LP~12-502 showed three
+``state-switch'' events over the six months of available TESS
 observations, during cycles 248-264, 299-315, and 1233-1247.  In each
-case, a dip ``turned off''.  It is
-plausible to imagine that these events correspond to either mass being
-ejected from corotation, or perhaps being accreted onto the star.  In
-either case, the corresponding $\dot{M} \equiv M\cdot {\rm d}N/{\rm d}t$
-time-averaged over six months
-is $\approx$3$\times$$10^{-18} M_\odot\,{\rm yr}^{-1} \approx
-1\times10^{-12} M_\oplus\,{\rm yr}^{-1}$.  Considered cumulatively
-over the $\approx$$10^8$ years for which the CQV phenomenon is
-observed, this yields a cumulative moved dust mass of
-$10^{-4}\,M_\oplus$, of order the Solar System's asteroid belt.
-If the occulting material is gas, the masses involved would be of
-order 100 times larger.
-For cases in which we observe the {\it growth} of
-dips, such as the Sector~29 data for TIC~224283342,
-or Sector~5 of TIC~294328885,
-the dip depths
-typically increase by of order a few percent over ten to twenty days.
-This growth rate yields a mass flux one order of magnitude larger
-than the earlier estimate.
-
-\subsection{Is it inflow or outflow?}
-
-The B-star analogy is an outflow.
-Debris disks are an inflow.
-It seems to match the B-star analogy.
+case, a dip ``turned off''.  It is plausible to imagine that these
+events correspond to either mass being ejected from corotation, or
+perhaps being accreted onto the star.  In either case, the
+corresponding $\dot{M} \equiv M\cdot {\rm d}N/{\rm d}t$ time-averaged
+over six months is $\approx$3$\times$$10^{-18} M_\odot\,{\rm yr}^{-1}
+\approx 1\times10^{-12} M_\oplus\,{\rm yr}^{-1}$.  Considered
+cumulatively over the $\approx$$10^8$ years for which the CQV
+phenomenon is observed, this yields a cumulative moved dust mass of
+$10^{-4}\,M_\oplus$, of order the Solar System's asteroid belt.  If
+the occulting material is gas, the masses involved would be of order
+100 times larger.  For cases in which we observe the {\it growth} of
+dips, such as the Sector~29 data for TIC~224283342, or Sector~5 of
+TIC~294328885, the dip depths typically increase by of order a few
+percent over ten to twenty days.  This growth rate yields a mass flux
+one order of magnitude larger than the earlier estimate.
+
+\subsection{Strengthening the magnetic B-Star connection}
+Previous work by \citet{2017AJ....153..152S} noted an intriguing
+connection between the CQVs and rapidly rotating magnetic B-stars such
+as $\sigma$~Ori~E, which are known to have circumstellar gas clouds
+trapped in corotation \citep{2005ApJ...630L..81T}.  Spectropolarimetry
+has indicated that, similar to $\sigma$~Ori~E, most magnetic B-stars
+have relatively simple field geometries that are predominantly
+dipolar, though generally not aligned with the stellar spin axis
+\citep{2009ARA&A..47..333D}.  Two exceptions to this rule are HD~37776
+and HD~64740, which are B-stars that were previously known from
+spectropolarimetry in the 2000s-2010s to have more complicated field
+geometries - dominated by high order multipoles
+\citep{2011ApJ...726...24K}.  It turns out, recent TESS light curves
+of these two B-stars look surprisingly similar to the CQV light curves
+\citep{2020pase.conf...46M}.  
+Figure~\ref{fig:bstar} shows the phased TESS light curves for
+the two outlying magnetic B-stars,
+with by-eye ``best matching'' CQVs shown for comparison.
+The number of dips per cycle, the shapes of the dips, and the dip
+depths relative to the sinusoidal envelope, all seem to be quite
+similar.
+If this connection is taken seriously, then the implication would be
+that the highly-structured M-dwarf light curves imply multipolar magnetic fields --
+since that is the defining characteristic of these two B-stars,
+relative to other known magnetic B stars like $\sigma$~Ori~E.
 
@@
 	%
-  \item CQVs are quasiperiodic.  The mean periods 
-    remain fixed over the $>$1{,}000-cycle baseline of available
-    observations; but the light curve shapes always evolve (Figure~\ref{fig:evoln}).
+	\item CQVs are quasiperiodic.  The mean periods remain fixed over the
+		$>$1{,}000-cycle baseline of available observations; but the light curve shapes
+		always evolve (Figure~\ref{fig:evoln}).
   %
@@
     scrutiny of these objects in future work.
+  %
+    \item Surprising analogs to the M- and K-dwarf CQVs exist in
+    magnetic B-stars, but only those with multipolar field topologies.
+    This suggests that the CQV dips and warps are strongly sculpted
+    by the stellar magnetic fields, which would also be multipolar.
   %
@@
 In both the gas and dust scenarios, CQVs are preferentially viewed
-edge-on.
-This implies that after correcting for the line-of-sight inclination,
-at least one third of low mass stars
-\citep{2022AJ....163..144G} trap circumstellar
-material in the same way.
-In addition, CQVs should preferentially show edge-on
+edge-on.  This implies that after correcting for the line-of-sight
+inclination, at least one third of low mass stars
+\citep{2022AJ....163..144G} trap circumstellar material in the same
+way.  This suggests that CQVs should preferentially show edge-on
 transiting planets, at larger distances from the star than the
-corotating material.
-Given the interest level inherent to both of these points, important follow-up
-observational work also includes searching for outer transiting
-planets, and measuring equatorial velocities in
-order to test whether the stellar inclination angles are indeed
-preferentially edge-on.
-
-On the theoretical front,
-building a physical understanding what sets the characteristic size
-scale of the clumping material would help clarify the nature of
-the magnetic and plasma environments around these young stars, 
-and would also help build intuition for why the light curves have the
-bizarre shapes that are observed.
-The relevant puzzles in plasma physics and radiative transfer could
-likely be connected to our understanding of the close-in rocky planets
-that are expected to be present around most of these stars.
-The challenges intrinsic to both the observational and theoretical
-work seem worth the effort.
+corotating material.  Given these points, important follow-up
+observations should include searching for outer transiting planets,
+and measuring equatorial velocities in order to test whether the
+stellar inclination angles are indeed preferentially edge-on.
+
+On the theoretical front, building a physical understanding what sets
+the characteristic size scale of the clumping material would help
+clarify the nature of the magnetic and plasma environments around
+these young stars, and would also help build intuition for why the
+light curves have the bizarre shapes that are observed.  The relevant
+puzzles in plasma physics and radiative transfer could likely be
+connected to our understanding of the close-in rocky planets that are
+expected to be present around most of these stars.  The challenges
+intrinsic to both the observational and theoretical work seem worth
+the effort.
 

### 2023-07-25 paper/collect.sh

@@ -19,3 +19,6 @@ cp $resultsdir/phase_timegroups_mosaic/TIC_402980664/TIC_402980664_P18.5611_2min
 
 # fig6
 cp $resultsdir/catalogscatter/catalogscatter_showmaybe.pdf f7.pdf
+
+# fig8
+cp $resultsdir/magnetic_bstar_comparison/magnetic_bstar_comparison_showtitles_both.pdf f8.pdf

### 2023-07-25 complexrotators/plotting.py
plot: update magnetic b-star comparison

@@ -3650,19 +3650,26 @@ def underplot_cqvtargets(ax, get_xval, get_yval):
     return density
 
 
-def plot_hd37776_comparison(outdir, showtitles=1, titlefontsize=3.75,
-                            selfn='hd37776'):
+def plot_magnetic_bstar_comparison(outdir, showtitles=1, titlefontsize=3.75,
+                                   selfn='hd37776'):
 
     # mostmassiveCQV,  HD 37776/landstreet/V901 Ori
     if selfn == 'hd37776':
         ticids = ['405754448', '11400909']
         optionalid = [None, 'HD 37776']
         showsectors = [38, 6]
+        texts = None
     # HD 64740, in VelaOB2
     elif selfn == 'hd64740':
         ticids = ['201789285', '268971806']
         optionalid = [None, 'HD 64740']
         showsectors = [3, 34]
+        texts = None
+    elif selfn == 'both':
+        ticids = ['405754448', '11400909', '201789285', '268971806']
+        optionalid = [None, 'HD 37776', None, 'HD 64740']
+        showsectors = [38, 6, 3, 34]
+        texts = [0.8, 7, 0.1, 7] # masses
     # sigma-ori
     elif selfn == 'sigmaoriE':
         msg = (
@@ -3670,6 +3677,8 @@ def plot_hd37776_comparison(outdir, showtitles=1, titlefontsize=3.75,
             "because i would have labelled sigma Ori E an RS CVn"
         )
         raise NotImplementedError(msg)
+    else:
+        raise NotImplementedError
 
     # prepare to get lc data
     from complexrotators.lcprocessing import (
@@ -3680,7 +3689,10 @@ def plot_hd37776_comparison(outdir, showtitles=1, titlefontsize=3.75,
     # instantiate plot
     #
     set_style("science")
-    fig, axs = plt.subplots(figsize=(2,4), nrows=2)
+    if len(ticids) == 2:
+        fig, axs = plt.subplots(figsize=(2,4), nrows=2)
+    elif len(ticids) == 4:
+        fig, axs = plt.subplots(figsize=(4,1.5), ncols=4)
 
     ix = 0
 
@@ -3724,7 +3736,7 @@ def plot_hd37776_comparison(outdir, showtitles=1, titlefontsize=3.75,
 
         if showtitles:
             if isinstance(opt, str):
[…]

### 2023-07-25 drivers/plot_hd37776_comparison.py

@@ -1,19 +1,0 @@
-import os
-import complexrotators.plotting as rp
-from complexrotators.paths import RESULTSDIR
-
-def main():
-
-    PLOTDIR = os.path.join(RESULTSDIR, 'hd37776_comparison')
-    if not os.path.exists(PLOTDIR):
-        os.mkdir(PLOTDIR)
-
-    rp.plot_hd37776_comparison(PLOTDIR, selfn='hd64740')
-
-    rp.plot_hd37776_comparison(PLOTDIR, selfn='hd37776')
-
-    #NOTE: not implemented, b/c i would have probably autolabelled it an EB
-    #rp.plot_hd37776_comparison(PLOTDIR, selfn='sigmaoriE')
-
-if __name__ == "__main__":
-    main()

### 2023-07-25 drivers/plot_magnetic_bstar_comparison.py

@@ -1,0 +1,20 @@
+import os
+import complexrotators.plotting as rp
+from complexrotators.paths import RESULTSDIR
+
+def main():
+
+    PLOTDIR = os.path.join(RESULTSDIR, 'magnetic_bstar_comparison')
+    if not os.path.exists(PLOTDIR):
+        os.mkdir(PLOTDIR)
+
+    rp.plot_magnetic_bstar_comparison(PLOTDIR, selfn='both')
+
+    rp.plot_magnetic_bstar_comparison(PLOTDIR, selfn='hd64740')
+    rp.plot_magnetic_bstar_comparison(PLOTDIR, selfn='hd37776')
+
+    #NOTE: not implemented, b/c i would have probably autolabelled it an EB
+    #rp.plot_magnetic_bstar_comparison(PLOTDIR, selfn='sigmaoriE')
+
+if __name__ == "__main__":
+    main()

### 2023-07-26 paper/ms.tex
update ms

@@
 
-An interesting point of comparison is the rapidly rotating magnetic
+An instructive point of comparison is the rapidly rotating magnetic
 B-star, $\sigma$~Ori~E, which shows dips that are deeper in the blue
@@
 spectroscopic observations of this star have been understood in terms
-of absorbing circumstellar material, analogous to the geometries we
-are discussing for much cooler M-dwarfs \citep{2005ApJ...630L..81T}.
-This material however is unlikely to be dust, due to the relevant
-sublimation timescales.  The opacity is instead thought to be sourced
-from bound-free absorption from neutral hydrogen
-\citep{2005ApJ...630L..81T}.  Separate and smaller-amplitude emission
-in that system may also come from electrons scattering photospheric
-light toward the observer when the clouds are not in transit
-\citep{2022MNRAS.511.4815B}.
+of a warped torus of circumstellar material, analogous to the
+geometries we are discussing for much cooler M-dwarfs
+\citep{1978ApJ...224L...5L,2005ApJ...630L..81T}.  This material
+however is unlikely to be dust, due to the relevant sublimation
+timescales.  The opacity is instead thought to be sourced from
+bound-free absorption from neutral hydrogen
+\citep{2005ApJ...630L..81T}, although to our best knowledge direct
+evidence for this conclusion has yet to be acquired.  Separate and
+smaller-amplitude emission in $\sigma$~Ori~E may also come from
+electrons scattering photospheric light toward the observer when the
+clouds are not in transit \citep{2022MNRAS.511.4815B}.
 
@@
 
-\subsection{Strengthening the magnetic B-Star connection}
-Previous work by \citet{2017AJ....153..152S} noted an intriguing
+\subsection{Strengthening the magnetic B-star connection}
+
+Previous work by \citet{2017AJ....153..152S} noted the possible
 connection between the CQVs and rapidly rotating magnetic B-stars such
-as $\sigma$~Ori~E, which are known to have circumstellar gas clouds
-trapped in corotation \citep{2005ApJ...630L..81T}.  Spectropolarimetry
-has indicated that, similar to $\sigma$~Ori~E, most magnetic B-stars
-have relatively simple field geometries that are predominantly
-dipolar, though generally not aligned with the stellar spin axis
-\citep{2009ARA&A..47..333D}.  Two exceptions to this rule are HD~37776
-and HD~64740, which are B-stars that were previously known from
-spectropolarimetry in the 2000s-2010s to have more complicated field
-geometries - dominated by high order multipoles
-\citep{2011ApJ...726...24K}.  It turns out, recent TESS light curves
-of these two B-stars look surprisingly similar to the CQV light curves
-\citep{2020pase.conf...46M}.  
-Figure~\ref{fig:bstar} shows the phased TESS light curves for
-the two outlying magnetic B-stars,
-with by-eye ``best matching'' CQVs shown for comparison.
-The number of dips per cycle, the shapes of the dips, and the dip
-depths relative to the sinusoidal envelope, all seem to be quite
-similar.
-If this connection is taken seriously, then the implication would be
-that the highly-structured M-dwarf light curves imply multipolar magnetic fields --
-since that is the defining characteristic of these two B-stars,
-relative to other known magnetic B stars like $\sigma$~Ori~E.
+as $\sigma$~Ori~E, which can have circumstellar gas clouds trapped in
+corotation \citep{2005ApJ...630L..81T}.  The $\sigma$~Ori class is
+distinct from Be-star decretion disks, which do not have any obvious
+connection to the stellar magnetic field \citep{2013A&ARv..21...69R}.
+
+One possible argument against the connection between CQVs and the
+$\sigma$~Ori~E analogs is that the light curve of $\sigma$~Ori~E is
+much simpler than those in Figure~\ref{fig:cqvs}, with only two broad
+local minima, and one ``hump'' \citep{2005ApJ...630L..81T}.  Within
+the model proposed by Townsend et al., this is tied to the star's
+magnetic field, which to first-order is reasonably described as a
+dipole, similar to most other magnetic B-stars
+\citep{2009ARA&A..47..333D}.  This approximation fits the qualitative
+behavior of not only the broadband light curves, but also the
+line-profile variations seen in hydrogen, helium, and carbon
+\citep{2012MNRAS.419..959O}.
+
+Two exceptions to the rule of ``simple field topologies for magnetic
+B-stars'' are HD~37776 and HD~64740, which are B-stars that were
+previously known from spectropolarimetry in the 2000s-2010s to have
+field geometries dominated by high order multipoles
+\citep{2011ApJ...726...24K}.  In a review of the literature, we
+learned that recent TESS light curves of these two B-stars appear
+surprisingly similar to the CQV light curves
+\citep{2020pase.conf...46M}.  Figure~\ref{fig:bstar} shows the phased
+TESS light curves for the two outlying magnetic B-stars, with by-eye
+``best matching'' CQVs shown for comparison.  The number of dips per
+cycle, the shapes of the dips, and the dip depths relative to the
+sinusoidal envelope, all seem to be quite similar.  If this connection
+is taken seriously, the implication would be that the
+highly-structured M-dwarf light curves imply multipolar magnetic
+fields -- since it is the complex fields which are the defining
+characteristic of these two B-stars, relative to other known magnetic
+B stars like $\sigma$~Ori~E.  
+This is consistent with the non-axisymmetric topologies that have been
+reported in a small number of M-dwarfs for which Zeeman Doppler
+Imaging is technically feasible 
+\citep[see the recent review by][]{2021A&ARv..29....1K}.
+
+The physical similarity between the B-stars and the M-dwarfs is
+presumably the existence of a ``centrifugal magnetosphere'': in other
+words, they both satisfy the condition $R_{\rm A} > R_{\rm cr}$, for
+$R_{\rm A}$ the Alfv\'en radius.
+% TODO : qualitiatively explain, and cite Petit+2013
+In the converse case of a ``dynamical'' magnetosphere...
+{\bf todo: summarize Petit2013}
+%FIXME TODO
+%FIXME TODO
+%FIXME TODO
+{\bf
+LGB todo: make the connection to Jupiter-Io magnetosphere, and that
+plasma torus too
+}
 

### 2023-07-26 paper/ms.tex
update ms

@@
 
-\begin{figure*}[!t]
+\begin{figure}[!t]
 	\begin{center}
 		\centering
-		\includegraphics[width=0.9\textwidth]{f8.pdf}
+		%\includegraphics[width=0.9\textwidth]{f8.pdf}
+		\subfloat{
+			\includegraphics[width=0.48\textwidth]{f8a.pdf}
+		}
+
+		\vspace{-0.4cm}
+		\subfloat{
+			\includegraphics[width=0.48\textwidth]{f8b.pdf}
+		}
 		\vspace{-0.1cm}
 		\caption{
-			{\bf The magnetic B-star connection}.
-			HD~37776 (TIC~11400909) and HD~64740 (TIC~268971806) are
-			magnetic B-stars with field geometries dominated by
-			high order multipoles.
+      {\bf The magnetic B-star connection}.  HD~37776 and HD~64740 (right column) are
+      magnetic B-stars with field geometries dominated by high order
+      multipoles.
 			Here, we compare their phased TESS light curves against the
-			``best-matching'' CQV light curves, selected by eye from
+			``best-matching'' CQV light curves (left column), selected by eye from
 			Figure~\ref{fig:cqvs}.
-			Stellar masses approximate to one significant figure are given in the
-			lower right of each panel; the star, TESS sector, and period are also noted.
+      Stellar masses rounded to one significant figure are given
+      in the lower right of each panel; the star, TESS sector, and
+      period are listed in the title.
 		}
@@
 	\end{center}
-\end{figure*}
+\end{figure}
 

### 2023-07-26 paper/collect.sh

@@ -21,4 +21,5 @@ cp $resultsdir/phase_timegroups_mosaic/TIC_402980664/TIC_402980664_P18.5611_2min
 cp $resultsdir/catalogscatter/catalogscatter_showmaybe.pdf f7.pdf
 
 # fig8
-cp $resultsdir/magnetic_bstar_comparison/magnetic_bstar_comparison_showtitles_both.pdf f8.pdf
+cp $resultsdir/magnetic_bstar_comparison/magnetic_bstar_comparison_showtitles_hd37776.pdf f8a.pdf
+cp $resultsdir/magnetic_bstar_comparison/magnetic_bstar_comparison_showtitles_hd64740.pdf f8b.pdf

### 2023-07-26 paper/ms.tex
ms: incorporate LAH suggestions

@@
   discovered in TESS short-cadence data collected between July~2018
-  and Sep~2022.  Our search of \nstarssearched\ K- and M-dwarfs with
+  and Sep~2022.  Our search of \nstarssearched\ K and M dwarfs with
   $T$$<$16 and $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most
@@
   ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc) examples of this
-  class of object known, and probably also the most massive
+  class of object known, as well as the most massive
   ($\approx$0.6-0.8\,$M_\odot$) and oldest ($\approx$200\,Myr).  A few
@@
   recurring ``dip complex'' with a period and total duration that are
-  fixed over more than 1{,}000 cycles, but which in detail exhibits
-  anywhere from four to eight local minima per cycle.  LP 12-502 also
-  displayed distinct superposed periods simultaneously, and showed
-  drastic shape changes shortly after flares.  Broadly speaking, we
-  find that none of the CQVs maintain a fixed light curve shape over
-  timescales of more than a few hundred cycles, and we revisit the
-  arguments for why transient corotating material is the most viable
-  explanation.  In the future, we expect that our sample will
-  facilitate modeling and observational efforts aimed at understanding
-  these objects, and connecting them to the broader contexts of star,
-  disk, and exoplanet evolution.  For instance, if the transiting
-  material is dust, then the rate of dip evolution implies that of
-  order an asteroid belt's worth of mass passes through these
-  structures over their lifetime of $\approx$$10^8$ years.
+  fixed over more than 1{,}000 cycles, but which in detail showed
+  anywhere from four to eight local minima per cycle, and at times
+  displayed distinct superposed periods simultaneously.  Broadly
+  speaking, we find that none of the CQVs maintain a fixed light curve
+  shape over timescales of more than a few hundred cycles, and we
+  revisit the arguments for why transient corotating material is the
+  most viable explanation.  We expect that our sample will facilitate
+  future efforts aimed at connecting these objects to the broader
+  contexts of star, disk, and exoplanet evolution. 
+  %For instance, if the transiting material is dust, then the rate of
+  %dip evolution implies that of order an asteroid belt's worth of mass
+  %passes through these structures over their lifetime of
+  %$\approx$$10^8$ years.
 \end{abstract}
@@
 \citealt{2019A&A...625L..13Z}) and disintegrating rocky bodies around
-both M-dwarfs (e.g. KOI-2700; \citealt{2014ApJ...784...40R}) and white
+both M dwarfs (e.g. KOI-2700; \citealt{2014ApJ...784...40R}) and white
 dwarfs (e.g. WD~1145; \citealt{2015Natur.526..546V}).
@@
 Some CQVs show up to eight local minima (dips) per cycle.  Most are
-pre-main-sequence M-dwarfs without near-infrared excesses, ages of
+pre-main-sequence M dwarfs without near-infrared excesses, ages of
 $\approx$5-150 million years (Myr), and rotation periods of at most
-two days; they are observed to be $\approx$1-3\% of M-dwarfs younger
+two days; they are observed to be $\approx$1-3\% of M dwarfs younger
 than 100 Myr \citep{2016AJ....152..114R,2022AJ....163..144G}.  The
@@
 A few competing explanations for what causes the complex quasiperiodic
-variability are shown in Figure~\ref{fig:f1}.  All young M-dwarfs are
+variability are shown in Figure~\ref{fig:f1}.  All young M dwarfs are
 spotted, which produces flux variations over characteristic timescales
@@
 and hard to characterize.   Discoverability is tied to rarity: CQVs
-comprise $\approx$1\% of the youngest $\approx$1\% of M-dwarfs
+comprise $\approx$1\% of the youngest $\approx$1\% of M dwarfs
 \citep{2018AJ....155..196R}.  Out of the millions of stars monitored
@@
 one-to-one crossmatch using the Gaia source identifiers.  This
-exercise showed that for $T$$<$16 M-dwarfs, the TESS 2-minute data are
+exercise showed that for $T$$<$16 M dwarfs, the TESS 2-minute data are
 roughly 50\% complete at $\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\%
-of the $T$$<$16 M-dwarfs have at least one sector of short-cadence
-data; at $>$100\,pc, $\lesssim$10\% of such M-dwarfs have at least one
+of the $T$$<$16 M dwarfs have at least one sector of short-cadence
+data; at $>$100\,pc, $\lesssim$10\% of such M dwarfs have at least one
 sector of short-cadence data.  Armed with this understanding, we then
@@
 arcseconds, and a geometric distance $d$ defined by inverting the
-parallax and ignoring any zero-point correction.  This selection
-function includes dwarf stars later than spectral types of
-$\approx$K6V \citep{2013ApJS..208....9P} for which TESS can acquire
-1\% relative precision photometry in 1 hour of observation
-\citep{2015JATIS...1a4003R}.  The target sample therefore includes
-\nstarssearched\ M-dwarfs and late-K dwarfs, down to $T$$<$16 and out
+parallax and ignoring any zero-point correction.  The target sample therefore includes
+\nstarssearched\ M dwarfs and late-K dwarfs, down to $T$$<$16 and out
 to $d$$<$150\,pc.
@@
 isochrones \citep[v1.2S][]{2014MNRAS.444.2525C}.  The need for models
-that incorporate some form of correction for young, active M-dwarfs is
+that incorporate some form of correction for young, active M dwarfs is
 well-documented
 \citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2020ApJ...891...29S}.
-Plausible explanations for anomalous M-dwarf colors and sizes relative
+Plausible explanations for anomalous M dwarf colors and sizes relative
 to model predictions include starspot coverage
@@
 Table~\ref{tab:thetable}.
+{\bf lgb todo: real interpolation, rather than nearest neighbor}
 
@@
 we labeled two objects as having ``good'' infrared excesses (both W3
-and W4), and three as ``possible'' infrared excess.
+and W4 at $>$3$\sigma$ above the photospheric prediction), and three
+as ``possible'' infrared excess (only W3 at $>$3$\sigma$).
 
@@
 over two years.
-
-Of these 27 CQVs in Figure~\ref{fig:evoln}, a few show clear signs of the
-CQV phenomenon in one sector, and marginal or non-existent signs in the
-other.  While there is subjectivity in this assessment, to our
+The achievable period precision, $\sigma_P$, can be estimated as
+\begin{equation}
+  \sigma_{P} = \frac { \sigma_{\phi} P } { N_{\rm baseline} },
+  \label{eq:periodprecision}
+\end{equation}
+for $N_{\rm baseline}$ the number of cycles in the observed baseline
+and $\sigma_{\phi}$ the phase precision with which any one feature
+(e.g.~a dip, or the overall shape of the sinusoidal envelope) can be
+tracked.  Assuming $\sigma_\phi$$\approx$$0.02$ and a 20-day
+baseline over a single TESS sector yields $\sigma_{P}$$\approx$$0.25^{+0.38}_{-0.14}$\,minutes for the population shown in
+Figure~\ref{fig:evoln}; propagated forward 1{,}000 cycles
+yields a typical ephemeris uncertainty range of 2-11\,hours.
+Measuring the periods for each sector
+independently, there did not seem to be any significant ($>$3$\sigma$)
+period changes.  This implies an absolute period
+stability of $\lesssim$0.1\% over the two-year baseline.
+
+Of the 27 CQVs in Figure~\ref{fig:evoln}, a few show clear signs of
+the CQV phenomenon in one sector, and marginal or non-existent signs
+in the other.  While there is subjectivity in this assessment, to our
 eyes cases for which at least one sector would be flagged as
@@
 range between the maximum and minimum sector-specific periods was
-measured to be about one minute.  Based on this range, the star's
-period is stable to at least one minute ($\pm$0.017\,hr) over the
-three year baseline.  However, in detail, a period shift of
+measured to be about one minute.   However, in detail, a period shift of
 $\pm$1\,minute would yield major phase drifts over the baseline; that
 time interval corresponds to roughly 1/1000$^{\rm th}$ of a period,
-and we have observed 1500 cycles.  The achievable period precision,
-$\sigma_{\rm P}$, can be estimated as
-\begin{equation}
-  \sigma_{\rm P} = \frac { \sigma_{\phi} P } { N_{\rm baseline} },
-\end{equation}
-for $N_{\rm baseline}$ the number of cycles in the observed baseline
-and $\sigma_{\phi}$ the phase precision with which any one feature
-(e.g.~a dip, or the overall shape of the sinusoidal envelope) can be
-tracked.  Assuming $\sigma_{\phi} \approx 0.01$ yields an expected
-period precision $\sigma_{\rm P} \approx 0.45\,{\rm sec} \approx
-1.2\times 10^{-4}\,{\rm hr}$.  By visually fine-tuning over a grid in
-period, we eventually found $P=18.5611 \pm 0.0001$\,hr, which seems to
-track certain features in the LP 12-502 light curve over its entire
-baseline.
+and we have observed 1500 cycles.  
+%Assuming $\sigma_{\phi} \approx
+%0.01$ and applying Equation~\ref{eq:periodprecision} yields an
+%expected period precision $\sigma_{\rm P} \approx 0.45\,{\rm sec}
+%\approx 1.2\times 10^{-4}\,{\rm hr}$. 
+ By visually fine-tuning over a
+grid in period, we eventually found $P=18.5611 \pm 0.0001$\,hr, which
+seems to track certain features in the LP 12-502 light curve well over
+the entire dataset.
 
@@
 minima.  We dub these dips $\{ 1, 2, 3, 4 \}$ at phases $\{ -0.28,
--0.08, 0, 0.25 \}$, respectively.  Over cycles 0 to 64, the depth of
-dips 1 and 3 remain roughly fixed.  However dip 4 {\it decreases} in
-depth by about 2\%, while dip 2 {\it increases} in depth, by about the
+-0.08, 0, 0.25 \}$, respectively.  Over cycles 0-64, the depth of
+dips 1 and 3 remain roughly fixed.  However dip 4 decreases in
+depth by about 2\%, while dip 2 increases in depth, by about the
 same amount (see Figure~\ref{fig:lp}).  During cycles 48-64, a fifth
@@
       rotation--color distribution of CQVs against the rotation
-      periods of K- and M-dwarfs in the Pleiades from
+      periods of K and M dwarfs in the Pleiades from
       \citet{2016AJ....152..114R}.  The lower-middle panel plots the
@@
 In terms of their rotation, relative to the Pleiades,
-they are among the more rapidly rotating half of M-dwarfs.
+they are among the more rapidly rotating half of M dwarfs.
 The dearth of $T$$>$15.5 CQVs in our sample, despite our search extending
@@
 regime.  To date, the only stars reported to show the CQV phenomenon
-are M-dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
+are M dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
 \citep{2022AJ....163..144G}.  TIC~405754448 and TIC~405910546 however
@@
 in sum, both of these objects seem to suggest that the CQV phenomenon
-extends up in mass to pre-main-sequence K-dwarfs.
+extends up in mass to pre-main-sequence K dwarfs.
 
@@
 An instructive point of comparison is the rapidly rotating magnetic
-B-star, $\sigma$~Ori~E, which shows dips that are deeper in the blue
+B star, $\sigma$~Ori~E, which shows dips that are deeper in the blue
 than in the red \citep{1977ApJ...216L..31H}.  Photometric and
@@
 of a warped torus of circumstellar material, analogous to the
-geometries we are discussing for much cooler M-dwarfs
+geometries we are discussing for much cooler M dwarfs
 \citep{1978ApJ...224L...5L,2005ApJ...630L..81T}.  This material
@@
 This is odd in the context of the prominence scenario, because
-pre-main-sequence M-dwarfs spin up over the first $\approx$$10^8$\,yr;
+pre-main-sequence M dwarfs spin up over the first $\approx$$10^8$\,yr;
 prominences might even be expected to be {\it more} common at the age
@@
 a condition on the star's mass, rotation period, and magnetic field
-strength.  Based on the degree to which M-dwarfs remain rapid rotators
+strength.  Based on the degree to which M dwarfs remain rapid rotators
 over the first 700\,Myr \citep[e.g. Figure~13
@@
 %This is not a particularly drastic size change.
-%Similarly, at 700\,Myr many M-dwarfs have comparably rapid rotation periods 
+%Similarly, at 700\,Myr many M dwarfs have comparably rapid rotation periods 
 %to those at 100\,Myr \citep[e.g. Figure~13 of][]{2022AJ....164...80R};
@@
 %PMS contraction finishes, but there are still a large number of 
-%700\,Myr M-dwarfs with $P_{\rm rot}\lesssim$2\,days, beyond
+%700\,Myr M dwarfs with $P_{\rm rot}\lesssim$2\,days, beyond
 %which the CQV phenomenon becomes less common.
@@
 Planet occurrence rate studies from Kepler have shown that high-mass
-M- dwarfs have $\approx$0.1 planets per star with sizes between
+M  dwarfs have $\approx$0.1 planets per star with sizes between
 1-4\,$R_\oplus$ and orbital periods within 3 days
@@
 0.1-4\,$R_\oplus$ and within 10 days, it is reasonable to expect on
-average one planet per M-dwarf.  TRAPPIST-1b ($P$=1.5\,days) is an
+average one planet per M dwarf.  TRAPPIST-1b ($P$=1.5\,days) is an
 example of this type of planet, in orbit around a 0.08\,$M_\odot$ star
@@
 %around 5-10 days for FGK stars, and perhaps even closer-in for
-%M-dwarfs (CITE Petigura2022, and CITE for M-dwarfs).
+%M dwarfs (CITE Petigura2022, and CITE for M dwarfs).
 %
@@
 		\caption{
-      {\bf The magnetic B-star connection}.  HD~37776 and HD~64740 (right column) are
-      magnetic B-stars with field geometries dominated by high order
+      {\bf The magnetic B star connection}.  HD~37776 and HD~64740 (right column) are
+      magnetic B stars with field geometries dominated by high order
       multipoles.
@@
 
-\subsection{Strengthening the magnetic B-star connection}
+\subsection{Strengthening the magnetic B star connection}
 
 Previous work by \citet{2017AJ....153..152S} noted the possible
-connection between the CQVs and rapidly rotating magnetic B-stars such
+connection between the CQVs and rapidly rotating magnetic B stars such
 as $\sigma$~Ori~E, which can have circumstellar gas clouds trapped in
@@
 magnetic field, which to first-order is reasonably described as a
-dipole, similar to most other magnetic B-stars
+dipole, similar to most other magnetic B stars
 \citep{2009ARA&A..47..333D}.  This approximation fits the qualitative
@@
 Two exceptions to the rule of ``simple field topologies for magnetic
-B-stars'' are HD~37776 and HD~64740, which are B-stars that were
+B stars'' are HD~37776 and HD~64740, which are B stars that were
 previously known from spectropolarimetry in the 2000s-2010s to have
@@
 \citep{2011ApJ...726...24K}.  In a review of the literature, we
-learned that recent TESS light curves of these two B-stars appear
+learned that recent TESS light curves of these two B stars appear
 surprisingly similar to the CQV light curves
 \citep{2020pase.conf...46M}.  Figure~\ref{fig:bstar} shows the phased
-TESS light curves for the two outlying magnetic B-stars, with by-eye
+TESS light curves for the two outlying magnetic B stars, with by-eye
 ``best matching'' CQVs shown for comparison.  The number of dips per
@@
 is taken seriously, the implication would be that the
-highly-structured M-dwarf light curves imply multipolar magnetic
+highly-structured M dwarf light curves imply multipolar magnetic
 fields -- since it is the complex fields which are the defining
-characteristic of these two B-stars, relative to other known magnetic
+characteristic of these two B stars, relative to other known magnetic
 B stars like $\sigma$~Ori~E.  
 This is consistent with the non-axisymmetric topologies that have been
-reported in a small number of M-dwarfs for which Zeeman Doppler
+reported in a small number of M dwarfs for which Zeeman Doppler
 Imaging is technically feasible 
@@
 
-The physical similarity between the B-stars and the M-dwarfs is
+The physical similarity between the B stars and the M dwarfs is
 presumably the existence of a ``centrifugal magnetosphere'': in other
@@
 between July~2018 and Sep~2022 for complex quasiperiodic variables
-(CQVs).  Our search sample included \nstarssearched\ K- and M-dwarfs
+(CQVs).  Our search sample included \nstarssearched\ K and M dwarfs
 within 150\,pc, and was $\gtrsim 80\%$ complete within 30\,pc, and
@@
     0.1-0.5\,$M_\odot$, the upper mass limit for the CQV phenomenon
-    might extend into the K-dwarf regime ($<$$0.8$\,$M_\odot$).
+    might extend into the K dwarf regime ($<$$0.8$\,$M_\odot$).
     TIC~405754448 and TIC~405910546, with masses of $\approx$0.8 and
@@
   %
-    \item Surprising analogs to the M- and K-dwarf CQVs exist in
-    magnetic B-stars, but only those with multipolar field topologies.
+    \item Surprising analogs to the M  and K dwarf CQVs exist in
+    magnetic B stars, but only those with multipolar field topologies.
     This suggests that the CQV dips and warps are strongly sculpted

### 2023-07-27 paper/ms.tex
update ms

@@
 \newcommand{\esa}{European Space Agency (ESA), European Space Research and Technology Centre (ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, Netherlands}
+\newcommand{\howard}{Department of Physics and Astronomy, Howard University, Washington DC, 20059}
+\newcommand{\goddard}{Center for Research and Exploration in Space Science and Technology, and X-ray Astrophysics Laboratory, NASA/GSFC, Greenbelt, MD 20771, USA}
 
@@
 
+\author{Saul~Rappaport}
+\affiliation{\mitkavli}
+
 \author{Lynne~A.~Hillenbrand}
@@
 
+\author[0000-0003-4062-0776]{Alexandre David-Uraz}
+\affiliation{\howard}
+\affiliation{\goddard}
+
 \author[0000-0001-7204-6727]{G\'asp\'ar \'A. Bakos}
@@
 %
-\author{Saul~Rappaport}
-\affiliation{\mitkavli}
-
 \author[0000-0001-6381-515X]{Luisa M. Rebull}
@@
   class of object known, as well as the most massive
-  ($\approx$0.6-0.8\,$M_\odot$) and oldest ($\approx$200\,Myr).  A few
+  ($\approx$0.6-0.8\,$M_\odot$) and the oldest ($\approx$200\,Myr).  A few
   objects are outliers among outliers; LP 12-502 for instance shows a
   recurring ``dip complex'' with a period and total duration that are
-  fixed over more than 1{,}000 cycles, but which in detail showed
+  fixed over more than 1{,}000 cycles, but which in detail contains
   anywhere from four to eight local minima per cycle, and at times
-  displayed distinct superposed periods simultaneously.  Broadly
+  displays distinct superposed periods simultaneously.  Broadly
   speaking, we find that none of the CQVs maintain a fixed light curve
@@
   future efforts aimed at connecting these objects to the broader
-  contexts of star, disk, and exoplanet evolution. 
+  contexts of star, disk, and perhaps even exoplanet evolution. 
   %For instance, if the transiting material is dust, then the rate of
@@
 silicate 10\,$\mu$m dust absorption during a dip, or perhaps detection
-of transient Balmer-line absorption as a function of cycle phase,
-similar to observations made in systems such as AB~Dor \citep[see the
-review by][]{1999ASPC..158..146C}.
+of transient Balmer-line excesses as a function of cycle phase,
+similar to observations made in systems such as AB~Dor
+\citep[see][]{1999ASPC..158..146C} or PTFO 8-8695 \citep{2016ApJ...830...15J}.
 
@@
 baseline is described in Section~\ref{sec:evoln}, including a
-deep-dive into LP 12-502.  We describe a few implications in
+deep-dive into LP 12-502.  We discuss a few implications in
 Section~\ref{sec:discussion}, and conclude in
@@
 
-Planet occurrence rate studies from Kepler have shown that high-mass
+Close-in planets are common around M-dwarfs;
+studies from Kepler have shown that high-mass
 M  dwarfs have $\approx$0.1 planets per star with sizes between
@@
 \citep{2015ApJ...807...45D}.  The number increases to $\approx$0.7
-planets per star for planets with 1-4\,$R_\oplus$ and $P$$<$10\,days.
-Extrapolating to all small close-in planets, with say
+planets per star considering planets out to $P$$<$10\,days.
+Extrapolating to all small close-in planets with say
 0.1-4\,$R_\oplus$ and within 10 days, it is reasonable to expect on
-average one planet per M dwarf.  TRAPPIST-1b ($P$=1.5\,days) is an
-example of this type of planet, in orbit around a 0.08\,$M_\odot$ star
-\citep{2017Natur.542..456G}.
+average one close-in planet per M dwarf.  
+%TRAPPIST-1b ($P$=1.5\,days) is an
+%example of this type of planet, orbiting around a 0.08\,$M_\odot$ star
+%\citep{2017Natur.542..456G}.
 
@@
 radius \citep{2016ARA&A..54..135H}.  Within models that have compact
-multiplanet resonant chains migrate inward due to gas drag, the
-inner-most planets arrive within $\approx$5-10 stellar radii before
+multiplanet resonant chains migrating inward due to gas drag, the
+inner-most planets therefore arrive at $\approx$5-10 stellar radii before
 the disk becomes depleted.
 
-In this context, it is tempting to try to interpret features of the
+Given this context, it is tempting to try to interpret features of the
 CQV light curves in terms of the possible presence of close-in
-exoplanets, or even planetesimals, that are expected to exist in
-abundance around these stars.  Rocky planets this young could have
+exoplanets, or even planetesimals.  Rocky planets this young could have
 molten global magma oceans analogous to those that existed on the
 Earth and Moon \citep[see][]{2022arXiv220310023L}, and thus might be
-undergoing significant outgassing and atmospheric escape.  However,
-although it is {\it a priori} plausible that close-in rocky planets or
-planetesimals could serve as a possible source of material for the
-clouds, any evidence in support of such a picture currently seems
+undergoing significant outgassing and atmospheric escape.  The system
+would then be analogous to the Jupiter-Io plasma torus \citep[e.g.][]{1980JGR....85.1171N}, with a similar rotation
+period for the primary and orbital period for the secondary,
+but magnetic fields stronger by a factor of $\approx$1{,}000.
+While this type of configuration is {\it a priori} plausible,
+any evidence in support of such a picture currently seems
 ambiguous at best.
@@
 planetesimal swarm, rather than just a single planetesimal.  
-While the number of free parameters in this type of model is somewhat
-dizzying, we have no right to believe that nature need be simple.
+%While the number of free parameters in this type of model is somewhat
+%dizzying, we have no right to believe that nature need be simple.
 The need for a swarm rather than just one launching body would
@@
 
-The planetesimal swarm model would predict that certain orbital phases
+There are at least three problems with the idea of a disintegrating
+planetesimal swarm.
+First, this model would predict that certain orbital phases
 would produce recurrent dips if observed over sufficiently long
-timescales, since the launching planetesimal would be massive enough
-to remain in orbit, and similar to say K2-22 would stochastically
-eject material.  While the regularity of the dip phases of LP~12-502
-over the existing baseline (Figure~\ref{fig:lp2}) might agree with
-this prediction, for most other CQVs (Figure~\ref{fig:evoln}) the data
+baselines, because the launching planetesimal would be massive enough
+to remain in orbit, while stochastically
+ejecting material.  An analogous system might be K2-22.
+For most CQVs (Figure~\ref{fig:evoln}), the data
 seem to be in tension with this expectation.
-
-There are a few additional problems for the idea of a disintegrating
-planetesimal swarm.  First, many of the dips show asymmetries in the
+A second issue is that many of the dips show asymmetries in the
 wrong direction relative to the naive expectation of a trailing comet
@@
 function of azimuth might be one way out of this, but such an idea
-would need stronger theoretical footing.  Dynamical stability would be
-a separate concern: in a model in which any new dip is ``explained''
+lacks firm theoretical footing.  Finally, dynamical stability is a concern:
+in a model in which any new dip is ``explained''
 by invoking a new planetesimal, one might eventually pack the
@@
 up being connected to the CQV phenomenon, for instance as a possible
-source of dust through collisions at greater separations from the
-star.  However for the time being, none of the CQVs that we have
-studied in this work seem to show clear evidence for this type of
+sources for the occulting dust or gas.
+However for the time being, none of the CQVs that we have
+studied in this work show clear evidence for this type of
 origin scenario.
@@
 		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f8a.pdf}
+			\includegraphics[width=0.49\textwidth]{f8a.pdf}
 		}
@@
 		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f8b.pdf}
+			\includegraphics[width=0.49\textwidth]{f8b.pdf}
 		}
@@
 		\caption{
-      {\bf The magnetic B star connection}.  HD~37776 and HD~64740 (right column) are
+      {\bf The magnetic B star connection.}  HD~37776 and HD~64740 (left column) are
       magnetic B stars with field geometries dominated by high order
@@
 			Here, we compare their phased TESS light curves against the
-			``best-matching'' CQV light curves (left column), selected by eye from
+			``best-matching'' CQV light curves (right column), selected by eye from
 			Figure~\ref{fig:cqvs}.
@@
 
-One possible argument against the connection between CQVs and the
+An argument against the connection between CQVs and the
 $\sigma$~Ori~E analogs is that the light curve of $\sigma$~Ori~E is
@@
 local minima, and one ``hump'' \citep{2005ApJ...630L..81T}.  Within
-the model proposed by Townsend et al., this is tied to the star's
-magnetic field, which to first-order is reasonably described as a
+the model proposed by Townsend et al., this is explained by the simplicity of the star's
+magnetic field, which to first-order is a
 dipole, similar to most other magnetic B stars
-\citep{2009ARA&A..47..333D}.  This approximation fits the qualitative
-behavior of not only the broadband light curves, but also the
+\citep{2009ARA&A..47..333D}.  This approximation matches the qualitative
+behavior of both the broadband light curves, and the
 line-profile variations seen in hydrogen, helium, and carbon
@@
 Imaging is technically feasible 
-\citep[see the recent review by][]{2021A&ARv..29....1K}.
-
-The physical similarity between the B stars and the M dwarfs is
-presumably the existence of a ``centrifugal magnetosphere'': in other
-words, they both satisfy the condition $R_{\rm A} > R_{\rm cr}$, for
+\citep[see the review by][]{2021A&ARv..29....1K}.
+
+The physical similarity between the B stars and the M dwarfs 
+presumably has its origin in the existence of a ``centrifugal magnetosphere'' \citep[see][]{2013MNRAS.429..398P}.
+In other
+words, both classes of objects probably satisfy the condition $R_{\rm A} > R_{\rm cr}$, for
 $R_{\rm A}$ the Alfv\'en radius.
-% TODO : qualitiatively explain, and cite Petit+2013
-In the converse case of a ``dynamical'' magnetosphere...
-{\bf todo: summarize Petit2013}
-%FIXME TODO
-%FIXME TODO
-%FIXME TODO
-{\bf
-LGB todo: make the connection to Jupiter-Io magnetosphere, and that
-plasma torus too
-}
+When this condition holds, stable points exist wherever the outward
+centrifugal force is balanced by magnetic tension of closed field loops.
+In the converse ``dynamical'' case, when  $R_{\rm A} < R_{\rm cr}$, any
+material launched by the star returns to its surface over the free-fall timescale.
+% While there are some qualitative connections to Jupiter-Io, it's not perfect.
+% In that system, R_A>R_cr...
+% But the plasma torus exists near Io's 42 hour orbit
+% ...and is nonetheless STILL FORCED into corotation at a 10hr period (presumably by Jupiter's B-field).
+% This type of structure is very different, because here we actually see the plasma at corotation!
 
@@
     This suggests that the CQV dips and warps are strongly sculpted
-    by the stellar magnetic fields, which would also be multipolar.
+    by the stellar magnetic fields, which are probably also multipolar.
   %
@@
 LAH advised on project scope and experiment design.
+AD identified the magnetic B star connection.
 G\'AB acquired and maintained the servers used to run the dip-finding

### 2023-07-27 complexrotators/plotting.py
plotting: update b-star comp

@@ -2500,7 +2500,7 @@ def plot_full_lcmosaic(outdir, showtitles=1, titlefontsize=3.5,
 
     for ticid, sector, ax in zip(df.ticid, df.showsector, axs):
 
-        lcdir = '/Users/luke/.lightkurve-cache/mastDownload/TESS'
+        lcdir = '/Users/luke/.lightkurve/cache/mastDownload/TESS'
         lcpaths = glob(join(
             lcdir, f"tess*s{str(sector).zfill(4)}*{ticid}*",
             f"*{ticid}*_lc.fits")
@@ -2721,7 +2721,7 @@ def plot_beforeafter_mosaic(outdir, showtitles=1, titlefontsize=3.75,
     beforesectorfound, aftersectorfound = [], []
     for sectorcol in ['beforesector','aftersector']:
         for ticid, sector in zip(df['ticid'], df[sectorcol]):
-            lcdir = '/Users/luke/.lightkurve-cache/mastDownload/TESS'
+            lcdir = '/Users/luke/.lightkurve/cache/mastDownload/TESS'
             lcpaths = glob(join(
                 lcdir, f"tess*s{str(sector).zfill(4)}*{ticid}*",
                 f"*{ticid}*_lc.fits")
@@ -2834,9 +2834,10 @@ def plot_beforeafter_mosaic(outdir, showtitles=1, titlefontsize=3.75,
 
     ix = 0
 
+    _periods = []
     for ticid, sector, ax in zip(ticids, sectors, axs):
 
-        lcdir = '/Users/luke/.lightkurve-cache/mastDownload/TESS'
+        lcdir = '/Users/luke/.lightkurve/cache/mastDownload/TESS'
         lcpaths = glob(join(
             lcdir, f"tess*s{str(sector).zfill(4)}*{ticid}*",
             f"*{ticid}*_lc.fits")
@@ -2871,6 +2872,8 @@ def plot_beforeafter_mosaic(outdir, showtitles=1, titlefontsize=3.75,
             d['period'] = 0.3708350878122453
         if str(ticid) == '289840926':
             d['period'] = 0.1999953362691368 # lol what
+
+        _periods.append(d['period'])
 
         bd = time_bin_magseries(d['times'], d['fluxs'], binsize=1200, minbinelems=1)
 
@@ -3078,6 +3081,14 @@ def plot_beforeafter_mosaic(outdir, showtitles=1, titlefontsize=3.75,
                        pad=1.5)
 
         ix += 1
+
+    outdf = pd.DataFrame({
[…]

### 2023-08-03 paper/ms.tex
update ms

@@
   anywhere from four to eight local minima per cycle, and at times
-  displays distinct superposed periods simultaneously.  Broadly
+  displays multiple periods simultaneously.  Broadly
   speaking, we find that none of the CQVs maintain a fixed light curve
@@
 root cause is only beginning to become clear: complex quasiperiodic
-variables (CQVs).  These objects are identified phenomenologically
-using their optical light curves, which show nearly periodic troughs
+variables (CQVs).  These objects are identified 
+from their optical light curves, which show nearly periodic troughs
 that can be either sharp or broad, often superposed on smooth
@@
 $\approx$5-150 million years (Myr), and rotation periods of at most
-two days; they are observed to be $\approx$1-3\% of M dwarfs younger
+two days; they are observed to comprise $\approx$1-3\% of M dwarfs younger
 than 100 Myr \citep{2016AJ....152..114R,2022AJ....163..144G}.  The
@@
 CQV light curves in terms of the possible presence of close-in
-exoplanets, or even planetesimals.  Rocky planets this young could have
-molten global magma oceans analogous to those that existed on the
+exoplanets, or even planetesimals.  Rocky planets this young could
+have molten global magma oceans analogous to those that existed on the
 Earth and Moon \citep[see][]{2022arXiv220310023L}, and thus might be
 undergoing significant outgassing and atmospheric escape.  The system
-would then be analogous to the Jupiter-Io plasma torus \citep[e.g.][]{1980JGR....85.1171N}, with a similar rotation
-period for the primary and orbital period for the secondary,
-but magnetic fields stronger by a factor of $\approx$1{,}000.
-While this type of configuration is {\it a priori} plausible,
-any evidence in support of such a picture currently seems
-ambiguous at best.
+would then be analogous to the Jupiter-Io plasma torus
+\citep[e.g.][]{1980JGR....85.1171N}, with a similar rotation period
+for the primary and orbital period for the secondary, but magnetic
+fields stronger by a factor of $\approx$1{,}000.  While this type of
+configuration is {\it a priori} plausible, no direct evidence in
+support of such a picture currently exists.
 

### 2023-08-06 paper/ms.tex
incorporate Luisa Rebull's suggestions

@@
 %
+% * Verify "32" in Figure 4 does not change with number of stars in
+%   subsample changing
 %
@@
 sources of optical variability include inhomogeneities on stellar
-surfaces such as starspots and faculae \citep{2021isma.book.....B},
+surfaces such as starspots and faculae \citep[e.g.][]{2021isma.book.....B},
 occultations by gas-rich circumstellar disks
-\citep{2017MNRAS.470..202B}, and, in geometrically favorable
+\citep[e.g.][]{2017MNRAS.470..202B}, and, in geometrically favorable
 circumstances, eclipses by stars and planets
-\citep{2010exop.book...55W}.  More exotic forms of optical variability
+\citep[e.g.][]{2010exop.book...55W}.  More exotic forms of optical variability
 relevant to this work include transiting exocomets (e.g.~$\beta$~Pic;
@@
 curve to 100 points per cycle.  To separate ``sharp'' local minima
-from smooth spot-induced variability, we then iteratively fit
+from smooth spot-induced variability, we then iteratively fit robust
 penalized splines to the wrapped phase-folded light curve, excluding
@@
 meaning of ``sharp'' --- we allowed at most 10 such knots per cycle,
-though for most stars fewer knots were preferred based on an
-$\ell^2$-norm penalty.
+though for most stars fewer knots were preferred based on
+cross-validation using an $\ell^2$-norm penalty.  An example fit is
+shown in panel {\it (e)} of Figure~\ref{fig:vetting}.
 
@@
 DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
-WISE 1-2 passbands.  We specifically omitted UV flux measurements to
-avoid biasing our fit with any possible chromospheric UV excess.
+WISE 1-2 passbands.  We specifically omitted UV flux measurements from
+our SED fit to avoid any possible bias induced by chromospheric UV
+excess; we similarly omitted WISE 3-4, but due to reliability
+concerns.
 \texttt{astroARIADNE} compares the measured broadband flux
@@
       Phased TESS light curves over one month are shown for \ngoods\
-      CQVs.  Gray are raw 2-minute data; black bins to 300 points per
-      cycle.  Each panel is labeled by the TIC identifier, the TESS
-      sector number, and the period in hours.  Objects are ordered
-      such that sources with the most TESS data available are on top
-      (see Section~\ref{sec:catalog}).
+      CQVs in the high quality sample.  Gray are raw 2-minute data;
+      black bins to 300 points per cycle.  Each panel is labeled by
+      the TIC identifier, the TESS sector number, and the period in
+      hours.  Objects are ordered such that sources with the most TESS
+      data available are on top (see Section~\ref{sec:catalog}).
 		}
@@
 Table~\ref{tab:thetable} lists the \ncpvsfound\ objects identified by
-our search.  \ngoods\ objects demonstrated what we viewed as
+our search.  The ``high-quality sample'' includes \ngoods\ of these
+objects, which demonstrated what we viewed as
 unambiguous characteristics of the CQV phenomenon in at least one TESS
-sector; we refer to these as the ``high-quality sample''.  The
+sector.  The
 classification of the remaining \nmaybes\ CQV candidates was
@@
 periods were also relatively long.  After labeling them, inspection
-of further sectors clarified that both sources are dippers (see plots
+of further sectors clarified that both sources are dippers (see online plots
 in Figure~\ref{fig:vet}).  Independently, TIC 193136669 has a cold
@@
 source shows a superposed 8.39\,hr sinusoidal signal, probably from an
-unresolved neighboring star.
+unresolved neighboring star or binary companion.
 
@@
 		\caption{
+      %TODO : 
 		{\bf CQVs keep their periods but change their shapes.}
-      32 of our \ngoods\ CQVs from Figure~\ref{fig:cqvs} had
+      Out of the \ngoods\ CQVs in Figure~\ref{fig:cqvs}, 32 had
       120-second cadence TESS data available for a baseline of at
-      least two years; the 27 brightest are shown here.  Each panel
-      shows one sector of TESS data, and is phased to its deepest
-      minimum in flux.  Each panel's title shows the TIC identifier
-      and approximate period in hours.  Text insets show the TESS
-      sector numbers, which generally span two years, or at least
-      1{,}000 cycles.  The vertical scale is fixed across sectors to
-      clarify shape changes.
-      Gray circles are raw 2-minute data; colored circles bin to 300
-      points per cycle. 
+      least two years; the 27 brightest are shown here due to space
+      constraints.  Each panel shows one sector of TESS data, and is
+      phased to its deepest minimum in flux.  Each panel's title shows
+      the TIC identifier and approximate period in hours.  Text insets
+      show the TESS sector numbers, which generally span two years, or
+      at least 1{,}000 cycles.  The vertical scale is fixed across
+      sectors to clarify shape changes.  Gray circles are raw 2-minute
+      data; colored circles bin to 300 points per cycle. 
 		}
@@
       binned black points per cycle.  The TESS pointing law dictates
-      time gaps; larger gaps tend to yield larger shape changes.  The
+      the large time gaps between Cycles 64-248, 315-1233, and
+      1264-1410; larger gaps tend to yield larger shape changes.  The
       dips usually evolve over tens to hundreds of cycles.  However
@@
 
+Out of the \ngoods\ CQVs, a small fraction were in regions of sky with
+many sectors of adjacent TESS data.  Out of these objects, LP 12-502
+(TIC 402980664; $d$=21\,pc, $J$=9.4, $T$=11.1) stood out due to the
+quality and content of its data.  We describe another interesting
+source, TIC~300651846, in Appendix~\ref{app:tic3006}.  For this
+section, we first present the LP 12-502 observations
+(Section~\ref{subsec:lpobservations}), and then highlight their
+interpretation (Section~\ref{subsec:lplessons}).
+
 \subsubsection{LP 12-502 observations}
-While many CQVs had multiple sectors of adjacent or nearly-adjacent
-data, LP 12-502 (TIC 402980664; $d$=21\,pc, $J$=9.4, $T$=11.1) stood
-out due to the quality and content of its data.  Figure~\ref{fig:lplc}
-shows all available data from Sectors 18, 19, 25, 26, 53, 58, and 59,
-split into successive orbits; the star was observed at 120-second
-cadence whenever it was observable by TESS.  We binned the light curve
-to 15-minute intervals for visual clarity, and required at least one
-(120-second cadence) flux measurement per bin.  Points more than
-2.5$\sigma$ above the median are drawn in gray, also for visual
-clarity.  Missing data are not drawn.  Figure~\ref{fig:lp} then shows
-the same data, but stacked into successive TESS orbits spanning half a
-lunar month each.
+\label{subsec:lpobservations}
+
+Figure~\ref{fig:lplc} shows all available data for LP 12-502 from TESS
+Sectors 18, 19, 25, 26, 53, 58, and 59, split into successive orbits.
+The star was observed at 120-second cadence whenever it was observable
+by TESS.  We binned the light curve to 15-minute intervals for visual
+clarity, and required at least one (120-second cadence) flux
+measurement per bin.  Points more than 2.5$\sigma$ above the median
+are drawn in gray, also for visual clarity.  Missing data are not
+drawn.  Figure~\ref{fig:lp} then shows the same data, but stacked into
+successive TESS orbits spanning half a lunar month each.
 
@@
 of 3.5\% over about 22 minutes (0.02\,$P$), which is the steepest
-slope exhibited anywhere in the LP~12-502 remarkable dataset.  After
+slope exhibited anywhere in the LP~12-502 dataset.  After
 the sharp dip, there is a roughly exponential fall-off spanning about
@@
 \subsubsection{Lessons from LP 12-502}
+\label{subsec:lplessons}
 
@@
       {\bf Properties of CQVs identified by our search}.
+      CQVs are pre-main-sequence K and M dwarfs, younger than
+      $\approx$200 Myr, with rotation periods faster than around half
+      of Pleiades-age M dwarfs.
       The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are the
@@
       units of stellar radii against the measured CQV periods, in
-      units of hours.
+      units of hours.  Ages in the final panel are known from cluster
+      membership.
 		}
@@
 are M dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
-\citep{2022AJ....163..144G}.  TIC~405754448 and TIC~405910546 however
+\citep{2017AJ....153..152S,2022AJ....163..144G}.  TIC~405754448 and TIC~405910546 however
 appear to have masses of $\approx$0.82 and $\approx$0.60\,$M_\odot$
 respectively.  The next-highest masses are $\approx$0.40\,$M_\odot$.
-The masses for the former two objects are consistent with their CAMD
-locations, and their membership in LCC.  Based on its light curve
-morphology, TIC~405910546 should be studied in greater depth, to
-confirm it is not an eclipsing binary.  TIC~405754448 similarly shows
-distinct morphology from many of the CQVs in Figure~\ref{fig:cqvs}, in
-that it has some of the lowest amplitude dips.  While TIC~405754448
-might be an unresolved binary (RUWE$_{\rm DR3}$=4.7),  the depth of
-the coherent dips present in the Sector~11 light curve imply that the
-CQV signal is indeed from the apparent primary of the system.  Taken
-in sum, both of these objects seem to suggest that the CQV phenomenon
-extends up in mass to pre-main-sequence K dwarfs.
+The masses for the former two objects are consistent with their
+locations in the color--absolute magnitude diagram, and with their
+membership in LCC.  Based on its light curve morphology, TIC~405910546
+should be studied in greater depth, to confirm it is not an eclipsing
+binary.  TIC~405754448 similarly shows distinct morphology from many
+of the CQVs in Figure~\ref{fig:cqvs}, in that it has some of the
+lowest amplitude dips.  While TIC~405754448 might be an unresolved
+binary (RUWE$_{\rm DR3}$=4.7),  the depth of the coherent dips present
+in the Sector~11 light curve imply that the CQV signal is indeed from
+the apparent primary of the system.  Taken in sum, both of these
+objects seem to suggest that the CQV phenomenon extends up in mass to
+pre-main-sequence K dwarfs.
 
@@
 dimension to discern between the gas {\it vs.} dust clump scenarios.
-Based on the available statistics from the studies by L.~Rebull and
-J.~Stauffer, it seems plausible that CQV occurrence decreases in time,
-bottoming to zero well before the $\approx$700\,Myr age of Praesepe.
-This is odd in the context of the prominence scenario, because
+Based on the available statistics from e.g.
+\citet{2022AJ....164...80R} and references therein, it seems plausible
+that CQV occurrence decreases in time, bottoming to zero well before
+the $\approx$700\,Myr age of Praesepe.  This is odd in the context of
+the prominence scenario, because
 pre-main-sequence M dwarfs spin up over the first $\approx$$10^8$\,yr;
@@
 of the Pleiades than for younger stars.  This broadly assumes that any
-star that can support prominences will, which translates in detail to
-a condition on the star's mass, rotation period, and magnetic field
-strength.  Based on the degree to which M dwarfs remain rapid rotators
-over the first 700\,Myr \citep[e.g. Figure~13
-of][]{2022AJ....164...80R}, it seems surprising in the gas clump
-(prominence) scenario that very few stars older than 150\,Myr have
-been seen to exhibit the phenomenon.  In the dust clump scenario this
-is not a problem, because if the dust were externally sourced, it
-would be expected to have a finite supply.
+star that can support prominences will, and that the magnetic topology
+of rapidly rotating M dwarfs at 100\,Myr is similar to that of 
+rapidly rotating M dwarfs at say, 10\,Myr.  Based on the degree to
+which M dwarfs remain rapid rotators over the first 700\,Myr
+\citep[e.g. Figure~13 of][]{2022AJ....164...80R}, it seems surprising
+in the gas clump (prominence) scenario that very few stars older than
+150\,Myr have been seen to exhibit the phenomenon.  In the dust clump
+scenario this is not a problem, because if the dust were externally
+sourced, it would be expected to have a finite supply.
 
@@
 context of CQVs for two reasons.  The first is that for material on a
-circular orbit viewed edge-on, it corresponds to the interval between
-transit and secondary eclipse.  The second is that it also corresponds
+circular orbit viewed edge-on, a half-cycle corresponds to the interval between
+transit and secondary eclipse.  The second is that the half-cycle also corresponds
 to the interval over which half of the star's surface is visible.  Of
-the CQVs in Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, a number that
+the CQVs in Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, a fraction that
 seems greater than random might exhibit a preference for showing dips
@@
 (CQVs).  Our search sample included \nstarssearched\ K and M dwarfs
-within 150\,pc, and was $\gtrsim 80\%$ complete within 30\,pc, and
-$\lesssim 10\%$ complete at distances exceeding 100\,pc.
+within 150\,pc, yielding a selection function with $\gtrsim 80\%$ completeness within 30\,pc,
+and $\lesssim 10\%$ completeness at distances exceeding 100\,pc.
 
@@
 turn propagate to our understanding of whether observing the
-phenomenon is primarily teaching us about e.g.~dust production and
+phenomenon is primarily teaching us about dust production and
 processing in circumstellar disks, or whether it is teaching us about
@@
   %\texttt{astropy} \citep{astropy_2018},
-  %\texttt{astroquery} \citep{astroquery_2018},
+ % \texttt{astroquery} \citep{astroquery_2018},
   %\texttt{BATMAN} \citep{kreidberg_batman_2015},
@@
   %\texttt{pandas} \citep{mckinney-proc-scipy-2010},
-  %\texttt{pyGAM} \citep{serven_pygam_2018_1476122},
+  \texttt{pyGAM} \citep{daniel_serven_2018_1208723},
   %\texttt{PyMC3} \citep{salvatier_2016_PyMC3},
@@
   %\texttt{webplotdigitzer} \citep{rohatgi_2019},
-  %\texttt{wotan} \citep{hippke_wotan_2019}.
+  \texttt{wotan} \citep{hippke_wotan_2019}.
 }
@@
 	      (Figure~\ref{fig:lp}), arranged to emphasize changes in transit
-	      times.  There are 200 binned black points per cycle; a two-harmonic
-	      sinusoid has been subtracted over specific chunks in time ({\bf see text}).
+	      times.  There are 200 binned black points per $P$=18.5611\,hr cycle; a two-harmonic
+	      sinusoid has been subtracted from the PDC\_SAP light curve.
 	      Vertical gray lines are underplotted to help guide the eye to instances
@@
 	      The orange and green lines guide the eye to where dips
-	      appear to change the positions of their local minima.
+	      change the positions of their local minima; orange
+        lines have periods slightly less than $P$, the green line has
+        a period greater than $P$.
 		}
@@
 
-\section{More river plots}
+\section{TIC~300651846}
+\label{app:tic3006}
 

### 2023-08-06 complexrotators/plotting.py
minor plot fixes

@@ -3267,7 +3267,7 @@ def plot_beforeafter_mosaic(outdir, showtitles=1, titlefontsize=3.75,
             ax.set_xticklabels(['-0.5','0','0.5'], fontsize='small')
     else:
         for ix in [16,17, 34,35, 52,53]:
-            axs[ix].set_xticklabels(['-0.5','0','0.5'], fontsize='small')
+            axs[ix].set_xticklabels(['-0.5','0','0.5'], fontsize=labelsize)
 
     fs = 'medium'
     if SIMPLEGRID:
@@ -3486,7 +3486,7 @@ def plot_tic4029_segments(outdir):
         # between time gaps.
         _, _groups = find_lc_timegroups(x, mingap=0.5/24)
         for _g in _groups:
-            ax.plot(x[_g], y[_g], c='k', zorder=1, lw=0.2, alpha=0.15)
+            ax.plot(x[_g], y[_g], c='k', zorder=1, lw=0.2, alpha=0.25)
 
         _, _groups = find_lc_timegroups(sx, mingap=0.5/24)
         for _g in _groups:

### 2023-08-08 paper/ms.tex
update validation plot annotations
first draft of Fourier text, tightened up a bit of language, and added some citations

--- 2023-07-27 paper/ms.tex
@@
 \usepackage{enumitem}
+
+\newcommand{\red}{\color{red}}
 
@@
 %\title{Complex Quasiperiodic Variables From Four Years of TESS}
-\title{Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS}
+\title{Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS}
 
@@
 
-\shortauthors{Bouma, Jayararaman, et al.}
+\shortauthors{Bouma, Jayaraman, et al.}
 
@@
 
-\author[0000-0002-7778-3117]{Rahul~Jayararaman}
+\author[0000-0002-7778-3117]{Rahul~Jayaraman}
 \affiliation{\mitkavli}
@@
 
-Data from K2 and TESS have yielded a new class of variable star whose
-root cause is only beginning to become clear: complex quasiperiodic
-variables (CQVs).  These objects are identified phenomenologically
+Data from K2 and TESS have yielded a new class of variable star---
+complex quasiperiodic variables---for which the underlying cause of
+variability has only begun to be explored recently. These objects are 
+identified phenomenologically
 using their optical light curves, which show nearly periodic troughs
-that can be either sharp or broad, often superposed on smooth
-spot-like modulation
+that are either sharp or broad; these are often superposed on smooth
+spot-like modulations
 \citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z}.
-Some CQVs show up to eight local minima (dips) per cycle.  Most are
+Some CQVs show up to eight local minima (``dips'') per cycle.  Most are
 pre-main-sequence M dwarfs without near-infrared excesses, ages of
@@
 at high resolution out of reach for current facilities, despite its
-potential utility in ruling between the models.
+potential utility in ruling out some of these models.
 
@@
 
-A point on nomenclature.  CQVs have been called ``transient flux
+We note that the ``proper'' nomenclature for these stars in the literature
+has generally been unclear. CQVs have been called ``transient flux
 dips'', ``persistent flux dips'', ``scallop shells'', ``batwings'',
@@
 Science Processing and Operations Center at NASA Ames
-\citep{2016SPIE.9913E..3EJ}.  While the TESS data products also
-include full frame images with cadences of 200, 600, and 1800 seconds,
-we limited our scope in this work for the sake of simplicity in data
+\citep{2016SPIE.9913E..3EJ}.  While the TESS data products from these 
+sectors also include full frame images with cadences of 600 and 1800 seconds,
+we limited our scope to 120-s cadence in this work for the sake of simplicity in data
 handling.  In exchange, we lose in both completeness and homogeneity
@@
 \label{subsec:fourier}
-For the Fourier analysis, we followed \citet{2019ApJ...876..127Z}.
-
-{\bf TODO for Rahul or Saul: explain the approach, in a few
-	paragraphs.  Was the SAP\_FLUX or PDCSAP used? etc. }
+For the Fourier analysis, we followed the techniques presented in 
+\citet{2019ApJ...876..127Z} and Section 1.3 of \citet{2023MNRAS.524.4220P}.
+All 120-s targets were searched for strongly periodic phenomena using our
+Fourier pipeline. We used the {\tt PDCSAP\_FLUX} column from the data  
+and normalized and  re-binned the light curve into equal width bins, due to the
+uneven spacing in the TESS data, as well as the data gap in the middle of
+each sector due to the lack of data collection during downlink. Data was
+padded to ensure that the light curve had a length that was a power of 2, 
+as described in \citeauthor{2019ApJ...876..127Z}. We
+then took the Fourier transform of the corrected, padded light curve using 
+{\tt numpy.fft.fft} and searched for peaks with a significance of over 
+12-$\sigma$ within each set of 500 bins.
+
+If a peak of such significance was found, we generated a ``summary sheet'' 
+with information about the target, its full and folded light curves, Fourier 
+transform, potential contaminating stars, and information about these
+ contaminating stars. Throughout the 35 sectors for which we performed
+ this analysis, we found that ``summary'' sheets were generated for 
+ approximately 10\% of the 20\,000
+120-s targets in a given sector. Each summary sheet was manually reviewed.
+During this manual review, each light curve was sorted into a category based on its
+morphology (e.g., eclipsing binary, CQV, or cataclysmic variable). For
+the CQVs, a further cut was made based on the target's temperature---any
+stars exhibiting phenomena that looked similar to CQVs, but had a $T_{\rm eff}$ 
+over 4\,000\,K were discarded from the target list (e.g., RS CVn stars). 
+{\red (RJ: can we add an example of these sheets to this paper? i know it's not 
+the ``main'' vetting, though, so happy to not do this as well)}.
+
+CQVs that were observed in multiple sectors had their light curves
+stitched together and analyzed for a more accurate period determination.
 
@@
 pipeline were 5:1, with \nuniqdipflagged\ unique stars flagged, and
-about 20\% being labeled either ``good'' or ``possible'' CQVs; for
-the Fourier pipeline, {\bf the rate was X:Y, with ZZZZ unique stars
-flagged, and NN\% being labeled ``good'' or ``possible'' CQVs}.
+about 20\% being labeled either ``good'' or ``possible'' CQVs.
+
+The Fourier pipeline, on the other hand, was less CQV-focused than
+the dip-counting technique, as its results were used for other sorts of
+analyses; as a result, we cannot calculate a similar ``false-positive''
+probability. Between the targets identified as CQVs by both pipelines,
+
+ {\red
+
+\begin{itemize}
+\item XX targets were found to overlap
+\item YY targets were found via Fourier but not via dip counting
+\end{itemize}
+
+}
+The difference in discovery rate between these techniques can be attributed to
+low-amplitude peaks in the periodogram that were missed, some of which likely
+arose from fainter CQVs.
 
@@
 much simpler than those in Figure~\ref{fig:cqvs}, with only two broad
-local minima, and one ``hump'' \citep{2005ApJ...630L..81T}.  Within
-the model proposed by Townsend et al., this is explained by the simplicity of the star's
-magnetic field, which to first-order is a
+local minima, and one ``hump'' \citep{2005ApJ...630L..81T, 2022ApJ...924L..10J}.  
+Within the model proposed by Townsend et al., this is explained by the simplicity of 
+the star's magnetic field, which to first-order is a
 dipole, similar to most other magnetic B stars
@@
 cycle, the shapes of the dips, and the dip depths relative to the
-sinusoidal envelope, all seem to be quite similar.  If this connection
-is taken seriously, the implication would be that the
+sinusoidal envelope, all seem to be quite similar.  The
+implication of such a surprising connection would be that the
 highly-structured M dwarf light curves imply multipolar magnetic
@@
 	%\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
-  %\texttt{astropy} \citep{astropy_2018},
+  \texttt{astropy} \citep{astropy_2013,astropy_2018,astropy_2022},
   %\texttt{astroquery} \citep{astroquery_2018},
@@
   %\texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
-  %\texttt{numpy} \citep{walt_numpy_2011}, 
+  \texttt{numpy} \citep{2020Natur.585..357H}, 
   %\texttt{pandas} \citep{mckinney-proc-scipy-2010},

### 2023-08-11 paper/ms.tex
update ms

--- 2023-08-06 paper/ms.tex
@@
 
-\author{Lynne~A.~Hillenbrand}
+\author[0000-0001-6381-515X]{Luisa M. Rebull}
 \affiliation{\caltech}
@@
 
+\author{Lynne~A.~Hillenbrand}
+\affiliation{\caltech}
+
 \author[0000-0001-7204-6727]{G\'asp\'ar \'A. Bakos}
@@
 %
-\author[0000-0001-6381-515X]{Luisa M. Rebull}
-\affiliation{\caltech}
 
@@
 \begin{abstract}
-  Complex quasiperiodic variables (CQVs) are low-mass
-  pre-main-sequence stars with nearly periodic optical modulation.
-  The modulation is likely induced by dust or gas clumps in orbit at
-  the Keplerian corotation radius.  Here, we report new CQVs
-  discovered in TESS short-cadence data collected between July~2018
-  and Sep~2022.  Our search of \nstarssearched\ K and M dwarfs with
-  $T$$<$16 and $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most
-  of these discoveries are new, and they include the brightest
-  ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc) examples of this
-  class of object known, as well as the most massive
-  ($\approx$0.6-0.8\,$M_\odot$) and the oldest ($\approx$200\,Myr).  A few
-  objects are outliers among outliers; LP 12-502 for instance shows a
-  recurring ``dip complex'' with a period and total duration that are
-  fixed over more than 1{,}000 cycles, but which in detail contains
-  anywhere from four to eight local minima per cycle, and at times
-  displays multiple periods simultaneously.  Broadly
-  speaking, we find that none of the CQVs maintain a fixed light curve
-  shape over timescales of more than a few hundred cycles, and we
-  revisit the arguments for why transient corotating material is the
-  most viable explanation.  We expect that our sample will facilitate
-  future efforts aimed at connecting these objects to the broader
-  contexts of star, disk, and perhaps even exoplanet evolution. 
-  %For instance, if the transiting material is dust, then the rate of
-  %dip evolution implies that of order an asteroid belt's worth of mass
-  %passes through these structures over their lifetime of
-  %$\approx$$10^8$ years.
+Complex quasiperiodic variables (CQVs) are low-mass pre-main-sequence
+stars with nearly periodic optical modulation.  The modulation is
+likely induced by dust or gas clumps in orbit at the Keplerian
+corotation radius.  Here, we report new CQVs discovered in TESS
+short-cadence data collected between July~2018 and Sep~2022.  Our
+search of \nstarssearched\ K and M dwarfs with $T$$<$16 and
+$d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most of these
+discoveries are new, and they include the brightest
+($T$$\approx$9.5), closest ($d$$\approx$20\,pc), most massive
+($\approx$0.6-0.8\,$M_\odot$), and the oldest ($\approx$200\,Myr)
+examples of this class of object currently known.  A few objects are
+outliers: LP 12-502 for instance showed a ``dip complex'' with a
+period and duration that were fixed over 1,500 cycles, but in
+detail, this system exhibited between four and eight local minima
+per cycle, and at times also displayed multiple periods
+simultaneously.  We demonstrate that transient corotating material
+is the most viable explanation for this class of object, and present
+evidence supporting the hypothesis that this material is sculpted by
+stellar magnetic fields dominated by high order multipoles.  We
+expect that our sample will facilitate future efforts aimed at
+connecting CQVs to the broader contexts of star, disk, and perhaps
+even exoplanet evolution. 	
 \end{abstract}
@@
 cross-validation using an $\ell^2$-norm penalty.  An example fit is
-shown in panel {\it (e)} of Figure~\ref{fig:vetting}.
+shown in panel {\it (e)} of Figure~\ref{fig:vet}.
 
@@
 between July~2018 and Sep~2022 for complex quasiperiodic variables
-(CQVs).  Our search sample included \nstarssearched\ K and M dwarfs
-within 150\,pc, yielding a selection function with $\gtrsim 80\%$ completeness within 30\,pc,
-and $\lesssim 10\%$ completeness at distances exceeding 100\,pc.
+(CQVs).  The target stars were \nstarssearched\ K and M dwarfs
+within 150\,pc.  The selection function was $\gtrsim 80\%$ complete within 30\,pc,
+and $\lesssim 10\%$ complete at distances exceeding 100\,pc.
 
@@
   %
-  \item The same CQV can show dips with similar but clearly
-    distinct periods.  LP 12-502, for instance, showed dips with four
+  \item The same CQV can show multiple periods simultaneously.
+     LP 12-502, for instance, showed dips with four
     distinct periods within $\pm 0.3\%$ of its fundamental period,
@@
     \item The rate of dip evolution can be used to place a model-dependent
-    constraint on amount of material that is either being accreted or ejected
+    constraint on how much material is either being accreted or ejected
     during the state changes (Section~\ref{subsec:massflux}).
@@
     \item The duty cycle for CQVs seems to be $\approx$$75$\%, based on
-    the fraction of bonafide CQVs that turned on or turned off during
-    TESS re-observations, two years after their initial observation.
+    the fraction of bonafide CQVs that either turned on or turned off during
+    TESS re-observations, two years after the initial observation.
   %
@@
     TIC~405754448 and TIC~405910546, with masses of $\approx$0.8 and
-    $\approx$0.6 solar masses, are the two massive outliers
+    $\approx$0.6\,$M_\odot$, are the two massive outliers
     (Section~\ref{subsec:extreme}), and we encourage additional
@@
     magnetic B stars, but only those with multipolar field topologies.
-    This suggests that the CQV dips and warps are strongly sculpted
-    by the stellar magnetic fields, which are probably also multipolar.
+    Since most magnetic B stars have dipolar magnetic fields,
+    this suggests that the CQV dips and warps are similarly being sculpted
+    by the stellar magnetic fields, and that the magnetic
+    fields themselves are probably also multipolar.
   %
     \item The closest CQVs to the Sun are at distances of 15-20\,pc, and
-    the brightest CQVs have $V$$\approx$12 ($J$$\approx$7.5).  This
+    the brightest have $V$$\approx$12 ($J$$\approx$7.5).  This
     conclusion is an extrapolation from the CQV sample derived in this work
-    being $\gtrsim$80\% complete within 20\,pc.  Expanding our analysis of
+    being $\gtrsim$80\% complete within 30\,pc.  Expanding our analysis of
     the TESS data to the full frame images would yield a truly
@@
 The distinction between gas or dust is important because it will
-clarify whether the CQV phenomenon is intrinsic, so that the material
+clarify whether the CQV phenomenon is intrinsic, so that material
 comes from the star, or extrinsic, so that it is sourced through some
-generic evolutionary phase of circumstellar disks.  This knowledge would in
-turn propagate to our understanding of whether observing the
+generic evolutionary phase of circumstellar disks.
+This knowledge would in
+turn propagate to our understanding of whether the
 phenomenon is primarily teaching us about dust production and
@@
 Observationally, acquisition of medium- or high-resolution time-series
-spectroscopy holds the best chance at resolving the gas vs.~dust
+spectra holds the best chance at resolving the gas vs.~dust
 question.  Given the observed evolutionary timescales, such data
@@
 
+%TODO: nix this paragraph?  This edge on hypothesis only holds
+%TODO if the magnetic field is aligned with the stellar spin axis.
+{\bf todo: nix paragraph? technically this only works if B is aligned
+with stellar spin axis... which would be aligned w planetary system}
 In both the gas and dust scenarios, CQVs are preferentially viewed

### 2023-08-11 paper/ms.tex

@@
 from their optical light curves, which show nearly periodic troughs
-that can be either sharp or broad, often superposed on smooth
-spot-like modulation
+that are either sharp or broad; these troughs are often superposed on
+smooth spot-like modulation
 \citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z}.
-Some CQVs show up to eight local minima (dips) per cycle.  Most are
+Some CQVs show up to eight local minima (``dips'') per cycle.  Most are
 pre-main-sequence M dwarfs without near-infrared excesses, ages of
@@
 
-A point on nomenclature.  CQVs have been called ``transient flux
+A point on nomenclature. 
+CQVs have been called ``transient flux
 dips'', ``persistent flux dips'', ``scallop shells'', ``batwings'',
@@
 between July~2018 and Sep~2022 (Sectors 1-55).  Specifically, we used
-the 120-second cadence light curve products produced by the 
-Science Processing and Operations Center at NASA Ames
-\citep{2016SPIE.9913E..3EJ}.  While the TESS data products also
-include full frame images with cadences of 200, 600, and 1800 seconds,
-we limited our scope in this work for the sake of simplicity in data
-handling.  In exchange, we lose in both completeness and homogeneity
-of the selection function.  While TESS cumulatively observed
-$\approx$90\% of the sky for at least one lunar month between
-July~2018 and Sep~2022, the 120-second cadence data were acquired for
-only a pre-selected set of stars over Sectors 1-26, and then a
-guest-investigator driven set of stars over Sectors 27-55
-\citep{2021PASP..133i5002F}.
+the 120-second cadence light curves produced by the Science
+Processing and Operations Center at NASA Ames
+\citep{2016SPIE.9913E..3EJ}.  While the TESS data products from these
+sectors also included full frame images with cadences of 600 and 1800
+seconds, we limited our scope in this study for the sake of simplicity
+in data handling.  In exchange, we sacrificed both completeness and
+homogeneity of the selection function.  While TESS cumulatively
+observed $\approx$90\% of the sky for at least one lunar month between
+July~2018 and Sep~2022, the 120-second cadence data were collected for
+only a subset of observable stars during this time due to telemetric
+constraints
+\citep[see][]{2021PASP..133i5002F}.
 
@@
 \label{subsec:fourier}
-For the Fourier analysis, we followed \citet{2019ApJ...876..127Z}.
-
-{\bf TODO for Rahul or Saul: explain the approach, in a few
-	paragraphs.  Was the SAP\_FLUX or PDCSAP used? etc. }
+
+We performed an independent search for strongly periodic phenomena
+using our Fourier pipeline, following \citet{2019ApJ...876..127Z} and
+\citet[][their Section~1.3]{2023MNRAS.524.4220P}.
+Starting with the PDC\_SAP light curves, we normalized each light
+curve, and then re-binned it into equal width bins {\bf LB: how long?} to
+account for the uneven spacing in the TESS data, as well as the data
+gap during each sector caused by satellite downlink.  We then padded
+the data to ensure that the light curve had a length that was a power
+of two, as described by \citeauthor{2019ApJ...876..127Z}.  We
+then took the Fourier transform of the corrected, padded light curve using 
+{\tt numpy.fft.fft} and searched for peaks with a significance of over 
+12-$\sigma$ within each set of 500 bins.
+
+If a peak of such significance was found, we generated a ``summary
+sheet'' with information about the star, its full and folded light
+curves, Fourier transform, potential contaminating stars, and
+information about these contaminating stars.  
+In the sectors for which
+we performed this analysis, we found that ``summary'' sheets were
+generated for approximately 10\% of the 20\,000 120-second targets in
+a given sector.  
+We then manually reviewed each summary sheet, and
+visually labelled each star based on its morphology (including e.g.,
+eclipsing binary, CQV, RS CVn, or cataclysmic variable).  CQVs that
+were observed in multiple sectors had their light curves stitched
+together and analyzed for a more accurate period determination.
 
@@
 pipeline were 5:1, with \nuniqdipflagged\ unique stars flagged, and
-about 20\% being labeled either ``good'' or ``possible'' CQVs; for
-the Fourier pipeline, {\bf the rate was X:Y, with ZZZZ unique stars
-flagged, and NN\% being labeled ``good'' or ``possible'' CQVs}.
+about 20\% being labeled either ``good'' or ``possible'' CQVs.
+The Fourier analysis was not amenable to calculating a similar
+false-positive probability, because it was implemented as a general
+variability search; its results are also being used for other types of
+variability analyses beyond CQVs.
+
+%TODO: include?
+%Between the targets identified as CQVs by both pipelines,
+% {\red 
+%\begin{itemize}
+%\item XX targets were found to overlap
+%\item YY targets were found via Fourier but not via dip counting
+%\end{itemize}
+%}
+%The difference in discovery rate between these techniques can be attributed to
+%low-amplitude peaks in the periodogram that were missed, some of which likely
+%arose from fainter CQVs.
 
@@
  % \texttt{astroquery} \citep{astroquery_2018},
+  \texttt{astropy} \citep{astropy_2013,astropy_2018,astropy_2022},
+  %\texttt{astroquery} \citep{astroquery_2018},
   %\texttt{BATMAN} \citep{kreidberg_batman_2015},

### 2023-08-11 paper/ms.tex
update ms

@@
 distribution with mean $\mu$, standard deviation $\sigma$, and lower
-and upper bounds $a$ and $b$.  Using \texttt{Dynesty}
-\citep{2020MNRAS.493.3132S}, we statically sampled the posterior
-probability assuming the default Gaussian likelihood, and set a
-stopping threshold of ${\rm d}\log \mathcal{Z} < 0.01$, where
-$\mathcal{Z}$ denotes the evidence.
+and upper bounds $a$ and $b$.  We validated our chosen upper bound on
+$A_{\rm V}$ using a 2MASS color-color diagram.  Finally, using
+\texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we statically sampled
+the posterior probability assuming the default Gaussian likelihood,
+and set a stopping threshold of ${\rm d}\log \mathcal{Z} < 0.01$,
+where $\mathcal{Z}$ denotes the evidence.
 

### 2023-08-11 paper/ms.tex
ms: improve magnetic B star connection

@@
 
-\begin{figure}[!t]
+\begin{figure}[!th]
 	\begin{center}
 		\centering
-		%\includegraphics[width=0.9\textwidth]{f8.pdf}
 		\subfloat{
-			\includegraphics[width=0.49\textwidth]{f8a.pdf}
+			\includegraphics[width=0.48\textwidth]{f8a.pdf}
 		}
@@
 		\subfloat{
-			\includegraphics[width=0.49\textwidth]{f8b.pdf}
-		}
+			\includegraphics[width=0.48\textwidth]{f8b.pdf}
+		}
+
+		\vspace{-0.4cm}
+		\subfloat{
+			\includegraphics[width=0.48\textwidth]{f8c.pdf}
+		}
+
 		\vspace{-0.1cm}
 		\caption{
-      {\bf The magnetic B star connection.}  HD~37776 and HD~64740 (left column) are
-      magnetic B stars with field geometries dominated by high order
-      multipoles.
-			Here, we compare their phased TESS light curves against the
-			``best-matching'' CQV light curves (right column), selected by eye from
-			Figure~\ref{fig:cqvs}.
-      Stellar masses rounded to one significant figure are given
-      in the lower right of each panel; the star, TESS sector, and
-      period are listed in the title.
+      {\bf The magnetic B star connection.}
+      $\sigma$~Ori~E and HD~345439 (top row) are magnetic B stars with
+      predominantly dipolar magnetic fields known to host
+      circumstellar plasma tori.  HD~37776 and HD~64740 (middle row)
+      are analogous magnetic B stars with field toplogies dominated
+      by high order multipoles.  The bottom row compares the latter
+      systems against the ``best-matching'' CQV light curves, selected
+      by eye from Figure~\ref{fig:cqvs}.  CQVs have light curves that are
+      visually similar to the topologically complex magnetic B stars.
+      Stellar masses rounded to one significant figure are given in
+      the lower right of each panel; the star, TESS sector, and period
+      are listed in each subtitle.
 		}
@@
 
-An argument against the connection between CQVs and the
-$\sigma$~Ori~E analogs is that the light curve of $\sigma$~Ori~E is
-much simpler than those in Figure~\ref{fig:cqvs}, with only two broad
-local minima, and one ``hump'' \citep{2005ApJ...630L..81T, 2022ApJ...924L..10J}.  
-Within the model proposed by Townsend et al., this is explained by the simplicity of 
-the star's magnetic field, which to first-order is a
+An argument against the connection between CQVs and the $\sigma$~Ori~E
+analogs is that the light curve of $\sigma$~Ori~E is much simpler than
+those in Figure~\ref{fig:cqvs}, with only two broad local minima, and
+one ``hump'' \citep{2005ApJ...630L..81T, 2022ApJ...924L..10J}.  Within
+the model proposed by Townsend et al., this is explained by the
+simplicity of the star's magnetic field, which to first-order is a
 dipole, similar to most other magnetic B stars
-\citep{2009ARA&A..47..333D}.  This approximation matches the qualitative
-behavior of both the broadband light curves, and the
-line-profile variations seen in hydrogen, helium, and carbon
+\citep{2007A&A...475.1053A,2009ARA&A..47..333D}.  This approximation
+matches the qualitative behavior of both the broadband light curves,
+and the line-profile variations seen in hydrogen, helium, and carbon
 \citep{2012MNRAS.419..959O}.
@@
 B stars'' are HD~37776 and HD~64740, which are B stars that were
-previously known from spectropolarimetry in the 2000s-2010s to have
+previously known from spectropolarimetry to have
 field geometries dominated by high order multipoles
-\citep{2011ApJ...726...24K}.  In a review of the literature, we
+\citep{2011ApJ...726...24K}.  Reviewing the literature, we
 learned that recent TESS light curves of these two B stars appear
 surprisingly similar to the CQV light curves
-\citep{2020pase.conf...46M}.  Figure~\ref{fig:bstar} shows the phased
-TESS light curves for the two outlying magnetic B stars, with by-eye
-``best matching'' CQVs shown for comparison.  The number of dips per
-cycle, the shapes of the dips, and the dip depths relative to the
-sinusoidal envelope, all seem to be quite similar.  The
-implication of such a surprising connection would be that the
-highly-structured M dwarf light curves imply multipolar magnetic
+\citep{2020pase.conf...46M}.  The middle row of Figure~\ref{fig:bstar}
+shows the phased TESS light curves for these two outlying magnetic B
+stars, with by-eye ``best matching'' CQVs shown for comparison.  The
+number of dips per cycle, the shapes of the dips, and the dip depths
+relative to the sinusoidal envelope, all seem to be quite similar.
+The implication of this surprising connection is that the
+highly-structured M dwarf light curves may imply multipolar magnetic
 fields -- since it is the complex fields which are the defining
 characteristic of these two B stars, relative to other known magnetic
-B stars like $\sigma$~Ori~E.  
-This is consistent with the non-axisymmetric topologies that have been
-reported in a small number of M dwarfs for which Zeeman Doppler
-Imaging is technically feasible 
+B stars like $\sigma$~Ori~E.  This is consistent with the
+non-axisymmetric topologies that have been reported in a small number
+of M dwarfs for which Zeeman Doppler Imaging is technically feasible
 \citep[see the review by][]{2021A&ARv..29....1K}.
@@
 The physical similarity between the B stars and the M dwarfs
-presumably has its origin in the existence of a ``centrifugal magnetosphere'' \citep[see][]{2013MNRAS.429..398P}.
-In other
-words, both classes of objects probably satisfy the condition $R_{\rm A} > R_{\rm cr}$, for
-$R_{\rm A}$ the Alfv\'en radius.
-When this condition holds, stable points exist wherever the outward
-centrifugal force is balanced by magnetic tension of closed field loops.
-In the converse ``dynamical'' case, when  $R_{\rm A} < R_{\rm cr}$, any
-material launched by the star returns to its surface over the free-fall timescale.
-% While there are some qualitative connections to Jupiter-Io, it's not perfect.
-% In that system, R_A>R_cr...
-% But the plasma torus exists near Io's 42 hour orbit
-% ...and is nonetheless STILL FORCED into corotation at a 10hr period (presumably by Jupiter's B-field).
-% This type of structure is very different, because here we actually see the plasma at corotation!
+presumably has its origin in the existence of a ``centrifugal
+magnetosphere'' \citep[see][]{2013MNRAS.429..398P}.  In other words,
+both classes of objects probably satisfy the condition $R_{\rm A} >
+R_{\rm cr}$, for $R_{\rm A}$ the Alfv\'en radius.  When this condition
+holds, stable points exist wherever the outward centrifugal force is
+balanced by magnetic tension of closed field loops.  In the converse
+``dynamical'' case, when  $R_{\rm A} < R_{\rm cr}$, any material
+launched by the star returns to its surface over the free-fall
+timescale.
+
+% While there are some qualitative connections to Jupiter-Io, it's not
+% perfect.  In that system, R_A>R_cr...  But the plasma torus exists
+% near Io's 42 hour orbit ...and is nonetheless STILL FORCED into
+% corotation at a 10hr period (presumably by Jupiter's B-field).  This
+% type of structure is very different, because here we actually see
+% the plasma at corotation!
 
@@
 (CQVs).  The target stars were \nstarssearched\ K and M dwarfs
-within 150\,pc.  The selection function was $\gtrsim 80\%$ complete within 30\,pc,
-and $\lesssim 10\%$ complete at distances exceeding 100\,pc.
-
-In this sample of stars, we found \ngoods\ objects that showed complex
-quasiperiodic behavior over at least one TESS sector.  Because the
-TESS 120-second stellar sample was rooted in a heterogeneous selection
-function that may have been biased in favor of young stars over field
-stars, we caution against interpreting our detection fraction in
-terms of broader population statistics.  The \ngoods\ bonafide
+within 150\,pc.  The selection function was $>$$80\%$ complete within 30\,pc,
+and $<$$10\%$ complete at distances exceeding 100\,pc.
+
+In our target sample, we found \ngoods\ objects that showed complex
+quasiperiodic behavior over at least one TESS sector.  
+These \ngoods\ bonafide
 CQVs are listed in Table~\ref{tab:thetable}.  This table also includes
@@
 certain.
-
-Analyzing the TESS light curves and stellar properties of these
-objects, we draw the following conclusions.
+We inferred ages for all but two of the \ncpvsfound\ objects based on association
+memberships; we also derived temperatures and radii using SED fitting,
+and then inferred stellar masses by
+interpolating against stellar evolutionary models.
+We caution that our selection function was not volume-limited:
+the
+TESS 120-second stellar sample had a heterogeneous selection
+function which may have been biased in favor of young stars over field
+stars.
+Previous work however has shown that $\approx$1-3\% of M dwarfs
+younger than $\approx$100\,Myr show the CQV phenomenon
+\citep{2016AJ....152..114R,2022AJ....163..144G}.
+
+Analyzing the TESS light curves and stellar properties of our
+CQVs, we draw the following conclusions.
 
@@
     \item CQVs evolve over timescales that are both secular
-    ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
-    can cause dips to collapse instantaneously, and are often but not
-    exclusively linked with observed optical flares.  Dip growth
-    however seems to happen over durations of at least ten cycles, and
-    slow dip decay can also occur.
+    ($>$100\,cycles) and impulsive ($<$1 cycle).  
+    Dip growth seems to happen over durations of at least ten cycles, and slow dip decay can also occur.
+    ``State-switches''
+    correspond to dips to collapsing instantaneously, and are almost always
+    linked with observed optical flares.
+    This suggests that the occulting material is responding to sudden changes
+    in the magnetic field.
   %
@@
 
-%TODO: nix this paragraph?  This edge on hypothesis only holds
-%TODO if the magnetic field is aligned with the stellar spin axis.
-{\bf todo: nix paragraph? technically this only works if B is aligned
-with stellar spin axis... which would be aligned w planetary system}
 In both the gas and dust scenarios, CQVs are preferentially viewed
 edge-on.  This implies that after correcting for the line-of-sight
-inclination, at least one third of low mass stars
-\citep{2022AJ....163..144G} trap circumstellar material in the same
-way.  This suggests that CQVs should preferentially show edge-on
-transiting planets, at larger distances from the star than the
-corotating material.  Given these points, important follow-up
-observations should include searching for outer transiting planets,
+inclination, roughly one third of low mass stars
+\citep{2022AJ....163..144G} could trap circumstellar material in the same
+way.  It also suggests that CQVs may preferentially show
+transiting planets at larger distances than the corotating material, though
+this may be dependent on whether the magnetic and stellar
+spin axes tend to be aligned.  Given these points, observational follow-up
+work should include searching for outer transiting planets,
 and measuring equatorial velocities in order to test whether the

### 2023-08-11 complexrotators/plotting.py

@@ -3852,6 +3852,76 @@ def plot_magnetic_bstar_comparison(outdir, showtitles=1, titlefontsize=3.75,
         optionalid = [None, 'HD 37776', None, 'HD 64740']
         showsectors = [38, 6, 3, 34]
         texts = [0.8, 7, 0.1, 7] # masses
+    elif selfn == 'all':
+        ticids = [
+            '11286209', '424048289', # simple B star field topplogies
+            '11400909', '268971806', # complex B star field topologies
+            '405754448', '201789285', # M dwarf matches
+        ]
+        optionalid = [
+            'σ Ori E', 'HD 345439',
+            #None, 'HD 37776',
+            #None, 'HD 64740'
+            'HD 37776', 'HD 64740',
+            None, None
+        ]
+        showsectors = [
+            32, 41,
+            #38, 6,
+            #3, 34
+            6, 34,
+            38, 3
+        ]
+        # sigmaOriE from Townsend2013
+        texts = [
+            8, 7,
+			7, 7,
+            0.8, 0.1
+        ] # masses
+    elif selfn == 'simpleB':
+        ticids = [
+            '11286209', '424048289' # simple B star field topplogies
+        ]
+        optionalid = [
+            'σ Ori E', 'HD 345439',
+        ]
+        showsectors = [
+            32, 41,
+        ]
+        # sigmaOriE from Townsend2013
+        texts = [
+            8, 7,
+        ] # masses
+    elif selfn == 'complexB':
+        ticids = [
+            '11400909', '268971806', # complex B star field topologies
+        ]
+        optionalid = [
+            'HD 37776', 'HD 64740',
+        ]
+        showsectors = [
+            6, 34,
+        ]
+        # sigmaOriE from Townsend2013
+        texts = [
+			7, 7,
+        ] # masses
+    elif selfn == 'complexM':
+        ticids = [
+            '405754448', '201789285', # M dwarf matches
+        ]
+        optionalid = [
+            None, None
+        ]
+        showsectors = [
+            38, 3
+        ]
+        # sigmaOriE from Townsend2013
+        texts = [
+            0.8, 0.1
+        ] # masses
+
+
     # sigma-ori
     elif selfn == 'sigmaoriE':
         msg = (
[…]

### 2023-08-11 drivers/plot_magnetic_bstar_comparison.py

@@ -8,10 +8,16 @@ def main():
     if not os.path.exists(PLOTDIR):
         os.mkdir(PLOTDIR)
 
+    rp.plot_magnetic_bstar_comparison(PLOTDIR, selfn='simpleB')
+    rp.plot_magnetic_bstar_comparison(PLOTDIR, selfn='complexB')
+    rp.plot_magnetic_bstar_comparison(PLOTDIR, selfn='complexM')
+    assert 0
     rp.plot_magnetic_bstar_comparison(PLOTDIR, selfn='hd64740')
     rp.plot_magnetic_bstar_comparison(PLOTDIR, selfn='hd37776')
-
+    assert 0
+    rp.plot_magnetic_bstar_comparison(PLOTDIR, selfn='all')
     rp.plot_magnetic_bstar_comparison(PLOTDIR, selfn='both')
+
 
     #NOTE: not implemented, b/c i would have probably autolabelled it an EB
     #rp.plot_magnetic_bstar_comparison(PLOTDIR, selfn='sigmaoriE')

### 2023-08-11 paper/collect.sh

@@ -21,5 +21,6 @@ cp $resultsdir/phase_timegroups_mosaic/TIC_402980664/TIC_402980664_P18.5611_2min
 cp $resultsdir/catalogscatter/catalogscatter_showmaybe.pdf f7.pdf
 
 # fig8
-cp $resultsdir/magnetic_bstar_comparison/magnetic_bstar_comparison_showtitles_hd37776.pdf f8a.pdf
-cp $resultsdir/magnetic_bstar_comparison/magnetic_bstar_comparison_showtitles_hd64740.pdf f8b.pdf
+cp $resultsdir/magnetic_bstar_comparison/magnetic_bstar_comparison_showtitles_simpleB.pdf f8a.pdf
+cp $resultsdir/magnetic_bstar_comparison/magnetic_bstar_comparison_showtitles_complexB.pdf f8b.pdf
+cp $resultsdir/magnetic_bstar_comparison/magnetic_bstar_comparison_showtitles_complexM.pdf f8c.pdf

### 2023-08-11 paper/ms.tex
update ms

@@
 \label{subsec:extreme}
-Figure~\ref{fig:catalogscatter} shows some of the derived properties
-for our CQV catalog, and contrasts them against both the target star
-sample (top panels), and the population of rotating stars in the Pleiades
-from \citet{2016AJ....152..114R}.
-Generally, CQVs are much younger than typical field stars. 
-In terms of their rotation, relative to the Pleiades,
-they are among the more rapidly rotating half of M dwarfs.
-The dearth of $T$$>$15.5 CQVs in our sample, despite our search extending
-to $T$$=$16, is a consequence of the 120-second selection function,
-not detection sensitivity.
+Figure~\ref{fig:catalogscatter} shows some of the derived properties for our
+CQV catalog, and compares them against both the target star sample (top
+panels), and against stars in the Pleiades
+\citep{2016AJ....152..114R}.  Typical CQV masses span
+0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This
+is a mass and age regime that includes fully convective stars
+($M_\star$$\lesssim$0.25\,$M_\odot$), as well as stars with radiative cores
+($M_\star$$\gtrsim$0.25\,$M_\odot$; \citealt{2018A&A...619A.177B}).  We found
+no obvious morphology differences between the two classes.  In terms of their
+rotation, relative to the Pleiades, the CQVs are among the more rapidly
+rotating half of M dwarfs.  The dearth of $T$$>$15.5 CQVs in our sample,
+despite our search extending to $T$$=$16, is a consequence of the 120-second
+selection function, not detection sensitivity.
 
@@
 $d$$=$18\,pc), a member of AB Dor.  To our knowledge, this manuscript
-is the first time that it has been noted as a CQV.  The three
+is the first time that it has been noted as a CQV.
+The three
 brightest CQVs are DG~CVn ($T$=9.3), TIC~405754448 ($T$=9.6), and
@@
 The catalog contains a few other stars with similar mass.  Given the
-small number of sub-stellar mass objects in our target sample, this
-suggests that future studies of brown dwarf photometric variability
-might also yield complex quasiperiodic variables, though there could
+small number of sub-stellar mass objects in our target sample, 
+future studies of brown dwarf photometric variability
+might also yield CQVs, though there could
 be degeneracies in interpretation with planetary surface features such
@@
 
-The most massive CQVs in our sample might represent an interesting new
-regime.  To date, the only stars reported to show the CQV phenomenon
-are M dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
-\citep{2017AJ....153..152S,2022AJ....163..144G}.  TIC~405754448 and TIC~405910546 however
-appear to have masses of $\approx$0.82 and $\approx$0.60\,$M_\odot$
-respectively.  The next-highest masses are $\approx$0.40\,$M_\odot$.
-The masses for the former two objects are consistent with their
-locations in the color--absolute magnitude diagram, and with their
-membership in LCC.  Based on its light curve morphology, TIC~405910546
-should be studied in greater depth, to confirm it is not an eclipsing
-binary.  TIC~405754448 similarly shows distinct morphology from many
-of the CQVs in Figure~\ref{fig:cqvs}, in that it has some of the
-lowest amplitude dips.  While TIC~405754448 might be an unresolved
-binary (RUWE$_{\rm DR3}$=4.7),  the depth of the coherent dips present
-in the Sector~11 light curve imply that the CQV signal is indeed from
-the apparent primary of the system.  Taken in sum, both of these
-objects seem to suggest that the CQV phenomenon extends up in mass to
-pre-main-sequence K dwarfs.
+The two most massive CQVs in our sample might represent an interesting
+new regime, but both have ambiguities.  To date, the only stars
+reported to show the CQV phenomenon are M dwarfs, with typical stellar
+masses $\lesssim$0.3\,$M_\odot$
+\citep{2017AJ....153..152S,2022AJ....163..144G}.  TIC~405754448 and
+TIC~405910546 however appear to have masses of $\approx$0.82 and
+$\approx$0.60\,$M_\odot$ respectively.  The next-highest masses in our
+sample are $\approx$0.40\,$M_\odot$.  The masses for the former two
+objects are consistent with their locations in the color--absolute
+magnitude diagram, and with their membership in LCC.  However based on
+its light curve morphology, TIC~405910546 should be studied in greater
+depth, to confirm it is not an eclipsing binary.  For TIC~405754448,
+we expect that the source is an unresolved binary, because RUWE$_{\rm
+DR3}$=4.7, and because the raw light curves in Sectors 11, 37, and 38
+for this source show an additional $\approx$6.5\,day, $\approx$0.3\%
+amplitude sinusoidal signal suggestive of an unresolved photometric
+companion.  If TIC~405754448 is a K+M binary, then the flux ratio
+between the primary and secondary would be expected to be
+$\approx$10:1.  It would be somewhat challenging for the M dwarf to
+produce the observed 12.9\,hr signal with such a flux deficit, but not
+impossible.  Therefore while both of these objects seem to suggest
+that the CQV phenomenon may extend up in mass to pre-main-sequence K
+dwarfs, more data are needed to fully substantiate this claim.
 
@@
 rapidly rotating M dwarfs at say, 10\,Myr.  Based on the degree to
-which M dwarfs remain rapid rotators over the first 700\,Myr
-\citep[e.g. Figure~13 of][]{2022AJ....164...80R}, it seems surprising
+which M dwarfs remain rapid rotators over the first few gigayears
+of their lives
+\citep[e.g.][]{2022AJ....164...80R,2022ApJ...936..109P}, it seems surprising
 in the gas clump (prominence) scenario that very few stars older than

### 2023-08-11 paper/ms.tex
update ms

@@
 discoveries are new, and they include the brightest
-($T$$\approx$9.5), closest ($d$$\approx$20\,pc), most massive
-($\approx$0.6-0.8\,$M_\odot$), and the oldest ($\approx$200\,Myr)
-examples of this class of object currently known.  A few objects are
-outliers: LP 12-502 for instance showed a ``dip complex'' with a
-period and duration that were fixed over 1,500 cycles, but in
-detail, this system exhibited between four and eight local minima
-per cycle, and at times also displayed multiple periods
-simultaneously.  We demonstrate that transient corotating material
-is the most viable explanation for this class of object, and present
-evidence supporting the hypothesis that this material is sculpted by
-stellar magnetic fields dominated by high order multipoles.  We
-expect that our sample will facilitate future efforts aimed at
-connecting CQVs to the broader contexts of star, disk, and perhaps
-even exoplanet evolution. 	
+($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and oldest
+($\approx$200\,Myr) examples of this class of object currently
+known.  A few objects are outliers: LP 12-502 for instance showed a
+``dip complex'' with a period and duration that were fixed over
+1,500 cycles, but in detail, this system exhibited between four and
+eight local minima per cycle, and at times also displayed multiple
+periods simultaneously.  We demonstrate that transient corotating
+material is the most viable explanation for this class of object,
+and present evidence supporting the hypothesis that this material is
+sculpted by stellar magnetic fields dominated by high order
+multipoles.  We expect that our sample will facilitate future
+efforts aimed at connecting CQVs to the broader contexts of star,
+disk, and perhaps even exoplanet evolution. 	
 \end{abstract}
@@
       {\bf Properties of CQVs identified by our search}.
-      CQVs are pre-main-sequence K and M dwarfs, younger than
-      $\approx$200 Myr, with rotation periods faster than around half
-      of Pleiades-age M dwarfs.
+      CQVs are mostly pre-main-sequence M dwarfs, younger than
+      $\approx$150 Myr, with rotation periods faster than $\approx$1\,day.
       The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are the
@@
 
-TIC~425937691 is a suprising case: it shows two seemingly independent
+TIC~425937691 is a surprising case: it shows two seemingly independent
 CQV signals on what appears to be the same star.  The two signals have
-periods of $\approx$4.816\,hr and $\approx$3.218\,hr, respectively.
+periods of $\approx$4.82\,hr and $\approx$3.22\,hr, respectively.
 The former is the larger amplitude signal visible in
@@
 simply be a coincidence.
+
+\subsection{TIC~435903839}
+%TODO: move these to their own ``debunked'' table, I think...
+%TODO: along with the IR excess ones
+TIC~435903839, which we originally classified as an ``ambiguous'' CQV, is an apparently
+similar case.
+We initially labeled this source as having a 10.82\,hr period, because this
+period minimized the dispersion in the phase-folded light curve.
+However closer inspection reveals that this source is a photometric
+blend of two ordinary rotating stars with $P_0$=3.60\,hr, and $P_1$=5.41\,hr.
+This is a novel false positive scenario for CQVs:
+two rapidly-rotating stars with near-integer ratios of rotation periods.
+The beat between the two rotation signals produces the spurious
+CQV signal.
+Such false positives can be excluded through careful accounting of
+all peaks in a periodogram.
+For instance, TIC~435903839 shows a peak at 16.27\,hr, which is not
+an integer multiple of the nominal ``10.82\,hr'' period.
 
@@
   %
-    \item Surprising analogs to the M  and K dwarf CQVs exist in
-    magnetic B stars, but only those with multipolar field topologies.
-    Since most magnetic B stars have dipolar magnetic fields,
-    this suggests that the CQV dips and warps are similarly being sculpted
-    by the stellar magnetic fields, and that the magnetic
-    fields themselves are probably also multipolar.
+    \item Surprising analogs to the CQVs exist in magnetic B stars,
+    but only those with multipolar field topologies.  Since most
+    magnetic B stars have dipolar magnetic fields, this suggests
+    that the CQV dips and warps are similarly being sculpted by the
+    stellar magnetic fields, and that the magnetic fields themselves
+    are probably also multipolar.
   %

### 2023-08-11 paper/ms.tex
tic 3006 appendix improvements

@@
 
-Figures~\ref{fig:tic3006river} and~\ref{fig:tic3006timegroups} show 120-second
-cadence data for TIC~300651846, a CQV in the TESS continuous viewing zone.
-With the exception of a few sectors, TESS data will exist for this source
-over Sectors 1-12, 27-39, and 61-69.
-The majority are in the full frame images, and are the subject of future work.
+Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river} show
+120-second cadence data for TIC~300651846, a CQV in the TESS
+continuous viewing zone.  If it were not for the existence of
+TIC~402980664, this source would likely have been the subject of
+greater attention.  With the exception of a few sectors, TESS data
+will exist for TIC~300651846 over Sectors 1-12, 27-39, and 61-69.
+While most of the available data will exist in the full frame images,
+in Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river}
+focus only on the 120-second cadence data.
+
+During Sectors 32-39, the source shows between one and four local
+minima per cycle.  During the early portions of Sectors 61-65, it is
+somewhat more complex, with at least five clear local minima per
+cycle.  As the source evolves, this complexity decreases, while the
+sharpness of one of the minima appears to increase.  We did not find
+evidence for any obvious ``state-switches'' analogous to those that we
+observed in LP 12-502; gradual evolution over timescales of
+$\approx$50-100 cycles seem to be the norm for TIC~300651846.
+
+\begin{figure*}[!t]
+	\begin{center}
+		\subfloat{
+			\includegraphics[width=0.43\textwidth]{f11a.pdf}
+			\includegraphics[width=0.43\textwidth]{f11b.pdf}
+		}
+	\end{center}
+	\vspace{-0.4cm}
+	\caption{
+		{\bf Long-term evolution of TIC 300651846}.
+    All available 120-second cadence data as of 11 August 2023 are shown.
+    Cycles 0 to 622 span TESS Sectors 32-39 (Nov 2020--June 2021);
+    cycles 2296-2676 span Sectors 61-65 (Jan--June 2023).  We assumed
+    a 8.254\,hr period and a fixed reference epoch (BTJD 2174.127) for
+    both panels.
+    Light curve segments are split based on the presence of gaps
+    longer than three hours.
+	}
+	\label{fig:tic3006timegroups}
+\end{figure*}
 
@@
 
-\begin{figure*}[!t]
-	\begin{center}
-		\subfloat{
-			\includegraphics[width=0.43\textwidth]{TIC_300651846_P8.254_2min_phase_timegroups.png}
-		}
-	\end{center}
-	\vspace{-0.4cm}
-	\caption{
-		{\bf Orbit-phased plots of TIC 300651846}.
-		The envelope has not been subtracted.
-	}
-	\label{fig:tic3006timegroups}
-\end{figure*}
-
 \section{No significant power at 20~second cadence}

### 2023-08-11 complexrotators/plotting.py

@@ -474,7 +474,9 @@ def plot_phase_timegroups(
     yoffset=5,
     showtitle=1,
     figsize_y=7,
-    do4029_resid=0
+    do4029_resid=0,
+    cyclewindow=None,
+    mingap=3/24  # days
     ):
     """
     As in plot_phase
@@ -540,7 +542,7 @@ def plot_phase_timegroups(
         fluxs = np.array(df.r_flux)
 
     from astrobase.lcmath import find_lc_timegroups
-    ngroups, groups = find_lc_timegroups(times, mingap=3/24)
+    ngroups, groups = find_lc_timegroups(times, mingap=mingap)
 
     # Make plots
     plt.close('all')
@@ -571,6 +573,12 @@ def plot_phase_timegroups(
         if len(gtime) < 100:
             continue
         #print(txt, N_cycles_in_group, len(gtime))
+
+        if isinstance(cyclewindow, (tuple, list)):
+            if e_start < cyclewindow[0]:
+                continue
+            if e_end > cyclewindow[1]:
+                continue
 
         plot_phased_light_curve(
             gtime, gflux, plot_t0, plot_period, None,
@@ -608,6 +616,9 @@ def plot_phase_timegroups(
     s = ''
     if do4029_resid:
         s += 'resid_'
+    if isinstance(cyclewindow, (tuple, list)):
+        s += f'cycle{cyclewindow[0]}_to_{cyclewindow[1]}'
+
     outpath = join(outdir, f"{s}{ticid}_P{plot_period*24:.4f}_{lc_cadences}_phase_timegroups.png")
     #fig.savefig(outpath, dpi=300)
     savefig(fig, outpath, dpi=450)
@@ -974,12 +985,12 @@ def plot_phased_light_curve(
                 ax.text(0.97+xtxtoffset,
                         np.nanmin(norm(orb_bd['binnedmags'][sel])-dy/5), txt,
                         transform=tform, ha='right',va='top', color='k',
-                        fontsize=fontsize, bbox=props)
+                        fontsize=fontsize, bbox=props, zorder=999999)
             else:
                 ax.text(0.97+xtxtoffset,
                         np.nanmin(norm(orb_bd['binnedmags'])-dy/5), txt,
                         transform=ax.transAxes, ha='right',va='top', color='k',
-                        fontsize=fontsize, bbox=props)
+                        fontsize=fontsize, bbox=props, zorder=999999)
 
         else:
             if isinstance(t0, float):

### 2023-08-11 drivers/plot_phase_timegroups.py

@@ -10,8 +10,8 @@ def main():
     ticids = [
         #"224283342",
         #"146539195"
-        "402980664"
-        #"300651846"
+        #"402980664"
+        "300651846"
     ]
 
     for ticid in ticids:
@@ -19,28 +19,73 @@ def main():
         outdir = os.path.join(PLOTDIR, f'TIC_{ticid}')
         if not os.path.exists(outdir): os.mkdir(outdir)
 
+        if ticid == '402980664':
+            t0 = 1791.12
+            ylim = [-100,5]
+            yoffset = 5.5
+            manual_period = 18.5611/24
+            do4029_resid = 1
+            lc_cadences = '2min'
+            figsize_y = 7
+            cyclewindow = None
+            mingap = 3/24
+
+        elif ticid == '300651846':
+            # 2min
+            yoffset = 6.5
+            manual_period = 8.254/24
+            t0 = 2170. + 12*manual_period
+            figsize_y = 7
+
+            ## for 2min firsthalf
+            #lc_cadences = '2min'
+            #cyclewindow = [-1,630]
+            #ylim = [-105,5]
+
+            # for 2min secondthalf
+            lc_cadences = '2min'
+            cyclewindow = [2290,2680]
+            ylim = [-133,5]
+            mingap = 3/24
+
+            ## for all available 2min
+            #lc_cadences = '2min'
+            #cyclewindow = None
+            #ylim = [-240,5]
+
+            # for 3006 QLP
+            #lc_cadences='QLP'
+            #ylim=[-450,5],
+            #figsize_y=12,
+
+            do4029_resid = 0
+
+        else:
+            t0 = 'binmin'
+            ylim = None
+            yoffset = None
+            manual_period = None
+            lc_cadences = '2min_20sec'
+            figsize_y = 7
+            cyclewindow = None
+            mingap = 3/24
+
+            do4029_resid = 0
+
         cp.plot_phase_timegroups(
             outdir,
             ticid=f'TIC_{ticid}',
             lc_cadences='2min',
             binsize_phase=0.005,
-            #t0='binmin',
-            # for 4029
-            t0=1791.12,
-            ylim=[-100,5],
-            yoffset=5.5,
-            manual_period=18.5611/24,
-            # for 3006 2min
-            #ylim=[-190,5],
-            #yoffset=6.5,
-            # for 3006 QLP
-            #lc_cadences='QLP',
-            #binsize_minutes=30,
-            #ylim=[-450,5],
[…]

### 2023-08-11 paper/collect.sh

@@ -24,3 +24,8 @@ cp $resultsdir/catalogscatter/catalogscatter_showmaybe.pdf f7.pdf
 cp $resultsdir/magnetic_bstar_comparison/magnetic_bstar_comparison_showtitles_simpleB.pdf f8a.pdf
 cp $resultsdir/magnetic_bstar_comparison/magnetic_bstar_comparison_showtitles_complexB.pdf f8b.pdf
 cp $resultsdir/magnetic_bstar_comparison/magnetic_bstar_comparison_showtitles_complexM.pdf f8c.pdf
+
+# appendix
+cp $resultsdir/phase_timegroups/TIC_300651846/cycle-1_to_630TIC_300651846_P8.2540_2min_phase_timegroups.pdf f11a.pdf
+cp $resultsdir/phase_timegroups/TIC_300651846/cycle2290_to_2680TIC_300651846_P8.2540_2min_phase_timegroups.pdf f11b.pdf
+

### 2023-08-11 paper/ms.tex
ditto
ms: update

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% MS TODO's
-%
-% * find/replace "centrifugally supported" with something less
-% jargony, and more physically meaningful.  (read CR89)
-%
-% * "Bound-free absorption can provide
-%   wavelength-dependent opacity, but the absorption coefficients
-%   generally {\it grow} with increasing wavelength, rather than {\it
-%   shrink} as one needs in order to get deeper absorption in the blue
-%   than in the red."
-%   --> Isn't this statement wavelength dependent????
-%
-% * Verify "32" in Figure 4 does not change with number of stars in
-%   subsample changing
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 % upon AAS submission
@@
 sources of optical variability include inhomogeneities on stellar
-surfaces such as starspots and faculae \citep[e.g.][]{2021isma.book.....B},
-occultations by gas-rich circumstellar disks
-\citep[e.g.][]{2017MNRAS.470..202B}, and, in geometrically favorable
-circumstances, eclipses by stars and planets
-\citep[e.g.][]{2010exop.book...55W}.  More exotic forms of optical variability
-relevant to this work include transiting exocomets (e.g.~$\beta$~Pic;
-\citealt{2019A&A...625L..13Z}) and disintegrating rocky bodies around
-both M dwarfs (e.g. KOI-2700; \citealt{2014ApJ...784...40R}) and white
-dwarfs (e.g. WD~1145; \citealt{2015Natur.526..546V}).
+surfaces such as starspots and faculae
+\citep[e.g.][]{2021isma.book.....B}, occultations by gas-rich
+circumstellar disks \citep[e.g.][]{2017MNRAS.470..202B}, and, in
+geometrically favorable circumstances, eclipses by stars and planets
+\citep[e.g.][]{2010exop.book...55W}.  More exotic forms of optical
+variability relevant to this work include transiting exocomets
+(e.g.~$\beta$~Pic; \citealt{2019A&A...625L..13Z}) and disintegrating
+rocky bodies around both M dwarfs (e.g. KOI-2700;
+\citealt{2014ApJ...784...40R}) and white dwarfs (e.g. WD~1145;
+\citealt{2015Natur.526..546V}).
 
@@
 root cause is only beginning to become clear: complex quasiperiodic
-variables (CQVs).  These objects are identified 
-from their optical light curves, which show nearly periodic troughs
-that are either sharp or broad; these troughs are often superposed on
-smooth spot-like modulation
+variables (CQVs).  These objects are identified from their optical
+light curves, which show nearly periodic troughs that are either sharp
+or broad; these troughs are often superposed on smooth spot-like
+modulation
 \citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z}.
-Some CQVs show up to eight local minima (``dips'') per cycle.  Most are
-pre-main-sequence M dwarfs without near-infrared excesses, ages of
+Some CQVs show up to eight local minima (``dips'') per cycle.  Most
+are pre-main-sequence M dwarfs without near-infrared excesses, ages of
 $\approx$5-150 million years (Myr), and rotation periods of at most
-two days; they are observed to comprise $\approx$1-3\% of M dwarfs younger
-than 100 Myr \citep{2016AJ....152..114R,2022AJ....163..144G}.  The
-dips can be chromatic, with a reddening law plausibly consistent with
-dust
+two days; they are observed to comprise $\approx$1-3\% of M dwarfs
+younger than 100 Myr \citep{2016AJ....152..114R,2022AJ....163..144G}.
+The dips can be chromatic, with a reddening law plausibly consistent
+with dust
 \citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
@@
 similar to observations made in systems such as AB~Dor
-\citep[see][]{1999ASPC..158..146C} or PTFO 8-8695 \citep{2016ApJ...830...15J}.
+\citep[see][]{1999ASPC..158..146C} or PTFO 8-8695
+\citep{2016ApJ...830...15J}.
 
@@
 
-A point on nomenclature. 
-CQVs have been called ``transient flux
+A point on nomenclature.  CQVs have been called ``transient flux
 dips'', ``persistent flux dips'', ``scallop shells'', ``batwings'',
@@
 between July~2018 and Sep~2022 (Sectors 1-55).  Specifically, we used
-the 120-second cadence light curves produced by the Science
-Processing and Operations Center at NASA Ames
-\citep{2016SPIE.9913E..3EJ}.  While the TESS data products from these
-sectors also included full frame images with cadences of 600 and 1800
-seconds, we limited our scope in this study for the sake of simplicity
-in data handling.  In exchange, we sacrificed both completeness and
-homogeneity of the selection function.  While TESS cumulatively
-observed $\approx$90\% of the sky for at least one lunar month between
-July~2018 and Sep~2022, the 120-second cadence data were collected for
-only a subset of observable stars during this time due to telemetric
-constraints
+the 120-second cadence light curves produced by the Science Processing
+and Operations Center at NASA Ames \citep{2016SPIE.9913E..3EJ}.  While
+the TESS data products from these sectors also included full frame
+images with cadences of 600 and 1800 seconds, we limited our scope in
+this study for the sake of simplicity in data handling.  In exchange,
+we sacrificed both completeness and homogeneity of the selection
+function.  While TESS cumulatively observed $\approx$90\% of the sky
+for at least one lunar month between July~2018 and Sep~2022, the
+120-second cadence data were collected for only a subset of observable
+stars during this time due to telemetric constraints
 \citep[see][]{2021PASP..133i5002F}.
@@
 arcseconds, and a geometric distance $d$ defined by inverting the
-parallax and ignoring any zero-point correction.  The target sample therefore includes
-\nstarssearched\ M dwarfs and late-K dwarfs, down to $T$$<$16 and out
-to $d$$<$150\,pc.
+parallax and ignoring any zero-point correction.  The target sample
+therefore includes \nstarssearched\ M dwarfs and late-K dwarfs, down
+to $T$$<$16 and out to $d$$<$150\,pc.
 
@@
 spline knots per cycle, and how large and wide of a local minimum to
-consider a ``true dip'', were chosen during testing based on
-their ability to correctly re-identify a large fraction ($>$90\%) of
-known CQVs, while also being able to consistently reject common false
+consider a ``true dip'', were chosen during testing based on their
+ability to correctly re-identify a large fraction ($>$90\%) of known
+CQVs, while also being able to consistently reject common false
 positives such as rapidly rotating spot-induced variability and
@@
 
-Overall, for a star to proceed to manual
-examination, we required that it have a peak PDM period below two
-days, and that it exhibited at least three sharp local minima (as
-algorithmically reported) in at least one observed TESS sector.
+Overall, for a star to proceed to manual examination, we required that
+it have a peak PDM period below two days, and that it exhibited at
+least three sharp local minima (as algorithmically reported) in at
+least one observed TESS sector.
 
@@
 We performed an independent search for strongly periodic phenomena
-using our Fourier pipeline, following \citet{2019ApJ...876..127Z} and
-\citet[][their Section~1.3]{2023MNRAS.524.4220P}.
-Starting with the PDC\_SAP light curves, we normalized each light
-curve, and then re-binned it into equal width bins {\bf LB: how long?} to
-account for the uneven spacing in the TESS data, as well as the data
-gap during each sector caused by satellite downlink.  We then padded
-the data to ensure that the light curve had a length that was a power
-of two, as described by \citeauthor{2019ApJ...876..127Z}.  We
-then took the Fourier transform of the corrected, padded light curve using 
-{\tt numpy.fft.fft} and searched for peaks with a significance of over 
+using a Fourier-based approach, following \citet{2019ApJ...876..127Z}
+and \citet[][their Section~1.3]{2023MNRAS.524.4220P}.  Starting with
+the PDC\_SAP light curves, we normalized each light curve, and then
+re-binned it into equal width bins {\bf LB: how long?} to account for
+the uneven spacing in the TESS data, as well as the data gap during
+each sector caused by satellite downlink.  We then padded the data to
+ensure that the light curve had a length that was a power of two, as
+described by \citeauthor{2019ApJ...876..127Z}.  We then took the
+Fourier transform of the corrected, padded light curve using {\tt
+numpy.fft.fft} and searched for peaks with a significance of over
 12-$\sigma$ within each set of 500 bins.
@@
 curves, Fourier transform, potential contaminating stars, and
-information about these contaminating stars.  
-In the sectors for which
+information about these contaminating stars.  In the sectors for which
 we performed this analysis, we found that ``summary'' sheets were
 generated for approximately 10\% of the 20\,000 120-second targets in
-a given sector.  
-We then manually reviewed each summary sheet, and
+a given sector.  We then manually reviewed each summary sheet, and
 visually labelled each star based on its morphology (including e.g.,
@@
 oddly-shaped dips; relative stability over a timescale of 30\,days).
-We independently noted stars that we thought could be CQVs, but that were more
-ambiguous.
+We independently noted stars that we thought could be CQVs, but that
+were more ambiguous.
 
@@
 pipeline were 5:1, with \nuniqdipflagged\ unique stars flagged, and
-about 20\% being labeled either ``good'' or ``possible'' CQVs.
-The Fourier analysis was not amenable to calculating a similar
+about 20\% being labeled either ``good'' or ``possible'' CQVs.  The
+Fourier analysis was not amenable to calculating a similar
 false-positive probability, because it was implemented as a general
@@
 variability analyses beyond CQVs.
-
-%TODO: include?
-%Between the targets identified as CQVs by both pipelines,
-% {\red 
-%\begin{itemize}
-%\item XX targets were found to overlap
-%\item YY targets were found via Fourier but not via dip counting
-%\end{itemize}
-%}
-%The difference in discovery rate between these techniques can be attributed to
-%low-amplitude peaks in the periodogram that were missed, some of which likely
-%arose from fainter CQVs.
 
@@
 probabilities returned by this procedure are qualitatively useful, but
-should be assessed with caution due to the
-non-Gaussian nature of most groups within the solar neighborhood
-\citep[see e.g.][Figure~10]{2021ApJ...917...23K}.
+should be assessed with caution due to the non-Gaussian nature of most
+groups within the solar neighborhood \citep[see
+e.g.][Figure~10]{2021ApJ...917...23K}.
 
@@
 excess; we similarly omitted WISE 3-4, but due to reliability
-concerns.
-\texttt{astroARIADNE} compares the measured broadband flux
+concerns.  \texttt{astroARIADNE} compares the measured broadband flux
 measurements against pre-computed model grids, and by default fits for
@@
 our search.  The ``high-quality sample'' includes \ngoods\ of these
-objects, which demonstrated what we viewed as
-unambiguous characteristics of the CQV phenomenon in at least one TESS
-sector.  The
-classification of the remaining \nmaybes\ CQV candidates was
+objects, which demonstrated what we viewed as unambiguous
+characteristics of the CQV phenomenon in at least one TESS sector.
+The classification of the remaining \nmaybes\ CQV candidates was
 ambiguous.  Additional data from TESS or other instruments could help
@@
 The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
-\ngoods\ CQVs.  The objects are sorted first in order of the
-number of TESS 120-second cadence sectors in which they clearly
-demonstrated the CQV phenomenon, and secondarily by descending
-brightness.  The top five objects by this metric are TIC~300651846
-($T$$=$13.5, 12 sectors); TIC~402980664 ($T$$=$11.1, 7 sectors);
-TIC~89463560 ($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5
-sectors); and TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest
-five CQVs span 9.3$<$$T$$<$11.1; the faintest five span
-14.5$<$$T$$<$15.0.  The fastest five have periods spanning
-3.6\,hr$<$$P$$<$6.2\,hr, and the slowest five span
-27\,hr$<$$P$$<$38\,hr.
-Regarding likely astrometric or visual binaries,
-\ngoodhighruwe/\ngoods\ high-quality CQVs have a Gaia DR3 RUWE$>$2;
-\nmaybehighruwe/\nmaybes\ of the ambiguous sample share this
-characteristic.
-% This is consistent with Rappaport2014's visual binary fraction determined from
-% 30/100 rapidly rotating Kepler stars having multiple periodicities
+\ngoods\ CQVs.  The objects are sorted first in order of the number of
+TESS 120-second cadence sectors in which they clearly demonstrated the
+CQV phenomenon, and secondarily by descending brightness.  The top
+five objects by this metric are TIC~300651846 ($T$$=$13.5, 12
+sectors); TIC~402980664 ($T$$=$11.1, 7 sectors); TIC~89463560
+($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5 sectors); and
+TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest five CQVs span
+9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
+fastest five have periods spanning 3.6\,hr$<$$P$$<$6.2\,hr, and the
+slowest five span 27\,hr$<$$P$$<$38\,hr.  Regarding likely astrometric
+or visual binaries, \ngoodhighruwe/\ngoods\ high-quality CQVs have a
+Gaia DR3 RUWE$>$2; \nmaybehighruwe/\nmaybes\ of the ambiguous sample
+share this characteristic.
+
+% This is consistent with Rappaport2014's visual binary fraction
+% determined from 30/100 rapidly rotating Kepler stars having multiple
+% periodicities
 
@@
 minima per cycle.  Some stars show relatively ordinary modulation
-during one portion of the phased light curve, and highly
-structured modulation in the remainder of the cycle (e.g.
-TIC~206544316, TIC~224283342, TIC~402980664).  Others show structured
-modulation over the entire span of a cycle (e.g. TIC~2234692,
-TIC~401789285, TIC~425933644, TIC~142173958).  Others show some
-mix between these two modes.
+during one portion of the phased light curve, and highly structured
+modulation in the remainder of the cycle (e.g.  TIC~206544316,
+TIC~224283342, TIC~402980664).  Others show structured modulation over
+the entire span of a cycle (e.g. TIC~2234692, TIC~401789285,
+TIC~425933644, TIC~142173958).  Others show some mix between these two
+modes.
 
@@
 discovered in Sco-Cen.
-%IC\,2602 and IC\,2391, which are located slightly beyond
-%100\,pc, are an example of this completeness effect: our search did
-%not find any CQVs in those clusters.
+
+% IC\,2602 and IC\,2391, which are located slightly beyond 100\,pc, are
+% an example of this completeness effect: our search did not find any
+% CQVs in those clusters.
 
@@
 photometrically elevated relative to the main sequence.  For instance,
-both were noted by \citet{2021ApJ...917...23K} as being in the ``diffuse'' population
-of $<$50\,Myr stars near the Sun.
+both were noted by \citet{2021ApJ...917...23K} as being in the
+``diffuse'' population of $<$50\,Myr stars near the Sun.
 
 Our search confirms that the CQV phenomenon persists for at least
-$\approx$150\,Myr.  Table~\ref{tab:thetable} includes three $\approx$150\,Myr CQVs
-in AB~Dor \citep{2015MNRAS.454..593B}, a $\approx$112\,Myr old Pleiades CQV
-\citep{2015ApJ...813..108D}, and
-a similarly-aged Psc-Eri member \citep{2020A&A...639A..64R}.  To our knowledge, TIC~332517282
-in AB~Dor was the previous record-holder for oldest-known CQV
-\citep{2019ApJ...876..127Z,2022AJ....163..144G}; at least one
-unambiguous CQV (EPIC~211070495) and a few other candidates were also
-previously known in the Pleiades \citep{2016AJ....152..114R}.
-
-%FIXME it'd be useful to get an RV for this one...
+$\approx$150\,Myr.  Table~\ref{tab:thetable} includes three
+$\approx$150\,Myr CQVs in AB~Dor \citep{2015MNRAS.454..593B}, a
+$\approx$112\,Myr old Pleiades CQV \citep{2015ApJ...813..108D}, and a
+similarly-aged Psc-Eri member \citep{2020A&A...639A..64R}.  To our
+knowledge, TIC~332517282 in AB~Dor was the previous record-holder for
+oldest-known CQV \citep{2019ApJ...876..127Z,2022AJ....163..144G}; at
+least one unambiguous CQV (EPIC~211070495) and a few other candidates
+were also previously known in the Pleiades
+\citep{2016AJ....152..114R}.
+
+% NOTE: it'd be useful to get an RV for this one...
+
 The upper age limit for CQVs may even pass 200\,Myr, based on the
@@
 This could be relatively easily resolved by acquiring even a
-medium-resolution spectrum.
-An independent assessment of the group's kinematics using Gaia data,
-and its rotation sequence using TESS, could lend further credence in
-such an analysis.
+medium-resolution spectrum.  An independent assessment of the group's
+kinematics using Gaia data, and its rotation sequence using TESS,
+could lend further credence in such an analysis.
 
@@
 As is typical for CQVs \citep{2017AJ....153..152S}, most CQVs in our
-catalog did not show infrared excesses in the WISE1-4 bands.
-Visually inspecting the SEDs of our entire \ncpvsfound\ star sample,
-we labeled two objects as having ``good'' infrared excesses (both W3
-and W4 at $>$3$\sigma$ above the photospheric prediction), and three
-as ``possible'' infrared excess (only W3 at $>$3$\sigma$).
+catalog did not show infrared excesses in the WISE1-4 bands.  Visually
+inspecting the SEDs of our entire \ncpvsfound\ star sample, we labeled
+two objects as having ``good'' infrared excesses (both W3 and W4 at
+$>$3$\sigma$ above the photospheric prediction), and three as
+``possible'' infrared excess (only W3 at $>$3$\sigma$).
 
@@
 curves did not show the rigid periodicity typical of CQVs;  their
-periods were also relatively long.  After labeling them, inspection
-of further sectors clarified that both sources are dippers (see online plots
-in Figure~\ref{fig:vet}).  Independently, TIC 193136669 has a cold
-molecular disk based on observed 1.3\,mm continuum emission and
+periods were also relatively long.  After labeling them, inspection of
+further sectors clarified that both sources are dippers (see online
+plots in Figure~\ref{fig:vet}).  Independently, TIC 193136669 has a
+cold molecular disk based on observed 1.3\,mm continuum emission and
 resolved Keplerian $^{12}{\rm CO}(2-1)$ emission
@@
 \citep{2015A&A...582L...5R}, suggestive of cold dust grains being
-present.  It is also a dipper.
-Section~\ref{subsec:discdippers} highlights plausible evolutionary
-connections between CQVs and dippers in light of these
-``misclassifications'' .
+present.  It is also a dipper.  Section~\ref{subsec:discdippers}
+highlights plausible evolutionary connections between CQVs and dippers
+in light of these ``misclassifications'' .
 
@@
 clear CQV signal, but has no definitive evidence for a large, dusty
-disk.  TIC~244161191 (TOI-278), in Columba, also has no
-definitive evidence for a large disk.  It is however
-``multi-periodic''---in addition to the 7.17\,hr CQV signal, this
-source shows a superposed 8.39\,hr sinusoidal signal, probably from an
-unresolved neighboring star or binary companion.
+disk.  TIC~244161191 (TOI-278), in Columba, also has no definitive
+evidence for a large disk.  It is however ``multi-periodic''---in
+addition to the 7.17\,hr CQV signal, this source shows a superposed
+8.39\,hr sinusoidal signal, probably from an unresolved neighboring
+star or binary companion.
 
@@
 precision necessary to be able to accurately propagate an ephemeris
-over two years.
-The achievable period precision, $\sigma_P$, can be estimated as
+over two years.  The achievable period precision, $\sigma_P$, can be
+estimated as
 \begin{equation}
@@
 (e.g.~a dip, or the overall shape of the sinusoidal envelope) can be
-tracked.  Assuming $\sigma_\phi$$\approx$$0.02$ and a 20-day
-baseline over a single TESS sector yields $\sigma_{P}$$\approx$$0.25^{+0.38}_{-0.14}$\,minutes for the population shown in
-Figure~\ref{fig:evoln}; propagated forward 1{,}000 cycles
-yields a typical ephemeris uncertainty range of 2-11\,hours.
-Measuring the periods for each sector
-independently, there did not seem to be any significant ($>$3$\sigma$)
-period changes.  This implies an absolute period
-stability of $\lesssim$0.1\% over the two-year baseline.
+tracked.  Assuming $\sigma_\phi$$\approx$$0.02$ and a 20-day baseline
+over a single TESS sector yields
+$\sigma_{P}$$\approx$$0.25^{+0.38}_{-0.14}$\,minutes for the
+population shown in Figure~\ref{fig:evoln}; propagated forward 1{,}000
+cycles yields a typical ephemeris uncertainty range of 2-11\,hours.
+Measuring the periods for each sector independently, there did not
+seem to be any significant ($>$3$\sigma$) period changes.  This
+implies an absolute period stability of $\lesssim$0.1\% over the
+two-year baseline.
 
@@
 based on the the shape evolution between Sectors 13 and 39, it is a
-CQV.  
-Based on the fraction of sources overall that ``turned off'', the
-observed shape evolution implies that CQVs have a duty cycle of
-$\approx$75\%.
-This type of correction is likely worth including in population-level
-estimates of how intrinsically common CQVs are in the low-mass stellar
-population \citep[e.g.][]{2022AJ....163..144G}.
+CQV.  Based on the fraction of sources overall that ``turned off'',
+the observed shape evolution implies that CQVs have a duty cycle of
+$\approx$75\%.  This type of correction is likely worth including in
+population-level estimates of how intrinsically common CQVs are in the
+low-mass stellar population \citep[e.g.][]{2022AJ....163..144G}.
 
@@
 		\caption{
-      %TODO : 
 		{\bf CQVs keep their periods but change their shapes.}
@@
       in the shape of the dip pattern.  The light curve is binned to
-      15-minute intervals so that there are 96 points per day, and each
-      point is connected by a line.  
-      Data gaps longer than 15-minutes are not
-      interpolated; if data are missing, nothing is plotted.
+      15-minute intervals so that there are 96 points per day, and
+      each point is connected by a line.  Data gaps longer than
+      15-minutes are not interpolated; if data are missing, nothing is
+      plotted.
 		}
@@
 range between the maximum and minimum sector-specific periods was
-measured to be about one minute.   However, in detail, a period shift of
-$\pm$1\,minute would yield major phase drifts over the baseline; that
-time interval corresponds to roughly 1/1000$^{\rm th}$ of a period,
-and we have observed 1500 cycles.  
-%Assuming $\sigma_{\phi} \approx
-%0.01$ and applying Equation~\ref{eq:periodprecision} yields an
-%expected period precision $\sigma_{\rm P} \approx 0.45\,{\rm sec}
-%\approx 1.2\times 10^{-4}\,{\rm hr}$. 
- By visually fine-tuning over a
-grid in period, we eventually found $P=18.5611 \pm 0.0001$\,hr, which
-seems to track certain features in the LP 12-502 light curve well over
-the entire dataset.
+measured to be about one minute.   However, in detail, a period shift
+of $\pm$1\,minute would yield major phase drifts over the baseline;
+that time interval corresponds to roughly 1/1000$^{\rm th}$ of a
+period, and we have observed 1500 cycles.  By visually fine-tuning
+over a grid in period, we eventually found $P=18.5611 \pm 0.0001$\,hr,
+which seems to track certain features in the LP 12-502 light curve
+well over the entire dataset.
 
@@
 minima.  We dub these dips $\{ 1, 2, 3, 4 \}$ at phases $\{ -0.28,
--0.08, 0, 0.25 \}$, respectively.  Over cycles 0-64, the depth of
-dips 1 and 3 remain roughly fixed.  However dip 4 decreases in
-depth by about 2\%, while dip 2 increases in depth, by about the
-same amount (see Figure~\ref{fig:lp}).  During cycles 48-64, a fifth
-dip may also be emerging, in the main ``large'' dip group.
+-0.08, 0, 0.25 \}$, respectively.  Over cycles 0-64, the depth of dips
+1 and 3 remain roughly fixed.  However dip 4 decreases in depth by
+about 2\%, while dip 2 increases in depth, by about the same amount
+(see Figure~\ref{fig:lp}).  During cycles 48-64, a fifth dip may also
+be emerging, in the main ``large'' dip group.
 
@@
 two intricately structured dip complexes, plus a small leading dip.
-The single leading dip is present at the same phase as in
-cycles 0-64, and is therefore likely to be the same struture.  Along a
-similar line of logic, it seems plausible that the first ``dip
-complex'' during cycles 248-264 represents an evolution of the initial
-complex seen during cycles 0-64, though with greatly reduced depth.
-During cycles 266-310, an additional local minimum develops between
-the two complexes; this feature is best visualized on the river plots
+The single leading dip is present at the same phase as in cycles 0-64,
+and is therefore likely to be the same struture.  Along a similar line
+of logic, it seems plausible that the first ``dip complex'' during
+cycles 248-264 represents an evolution of the initial complex seen
+during cycles 0-64, though with greatly reduced depth.  During cycles
+266-310, an additional local minimum develops between the two
+complexes; this feature is best visualized on the river plots
 (Appendix~\ref{app:lp}), and we discuss its (shorter) period below.
@@
 of 3.5\% over about 22 minutes (0.02\,$P$), which is the steepest
-slope exhibited anywhere in the LP~12-502 dataset.  After
-the sharp dip, there is a roughly exponential fall-off spanning about
-a quarter of a period, punctuated by coherent local minima and maxima
-which in detail (Appendix~\ref{app:lp}) have slightly longer periods
-than the sharp dip.  The sharp leading dip only decreases in depth
-following a sudden state-switch at BTJD 2030.7 (cycles 299-315), which
-happens during a flare (Figure~\ref{fig:lplc}).  The trailing dips
-remain thereafter.
+slope exhibited anywhere in the LP~12-502 dataset.  After the sharp
+dip, there is a roughly exponential fall-off spanning about a quarter
+of a period, punctuated by coherent local minima and maxima which in
+detail (Appendix~\ref{app:lp}) have slightly longer periods than the
+sharp dip.  The sharp leading dip only decreases in depth following a
+sudden state-switch at BTJD 2030.7 (cycles 299-315), which happens
+during a flare (Figure~\ref{fig:lplc}).  The trailing dips remain
+thereafter.
 
@@
 % 16 px vs 310 px for a full phase
-%Based on our SED fitting $R_\star=0.369\,R_\odot$
-%star, and from the isochrone mass, $M_\star=0.215\,M_\odot$ 
+% Based on our SED fitting $R_\star=0.369\,R_\odot$ star, and from the
+% isochrone mass, $M_\star=0.215\,M_\odot$
+
 {\sc Dip durations}---The shortest dip duration for any of the
@@
       CQVs are mostly pre-main-sequence M dwarfs, younger than
-      $\approx$150 Myr, with rotation periods faster than $\approx$1\,day.
-      The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are the
-      dark blue circles; \nmaybes\ ambiguous CQV candidates are light
-      blue circles.  The top panels show the \nstarssearched\ target
-      stars with 120-second cadence TESS data as the shaded gray
-      background; darker regions correspond to a larger relative
-      number of searched stars.  The lower-left panel compares the
-      rotation--color distribution of CQVs against the rotation
-      periods of K and M dwarfs in the Pleiades from
-      \citet{2016AJ....152..114R}.  The lower-middle panel plots the
-      derived corotation radii $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in
-      units of stellar radii against the measured CQV periods, in
-      units of hours.  Ages in the final panel are known from cluster
-      membership.
+      $\approx$150 Myr, with rotation periods faster than
+      $\approx$1\,day.  The \ngoods\ bonafide CQVs in
+      Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
+      ambiguous CQV candidates are light blue circles.  The top panels
+      show the \nstarssearched\ target stars with 120-second cadence
+      TESS data as the shaded gray background; darker regions
+      correspond to a larger relative number of searched stars.  The
+      lower-left panel compares the rotation--color distribution of
+      CQVs against the rotation periods of K and M dwarfs in the
+      Pleiades from \citet{2016AJ....152..114R}.  The lower-middle
+      panel plots the derived corotation radii $R_{\rm cr} =
+      (GM/\Omega^2)^{1/3}$ in units of stellar radii against the
+      measured CQV periods, in units of hours.  Ages in the final
+      panel are known from cluster membership.
 		}
@@
 \label{subsec:extreme}
-Figure~\ref{fig:catalogscatter} shows some of the derived properties for our
-CQV catalog, and compares them against both the target star sample (top
-panels), and against stars in the Pleiades
+
+Figure~\ref{fig:catalogscatter} shows some of the derived properties
+for our CQV catalog, and compares them against both the target star
+sample (top panels), and against stars in the Pleiades
 \citep{2016AJ....152..114R}.  Typical CQV masses span
-0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This
-is a mass and age regime that includes fully convective stars
-($M_\star$$\lesssim$0.25\,$M_\odot$), as well as stars with radiative cores
-($M_\star$$\gtrsim$0.25\,$M_\odot$; \citealt{2018A&A...619A.177B}).  We found
-no obvious morphology differences between the two classes.  In terms of their
-rotation, relative to the Pleiades, the CQVs are among the more rapidly
-rotating half of M dwarfs.  The dearth of $T$$>$15.5 CQVs in our sample,
-despite our search extending to $T$$=$16, is a consequence of the 120-second
-selection function, not detection sensitivity.
+0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This is a mass
+and age regime that includes fully convective stars
+($M_\star$$\lesssim$0.25\,$M_\odot$), as well as stars with radiative
+cores ($M_\star$$\gtrsim$0.25\,$M_\odot$;
+\citealt{2018A&A...619A.177B}).  We found no obvious morphology
+differences between the two classes.  In terms of their rotation,
+relative to the Pleiades, the CQVs are among the more rapidly rotating
+half of M dwarfs.  The dearth of $T$$>$15.5 CQVs in our sample,
+despite our search extending to $T$$=$16, is a consequence of the
+120-second selection function, not detection sensitivity.
 
@@
 $d$$=$18\,pc), a member of AB Dor.  To our knowledge, this manuscript
-is the first time that it has been noted as a CQV.
-The three
+is the first time that it has been noted as a CQV.  The three
 brightest CQVs are DG~CVn ($T$=9.3), TIC~405754448 ($T$=9.6), and
@@
 The catalog contains a few other stars with similar mass.  Given the
-small number of sub-stellar mass objects in our target sample, 
-future studies of brown dwarf photometric variability
-might also yield CQVs, though there could
-be degeneracies in interpretation with planetary surface features such
-as clouds and latitudinal bands
+small number of sub-stellar mass objects in our target sample, future
+studies of brown dwarf photometric variability might also yield CQVs,
+though there could be degeneracies in interpretation with planetary
+surface features such as clouds and latitudinal bands
 \citep[e.g.][]{2021ApJ...906...64A,2022ApJ...924...68V}.
@@
 \subsection{TIC~435903839}
+
 %TODO: move these to their own ``debunked'' table, I think...
 %TODO: along with the IR excess ones
-TIC~435903839, which we originally classified as an ``ambiguous'' CQV, is an apparently
-similar case.
-We initially labeled this source as having a 10.82\,hr period, because this
-period minimized the dispersion in the phase-folded light curve.
-However closer inspection reveals that this source is a photometric
-blend of two ordinary rotating stars with $P_0$=3.60\,hr, and $P_1$=5.41\,hr.
-This is a novel false positive scenario for CQVs:
-two rapidly-rotating stars with near-integer ratios of rotation periods.
-The beat between the two rotation signals produces the spurious
-CQV signal.
-Such false positives can be excluded through careful accounting of
-all peaks in a periodogram.
-For instance, TIC~435903839 shows a peak at 16.27\,hr, which is not
-an integer multiple of the nominal ``10.82\,hr'' period.
+
+TIC~435903839, which we originally classified as an ``ambiguous'' CQV,
+is an apparently similar case.  We initially labeled this source as
+having a 10.82\,hr period, because this period minimized the
+dispersion in the phase-folded light curve.  However closer inspection
+reveals that this source is a photometric blend of two ordinary
+rotating stars with $P_0$=3.60\,hr, and $P_1$=5.41\,hr.  This is a
+novel false positive scenario for CQVs: two rapidly-rotating stars
+with near-integer ratios of rotation periods.  The beat between the
+two rotation signals produces the spurious CQV signal.  Such false
+positives can be excluded through careful accounting of all peaks in a
+periodogram.  For instance, TIC~435903839 shows a peak at 16.27\,hr,
+which is not an integer multiple of the nominal ``10.82\,hr'' period.
 
 \subsection{CQVs are quasiperiodic}
+
 A periodic signal repeats exactly; the CQVs do not
@@
 able to explore all phase angles with equal weight.  LP 12-502, and
-perhaps other CQVs, seem to have preferred phases.  For LP 12-502,
-all of the dips happen over phases corresponding to only two thirds of
-the period (Figure~\ref{fig:lp}).  The remaining third seems to be
-``out of limits'' for any dipping material.  This could be evidence
-that some aspect the stellar magnetic field is strongly asymmetric,
-and can generate and hold extrinsic material at corotation, but only
-over two thirds of the equatorial circle.  Alternatively, the source
-of the material (e.g. a planetesimal swarm) might be distributed over
-an arc of the same angular extent (240$^\circ$).  We favor the former
+perhaps other CQVs, seem to have preferred phases.  For LP 12-502, all
+of the dips happen over phases corresponding to only two thirds of the
+period (Figure~\ref{fig:lp}).  The remaining third seems to be ``out
+of limits'' for any dipping material.  This could be evidence that
+some aspect the stellar magnetic field is strongly asymmetric, and can
+generate and hold extrinsic material at corotation, but only over two
+thirds of the equatorial circle.  Alternatively, the source of the
+material (e.g. a planetesimal swarm) might be distributed over an arc
+of the same angular extent (240$^\circ$).  We favor the former
 explanation, for reasons discussed below.
@@
 \subsection{Dip asymmetries and dust geometries}
+
 The asymmetry of a dip can help diagnose the optical depth of the
@@
 \subsection{Dust, or gas?}
+
 We believe that the most likely scenarios to explain CQVs are either
@@
 %TODO: improve this to make it less jargony
+
 The difference between the prominence and dust clump scenarios is
@@
 \subsubsection{Gas absorption microphysics}
+
 CQVs show broadband flux variations that can be 1-2$\times$ deeper in
@@
 
-An instructive point of comparison is the rapidly rotating magnetic
-B star, $\sigma$~Ori~E, which shows dips that are deeper in the blue
+An instructive point of comparison is the rapidly rotating magnetic B
+star, $\sigma$~Ori~E, which shows dips that are deeper in the blue
 than in the red \citep{1977ApJ...216L..31H}.  Photometric and
@@
 question of whether the CQVs are explained by dust or by gas, which
-likely has bearing on whether the material producing the dips
-is coming from the star, or whether it is a byproduct of the
+likely has bearing on whether the material producing the dips is
+coming from the star, or whether it is a byproduct of the
 protoplanetary disk.
@@
 %fixed points exist, enable the fixed points to not be located at
-%corotation.
-%In addition, the Balmer absorption line measurements have been used to
-%argue for material being generally located at positions other than
-%just corotation (CHECK Collier-Cameron1989).
+%corotation.  In addition, the Balmer absorption line measurements
+%have been used to argue for material being generally located at
+%positions other than just corotation (CHECK Collier-Cameron1989).
 
 \subsubsection{The lifetime constraint}
+
 Independent of the microphysical basis for gas absorption, the
@@
 the $\approx$700\,Myr age of Praesepe.  This is odd in the context of
-the prominence scenario, because
-pre-main-sequence M dwarfs spin up over the first $\approx$$10^8$\,yr;
-prominences might even be expected to be {\it more} common at the age
-of the Pleiades than for younger stars.  This broadly assumes that any
-star that can support prominences will, and that the magnetic topology
-of rapidly rotating M dwarfs at 100\,Myr is similar to that of 
-rapidly rotating M dwarfs at say, 10\,Myr.  Based on the degree to
-which M dwarfs remain rapid rotators over the first few gigayears
-of their lives
-\citep[e.g.][]{2022AJ....164...80R,2022ApJ...936..109P}, it seems surprising
-in the gas clump (prominence) scenario that very few stars older than
-150\,Myr have been seen to exhibit the phenomenon.  In the dust clump
-scenario this is not a problem, because if the dust were externally
-sourced, it would be expected to have a finite supply.
-
-%\subsubsection{Does the CQV lifetime inform the mechanism?}
-%Independent of the microphysical basis for gas absorption, the
-%prominence scenario may present another issue: why don't stars in the
-%Hyades and Praesepe show the phenomenon?
-%In a broad sense, the prominence scenario argues that an intrinsic
-%stellar process is key for generating the CQV phenomenon.
-%If this were true, then stars of identical mass, size, and rotation
-%periods might be expected to show the phenomenon in equal number,
-%simply because the stellar dynamo is generated by fluid
-%motions inside the star, which should be identical for stars of the
-%same mass, size, and rotation period.
-%
-%Between ages of $\approx$100\,Myr (AB Dor, Pleiades, Psc-Eri) and
-%$\approx$700\,Myr (Praesepe and Hyades), a 0.3\,M$_\odot$ star will
-%shrink by $\approx$10\%, from $\approx$0.33\,R$_\odot$ to 
-%$\approx$0.29\,R$_\odot$ \citep[e.g.][]{2014AJ....147...82C}.
-%This is not a particularly drastic size change.
-%Similarly, at 700\,Myr many M dwarfs have comparably rapid rotation periods 
-%to those at 100\,Myr \citep[e.g. Figure~13 of][]{2022AJ....164...80R};
-%the mean population does show evidence for spin-down after the
-%PMS contraction finishes, but there are still a large number of 
-%700\,Myr M dwarfs with $P_{\rm rot}\lesssim$2\,days, beyond
-%which the CQV phenomenon becomes less common.
-%
-%Broadly speaking -- the absence of old CQVs seems to be
-%more plausibly linked to a gradual depletion of dusty detritus from the
-%planet formation era than it does to the changing stellar properties
-%as the stars gradually finish their pre-main-sequence evolution, and then
-%continue to spin rapidly for many hundreds of millions of years.
+the prominence scenario, because pre-main-sequence M dwarfs spin up
+over the first $\approx$$10^8$\,yr; prominences might even be expected
+to be {\it more} common at the age of the Pleiades than for younger
+stars.  This broadly assumes that any star that can support
+prominences will, and that the magnetic topology of rapidly rotating M
+dwarfs at 100\,Myr is similar to that of rapidly rotating M dwarfs at
+say, 10\,Myr.  Based on the degree to which M dwarfs remain rapid
+rotators over the first few gigayears of their lives
+\citep[e.g.][]{2022AJ....164...80R,2022ApJ...936..109P}, it seems
+surprising in the gas clump (prominence) scenario that very few stars
+older than 150\,Myr have been seen to exhibit the phenomenon.  In the
+dust clump scenario this is not a problem, because if the dust were
+externally sourced, it would be expected to have a finite supply.
 
@@
 
-Close-in planets are common around M-dwarfs;
-studies from Kepler have shown that high-mass
-M  dwarfs have $\approx$0.1 planets per star with sizes between
-1-4\,$R_\oplus$ and orbital periods within 3 days
+Close-in planets are common around M-dwarfs; studies from Kepler have
+shown that high-mass M  dwarfs have $\approx$0.1 planets per star with
+sizes between 1-4\,$R_\oplus$ and orbital periods within 3 days
 \citep{2015ApJ...807...45D}.  The number increases to $\approx$0.7
 planets per star considering planets out to $P$$<$10\,days.
-Extrapolating to all small close-in planets with say
-0.1-4\,$R_\oplus$ and within 10 days, it is reasonable to expect on
-average one close-in planet per M dwarf.  
+Extrapolating to all small close-in planets with say 0.1-4\,$R_\oplus$
+and within 10 days, it is reasonable to expect on average one close-in
+planet per M dwarf.
+
 %TRAPPIST-1b ($P$=1.5\,days) is an
@@
 multiplanet resonant chains migrating inward due to gas drag, the
-inner-most planets therefore arrive at $\approx$5-10 stellar radii before
-the disk becomes depleted.
+inner-most planets therefore arrive at $\approx$5-10 stellar radii
+before the disk becomes depleted.
 
@@
 necessarily drive one toward a picture of a disintegrating
-planetesimal swarm, rather than just a single planetesimal.  
-%While the number of free parameters in this type of model is somewhat
-%dizzying, we have no right to believe that nature need be simple.
-The need for a swarm rather than just one launching body would
-be driven by the observation that we see dips appear and disappear at
-many {\it different phases}, but with roughly the same period.
-The observed changing dip depths in response to flares would be
-understood through the planetesimal outflow rates being stalled by
-changes in the local magnetic field or coronal plasma density.
-The sizes of these purported planetesimals would need to be $\lesssim
-1$\,$R_\oplus$, based on the non-detections of their transits,
-analogous to e.g.  K2-22 \citep{2015ApJ...812..112S} or KOI-2700
+planetesimal swarm, rather than just a single planetesimal.  The need
+for a swarm rather than just one launching body would be driven by the
+observation that we see dips appear and disappear at many {\it
+different phases}, but with roughly the same period.  The observed
+changing dip depths in response to flares would be understood through
+the planetesimal outflow rates being stalled by changes in the local
+magnetic field or coronal plasma density.  The sizes of these
+purported planetesimals would need to be $\lesssim 1$\,$R_\oplus$,
+based on the non-detections of their transits, analogous to e.g.
+K2-22 \citep{2015ApJ...812..112S} or KOI-2700
 \citep{2014ApJ...784...40R}.  Typical sizes of bodies in the asteroid
@@
 There are at least three problems with the idea of a disintegrating
-planetesimal swarm.
-First, this model would predict that certain orbital phases
-would produce recurrent dips if observed over sufficiently long
-baselines, because the launching planetesimal would be massive enough
-to remain in orbit, while stochastically
-ejecting material.  An analogous system might be K2-22.
-For most CQVs (Figure~\ref{fig:evoln}), the data
-seem to be in tension with this expectation.
-A second issue is that many of the dips show asymmetries in the
-wrong direction relative to the naive expectation of a trailing comet
-tail.  Invoking non-exponentially decaying dust distributions as a
-function of azimuth might be one way out of this, but such an idea
-lacks firm theoretical footing.  Finally, dynamical stability is a concern:
-in a model in which any new dip is ``explained''
-by invoking a new planetesimal, one might eventually pack the
-corotation radius to a degree where instability over short timescales
-would be guaranteed.
+planetesimal swarm.  First, this model would predict that certain
+orbital phases would produce recurrent dips if observed over
+sufficiently long baselines, because the launching planetesimal would
+be massive enough to remain in orbit, while stochastically ejecting
+material.  An analogous system might be K2-22.  For most CQVs
+(Figure~\ref{fig:evoln}), the data seem to be in tension with this
+expectation.  A second issue is that many of the dips show asymmetries
+in the wrong direction relative to the naive expectation of a trailing
+comet tail.  Invoking non-exponentially decaying dust distributions as
+a function of azimuth might be one way out of this, but such an idea
+lacks firm theoretical footing.  Finally, dynamical stability is a
+concern: in a model in which any new dip is ``explained'' by invoking
+a new planetesimal, one might eventually pack the corotation radius to
+a degree where instability over short timescales would be guaranteed.
 
@@
 up being connected to the CQV phenomenon, for instance as a possible
-sources for the occulting dust or gas.
-However for the time being, none of the CQVs that we have
-studied in this work show clear evidence for this type of
-origin scenario.
-
-%The dip-profile asymmetries during certain segments of the light curve
-%plausibly match this idea; for instance, the complex in cycles 248-298
-%could be well-fit by a sharp leading edge that decays over 0.2\,$P$
-%(3.7\,hours).  The earlier complex, during cycles 248-264
-%(pre-state-switch), could be fit by a similar profile.
-
-%There are two degenerate explanations for the small
-%``wiggles'' in the exponential decay.  In one explanation, the decay
-%timescale is fast ($\approx$0.03\,$P$), and there are up to five
-%exocomets, superposed.  In the other, there is only one main
-%``launching body'', and the material it ejects either has some
-%sub-structure, or else is passing across (and in synchronicity with) a
-%star with heavily substructured starspots across its surface.
-
-%Every dip in such a model would have as free parameters the dip phase,
-%the duration (captured by an exponential decay timescale), and the dip
-%depth.  In detail, the impact parameter would also enter.  Allotting
-%four free parameters per dip yields up to 32 free parameters for the
-%light curve at the most complicated times (assigning one exocomet per
-%local minimum).
-
-%It seems
-%challenging to reconcile this behavior with the possible presence of
-%just a single launching body.  Finally, the fact that the dips often
-%respond to events like flares suggests that that the responsible
-%material be much less massive than a 1--100\,km sized planetesimal,
-%and therefore more easily influenced by the stellar magnetic field.
-
-%  % TODO: needed??
-%  {\sc Some CQVs require external occulters}
-%  (rehash Bodman2017 timescale arguments)
-
-%{\sc Each CQV a snowflake?}
-%An intriguing aspect of Figure~\ref{fig:cqvs} is that very few CQVs
-%exhibit exactly identical light curve morphology.
-%There are of course similarities.
-%TIC 272248916 and TIC 442571495 match.
-%But overall, they all different.
-
-% \paragraph{Predicting the future, given the past}
-% Figure~\ref{fig:evoln}
-% shows that for 21 CQVs that were observed roughly two years
-% apart, 5 showed obvious signs of the phenomenon in one sector,
-% and marginal or non-existence signs in the other.
-% We emphasize that the periods themselves were usually stable to $<$0.1\%.
-% However, this shape evolution
-% suggests that CQVs have a duty cycle of $\approx$75\%.
-
-% \paragraph{Why would the prominence scenario tend toward corotation?}
-% This is analogous to quiescent
-% prominences on the Sun \citep{1967SoPh....2...39K}.
+sources for the occulting dust or gas.  However for the time being,
+none of the CQVs that we have studied in this work show clear evidence
+for this type of origin scenario.
 
@@
 
-In identifying the two ambiguous CQVs with outlying SEDs (TICs~193136669 and
-TIC~57830249; Section~\ref{subsec:irexcess}), we were prompted to reconsider our light curve-based
-labeling, and ultimately concluded that these sources are dippers.  This
-episode suggests that there could be overlap between CQVs and dippers.
-It is also worth emphasizing that our labeling of e.g.~TIC~57830249
-was based on a single sector of TESS data (Sector~36) when its
-behavior is relatively periodic and it showed dip depths of a few
-percent.  However in other TESS sectors (e.g. Sector~10), this source
-looks completely different, varying in apparent flux by a factor of
-two, with hardly any discernible periodicity at all.
+In identifying the two ambiguous CQVs with outlying SEDs
+(TICs~193136669 and TIC~57830249; Section~\ref{subsec:irexcess}), we
+were prompted to reconsider our light curve-based labeling, and
+ultimately concluded that these sources are dippers.  This episode
+suggests that there could be overlap between CQVs and dippers.  It is
+also worth emphasizing that our labeling of e.g.~TIC~57830249 was
+based on a single sector of TESS data (Sector~36) when its behavior is
+relatively periodic and it showed dip depths of a few percent.
+However in other TESS sectors (e.g. Sector~10), this source looks
+completely different, varying in apparent flux by a factor of two,
+with hardly any discernible periodicity at all.
 
@@
 
-%The concordance model for planet formation invokes the presence of an
-%accretion disk.  The innermost regions of the disk are located at the
-%magnetospheric truncation radius, which happens to often
-%coincidentally be at the Keplerian corotation radius ({\bf lgb: careful...}).  In such a
-%scenario, planetesimals and boulders can migrate inward due to Type X
-%migration (CITE), until they hit a ``dust trap'' at the inner wall
-%(CITE eg Kama2009,and related).  Support for this model comes from the
-%rotation periods of classical and weak-lined T Tauri stars (CITE
-%Rebull2018,2019); from near-infrared interferometric observations that
-%detect thermal emission from the disk wall (CITE CITE); and from the
-%turn-over in the exoplanet orbital period distribution, which occurs
-%around 5-10 days for FGK stars, and perhaps even closer-in for
-%M dwarfs (CITE Petigura2022, and CITE for M dwarfs).
-%
-%Broadly, the existence of a dust trap at the disk truncation radius
-%might be expected to trap larger boulders as well.  Once the disk
-%loses the gas, what happens to those boulders?  They are no longer
-%shielded.  We then enter a phase of mass loss.  Perhaps that phase is
-%what we are observing.
-
 \subsection{Are half-cycles important?}
@@
 context of CQVs for two reasons.  The first is that for material on a
-circular orbit viewed edge-on, a half-cycle corresponds to the interval between
-transit and secondary eclipse.  The second is that the half-cycle also corresponds
-to the interval over which half of the star's surface is visible.  Of
-the CQVs in Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, a fraction that
-seems greater than random might exhibit a preference for showing dips
-or peaks that correspond to the half-cycle interval.
+circular orbit viewed edge-on, a half-cycle corresponds to the
+interval between transit and secondary eclipse.  The second is that
+the half-cycle also corresponds to the interval over which half of the
+star's surface is visible.  Of the CQVs in Figures~\ref{fig:cqvs}
+and~\ref{fig:evoln}, a fraction that seems greater than random might
+exhibit a preference for showing dips or peaks that correspond to the
+half-cycle interval.
 
@@
 between July~2018 and Sep~2022 for complex quasiperiodic variables
-(CQVs).  The target stars were \nstarssearched\ K and M dwarfs
-within 150\,pc.  The selection function was $>$$80\%$ complete within 30\,pc,
+(CQVs).  The target stars were \nstarssearched\ K and M dwarfs within
+150\,pc.  The selection function was $>$$80\%$ complete within 30\,pc,
 and $<$$10\%$ complete at distances exceeding 100\,pc.
@@
 In our target sample, we found \ngoods\ objects that showed complex
-quasiperiodic behavior over at least one TESS sector.  
-These \ngoods\ bonafide
-CQVs are listed in Table~\ref{tab:thetable}.  This table also includes
-an additional \nmaybes\ ambiguous CQVs, whose designation is less
-certain.
-We inferred ages for all but two of the \ncpvsfound\ objects based on association
-memberships; we also derived temperatures and radii using SED fitting,
-and then inferred stellar masses by
-interpolating against stellar evolutionary models.
-We caution that our selection function was not volume-limited:
-the
-TESS 120-second stellar sample had a heterogeneous selection
-function which may have been biased in favor of young stars over field
-stars.
-Previous work however has shown that $\approx$1-3\% of M dwarfs
-younger than $\approx$100\,Myr show the CQV phenomenon
+quasiperiodic behavior over at least one TESS sector.  These \ngoods\
+bonafide CQVs are listed in Table~\ref{tab:thetable}.  This table also
+includes an additional \nmaybes\ ambiguous CQVs, whose designation is
+less certain.  We inferred ages for all but two of the \ncpvsfound\
+objects based on association memberships; we also derived temperatures
+and radii using SED fitting, and then inferred stellar masses by
+interpolating against stellar evolutionary models.  We caution that
+our selection function was not volume-limited: the TESS 120-second
+stellar sample had a heterogeneous selection function which may have
+been biased in favor of young stars over field stars.  Previous work
+however has shown that $\approx$1-3\% of M dwarfs younger than
+$\approx$100\,Myr show the CQV phenomenon
 \citep{2016AJ....152..114R,2022AJ....163..144G}.
 
-Analyzing the TESS light curves and stellar properties of our
-CQVs, we draw the following conclusions.
+Analyzing the TESS light curves and stellar properties of our CQVs, we
+draw the following conclusions.
 
@@
 	%
-	\item CQVs are quasiperiodic.  The mean periods remain fixed over the
-		$>$1{,}000-cycle baseline of available observations; but the light curve shapes
-		always evolve (Figure~\ref{fig:evoln}).
+  \item CQVs are quasiperiodic.  The mean periods remain fixed over
+    the $>$1{,}000-cycle baseline of available observations; but the
+    light curve shapes always evolve (Figure~\ref{fig:evoln}).
   %
-  \item The same CQV can show multiple periods simultaneously.
-     LP 12-502, for instance, showed dips with four
-    distinct periods within $\pm 0.3\%$ of its fundamental period,
-    sometimes simultaneously, and each lasting for up to 50 cycles
+  \item The same CQV can show multiple periods simultaneously.  LP
+    12-502, for instance, showed dips with four distinct periods
+    within $\pm 0.3\%$ of its fundamental period, sometimes
+    simultaneously, and each lasting for up to 50 cycles
     (Figure~\ref{fig:lpriver0}).
@@
     \item CQVs evolve over timescales that are both secular
-    ($>$100\,cycles) and impulsive ($<$1 cycle).  
-    Dip growth seems to happen over durations of at least ten cycles, and slow dip decay can also occur.
-    ``State-switches''
-    correspond to dips to collapsing instantaneously, and are almost always
-    linked with observed optical flares.
-    This suggests that the occulting material is responding to sudden changes
-    in the magnetic field.
+      ($>$100\,cycles) and impulsive ($<$1 cycle).  Dip growth seems
+      to happen over durations of at least ten cycles, and slow dip
+      decay can also occur.  ``State-switches'' correspond to dips to
+      collapsing instantaneously, and are almost always linked with
+      observed optical flares.  This suggests that the occulting
+      material is responding to sudden changes in the magnetic field.
   %
-    \item The rate of dip evolution can be used to place a model-dependent
-    constraint on how much material is either being accreted or ejected
-    during the state changes (Section~\ref{subsec:massflux}).
-    Order of magnitude estimates require at least an asteroid belt's worth
-    of dust ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or 100 times more 
+    \item The rate of dip evolution can be used to place a
+      model-dependent constraint on how much material is either being
+      accreted or ejected during the state changes
+      (Section~\ref{subsec:massflux}).  Order of magnitude estimates
+      require at least an asteroid belt's worth of dust
+      ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or 100 times more
       material if the occulting matter is gas.
@@
     Psc-Eri (Section~\ref{subsec:starprops}).  It may even extend to
-    200\,Myr, based on the one CQV we found in the Carina Near
-    moving group (TIC~294328887; $\approx$200\,Myr).  The lack of
+    200\,Myr, based on the one CQV we found in the Carina Near moving
+    group (TIC~294328887; $\approx$200\,Myr).  However the lack of
     detected CQVs in the Hyades and Praesepe suggests that the
-    lifetime of the phenomenon is likely limited to the first few
-    hundred million years.
+    lifetime of the phenomenon is limited to the first few hundred
+    million years.
 	%
-    \item The duty cycle for CQVs seems to be $\approx$$75$\%, based on
-    the fraction of bonafide CQVs that either turned on or turned off during
-    TESS re-observations, two years after the initial observation.
+    \item The duty cycle for CQVs seems to be $\approx$$75$\%, based
+      on the fraction of bonafide CQVs that either turned on or turned
+      off during TESS re-observations, two years after the initial
+      observation.
   %
@@
   %
-    \item The closest CQVs to the Sun are at distances of 15-20\,pc, and
-    the brightest have $V$$\approx$12 ($J$$\approx$7.5).  This
-    conclusion is an extrapolation from the CQV sample derived in this work
-    being $\gtrsim$80\% complete within 30\,pc.  Expanding our analysis of
-    the TESS data to the full frame images would yield a truly
-    volume-limited selection function, and would expand the CQV census
-    by about a factor of two within 50\,pc, and by a factor of ten
-    within 100\,pc.
+    \item The closest CQVs to the Sun are at distances of 15-20\,pc,
+      and the brightest have $V$$\approx$12 ($J$$\approx$7.5).  This
+      conclusion is an extrapolation from the CQV sample derived in
+      this work being $\gtrsim$80\% complete within 30\,pc.  Expanding
+      our analysis of the TESS data to the full frame images would
+      yield a truly volume-limited selection function, and would
+      expand the CQV census by about a factor of two within 50\,pc,
+      and by a factor of ten within 100\,pc.
 \end{enumerate}
 
-While many questions remain, two in particular will be 
-important for clarifying what these objects might teach us in a
-broader astrophysical context: {\it 1)} Is the eclipsing material
-responsible for the phenomenon gas or dust?  {\it 2)} What sets
-the characteristic clumping size for the circumstellar material?
+While many questions remain, two in particular will be important for
+clarifying what these objects might teach us in a broader
+astrophysical context: {\it 1)} Is the eclipsing material responsible
+for the phenomenon gas or dust?  {\it 2)} What sets the characteristic
+clumping size for the circumstellar material?
 
@@
 comes from the star, or extrinsic, so that it is sourced through some
-generic evolutionary phase of circumstellar disks.
-This knowledge would in
-turn propagate to our understanding of whether the
-phenomenon is primarily teaching us about dust production and
-processing in circumstellar disks, or whether it is teaching us about
-the ability of cold gas to remain stable in hot stellar coronae for
-long durations.
+generic evolutionary phase of circumstellar disks.  This knowledge
+would in turn propagate to our understanding of whether the phenomenon
+is primarily teaching us about dust production and processing in
+circumstellar disks, or whether it is teaching us about the ability of
+cold gas to remain stable in hot stellar coronae for long durations.
 Observationally, acquisition of medium- or high-resolution time-series
-spectra holds the best chance at resolving the gas vs.~dust
-question.  Given the observed evolutionary timescales, such data
-should be acquired simultaneously with photometric time-series
-observations to help clarify its interpretation.
+spectra holds the best chance at resolving the gas vs.~dust question.
+Given the observed evolutionary timescales, such data should be
+acquired simultaneously with photometric time-series observations to
+help clarify its interpretation.
 
@@
 inclination, roughly one third of low mass stars
-\citep{2022AJ....163..144G} could trap circumstellar material in the same
-way.  It also suggests that CQVs may preferentially show
-transiting planets at larger distances than the corotating material, though
-this may be dependent on whether the magnetic and stellar
-spin axes tend to be aligned.  Given these points, observational follow-up
-work should include searching for outer transiting planets,
-and measuring equatorial velocities in order to test whether the
-stellar inclination angles are indeed preferentially edge-on.
+\citep{2022AJ....163..144G} could trap circumstellar material in the
+same way.  It also suggests that CQVs may preferentially show
+transiting planets at larger distances than the corotating material,
+though this may be dependent on whether the magnetic and stellar spin
+axes tend to be aligned.  Given these points, observational follow-up
+work should include searching for outer transiting planets, and
+measuring equatorial velocities in order to test whether the stellar
+inclination angles are indeed preferentially edge-on.
 
@@
 \acknowledgments
-LGB gratefully acknowledges support from the
-Heising-Simons 51~Pegasi~b Fellowship.
-While many conversations helped encourage this work,
-a few thank-yous in particular (from LGB) 
-are owed to G.~Laughlin, A.~Mann, and J.~Spake for clarifications and ideas.
-This paper relies on data collected by the TESS mission, which are publicly available from the Mikulski Archive for Space Telescopes (MAST).
-Funding for the TESS mission is provided by NASA’s Science Mission Directorate.
-TIC 402980664 in particular was observed at 120-second cadence thanks to the TESS Guest
-Investigator programs G022252 (PI: J.~Schlieder; Sectors 18, 19, 25,
-26) and G04168 (PI: R.~Jayaraman; Sector 53).
-
-{\bf DRAFT AUTHOR CONTRIBUTION STATEMENTS -- PLEASE REVISE IF 
-	APPROPRIATE)}
-LGB~and RJ conceived the project and executed the
-dip-based and Fourier-based searches, respectively.
-LGB~drafted the initial manuscript, and performed the cluster
-membership, SED, and variability analyses.
+LGB gratefully acknowledges support from the Heising-Simons
+51~Pegasi~b Fellowship.  While many conversations helped encourage
+this work, a few thank-yous in particular (from LGB) are owed to
+G.~Laughlin, A.~Mann, and J.~Spake for clarifications and ideas.  This
+paper relies on data collected by the TESS mission, which are publicly
+available from the Mikulski Archive for Space Telescopes (MAST).
+Funding for the TESS mission is provided by NASA’s Science Mission
+Directorate.  TIC 402980664 in particular was observed at 120-second
+cadence thanks to the TESS Guest Investigator programs G022252 (PI:
+J.~Schlieder; Sectors 18, 19, 25, 26) and G04168 (PI: R.~Jayaraman;
+Sector 53).
+
+{\bf AUTHOR CONTRIBUTION STATEMENTS: PLEASE REVISE IF APPROPRIATE)}
+LGB~and RJ conceived the project and executed the dip-based and
+Fourier-based analyses, respectively.
 SR and RJ vetted the results from the Fourier search.
-LAH advised on project scope and experiment design.
+LGB performed the cluster membership, SED, and variability analyses.
+LR contributed an independent SED analysis, and cross-checked the
+variability analyses.
 AD identified the magnetic B star connection.
+LAH contributed to data analysis and interpretation.
 G\'AB acquired and maintained the servers used to run the dip-finding
@@
 GRR is an architect of the TESS mission.
-All authors assisted in manuscript revision.
+All authors assisted in manuscript writing and revision.
 
@@
     longer than three hours.
+    Cycle numbers are listed in the lower-right of each light curve segment.
 	}

### 2023-08-12 paper/ms.tex
add Nakajima+1985
ms: improve intro

@@
 with dust
-\citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
+\citep{2017PASJ...69L...2O,2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
 And finally, while the dip shapes can ``jump'' between different
@@
 
+The CQV light curves cannot be explained by pure starspots.  Although
+all young M dwarfs are spotted, this tends to produce flux variations
+over characteristic timescales of the rotation period, $P_{\rm rot}$,
+and its half-harmonic, $0.5\,P_{\rm rot}$.  If one fine-tunes the
+viewing geometry, starspots can produce dips with durations as short
+as $\approx$$0.2\,P_{\rm rot}$, and the dip amplitudes quickly
+decrease due to limb-darkening (see \citealt{2017AJ....153..152S},
+Figures 37-41).  The observed dips in CQVs can happen over durations as
+short as $0.05\,P_{\rm rot}$ with characteristic depths of a few
+percent; a ``starspot-only'' scenario can be discarded for any object
+with dips that are sufficiently deep and short in duration
+\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The timescales and
+amplitudes of the flux variations in such objects instead require
+sharp geometries with material extrinsic to the stellar surface
+\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  Since the
+entire class of star is probably part of the same phenomenon, we
+therefore generally discard the ``spot-only'' scenario.
+
 A few competing explanations for what causes the complex quasiperiodic
-variability are shown in Figure~\ref{fig:f1}.  All young M dwarfs are
-spotted, which produces flux variations over characteristic timescales
-of the rotation period, $P_{\rm rot}$, and its half-harmonic,
-$0.5\,P_{\rm rot}$.  The observed dips occur over durations as short
-as $0.05\,P_{\rm rot}$; a ``starspot-only'' scenario can be discarded
-for any object with sufficiently sharp dips
-\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The timescales and
-amplitudes of the flux variations instead require sharp geometries
-with material extrinsic to the stellar surface
-\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  The
-``clump'' scenario invokes opaque dust clumps orbiting near the
-Keplerian corotation radius, which periodically eclipse the star
+variability are shown in Figure~\ref{fig:f1}.  The ``clump'' scenario
+invokes opaque dust clumps orbiting near the Keplerian corotation
+radius, which periodically eclipse the star
 \citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The ``prominence''
@@
     TIC 425933644 (Sector~28).
-    {\it Bottom:} Cartoon models for the phenomenon.  The dust clump
+    {\it Bottom:} Cartoon explanations for the phenomenon.  The dust clump
     scenario (lower left) and prominence scenario (lower center) both
@@
 geometries we are discussing for much cooler M dwarfs
-\citep{1978ApJ...224L...5L,2005ApJ...630L..81T}.  This material
+\citep{1978ApJ...224L...5L,1985Ap&SS.116..285N,2005ApJ...630L..81T}.  This material
 however is unlikely to be dust, due to the relevant sublimation
@@
 bound-free absorption from neutral hydrogen
-\citep{2005ApJ...630L..81T}, although to our best knowledge direct
+\citep{1985Ap&SS.116..285N}, although to our best knowledge direct
 evidence for this conclusion has yet to be acquired.  Separate and
@@
 %\subsubsection{Why corotation?}
-%All of the prominence models, and the diagrams of where the magnetic
-%fixed points exist, enable the fixed points to not be located at
-%corotation.  In addition, the Balmer absorption line measurements
-%have been used to argue for material being generally located at
-%positions other than just corotation (CHECK Collier-Cameron1989).
+% The stable point only exists if R_A > R_K.
+For radii between R_A and R_K in such cases, consider a magnetic field line extending out beyond R_K.
+Whenever R>R_K, the material is centrifugally supported (pushed out by the ~Ω^2R^2 centrifugal term in the corotating frame).
+If R<R_K in such cases along a given field line, the material will fall back to the star.
+So there are two conditions that must be met: the star must spin fast enough, and closed magnetic loops must extend beyond the corotation radius.
+(This is all spelled out by Nakajima1985, and Petit2013).
 

### 2023-08-12 paper/ms.tex
update ms

@@
 CQVs should not be conflated with ``dippers'', which are classical T
-Tauri stars with infrared excesses, and large-amplitude variability
+Tauri stars with infrared excesses, and which show large-amplitude variability
 linked to obscuring inner disk structures and accretion hot spots
-\citep{2014AJ....147...82C,2021ApJ...908...16R}.  With that said, a
-few similarities between CQVs and dippers do exist (see
-Sections~\ref{subsec:irexcess} and~\ref{subsec:discdippers}).  At the
-risk of introducing yet another standard, we hope to introduce a
+\citep{2014AJ....147...82C,2021ApJ...908...16R}.  While a few
+similarities between CQVs and dippers do exist (see
+Sections~\ref{subsec:irexcess} and~\ref{subsec:discdippers}), their
+phenomenology and stellar properties are quite different.  At the
+risk of introducing yet another standard, we hope to use a
 nomenclature that reflects how, when observed over timescales of more
@@
 they are all explained by a single underlying phenomenon, and so we
-opt to refer to them by a single empirically descriptive name.
+opt to refer to them by a single empirically descriptive name.  We
+also considered names that focused on the presence of transient
+corotating clumps, or more generally on circumstellar plasma tori;
+for the time being, ``CQV'' seems to more accurately mirror the state
+of our ignorance.
 
@@
 
+%\begin{figure*}[!t]
+%	\begin{center}
+%		\includegraphics[width=0.45\textwidth]{ANNOTATED_resid_TIC_402980664_P18.5611_2min_phase_timegroups.png}
+%	\end{center}
+%	\vspace{-0.4cm}
+%	\caption{
+%		{\bf Alternative view of the evolution of LP 12-502}
+%		(Figure~\ref{fig:lp}), arranged to emphasize changes in transit
+%		times.  There are 200 binned black points per $P$=18.5611\,hr cycle; a two-harmonic
+%		sinusoid has been subtracted from the PDC\_SAP light curve.
+%		Vertical gray lines are underplotted to help guide the eye to instances
+%		in which preferred dip phases synchronize over long baselines.
+%		The orange and green lines guide the eye to where dips
+%		change the positions of their local minima; orange
+%		lines have periods slightly less than $P$, the green line has
+%		a period greater than $P$.
+%	}
+%	\label{fig:lp2}
+%\end{figure*}
+
+\begin{figure*}[!t]
+	\begin{center}
+		\subfloat{
+			\includegraphics[width=0.48\textwidth]{f10a.pdf}
+			\includegraphics[width=0.48\textwidth]{f10b.pdf}
+		}
+	   \vspace{-0.1cm}
+
+		\subfloat{
+			\includegraphics[width=0.48\textwidth]{f10d.pdf}
+			\includegraphics[width=0.48\textwidth]{f10c.pdf}
+		}
+	\end{center}
+	\vspace{-0.4cm}
+	\caption{
+		{\bf River plots of the LP 12-502 light curve}, showing (clockwise from top-left)
+		Sectors 18-19, 25-26, 53, and 58-59.  A two-harmonic sinusoid has
+		been subtracted to highlight the sharp dips.
+		In Sectors 25-26 (cycles 248-315), periods are visible at the fundamental
+		period of 18.5611\,hr, as well as at faster and slower relative periods (e.g. $\phi$$\approx$0.3 and $\phi$$\approx$0.1).
+		Similar instances of multiple simultaneous periods are also visible in
+		Sector 53 and 58-59.
+%		$P$=18.5611\,hr (gray vertical line); 18.5404\,hr (orange); 18.5683\,hr (green).
+%		For Sector 53, gray is identical, while cyan is 18.5145\,hr.
+%		For Sectors 58-59, the magenta line is 18.5473\,hr, and the green
+%		line is 18.5672\,hr.
+		White chunks denote missing data.
+	}
+	\label{fig:lpriver0}
+\end{figure*}
+
 Out of the \ngoods\ CQVs, a small fraction were in regions of sky with
@@
 successive TESS orbits spanning half a lunar month each.
+Finally, Figure~\ref{fig:lpriver0} shows ``river plots'' of the
+same data, split into similar intervals:
+the Sector 18-19 data, 25-26 data, 53 data, and 58-59 data.
+The river plots are slightly more processed:
+a maximum-likelihood two-harmonic sinusoid has been independently fitted and
+subtracted from the Sector 18-19 data, 25-26 data, and 53, 58, and 59
+data in order to accentuate any changes in the dip timing and structure.
 
@@
 complexes; this feature is best visualized on the river plots
-(Appendix~\ref{app:lp}), and we discuss its (shorter) period below.
+(Figure~\ref{fig:lpriver0}), and we describe its (shorter) period below.
 
@@
 of a period, punctuated by coherent local minima and maxima which in
-detail (Appendix~\ref{app:lp}) have slightly longer periods than the
+detail (Figure~\ref{fig:lpriver0}) have slightly longer periods than the
 sharp dip.  The sharp leading dip only decreases in depth following a
@@
 its depth and duration), while the trailing two dips remained fixed.
+This is visible in Figure~\ref{fig:lp}.
 In other words, the structures producing these dips are independent to
@@
 $P=18.5611 \pm 0.0001$\,hr.  However the river plots
-(Appendix~\ref{app:lp}) reveal multiple distinct periodicities in the
+(Figure~\ref{fig:lpriver0}) reveal multiple distinct periodicities in the
 light curve for specific dips.  For instance, in sectors 25-26, the
@@
 18.5683, 18.5672, 18.5473, and 18.5145\,hr, with a typical measurement
-uncertainty of $\approx$0.0002\,hr.  If each period corresponds to a
-dust clump, then this implies that multiple distinct clumps can orbit
+uncertainty of $\approx$0.0002\,hr.  If each period corresponds to an
+individual dust or gas clump, then this implies that multiple distinct clumps can orbit
 the star simultaneously, at marginally different separations.
@@
 
-Figure~\ref{fig:catalogscatter} shows some of the derived properties
+Figure~\ref{fig:catalogscatter} shows some of the derived stellar properties
 for our CQV catalog, and compares them against both the target star
@@
 \citep{2016AJ....152..114R}.  Typical CQV masses span
-0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This is a mass
-and age regime that includes fully convective stars
-($M_\star$$\lesssim$0.25\,$M_\odot$), as well as stars with radiative
-cores ($M_\star$$\gtrsim$0.25\,$M_\odot$;
+0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This is mass
+and age includes both fully convective stars
+($M_\star$$\lesssim$0.25\,$M_\odot$), and stars with a combination of radiative
+cores and convective envelopes ($M_\star$$\gtrsim$0.25\,$M_\odot$;
 \citealt{2018A&A...619A.177B}).  We found no obvious morphology
@@
 \citep{2017AJ....153..152S,2022AJ....163..144G}.  TIC~405754448 and
-TIC~405910546 however appear to have masses of $\approx$0.82 and
+TIC~405910546 however appear to have masses of $\approx$0.82\,$M_\odot$ and
 $\approx$0.60\,$M_\odot$ respectively.  The next-highest masses in our
@@
 sinusoidal envelope with a peak-to-peak amplitude of 2.5\%, and with
-three sharp dips super-posed over each cycle.  The Gaia DR3 RUWE for
-TIC~425937691 is 2.9.
+three sharp dips super-posed over each cycle.  For
+TIC~425937691, ${\rm RUWE}_{\rm DR3}=2.9$.
 
@@
 
-\section{LP 12-502}
-\label{app:lp}
-
-{\it The light curve}---
-Figure~\ref{fig:lp2} shows another alternative view of
-Figure~\ref{fig:lp}, but arranged to enable easy visual appreciation
-of transit timing changes, rather than transit depth changes.  A
-best-fitting two-harmonic sinusoid has been independently fitted and
-subtracted from the Sector 18-19 data, 25-26 data, and 53, 58, and 59
-data.
-
-Finally, Figure~\ref{fig:lpriver0} shows ``river plots'' of the
-same data, split into similar intervals:
-the Sector 18-19 data, 25-26 data, 53 data, and 58-59 data.
-State changes are evident in these plots whenever there is a sudden
-change in color.
-{\bf todo: fix missing data to be different from the flare color}
-
-\begin{figure*}[!t]
-	\begin{center}
-    \includegraphics[width=0.45\textwidth]{ANNOTATED_resid_TIC_402980664_P18.5611_2min_phase_timegroups.png}
-    	\end{center}
-    \vspace{-0.4cm}
-		\caption{
-	      {\bf Alternative view of the evolution of LP 12-502}
-	      (Figure~\ref{fig:lp}), arranged to emphasize changes in transit
-	      times.  There are 200 binned black points per $P$=18.5611\,hr cycle; a two-harmonic
-	      sinusoid has been subtracted from the PDC\_SAP light curve.
-	      Vertical gray lines are underplotted to help guide the eye to instances
-	      in which preferred dip phases synchronize over long baselines.
-	      The orange and green lines guide the eye to where dips
-	      change the positions of their local minima; orange
-        lines have periods slightly less than $P$, the green line has
-        a period greater than $P$.
-		}
-		\label{fig:lp2}
-\end{figure*}
-
-\begin{figure*}[!t]
-	\begin{center}
-		\subfloat{
-			\includegraphics[width=0.43\textwidth]{TIC402980664_river_gist_stern_0_64_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
-			\includegraphics[width=0.43\textwidth]{ANNOTATED_TIC402980664_river_gist_stern_248_315_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
-		}
-	\vspace{-1cm}
-			\subfloat{
-		\includegraphics[width=0.43\textwidth]{ANNOTATED_TIC402980664_river_gist_stern_1411_1481_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
-				\includegraphics[width=0.43\textwidth]{ANNOTATED_TIC402980664_river_gist_stern_1233_1265_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
-	}
-	\end{center}
-	\vspace{-0.4cm}
-	\caption{
-    {\bf River plots of LP 12-502}, showing (clockwise from top-left)
-    Sectors 18-19, 25-26, 53, and 58-59.  A two-harmonic sinusoid has
-    been subtracted over specific chunks in time ({\bf see text}).
-    For Sectors 25-26 (cycles 248-315), three periods are overplotted:
-    $P$=18.5611\,hr (gray vertical line); 18.5404\,hr (orange); 18.5683\,hr (green).
-    For Sector 53, gray is identical, while cyan is 18.5145\,hr.
-    For Sectors 58-59, the magenta line is 18.5473\,hr, and the green
-    line is 18.5672\,hr.
-	}
-	\label{fig:lpriver0}
-\end{figure*}
-
 \section{TIC~300651846}
@@
 continuous viewing zone.  If it were not for the existence of
-TIC~402980664, this source would likely have been the subject of
-greater attention.  With the exception of a few sectors, TESS data
-will exist for TIC~300651846 over Sectors 1-12, 27-39, and 61-69.
-While most of the available data will exist in the full frame images,
-in Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river}
-focus only on the 120-second cadence data.
+TIC~402980664, this source would probably have received greater
+attention.  With the exception of a few sectors, TESS data will exist
+for TIC~300651846 for at least Sectors 1-12, 27-39, and 61-69.  While most of
+the available data will exist in the full frame images, in
+Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river} focus
+only on the currently available 120-second cadence data.
 
@@
 $\approx$50-100 cycles seem to be the norm for TIC~300651846.
+Unlike the TIC~402980664 river plots (Figure~\ref{fig:lpriver0}), we
+did not subtract any ``continuum sinusoid'' for this source, because
+the continuum is not as obviously defined.
 
@@
 		\subfloat{
-			\includegraphics[width=0.43\textwidth]{f11a.pdf}
-			\includegraphics[width=0.43\textwidth]{f11b.pdf}
+			\includegraphics[width=0.48\textwidth]{f11a.pdf}
+			\includegraphics[width=0.48\textwidth]{f11b.pdf}
 		}
@@
 	\caption{
-		{\bf Long-term evolution of TIC 300651846}.
-    All available 120-second cadence data as of 11 August 2023 are shown.
+		{\bf Light curve evolution of TIC 300651846}.
+    All available 120-second cadence data as of 2023 Aug 11 are shown.
     Cycles 0 to 622 span TESS Sectors 32-39 (Nov 2020--June 2021);
@@
 		\subfloat{
-			\includegraphics[width=0.43\textwidth]{TIC300651846_river_seismic_0_650_vmin-0.06000_vmax0.06000.png}
-			\includegraphics[width=0.43\textwidth]{TIC300651846_river_seismic_2305_2630_vmin-0.06000_vmax0.06000.png}
+			\includegraphics[width=0.48\textwidth]{f12a.pdf}
+			\includegraphics[width=0.48\textwidth]{f12b.pdf}
 		}
@@
 		{\bf River plots of TIC 300651846}.
-		The envelope has not been subtracted.
-		7 sectors of continuous 2-minute observations S32-S39.  (Thanks to DDT029)
-		Then a few in S60+ on the right.
-		Compare to Figure~\ref{fig:cqvs}.
+    This is an alternative visualization of the data in
+    Figure~\ref{fig:tic3006timegroups}.
+    All available 120-second cadence data as of 2023 Aug 11 are shown.
+    Cycles 0 to 622 span TESS Sectors 32-39 (Nov 2020--June 2021);
+    cycles 2296-2676 span Sectors 61-65 (Jan--June 2023).  We assumed
+    $P$$=$8.254\,hr and $t_0$=2174.127 [BTJD].
+    Note that the two panels have slightly different color scales.
 	}
@@
 power at timescales of a few minutes
-\citep{127Z,2020AJ....160...86B,2022AJ....163..144G}.  This advance
-was primarily enabled by the fifteen-fold faster cadence in the TESS
-2-minute data, relative to K2.
-
-A logical follow-up question to ask is whether the periodic components
-of the CQV light curves contain power at timescales below one minute.
-Between 2020 and 2021, we observed 10 CQVs at 20-second cadence with
-TESS in order to explore this question (TESS DDT029).  The stars were
-TICs 142173958, 146539195, 24518895, 276453848, 264599508, 363963079,
-144486786, 408188366, 300651846, 262400835.  The general conclusion
-derived from comparing the 20-second to 120-second data for these
-stars (available on MAST) was that CQVs do not contain appreciable
-power at this timescale.
+\citep{2019A&A...625L..13Z,2022AJ....163..144G}.  This advance was
+enabled by the fifteen-fold faster cadence in the TESS 2-minute data,
+relative to K2.  A logical follow-up is to ask whether the periodic
+components of the CQV light curves contain power at timescales below
+one minute.  Between 2020 and 2021, we observed 10 CQVs at 20-second
+cadence with TESS in order to explore this question (TESS DDT029).
+The stars were TICs 142173958, 146539195, 24518895, 276453848,
+264599508, 363963079, 144486786, 408188366, 300651846, 262400835.
+These sources were selected from CQVs known at the time to have short
+periods and sharp features when observed at 2-minute cadence.
+Comparing the 20-second to 120-second data for these stars (data
+available on MAST), we concluded that these CQVs did not contain
+appreciable power at timescales shorter than a few minutes.
 

### 2023-08-12 paper/collect.sh

@@ -1,4 +1,4 @@
-resultsdir="/Users/luke/Dropbox/proj/cpv/results/"
+resultsdir="/Users/luke/Dropbox/proj/cpv/results"
 addir="/Users/luke/Dropbox/Documents/proposals/2023_05_ADAP/latex/figs/"
 
 # fig1
@@ -26,6 +26,13 @@ cp $resultsdir/magnetic_bstar_comparison/magnetic_bstar_comparison_showtitles_co
 cp $resultsdir/magnetic_bstar_comparison/magnetic_bstar_comparison_showtitles_complexM.pdf f8c.pdf
 
 # appendix
+cp $resultsdir/river/TIC_402980664/TIC402980664_river_gist_stern_truncated_-1_64_manual_20230617_mask_v0_nterms2_vmin-4.00000_vmax1.00000.pdf f10a.pdf
+cp $resultsdir/river/TIC_402980664/TIC402980664_river_gist_stern_truncated_248_315_manual_20230617_mask_v0_nterms2_vmin-4.00000_vmax1.00000.pdf f10b.pdf
+cp $resultsdir/river/TIC_402980664/TIC402980664_river_gist_stern_truncated_1233_1265_manual_20230617_mask_v0_nterms2_vmin-4.00000_vmax1.00000.pdf f10c.pdf
+cp $resultsdir/river/TIC_402980664/TIC402980664_river_gist_stern_truncated_1411_1481_manual_20230617_mask_v0_nterms2_vmin-4.00000_vmax1.00000.pdf f10d.pdf
+
 cp $resultsdir/phase_timegroups/TIC_300651846/cycle-1_to_630TIC_300651846_P8.2540_2min_phase_timegroups.pdf f11a.pdf
 cp $resultsdir/phase_timegroups/TIC_300651846/cycle2290_to_2680TIC_300651846_P8.2540_2min_phase_timegroups.pdf f11b.pdf
 
+cp $resultsdir/river/tic_300651846/TIC300651846_river_seismic_-1_630_vmin-6.00000_vmax6.00000.pdf f12a.pdf
+cp $resultsdir/river/tic_300651846/TIC300651846_river_seismic_2290_2680_vmin-8.00000_vmax8.00000.pdf f12b.pdf

### 2023-08-12 complexrotators/plotting.py
make river plots better

@@ -188,6 +188,7 @@ def plot_river(time, flux, period, outdir, titlestr=None, cmap='Blues_r',
         assert ALGORITHM1 + ALGORITHM2 == 1
 
         if ALGORITHM1:
+            raise NotImplementedError("indexing by cycle_ind wrong")
             if len(flux[sel])/N_obs_per_cycle < 0.9:
                 # for significantly empty cycles, do all nan.  "significantly
                 # empty" here means any more than 5 cadences (10 minutes, out of a
@@ -214,16 +215,16 @@ def plot_river(time, flux, period, outdir, titlestr=None, cmap='Blues_r',
 
         if ALGORITHM2:
 
-            if len(time[sel])/N_obs_per_cycle < 0.1:
+            if len(time[sel])/N_obs_per_cycle < 0.2:
                 # for significantly empty cycles, do all nan.  "significantly
                 # empty" here means any more than 5 cadences (10 minutes, out of a
                 # ~1 day periods typically) off.
-                flux_arr[:, cycle_ind] = 0
+                flux_arr[:, ix] = np.nan
 
             else:
                 # select points slightly inside and outside of this cycle
                 out_sel = (
-                    (time > begin-0.05*period) & (time <= end+0.05*period)
+                    (time > begin-0.03*period) & (time <= end+0.03*period)
                 )
 
                 t_start_this_cycle = t0 + cycle_ind * period
@@ -242,32 +243,58 @@ def plot_river(time, flux, period, outdir, titlestr=None, cmap='Blues_r',
                 flux_this_cycle = fn(t_grid_this_cycle)
 
                 print(cycle_ind, N_obs_per_cycle)
-                try:
-                    flux_arr[:, ix] = flux_this_cycle
-                except IndexError:
-                    import IPython; IPython.embed()
+                N_uniq = len(np.unique(flux_this_cycle))
+                N_pt = len(flux_this_cycle)
+
+                if N_uniq / N_pt < 0.8:
+                    flux_arr[:, ix] = np.nan
+                else:
+                    try:
+                        flux_arr[:, ix] = flux_this_cycle
+                    except IndexError:
+                        import IPython; IPython.embed()
 
     if not isinstance(vmin, float):
[…]

### 2023-08-12 drivers/plot_river.py

@@ -13,11 +13,12 @@ from os.path import join
 from complexrotators.lcprocessing import (
     prepare_cpv_light_curve
 )
+import matplotlib.colors as colors
+import matplotlib.pyplot as plt
 
-
-cmap = 'seismic'
+#cmap = 'seismic'
 #cmap = 'Paired'
-#cmap = 'gist_stern'
+cmap = 'gist_stern'
 #cmap = 'PiYG'
 
 def many_ticids():
@@ -47,29 +48,17 @@ def many_ticids():
                        idstr=idstr)
 
 
+def truncate_colormap(cmap, minval=0.0, maxval=1.0, n=100):
+    new_cmap = colors.LinearSegmentedColormap.from_list(
+        'trunc({n},{a:.2f},{b:.2f})'.format(n=cmap.name, a=minval, b=maxval),
+        cmap(np.linspace(minval, maxval, n)))
+    return new_cmap
+
+
 def single_ticid():
 
     ##########################################
     # change these
-
-    ##########
-    # TIC 4029 CONFIGURATION
-    ticid = '402980664'
-    cyclewindows = [(0,1481), (0,64), (248,315), (1233, 1265), (1233,1481), (1411, 1481)]
-    sample_id = '2023catalog_LGB_RJ_concat' # used for cacheing
-    manual_period = 18.5611 / 24
-    t0 = 1791.15 + manual_period/2  # can be None
-    # e.g. written by build_4029_mask.py
-    nterms = 2
-    model_id = f"manual_20230617_mask_v0_nterms{nterms}"
-    # specifies lc subtrxn model
-    manual_csvpath = f'/Users/luke/Dropbox/proj/cpv/results/4029_mask/lc_lsresid_{model_id}.csv'
-
-    savstr = model_id # can be None; used for cacheing
-
-    vmin, vmax = -0.03, 0.03 #  can be None
-    vmin, vmax = -0.04, 0.01 #  can be None
-    ##########
 
     ##########
     # TIC 405910546
@@ -88,18 +77,41 @@ def single_ticid():
     ##########
 
     ##########
+    # TIC 4029 CONFIGURATION
+    ticid = '402980664'
+    cyclewindows = [(0,1481), (-1,64), (248,315), (1233, 1265), (1233,1481), (1411, 1481)]
+    sample_id = '2023catalog_LGB_RJ_concat' # used for cacheing
+    manual_period = 18.5611 / 24
[…]

### 2023-08-13 paper/ms.tex
update ms

@@
 entire class of star is probably part of the same phenomenon, we
-therefore generally discard the ``spot-only'' scenario.
+therefore discard the ``spot-only'' scenario.
 
@@
 extending an order of magnitude longer than the $\approx$$10^7$ year
-timescale typically quoted for primordial disk dispersal.  However,
+timescale often quoted for primordial disk dispersal.  However,
 unambiguous evidence in support of any one scenario has yet to be
@@
 exercise showed that for $T$$<$16 M dwarfs, the TESS 2-minute data are
-roughly 50\% complete at $\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\%
+$\approx$50\% complete at $\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\%
 of the $T$$<$16 M dwarfs have at least one sector of short-cadence
@@
 
-To correctly identify local minima near the edges of the phased light
+To identify local minima near the edges of the phased light
 curve, which usually would cover phases $\phi \in [ 0,1 ]$, we
@@
 we performed this analysis, we found that ``summary'' sheets were
-generated for approximately 10\% of the 20\,000 120-second targets in
+generated for $\approx$10\% of the 20\,000 120-second targets in
 a given sector.  We then manually reviewed each summary sheet, and
@@
 
-We visually assessed whether the objects found using the dip-counting
+We assessed whether the objects found using the dip-counting
 (Section~\ref{subsec:counting}) and Fourier
@@
 DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
-WISE 1-2 passbands.  We specifically omitted UV flux measurements from
+WISE 1-2 passbands.  We omitted UV flux measurements from
 our SED fit to avoid any possible bias induced by chromospheric UV
@@
 $A_{\rm V}$ using a 2MASS color-color diagram.  Finally, using
-\texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we statically sampled
+\texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we sampled
 the posterior probability assuming the default Gaussian likelihood,
@@
 evidence supporting the reality, and youth, of that group.  The yield
-in Sco-Cen is not particularly surprising, since Sco-Cen contains the
+in Sco-Cen is not surprising, since Sco-Cen contains the
 majority of pre-main-sequence stars in the solar neighborhood.
@@
 associate either star with any young groups.  However both do seem to
-clearly show the CQV signal over multiple TESS sectors, and both are
+show the CQV signal over multiple TESS sectors, and both are
 photometrically elevated relative to the main sequence.  For instance,
@@
 \citep{2006ApJ...649L.115Z}.  This group's $200 \pm 50$\,Myr age
-primarily rests on the lithium sequence of its G-dwarfs
+is based on the lithium sequence of its G-dwarfs
 \citep{2006ApJ...649L.115Z}, which shows a coeval population of stars
@@
 however somewhat low, perhaps due to the missing radial velocity.
-This could be relatively easily resolved by acquiring even a
+This could be resolved by acquiring even a
 medium-resolution spectrum.  An independent assessment of the group's
@@
 the observed shape evolution implies that CQVs have a duty cycle of
-$\approx$75\%.  This type of correction is likely worth including in
+$\approx$75\%.  This type of correction is worth including in
 population-level estimates of how intrinsically common CQVs are in the
@@
 the Sector 18-19 data, 25-26 data, 53 data, and 58-59 data.
-The river plots are slightly more processed:
-a maximum-likelihood two-harmonic sinusoid has been independently fitted and
-subtracted from the Sector 18-19 data, 25-26 data, and 53, 58, and 59
-data in order to accentuate any changes in the dip timing and structure.
+The river plots are subject to one additional processing step:
+we fitted and subtracted a maximum-likelihood two-harmonic sinusoid
+independently from the Sector 18-19 data, 25-26 data, and 53, 58, and 59 data
+in order to accentuate changes in the dip timing and structure.
 
@@
 of $\pm$1\,minute would yield major phase drifts over the baseline;
-that time interval corresponds to roughly 1/1000$^{\rm th}$ of a
-period, and we have observed 1500 cycles.  By visually fine-tuning
+that time interval corresponds to $\approx$1/1000$^{\rm th}$ of a
+period, and we have observed 1500 cycles.  By fine-tuning
 over a grid in period, we eventually found $P=18.5611 \pm 0.0001$\,hr,
@@
 There is then a 6-month (184 cycle) gap to Cycles 248-315, which show
-two intricately structured dip complexes, plus a small leading dip.
+two highly structured dip complexes, plus a small leading dip.
 The single leading dip is present at the same phase as in cycles 0-64,
@@
 cycles 248-264 represents an evolution of the initial complex seen
-during cycles 0-64, though with greatly reduced depth.  During cycles
+during cycles 0-64, though with reduced depth.  During cycles
 266-310, an additional local minimum develops between the two
@@
 the degree that one can undergo a severe change while the others
-remain essentially identical.  The state switches during cycles
+remain identical.  The state switches during cycles
 248-264 and 299-315 share the same characteristic: it is always the
@@
 visible around BTJD 1993.2, and growths in depth by about 2\% over
-about six cycles, to become easily detectable by eye by BTJD 1997.7.
+about six cycles, to become visible by eye by BTJD 1997.7.
 The evolution of this particular dip is most clear in the river plots.
@@
 \citealt{2018A&A...619A.177B}).  We found no obvious morphology
-differences between the two classes.  In terms of their rotation,
+differences between the two classes, which is somewhat surprising 
+if the two stellar classes tend to have distinct field topologies
+\citep{2009A&A...496..787R}.  In terms of their rotation rates,
 relative to the Pleiades, the CQVs are among the more rapidly rotating
@@
 single clear sharp ingress with an exponential egress, which could be
-directly fit using e.g.~a model analogous to those used for exocomets
+fitted using e.g.~a model analogous to those used for exocomets
 \citep[e.g.][]{2019A&A...625L..13Z}.  The main quantities of interest
@@
 depth (and its implications for the equivalent ``radius'' of the
-transiting cloud).  Although we briefly explored such models, it
-quickly became clear that careful modeling of sources such as LP
+transiting cloud).  We briefly explored such models, until it
+became clear that careful modeling of sources such as LP
 12-502 merits its own in-depth study.  Connections could likely also
@@
 
-%TODO: improve this to make it less jargony
-
-The difference between the prominence and dust clump scenarios is
-essentially only in whether the occulting material of interest is
+The key difference between the prominence and dust clump scenarios is
+in whether the occulting material of interest is
 neutral hydrogen, or dust.  In the phrasing of the ``frozen flux''
@@
 loops to exist that can support prominences
-\citep{2019MNRAS.482.2853J} {\bf lgb todo: verify \& de-jargonify!}.
-In detail however, whether such magnetic fixed points lie in the
-equatorial plane, or elsewhere, depends on the star's magnetic field
-geometry \citep{2023MNRAS.518.4734S}.
+\citep{2019MNRAS.482.2853J}.  In detail however, the locations of such
+magnetic fixed points depends on the star's magnetic field topology
+\citep{2023MNRAS.518.4734S}.
 
@@
 the blue than in the red
-\citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
+\citep{2017PASJ...69L...2O,2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
 For neutral hydrogen to produce this effect in absorption, its opacity
@@
 $\approx$3{,}000\,K to $\approx$10{,}000\,K the observed chromatic
-transit depths might be reproduced.  Thompson scattering is ruled out
-as a relevant opacity source, because it is gray.  The other plausible
-alternative opacity source is dust, which also has a larger absorption
+transit depths might be reproduced.  While bound-free absorption of
+${\rm H}^{-}$ seems like it might be important at such cool temperatures, in
+detail this opacity source has the {\it opposite sign} from
+what is required to produce deeper dips in the blue than in the red.
+Thompson scattering is similarly ruled out as a relevant opacity
+source, because it is gray.  The final plausible alternative opacity
+source is dust, which has the requisite larger absorption
 cross-section in the blue than the red \citep{1989ApJ...345..245C}.
@@
 \citep{1978ApJ...224L...5L,1985Ap&SS.116..285N,2005ApJ...630L..81T}.  This material
-however is unlikely to be dust, due to the relevant sublimation
+is unlikely to be dust, due to the relevant sublimation
 timescales.  The opacity is instead thought to be sourced from
@@
 the stellar magnetosphere with the ram pressure form the inflowing
-gas, it also tends to roughly coincide with the Keplerian corotation
-radius \citep{2016ARA&A..54..135H}.  Within models that have compact
-multiplanet resonant chains migrating inward due to gas drag, the
-inner-most planets therefore arrive at $\approx$5-10 stellar radii
-before the disk becomes depleted.
+gas, it also tends to coincide with the Keplerian corotation radius
+for low accretion rates
+\citep{2016ARA&A..54..135H,2022MNRAS.510.5246L}.  Within models that
+have compact multiplanet resonant chains migrating inward due to gas
+drag, the inner-most planets therefore arrive at $\approx$5-10 stellar
+radii before the disk becomes depleted.
 
 Given this context, it is tempting to try to interpret features of the
-CQV light curves in terms of the possible presence of close-in
-exoplanets, or even planetesimals.  Rocky planets this young could
+CQV light curves in terms of the possible presence of either close-in
+exoplanets or close-in planetesimals.  Rocky planets this young could
 have molten global magma oceans analogous to those that existed on the
@@
 would then be analogous to the Jupiter-Io plasma torus
-\citep[e.g.][]{1980JGR....85.1171N}, with a similar rotation period
-for the primary and orbital period for the secondary, but magnetic
-fields stronger by a factor of $\approx$1{,}000.  While this type of
-configuration is {\it a priori} plausible, no direct evidence in
-support of such a picture currently exists.
-
-In systems like LP 12-502, the observed dip depth variations would
-necessarily drive one toward a picture of a disintegrating
-planetesimal swarm, rather than just a single planetesimal.  The need
-for a swarm rather than just one launching body would be driven by the
-observation that we see dips appear and disappear at many {\it
-different phases}, but with roughly the same period.  The observed
+\citep[e.g.][]{1980JGR....85.1171N}, although with magnetic fields
+stronger by a factor of $\approx$1{,}000.  However we emphasize that
+while this type of configuration seems {\it a priori} plausible, no
+direct evidence currently supports it.
+
+One challenge is perhaps that in systems like LP 12-502, the observed
+dip depth variations would necessarily drive one toward a picture of a
+disintegrating planetesimal swarm, rather than just a single
+planetesimal.  The need for more than just one launching body would be
+driven by the observation that we see dips appear and disappear at
+many different phases, but with roughly the same period.  The observed
 changing dip depths in response to flares would be understood through
@@
 
-There are at least three problems with the idea of a disintegrating
-planetesimal swarm.  First, this model would predict that certain
-orbital phases would produce recurrent dips if observed over
-sufficiently long baselines, because the launching planetesimal would
-be massive enough to remain in orbit, while stochastically ejecting
-material.  An analogous system might be K2-22.  For most CQVs
-(Figure~\ref{fig:evoln}), the data seem to be in tension with this
-expectation.  A second issue is that many of the dips show asymmetries
-in the wrong direction relative to the naive expectation of a trailing
-comet tail.  Invoking non-exponentially decaying dust distributions as
-a function of azimuth might be one way out of this, but such an idea
-lacks firm theoretical footing.  Finally, dynamical stability is a
-concern: in a model in which any new dip is ``explained'' by invoking
-a new planetesimal, one might eventually pack the corotation radius to
-a degree where instability over short timescales would be guaranteed.
+There are at least three problems with this concept of a
+disintegrating planetesimal swarm.  First, the model would predict
+that certain orbital phases would produce recurrent dips if observed
+over sufficiently long baselines, because the launching planetesimal
+would be massive enough to remain in orbit, while stochastically
+ejecting material.  An analogous system would be K2-22
+\citep{2015ApJ...812..112S}.  For most CQVs (Figure~\ref{fig:evoln}),
+the data are in tension with this expectation.  A second issue
+is that many of the dips show asymmetries in the wrong direction
+relative to the naive expectation of a trailing comet tail.  Invoking
+non-exponentially decaying dust distributions as a function of azimuth
+might be one way out, but such an idea lacks firm theoretical footing.
+Finally, dynamical stability is a concern: in a model in which any new
+dip is ``explained'' by invoking a new planetesimal, one might
+eventually pack the corotation radius to a degree where instability
+over short timescales would be guaranteed.
 
@@
 none of the CQVs that we have studied in this work show clear evidence
-for this type of origin scenario.
+for the nearby planets that we statistically expect should be common.
 
@@
 (Sector 38), TIC~146539195 (Sector 5), TIC~118449916 (Sector 44), and
-TIC~312410638 (Sector 38) seem to show essentially the same tendency.
+TIC~312410638 (Sector 38) seem to show the same tendency.
 
@@
 holds, stable points exist wherever the outward centrifugal force is
-balanced by magnetic tension of closed field loops.  In the converse
+balanced by the combined effect of gravity and magnetic tension along
+closed field loops \citep{1985Ap&SS.116..285N}.  In the converse
 ``dynamical'' case, when  $R_{\rm A} < R_{\rm cr}$, any material
@@
 timescale.
+A simple order of magnitude estimate assuming a dipole field with
+$B_0\approx1\,{\rm kG}$ at the star's surface, a local plasma
+number density $n\approx10^9\,{\rm cm^{-3}}$, and a plasma temperature
+$10^6\,{\rm K}$ tends to give Alfv\'en radii of order a few times
+the corotation radii, $R_{\rm cr}$.
 
@@
       Psc-Eri (Section~\ref{subsec:starprops}).  It may even extend to
-    200\,Myr, based on the one CQV we found in the Carina Near moving
-    group (TIC~294328887; $\approx$200\,Myr).  However the lack of
-    detected CQVs in the Hyades and Praesepe suggests that the
-    lifetime of the phenomenon is limited to the first few hundred
-    million years.
+      200\,Myr, based on the one CQV we found in the Carina Near
+      moving group (TIC~294328887; $\approx$200\,Myr).  However the
+      lack of detected CQVs in the Hyades and Praesepe suggests that
+      the lifetime of the phenomenon is limited to the first few
+      hundred million years.
 	%
@@
     \item The closest CQVs to the Sun are at distances of 15-20\,pc,
-      and the brightest have $V$$\approx$12 ($J$$\approx$7.5).  This
-      conclusion is an extrapolation from the CQV sample derived in
-      this work being $\gtrsim$80\% complete within 30\,pc.  Expanding
-      our analysis of the TESS data to the full frame images would
-      yield a truly volume-limited selection function, and would
-      expand the CQV census by about a factor of two within 50\,pc,
-      and by a factor of ten within 100\,pc.
+      and the brightest have $V$$\approx$12 ($J$$\approx$7.5).  We
+      have found most of them in this work, since our CQV sample was
+      $\gtrsim$80\% complete within 30\,pc.  The lack of CQVs in the
+      volume-complete $<$15\,pc sample of 0.1-0.3\,$M_\odot$ stars
+      analyzed by \citet{2021AJ....161...63W} is consistent with this
+      estimate.  Expanding our analysis of the TESS data to the full
+      frame images would yield a truly volume-limited selection
+      function, and would expand the CQV census by about a factor of
+      two within 50\,pc, and by a factor of ten within 100\,pc.
 \end{enumerate}

### 2023-08-13 drivers/calc_alfven_radius_estimate.py
update oom estimates

@@ -2,22 +2,25 @@ from astropy import units as u, constants as c
 import numpy as np
 
 # way #1: set magnetic pressure B^2/8pi equal to 3/2 nkT
+R_cr_by_Rstar = 5.76 # tic 4029*
+print(f'r_CR/r_* = {R_cr_by_Rstar:.2f}')
 
-B_0 = 1e3*u.cm**(-1/2)*u.g**(1/2)*u.s**(-1)
+B_0 = 1e3 * u.cm**(-1/2)*u.g**(1/2)*u.s**(-1) # units: gauss
 
-T = 1e6*u.K
-n = 1e12/(u.cm**3)  # !!!! this is high!?   [seems super high!]
+T = 1e3*u.K
+n = 1e9/(u.cm**3)  # !!!! this is high!?   [seems super high!]
 m = n*c.m_p
 print(m.cgs)
 
 R_star = 0.4*u.Rsun
 
 r_A = R_star * (
-    B_0**2 / (3*np.pi) * (1/(n*c.k_B*T))
+    B_0**2 / (4*3*np.pi) * (1/(n*c.k_B*T))
 ).cgs**(1/4)
 
 print(f'r_A = {r_A:.4f}')
 print(f'r_A/r_* = {r_A/R_star:.4f}')
+print(f'r_A > r_CR (centrifugal magnetosphere) = {r_A/R_star > R_cr_by_Rstar}')
 
 # way #2: hartmann+2016
 B_3 = 1e4 / (1e3)
@@ -35,7 +38,6 @@ r_M = 18 * (
 print(f'r_M = {r_M:.2f}')
 print(f'r_M/r_* = {r_M/R_star:.2f}')
 
-R_cr_by_Rstar = 5.76 # tic 4029*
 print(f'r_CR/r_* = {R_cr_by_Rstar}')
 
 print(f'r_M > r_CR (centrifugal magnetosphere) = {r_M/R_star > R_cr_by_Rstar}')

### 2023-08-13 drivers/calc_corotation_radii.py

@@ -7,6 +7,7 @@ params = [
     [0.3*u.Msun,  0.4*u.Rsun, 0.2*u.day],
     [0.22*u.Msun,  0.54*u.Rsun, 7.7*u.hour], # TIC 206544316
     [0.10*u.Msun, 0.27*u.Rsun, 3.6*u.hour], # TIC 201789285
+    [1*u.Msun,  1*u.Rsun, 28*u.day], # sun
 ]
 
 for p in params:
@@ -15,11 +16,15 @@ for p in params:
     R_star = p[1]
     P_star = p[2]
 
-    a_corotation = (P_star/R_star)**2 * (c.G * M_star / (4*np.pi**2))
+    Ω = 2*np.pi / P_star
+    R_cr = (c.G * M_star / Ω**2)**(1/3)
+    a_corotation = R_cr
 
     msg = (
         f"M_star={M_star}, R_star={R_star}, P_star={P_star.to(u.day):.2f}, "+
-        f"a_corotation={a_corotation.to(u.Rsun):.2f}"
+        f"a_corotation={a_corotation.to(u.Rsun):.2f} = "+
+        f"{a_corotation.to(u.au):.2f} = {(a_corotation/R_star).cgs.value:.2f}"+
+        "Rstar"
     )
 
     print(msg)

### 2023-08-13 paper/ms.tex
update ms

@@
 decrease due to limb-darkening (see \citealt{2017AJ....153..152S},
-Figures 37-41).  The observed dips in CQVs can happen over durations as
+Figures 37-41).  The observed dips can happen over durations as
 short as $0.05\,P_{\rm rot}$ with characteristic depths of a few
@@
 \citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  Since the
-entire class of star is probably part of the same phenomenon, we
+CQVs are probably all explained by the same phenomenon, we
 therefore discard the ``spot-only'' scenario.
@@
 variability are shown in Figure~\ref{fig:f1}.  The ``clump'' scenario
-invokes opaque dust clumps orbiting near the Keplerian corotation
-radius, which periodically eclipse the star
+invokes opaque dust clumps periodically transiting the star near the Keplerian corotation
+radius, $R_{\rm cr} = (GM/\Omega^2)^{1/3}$
 \citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The ``prominence''
@@
 marginally-ionized gas, embedded within the hotter corona, that would
-be centrifugally supported near corotation
+be centrifugally supported to also be near corotation
 \citep{1989MNRAS.238..657C,2019MNRAS.482.2853J,2022MNRAS.514.5465W}.
@@
 though at much larger relative distances from the stellar surface.  A
-final possibility that has been suggested is one of a ``screen'', in
+final possibility is one of a ``screen'', in
 which the inner wall of a quiescent circumstellar disk blocks a
@@
 transitions in hydrogen or perhaps a molecular opacity.  The screen
-scenario seems inconsistent with the degree of observed periodicity,
+scenario seems inconsistent with the sharpness
+of the observed dips,
 the lack of infrared excess, and the observed lifetime of CQVs
@@
 
-\begin{figure*}[!t]
+\begin{figure*}[!tp]
 	\begin{center}
 		\centering
-		\includegraphics[width=0.96\textwidth]{annotated_lp12502.pdf}
+		\includegraphics[width=0.96\textwidth]{f2.pdf}
 		\vspace{-0.3cm}
@@
 or visual binaries, \ngoodhighruwe/\ngoods\ high-quality CQVs have a
-Gaia DR3 RUWE$>$2; \nmaybehighruwe/\nmaybes\ of the ambiguous sample
+Gaia DR2 RUWE$>$2; \nmaybehighruwe/\nmaybes\ of the ambiguous sample
 share this characteristic.
@@
 evidence supporting the reality, and youth, of that group.  The yield
-in Sco-Cen is not surprising, since Sco-Cen contains the
-majority of pre-main-sequence stars in the solar neighborhood.
-However, given the $\lesssim$$10\%$ completeness of TESS beyond
-100\,pc, there are probably many more CQVs that remain to be
-discovered in Sco-Cen.
-
-% IC\,2602 and IC\,2391, which are located slightly beyond 100\,pc, are
-% an example of this completeness effect: our search did not find any
-% CQVs in those clusters.
+in Sco-Cen is not surprising, since Sco-Cen contains the majority of
+pre-main-sequence stars in the solar neighborhood.  However, given the
+$\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there are
+probably many more CQVs that remain to be discovered in Sco-Cen.
 
@@
 
-As is typical for CQVs \citep{2017AJ....153..152S}, most CQVs in our
-catalog did not show infrared excesses in the WISE1-4 bands.  Visually
-inspecting the SEDs of our entire \ncpvsfound\ star sample, we labeled
-two objects as having ``good'' infrared excesses (both W3 and W4 at
-$>$3$\sigma$ above the photospheric prediction), and three as
-``possible'' infrared excess (only W3 at $>$3$\sigma$).
-
-The two ``good'' IR excesses belonged to ``ambiguous'' CQVs
-TIC~193136669 (TWA~34) and TIC~57830249 (TWA~33).  Both are in the TW
-Hydrae association ($\approx$10\,Myr), and have relatively long
-periods of 38\,hr and 44\,hr respectively.  In our initial labeling,
-we labeled both as ``ambiguous'' CQVs because the dips in their light
-curves did not show the rigid periodicity typical of CQVs;  their
-periods were also relatively long.  After labeling them, inspection of
-further sectors clarified that both sources are dippers (see online
-plots in Figure~\ref{fig:vet}).  Independently, TIC 193136669 has a
-cold molecular disk based on observed 1.3\,mm continuum emission and
+Most CQVs in our catalog did not show infrared excesses in the W1-W4
+bands, which is typical for this class of object
+\citep{2017AJ....153..152S}.  Visually inspecting the SEDs of our
+\ncpvsfound\ star sample, we labeled two objects as having ``good''
+infrared excesses (both W3 and W4 at $>$3$\sigma$ above the
+photospheric prediction), and three as ``possible'' infrared excess
+(only W3 at $>$3$\sigma$).
+
+The two ``good'' IR excesses belonged to TIC~193136669 (TWA~34) and
+TIC~57830249 (TWA~33).  Both are in the TW Hydrae association
+($\approx$10\,Myr), and have relatively long periods of 38\,hr and
+44\,hr respectively.  In our initial labeling, we labeled both as
+``ambiguous'' CQVs because the dips in their light curves did not show
+the rigid periodicity typical of CQVs;  their periods were also
+relatively long.  However, inspection of further sectors clarified
+that both sources are dippers (see online plots in
+Figure~\ref{fig:vet}).  Independently, TIC 193136669 has a cold
+molecular disk based on observed 1.3\,mm continuum emission and
 resolved Keplerian $^{12}{\rm CO}(2-1)$ emission
 \citep{2015A&A...582L...5R}.  It was also labeled a dipper by
-\citet{2022ApJS..263...14C}; we agree with their designation, but
-nonetheless leave it in our catalog as an indication of possible
-ambiguities in our search process.  TIC 57830249 (TWA~33) also has
-previously detected 1.3\,mm continuum emission
-\citep{2015A&A...582L...5R}, suggestive of cold dust grains being
-present.  It is also a dipper.  Section~\ref{subsec:discdippers}
+\citet{2022ApJS..263...14C}; we agree with their designation, and
+label it an ``impostor'' CQV in Table~\ref{tab:thetable}.  TIC
+57830249 (TWA~33) also has previously detected 1.3\,mm continuum
+emission \citep{2015A&A...582L...5R}, suggestive of cold dust grains
+being present.  It is also a dipper.  Section~\ref{subsec:discdippers}
 highlights plausible evolutionary connections between CQVs and dippers
@@
 star or binary companion.
+
+\begin{figure*}[!tp]
+	\begin{center}
+		\centering
+		\includegraphics[width=\textwidth]{f4.pdf}
+		\vspace{-0.6cm}
+		\caption{
+			{\bf CQVs keep their periods but change their shapes.}
+			Out of the \ngoods\ CQVs in Figure~\ref{fig:cqvs}, 32 had
+			120-second cadence TESS data available for a baseline of at
+			least two years; the 27 brightest are shown here due to space
+			constraints.  Each panel shows one sector of TESS data, and is
+			phased to its deepest minimum in flux.  Each panel's title shows
+			the TIC identifier and approximate period in hours.  Text insets
+			show the TESS sector numbers, which generally span two years, or
+			at least 1{,}000 cycles.  The vertical scale is fixed across
+			sectors to clarify shape changes.  Gray circles are raw 2-minute
+			data; colored circles bin to 300 points per cycle. 
+		}
+		\label{fig:evoln}
+	\end{center}
+\end{figure*}
 
@@
 
-\begin{figure*}[!tp]
-	\begin{center}
-		\centering
-		\includegraphics[width=\textwidth]{f4.pdf}
-		\vspace{-0.6cm}
-		\caption{
-		{\bf CQVs keep their periods but change their shapes.}
-      Out of the \ngoods\ CQVs in Figure~\ref{fig:cqvs}, 32 had
-      120-second cadence TESS data available for a baseline of at
-      least two years; the 27 brightest are shown here due to space
-      constraints.  Each panel shows one sector of TESS data, and is
-      phased to its deepest minimum in flux.  Each panel's title shows
-      the TIC identifier and approximate period in hours.  Text insets
-      show the TESS sector numbers, which generally span two years, or
-      at least 1{,}000 cycles.  The vertical scale is fixed across
-      sectors to clarify shape changes.  Gray circles are raw 2-minute
-      data; colored circles bin to 300 points per cycle. 
-		}
-		\label{fig:evoln}
-	\end{center}
-\end{figure*}
-
 \subsection{Evolution over adjacent sectors, \& LP 12-502}
@@
 
-\begin{figure*}[!t]
+\begin{figure*}[!tp]
 	\begin{center}
 		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f10a.pdf}
-			\includegraphics[width=0.48\textwidth]{f10b.pdf}
+			\includegraphics[width=0.48\textwidth]{f7a.pdf}
+			\includegraphics[width=0.48\textwidth]{f7b.pdf}
 		}
@@
 		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f10d.pdf}
-			\includegraphics[width=0.48\textwidth]{f10c.pdf}
+			\includegraphics[width=0.48\textwidth]{f7d.pdf}
+			\includegraphics[width=0.48\textwidth]{f7c.pdf}
 		}
@@
 	\caption{
-		{\bf River plots of the LP 12-502 light curve}, showing (clockwise from top-left)
-		Sectors 18-19, 25-26, 53, and 58-59.  A two-harmonic sinusoid has
-		been subtracted to highlight the sharp dips.
-		In Sectors 25-26 (cycles 248-315), periods are visible at the fundamental
-		period of 18.5611\,hr, as well as at faster and slower relative periods (e.g. $\phi$$\approx$0.3 and $\phi$$\approx$0.1).
-		Similar instances of multiple simultaneous periods are also visible in
-		Sector 53 and 58-59.
-%		$P$=18.5611\,hr (gray vertical line); 18.5404\,hr (orange); 18.5683\,hr (green).
-%		For Sector 53, gray is identical, while cyan is 18.5145\,hr.
-%		For Sectors 58-59, the magenta line is 18.5473\,hr, and the green
-%		line is 18.5672\,hr.
-		White chunks denote missing data.
+    {\bf River plots of the LP 12-502 light curve}, showing (clockwise
+    from top-left) Sectors 18-19, 25-26, 53, and 58-59.  A
+    two-harmonic sinusoid has been subtracted to highlight the sharp
+    dips.  In Sectors 25-26 (cycles 248-315), periods are visible at
+    the fundamental period of 18.5611\,hr, as well as at faster and
+    slower relative periods (e.g. $\phi$$\approx$0.3 and
+    $\phi$$\approx$0.1).  Similar instances of multiple simultaneous
+    periods are also visible in Sector 53 and 58-59.  White chunks
+    denote missing data.
 	}
@@
 quality and content of its data.  We describe another interesting
-source, TIC~300651846, in Appendix~\ref{app:tic3006}.  For this
+source, TIC~300651846, in Appendix~\ref{app:tic3006}.  In this
 section, we first present the LP 12-502 observations
 (Section~\ref{subsec:lpobservations}), and then highlight their
-interpretation (Section~\ref{subsec:lplessons}).
+implications (Section~\ref{subsec:lplessons}).
 
@@
 drawn.  Figure~\ref{fig:lp} then shows the same data, but stacked into
-successive TESS orbits spanning half a lunar month each.
-Finally, Figure~\ref{fig:lpriver0} shows ``river plots'' of the
-same data, split into similar intervals:
-the Sector 18-19 data, 25-26 data, 53 data, and 58-59 data.
-The river plots are subject to one additional processing step:
-we fitted and subtracted a maximum-likelihood two-harmonic sinusoid
-independently from the Sector 18-19 data, 25-26 data, and 53, 58, and 59 data
-in order to accentuate changes in the dip timing and structure.
+successive TESS orbits spanning half a lunar month each.  Finally,
+Figure~\ref{fig:lpriver0} shows ``river plots'' of the same data,
+split into similar intervals: the Sector 18-19 data, 25-26 data, 53
+data, and 58-59 data.  The river plots are subject to one additional
+processing step: we fitted and subtracted a maximum-likelihood
+two-harmonic sinusoid independently from the Sector 18-19 data, 25-26
+data, and 53, 58, and 59 data in order to accentuate changes in the
+dip timing and structure.
 
@@
 that time interval corresponds to $\approx$1/1000$^{\rm th}$ of a
-period, and we have observed 1500 cycles.  By fine-tuning
-over a grid in period, we eventually found $P=18.5611 \pm 0.0001$\,hr,
-which seems to track certain features in the LP 12-502 light curve
-well over the entire dataset.
+period, and we have observed 1500 cycles.  By fine-tuning over a grid
+in period, we found $P=18.5611 \pm 0.0001$\,hr, which seems to track
+certain features in the LP 12-502 light curve well over the entire
+dataset.
 
@@
 There is then a 6-month (184 cycle) gap to Cycles 248-315, which show
-two highly structured dip complexes, plus a small leading dip.
-The single leading dip is present at the same phase as in cycles 0-64,
-and is therefore likely to be the same struture.  Along a similar line
-of logic, it seems plausible that the first ``dip complex'' during
-cycles 248-264 represents an evolution of the initial complex seen
-during cycles 0-64, though with reduced depth.  During cycles
-266-310, an additional local minimum develops between the two
-complexes; this feature is best visualized on the river plots
-(Figure~\ref{fig:lpriver0}), and we describe its (shorter) period below.
+two highly structured dip complexes, plus a small leading dip.  The
+single leading dip is present at the same phase as in cycles 0-64, and
+is therefore likely to be the same struture.  Along a similar line of
+logic, it seems plausible that the first ``dip complex'' during cycles
+248-264 represents an evolution of the initial complex seen during
+cycles 0-64, though with reduced depth.  During cycles 266-310, an
+additional local minimum develops between the two complexes; this
+feature is best visualized on the river plots
+(Figure~\ref{fig:lpriver0}), and we describe its (shorter) period
+below.
 
@@
 of a period, punctuated by coherent local minima and maxima which in
-detail (Figure~\ref{fig:lpriver0}) have slightly longer periods than the
-sharp dip.  The sharp leading dip only decreases in depth following a
-sudden state-switch at BTJD 2030.7 (cycles 299-315), which happens
-during a flare (Figure~\ref{fig:lplc}).  The trailing dips remain
-thereafter.
+detail (Figure~\ref{fig:lpriver0}) have slightly longer periods than
+the sharp dip.  The sharp leading dip only decreases in depth
+following a sudden state-switch at BTJD 2030.7 (cycles 299-315), which
+happens during a flare (Figure~\ref{fig:lplc}).  The trailing dips
+remain thereafter.
 
@@
 dur} \equiv R_\star P / (\pi a)$ for the transit of a point-source at
-corotation is 1.03\,hr ({\bf uncertainties?}).  This means that while
+corotation is 1.02$\pm$0.10\,hr.  This means that while
 some of the LP 12-502 dips are sufficiently long to require structures
@@
 eff} \ll R_\star$.  This implies $a/R_\star \approx 5.8$ for this
-material, and so the analogous timescale at the stellar surface is
+material; the analogous timescale at the stellar surface is
 about six times slower.
@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{f7.pdf}
+		\includegraphics[width=0.95\textwidth]{f8.pdf}
 		\vspace{-0.1cm}
@@
       Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
-      ambiguous CQV candidates are light blue circles.  The top panels
-      show the \nstarssearched\ target stars with 120-second cadence
-      TESS data as the shaded gray background; darker regions
-      correspond to a larger relative number of searched stars.  The
-      lower-left panel compares the rotation--color distribution of
-      CQVs against the rotation periods of K and M dwarfs in the
-      Pleiades from \citet{2016AJ....152..114R}.  The lower-middle
-      panel plots the derived corotation radii $R_{\rm cr} =
-      (GM/\Omega^2)^{1/3}$ in units of stellar radii against the
-      measured CQV periods, in units of hours.  Ages in the final
-      panel are known from cluster membership.
+      ambiguous CQV candidates are light blue circles.  Cases with
+      elevated Gaia DR2 RUWE values are highlighted.
+      The top panels show the \nstarssearched\ target stars with
+      120-second cadence TESS data as the shaded gray background;
+      darker regions correspond to a larger relative number of
+      searched stars.  The lower-left panel compares the
+      rotation--color distribution of CQVs against the rotation
+      periods of K and M dwarfs in the Pleiades from
+      \citet{2016AJ....152..114R}.  The lower-middle panel plots the
+      derived corotation radii $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in
+      units of stellar radii against the measured CQV periods, in
+      units of hours.  Ages in the final panel are known from cluster
+      membership.
 		}
@@
 
-Figure~\ref{fig:catalogscatter} shows some of the derived stellar properties
-for our CQV catalog, and compares them against both the target star
-sample (top panels), and against stars in the Pleiades
+Figure~\ref{fig:catalogscatter} shows derived stellar
+properties for our CQV catalog, and compares the CQVs against both the
+target star sample (top panels), and against stars in the Pleiades
 \citep{2016AJ....152..114R}.  Typical CQV masses span
-0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This is mass
-and age includes both fully convective stars
-($M_\star$$\lesssim$0.25\,$M_\odot$), and stars with a combination of radiative
-cores and convective envelopes ($M_\star$$\gtrsim$0.25\,$M_\odot$;
-\citealt{2018A&A...619A.177B}).  We found no obvious morphology
-differences between the two classes, which is somewhat surprising 
-if the two stellar classes tend to have distinct field topologies
-\citep{2009A&A...496..787R}.  In terms of their rotation rates,
-relative to the Pleiades, the CQVs are among the more rapidly rotating
-half of M dwarfs.  The dearth of $T$$>$15.5 CQVs in our sample,
-despite our search extending to $T$$=$16, is a consequence of the
-120-second selection function, not detection sensitivity.
+0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This mass
+and age range includes both fully convective stars
+($M_\star$$\lesssim$0.25\,$M_\odot$), and stars with a combination of
+radiative cores and convective envelopes
+($M_\star$$\gtrsim$0.25\,$M_\odot$; \citealt{2018A&A...619A.177B}).
+We found no obvious morphology differences between the two classes,
+which is somewhat surprising given that the star's interior structure may influence
+the field topology \citep{2009A&A...496..787R}.  In terms of
+their rotation rates relative to the Pleiades, the CQVs are among the
+more rapidly rotating half of M dwarfs. 
+%The dearth of $T$$>$15.5 CQVs
+in our sample, despite our search extending to $T$$=$16, is a
+consequence of the 120-second selection function, not detection
+sensitivity.
 
@@
 
-The lowest mass ($\approx 0.12$\,$M_\odot$) belongs to TIC~267953787.
+The lowest mass ($\approx$$0.12$\,$M_\odot$) belongs to TIC~267953787.
 The catalog contains a few other stars with similar mass.  Given the
@@
 
-The two most massive CQVs in our sample might represent an interesting
-new regime, but both have ambiguities.  To date, the only stars
-reported to show the CQV phenomenon are M dwarfs, with typical stellar
-masses $\lesssim$0.3\,$M_\odot$
+\subsection{Binaries, massive CQVs, and a new class of false positive}
+
+The high-RUWE objects in Figure~\ref{fig:catalogscatter} tend to be
+among the more massive half of the CQV sample.  This suggests that either
+that the RUWE indicator is not sensitive to binarity among lower mass
+stars, or that these ``high-mass CQVs'' may be unresolved blends in
+which the lower mass companion is produces the CQV signal.
+
+\subsubsection{Do K dwarf CQVs exist?}
+\label{subsec:massive}
+
+The two most massive CQVs in our sample present a relevant case study.
+To date, the only stars reported to show the CQV phenomenon are M
+dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
 \citep{2017AJ....153..152S,2022AJ....163..144G}.  TIC~405754448 and
-TIC~405910546 however appear to have masses of $\approx$0.82\,$M_\odot$ and
-$\approx$0.60\,$M_\odot$ respectively.  The next-highest masses in our
-sample are $\approx$0.40\,$M_\odot$.  The masses for the former two
-objects are consistent with their locations in the color--absolute
-magnitude diagram, and with their membership in LCC.  However based on
-its light curve morphology, TIC~405910546 should be studied in greater
-depth, to confirm it is not an eclipsing binary.  For TIC~405754448,
-we expect that the source is an unresolved binary, because RUWE$_{\rm
-DR3}$=4.7, and because the raw light curves in Sectors 11, 37, and 38
-for this source show an additional $\approx$6.5\,day, $\approx$0.3\%
-amplitude sinusoidal signal suggestive of an unresolved photometric
-companion.  If TIC~405754448 is a K+M binary, then the flux ratio
-between the primary and secondary would be expected to be
-$\approx$10:1.  It would be somewhat challenging for the M dwarf to
-produce the observed 12.9\,hr signal with such a flux deficit, but not
-impossible.  Therefore while both of these objects seem to suggest
-that the CQV phenomenon may extend up in mass to pre-main-sequence K
-dwarfs, more data are needed to fully substantiate this claim.
-
-\subsection{TIC~425937691}
-
-TIC~425937691 is a surprising case: it shows two seemingly independent
+TIC~405910546 however appear to have masses of
+$\approx$0.82\,$M_\odot$ and $\approx$0.60\,$M_\odot$ respectively.
+The next-highest masses in our sample are $\approx$0.40\,$M_\odot$.
+The masses for the former two objects are consistent with their
+locations in the color--absolute magnitude diagram, and with their
+membership in LCC.  However the light curve morphology of
+TIC~405910546 is unique among the CQV sample, and suggestive of an
+eclipsing binary; it should be studied further to clarify its
+classification.  For TIC~405754448, we expect that this source {\it
+is} an unresolved binary, because RUWE$_{\rm DR2}$=4.7, and because
+the raw light curves in Sectors 11, 37, and 38 show an
+additional $\approx$6.5\,day, $\approx$0.3\% amplitude sinusoidal
+signal suggestive of an unresolved photometric companion.  If
+TIC~405754448 is a K+M binary, then the flux ratio between the primary
+and secondary would be expected to be $\approx$10:1.  It would be
+challenging for the M dwarf to produce the observed 12.9\,hr signal
+with such a flux deficit, but not impossible.  While both of
+these objects suggest that the CQV phenomenon may extend up in mass to
+pre-main-sequence K dwarfs, more data are needed to fully substantiate
+this claim.
+
+\subsubsection{Systems near the 3:2 commensurability}
+
+\paragraph{TIC~435903839}
+We originally classified TIC~435903839, with RUWE$_{\rm DR2}$=11.6, as
+an ``ambiguous'' CQV with 
+a 10.82\,hr period, because this period minimized the
+dispersion in the phase-folded light curve.  However careful inspection
+of the periodogram
+reveals that this source is a photometric blend of two ordinary
+rotating stars with $P_0$=3.60\,hr, and $P_1$=5.41\,hr.  This is a
+novel false positive scenario for CQVs: two rapidly-rotating stars
+with near-integer ratios of rotation periods.  The beat between the
+two rotation signals produces the apparent CQV signal.  Such false
+positives can be excluded through careful accounting of all peaks in a
+periodogram.  For instance, TIC~435903839 shows a peak at 16.27\,hr,
+which is not an integer multiple of the dispersion-minimizing 10.82\,hr period.
+This particular case is an ``impostor'' CQV.
+
+\paragraph{TIC~425937691}
+TIC~425937691 is an odd converse case: it shows two seemingly independent
 CQV signals on what appears to be the same star.  The two signals have
-periods of $\approx$4.82\,hr and $\approx$3.22\,hr, respectively.
+periods of $\approx$4.82\,hr and $\approx$3.22\,hr, and so also fall near
+the 3:2 commensurability.
 The former is the larger amplitude signal visible in
@@
 three sharp dips super-posed over each cycle.  For
-TIC~425937691, ${\rm RUWE}_{\rm DR3}=2.9$.
-
-The explanation that seems most likely for this source, given the two
-photometric signals and the elevated RUWE, is an unresolved binary
-consisting of two CQVs.  Recent work has shown that the orbits of
+TIC~425937691, ${\rm RUWE}_{\rm DR2}=2.9$.
+
+Given the two photometric signals and the elevated RUWE, this source is 
+probably an unresolved binary consisting of two CQVs.  Recent work has shown that the orbits of
 binaries closer than $\lesssim$700 AU tend to be aligned with their
@@
 simply be a coincidence.
-
-\subsection{TIC~435903839}
-
-%TODO: move these to their own ``debunked'' table, I think...
-%TODO: along with the IR excess ones
-
-TIC~435903839, which we originally classified as an ``ambiguous'' CQV,
-is an apparently similar case.  We initially labeled this source as
-having a 10.82\,hr period, because this period minimized the
-dispersion in the phase-folded light curve.  However closer inspection
-reveals that this source is a photometric blend of two ordinary
-rotating stars with $P_0$=3.60\,hr, and $P_1$=5.41\,hr.  This is a
-novel false positive scenario for CQVs: two rapidly-rotating stars
-with near-integer ratios of rotation periods.  The beat between the
-two rotation signals produces the spurious CQV signal.  Such false
-positives can be excluded through careful accounting of all peaks in a
-periodogram.  For instance, TIC~435903839 shows a peak at 16.27\,hr,
-which is not an integer multiple of the nominal ``10.82\,hr'' period.
 
@@
 		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f8a.pdf}
+			\includegraphics[width=0.48\textwidth]{f9a.pdf}
 		}
@@
 		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f8b.pdf}
+			\includegraphics[width=0.48\textwidth]{f9b.pdf}
 		}
@@
 		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f8c.pdf}
+			\includegraphics[width=0.48\textwidth]{f9c.pdf}
 		}
@@
 includes an additional \nmaybes\ ambiguous CQVs, whose designation is
-less certain.  We inferred ages for all but two of the \ncpvsfound\
+less certain, and \ndebunked\ impostors.  We inferred ages for all but two of the \ncpvsfound\
 objects based on association memberships; we also derived temperatures
@@
       observed optical flares.  This suggests that the occulting
-      material is responding to sudden changes in the magnetic field.
+      material is sensitive to sudden changes in the magnetic field.
   %
@@
       require at least an asteroid belt's worth of dust
-      ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or 100 times more
-      material if the occulting matter is gas.
+      ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or $\approx$$10^{-2}$\,$M_\oplus$
+      if the occulting material is gas.
   %
@@
       TIC~405754448 and TIC~405910546, with masses of $\approx$0.8 and
-      $\approx$0.6\,$M_\odot$, are the two massive outliers
-      (Section~\ref{subsec:extreme}), and we encourage additional
+      $\approx$0.6\,$M_\odot$, are the two massive outliers.
+      However both have peculiarities (Section~\ref{subsec:massive}), and 
+      we encourage additional
       scrutiny of these objects in future work.
@@
 %\tabletypesize{\scriptsize}
-\tablecaption{Complex quasiperiodic variables identified in the TESS
-  2-minute data. {\bf For internal review, full versions are available
-  here
+\tablecaption{Bonafide, candidate, and debunked complex quasiperiodic
+  variables from the TESS 2-minute data. {\bf For internal
+  review, full versions are available here
   \url{https://www.dropbox.com/scl/fo/twn4s9ckbevf75jqhtoy1/h?rlkey=t5cn8cx2uoc2ptdm9e570kp1b&dl=0}} \label{tab:thetable}}
@@
 \tablecomments{This table includes \ngoods\ CQVs (\texttt{Quality}
-  flag true), and \nmaybes\ ambiguous CQVs (\texttt{Quality} flag
-  false).  The machine-readable version, available online, includes
-  additional columns for the Gaia DR2 source identifiers and parameter
+  flag 1), \nmaybes\ ambiguous CQVs (\texttt{Quality} flag 0), and
+  \ndebunked\ impostors (\texttt{Quality} flag -1).  The
+  machine-readable version, available online, includes additional
+  columns for the Gaia DR2 source identifiers and parameter
   uncertainties.  The age uncertainties are typically $\approx \pm
-  10\%$, but can be asymmetric.  The median temperature, radius, and
+  10\%$, but can be asymmetric.  {\bf The median temperature, radius, and
   mass uncertainties are $\pm XXX$\,K, $\pm XX$\%, and $\pm YY$\%
-  respectively.  $N_{\rm sector}$ denotes the number of TESS sectors
+  respectively}.  $N_{\rm sector}$ denotes the number of TESS sectors
   for which data are expected to be acquired between July~2018 and

### 2023-08-13 drivers/calc_tdur_pointsource.py

@@ -1,0 +1,20 @@
+import numpy as np
+from astropy import units as u, constants as c
+
+# a^3 = P^2 * GMtot / (4pi^2)
+
+P = 18.56 * u.hr
+R_star = 0.37 * u.Rsun
+M_star = 0.22 * u.Msun
+a = (P**2 * c.G * M_star / (4*np.pi**2))**(1/3)
+
+Tdur = R_star * P / (np.pi * a)
+print(f"{Tdur.to(u.hr):.2f}")
+
+P = 18.56 * u.hr
+R_star = (0.37+(0.1*0.37)) * u.Rsun
+M_star = 0.22 * u.Msun
+a = (P**2 * c.G * M_star / (4*np.pi**2))**(1/3)
+
+Tdur = R_star * P / (np.pi * a)
+print(f"{Tdur.to(u.hr):.2f}")

### 2023-08-13 paper/collect.sh

@@ -5,31 +5,33 @@ addir="/Users/luke/Dropbox/Documents/proposals/2023_05_ADAP/latex/figs/"
 cp $resultsdir/lc_mosaic/lc_mosaic_fav3.pdf f1a.pdf
 cp $addir/models.pdf f1b.pdf
 
-# fig2
-cp $resultsdir/full_lcmosaic/full_lcmosaic_showtitles_Ngoodsectors_tic8_Tmag.pdf f3.pdf
+# fig2 is annotated_lp12502.key exported
 
 # fig3
-cp $resultsdir/beforeafter_mosaic/beforeafter_mosaic_showtitles_tic8_Tmag.pdf f4.pdf
+cp $resultsdir/full_lcmosaic/full_lcmosaic_showtitles_Ngoodsectors_tic8_Tmag.pdf f3.pdf
 
 # fig4
-cp $resultsdir/tic4029_segments/tic4029_segments.pdf f5.pdf
+cp $resultsdir/beforeafter_mosaic/beforeafter_mosaic_showtitles_tic8_Tmag.pdf f4.pdf
 
 # fig5
-cp $resultsdir/phase_timegroups_mosaic/TIC_402980664/TIC_402980664_P18.5611_2min_phase_timegroups_mosaic_ymin-4.8_ymax3.pdf f6.pdf
+cp $resultsdir/tic4029_segments/tic4029_segments.pdf f5.pdf
 
 # fig6
-cp $resultsdir/catalogscatter/catalogscatter_showmaybe.pdf f7.pdf
+cp $resultsdir/phase_timegroups_mosaic/TIC_402980664/TIC_402980664_P18.5611_2min_phase_timegroups_mosaic_ymin-4.8_ymax3.pdf f6.pdf
+
+# fig7
+cp $resultsdir/river/TIC_402980664/TIC402980664_river_gist_stern_truncated_-1_64_manual_20230617_mask_v0_nterms2_vmin-4.00000_vmax1.00000.pdf f7a.pdf
+cp $resultsdir/river/TIC_402980664/TIC402980664_river_gist_stern_truncated_248_315_manual_20230617_mask_v0_nterms2_vmin-4.00000_vmax1.00000.pdf f7b.pdf
+cp $resultsdir/river/TIC_402980664/TIC402980664_river_gist_stern_truncated_1233_1265_manual_20230617_mask_v0_nterms2_vmin-4.00000_vmax1.00000.pdf f7c.pdf
[…]

### 2023-08-13 paper/ms.tex
update ms

@@
 			{\bf Validation plots used to  label CQVs}.  The complete figure
-			set, with one image per sector for each of \ncpvsfound\ CQVs
-			and CQV candidates
+			set, with one image per sector for each of the \nallcands\
+      objects in Table~\ref{tab:thetable}
 			is available online {\bf For internal collaboration review:
@@
 Fourier analysis was not amenable to calculating a similar
-false-positive probability, because it was implemented as a general
-variability search; its results are also being used for other types of
-variability analyses beyond CQVs.
+false-positive rate, because it was implemented as a general
+variability search; its results are also being used for analyses
+on topics other than CQVs.
 
@@
 
-Table~\ref{tab:thetable} lists the \ncpvsfound\ objects identified by
+Table~\ref{tab:thetable} lists the \nallcands\ objects identified by
 our search.  The ``high-quality sample'' includes \ngoods\ of these
@@
 characteristics of the CQV phenomenon in at least one TESS sector.
-The classification of the remaining \nmaybes\ CQV candidates was
-ambiguous.  Additional data from TESS or other instruments could help
-resolve their classification.  The boolean \texttt{quality} column in
-the table divides the two classes.  In the following, we will restrict
-our discussion to the high-quality sample.
+The classification of \nmaybes\ CQV candidates was ambiguous, and the
+\ndebunked\ remaining objects were false positives that we discuss below.
+The \texttt{quality} column in the table divides the three classes;
+additional data from TESS or other instruments could help resolve the
+classification of the ambiguous cases.   Of the \ncqvsnodebunked\ CQVs
+and candidate CQVs, \nbothdipfourier\ were found using both the
+dip-counting and Fourier techniques, \nyesdipnofourier\ were found
+using only the dip-counting technique, and \nyesfouriernodip\ were
+found using only the Fourier technique.  In the following, we will
+restrict our discussion to the high-quality sample, irrespective of
+discovery method.
 
@@
 A small number of objects at first glance seem reminiscent of
-eclipsing binaries, such as TIC~193831684 or TIC~5714469.  In these
-few cases, we believe that that are unlikely to be eclipsing binaries
-due to additional coherent variations in the light curves that are
-distinct from any binary phenomenology of which we are aware.
+eclipsing binaries, such as TIC~193831684 or TIC~5714469.  We 
+believe these cases are unlikely to be eclipsing binaries
+due to the additional coherent peaks and troughs in the light curves,
+which are
+distinct from any binary phenomena of which we are aware.
 
@@
 
-Of our \ncpvsfound\ confirmed and candidate CQVs, \nnotfieldbanyan\
+Of our \ncqvsnodebunked\ confirmed and candidate CQVs, \nnotfieldbanyan\
 were associated with a nearby moving group or open cluster using
@@
 $\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there are
-probably many more CQVs that remain to be discovered in Sco-Cen.
+probably many more CQVs in Sco-Cen that remain to be discovered.
 
@@
 (TIC~58084670 and TIC~141146667), we were not able to confidently
-associate either star with any young groups.  However both do seem to
+associate either star with any young groups.  Both do seem to
 show the CQV signal over multiple TESS sectors, and both are
-photometrically elevated relative to the main sequence.  For instance,
-both were noted by \citet{2021ApJ...917...23K} as being in the
+photometrically elevated relative to the main sequence.  
+Both were also noted by \citet{2021ApJ...917...23K} as being in the
 ``diffuse'' population of $<$50\,Myr stars near the Sun.
@@
 \citep{2017AJ....153..152S}.  Visually inspecting the SEDs of our
-\ncpvsfound\ star sample, we labeled two objects as having ``good''
+\nallcands\ star sample, we labeled two objects as having ``good''
 infrared excesses (both W3 and W4 at $>$3$\sigma$ above the
@@
 
-Out of the \ngoods\ CQVs, a small fraction were in regions of sky with
-many sectors of adjacent TESS data.  Out of these objects, LP 12-502
+A small fraction of our objects were in regions of sky with
+many sectors of adjacent TESS data.  Out of this already small sample, LP 12-502
 (TIC 402980664; $d$=21\,pc, $J$=9.4, $T$=11.1) stood out due to the
-quality and content of its data.  We describe another interesting
+quality and content of its data.  We discuss another interesting
 source, TIC~300651846, in Appendix~\ref{app:tic3006}.  In this
@@
 
-One challenge is perhaps that in systems like LP 12-502, the observed
-dip depth variations would necessarily drive one toward a picture of a
+In systems like LP 12-502, the observed
+variability would probably drive one toward a picture of a
 disintegrating planetesimal swarm, rather than just a single
-planetesimal.  The need for more than just one launching body would be
-driven by the observation that we see dips appear and disappear at
+planetesimal.  The need for more than just one launching body 
+is because we see dips appear and disappear at
 many different phases, but with roughly the same period.  The observed
@@
 
-There are at least three problems with this concept of a
-disintegrating planetesimal swarm.  First, the model would predict
+There are at least three problems with this 
+disintegrating planetesimal swarm concept.  First, the model would predict
 that certain orbital phases would produce recurrent dips if observed
@@
 includes an additional \nmaybes\ ambiguous CQVs, whose designation is
-less certain, and \ndebunked\ impostors.  We inferred ages for all but two of the \ncpvsfound\
+less certain, and \ndebunked\ impostors.  We inferred ages for all but two of the \nallcands\
 objects based on association memberships; we also derived temperatures

### 2023-08-13 drivers/make_cpv_table.py
add venn

@@ -20,7 +20,7 @@ Utilities:
 
 from glob import glob
 from os.path import join
-import pandas as pd, numpy as np
+import pandas as pd, numpy as np, matplotlib.pyplot as plt
 import os, time
 from complexrotators.paths import (
     DATADIR, RESULTSDIR, TABLEDIR, LITDIR, LOCALDIR, PAPERDIR
@@ -50,6 +50,12 @@ def main(overwrite=0):
 
     csvpath2 = join(DATADIR, "targetlists", "20230813_DEBUNKED_CQVs.txt")
     debunked_df = pd.read_csv(csvpath2)
+
+    csvpath3 = join(DATADIR, "targetlists", "20230411_goodandmaybe_CPV_ticids_d_lt_150pc.csv")
+    dipcount_df = pd.read_csv(csvpath3)
+
+    csvpath4 = join(DATADIR, "targetlists", "20230501_RAHUL_FULL_LIST_NO_DUPLICATES.csv")
+    fourier_df = pd.read_csv(csvpath4)
 
     rows = []
     for t in _df['ticid']:
@@ -114,7 +120,9 @@ def main(overwrite=0):
     sdf.to_csv(csvpath, index=False, sep="|")
     print(f"Wrote {csvpath}")
 
-    N_1 = len(sdf)
+    N_allcands = len(sdf)
+    N_cqvs_nodebunked = len(sdf[(sdf.quality == 1) | (sdf.quality == 0)])
+
     N_2 = len(sdf[sdf.quality == 1])
     N_3 = len(sdf[sdf.quality == 0])
     N_debunked = len(sdf[sdf.quality == -1])
@@ -144,11 +152,40 @@ def main(overwrite=0):
     N_8 = len(sgdf[sgdf.ruwe > 2])
     N_9 = len(smdf[smdf.ruwe > 2])
 
+    _mdf = pd.concat((sgdf, smdf))
+    dipcount_ticid = set(np.array(dipcount_df[dipcount_df.ticid.isin(_mdf.ticid)].ticid))
+    fourier_ticid = set(np.array(fourier_df[fourier_df.ticid.isin(_mdf.ticid)].ticid))
+    from gyrojo import venn
+    plt.close("all")
+    labels = venn.get_labels([dipcount_ticid, fourier_ticid],
+                             fill=['number','logic'])
+    fig,ax = venn.venn2(labels, names=['dipcount','fourier'])
+    _outdir = join(RESULTSDIR, 'venn')
[…]

### 2023-08-13 paper/ms.tex
re-classify three CQVs
dropped entirely:
  TIC 251496897 (alpha per / s58)
  TIC 302160226 (s58)

good->maybe:
  TIC 5714469

@@
 
-Of the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
-find any association, one (TIC~302160226) is a member of $\alpha$~Per
-($t\approx 86\pm16$\,Myr;
-\citealt{2021A&A...645A..84M,2023AJ....166...14B}).  For the other two
-(TIC~58084670 and TIC~141146667), we were not able to confidently
-associate either star with any young groups.  Both do seem to
-show the CQV signal over multiple TESS sectors, and both are
-photometrically elevated relative to the main sequence.  
-Both were also noted by \citet{2021ApJ...917...23K} as being in the
-``diffuse'' population of $<$50\,Myr stars near the Sun.
+For the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
+find any association, we were not able to confidently associate either
+star with any young groups.  Both do seem to show the CQV signal over
+multiple TESS sectors, and both are photometrically elevated relative
+to the main sequence.  Both were also noted by
+\citet{2021ApJ...917...23K} as being in the ``diffuse'' population of
+$<$50\,Myr stars near the Sun.
 
@@
 	ARG: Argus \citep{2019ApJ...870...27Z}.
-	APER: $\alpha$~Persei open cluster \citep{2023AJ....166...14B}.
+	%APER: $\alpha$~Persei open cluster \citep{2023AJ....166...14B}.
 	BPMG: $\beta$~Pic moving group \citep{2015MNRAS.454..593B}.

### 2023-08-13 complexrotators/plotting.py

@@ -2658,14 +2658,14 @@ def plot_full_lcmosaic(outdir, showtitles=1, titlefontsize=3.5,
     """
 
     # load ticids
-    N_objects = 53 # fine if longer/shorter, just requires tweaking
+    N_objects = 50 # fine if longer/shorter, just requires tweaking
 
     tablepath = join(
         TABLEDIR, "2023_catalog_table",
         '20230613_LGB_RJ_CPV_TABLE_supplemental_selfnapplied.csv'
     )
     df = pd.read_csv(tablepath, sep="|")
-    _df = df[~pd.isnull(df.goodsectors)]
+    _df = df[df.quality == 1]
     assert len(_df) == N_objects
 
     # get manually written sectors to plot
@@ -2705,7 +2705,8 @@ def plot_full_lcmosaic(outdir, showtitles=1, titlefontsize=3.5,
     set_style('science')
 
     factor = 0.8
-    fig, axs = plt.subplots(nrows=9, ncols=6,
+    ncols = 5
+    fig, axs = plt.subplots(nrows=10, ncols=ncols,
                             figsize=(factor*7,factor*8.7),
                             constrained_layout=True)
     axs = axs.flatten()
@@ -2851,9 +2852,9 @@ def plot_full_lcmosaic(outdir, showtitles=1, titlefontsize=3.5,
 
         ix += 1
 
-    for ax in axs[-6:]:
+    for ax in axs[-ncols:]:
         ax.set_xticklabels(['-0.5','0','0.5'])
-    axs[-1].set_axis_off()
+    #axs[-1].set_axis_off()
 
     fs = 'medium'
     fig.text(0.5,0.0, r"Phase, φ", fontsize=fs)
@@ -2867,9 +2868,9 @@ def plot_full_lcmosaic(outdir, showtitles=1, titlefontsize=3.5,
         s += f'_{sortby}'
 
     # height/width
-    fig.tight_layout(h_pad=0.1, w_pad=0.)
+    fig.tight_layout(h_pad=0.02, w_pad=0.)
 
-    axs[-1].set_axis_off()
+    #axs[-1].set_axis_off()
 
     outpath = join(outdir, f'full_lcmosaic{s}.png')
     savefig(fig, outpath, dpi=400)

### 2023-08-13 drivers/make_cpv_table.py

@@ -100,9 +100,12 @@ def main(overwrite=0):
     sel_max55 = (
         (min_goodsector <= 55) | (min_maybesector <= 55)
     )
+
+    sel &= sel_max55
+
     selcols = "ticid goodsectors maybesectors".split()
     print(f"\n...\n")
-    print(f"WRN! including\n{df[~sel_max55][selcols]}\n, bc alpha per")
+    print(f"WRN! dropping {df[~sel_max55][selcols]}\n")
     print(f"\n...\n")
 
     N_0 = len(df)
@@ -143,10 +146,10 @@ def main(overwrite=0):
         assert num <= 10
         return units[num]
 
-    N_4 = num2word(len(sgdf[sgdf.banyan_assoc == 'FIELD']) + 1)
+    N_4 = num2word(len(sgdf[sgdf.banyan_assoc == 'FIELD']))
     N_5 = len(smdf[smdf.banyan_assoc == 'FIELD'])
 
-    N_6 = len(sgdf[sgdf.banyan_assoc != 'FIELD']) - 1
+    N_6 = len(sgdf[sgdf.banyan_assoc != 'FIELD'])
     N_7 = len(smdf[smdf.banyan_assoc != 'FIELD'])
 
     N_8 = len(sgdf[sgdf.ruwe > 2])

### 2023-08-13 paper/ms.tex
propagate to ms

@@
 In systems like LP 12-502, the observed
-variability would probably drive one toward a picture of a
+variability would perhaps drive one toward a picture of a
 disintegrating planetesimal swarm, rather than just a single

### 2023-08-13 paper/ms.tex
merge LR light curve classifxn; update ms

@@
 Gaia DR2 RUWE$>$2; \nmaybehighruwe/\nmaybes\ of the ambiguous sample
-share this characteristic.
+share this characteristic.\footnote{For an explanation of the renormalized unit weight error (RUWE), see the GAIA DPAC technical note \url{http://www.rssd.esa.int/doc_fetch.php?
+id=3757412}.
+Elevated RUWEs imply elevated noise relative to a single-source astrometric model, which can be caused by marginally resolved point sources, astrophysical photometric variability, or astrophysical astrometric motion.}
 
@@
 A small number of objects at first glance seem reminiscent of
-eclipsing binaries, such as TIC~193831684 or TIC~5714469.  We 
-believe these cases are unlikely to be eclipsing binaries
-due to the additional coherent peaks and troughs in the light curves,
-which are
-distinct from any binary phenomena of which we are aware.
+eclipsing binaries, such as TIC~193831684, TIC~59836633, or
+TIC~5714469.  We believe these cases are unlikely to be eclipsing
+binaries due to the additional coherent peaks and troughs in the light
+curves, which are distinct from any binary phenomena of which we are
+aware.
 
@@
 \citep{2019ApJ...870...27Z}, which serves as an indirect line of
-evidence supporting the reality, and youth, of that group.  The yield
+evidence supporting the reality and youth of that group.  The yield
 in Sco-Cen is not surprising, since Sco-Cen contains the majority of
-pre-main-sequence stars in the solar neighborhood.  However, given the
-$\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there are
-probably many more CQVs in Sco-Cen that remain to be discovered.
+pre-main-sequence stars in the solar neighborhood, any many of its stars
+were selected for TESS 120-second cadence observations by various
+guest investigators.  Given the
+$\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there may
+be many more CQVs in Sco-Cen that remain to be discovered.
 
@@
 		\label{fig:evoln}
+	\end{center}
+\end{figure*}
+
+\begin{figure*}[!tp]
+	\begin{center}
+		\centering
+		\includegraphics[width=0.98\textwidth]{f5.pdf}
+		\vspace{-0.35cm}
+		\caption{
+			{\bf LP 12-502 (TIC~402980664) light curve}, where each time
+			chunk represents one TESS orbit.  Data were acquired in Sectors
+			18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  The red
+			vertical lines highlight apparently instantaneous state changes
+			in the shape of the dip pattern.  The light curve is binned to
+			15-minute intervals so that there are 96 points per day, and
+			each point is connected by a line.  Data gaps longer than
+			15-minutes are not interpolated; if data are missing, nothing is
+			plotted.
+		}
+		\label{fig:lplc}
 	\end{center}
@@
 
-\subsection{Evolution over adjacent sectors, \& LP 12-502}
-
-\begin{figure*}[!tp]
-	\begin{center}
-		\centering
-		\includegraphics[width=0.98\textwidth]{f5.pdf}
-		\vspace{-0.35cm}
-		\caption{
-      {\bf LP 12-502 (TIC~402980664) light curve}, where each time
-      chunk represents one TESS orbit.  Data were acquired in Sectors
-      18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  The red
-      vertical lines highlight apparently instantaneous state changes
-      in the shape of the dip pattern.  The light curve is binned to
-      15-minute intervals so that there are 96 points per day, and
-      each point is connected by a line.  Data gaps longer than
-      15-minutes are not interpolated; if data are missing, nothing is
-      plotted.
-		}
-		\label{fig:lplc}
-	\end{center}
-\end{figure*}
-
 \begin{figure*}[!t]
@@
 		\centering
-		\includegraphics[width=\textwidth]{f6.pdf}
-		\vspace{-0.6cm}
+		\includegraphics[width=0.98\textwidth]{f6.pdf}
+		\vspace{-0.3cm}
 		\caption{
@@
 
-\begin{figure*}[!tp]
+\begin{figure*}[!t]
 	\begin{center}
 		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f7a.pdf}
-			\includegraphics[width=0.48\textwidth]{f7b.pdf}
+			\includegraphics[width=0.46\textwidth]{f7a.pdf}
+			\includegraphics[width=0.46\textwidth]{f7b.pdf}
 		}
-	   \vspace{-0.1cm}
+		\vspace{-0.2cm}
 
 		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f7d.pdf}
-			\includegraphics[width=0.48\textwidth]{f7c.pdf}
+			\includegraphics[width=0.46\textwidth]{f7d.pdf}
+			\includegraphics[width=0.46\textwidth]{f7c.pdf}
 		}
@@
 \end{figure*}
+
+\subsection{Evolution over adjacent sectors, \& LP 12-502}
 
@@
 
-{\sc Dip periods}---Most of the LP 12-502 dips recur with a period of
+{\sc Dip periods}---Most of the LP 12-502 dips repeat with a period of
 $P=18.5611 \pm 0.0001$\,hr.  However the river plots
-(Figure~\ref{fig:lpriver0}) reveal multiple distinct periodicities in the
-light curve for specific dips.  For instance, in sectors 25-26, the
+(Figure~\ref{fig:lpriver0}) reveal that the
+light curve has specific dips with simultaneous but distinct periods.  For instance, in sectors 25-26, the
 local minimum that develops around cycle 262 has a period faster than
@@
 
-		\vspace{-0.4cm}
+		\vspace{-0.35cm}
 		\subfloat{
@@
 LGB gratefully acknowledges support from the Heising-Simons
-51~Pegasi~b Fellowship.  While many conversations helped encourage
-this work, a few thank-yous in particular (from LGB) are owed to
-G.~Laughlin, A.~Mann, and J.~Spake for clarifications and ideas.  This
-paper relies on data collected by the TESS mission, which are publicly
+51~Pegasi~b Fellowship.  
+A few thank-yous in particular (from LGB) are owed to
+G.~Laughlin, A.~Mann, and J.~Spake for clarifications and ideas, and to E.~Schaller
+and the 51 Peg science team for encouraging lightning talks at the annual summits.
+In addition, this paper relied on data collected by the TESS mission, which are publicly
 available from the Mikulski Archive for Space Telescopes (MAST).
@@
 
-{\bf AUTHOR CONTRIBUTION STATEMENTS: PLEASE REVISE IF APPROPRIATE)}
-LGB~and RJ conceived the project and executed the dip-based and
-Fourier-based analyses, respectively.
-SR and RJ vetted the results from the Fourier search.
-LGB performed the cluster membership, SED, and variability analyses.
-LR contributed an independent SED analysis, and cross-checked the
-variability analyses.
+%{\bf AUTHOR CONTRIBUTION STATEMENTS: PLEASE REVISE IF APPROPRIATE)}
+LGB conceived the project and performed the
+dip-counting search,
+light curve classification,
+cluster membership, SED, and variability analyses.
+RJ and SR performed the Fourier-based analysis and contributed
+to light curve classification.
+LR cross-examined the light curve classification, and contributed an independent SED analysis.
 AD identified the magnetic B star connection.
 LAH contributed to data analysis and interpretation.
-G\'AB acquired and maintained the servers used to run the dip-finding
-pipeline.
+G\'AB acquired and maintained the servers used to run the dip-finding pipeline.
 GRR is an architect of the TESS mission.
+{\bf JNW?  MNG?}
 All authors assisted in manuscript writing and revision.
@@
   respectively}.  $N_{\rm sector}$ denotes the number of TESS sectors
-  for which data are expected to be acquired between July~2018 and
-  Oct~2024.   Association names and provenance follow conventions
-  adopted by \citet{2018ApJ...856...23G}: 
+  for which {\it any} data are expected to be acquired between July~2018 and
+  Oct~2024.  This number is generally greater than the number of
+  sectors for which 120-second cadence data exist.   Association names
+  and provenance follow conventions adopted by
+  \citet{2018ApJ...856...23G}: 
 	ABDMG: AB~Doradus moving group \citep{2015MNRAS.454..593B}.

### 2023-08-13 paper/ms.tex
update ms

@@
 \citep{2017AJ....153..152S}.  Visually inspecting the SEDs of our
-\nallcands\ star sample, we labeled two objects as having ``good''
-infrared excesses (both W3 and W4 at $>$3$\sigma$ above the
-photospheric prediction), and three as ``possible'' infrared excess
-(only W3 at $>$3$\sigma$).
-
-The two ``good'' IR excesses belonged to TIC~193136669 (TWA~34) and
-TIC~57830249 (TWA~33).  Both are in the TW Hydrae association
-($\approx$10\,Myr), and have relatively long periods of 38\,hr and
-44\,hr respectively.  In our initial labeling, we labeled both as
-``ambiguous'' CQVs because the dips in their light curves did not show
-the rigid periodicity typical of CQVs;  their periods were also
-relatively long.  However, inspection of further sectors clarified
-that both sources are dippers (see online plots in
-Figure~\ref{fig:vet}).  Independently, TIC 193136669 has a cold
-molecular disk based on observed 1.3\,mm continuum emission and
-resolved Keplerian $^{12}{\rm CO}(2-1)$ emission
-\citep{2015A&A...582L...5R}.  It was also labeled a dipper by
+\nallcands\ star sample and the WISE images available through IRSA, we
+labeled two objects as having reliable infrared excesses (both W3 and
+W4 at $>$3$\sigma$ above the photospheric prediction).
+
+The two IR excess sources were TIC~193136669 (TWA~34) and TIC~57830249
+(TWA~33).  Both are in the TW Hydrae association ($\approx$10\,Myr),
+and have relatively long periods of 38\,hr and 44\,hr respectively.
+In our initial labeling, we labeled both as ``ambiguous'' CQVs because
+the dips in their light curves did not show the rigid periodicity
+typical of CQVs;  their periods were also relatively long.  However,
+inspection of further sectors clarified that both sources are dippers
+(see online plots in Figure~\ref{fig:vet}).  Independently, TIC
+193136669 has a cold molecular disk based on observed 1.3\,mm
+continuum emission and resolved Keplerian $^{12}{\rm CO}(2-1)$
+emission \citep{2015A&A...582L...5R}.  It was also labeled a dipper by
 \citet{2022ApJS..263...14C}; we agree with their designation, and
@@
 
-Our three ``possible'' infrared excesses were TIC~405910546,
-289840926, and 244161191.  After a literature search, we concluded
-that none have clear evidence for the presence of a disk.
-TIC~405910546, in LCC, shows a unique TESS light curve, reminiscent of
-a $P$=38\,hr singly-eclipsing binary, except with additional
-substructure during each eclipse that resembles the CQV phenomenon
-more than any other variability of which we are aware.  TIC~289840926
-($\beta$~Pic moving group, $P$=4.8\,hr), shows what we believe is a
-clear CQV signal, but has no definitive evidence for a large, dusty
-disk.  TIC~244161191 (TOI-278), in Columba, also has no definitive
-evidence for a large disk.  It is however ``multi-periodic''---in
-addition to the 7.17\,hr CQV signal, this source shows a superposed
-8.39\,hr sinusoidal signal, probably from an unresolved neighboring
-star or binary companion.
+% Our three ``possible'' infrared excesses were TIC~405910546,
+% 289840926, and 244161191.  After a literature search, we concluded
+% that none have clear evidence for the presence of a disk.
+% TIC~405910546, in LCC, shows a unique TESS light curve, reminiscent of
+% a $P$=38\,hr singly-eclipsing binary, except with additional
+% substructure during each eclipse that resembles the CQV phenomenon
+% more than any other variability of which we are aware.  TIC~289840926
+% ($\beta$~Pic moving group, $P$=4.8\,hr), shows what we believe is a
+% clear CQV signal, but has no definitive evidence for a large, dusty
+% disk.  TIC~244161191 (TOI-278), in Columba, also has no definitive
+% evidence for a large disk.  It is however ``multi-periodic''---in
+% addition to the 7.17\,hr CQV signal, this source shows a superposed
+% 8.39\,hr sinusoidal signal, probably from an unresolved neighboring
+% star or binary companion.
 
@@
 		\includegraphics[width=0.98\textwidth]{f5.pdf}
-		\vspace{-0.35cm}
+		\vspace{-0.3cm}
 		\caption{
@@
 			chunk represents one TESS orbit.  Data were acquired in Sectors
-			18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  The red
+			18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  
+			The light curve is binned to
+			15-minute intervals so that there are 96 points per day, and
+			each point is connected by a line.  Data gaps longer are not interpolated; if data are missing, nothing is
+			plotted.
+			The red
 			vertical lines highlight apparently instantaneous state changes
-			in the shape of the dip pattern.  The light curve is binned to
-			15-minute intervals so that there are 96 points per day, and
-			each point is connected by a line.  Data gaps longer than
-			15-minutes are not interpolated; if data are missing, nothing is
-			plotted.
+			in the shape of the dip pattern.  
 		}
@@
 estimate by requiring the optical depth $\tau$ of the cloud to be at
-least unity and by positing some composition for the cloud.  In other
+least unity and by positing a cloud composition.  In other
 words, a minimum constraint on the number density follows by requiring
 the cloud to be optically thick.  For cases like LP 12-502, this is
-reasonable because the transit duration implies $R_{\rm cloud}\ll
+reasonable because the transit duration of the shortest dips implies $R_{\rm cloud}\ll
 R_\star$.  Carrying out the relevant calculation assuming the
 occulting material is dust grains 1\,$\mu$m in size,
-\citet{2023MNRAS.518.4734S} find minimum cloud masses of order
+\citet{2023MNRAS.518.4734S} reported minimum cloud masses of order
 $10^{12}$\,kg (their Eq.~23), which scale linearly with both the
@@
 case, a dip ``turned off''.  It is plausible to imagine that these
-events correspond to either mass being ejected from corotation, or
-perhaps being accreted onto the star.  In either case, the
-corresponding $\dot{M} \equiv M\cdot {\rm d}N/{\rm d}t$ time-averaged
-over six months is $\approx$3$\times$$10^{-18} M_\odot\,{\rm yr}^{-1}
-\approx 1\times10^{-12} M_\oplus\,{\rm yr}^{-1}$.  Considered
-cumulatively over the $\approx$$10^8$ years for which the CQV
-phenomenon is observed, this yields a cumulative moved dust mass of
-$10^{-4}\,M_\oplus$, of order the Solar System's asteroid belt.  If
-the occulting material is gas, the masses involved would be of order
-100 times larger.  For cases in which we observe the {\it growth} of
-dips, such as the Sector~29 data for TIC~224283342, or Sector~5 of
-TIC~294328885, the dip depths typically increase by of order a few
-percent over ten to twenty days.  This growth rate yields a mass flux
-one order of magnitude larger than the earlier estimate.
+events correspond to either mass being ejected from the corotating
+clumps, or else perhaps being accreted onto the star.  In either case,
+the corresponding $\dot{M} \equiv M\cdot {\rm d}N/{\rm d}t$
+time-averaged over six months is $\approx$3$\times$$10^{-18}
+M_\odot\,{\rm yr}^{-1} \approx 1\times10^{-12} M_\oplus\,{\rm
+yr}^{-1}$.  Considered cumulatively over the $\approx$$10^8$ years for
+which the CQV phenomenon is observed, this yields a cumulative moved
+dust mass of $10^{-4}\,M_\oplus$, of order the Solar System's asteroid
+belt.  If the occulting material is gas, the masses involved would be
+of order 100 times larger.  For cases in which we observe the {\it
+growth} of dips, such as the Sector~29 data for TIC~224283342, or
+Sector~5 of TIC~294328885, the dip depths typically increase by of
+order a few percent over ten to twenty days.  This growth rate yields
+a mass flux one order of magnitude larger than the earlier estimate.
 
@@
 those in Figure~\ref{fig:cqvs}, with only two broad local minima, and
-one ``hump'' \citep{2005ApJ...630L..81T, 2022ApJ...924L..10J}.  Within
-the model proposed by Townsend et al., this is explained by the
-simplicity of the star's magnetic field, which to first-order is a
-dipole, similar to most other magnetic B stars
-\citep{2007A&A...475.1053A,2009ARA&A..47..333D}.  This approximation
-matches the qualitative behavior of both the broadband light curves,
-and the line-profile variations seen in hydrogen, helium, and carbon
-\citep{2012MNRAS.419..959O}.
+one ``hump'' (Figure~\ref{fig:bstar}), top-left; see also
+\citealt{2022ApJ...924L..10J}).  Within the model proposed by Townsend
+et al., this is explained by the simplicity of the star's magnetic
+field, which to first-order is a dipole, similar to most other
+magnetic B stars \citep{2007A&A...475.1053A,2009ARA&A..47..333D}.
+This approximation matches the qualitative behavior of both the
+broadband light curves, and the line-profile variations seen in
+hydrogen, helium, and carbon \citep{2012MNRAS.419..959O}.
 

### 2023-08-13 complexrotators/plotting.py

@@ -259,6 +259,7 @@ def plot_river(time, flux, period, outdir, titlestr=None, cmap='Blues_r',
     if not isinstance(vmax, float):
         vmax = np.nanmedian(flux)+4*np.nanstd(flux)
 
+    set_style('science')
     fig, ax = plt.subplots(figsize=(6,6))
     c = ax.pcolor(np.arange(0, period, cadence)/period - 0.5,
                   list(range(cycle_min, cycle_max)),
@@ -3547,10 +3548,10 @@ def plot_tic4029_segments(outdir):
                 fontsize=fontsize, bbox=props)
 
     x, y, dx, dy = 7.52, -44, 0, 2
-    ax.vlines(x, y, y+dy, colors='red', zorder=30, linewidths=0.5)
+    ax.vlines(x, y, y+dy, colors='red', zorder=30, linewidths=1.2)
 
     x, y, dx, dy = 5.98, -51, 0, 2
-    ax.vlines(x, y, y+dy, colors='red', zorder=30, linewidths=0.5)
+    ax.vlines(x, y, y+dy, colors='red', zorder=30, linewidths=1.2)
 
     ax.text(0.97, 0.98, 'Cycle #', va='top', ha='right', fontsize=7,
             bbox=props, transform=ax.transAxes)

### 2023-08-13 drivers/plot_river.py

@@ -97,6 +97,7 @@ def single_ticid():
     cmap = truncate_colormap(_cmap, 0, 0.95)
     ##########
 
+
     ##########
     ticid = '300651846'
     cyclewindows = [(-1, 630), (2290, 2680)]
@@ -109,8 +110,9 @@ def single_ticid():
     # specifies lc subtrxn model
     manual_csvpath = None
     savstr = model_id # can be None; used for cacheing
-    vmin, vmax = -8., 8. #  can be None; must be float
+    vmin, vmax = -6., 6. #  can be None; must be float
     cmap = 'seismic'
+
 
 
     ##########################################

### 2023-08-14 paper/ms.tex
update ms
Check <5% BANYAN probabilities

@@
 the PDC\_SAP light curves, we normalized each light curve, and then
-re-binned it into equal width bins {\bf LB: how long?} to account for
-the uneven spacing in the TESS data, as well as the data gap during
-each sector caused by satellite downlink.  We then padded the data to
+re-binned it into equal width 120-second bins to account for the
+uneven spacing in the TESS data, as well as the data gap caused by
+satellite downlink during each sector.  We then padded the data to
 ensure that the light curve had a length that was a power of two, as
-described by \citeauthor{2019ApJ...876..127Z}.  We then took the
-Fourier transform of the corrected, padded light curve using {\tt
-numpy.fft.fft} and searched for peaks with a significance of over
-12-$\sigma$ within each set of 500 bins.
+described by \citeauthor{2019ApJ...876..127Z}.  Taking the Fourier
+transform of the corrected, padded light curve using {\tt
+numpy.fft.fft}, we then searched for peaks with a significance of over
+12-$\sigma$ within a set of 500 bins. 
+{\bf LB: by the latter ``bins'', does this mean frequencies?}
 
@@
 id=3757412}.
-Elevated RUWEs imply elevated noise relative to a single-source astrometric model, which can be caused by marginally resolved point sources, astrophysical photometric variability, or astrophysical astrometric motion.}
+Elevated RUWEs imply elevated noise relative to a single-source astrometric model.
+This can be caused by marginally resolved point sources, photometric variability, or astrometric motion.}
 
@@
 Of our \ncqvsnodebunked\ confirmed and candidate CQVs, \nnotfieldbanyan\
-were associated with a nearby moving group or open cluster using
-BANYAN\,$\Sigma$.  The relevant groups are listed in
-Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  The
+were associated with a nearby moving group or open cluster, primarily using
+BANYAN\,$\Sigma$.\footnote{Two of the
+	\nnotfieldbanyan\ memberships were made with low confidence and are flagged
+	in Table~\ref{tab:thetable}.
+	One membership, of TIC~397791443 in IC\,2602, was made manually
+	from a literature search
+	\citep[e.g.][]{2020A&A...633A..99C}.}  
+The relevant groups are listed in
+Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  
+The
 most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CQVs
@@
 	USCO: Upper Scorpius \citep{2016MNRAS.461..794P}.
+	The ``(?)'' string denotes low-confidence membership.
 }

### 2023-08-15 paper/ms.tex
[WIP] ms: add binarity section

@@
 			is available online {\bf For internal collaboration review:
-				\url{https://www.dropbox.com/scl/fo/zlj3txot4cvymfb22wewu/h?dl=0&rlkey=3ec5f9o5xewrixzfkhkdenopa}}.
+				\url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
 			Panels are as follows.
@@
 
-\section{Results}
-\label{sec:results}
-
-\subsection{CQV catalog}
-\label{sec:catalog}
-
-Table~\ref{tab:thetable} lists the \nallcands\ objects identified by
-our search.  The ``high-quality sample'' includes \ngoods\ of these
-objects, which demonstrated what we viewed as unambiguous
-characteristics of the CQV phenomenon in at least one TESS sector.
-The classification of \nmaybes\ CQV candidates was ambiguous, and the
-\ndebunked\ remaining objects were false positives that we discuss below.
-The \texttt{quality} column in the table divides the three classes;
-additional data from TESS or other instruments could help resolve the
-classification of the ambiguous cases.   Of the \ncqvsnodebunked\ CQVs
-and candidate CQVs, \nbothdipfourier\ were found using both the
-dip-counting and Fourier techniques, \nyesdipnofourier\ were found
-using only the dip-counting technique, and \nyesfouriernodip\ were
-found using only the Fourier technique.  In the following, we will
-restrict our discussion to the high-quality sample, irrespective of
-discovery method.
-
-The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
-\ngoods\ CQVs.  The objects are sorted first in order of the number of
-TESS 120-second cadence sectors in which they clearly demonstrated the
-CQV phenomenon, and secondarily by descending brightness.  The top
-five objects by this metric are TIC~300651846 ($T$$=$13.5, 12
-sectors); TIC~402980664 ($T$$=$11.1, 7 sectors); TIC~89463560
-($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5 sectors); and
-TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest five CQVs span
-9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
-fastest five have periods spanning 3.6\,hr$<$$P$$<$6.2\,hr, and the
-slowest five span 27\,hr$<$$P$$<$38\,hr.  Regarding likely astrometric
-or visual binaries, \ngoodhighruwe/\ngoods\ high-quality CQVs have a
-Gaia DR2 RUWE$>$2; \nmaybehighruwe/\nmaybes\ of the ambiguous sample
-share this characteristic.\footnote{For an explanation of the renormalized unit weight error (RUWE), see the GAIA DPAC technical note \url{http://www.rssd.esa.int/doc_fetch.php?
-id=3757412}.
-Elevated RUWEs imply elevated noise relative to a single-source astrometric model.
-This can be caused by marginally resolved point sources, photometric variability, or astrometric motion.}
-
-% This is consistent with Rappaport2014's visual binary fraction
-% determined from 30/100 rapidly rotating Kepler stars having multiple
-% periodicities
-
-In terms of the light curve shapes, Figure~\ref{fig:cqvs} shows a
-broad range of variability, with anywhere from two to eight local
-minima per cycle.  Some stars show relatively ordinary modulation
-during one portion of the phased light curve, and highly structured
-modulation in the remainder of the cycle (e.g.  TIC~206544316,
-TIC~224283342, TIC~402980664).  Others show structured modulation over
-the entire span of a cycle (e.g. TIC~2234692, TIC~401789285,
-TIC~425933644, TIC~142173958).  Others show some mix between these two
-modes.
-
-A small number of objects at first glance seem reminiscent of
-eclipsing binaries, such as TIC~193831684, TIC~59836633, or
-TIC~5714469.  We believe these cases are unlikely to be eclipsing
-binaries due to the additional coherent peaks and troughs in the light
-curves, which are distinct from any binary phenomena of which we are
-aware.
-
-\subsection{Ages}
-
-Of our \ncqvsnodebunked\ confirmed and candidate CQVs, \nnotfieldbanyan\
-were associated with a nearby moving group or open cluster, primarily using
-BANYAN\,$\Sigma$.\footnote{Two of the
-	\nnotfieldbanyan\ memberships were made with low confidence and are flagged
-	in Table~\ref{tab:thetable}.
-	One membership, of TIC~397791443 in IC\,2602, was made manually
-	from a literature search
-	\citep[e.g.][]{2020A&A...633A..99C}.}  
-The relevant groups are listed in
-Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  
-The
-most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CQVs
-were also identified in the Argus association
-\citep{2019ApJ...870...27Z}, which serves as an indirect line of
-evidence supporting the reality and youth of that group.  The yield
-in Sco-Cen is not surprising, since Sco-Cen contains the majority of
-pre-main-sequence stars in the solar neighborhood, any many of its stars
-were selected for TESS 120-second cadence observations by various
-guest investigators.  Given the
-$\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there may
-be many more CQVs in Sco-Cen that remain to be discovered.
-
-For the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
-find any association, we were not able to confidently associate either
-star with any young groups.  Both do seem to show the CQV signal over
-multiple TESS sectors, and both are photometrically elevated relative
-to the main sequence.  Both were also noted by
-\citet{2021ApJ...917...23K} as being in the ``diffuse'' population of
-$<$50\,Myr stars near the Sun.
-
-Our search confirms that the CQV phenomenon persists for at least
-$\approx$150\,Myr.  Table~\ref{tab:thetable} includes three
-$\approx$150\,Myr CQVs in AB~Dor \citep{2015MNRAS.454..593B}, a
-$\approx$112\,Myr old Pleiades CQV \citep{2015ApJ...813..108D}, and a
-similarly-aged Psc-Eri member \citep{2020A&A...639A..64R}.  To our
-knowledge, TIC~332517282 in AB~Dor was the previous record-holder for
-oldest-known CQV \citep{2019ApJ...876..127Z,2022AJ....163..144G}; at
-least one unambiguous CQV (EPIC~211070495) and a few other candidates
-were also previously known in the Pleiades
-\citep{2016AJ....152..114R}.
-
-% NOTE: it'd be useful to get an RV for this one...
-
-The upper age limit for CQVs may even pass 200\,Myr, based on the
-candidate membership of TIC~294328887 in the Carina Near moving group
-\citep{2006ApJ...649L.115Z}.  This group's $200 \pm 50$\,Myr age
-is based on the lithium sequence of its G-dwarfs
-\citep{2006ApJ...649L.115Z}, which shows a coeval population of stars
-older than the Pleiades and younger than the 400\,Myr Ursa Major
-moving group.  The formal BANYAN-$\Sigma$ membership probability is
-however somewhat low, perhaps due to the missing radial velocity.
-This could be resolved by acquiring even a
-medium-resolution spectrum.  An independent assessment of the group's
-kinematics using Gaia data, and its rotation sequence using TESS,
-could lend further credence in such an analysis.
-
-\subsection{Infrared excesses}
-\label{subsec:irexcess}
-
-Most CQVs in our catalog did not show infrared excesses in the W1-W4
-bands, which is typical for this class of object
-\citep{2017AJ....153..152S}.  Visually inspecting the SEDs of our
-\nallcands\ star sample and the WISE images available through IRSA, we
-labeled two objects as having reliable infrared excesses (both W3 and
-W4 at $>$3$\sigma$ above the photospheric prediction).
-
-The two IR excess sources were TIC~193136669 (TWA~34) and TIC~57830249
-(TWA~33).  Both are in the TW Hydrae association ($\approx$10\,Myr),
-and have relatively long periods of 38\,hr and 44\,hr respectively.
-In our initial labeling, we labeled both as ``ambiguous'' CQVs because
-the dips in their light curves did not show the rigid periodicity
-typical of CQVs;  their periods were also relatively long.  However,
-inspection of further sectors clarified that both sources are dippers
-(see online plots in Figure~\ref{fig:vet}).  Independently, TIC
-193136669 has a cold molecular disk based on observed 1.3\,mm
-continuum emission and resolved Keplerian $^{12}{\rm CO}(2-1)$
-emission \citep{2015A&A...582L...5R}.  It was also labeled a dipper by
-\citet{2022ApJS..263...14C}; we agree with their designation, and
-label it an ``impostor'' CQV in Table~\ref{tab:thetable}.  TIC
-57830249 (TWA~33) also has previously detected 1.3\,mm continuum
-emission \citep{2015A&A...582L...5R}, suggestive of cold dust grains
-being present.  It is also a dipper.  Section~\ref{subsec:discdippers}
-highlights plausible evolutionary connections between CQVs and dippers
-in light of these ``misclassifications'' .
-
-% Our three ``possible'' infrared excesses were TIC~405910546,
-% 289840926, and 244161191.  After a literature search, we concluded
-% that none have clear evidence for the presence of a disk.
-% TIC~405910546, in LCC, shows a unique TESS light curve, reminiscent of
-% a $P$=38\,hr singly-eclipsing binary, except with additional
-% substructure during each eclipse that resembles the CQV phenomenon
-% more than any other variability of which we are aware.  TIC~289840926
-% ($\beta$~Pic moving group, $P$=4.8\,hr), shows what we believe is a
-% clear CQV signal, but has no definitive evidence for a large, dusty
-% disk.  TIC~244161191 (TOI-278), in Columba, also has no definitive
-% evidence for a large disk.  It is however ``multi-periodic''---in
-% addition to the 7.17\,hr CQV signal, this source shows a superposed
-% 8.39\,hr sinusoidal signal, probably from an unresolved neighboring
-% star or binary companion.
-
-\begin{figure*}[!tp]
-	\begin{center}
-		\centering
-		\includegraphics[width=\textwidth]{f4.pdf}
-		\vspace{-0.6cm}
-		\caption{
-			{\bf CQVs keep their periods but change their shapes.}
-			Out of the \ngoods\ CQVs in Figure~\ref{fig:cqvs}, 32 had
-			120-second cadence TESS data available for a baseline of at
-			least two years; the 27 brightest are shown here due to space
-			constraints.  Each panel shows one sector of TESS data, and is
-			phased to its deepest minimum in flux.  Each panel's title shows
-			the TIC identifier and approximate period in hours.  Text insets
-			show the TESS sector numbers, which generally span two years, or
-			at least 1{,}000 cycles.  The vertical scale is fixed across
-			sectors to clarify shape changes.  Gray circles are raw 2-minute
-			data; colored circles bin to 300 points per cycle. 
-		}
-		\label{fig:evoln}
-	\end{center}
-\end{figure*}
-
-\begin{figure*}[!tp]
-	\begin{center}
-		\centering
-		\includegraphics[width=0.98\textwidth]{f5.pdf}
-		\vspace{-0.3cm}
-		\caption{
-			{\bf LP 12-502 (TIC~402980664) light curve}, where each time
-			chunk represents one TESS orbit.  Data were acquired in Sectors
-			18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  
-			The light curve is binned to
-			15-minute intervals so that there are 96 points per day, and
-			each point is connected by a line.  Data gaps longer are not interpolated; if data are missing, nothing is
-			plotted.
-			The red
-			vertical lines highlight apparently instantaneous state changes
-			in the shape of the dip pattern.  
-		}
-		\label{fig:lplc}
-	\end{center}
-\end{figure*}
-
-\section{CQV evolution}
-\label{sec:evoln}
-
-\subsection{Evolution over two year baseline}
-
-Figure~\ref{fig:evoln} shows ``before'' and ``after'' views of 27 CQVs
-for which TESS 120-second cadence observations were available at least
-two years apart.  Such a baseline was available for 32 of the
-confirmed \ngoods\ CQVs in our catalog; for plotting purposes we show
-the brightest 27.  We have phased each sector to its own local minimum
-because for most of the sources we do not know the period at the
-precision necessary to be able to accurately propagate an ephemeris
-over two years.  The achievable period precision, $\sigma_P$, can be
-estimated as
-\begin{equation}
-  \sigma_{P} = \frac { \sigma_{\phi} P } { N_{\rm baseline} },
-  \label{eq:periodprecision}
-\end{equation}
-for $N_{\rm baseline}$ the number of cycles in the observed baseline
-and $\sigma_{\phi}$ the phase precision with which any one feature
-(e.g.~a dip, or the overall shape of the sinusoidal envelope) can be
-tracked.  Assuming $\sigma_\phi$$\approx$$0.02$ and a 20-day baseline
-over a single TESS sector yields
-$\sigma_{P}$$\approx$$0.25^{+0.38}_{-0.14}$\,minutes for the
-population shown in Figure~\ref{fig:evoln}; propagated forward 1{,}000
-cycles yields a typical ephemeris uncertainty range of 2-11\,hours.
-Measuring the periods for each sector independently, there did not
-seem to be any significant ($>$3$\sigma$) period changes.  This
-implies an absolute period stability of $\lesssim$0.1\% over the
-two-year baseline.
-
-Of the 27 CQVs in Figure~\ref{fig:evoln}, a few show clear signs of
-the CQV phenomenon in one sector, and marginal or non-existent signs
-in the other.  While there is subjectivity in this assessment, to our
-eyes cases for which at least one sector would be flagged as
-``ambiguous'' include
-TIC~368129164 (Sector 23 might be labeled an EB),
-TIC~177309964 (Sector 38 would be simply a rotating star),
-TIC~404144841 (Sector 38 looks like a rotating star),
-TIC~201898222 (Sector 3 looks like a rotating star),
-TIC~144486786 (Sector 32 might be an RS CVn),
-and
-TIC~38820496 (Sector 28 might be an RS CVn).
-TIC~193831684, assessed on a single-sector basis, would probably be
-labeled an eclipsing binary---in fact, \citet{2021ApJ...912..123J}
-implicitly have already given this source such a label.  However,
-based on the the shape evolution between Sectors 13 and 39, it is a
-CQV.  Based on the fraction of sources overall that ``turned off'',
-the observed shape evolution implies that CQVs have a duty cycle of
-$\approx$75\%.  This type of correction is worth including in
-population-level estimates of how intrinsically common CQVs are in the
-low-mass stellar population \citep[e.g.][]{2022AJ....163..144G}.
-
-\begin{figure*}[!t]
-	\begin{center}
-		\centering
-		\includegraphics[width=0.98\textwidth]{f6.pdf}
-		\vspace{-0.3cm}
-		\caption{
-			{\bf Evolution of LP 12-502} ($P$=18.6\,h) at fixed period and
-			epoch over three years.  Each panel shows one (stacked) TESS
-			orbit; small text denotes relative cycle number.  There are 200
-			binned black points per cycle.  The TESS pointing law dictates
-			the large time gaps between Cycles 64-248, 315-1233, and
-			1264-1410; larger gaps tend to yield larger shape changes.  The
-			dips usually evolve over tens to hundreds of cycles.  However
-			cycles 1233-1264 show a dip that ``switched'' from a depth and
-			duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than one
-			cycle (cf.~Figure~\ref{fig:lplc}).
-		}
-		\label{fig:lp}
-	\end{center}
-\end{figure*}
-
-%\begin{figure*}[!t]
-%	\begin{center}
-%		\includegraphics[width=0.45\textwidth]{ANNOTATED_resid_TIC_402980664_P18.5611_2min_phase_timegroups.png}
-%	\end{center}
-%	\vspace{-0.4cm}
-%	\caption{
-%		{\bf Alternative view of the evolution of LP 12-502}
-%		(Figure~\ref{fig:lp}), arranged to emphasize changes in transit
-%		times.  There are 200 binned black points per $P$=18.5611\,hr cycle; a two-harmonic
-%		sinusoid has been subtracted from the PDC\_SAP light curve.
-%		Vertical gray lines are underplotted to help guide the eye to instances
-%		in which preferred dip phases synchronize over long baselines.
-%		The orange and green lines guide the eye to where dips
-%		change the positions of their local minima; orange
-%		lines have periods slightly less than $P$, the green line has
-%		a period greater than $P$.
-%	}
-%	\label{fig:lp2}
-%\end{figure*}
-
-\begin{figure*}[!t]
-	\begin{center}
-		\subfloat{
-			\includegraphics[width=0.46\textwidth]{f7a.pdf}
-			\includegraphics[width=0.46\textwidth]{f7b.pdf}
-		}
-		\vspace{-0.2cm}
-
-		\subfloat{
-			\includegraphics[width=0.46\textwidth]{f7d.pdf}
-			\includegraphics[width=0.46\textwidth]{f7c.pdf}
-		}
-	\end{center}
-	\vspace{-0.4cm}
-	\caption{
-		{\bf River plots of the LP 12-502 light curve}, showing (clockwise
-		from top-left) Sectors 18-19, 25-26, 53, and 58-59.  A
-		two-harmonic sinusoid has been subtracted to highlight the sharp
-		dips.  In Sectors 25-26 (cycles 248-315), periods are visible at
-		the fundamental period of 18.5611\,hr, as well as at faster and
-		slower relative periods (e.g. $\phi$$\approx$0.3 and
-		$\phi$$\approx$0.1).  Similar instances of multiple simultaneous
-		periods are also visible in Sector 53 and 58-59.  White chunks
-		denote missing data.
-	}
-	\label{fig:lpriver0}
-\end{figure*}
-
-\subsection{Evolution over adjacent sectors, \& LP 12-502}
-
-A small fraction of our objects were in regions of sky with
-many sectors of adjacent TESS data.  Out of this already small sample, LP 12-502
-(TIC 402980664; $d$=21\,pc, $J$=9.4, $T$=11.1) stood out due to the
-quality and content of its data.  We discuss another interesting
-source, TIC~300651846, in Appendix~\ref{app:tic3006}.  In this
-section, we first present the LP 12-502 observations
-(Section~\ref{subsec:lpobservations}), and then highlight their
-implications (Section~\ref{subsec:lplessons}).
-
-\subsubsection{LP 12-502 observations}
-\label{subsec:lpobservations}
-
-Figure~\ref{fig:lplc} shows all available data for LP 12-502 from TESS
-Sectors 18, 19, 25, 26, 53, 58, and 59, split into successive orbits.
-The star was observed at 120-second cadence whenever it was observable
-by TESS.  We binned the light curve to 15-minute intervals for visual
-clarity, and required at least one (120-second cadence) flux
-measurement per bin.  Points more than 2.5$\sigma$ above the median
-are drawn in gray, also for visual clarity.  Missing data are not
-drawn.  Figure~\ref{fig:lp} then shows the same data, but stacked into
-successive TESS orbits spanning half a lunar month each.  Finally,
-Figure~\ref{fig:lpriver0} shows ``river plots'' of the same data,
-split into similar intervals: the Sector 18-19 data, 25-26 data, 53
-data, and 58-59 data.  The river plots are subject to one additional
-processing step: we fitted and subtracted a maximum-likelihood
-two-harmonic sinusoid independently from the Sector 18-19 data, 25-26
-data, and 53, 58, and 59 data in order to accentuate changes in the
-dip timing and structure.
-
-The average period, determined by measuring the PDM peak period over
-each sector independently, was $\langle P \rangle = 18.5560$\,hr.  The
-range between the maximum and minimum sector-specific periods was
-measured to be about one minute.   However, in detail, a period shift
-of $\pm$1\,minute would yield major phase drifts over the baseline;
-that time interval corresponds to $\approx$1/1000$^{\rm th}$ of a
-period, and we have observed 1500 cycles.  By fine-tuning over a grid
-in period, we found $P=18.5611 \pm 0.0001$\,hr, which seems to track
-certain features in the LP 12-502 light curve well over the entire
-dataset.
-
-What exactly is observed?  For the first 64 cycles, the star shows a
-pattern reminiscent of an eclipsing binary, with four obvious local
-minima.  We dub these dips $\{ 1, 2, 3, 4 \}$ at phases $\{ -0.28,
--0.08, 0, 0.25 \}$, respectively.  Over cycles 0-64, the depth of dips
-1 and 3 remain roughly fixed.  However dip 4 decreases in depth by
-about 2\%, while dip 2 increases in depth, by about the same amount
-(see Figure~\ref{fig:lp}).  During cycles 48-64, a fifth dip may also
-be emerging, in the main ``large'' dip group.
-
-There is then a 6-month (184 cycle) gap to Cycles 248-315, which show
-two highly structured dip complexes, plus a small leading dip.  The
-single leading dip is present at the same phase as in cycles 0-64, and
-is therefore likely to be the same struture.  Along a similar line of
-logic, it seems plausible that the first ``dip complex'' during cycles
-248-264 represents an evolution of the initial complex seen during
-cycles 0-64, though with reduced depth.  During cycles 266-310, an
-additional local minimum develops between the two complexes; this
-feature is best visualized on the river plots
-(Figure~\ref{fig:lpriver0}), and we describe its (shorter) period
-below.
-
-The second dip complex during cycles 248-315 shows the most
-substructure.  During e.g.~cycles 283-298, this single complex shows
-six local minima.  The deepest dip is sharp: it shows a flux excursion
-of 3.5\% over about 22 minutes (0.02\,$P$), which is the steepest
-slope exhibited anywhere in the LP~12-502 dataset.  After the sharp
-dip, there is a roughly exponential fall-off spanning about a quarter
-of a period, punctuated by coherent local minima and maxima which in
-detail (Figure~\ref{fig:lpriver0}) have slightly longer periods than
-the sharp dip.  The sharp leading dip only decreases in depth
-following a sudden state-switch at BTJD 2030.7 (cycles 299-315), which
-happens during a flare (Figure~\ref{fig:lplc}).  The trailing dips
-remain thereafter.
-
-Sectors 53--58 (cycles 1233-1481) are comparatively tame; they showed
-only four to six dips per cycle.  Some dips remain stable in depth and
-duration over this five month interval.  Other dips grow, like the one
-at $\phi = +0.06$ between cycles 1499 and 1481.  Other dips, such as
-the one at $\phi = +0.12$ in cycles 1233-1264, disappear entirely.
-The most dramatic state switch occurs during cycles 1233-1247, when a
-large dip ``switches'' from a depth of 3\% and duration of 3 hours to
-a depth of 0.3\%, and a duration of 1 hour.
-
-\subsubsection{Lessons from LP 12-502}
-\label{subsec:lplessons}
-
-{\sc State-switches reveal dip independence}---The state-switches seen
-in cycles 1233-1247 and 299-315 confirm that dips can disappear in
-less than one cycle, a point which has been previously appreciated
-\citep{2017AJ....153..152S}.  What is new in these particular changes
-is that the morphology changes show that the dips can be {\it
-independent} and {\it additive}.  For example, throughout cycles
-1233-1264, there are three local minima between phases of 0 and 0.3.
-They all have identical ingress times.  The shape change during the
-transition implies that the leading dip that ``turned off'' (reduced
-its depth and duration), while the trailing two dips remained fixed.
-This is visible in Figure~\ref{fig:lp}.
-In other words, the structures producing these dips are independent to
-the degree that one can undergo a severe change while the others
-remain identical.  The state switches during cycles
-248-264 and 299-315 share the same characteristic: it is always the
-{\it leading} dip of a complex that ``switches off'', leaving the
-(fixed-depth) trailing dips in its wake.
-
-{\sc Slow growth; rapid death}---Although there are a few instances in
-which we observe dips switch off over less than one cycle, dip
-growth seems to happen more slowly.  For instance, the dip that grows
-between phase 0 and 0.1 between cycles 260-290 begins to become
-visible around BTJD 1993.2, and growths in depth by about 2\% over
-about six cycles, to become visible by eye by BTJD 1997.7.
-The evolution of this particular dip is most clear in the river plots.
-The evolution of the latter dip group in cycles 1410-1481 is another
-example of this slow mode of dip growth.
-
-% 16 px vs 310 px for a full phase
-% Based on our SED fitting $R_\star=0.369\,R_\odot$ star, and from the
-% isochrone mass, $M_\star=0.215\,M_\odot$
-
-{\sc Dip durations}---The shortest dip duration for any of the
-individual LP 12-502 dips seems to be $\approx$0.06\,$P$ $\approx$
-1.08\,hr.  In comparison, using the stellar radius and mass derived in
-Section~\ref{subsec:starprops}, the characteristic timescale $T_{\rm
-dur} \equiv R_\star P / (\pi a)$ for the transit of a point-source at
-corotation is 1.02$\pm$0.10\,hr.  This means that while
-some of the LP 12-502 dips are sufficiently long to require structures
-that are extended in orbital azimuth, the durations of other dips are
-consistent with effective radii for the occulting material $R_{\rm
-eff} \ll R_\star$.  This implies $a/R_\star \approx 5.8$ for this
-material; the analogous timescale at the stellar surface is
-about six times slower.
-
-{\sc Dip periods}---Most of the LP 12-502 dips repeat with a period of
-$P=18.5611 \pm 0.0001$\,hr.  However the river plots
-(Figure~\ref{fig:lpriver0}) reveal that the
-light curve has specific dips with simultaneous but distinct periods.  For instance, in sectors 25-26, the
-local minimum that develops around cycle 262 has a period faster than
-the mean period by $\approx$0.1\%, while some of the trailing local
-minima in the main dip complex have periods slower than the mean
-period, by $\approx$0.04\%.  In addition to the fundamental period, we
-were able to identify at least four distinct periods shown by specific
-dips over the full Sectors 18-59 dataset, including periods at
-18.5683, 18.5672, 18.5473, and 18.5145\,hr, with a typical measurement
-uncertainty of $\approx$0.0002\,hr.  If each period corresponds to an
-individual dust or gas clump, then this implies that multiple distinct clumps can orbit
-the star simultaneously, at marginally different separations.
-
-\section{Discussion}
-\label{sec:discussion}
-
 \begin{figure*}[!t]
@@
 
+\section{Results}
+\label{sec:results}
+
+\subsection{CQV catalog}
+\label{sec:catalog}
+
+Table~\ref{tab:thetable} lists the \nallcands\ objects identified by
+our search.  The ``high-quality sample'' includes \ngoods\ of these
+objects, which demonstrated what we viewed as unambiguous
+characteristics of the CQV phenomenon in at least one TESS sector.
+The classification of \nmaybes\ CQV candidates was ambiguous, and the
+\ndebunked\ remaining objects were false positives that we discuss below.
+The \texttt{quality} column in the table divides the three classes;
+additional data from TESS or other instruments could help resolve the
+classification of the ambiguous cases.   Of the \ncqvsnodebunked\ CQVs
+and candidate CQVs, \nbothdipfourier\ were found using both the
+dip-counting and Fourier techniques, \nyesdipnofourier\ were found
+using only the dip-counting technique, and \nyesfouriernodip\ were
+found using only the Fourier technique.  In the following, we will
+restrict our discussion to the high-quality sample, irrespective of
+discovery method.
+
+The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
+\ngoods\ CQVs.  The objects are sorted first in order of the number of
+TESS 120-second cadence sectors in which they clearly demonstrated the
+CQV phenomenon, and secondarily by descending brightness.  The top
+five objects by this metric are TIC~300651846 ($T$$=$13.5, 12
+sectors); TIC~402980664 ($T$$=$11.1, 7 sectors); TIC~89463560
+($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5 sectors); and
+TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest five CQVs span
+9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
+fastest five have periods spanning 3.6\,hr$<$$P$$<$6.2\,hr, and the
+slowest five span 27\,hr$<$$P$$<$38\,hr.
+
+% This is consistent with Rappaport2014's visual binary fraction
+% determined from 30/100 rapidly rotating Kepler stars having multiple
+% periodicities
+
+In terms of the light curve shapes, Figure~\ref{fig:cqvs} shows a
+broad range of variability, with anywhere from two to eight local
+minima per cycle.  Some stars show relatively ordinary modulation
+during one portion of the phased light curve, and highly structured
+modulation in the remainder of the cycle (e.g.  TIC~206544316,
+TIC~224283342, TIC~402980664).  Others show structured modulation over
+the entire span of a cycle (e.g. TIC~2234692, TIC~401789285,
+TIC~425933644, TIC~142173958).  Others show some mix between these two
+modes.
+
+A small number of objects at first glance seem reminiscent of
+eclipsing binaries, such as TIC~193831684, TIC~59836633, or
+TIC~5714469.  We believe these cases are unlikely to be eclipsing
+binaries due to the additional coherent peaks and troughs in the light
+curves, which are distinct from any binary phenomena of which we are
+aware.
+
+\subsection{Ages}
+
+Of our \ncqvsnodebunked\ confirmed and candidate CQVs, \nnotfieldbanyan\
+were associated with a nearby moving group or open cluster, primarily using
+BANYAN\,$\Sigma$.\footnote{Two of the
+	\nnotfieldbanyan\ memberships were made with low confidence and are flagged
+	in Table~\ref{tab:thetable}.
+	One membership, of TIC~397791443 in IC\,2602, was made manually
+	from a literature search
+	\citep[e.g.][]{2020A&A...633A..99C}.}  
+The relevant groups are listed in
+Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  
+The
+most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CQVs
+were also identified in the Argus association
+\citep{2019ApJ...870...27Z}, which serves as an indirect line of
+evidence supporting the reality and youth of that group.  The yield
+in Sco-Cen is not surprising, since Sco-Cen contains the majority of
+pre-main-sequence stars in the solar neighborhood, any many of its stars
+were selected for TESS 120-second cadence observations by various
+guest investigators.  Given the
+$\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there may
+be many more CQVs in Sco-Cen that remain to be discovered.
+
+For the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
+find any association, we were not able to confidently associate either
+star with any young groups.  Both do seem to show the CQV signal over
+multiple TESS sectors, and both are photometrically elevated relative
+to the main sequence.  Both were also noted by
+\citet{2021ApJ...917...23K} as being in the ``diffuse'' population of
+$<$50\,Myr stars near the Sun.
+
+Our search confirms that the CQV phenomenon persists for at least
+$\approx$150\,Myr.  Table~\ref{tab:thetable} includes three
+$\approx$150\,Myr CQVs in AB~Dor \citep{2015MNRAS.454..593B}, a
+$\approx$112\,Myr old Pleiades CQV \citep{2015ApJ...813..108D}, and a
+similarly-aged Psc-Eri member \citep{2020A&A...639A..64R}.  To our
+knowledge, TIC~332517282 in AB~Dor was the previous record-holder for
+oldest-known CQV \citep{2019ApJ...876..127Z,2022AJ....163..144G}; at
+least one unambiguous CQV (EPIC~211070495) and a few other candidates
+were also previously known in the Pleiades
+\citep{2016AJ....152..114R}.
+
+% NOTE: it'd be useful to get an RV for this one...
+
+The upper age limit for CQVs may even pass 200\,Myr, based on the
+candidate membership of TIC~294328887 in the Carina Near moving group
+\citep{2006ApJ...649L.115Z}.  This group's $200 \pm 50$\,Myr age
+is based on the lithium sequence of its G-dwarfs
+\citep{2006ApJ...649L.115Z}, which shows a coeval population of stars
+older than the Pleiades and younger than the 400\,Myr Ursa Major
+moving group.  The formal BANYAN-$\Sigma$ membership probability is
+however somewhat low, perhaps due to the missing radial velocity.
+This could be resolved by acquiring even a
+medium-resolution spectrum.  An independent assessment of the group's
+kinematics using Gaia data, and its rotation sequence using TESS,
+could lend further credence in such an analysis.
+
+\subsection{Infrared excesses}
+\label{subsec:irexcess}
+
+Most CQVs in our catalog did not show infrared excesses in the W1-W4
+bands, which is typical for this class of object
+\citep{2017AJ....153..152S}.  Visually inspecting the SEDs of our
+\nallcands\ star sample and the WISE images available through IRSA, we
+labeled two objects as having reliable infrared excesses (both W3 and
+W4 at $>$3$\sigma$ above the photospheric prediction).
+
+The two IR excess sources were TIC~193136669 (TWA~34) and TIC~57830249
+(TWA~33).  Both are in the TW Hydrae association ($\approx$10\,Myr),
+and have relatively long periods of 38\,hr and 44\,hr respectively.
+In our initial labeling, we labeled both as ``ambiguous'' CQVs because
+the dips in their light curves did not show the rigid periodicity
+typical of CQVs;  their periods were also relatively long.  However,
+inspection of further sectors clarified that both sources are dippers
+(see online plots in Figure~\ref{fig:vet}).  Independently, TIC
+193136669 has a cold molecular disk based on observed 1.3\,mm
+continuum emission and resolved Keplerian $^{12}{\rm CO}(2-1)$
+emission \citep{2015A&A...582L...5R}.  It was also labeled a dipper by
+\citet{2022ApJS..263...14C}; we agree with their designation, and
+label it an ``impostor'' CQV in Table~\ref{tab:thetable}.  TIC
+57830249 (TWA~33) also has previously detected 1.3\,mm continuum
+emission \citep{2015A&A...582L...5R}, suggestive of cold dust grains
+being present.  It is also a dipper.  Section~\ref{subsec:discdippers}
+highlights plausible evolutionary connections between CQVs and dippers
+in light of these ``misclassifications'' .
+
+% Our three ``possible'' infrared excesses were TIC~405910546,
+% 289840926, and 244161191.  After a literature search, we concluded
+% that none have clear evidence for the presence of a disk.
+% TIC~405910546, in LCC, shows a unique TESS light curve, reminiscent of
+% a $P$=38\,hr singly-eclipsing binary, except with additional
+% substructure during each eclipse that resembles the CQV phenomenon
+% more than any other variability of which we are aware.  TIC~289840926
+% ($\beta$~Pic moving group, $P$=4.8\,hr), shows what we believe is a
+% clear CQV signal, but has no definitive evidence for a large, dusty
+% disk.  TIC~244161191 (TOI-278), in Columba, also has no definitive
+% evidence for a large disk.  It is however ``multi-periodic''---in
+% addition to the 7.17\,hr CQV signal, this source shows a superposed
+% 8.39\,hr sinusoidal signal, probably from an unresolved neighboring
+% star or binary companion.
+
+\subsection{Binarity}
+\label{subsec:binarity}
+
+The main types of binarity of interest in this work were those that
+could confuse our understanding of CQVs.  For instance, within the
+21$''$ TESS pixels, binary companions can produce multiple photometric
+signals and hinder our ability to correctly identify the star hosting
+the CQV signal.  Binary companions can also bias photometric magnitude
+and color measurements, thereby biasing our stellar parameter
+estimates.  To attempt to identify binaries, we considered the
+following lines of information.
+%
+\paragraph{Radial velocity scatter}---We examined diagrams of the Gaia
+DR3 ``radial velocity error'' as a function of stellar color for all
+\ncqvsnodebunked\ CQVs and candidate CQVs.  Since this quantity
+represents the standard deviation of the non-published Gaia RV time
+series, outliers can suggest single-lined spectroscopic binarity.
+These plots showed two clusters of stars, at $\lesssim$10\,\kms and
+20-25\,\kms.  We there adopted a threshold of $20$\,km\,s$^{-1}$
+to flag possible single-lined spectroscopic binaries, which selected
+\nrvscatter\ stars: TIC~405910546, TIC~224283342, and TIC~280945693.
+%
+\paragraph{RUWE}---We examined plots of Gaia DR3 renormalized unit
+weight error (RUWE) as a function of brightness as color.\footnote{For
+an explanation of the renormalized unit weight error (RUWE), see the
+GAIA DPAC technical note \url{http://www.rssd.esa.int/doc_fetch.php?
+id=3757412}.}  Elevated RUWEs imply elevated noise relative to a
+single-source astrometric model.  This can be caused by marginally
+resolved point sources skewing the single-transit centroid
+measurements,  intrinsic photometric variability, or intrinsic
+astrometric motion.  Based on this exercise, we adopted a threshold of
+RUWE$_{\rm DR3}$ $>$ 2 to flag sources with excess astrometric noise.
+This threshold yielded \ngoodhighruwe/\ngoods\ high-quality CQVs with
+a Gaia DR2 RUWE$>$2; \nmaybehighruwe/\nmaybes\ of the ambiguous sample
+share this characteristic.
+%
+\paragraph{Gaia DR3 non-single stars}---Gaia DR3 included a
+``non\_single\_star'' column that flagged known or suspected
+eclipsing, astrometric, and spectroscopic binaries.  None of the stars
+in our CQV sample were identified as possible binaries in this column.
+%
+\paragraph{Multiple periodic TESS signals}---During our visual
+analysis of the TESS light curves and PDM periodograms, we flagged
+sources with beating light curves, and with PDM periodograms that
+showed multiple periods.  We also attempted to disentangle the two
+signals by subtracting the mean CQV signal over each sector, and then
+repeating the phase-dispersion minization analysis.  The results of
+this effort are summarized in the secondary periods, $P_{\rm sec}$,
+listed in Table~\ref{tab:thetable}.  {\bf We found additional periods
+in XX of the CQVs, of which YY also had elevated RUWEs}.
+
+%FIXME FIXME FIXME:
+% Need to actually incorporate into the table!
+
+We incorporated each of these sources of information into a column in
+Table~\ref{tab:thetable} that expresses whether any given source
+passed each of the binarity indicators.
+We discuss some important--and complicated--aspects of the systems
+that seem to be binary in Section~\ref{subsec:discbinary}.
+
+\section{CQV evolution}
+\label{sec:evoln}
+
+\begin{figure*}[!tp]
+	\begin{center}
+		\centering
+		\includegraphics[width=\textwidth]{f4.pdf}
+		\vspace{-0.6cm}
+		\caption{
+			{\bf CQVs keep their periods but change their shapes.}
+			Out of the \ngoods\ CQVs in Figure~\ref{fig:cqvs}, 32 had
+			120-second cadence TESS data available for a baseline of at
+			least two years; the 27 brightest are shown here due to space
+			constraints.  Each panel shows one sector of TESS data, and is
+			phased to its deepest minimum in flux.  Each panel's title shows
+			the TIC identifier and approximate period in hours.  Text insets
+			show the TESS sector numbers, which generally span two years, or
+			at least 1{,}000 cycles.  The vertical scale is fixed across
+			sectors to clarify shape changes.  Gray circles are raw 2-minute
+			data; colored circles bin to 300 points per cycle. 
+		}
+		\label{fig:evoln}
+	\end{center}
+\end{figure*}
+
+\begin{figure*}[!tp]
+	\begin{center}
+		\centering
+		\includegraphics[width=0.98\textwidth]{f5.pdf}
+		\vspace{-0.3cm}
+		\caption{
+			{\bf LP 12-502 (TIC~402980664) light curve}, where each time
+			chunk represents one TESS orbit.  Data were acquired in Sectors
+			18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  
+			The light curve is binned to
+			15-minute intervals so that there are 96 points per day, and
+			each point is connected by a line.  Data gaps longer are not interpolated; if data are missing, nothing is
+			plotted.
+			The red
+			vertical lines highlight apparently instantaneous state changes
+			in the shape of the dip pattern.  
+		}
+		\label{fig:lplc}
+	\end{center}
+\end{figure*}
+
+\subsection{Evolution over two year baseline}
+
+Figure~\ref{fig:evoln} shows ``before'' and ``after'' views of 27 CQVs
+for which TESS 120-second cadence observations were available at least
+two years apart.  Such a baseline was available for 32 of the
+confirmed \ngoods\ CQVs in our catalog; for plotting purposes we show
+the brightest 27.  We have phased each sector to its own local minimum
+because for most of the sources we do not know the period at the
+precision necessary to be able to accurately propagate an ephemeris
+over two years.  The achievable period precision, $\sigma_P$, can be
+estimated as
+\begin{equation}
+  \sigma_{P} = \frac { \sigma_{\phi} P } { N_{\rm baseline} },
+  \label{eq:periodprecision}
+\end{equation}
+for $N_{\rm baseline}$ the number of cycles in the observed baseline
+and $\sigma_{\phi}$ the phase precision with which any one feature
+(e.g.~a dip, or the overall shape of the sinusoidal envelope) can be
+tracked.  Assuming $\sigma_\phi$$\approx$$0.02$ and a 20-day baseline
+over a single TESS sector yields
+$\sigma_{P}$$\approx$$0.25^{+0.38}_{-0.14}$\,minutes for the
+population shown in Figure~\ref{fig:evoln}; propagated forward 1{,}000
+cycles yields a typical ephemeris uncertainty range of 2-11\,hours.
+Measuring the periods for each sector independently, there did not
+seem to be any significant ($>$3$\sigma$) period changes.  This
+implies an absolute period stability of $\lesssim$0.1\% over the
+two-year baseline.
+
+Of the 27 CQVs in Figure~\ref{fig:evoln}, a few show clear signs of
+the CQV phenomenon in one sector, and marginal or non-existent signs
+in the other.  While there is subjectivity in this assessment, to our
+eyes cases for which at least one sector would be flagged as
+``ambiguous'' include
+TIC~368129164 (Sector 23 might be labeled an EB),
+TIC~177309964 (Sector 38 would be simply a rotating star),
+TIC~404144841 (Sector 38 looks like a rotating star),
+TIC~201898222 (Sector 3 looks like a rotating star),
+TIC~144486786 (Sector 32 might be an RS CVn),
+and
+TIC~38820496 (Sector 28 might be an RS CVn).
+TIC~193831684, assessed on a single-sector basis, would probably be
+labeled an eclipsing binary---in fact, \citet{2021ApJ...912..123J}
+implicitly have already given this source such a label.  However,
+based on the the shape evolution between Sectors 13 and 39, it is a
+CQV.  Based on the fraction of sources overall that ``turned off'',
+the observed shape evolution implies that CQVs have a duty cycle of
+$\approx$75\%.  This type of correction is worth including in
+population-level estimates of how intrinsically common CQVs are in the
+low-mass stellar population \citep[e.g.][]{2022AJ....163..144G}.
+
+\begin{figure*}[!t]
+	\begin{center}
+		\centering
+		\includegraphics[width=0.98\textwidth]{f6.pdf}
+		\vspace{-0.3cm}
+		\caption{
+			{\bf Evolution of LP 12-502} ($P$=18.6\,h) at fixed period and
+			epoch over three years.  Each panel shows one (stacked) TESS
+			orbit; small text denotes relative cycle number.  There are 200
+			binned black points per cycle.  The TESS pointing law dictates
+			the large time gaps between Cycles 64-248, 315-1233, and
+			1264-1410; larger gaps tend to yield larger shape changes.  The
+			dips usually evolve over tens to hundreds of cycles.  However
+			cycles 1233-1264 show a dip that ``switched'' from a depth and
+			duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than one
+			cycle (cf.~Figure~\ref{fig:lplc}).
+		}
+		\label{fig:lp}
+	\end{center}
+\end{figure*}
+
+%\begin{figure*}[!t]
+%	\begin{center}
+%		\includegraphics[width=0.45\textwidth]{ANNOTATED_resid_TIC_402980664_P18.5611_2min_phase_timegroups.png}
+%	\end{center}
+%	\vspace{-0.4cm}
+%	\caption{
+%		{\bf Alternative view of the evolution of LP 12-502}
+%		(Figure~\ref{fig:lp}), arranged to emphasize changes in transit
+%		times.  There are 200 binned black points per $P$=18.5611\,hr cycle; a two-harmonic
+%		sinusoid has been subtracted from the PDC\_SAP light curve.
+%		Vertical gray lines are underplotted to help guide the eye to instances
+%		in which preferred dip phases synchronize over long baselines.
+%		The orange and green lines guide the eye to where dips
+%		change the positions of their local minima; orange
+%		lines have periods slightly less than $P$, the green line has
+%		a period greater than $P$.
+%	}
+%	\label{fig:lp2}
+%\end{figure*}
+
+\begin{figure*}[!t]
+	\begin{center}
+		\subfloat{
+			\includegraphics[width=0.46\textwidth]{f7a.pdf}
+			\includegraphics[width=0.46\textwidth]{f7b.pdf}
+		}
+		\vspace{-0.2cm}
+
+		\subfloat{
+			\includegraphics[width=0.46\textwidth]{f7d.pdf}
+			\includegraphics[width=0.46\textwidth]{f7c.pdf}
+		}
+	\end{center}
+	\vspace{-0.4cm}
+	\caption{
+		{\bf River plots of the LP 12-502 light curve}, showing (clockwise
+		from top-left) Sectors 18-19, 25-26, 53, and 58-59.  A
+		two-harmonic sinusoid has been subtracted to highlight the sharp
+		dips.  In Sectors 25-26 (cycles 248-315), periods are visible at
+		the fundamental period of 18.5611\,hr, as well as at faster and
+		slower relative periods (e.g. $\phi$$\approx$0.3 and
+		$\phi$$\approx$0.1).  Similar instances of multiple simultaneous
+		periods are also visible in Sector 53 and 58-59.  White chunks
+		denote missing data.
+	}
+	\label{fig:lpriver0}
+\end{figure*}
+
+\subsection{Evolution over adjacent sectors, \& LP 12-502}
+
+A small fraction of our objects were in regions of sky with
+many sectors of adjacent TESS data.  Out of this already small sample, LP 12-502
+(TIC 402980664; $d$=21\,pc, $J$=9.4, $T$=11.1) stood out due to the
+quality and content of its data.  We discuss another interesting
+source, TIC~300651846, in Appendix~\ref{app:tic3006}.  In this
+section, we first present the LP 12-502 observations
+(Section~\ref{subsec:lpobservations}), and then highlight their
+implications (Section~\ref{subsec:lplessons}).
+
+\subsubsection{LP 12-502 observations}
+\label{subsec:lpobservations}
+
+Figure~\ref{fig:lplc} shows all available data for LP 12-502 from TESS
+Sectors 18, 19, 25, 26, 53, 58, and 59, split into successive orbits.
+The star was observed at 120-second cadence whenever it was observable
+by TESS.  We binned the light curve to 15-minute intervals for visual
+clarity, and required at least one (120-second cadence) flux
+measurement per bin.  Points more than 2.5$\sigma$ above the median
+are drawn in gray, also for visual clarity.  Missing data are not
+drawn.  Figure~\ref{fig:lp} then shows the same data, but stacked into
+successive TESS orbits spanning half a lunar month each.  Finally,
+Figure~\ref{fig:lpriver0} shows ``river plots'' of the same data,
+split into similar intervals: the Sector 18-19 data, 25-26 data, 53
+data, and 58-59 data.  The river plots are subject to one additional
+processing step: we fitted and subtracted a maximum-likelihood
+two-harmonic sinusoid independently from the Sector 18-19 data, 25-26
+data, and 53, 58, and 59 data in order to accentuate changes in the
+dip timing and structure.
+
+The average period, determined by measuring the PDM peak period over
+each sector independently, was $\langle P \rangle = 18.5560$\,hr.  The
+range between the maximum and minimum sector-specific periods was
+measured to be about one minute.   However, in detail, a period shift
+of $\pm$1\,minute would yield major phase drifts over the baseline;
+that time interval corresponds to $\approx$1/1000$^{\rm th}$ of a
+period, and we have observed 1500 cycles.  By fine-tuning over a grid
+in period, we found $P=18.5611 \pm 0.0001$\,hr, which seems to track
+certain features in the LP 12-502 light curve well over the entire
+dataset.
+
+What exactly is observed?  For the first 64 cycles, the star shows a
+pattern reminiscent of an eclipsing binary, with four obvious local
+minima.  We dub these dips $\{ 1, 2, 3, 4 \}$ at phases $\{ -0.28,
+-0.08, 0, 0.25 \}$, respectively.  Over cycles 0-64, the depth of dips
+1 and 3 remain roughly fixed.  However dip 4 decreases in depth by
+about 2\%, while dip 2 increases in depth, by about the same amount
+(see Figure~\ref{fig:lp}).  During cycles 48-64, a fifth dip may also
+be emerging, in the main ``large'' dip group.
+
+There is then a 6-month (184 cycle) gap to Cycles 248-315, which show
+two highly structured dip complexes, plus a small leading dip.  The
+single leading dip is present at the same phase as in cycles 0-64, and
+is therefore likely to be the same struture.  Along a similar line of
+logic, it seems plausible that the first ``dip complex'' during cycles
+248-264 represents an evolution of the initial complex seen during
+cycles 0-64, though with reduced depth.  During cycles 266-310, an
+additional local minimum develops between the two complexes; this
+feature is best visualized on the river plots
+(Figure~\ref{fig:lpriver0}), and we describe its (shorter) period
+below.
+
+The second dip complex during cycles 248-315 shows the most
+substructure.  During e.g.~cycles 283-298, this single complex shows
+six local minima.  The deepest dip is sharp: it shows a flux excursion
+of 3.5\% over about 22 minutes (0.02\,$P$), which is the steepest
+slope exhibited anywhere in the LP~12-502 dataset.  After the sharp
+dip, there is a roughly exponential fall-off spanning about a quarter
+of a period, punctuated by coherent local minima and maxima which in
+detail (Figure~\ref{fig:lpriver0}) have slightly longer periods than
+the sharp dip.  The sharp leading dip only decreases in depth
+following a sudden state-switch at BTJD 2030.7 (cycles 299-315), which
+happens during a flare (Figure~\ref{fig:lplc}).  The trailing dips
+remain thereafter.
+
+Sectors 53--58 (cycles 1233-1481) are comparatively tame; they showed
+only four to six dips per cycle.  Some dips remain stable in depth and
+duration over this five month interval.  Other dips grow, like the one
+at $\phi = +0.06$ between cycles 1499 and 1481.  Other dips, such as
+the one at $\phi = +0.12$ in cycles 1233-1264, disappear entirely.
+The most dramatic state switch occurs during cycles 1233-1247, when a
+large dip ``switches'' from a depth of 3\% and duration of 3 hours to
+a depth of 0.3\%, and a duration of 1 hour.
+
+\subsubsection{Lessons from LP 12-502}
+\label{subsec:lplessons}
+
+{\sc State-switches reveal dip independence}---The state-switches seen
+in cycles 1233-1247 and 299-315 confirm that dips can disappear in
+less than one cycle, a point which has been previously appreciated
+\citep{2017AJ....153..152S}.  What is new in these particular changes
+is that the morphology changes show that the dips can be {\it
+independent} and {\it additive}.  For example, throughout cycles
+1233-1264, there are three local minima between phases of 0 and 0.3.
+They all have identical ingress times.  The shape change during the
+transition implies that the leading dip that ``turned off'' (reduced
+its depth and duration), while the trailing two dips remained fixed.
+This is visible in Figure~\ref{fig:lp}.
+In other words, the structures producing these dips are independent to
+the degree that one can undergo a severe change while the others
+remain identical.  The state switches during cycles
+248-264 and 299-315 share the same characteristic: it is always the
+{\it leading} dip of a complex that ``switches off'', leaving the
+(fixed-depth) trailing dips in its wake.
+
+{\sc Slow growth; rapid death}---Although there are a few instances in
+which we observe dips switch off over less than one cycle, dip
+growth seems to happen more slowly.  For instance, the dip that grows
+between phase 0 and 0.1 between cycles 260-290 begins to become
+visible around BTJD 1993.2, and growths in depth by about 2\% over
+about six cycles, to become visible by eye by BTJD 1997.7.
+The evolution of this particular dip is most clear in the river plots.
+The evolution of the latter dip group in cycles 1410-1481 is another
+example of this slow mode of dip growth.
+
+% 16 px vs 310 px for a full phase
+% Based on our SED fitting $R_\star=0.369\,R_\odot$ star, and from the
+% isochrone mass, $M_\star=0.215\,M_\odot$
+
+{\sc Dip durations}---The shortest dip duration for any of the
+individual LP 12-502 dips seems to be $\approx$0.06\,$P$ $\approx$
+1.08\,hr.  In comparison, using the stellar radius and mass derived in
+Section~\ref{subsec:starprops}, the characteristic timescale $T_{\rm
+dur} \equiv R_\star P / (\pi a)$ for the transit of a point-source at
+corotation is 1.02$\pm$0.10\,hr.  This means that while
+some of the LP 12-502 dips are sufficiently long to require structures
+that are extended in orbital azimuth, the durations of other dips are
+consistent with effective radii for the occulting material $R_{\rm
+eff} \ll R_\star$.  This implies $a/R_\star \approx 5.8$ for this
+material; the analogous timescale at the stellar surface is
+about six times slower.
+
+{\sc Dip periods}---Most of the LP 12-502 dips repeat with a period of
+$P=18.5611 \pm 0.0001$\,hr.  However the river plots
+(Figure~\ref{fig:lpriver0}) reveal that the
+light curve has specific dips with simultaneous but distinct periods.  For instance, in sectors 25-26, the
+local minimum that develops around cycle 262 has a period faster than
+the mean period by $\approx$0.1\%, while some of the trailing local
+minima in the main dip complex have periods slower than the mean
+period, by $\approx$0.04\%.  In addition to the fundamental period, we
+were able to identify at least four distinct periods shown by specific
+dips over the full Sectors 18-59 dataset, including periods at
+18.5683, 18.5672, 18.5473, and 18.5145\,hr, with a typical measurement
+uncertainty of $\approx$0.0002\,hr.  If each period corresponds to an
+individual dust or gas clump, then this implies that multiple distinct clumps can orbit
+the star simultaneously, at marginally different separations.
+
+\section{Discussion}
+\label{sec:discussion}
+
 \subsection{Typical and extreme CQVs}
@@
 \subsection{Binaries, massive CQVs, and a new class of false positive}
+\label{subsec:discbinary}
+
+%FIXME FIXME FIXME
+%TODO: update to give some flavor for how many sources show second periods!
 
 The high-RUWE objects in Figure~\ref{fig:catalogscatter} tend to be
-among the more massive half of the CQV sample.  This suggests that either
-that the RUWE indicator is not sensitive to binarity among lower mass
-stars, or that these ``high-mass CQVs'' may be unresolved blends in
-which the lower mass companion is produces the CQV signal.
+among the more massive half of the CQV sample.  This suggests that
+some of the ``high-mass CQVs'' may be unresolved blends in which the
+lower mass companion produces the CQV signal.
 
@@
 
-The two most massive CQVs in our sample present a relevant case study.
-To date, the only stars reported to show the CQV phenomenon are M
-dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
+The two most massive CQVs in our sample, nominally in the K dwarf mass
+regime, present a relevant case study.  To date, the only stars
+reported to show the CQV phenomenon are M dwarfs, with typical stellar
+masses $\lesssim$0.3\,$M_\odot$
 \citep{2017AJ....153..152S,2022AJ....163..144G}.  TIC~405754448 and
-TIC~405910546 however appear to have masses of
-$\approx$0.82\,$M_\odot$ and $\approx$0.60\,$M_\odot$ respectively.
-The next-highest masses in our sample are $\approx$0.40\,$M_\odot$.
-The masses for the former two objects are consistent with their
-locations in the color--absolute magnitude diagram, and with their
-membership in LCC.  However the light curve morphology of
-TIC~405910546 is unique among the CQV sample, and suggestive of an
-eclipsing binary; it should be studied further to clarify its
-classification.  For TIC~405754448, we expect that this source {\it
+TIC~405910546 appear to have masses of $\approx$0.82\,$M_\odot$ and
+$\approx$0.60\,$M_\odot$ respectively.  The next-highest masses in our
+sample are $\approx$0.40\,$M_\odot$.
+
+Based on their locations locations in the color--absolute magnitude
+diagram and membership in LCC, both of the K dwarfs do indeed appear
+to be high mass.  However in detail, both are subject to ambiguities
+in interpretation.  The light curve morphology of TIC~405910546 is
+unique in the CQV sample, and suggestive of an eclipsing binary.
+Independently, TIC~405910546 was one of the \nrvscatter\ CQVs flagged
+with a Gaia DR3 radial velocity scatter exceeding 20\,\kms.  Combined,
+these factors suggest that TIC~405910546 might be a pre-main-sequence
+eclipsing binary; it should be studied further to clarify this
+classification.  For TIC~405754448, we believe that this source {\it
 is} an unresolved binary, because RUWE$_{\rm DR2}$=4.7, and because
-the raw light curves in Sectors 11, 37, and 38 show an
-additional $\approx$6.5\,day, $\approx$0.3\% amplitude sinusoidal
-signal suggestive of an unresolved photometric companion.  If
-TIC~405754448 is a K+M binary, then the flux ratio between the primary
-and secondary would be expected to be $\approx$10:1.  It would be
-challenging for the M dwarf to produce the observed 12.9\,hr signal
-with such a flux deficit, but not impossible.  While both of
-these objects suggest that the CQV phenomenon may extend up in mass to
-pre-main-sequence K dwarfs, more data are needed to fully substantiate
-this claim.
+the raw light curves in Sectors 11, 37, and 38 show an additional
+$\approx$6.5\,day, $\approx$0.3\% amplitude sinusoidal signal
+suggestive of an unresolved photometric companion.  If TIC~405754448
+is a K+M binary, then the flux ratio between the primary and secondary
+would be expected to be $\approx$10:1.  It would be challenging for
+the M dwarf to produce the observed 12.9\,hr signal with such a flux
+deficit, but not impossible.  While both of these objects suggest that
+the CQV phenomenon may extend up in mass to pre-main-sequence K
+dwarfs, more data are needed to fully substantiate this claim.
 
@@
 TIC~224283342 (Sector 2), and TIC~442571495 (Sector 12).
-
-It is challenging to interpret the significance of such apparent
-regularities;  the objects exhibit such a wide range of variability
-that for seemingly any ``regularity'' one might posit, it is easy to
-come up with counter-example objects which do not follow the trend.
-In other words, these half-cycle CQVs could simply be a product of the
-human tendency to pattern match; alternatively, they might yield some
-important physical significance.
+For the particular case of TIC~224283342, this observation, coupled
+with Gaia DR3 radial velocities suggesting a radial
+velocity scatter exceeding 20\,\kms, suggests that the system could be
+a low-mass eclipsing binary transiting a giant polar spot, analogous to
+TOI-3884 \citep{2022A&A...667L..11A}.
+
+In general however, it is challenging to interpret the significance of
+the potential regularities listed above;  the CQVs exhibit such a wide
+range of variability that for seemingly any ``regularity'' one might
+posit, it is easy to come up with counter-example objects which do not
+follow the trend.  In other words, these half-cycle CQVs could simply
+be a product of the human tendency to pattern match.  The alternative
+is that some subset of these pattern could  have real physical
+significance.
 
@@
   %
-    \item While the majority of detected CQVs have masses of
-      0.1-0.5\,$M_\odot$, the upper mass limit for the CQV phenomenon
-      might extend into the K dwarf regime ($<$$0.8$\,$M_\odot$).
-      TIC~405754448 and TIC~405910546, with masses of $\approx$0.8 and
-      $\approx$0.6\,$M_\odot$, are the two massive outliers.
-      However both have peculiarities (Section~\ref{subsec:massive}), and 
-      we encourage additional
+    \item The majority of detected CQVs have masses of
+      0.1-0.5\,$M_\odot$.  Two sources, TIC~405754448 and
+      TIC~405910546, have masses that appear to exceed the M dwarf
+      limit.  However both are potentially binaries, and this may
+      confuse our ability to accurate identify the source of the CQV
+      signal (Section~\ref{subsec:massive}).  We encourage additional
       scrutiny of these objects in future work.

### 2023-08-15 paper/ms.tex
added planet constraint discussion and some minor edits throughout the paper

@@
 decrease due to limb-darkening (see \citealt{2017AJ....153..152S},
-Figures 37-41).  The observed dips can happen over durations as
+Figures 37-41).  The observed dips, however, happen over durations as
 short as $0.05\,P_{\rm rot}$ with characteristic depths of a few
@@
 spectroscopic analyses.  To do this, we use 120-second cadence data
-acquired by TESS between July~2018 and Sep~2022 (Sectors 1-55; Cycles
+acquired by TESS between 2018 July and 2022 September (Sectors 1-55; Cycles
 1-4).  We present our search methods in Section~\ref{sec:methods}, and
@@
 \citep{2017AJ....153..152S} ``complex rotators'',
-\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
+\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P},
 and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  The
@@
 corotating clumps, or more generally on circumstellar plasma tori;
-for the time being, ``CQV'' seems to more accurately mirror the state
-of our ignorance.
+for the time being, ``CQV'' is agnostic to the true underlying phenomenon.
 
@@
 
-We analyzed the ``short'' 120-second cadence data acquired by TESS
-between July~2018 and Sep~2022 (Sectors 1-55).  Specifically, we used
+To construct our sample, we analyzed the short-cadence data acquired by TESS
+between 2018 July and 2022 September (Sectors 1-55).  Specifically, we used
 the 120-second cadence light curves produced by the Science Processing
@@
 images with cadences of 600 and 1800 seconds, we limited our scope in
-this study for the sake of simplicity in data handling.  In exchange,
+this study for the sake of simplicity in data handling and some degree of 
+uniformity in the properties of the data itself.  In exchange,
 we sacrificed both completeness and homogeneity of the selection
 function.  While TESS cumulatively observed $\approx$90\% of the sky
-for at least one lunar month between July~2018 and Sep~2022, the
+for at least one lunar month between 2018 July and 2022 September, the
 120-second cadence data were collected for only a subset of observable
@@
 interest, which we defined as stars with 120-second cadence TESS light
-curves that satisfied
+curves satisfying these four conditions:
 \begin{align}
   T &< 16 \quad&(\mathrm{Bright\ for\ TESS})\\
-  \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only}) \\
-  M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})  \\
-  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}),
+  \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only})\\
+  M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})\\
+  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}).
 \end{align}
-for $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ the Gaia $G$-band
+Here, $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ is the Gaia $G$-band
 absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
-arcseconds, and a geometric distance $d$ defined by inverting the
+arcseconds, and $d$ a geometric distance defined by inverting the
 parallax and ignoring any zero-point correction.  The target sample
@@
 
-For our dip-counting pipeline, we began with the PDC\_SAP flux for
+For our dip-counting pipeline, we began with the {\tt PDC\_SAP} flux for
 each sector, removed non-zero quality flags, and normalized the light
@@
 \citep{2021zndo...1011188B} due to its shape agnosticism.  If a period
-below 2 days was identified, we reran the periodogram at a finer grid
+$P$ below 2 days was identified, we reran the periodogram at a finer grid
 to improve the accuracy of the period determination.
 
-Once a star's period $P$ was identified, we binned the phased light
+Once a star's period was identified, we binned the phased light
 curve to 100 points per cycle.  To separate ``sharp'' local minima
@@
 points more than two standard deviations away from the local continuum
-\citep{2019AJ....158..143H}.  The maximum number of equidistant spline
+\citep{2019AJ....158..143H} {\red (RJ: was this to guard against flares?
+might be good to explicitly mention, if so.)}.  The maximum number of equidistant spline
 knots per cycle is the parameter in this framework that controlled the
@@
 and \citet[][their Section~1.3]{2023MNRAS.524.4220P}.  Starting with
-the PDC\_SAP light curves, we normalized each light curve, and then
+the {\tt PDC\_SAP} light curves, we normalized each light curve, and then
 re-binned it into equal width 120-second bins to account for the
@@
 numpy.fft.fft}, we then searched for peaks with a significance of over
-12-$\sigma$ within a set of 500 bins. 
-{\bf LB: by the latter ``bins'', does this mean frequencies?}
+12-$\sigma$ within a set of 500 frequency bins.
 
@@
 				\url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
+			{\red (RJ: Will these be made available on Zenodo, or something with a permanent DOI?)}
 			Panels are as follows.
@@
 consulted the meta-catalog of young, age-dated, and age-dateable stars
-within a kiloparsec from \citet{2022AJ....163..121B}, and also
+within 1 kpc from \citet{2022AJ....163..121B}, and also
 searched the local volume around each star for co-moving
@@
 the masses by interpolating against the sizes, temperatures, and ages
-against the PARSEC v1.2S models
+of the PARSEC v1.2S models
 \citep{2012MNRAS.427..127B,2014MNRAS.444.2525C}.
@@
 DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
-WISE 1-2 passbands.  We omitted UV flux measurements from
+WISE $W1$ and $W2$ passbands.  We omitted UV flux measurements from
 our SED fit to avoid any possible bias induced by chromospheric UV
-excess; we similarly omitted WISE 3-4, but due to reliability
+excess; we similarly omitted WISE bands $W3$ and $W4$, but due to reliability
 concerns.  \texttt{astroARIADNE} compares the measured broadband flux
@@
 evidence supporting the reality and youth of that group.  The yield
-in Sco-Cen is not surprising, since Sco-Cen contains the majority of
-pre-main-sequence stars in the solar neighborhood, any many of its stars
+in Sco-Cen is not surprising since Sco-Cen contains the majority of
+pre-main-sequence stars in the solar neighborhood, many of its stars
 were selected for TESS 120-second cadence observations by various
@@
 \citet{2021ApJ...917...23K} as being in the ``diffuse'' population of
-$<$50\,Myr stars near the Sun.
+$<$50\,Myr stars near the Sun.  {\red (RJ: right now, the current value
+is 1, but you say "both", would be good to fix this consistency issue)}
 
@@
 similarly-aged Psc-Eri member \citep{2020A&A...639A..64R}.  To our
-knowledge, TIC~332517282 in AB~Dor was the previous record-holder for
+knowledge, TIC~332517282 in AB~Dor was the previous record-holder for the
 oldest-known CQV \citep{2019ApJ...876..127Z,2022AJ....163..144G}; at
@@
 \citep{2006ApJ...649L.115Z}, which shows a coeval population of stars
-older than the Pleiades and younger than the 400\,Myr Ursa Major
+older than the Pleiades but younger than the 400\,Myr Ursa Major
 moving group.  The formal BANYAN-$\Sigma$ membership probability is
 however somewhat low, perhaps due to the missing radial velocity.
-This could be resolved by acquiring even a
+This lack of information could be resolved by acquiring even a
 medium-resolution spectrum.  An independent assessment of the group's
@@
 
-Most CQVs in our catalog did not show infrared excesses in the W1-W4
+Most CQVs in our catalog did not show infrared excesses in the $W1--W4$
 bands, which is typical for this class of object
@@
 \nallcands\ star sample and the WISE images available through IRSA, we
-labeled two objects as having reliable infrared excesses (both W3 and
-W4 at $>$3$\sigma$ above the photospheric prediction).
-
-The two IR excess sources were TIC~193136669 (TWA~34) and TIC~57830249
+labeled two objects as having reliable infrared excesses (both $W3$ and
+$W4$ at $>$3$\sigma$ above the photospheric prediction).
+
+The two sources exhibiting an IR excess were TIC~193136669 (TWA~34) and TIC~57830249
 (TWA~33).  Both are in the TW Hydrae association ($\approx$10\,Myr),
@@
 to flag possible single-lined spectroscopic binaries, which selected
-\nrvscatter\ stars: TIC~405910546, TIC~224283342, and TIC~280945693.
+the following stars: TIC~405910546, TIC~224283342, and TIC~280945693.
 %
@@
 RUWE$_{\rm DR3}$ $>$ 2 to flag sources with excess astrometric noise.
-This threshold yielded \ngoodhighruwe/\ngoods\ high-quality CQVs with
-a Gaia DR2 RUWE$>$2; \nmaybehighruwe/\nmaybes\ of the ambiguous sample
+This threshold yielded \ngoodhighruwe of the \ngoods\ high-quality CQVs with
+a Gaia DR2 RUWE$>$2; \nmaybehighruwe of the \nmaybes\ ambiguous ones
 share this characteristic.
@@
 \paragraph{Gaia DR3 non-single stars}---Gaia DR3 included a
-``non\_single\_star'' column that flagged known or suspected
+{\tt non\_single\_star} column that flagged known or suspected
 eclipsing, astrometric, and spectroscopic binaries.  None of the stars
@@
 passed each of the binarity indicators.
-We discuss some important--and complicated--aspects of the systems
+We discuss some important---and complicated---aspects of the systems
 that seem to be binary in Section~\ref{subsec:discbinary}.
+
+\subsection{Constraints on the presence of a planet}
+\label{subsec:planet_constraints}
+We searched for evidence of a transiting exoplanet for 10 of the brightest
+CQVs {\red (RJ: was this the selection function?)} using the transit least
+squares algorithm from \citet{2019A&A...623A..39H}. We first fit for 40
+harmonics of the CQV period and subtracted these from the light curve,
+along with two sidebands at frequencies of $1/T$, where $T$ was the
+length of the TESS data for the sector whose data we used. We found
+no evidence for a planet with $R > 2-3 R_\oplus$ and a period less
+than 12\,d (FAP > 0.05) in most cases. The three false positive cases
+could be explained by residual signals from the CQV that were not
+properly removed, due to the modulation of the CQV profile over
+the duration of a period. Further observations may be necessary to
+conclusively rule out the presence of planets around CQVs.
 
@@
 source, TIC~300651846, in Appendix~\ref{app:tic3006}.  In this
-section, we first present the LP 12-502 observations
-(Section~\ref{subsec:lpobservations}), and then highlight their
-implications (Section~\ref{subsec:lplessons}).
+section, we first present the LP 12-502 observations and then highlight their
+implications.
 
@@
 The closest CQV in our catalog is DG~CVn (TIC~368129164;
-$d$$=$18\,pc), a member of AB Dor.  To our knowledge, this manuscript
+$d$$=$18\,pc), a member of AB Dor.  To our knowledge, this work
 is the first time that it has been noted as a CQV.  The three
@@
 a 10.82\,hr period, because this period minimized the
-dispersion in the phase-folded light curve.  However careful inspection
+dispersion in the phase-folded light curve.  However, careful inspection
 of the periodogram
@@
 light curve shapes evolve over 10 to 1{,}000 cycles.  They are
-therefore {\it quasi}periodic.  This observation is consistent studies
-by \citet{2022AJ....163..144G} and \citet{2023ApJ...945..114P}.
-However it marks a qualitative departure from the ``persistent'' {\it
+therefore {\it quasi}periodic.  This observation is consistent with
+\citet{2022AJ....163..144G} and \citet{2023ApJ...945..114P}.
+However, it marks a qualitative departure from the ``persistent'' {\it
 vs.} ``transient'' flux dip distinction described by
-\citet{2017AJ....153..152S};  since all CQV dips seem to be transient
+\citet{2017AJ....153..152S}, since all CQV dips seem to be transient
 over timescales of more than 1{,}000 cycles (Figure~\ref{fig:evoln}).
@@
 of limits'' for any dipping material.  This could be evidence that
-some aspect the stellar magnetic field is strongly asymmetric, and can
+some aspect of the stellar magnetic field is strongly asymmetric, and can
 generate and hold extrinsic material at corotation, but only over two
@@
 what is required to produce deeper dips in the blue than in the red.
-Thompson scattering is similarly ruled out as a relevant opacity
+Thomson scattering is similarly ruled out as a relevant opacity
 source, because it is gray.  The final plausible alternative opacity
@@
 stars.  This broadly assumes that any star that can support
-prominences will, and that the magnetic topology of rapidly rotating M
+prominences will do so, and that the magnetic topology of rapidly rotating M
 dwarfs at 100\,Myr is similar to that of rapidly rotating M dwarfs at
 say, 10\,Myr.  Based on the degree to which M dwarfs remain rapid
-rotators over the first few gigayears of their lives
+rotators over the first few Gyr of their lives
 \citep[e.g.][]{2022AJ....164...80R,2022ApJ...936..109P}, it seems
@@
 and within 10 days, it is reasonable to expect on average one close-in
-planet per M dwarf.
+planet per M dwarf. However, we do not find evidence of a transiting
+large rocky planet for a selected subset of the stars in our sample 
+(Section \ref{subsec:planet_constraints}).
 
@@
 relatively periodic and it showed dip depths of a few percent.
-However in other TESS sectors (e.g. Sector~10), this source looks
+However, in other TESS sectors (e.g. Sector~10), this source looks
 completely different, varying in apparent flux by a factor of two,
@@
 posit, it is easy to come up with counter-example objects which do not
-follow the trend.  In other words, these half-cycle CQVs could simply
-be a product of the human tendency to pattern match.  The alternative
-is that some subset of these pattern could  have real physical
-significance.
+follow the trend. However, there may be some subset of these
+identified patterns with real physical significance.
 
@@
 one ``hump'' (Figure~\ref{fig:bstar}), top-left; see also
-\citealt{2022ApJ...924L..10J}).  Within the model proposed by Townsend
-et al., this is explained by the simplicity of the star's magnetic
-field, which to first-order is a dipole, similar to most other
+\citealt{2022ApJ...924L..10J}).  Within the model proposed by 
+\citeauthor{2005ApJ...630L..81T}, this is explained by the simplicity of the star's 
+magnetic field, which to first-order is a dipole, similar to most other
 magnetic B stars \citep{2007A&A...475.1053A,2009ARA&A..47..333D}.
@@
 $10^6\,{\rm K}$ tends to give Alfv\'en radii of order a few times
-the corotation radii, $R_{\rm cr}$.
+the corotation radii, $R_{\rm cr}$, suggesting that the presence of
+a complex multipolar magnetic field trapping dust may be a plausible
+explanation for the CQV phenomenon.
 
@@
 In this work, we searched 120-second cadence TESS data collected
-between July~2018 and Sep~2022 for complex quasiperiodic variables
+from 2018 July to 2022 September for complex quasiperiodic variables
 (CQVs).  The target stars were \nstarssearched\ K and M dwarfs within
@@
 quasiperiodic behavior over at least one TESS sector.  These \ngoods\
-bonafide CQVs are listed in Table~\ref{tab:thetable}.  This table also
+bona fide CQVs are listed in Table~\ref{tab:thetable}.  This table also
 includes an additional \nmaybes\ ambiguous CQVs, whose designation is
@@
 stellar sample had a heterogeneous selection function which may have
-been biased in favor of young stars over field stars.  Previous work
-however has shown that $\approx$1-3\% of M dwarfs younger than
+been biased in favor of young stars over field stars.  Previous work,
+however, has shown that $\approx$1-3\% of M dwarfs younger than
 $\approx$100\,Myr show the CQV phenomenon
@@
     \item The duty cycle for CQVs seems to be $\approx$$75$\%, based
-      on the fraction of bonafide CQVs that either turned on or turned
+      on the fraction of bona fide CQVs that either turned on or turned
       off during TESS re-observations, two years after the initial
@@
 In addition, this paper relied on data collected by the TESS mission, which are publicly
-available from the Mikulski Archive for Space Telescopes (MAST).
-Funding for the TESS mission is provided by NASA’s Science Mission
-Directorate.  TIC 402980664 in particular was observed at 120-second
-cadence thanks to the TESS Guest Investigator programs G022252 (PI:
-J.~Schlieder; Sectors 18, 19, 25, 26) and G04168 (PI: R.~Jayaraman;
+available from the Mikulski Archive for Space Telescopes (MAST). Funding for the TESS 
+mission is provided by NASA’s Science Mission Directorate. TIC 402980664 in particular 
+was observed at 120-second cadence thanks to the TESS Guest Investigator programs 
+G022252 (PI: J.~Schlieder; Sectors 18, 19, 25, 26) and G04168 (PI: R.~Jayaraman;
 Sector 53).
+
+Resources supporting this work were provided by the NASA High-End Computing (HEC)
+Program through the NASA Advanced Supercomputing (NAS)
+Division at Ames Research Center to produce the SPOC data
+products.
 

### 2023-08-15 paper/ms.tex
updated planet paragraph based on feedback from Saul

@@
 CQVs {\red (RJ: was this the selection function?)} using the transit least
-squares algorithm from \citet{2019A&A...623A..39H}. We first fit for 40
-harmonics of the CQV period and subtracted these from the light curve,
-along with two sidebands at frequencies of $1/T$, where $T$ was the
-length of the TESS data for the sector whose data we used. We found
+squares algorithm from \citet{2019A&A...623A..39H}. We first fit simultaneously
+for 30 harmonics of the CQV period, along with $\pm$\,3 sidebands of each
+harmonic spaced by $1/T$, where $T$ was the duration of the TESS
+data for the sector we used. This fit, using 420 frequencies, was then subtracted 
+from the TESS light curve, and we then analyzed the residual. We found
 no evidence for a planet with $R > 2-3 R_\oplus$ and a period less

### 2023-08-15 paper/ms.tex
update ms: add binarity section

--- 2023-08-15 paper/ms.tex
@@
 			data and black points are binned to 200 points per cycle.
+      The adopted period is given in the lower-right corner.
 			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
@@
       data available are on top (see Section~\ref{sec:catalog}).
+      Sources with large apparent scatter in gray typically show
+      secondary periods from unresolved binaries, which are enumerated
+      in Table~\ref{tab:thetable}.
 		}
@@
 
-\begin{figure*}[!t]
-	\begin{center}
-		\centering
-		\includegraphics[width=0.95\textwidth]{f8.pdf}
-		\vspace{-0.1cm}
-		\caption{
-      {\bf Properties of CQVs identified by our search}.
-      CQVs are mostly pre-main-sequence M dwarfs, younger than
-      $\approx$150 Myr, with rotation periods faster than
-      $\approx$1\,day.  The \ngoods\ bonafide CQVs in
-      Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
-      ambiguous CQV candidates are light blue circles.  Cases with
-      elevated Gaia DR2 RUWE values are highlighted.
-      The top panels show the \nstarssearched\ target stars with
-      120-second cadence TESS data as the shaded gray background;
-      darker regions correspond to a larger relative number of
-      searched stars.  The lower-left panel compares the
-      rotation--color distribution of CQVs against the rotation
-      periods of K and M dwarfs in the Pleiades from
-      \citet{2016AJ....152..114R}.  The lower-middle panel plots the
-      derived corotation radii $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in
-      units of stellar radii against the measured CQV periods, in
-      units of hours.  Ages in the final panel are known from cluster
-      membership.
-		}
-		\label{fig:catalogscatter}
-	\end{center}
-\end{figure*}
-
 \section{Results}
@@
 Table~\ref{tab:thetable} lists the \nallcands\ objects identified by
-our search.  The ``high-quality sample'' includes \ngoods\ of these
-objects, which demonstrated what we viewed as unambiguous
+our search.  The ``high-quality sample'' includes \ngoods\ objects,
+which demonstrated what we viewed as unambiguous
 characteristics of the CQV phenomenon in at least one TESS sector.
@@
 TIC~224283342, TIC~402980664).  Others show structured modulation over
-the entire span of a cycle (e.g. TIC~2234692, TIC~401789285,
-TIC~425933644, TIC~142173958).  Others show some mix between these two
+the entire span of a cycle (e.g. TIC~2234692, TIC~425933644, TIC~142173958).  Others show some mix between these two
 modes.
@@
 
-For the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
+For the two stars for which BANYAN\,$\Sigma$ did not
 find any association, we were not able to confidently associate either
@@
 
+\begin{figure*}[!t]
+	\begin{center}
+		\centering
+		\includegraphics[width=0.95\textwidth]{f8.pdf}
+		\vspace{-0.1cm}
+		\caption{
+			{\bf Properties of CQVs identified by our search}.
+			CQVs are mostly pre-main-sequence M dwarfs, younger than
+			$\approx$150 Myr, with rotation periods faster than
+			$\approx$1\,day.  The \ngoods\ bonafide CQVs in
+			Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
+			ambiguous CQV candidates are light blue circles.  
+			Unresolved binaries are flagged either if the Gaia DR3 radial
+			velocity scatter exceeded 20\,\kms, or if
+			Gaia ${\rm RUWE}_{\rm DR3}$$>$2 and multiple photometric signals were present in the
+			TESS light curve.
+			The top panels show the \nstarssearched\ target stars with
+			120-second cadence TESS data as the shaded gray background;
+			darker regions correspond to a larger relative number of
+			searched stars.  The lower-left panel compares the
+			rotation--color distribution of CQVs against the rotation
+			periods of K and M dwarfs in the Pleiades from
+			\citet{2016AJ....152..114R}.  The lower-middle panel plots the
+			derived corotation radii $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in
+			units of stellar radii against the measured CQV periods, in
+			units of hours.  Ages in the final panel are known from cluster
+			membership.
+		}
+		\label{fig:catalogscatter}
+	\end{center}
+\end{figure*}
+
 \subsection{Binarity}
@@
 the CQV signal.  Binary companions can also bias photometric magnitude
-and color measurements, thereby biasing our stellar parameter
+and color measurements, which would affect our stellar parameter
 estimates.  To attempt to identify binaries, we considered the
 following lines of information.
-%
-\paragraph{Radial velocity scatter}---We examined diagrams of the Gaia
+
+{\it Radial velocity scatter}---We examined diagrams of the Gaia
 DR3 ``radial velocity error'' as a function of stellar color for all
@@
 to flag possible single-lined spectroscopic binaries, which selected
-\nrvscatter\ stars: TIC~405910546, TIC~224283342, and TIC~280945693.
-%
-\paragraph{RUWE}---We examined plots of Gaia DR3 renormalized unit
-weight error (RUWE) as a function of brightness as color.\footnote{For
+\nrvscatterflag\ stars: TIC~405910546, TIC~224283342, and TIC~280945693.
+
+{\it RUWE}---We examined plots of Gaia DR3 RUWE as a function of color.\footnote{For
 an explanation of the renormalized unit weight error (RUWE), see the
 GAIA DPAC technical note \url{http://www.rssd.esa.int/doc_fetch.php?
-id=3757412}.}  Elevated RUWEs imply elevated noise relative to a
+id=3757412}.}  Elevated RUWEs imply excess noise relative to a
 single-source astrometric model.  This can be caused by marginally
@@
 RUWE$_{\rm DR3}$ $>$ 2 to flag sources with excess astrometric noise.
-This threshold yielded \ngoodhighruwe/\ngoods\ high-quality CQVs with
-a Gaia DR2 RUWE$>$2; \nmaybehighruwe/\nmaybes\ of the ambiguous sample
-share this characteristic.
-%
-\paragraph{Gaia DR3 non-single stars}---Gaia DR3 included a
+This threshold was met for \ngoodhighruwe/\ngoods\ high-quality CQVs;
+\nmaybehighruwe/\nmaybes\ of the ambiguous sample
+had this characteristic.
+There is some subjectivity in where to set the threshold, since the RUWE distribution has
+an extended tail \citep[e.g.][]{2022MNRAS.513.5270P}.
+If we had instead required RUWE$_{\rm DR3}$ $>$ 1.4,
+\ngoodweakruwe/\ngoods\ high-quality CQVs and \nmaybeweakruwe/\nmaybes\ of the ambiguous sample
+would have been flagged.
+
+{\it Gaia DR3 non-single stars}---Gaia DR3 included a
 ``non\_single\_star'' column that flagged known or suspected
@@
 in our CQV sample were identified as possible binaries in this column.
-%
-\paragraph{Multiple periodic TESS signals}---During our visual
+
+{\it Multiple periodic TESS signals}---During our visual
 analysis of the TESS light curves and PDM periodograms, we flagged
@@
 this effort are summarized in the secondary periods, $P_{\rm sec}$,
-listed in Table~\ref{tab:thetable}.  {\bf We found additional periods
-in XX of the CQVs, of which YY also had elevated RUWEs}.
-
-%FIXME FIXME FIXME:
-% Need to actually incorporate into the table!
-
-We incorporated each of these sources of information into a column in
-Table~\ref{tab:thetable} that expresses whether any given source
-passed each of the binarity indicators.
-We discuss some important--and complicated--aspects of the systems
-that seem to be binary in Section~\ref{subsec:discbinary}.
+listed in Table~\ref{tab:thetable}.  This process yielded \ngoodmultperiodflag/\ngoods\ high-quality CQVs
+with secondary periods; \nmaybemultperiodflag/\nmaybes\ of the ambiguous
+sample met the same criterion.
+Of the \ngoodhighruwe\ good CQVs with RUWE$_{\rm DR3}$ $>$ 2,
+\ngoodruweandmultperiod\ also showed secondary periods in the TESS
+light curves.
+Considering the weaker threshold of 
+RUWE$_{\rm DR3}$ $>$ 1.4,
+\ngoodweakruweandmultperiod/\ngoodweakruwe\ such CQVs showed secondary TESS periods.
+
+Table~\ref{tab:thetable} summarizes
+each of the above sources of information into a single
+bitwise column.
+We discuss possible connections between binarity and the CQV phenomenon
+in Section~\ref{subsec:discbinary}.
 
@@
 ($M_\star$$\gtrsim$0.25\,$M_\odot$; \citealt{2018A&A...619A.177B}).
-We found no obvious morphology differences between the two classes,
-which is somewhat surprising given that the star's interior structure may influence
-the field topology \citep{2009A&A...496..787R}.  In terms of
+We found no obvious light curve morphology differences between the two classes.
+%which suggests that the star's interior structure may influence
+%the field topology \citep{2009A&A...496..787R}.  
+In terms of
 their rotation rates relative to the Pleiades, the CQVs are among the
@@
 %The dearth of $T$$>$15.5 CQVs
-in our sample, despite our search extending to $T$$=$16, is a
-consequence of the 120-second selection function, not detection
-sensitivity.
+%in our sample, despite our search extending to $T$$=$16, is a
+%consequence of the 120-second selection function, not detection
+%sensitivity.
 
@@
 
-\subsection{Binaries, massive CQVs, and a new class of false positive}
+\subsection{CQVs and binarity}
 \label{subsec:discbinary}
 
-%FIXME FIXME FIXME
-%TODO: update to give some flavor for how many sources show second periods!
-
-The high-RUWE objects in Figure~\ref{fig:catalogscatter} tend to be
-among the more massive half of the CQV sample.  This suggests that
-some of the ``high-mass CQVs'' may be unresolved blends in which the
-lower mass companion produces the CQV signal.
+\subsubsection{Binary statistics}
+
+In Section~\ref{subsec:binarity}, we found that a significant fraction
+of the CQVs show indications of unresolved binarity.  Excess noise
+above the Gaia single-source astrometric model is common
+(\ngoodhighruwe/\ngoods\ high-quality CQVs with RUWE$_{\rm DR3}$$>$2),
+as is the presence of multiple periods in the TESS light curves
+(\ngoodmultperiodflag/\ngoods).  Elevated astrometric noise is almost
+always accompanied by multiple detectable TESS periods
+(\ngoodruweandmultperiod/\ngoodhighruwe high-quality CQVs).  The
+latter point strongly corroborates the idea that most sources with
+RUWE$_{\rm DR3}$$>$2 are intermediate separation binaries with
+projected apparent separations below 1$''$, and projected physical
+separations $\lesssim$50\,AU.
+
+The multiplicity rate of M dwarfs near the Sun is 26.8$\pm$1.4\%
+\citep{2019AJ....157..216W}.  Based on the same study, the peak of the
+separation distribution decreases from $\approx$49\,AU for
+$0.30$-$0.60$\,$M_\odot$ stars, to $\approx$11\,AU for
+$0.15$-$0.30$\,$M_\odot$ M dwarfs.  The multiplicity fraction in our
+CQV sample seems either consistent or perhaps marginally higher than
+the field fraction.  This could plausibly be understood in a physical
+framework in which the presence of intermediate-separation binaries
+causes early disk dispersal, freeing the star to contract.  The CQV
+phenomenon seems to require rapid rotation; thus if binary systems
+tend to produce more rapidly rotating stars, we would expect a sample
+of CQVs to have a larger binary fraction than the field.
 
@@
 
-The two most massive CQVs in our sample, nominally in the K dwarf mass
-regime, present a relevant case study.  To date, the only stars
-reported to show the CQV phenomenon are M dwarfs, with typical stellar
-masses $\lesssim$0.3\,$M_\odot$
-\citep{2017AJ....153..152S,2022AJ....163..144G}.  TIC~405754448 and
-TIC~405910546 appear to have masses of $\approx$0.82\,$M_\odot$ and
-$\approx$0.60\,$M_\odot$ respectively.  The next-highest masses in our
-sample are $\approx$0.40\,$M_\odot$.
+To date, the only stars reported to show the CQV phenomenon are M
+dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
+\citep{2017AJ....153..152S,2022AJ....163..144G}.  However the two most
+massive CQVs in our sample, TIC~405754448 and TIC~405910546, appear to
+have masses of $\approx$0.82\,$M_\odot$ and $\approx$0.60\,$M_\odot$
+respectively.  The next-highest masses in our sample are
+$\approx$0.40\,$M_\odot$.
 
@@
 to be high mass.  However in detail, both are subject to ambiguities
-in interpretation.  The light curve morphology of TIC~405910546 is
-unique in the CQV sample, and suggestive of an eclipsing binary.
-Independently, TIC~405910546 was one of the \nrvscatter\ CQVs flagged
-with a Gaia DR3 radial velocity scatter exceeding 20\,\kms.  Combined,
-these factors suggest that TIC~405910546 might be a pre-main-sequence
-eclipsing binary; it should be studied further to clarify this
-classification.  For TIC~405754448, we believe that this source {\it
-is} an unresolved binary, because RUWE$_{\rm DR2}$=4.7, and because
-the raw light curves in Sectors 11, 37, and 38 show an additional
-$\approx$6.5\,day, $\approx$0.3\% amplitude sinusoidal signal
-suggestive of an unresolved photometric companion.  If TIC~405754448
-is a K+M binary, then the flux ratio between the primary and secondary
-would be expected to be $\approx$10:1.  It would be challenging for
-the M dwarf to produce the observed 12.9\,hr signal with such a flux
-deficit, but not impossible.  While both of these objects suggest that
-the CQV phenomenon may extend up in mass to pre-main-sequence K
-dwarfs, more data are needed to fully substantiate this claim.
-
-\subsubsection{Systems near the 3:2 commensurability}
-
-\paragraph{TIC~435903839}
-We originally classified TIC~435903839, with RUWE$_{\rm DR2}$=11.6, as
-an ``ambiguous'' CQV with 
-a 10.82\,hr period, because this period minimized the
-dispersion in the phase-folded light curve.  However careful inspection
-of the periodogram
-reveals that this source is a photometric blend of two ordinary
-rotating stars with $P_0$=3.60\,hr, and $P_1$=5.41\,hr.  This is a
-novel false positive scenario for CQVs: two rapidly-rotating stars
-with near-integer ratios of rotation periods.  The beat between the
-two rotation signals produces the apparent CQV signal.  Such false
-positives can be excluded through careful accounting of all peaks in a
-periodogram.  For instance, TIC~435903839 shows a peak at 16.27\,hr,
-which is not an integer multiple of the dispersion-minimizing 10.82\,hr period.
-This particular case is an ``impostor'' CQV.
-
-\paragraph{TIC~425937691}
-TIC~425937691 is an odd converse case: it shows two seemingly independent
-CQV signals on what appears to be the same star.  The two signals have
-periods of $\approx$4.82\,hr and $\approx$3.22\,hr, and so also fall near
-the 3:2 commensurability.
-The former is the larger amplitude signal visible in
-Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, corresponding to signal
-with peak-to-peak amplitude of $\approx$8\%.  The latter signal is
-only visible after subtracting the primary period, and it has a
-sinusoidal envelope with a peak-to-peak amplitude of 2.5\%, and with
-three sharp dips super-posed over each cycle.  For
-TIC~425937691, ${\rm RUWE}_{\rm DR2}=2.9$.
-
-Given the two photometric signals and the elevated RUWE, this source is 
-probably an unresolved binary consisting of two CQVs.  Recent work has shown that the orbits of
-binaries closer than $\lesssim$700 AU tend to be aligned with their
-planetary systems \citep{2022AJ....163..207C}.  If we assume that
-observing CQV variability similarly requires near edge-on viewing
-geometries, then we might expect a sufficiently close binary with one
-CQV to also have another, since the spin axes in sufficiently close
-binaries would tend to be aligned.  In this scenario, the two periods
-being within $\approx$0.2\% of the 3:2 period commensurability would
-simply be a coincidence.
+in interpretation.  The TIC~405910546 light curve has a unique shape,
+suggestive of an eclipsing binary.  Independently, TIC~405910546 was
+one of only \nrvscatterflag\ CQVs flagged with a Gaia DR3 radial
+velocity scatter exceeding 20\,\kms.  Combined, these factors suggest
+that TIC~405910546 might be a pre-main-sequence eclipsing binary; it
+should be studied further to clarify this classification.  For
+TIC~405754448, we believe that the source {\it is} an unresolved
+binary, because RUWE$_{\rm DR3}$=6.8, and because the raw light curves
+in Sectors 11, 37, and 38 show an additional $\approx$6.5\,day,
+$\approx$0.3\% amplitude sinusoidal signal suggestive of an unresolved
+photometric companion.  If TIC~405754448 is a K+M binary, then the
+flux ratio between the primary and secondary would be expected to be
+$\approx$10:1.  It would be challenging for the M dwarf to produce the
+observed 12.9\,hr signal with such a flux deficit, but not impossible.
+While both of these objects suggest that the CQV phenomenon may extend
+up in mass to pre-main-sequence K dwarfs, more data are needed to
+fully substantiate this claim.
+
+\subsubsection{An astrophysical CQV false positive: TIC~435903839}
+
+We originally classified TIC~435903839, with RUWE$_{\rm DR3}$=17.7, as
+an ``ambiguous'' CQV with a 10.8\,hr period, because this period
+minimized the dispersion in the phase-folded light curve.  More careful
+inspection however showed that this source is an impostor:
+this source is a
+photometric blend of two ordinary rotating stars with $P_0$=3.60\,hr,
+and $P_1$=5.41\,hr, with a beat period $(P_0^{-1} - P_1^{-1})^{-1}$ of
+10.8\,hr.  This is a novel false positive scenario for CQVs:
+two rapidly-rotating stars with near-integer ratios of rotation
+periods.  The beat between the two rotation signals produces the
+apparent CQV signal.  Such false positives can be excluded through
+careful accounting of all peaks in a periodogram.  For instance,
+TIC~435903839 shows a peak at 16.27\,hr, which is not an integer
+multiple of the dispersion-minimizing 10.82\,hr period.
+
+\subsubsection{Multiple CQVs in the same system: TIC~425937691 and TIC~142173958}
+
+TIC~142173958 and TIC~425937691 both show evidence for two separate
+CQV signals in their TESS light curves.  For TIC~142173958, the
+signals are at 11.76\,hr and 12.84\,hr.  For TIC~425937691, they are
+at $\approx$4.82\,hr and $\approx$3.22\,hr, near the 3:2
+commensurability.  Given that both sources have two photometric
+signals and elevated RUWEs, they are probably unresolved binaries
+consisting of two independent CQVs.  Recent work has shown that the
+orbits of binaries closer than $\lesssim$700 AU tend to be aligned
+with their planetary systems \citep[e.g.][]{2022AJ....163..207C}.  If we
+assume that observing CQV variability similarly requires near edge-on
+viewing geometries, then we might expect a sufficiently close binary
+with one CQV to also have another, since the spin axes in sufficiently
+close binaries would tend to be aligned.  In this scenario, the two
+periods of TIC~425937691 being within $\lesssim$1\% of the 3:2 period
+commensurability would simply be a coincidence.
 
@@
 of limits'' for any dipping material.  This could be evidence that
-some aspect the stellar magnetic field is strongly asymmetric, and can
-generate and hold extrinsic material at corotation, but only over two
+the stellar magnetic field is strongly asymmetric, such that it can
+hold extrinsic material at corotation, but only over two
 thirds of the equatorial circle.  Alternatively, the source of the
@@
 is only relevant in this formulation of the system in that we must
-have $R_{\rm sonic} < R_{\rm cr} < R_{\rm Alfven}$ in order for closed
+have $ R_{\rm cr} < R_{\rm Alfven}$ in order for closed
 loops to exist that can support prominences
-\citep{2019MNRAS.482.2853J}.  In detail however, the locations of such
-magnetic fixed points depends on the star's magnetic field topology
-\citep{2023MNRAS.518.4734S}.
+\citep[e.g.][]{1985Ap&SS.116..285N,2019MNRAS.482.2853J}.  In detail however, the locations of such
+magnetic fixed points depends on the star's magnetic field topology.
 
@@
 Eq.~8.8]{1992oasp.book.....G}, such that at temperatures of
-$\approx$3{,}000\,K to $\approx$10{,}000\,K the observed chromatic
-transit depths might be reproduced.  While bound-free absorption of
-${\rm H}^{-}$ seems like it might be important at such cool temperatures, in
+$\approx$3{,}000\,K to $\approx$10{,}000\,K the observed chromaticities
+might be reproduced.  While bound-free absorption of
+${\rm H}^{-}$ seems like it should be important at such cool temperatures, in
 detail this opacity source has the {\it opposite sign} from
 what is required to produce deeper dips in the blue than in the red.
-Thompson scattering is similarly ruled out as a relevant opacity
-source, because it is gray.  The final plausible alternative opacity
+Thompson scattering is similarly ruled out, because it is gray.
+The final plausible alternative opacity
 source is dust, which has the requisite larger absorption
@@
 question of whether the CQVs are explained by dust or by gas, which
-likely has bearing on whether the material producing the dips is
+has bearing on whether the material producing the dips is
 coming from the star, or whether it is a byproduct of the
@@
 
-In identifying the two ambiguous CQVs with outlying SEDs
+In identifying the two candidate CQVs with outlying SEDs
 (TICs~193136669 and TIC~57830249; Section~\ref{subsec:irexcess}), we
@@
 also worth emphasizing that our labeling of e.g.~TIC~57830249 was
-based on a single sector of TESS data (Sector~36) when its behavior is
+based on a single sector of TESS data (Sector~36) when its behavior was
 relatively periodic and it showed dip depths of a few percent.
@@
 completely different, varying in apparent flux by a factor of two,
-with hardly any discernible periodicity at all.
+with no discernible periodicity at all.
 
@@
 understanding of dippers
-\citep[e.g.][]{2014AJ....147...82C,2016ApJ...816...69A,2021ApJ...908...16R,2022ApJS..263...14C},
+\citep[e.g.][]{2014AJ....147...82C,2016ApJ...816...69A,2021ApJ...908...16R,2022ApJS..263...14C,2022MNRAS.514.1386G},
 it is clear that the loss of an infrared excess is associated with
@@
 The dips in both are probably associated with clumps of dust or gas.
-However the CQV dips are typically more periodic and less deep than
-those of dippers, and they display far less transience over timescales
-of a few to tens of cycles.  This is probably because CQV stars have
+However the CQV dips are both more periodic and less deep than
+those of dippers; they also display far less transience over timescales
+of a few to tens of cycles.  This is presumably because CQVs have
 demonstrably less dust than (most) dipper stars.  At a population
@@
 In general however, it is challenging to interpret the significance of
-the potential regularities listed above;  the CQVs exhibit such a wide
-range of variability that for seemingly any ``regularity'' one might
+the potential ``half-period regularities'';  the CQVs exhibit such a wide
+range of variability that for seemingly any regularity one might
 posit, it is easy to come up with counter-example objects which do not
 follow the trend.  In other words, these half-cycle CQVs could simply
-be a product of the human tendency to pattern match.  The alternative
-is that some subset of these pattern could  have real physical
-significance.
+be a product of the human tendency to pattern match.
 
@@
 transit depth to an effective cloud radius, $R_{\rm cloud}$.  For most
-CQVs in Figure~\ref{fig:cqvs}, this typically yields
-$\approx$2-20\,$R_\oplus$.  This size can be converted into a mass
-estimate by requiring the optical depth $\tau$ of the cloud to be at
-least unity and by positing a cloud composition.  In other
-words, a minimum constraint on the number density follows by requiring
+CQVs in Figure~\ref{fig:cqvs}, this yields
+$\approx$2-20\,$R_\oplus$.  A minimum constraint on the number
+density follows by requiring
 the cloud to be optically thick.  For cases like LP 12-502, this is
@@
 asteroid; the asteroid belt itself has a mass of order
-$\approx$10$^{21}$\,kg \citep{2019Icar..319..812P}.  The previously
-discussed cool gas prominences would need to have masses of order
+$\approx$10$^{21}$\,kg \citep{2019Icar..319..812P}.  If
+the material were
+cool gas prominences rather than dust, the mass would need to be of order
 $10^{14}$\,kg \citep{1990MNRAS.247..415C}, about 100$\times$ larger
@@
 
-Previous work by \citet{2017AJ....153..152S} noted the possible
+\citet{2017AJ....153..152S} previously noted a possible
 connection between the CQVs and rapidly rotating magnetic B stars such
@@
 those in Figure~\ref{fig:cqvs}, with only two broad local minima, and
-one ``hump'' (Figure~\ref{fig:bstar}), top-left; see also
+one ``hump'' (Figure~\ref{fig:bstar}; see also
 \citealt{2022ApJ...924L..10J}).  Within the model proposed by Townsend
 et al., this is explained by the simplicity of the star's magnetic
-field, which to first-order is a dipole, similar to most other
+field, which is well-approximated by a dipole, similar to most other
 magnetic B stars \citep{2007A&A...475.1053A,2009ARA&A..47..333D}.
-This approximation matches the qualitative behavior of both the
+The magnetic axis needs to be tilted relative to the stellar spin
+axis in order to match the qualitative behavior of both the
 broadband light curves, and the line-profile variations seen in
@@
 number of dips per cycle, the shapes of the dips, and the dip depths
-relative to the sinusoidal envelope, all seem to be quite similar.
+relative to the sinusoidal envelope all appear to be similar.
 The implication of this surprising connection is that the
@@
 number density $n\approx10^9\,{\rm cm^{-3}}$, and a plasma temperature
-$10^6\,{\rm K}$ tends to give Alfv\'en radii of order a few times
+$10^6\,{\rm K}$ gives Alfv\'en radii of order a few times
 the corotation radii, $R_{\rm cr}$.
@@
   %
-    \item The majority of detected CQVs have masses of
+    \item Most CQVs are M dwarfs with masses
       0.1-0.5\,$M_\odot$.  Two sources, TIC~405754448 and
@@
 comes from the star, or extrinsic, so that it is sourced through some
-generic evolutionary phase of circumstellar disks.  This knowledge
-would in turn propagate to our understanding of whether the phenomenon
-is primarily teaching us about dust production and processing in
-circumstellar disks, or whether it is teaching us about the ability of
-cold gas to remain stable in hot stellar coronae for long durations.
+generic evolutionary phase of debris disks.  This knowledge would in
+turn propagate to our understanding of whether the phenomenon is
+primarily teaching us about dust production and processing in gas-poor
+disks, or whether it is teaching us about the ability of cold gas to
+remain stable in hot stellar coronae for long durations.
 Observationally, acquisition of medium- or high-resolution time-series
-spectra holds the best chance at resolving the gas vs.~dust question.
-Given the observed evolutionary timescales, such data should be
-acquired simultaneously with photometric time-series observations to
-help clarify its interpretation.
+spectra holds a good chance at resolving the gas vs.~dust question.
+Given our observed $\approx$75\% duty cycles, such data must be
+acquired simultaneously with photometric time-series observations
+(e.g. during TESS re-observation) in order for detections and
+non-detections to be interpretable.
 
@@
 edge-on.  This implies that after correcting for the line-of-sight
-inclination, roughly one third of low mass stars
-\citep{2022AJ....163..144G} could trap circumstellar material in the
-same way.  It also suggests that CQVs may preferentially show
-transiting planets at larger distances than the corotating material,
-though this may be dependent on whether the magnetic and stellar spin
-axes tend to be aligned.  Given these points, observational follow-up
-work should include searching for outer transiting planets, and
-measuring equatorial velocities in order to test whether the stellar
-inclination angles are indeed preferentially edge-on.
+inclination, roughly one third of low mass stars \citep[those that
+rotate rapidly enough][]{2022AJ....163..144G} could trap circumstellar
+material in the same way.  It also suggests that CQVs may
+preferentially show transiting planets at larger distances than the
+corotating material, though this may be dependent on whether the
+magnetic and stellar spin axes tend to be aligned.  Given these
+points, observational follow-up work should include searching for
+outer transiting planets, and measuring equatorial velocities in order
+to test whether the stellar inclination angles are indeed
+preferentially edge-on.  Any source of empirical information on the
+stellar magnetic field, whether from the Zeeman effect
+\citep[e.g.][]{2021A&ARv..29....1K} or perhaps radio emission
+\citep[e.g.][]{2015Natur.523..568H}, could also help clarify the
+strength of the magnetospheres for these objects.
 
@@
 the characteristic size scale of the clumping material would help
-clarify the nature of the magnetic and plasma environments around
-these young stars, and would also help build intuition for why the
-light curves have the bizarre shapes that are observed.  The relevant
-puzzles in plasma physics and radiative transfer could likely be
-connected to our understanding of the close-in rocky planets that are
-expected to be present around most of these stars.  The challenges
-intrinsic to both the observational and theoretical work seem worth
-the effort.
+clarify why the light curves have the bizarre shapes that are
+observed.  The relevant puzzles in plasma physics and radiative
+transfer could perhaps be connected to our understanding of the
+close-in rocky planets that are expected to be present around most of
+these stars.  The challenges intrinsic to both the observational and
+theoretical work seem worth the effort.
 
@@
 LGB gratefully acknowledges support from the Heising-Simons
-51~Pegasi~b Fellowship.  
-A few thank-yous in particular (from LGB) are owed to
-G.~Laughlin, A.~Mann, and J.~Spake for clarifications and ideas, and to E.~Schaller
-and the 51 Peg science team for encouraging lightning talks at the annual summits.
-In addition, this paper relied on data collected by the TESS mission, which are publicly
-available from the Mikulski Archive for Space Telescopes (MAST).
-Funding for the TESS mission is provided by NASA’s Science Mission
-Directorate.  TIC 402980664 in particular was observed at 120-second
-cadence thanks to the TESS Guest Investigator programs G022252 (PI:
-J.~Schlieder; Sectors 18, 19, 25, 26) and G04168 (PI: R.~Jayaraman;
-Sector 53).
+51~Pegasi~b Fellowship.  A few thank-yous in particular (from LGB) are
+owed to G.~Laughlin, A.~Mann, and J.~Spake for clarifications and
+ideas, and to E.~Schaller and the 51 Peg science team for organizing
+the annual summits.  In addition, this paper relied on data collected
+by the TESS mission, which are publicly available from the Mikulski
+Archive for Space Telescopes (MAST).  Funding for the TESS mission is
+provided by NASA’s Science Mission Directorate.  TIC 402980664 in
+particular was observed at 120-second cadence thanks to the TESS Guest
+Investigator programs G022252 (PI: J.~Schlieder; Sectors 18, 19, 25,
+26) and G04168 (PI: R.~Jayaraman; Sector 53).
 
 %{\bf AUTHOR CONTRIBUTION STATEMENTS: PLEASE REVISE IF APPROPRIATE)}
-LGB conceived the project and performed the
-dip-counting search,
-light curve classification,
-cluster membership, SED, and variability analyses.
+LGB conceived the project and performed the dip-counting search, light
+curve classification, cluster membership, SED, variability, and
+secondary-period analyses.
 RJ and SR performed the Fourier-based analysis and contributed
@@
 \startlongtable
-\begin{deluxetable}{rrrrrrlrllrrrr}
+\begin{deluxetable}{rrrrrrlrllrrrrrr}
 \tabletypesize{\footnotesize}
@@
 \startdata
-TIC & $T$ & $d$ & $\bprp$ & RUWE & $P$ & Assoc & Age & $T_{\rm eff}$ & $R_\star$ & $M_\star$ & $R$$_{\rm cr}$ & Quality & $N_{\rm sector}$ \\
--- & mag & pc & mag & -- & hr & -- & Myr & K & $R_\odot$ & $M_\odot$ & $R_\star$ & -- & -- \\
+  TIC & $T$ & $d$ & $\bprp$ & RUWE & $P$ & Assoc & Age & $T_{\rm eff}$ & $R_\star$ & $M_\star$ & $R$$_{\rm cr}$ & $P_{\rm sec}$ & Quality & Bin & $N_{\rm sector}$ \\
+  -- &   mag & pc &    mag &      -- &        hr &   -- &        Myr &  K                  & $R_\odot$ & $M_\odot$ & $R_\star$         & hr                     & -- & -- & -- \\
 \hline
@@
   flag 1), \nmaybes\ ambiguous CQVs (\texttt{Quality} flag 0), and
-  \ndebunked\ impostors (\texttt{Quality} flag -1).  The
+  \ndebunked\ impostors (\texttt{Quality} flag -1).
+The three-bit binarity flag ``Bin'' is for Gaia DR3 \texttt{radial\_velocity\_error} outliers (bit 1), Gaia DR3 \texttt{ruwe} outliers (bit 2), and stars with multiple TESS periods (bit 3).
+The
   machine-readable version, available online, includes additional
-  columns for the Gaia DR2 source identifiers and parameter
+  columns for the Gaia DR2 and DR3 source identifiers, as well as the
+  stellar parameter
   uncertainties.  The age uncertainties are typically $\approx \pm

### 2023-08-15 complexrotators/plotting.py
catalogscatter: better binarity flag

@@ -3728,7 +3728,18 @@ def plot_catalogscatter(outdir, showmaybe=0, plotsubset=None, emphruwe=1):
     # drop "debunked" CQVs
     maybe_df = df[df.quality == 0]
     df = df[df.quality == 1]
-    ruwe_df = pd.concat(( df[df.ruwe > 2], maybe_df[maybe_df.ruwe > 2]))
+    binary_df = pd.concat((
+        df[
+            ( (df.dr3_ruwe > 2) & (df.multipleperiodflag.astype(int)==1) )
+            |
+            (df.rvscatterflag.astype(int)==1)
+        ],
+        maybe_df[
+            ((maybe_df.dr3_ruwe > 2) & (maybe_df.multipleperiodflag.astype(int)==1))
+            |
+            (maybe_df.rvscatterflag.astype(int)==1)
+        ]
+    ))
 
     #y, x, ylabel, xlabel, yscale, xscale
     if plotsubset is None:
@@ -3763,7 +3774,7 @@ def plot_catalogscatter(outdir, showmaybe=0, plotsubset=None, emphruwe=1):
             ('dist_metric_parsec', 'rstar_sedfit', 'dist_metric_parsec', 'rstar_sedfit', 'linear', 'linear'),
             ('dist_metric_parsec', 'mstar_parsec', 'dist_metric_parsec', 'mstar_parsec', 'linear', 'linear'),
             ('banyan_adopted_age', 'age_parsec', 'banyan_adopted_age', 'age_parsec', 'linear', 'linear'),
-            ('ruwe', 'bp_rp', 'RUWE', '$G_{\mathrm{BP}}-G_{\mathrm{RP}}$ [mag]', 'log', 'linear'),
+            ('dr3_ruwe', 'bp_rp', 'DR3 RUWE', '$G_{\mathrm{BP}}-G_{\mathrm{RP}}$ [mag]', 'log', 'linear'),
         ]
     else:
         raise NotImplementedError
@@ -3834,8 +3845,8 @@ def plot_catalogscatter(outdir, showmaybe=0, plotsubset=None, emphruwe=1):
                 ax.text(0.97,0.87, 'Searched TESS targets', transform=ax.transAxes,
                         ha='right',va='top', color='darkgray', fontsize='small',
                         alpha=0.9)
-                ax.text(0.97,0.82, 'RUWE > 2', transform=ax.transAxes,
-                        ha='right',va='top', color='salmon', fontsize='small',
[…]

### 2023-08-15 paper/ms.tex

@@
 
-We analyzed the ``short'' 120-second cadence data acquired by TESS
-between July~2018 and Sep~2022 (Sectors 1-55).  Specifically, we used
+To construct our sample, we analyzed the short-cadence data acquired by TESS
+between 2018 July 25 and 2022 September 1 (Sectors 1-55).  Specifically, we used
 the 120-second cadence light curves produced by the Science Processing
@@
 interest, which we defined as stars with 120-second cadence TESS light
-curves that satisfied
+curves satisfying these four conditions:
 \begin{align}
   T &< 16 \quad&(\mathrm{Bright\ for\ TESS})\\
-  \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only}) \\
-  M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})  \\
-  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}),
+  \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only})\\
+  M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})\\
+  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}).
 \end{align}
-for $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ the Gaia $G$-band
-absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
-arcseconds, and a geometric distance $d$ defined by inverting the
+Here, $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ is the Gaia $G$-band
+absolute magnitude, $\varpi_{\rm as}$ is the parallax in units of
+arcseconds, and $d$ is a geometric distance defined by inverting the
 parallax and ignoring any zero-point correction.  The target sample
@@
 \citep{2021zndo...1011188B} due to its shape agnosticism.  If a period
-below 2 days was identified, we reran the periodogram at a finer grid
+$P$ below 2 days was identified, we reran the periodogram at a finer grid
 to improve the accuracy of the period determination.
 
-Once a star's period $P$ was identified, we binned the phased light
+Once a star's period was identified, we binned the phased light
 curve to 100 points per cycle.  To separate ``sharp'' local minima
-from smooth spot-induced variability, we then iteratively fit robust
-penalized splines to the wrapped phase-folded light curve, excluding
-points more than two standard deviations away from the local continuum
-\citep{2019AJ....158..143H}.  The maximum number of equidistant spline
-knots per cycle is the parameter in this framework that controlled the
-meaning of ``sharp'' --- we allowed at most 10 such knots per cycle,
-though for most stars fewer knots were preferred based on
-cross-validation using an $\ell^2$-norm penalty.  An example fit is
-shown in panel {\it (e)} of Figure~\ref{fig:vet}.
+from smooth but double-dipped spot variability, we then iteratively
+fit robust penalized splines to the wrapped phase-folded light curve,
+excluding points more than two standard deviations away from the local
+continuum \citep{2019AJ....158..143H}.  The maximum number of
+equidistant spline knots per cycle is the parameter in this framework
+that controlled the meaning of ``sharp'' --- we allowed at most 10
+such knots per cycle, though for most stars fewer knots were preferred
+based on cross-validation using an $\ell^2$-norm penalty.  An example
+fit is shown in panel {\it (e)} of Figure~\ref{fig:vet}.
 
@@
       objects in Table~\ref{tab:thetable}
-			is available online {\bf For internal collaboration review:
+			is available in the online journal. {\bf For internal collaboration review:
 				\url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
@@
 consulted the meta-catalog of young, age-dated, and age-dateable stars
-within a kiloparsec from \citet{2022AJ....163..121B}, and also
+within from \citet{2022AJ....163..121B}, and also
 searched the local volume around each star for co-moving
@@
 evidence supporting the reality and youth of that group.  The yield
-in Sco-Cen is not surprising, since Sco-Cen contains the majority of
-pre-main-sequence stars in the solar neighborhood, any many of its stars
+in Sco-Cen is not surprising since Sco-Cen contains the majority of
+pre-main-sequence stars in the solar neighborhood, and many of its stars
 were selected for TESS 120-second cadence observations by various
@@
 
-Most CQVs in our catalog did not show infrared excesses in the W1-W4
+Most CQVs in our catalog did not show infrared excesses in the $W1$-$W4$
 bands, which is typical for this class of object
@@
 This threshold was met for \ngoodhighruwe/\ngoods\ high-quality CQVs;
-\nmaybehighruwe/\nmaybes\ of the ambiguous sample
-had this characteristic.
-There is some subjectivity in where to set the threshold, since the RUWE distribution has
-an extended tail \citep[e.g.][]{2022MNRAS.513.5270P}.
-If we had instead required RUWE$_{\rm DR3}$ $>$ 1.4,
-\ngoodweakruwe/\ngoods\ high-quality CQVs and \nmaybeweakruwe/\nmaybes\ of the ambiguous sample
-would have been flagged.
+\nmaybehighruwe/\nmaybes\ of the ambiguous ones had this
+characteristic.  There is some subjectivity in where to set the
+threshold, since the RUWE distribution has an extended tail
+\citep[e.g.][]{2022MNRAS.513.5270P}.  If we had instead required
+RUWE$_{\rm DR3}$ $>$ 1.4, \ngoodweakruwe/\ngoods\ high-quality CQVs
+and \nmaybeweakruwe/\nmaybes\ of the ambiguous sample would have been
+flagged.
 
 {\it Gaia DR3 non-single stars}---Gaia DR3 included a
-``non\_single\_star'' column that flagged known or suspected
+{\tt non\_single\_star} column that flagged known or suspected
 eclipsing, astrometric, and spectroscopic binaries.  None of the stars
@@
 this effort are summarized in the secondary periods, $P_{\rm sec}$,
-listed in Table~\ref{tab:thetable}.  This process yielded \ngoodmultperiodflag/\ngoods\ high-quality CQVs
-with secondary periods; \nmaybemultperiodflag/\nmaybes\ of the ambiguous
-sample met the same criterion.
-Of the \ngoodhighruwe\ good CQVs with RUWE$_{\rm DR3}$ $>$ 2,
-\ngoodruweandmultperiod\ also showed secondary periods in the TESS
-light curves.
-Considering the weaker threshold of 
-RUWE$_{\rm DR3}$ $>$ 1.4,
-\ngoodweakruweandmultperiod/\ngoodweakruwe\ such CQVs showed secondary TESS periods.
-
-Table~\ref{tab:thetable} summarizes
-each of the above sources of information into a single
-bitwise column.
-We discuss possible connections between binarity and the CQV phenomenon
-in Section~\ref{subsec:discbinary}.
+listed in Table~\ref{tab:thetable}.  This process yielded
+\ngoodmultperiodflag/\ngoods\ high-quality CQVs with secondary
+periods; \nmaybemultperiodflag/\nmaybes\ of the ambiguous sample met
+the same criterion.  Of the \ngoodhighruwe\ good CQVs with RUWE$_{\rm
+DR3}$ $>$ 2, \ngoodruweandmultperiod\ also showed secondary periods in
+the TESS light curves.  Considering the weaker threshold of RUWE$_{\rm
+DR3}$ $>$ 1.4, \ngoodweakruweandmultperiod/\ngoodweakruwe\ such CQVs
+showed secondary TESS periods.
+
+Table~\ref{tab:thetable} summarizes each of the above sources of
+information into a single bitwise column.  We discuss possible
+connections between binarity and the CQV phenomenon in
+Section~\ref{subsec:discbinary}.
 
@@
 
-A small fraction of our objects were in regions of sky with
-many sectors of adjacent TESS data.  Out of this already small sample, LP 12-502
-(TIC 402980664; $d$=21\,pc, $J$=9.4, $T$=11.1) stood out due to the
-quality and content of its data.  We discuss another interesting
+A small fraction of our objects were in regions of sky with many
+sectors of adjacent TESS data.  Out of this already small sample, LP
+12-502 (TIC 402980664; $d$=21\,pc, $J$=9.4, $T$=11.1) stood out due to
+the quality and content of its data.  We discuss another interesting
 source, TIC~300651846, in Appendix~\ref{app:tic3006}.  In this
-section, we first present the LP 12-502 observations
-(Section~\ref{subsec:lpobservations}), and then highlight their
-implications (Section~\ref{subsec:lplessons}).
+section, we first present the LP 12-502 observations and then
+highlight their implications.
 
@@
 light curve shapes evolve over 10 to 1{,}000 cycles.  They are
-therefore {\it quasi}periodic.  This observation is consistent studies
-by \citet{2022AJ....163..144G} and \citet{2023ApJ...945..114P}.
-However it marks a qualitative departure from the ``persistent'' {\it
-vs.} ``transient'' flux dip distinction described by
-\citet{2017AJ....153..152S};  since all CQV dips seem to be transient
-over timescales of more than 1{,}000 cycles (Figure~\ref{fig:evoln}).
+therefore {\it quasi}periodic.  While this observation is consistent
+with the analyses by \citet{2022AJ....163..144G} and
+\citet{2023ApJ...945..114P}, it marks a qualitative departure from the
+``persistent'' {\it vs.} ``transient'' flux dip distinction described
+by \citet{2017AJ....153..152S}, since all CQV dips seem to be
+transient over timescales of more than 1{,}000 cycles
+(Figure~\ref{fig:evoln}).
 
@@
 period (Figure~\ref{fig:lp}).  The remaining third seems to be ``out
-of limits'' for any dipping material.  This could be evidence that
-the stellar magnetic field is strongly asymmetric, such that it can
-hold extrinsic material at corotation, but only over two
-thirds of the equatorial circle.  Alternatively, the source of the
-material (e.g. a planetesimal swarm) might be distributed over an arc
-of the same angular extent (240$^\circ$).  We favor the former
-explanation, for reasons discussed below.
+of limits'' for any dipping material.  This could be evidence that the
+stellar magnetic field is strongly asymmetric, and can hold extrinsic
+material at corotation, but only over two thirds of the equatorial
+circle.  Alternatively, the source of the material (e.g. a
+planetesimal swarm) might be distributed over an arc of the same
+angular extent (240$^\circ$).  We favor the former explanation, for
+reasons discussed below.
 
@@
 what is required to produce deeper dips in the blue than in the red.
-Thompson scattering is similarly ruled out, because it is gray.
-The final plausible alternative opacity
+Thomson scattering is similarly ruled out as a relevant opacity
+source, because it is gray.  The final plausible alternative opacity
 source is dust, which has the requisite larger absorption
@@
 stars.  This broadly assumes that any star that can support
-prominences will, and that the magnetic topology of rapidly rotating M
+prominences will do so, and that the magnetic topology of rapidly rotating M
 dwarfs at 100\,Myr is similar to that of rapidly rotating M dwarfs at
@@
 one ``hump'' (Figure~\ref{fig:bstar}; see also
-\citealt{2022ApJ...924L..10J}).  Within the model proposed by Townsend
-et al., this is explained by the simplicity of the star's magnetic
-field, which is well-approximated by a dipole, similar to most other
-magnetic B stars \citep{2007A&A...475.1053A,2009ARA&A..47..333D}.
-The magnetic axis needs to be tilted relative to the stellar spin
-axis in order to match the qualitative behavior of both the
-broadband light curves, and the line-profile variations seen in
-hydrogen, helium, and carbon \citep{2012MNRAS.419..959O}.
+\citealt{2022ApJ...924L..10J}).  Within the model proposed by
+\citeauthor{2005ApJ...630L..81T}, this is explained by the simplicity
+of the star's magnetic field, which is well-approximated by a dipole,
+similar to most other magnetic B stars
+\citep{2007A&A...475.1053A,2009ARA&A..47..333D}.  The magnetic axis
+needs to be tilted relative to the stellar spin axis in order to match
+the qualitative behavior of both the broadband light curves, and the
+line-profile variations seen in hydrogen, helium, and carbon
+\citep{2012MNRAS.419..959O}.
 
@@
 A simple order of magnitude estimate assuming a dipole field with
-$B_0\approx1\,{\rm kG}$ at the star's surface, a local plasma
-number density $n\approx10^9\,{\rm cm^{-3}}$, and a plasma temperature
-$10^6\,{\rm K}$ gives Alfv\'en radii of order a few times
-the corotation radii, $R_{\rm cr}$.
+$B_0\approx1\,{\rm kG}$ at the star's surface, a local plasma number
+density $n\approx10^9\,{\rm cm^{-3}}$, and a plasma temperature
+$10^6\,{\rm K}$ gives Alfv\'en radii of order a few times the
+corotation radii, $R_{\rm cr}$.  This suggests that the existence of a
+centrifugal magnetosphere is plausible in young, rapidly rotating M
+dwarfs.
 

### 2023-08-15 paper/ms.tex
ms: clean up latex

@@
 
-%\title{Pre-Main-Sequence M-Dwarfs With Complex Quasiperiodic Variability From Four Years of TESS}
-%\title{Complex Quasiperiodic Variables From Four Years of TESS}
 \title{Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS}
@@
 \begin{abstract}
-  Complex quasiperiodic variables (CQVs) are low-mass pre-main-sequence
-  stars with nearly periodic optical modulation.  The modulation is
-  likely induced by dust or gas clumps in orbit at the Keplerian
-  corotation radius.  Here, we report new CQVs discovered in TESS
-  short-cadence data collected between July~2018 and Sep~2022.  Our
-  search of \nstarssearched\ K and M dwarfs with $T$$<$16 and
-  $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most of these
-  discoveries are new, and they include the brightest
+  Complex quasiperiodic variables (CQVs) are low-mass
+  pre-main-sequence stars with nearly periodic optical modulation.
+  The modulation is likely induced by dust or gas clumps in orbit at
+  the Keplerian corotation radius.  Here, we report new CQVs
+  discovered in TESS short-cadence data collected between July~2018
+  and Sep~2022.  Our search of \nstarssearched\ K and M dwarfs with
+  $T$$<$16 and $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most
+  of these discoveries are new, and they include the brightest
   ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and oldest
@@
 \citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  Since the
-CQVs are probably all explained by the same phenomenon, we
-therefore discard the ``spot-only'' scenario.
+CQVs are probably all explained by the same phenomenon, we therefore
+discard the ``spot-only'' scenario.
 
@@
 variability are shown in Figure~\ref{fig:f1}.  The ``clump'' scenario
-invokes opaque dust clumps periodically transiting the star near the Keplerian corotation
-radius, $R_{\rm cr} = (GM/\Omega^2)^{1/3}$
+invokes opaque dust clumps periodically transiting the star near the
+Keplerian corotation radius, $R_{\rm cr} = (GM/\Omega^2)^{1/3}$
 \citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The ``prominence''
@@
 though at much larger relative distances from the stellar surface.  A
-final possibility is one of a ``screen'', in
-which the inner wall of a quiescent circumstellar disk blocks a
-portion of the stellar surface to produce sudden dips whenever spots
-come into view \citep{2019ApJ...876..127Z}.
+final possibility is one of a ``screen'', in which the inner wall of a
+quiescent circumstellar disk blocks a portion of the stellar surface
+to produce sudden dips whenever spots come into view
+\citep{2019ApJ...876..127Z}.
 
@@
 transitions in hydrogen or perhaps a molecular opacity.  The screen
-scenario seems inconsistent with the sharpness
-of the observed dips,
+scenario seems inconsistent with the sharpness of the observed dips,
 the lack of infrared excess, and the observed lifetime of CQVs
@@
 spectroscopic analyses.  To do this, we use 120-second cadence data
-acquired by TESS between 2018 July and 2022 September (Sectors 1-55; Cycles
-1-4).  We present our search methods in Section~\ref{sec:methods}, and
-the properties of the resulting CQV catalog in
-Section~\ref{sec:results}.  The evolution of many CQVs over a two-year
-baseline is described in Section~\ref{sec:evoln}, including a
-deep-dive into LP 12-502.  We discuss a few implications in
+acquired by TESS between 2018 July and 2022 September (Sectors 1-55;
+Cycles 1-4).  We present our search methods in
+Section~\ref{sec:methods}, and the properties of the resulting CQV
+catalog in Section~\ref{sec:results}.  The evolution of many CQVs over
+a two-year baseline is described in Section~\ref{sec:evoln}, including
+a deep-dive into LP 12-502.  We discuss a few implications in
 Section~\ref{sec:discussion}, and conclude in
@@
 CQVs should not be conflated with ``dippers'', which are classical T
-Tauri stars with infrared excesses, and which show large-amplitude variability
-linked to obscuring inner disk structures and accretion hot spots
-\citep{2014AJ....147...82C,2021ApJ...908...16R}.  While a few
-similarities between CQVs and dippers do exist (see
+Tauri stars with infrared excesses, and which show large-amplitude
+variability linked to obscuring inner disk structures and accretion
+hot spots \citep{2014AJ....147...82C,2021ApJ...908...16R}.  While a
+few similarities between CQVs and dippers do exist (see
 Sections~\ref{subsec:irexcess} and~\ref{subsec:discdippers}), their
-phenomenology and stellar properties are quite different.  At the
-risk of introducing yet another standard, we hope to use a
-nomenclature that reflects how, when observed over timescales of more
-than tens of cycles, CQVs are almost but not exactly periodic.  They
-are quasiperiodic.  While the three-type classification scheme
-proposed by \citet{2017AJ....153..152S} may indeed provide some
-helpful visual distinctions amongst the CQVs, it seems likely that
-they are all explained by a single underlying phenomenon, and so we
-opt to refer to them by a single empirically descriptive name.  We
-also considered names that focused on the presence of transient
-corotating clumps, or more generally on circumstellar plasma tori;
-for the time being, ``CQV'' is agnostic to the true underlying phenomenon.
+phenomenology and stellar properties are quite different.  At the risk
+of introducing yet another standard, we hope to use a nomenclature
+that reflects how, when observed over timescales of more than tens of
+cycles, CQVs are almost but not exactly periodic.  They are
+quasiperiodic.  While the three-type classification scheme proposed by
+\citet{2017AJ....153..152S} may indeed provide some helpful visual
+distinctions amongst the CQVs, it seems likely that they are all
+explained by a single underlying phenomenon, and so we opt to refer to
+them by a single empirically descriptive name.  We also considered
+names that focused on the presence of transient corotating clumps, or
+more generally on circumstellar plasma tori; for the time being,
+``CQV'' is agnostic to the true underlying phenomenon.
 
@@
 
-To construct our sample, we analyzed the short-cadence data acquired by TESS
-between 2018 July 25 and 2022 September 1 (Sectors 1-55).  Specifically, we used
-the 120-second cadence light curves produced by the Science Processing
-and Operations Center at NASA Ames \citep{2016SPIE.9913E..3EJ}.  While
-the TESS data products from these sectors also included full frame
-images with cadences of 600 and 1800 seconds, we limited our scope in
-this study for the sake of simplicity in data handling and some degree of 
-uniformity in the properties of the data itself.  In exchange,
-we sacrificed both completeness and homogeneity of the selection
-function.  While TESS cumulatively observed $\approx$90\% of the sky
-for at least one lunar month between 2018 July and 2022 September, the
-120-second cadence data were collected for only a subset of observable
-stars during this time due to telemetric constraints
-\citep[see][]{2021PASP..133i5002F}.
+To construct our sample, we analyzed the short-cadence data acquired
+by TESS between 2018 July 25 and 2022 September 1 (Sectors 1-55).
+Specifically, we used the 120-second cadence light curves produced by
+the Science Processing and Operations Center at NASA Ames
+\citep{2016SPIE.9913E..3EJ}.  While the TESS data products from these
+sectors also included full frame images with cadences of 600 and 1800
+seconds, we limited our scope in this study for the sake of simplicity
+in data handling and some degree of uniformity in the properties of
+the data itself.  In exchange, we sacrificed both completeness and
+homogeneity of the selection function.  While TESS cumulatively
+observed $\approx$90\% of the sky for at least one lunar month between
+2018 July and 2022 September, the 120-second cadence data were
+collected for only a subset of observable stars during this time due
+to telemetric constraints \citep[see][]{2021PASP..133i5002F}.
 
@@
 exercise showed that for $T$$<$16 M dwarfs, the TESS 2-minute data are
-$\approx$50\% complete at $\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\%
-of the $T$$<$16 M dwarfs have at least one sector of short-cadence
-data; at $>$100\,pc, $\lesssim$10\% of such M dwarfs have at least one
-sector of short-cadence data.  Armed with this understanding, we then
-used our cross-match between Gaia DR2 and TIC8 to select our stars of
-interest, which we defined as stars with 120-second cadence TESS light
-curves satisfying these four conditions:
+$\approx$50\% complete at $\approx$50\,pc.  At $<$20\,pc,
+$\gtrsim$80\% of the $T$$<$16 M dwarfs have at least one sector of
+short-cadence data; at $>$100\,pc, $\lesssim$10\% of such M dwarfs
+have at least one sector of short-cadence data.  Armed with this
+understanding, we then used our cross-match between Gaia DR2 and TIC8
+to select our stars of interest, which we defined as stars with
+120-second cadence TESS light curves satisfying these four conditions:
 \begin{align}
@@
 \end{align}
-Here, $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ is the Gaia $G$-band
-absolute magnitude, $\varpi_{\rm as}$ is the parallax in units of
-arcseconds, and $d$ is a geometric distance defined by inverting the
-parallax and ignoring any zero-point correction.  The target sample
-therefore includes \nstarssearched\ M dwarfs and late-K dwarfs, down
-to $T$$<$16 and out to $d$$<$150\,pc.
+Here, $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ is the Gaia
+$G$-band absolute magnitude, $\varpi_{\rm as}$ is the parallax in
+units of arcseconds, and $d$ is a geometric distance defined by
+inverting the parallax and ignoring any zero-point correction.  The
+target sample therefore includes \nstarssearched\ M dwarfs and late-K
+dwarfs, down to $T$$<$16 and out to $d$$<$150\,pc.
 
@@
 
-For our dip-counting pipeline, we began with the {\tt PDC\_SAP} flux for
-each sector, removed non-zero quality flags, and normalized the light
-curve to one by dividing out its median value.  We then flattened the
-light curve using a 5-day sliding median filter, as implemented in
-\texttt{wotan} \citep{2019AJ....158..143H}.  On the resulting cleaned
-and flattened light curve, we ran a periodogram search, opting for the
-\citet{1978ApJ...224..953S} phase dispersion minimization (PDM)
-algorithm implemented in \texttt{astrobase}
+For our dip-counting pipeline, we began with the {\tt PDC\_SAP} flux
+for each sector, removed non-zero quality flags, and normalized the
+light curve to one by dividing out its median value.  We then
+flattened the light curve using a 5-day sliding median filter, as
+implemented in \texttt{wotan} \citep{2019AJ....158..143H}.  On the
+resulting cleaned and flattened light curve, we ran a periodogram
+search, opting for the \citet{1978ApJ...224..953S} phase dispersion
+minimization (PDM) algorithm implemented in \texttt{astrobase}
 \citep{2021zndo...1011188B} due to its shape agnosticism.  If a period
-$P$ below 2 days was identified, we reran the periodogram at a finer grid
-to improve the accuracy of the period determination.
-
-Once a star's period was identified, we binned the phased light
-curve to 100 points per cycle.  To separate ``sharp'' local minima
-from smooth but double-dipped spot variability, we then iteratively
-fit robust penalized splines to the wrapped phase-folded light curve,
+$P$ below 2 days was identified, we reran the periodogram at a finer
+grid to improve the accuracy of the period determination.
+
+Once a star's period was identified, we binned the phased light curve
+to 100 points per cycle.  To separate ``sharp'' local minima from
+smooth but double-dipped spot variability, we then iteratively fit
+robust penalized splines to the wrapped phase-folded light curve,
 excluding points more than two standard deviations away from the local
@@
 
-To identify local minima near the edges of the phased light
-curve, which usually would cover phases $\phi \in [ 0,1 ]$, we
-performed the entire procedure over a phase-folded light curve
-spanning $\phi \in [-1,2 ]$, by duplicating and concatenating the
-ordinary phase-folded light curve.  The free parameters we adopted
-throughout this analysis procedure, for instance the maximum number of
-spline knots per cycle, and how large and wide of a local minimum to
-consider a ``true dip'', were chosen during testing based on their
-ability to correctly re-identify a large fraction ($>$90\%) of known
-CQVs, while also being able to consistently reject common false
-positives such as rapidly rotating spot-induced variability and
-typical eclipsing binaries.
+To identify local minima near the edges of the phased light curve,
+which usually would cover phases $\phi \in [ 0,1 ]$, we performed the
+entire procedure over a phase-folded light curve spanning $\phi \in
+[-1,2 ]$, by duplicating and concatenating the ordinary phase-folded
+light curve.  The free parameters we adopted throughout this analysis
+procedure, for instance the maximum number of spline knots per cycle,
+and how large and wide of a local minimum to consider a ``true dip'',
+were chosen during testing based on their ability to correctly
+re-identify a large fraction ($>$90\%) of known CQVs, while also being
+able to consistently reject common false positives such as rapidly
+rotating spot-induced variability and typical eclipsing binaries.
 
@@
 and \citet[][their Section~1.3]{2023MNRAS.524.4220P}.  Starting with
-the {\tt PDC\_SAP} light curves, we normalized each light curve, and then
-re-binned it into equal width 120-second bins to account for the
+the {\tt PDC\_SAP} light curves, we normalized each light curve, and
+then re-binned it into equal width 120-second bins to account for the
 uneven spacing in the TESS data, as well as the data gap caused by
@@
 we performed this analysis, we found that ``summary'' sheets were
-generated for $\approx$10\% of the 20\,000 120-second targets in
-a given sector.  We then manually reviewed each summary sheet, and
+generated for $\approx$10\% of the 20\,000 120-second targets in a
+given sector.  We then manually reviewed each summary sheet, and
 visually labelled each star based on its morphology (including e.g.,
@@
 false-positive rate, because it was implemented as a general
-variability search; its results are also being used for analyses
-on topics other than CQVs.
+variability search; its results are also being used for analyses on
+topics other than CQVs.
 
@@
 consulted the meta-catalog of young, age-dated, and age-dateable stars
-within from \citet{2022AJ....163..121B}, and also
-searched the local volume around each star for co-moving
+within from \citet{2022AJ....163..121B}, and also searched the local
+volume around each star for co-moving
 companions.\footnote{\url{https://github.com/adamkraus/Comove}, git
@@
 our SED fit to avoid any possible bias induced by chromospheric UV
-excess; we similarly omitted WISE bands $W3$ and $W4$, but due to reliability
-concerns.  \texttt{astroARIADNE} compares the measured broadband flux
-measurements against pre-computed model grids, and by default fits for
-six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
-Fe/H}], d \}$.  The distance  prior is drawn from
+excess; we similarly omitted WISE bands $W3$ and $W4$, but due to
+reliability concerns.  \texttt{astroARIADNE} compares the measured
+broadband flux measurements against pre-computed model grids, and by
+default fits for six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V},
+\log g, [{\rm Fe/H}], d \}$.  The distance  prior is drawn from
 \citet{2021AJ....161..147B}.  The surface gravity and metallicity are
@@
 our search.  The ``high-quality sample'' includes \ngoods\ objects,
-which demonstrated what we viewed as unambiguous
-characteristics of the CQV phenomenon in at least one TESS sector.
-The classification of \nmaybes\ CQV candidates was ambiguous, and the
-\ndebunked\ remaining objects were false positives that we discuss below.
-The \texttt{quality} column in the table divides the three classes;
+which demonstrated what we viewed as unambiguous characteristics of
+the CQV phenomenon in at least one TESS sector.  The classification of
+\nmaybes\ CQV candidates was ambiguous, and the \ndebunked\ remaining
+objects were false positives that we discuss below.  The
+\texttt{quality} column in the table divides the three classes;
 additional data from TESS or other instruments could help resolve the
@@
 
-% This is consistent with Rappaport2014's visual binary fraction
-% determined from 30/100 rapidly rotating Kepler stars having multiple
-% periodicities
-
 In terms of the light curve shapes, Figure~\ref{fig:cqvs} shows a
@@
 TIC~224283342, TIC~402980664).  Others show structured modulation over
-the entire span of a cycle (e.g. TIC~2234692, TIC~425933644, TIC~142173958).  Others show some mix between these two
-modes.
+the entire span of a cycle (e.g. TIC~2234692, TIC~425933644,
+TIC~142173958).  Others show some mix between these two modes.
 
@@
 
-Of our \ncqvsnodebunked\ confirmed and candidate CQVs, \nnotfieldbanyan\
-were associated with a nearby moving group or open cluster, primarily using
-BANYAN\,$\Sigma$.\footnote{Two of the
-	\nnotfieldbanyan\ memberships were made with low confidence and are flagged
-	in Table~\ref{tab:thetable}.
-	One membership, of TIC~397791443 in IC\,2602, was made manually
-	from a literature search
-	\citep[e.g.][]{2020A&A...633A..99C}.}  
-The relevant groups are listed in
-Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  
-The
+Of our \ncqvsnodebunked\ confirmed and candidate CQVs,
+\nnotfieldbanyan\ were associated with a nearby moving group or open
+cluster, primarily using BANYAN\,$\Sigma$.\footnote{Two of the
+\nnotfieldbanyan\ memberships were made with low confidence and are
+flagged in Table~\ref{tab:thetable}.  One membership, of TIC~397791443
+in IC\,2602, was made manually from a literature search
+\citep[e.g.][]{2020A&A...633A..99C}.}  The relevant groups are listed
+in Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  The
 most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CQVs
@@
 \citep{2019ApJ...870...27Z}, which serves as an indirect line of
-evidence supporting the reality and youth of that group.  The yield
-in Sco-Cen is not surprising since Sco-Cen contains the majority of
-pre-main-sequence stars in the solar neighborhood, and many of its stars
-were selected for TESS 120-second cadence observations by various
-guest investigators.  Given the
-$\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there may
-be many more CQVs in Sco-Cen that remain to be discovered.
-
-For the two stars for which BANYAN\,$\Sigma$ did not
-find any association, we were not able to confidently associate either
-star with any young groups.  Both do seem to show the CQV signal over
+evidence supporting the reality and youth of that group.  The yield in
+Sco-Cen is not surprising since Sco-Cen contains the majority of
+pre-main-sequence stars in the solar neighborhood, and many of its
+stars were selected for TESS 120-second cadence observations by
+various guest investigators.  Given the $\lesssim$$10\%$ completeness
+of TESS beyond 100\,pc, there may be many more CQVs in Sco-Cen that
+remain to be discovered.
+
+For the two stars for which BANYAN\,$\Sigma$ did not find any
+association, we were not able to confidently associate either star
+with any young groups.  Both do seem to show the CQV signal over
 multiple TESS sectors, and both are photometrically elevated relative
@@
 similarly-aged Psc-Eri member \citep{2020A&A...639A..64R}.  To our
-knowledge, TIC~332517282 in AB~Dor was the previous record-holder for the
-oldest-known CQV \citep{2019ApJ...876..127Z,2022AJ....163..144G}; at
-least one unambiguous CQV (EPIC~211070495) and a few other candidates
-were also previously known in the Pleiades
+knowledge, TIC~332517282 in AB~Dor was the previous record-holder for
+the oldest-known CQV \citep{2019ApJ...876..127Z,2022AJ....163..144G};
+at least one unambiguous CQV (EPIC~211070495) and a few other
+candidates were also previously known in the Pleiades
 \citep{2016AJ....152..114R}.
-
-% NOTE: it'd be useful to get an RV for this one...
 
@@
 candidate membership of TIC~294328887 in the Carina Near moving group
-\citep{2006ApJ...649L.115Z}.  This group's $200 \pm 50$\,Myr age
-is based on the lithium sequence of its G-dwarfs
+\citep{2006ApJ...649L.115Z}.  This group's $200 \pm 50$\,Myr age is
+based on the lithium sequence of its G-dwarfs
 \citep{2006ApJ...649L.115Z}, which shows a coeval population of stars
@@
 
-Most CQVs in our catalog did not show infrared excesses in the $W1$-$W4$
-bands, which is typical for this class of object
+Most CQVs in our catalog did not show infrared excesses in the
+$W1$-$W4$ bands, which is typical for this class of object
 \citep{2017AJ....153..152S}.  Visually inspecting the SEDs of our
 \nallcands\ star sample and the WISE images available through IRSA, we
-labeled two objects as having reliable infrared excesses (both $W3$ and
-$W4$ at $>$3$\sigma$ above the photospheric prediction).
-
-The two sources exhibiting an IR excess were TIC~193136669 (TWA~34) and TIC~57830249
-(TWA~33).  Both are in the TW Hydrae association ($\approx$10\,Myr),
-and have relatively long periods of 38\,hr and 44\,hr respectively.
-In our initial labeling, we labeled both as ``ambiguous'' CQVs because
-the dips in their light curves did not show the rigid periodicity
-typical of CQVs;  their periods were also relatively long.  However,
-inspection of further sectors clarified that both sources are dippers
-(see online plots in Figure~\ref{fig:vet}).  Independently, TIC
-193136669 has a cold molecular disk based on observed 1.3\,mm
-continuum emission and resolved Keplerian $^{12}{\rm CO}(2-1)$
-emission \citep{2015A&A...582L...5R}.  It was also labeled a dipper by
+labeled two objects as having reliable infrared excesses (both $W3$
+and $W4$ at $>$3$\sigma$ above the photospheric prediction).
+
+The two sources exhibiting an IR excess were TIC~193136669 (TWA~34)
+and TIC~57830249 (TWA~33).  Both are in the TW Hydrae association
+($\approx$10\,Myr), and have relatively long periods of 38\,hr and
+44\,hr respectively.  In our initial labeling, we labeled both as
+``ambiguous'' CQVs because the dips in their light curves did not show
+the rigid periodicity typical of CQVs;  their periods were also
+relatively long.  However, inspection of further sectors clarified
+that both sources are dippers (see online plots in
+Figure~\ref{fig:vet}).  Independently, TIC 193136669 has a cold
+molecular disk based on observed 1.3\,mm continuum emission and
+resolved Keplerian $^{12}{\rm CO}(2-1)$ emission
+\citep{2015A&A...582L...5R}.  It was also labeled a dipper by
 \citet{2022ApJS..263...14C}; we agree with their designation, and
@@
       Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
-			ambiguous CQV candidates are light blue circles.  
-			Unresolved binaries are flagged either if the Gaia DR3 radial
-			velocity scatter exceeded 20\,\kms, or if
-			Gaia ${\rm RUWE}_{\rm DR3}$$>$2 and multiple photometric signals were present in the
-			TESS light curve.
-			The top panels show the \nstarssearched\ target stars with
-			120-second cadence TESS data as the shaded gray background;
+      ambiguous CQV candidates are light blue circles.  Unresolved
+      binaries are flagged either if the Gaia DR3 radial velocity
+      scatter exceeded 20\,\kms, or if Gaia ${\rm RUWE}_{\rm DR3}$$>$2
+      and multiple photometric signals were present in the TESS light
+      curve.  The top panels show the \nstarssearched\ target stars
+      with 120-second cadence TESS data as the shaded gray background;
       darker regions correspond to a larger relative number of
@@
 
-{\it Radial velocity scatter}---We examined diagrams of the Gaia
-DR3 ``radial velocity error'' as a function of stellar color for all
+{\it Radial velocity scatter}---We examined diagrams of the Gaia DR3
+``radial velocity error'' as a function of stellar color for all
 \ncqvsnodebunked\ CQVs and candidate CQVs.  Since this quantity
@@
 These plots showed two clusters of stars, at $\lesssim$10\,\kms and
-20-25\,\kms.  We there adopted a threshold of $20$\,km\,s$^{-1}$
-to flag possible single-lined spectroscopic binaries, which selected
-\nrvscatterflag\ stars: TIC~405910546, TIC~224283342, and TIC~280945693.
-
-{\it RUWE}---We examined plots of Gaia DR3 RUWE as a function of color.\footnote{For
-an explanation of the renormalized unit weight error (RUWE), see the
-GAIA DPAC technical note \url{http://www.rssd.esa.int/doc_fetch.php?
-id=3757412}.}  Elevated RUWEs imply excess noise relative to a
-single-source astrometric model.  This can be caused by marginally
-resolved point sources skewing the single-transit centroid
-measurements,  intrinsic photometric variability, or intrinsic
-astrometric motion.  Based on this exercise, we adopted a threshold of
-RUWE$_{\rm DR3}$ $>$ 2 to flag sources with excess astrometric noise.
-This threshold was met for \ngoodhighruwe/\ngoods\ high-quality CQVs;
+20-25\,\kms.  We there adopted a threshold of $20$\,km\,s$^{-1}$ to
+flag possible single-lined spectroscopic binaries, which selected
+\nrvscatterflag\ stars: TIC~405910546, TIC~224283342, and
+TIC~280945693.
+
+{\it RUWE}---We examined plots of Gaia DR3 RUWE as a function of
+color.\footnote{For an explanation of the renormalized unit weight
+error (RUWE), see the GAIA DPAC technical note
+\url{http://www.rssd.esa.int/doc_fetch.php?  id=3757412}.}  Elevated
+RUWEs imply excess noise relative to a single-source astrometric
+model.  This can be caused by marginally resolved point sources
+skewing the single-transit centroid measurements,  intrinsic
+photometric variability, or intrinsic astrometric motion.  Based on
+this exercise, we adopted a threshold of RUWE$_{\rm DR3}$ $>$ 2 to
+flag sources with excess astrometric noise.  This threshold was met
+for \ngoodhighruwe/\ngoods\ high-quality CQVs;
 \nmaybehighruwe/\nmaybes\ of the ambiguous ones had this
@@
 
-{\it Gaia DR3 non-single stars}---Gaia DR3 included a
-{\tt non\_single\_star} column that flagged known or suspected
-eclipsing, astrometric, and spectroscopic binaries.  None of the stars
-in our CQV sample were identified as possible binaries in this column.
-
-{\it Multiple periodic TESS signals}---During our visual
-analysis of the TESS light curves and PDM periodograms, we flagged
-sources with beating light curves, and with PDM periodograms that
-showed multiple periods.  We also attempted to disentangle the two
-signals by subtracting the mean CQV signal over each sector, and then
-repeating the phase-dispersion minization analysis.  The results of
-this effort are summarized in the secondary periods, $P_{\rm sec}$,
-listed in Table~\ref{tab:thetable}.  This process yielded
+{\it Gaia DR3 non-single stars}---Gaia DR3 included a {\tt
+non\_single\_star} column that flagged known or suspected eclipsing,
+astrometric, and spectroscopic binaries.  None of the stars in our CQV
+sample were identified as possible binaries in this column.
+
+{\it Multiple periodic TESS signals}---During our visual analysis of
+the TESS light curves and PDM periodograms, we flagged sources with
+beating light curves, and with PDM periodograms that showed multiple
+periods.  We also attempted to disentangle the two signals by
+subtracting the mean CQV signal over each sector, and then repeating
+the phase-dispersion minization analysis.  The results of this effort
+are summarized in the secondary periods, $P_{\rm sec}$, listed in
+Table~\ref{tab:thetable}.  This process yielded
 \ngoodmultperiodflag/\ngoods\ high-quality CQVs with secondary
@@
       chunk represents one TESS orbit.  Data were acquired in Sectors
-			18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  
-			The light curve is binned to
-			15-minute intervals so that there are 96 points per day, and
-			each point is connected by a line.  Data gaps longer are not interpolated; if data are missing, nothing is
-			plotted.
-			The red
-			vertical lines highlight apparently instantaneous state changes
-			in the shape of the dip pattern.  
+      18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  The
+      light curve is binned to 15-minute intervals so that there are
+      96 points per day, and each point is connected by a line.  Data
+      gaps longer are not interpolated; if data are missing, nothing
+      is plotted.  The red vertical lines highlight apparently
+      instantaneous state changes in the shape of the dip pattern.  
 		}
@@
 its depth and duration), while the trailing two dips remained fixed.
-This is visible in Figure~\ref{fig:lp}.
-In other words, the structures producing these dips are independent to
-the degree that one can undergo a severe change while the others
-remain identical.  The state switches during cycles
-248-264 and 299-315 share the same characteristic: it is always the
-{\it leading} dip of a complex that ``switches off'', leaving the
-(fixed-depth) trailing dips in its wake.
+This is visible in Figure~\ref{fig:lp}.  In other words, the
+structures producing these dips are independent to the degree that one
+can undergo a severe change while the others remain identical.  The
+state switches during cycles 248-264 and 299-315 share the same
+characteristic: it is always the {\it leading} dip of a complex that
+``switches off'', leaving the (fixed-depth) trailing dips in its wake.
 
 {\sc Slow growth; rapid death}---Although there are a few instances in
-which we observe dips switch off over less than one cycle, dip
-growth seems to happen more slowly.  For instance, the dip that grows
-between phase 0 and 0.1 between cycles 260-290 begins to become
-visible around BTJD 1993.2, and growths in depth by about 2\% over
-about six cycles, to become visible by eye by BTJD 1997.7.
-The evolution of this particular dip is most clear in the river plots.
-The evolution of the latter dip group in cycles 1410-1481 is another
-example of this slow mode of dip growth.
+which we observe dips switch off over less than one cycle, dip growth
+seems to happen more slowly.  For instance, the dip that grows between
+phase 0 and 0.1 between cycles 260-290 begins to become visible around
+BTJD 1993.2, and growths in depth by about 2\% over about six cycles,
+to become visible by eye by BTJD 1997.7.  The evolution of this
+particular dip is most clear in the river plots.  The evolution of the
+latter dip group in cycles 1410-1481 is another example of this slow
+mode of dip growth.
 
@@
 dur} \equiv R_\star P / (\pi a)$ for the transit of a point-source at
-corotation is 1.02$\pm$0.10\,hr.  This means that while
-some of the LP 12-502 dips are sufficiently long to require structures
-that are extended in orbital azimuth, the durations of other dips are
+corotation is 1.02$\pm$0.10\,hr.  This means that while some of the LP
+12-502 dips are sufficiently long to require structures that are
+extended in orbital azimuth, the durations of other dips are
 consistent with effective radii for the occulting material $R_{\rm
 eff} \ll R_\star$.  This implies $a/R_\star \approx 5.8$ for this
-material; the analogous timescale at the stellar surface is
-about six times slower.
+material; the analogous timescale at the stellar surface is about six
+times slower.
 
@@
 $P=18.5611 \pm 0.0001$\,hr.  However the river plots
-(Figure~\ref{fig:lpriver0}) reveal that the
-light curve has specific dips with simultaneous but distinct periods.  For instance, in sectors 25-26, the
-local minimum that develops around cycle 262 has a period faster than
-the mean period by $\approx$0.1\%, while some of the trailing local
-minima in the main dip complex have periods slower than the mean
-period, by $\approx$0.04\%.  In addition to the fundamental period, we
-were able to identify at least four distinct periods shown by specific
-dips over the full Sectors 18-59 dataset, including periods at
-18.5683, 18.5672, 18.5473, and 18.5145\,hr, with a typical measurement
-uncertainty of $\approx$0.0002\,hr.  If each period corresponds to an
-individual dust or gas clump, then this implies that multiple distinct clumps can orbit
-the star simultaneously, at marginally different separations.
+(Figure~\ref{fig:lpriver0}) reveal that the light curve has specific
+dips with simultaneous but distinct periods.  For instance, in sectors
+25-26, the local minimum that develops around cycle 262 has a period
+faster than the mean period by $\approx$0.1\%, while some of the
+trailing local minima in the main dip complex have periods slower than
+the mean period, by $\approx$0.04\%.  In addition to the fundamental
+period, we were able to identify at least four distinct periods shown
+by specific dips over the full Sectors 18-59 dataset, including
+periods at 18.5683, 18.5672, 18.5473, and 18.5145\,hr, with a typical
+measurement uncertainty of $\approx$0.0002\,hr.  If each period
+corresponds to an individual dust or gas clump, then this implies that
+multiple distinct clumps can orbit the star simultaneously, at
+marginally different separations.
 
@@
 
-Figure~\ref{fig:catalogscatter} shows derived stellar
-properties for our CQV catalog, and compares the CQVs against both the
-target star sample (top panels), and against stars in the Pleiades
+Figure~\ref{fig:catalogscatter} shows derived stellar properties for
+our CQV catalog, and compares the CQVs against both the target star
+sample (top panels), and against stars in the Pleiades
 \citep{2016AJ....152..114R}.  Typical CQV masses span
-0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This mass
-and age range includes both fully convective stars
+0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This mass and
+age range includes both fully convective stars
 ($M_\star$$\lesssim$0.25\,$M_\odot$), and stars with a combination of
@@
 ($M_\star$$\gtrsim$0.25\,$M_\odot$; \citealt{2018A&A...619A.177B}).
-We found no obvious light curve morphology differences between the two classes.
-%which suggests that the star's interior structure may influence
-%the field topology \citep{2009A&A...496..787R}.  
-In terms of
-their rotation rates relative to the Pleiades, the CQVs are among the
-more rapidly rotating half of M dwarfs. 
-%The dearth of $T$$>$15.5 CQVs
-%in our sample, despite our search extending to $T$$=$16, is a
-%consequence of the 120-second selection function, not detection
-%sensitivity.
+We found no obvious light curve morphology differences between the two
+classes.  In terms of their rotation rates relative to the Pleiades,
+the CQVs are among the more rapidly rotating half of M dwarfs.
 
 The closest CQV in our catalog is DG~CVn (TIC~368129164;
-$d$$=$18\,pc), a member of AB Dor.  To our knowledge, this work
-is the first time that it has been noted as a CQV.  The three
-brightest CQVs are DG~CVn ($T$=9.3), TIC~405754448 ($T$=9.6), and
-TIC~167664935 ($T$=10.3).  The shortest period belongs to
-TIC~201789285, at 3.64\,hr.  The longest period belongs to
-TIC~405910546, at 37.9\,hr.  If the latter source turns out to be an
-eclipsing binary, the next-longest would be TIC~193831684 (31.0\,hr).
+$d$$=$18\,pc), a member of AB Dor.  To our knowledge, this work is the
+first time that it has been noted as a CQV.  The three brightest CQVs
+are DG~CVn ($T$=9.3), TIC~405754448 ($T$=9.6), and TIC~167664935
+($T$=10.3).  The shortest period belongs to TIC~201789285, at
+3.64\,hr.  The longest period belongs to TIC~405910546, at 37.9\,hr.
+If the latter source turns out to be an eclipsing binary, the
+next-longest would be TIC~193831684 (31.0\,hr).
 
@@
 an ``ambiguous'' CQV with a 10.8\,hr period, because this period
-minimized the dispersion in the phase-folded light curve.  More careful
-inspection however showed that this source is an impostor:
-this source is a
-photometric blend of two ordinary rotating stars with $P_0$=3.60\,hr,
-and $P_1$=5.41\,hr, with a beat period $(P_0^{-1} - P_1^{-1})^{-1}$ of
-10.8\,hr.  This is a novel false positive scenario for CQVs:
-two rapidly-rotating stars with near-integer ratios of rotation
-periods.  The beat between the two rotation signals produces the
-apparent CQV signal.  Such false positives can be excluded through
+minimized the dispersion in the phase-folded light curve.  More
+careful inspection however showed that this source is an impostor:
+this source is a photometric blend of two ordinary rotating stars with
+$P_0$=3.60\,hr, and $P_1$=5.41\,hr, with a beat period $(P_0^{-1} -
+P_1^{-1})^{-1}$ of 10.8\,hr.  This is a novel false positive scenario
+for CQVs: two rapidly-rotating stars with near-integer ratios of
+rotation periods.  The beat between the two rotation signals produces
+the apparent CQV signal.  Such false positives can be excluded through
 careful accounting of all peaks in a periodogram.  For instance,
@@
 orbits of binaries closer than $\lesssim$700 AU tend to be aligned
-with their planetary systems \citep[e.g.][]{2022AJ....163..207C}.  If we
-assume that observing CQV variability similarly requires near edge-on
-viewing geometries, then we might expect a sufficiently close binary
-with one CQV to also have another, since the spin axes in sufficiently
-close binaries would tend to be aligned.  In this scenario, the two
-periods of TIC~425937691 being within $\lesssim$1\% of the 3:2 period
-commensurability would simply be a coincidence.
+with their planetary systems \citep[e.g.][]{2022AJ....163..207C}.  If
+we assume that observing CQV variability similarly requires near
+edge-on viewing geometries, then we might expect a sufficiently close
+binary with one CQV to also have another, since the spin axes in
+sufficiently close binaries would tend to be aligned.  In this
+scenario, the two periods of TIC~425937691 being within $\lesssim$1\%
+of the 3:2 period commensurability would simply be a coincidence.
 
@@
 The key difference between the prominence and dust clump scenarios is
-in whether the occulting material of interest is
-neutral hydrogen, or dust.  In the phrasing of the ``frozen flux''
-condition of ideal rigid field magnetohydrodynamics, the tendency of
-both to become trapped at the corotation radius in the equatorial
-plane is tied to how of the four relevant forces (gravity, Lorentz,
-inertial Coriolis, and inertial centrifugal), the Lorentz and Coriolis
-only act perpendicular to field lines, while gravity and the
-centrifugal force are in balance at $R_{\rm cr}$
-\citep[see][Sec.~2]{2005MNRAS.357..251T}.  The magnetic field strength
-is only relevant in this formulation of the system in that we must
-have $ R_{\rm cr} < R_{\rm Alfven}$ in order for closed
-loops to exist that can support prominences
-\citep[e.g.][]{1985Ap&SS.116..285N,2019MNRAS.482.2853J}.  In detail however, the locations of such
-magnetic fixed points depends on the star's magnetic field topology.
+in whether the occulting material of interest is neutral hydrogen, or
+dust.  In the phrasing of the ``frozen flux'' condition of ideal rigid
+field magnetohydrodynamics, the tendency of both to become trapped at
+the corotation radius in the equatorial plane is tied to how of the
+four relevant forces (gravity, Lorentz, inertial Coriolis, and
+inertial centrifugal), the Lorentz and Coriolis only act perpendicular
+to field lines, while gravity and the centrifugal force are in balance
+at $R_{\rm cr}$ \citep[see][Sec.~2]{2005MNRAS.357..251T}.  The
+magnetic field strength is only relevant in this formulation of the
+system in that we must have $ R_{\rm cr} < R_{\rm Alfven}$ in order
+for closed loops to exist that can support prominences
+\citep[e.g.][]{1985Ap&SS.116..285N,2019MNRAS.482.2853J}.  In detail
+however, the locations of such magnetic fixed points depends on the
+star's magnetic field topology.
 
@@
 Eq.~8.8]{1992oasp.book.....G}, such that at temperatures of
-$\approx$3{,}000\,K to $\approx$10{,}000\,K the observed chromaticities
-might be reproduced.  While bound-free absorption of
-${\rm H}^{-}$ seems like it should be important at such cool temperatures, in
-detail this opacity source has the {\it opposite sign} from
-what is required to produce deeper dips in the blue than in the red.
-Thomson scattering is similarly ruled out as a relevant opacity
-source, because it is gray.  The final plausible alternative opacity
-source is dust, which has the requisite larger absorption
+$\approx$3{,}000\,K to $\approx$10{,}000\,K the observed
+chromaticities might be reproduced.  While bound-free absorption of
+${\rm H}^{-}$ seems like it should be important at such cool
+temperatures, in detail this opacity source has the {\it opposite
+sign} from what is required to produce deeper dips in the blue than in
+the red.  Thomson scattering is similarly ruled out as a relevant
+opacity source, because it is gray.  The final plausible alternative
+opacity source is dust, which has the requisite larger absorption
 cross-section in the blue than the red \citep{1989ApJ...345..245C}.
@@
 geometries we are discussing for much cooler M dwarfs
-\citep{1978ApJ...224L...5L,1985Ap&SS.116..285N,2005ApJ...630L..81T}.  This material
-is unlikely to be dust, due to the relevant sublimation
+\citep{1978ApJ...224L...5L,1985Ap&SS.116..285N,2005ApJ...630L..81T}.
+This material is unlikely to be dust, due to the relevant sublimation
 timescales.  The opacity is instead thought to be sourced from
@@
 question of whether the CQVs are explained by dust or by gas, which
-has bearing on whether the material producing the dips is
-coming from the star, or whether it is a byproduct of the
-protoplanetary disk.
+has bearing on whether the material producing the dips is coming from
+the star, or whether it is a byproduct of the protoplanetary disk.
 
 %\subsubsection{Why corotation?}
-% The stable point only exists if R_A > R_K.
-For radii between R_A and R_K in such cases, consider a magnetic field line extending out beyond R_K.
-Whenever R>R_K, the material is centrifugally supported (pushed out by the ~Ω^2R^2 centrifugal term in the corotating frame).
-If R<R_K in such cases along a given field line, the material will fall back to the star.
-So there are two conditions that must be met: the star must spin fast enough, and closed magnetic loops must extend beyond the corotation radius.
-(This is all spelled out by Nakajima1985, and Petit2013).
+
+% The stable point only exists if R_A > R_K.  For radii between R_A
+% and R_K in such cases, consider a magnetic field line extending out
+% beyond R_K.  Whenever R>R_K, the material is centrifugally supported
+% (pushed out by the ~Ω^2R^2 centrifugal term in the corotating
+% frame).  If R<R_K in such cases along a given field line, the
+% material will fall back to the star.  So there are two conditions
+% that must be met: the star must spin fast enough, and closed
+% magnetic loops must extend beyond the corotation radius.  (This is
+% all spelled out by Nakajima1985, and Petit2013).
 
@@
 stars.  This broadly assumes that any star that can support
-prominences will do so, and that the magnetic topology of rapidly rotating M
-dwarfs at 100\,Myr is similar to that of rapidly rotating M dwarfs at
-say, 10\,Myr.  Based on the degree to which M dwarfs remain rapid
-rotators over the first few gigayears of their lives
+prominences will do so, and that the magnetic topology of rapidly
+rotating M dwarfs at 100\,Myr is similar to that of rapidly rotating M
+dwarfs at say, 10\,Myr.  Based on the degree to which M dwarfs remain
+rapid rotators over the first few gigayears of their lives
 \citep[e.g.][]{2022AJ....164...80R,2022ApJ...936..109P}, it seems
@@
 planet per M dwarf.
-
-%TRAPPIST-1b ($P$=1.5\,days) is an
-%example of this type of planet, orbiting around a 0.08\,$M_\odot$ star
-%\citep{2017Natur.542..456G}.
 
@@
 
-In systems like LP 12-502, the observed
-variability would perhaps drive one toward a picture of a
-disintegrating planetesimal swarm, rather than just a single
-planetesimal.  The need for more than just one launching body 
-is because we see dips appear and disappear at
-many different phases, but with roughly the same period.  The observed
+In systems like LP 12-502, the observed variability would perhaps
+drive one toward a picture of a disintegrating planetesimal swarm,
+rather than just a single planetesimal.  The need for more than just
+one launching body is because we see dips appear and disappear at many
+different phases, but with roughly the same period.  The observed
 changing dip depths in response to flares would be understood through
@@
 
-There are at least three problems with this 
-disintegrating planetesimal swarm concept.  First, the model would predict
-that certain orbital phases would produce recurrent dips if observed
-over sufficiently long baselines, because the launching planetesimal
-would be massive enough to remain in orbit, while stochastically
-ejecting material.  An analogous system would be K2-22
+There are at least three problems with this disintegrating
+planetesimal swarm concept.  First, the model would predict that
+certain orbital phases would produce recurrent dips if observed over
+sufficiently long baselines, because the launching planetesimal would
+be massive enough to remain in orbit, while stochastically ejecting
+material.  An analogous system would be K2-22
 \citep{2015ApJ...812..112S}.  For most CQVs (Figure~\ref{fig:evoln}),
-the data are in tension with this expectation.  A second issue
-is that many of the dips show asymmetries in the wrong direction
-relative to the naive expectation of a trailing comet tail.  Invoking
+the data are in tension with this expectation.  A second issue is that
+many of the dips show asymmetries in the wrong direction relative to
+the naive expectation of a trailing comet tail.  Invoking
 non-exponentially decaying dust distributions as a function of azimuth
@@
 also worth emphasizing that our labeling of e.g.~TIC~57830249 was
-based on a single sector of TESS data (Sector~36) when its behavior was
-relatively periodic and it showed dip depths of a few percent.
+based on a single sector of TESS data (Sector~36) when its behavior
+was relatively periodic and it showed dip depths of a few percent.
 However, in other TESS sectors (e.g. Sector~10), this source looks
@@
 The dips in both are probably associated with clumps of dust or gas.
-However the CQV dips are both more periodic and less deep than
-those of dippers; they also display far less transience over timescales
-of a few to tens of cycles.  This is presumably because CQVs have
+However the CQV dips are both more periodic and less deep than those
+of dippers; they also display far less transience over timescales of a
+few to tens of cycles.  This is presumably because CQVs have
 demonstrably less dust than (most) dipper stars.  At a population
@@
 the sharpest, deepest minimum), TIC~89463560 (Sector 36),
-TIC~224283342 (Sector 2), and TIC~442571495 (Sector 12).
-For the particular case of TIC~224283342, this observation, coupled
-with Gaia DR3 radial velocities suggesting a radial
-velocity scatter exceeding 20\,\kms, suggests that the system could be
-a low-mass eclipsing binary transiting a giant polar spot, analogous to
-TOI-3884 \citep{2022A&A...667L..11A}.
+TIC~224283342 (Sector 2), and TIC~442571495 (Sector 12).  For the
+particular case of TIC~224283342, this observation, coupled with Gaia
+DR3 radial velocities suggesting a radial velocity scatter exceeding
+20\,\kms, suggests that the system could be a low-mass eclipsing
+binary transiting a giant polar spot, analogous to TOI-3884
+\citep{2022A&A...667L..11A}.
 
 In general however, it is challenging to interpret the significance of
-the potential ``half-period regularities'';  the CQVs exhibit such a wide
-range of variability that for seemingly any regularity one might
+the potential ``half-period regularities'';  the CQVs exhibit such a
+wide range of variability that for seemingly any regularity one might
 posit, it is easy to come up with counter-example objects which do not
@@
       circumstellar plasma tori.  HD~37776 and HD~64740 (middle row)
-      are analogous magnetic B stars with field toplogies dominated
-      by high order multipoles.  The bottom row compares the latter
+      are analogous magnetic B stars with field toplogies dominated by
+      high order multipoles.  The bottom row compares the latter
       systems against the ``best-matching'' CQV light curves, selected
-      by eye from Figure~\ref{fig:cqvs}.  CQVs have light curves that are
-      visually similar to the topologically complex magnetic B stars.
-      Stellar masses rounded to one significant figure are given in
-      the lower right of each panel; the star, TESS sector, and period
-      are listed in each subtitle.
+      by eye from Figure~\ref{fig:cqvs}.  CQVs have light curves that
+      are visually similar to the topologically complex magnetic B
+      stars.  Stellar masses rounded to one significant figure are
+      given in the lower right of each panel; the star, TESS sector,
+      and period are listed in each subtitle.
 		}
@@
 transit depth to an effective cloud radius, $R_{\rm cloud}$.  For most
-CQVs in Figure~\ref{fig:cqvs}, this yields
-$\approx$2-20\,$R_\oplus$.  A minimum constraint on the number
-density follows by requiring
-the cloud to be optically thick.  For cases like LP 12-502, this is
-reasonable because the transit duration of the shortest dips implies $R_{\rm cloud}\ll
-R_\star$.  Carrying out the relevant calculation assuming the
-occulting material is dust grains 1\,$\mu$m in size,
+CQVs in Figure~\ref{fig:cqvs}, this yields $\approx$2-20\,$R_\oplus$.
+A minimum constraint on the number density follows by requiring the
+cloud to be optically thick.  For cases like LP 12-502, this is
+reasonable because the transit duration of the shortest dips implies
+$R_{\rm cloud}\ll R_\star$.  Carrying out the relevant calculation
+assuming the occulting material is dust grains 1\,$\mu$m in size,
 \citet{2023MNRAS.518.4734S} reported minimum cloud masses of order
@@
 asteroid; the asteroid belt itself has a mass of order
-$\approx$10$^{21}$\,kg \citep{2019Icar..319..812P}.  If
-the material were
-cool gas prominences rather than dust, the mass would need to be of order
-$10^{14}$\,kg \citep{1990MNRAS.247..415C}, about 100$\times$ larger
-than the requisite dust mass.
+$\approx$10$^{21}$\,kg \citep{2019Icar..319..812P}.  If the material
+were cool gas prominences rather than dust, the mass would need to be
+of order $10^{14}$\,kg \citep{1990MNRAS.247..415C}, about 100$\times$
+larger than the requisite dust mass.
 
@@
 
-\citet{2017AJ....153..152S} previously noted a possible
-connection between the CQVs and rapidly rotating magnetic B stars such
-as $\sigma$~Ori~E, which can have circumstellar gas clouds trapped in
+\citet{2017AJ....153..152S} previously noted a possible connection
+between the CQVs and rapidly rotating magnetic B stars such as
+$\sigma$~Ori~E, which can have circumstellar gas clouds trapped in
 corotation \citep{2005ApJ...630L..81T}.  The $\sigma$~Ori class is
@@
 
-Two exceptions to the rule of ``simple field topologies for magnetic
-B stars'' are HD~37776 and HD~64740, which are B stars that were
-previously known from spectropolarimetry to have
-field geometries dominated by high order multipoles
-\citep{2011ApJ...726...24K}.  Reviewing the literature, we
-learned that recent TESS light curves of these two B stars appear
-surprisingly similar to the CQV light curves
+Two exceptions to the rule of ``simple field topologies for magnetic B
+stars'' are HD~37776 and HD~64740, which are B stars that were
+previously known from spectropolarimetry to have field geometries
+dominated by high order multipoles \citep{2011ApJ...726...24K}.
+Reviewing the literature, we learned that recent TESS light curves of
+these two B stars appear surprisingly similar to the CQV light curves
 \citep{2020pase.conf...46M}.  The middle row of Figure~\ref{fig:bstar}
@@
 number of dips per cycle, the shapes of the dips, and the dip depths
-relative to the sinusoidal envelope all appear to be similar.
-The implication of this surprising connection is that the
+relative to the sinusoidal envelope all appear to be similar.  The
+implication of this surprising connection is that the
 highly-structured M dwarf light curves may imply multipolar magnetic
@@
 launched by the star returns to its surface over the free-fall
-timescale.
-A simple order of magnitude estimate assuming a dipole field with
-$B_0\approx1\,{\rm kG}$ at the star's surface, a local plasma number
-density $n\approx10^9\,{\rm cm^{-3}}$, and a plasma temperature
-$10^6\,{\rm K}$ gives Alfv\'en radii of order a few times the
-corotation radii, $R_{\rm cr}$.  This suggests that the existence of a
-centrifugal magnetosphere is plausible in young, rapidly rotating M
-dwarfs.
+timescale.  A simple order of magnitude estimate assuming a dipole
+field with $B_0\approx1\,{\rm kG}$ at the star's surface, a local
+plasma number density $n\approx10^9\,{\rm cm^{-3}}$, and a plasma
+temperature $10^6\,{\rm K}$ gives Alfv\'en radii of order a few times
+the corotation radii, $R_{\rm cr}$.  This suggests that the existence
+of a centrifugal magnetosphere is plausible in young, rapidly rotating
+M dwarfs.
+
+% NOTE to the arxiv crawlers:
 
@@
 
-In this work, we searched 120-second cadence TESS data collected
-from 2018 July to 2022 September for complex quasiperiodic variables
+In this work, we searched 120-second cadence TESS data collected from
+2018 July to 2022 September for complex quasiperiodic variables
 (CQVs).  The target stars were \nstarssearched\ K and M dwarfs within
@@
 includes an additional \nmaybes\ ambiguous CQVs, whose designation is
-less certain, and \ndebunked\ impostors.  We inferred ages for all but two of the \nallcands\
-objects based on association memberships; we also derived temperatures
-and radii using SED fitting, and then inferred stellar masses by
-interpolating against stellar evolutionary models.  We caution that
-our selection function was not volume-limited: the TESS 120-second
-stellar sample had a heterogeneous selection function which may have
-been biased in favor of young stars over field stars.  Previous work
-however has shown that $\approx$1-3\% of M dwarfs younger than
-$\approx$100\,Myr show the CQV phenomenon
+less certain, and \ndebunked\ impostors.  We inferred ages for all but
+two of the \nallcands\ objects based on association memberships; we
+also derived temperatures and radii using SED fitting, and then
+inferred stellar masses by interpolating against stellar evolutionary
+models.  We caution that our selection function was not
+volume-limited: the TESS 120-second stellar sample had a heterogeneous
+selection function which may have been biased in favor of young stars
+over field stars.  Previous work however has shown that $\approx$1-3\%
+of M dwarfs younger than $\approx$100\,Myr show the CQV phenomenon
 \citep{2016AJ....152..114R,2022AJ....163..144G}.
@@
       require at least an asteroid belt's worth of dust
-      ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or $\approx$$10^{-2}$\,$M_\oplus$
-      if the occulting material is gas.
+      ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or
+      $\approx$$10^{-2}$\,$M_\oplus$ if the occulting material is gas.
   %
@@
   flag 1), \nmaybes\ ambiguous CQVs (\texttt{Quality} flag 0), and
-  \ndebunked\ impostors (\texttt{Quality} flag -1).
-The three-bit binarity flag ``Bin'' is for Gaia DR3 \texttt{radial\_velocity\_error} outliers (bit 1), Gaia DR3 \texttt{ruwe} outliers (bit 2), and stars with multiple TESS periods (bit 3).
-The
-  machine-readable version, available online, includes additional
-  columns for the Gaia DR2 and DR3 source identifiers, as well as the
-  stellar parameter
-  uncertainties.  The age uncertainties are typically $\approx \pm
-  10\%$, but can be asymmetric.  {\bf The median temperature, radius, and
-  mass uncertainties are $\pm XXX$\,K, $\pm XX$\%, and $\pm YY$\%
-  respectively}.  $N_{\rm sector}$ denotes the number of TESS sectors
-  for which {\it any} data are expected to be acquired between July~2018 and
-  Oct~2024.  This number is generally greater than the number of
-  sectors for which 120-second cadence data exist.   Association names
-  and provenance follow conventions adopted by
-  \citet{2018ApJ...856...23G}: 
+  \ndebunked\ impostors (\texttt{Quality} flag -1).  The three-bit
+  binarity flag ``Bin'' is for Gaia DR3
+  \texttt{radial\_velocity\_error} outliers (bit 1), Gaia DR3
+  \texttt{ruwe} outliers (bit 2), and stars with multiple TESS periods
+  (bit 3).  The machine-readable version, available online, includes
+  additional columns for the Gaia DR2 and DR3 source identifiers, as
+  well as the stellar parameter uncertainties.  The age uncertainties
+  are typically $\approx \pm 10\%$, but can be asymmetric.  {\bf The
+  median temperature, radius, and mass uncertainties are $\pm XXX$\,K,
+  $\pm XX$\%, and $\pm YY$\% respectively}.  $N_{\rm sector}$ denotes
+  the number of TESS sectors for which {\it any} data are expected to
+  be acquired between July~2018 and Oct~2024.  This number is
+  generally greater than the number of sectors for which 120-second
+  cadence data exist.   Association names and provenance follow
+  conventions adopted by \citet{2018ApJ...856...23G}: 
 	ABDMG: AB~Doradus moving group \citep{2015MNRAS.454..593B}.
@@
 attention.  With the exception of a few sectors, TESS data will exist
-for TIC~300651846 for at least Sectors 1-12, 27-39, and 61-69.  While most of
-the available data will exist in the full frame images, in
+for TIC~300651846 for at least Sectors 1-12, 27-39, and 61-69.  While
+most of the available data will exist in the full frame images, in
 Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river} focus
@@
 observed in LP 12-502; gradual evolution over timescales of
-$\approx$50-100 cycles seem to be the norm for TIC~300651846.
-Unlike the TIC~402980664 river plots (Figure~\ref{fig:lpriver0}), we
-did not subtract any ``continuum sinusoid'' for this source, because
-the continuum is not as obviously defined.
+$\approx$50-100 cycles seem to be the norm for TIC~300651846.  Unlike
+the TIC~402980664 river plots (Figure~\ref{fig:lpriver0}), we did not
+subtract any ``continuum sinusoid'' for this source, because the
+continuum is not as obviously defined.
 
@@
     a 8.254\,hr period and a fixed reference epoch (BTJD 2174.127) for
-    both panels.
-    Light curve segments are split based on the presence of gaps
-    longer than three hours.
-    Cycle numbers are listed in the lower-right of each light curve segment.
+    both panels.  Light curve segments are split based on the presence
+    of gaps longer than three hours.  Cycle numbers are listed in the
+    lower-right of each light curve segment.
 	}
@@
     This is an alternative visualization of the data in
-    Figure~\ref{fig:tic3006timegroups}.
-    All available 120-second cadence data as of 2023 Aug 11 are shown.
-    Cycles 0 to 622 span TESS Sectors 32-39 (Nov 2020--June 2021);
-    cycles 2296-2676 span Sectors 61-65 (Jan--June 2023).  We assumed
-    $P$$=$8.254\,hr and $t_0$=2174.127 [BTJD].
-    Note that the two panels have slightly different color scales.
+    Figure~\ref{fig:tic3006timegroups}.  All available 120-second
+    cadence data as of 2023 Aug 11 are shown.  Cycles 0 to 622 span
+    TESS Sectors 32-39 (Nov 2020--June 2021); cycles 2296-2676 span
+    Sectors 61-65 (Jan--June 2023).  We assumed $P$$=$8.254\,hr and
+    $t_0$=2174.127 [BTJD].  Note that the two panels have slightly
+    different color scales.
 	}

### 2023-08-16 paper/ms.tex
update ms

@@
 % primary authors
-\author{---AUTHOR LIST \& ORDER NOT FINAL}
 \author[0000-0002-0514-5538]{Luke~G.~Bouma}
@@
 all young M dwarfs are spotted, this tends to produce flux variations
-over characteristic timescales of the rotation period, $P_{\rm rot}$,
-and its half-harmonic, $0.5\,P_{\rm rot}$.  If one fine-tunes the
-viewing geometry, starspots can produce dips with durations as short
-as $\approx$$0.2\,P_{\rm rot}$, and the dip amplitudes quickly
-decrease due to limb-darkening (see \citealt{2017AJ....153..152S},
-Figures 37-41).  The observed dips, however, happen over durations as
+over timescales of the rotation period, $P_{\rm rot}$,
+and its half-harmonic, $0.5\,P_{\rm rot}$.  With fine-tuned
+viewing geometries, starspots can produce dip durations as short
+as $\approx$$0.2\,P_{\rm rot}$, and the dip amplitudes in such
+geometries are small
+due to limb-darkening (see \citealt{2017AJ....153..152S},
+Figures 37-41).  The observed dips occur over durations as
 short as $0.05\,P_{\rm rot}$ with characteristic depths of a few
 percent; a ``starspot-only'' scenario can be discarded for any object
-with dips that are sufficiently deep and short in duration
-\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The timescales and
-amplitudes of the flux variations in such objects instead require
+with dips that are sufficiently large in depth and short in duration
+\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The dip durations and
+amplitudes instead require
 sharp geometries with material extrinsic to the stellar surface
-\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  Since the
-CQVs are probably all explained by the same phenomenon, we therefore
+\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  Since some CQVs require
+such geometries, and the
+CQVs probably all have a single explanation, we therefore
 discard the ``spot-only'' scenario.
@@
 To assess the completeness of the resulting 120-second cadence data
-that is the basis of this study, we cross-matched TIC8
-\citep{2018AJ....156..102S} against the Gaia DR2 point-source catalog
+that is the basis of this study, we cross-matched TIC8.2
+\citep{2019AJ....158..138S,2021arXiv210804778P} against the Gaia DR2 point-source catalog
 \citep{2018A&A...616A...1G}.  We opted for Gaia DR2 rather than DR3
@@
       CQVs in the high quality sample.  Gray are raw 2-minute data;
-      black bins to 300 points per cycle.  Each panel is labeled by
-      the TIC identifier, the TESS sector number, and the period in
-      hours.  Objects are ordered such that sources with the most TESS
-      data available are on top (see Section~\ref{sec:catalog}).
-      Sources with large apparent scatter in gray typically show
-      secondary periods from unresolved binaries, which are enumerated
-      in Table~\ref{tab:thetable}.
+      black bins to 300 points per cycle.  Objects are ordered such
+      that sources with the most TESS data available are on top (see
+      Section~\ref{sec:catalog}).  
+      Each panel is labeled by
+      the TIC identifier, the TESS sector number, the period in
+      hours, and the three-bit binarity flag from Table~\ref{tab:thetable},
+      which denotes Gaia DR3 \texttt{radial\_velocity\_error} outliers
+      (bit 1), Gaia DR3 \texttt{ruwe} outliers (bit 2), and stars with
+      secondary TESS periods (bit 3). 
 		}
@@
 
-The main types of binarity of interest in this work were those that
-could confuse our understanding of CQVs.  For instance, within the
-21$''$ TESS pixels, binary companions can produce multiple photometric
+The main types of binaries of interest in this work were those that
+were unresolved, because they could confuse our understanding of CQVs.
+For instance, unresolved binaries might produce multiple photometric
 signals and hinder our ability to correctly identify the star hosting
-the CQV signal.  Binary companions can also bias photometric magnitude
+the CQV signal.  Unresolved binaries could also bias photometric magnitude
 and color measurements, which would affect our stellar parameter
@@
 
-Of the 27 CQVs in Figure~\ref{fig:evoln}, a few show clear signs of
+A few objects in Figure~\ref{fig:evoln}
+show clear signs of
 the CQV phenomenon in one sector, and marginal or non-existent signs
@@
 labeled an eclipsing binary---in fact, \citet{2021ApJ...912..123J}
-implicitly have already given this source such a label.  However,
+already gave this source such a label.  However,
 based on the the shape evolution between Sectors 13 and 39, it is a
@@
 AD identified the magnetic B star connection.
-LAH contributed to data analysis and interpretation.
+LAH contributed to project design and to the interpretation of the light curves.
 G\'AB acquired and maintained the servers used to run the dip-finding pipeline.
@@
 
-%\clearpage
+\clearpage
 

### 2023-08-16 paper/collect.sh

@@ -8,7 +8,7 @@ cp $addir/models.pdf f1b.pdf
 # fig2 is annotated_lp12502.key exported
 
 # fig3
-cp $resultsdir/full_lcmosaic/full_lcmosaic_showtitles_Ngoodsectors_tic8_Tmag.pdf f3.pdf
+cp $resultsdir/full_lcmosaic/full_lcmosaic_showtitles_binarytitle_Ngoodsectors_tic8_Tmag.pdf f3.pdf
 
 # fig4
 cp $resultsdir/beforeafter_mosaic/beforeafter_mosaic_showtitles_tic8_Tmag.pdf f4.pdf

### 2023-08-16 complexrotators/plotting.py
full_lcmosiac: add binflag

@@ -2798,7 +2798,7 @@ def plot_lc_mosaic(outdir, subset_id=None, showtitles=0,
 
 
 def plot_full_lcmosaic(outdir, showtitles=1, titlefontsize=3.5,
-                       sortby=None):
+                       sortby=None, binarytitle=0):
     """
     the one that makes the publication
     (on mico, assuming that find_CPVs.py has been run using sample_id=="2023catalog_LGB_RJ_concat")
@@ -2839,6 +2839,11 @@ def plot_full_lcmosaic(outdir, showtitles=1, titlefontsize=3.5,
             )
         else:
             raise NotImplementedError
+
+    if binarytitle:
+        csvpath = join(TABLEDIR, "2023_catalog_table",
+                       "20230613_LGB_RJ_CPV_TABLE_supplemental_selfnapplied.csv")
+        tabdf = pd.read_csv(csvpath, sep="|", dtype={'binarityflag':str})
 
     # prepare to get lc data
     from complexrotators.lcprocessing import (
@@ -2901,6 +2906,11 @@ def plot_full_lcmosaic(outdir, showtitles=1, titlefontsize=3.5,
 
         if showtitles:
             titlestr = f'TIC{ticid}, S{sector}, {d["period"]*24:.1f}h'
+            if binarytitle:
+                binflag = tabdf.loc[
+                    tabdf.ticid.astype(str)==str(ticid), 'binarityflag'
+                ]
+                titlestr += f", {binflag.iloc[0]}"
         else:
             titlestr = None
 
@@ -3011,6 +3021,8 @@ def plot_full_lcmosaic(outdir, showtitles=1, titlefontsize=3.5,
     s = ''
     if showtitles:
         s += '_showtitles'
+    if binarytitle:
+        s += '_binarytitle'
     if isinstance(sortby, str):
         s += f'_{sortby}'
 

### 2023-08-16 paper/ms.tex
bona fide

@@
       $\approx$150 Myr, with rotation periods faster than
-      $\approx$1\,day.  The \ngoods\ bonafide CQVs in
+      $\approx$1\,day.  The \ngoods\ bona fide CQVs in
       Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
@@
 %\tabletypesize{\scriptsize}
-\tablecaption{Bonafide, candidate, and debunked complex quasiperiodic
+\tablecaption{Bona fide, candidate, and debunked complex quasiperiodic
   variables from the TESS 2-minute data. {\bf For internal

### 2023-08-16 complexrotators/isochroneinterp.py
isochroneinterp: explicit error handling

@@ -3,13 +3,17 @@ Tools when interpolating against isochrones.
 
 | get_Feiden2016
 | get_PARSEC
+| nn_PARSEC_interpolator
+| PARSEC_interpolator
 """
 import os
 from os.path import join
 from glob import glob
 from complexrotators.paths import DATADIR
-import pandas as pd, numpy as np
+import pandas as pd, numpy as np, matplotlib.pyplot as plt
 from astropy import units as u, constants as c
+
+from scipy.interpolate import LinearNDInterpolator
 
 def get_Feiden2016(subtype='mag'):
     """
@@ -80,3 +84,176 @@ def get_PARSEC():
     df['age'] = 10**(df.logAge) / (1e6)
 
     return df
+
+
+def nn_PARSEC_interpolator(rstar, teff, age, rstar_err, teff_err, age_err):
+    # age: myr
+
+    # 1 to 200 myr, linearly spaced by 1 myr; all available masses.  solar metallicity.
+    # get and clean 
+    df = get_PARSEC()
+    sel = (
+        (df.Mass < 1.5)
+        &
+        (df.logRstar > -4)
+    )
+    df = df[sel] # < 2 solar
+
+    # calculate distance!
+    dist = np.sqrt(
+    np.array( ( (df['Rstar'] - rstar) / rstar_err )**2 )
+    +
+    np.array( ( (df['Teff'] - teff) / teff_err )**2 )
+    +
+    np.array( ( (df['age'] - age) / age_err )**2 )
+    )
+    df['dist_median'] = dist
+
+    varyparams = 'Rstar Teff age '
+    varyvals = [rstar_err, teff_err, age_err]
+
+    for varyparam, val in zip(varyparams.split(), varyvals):
+        if varyparam == 'Rstar':
+            _rstar = rstar + rstar_err
+            _teff = teff
+            _age_myr = age
+        elif varyparam == 'Teff':
+            _rstar = rstar
+            _teff = teff + teff_err
+            _age_myr = age
+        elif varyparam == 'age':
+            _rstar = rstar
+            _teff = teff
+            _age_myr = age + age_err
+        dist = np.sqrt(
+             np.array( ( (df['Rstar'] - _rstar) / rstar_err )**2 )
+             +
+             np.array( ( (df['Teff'] - _teff) / teff_err )**2 )
+             +
[…]

### 2023-08-16 drivers/make_cpv_table.py
table cleanup

@@ -38,7 +38,6 @@ from astroquery.exceptions import ResolverError
 from complexrotators.observability import (
     get_gaia_dr2_rows, assess_tess_holdings, get_gaia_dr3_rows
 )
-from complexrotators.isochroneinterp import get_PARSEC
 from complexrotators import pipeline_utils as pu
 
 vetdir = join(RESULTSDIR, "cpvvetter")
@@ -53,13 +52,16 @@ def main(overwrite=0):
     csvpath2 = join(DATADIR, "targetlists", "20230813_DEBUNKED_CQVs.txt")
     debunked_df = pd.read_csv(csvpath2)
 
-    csvpath3 = join(DATADIR, "targetlists", "20230411_goodandmaybe_CPV_ticids_d_lt_150pc.csv")
+    csvpath3 = join(DATADIR, "targetlists",
+                    "20230411_goodandmaybe_CPV_ticids_d_lt_150pc.csv")
     dipcount_df = pd.read_csv(csvpath3)
 
-    csvpath4 = join(DATADIR, "targetlists", "20230501_RAHUL_FULL_LIST_NO_DUPLICATES.csv")
+    csvpath4 = join(DATADIR, "targetlists",
+                    "20230501_RAHUL_FULL_LIST_NO_DUPLICATES.csv")
     fourier_df = pd.read_csv(csvpath4)
 
-    csvpath5 = join(TABLEDIR, "multiple_period_20230613_LGB_RJ_CPV", "20230814_multiperiod_MANUAL.csv")
+    csvpath5 = join(TABLEDIR, "multiple_period_20230613_LGB_RJ_CPV",
+                    "20230814_multiperiod_MANUAL.csv")
     multperiod_df = pd.read_csv(csvpath5)
     selcols = 'ticid P2_hr P2class'
     multperiod_df = multperiod_df[selcols.split()]
@@ -167,6 +169,11 @@ def main(overwrite=0):
     sdf['binarityflag'] = (
         sdf['rvscatterflag'] + sdf['ruweflag']  + sdf['multipleperiodflag']
     )
+
+    # manual string casting
+    strcols = 'dr2_source_id dr3_source_id'.split()
+    for strcol in strcols:
+        sdf[strcol] = '"' + sdf[strcol].astype(str) + '"'
 
     csvpath = join(indir, "20230613_LGB_RJ_CPV_TABLE_supplemental_selfnapplied.csv")
     sdf.to_csv(csvpath, index=False, sep="|")
[…]

### 2023-08-16 paper/ms.tex
update ms

@@
 
-\title{Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS}
+\title{Transient Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS}
 
@@
   pre-main-sequence stars with nearly periodic optical modulation.
-  The modulation is likely induced by dust or gas clumps in orbit at
+  The modulation is probably caused by eclipses of dust or gas clumps orbiting at
   the Keplerian corotation radius.  Here, we report new CQVs
-  discovered in TESS short-cadence data collected between July~2018
-  and Sep~2022.  Our search of \nstarssearched\ K and M dwarfs with
+  discovered in TESS short-cadence data collected between 2018~July
+  and 2022~September.  Our search of \nstarssearched\ K and M dwarfs with
   $T$$<$16 and $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most
@@
 model mass is then one that minimizes this distance, and is quoted in
-Table~\ref{tab:thetable}.
-{\bf lgb todo: real interpolation, rather than nearest neighbor}
+Table~\ref{tab:thetable}.  Uncertainties in the masses are propagated
+forward from the statistical uncertainties in the radii, temperatures,
+and ages.
 
@@
 		the fundamental period of 18.5611\,hr, as well as at faster and
-		slower relative periods (e.g. $\phi$$\approx$0.3 and
-		$\phi$$\approx$0.1).  Similar instances of multiple simultaneous
-		periods are also visible in Sector 53 and 58-59.  White chunks
+		slower relative periods.  For example, at $\phi$$\approx$0.05 and
+		$\phi$$\approx$0.3, the various blue ``dips'' have distinct slopes, rather than being
+		exactly vertical.  Multiple simultaneous
+		periods are also visible in Sectors 53 and 58-59.  White chunks
 		denote missing data.
@@
   well as the stellar parameter uncertainties.  The age uncertainties
-  are typically $\approx \pm 10\%$, but can be asymmetric.  {\bf The
-  median temperature, radius, and mass uncertainties are $\pm XXX$\,K,
-  $\pm XX$\%, and $\pm YY$\% respectively}.  $N_{\rm sector}$ denotes
-  the number of TESS sectors for which {\it any} data are expected to
-  be acquired between July~2018 and Oct~2024.  This number is
-  generally greater than the number of sectors for which 120-second
-  cadence data exist.   Association names and provenance follow
-  conventions adopted by \citet{2018ApJ...856...23G}: 
+  are typically $\approx \pm 10\%$, but can be asymmetric.  The median
+  statistical uncertainties on the temperature, radius, and mass are
+  $\pm$50\,K, $\pm$4\% and $\pm$9\% respectively.
+  $N_{\rm sector}$ denotes the number of TESS sectors for which {\it
+  any} data are expected to be acquired between July~2018 and
+  Oct~2024.  This number is generally greater than the number of
+  sectors for which 120-second cadence data exist.   Association names
+  and provenance follow conventions adopted by
+  \citet{2018ApJ...856...23G}: 
 	ABDMG: AB~Doradus moving group \citep{2015MNRAS.454..593B}.

### 2023-08-17 complexrotators/plotting.py
add spectrum_windows

@@ -1873,7 +1873,7 @@ def get_flx_wav_given_2d_and_target(flx_2d, wav_2d, target_wav):
     return flx, wav
 
 
-def plot_spectrum_windows(outdir, starid, inst='HIRES'):
+def plot_spectrum_windows(outdir, starid, inst='HIRES', ylims=None):
 
     # note: could add in K 7699..
     #lines = ['Ca K', 'Ca H & Hε', 'He', 'Hα', 'Li', 'K']
@@ -1889,14 +1889,15 @@ def plot_spectrum_windows(outdir, starid, inst='HIRES'):
         [6707.8-deltawav, 6707.8+deltawav], # li6708
         #[7699.-deltawav, 7699+deltawav], # K
     ]
-    ylims = [
-        [-1, 35],
-        [-1, 35],
-        #[0.8, 1.95],
-        None,
-        None,
-        #None,
-    ]
+    if ylims is None:
+        ylims = [
+            None,#[-1, 35],
+            None,#[-1, 35],
+            #[0.8, 1.95],
+            None,
+            None,
+            #None,
+        ]
     xticks = [
         [3930, 3940],
         [3965, 3975],
@@ -1919,9 +1920,10 @@ def plot_spectrum_windows(outdir, starid, inst='HIRES'):
     # make plot
     #
     plt.close('all')
-    set_style('clean')
+    set_style('science')
 
-    fig, axs = plt.subplots(ncols=len(lines), figsize=(3.3,1.15))
+    f = 1.5
+    fig, axs = plt.subplots(ncols=len(lines), figsize=(f*3.5,f*1.15))
     #fig, axs = plt.subplots(ncols=2, nrows=2, figsize=(2.5,2.5))
     axs = axs.flatten()
 
@@ -1934,6 +1936,13 @@ def plot_spectrum_windows(outdir, starid, inst='HIRES'):
         fitspaths = glob(join(DATADIR, 'spectra', inst, starid, _glob))
         assert len(fitspaths) == 1
         spectrum_path = fitspaths[0]
+
+        hdul = fits.open(spectrum_path)
+        dateobs = hdul[0].header['DATE-OBS']
+        exptime = hdul[0].header['EXPTIME']
+        utc = hdul[0].header['UTC'][:5]
+        timestr = f"{dateobs} {utc}UT"
+        hdul.close()
 
         flx_2d, wav_2d = read_hires(
             spectrum_path, is_registered=0, return_err=0
[…]

### 2023-08-17 drivers/make_cpv_table.py

@@ -170,10 +170,10 @@ def main(overwrite=0):
         sdf['rvscatterflag'] + sdf['ruweflag']  + sdf['multipleperiodflag']
     )
 
-    # manual string casting
-    strcols = 'dr2_source_id dr3_source_id'.split()
-    for strcol in strcols:
-        sdf[strcol] = '"' + sdf[strcol].astype(str) + '"'
+    ## manual string casting
+    #strcols = 'dr2_source_id dr3_source_id'.split()
+    #for strcol in strcols:
+    #    sdf[strcol] = '"' + sdf[strcol].astype(str) + '"'
 
     csvpath = join(indir, "20230613_LGB_RJ_CPV_TABLE_supplemental_selfnapplied.csv")
     sdf.to_csv(csvpath, index=False, sep="|")

### 2023-08-17 drivers/plot_spectrum_windows.py

@@ -8,9 +8,19 @@ if not os.path.exists(PLOTDIR):
 
 #starid = 'TIC146539195'
 
-starids = 'TIC141146667 TIC146539195 TIC264599508 TIC408188366 TIC59129133'
+starids = 'TIC402980664 TIC141146667 TIC146539195 TIC264599508 TIC408188366 TIC59129133'
 starids = starids.split(" ")
 
-for starid in starids:
-    rp.plot_spectrum_windows(PLOTDIR, starid, inst='HIRES')
+ylims = [
+    [[0.0,35],[0.0,35],[0.3,7],[0.3,1.4]], # tic 4029
+    None, # tic1411
+    [[0.0,35],[0.0,35],[0.3,7],[0.3,1.4]], # tic 1465
+    [[0.0,14],[0.0,14],[0.,3.5],[0.3,1.4]], # tic 2645
+    None,
+    None
+]
 
+for _ylims, starid in zip(ylims, starids):
+
+    rp.plot_spectrum_windows(PLOTDIR, starid, inst='HIRES',
+                             ylims=_ylims)

### 2023-08-17 paper/ms.tex
ms: add appendix

@@
 to 100 points per cycle.  To separate ``sharp'' local minima from
-smooth but double-dipped spot variability, we then iteratively fit
+smooth spot-induced variability, we then iteratively fit
 robust penalized splines to the wrapped phase-folded light curve,
@@
 were chosen during testing based on their ability to correctly
-re-identify a large fraction ($>$90\%) of known CQVs, while also being
+re-identify a large fraction ($>$90\%) of previously known CQVs, while also being
 able to consistently reject common false positives such as rapidly
@@
 described by \citeauthor{2019ApJ...876..127Z}.  Taking the Fourier
-transform of the corrected, padded light curve using {\tt
-numpy.fft.fft}, we then searched for peaks with a significance of over
-12-$\sigma$ within a set of 500 frequency bins.
+transform of the corrected, padded light curve using {\tt numpy.fft},
+we then searched for peaks with a significance of over 12-$\sigma$
+within a set of 500 frequency bins.
 
@@
 we performed this analysis, we found that ``summary'' sheets were
-generated for $\approx$10\% of the 20\,000 120-second targets in a
+generated for $\approx$10\% of the 20{,}000 120-second targets in a
 given sector.  We then manually reviewed each summary sheet, and
-visually labelled each star based on its morphology (including e.g.,
+visually labeled each star based on its morphology (including e.g.
 eclipsing binary, CQV, RS CVn, or cataclysmic variable).  CQVs that
@@
 
-Broadly speaking, the most common false positives for both the Fourier
+Broadly speaking, the most common false positive triggers for both the Fourier
 and dip-counting techniques were eclipsing binaries, spot-induced
@@
 that a given star belongs to one of 27 young clusters (or
-``assocations'') within 150\,pc of the Sun, by modeling the clusters
+``associations'') within 150\,pc of the Sun, by modeling the clusters
 as multivariate Gaussians in 3-D position and 3-D velocity space.  We
@@
 temperature--opacity relation drawn from the BT-Settl model
-atmospheres, in order to match observed masses and radii of younq
+atmospheres, in order to match observed masses and radii of young
 eclipsing binaries.  This is sufficient for our goal of estimating
@@
 subtracting the mean CQV signal over each sector, and then repeating
-the phase-dispersion minization analysis.  The results of this effort
+the phase-dispersion minimization analysis.  The results of this effort
 are summarized in the secondary periods, $P_{\rm sec}$, listed in
@@
 single leading dip is present at the same phase as in cycles 0-64, and
-is therefore likely to be the same struture.  Along a similar line of
+is therefore likely to be the same structure.  Along a similar line of
 logic, it seems plausible that the first ``dip complex'' during cycles
@@
 observed lifetime of the CQV phenomenon could provide another
-dimension to discern between the gas {\it vs.} dust clump scenarios.
+dimension to discern between the gas vs.~dust clump scenarios.
 Based on the available statistics from e.g.
@@
 stronger by a factor of $\approx$1{,}000.  However we emphasize that
-while this type of configuration seems {\it a priori} plausible, no
+while this type of configuration seems a priori plausible, no
 direct evidence currently supports it.
@@
       circumstellar plasma tori.  HD~37776 and HD~64740 (middle row)
-      are analogous magnetic B stars with field toplogies dominated by
+      are analogous magnetic B stars with field topologies dominated by
       high order multipoles.  The bottom row compares the latter
@@
 %\toprule
-%TIC & $T$ & $d$ & BP-RP & RUWE & $P$ & assoc & age & teff & rstar & mstar & rcr & qual & Nsectors \\
 %\midrule
@@
 \end{deluxetable}
-\clearpage
+
+%\clearpage
 
 \appendix
-
-%\section{Validation plots}
-%\label{app:vetting}
-%
-%Figure~\ref{fig:vet} shows the type of plot used to visually assess
-%whether a source was likely to be a CQV, eclipsing binary, or simply a
-%rapidly rotating star.
-%
-%\begin{figure*}[!t]
-%	\begin{center}
-%    \centering
-%    \includegraphics[width=0.96\textwidth]{annotated_402980664_S0018_120sec_cpvvetter.pdf}
-%		\vspace{-0.45cm}
-%		\caption{
-%      {\bf Validation plots used to manually label CQVs}.  The complete figure
-%      set, with one image per sector for each of \ncpvsfound\ CQVs
-%      and candidate CQVs
-%      is available online {\bf For internal collaboration review:
-%      \url{https://www.dropbox.com/scl/fo/zlj3txot4cvymfb22wewu/h?dl=0&rlkey=3ec5f9o5xewrixzfkhkdenopa}}.
-%      Panels are as follows.
-%      {\it a)}: Phase-folded light curve; gray points are raw 2-minute
-%      data and black points are binned to 200 points per cycle.
-%      {\it b)}: Phase-dispersion minimization (PDM) periodogram.
-%      Dotted lines show up to the 10$^{\rm th}$ harmonic and
-%      subharmonic.
-%      {\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
-%      circles displayed for scale.
-%      {\it d)}: Cleaned light curve, binned to 20-minute cadence, in
-%      Barycentric TESS Julian Date (BTJD).
-%      {\it e)}: Phase-folded light curve, binned to 100 points per
-%      cycle.  The gray line denotes the automated spline-fit to the
-%      wrapped phase-folded light curve, and small gray triangles
-%      denote automatically identified local minima.
-%      {\it f)}: Phase-folded light curve at twice the peak period.
-%      {\it g)}: Phase-folded light curve at half the peak period.
-%      {\it h)}: Phase-folded time-series within the ``background''
-%      aperture defined in the SPOC light curves.
-%      {\it i)}: Phase-folded flux-weighted centroid in the column
-%      direction.
-%      {\it j)}: Phase-folded flux-weighted centroid in the row
-%      direction.
-%      {\it k)}: Gaia DR2 color--absolute magnitude diagram.     
-%      The gray background denotes stars within 100\,pc.
-%      {\it l)}: Information from Gaia DR2, TIC8, and the automated
-%      dip-counting search pipeline.  ``Neighbors'', abbreviated
-%      ``nbhr'', are listed within apparent distances of 2 TESS pixels
-%      if $\Delta T$$<$2.5.
-%      {\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
-%      using positions, proper motions, and the parallax.
-%      }
-%		\label{fig:vet}
-%	\end{center}
-%\end{figure*}
 
@@
 appreciable power at timescales shorter than a few minutes.
+
+\section{The CQVs are not obviously accreting}
+
+We acquired iodine-free reconnaissance spectra using Keck/HIRES for
+three CQVs.  The goals were to determine the chromospheric activity
+levels, and to check for indications of either accretion or
+spectroscopic binarity.  We acquired a 15 minute exposure of
+TIC~146539195 on 2023 January 3, a 15 minute exposure of TIC~264599508
+on 2023 January 9, and a 30 minute exposure of TIC~402980664 on 2023
+July 10.  The acquisition and analysis followed the usual techniques
+of the California Planet Survey \citep{2010ApJ...721.1467H}.
+Figure~\ref{fig:speccutouts} shows cutouts from the resulting spectra,
+centered on the \ion{Ca}{2} HK windows, H$\alpha$, and the \ion{Li}{1}
+6708\,\AA\ doublet.  The \ion{Ca}{2} H emission line is blended with
+H$\epsilon$.  While a more detailed analysis will be left for future
+work, these spectra confirm previous understanding established by
+\citet{2017AJ....153..152S} that the stars are chromospherically
+active M dwarfs in the ``weak-lined'' T Tauri regime
+\citep[e.g.][Figure~15]{2019AJ....157...85B}.  Their H$\alpha$
+equivalent widths, at $\approx$14\,\AA, $\approx$8\,\AA, and
+$\approx$3\AA, are consistent with purely chromospheric emission.
+The blue excess in TIC~264599508 could be explained by a second
+unresolved star; the TESS light curve for this source shows both the
+7.90\,hr CQV signal, and a 9.00\,hr rotation signal with comparable
+amplitude.
+
+\begin{figure*}[!t]
+	\begin{center}
+	\subfloat{
+			\includegraphics[width=0.9\textwidth]{f13a.pdf}
+    }
+
+	\vspace{-1.1cm}
+	\subfloat{
+			\includegraphics[width=0.9\textwidth]{f13b.pdf}
+    }
+
+	\vspace{-1.1cm}
+	\subfloat{
+			\includegraphics[width=0.9\textwidth]{f13c.pdf}
+    }
+	\end{center}
+	\vspace{-0.4cm}
+	\caption{
+		{\bf Activity and age diagnostics for three CQVs}.
+		Wavelengths are in air;
+		the continuum normalization is relative to the entire order.
+		The H$\alpha$ emission strength classifies the stars as weak-lined
+		T Tauris.
+		The lithium detection for TIC~146539195 is consistent with its
+		mass and $\beta$~Pic membership;
+		the non-detections for TIC~402980664 and TIC~264599508
+		are consistent with the $\sim$42\,Myr age implied by their membership
+		in the Columba moving group.
+	}
+	\label{fig:tic3006timegroups}
+\end{figure*}
 

### 2023-08-17 paper/collect.sh

@@ -38,3 +38,7 @@ cp $resultsdir/phase_timegroups/TIC_300651846/cycle2290_to_2680TIC_300651846_P8.
 
 cp $resultsdir/river/tic_300651846/TIC300651846_river_seismic_-1_630_vmin-6.00000_vmax6.00000.pdf f12a.pdf
 cp $resultsdir/river/tic_300651846/TIC300651846_river_seismic_2290_2680_vmin-8.00000_vmax8.00000.pdf f12b.pdf
+
+cp $resultsdir/spectrum_windows/*402980664*pdf f13a.pdf
+cp $resultsdir/spectrum_windows/*146539195*pdf f13b.pdf
+cp $resultsdir/spectrum_windows/*264599508*pdf f13c.pdf

### 2023-08-17 paper/ms.tex
update ms

@@
 described by \citeauthor{2019ApJ...876..127Z}.  Taking the Fourier
-transform of the corrected, padded light curve using {\tt numpy.fft},
+transform of the padded light curve using {\tt numpy.fft},
 we then searched for peaks with a significance of over 12-$\sigma$
@@
 	\caption{
-		{\bf Activity and age diagnostics for three CQVs}.
+		{\bf Spectral age and activity diagnostics for three CQVs}.
 		Wavelengths are in air;
@@
 		the non-detections for TIC~402980664 and TIC~264599508
-		are consistent with the $\sim$42\,Myr age implied by their membership
+		are consistent with the $\approx$42\,Myr age implied by their membership
 		in the Columba moving group.

### 2023-08-17 paper/ms.tex
update ms

@@
 shows the phased TESS light curves for these two outlying magnetic B
-stars, with by-eye ``best matching'' CQVs shown for comparison.  The
+stars, with by-eye ``best matching'' CQVs shown underneath for comparison.  The
 number of dips per cycle, the shapes of the dips, and the dip depths
-relative to the sinusoidal envelope all appear to be similar.  The
-implication of this surprising connection is that the
+relative to the sinusoidal envelope all appear to be similar.  This surprising connection 
+suggests that the
 highly-structured M dwarf light curves may imply multipolar magnetic
@@
 of M dwarfs for which Zeeman Doppler Imaging is technically feasible
-\citep[see the review by][]{2021A&ARv..29....1K}.
+\citep[see][and references therein]{2021A&ARv..29....1K}.
 
@@
 launched by the star returns to its surface over the free-fall
-timescale.  A simple order of magnitude estimate assuming a dipole
+timescale.  A simple estimate assuming a dipole
 field with $B_0\approx1\,{\rm kG}$ at the star's surface, a local
@@
 	}
-	\label{fig:tic3006timegroups}
+	\label{fig:speccutouts}
 \end{figure*}

### 2023-08-17 paper/ms.tex
wordsmithing

@@
   pre-main-sequence stars with nearly periodic optical modulation.
-  The modulation is probably caused by eclipses of dust or gas clumps orbiting at
-  the Keplerian corotation radius.  Here, we report new CQVs
-  discovered in TESS short-cadence data collected between 2018~July
-  and 2022~September.  Our search of \nstarssearched\ K and M dwarfs with
-  $T$$<$16 and $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most
-  of these discoveries are new, and they include the brightest
-  ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and oldest
-  ($\approx$200\,Myr) examples of this class of object currently
-  known.  A few objects are outliers: LP 12-502 for instance showed a
-  ``dip complex'' with a period and duration that were fixed over
-  1,500 cycles, but in detail, this system exhibited between four and
-  eight local minima per cycle, and at times also displayed multiple
-  periods simultaneously.  We demonstrate that transient corotating
-  material is the most viable explanation for this class of object,
-  and present evidence supporting the hypothesis that this material is
-  sculpted by stellar magnetic fields dominated by high order
-  multipoles.  We expect that our sample will facilitate future
-  efforts aimed at connecting CQVs to the broader contexts of star,
-  disk, and perhaps even exoplanet evolution. 	
+  The modulation is probably caused by eclipsing clumps of dust or gas
+  in orbit at the Keplerian corotation radius.  Here, we
+  report new CQVs discovered in TESS short-cadence data collected
+  between 2018~July and 2022~September.  Our search of
+  \nstarssearched\ K and M dwarfs with $T$$<$16 and $d$$<$150\,pc
+  yielded \ngoods\ high-quality CQVs.  Most of these discoveries are
+  new, and they include the brightest ($T$$\approx$9.5), closest
+  ($d$$\approx$20\,pc), and oldest ($\approx$200\,Myr) examples of
+  this class of object currently known.  A few objects are outliers:
+  LP 12-502 for instance showed a ``dip complex'' with a period and
+  duration that were fixed over 1,500 cycles, but in detail, this
+  system exhibited between four and eight local minima per cycle, and
+  at times also displayed multiple periods simultaneously.  We
+  demonstrate that transient corotating material is the most viable
+  explanation for this class of object, and present evidence
+  supporting the hypothesis that this material is sculpted by stellar
+  magnetic fields dominated by high order multipoles.  We expect that
+  our sample will facilitate future efforts aimed at connecting CQVs
+  to the broader contexts of star, disk, and perhaps even exoplanet
+  evolution. 	
 \end{abstract}
@@
 quasiperiodic.  While the three-type classification scheme proposed by
-\citet{2017AJ....153..152S} may indeed provide some helpful visual
+\citet{2017AJ....153..152S} may provide helpful visual
 distinctions amongst the CQVs, it seems likely that they are all
@@
 seconds, we limited our scope in this study for the sake of simplicity
-in data handling and some degree of uniformity in the properties of
-the data itself.  In exchange, we sacrificed both completeness and
-homogeneity of the selection function.  While TESS cumulatively
-observed $\approx$90\% of the sky for at least one lunar month between
-2018 July and 2022 September, the 120-second cadence data were
-collected for only a subset of observable stars during this time due
-to telemetric constraints \citep[see][]{2021PASP..133i5002F}.
+in data handling and uniformity in the data.  In exchange, we
+sacrificed both completeness and homogeneity of the selection
+function.  While TESS cumulatively observed $\approx$90\% of the sky
+for at least one lunar month between 2018 July and 2022 September, the
+120-second cadence data were collected for only a subset of observable
+stars during this time due to telemetric constraints
+\citep[see][]{2021PASP..133i5002F}.
 
 To assess the completeness of the resulting 120-second cadence data
-that is the basis of this study, we cross-matched TIC8.2
+that are the basis of this study, we cross-matched TIC8.2
 \citep{2019AJ....158..138S,2021arXiv210804778P} against the Gaia DR2 point-source catalog
@@
 Previous methods for finding CQVs have included visually examining
-stars known to be in young clusters
-\citep{2016AJ....152..114R,2017AJ....153..152S}, and automatically
+stars in young clusters
+\citep{2016AJ....152..114R,2017AJ....153..152S} and automatically
 flagging rapid rotators with a large number of strong Fourier
 harmonics \citep{2019ApJ...876..127Z}.  The latter approach still
-requires visual vetting, since ``stars with many Fourier harmonics''
+requires visual vetting, since ``stars with strong Fourier harmonics''
 is a designation that includes objects such as eclipsing binaries or
@@
 number of sharp local minima in phase-folded light curves, while also
-using the previously tested Fourier approach.  We applied these two
+using the Fourier approach.  We applied these two
 search techniques independently.
@@
 \citep[e.g.][Figure~15]{2019AJ....157...85B}.  Their H$\alpha$
-equivalent widths, at $\approx$14\,\AA, $\approx$8\,\AA, and
-$\approx$3\AA, are consistent with purely chromospheric emission.
-The blue excess in TIC~264599508 could be explained by a second
-unresolved star; the TESS light curve for this source shows both the
-7.90\,hr CQV signal, and a 9.00\,hr rotation signal with comparable
-amplitude.
+equivalent widths, at $\approx$14\,\AA, $\approx$3\AA, and
+$\approx$8\,\AA (for TIC~264599508, 146539195, and 402980664
+respectively) are consistent with purely chromospheric emission.  The
+blue excess in TIC~264599508 could be explained by a second unresolved
+star; the TESS light curve for this source shows both the 7.90\,hr CQV
+signal, and a 9.00\,hr rotation signal with comparable amplitude.
 

### 2023-08-18 paper/ms.tex
update acknowledge

@@
 \affiliation{\princeton}
+
+\author[0000-0002-0531-1073]{H. Isaacson}
+\affiliation{\berkeley}
+
+\author[0000-0001-8638-0320]{A. W. Howard}
+\affiliation{\caltech}
 
@@
 \acknowledgments
-LGB gratefully acknowledges support from the Heising-Simons
-51~Pegasi~b Fellowship.  A few thank-yous in particular (from LGB) are
-owed to G.~Laughlin, A.~Mann, and J.~Spake for clarifications and
-ideas, and to E.~Schaller and the 51 Peg science team for organizing
-the annual summits.  In addition, this paper relied on data collected
-by the TESS mission, which are publicly available from the Mikulski
-Archive for Space Telescopes (MAST).  Funding for the TESS mission is
-provided by NASA’s Science Mission Directorate.  TIC 402980664 in
-particular was observed at 120-second cadence thanks to the TESS Guest
-Investigator programs G022252 (PI: J.~Schlieder; Sectors 18, 19, 25,
-26) and G04168 (PI: R.~Jayaraman; Sector 53).
+LGB is grateful for support from the Heising-Simons 51~Pegasi~b
+Fellowship.  A few thank-yous (from LGB) are owed to G.~Laughlin,
+A.~Mann, and J.~Spake for clarifications and ideas, and to E.~Schaller
+and the 51 Peg science team for organizing the annual summits.  In
+addition, this paper relied on data collected by the TESS mission,
+which are publicly available from the Mikulski Archive for Space
+Telescopes (MAST).  Funding for the TESS mission is provided by NASA’s
+Science Mission Directorate.  TIC 402980664 in particular was observed
+at 120-second cadence thanks to the TESS Guest Investigator programs
+G022252 (PI: J.~Schlieder; Sectors 18, 19, 25, 26) and G04168 (PI:
+R.~Jayaraman; Sector 53).
 
 %{\bf AUTHOR CONTRIBUTION STATEMENTS: PLEASE REVISE IF APPROPRIATE)}
-LGB conceived the project and performed the dip-counting search, light
-curve classification, cluster membership, SED, variability, and
-secondary-period analyses.
-RJ and SR performed the Fourier-based analysis and contributed
-to light curve classification.
+LGB conceived the project and performed the dip-counting search, light curve classification, cluster membership, SED, variability, and secondary-period analyses.
+RJ and SR performed the Fourier-based analysis and contributed to light curve classification.
 LR cross-examined the light curve classification, and contributed an independent SED analysis.
@@
 G\'AB acquired and maintained the servers used to run the dip-finding pipeline.
-GRR is an architect of the TESS mission.
-{\bf JNW?  MNG?}
+-----
+{\bf JNW, MNG, GRR, HI, and AH to confirm coauthorship \&/or to help out on interpretation!}
+HI and AH designed and maintain the architecture used to acquire and process the HIRES spectra.
 All authors assisted in manuscript writing and revision.

### 2023-08-18 paper/ms.tex
ms: fix typos

@@
 
-\author[0000-0002-0531-1073]{H. Isaacson}
-\affiliation{\berkeley}
-
-\author[0000-0001-8638-0320]{A. W. Howard}
-\affiliation{\caltech}
+% PENDING DISCUSSION!
+%\author[0000-0002-0531-1073]{H. Isaacson}
+%\affiliation{\berkeley}
+%
+%\author[0000-0001-8638-0320]{A. W. Howard}
+%\affiliation{\caltech}
 
@@
       off during TESS re-observations, two years after the initial
-      observation.
+      observation (Figure~\ref{fig:evoln}).
   %
@@
 inclination, roughly one third of low mass stars \citep[those that
-rotate rapidly enough][]{2022AJ....163..144G} could trap circumstellar
+rotate rapidly enough;][]{2022AJ....163..144G} could trap circumstellar
 material in the same way.  It also suggests that CQVs may
@@
 -----
-{\bf JNW, MNG, GRR, HI, and AH to confirm coauthorship \&/or to help out on interpretation!}
-HI and AH designed and maintain the architecture used to acquire and process the HIRES spectra.
+{\bf JNW, MNG, GRR to confirm coauthorship \&/or to help out on interpretation!}
+% Pending!
+%HI and AH designed and maintain the architecture used to acquire and process the HIRES spectra.
 All authors assisted in manuscript writing and revision.
@@
 for TIC~300651846 for at least Sectors 1-12, 27-39, and 61-69.  While
-most of the available data will exist in the full frame images, in
+most of the available data exist in the full frame images,
 Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river} focus
@@
 power at timescales of a few minutes
-\citep{2019A&A...625L..13Z,2022AJ....163..144G}.  This advance was
+\citep{2019ApJ...876..127Z,2022AJ....163..144G}.  This advance was
 enabled by the fifteen-fold faster cadence in the TESS 2-minute data,
@@
 equivalent widths, at $\approx$14\,\AA, $\approx$3\AA, and
-$\approx$8\,\AA (for TIC~264599508, 146539195, and 402980664
+$\approx$8\,\AA\ (for TIC~264599508, 146539195, and 402980664
 respectively) are consistent with purely chromospheric emission.  The

### 2023-08-19 complexrotators/plotting.py
update ms

@@ -3731,10 +3731,14 @@ def plot_tic4029_segments(outdir):
                 fontsize=fontsize, bbox=props)
 
     x, y, dx, dy = 7.52, -44, 0, 2
-    ax.vlines(x, y, y+dy, colors='red', zorder=30, linewidths=1.2)
+    ax.vlines(x, y, y+dy, colors='red', zorder=30, linewidths=1.4)
 
     x, y, dx, dy = 5.98, -51, 0, 2
-    ax.vlines(x, y, y+dy, colors='red', zorder=30, linewidths=1.2)
+    ax.vlines(x, y, y+dy, colors='red', zorder=30, linewidths=1.4)
+
+    x, y, dx, dy = 10.05, -26.5, 0, 2
+    ax.vlines(x, y, y+dy, colors='red', zorder=30, linewidths=1.4)
+
 
     ax.text(0.97, 0.98, 'Cycle #', va='top', ha='right', fontsize=7,
             bbox=props, transform=ax.transAxes)

### 2023-08-20 paper/ms.tex
update ms
fix typo

@@
       96 points per day, and each point is connected by a line.  Data
-      gaps longer are not interpolated; if data are missing, nothing
+      gaps are not interpolated; if data are missing, nothing
       is plotted.  The red vertical lines highlight apparently
@@
 always accompanied by multiple detectable TESS periods
-(\ngoodruweandmultperiod/\ngoodhighruwe high-quality CQVs).  The
+(\ngoodruweandmultperiod/\ngoodhighruwe\ high-quality CQVs).  The
 latter point strongly corroborates the idea that most sources with

### 2023-08-26 paper/ms.tex
Incorporate SAR manuscript suggestions (v0).
Co-authored-by: Saul Rappaport <saul.rappaport@icloud.com>
Co-authored-by: Saul Rappaport <sar@mit.edu>

@@
 with dips that are sufficiently large in depth and short in duration
-\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The dip durations and
+\citep{2017AJ....153..152S,2019ApJ...876..127Z,2021MNRAS.500.1366K}.   The dip durations and
 amplitudes instead require
@@
     {\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
-    stacked over one month.  Gray circles are raw 2-minute data; black
+    phase-folded over one month.  Gray circles are raw 2-minute data; black
     circles bin to 300 points per cycle.  Periods in hours are in the
@@
 \begin{align}
-  T &< 16 \quad&(\mathrm{Bright\ for\ TESS})\\
+  T &< 16 \quad&(\mathrm{Amenable\ with\ TESS})\\
   \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only})\\
@@
 			{\it k)}: Gaia DR2 color--absolute magnitude diagram.     
-			The gray background denotes stars within 100\,pc.
+			The gray background denotes stars within 100\,pc from \citet{2021A&A...649A...6G}.
 			{\it l)}: Information from Gaia DR2, TIC8, and the automated
@@
 similarly-aged Psc-Eri member \citep{2020A&A...639A..64R}.  To our
-knowledge, TIC~332517282 in AB~Dor was the previous record-holder for
-the oldest-known CQV \citep{2019ApJ...876..127Z,2022AJ....163..144G};
-at least one unambiguous CQV (EPIC~211070495) and a few other
-candidates were also previously known in the Pleiades
+knowledge, TIC~332517282 in AB~Dor ($t$$=$$149^{51}_{-19}$\,Myr;
+\citealt{2015MNRAS.454..593B}) was the previous record-holder for the
+oldest-known CQV \citealt{2019ApJ...876..127Z,2022AJ....163..144G}; at
+least one unambiguous CQV (EPIC~211070495) and a few other candidates
+were also previously known in the Pleiades
 \citep{2016AJ....152..114R}.
@@
 These plots showed two clusters of stars, at $\lesssim$10\,\kms and
-20-25\,\kms.  We there adopted a threshold of $20$\,km\,s$^{-1}$ to
+20-25\,\kms.  We therefore adopted a threshold of $20$\,km\,s$^{-1}$ to
 flag possible single-lined spectroscopic binaries, which selected
@@
 {\it Gaia DR3 non-single stars}---Gaia DR3 included a {\tt
-non\_single\_star} column that flagged known or suspected eclipsing,
-astrometric, and spectroscopic binaries.  None of the stars in our CQV
-sample were identified as possible binaries in this column.
+non\_single\_star} column that flagged eclipsing, astrometric, and
+spectroscopic binaries.  None of the stars in our CQV sample were
+identified as possible binaries in this column.
 
@@
 are summarized in the secondary periods, $P_{\rm sec}$, listed in
-Table~\ref{tab:thetable}.  This process yielded
+Table~\ref{tab:thetable}, which we required to be at least 5\%
+different from the primary period.  This process yielded
 \ngoodmultperiodflag/\ngoods\ high-quality CQVs with secondary
@@
       {\bf LP 12-502 (TIC~402980664) light curve}, where each time
-      chunk represents one TESS orbit.  Data were acquired in Sectors
+      segment represents one TESS orbit.  Data were acquired in Sectors
       18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  The
@@
 in the other.  While there is subjectivity in this assessment, to our
-eyes cases for which at least one sector would be flagged as
+eyes, cases for which at least one sector would be flagged as
 ``ambiguous'' include
@@
 already gave this source such a label.  However,
-based on the the shape evolution between Sectors 13 and 39, it is a
+based on the shape evolution between Sectors 13 and 39, it is a
 CQV.  Based on the fraction of sources overall that ``turned off'',
-the observed shape evolution implies that CQVs have a duty cycle of
+the observed shape evolution implies that CQVs have an on-off duty cycle of
 $\approx$75\%.  This type of correction is worth including in
@@
 		\caption{
-			{\bf Evolution of LP 12-502} ($P$=18.6\,h) at fixed period and
-			epoch over three years.  Each panel shows one (stacked) TESS
+			{\bf Evolution of LP 12-502} ($P$=18.5611\,h) at fixed period and
+			epoch over three years.  Each panel shows one phase-folded TESS
 			orbit; small text denotes relative cycle number.  There are 200
@@
     dips.  In Sectors 25-26 (cycles 248-315), periods are visible at
-		the fundamental period of 18.5611\,hr, as well as at faster and
-		slower relative periods.  For example, at $\phi$$\approx$0.05 and
-		$\phi$$\approx$0.3, the various blue ``dips'' have distinct slopes, rather than being
-		exactly vertical.  Multiple simultaneous
-		periods are also visible in Sectors 53 and 58-59.  White chunks
-		denote missing data.
+    the fundamental period of 18.5611\,hr, as well as at faster
+    ($\phi$$\approx$0-0.07) and slower ($\phi$$\approx$0.25-0.27)
+    relative periods based on the presence of blue dips with distinct
+    slopes.  Multiple simultaneous periods are also visible in Sectors
+    53 and 58-59.  White chunks denote missing data.
 	}
@@
 are drawn in gray, also for visual clarity.  Missing data are not
-drawn.  Figure~\ref{fig:lp} then shows the same data, but stacked into
-successive TESS orbits spanning half a lunar month each.  Finally,
-Figure~\ref{fig:lpriver0} shows ``river plots'' of the same data,
-split into similar intervals: the Sector 18-19 data, 25-26 data, 53
-data, and 58-59 data.  The river plots are subject to one additional
-processing step: we fitted and subtracted a maximum-likelihood
-two-harmonic sinusoid independently from the Sector 18-19 data, 25-26
-data, and 53, 58, and 59 data in order to accentuate changes in the
-dip timing and structure.
+drawn.  Figure~\ref{fig:lp} then shows the same data, but folded for
+each successive TESS orbit.  Finally, Figure~\ref{fig:lpriver0} shows
+``river plots'' of the same data, split into similar intervals: the
+Sector 18-19 data, 25-26 data, 53 data, and 58-59 data.  The river
+plots are subject to one additional processing step: we fitted and
+subtracted a maximum-likelihood two-harmonic sinusoid independently
+from the Sector 18-19 data, 25-26 data, and 53, 58, and 59 data in
+order to accentuate changes in the dip timing and structure.
 
@@
 
-Based on their locations locations in the color--absolute magnitude
+Based on their locations in the color--absolute magnitude
 diagram and membership in LCC, both of the K dwarfs do indeed appear
@@
 minimized the dispersion in the phase-folded light curve.  More
-careful inspection however showed that this source is an impostor:
+careful inspection however showed that it is an impostor:
 this source is a photometric blend of two ordinary rotating stars with
@@
 fitted using e.g.~a model analogous to those used for exocomets
-\citep[e.g.][]{2019A&A...625L..13Z}.  The main quantities of interest
+\citep[e.g.][]{2018MNRAS.474.1453R,2019A&A...625L..13Z}.  The main quantities of interest
 in such models would be the exponential decay time- and therefore
@@
 (Figure~\ref{fig:f1}).  Both invoke clumpy material that would be
-centrifugally supported at the corotation radius.  The prominence idea
+magnetically confined at the corotation radius.  The prominence idea
 has a longer history, based on analogy with quiescent
@@
 to field lines, while gravity and the centrifugal force are in balance
-at $R_{\rm cr}$ \citep[see][Sec.~2]{2005MNRAS.357..251T}.  The
-magnetic field strength is only relevant in this formulation of the
-system in that we must have $ R_{\rm cr} < R_{\rm Alfven}$ in order
-for closed loops to exist that can support prominences
-\citep[e.g.][]{1985Ap&SS.116..285N,2019MNRAS.482.2853J}.  In detail
-however, the locations of such magnetic fixed points depends on the
-star's magnetic field topology.
+at $R_{\rm cr}$ \citep[see][Sec.~2]{2005MNRAS.357..251T}.  
+This assumes that the magnetic field dominates the flow, i.e., that
+$B^2/8\pi > \rho v^2 /2$, so that matter is dragged along with the
+field lines.
+The locations where this condition holds may ultimately determine where
+matter can accumulate.
+
+%The magnetic field strength is only relevant in this formulation of
+%the system in that we must have $ R_{\rm cr} < R_{\rm M}$ in
+%order for closed loops to exist that can support prominences
+%\citep[e.g.][]{1985Ap&SS.116..285N,2019MNRAS.482.2853J}.  In detail
+%however, the locations of such magnetic fixed points depends on the
+%star's magnetic field topology.
 
@@
 In the context of planet formation, the stopping location for the
-inner-most planet is set by the location of the protoplanetary disk's
-truncation radius \citep{2018haex.bookE.142I}.  Although this disk
+innermost planet is set by the location of the protoplanetary disk's
+truncation radius \citep{2018haex.bookE.142I}.  Although the disk
 truncation radius is defined by equating the magnetic pressure from
-the stellar magnetosphere with the ram pressure form the inflowing
+the stellar magnetosphere with the ram pressure from the inflowing
 gas, it also tends to coincide with the Keplerian corotation radius
@@
 \citep{2016ARA&A..54..135H,2022MNRAS.510.5246L}.  Within models that
-have compact multiplanet resonant chains migrating inward due to gas
-drag, the inner-most planets therefore arrive at $\approx$5-10 stellar
-radii before the disk becomes depleted.
-
-Given this context, it is tempting to try to interpret features of the
-CQV light curves in terms of the possible presence of either close-in
-exoplanets or close-in planetesimals.  Rocky planets this young could
-have molten global magma oceans analogous to those that existed on the
-Earth and Moon \citep[see][]{2022arXiv220310023L}, and thus might be
-undergoing significant outgassing and atmospheric escape.  The system
-would then be analogous to the Jupiter-Io plasma torus
-\citep[e.g.][]{1980JGR....85.1171N}, although with magnetic fields
-stronger by a factor of $\approx$1{,}000.  However we emphasize that
-while this type of configuration seems a priori plausible, no
-direct evidence currently supports it.
-
-In systems like LP 12-502, the observed variability would perhaps
-drive one toward a picture of a disintegrating planetesimal swarm,
-rather than just a single planetesimal.  The need for more than just
-one launching body is because we see dips appear and disappear at many
-different phases, but with roughly the same period.  The observed
-changing dip depths in response to flares would be understood through
-the planetesimal outflow rates being stalled by changes in the local
-magnetic field or coronal plasma density.  The sizes of these
-purported planetesimals would need to be $\lesssim 1$\,$R_\oplus$,
-based on the non-detections of their transits, analogous to e.g.
-K2-22 \citep{2015ApJ...812..112S} or KOI-2700
-\citep{2014ApJ...784...40R}.  Typical sizes of bodies in the asteroid
-belt for instance span hundreds of meters to a few kilometers.
-
-There are at least three problems with this disintegrating
-planetesimal swarm concept.  First, the model would predict that
-certain orbital phases would produce recurrent dips if observed over
+have one or more planets migrating inward due to gas drag, the
+innermost planets therefore arrive at $\approx$5-10 stellar radii
+before the disk becomes depleted.
+
+Given the known abundance of small planets around M dwarfs, it is
+tempting to try to interpret features of the CQV light curves in terms
+of the possible presence of either close-in exoplanets or close-in
+planetesimals.  Rocky bodies this young could have molten global magma
+oceans analogous to those that existed on the Earth and Moon
+\citep[see][]{2022arXiv220310023L}, and could plausibly be outgassing
+either from those magma oceans, or from their unprocessed thin
+primordial atmospheres; in the former scenario, the gas would likely
+be enriched in heavy elements relative to the stellar wind.  The
+system would in certain respects be analogous to the Jupiter-Io plasma
+torus \citep[e.g.][]{2004jpsm.book..537S}, although with magnetic
+fields stronger by a factor of $\approx$1{,}000.  We emphasize that
+while this type of configuration seems a priori plausible, no direct
+evidence currently supports it.
+
+At their core, the planetesimals would primarily serve as the source
+for the occulting gas or dust; they would not necessarily need to
+explain the observed phases of the observed dips.  The azimuth angle
+of the eventual confinement could be entirely determined by the
+stellar magnetic field configuration.  In this scenario, the obscuring
+material could potentially inspiral from outgassing planetesimals many
+stellar radii away from the corotation radius.  While the
+planetesimals themselves would not necessarily need to transit, if
+they did, they would need to be $\lesssim 1$\,$R_\oplus$ based on
+their non-detections in the TESS data.  This would be analogous to
+previously known systems such as K2-22 \citep{2015ApJ...812..112S} and
+KOI-2700 \citep{2014ApJ...784...40R}, though the obscuring material
+would be observed much further from the emitting planet.
+
+A more restrictive variant of the planetesimal scenario would be to
+posit that the obscuring material remains close to the launching body,
+similar to comets, or to the aforementioned K2-22 and KOI-2700
+systems.  If so, then the planetesimals would need to be at the
+corotation radius.  One prediction would therefore be that certain
+orbital phases would produce recurrent dips when observed over
 sufficiently long baselines, because the launching planetesimal would
 be massive enough to remain in orbit, while stochastically ejecting
-material.  An analogous system would be K2-22
-\citep{2015ApJ...812..112S}.  For most CQVs (Figure~\ref{fig:evoln}),
-the data are in tension with this expectation.  A second issue is that
-many of the dips show asymmetries in the wrong direction relative to
-the naive expectation of a trailing comet tail.  Invoking
-non-exponentially decaying dust distributions as a function of azimuth
-might be one way out, but such an idea lacks firm theoretical footing.
-Finally, dynamical stability is a concern: in a model in which any new
-dip is ``explained'' by invoking a new planetesimal, one might
-eventually pack the corotation radius to a degree where instability
-over short timescales would be guaranteed.
-
-It is certainly possible that exoplanets or exoplanetesimals could end
-up being connected to the CQV phenomenon, for instance as a possible
-sources for the occulting dust or gas.  However for the time being,
-none of the CQVs that we have studied in this work show clear evidence
-for the nearby planets that we statistically expect should be common.
+material.  For most CQVs (Figure~\ref{fig:evoln}), the data seem to be
+in tension with this expectation because the relative spacing between
+dips is almost never conserved.  With that said, certain sources do
+seem to exhibit ``special phases'', including LP 12-502
+(TIC~402980664), DG~CVn (TIC~368129164), TIC~193831684, and
+TIC~146539195.  One possible explanation for this might be if
+obscuring material is remaining close to its launching body, or
+bodies.  An alternative explanation could be that the stellar magnetic
+field configurations responsible for confining said material are
+stable over the existing two-year baseline.
+
+%In systems like LP 12-502, the observed variability would perhaps
+%drive one toward a picture of a disintegrating planetesimal swarm,
+%rather than just a single planetesimal.  The need for more than just
+%one launching body would be because we see dips appear and disappear at many
+%different phases, but with roughly the same period.  The observed
+%changing dip depths in response to flares could be understood through
+%the planetesimal outflow rates being stalled by changes in the local
+%magnetic field or coronal plasma density.  The sizes of these
+%purported planetesimals would need to be $\lesssim 1$\,$R_\oplus$,
+%based on the non-detections of their transits, analogous to e.g.
+%K2-22 \citep{2015ApJ...812..112S} or KOI-2700
+%\citep{2014ApJ...784...40R}.  Typical sizes of bodies in the asteroid
+%belt for instance span hundreds of meters to a few kilometers.
+
+%There are at least three problems with this disintegrating
+%planetesimal swarm concept.  First, the model would predict that
+%certain orbital phases would produce recurrent dips if observed over
+%sufficiently long baselines, because the launching planetesimal would
+%be massive enough to remain in orbit, while stochastically ejecting
+%material.  An analogous system would be K2-22
+%\citep{2015ApJ...812..112S}.  For most CQVs (Figure~\ref{fig:evoln}),
+%the data are in tension with this expectation.  A second issue is that
+%many of the dips show asymmetries in the wrong direction relative to
+%the naive expectation of a trailing comet tail.  Invoking
+%non-exponentially decaying dust distributions as a function of azimuth
+%might be one way out, but such an idea lacks firm theoretical footing.
+%Finally, dynamical stability is a concern: in a model in which any new
+%dip is ``explained'' by invoking a new planetesimal, one might
+%eventually pack the corotation radius to a degree where instability
+%over short timescales would be guaranteed.
+
+%It is certainly possible that exoplanets or exoplanetesimals could end
+%up being connected to the CQV phenomenon, for instance as a possible
+%sources for the occulting dust or gas.  However for the time being,
+%none of the CQVs that we have studied in this work show clear evidence
+%for the nearby planets that we statistically expect should be common.
 
@@
 The dips in both are probably associated with clumps of dust or gas.
-However the CQV dips are both more periodic and less deep than those
-of dippers; they also display far less transience over timescales of a
-few to tens of cycles.  This is presumably because CQVs have
+However the CQV dips are generally more periodic and less deep than
+those of dippers; they also display far less transience over
+timescales of a few to tens of cycles.  The CQVs also have
 demonstrably less dust than (most) dipper stars.  At a population
@@
 
-\subsection{Are half-cycles important?}
-
-The interval of half a cycle period could be significant in the
-context of CQVs for two reasons.  The first is that for material on a
-circular orbit viewed edge-on, a half-cycle corresponds to the
-interval between transit and secondary eclipse.  The second is that
-the half-cycle also corresponds to the interval over which half of the
-star's surface is visible.  Of the CQVs in Figures~\ref{fig:cqvs}
-and~\ref{fig:evoln}, a fraction that seems greater than random might
-exhibit a preference for showing dips or peaks that correspond to the
-half-cycle interval.
-
-One set of CQVs shows ``CQV behavior'' (some form of dip complex), but
-which only lasts for half of any given cycle.  TIC~206544316 (Sector
-2) is a canonical example; TIC~405910546 (Sector 38), TIC~167664935
-(Sector 38), TIC~146539195 (Sector 5), TIC~118449916 (Sector 44), and
-TIC~312410638 (Sector 38) seem to show the same tendency.
-
-An independent set of CQVs exhibits small dips roughly half a cycle
-after large dips; it is tempting to label the small dips secondary
-eclipses.  Such sources include TIC~402980664 (Sector 25; relative to
-the sharpest, deepest minimum), TIC~89463560 (Sector 36),
-TIC~224283342 (Sector 2), and TIC~442571495 (Sector 12).  For the
-particular case of TIC~224283342, this observation, coupled with Gaia
-DR3 radial velocities suggesting a radial velocity scatter exceeding
-20\,\kms, suggests that the system could be a low-mass eclipsing
-binary transiting a giant polar spot, analogous to TOI-3884
-\citep{2022A&A...667L..11A}.
-
-In general however, it is challenging to interpret the significance of
-the potential ``half-period regularities'';  the CQVs exhibit such a
-wide range of variability that for seemingly any regularity one might
-posit, it is easy to come up with counter-example objects which do not
-follow the trend.  In other words, these half-cycle CQVs could simply
-be a product of the human tendency to pattern match.
+%\subsection{Are half-cycles important?}
+%
+%The interval of half a cycle period could be significant in the
+%context of CQVs for two reasons.  The first is that for material on a
+%circular orbit viewed edge-on, a half-cycle corresponds to the
+%interval between transit and secondary eclipse.  The second is that
+%the half-cycle also corresponds to the interval over which half of the
+%star's surface is visible.  Of the CQVs in Figures~\ref{fig:cqvs}
+%and~\ref{fig:evoln}, a fraction that seems greater than random might
+%exhibit a preference for showing dips or peaks that correspond to the
+%half-cycle interval.
+%
+%One set of CQVs shows ``CQV behavior'' (some form of dip complex), but
+%which only lasts for half of any given cycle.  TIC~206544316 (Sector
+%2) is a canonical example; TIC~405910546 (Sector 38), TIC~167664935
+%(Sector 38), TIC~146539195 (Sector 5), TIC~118449916 (Sector 44), and
+%TIC~312410638 (Sector 38) seem to show the same tendency.
+%
+%An independent set of CQVs exhibits small dips roughly half a cycle
+%after large dips; it is tempting to label the small dips secondary
+%eclipses.  Such sources include TIC~402980664 (Sector 25; relative to
+%the sharpest, deepest minimum), TIC~89463560 (Sector 36),
+%TIC~224283342 (Sector 2), and TIC~442571495 (Sector 12).  For the
+%particular case of TIC~224283342, this observation, coupled with Gaia
+%DR3 radial velocities suggesting a radial velocity scatter exceeding
+%20\,\kms, suggests that the system could be a low-mass eclipsing
+%binary transiting a giant polar spot, analogous to TOI-3884
+%\citep{2022A&A...667L..11A}.
+%
+%In general however, it is challenging to interpret the significance of
+%the potential ``half-period regularities'';  the CQVs exhibit such a
+%wide range of variability that for seemingly any regularity one might
+%posit, it is easy to come up with counter-example objects which do not
+%follow the trend.  In other words, these half-cycle CQVs could simply
+%be a product of the human tendency to pattern match.
 
@@
 magnetosphere'' \citep[see][]{2013MNRAS.429..398P}.  In other words,
-both classes of objects probably satisfy the condition $R_{\rm A} >
-R_{\rm cr}$, for $R_{\rm A}$ the Alfv\'en radius.  When this condition
+both classes of objects probably satisfy the condition $R_{\rm M} >
+R_{\rm cr}$, for $R_{\rm M}$ the magnetospheric radius (sometimes
+referred to as the Alfv\'en radius).  When this condition
 holds, stable points exist wherever the outward centrifugal force is
@@
 closed field loops \citep{1985Ap&SS.116..285N}.  In the converse
-``dynamical'' case, when  $R_{\rm A} < R_{\rm cr}$, any material
-launched by the star returns to its surface over the free-fall
-timescale.  A simple estimate assuming a dipole
+``dynamical'' case, when  $R_{\rm M} < R_{\rm cr}$, material
+interior to the magnetospheric radius returns to the stellar surface
+over the free-fall timescale.  A simple estimate assuming a dipole
 field with $B_0\approx1\,{\rm kG}$ at the star's surface, a local
 plasma number density $n\approx10^9\,{\rm cm^{-3}}$, and a plasma
-temperature $10^6\,{\rm K}$ gives Alfv\'en radii of order a few times
-the corotation radii, $R_{\rm cr}$.  This suggests that the existence
-of a centrifugal magnetosphere is plausible in young, rapidly rotating
-M dwarfs.
+temperature $10^6\,{\rm K}$ gives magnetospheric radii of order a few
+times the corotation radii, $R_{\rm cr}$.  This suggests that the
+existence of a centrifugal magnetosphere is plausible in young,
+rapidly rotating M dwarfs.
 
@@
       to happen over durations of at least ten cycles, and slow dip
-      decay can also occur.  ``State-switches'' correspond to dips to
+      decay can also occur.  ``State-switches'' correspond to dips 
       collapsing instantaneously, and are almost always linked with
@@
 	%
-    \item The duty cycle for CQVs seems to be $\approx$$75$\%, based
+    \item The on-off duty cycle for CQVs seems to be $\approx$$75$\%, based
       on the fraction of bona fide CQVs that either turned on or turned
@@
 spectra holds a good chance at resolving the gas vs.~dust question.
-Given our observed $\approx$75\% duty cycles, such data must be
+Given our observed $\approx$75\% on-off duty cycles, such data must be
 acquired simultaneously with photometric time-series observations
@@
 LGB is grateful for support from the Heising-Simons 51~Pegasi~b
-Fellowship.  A few thank-yous (from LGB) are owed to G.~Laughlin,
-A.~Mann, and J.~Spake for clarifications and ideas, and to E.~Schaller
-and the 51 Peg science team for organizing the annual summits.  In
-addition, this paper relied on data collected by the TESS mission,
-which are publicly available from the Mikulski Archive for Space
-Telescopes (MAST).  Funding for the TESS mission is provided by NASA’s
-Science Mission Directorate.  TIC 402980664 in particular was observed
-at 120-second cadence thanks to the TESS Guest Investigator programs
-G022252 (PI: J.~Schlieder; Sectors 18, 19, 25, 26) and G04168 (PI:
-R.~Jayaraman; Sector 53).
+Fellowship, and for helpful conversations with G.~Laughlin, A.~Mann,
+and J.~Spake.  This paper relied on data collected by the TESS
+mission, which are publicly available from the Mikulski Archive for
+Space Telescopes (MAST).  The specific 120-second cadence observations
+can be accessed via
+\dataset[DOI]{https://doi.org/10.17909/t9-nmc8-f686}.  Funding for the
+TESS mission is provided by NASA’s Science Mission Directorate.  TIC
+402980664 in particular was observed at 120-second cadence thanks to
+the TESS Guest Investigator programs G022252 (PI: J.~Schlieder;
+Sectors 18, 19, 25, 26) and G04168 (PI: R.~Jayaraman; Sector 53).
 

### 2023-08-26 complexrotators/plotting.py

@@ -1683,7 +1683,7 @@ def plot_cpvvetter(
     bp_rp = get_xval_no_corr(gdf)
     M_G = get_yval_no_corr(gdf)
     ax.scatter(bp_rp, M_G, zorder=9000,
-               c='lime', s=30, marker='X', edgecolors='k', linewidths=0.5)
+               c='lime', s=60, marker='X', edgecolors='k', linewidths=0.5)
 
     xmin, xmax = 0.9, 3.6
     if bp_rp > xmax:
@@ -2906,7 +2906,7 @@ def plot_full_lcmosaic(outdir, showtitles=1, titlefontsize=3.5,
 
         lcpath = lcpaths[0]
 
-        cachedir = '/Users/luke/local/complexrotators/cpv_finding/2023catalog_LGB_RJ_concat'
+        cachedir = '/Users/luke/local/complexrotators/cpv_finding/2023catalog_LGB_RJ_concat_BACKUP'
 
         # get the relevant light curve data
         (time, flux, qual, x_obs, y_obs, y_flat, y_trend, x_trend, cadence_sec,
@@ -3052,7 +3052,7 @@ def plot_full_lcmosaic(outdir, showtitles=1, titlefontsize=3.5,
         s += f'_{sortby}'
 
     # height/width
-    fig.tight_layout(h_pad=0.02, w_pad=0.)
+    fig.tight_layout(h_pad=0.06, w_pad=0.)
 
     #axs[-1].set_axis_off()
 
@@ -3743,7 +3743,7 @@ def plot_tic4029_segments(outdir):
     ax.text(0.97, 0.98, 'Cycle #', va='top', ha='right', fontsize=7,
             bbox=props, transform=ax.transAxes)
 
-    ax.set_xlabel('Days since chunk began')
+    ax.set_xlabel('Days since segment began')
     ax.set_ylabel('Flux [%]')
 
     ax.tick_params(axis='both', which='major', labelsize='small')

### 2023-08-29 paper/ms.tex
[WIP] Update ms with JNW suggestions (intro+abs)
Co-authored-by: Joshua Winn <jnwinn@princeton.edu>

@@
 
+\author[0000-0002-4265-047X]{Joshua N. Winn}
+\affiliation{\princeton}
+
 \author[0000-0001-7204-6727]{G\'asp\'ar \'A. Bakos}
@@
 \affiliation{\mitkavli}
-
-\author[0000-0002-4265-047X]{Joshua N. Winn}
-\affiliation{\princeton}
 
@@
 
-All pre-main-sequence stars vary in optical brightness, and the origin
-of such variability is, in most cases, understood.  Well-explored
-sources of optical variability include inhomogeneities on stellar
-surfaces such as starspots and faculae
-\citep[e.g.][]{2021isma.book.....B}, occultations by gas-rich
-circumstellar disks \citep[e.g.][]{2017MNRAS.470..202B}, and, in
-geometrically favorable circumstances, eclipses by stars and planets
-\citep[e.g.][]{2010exop.book...55W}.  More exotic forms of optical
-variability relevant to this work include transiting exocomets
-(e.g.~$\beta$~Pic; \citealt{2019A&A...625L..13Z}) and disintegrating
-rocky bodies around both M dwarfs (e.g. KOI-2700;
-\citealt{2014ApJ...784...40R}) and white dwarfs (e.g. WD~1145;
-\citealt{2015Natur.526..546V}).
-
-Data from K2 and TESS have yielded a new class of variable star whose
-root cause is only beginning to become clear: complex quasiperiodic
-variables (CQVs).  These objects are identified from their optical
-light curves, which show nearly periodic troughs that are either sharp
-or broad; these troughs are often superposed on smooth spot-like
-modulation
+All young stars vary in optical brightness, and the origin of such
+variability is, in most cases, understood.  Well-explored sources of
+optical variability include inhomogeneities on stellar surfaces such
+as starspots and faculae \citep[e.g.][]{2021isma.book.....B},
+occultations by circumstellar disks
+\citep[e.g.][]{2017MNRAS.470..202B}, and, in geometrically favorable
+circumstances, eclipses by stars and planets
+\citep[e.g.][]{2020AJ....160...33R}.  More exotic sources of optical
+variability that are potentially relevant to this work include
+transiting exocomets (e.g.~$\beta$~Pic;
+\citealt{2019A&A...625L..13Z}), disintegrating rocky bodies (e.g.
+KOI-2700; \citealt{2014ApJ...784...40R}), and occultations by
+circumstellar plasma clumps (e.g.~$\sigma$~Ori~E;
+\citealt{2005ApJ...630L..81T,2005MNRAS.357..251T}).
+
+Data from K2 \citep{2014PASP..126..398H} and TESS
+\citep{2015JATIS...1a4003R} have revealed a new class of variable
+star for which the root cause of variability is only beginning to
+become clear: complex quasiperiodic variables (CQVs).  These objects
+are identified from their optical light curves, which show nearly
+periodic troughs that are either sharp or broad; these troughs are
+often superposed on quasi-sinusoidal spot-like modulation
 \citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z}.
-Some CQVs show up to eight local minima (``dips'') per cycle.  Most
-are pre-main-sequence M dwarfs without near-infrared excesses, ages of
-$\approx$5-150 million years (Myr), and rotation periods of at most
-two days; they are observed to comprise $\approx$1-3\% of M dwarfs
-younger than 100 Myr \citep{2016AJ....152..114R,2022AJ....163..144G}.
-The dips can be chromatic, with a reddening law plausibly consistent
-with dust
+Some CQVs show up to eight dips per cycle.  Most CQVs are
+pre-main-sequence M dwarfs with ages of $\approx$5-150 million years
+(Myr), and rotation periods of 0.2--2 days.  They are observed to
+comprise $\approx$1-3\% of M dwarfs younger than 100 Myr
+\citep{2016AJ....152..114R,2022AJ....163..144G}.  They generally do
+not show near-infrared excesses indicative of dusty disks, but the
+wavelength-dependent dip amplitudes of some CQVs is consistent with
+reddening by dust
 \citep{2017PASJ...69L...2O,2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
-And finally, while the dip shapes can ``jump'' between different
-depths and durations over less than one cycle, they more often evolve
-gradually, over tens to hundreds of cycles
+The dip amplitudes and phases usually evolve gradually over tens to
+hundreds of cycles, although they have occasionally been observed to
+change abruptly within one cycle
 \citep[e.g.][]{2017AJ....153..152S,2022ApJ...925...75P,2023ApJ...945..114P}.
 
-The CQV light curves cannot be explained by pure starspots.  Although
-all young M dwarfs are spotted, this tends to produce flux variations
-over timescales of the rotation period, $P_{\rm rot}$,
-and its half-harmonic, $0.5\,P_{\rm rot}$.  With fine-tuned
-viewing geometries, starspots can produce dip durations as short
-as $\approx$$0.2\,P_{\rm rot}$, and the dip amplitudes in such
-geometries are small
-due to limb-darkening (see \citealt{2017AJ....153..152S},
-Figures 37-41).  The observed dips occur over durations as
-short as $0.05\,P_{\rm rot}$ with characteristic depths of a few
-percent; a ``starspot-only'' scenario can be discarded for any object
-with dips that are sufficiently large in depth and short in duration
-\citep{2017AJ....153..152S,2019ApJ...876..127Z,2021MNRAS.500.1366K}.   The dip durations and
-amplitudes instead require
-sharp geometries with material extrinsic to the stellar surface
-\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  Since some CQVs require
-such geometries, and the
-CQVs probably all have a single explanation, we therefore
-discard the ``spot-only'' scenario.
-
-A few competing explanations for what causes the complex quasiperiodic
-variability are shown in Figure~\ref{fig:f1}.  The ``clump'' scenario
-invokes opaque dust clumps periodically transiting the star near the
-Keplerian corotation radius, $R_{\rm cr} = (GM/\Omega^2)^{1/3}$
-\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The ``prominence''
-scenario invokes long-lived condensations of cool and dense
-marginally-ionized gas, embedded within the hotter corona, that would
-be centrifugally supported to also be near corotation
+The sharp features of CQV light curves can have durations as short as
+5\% of the rotation period ($P_{\rm rot}$), which is too short to be
+caused by starspots rotating into and out of view.  Starspots produce
+flux variations with characteristic timescales of $P_{\rm rot}$ and
+$0.5\,P_{\rm rot}$.  With finely-tuned viewing geometries, starspots
+can produce dip durations as short as $\approx$$0.2\,P_{\rm rot}$, but
+in such cases, limb darkening causes the dip amplitudes to be smaller
+than the observed amplitudes of $\sim$1\% (see
+\citealt{2017AJ....153..152S}, Figures 37-41).  Thus, a
+``starspot-only'' scenario can be ruled out for many CQVs
+\citep{2017AJ....153..152S,2019ApJ...876..127Z,2021MNRAS.500.1366K}.
+Given that many CQVs cannot be explained by starspots alone, and
+working under the assumption that all CQVs share the same basic
+physical scenario, we discard the ``starspot-only'' scenario.
+Instead, the correct explanation probably involves material above the
+stellar surface that is spatially confined with sharp boundaries
+\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.
+
+Figure~\ref{fig:f1} illustrates two proposed models for the extrinsic
+material.  The first scenario invokes opaque dust ``clumps'' that
+orbit near the Keplerian corotation radius [$R_{\rm cr} =
+(GM/\Omega^2)^{1/3}$, where $\Omega = 2\pi/P_{\rm rot}$] and
+periodically transit the star
+\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The second scenario
+invokes ``prominences'', long-lived condensations of cool, dense,
+marginally-ionized gas that are embedded within the hotter corona and
+corotate with the star
 \citep{1989MNRAS.238..657C,2019MNRAS.482.2853J,2022MNRAS.514.5465W}.
-Such structures are analogous to quiescent prominences and filaments
-seen in the solar corona \citep[see e.g.][]{2015ASSL..415.....V},
-though at much larger relative distances from the stellar surface.  A
-final possibility is one of a ``screen'', in which the inner wall of a
-quiescent circumstellar disk blocks a portion of the stellar surface
-to produce sudden dips whenever spots come into view
-\citep{2019ApJ...876..127Z}.
-
-The dust clump and prominence hypotheses seem most plausible.  They
-are qualitatively similar, except that one invokes opacity from dust,
-while the other invokes opacity from gas, likely bound-free
-transitions in hydrogen or perhaps a molecular opacity.  The screen
-scenario seems inconsistent with the sharpness of the observed dips,
-the lack of infrared excess, and the observed lifetime of CQVs
-extending an order of magnitude longer than the $\approx$$10^7$ year
-timescale often quoted for primordial disk dispersal.  However,
-unambiguous evidence in support of any one scenario has yet to be
-acquired.  Such evidence might include a spectroscopic detection of
-silicate 10\,$\mu$m dust absorption during a dip, or perhaps detection
-of transient Balmer-line excesses as a function of cycle phase,
-similar to observations made in systems such as AB~Dor
-\citep[see][]{1999ASPC..158..146C} or PTFO 8-8695
+These hypothetical structures are analogous to quiescent prominences
+and filaments seen in the solar corona \citep[see
+e.g.][]{2015ASSL..415.....V}, though rather than existing at a
+fraction of the stellar radius as in the solar case, they would exist
+at distances of a few stellar radii.  A final possibility is that a thin
+optically-thick ring obscures a small portion of the stellar
+photosphere \citep{2019ApJ...876..127Z}.  Hot spots passing behind such a structure could produce
+sudden dips.  We do not favor this scenario due to the issues
+discussed in Appendix~\ref{app:ring}.
+
+The dust clump and prominence hypotheses are qualitatively similar,
+except that one invokes opacity from dust, while the other invokes
+opacity from gas, likely bound-free transitions in hydrogen or perhaps
+a molecular opacity.  However unambiguous evidence in support of any particular
+scenario has yet to be acquired.  Such evidence might include a
+spectroscopic detection of silicate 10\,$\mu$m dust absorption during
+a dip, or perhaps detection of transient Balmer-line excesses as a
+function of cycle phase, similar to observations made in systems such
+as AB~Dor \citep[see][]{1999ASPC..158..146C} or PTFO 8-8695
 \citep{2016ApJ...830...15J}.
@@
 CQVs remain mysterious because they have been both hard to discover
-and hard to characterize.   Discoverability is tied to rarity: CQVs
-comprise $\approx$1\% of the youngest $\approx$1\% of M dwarfs
-\citep{2018AJ....155..196R}.  Out of the millions of stars monitored
-by K2 and TESS, about 50 CQVs have been reported to date
+and hard to characterize.   They are hard to discover because they are
+rare: CQVs comprise $\approx$1\% of the youngest $\approx$1\% of M
+dwarfs \citep{2018AJ....155..196R}.  Out of the millions of stars
+monitored by K2 and TESS, about 50 CQVs have been reported to date
 \citep{2016AJ....152..114R,2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2020AJ....160...86B,2022AJ....163..144G,2023ApJ...945..114P}.
-The known CQVs are correspondingly faint; the initial K2 discoveries
+They have been hard to characterize because many of the known CQVs are
+relatively faint; the initial K2 discoveries
 \citep{2016AJ....152..114R,2017AJ....153..152S} were M2-M6 dwarfs at
 distances $\gtrsim$100\,pc, yielding optical brightnesses of
-$V$$\approx$15.5 to $V$$>$20.  This renders time-series spectroscopy
-at high resolution out of reach for current facilities, despite its
-potential utility in ruling out some of these models.
+$V$$\approx$15.5 to $V$$>$20.  At such magnitudes, high-resolution
+time-series spectroscopy is out of reach with current facilities,
+despite the potential utility of such observations.
 
@@
 Cycles 1-4).  We present our search methods in
-Section~\ref{sec:methods}, and the properties of the resulting CQV
-catalog in Section~\ref{sec:results}.  The evolution of many CQVs over
-a two-year baseline is described in Section~\ref{sec:evoln}, including
-a deep-dive into LP 12-502.  We discuss a few implications in
+Section~\ref{sec:methods}, and the resulting CQV catalog in
+Section~\ref{sec:results}.  The observed evolution of many CQVs over a
+two-year baseline is described in Section~\ref{sec:evoln}, including a
+deep-dive into the behavior of an especially interesting object, LP
+12-502.  We discuss a few implications in
 Section~\ref{sec:discussion}, and conclude in
@@
 
-A point on nomenclature.  CQVs have been called ``transient flux
-dips'', ``persistent flux dips'', ``scallop shells'', ``batwings'',
-\citep{2017AJ....153..152S} ``complex rotators'',
+Some comments on nomenclature are needed.  What we are calling CQVs
+have also been called ``transient flux dips'', ``persistent flux
+dips'', ``scallop shells'', ``batwings'', \citep{2017AJ....153..152S}
+``complex rotators'',
 \citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P},
@@
 variability linked to obscuring inner disk structures and accretion
-hot spots \citep{2014AJ....147...82C,2021ApJ...908...16R}.  While a
-few similarities between CQVs and dippers do exist (see
-Sections~\ref{subsec:irexcess} and~\ref{subsec:discdippers}), their
-phenomenology and stellar properties are quite different.  At the risk
-of introducing yet another standard, we hope to use a nomenclature
-that reflects how, when observed over timescales of more than tens of
-cycles, CQVs are almost but not exactly periodic.  They are
-quasiperiodic.  While the three-type classification scheme proposed by
-\citet{2017AJ....153..152S} may provide helpful visual
-distinctions amongst the CQVs, it seems likely that they are all
-explained by a single underlying phenomenon, and so we opt to refer to
-them by a single empirically descriptive name.  We also considered
-names that focused on the presence of transient corotating clumps, or
-more generally on circumstellar plasma tori; for the time being,
-``CQV'' is agnostic to the true underlying phenomenon.
+hot spots \citep{2014AJ....147...82C,2021ApJ...908...16R}.  The
+phenomenology and stellar properties of CQVs and dippers are
+quite different (though see Sections~\ref{subsec:irexcess}
+and~\ref{subsec:discdippers}).  Despite the cost of introducing yet
+another naming standard, we prefer to use a single empirically
+descriptive name that highlights these objects as variable stars, and
+not ``rotators''.  We also prefer a nomenclature that reflects how the
+dips and peaks of these stars always appear to be transient 
+when observed over timescales exceeding hundreds of cycles.  ``Complex
+quasiperiodic variable'' meets these requirements, for the time being.
 
@@
 		\subfloat{
-			\includegraphics[width=0.8\textwidth]{f1b.pdf}
+			\includegraphics[width=0.66\textwidth]{f1b.pdf}
 		}
@@
 		{\bf Complex quasiperiodic variables (CQVs)}:
-    {\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
-    phase-folded over one month.  Gray circles are raw 2-minute data; black
-    circles bin to 300 points per cycle.  Periods in hours are in the
-    bottom right of each panel.  Left-to-right, the objects are LP
+    {\it Top:} Phase-folded TESS light curves of three CQVs.  Each panel shows
+    the average of the data accumulated over one month.
+    Gray circles are raw 2-minute data; black
+    circles are binned to 300 points per cycle.  The periods in hours
+    is printed in the
+    bottom right corner.  Left-to-right, the objects are LP
     12-502 (TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and
     TIC 425933644 (Sector~28).
-    {\it Bottom:} Cartoon explanations for the phenomenon.  The dust clump
-    scenario (lower left) and prominence scenario (lower center) both
-    invoke centrifugally-supported material at the corotation radius.
-    We disfavor the screen scenario (see Section~\ref{sec:intro}).
+    {\it Bottom:} Cartoon explanations for the phenomenon.  The dust
+    clump scenario (left) and prominence scenario (right) both invoke
+    magnetically-confined corotating material.
 	}
@@
 \citealt{2015MNRAS.454..593B}) was the previous record-holder for the
-oldest-known CQV \citealt{2019ApJ...876..127Z,2022AJ....163..144G}; at
+oldest-known CQV \citep{2019ApJ...876..127Z,2022AJ....163..144G}; at
 least one unambiguous CQV (EPIC~211070495) and a few other candidates
@@
 
-At their core, the planetesimals would primarily serve as the source
+The main logical function of the planetesimals is to serve as a source
 for the occulting gas or dust; they would not necessarily need to
@@
 
+\section{The ring hypothesis}
+\label{app:ring}
+
+One hypothesis for the CQVs, presented by \citet{2019ApJ...876..127Z},
+is that the star might be ``{\it orbited by one or more rings composed of
+dust-size or somewhat larger particles\ldots The ring particles would
+move in Keplerian orbits at relatively large distances from the star,
+and therefore the sublimation lifetime would not be an issue even if
+the particles are dust-like in size.}'' A sketch of this scenario is
+presented by \citet{2019ApJ...876..127Z}, in their Figure~11.
+An example set of proposed parameters involved a ring inclined with
+respect to the stellar spin axis by a few degrees, and with inner and
+outer radii of 10 and 15 stellar radii.
+
+One concern with the ring hypothesis is that if a cool spot were to
+transit behind the ring, it would produce a brightening, rather than a
+dimming.   Most CQVs show dimmings.   The ring scenario would
+therefore imply that large hot spots are common in the photospheres of
+pre-main-sequence M dwarfs.  Empirical evidence however suggests that
+the optical variability of disk-free pre-main-sequence stars is
+dominated by cool spots.  This evidence includes flux excursions
+caused by spot-crossings during planetary transits
+\citep[e.g.][]{2020AJ....160...33R,2022AJ....163..147G}, correlations
+between simultaneous photometric and chromospheric time-series
+\citep{2019A&A...621A..21R}, and stellar spectra that show molecules
+that only form at cool temperatures
+\citep[e.g.][]{2017ApJ...836..200G,2023ApJ...946...10P}.
+
+A stronger concern with the ring hypothesis is that it is fine-tuned.
+The model requires specific locations for the inner edge and the outer
+edge of the ring, an inclination that yields a band with a particular
+apparent size, and for material in the ring to be optically thick
+while also being homogeneous enough to not induce any apparent
+photometric variability.
+While it is challenging to ascribe specific probabilities to any one
+of these factors, 
+the requirement that they all be simultaneously met seems sufficiently
+severe to disfavor this scenario.
+
 \section{TIC~300651846}

### 2023-08-29 paper/collect.sh

@@ -1,9 +1,10 @@
 resultsdir="/Users/luke/Dropbox/proj/cpv/results"
+artdir="/Users/luke/Dropbox/proj/cpv/art"
 addir="/Users/luke/Dropbox/Documents/proposals/2023_05_ADAP/latex/figs/"
 
 # fig1
 cp $resultsdir/lc_mosaic/lc_mosaic_fav3.pdf f1a.pdf
-cp $addir/models.pdf f1b.pdf
+cp $artdir/twomodels.pdf f1b.pdf
 
 # fig2 is annotated_lp12502.key exported
 

### 2023-08-29 paper/ms.tex
Update ms
Co-authored-by: Joshua Winn <jnwinn@princeton.edu>

The "complex rotator" crowd made the case.  I bought it!

@@
 %%%%%%%%
-% CQVS %
+% CRS %
 %%%%%%%%
@@
 
-\title{Transient Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS}
+\title{Transient Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Rotators from TESS}
 
@@
 \accepted{---}
-\shorttitle{Four Years of CQVs}
+\shorttitle{Four Years of CRs}
 
@@
 \begin{abstract}
-  Complex quasiperiodic variables (CQVs) are low-mass
-  pre-main-sequence stars with nearly periodic optical modulation.
-  The modulation is probably caused by eclipsing clumps of dust or gas
-  in orbit at the Keplerian corotation radius.  Here, we
-  report new CQVs discovered in TESS short-cadence data collected
-  between 2018~July and 2022~September.  Our search of
-  \nstarssearched\ K and M dwarfs with $T$$<$16 and $d$$<$150\,pc
-  yielded \ngoods\ high-quality CQVs.  Most of these discoveries are
-  new, and they include the brightest ($T$$\approx$9.5), closest
-  ($d$$\approx$20\,pc), and oldest ($\approx$200\,Myr) examples of
-  this class of object currently known.  A few objects are outliers:
-  LP 12-502 for instance showed a ``dip complex'' with a period and
-  duration that were fixed over 1,500 cycles, but in detail, this
-  system exhibited between four and eight local minima per cycle, and
-  at times also displayed multiple periods simultaneously.  We
-  demonstrate that transient corotating material is the most viable
-  explanation for this class of object, and present evidence
-  supporting the hypothesis that this material is sculpted by stellar
-  magnetic fields dominated by high order multipoles.  We expect that
-  our sample will facilitate future efforts aimed at connecting CQVs
-  to the broader contexts of star, disk, and perhaps even exoplanet
-  evolution. 	
+  %Complex rotators (CRs) are low-mass
+  %pre-main-sequence stars with nearly periodic optical modulation.
+  %The modulation is probably caused by eclipsing clumps of dust or gas
+  %in orbit at the Keplerian corotation radius.  Here, we report new
+  %CRs discovered in TESS short-cadence data collected between
+  %2018~July and 2022~September.  Our search of \nstarssearched\ K and
+  %M dwarfs with $T$$<$16 and $d$$<$150\,pc yielded \ngoods\
+  %high-quality CRs.  Most of these discoveries are new, and they
+  %include the brightest ($T$$\approx$9.5), closest
+  %($d$$\approx$20\,pc), and oldest ($\approx$200\,Myr) examples of
+  %this class of object currently known.  A few objects are outliers:
+  %LP 12-502 for instance showed a ``dip complex'' with a period and
+  %duration that were fixed over 1,500 cycles, but in detail, this
+  %system exhibited between four and eight local minima per cycle, and
+  %at times also displayed multiple periods simultaneously.  We
+  %demonstrate that transient corotating material is the most viable
+  %explanation for this class of object, and present evidence
+  %supporting the hypothesis that this material is sculpted by stellar
+  %magnetic fields dominated by high order multipoles.  We expect that
+  %our sample will facilitate future efforts aimed at connecting CRs
+  %to the broader contexts of star, disk, and perhaps even exoplanet
+  %evolution. 	
+  % % JNW alternate:
+  Complex rotators (CRs) are low-mass pre-main-sequence stars with
+  light curves characterized by periods of 0.2--2 days, amplitudes of
+  a few percent, and slowly-evolving sharp features.  The sharp
+  features might be caused by eclipsing clumps of dust or gas orbiting
+  at the corotation radius.  To improve our understanding of these
+  enigmatic stars, we conducted a survey for CRs using TESS
+  short-cadence data collected between 2018~July and 2022~September.
+  Our search of \nstarssearched\ K and M dwarfs with $T$$<$16 and
+  $d$$<$150\,pc yielded \ngoods\ high-quality CRs, most of which are
+  new discoveries.  Our sample includes the brightest
+  ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and oldest
+  ($\approx$200\,Myr) known CRs.  One of the new discoveries, LP
+  12-502, stands out for the complexity of its light curve --- with as
+  many as eight flux dips per cycle --- and the detail with which the
+  evolution in each dip's amplitude and phase can be tracked over
+  1{,}500 cycles.  We argue that corotating gas or dust remains the
+  most viable explanation for CRs. The gas or dust is probably
+  entrained by the star's magnetic field, and the sharp features may
+  result from a multipolar field topology, a hypothesis supported by
+  correspondences between the light curves of CRs and of two B stars
+  known to have strong multipolar magnetic fields.
 \end{abstract}
@@
 star for which the root cause of variability is only beginning to
-become clear: complex quasiperiodic variables (CQVs).  These objects
+become clear: complex rotators (CRs).  These objects
 are identified from their optical light curves, which show nearly
@@
 \citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z}.
-Some CQVs show up to eight dips per cycle.  Most CQVs are
+Some CRs show up to eight dips per cycle.  Most CRs are
 pre-main-sequence M dwarfs with ages of $\approx$5-150 million years
@@
 not show near-infrared excesses indicative of dusty disks, but the
-wavelength-dependent dip amplitudes of some CQVs is consistent with
+wavelength-dependent dip amplitudes of some CRs is consistent with
 reddening by dust
@@
 
-The sharp features of CQV light curves can have durations as short as
+The sharp features of CR light curves can have durations as short as
 5\% of the rotation period ($P_{\rm rot}$), which is too short to be
@@
 \citealt{2017AJ....153..152S}, Figures 37-41).  Thus, a
-``starspot-only'' scenario can be ruled out for many CQVs
+``starspot-only'' scenario can be ruled out for many CRs
 \citep{2017AJ....153..152S,2019ApJ...876..127Z,2021MNRAS.500.1366K}.
-Given that many CQVs cannot be explained by starspots alone, and
-working under the assumption that all CQVs share the same basic
+Given that many CRs cannot be explained by starspots alone, and
+working under the assumption that all CRs share the same basic
 physical scenario, we discard the ``starspot-only'' scenario.
@@
 fraction of the stellar radius as in the solar case, they would exist
-at distances of a few stellar radii.  A final possibility is that a thin
-optically-thick ring obscures a small portion of the stellar
-photosphere \citep{2019ApJ...876..127Z}.  Hot spots passing behind such a structure could produce
-sudden dips.  We do not favor this scenario due to the issues
-discussed in Appendix~\ref{app:ring}.
+at distances of a few stellar radii.  A final possibility is that a
+thin optically-thick ring obscures a small portion of the stellar
+photosphere \citep{2019ApJ...876..127Z}.  Hot spots passing behind
+such a ring could produce sudden dips.  We do not favor this scenario
+due to two issues discussed in Appendix~\ref{app:ring}.
 
@@
 opacity from gas, likely bound-free transitions in hydrogen or perhaps
-a molecular opacity.  However unambiguous evidence in support of any particular
-scenario has yet to be acquired.  Such evidence might include a
-spectroscopic detection of silicate 10\,$\mu$m dust absorption during
-a dip, or perhaps detection of transient Balmer-line excesses as a
-function of cycle phase, similar to observations made in systems such
-as AB~Dor \citep[see][]{1999ASPC..158..146C} or PTFO 8-8695
-\citep{2016ApJ...830...15J}.
-
-CQVs remain mysterious because they have been both hard to discover
-and hard to characterize.   They are hard to discover because they are
-rare: CQVs comprise $\approx$1\% of the youngest $\approx$1\% of M
+a molecular opacity.  However unambiguous evidence in support of any
+particular scenario has yet to be acquired.  Such evidence might
+include a spectroscopic detection of silicate 10\,$\mu$m dust
+absorption during a dip, or perhaps detection of transient Balmer-line
+excesses as a function of cycle phase, similar to observations made in
+systems such as AB~Dor \citep[see][]{1999ASPC..158..146C} or PTFO
+8-8695 \citep{2016ApJ...830...15J}.
+
+CRs remain mysterious because they have been both hard to discover and
+hard to characterize.   They are hard to discover because they are
+rare: CRs comprise $\approx$1\% of the youngest $\approx$1\% of M
 dwarfs \citep{2018AJ....155..196R}.  Out of the millions of stars
-monitored by K2 and TESS, about 50 CQVs have been reported to date
+monitored by K2 and TESS, about 50 CRs have been reported to date
 \citep{2016AJ....152..114R,2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2020AJ....160...86B,2022AJ....163..144G,2023ApJ...945..114P}.
-They have been hard to characterize because many of the known CQVs are
+They have been hard to characterize because many of the known CRs are
 relatively faint; the initial K2 discoveries
@@
 
-In this work, we aim to find bright and nearby CQVs, since these
+In this work, we aim to find bright and nearby CRs, since these
 objects will be the most amenable to detailed photometric and
@@
 Cycles 1-4).  We present our search methods in
-Section~\ref{sec:methods}, and the resulting CQV catalog in
-Section~\ref{sec:results}.  The observed evolution of many CQVs over a
+Section~\ref{sec:methods}, and the resulting CR catalog in
+Section~\ref{sec:results}.  The observed evolution of many CRs over a
 two-year baseline is described in Section~\ref{sec:evoln}, including a
@@
 
-Some comments on nomenclature are needed.  What we are calling CQVs
+Some comments on nomenclature are needed.  What we are calling
+``complex rotators''
+\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
 have also been called ``transient flux dips'', ``persistent flux
-dips'', ``scallop shells'', ``batwings'', \citep{2017AJ....153..152S}
-``complex rotators'',
-\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P},
-and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  The
-CQVs should not be conflated with ``dippers'', which are classical T
-Tauri stars with infrared excesses, and which show large-amplitude
-variability linked to obscuring inner disk structures and accretion
-hot spots \citep{2014AJ....147...82C,2021ApJ...908...16R}.  The
-phenomenology and stellar properties of CQVs and dippers are
-quite different (though see Sections~\ref{subsec:irexcess}
-and~\ref{subsec:discdippers}).  Despite the cost of introducing yet
-another naming standard, we prefer to use a single empirically
-descriptive name that highlights these objects as variable stars, and
-not ``rotators''.  We also prefer a nomenclature that reflects how the
-dips and peaks of these stars always appear to be transient 
-when observed over timescales exceeding hundreds of cycles.  ``Complex
-quasiperiodic variable'' meets these requirements, for the time being.
+dips'', and ``scallop shells'' by \citet{2017AJ....153..152S}, or more
+generally ``complex periodic variables'' by
+\citet{2023MNRAS.518.2921K}.  The CRs should not be conflated with
+``dippers'', which are classical T Tauri stars with infrared excesses,
+and which show large-amplitude variability linked to obscuring inner
+disk structures and accretion hot spots
+\citep{2014AJ....147...82C,2021ApJ...908...16R}.  The phenomenology
+and stellar properties of CRs and dippers are quite different (though
+see Sections~\ref{subsec:irexcess} and~\ref{subsec:discdippers}).
+While we considered other possibilities, we ultimately concluded that
+``complex rotator'' correctly draws attention to the fact that
+rotation will play a fundamental role in explaining these objects, and
+that their key defining feature is the complexity of their optical
+light curves relative to the quasi-sinusoidal modulations of
+starspots.
 
@@
 	\caption{
-		{\bf Complex quasiperiodic variables (CQVs)}:
-    {\it Top:} Phase-folded TESS light curves of three CQVs.  Each panel shows
+		{\bf Complex rotators (CRs)}:
+    {\it Top:} Phase-folded TESS light curves of three CRs.  Each panel shows
     the average of the data accumulated over one month.
     Gray circles are raw 2-minute data; black
-    circles are binned to 300 points per cycle.  The periods in hours
+    circles are binned to 300 points per cycle.  The period in hours
     is printed in the
@@
 
-\subsection{CQV discovery}
+\subsection{CR discovery}
 \label{subsec:discoverymethods}
 
-Previous methods for finding CQVs have included visually examining
+Previous methods for finding CRs have included visually examining
 stars in young clusters
@@
 The dip counting technique aims to count sharp local minima in
-phase-folded light curves.  CQVs will preferably have at least three
+phase-folded light curves.  CRs will preferably have at least three
 such minima in order to be distinct from false positives such as
@@
 were chosen during testing based on their ability to correctly
-re-identify a large fraction ($>$90\%) of previously known CQVs, while also being
+re-identify a large fraction ($>$90\%) of previously known CRs, while also being
 able to consistently reject common false positives such as rapidly
@@
 visually labeled each star based on its morphology (including e.g.
-eclipsing binary, CQV, RS CVn, or cataclysmic variable).  CQVs that
+eclipsing binary, CR, RS CVn, or cataclysmic variable).  CRs that
 were observed in multiple sectors had their light curves stitched
@@
 		\caption{
-			{\bf Validation plots used to  label CQVs}.  The complete figure
+			{\bf Validation plots used to  label CRs}.  The complete figure
 			set, with one image per sector for each of the \nallcands\
@@
 (Section~\ref{subsec:fourier}) techniques were consistent with
-expectations for CQVs by assembling the data shown in
-Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CQV if at least
+expectations for CRs by assembling the data shown in
+Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CR if at least
 one TESS sector showed what we viewed as the unambiguous signatures of
@@
 oddly-shaped dips; relative stability over a timescale of 30\,days).
-We independently noted stars that we thought could be CQVs, but that
+We independently noted stars that we thought could be CRs, but that
 were more ambiguous.
@@
 pipeline were 5:1, with \nuniqdipflagged\ unique stars flagged, and
-about 20\% being labeled either ``good'' or ``possible'' CQVs.  The
+about 20\% being labeled either ``good'' or ``possible'' CRs.  The
 Fourier analysis was not amenable to calculating a similar
@@
 variability search; its results are also being used for analyses on
-topics other than CQVs.
+topics other than CRs.
 
@@
 We estimated the stellar ages by making probabilistic spatial and
-kinematic associations between the CQVs and known clusters in the
+kinematic associations between the CRs and known clusters in the
 solar neighborhood.  For most stars in our sample, we did this using
@@
 		\caption{
-      {\bf CQVs found in the TESS 2-minute data.}
+      {\bf CRs found in the TESS 2-minute data.}
       Phased TESS light curves over one month are shown for \ngoods\
-      CQVs in the high quality sample.  Gray are raw 2-minute data;
+      CRs in the high quality sample.  Gray are raw 2-minute data;
       black bins to 300 points per cycle.  Objects are ordered such
@@
 
-\subsection{CQV catalog}
+\subsection{CR catalog}
 \label{sec:catalog}
@@
 which demonstrated what we viewed as unambiguous characteristics of
-the CQV phenomenon in at least one TESS sector.  The classification of
-\nmaybes\ CQV candidates was ambiguous, and the \ndebunked\ remaining
+the CR phenomenon in at least one TESS sector.  The classification of
+\nmaybes\ CR candidates was ambiguous, and the \ndebunked\ remaining
 objects were false positives that we discuss below.  The
@@
 additional data from TESS or other instruments could help resolve the
-classification of the ambiguous cases.   Of the \ncqvsnodebunked\ CQVs
-and candidate CQVs, \nbothdipfourier\ were found using both the
+classification of the ambiguous cases.   Of the \ncqvsnodebunked\ CRs
+and candidate CRs, \nbothdipfourier\ were found using both the
 dip-counting and Fourier techniques, \nyesdipnofourier\ were found
@@
 The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
-\ngoods\ CQVs.  The objects are sorted first in order of the number of
+\ngoods\ CRs.  The objects are sorted first in order of the number of
 TESS 120-second cadence sectors in which they clearly demonstrated the
-CQV phenomenon, and secondarily by descending brightness.  The top
+CR phenomenon, and secondarily by descending brightness.  The top
 five objects by this metric are TIC~300651846 ($T$$=$13.5, 12
@@
 ($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5 sectors); and
-TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest five CQVs span
+TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest five CRs span
 9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
@@
 
-Of our \ncqvsnodebunked\ confirmed and candidate CQVs,
+Of our \ncqvsnodebunked\ confirmed and candidate CRs,
 \nnotfieldbanyan\ were associated with a nearby moving group or open
@@
 in Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  The
-most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CQVs
+most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CRs
 were also identified in the Argus association
@@
 various guest investigators.  Given the $\lesssim$$10\%$ completeness
-of TESS beyond 100\,pc, there may be many more CQVs in Sco-Cen that
+of TESS beyond 100\,pc, there may be many more CRs in Sco-Cen that
 remain to be discovered.
@@
 association, we were not able to confidently associate either star
-with any young groups.  Both do seem to show the CQV signal over
+with any young groups.  Both do seem to show the CR signal over
 multiple TESS sectors, and both are photometrically elevated relative
@@
 
-Our search confirms that the CQV phenomenon persists for at least
+Our search confirms that the CR phenomenon persists for at least
 $\approx$150\,Myr.  Table~\ref{tab:thetable} includes three
-$\approx$150\,Myr CQVs in AB~Dor \citep{2015MNRAS.454..593B}, a
-$\approx$112\,Myr old Pleiades CQV \citep{2015ApJ...813..108D}, and a
+$\approx$150\,Myr CRs in AB~Dor \citep{2015MNRAS.454..593B}, a
+$\approx$112\,Myr old Pleiades CR \citep{2015ApJ...813..108D}, and a
 similarly-aged Psc-Eri member \citep{2020A&A...639A..64R}.  To our
@@
 \citealt{2015MNRAS.454..593B}) was the previous record-holder for the
-oldest-known CQV \citep{2019ApJ...876..127Z,2022AJ....163..144G}; at
-least one unambiguous CQV (EPIC~211070495) and a few other candidates
+oldest-known CR \citep{2019ApJ...876..127Z,2022AJ....163..144G}; at
+least one unambiguous CR (EPIC~211070495) and a few other candidates
 were also previously known in the Pleiades
@@
 
-The upper age limit for CQVs may even pass 200\,Myr, based on the
+The upper age limit for CRs may even pass 200\,Myr, based on the
 candidate membership of TIC~294328887 in the Carina Near moving group
@@
 
-Most CQVs in our catalog did not show infrared excesses in the
+Most CRs in our catalog did not show infrared excesses in the
 $W1$-$W4$ bands, which is typical for this class of object
@@
 44\,hr respectively.  In our initial labeling, we labeled both as
-``ambiguous'' CQVs because the dips in their light curves did not show
-the rigid periodicity typical of CQVs;  their periods were also
+``ambiguous'' CRs because the dips in their light curves did not show
+the rigid periodicity typical of CRs;  their periods were also
 relatively long.  However, inspection of further sectors clarified
@@
 \citet{2022ApJS..263...14C}; we agree with their designation, and
-label it an ``impostor'' CQV in Table~\ref{tab:thetable}.  TIC
+label it an ``impostor'' CR in Table~\ref{tab:thetable}.  TIC
 57830249 (TWA~33) also has previously detected 1.3\,mm continuum
@@
 being present.  It is also a dipper.  Section~\ref{subsec:discdippers}
-highlights plausible evolutionary connections between CQVs and dippers
+highlights plausible evolutionary connections between CRs and dippers
 in light of these ``misclassifications'' .
@@
 % a $P$=38\,hr singly-eclipsing binary, except with additional
-% substructure during each eclipse that resembles the CQV phenomenon
+% substructure during each eclipse that resembles the CR phenomenon
 % more than any other variability of which we are aware.  TIC~289840926
 % ($\beta$~Pic moving group, $P$=4.8\,hr), shows what we believe is a
-% clear CQV signal, but has no definitive evidence for a large, dusty
+% clear CR signal, but has no definitive evidence for a large, dusty
 % disk.  TIC~244161191 (TOI-278), in Columba, also has no definitive
 % evidence for a large disk.  It is however ``multi-periodic''---in
-% addition to the 7.17\,hr CQV signal, this source shows a superposed
+% addition to the 7.17\,hr CR signal, this source shows a superposed
 % 8.39\,hr sinusoidal signal, probably from an unresolved neighboring
@@
 		\caption{
-			{\bf Properties of CQVs identified by our search}.
-      CQVs are mostly pre-main-sequence M dwarfs, younger than
+			{\bf Properties of CRs identified by our search}.
+      CRs are mostly pre-main-sequence M dwarfs, younger than
       $\approx$150 Myr, with rotation periods faster than
-      $\approx$1\,day.  The \ngoods\ bona fide CQVs in
+      $\approx$1\,day.  The \ngoods\ bona fide CRs in
       Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
-      ambiguous CQV candidates are light blue circles.  Unresolved
+      ambiguous CR candidates are light blue circles.  Unresolved
       binaries are flagged either if the Gaia DR3 radial velocity
@@
       searched stars.  The lower-left panel compares the
-      rotation--color distribution of CQVs against the rotation
+      rotation--color distribution of CRs against the rotation
       periods of K and M dwarfs in the Pleiades from
@@
       derived corotation radii $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in
-      units of stellar radii against the measured CQV periods, in
+      units of stellar radii against the measured CR periods, in
       units of hours.  Ages in the final panel are known from cluster
@@
 The main types of binaries of interest in this work were those that
-were unresolved, because they could confuse our understanding of CQVs.
+were unresolved, because they could confuse our understanding of CRs.
 For instance, unresolved binaries might produce multiple photometric
 signals and hinder our ability to correctly identify the star hosting
-the CQV signal.  Unresolved binaries could also bias photometric magnitude
+the CR signal.  Unresolved binaries could also bias photometric magnitude
 and color measurements, which would affect our stellar parameter
@@
 ``radial velocity error'' as a function of stellar color for all
-\ncqvsnodebunked\ CQVs and candidate CQVs.  Since this quantity
+\ncqvsnodebunked\ CRs and candidate CRs.  Since this quantity
 represents the standard deviation of the non-published Gaia RV time
@@
 flag sources with excess astrometric noise.  This threshold was met
-for \ngoodhighruwe/\ngoods\ high-quality CQVs;
+for \ngoodhighruwe/\ngoods\ high-quality CRs;
 \nmaybehighruwe/\nmaybes\ of the ambiguous ones had this
@@
 \citep[e.g.][]{2022MNRAS.513.5270P}.  If we had instead required
-RUWE$_{\rm DR3}$ $>$ 1.4, \ngoodweakruwe/\ngoods\ high-quality CQVs
+RUWE$_{\rm DR3}$ $>$ 1.4, \ngoodweakruwe/\ngoods\ high-quality CRs
 and \nmaybeweakruwe/\nmaybes\ of the ambiguous sample would have been
@@
 non\_single\_star} column that flagged eclipsing, astrometric, and
-spectroscopic binaries.  None of the stars in our CQV sample were
+spectroscopic binaries.  None of the stars in our CR sample were
 identified as possible binaries in this column.
@@
 periods.  We also attempted to disentangle the two signals by
-subtracting the mean CQV signal over each sector, and then repeating
+subtracting the mean CR signal over each sector, and then repeating
 the phase-dispersion minimization analysis.  The results of this effort
@@
 different from the primary period.  This process yielded
-\ngoodmultperiodflag/\ngoods\ high-quality CQVs with secondary
+\ngoodmultperiodflag/\ngoods\ high-quality CRs with secondary
 periods; \nmaybemultperiodflag/\nmaybes\ of the ambiguous sample met
-the same criterion.  Of the \ngoodhighruwe\ good CQVs with RUWE$_{\rm
+the same criterion.  Of the \ngoodhighruwe\ good CRs with RUWE$_{\rm
 DR3}$ $>$ 2, \ngoodruweandmultperiod\ also showed secondary periods in
 the TESS light curves.  Considering the weaker threshold of RUWE$_{\rm
-DR3}$ $>$ 1.4, \ngoodweakruweandmultperiod/\ngoodweakruwe\ such CQVs
+DR3}$ $>$ 1.4, \ngoodweakruweandmultperiod/\ngoodweakruwe\ such CRs
 showed secondary TESS periods.
@@
 information into a single bitwise column.  We discuss possible
-connections between binarity and the CQV phenomenon in
+connections between binarity and the CR phenomenon in
 Section~\ref{subsec:discbinary}.
 
-\section{CQV evolution}
+\section{CR evolution}
 \label{sec:evoln}
@@
 		\caption{
-			{\bf CQVs keep their periods but change their shapes.}
-			Out of the \ngoods\ CQVs in Figure~\ref{fig:cqvs}, 32 had
+			{\bf CRs keep their periods but change their shapes.}
+			Out of the \ngoods\ CRs in Figure~\ref{fig:cqvs}, 32 had
 			120-second cadence TESS data available for a baseline of at
@@
 
-Figure~\ref{fig:evoln} shows ``before'' and ``after'' views of 27 CQVs
+Figure~\ref{fig:evoln} shows ``before'' and ``after'' views of 27 CRs
 for which TESS 120-second cadence observations were available at least
 two years apart.  Such a baseline was available for 32 of the
-confirmed \ngoods\ CQVs in our catalog; for plotting purposes we show
+confirmed \ngoods\ CRs in our catalog; for plotting purposes we show
 the brightest 27.  We have phased each sector to its own local minimum
@@
 show clear signs of
-the CQV phenomenon in one sector, and marginal or non-existent signs
+the CR phenomenon in one sector, and marginal or non-existent signs
 in the other.  While there is subjectivity in this assessment, to our
@@
 based on the shape evolution between Sectors 13 and 39, it is a
-CQV.  Based on the fraction of sources overall that ``turned off'',
-the observed shape evolution implies that CQVs have an on-off duty cycle of
+CR.  Based on the fraction of sources overall that ``turned off'',
+the observed shape evolution implies that CRs have an on-off duty cycle of
 $\approx$75\%.  This type of correction is worth including in
-population-level estimates of how intrinsically common CQVs are in the
+population-level estimates of how intrinsically common CRs are in the
 low-mass stellar population \citep[e.g.][]{2022AJ....163..144G}.
@@
 
-\subsection{Typical and extreme CQVs}
+\subsection{Typical and extreme CRs}
 \label{subsec:extreme}
@@
 Figure~\ref{fig:catalogscatter} shows derived stellar properties for
-our CQV catalog, and compares the CQVs against both the target star
+our CR catalog, and compares the CRs against both the target star
 sample (top panels), and against stars in the Pleiades
-\citep{2016AJ....152..114R}.  Typical CQV masses span
+\citep{2016AJ....152..114R}.  Typical CR masses span
 0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This mass and
@@
 classes.  In terms of their rotation rates relative to the Pleiades,
-the CQVs are among the more rapidly rotating half of M dwarfs.
-
-The closest CQV in our catalog is DG~CVn (TIC~368129164;
+the CRs are among the more rapidly rotating half of M dwarfs.
+
+The closest CR in our catalog is DG~CVn (TIC~368129164;
 $d$$=$18\,pc), a member of AB Dor.  To our knowledge, this work is the
-first time that it has been noted as a CQV.  The three brightest CQVs
+first time that it has been noted as a CR.  The three brightest CRs
 are DG~CVn ($T$=9.3), TIC~405754448 ($T$=9.6), and TIC~167664935
@@
 small number of sub-stellar mass objects in our target sample, future
-studies of brown dwarf photometric variability might also yield CQVs,
+studies of brown dwarf photometric variability might also yield CRs,
 though there could be degeneracies in interpretation with planetary
@@
 
-\subsection{CQVs and binarity}
+\subsection{CRs and binarity}
 \label{subsec:discbinary}
@@
 In Section~\ref{subsec:binarity}, we found that a significant fraction
-of the CQVs show indications of unresolved binarity.  Excess noise
+of the CRs show indications of unresolved binarity.  Excess noise
 above the Gaia single-source astrometric model is common
-(\ngoodhighruwe/\ngoods\ high-quality CQVs with RUWE$_{\rm DR3}$$>$2),
+(\ngoodhighruwe/\ngoods\ high-quality CRs with RUWE$_{\rm DR3}$$>$2),
 as is the presence of multiple periods in the TESS light curves
@@
 always accompanied by multiple detectable TESS periods
-(\ngoodruweandmultperiod/\ngoodhighruwe\ high-quality CQVs).  The
+(\ngoodruweandmultperiod/\ngoodhighruwe\ high-quality CRs).  The
 latter point strongly corroborates the idea that most sources with
@@
 $0.15$-$0.30$\,$M_\odot$ M dwarfs.  The multiplicity fraction in our
-CQV sample seems either consistent or perhaps marginally higher than
+CR sample seems either consistent or perhaps marginally higher than
 the field fraction.  This could plausibly be understood in a physical
 framework in which the presence of intermediate-separation binaries
-causes early disk dispersal, freeing the star to contract.  The CQV
+causes early disk dispersal, freeing the star to contract.  The CR
 phenomenon seems to require rapid rotation; thus if binary systems
 tend to produce more rapidly rotating stars, we would expect a sample
-of CQVs to have a larger binary fraction than the field.
-
-\subsubsection{Do K dwarf CQVs exist?}
+of CRs to have a larger binary fraction than the field.
+
+\subsubsection{Do K dwarf CRs exist?}
 \label{subsec:massive}
 
-To date, the only stars reported to show the CQV phenomenon are M
+To date, the only stars reported to show the CR phenomenon are M
 dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
 \citep{2017AJ....153..152S,2022AJ....163..144G}.  However the two most
-massive CQVs in our sample, TIC~405754448 and TIC~405910546, appear to
+massive CRs in our sample, TIC~405754448 and TIC~405910546, appear to
 have masses of $\approx$0.82\,$M_\odot$ and $\approx$0.60\,$M_\odot$
@@
 suggestive of an eclipsing binary.  Independently, TIC~405910546 was
-one of only \nrvscatterflag\ CQVs flagged with a Gaia DR3 radial
+one of only \nrvscatterflag\ CRs flagged with a Gaia DR3 radial
 velocity scatter exceeding 20\,\kms.  Combined, these factors suggest
@@
 observed 12.9\,hr signal with such a flux deficit, but not impossible.
-While both of these objects suggest that the CQV phenomenon may extend
+While both of these objects suggest that the CR phenomenon may extend
 up in mass to pre-main-sequence K dwarfs, more data are needed to
@@
 
-\subsubsection{An astrophysical CQV false positive: TIC~435903839}
+\subsubsection{An astrophysical CR false positive: TIC~435903839}
 
 We originally classified TIC~435903839, with RUWE$_{\rm DR3}$=17.7, as
-an ``ambiguous'' CQV with a 10.8\,hr period, because this period
+an ``ambiguous'' CR with a 10.8\,hr period, because this period
 minimized the dispersion in the phase-folded light curve.  More
@@
 P_1^{-1})^{-1}$ of 10.8\,hr.  This is a novel false positive scenario
-for CQVs: two rapidly-rotating stars with near-integer ratios of
+for CRs: two rapidly-rotating stars with near-integer ratios of
 rotation periods.  The beat between the two rotation signals produces
-the apparent CQV signal.  Such false positives can be excluded through
+the apparent CR signal.  Such false positives can be excluded through
 careful accounting of all peaks in a periodogram.  For instance,
@@
 
-\subsubsection{Multiple CQVs in the same system: TIC~425937691 and TIC~142173958}
+\subsubsection{Multiple CRs in the same system: TIC~425937691 and TIC~142173958}
 
 TIC~142173958 and TIC~425937691 both show evidence for two separate
-CQV signals in their TESS light curves.  For TIC~142173958, the
+CR signals in their TESS light curves.  For TIC~142173958, the
 signals are at 11.76\,hr and 12.84\,hr.  For TIC~425937691, they are
@@
 signals and elevated RUWEs, they are probably unresolved binaries
-consisting of two independent CQVs.  Recent work has shown that the
+consisting of two independent CRs.  Recent work has shown that the
 orbits of binaries closer than $\lesssim$700 AU tend to be aligned
 with their planetary systems \citep[e.g.][]{2022AJ....163..207C}.  If
-we assume that observing CQV variability similarly requires near
+we assume that observing CR variability similarly requires near
 edge-on viewing geometries, then we might expect a sufficiently close
-binary with one CQV to also have another, since the spin axes in
+binary with one CR to also have another, since the spin axes in
 sufficiently close binaries would tend to be aligned.  In this
@@
 
-\subsection{CQVs are quasiperiodic}
-
-A periodic signal repeats exactly; the CQVs do not
+\subsection{CRs are quasiperiodic}
+
+A periodic signal repeats exactly; the CRs do not
 (Figure~\ref{fig:evoln}).  While their periods appear to remain
@@
 ``persistent'' {\it vs.} ``transient'' flux dip distinction described
-by \citet{2017AJ....153..152S}, since all CQV dips seem to be
+by \citet{2017AJ....153..152S}, since all CR dips seem to be
 transient over timescales of more than 1{,}000 cycles
@@
 able to explore all phase angles with equal weight.  LP 12-502, and
-perhaps other CQVs, seem to have preferred phases.  For LP 12-502, all
+perhaps other CRs, seem to have preferred phases.  For LP 12-502, all
 of the dips happen over phases corresponding to only two thirds of the
@@
 
-Examining Figure~\ref{fig:cqvs}, it is not obvious whether CQVs as a
+Examining Figure~\ref{fig:cqvs}, it is not obvious whether CRs as a
 whole show any preference for sharper ingresses, or sharper egresses.
@@
 
-We believe that the most likely scenarios to explain CQVs are either
+We believe that the most likely scenarios to explain CRs are either
 the dust clump scenario or the prominence scenario
@@
 A clear link between the dense gas clumps (prominences) that likely
-exist around rapidly rotating low-mass stars and the CQV phenomenon
+exist around rapidly rotating low-mass stars and the CR phenomenon
 has yet to be made.  A simple visual examination of the TESS light
@@
 \citet{2019MNRAS.482.2853J}--AB~Dor, Speedy~Mic, LQ Lup, HK Aqr, and
-V374 Peg--revealed no obvious CQV behavior, though all show
+V374 Peg--revealed no obvious CR behavior, though all show
 differential evolution, and Speedy~Mic shows two closely-spaced
 periods and a strong beat.  Spectroscopically observable prominences
-do not imply photometric CQV-like dips.
+do not imply photometric CR-like dips.
 
@@
 
-CQVs show broadband flux variations that can be 1-2$\times$ deeper in
+CRs show broadband flux variations that can be 1-2$\times$ deeper in
 the blue than in the red
@@
 study to be conducted to determine to what degree the observed
-chromaticities in CQVs match, or do not match, expectations from
+chromaticities in CRs match, or do not match, expectations from
 radiative transfer.  This issue has a key ability to resolve the
-question of whether the CQVs are explained by dust or by gas, which
+question of whether the CRs are explained by dust or by gas, which
 has bearing on whether the material producing the dips is coming from
@@
 Independent of the microphysical basis for gas absorption, the
-observed lifetime of the CQV phenomenon could provide another
+observed lifetime of the CR phenomenon could provide another
 dimension to discern between the gas vs.~dust clump scenarios.
@@
 \citet{2022AJ....164...80R} and references therein, it seems plausible
-that CQV occurrence decreases in time, bottoming to zero well before
+that CR occurrence decreases in time, bottoming to zero well before
 the $\approx$700\,Myr age of Praesepe.  This is odd in the context of
@@
 Given the known abundance of small planets around M dwarfs, it is
-tempting to try to interpret features of the CQV light curves in terms
+tempting to try to interpret features of the CR light curves in terms
 of the possible presence of either close-in exoplanets or close-in
@@
 be massive enough to remain in orbit, while stochastically ejecting
-material.  For most CQVs (Figure~\ref{fig:evoln}), the data seem to be
+material.  For most CRs (Figure~\ref{fig:evoln}), the data seem to be
 in tension with this expectation because the relative spacing between
@@
 %material.  An analogous system would be K2-22
-%\citep{2015ApJ...812..112S}.  For most CQVs (Figure~\ref{fig:evoln}),
+%\citep{2015ApJ...812..112S}.  For most CRs (Figure~\ref{fig:evoln}),
 %the data are in tension with this expectation.  A second issue is that
@@
 %It is certainly possible that exoplanets or exoplanetesimals could end
-%up being connected to the CQV phenomenon, for instance as a possible
+%up being connected to the CR phenomenon, for instance as a possible
 %sources for the occulting dust or gas.  However for the time being,
-%none of the CQVs that we have studied in this work show clear evidence
+%none of the CRs that we have studied in this work show clear evidence
 %for the nearby planets that we statistically expect should be common.
@@
 
-In identifying the two candidate CQVs with outlying SEDs
+In identifying the two candidate CRs with outlying SEDs
 (TICs~193136669 and TIC~57830249; Section~\ref{subsec:irexcess}), we
@@
 ultimately concluded that these sources are dippers.  This episode
-suggests that there could be overlap between CQVs and dippers.  It is
+suggests that there could be overlap between CRs and dippers.  It is
 also worth emphasizing that our labeling of e.g.~TIC~57830249 was
@@
 strong changes in a star's optical variability.  It is reasonable to
-imagine connections between CQVs and dippers: both classes of object
+imagine connections between CRs and dippers: both classes of object
 can show transient flux dips that are relatively narrow in duration.
 The dips in both are probably associated with clumps of dust or gas.
-However the CQV dips are generally more periodic and less deep than
+However the CR dips are generally more periodic and less deep than
 those of dippers; they also display far less transience over
-timescales of a few to tens of cycles.  The CQVs also have
+timescales of a few to tens of cycles.  The CRs also have
 demonstrably less dust than (most) dipper stars.  At a population
-level, the CQV stars are also older.  A common mystery between the
-CQVs and dippers, in our own estimation, is how exactly the {\it
+level, the CR stars are also older.  A common mystery between the
+CRs and dippers, in our own estimation, is how exactly the {\it
 narrowness} of the dust clumps is produced.  It is not unreasonable to
@@
 %The interval of half a cycle period could be significant in the
-%context of CQVs for two reasons.  The first is that for material on a
+%context of CRs for two reasons.  The first is that for material on a
 %circular orbit viewed edge-on, a half-cycle corresponds to the
@@
 %the half-cycle also corresponds to the interval over which half of the
-%star's surface is visible.  Of the CQVs in Figures~\ref{fig:cqvs}
+%star's surface is visible.  Of the CRs in Figures~\ref{fig:cqvs}
 %and~\ref{fig:evoln}, a fraction that seems greater than random might
@@
 %
-%One set of CQVs shows ``CQV behavior'' (some form of dip complex), but
+%One set of CRs shows ``CR behavior'' (some form of dip complex), but
 %which only lasts for half of any given cycle.  TIC~206544316 (Sector
@@
 %
-%An independent set of CQVs exhibits small dips roughly half a cycle
+%An independent set of CRs exhibits small dips roughly half a cycle
 %after large dips; it is tempting to label the small dips secondary
@@
 %In general however, it is challenging to interpret the significance of
-%the potential ``half-period regularities'';  the CQVs exhibit such a
+%the potential ``half-period regularities'';  the CRs exhibit such a
 %wide range of variability that for seemingly any regularity one might
 %posit, it is easy to come up with counter-example objects which do not
-%follow the trend.  In other words, these half-cycle CQVs could simply
+%follow the trend.  In other words, these half-cycle CRs could simply
 %be a product of the human tendency to pattern match.
@@
       high order multipoles.  The bottom row compares the latter
-      systems against the ``best-matching'' CQV light curves, selected
-      by eye from Figure~\ref{fig:cqvs}.  CQVs have light curves that
+      systems against the ``best-matching'' CR light curves, selected
+      by eye from Figure~\ref{fig:cqvs}.  CRs have light curves that
       are visually similar to the topologically complex magnetic B
@@
 transit depth to an effective cloud radius, $R_{\rm cloud}$.  For most
-CQVs in Figure~\ref{fig:cqvs}, this yields $\approx$2-20\,$R_\oplus$.
+CRs in Figure~\ref{fig:cqvs}, this yields $\approx$2-20\,$R_\oplus$.
 A minimum constraint on the number density follows by requiring the
@@
 yr}^{-1}$.  Considered cumulatively over the $\approx$$10^8$ years for
-which the CQV phenomenon is observed, this yields a cumulative moved
+which the CR phenomenon is observed, this yields a cumulative moved
 dust mass of $10^{-4}\,M_\oplus$, of order the Solar System's asteroid
@@
 \citet{2017AJ....153..152S} previously noted a possible connection
-between the CQVs and rapidly rotating magnetic B stars such as
+between the CRs and rapidly rotating magnetic B stars such as
 $\sigma$~Ori~E, which can have circumstellar gas clouds trapped in
@@
 
-An argument against the connection between CQVs and the $\sigma$~Ori~E
+An argument against the connection between CRs and the $\sigma$~Ori~E
 analogs is that the light curve of $\sigma$~Ori~E is much simpler than
@@
 Reviewing the literature, we learned that recent TESS light curves of
-these two B stars appear surprisingly similar to the CQV light curves
+these two B stars appear surprisingly similar to the CR light curves
 \citep{2020pase.conf...46M}.  The middle row of Figure~\ref{fig:bstar}
 shows the phased TESS light curves for these two outlying magnetic B
-stars, with by-eye ``best matching'' CQVs shown underneath for comparison.  The
+stars, with by-eye ``best matching'' CRs shown underneath for comparison.  The
 number of dips per cycle, the shapes of the dips, and the dip depths
@@
 In this work, we searched 120-second cadence TESS data collected from
-2018 July to 2022 September for complex quasiperiodic variables
-(CQVs).  The target stars were \nstarssearched\ K and M dwarfs within
+2018 July to 2022 September for complex rotators
+(CRs).  The target stars were \nstarssearched\ K and M dwarfs within
 150\,pc.  The selection function was $>$$80\%$ complete within 30\,pc,
@@
 quasiperiodic behavior over at least one TESS sector.  These \ngoods\
-bona fide CQVs are listed in Table~\ref{tab:thetable}.  This table also
-includes an additional \nmaybes\ ambiguous CQVs, whose designation is
+bona fide CRs are listed in Table~\ref{tab:thetable}.  This table also
+includes an additional \nmaybes\ ambiguous CRs, whose designation is
 less certain, and \ndebunked\ impostors.  We inferred ages for all but
@@
 over field stars.  Previous work however has shown that $\approx$1-3\%
-of M dwarfs younger than $\approx$100\,Myr show the CQV phenomenon
+of M dwarfs younger than $\approx$100\,Myr show the CR phenomenon
 \citep{2016AJ....152..114R,2022AJ....163..144G}.
 
-Analyzing the TESS light curves and stellar properties of our CQVs, we
+Analyzing the TESS light curves and stellar properties of our CRs, we
 draw the following conclusions.
@@
 	%
-    \item CQVs are quasiperiodic.  The mean periods remain fixed over
+    \item CRs are quasiperiodic.  The mean periods remain fixed over
       the $>$1{,}000-cycle baseline of available observations; but the
@@
   %
-    \item The same CQV can show multiple periods simultaneously.  LP
+    \item The same CR can show multiple periods simultaneously.  LP
       12-502, for instance, showed dips with four distinct periods
@@
   %
-    \item CQVs evolve over timescales that are both secular
+    \item CRs evolve over timescales that are both secular
       ($>$100\,cycles) and impulsive ($<$1 cycle).  Dip growth seems
@@
   %
-    \item The CQV phenomenon persists for $\gtrsim$150\,Myr, based on
-      the existence of multiple CQVs in AB Dor, the Pleiades, and
+    \item The CR phenomenon persists for $\gtrsim$150\,Myr, based on
+      the existence of multiple CRs in AB Dor, the Pleiades, and
       Psc-Eri (Section~\ref{subsec:starprops}).  It may even extend to
-      200\,Myr, based on the one CQV we found in the Carina Near
+      200\,Myr, based on the one CR we found in the Carina Near
       moving group (TIC~294328887; $\approx$200\,Myr).  However the
-      lack of detected CQVs in the Hyades and Praesepe suggests that
+      lack of detected CRs in the Hyades and Praesepe suggests that
       the lifetime of the phenomenon is limited to the first few
@@
 	%
-    \item The on-off duty cycle for CQVs seems to be $\approx$$75$\%, based
-      on the fraction of bona fide CQVs that either turned on or turned
+    \item The on-off duty cycle for CRs seems to be $\approx$$75$\%, based
+      on the fraction of bona fide CRs that either turned on or turned
       off during TESS re-observations, two years after the initial
@@
   %
-    \item Most CQVs are M dwarfs with masses
+    \item Most CRs are M dwarfs with masses
       0.1-0.5\,$M_\odot$.  Two sources, TIC~405754448 and
@@
       limit.  However both are potentially binaries, and this may
-      confuse our ability to accurate identify the source of the CQV
+      confuse our ability to accurate identify the source of the CR
       signal (Section~\ref{subsec:massive}).  We encourage additional
@@
   %
-    \item Surprising analogs to the CQVs exist in magnetic B stars,
+    \item Surprising analogs to the CRs exist in magnetic B stars,
       but only those with multipolar field topologies.  Since most
       magnetic B stars have dipolar magnetic fields, this suggests
-      that the CQV dips and warps are similarly being sculpted by the
+      that the CR dips and warps are similarly being sculpted by the
       stellar magnetic fields, and that the magnetic fields themselves
@@
   %
-    \item The closest CQVs to the Sun are at distances of 15-20\,pc,
+    \item The closest CRs to the Sun are at distances of 15-20\,pc,
       and the brightest have $V$$\approx$12 ($J$$\approx$7.5).  We
-      have found most of them in this work, since our CQV sample was
-      $\gtrsim$80\% complete within 30\,pc.  The lack of CQVs in the
+      have found most of them in this work, since our CR sample was
+      $\gtrsim$80\% complete within 30\,pc.  The lack of CRs in the
       volume-complete $<$15\,pc sample of 0.1-0.3\,$M_\odot$ stars
@@
       frame images would yield a truly volume-limited selection
-      function, and would expand the CQV census by about a factor of
+      function, and would expand the CR census by about a factor of
       two within 50\,pc, and by a factor of ten within 100\,pc.
@@
 The distinction between gas or dust is important because it will
-clarify whether the CQV phenomenon is intrinsic, so that material
+clarify whether the CR phenomenon is intrinsic, so that material
 comes from the star, or extrinsic, so that it is sourced through some
@@
 
-In both the gas and dust scenarios, CQVs are preferentially viewed
+In both the gas and dust scenarios, CRs are preferentially viewed
 edge-on.  This implies that after correcting for the line-of-sight
@@
 rotate rapidly enough;][]{2022AJ....163..144G} could trap circumstellar
-material in the same way.  It also suggests that CQVs may
+material in the same way.  It also suggests that CRs may
 preferentially show transiting planets at larger distances than the
@@
 %\tabletypesize{\scriptsize}
-\tablecaption{Bona fide, candidate, and debunked complex quasiperiodic
-  variables from the TESS 2-minute data. {\bf For internal
-  review, full versions are available here
-  \url{https://www.dropbox.com/scl/fo/twn4s9ckbevf75jqhtoy1/h?rlkey=t5cn8cx2uoc2ptdm9e570kp1b&dl=0}} \label{tab:thetable}}
+\tablecaption{Bona fide, candidate, and debunked complex rotators from
+  the TESS 2-minute data. {\bf For internal review, full versions are
+  available here
+  \url{https://www.dropbox.com/scl/fo/twn4s9ckbevf75jqhtoy1/h?rlkey=t5cn8cx2uoc2ptdm9e570kp1b&dl=0}}
+  \label{tab:thetable}}
 %\toprule
@@
 \enddata
-\tablecomments{This table includes \ngoods\ CQVs (\texttt{Quality}
-  flag 1), \nmaybes\ ambiguous CQVs (\texttt{Quality} flag 0), and
+\tablecomments{This table includes \ngoods\ CRs (\texttt{Quality}
+  flag 1), \nmaybes\ ambiguous CRs (\texttt{Quality} flag 0), and
   \ndebunked\ impostors (\texttt{Quality} flag -1).  The three-bit
@@
 
-One hypothesis for the CQVs, presented by \citet{2019ApJ...876..127Z},
+One hypothesis for the CRs, presented by \citet{2019ApJ...876..127Z},
 is that the star might be ``{\it orbited by one or more rings composed of
@@
 and therefore the sublimation lifetime would not be an issue even if
-the particles are dust-like in size.}'' A sketch of this scenario is
+the particles are dust-like in size.}'' A sketch of this scenario was
 presented by \citet{2019ApJ...876..127Z}, in their Figure~11.
@@
 One concern with the ring hypothesis is that if a cool spot were to
-transit behind the ring, it would produce a brightening, rather than a
-dimming.   Most CQVs show dimmings.   The ring scenario would
+transit behind the ring, it would produce a brightening, not a
+dimming.   Most CRs show dimmings.   The ring scenario would
 therefore imply that large hot spots are common in the photospheres of
 pre-main-sequence M dwarfs.  Empirical evidence however suggests that
-the optical variability of disk-free pre-main-sequence stars is
-dominated by cool spots.  This evidence includes flux excursions
+cool spots dominate the
+the optical variability of disk-free pre-main-sequence stars.
+This evidence includes flux excursions
 caused by spot-crossings during planetary transits
@@
 
-A stronger concern with the ring hypothesis is that it is fine-tuned.
+An independent  concern with the ring hypothesis is that it is fine-tuned.
 The model requires specific locations for the inner edge and the outer
-edge of the ring, an inclination that yields a band with a particular
-apparent size, and for material in the ring to be optically thick
+edge of the ring, an inclination that yields a band with a specific
+apparent size, and material in the ring that must be optically thick
 while also being homogeneous enough to not induce any apparent
 photometric variability.
-While it is challenging to ascribe specific probabilities to any one
-of these factors, 
-the requirement that they all be simultaneously met seems sufficiently
+It is challenging to ascribe specific probabilities to any one
+of these factors.
+However the requirement that they all be simultaneously met seems sufficiently
 severe to disfavor this scenario.
@@
 Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river} show
-120-second cadence data for TIC~300651846, a CQV in the TESS
+120-second cadence data for TIC~300651846, a CR in the TESS
 continuous viewing zone.  If it were not for the existence of
@@
 
-TESS was the first instrument to show that CQV light curves contain
+TESS was the first instrument to show that CR light curves contain
 power at timescales of a few minutes
@@
 relative to K2.  A logical follow-up is to ask whether the periodic
-components of the CQV light curves contain power at timescales below
-one minute.  Between 2020 and 2021, we observed 10 CQVs at 20-second
+components of the CR light curves contain power at timescales below
+one minute.  Between 2020 and 2021, we observed 10 CRs at 20-second
 cadence with TESS in order to explore this question (TESS DDT029).
@@
 264599508, 363963079, 144486786, 408188366, 300651846, 262400835.
-These sources were selected from CQVs known at the time to have short
+These sources were selected from CRs known at the time to have short
 periods and sharp features when observed at 2-minute cadence.
 Comparing the 20-second to 120-second data for these stars (data
-available on MAST), we concluded that these CQVs did not contain
+available on MAST), we concluded that these CRs did not contain
 appreciable power at timescales shorter than a few minutes.
 
-\section{The CQVs are not obviously accreting}
+\section{The CRs are not obviously accreting}
 
 We acquired iodine-free reconnaissance spectra using Keck/HIRES for
-three CQVs.  The goals were to determine the chromospheric activity
+three CRs.  The goals were to determine the chromospheric activity
 levels, and to check for indications of either accretion or
@@
 blue excess in TIC~264599508 could be explained by a second unresolved
-star; the TESS light curve for this source shows both the 7.90\,hr CQV
+star; the TESS light curve for this source shows both the 7.90\,hr CR
 signal, and a 9.00\,hr rotation signal with comparable amplitude.
@@
 	\caption{
-		{\bf Spectral age and activity diagnostics for three CQVs}.
+		{\bf Spectral age and activity diagnostics for three CRs}.
 		Wavelengths are in air;
@@
 % TIC~262400835 ($d$=174\,pc) is formally outside the scope of the
-% current work.  However, this CQV was observed using MuSCAT2 on 2020
+% current work.  However, this CR was observed using MuSCAT2 on 2020
 % December 12, 13, and 16, and the results might be worth including in

### 2023-08-29 paper/ms.tex
Update ms; add completeness figure.
More clear than trying to explain it in words!

Co-authored-by: Joshua Winn <jnwinn@princeton.edu>

@@
 \accepted{---}
-\shorttitle{Four Years of CRs}
+\shorttitle{Four Years of Complex Rotators}
 
@@
 \begin{abstract}
-  %Complex rotators (CRs) are low-mass
-  %pre-main-sequence stars with nearly periodic optical modulation.
-  %The modulation is probably caused by eclipsing clumps of dust or gas
-  %in orbit at the Keplerian corotation radius.  Here, we report new
-  %CRs discovered in TESS short-cadence data collected between
-  %2018~July and 2022~September.  Our search of \nstarssearched\ K and
-  %M dwarfs with $T$$<$16 and $d$$<$150\,pc yielded \ngoods\
-  %high-quality CRs.  Most of these discoveries are new, and they
-  %include the brightest ($T$$\approx$9.5), closest
-  %($d$$\approx$20\,pc), and oldest ($\approx$200\,Myr) examples of
-  %this class of object currently known.  A few objects are outliers:
-  %LP 12-502 for instance showed a ``dip complex'' with a period and
-  %duration that were fixed over 1,500 cycles, but in detail, this
-  %system exhibited between four and eight local minima per cycle, and
-  %at times also displayed multiple periods simultaneously.  We
-  %demonstrate that transient corotating material is the most viable
-  %explanation for this class of object, and present evidence
-  %supporting the hypothesis that this material is sculpted by stellar
-  %magnetic fields dominated by high order multipoles.  We expect that
-  %our sample will facilitate future efforts aimed at connecting CRs
-  %to the broader contexts of star, disk, and perhaps even exoplanet
-  %evolution. 	
-  % % JNW alternate:
   Complex rotators (CRs) are low-mass pre-main-sequence stars with
@@
 material.  The first scenario invokes opaque dust ``clumps'' that
-orbit near the Keplerian corotation radius [$R_{\rm cr} =
+orbit near the Keplerian corotation radius [$R_{\rm c} =
 (GM/\Omega^2)^{1/3}$, where $\Omega = 2\pi/P_{\rm rot}$] and
@@
 		{\bf Complex rotators (CRs)}:
-    {\it Top:} Phase-folded TESS light curves of three CRs.  Each panel shows
-    the average of the data accumulated over one month.
-    Gray circles are raw 2-minute data; black
-    circles are binned to 300 points per cycle.  The period in hours
-    is printed in the
-    bottom right corner.  Left-to-right, the objects are LP
-    12-502 (TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and
-    TIC 425933644 (Sector~28).
+    {\it Top:} Phase-folded TESS light curves of three CRs.  Each
+    panel shows the average of the data accumulated over one month.
+    Gray circles are raw 2-minute data; black circles are binned to
+    300 points per cycle.  The period in hours is printed in the
+    bottom right corner.  Left-to-right, the objects are LP 12-502
+    (TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
+    425933644 (Sector~28).
     {\it Bottom:} Cartoon explanations for the phenomenon.  The dust
     clump scenario (left) and prominence scenario (right) both invoke
-    magnetically-confined corotating material.
+    magnetically-entrained corotating material.
 	}
@@
 Specifically, we used the 120-second cadence light curves produced by
-the Science Processing and Operations Center at NASA Ames
-\citep{2016SPIE.9913E..3EJ}.  While the TESS data products from these
-sectors also included full frame images with cadences of 600 and 1800
-seconds, we limited our scope in this study for the sake of simplicity
-in data handling and uniformity in the data.  In exchange, we
-sacrificed both completeness and homogeneity of the selection
-function.  While TESS cumulatively observed $\approx$90\% of the sky
-for at least one lunar month between 2018 July and 2022 September, the
-120-second cadence data were collected for only a subset of observable
-stars during this time due to telemetric constraints
-\citep[see][]{2021PASP..133i5002F}.
-
-To assess the completeness of the resulting 120-second cadence data
-that are the basis of this study, we cross-matched TIC8.2
-\citep{2019AJ....158..138S,2021arXiv210804778P} against the Gaia DR2 point-source catalog
-\citep{2018A&A...616A...1G}.  We opted for Gaia DR2 rather than DR3
-because the base catalog for TIC8 was Gaia DR2, which facilitated a
-one-to-one crossmatch using the Gaia source identifiers.  This
-exercise showed that for $T$$<$16 M dwarfs, the TESS 2-minute data are
-$\approx$50\% complete at $\approx$50\,pc.  At $<$20\,pc,
-$\gtrsim$80\% of the $T$$<$16 M dwarfs have at least one sector of
-short-cadence data; at $>$100\,pc, $\lesssim$10\% of such M dwarfs
-have at least one sector of short-cadence data.  Armed with this
-understanding, we then used our cross-match between Gaia DR2 and TIC8
-to select our stars of interest, which we defined as stars with
-120-second cadence TESS light curves satisfying these four conditions:
+the Science Processing and Operations Center at the NASA Ames Research
+Center \citep{2016SPIE.9913E..3EJ}.  While the TESS data products from
+these sectors also included full frame images with cadences of 600 and
+1800 seconds for a larger number of sources, we restricted our
+attention to the 120-second data for the sake of uniformity and
+simplicity in data handling.  In exchange, we sacrificed both
+completeness and homogeneity of the selection function.  While TESS
+cumulatively observed $\approx$90\% of the sky for at least one lunar
+month between 2018 July and 2022 September, the 120-second cadence
+data were collected for only a subset of observable stars that were
+preferentially nearby and bright \citep[see][]{2021PASP..133i5002F}.
+The total 120-second data volume
+from Sectors 1-55 included 1{,}087{,}475 short-cadence light curves, which were
+available for 428{,}121 unique stars.
+% latter stats from MERGED_spoc2min_sector1_to_sector58.csv
+
+To further simplify our search, we defined our target sample as
+stars with 120-second cadence TESS light curves satisfying the
+following four conditions:
 \begin{align}
-  T &< 16 \quad&(\mathrm{Amenable\ with\ TESS})\\
+  T &< 16 \quad&(\mathrm{Amenable\ with\ TESS}) \label{eq:one}\\
   \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only})\\
   M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})\\
-  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}).
+  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}) \label{eq:four}.
 \end{align}
@@
 units of arcseconds, and $d$ is a geometric distance defined by
-inverting the parallax and ignoring any zero-point correction.  The
-target sample therefore includes \nstarssearched\ M dwarfs and late-K
-dwarfs, down to $T$$<$16 and out to $d$$<$150\,pc.
+inverting the parallax and ignoring any zero-point correction.  We
+performed this selection by cross-matching TIC8.2
+\citep{2019AJ....158..138S,2021arXiv210804778P} against the Gaia DR2
+point-source catalog \citep{2018A&A...616A...1G}.  We opted for Gaia
+DR2 rather than DR3 because the base catalog for TIC8 was Gaia DR2,
+which facilitated a one-to-one crossmatch using the Gaia source
+identifiers.  The target sample ultimately included \nstarssearched\ M
+dwarfs and late-K dwarfs, down to $T$$<$16 and out to $d$$<$150\,pc.
+For stars with multiple sectors of TESS data available, we searched
+for CR signals independently.
+In total, our \nstarssearched\ star target list included \nlcssearched\ month-long light
+curves.
+
+We assessed the completeness of our selection function by comparing
+the number of stars with TESS Sector 1-55 short-cadence data against
+the number of Gaia DR2 point sources.
+We required all stars to meet conditions~\ref{eq:one}--\ref{eq:four}.
+The results are shown in Figure~\ref{fig:completeness}.
+TESS 2-minute data exist for $\approx$50\%
+of $T$$<$16 M and late-K dwarfs at $\approx$50\,pc.
+Within 20\,pc, $\gtrsim$80\% of the $T$$<$16 M and late-K dwarfs have
+at least one sector of short-cadence data.
+Beyond 100\,pc, $\lesssim$10\% of such stars have any short-cadence
+data available.
+This can be translated into our sensitivity for the lowest mass stars
+by considering that the spectral type of a $T$=16 star at $d$=50\,pc
+is $\approx$M5.5V, corresponding to a main-sequence mass of
+$\approx$0.12\,$M_\odot$.
+
+\begin{figure}[!tp]
+	\begin{center}
+		\centering
+		\includegraphics[width=0.48\textwidth]{f2completeness.pdf}
+		\vspace{-0.5cm}
+		\caption{
+			{\bf Completeness of the TESS 2-minute cadence data for late-K
+      and early M dwarfs near the Sun, from Sectors 1-55.}  
+      The orange dotted curve shows the number of stars in successive
+      radial shells, each with a width of 10\,pc.  To be counted, these stars must meet
+      the listed conditions: they must
+      be red ($\bprp$>$1.5$)
+      dwarf stars ($M_{\rm G}$>4) amenable for TESS observations ($T$<16).
+      The blue solid curve shows the
+      fraction of such stars with at least one sector of TESS
+      2-minute cadence data acquired between Sectors 1-55.  The
+      latter data comprise the selection function for our complex
+      rotator search.
+		}
+			\vspace{-0.5cm}
+		\label{fig:completeness}
+	\end{center}
+\end{figure}
 

### 2023-08-29 drivers/fraction_coverage.py

@@ -1,0 +1,171 @@
+"""
+Want to quote the following stat:
+
+    Only XX.X% of K- and M-dwarfs with d<100pc and T<16 received 2-minute
+    observations across Sectors 1-58.
+"""
+import numpy as np, pandas as pd, matplotlib.pyplot as plt
+
+# S1-S58 2-min data
+csvpath = "/Users/luke/local/SPOCLC/gaia_X_spoc2min_merge.csv"
+tdf = pd.read_csv(csvpath)
+
+sel = (
+    (tdf.bp_rp > 1.5) &
+    (tdf.TESSMAG < 16) &
+    (tdf.parallax > 1e3*(1/150)) &
+    (tdf.M_G > 4) &
+    (tdf.SECTOR <= 55)
+)
+# S1-S55, sel fn applied
+stdf = tdf[sel]
+
+N_TESS_2min = len(np.unique(stdf.dr2_source_id))
+
+# Gaia 100pc
+do_100pc = 0
+do_150pc = 1
+if do_100pc:
+    from rudolf.helpers import get_gaia_catalog_of_nearby_stars
+    gdf = get_gaia_catalog_of_nearby_stars()
+elif do_150pc:
+    # Gaia DR2 <150pc
+    # select
+    # g.source_id, g.ra, g.dec, g.parallax, g.parallax_over_error, g.pmra,
+    # g.pmdec, g.phot_g_mean_mag, g.phot_bp_mean_mag, g.phot_rp_mean_mag,
+    # g.phot_g_mean_flux_over_error, g.phot_bp_mean_flux_over_error,
+    # g.phot_rp_mean_flux_over_error, g.bp_rp, g.g_rp, g.radial_velocity, g.l,
+    # g.b
+    # from gaiadr2.gaia_source import as g
+    # where g.parallax > 6.6666666666
+    # and g.bp_rp > 1.5
+    gdf = pd.read_csv('/Users/luke/local/complexrotators/lt150pc_mkdwarf-result.csv')
+
+
+Tmag_pred = (
+        gdf['phot_g_mean_mag']
+        - 0.00522555 * (gdf['phot_bp_mean_mag'] - gdf['phot_rp_mean_mag'])**3
+        + 0.0891337 * (gdf['phot_bp_mean_mag'] - gdf['phot_rp_mean_mag'])**2
[…]

### 2023-08-29 paper/collect.sh

@@ -8,6 +8,9 @@ cp $artdir/twomodels.pdf f1b.pdf
 
 # fig2 is annotated_lp12502.key exported
 
+# fig2 completeness
+cp $resultsdir/fraction_coverage/fraction_coverage.pdf f2completeness.pdf
+
 # fig3
 cp $resultsdir/full_lcmosaic/full_lcmosaic_showtitles_binarytitle_Ngoodsectors_tic8_Tmag.pdf f3.pdf
 

### 2023-08-29 paper/ms.tex
Update ms (JNW comments): methods
Co-authored-by: Joshua Winn <jnwinn@princeton.edu>

@@
 
-		\vspace{-0.6cm}
+		\vspace{-0.65cm}
 		\subfloat{
@@
 	\end{center}
-		\vspace{-0.3cm}
+		\vspace{-0.5cm}
 	\caption{
 		{\bf Complex rotators (CRs)}:
-    {\it Top:} Phase-folded TESS light curves of three CRs.  Each
-    panel shows the average of the data accumulated over one month.
+    {\it Top:} Phase-folded TESS light curves for three CRs.  Each
+    panel shows the average of the data accumulated over one month,
+    relative to the mean stellar brightness.
     Gray circles are raw 2-minute data; black circles are binned to
@@
       The orange dotted curve shows the number of stars in successive
-      radial shells, each with a width of 10\,pc.  To be counted, these stars must meet
-      the listed conditions: they must
-      be red ($\bprp$>$1.5$)
-      dwarf stars ($M_{\rm G}$>4) amenable for TESS observations ($T$<16).
-      The blue solid curve shows the
-      fraction of such stars with at least one sector of TESS
-      2-minute cadence data acquired between Sectors 1-55.  The
-      latter data comprise the selection function for our complex
-      rotator search.
+      radial shells, each with a width of 10\,pc.  To be counted,
+      these stars must meet the listed conditions: they must be red
+      ($\bprp$>$1.5$) dwarf stars ($M_{\rm G}$>4) amenable for TESS
+      observations ($T$<16).  The blue solid curve shows the fraction
+      of such stars with at least one sector of TESS 2-minute cadence
+      data acquired between Sectors 1-55.  The latter data comprise
+      the selection function for our complex rotator search.
 		}
@@
 
-Previous methods for finding CRs have included visually examining
-stars in young clusters
-\citep{2016AJ....152..114R,2017AJ....153..152S} and automatically
-flagging rapid rotators with a large number of strong Fourier
-harmonics \citep{2019ApJ...876..127Z}.  The latter approach still
-requires visual vetting, since ``stars with strong Fourier harmonics''
-is a designation that includes objects such as eclipsing binaries or
-multiple stars blended into a single photometric aperture.  In this
-work, we implemented a new search approach based on counting the
-number of sharp local minima in phase-folded light curves, while also
-using the Fourier approach.  We applied these two
-search techniques independently.
-
+Prior to this study, most CRs have been found by visually examining
+all the light curves of stars in young clusters
+\citep{2016AJ....152..114R,2017AJ....153..152S,2023ApJ...945..114P},
+or by flagging light curves with short periods and a large number of
+strong Fourier harmonics for visual inspection
+\citep{2019ApJ...876..127Z}.  In this work, we implemented a new
+search approach based on counting the number of sharp local minima in
+phase-folded light curves, while also using the Fourier approach.  We
+applied these two search techniques independently.
+
+%FIXME TODO LEFT OFF HERE
 \subsubsection{Counting dips}
@@
 The dip counting technique aims to count sharp local minima in
-phase-folded light curves.  CRs will preferably have at least three
-such minima in order to be distinct from false positives such as
-synchronized and spotted binaries (``RS CVn'' stars).
-
-For our dip-counting pipeline, we began with the {\tt PDC\_SAP} flux
-for each sector, removed non-zero quality flags, and normalized the
-light curve to one by dividing out its median value.  We then
-flattened the light curve using a 5-day sliding median filter, as
-implemented in \texttt{wotan} \citep{2019AJ....158..143H}.  On the
-resulting cleaned and flattened light curve, we ran a periodogram
-search, opting for the \citet{1978ApJ...224..953S} phase dispersion
-minimization (PDM) algorithm implemented in \texttt{astrobase}
+phase-folded light curves.  The most remarkable CRs often show three
+or more dips per cycle, which distinguishes them from other types of
+variables such as synchronized and spotted binaries (RS CVn stars).
+
+For our dip-counting pipeline, we began with the {\tt PDC\_SAP} light
+curves for each sector, removed non-zero quality flags, and normalized
+the light curve by dividing out its median value.  We then flattened
+the light curve using a 5-day sliding median filter, as implemented in
+\texttt{wotan} \citep{2019AJ....158..143H}.  We computed a periodogram
+of the resulting cleaned and flattened light curve, opting for the
+\citet{1978ApJ...224..953S} phase dispersion minimization (PDM)
+algorithm implemented in \texttt{astrobase}
 \citep{2021zndo...1011188B} due to its shape agnosticism.  If a period
@@
 Once a star's period was identified, we binned the phased light curve
-to 100 points per cycle.  To separate ``sharp'' local minima from
-smooth spot-induced variability, we then iteratively fit
-robust penalized splines to the wrapped phase-folded light curve,
-excluding points more than two standard deviations away from the local
-continuum \citep{2019AJ....158..143H}.  The maximum number of
-equidistant spline knots per cycle is the parameter in this framework
-that controlled the meaning of ``sharp'' --- we allowed at most 10
-such knots per cycle, though for most stars fewer knots were preferred
-based on cross-validation using an $\ell^2$-norm penalty.  An example
-fit is shown in panel {\it (e)} of Figure~\ref{fig:vet}.
+to 100 points per cycle.  To separate sharp local minima from smooth
+spot-induced variability, we then iteratively fit robust penalized
+splines to the wrapped phase-folded light curve, excluding points more
+than two standard deviations away from the local continuum
+\citep{2019AJ....158..143H}.  The wrapping procedure is discussed
+below.  In this fitting framework, the maximum number of equidistant
+spline knots per cycle is the parameter that controlled the meaning of
+``sharp'' --- we allowed at most 10 such knots per cycle, though for
+most stars fewer knots were preferred based on cross-validation using
+an $\ell^2$-norm penalty.  An example fit is shown in panel {\it (e)}
+of Figure~\ref{fig:vet}.
 
@@
 required it to have a width of at least $0.02\,P$, and a height of at
-least twice the point-to-point RMS.  This latter quantity is defined
+least twice the noise level.  The noise level was defined
 as the 68$^{\rm th}$ percentile of the distribution of the residuals
@@
 is the flux and $i$ is an index over time.
-
-To identify local minima near the edges of the phased light curve,
-which usually would cover phases $\phi \in [ 0,1 ]$, we performed the
-entire procedure over a phase-folded light curve spanning $\phi \in
-[-1,2 ]$, by duplicating and concatenating the ordinary phase-folded
-light curve.  The free parameters we adopted throughout this analysis
-procedure, for instance the maximum number of spline knots per cycle,
-and how large and wide of a local minimum to consider a ``true dip'',
-were chosen during testing based on their ability to correctly
-re-identify a large fraction ($>$90\%) of previously known CRs, while also being
-able to consistently reject common false positives such as rapidly
-rotating spot-induced variability and typical eclipsing binaries.
-
-Overall, for a star to proceed to manual examination, we required that
-it have a peak PDM period below two days, and that it exhibited at
-least three sharp local minima (as algorithmically reported) in at
-least one observed TESS sector.
+In panel {\it (e)} of Figure~\ref{fig:vet}, automatically-identified
+local minima are shown with the gray triangles.
+
+Wrapping is necessary to eliminate edge
+effects when fitting the light curve and when identifying local minima
+in the residuals.  A phased light curve would usually cover phases
+$\phi \in [ 0,1 ]$.  We instead performed the entire preceding
+procedure over a phase-folded light curve spanning $\phi \in [-1,2 ]$,
+which was created by duplicating and concatenating the ordinary
+phase-folded light curve.  The free parameters we adopted throughout
+this analysis -- for instance the maximum number of spline knots per
+cycle, and the height and depth criteria for dips -- were chosen
+during testing based on the desire to correctly re-identify a large
+fraction ($>$90\%) of previously known CRs, while also being able to
+consistently reject common false positives such as rapidly rotating
+spot-induced variability and typical eclipsing binaries.
+
+In short, CR candidates were identified by requiring a peak PDM period
+below two days and the presence of at least three sharp local minima,
+based on at least one sector of the TESS 120-second data. Candidates
+were then inspected visually as described in
+Section~\ref{subsec:visual}.
 
@@
 
-We performed an independent search for strongly periodic phenomena
-using a Fourier-based approach, following \citet{2019ApJ...876..127Z}
-and \citet[][their Section~1.3]{2023MNRAS.524.4220P}.  Starting with
-the {\tt PDC\_SAP} light curves, we normalized each light curve, and
-then re-binned it into equal width 120-second bins to account for the
-uneven spacing in the TESS data, as well as the data gap caused by
-satellite downlink during each sector.  We then padded the data to
-ensure that the light curve had a length that was a power of two, as
-described by \citeauthor{2019ApJ...876..127Z}.  Taking the Fourier
-transform of the padded light curve using {\tt numpy.fft},
-we then searched for peaks with a significance of over 12-$\sigma$
-within a set of 500 frequency bins.
+We performed an independent search using a Fourier-based approach,
+following \citet{2019ApJ...876..127Z} and \citet[][their
+Section~1.3]{2023MNRAS.524.4220P}.  Starting with the {\tt PDC\_SAP}
+light curves, we normalized each light curve, and then re-binned it
+into equal width 120-second bins to account for the uneven spacing in
+the TESS data, as well as the data gap caused by satellite downlink
+during each sector.  We then padded the data to ensure that the light
+curve had a length that was a power of two, as described by
+\citeauthor{2019ApJ...876..127Z}.  After taking the Fourier transform
+of the padded light curve using {\tt numpy.fft}, we searched for peaks
+with a significance exceeding 12-$\sigma$ within a set of 500
+frequency bins.
 
@@
 curves, Fourier transform, potential contaminating stars, and
-information about these contaminating stars.  In the sectors for which
-we performed this analysis, we found that ``summary'' sheets were
-generated for $\approx$10\% of the 20{,}000 120-second targets in a
-given sector.  We then manually reviewed each summary sheet, and
-visually labeled each star based on its morphology (including e.g.
-eclipsing binary, CR, RS CVn, or cataclysmic variable).  CRs that
-were observed in multiple sectors had their light curves stitched
-together and analyzed for a more accurate period determination.
+information about these contaminating stars.  Summary sheets were
+generated for $\approx$10\% of the 20{,}000 120-second targets in each
+sector.  We reviewed each summary sheet and tried to classify each
+light curve based on visual inspection of its morphology (with
+categories including eclipsing binary, CR, RS CVn, and cataclysmic
+variable). Whenever a CR was identified, the light curves from
+multiple sectors were stitched together and analyzed jointly, for a
+more accurate period determination.
 
 \subsubsection{Manual vetting}
+\label{subsec:visual}
 
@@
 			subharmonic.
-			{\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
-			circles displayed for scale.
+      {\it c)}: DSS finder chart, with 21$''$ and 42$''$ radius
+      circles for scale.  One TESS pixel has a full side length of
+      21$''$.
 			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
@@
 			{\it e)}: Phase-folded light curve, binned to 100 points per
-			cycle.  The gray line denotes the automated spline-fit to the
+			cycle.  The gray line denotes the spline-fit to the
 			wrapped phase-folded light curve, and small gray triangles
@@
 			direction.
-			{\it k)}: Gaia DR2 color--absolute magnitude diagram.     
-			The gray background denotes stars within 100\,pc from \citet{2021A&A...649A...6G}.
+      {\it k)}: Gaia DR2 color--absolute magnitude diagram. The gray
+      background denotes stars within 100\,pc from
+      \citet{2021A&A...649A...6G}.
       {\it l)}: Information from Gaia DR2, TIC8, and the automated
@@
       if $\Delta T$$<$2.5.
-			{\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
-			using positions, proper motions, and the parallax.
+      {\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities,
+      calculated using positions, proper motions, and the parallax.
 		}
@@
 expectations for CRs by assembling the data shown in
-Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CR if at least
-one TESS sector showed what we viewed as the unambiguous signatures of
-the class (short period; at least three dips or else otherwise
-oddly-shaped dips; relative stability over a timescale of 30\,days).
-We independently noted stars that we thought could be CRs, but that
-were more ambiguous.
-
-Broadly speaking, the most common false positive triggers for both the Fourier
-and dip-counting techniques were eclipsing binaries, spot-induced
-variability from rapid rotators, and variability from neighboring,
-off-target stars.  Typical false positive rates from our dip-counting
-pipeline were 5:1, with \nuniqdipflagged\ unique stars flagged, and
-about 20\% being labeled either ``good'' or ``possible'' CRs.  The
-Fourier analysis was not amenable to calculating a similar
-false-positive rate, because it was implemented as a general
-variability search; its results are also being used for analyses on
-topics other than CRs.
+Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CR if it met
+all of the following criteria for at least one TESS sector:
+\vspace{-2pt}
+\begin{itemize}[leftmargin=*]
+  \setlength\itemsep{-2pt}
+  \item $P<2$\,days.
+  %
+  \item At least three dips per cycle, or else otherwise
+    oddly-shaped dips.
+  %
+  \item Dip phases (mostly) repeat over $\approx$30\,day sector duration.
+\end{itemize}
+\vspace{-2pt}
+We also noted ''possible'' CRs for which the classification was more
+ambiguous, and ``false positives'' that are definitely not CRs.  The
+most common false positives for both the Fourier and dip-counting
+techniques were eclipsing binaries, ordinary spotted rapid rotators,
+and complex light curves due to multiple stars contributing to the
+photometric aperture.  Our dip-counting pipeline flagged
+\nuniqdipflagged\ unique stars for visual inspection; about 20\% were
+subsequently labeled either good or possible CRs.  From the Fourier
+pipeline, $\approx$0.5\% of stars that passed the 12-$\sigma$ peak
+threshold were eventually classified as CRs.  This is because the
+Fourier pipeline was implemented as a general variability search; its
+results are also being used for analyses on topics other than CRs.
 
@@
 We estimated the stellar ages by making probabilistic spatial and
-kinematic associations between the CRs and known clusters in the
-solar neighborhood.  For most stars in our sample, we did this using
+kinematic associations between the CRs and known clusters in the solar
+neighborhood.  For most stars in our sample, we did this using
 BANYAN\,$\Sigma$
@@
 ``associations'') within 150\,pc of the Sun, by modeling the clusters
-as multivariate Gaussians in 3-D position and 3-D velocity space.  We
-used the Gaia DR2 sky positions, proper motions, and distances to
-calculate the membership probabilities.  BANYAN\,$\Sigma$ in turn
-analytically marginalizes over the radial velocity dimension.  The
-probabilities returned by this procedure are qualitatively useful, but
-should be assessed with caution due to the non-Gaussian nature of most
+as multivariate Gaussian distributions in 3-D position and 3-D
+velocity space.  We used the Gaia DR2 sky positions, proper motions,
+and distances to calculate the membership probabilities.
+BANYAN\,$\Sigma$ in turn analytically marginalizes over the radial
+velocity dimension.  The probabilities returned by this procedure are
+qualitatively useful, but should be interpreted with caution because
+the assumption of Gaussian distributions is questionable for most
 groups within the solar neighborhood \citep[see
@@
 consulted the meta-catalog of young, age-dated, and age-dateable stars
-within from \citet{2022AJ....163..121B}, and also searched the local
+provided by \citet{2022AJ....163..121B}, and also searched the local
 volume around each star for co-moving
@@
 our SED fit to avoid any possible bias induced by chromospheric UV
-excess; we similarly omitted WISE bands $W3$ and $W4$, but due to
-reliability concerns.  \texttt{astroARIADNE} compares the measured
-broadband flux measurements against pre-computed model grids, and by
-default fits for six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V},
-\log g, [{\rm Fe/H}], d \}$.  The distance  prior is drawn from
+excess.  We omitted WISE bands $W3$ and $W4$ due to reliability
+concerns.  \texttt{astroARIADNE} compares the measured broadband flux
+measurements against pre-computed model grids, and by default fits for
+six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
+Fe/H}], d \}$.  The distance  prior is drawn from
 \citet{2021AJ....161..147B}.  The surface gravity and metallicity are
-generally unconstrained.  And finally, given our particular use-case,
+generally unconstrained.  Given our selection criteria for the stars,
 we assumed the following priors for the temperature, stellar size, and
@@
 With the effective temperatures and stellar radii from the SED fit, we
-then estimated the stellar masses by interpolating against the PARSEC
+estimated the stellar masses by interpolating against the PARSEC
 isochrones \citep[v1.2S][]{2014MNRAS.444.2525C}.  The need for models
@@
 \citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2020ApJ...891...29S}.
-Plausible explanations for anomalous M dwarf colors and sizes relative
-to model predictions include starspot coverage
-\citep[e.g.][]{2017ApJ...836..200G}, and potentially incomplete line
+Plausible explanations for the disagreement between observed and
+theoretical M dwarf colors and sizes include starspot coverage
+\citep[e.g.][]{2017ApJ...836..200G} and potentially incomplete line
 lists \citep[e.g.][]{2013A&A...556A..15R}.  In the PARSEC models,
@@
 eclipsing binaries.  This is sufficient for our goal of estimating
-stellar masses.  Given our observed $\{ \tilde{T}_{\rm eff},
+stellar masses.  Given our estimates of $\{ \tilde{T}_{\rm eff},
 \tilde{M}_\star, \tilde{t} \}$, and approximating their uncertainties
 as Gaussian $\sigma_{\tilde{T}_{\rm eff}}$, $\sigma_{\tilde{M}_\star}$
-and $\sigma_{\tilde{t}}$, we evaluate a distance $d$ between our
-observations and any model PARSEC grid-point $\{ T_{\rm eff}, M_\star,
-t \}$ as
+and $\sigma_{\tilde{t}}$, we define a distance metric $\Delta$ to each
+model PARSEC grid-point $\{ T_{\rm eff}, M_\star, t \}$ via
 \begin{equation}
-  d^2 = 
+  \Delta^2 = 
   \left( \frac{\tilde{T}_{\rm eff} - T_{\rm eff}}{\sigma_{\tilde{T}_{\rm eff}}} \right)^2
@@
 \end{equation}
-in order to assign equal importance to each dimension.  The preferred
-model mass is then one that minimizes this distance, and is quoted in
-Table~\ref{tab:thetable}.  Uncertainties in the masses are propagated
-forward from the statistical uncertainties in the radii, temperatures,
+where the division by the uncertainties helps to assign equal
+importance to each dimension.  The mass reported in
+Table~\ref{tab:thetable} is the model mass that minimizes the
+distance.  The reported uncertainties in the masses are based on
+propagating the statistical uncertainties in the radii, temperatures,
 and ages.
@@
       that sources with the most TESS data available are on top (see
-      Section~\ref{sec:catalog}).  
-      Each panel is labeled by
-      the TIC identifier, the TESS sector number, the period in
-      hours, and the three-bit binarity flag from Table~\ref{tab:thetable},
-      which denotes Gaia DR3 \texttt{radial\_velocity\_error} outliers
-      (bit 1), Gaia DR3 \texttt{ruwe} outliers (bit 2), and stars with
-      secondary TESS periods (bit 3). 
+      Section~\ref{sec:catalog}).  Zero phase is chosen to correspond
+      to minimum light.  Each panel is labeled by the TIC identifier,
+      the TESS sector number, the period in hours, and the three-bit
+      binarity flag from Table~\ref{tab:thetable}, which denotes Gaia
+      DR3 \texttt{radial\_velocity\_error} outliers (bit 1), Gaia DR3
+      \texttt{ruwe} outliers (bit 2), and stars with secondary TESS
+      periods (bit 3). 
 		}

### 2023-08-29 complexrotators/plotting.py

@@ -276,7 +276,7 @@ def plot_river(time, flux, period, outdir, titlestr=None, cmap='Blues_r',
     if isinstance(titlestr, str):
         cax0 = divider0.append_axes('right', size='5%', pad=0.05)
         cb0 = fig.colorbar(c, ax=ax, cax=cax0, extend='both')
-        cb0.set_label("Flux [%]", rotation=270, labelpad=10)
+        cb0.set_label("$\Delta$ Flux [%]", rotation=270, labelpad=10)
     elif titlestr is None:
         # sick inset colorbar
         x0,y0,dx,dy = 0.02, -0.09, 0.3, 0.02
@@ -287,7 +287,7 @@ def plot_river(time, flux, period, outdir, titlestr=None, cmap='Blues_r',
 
         cb = fig.colorbar(c, cax=axins1, orientation="horizontal",
                           extend="both")
-        cb.set_label("Flux [%]", rotation=0, labelpad=3)
+        cb.set_label("$\Delta$ Flux [%]", rotation=0, labelpad=3)
         #cb.set_ticks([min_cycle, max_cycle])
         #cb.set_ticklabels([int(min_cycle), int(max_cycle)])
         #cb.ax.tick_params(labelsize='x-small')
@@ -635,7 +635,7 @@ def plot_phase_timegroups(
             f"P={plot_period*24:.4f}$\pm${plot_period_std*24:.3f}hr"
         )
 
-    fig.text(-0.01,0.5, r"Flux [%]", va='center',
+    fig.text(-0.01,0.5, r"$\Delta$ Flux [%]", va='center',
              rotation=90)
 
     if isinstance(ylim, list):
@@ -822,7 +822,7 @@ def plot_phase_timegroups_mosaic(
             va='center',
         )
 
-    fig.text(-0.01,0.5, r"Flux [%]", va='center', rotation=90, fontsize='large')
+    fig.text(-0.01,0.5, r"$\Delta$ Flux [%]", va='center', rotation=90, fontsize='large')
     fig.text(0.5,-0.01, r"Phase, φ", ha='center', fontsize='large')
 
     format_ax(ax)
@@ -872,7 +872,7 @@ def plot_quicklook_cr(x_obs, y_obs, x_trend, y_trend, x_flat, y_flat, outpath,
[…]

### 2023-08-29 drivers/find_CPVs.py

@@ -63,14 +63,14 @@ def get_ticids(sample_id):
         #"268963753"
         #"67745212"
         #"201789285",
-        #"402980664"
+        "402980664"
         #"251496897"
         #"141146666" # neighbor of 141146667
         #"353927317" # EPIC 211070495, Rebull2016
         #"220433363" # tess blend; gaia multipeaked; wanna see s32
         #"268971806" # HD 64740 has lots of data!
         #"254612758"  # rahul...
-        "435903839"
+        #"435903839"
         ]
 
         N_stars_to_search = len(ticids)
@@ -365,8 +365,8 @@ def find_CPV(ticid, sample_id, forcepdf=0):
 def main():
 
     sample_ids = [
-        #'debug'
-        '2023catalog_LGB_RJ_concat'
+        'debug'
+        #'2023catalog_LGB_RJ_concat'
         #'30pc_mkdwarf',
         #'30to50pc_mkdwarf',
         #'50to60pc_mkdwarf',

### 2023-08-29 drivers/plot_lc_mosaic.py

@@ -6,6 +6,10 @@ PLOTDIR = os.path.join(RESULTSDIR, 'lc_mosaic')
 if not os.path.exists(PLOTDIR):
     os.mkdir(PLOTDIR)
 
+rp.plot_lc_mosaic(PLOTDIR, subset_id='fav3')
+rp.plot_lc_mosaic(PLOTDIR, subset_id='fav3', showtitles=1)
+assert 0
+
 # NOTE: allchangers not implemented...
 rp.plot_lc_mosaic(PLOTDIR, subset_id='dlt150_good_allchangers_3count',
                   showtitles=1, titlefontsize=3)
@@ -18,8 +22,6 @@ rp.plot_lc_mosaic(PLOTDIR, subset_id='dlt150_good_changers')
 rp.plot_lc_mosaic(PLOTDIR, subset_id='dlt150_good_changers', showtitles=1)
 rp.plot_lc_mosaic(PLOTDIR, subset_id='dlt150_good_all')
 rp.plot_lc_mosaic(PLOTDIR, subset_id='dlt150_good_all', showtitles=1)
-rp.plot_lc_mosaic(PLOTDIR, subset_id='fav3')
-rp.plot_lc_mosaic(PLOTDIR, subset_id='fav3', showtitles=1)
 rp.plot_lc_mosaic(PLOTDIR, subset_id='dlt150_good_0')
 rp.plot_lc_mosaic(PLOTDIR, subset_id='dlt150_good_0', showtitles=1)
 rp.plot_lc_mosaic(PLOTDIR, subset_id='dlt150_good_1')

### 2023-08-30 paper/ms.tex
Update ms (JNW comments) - results
Co-authored-by: Joshua Winn <jnwinn@princeton.edu>

@@
 
-%FIXME TODO LEFT OFF HERE
 \subsubsection{Counting dips}
@@
 
-Wrapping is necessary to eliminate edge
-effects when fitting the light curve and when identifying local minima
-in the residuals.  A phased light curve would usually cover phases
-$\phi \in [ 0,1 ]$.  We instead performed the entire preceding
-procedure over a phase-folded light curve spanning $\phi \in [-1,2 ]$,
-which was created by duplicating and concatenating the ordinary
-phase-folded light curve.  The free parameters we adopted throughout
-this analysis -- for instance the maximum number of spline knots per
-cycle, and the height and depth criteria for dips -- were chosen
-during testing based on the desire to correctly re-identify a large
-fraction ($>$90\%) of previously known CRs, while also being able to
-consistently reject common false positives such as rapidly rotating
-spot-induced variability and typical eclipsing binaries.
+Wrapping is necessary to eliminate edge effects when fitting the light
+curve and when identifying local minima in the residuals.  A phased
+light curve would usually cover phases $\phi \in [ 0,1 ]$.  We instead
+performed the analysis described above using a phase-folded light
+curve spanning $\phi \in [-1,2 ]$, which was created by duplicating
+and concatenating the ordinary phase-folded light curve.  The free
+parameters we adopted throughout the analysis -- for instance the
+maximum number of spline knots per cycle, and the height and depth
+criteria for dips -- were chosen during testing based on the desire to
+correctly re-identify a large fraction ($>$90\%) of previously known
+CRs, while also being able to consistently reject common false
+positives such as rapidly rotating spot-induced variability and
+typical eclipsing binaries.
 
@@
       set, with one image per sector for each of the \nallcands\
-      objects in Table~\ref{tab:thetable}
-			is available in the online journal. {\bf For internal collaboration review:
+      objects in Table~\ref{tab:thetable} is available in the online
+      journal. {\bf For internal collaboration review:
       \url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
@@
 Table~\ref{tab:thetable} lists the \nallcands\ objects identified by
-our search.  The ``high-quality sample'' includes \ngoods\ objects,
-which demonstrated what we viewed as unambiguous characteristics of
-the CR phenomenon in at least one TESS sector.  The classification of
-\nmaybes\ CR candidates was ambiguous, and the \ndebunked\ remaining
-objects were false positives that we discuss below.  The
-\texttt{quality} column in the table divides the three classes;
-additional data from TESS or other instruments could help resolve the
-classification of the ambiguous cases.   Of the \ncqvsnodebunked\ CRs
-and candidate CRs, \nbothdipfourier\ were found using both the
-dip-counting and Fourier techniques, \nyesdipnofourier\ were found
-using only the dip-counting technique, and \nyesfouriernodip\ were
-found using only the Fourier technique.  In the following, we will
-restrict our discussion to the high-quality sample, irrespective of
-discovery method.
-
-The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
+our search.  The \ngoods\ stars in the ``good'' sample demonstrated
+what we deemed to be the key characteristics of the CR phenomenon in
+at least one TESS sector.  The classification of \nmaybes\ CR
+candidates was ambiguous, and the \ndebunked\ remaining objects were
+notable false positives that we discuss below.  The \texttt{quality}
+column in the table divides the three classes; additional data from
+TESS or other instruments could help resolve the classification of the
+ambiguous cases.   Of the \ncqvsnodebunked\ CRs and candidate CRs,
+\nbothdipfourier\ were found using both the dip-counting and Fourier
+techniques, \nyesdipnofourier\ were found using only the dip-counting
+technique, and \nyesfouriernodip\ were found using only the Fourier
+technique.  In the following, we will focus our discussion on the good
+sample, irrespective of discovery method.  We will often refer to
+stars by their TIC identifiers; the easiest way to reference these
+against the figures in most document readers is to use a
+``find'' ({\tt Ctrl+F}) utility.
+
+Figure~\ref{fig:cqvs} is a mosaic of phased light curves for the
 \ngoods\ CRs.  The objects are sorted first in order of the number of
@@
 
-In terms of the light curve shapes, Figure~\ref{fig:cqvs} shows a
-broad range of variability, with anywhere from two to eight local
-minima per cycle.  Some stars show relatively ordinary modulation
-during one portion of the phased light curve, and highly structured
-modulation in the remainder of the cycle (e.g.  TIC~206544316,
-TIC~224283342, TIC~402980664).  Others show structured modulation over
-the entire span of a cycle (e.g. TIC~2234692, TIC~425933644,
-TIC~142173958).  Others show some mix between these two modes.
+The light curves show between two and eight local minima per cycle.
+Some stars show ordinary sinusoidal modulation during one portion of
+the phased light curve, and highly structured modulation in the
+remainder of the cycle (e.g. TIC~206544316, TIC~224283342,
+TIC~402980664).  Others show structured modulation over the entire
+span of a cycle (e.g. TIC~2234692, TIC~425933644, TIC~142173958).
+Others show some mix between these two modes.
 
@@
 \nnotfieldbanyan\ memberships were made with low confidence and are
-flagged in Table~\ref{tab:thetable}.  One membership, of TIC~397791443
-in IC\,2602, was made manually from a literature search
-\citep[e.g.][]{2020A&A...633A..99C}.}  The relevant groups are listed
-in Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  The
-most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CRs
-were also identified in the Argus association
-\citep{2019ApJ...870...27Z}, which serves as an indirect line of
-evidence supporting the reality and youth of that group.  The yield in
-Sco-Cen is not surprising since Sco-Cen contains the majority of
-pre-main-sequence stars in the solar neighborhood, and many of its
-stars were selected for TESS 120-second cadence observations by
-various guest investigators.  Given the $\lesssim$$10\%$ completeness
-of TESS beyond 100\,pc, there may be many more CRs in Sco-Cen that
-remain to be discovered.
-
-For the two stars for which BANYAN\,$\Sigma$ did not find any
-association, we were not able to confidently associate either star
-with any young groups.  Both do seem to show the CR signal over
-multiple TESS sectors, and both are photometrically elevated relative
-to the main sequence.  Both were also noted by
-\citet{2021ApJ...917...23K} as being in the ``diffuse'' population of
-$<$50\,Myr stars near the Sun.
+flagged in Table~\ref{tab:thetable}.  The assignment of TIC~397791443
+to IC\,2602 was based not on BANYAN\,$\Sigma$ but instead on a
+literature search \citep[e.g.][]{2020A&A...633A..99C}.}  The relevant
+groups are listed in Table~\ref{tab:thetable}; their ages span
+$\approx$5-200\,Myr.  The groups that contain the largest number of
+CRs in our catalog are Sco-Cen, Tuc-Hor, and Columba.  Six CRs were
+also identified in the Argus association \citep{2019ApJ...870...27Z},
+which serves as an indirect line of evidence supporting the reality
+and youth of that group.  The large contribution from Sco-Cen is not
+surprising since Sco-Cen contains the majority of pre-main-sequence
+stars in the solar neighborhood, and many of its stars were selected
+for TESS 120-second cadence observations by guest investigators.
+Given the $\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there
+may be many more CRs in Sco-Cen that remain to be discovered.
+
+There were two stars for which neither BANYAN\,$\Sigma$ nor a
+literature search led to a confident association with any young group.
+Both stars display CR signals over multiple TESS sectors. Both are
+photometrically elevated relative to the main sequence, an indication
+of youth.  Both were also noted by \citet{2021ApJ...917...23K} as
+being in the ``diffuse'' population of $<$50\,Myr stars near the Sun.
 
@@
 
-The upper age limit for CRs may even pass 200\,Myr, based on the
+The maximum age of CRs might even exceed 200\,Myr, based on the
 candidate membership of TIC~294328887 in the Carina Near moving group
-\citep{2006ApJ...649L.115Z}.  This group's $200 \pm 50$\,Myr age is
-based on the lithium sequence of its G-dwarfs
+\citep{2006ApJ...649L.115Z}.  The estimated age of this group, $200
+\pm 50$\,Myr, is based on the lithium sequence of its G-dwarfs
 \citep{2006ApJ...649L.115Z}, which shows a coeval population of stars
-older than the Pleiades but younger than the 400\,Myr Ursa Major
-moving group.  The formal BANYAN-$\Sigma$ membership probability is
-however somewhat low, perhaps due to the missing radial velocity.
-This lack of information could be resolved by acquiring even a
-medium-resolution spectrum.  An independent assessment of the group's
-kinematics using Gaia data, and its rotation sequence using TESS,
-could lend further credence in such an analysis.
+older than the Pleiades and younger than the 400\,Myr Ursa Major
+moving group.  However, the formal BANYAN-$\Sigma$ membership
+probability is somewhat low (only 6\%), perhaps due to the missing
+radial velocity.  This lack of information could be rectified by
+acquiring even a medium-resolution spectrum.  An independent
+assessment of the group's kinematics using Gaia data, and its rotation
+sequence using TESS, could also bear on the question of whether
+TIC~294328887 is a member.
 
@@
 labeled two objects as having reliable infrared excesses (both $W3$
-and $W4$ at $>$3$\sigma$ above the photospheric prediction).
-
-The two sources exhibiting an IR excess were TIC~193136669 (TWA~34)
-and TIC~57830249 (TWA~33).  Both are in the TW Hydrae association
-($\approx$10\,Myr), and have relatively long periods of 38\,hr and
-44\,hr respectively.  In our initial labeling, we labeled both as
-``ambiguous'' CRs because the dips in their light curves did not show
-the rigid periodicity typical of CRs;  their periods were also
-relatively long.  However, inspection of further sectors clarified
-that both sources are dippers (see online plots in
-Figure~\ref{fig:vet}).  Independently, TIC 193136669 has a cold
-molecular disk based on observed 1.3\,mm continuum emission and
-resolved Keplerian $^{12}{\rm CO}(2-1)$ emission
-\citep{2015A&A...582L...5R}.  It was also labeled a dipper by
+and $W4$ fluxes are more than 3$\sigma$ above the photospheric
+prediction): TIC~193136669 (TWA~34) and TIC~57830249 (TWA~33).
+
+Both of these stars with IR exceses are in the TW Hydrae association
+($\approx$10\,Myr).  They have periods of 38\,hr and 44\,hr,
+respectively.  In our initial labeling, we labeled both as
+``ambiguous'' CRs because the dips in their Sector~36 light curves
+seemed to stochastically evolve over only one or a few cycles, which
+is not typical of CRs; their periods were also long in comparison with
+most of the other CRs.  Inspection of additional sectors clarified
+that both sources are dippers, not CRs (see the online plots in
+Figure~\ref{fig:vet}).  For TIC~57830249, the Sector~10 light curve of
+shows completely different behavior from Sector~36, with variability
+amplitudes of $\pm 50\%$ and no obvious periodicity.  TIC 57830249
+also shows continuum emission at 1.3\,mm \citep{2015A&A...582L...5R},
+which suggests that cold dust grains are present.
+
+The dipper classification of TIC~193136669 is less obvious; the main
+indication that it is a dipper is that Sectors 62 and 63 show its dips
+appearing and disappearing within the span of one cycle.  None of the
+CRs in our sample exhibit this property.  Independently, TIC~193136669
+is known to have a cold disk of dust and molecular gas, based on
+1.3\,mm continuum emission and resolved $^{12}{\rm CO}(2-1)$ emission
+\citep{2015A&A...582L...5R}.  It was labeled a dipper by
 \citet{2022ApJS..263...14C}; we agree with their designation, and
-label it an ``impostor'' CR in Table~\ref{tab:thetable}.  TIC
-57830249 (TWA~33) also has previously detected 1.3\,mm continuum
-emission \citep{2015A&A...582L...5R}, suggestive of cold dust grains
-being present.  It is also a dipper.  Section~\ref{subsec:discdippers}
-highlights plausible evolutionary connections between CRs and dippers
-in light of these ``misclassifications'' .
+label it an ``impostor'' CR in Table~\ref{tab:thetable}.
+Section~\ref{subsec:discdippers} highlights plausible evolutionary
+connections between CRs and dippers in light of these
+``misclassifications''.
 
@@
       ambiguous CR candidates are light blue circles.  Unresolved
-      binaries are flagged either if the Gaia DR3 radial velocity
+      binaries (red circles) are objects for which the Gaia DR3 radial velocity
       scatter exceeded 20\,\kms, or if Gaia ${\rm RUWE}_{\rm DR3}$$>$2
@@
 The main types of binaries of interest in this work were those that
-were unresolved, because they could confuse our understanding of CRs.
+were unresolved, because they can lead to misinterpretations of the data.
 For instance, unresolved binaries might produce multiple photometric
@@
 \url{http://www.rssd.esa.int/doc_fetch.php?  id=3757412}.}  Elevated
-RUWEs imply excess noise relative to a single-source astrometric
-model.  This can be caused by marginally resolved point sources
-skewing the single-transit centroid measurements,  intrinsic
+RUWEs imply excess astrometric noise relative to a single-source
+model.  This can be caused by marginally resolved binaries,  intrinsic
 photometric variability, or intrinsic astrometric motion.  Based on
@@
 flag sources with excess astrometric noise.  This threshold was met
-for \ngoodhighruwe/\ngoods\ high-quality CRs;
-\nmaybehighruwe/\nmaybes\ of the ambiguous ones had this
-characteristic.  There is some subjectivity in where to set the
-threshold, since the RUWE distribution has an extended tail
+by \ngoodhighruwe/\ngoods\ high-quality CRs and by
+\nmaybehighruwe/\nmaybes\ of the ambiguous CRs.  The choice of the threshold RUWE
+is somewhat subjective, since the RUWE distribution has an extended tail
 \citep[e.g.][]{2022MNRAS.513.5270P}.  If we had instead required
@@
 \enddata
-\tablecomments{This table includes \ngoods\ CRs (\texttt{Quality}
+\tablecomments{This table includes \ngoods\ good CRs (\texttt{Quality}
   flag 1), \nmaybes\ ambiguous CRs (\texttt{Quality} flag 0), and

### 2023-08-30 paper/ms.tex
Update ms (JNW comments) - CR evolution
Co-authored-by: Joshua Winn <jnwinn@princeton.edu>

@@
 		\caption{
-      {\bf Validation plots used to  label CRs}.  The complete figure
+      {\bf Validation plots used to classify CRs}.  The complete figure
       set, with one image per sector for each of the \nallcands\
@@
 		\caption{
-			{\bf CRs keep their periods but change their shapes.}
+			{\bf Evolution of CR light curves over two years.}
 			Out of the \ngoods\ CRs in Figure~\ref{fig:cqvs}, 32 had
@@
 			phased to its deepest minimum in flux.  Each panel's title shows
-			the TIC identifier and approximate period in hours.  Text insets
+			the TIC identifier and period in hours.  Text insets
 			show the TESS sector numbers, which generally span two years, or
@@
       {\bf LP 12-502 (TIC~402980664) light curve}, where each time
-      segment represents one TESS orbit.  Data were acquired in Sectors
-      18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  The
-      light curve is binned to 15-minute intervals so that there are
-      96 points per day, and each point is connected by a line.  Data
-      gaps are not interpolated; if data are missing, nothing
-      is plotted.  The red vertical lines highlight apparently
-      instantaneous state changes in the shape of the dip pattern.  
+      segment represents one TESS orbit.  Data were acquired in
+      Sectors 18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.
+      The light curve is binned to 15-minute intervals so that there
+      are 96 points per day, and each point is connected by a line.
+      Data gaps have nothing plotted.  The red vertical lines
+      highlight apparently instantaneous state changes in the shape of
+      the dip pattern.  
 		}
@@
 \subsection{Evolution over two year baseline}
+\label{subsec:twoyear}
 
@@
 confirmed \ngoods\ CRs in our catalog; for plotting purposes we show
-the brightest 27.  We have phased each sector to its own local minimum
-because for most of the sources we do not know the period at the
+the brightest 27.  
+We have defined $\phi=0$ for each sector to be the time of minimum
+light observed in that sector, rather than using a consistent phase
+definition across multiple sectors.
+This is because for most of the sources we do not know the period at the
 precision necessary to be able to accurately propagate an ephemeris
@@
 cycles yields a typical ephemeris uncertainty range of 2-11\,hours.
-Measuring the periods for each sector independently, there did not
-seem to be any significant ($>$3$\sigma$) period changes.  This
-implies an absolute period stability of $\lesssim$0.1\% over the
-two-year baseline.
-
-A few objects in Figure~\ref{fig:evoln}
-show clear signs of
-the CR phenomenon in one sector, and marginal or non-existent signs
-in the other.  While there is subjectivity in this assessment, to our
-eyes, cases for which at least one sector would be flagged as
-``ambiguous'' include
+Measuring the period independently for each sector did not reveal
+evidence for significant ($>$3$\sigma$) changes in period, implying
+a period stability of $\lesssim$0.1\% over two years.
+
+A few objects in Figure~\ref{fig:evoln} show the CR phenomenon in one
+sector, and only marginal signs or no sign of CR behavior in the other
+sector.  In our subjective assessment, cases for which at least one
+sector would be flagged as ``ambiguous'' include
 TIC~368129164 (Sector 23 might be labeled an EB),
@@
 labeled an eclipsing binary---in fact, \citet{2021ApJ...912..123J}
-already gave this source such a label.  However,
-based on the shape evolution between Sectors 13 and 39, it is a
-CR.  Based on the fraction of sources overall that ``turned off'',
-the observed shape evolution implies that CRs have an on-off duty cycle of
-$\approx$75\%.  This type of correction is worth including in
-population-level estimates of how intrinsically common CRs are in the
-low-mass stellar population \citep[e.g.][]{2022AJ....163..144G}.
+already gave this source such a label.  However, based on the shape
+evolution between Sectors 13 and 39, it is a CR.  Based on the
+fraction of sources overall that ``turned off'', the observed shape
+evolution implies that CRs have an on-off duty cycle of $\approx$75\%.
+Correcting for the duty cycle might be important in population-level
+estimates of the intrinsic frequency of the CR phenomenon
+\citep[e.g.][]{2022AJ....163..144G}.
 
@@
 			{\bf Evolution of LP 12-502} ($P$=18.5611\,h) at fixed period and
-			epoch over three years.  Each panel shows one phase-folded TESS
+      epoch over three years.  Each panel shows one (averaged) TESS
 			orbit; small text denotes relative cycle number.  There are 200
 			binned black points per cycle.  The TESS pointing law dictates
-			the large time gaps between Cycles 64-248, 315-1233, and
+			the large time gaps between cycles 64-248, 315-1233, and
 			1264-1410; larger gaps tend to yield larger shape changes.  The
 			dips usually evolve over tens to hundreds of cycles.  However
-			cycles 1233-1264 show a dip that ``switched'' from a depth and
+			cycles 1233-1264 show a dip that switched from a depth and
 			duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than one
@@
     two-harmonic sinusoid has been subtracted to highlight the sharp
-    dips.  In Sectors 25-26 (cycles 248-315), periods are visible at
+    dips.  
+    A fixed period and phase are adopted for all sectors; the dips
+    across all observations are bounded by $\phi \in [-0.35,0.35]$.
+    In Sectors 25-26 (cycles 248-315), periods are visible at
     the fundamental period of 18.5611\,hr, as well as at faster
@@
     relative periods based on the presence of blue dips with distinct
-    slopes.  Multiple simultaneous periods are also visible in Sectors
-    53 and 58-59.  White chunks denote missing data.
+    slopes.  Multiple simultaneous periods are also visible in Sector
+    53 (cycles 1234-1263) and Sectors 58-59 (cycles 1411-1479).  White
+    chunks denote missing data.
+    The state changes noted in red in Figure~\ref{fig:lplc} occur in
+    cycles 261, 309, and 1241.
 	}
@@
 
-\subsection{Evolution over adjacent sectors, \& LP 12-502}
-
-A small fraction of our objects were in regions of sky with many
-sectors of adjacent TESS data.  Out of this already small sample, LP
-12-502 (TIC 402980664; $d$=21\,pc, $J$=9.4, $T$=11.1) stood out due to
-the quality and content of its data.  We discuss another interesting
-source, TIC~300651846, in Appendix~\ref{app:tic3006}.  In this
-section, we first present the LP 12-502 observations and then
-highlight their implications.
+\subsection{Evolution over consecutive sectors, \& LP 12-502}
+
+A few of our complex rotators were near the TESS continuous viewing
+zones (Figure~\ref{fig:catalogscatter}, top right).  Out of this
+already small sample, LP 12-502 (TIC 402980664; $d$=21\,pc, $J$=9.4,
+$T$=11.1) stood out due to the quality and content of its data.  We
+discuss another interesting source, TIC~300651846, in
+Appendix~\ref{app:tic3006}.  In this section, we describe the LP
+12-502 observations and the possible implications.
 
@@
 
-Figure~\ref{fig:lplc} shows all available data for LP 12-502 from TESS
-Sectors 18, 19, 25, 26, 53, 58, and 59, split into successive orbits.
-The star was observed at 120-second cadence whenever it was observable
-by TESS.  We binned the light curve to 15-minute intervals for visual
-clarity, and required at least one (120-second cadence) flux
-measurement per bin.  Points more than 2.5$\sigma$ above the median
-are drawn in gray, also for visual clarity.  Missing data are not
-drawn.  Figure~\ref{fig:lp} then shows the same data, but folded for
-each successive TESS orbit.  Finally, Figure~\ref{fig:lpriver0} shows
-``river plots'' of the same data, split into similar intervals: the
-Sector 18-19 data, 25-26 data, 53 data, and 58-59 data.  The river
-plots are subject to one additional processing step: we fitted and
-subtracted a maximum-likelihood two-harmonic sinusoid independently
-from the Sector 18-19 data, 25-26 data, and 53, 58, and 59 data in
-order to accentuate changes in the dip timing and structure.
+Whenever LP 12-502 was located within a TESS sector, it was observed
+at 120-second cadence.  Figure~\ref{fig:lplc} shows all the available
+data, from Sectors 18, 19, 25, 26, 53, 58, and 59. Vertical offsets
+were applied to separate the data from different spacecraft orbit
+numbers; there are always two orbits per sector.  We binned the light
+curve to 15-minute intervals to facilitate visual inspection.  Points
+more than 2.5$\sigma$ above the median are drawn in gray, to prevent
+outliers from seizing attention.  Data gaps are not connected by lines
+(a common source of confusion in light curve visualization).
+Figure~\ref{fig:lp} shows the same data after phase-folding each TESS
+spacecraft orbit, assuming $P$=18.5611\,hr and a fixed reference epoch
+of BTJD=1791.5367.  Finally, Figure~\ref{fig:lpriver0} shows ``river
+plots'' of the same data, split into similar intervals: the Sector
+18-19 data, 25-26 data, 53 data, and 58-59 data.  The river plots are
+subject to one additional processing step: we fitted and subtracted a
+maximum-likelihood two-harmonic sinusoid independently from the Sector
+18-19 data, 25-26 data, and 53, 58, and 59 data in order to accentuate
+changes in the dip timing and structure.
 
@@
 range between the maximum and minimum sector-specific periods was
-measured to be about one minute.   However, in detail, a period shift
-of $\pm$1\,minute would yield major phase drifts over the baseline;
-that time interval corresponds to $\approx$1/1000$^{\rm th}$ of a
-period, and we have observed 1500 cycles.  By fine-tuning over a grid
-in period, we found $P=18.5611 \pm 0.0001$\,hr, which seems to track
-certain features in the LP 12-502 light curve well over the entire
-dataset.
-
-What exactly is observed?  For the first 64 cycles, the star shows a
-pattern reminiscent of an eclipsing binary, with four obvious local
-minima.  We dub these dips $\{ 1, 2, 3, 4 \}$ at phases $\{ -0.28,
--0.08, 0, 0.25 \}$, respectively.  Over cycles 0-64, the depth of dips
-1 and 3 remain roughly fixed.  However dip 4 decreases in depth by
-about 2\%, while dip 2 increases in depth, by about the same amount
-(see Figure~\ref{fig:lp}).  During cycles 48-64, a fifth dip may also
-be emerging, in the main ``large'' dip group.
-
-There is then a 6-month (184 cycle) gap to Cycles 248-315, which show
+measured to be about one minute.   However, a period shift of
+$\pm$1\,minute leads to large phase drifts over the entire timespan of
+observations.  One minute is $\approx$1/1000$^{\rm th}$ of a period,
+and we have observed 1500 cycles.  By folding with a fine grid of
+trial periods, we found that the choice $P=18.5611 \pm 0.0001$ causes
+more of the features in the LP 12-502 light curve to maintain constant
+phases over the entire dataset.
+
+We now attempt to describe the complex morphology of the light curve
+and its evolution.  For the first 64 cycles, the star shows four
+obvious local minima.  We dub these dips $\{ 1, 2, 3, 4 \}$ at phases
+$\{ -0.28, -0.08, 0, 0.25 \}$, respectively.  Dips 2 and 3 are part of
+the same ``global'' minimum, which otherwise resembles a long eclipse.
+Over cycles 0-64, the depth of dips 1 and 3 remain roughly fixed.  Dip
+4 decreases in depth by about 2\%, and dip 2 increases in depth by
+about the same amount (see Figure~\ref{fig:lp}).  A subtle fifth dip
+may also be present at phase +0.08, at the end of the global minimum
+that includes dips 2 and 3.
+
+There is then a 6-month (184-cycle) gap to Cycles 248-315, which show
 two highly structured dip complexes, plus a small leading dip.  The
-single leading dip is present at the same phase as in cycles 0-64, and
-is therefore likely to be the same structure.  Along a similar line of
-logic, it seems plausible that the first ``dip complex'' during cycles
-248-264 represents an evolution of the initial complex seen during
-cycles 0-64, though with reduced depth.  During cycles 266-310, an
-additional local minimum develops between the two complexes; this
-feature is best visualized on the river plots
-(Figure~\ref{fig:lpriver0}), and we describe its (shorter) period
-below.
+leading dip has the same phase (relative to minimum light) as in
+cycles 0-64, and therefore seems likely to be due to the same
+structure.  Along a similar line of logic, it seems plausible that the
+first ``dip complex'' during cycles 248-264 represents an evolution
+and reduction in amplitude of dips 2 and 3 that were seen during
+cycles 0-64.  During cycles 266-310, an additional local minimum
+develops between the two complexes; this feature is best visualized on
+the river plots (Figure~\ref{fig:lpriver0}), where it is seen to have
+a shorter period than the other dips (as described below).
 
@@
 substructure.  During e.g.~cycles 283-298, this single complex shows
-six local minima.  The deepest dip is sharp: it shows a flux excursion
-of 3.5\% over about 22 minutes (0.02\,$P$), which is the steepest
-slope exhibited anywhere in the LP~12-502 dataset.  After the sharp
-dip, there is a roughly exponential fall-off spanning about a quarter
-of a period, punctuated by coherent local minima and maxima which in
-detail (Figure~\ref{fig:lpriver0}) have slightly longer periods than
-the sharp dip.  The sharp leading dip only decreases in depth
-following a sudden state-switch at BTJD 2030.7 (cycles 299-315), which
-happens during a flare (Figure~\ref{fig:lplc}).  The trailing dips
-remain thereafter.
-
-Sectors 53--58 (cycles 1233-1481) are comparatively tame; they showed
+six local minima.  The first and deepest dip is sharp: it shows a flux
+excursion of 3.5\% over about 22 minutes (0.02\,$P$), which is the
+steepest slope exhibited anywhere in the LP~12-502 dataset.  After the
+sharp dip, there is a roughly exponential return to the baseline flux
+spanning about a quarter of a period, punctuated by coherent local
+minima and maxima that the river plot (Figure~\ref{fig:lpriver0})
+reveals to have slightly longer periods than the sharp dip.  The sharp
+leading dip remains roughly constant in amplitude until a sudden
+``state change'' at BTJD 2030.7 (cycle 309) that occurred at the same
+time as a flare, and left the trailing dips seemingly unaffected.
+This apparent state change, and two others, are marked with red lines
+in Figure~\ref{fig:lplc}.
+
+The behavior during Sectors 53--58 (cycles 1233-1481) is comparatively tame; the light curve shows
 only four to six dips per cycle.  Some dips remain stable in depth and
-duration over this five month interval.  Other dips grow, like the one
+duration over this five-month interval.  Other dips grow, like the one
 at $\phi = +0.06$ between cycles 1499 and 1481.  Other dips, such as
 the one at $\phi = +0.12$ in cycles 1233-1264, disappear entirely.
-The most dramatic state switch occurs during cycles 1233-1247, when a
-large dip ``switches'' from a depth of 3\% and duration of 3 hours to
-a depth of 0.3\%, and a duration of 1 hour.
+The most dramatic state change occurs during cycle 1241, when a large
+dip switches from a depth of 3\% and a duration of 3 hours to a depth
+of 0.3\% and a duration of 1 hour.
 
@@
 
-{\sc State-switches reveal dip independence}---The state-switches seen
+{\sc State-changes reveal dip independence}---The state-changes seen
 in cycles 1233-1247 and 299-315 confirm that dips can disappear in
-less than one cycle, a point which has been previously appreciated
-\citep{2017AJ....153..152S}.  What is new in these particular changes
-is that the morphology changes show that the dips can be {\it
-independent} and {\it additive}.  For example, throughout cycles
-1233-1264, there are three local minima between phases of 0 and 0.3.
-They all have identical ingress times.  The shape change during the
-transition implies that the leading dip that ``turned off'' (reduced
-its depth and duration), while the trailing two dips remained fixed.
-This is visible in Figure~\ref{fig:lp}.  In other words, the
-structures producing these dips are independent to the degree that one
-can undergo a severe change while the others remain identical.  The
-state switches during cycles 248-264 and 299-315 share the same
-characteristic: it is always the {\it leading} dip of a complex that
-``switches off'', leaving the (fixed-depth) trailing dips in its wake.
-
-{\sc Slow growth; rapid death}---Although there are a few instances in
-which we observe dips switch off over less than one cycle, dip growth
-seems to happen more slowly.  For instance, the dip that grows between
-phase 0 and 0.1 between cycles 260-290 begins to become visible around
-BTJD 1993.2, and growths in depth by about 2\% over about six cycles,
-to become visible by eye by BTJD 1997.7.  The evolution of this
-particular dip is most clear in the river plots.  The evolution of the
-latter dip group in cycles 1410-1481 is another example of this slow
-mode of dip growth.
+less than one cycle. While such behavior was also noted by
+\cite{2017AJ....153..152S}, the data presented here show further that
+the dips can be {\it independent} and {\it additive}.  For example,
+throughout cycles 1233-1264, there are three sharp dips between phases
+of 0 and 0.3 with different amplitudes but similar slopes.  During the
+transition, the leading dip nearly disappeared while the other two
+dips hardly changed; compare the centermost two panels of
+Figure~\ref{fig:lp}.  Evidently, the material or process responsible
+for one dip can vary independently of the materials or processes
+responsible for other dips.  The state changes during cycles 248-264
+and 299-315 support the same conclusion, while also hinting that the
+{\it leading} dip of a complex is most prone to disappearing, leaving
+the trailing dips unchanged in its wake.
+
+{\sc Slow growth; rapid death}---LP 12-502 shows at least three
+instances in which dips switch off over less than one cycle; we did
+not see any such instances of dips switching on.  Dip growth instead
+seems to happen more slowly.  For instance, the dip at phase 0-0.1
+between cycles 258-290 begins to become detectable during cycle 258,
+and growths in depth by about 2\% over the next eight cycles.  The
+evolution of this particular dip is most clear in the river plots.
+The evolution of the dip group at phases 0.1-0.3 during cycles
+1410-1481 is another example of this slow mode of dip growth.
 
@@
 individual LP 12-502 dips seems to be $\approx$0.06\,$P$ $\approx$
-1.08\,hr.  In comparison, using the stellar radius and mass derived in
-Section~\ref{subsec:starprops}, the characteristic timescale $T_{\rm
-dur} \equiv R_\star P / (\pi a)$ for the transit of a point-source at
-corotation is 1.02$\pm$0.10\,hr.  This means that while some of the LP
-12-502 dips are sufficiently long to require structures that are
-extended in orbital azimuth, the durations of other dips are
-consistent with effective radii for the occulting material $R_{\rm
-eff} \ll R_\star$.  This implies $a/R_\star \approx 5.8$ for this
-material; the analogous timescale at the stellar surface is about six
-times slower.
+1.08\,hr.  This is very similar to the characteristic timescale of of
+transiting small body at the corotation radius,
+\begin{equation}
+T_{\rm dur} \equiv R_\star P_{\rm rot} / (\pi a) = 1.02\pm 0.10\,{\rm hr},
+\end{equation}
+where we have inserted the stellar radius and mass derived in
+Section~\ref{subsec:starprops}.  Thus, the shortest-duration dips
+could be produced by transits of bodies or distributions of material
+that are smaller than the star.  The corotation radius corresponds to
+$a/R_\star \approx 5.8$, i.e., the transit of a body at the corotation
+radius has a duration about six times shorter than a feature on the
+stellar photosphere that is carried across the visible hemisphere by
+rotation.  On the other hand, some dip durations are sufficiently long
+that an explanation involving transits would require structures that
+are larger than the star along the direction of orbital motion.
 
@@
 $P=18.5611 \pm 0.0001$\,hr.  However the river plots
-(Figure~\ref{fig:lpriver0}) reveal that the light curve has specific
-dips with simultaneous but distinct periods.  For instance, in sectors
-25-26, the local minimum that develops around cycle 262 has a period
-faster than the mean period by $\approx$0.1\%, while some of the
-trailing local minima in the main dip complex have periods slower than
-the mean period, by $\approx$0.04\%.  In addition to the fundamental
-period, we were able to identify at least four distinct periods shown
-by specific dips over the full Sectors 18-59 dataset, including
-periods at 18.5683, 18.5672, 18.5473, and 18.5145\,hr, with a typical
-measurement uncertainty of $\approx$0.0002\,hr.  If each period
-corresponds to an individual dust or gas clump, then this implies that
-multiple distinct clumps can orbit the star simultaneously, at
-marginally different separations.
+(Figure~\ref{fig:lpriver0}) reveal that a few dips have detectably
+distinct periods.  For instance, in sectors 25-26, the dip that
+develops around cycle 262 has a period shorter than the mean period by
+$\approx$0.1\%, and some of the trailing local minima in the main dip
+complex have periods slower than the mean period by $\approx$0.04\%.
+In addition to the fundamental period, we were able to identify at
+least four distinct periods shown by specific dips over the full
+Sectors 18-59 dataset: 18.5683, 18.5672, 18.5473, and 18.5145\,hr,
+with a measurement uncertainty of $\approx$0.0002\,hr. Possibly, the
+different periods belong to clumps of dust or prominences of gas at
+slightly different orbital distances surrounding the corotation
+radius.
 

### 2023-08-30 paper/ms.tex
[WIP] Update ms - discussion - JNW comments
Co-authored-by: Joshua Winn <jnwinn@princeton.edu>

@@
 
-\title{Transient Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Rotators from TESS}
+%\title{Transient Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Rotators from TESS}
+\title{Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS}
 
@@
 \begin{abstract}
-  Complex rotators (CRs) are low-mass pre-main-sequence stars with
-  light curves characterized by periods of 0.2--2 days, amplitudes of
-  a few percent, and slowly-evolving sharp features.  The sharp
-  features might be caused by eclipsing clumps of dust or gas orbiting
-  at the corotation radius.  To improve our understanding of these
+%  This work focuses on a subset of low-mass pre-main-sequence stars
+%  with rotation periods of 0.2--2 days, optical variability amplitudes
+%  of a few percent, and sharp recurring light curve features that last for
+%  hundreds of cycles.  The sharp features are probably caused by
+%  eclipsing clumps of dust or gas orbiting at the corotation radius.
+%  We therefore refer to the objects as ``transient corotating clumps''
+%  (TCCs).
+%
+  Complex rotators (CRs) are low-mass pre-main-sequence stars with light
+  curves characterized by periods of 0.2--2 days, amplitudes of a few
+  percent, and slowly-evolving sharp features.  The sharp features
+  might be caused by eclipsing clumps of dust or gas orbiting at the
+  corotation radius.
+  To improve our understanding of these
   enigmatic stars, we conducted a survey for CRs using TESS
@@
 Data from K2 \citep{2014PASP..126..398H} and TESS
-\citep{2015JATIS...1a4003R} have revealed a new class of variable
-star for which the root cause of variability is only beginning to
-become clear: complex rotators (CRs).  These objects
-are identified from their optical light curves, which show nearly
-periodic troughs that are either sharp or broad; these troughs are
-often superposed on quasi-sinusoidal spot-like modulation
+\citep{2015JATIS...1a4003R} have revealed a new class of variable star
+for which the root cause of variability is only beginning to become
+clear: complex rotators (CRs).  These objects are identified from
+their optical light curves, which show nearly periodic troughs that
+are either sharp or broad; these troughs are often superposed on
+quasi-sinusoidal spot-like modulation
 \citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z}.
@@
 marginally-ionized gas that are embedded within the hotter corona and
-corotate with the star
+that corotate with the star
 \citep{1989MNRAS.238..657C,2019MNRAS.482.2853J,2022MNRAS.514.5465W}.
-These hypothetical structures are analogous to quiescent prominences
+These hypothetical prominences are analogous to quiescent prominences
 and filaments seen in the solar corona \citep[see
@@
 fraction of the stellar radius as in the solar case, they would exist
-at distances of a few stellar radii.  A final possibility is that a
-thin optically-thick ring obscures a small portion of the stellar
+at distances of a few stellar radii.  A final possibility is that an
+optically-thick ring obscures a small portion of the stellar
 photosphere \citep{2019ApJ...876..127Z}.  Hot spots passing behind
 such a ring could produce sudden dips.  We do not favor this scenario
-due to two issues discussed in Appendix~\ref{app:ring}.
-
-The dust clump and prominence hypotheses are qualitatively similar,
-except that one invokes opacity from dust, while the other invokes
-opacity from gas, likely bound-free transitions in hydrogen or perhaps
-a molecular opacity.  However unambiguous evidence in support of any
-particular scenario has yet to be acquired.  Such evidence might
-include a spectroscopic detection of silicate 10\,$\mu$m dust
-absorption during a dip, or perhaps detection of transient Balmer-line
-excesses as a function of cycle phase, similar to observations made in
-systems such as AB~Dor \citep[see][]{1999ASPC..158..146C} or PTFO
-8-8695 \citep{2016ApJ...830...15J}.
-
-CRs remain mysterious because they have been both hard to discover and
-hard to characterize.   They are hard to discover because they are
-rare: CRs comprise $\approx$1\% of the youngest $\approx$1\% of M
-dwarfs \citep{2018AJ....155..196R}.  Out of the millions of stars
-monitored by K2 and TESS, about 50 CRs have been reported to date
+(see Appendix~\ref{app:ring}).
+
+The dust clump and gas prominence hypotheses are geometrically
+indistinguishable; one could imagine dust or gas accumulating in
+either of the geometries shown in Figure~\ref{fig:f1}.  The main
+distinguishing factor between the two models is the composition of the
+occulting material.   ``Dust clumps'' invoke opacity from dust, which
+would need to be collisionally charged \citep{2023MNRAS.518.4734S}.
+``Gas prominences'' invoke opacity from partially-ionized gas, likely
+bound-free transitions in hydrogen or perhaps a molecular opacity.
+Unambiguous evidence in support of either scenario has yet to be
+acquired.  Such evidence might include a spectroscopic detection of
+silicate 10\,$\mu$m dust absorption during a dip, or perhaps detection
+of transient Balmer-line excesses as a function of cycle phase,
+similar to observations made in systems such as AB~Dor
+\citep[see][]{1999ASPC..158..146C} or PTFO 8-8695
+\citep{2016ApJ...830...15J}.
+
+In both models, the corotation radius is the location at which matter
+concentrates.  This is empirically justified by the observation that
+the sharp CR features are superposed over smooth, quasi-sinusoidal
+starspot profiles.  The theoretical importance of the corotation
+radius has been discussed in studies of rapid magnetic rotators,
+including neutron stars \citep[e.g.]{1973ApJ...184..271L}, magnetic
+massive stars \citep[e.g.][]{1985Ap&SS.116..285N}, and accreting T
+Tauri stars \citep[e.g.][]{2005ApJ...634.1214L}.  In regions where the
+magnetic field dominates the flow (i.e.  $B^2/8\pi > \rho v^2 /2$),
+matter is dragged along with the field lines.  Assuming a dipolar
+magnetic field geometry, then the tendency of both gas and dust to
+become trapped at corotation is tied to how of the four relevant
+forces -- gravity, Lorentz, inertial Coriolis, and inertial
+centrifugal -- the Lorentz and Coriolis only act perpendicular to
+field lines, while gravity and the centrifugal force are in balance at
+$R_{\rm c}$ \citep[e.g.][Sec.~2]{2005MNRAS.357..251T}.  Another way to
+phrase this statement is that there is a local minimum in the
+effective potential of the corotating frame; given a flow from the
+either the star or from a tenuous accretion disk, this local potential
+minimum enables material to build up \citep{2005MNRAS.357..251T}.
+
+While theoretical heritage for understanding rapid magnetic
+rotators exists, CRs have remained mysterious because they have been both
+hard to discover and hard to characterize.   They are hard to discover
+because they are rare: CRs comprise $\approx$1\% of the youngest
+$\approx$1\% of M dwarfs \citep{2018AJ....155..196R}.  Out of the
+millions of stars monitored by K2 and TESS, about 50 CRs have been
+reported to date
 \citep{2016AJ....152..114R,2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2020AJ....160...86B,2022AJ....163..144G,2023ApJ...945..114P}.
@@
       \citet{2016AJ....152..114R}.  The lower-middle panel plots the
-      derived corotation radii $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in
+      derived corotation radii $R_{\rm c} = (GM/\Omega^2)^{1/3}$ in
       units of stellar radii against the measured CR periods, in
@@
 
-Figure~\ref{fig:catalogscatter} shows derived stellar properties for
-our CR catalog, and compares the CRs against both the target star
-sample (top panels), and against stars in the Pleiades
-\citep{2016AJ....152..114R}.  Typical CR masses span
-0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This mass and
-age range includes both fully convective stars
-($M_\star$$\lesssim$0.25\,$M_\odot$), and stars with a combination of
-radiative cores and convective envelopes
-($M_\star$$\gtrsim$0.25\,$M_\odot$; \citealt{2018A&A...619A.177B}).
-We found no obvious light curve morphology differences between the two
-classes.  In terms of their rotation rates relative to the Pleiades,
-the CRs are among the more rapidly rotating half of M dwarfs.
-
-The closest CR in our catalog is DG~CVn (TIC~368129164;
-$d$$=$18\,pc), a member of AB Dor.  To our knowledge, this work is the
-first time that it has been noted as a CR.  The three brightest CRs
-are DG~CVn ($T$=9.3), TIC~405754448 ($T$=9.6), and TIC~167664935
-($T$=10.3).  The shortest period belongs to TIC~201789285, at
-3.64\,hr.  The longest period belongs to TIC~405910546, at 37.9\,hr.
-If the latter source turns out to be an eclipsing binary, the
-next-longest would be TIC~193831684 (31.0\,hr).
+Referring back to Figure~\ref{fig:catalogscatter}, which compares the
+properties of CRs with those of the search sample (top panels) and the
+Pleiades \citep{2016AJ....152..114R}, we see that the typical CR
+masses span 0.1-0.4\,$M_\odot$, and the typical ages span 2-150\,Myr.
+This mass and age range includes both fully convective stars and stars
+with a combination of radiative cores and convective envelopes, with
+the dividing line at around $M_\star = 0.25\,M_\odot$
+\citep{2018A&A...619A.177B}.  We found no obvious differences in light
+curve morphology between CRs above and below the boundary of
+0.25\,$M_\odot$.  In terms of their rotation rates relative to the
+Pleiades, the CRs are among the more rapidly rotating half of M
+dwarfs.
+
+The closest CR in our catalog is DG~CVn (TIC~368129164; $d$$=$18\,pc),
+a member of AB Dor.  To our knowledge, this star had not previously
+been recognized as a CR.  The three brightest CRs are DG~CVn
+($T$=9.3), TIC~405754448 ($T$=9.6), and TIC~167664935 ($T$=10.3).  The
+shortest period, 3.64\,hr, belongs to TIC~201789285.  The longest
+period, 37.9\,hr, belongs to TIC~405910546.  If the latter source
+turns out to be an eclipsing binary, the longest-period CR in the
+catalog would be TIC~193831684 (31.0\,hr).  By definition, we required
+the periods to be below 48\,hr.
 
 The lowest mass ($\approx$$0.12$\,$M_\odot$) belongs to TIC~267953787.
-The catalog contains a few other stars with similar mass.  Given the
-small number of sub-stellar mass objects in our target sample, future
-studies of brown dwarf photometric variability might also yield CRs,
-though there could be degeneracies in interpretation with planetary
-surface features such as clouds and latitudinal bands
-\citep[e.g.][]{2021ApJ...906...64A,2022ApJ...924...68V}.
+The catalog contains a few other stars with similar mass.  We cannot
+rule out the possibility that CRs exist with even lower masses, given
+the small number of such low-mass stars in our target sample.  Perhaps
+even brown dwarfs can be CRs, although it might be difficult to
+distinguish the type of variability we associate with CRs from the
+usual variability of brown dwarfs caused by clouds and latitudinal
+bands \citep[e.g.][]{2021ApJ...906...64A,2022ApJ...924...68V}.
 
@@
 (\ngoodruweandmultperiod/\ngoodhighruwe\ high-quality CRs).  The
-latter point strongly corroborates the idea that most sources with
-RUWE$_{\rm DR3}$$>$2 are intermediate separation binaries with
-projected apparent separations below 1$''$, and projected physical
-separations $\lesssim$50\,AU.
-
-The multiplicity rate of M dwarfs near the Sun is 26.8$\pm$1.4\%
-\citep{2019AJ....157..216W}.  Based on the same study, the peak of the
-separation distribution decreases from $\approx$49\,AU for
-$0.30$-$0.60$\,$M_\odot$ stars, to $\approx$11\,AU for
+latter observation corroborates the claim that most sources with
+RUWE$_{\rm DR3}$$>$2 are binaries with projected apparent separations
+below 1$''$, and projected physical separations $\lesssim$50\,AU.
+
+One possible relation between binarity and CRs is that the presence of
+an intermediate-separation binary could cause early disk dispersal,
+freeing the star to contract.  The CR phenomenon seems to require
+rapid rotation; thus if binary systems tend to produce more rapidly
+rotating stars, we would expect a sample of CRs to have a larger
+binary fraction than the field.  We do not see clear evidence for such
+an effect.  The multiplicity rate of M dwarfs near the Sun is
+26.8$\pm$1.4\% \citep{2019AJ....157..216W}.  Based on the same study,
+the peak of the separation distribution decreases from $\approx$49\,AU
+for $0.30$-$0.60$\,$M_\odot$ stars, to $\approx$11\,AU for
 $0.15$-$0.30$\,$M_\odot$ M dwarfs.  The multiplicity fraction in our
-CR sample seems either consistent or perhaps marginally higher than
-the field fraction.  This could plausibly be understood in a physical
-framework in which the presence of intermediate-separation binaries
-causes early disk dispersal, freeing the star to contract.  The CR
-phenomenon seems to require rapid rotation; thus if binary systems
-tend to produce more rapidly rotating stars, we would expect a sample
-of CRs to have a larger binary fraction than the field.
+CR sample seems approximately consistent with this field fraction.
 
@@
 \citep{2017AJ....153..152S,2022AJ....163..144G}.  However the two most
-massive CRs in our sample, TIC~405754448 and TIC~405910546, appear to
-have masses of $\approx$0.82\,$M_\odot$ and $\approx$0.60\,$M_\odot$
-respectively.  The next-highest masses in our sample are
-$\approx$0.40\,$M_\odot$.
-
-Based on their locations in the color--absolute magnitude
-diagram and membership in LCC, both of the K dwarfs do indeed appear
-to be high mass.  However in detail, both are subject to ambiguities
+massive CRs in our sample, TIC~405754448 and TIC~405910546, were
+assigned masses of $\approx$0.82\,$M_\odot$ and
+$\approx$0.60\,$M_\odot$ respectively.  The next-highest masses in our
+sample are $\approx$0.40\,$M_\odot$.
+
+These stars' locations in color--absolute magnitude diagrams and
+their probable membership in Lower Centaurus Crux both support the
+conclusion that they have relatively high masses.
+However in detail, both are subject to ambiguities
 in interpretation.  The TIC~405910546 light curve has a unique shape,
@@
 velocity scatter exceeding 20\,\kms.  Combined, these factors suggest
-that TIC~405910546 might be a pre-main-sequence eclipsing binary; it
-should be studied further to clarify this classification.  For
-TIC~405754448, we believe that the source {\it is} an unresolved
-binary, because RUWE$_{\rm DR3}$=6.8, and because the raw light curves
-in Sectors 11, 37, and 38 show an additional $\approx$6.5\,day,
-$\approx$0.3\% amplitude sinusoidal signal suggestive of an unresolved
-photometric companion.  If TIC~405754448 is a K+M binary, then the
+that TIC~405910546 could be a pre-main-sequence eclipsing binary; it
+should be studied further to clarify this classification.
+
+For the other object, TIC~405754448, the evidence for binarity is
+stronger.  The RUWE$_{\rm DR3}$ statistic is 6.8, and the raw light
+curves in Sectors 11, 37, and 38 show both the CR signal with period
+12.9\,hr and amplitude $\approx$1\% and an additional sinusoidal
+signal with a period $\approx$6.5\,days and amplitude $\approx$0.3\%,
+likely from a second star.  If TIC~405754448 is a K+M binary, then the
 flux ratio between the primary and secondary would be expected to be
-$\approx$10:1.  It would be challenging for the M dwarf to produce the
-observed 12.9\,hr signal with such a flux deficit, but not impossible.
-While both of these objects suggest that the CR phenomenon may extend
-up in mass to pre-main-sequence K dwarfs, more data are needed to
-fully substantiate this claim.
+$\approx$10:1.  Thus, if the K star were the source of the CR signal,
+its intrinsic variability amplitude would be $\approx$1\%, while if
+the M star were responsible its intrinsic variability amplitude would
+be $\approx$10\%.
+
+In short, these two objects suggest that the CR phenomenon may extend
+up in mass to pre-main-sequence K dwarfs, but more data are needed to
+substantiate this claim.
 
@@
 minimized the dispersion in the phase-folded light curve.  More
-careful inspection however showed that it is an impostor:
+careful inspection revealed an impostor:
 this source is a photometric blend of two ordinary rotating stars with
-$P_0$=3.60\,hr, and $P_1$=5.41\,hr, with a beat period $(P_0^{-1} -
+$P_0$=3.60\,hr, and $P_1$=5.41\,hr, giving a beat period $(P_0^{-1} -
 P_1^{-1})^{-1}$ of 10.8\,hr.  This is a novel false positive scenario
@@
 
-TIC~142173958 and TIC~425937691 both show evidence for two separate
-CR signals in their TESS light curves.  For TIC~142173958, the
-signals are at 11.76\,hr and 12.84\,hr.  For TIC~425937691, they are
-at $\approx$4.82\,hr and $\approx$3.22\,hr, near the 3:2
-commensurability.  Given that both sources have two photometric
-signals and elevated RUWEs, they are probably unresolved binaries
-consisting of two independent CRs.  Recent work has shown that the
-orbits of binaries closer than $\lesssim$700 AU tend to be aligned
-with their planetary systems \citep[e.g.][]{2022AJ....163..207C}.  If
-we assume that observing CR variability similarly requires near
-edge-on viewing geometries, then we might expect a sufficiently close
-binary with one CR to also have another, since the spin axes in
-sufficiently close binaries would tend to be aligned.  In this
-scenario, the two periods of TIC~425937691 being within $\lesssim$1\%
-of the 3:2 period commensurability would simply be a coincidence.
-
-\subsection{CRs are quasiperiodic}
-
-A periodic signal repeats exactly; the CRs do not
-(Figure~\ref{fig:evoln}).  While their periods appear to remain
-constant to within measurement precision over thousands of cycles, the
-light curve shapes evolve over 10 to 1{,}000 cycles.  They are
-therefore {\it quasi}periodic.  While this observation is consistent
-with the analyses by \citet{2022AJ....163..144G} and
+TIC~142173958 and TIC~425937691 both show evidence for two separate CR
+signals in their TESS light curves.  For TIC~142173958, the signals
+have periods of 11.76\,hr and 12.84\,hr.  For TIC~425937691, the two
+periods are 4.82\,hr and 3.22\,hr, near the 3:2 commensurability.
+Given that both sources have two photometric signals and elevated
+RUWEs, each source is probably an unresolved binary consisting of two
+CRs.
+
+Recent work has shown that the orbits of binaries closer than
+$\lesssim$700 AU tend to be aligned with their planetary systems
+\citep[e.g.][]{2022AJ....163..207C}.  If we assume that observing CR
+variability requires high inclinations relative to the line of sight,
+and that the inclinations in binaries are correlated, then we would
+expect the detection of one CR in a binary system to raise the
+probability that the other star is a CR.  The limitations of the
+current catalog prevent further exploration of this issue, but it
+might be interesting for future study.  Even if this scenario is
+correct, it would not provide an immediate explanation for the
+near-commensurability of the two periods of TIC~425937691 (the ratio
+is within 1\% of 3:2).
+
+\subsection{Transience \& special phases of CR dips}
+
+While CR periods appear to remain constant to within measurement
+precision over thousands of cycles, the light curve shapes evolve over
+typical timescales of 10 to 1{,}000 cycles (e.g.
+Figures~\ref{fig:evoln} and~\ref{fig:lpriver0}).  The CRs are
+therefore quasiperiodic, with a characteristic dip longevity of
+$\approx$100 cycles.  While this observation is consistent with the
+analyses by \citet{2022AJ....163..144G} and
 \citet{2023ApJ...945..114P}, it marks a qualitative departure from the
 ``persistent'' {\it vs.} ``transient'' flux dip distinction described
-by \citet{2017AJ....153..152S}, since all CR dips seem to be
-transient over timescales of more than 1{,}000 cycles
-(Figure~\ref{fig:evoln}).
-
-With that said, one might expect a truly quasiperiodic process to be
-able to explore all phase angles with equal weight.  LP 12-502, and
-perhaps other CRs, seem to have preferred phases.  For LP 12-502, all
-of the dips happen over phases corresponding to only two thirds of the
-period (Figure~\ref{fig:lp}).  The remaining third seems to be ``out
-of limits'' for any dipping material.  This could be evidence that the
-stellar magnetic field is strongly asymmetric, and can hold extrinsic
-material at corotation, but only over two thirds of the equatorial
-circle.  Alternatively, the source of the material (e.g. a
-planetesimal swarm) might be distributed over an arc of the same
-angular extent (240$^\circ$).  We favor the former explanation, for
-reasons discussed below.
+by \citet{2017AJ....153..152S}, since all CR dips seem to be transient
+over timescales of more than 1{,}000 cycles (Figure~\ref{fig:evoln}).
+
+One peculiarity of CR evolution however is that the dips do not
+explore all phase angles with equal weight.  LP 12-502, and other CRs,
+have preferred phases lasting for at least two years.  For LP 12-502,
+all of the dips happen over phases corresponding to only two thirds of
+the period (Figures~\ref{fig:lp} and~\ref{fig:lpriver0}).  The
+remaining third seems to be ``out of limits'' for dips over the
+timespan of observations.  This could be evidence that the stellar
+magnetic field is not azimuthally symmetric.  Alternatively, the
+source of the material (e.g. a planetesimal swarm) might be
+distributed over an arc rather than occurring randomly around the
+entire orbit.
 
@@
 
-The asymmetry of a dip can help diagnose the optical depth of the
-occulting material as a function of orbital phase angle.  Sharp
-leading edges with trailing exponential egresses for instance have
-been previously seen for transiting exocomets and disintegrating rocky
-bodies
+The asymmetry of a dip around the time of minimum light might be
+caused by the variation in optical depth of the occulting material as
+a function of orbital phase angle.  Sharp leading edges with trailing
+exponential egresses, for instance, have been previously seen for
+transiting exocomets and disintegrating rocky bodies
 \citep[e.g.][]{2012ApJ...752....1R,2012A&A...545L...5B,2015Natur.526..546V,2019A&A...625L..13Z}.
 
-Examining Figure~\ref{fig:cqvs}, it is not obvious whether CRs as a
-whole show any preference for sharper ingresses, or sharper egresses.
-In some cases (e.g. TIC~425933644), the continuum itself is not
-well-defined, and so the meaning of ``ingress'' and ``egress'' are not
-clear.  In others, such as Sector~36 of TIC~89463560, there is a
-single clear sharp ingress with an exponential egress, which could be
-fitted using e.g.~a model analogous to those used for exocomets
-\citep[e.g.][]{2018MNRAS.474.1453R,2019A&A...625L..13Z}.  The main quantities of interest
-in such models would be the exponential decay time- and therefore
-length-scale, as well as the impact parameter and the inferred transit
-depth (and its implications for the equivalent ``radius'' of the
-transiting cloud).  We briefly explored such models, until it
-became clear that careful modeling of sources such as LP
-12-502 merits its own in-depth study.  Connections could likely also
-be made to the toroidal geometries that can be produced by outflowing
-atmospheres of transiting planets
+Examining Figure~\ref{fig:cqvs}, it is clear that CR dips can be
+asymmetric but it is not obvious whether there is a preference for
+sharper ingresses or sharper egresses.  In some cases (e.g.
+TIC~425933644), the flux variations do not resemble isolated dips,
+making the meaning of ``ingress'' and ``egress'' unclear.  In other
+cases, such as Sector~36 of TIC~89463560, there is a sharp drop with
+an exponential return to the baseline flux, resembling the signatures
+of exocomet \citep[e.g.][]{2018MNRAS.474.1453R,2019A&A...625L..13Z},
+or the outflowing exospheres of certain transiting planets
 \citep[e.g.][]{2019ApJ...873...89M,2022ApJ...926..226M}.
 
-\subsection{Dust, or gas?}
-
-We believe that the most likely scenarios to explain CRs are either
-the dust clump scenario or the prominence scenario
-(Figure~\ref{fig:f1}).  Both invoke clumpy material that would be
-magnetically confined at the corotation radius.  The prominence idea
-has a longer history, based on analogy with quiescent
-prominences/filaments observed to exist in the solar corona for up to
-a few weeks \citep[see][]{2015ASSL..415.....V}.  In an extrasolar
-context, spectroscopic detections of transient Balmer- and
-resonance-line absorption seen for stars such as AB~Dor and Speedy~Mic
+\subsection{Dust vs. gas}
+
+Both the dust clump and the gas prominence scenario invoke clumps
+of material at the corotation radius;
+the main property that we believe distinguishes the two ideas is 
+the composition of the material.
+
+\subsubsection{What is a prominence?}
+The prominence idea is based on an analogy with quiescent
+prominences/filaments in the solar corona that last as long as a few
+weeks \citep[see][]{2015ASSL..415.....V}.  In the context of the Sun,
+a prominence is a clump of cold, partially ionized hydrogen viewed in
+emission against the dark backdrop of space.  A filament is the same
+clump of plasma, but viewed in absorption against the solar disk.  In
+an extrasolar context, spectroscopic detections of transient Balmer-
+and resonance-line absorption seen for stars such as AB~Dor and
+Speedy~Mic
 \citep[e.g.][]{1989MNRAS.238..657C,1993MNRAS.262..369J,2006MNRAS.365..530D,2016MNRAS.463..965L}
-led to the interpretation that the data could best be explained by
-similar structures: cold, minimally ionized hydrogen clouds or
-filaments that scatter chromospheric emission from the star to produce
-the observed spectroscopic line variations
-\citep[see][]{1989MNRAS.238..657C}.  The short-term mechanical
-stability of such gas configurations is theoretically plausible
-\citep{2000MNRAS.316..647F,2022MNRAS.514.5465W}, and the
-interpretation of this class of observations seems at least somewhat
-secure.
-
-A clear link between the dense gas clumps (prominences) that likely
-exist around rapidly rotating low-mass stars and the CR phenomenon
-has yet to be made.  A simple visual examination of the TESS light
-curves for five prominence-hosting systems studied by
+have been interpreted as prominences that scatter a star's
+chromospheric emission \citep[see][]{1989MNRAS.238..657C}.  The
+short-term mechanical stability of such gas configurations is
+theoretically plausible for such stars
+\citep{2000MNRAS.316..647F,2022MNRAS.514.5465W}.   To our best
+knowledge, this class of spectroscopic observation also has no viable
+alternative explanations.
+
+We performed a simple visual examination of the TESS light curves for
+five prominence-hosting systems studied by
 \citet{2019MNRAS.482.2853J}--AB~Dor, Speedy~Mic, LQ Lup, HK Aqr, and
-V374 Peg--revealed no obvious CR behavior, though all show
-differential evolution, and Speedy~Mic shows two closely-spaced
-periods and a strong beat.  Spectroscopically observable prominences
-do not imply photometric CR-like dips.
-
-The key difference between the prominence and dust clump scenarios is
-in whether the occulting material of interest is neutral hydrogen, or
-dust.  In the phrasing of the ``frozen flux'' condition of ideal rigid
-field magnetohydrodynamics, the tendency of both to become trapped at
-the corotation radius in the equatorial plane is tied to how of the
-four relevant forces (gravity, Lorentz, inertial Coriolis, and
-inertial centrifugal), the Lorentz and Coriolis only act perpendicular
-to field lines, while gravity and the centrifugal force are in balance
-at $R_{\rm cr}$ \citep[see][Sec.~2]{2005MNRAS.357..251T}.  
-This assumes that the magnetic field dominates the flow, i.e., that
-$B^2/8\pi > \rho v^2 /2$, so that matter is dragged along with the
-field lines.
-The locations where this condition holds may ultimately determine where
-matter can accumulate.
-
-%The magnetic field strength is only relevant in this formulation of
-%the system in that we must have $ R_{\rm cr} < R_{\rm M}$ in
-%order for closed loops to exist that can support prominences
-%\citep[e.g.][]{1985Ap&SS.116..285N,2019MNRAS.482.2853J}.  In detail
-%however, the locations of such magnetic fixed points depends on the
-%star's magnetic field topology.
-
-\subsubsection{Gas absorption microphysics}
+V374 Peg--and detected no CR behavior.  Assuming that
+spectroscopically observable prominence systems do not turn off, this would
+imply that they are not always accompanied by photometric CR-like
+dips: a link between the spectroscopic prominences
+that may exist around rapidly rotating low-mass stars and the CR
+phenomenon has yet to be made.
+
+\subsubsection{What is the microphysical source of opacity?}
 
@@
 \citep{2017PASJ...69L...2O,2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
-For neutral hydrogen to produce this effect in absorption, its opacity
-must be larger in the blue than in the red.
-\citet{1992oasp.book.....G} suggests that this might be
-microphysically possible: while bound-bound absorption provides
-opacity only at narrow resonant lines, the hydrogen opacity due to
-bound-free absorption is ``jagged'' \citep[see][Figure 8.5 and
+Dust can naturally explain this chromaticity, since it has a larger
+absorption cross-section in the blue than the red
+\citep[e.g.][]{1989ApJ...345..245C}.  Gas might also explain the observed
+chromaticities \citep{1992oasp.book.....G}.  While bound-bound
+absorption can be excluded, since it provides opacity only at narrow
+resonant lines, the (neutral) hydrogen opacity due to bound-free
+absorption is ``jagged'' \citep[see][Figure 8.5 and
 Eq.~8.8]{1992oasp.book.....G}, such that at temperatures of
-$\approx$3{,}000\,K to $\approx$10{,}000\,K the observed
-chromaticities might be reproduced.  While bound-free absorption of
-${\rm H}^{-}$ seems like it should be important at such cool
-temperatures, in detail this opacity source has the {\it opposite
-sign} from what is required to produce deeper dips in the blue than in
-the red.  Thomson scattering is similarly ruled out as a relevant
-opacity source, because it is gray.  The final plausible alternative
-opacity source is dust, which has the requisite larger absorption
-cross-section in the blue than the red \citep{1989ApJ...345..245C}.
+$\approx$3{,}000\,K to $\approx$10{,}000\,K the opacity can be larger
+at blue wavelengths than at red wavelengths.  Bound-free absorption of
+${\rm H}^{-}$ is often important at such temperatures, but this
+opacity source is stronger in the red than the blue, the opposite of
+what is required to produce deeper dips in the blue than in the red.
+Likewise, Thomson scattering is too gray to be the dominant opacity
+source.
 
@@
 spectroscopic observations of this star have been understood in terms
-of a warped torus of circumstellar material, analogous to the
-geometries we are discussing for much cooler M dwarfs
+of a warped torus of corotating circumstellar material
 \citep{1978ApJ...224L...5L,1985Ap&SS.116..285N,2005ApJ...630L..81T}.
-This material is unlikely to be dust, due to the relevant sublimation
-timescales.  The opacity is instead thought to be sourced from
-bound-free absorption from neutral hydrogen
-\citep{1985Ap&SS.116..285N}, although to our best knowledge direct
-evidence for this conclusion has yet to be acquired.  Separate and
-smaller-amplitude emission in $\sigma$~Ori~E may also come from
-electrons scattering photospheric light toward the observer when the
-clouds are not in transit \citep{2022MNRAS.511.4815B}.
+The circumstellar material is unlikely to be dust, which would
+sublimate quickly at the distance of the torus from the
+star.\footnote{\citet{2019ApJ...876..127Z} explored the sublimation
+timescales for a canonical CR with $M_\star=0.2\,M_\odot$,
+$R_\star=0.3\,R_\odot$, and $T_{\rm eff}=3200\,{\rm K}$.  They found
+that non-shielded, generic silicate dust mixture \citep{1985ApJS...57..587D} with a
+single size of 0.1\,$\mu$m reached the $\approx$1500\,K sublimination
+temperature at $\approx$3\,$R_\star$.  This suggests that dust
+sublimation could be an important effect even for CRs. }  The opacity
+source for $\sigma$~Ori~E and its analogs is instead thought to be
+bound-free absorption by neutral hydrogen \citep{1985Ap&SS.116..285N},
+although to our best knowledge direct evidence for this conclusion has
+yet to be acquired.  Separate and smaller-amplitude continuum flux
+brightenings in $\sigma$~Ori~E may also come from electrons scattering
+photospheric light toward the observer when the clouds are not
+transiting \citep{2022MNRAS.511.4815B}.
 
@@
 radiative transfer.  This issue has a key ability to resolve the
-question of whether the CRs are explained by dust or by gas, which
-has bearing on whether the material producing the dips is coming from
-the star, or whether it is a byproduct of the protoplanetary disk.
-
-%\subsubsection{Why corotation?}
-
-% The stable point only exists if R_A > R_K.  For radii between R_A
-% and R_K in such cases, consider a magnetic field line extending out
-% beyond R_K.  Whenever R>R_K, the material is centrifugally supported
-% (pushed out by the ~Ω^2R^2 centrifugal term in the corotating
-% frame).  If R<R_K in such cases along a given field line, the
-% material will fall back to the star.  So there are two conditions
-% that must be met: the star must spin fast enough, and closed
-% magnetic loops must extend beyond the corotation radius.  (This is
-% all spelled out by Nakajima1985, and Petit2013).
+question of whether the CRs are explained by dust or by gas, which has
+bearing on whether the material producing the dips is coming from the
+star, or whether it is a byproduct of the protoplanetary disk.
 
@@
 
-Independent of the microphysical basis for gas absorption, the
-observed lifetime of the CR phenomenon could provide another
-dimension to discern between the gas vs.~dust clump scenarios.
-Based on the available statistics from e.g.
-\citet{2022AJ....164...80R} and references therein, it seems plausible
-that CR occurrence decreases in time, bottoming to zero well before
-the $\approx$700\,Myr age of Praesepe.  This is odd in the context of
-the prominence scenario, because pre-main-sequence M dwarfs spin up
-over the first $\approx$$10^8$\,yr; prominences might even be expected
-to be {\it more} common at the age of the Pleiades than for younger
-stars.  This broadly assumes that any star that can support
-prominences will do so, and that the magnetic topology of rapidly
-rotating M dwarfs at 100\,Myr is similar to that of rapidly rotating M
-dwarfs at say, 10\,Myr.  Based on the degree to which M dwarfs remain
-rapid rotators over the first few gigayears of their lives
-\citep[e.g.][]{2022AJ....164...80R,2022ApJ...936..109P}, it seems
-surprising in the gas clump (prominence) scenario that very few stars
-older than 150\,Myr have been seen to exhibit the phenomenon.  In the
-dust clump scenario this is not a problem, because if the dust were
-externally sourced, it would be expected to have a finite supply.
+The observed lifetime of the CR phenomenon could provide another way
+to discern between the gas and dust clump scenarios.  Based on the
+available statistics from e.g.  \citet{2022AJ....164...80R} and
+references therein, it seems plausible that CR occurrence decreases
+with stellar age from $\approx$3\% at 10\,Myr (Sco-Cen),
+to $\approx$1\% at 100\,Myr (Pleiades),
+down to 0\% by the $\approx$700\,Myr
+age of Praesepe.  This is odd in the context of the prominence
+scenario, because pre-main-sequence M dwarfs spin up over the first
+100\,Myr; prominences might therefore even be expected to be {\it
+more} common at 100\,Myr than at 10\,Myr, under the assumption that the
+production of prominences depends only on the stellar rotation rate. 
+The dust clump scenario would hold a natural explanation: the lower occurrence of CRs around older stars would
+simply reflect a finite supply of dust.
+One possible complication however is that the magnetic field topology
+of rapidly rotating M dwarfs may depend on factors other than the
+rotation rate (e.g. the age), which might affect the production of prominences.
 
@@
 
-Close-in planets are common around M-dwarfs; studies from Kepler have
-shown that high-mass M dwarfs have $\approx$0.1 planets per star with
+Close-in planets are common around M dwarfs; studies from Kepler have
+shown that early M dwarfs have $\approx$0.1 planets per star with
 sizes between 1-4\,$R_\oplus$ and orbital periods within 3 days
-\citep{2015ApJ...807...45D}.  The number increases to $\approx$0.7
-planets per star considering planets out to $P$$<$10\,days.
-Extrapolating to all small close-in planets with say 0.1-4\,$R_\oplus$
-and within 10 days, it is reasonable to expect on average one close-in
-planet per M dwarf.
-
-In the context of planet formation, the stopping location for the
-innermost planet is set by the location of the protoplanetary disk's
-truncation radius \citep{2018haex.bookE.142I}.  Although the disk
-truncation radius is defined by equating the magnetic pressure from
-the stellar magnetosphere with the ram pressure from the inflowing
-gas, it also tends to coincide with the Keplerian corotation radius
-for low accretion rates
-\citep{2016ARA&A..54..135H,2022MNRAS.510.5246L}.  Within models that
-have one or more planets migrating inward due to gas drag, the
-innermost planets therefore arrive at $\approx$5-10 stellar radii
-before the disk becomes depleted.
-
-Given the known abundance of small planets around M dwarfs, it is
-tempting to try to interpret features of the CR light curves in terms
-of the possible presence of either close-in exoplanets or close-in
-planetesimals.  Rocky bodies this young could have molten global magma
-oceans analogous to those that existed on the Earth and Moon
-\citep[see][]{2022arXiv220310023L}, and could plausibly be outgassing
-either from those magma oceans, or from their unprocessed thin
-primordial atmospheres; in the former scenario, the gas would likely
-be enriched in heavy elements relative to the stellar wind.  The
-system would in certain respects be analogous to the Jupiter-Io plasma
-torus \citep[e.g.][]{2004jpsm.book..537S}, although with magnetic
-fields stronger by a factor of $\approx$1{,}000.  We emphasize that
-while this type of configuration seems a priori plausible, no direct
-evidence currently supports it.
-
-The main logical function of the planetesimals is to serve as a source
-for the occulting gas or dust; they would not necessarily need to
-explain the observed phases of the observed dips.  The azimuth angle
-of the eventual confinement could be entirely determined by the
-stellar magnetic field configuration.  In this scenario, the obscuring
-material could potentially inspiral from outgassing planetesimals many
-stellar radii away from the corotation radius.  While the
-planetesimals themselves would not necessarily need to transit, if
-they did, they would need to be $\lesssim 1$\,$R_\oplus$ based on
-their non-detections in the TESS data.  This would be analogous to
-previously known systems such as K2-22 \citep{2015ApJ...812..112S} and
-KOI-2700 \citep{2014ApJ...784...40R}, though the obscuring material
-would be observed much further from the emitting planet.
+\citep{2015ApJ...807...45D}.  The frequency of planets per star
+increases to $\approx$0.7 when considering periods as long as
+10\,days.  Extrapolating to all small (0.1-4\,$R_\oplus$) planets within
+10 days, it is reasonable to expect
+nearly all M dwarfs to have at least one planet.
+
+In the context of disk-driven planet migration, the stopping location
+for the innermost planet is set by the location of the protoplanetary
+disk's truncation radius \citep{2018haex.bookE.142I}.  The disk
+truncation radius is traditionally calculated by equating the magnetic
+pressure from the stellar magnetosphere with the ram pressure of the
+inflowing gas.  As it happens, the truncation radius is close to the
+corotation radius for low accretion rates
+\citep{2016ARA&A..54..135H,2022MNRAS.510.5246L}.  These considerations
+invite us to imagine one or more planets migrating inward due to gas
+drag, and the innermost planets arriving at $\approx$5-10 stellar
+radii before the disk is depleted.
+
+With this picture in mind, it is tempting to attribute features of the
+CR light curves as transits of material ejected by planets or
+planetesimals.  Young rocky bodies are expected to be hot, and they
+might expel either gas or dust.  The Jupiter-Io
+system \citep[e.g.][]{2004jpsm.book..537S} is analogous, in that a small rocky
+body similarly feeds the construction of a plasma torus.  We emphasize
+that while this type of configuration seems a priori plausible, no
+direct evidence currently supports it.
+
+The main logical function of the planetesimals would be to serve as a
+source for the occulting gas or dust; they would not necessarily need
+to explain the observed phases of the observed dips.  The azimuthal
+angle of the eventual entrainment would be entirely determined by the
+stellar magnetic field.  In this scenario, the obscuring material
+would inspiral from one or more rocky bodies well beyond the
+corotation radius.  The planetesimals themselves would not necessarily
+need to transit.  However if they did, they would need to be $\lesssim
+1$\,$R_\oplus$ based on their non-detections in the TESS data.
+Possibly analogous systems include K2-22 \citep{2015ApJ...812..112S}
+and KOI-2700 \citep{2014ApJ...784...40R}, though the obscuring
+material in the CRs would need to be observed much further from the
+emitting planet than for those two examples.
 
@@
 
-%In systems like LP 12-502, the observed variability would perhaps
-%drive one toward a picture of a disintegrating planetesimal swarm,
-%rather than just a single planetesimal.  The need for more than just
-%one launching body would be because we see dips appear and disappear at many
-%different phases, but with roughly the same period.  The observed
-%changing dip depths in response to flares could be understood through
-%the planetesimal outflow rates being stalled by changes in the local
-%magnetic field or coronal plasma density.  The sizes of these
-%purported planetesimals would need to be $\lesssim 1$\,$R_\oplus$,
-%based on the non-detections of their transits, analogous to e.g.
-%K2-22 \citep{2015ApJ...812..112S} or KOI-2700
-%\citep{2014ApJ...784...40R}.  Typical sizes of bodies in the asteroid
-%belt for instance span hundreds of meters to a few kilometers.
-
-%There are at least three problems with this disintegrating
-%planetesimal swarm concept.  First, the model would predict that
-%certain orbital phases would produce recurrent dips if observed over
-%sufficiently long baselines, because the launching planetesimal would
-%be massive enough to remain in orbit, while stochastically ejecting
-%material.  An analogous system would be K2-22
-%\citep{2015ApJ...812..112S}.  For most CRs (Figure~\ref{fig:evoln}),
-%the data are in tension with this expectation.  A second issue is that
-%many of the dips show asymmetries in the wrong direction relative to
-%the naive expectation of a trailing comet tail.  Invoking
-%non-exponentially decaying dust distributions as a function of azimuth
-%might be one way out, but such an idea lacks firm theoretical footing.
-%Finally, dynamical stability is a concern: in a model in which any new
-%dip is ``explained'' by invoking a new planetesimal, one might
-%eventually pack the corotation radius to a degree where instability
-%over short timescales would be guaranteed.
-
-%It is certainly possible that exoplanets or exoplanetesimals could end
-%up being connected to the CR phenomenon, for instance as a possible
-%sources for the occulting dust or gas.  However for the time being,
-%none of the CRs that we have studied in this work show clear evidence
-%for the nearby planets that we statistically expect should be common.
+%FIXME TODO LEFT OFF HERE
 
@@
 both classes of objects probably satisfy the condition $R_{\rm M} >
-R_{\rm cr}$, for $R_{\rm M}$ the magnetospheric radius (sometimes
+R_{\rm c}$, for $R_{\rm M}$ the magnetospheric radius (sometimes
 referred to as the Alfv\'en radius).  When this condition
@@
 closed field loops \citep{1985Ap&SS.116..285N}.  In the converse
-``dynamical'' case, when  $R_{\rm M} < R_{\rm cr}$, material
+``dynamical'' case, when  $R_{\rm M} < R_{\rm c}$, material
 interior to the magnetospheric radius returns to the stellar surface
@@
 temperature $10^6\,{\rm K}$ gives magnetospheric radii of order a few
-times the corotation radii, $R_{\rm cr}$.  This suggests that the
+times the corotation radii, $R_{\rm c}$.  This suggests that the
 existence of a centrifugal magnetosphere is plausible in young,
@@
 \startdata
-  TIC & $T$ & $d$ & $\bprp$ & RUWE & $P$ & Assoc & Age & $T_{\rm eff}$ & $R_\star$ & $M_\star$ & $R$$_{\rm cr}$ & $P_{\rm sec}$ & Quality & Bin & $N_{\rm sector}$ \\
+  TIC & $T$ & $d$ & $\bprp$ & RUWE & $P$ & Assoc & Age & $T_{\rm eff}$ & $R_\star$ & $M_\star$ & $R$$_{\rm c}$ & $P_{\rm sec}$ & Quality & Bin & $N_{\rm sector}$ \\
   -- &   mag & pc &    mag &      -- &        hr &   -- &        Myr &  K                  & $R_\odot$ & $M_\odot$ & $R_\star$         & hr                     & -- & -- & -- \\

### 2023-08-30 complexrotators/plotting.py

@@ -3764,8 +3764,8 @@ def plot_catalogscatter(outdir, showmaybe=0, plotsubset=None, emphruwe=1):
             #('rstar_sedfit', 'teff_sedfit', '$R_{\! \star}$ [$R_\odot$]', '$T_\mathrm{eff}$ [K]', 'linear', 'linear'),
             #('ruwe', 'bp_rp', 'RUWE', '$G_{\mathrm{BP}}-G_{\mathrm{RP}}$ [mag]', 'log', 'linear'),
             #('tlc_mean_period', 'Rcr_over_Rstar', '$P$ [hours]', '$R_{\mathrm{cr}}/R_{\! \star}$', 'log', 'linear'),
-            ('Rcr_over_Rstar', 'tlc_mean_period',  '$R_{\mathrm{cr}}/R_{\! \star}$', '$P$ [hours]', 'linear', 'log'),
-            ('banyan_adopted_age', 'mstar_parsec', 'Age [Myr]', '$M_{\! \star}$ [$M_\odot$]', 'log', 'linear'),
+            ('Rcr_over_Rstar', 'tlc_mean_period',  '$R_{\mathrm{c}}/R_{\! \star}$', '$P$ [hours]', 'linear', 'log'),
+            ('banyan_adopted_age', 'mass_parsec', 'Age [Myr]', '$M_{\! \star}$ [$M_\odot$]', 'log', 'linear'),
             #('rstar_sedfit', 'banyan_singleagefloat', '$R_{\! \star}$ [$R_\odot$]', 'Age [Myr]', 'linear', 'log'),
         ]
     elif plotsubset == 'sanitychecks':
@@ -3780,11 +3780,11 @@ def plot_catalogscatter(outdir, showmaybe=0, plotsubset=None, emphruwe=1):
             #('Rcr_over_Rstar', 'tlc_mean_period',  '$R_{\mathrm{cr}}/R_{\! \star}$', '$P$ [hours]', 'linear', 'log'),
             #('rstar_sedfit', 'banyan_singleagefloat', '$R_{\! \star}$ [$R_\odot$]', 'Age [Myr]', 'linear', 'log'),
             ('bp_rp', 'teff_sedfit', 'bp_rp', 'teff_sedfit', 'linear', 'linear'),
-            ('banyan_adopted_age', 'mstar_parsec', 'Age [Myr]', '$M_{\! \star}$ [$M_\odot$]', 'log', 'linear'),
[…]

### 2023-08-30 paper/ms.tex
update ms

@@
 \affiliation{\princeton}
-
-\author{-----SUGGESTED CONTRIBUTORS, PENDING DISCUSSION, COMMENTS, ANALYSES, ETC-----}
 %
-
-\author[0000-0002-3164-9086]{Maximilian N. G\"unther}
-\affiliation{\esa}
-
-\author[0000-0003-2058-6662]{George~R.~Ricker}
-\affiliation{\mitkavli}
+%\author{-----SUGGESTED CONTRIBUTORS, PENDING DISCUSSION, COMMENTS, ANALYSES, ETC-----}
+%%
+%
+%\author[0000-0002-3164-9086]{Maximilian N. G\"unther}
+%\affiliation{\esa}
+%
+%\author[0000-0003-2058-6662]{George~R.~Ricker}
+%\affiliation{\mitkavli}
 
@@
 \begin{abstract}
-%  This work focuses on a subset of low-mass pre-main-sequence stars
-%  with rotation periods of 0.2--2 days, optical variability amplitudes
-%  of a few percent, and sharp recurring light curve features that last for
-%  hundreds of cycles.  The sharp features are probably caused by
-%  eclipsing clumps of dust or gas orbiting at the corotation radius.
-%  We therefore refer to the objects as ``transient corotating clumps''
-%  (TCCs).
-%
-  Complex rotators (CRs) are low-mass pre-main-sequence stars with light
-  curves characterized by periods of 0.2--2 days, amplitudes of a few
-  percent, and slowly-evolving sharp features.  The sharp features
-  might be caused by eclipsing clumps of dust or gas orbiting at the
-  corotation radius.
+  We study a set of sub-solar mass pre-main-sequence stars
+  with rotation periods of 0.2--2 days, optical variability amplitudes
+  of a few percent, and sharp recurring light curve features that last for
+  hundreds of cycles.  The sharp features are probably caused by
+  eclipsing clumps of dust or gas orbiting at the corotation radius.
+  We refer to this class of variable star as ``complex rotators'' (CRs).
   To improve our understanding of these
@@
   result from a multipolar field topology, a hypothesis supported by
-  correspondences between the light curves of CRs and of two B stars
+  correspondences between the light curves of CRs and of B stars
   known to have strong multipolar magnetic fields.
@@
 \label{sec:intro}
+
+\begin{figure*}[!t]
+	\begin{center}
+		\subfloat{
+			\includegraphics[width=0.8\textwidth]{f1a.pdf}
+		}
+
+		\vspace{-0.65cm}
+		\subfloat{
+			\includegraphics[width=0.66\textwidth]{f1b.pdf}
+		}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+		{\bf Complex rotators (CRs)}:
+		{\it Top:} Phase-folded TESS light curves for three CRs.  Each
+		panel shows the average of the data accumulated over one month,
+		relative to the mean stellar brightness.
+		Gray circles are raw 2-minute data; black circles are binned to
+		300 points per cycle.  The period in hours is printed in the
+		bottom right corner.  Left-to-right, the objects are LP 12-502
+		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
+		425933644 (Sector~28).
+		{\it Bottom:} Cartoon explanations for the phenomenon.  The dust
+		clump scenario (left) and prominence scenario (right) both invoke
+		magnetically-entrained corotating material.
+	}
+	\label{fig:f1}
+\end{figure*}
 
@@
 The dust clump and gas prominence hypotheses are geometrically
-indistinguishable; one could imagine dust or gas accumulating in
+similar; one could imagine dust or gas accumulating in
 either of the geometries shown in Figure~\ref{fig:f1}.  The main
@@
 In both models, the corotation radius is the location at which matter
-concentrates.  This is empirically justified by the observation that
+concentrates.  The empirical basis for this is that
 the sharp CR features are superposed over smooth, quasi-sinusoidal
 starspot profiles.  The theoretical importance of the corotation
-radius has been discussed in studies of rapid magnetic rotators,
-including neutron stars \citep[e.g.]{1973ApJ...184..271L}, magnetic
-massive stars \citep[e.g.][]{1985Ap&SS.116..285N}, and accreting T
-Tauri stars \citep[e.g.][]{2005ApJ...634.1214L}.  In regions where the
-magnetic field dominates the flow (i.e.  $B^2/8\pi > \rho v^2 /2$),
-matter is dragged along with the field lines.  Assuming a dipolar
-magnetic field geometry, then the tendency of both gas and dust to
-become trapped at corotation is tied to how of the four relevant
+radius has been discussed in studies of rapid magnetic rotators
+\citep[e.g.][]{1973ApJ...184..271L,1985Ap&SS.116..285N,2005ApJ...634.1214L}.
+%including neutron stars \citep[e.g.]{1973ApJ...184..271L}, magnetic
+%massive stars \citep[e.g.][]{1985Ap&SS.116..285N}, and accreting T
+%Tauri stars \citep[e.g.][]{2005ApJ...634.1214L}.  
+In regions where the
+magnetic field dominates the flow (i.e.~$B^2/8\pi > \rho v^2 /2$),
+matter is dragged along with the field lines.  
+The tendency of both gas and dust to
+become trapped at corotation is then tied to how of the four relevant
 forces -- gravity, Lorentz, inertial Coriolis, and inertial
@@
 field lines, while gravity and the centrifugal force are in balance at
-$R_{\rm c}$ \citep[e.g.][Sec.~2]{2005MNRAS.357..251T}.  Another way to
+$R_{\rm c}$ \citep[e.g.][their Section~2]{2005MNRAS.357..251T}.  Another way to
 phrase this statement is that there is a local minimum in the
@@
 
-While theoretical heritage for understanding rapid magnetic
+Although theoretical heritage for understanding rapid magnetic
 rotators exists, CRs have remained mysterious because they have been both
@@
 starspots.
-
-\begin{figure*}[!t]
-	\begin{center}
-		\subfloat{
-			\includegraphics[width=0.8\textwidth]{f1a.pdf}
-		}
-
-		\vspace{-0.65cm}
-		\subfloat{
-			\includegraphics[width=0.66\textwidth]{f1b.pdf}
-		}
-	\end{center}
-		\vspace{-0.5cm}
-	\caption{
-		{\bf Complex rotators (CRs)}:
-    {\it Top:} Phase-folded TESS light curves for three CRs.  Each
-    panel shows the average of the data accumulated over one month,
-    relative to the mean stellar brightness.
-    Gray circles are raw 2-minute data; black circles are binned to
-    300 points per cycle.  The period in hours is printed in the
-    bottom right corner.  Left-to-right, the objects are LP 12-502
-    (TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
-    425933644 (Sector~28).
-    {\it Bottom:} Cartoon explanations for the phenomenon.  The dust
-    clump scenario (left) and prominence scenario (right) both invoke
-    magnetically-entrained corotating material.
-	}
-	\label{fig:f1}
-\end{figure*}
 
@@
 
-\begin{figure}[!tp]
+\begin{figure}[!t]
 	\begin{center}
 		\centering
-		\includegraphics[width=0.48\textwidth]{f2completeness.pdf}
-		\vspace{-0.5cm}
+		\includegraphics[width=0.46\textwidth]{f2completeness.pdf}
+		\vspace{-0.2cm}
 		\caption{
-			{\bf Completeness of the TESS 2-minute cadence data for late-K
+			{\bf Completeness of the TESS 2-minute data for late-K
       and early M dwarfs near the Sun, from Sectors 1-55.}  
@@
       radial shells, each with a width of 10\,pc.  To be counted,
-      these stars must meet the listed conditions: they must be red
-      ($\bprp$>$1.5$) dwarf stars ($M_{\rm G}$>4) amenable for TESS
+      these stars must meet the listed conditions: they must be red dwarf
+      stars
+      ($\bprp$>$1.5$; $M_{\rm G}$>4) amenable for TESS
       observations ($T$<16).  The blue solid curve shows the fraction
       of such stars with at least one sector of TESS 2-minute cadence
-      data acquired between Sectors 1-55.  The latter data comprise
-      the selection function for our complex rotator search.
+      data acquired between Sectors 1-55.
 		}
@@
 instances in which dips switch off over less than one cycle; we did
-not see any such instances of dips switching on.  Dip growth instead
-seems to happen more slowly.  For instance, the dip at phase 0-0.1
+not see any such instances of dips switching on.  Dip growth seems to happen more slowly.  For instance, the dip at phase 0-0.1
 between cycles 258-290 begins to become detectable during cycle 258,
@@
 for the innermost planet is set by the location of the protoplanetary
-disk's truncation radius \citep{2018haex.bookE.142I}.  The disk
+disk's truncation radius \citep{2018haex.bookE.142I}.  The 
 truncation radius is traditionally calculated by equating the magnetic
@@
 invite us to imagine one or more planets migrating inward due to gas
-drag, and the innermost planets arriving at $\approx$5-10 stellar
+drag, and arriving at $\approx$5-10 stellar
 radii before the disk is depleted.
@@
 Space Telescopes (MAST).  The specific 120-second cadence observations
-can be accessed via
-\dataset[DOI]{https://doi.org/10.17909/t9-nmc8-f686}.  Funding for the
+can be accessed via DOI\!\!\!~\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.  Funding for the
 TESS mission is provided by NASA’s Science Mission Directorate.  TIC
@@
 LAH contributed to project design and to the interpretation of the light curves.
+JNW significantly improved the clarity of the manuscript.
 G\'AB acquired and maintained the servers used to run the dip-finding pipeline.
------
-{\bf JNW, MNG, GRR to confirm coauthorship \&/or to help out on interpretation!}
+%-----
+%{\bf JNW, MNG, GRR to confirm coauthorship \&/or to help out on interpretation!}
 % Pending!

### 2023-08-30 drivers/fraction_coverage.py

@@ -135,18 +135,18 @@ from aesthetic.plot import set_style, savefig
 
 plt.close("all")
 set_style("science")
-f = 1.4
+f = 2
 fig, ax = plt.subplots(figsize=(f*2, f*2))
 ax.spines['top'].set_visible(True)
 ax.spines['right'].set_visible(True)
 
 ax2 = ax.twinx()
-ax2.plot(outdf.dist_mids_pc, outdf.N_Gaia, c='C1', marker='+', lw=1, zorder=-3,
-         ms=f*3, ls=':')
+ax2.plot(outdf.dist_mids_pc, outdf.N_Gaia, c='C1', marker='o', lw=2, zorder=-3,
+         ms=f*4.5, ls=':')
 ax2.set_yscale('log')
 
-ax.plot(outdf.dist_mids_pc, outdf.frac, c='C0', marker='o', lw=1, zorder=4,
-        ms=f*3)
+ax.plot(outdf.dist_mids_pc, outdf.frac, c='C0', marker='P', lw=2, zorder=4,
+        ms=f*4.5)
 
 ax.update({
     'xlabel': 'Distance [pc]',

### 2023-08-31 paper/ms.tex
Update ms: discussion and conclusion
Co-authored-by: Joshua Winn <jnwinn@princeton.edu>

@@
 \begin{abstract}
-  We study a set of sub-solar mass pre-main-sequence stars
-  with rotation periods of 0.2--2 days, optical variability amplitudes
+  We study a set of pre-main-sequence stars
+  with sub-solar masses, rotation periods of 0.2--2 days, optical variability amplitudes
   of a few percent, and sharp recurring light curve features that last for
@@
   To improve our understanding of these
-  enigmatic stars, we conducted a survey for CRs using TESS
+  enigmatic objects, we conducted a survey for CRs using TESS
   short-cadence data collected between 2018~July and 2022~September.
@@
 		{\it Bottom:} Cartoon explanations for the phenomenon.  The dust
-		clump scenario (left) and prominence scenario (right) both invoke
+		clump scenario (left) and gas prominence scenario (right) both invoke
 		magnetically-entrained corotating material.
@@
 at distances of a few stellar radii.  A final possibility is that an
-optically-thick ring obscures a small portion of the stellar
+optically-thick ring obscures a narrow band of the stellar
 photosphere \citep{2019ApJ...876..127Z}.  Hot spots passing behind
@@
 starspot profiles.  The theoretical importance of the corotation
-radius has been discussed in studies of rapid magnetic rotators
+radius has been discussed in studies of magnetic rotators
 \citep[e.g.][]{1973ApJ...184..271L,1985Ap&SS.116..285N,2005ApJ...634.1214L}.
+%
 %including neutron stars \citep[e.g.]{1973ApJ...184..271L}, magnetic
@@
 %Tauri stars \citep[e.g.][]{2005ApJ...634.1214L}.  
-In regions where the
-magnetic field dominates the flow (i.e.~$B^2/8\pi > \rho v^2 /2$),
-matter is dragged along with the field lines.  
-The tendency of both gas and dust to
-become trapped at corotation is then tied to how of the four relevant
-forces -- gravity, Lorentz, inertial Coriolis, and inertial
-centrifugal -- the Lorentz and Coriolis only act perpendicular to
-field lines, while gravity and the centrifugal force are in balance at
-$R_{\rm c}$ \citep[e.g.][their Section~2]{2005MNRAS.357..251T}.  Another way to
-phrase this statement is that there is a local minimum in the
-effective potential of the corotating frame; given a flow from the
-either the star or from a tenuous accretion disk, this local potential
-minimum enables material to build up \citep{2005MNRAS.357..251T}.
+%
+In regions where the magnetic field dominates the flow (i.e.~$B^2/8\pi
+> \rho v^2 /2$), matter is dragged along with the field lines.  The
+tendency for charged gas or dust to become trapped at corotation is
+then tied to how of the four relevant forces -- gravity, Lorentz,
+inertial Coriolis, and inertial centrifugal -- the Lorentz and
+Coriolis only act perpendicular to field lines, while gravity and the
+centrifugal force are in balance at $R_{\rm c}$ \citep[e.g.][their
+Section~2]{2005MNRAS.357..251T}.  Another way to phrase this statement
+is that there is a local minimum in the effective potential of the
+corotating frame; given a flow from the either the star or from a
+tenuous accretion disk, this local potential minimum enables material
+to build up \citep{2005MNRAS.357..251T}.
 
@@
 		\centering
-		\includegraphics[width=0.46\textwidth]{f2completeness.pdf}
+		\includegraphics[width=0.43\textwidth]{f2completeness.pdf}
 		\vspace{-0.2cm}
@@
       The orange dotted curve shows the number of stars in successive
-      radial shells, each with a width of 10\,pc.  To be counted,
+      radial shells, each with a width of 10\,pc.  To be part of our selection function,
       these stars must meet the listed conditions: they must be red dwarf
@@
 instances in which dips switch off over less than one cycle; we did
-not see any such instances of dips switching on.  Dip growth seems to happen more slowly.  For instance, the dip at phase 0-0.1
-between cycles 258-290 begins to become detectable during cycle 258,
-and growths in depth by about 2\% over the next eight cycles.  The
+not see any such instances of dips switching on.  Dip growth seems to
+happen more slowly.  For instance, the dip at phase 0-0.1 between
+cycles 258-290 begins to become detectable during cycle 258, and
+growths in depth by about 2\% over the next eight cycles.  The
 evolution of this particular dip is most clear in the river plots.
@@
 individual LP 12-502 dips seems to be $\approx$0.06\,$P$ $\approx$
-1.08\,hr.  This is very similar to the characteristic timescale of of
+1.08\,hr.  This is very similar to the characteristic timescale of a
 transiting small body at the corotation radius,
@@
 
-%FIXME TODO LEFT OFF HERE
-
 \subsection{From dippers to debris disks}
 \label{subsec:discdippers}
+
+About one in three young stars with infrared-detected inner dusty
+disks show quasiperiodic or stochastic dimming over timescales of
+roughly one day \citep[e.g.][]{2010A&A...519A..88A}.  The dimming
+amplitudes can reach a few tenths of the stellar brightness, and dips
+with identical depths and phases rarely recur.  These ``dipper'' stars
+are probably explained by occulting circumstellar dust in the inner
+disk
+\citep[e.g.][]{2014AJ....147...82C,2016ApJ...816...69A,2021ApJ...908...16R,2022ApJS..263...14C}.
+While the phenomenon can persist beyond $\approx$10\,Myr
+\citep{2019MNRAS.488.4465G,2022MNRAS.514.1386G}, in all such cases it
+seems to be associated with the presence of infrared excesses.
+Phenomenologically, dippers are different from CRs in that their dips
+are usually deeper, less periodic, and more variable in depth over
+timescales of only one or a few cycles.  Dipper stars also tend to be
+younger, since they tend to be classical T Tauri stars with infrared
+excesses.
 
@@
 ultimately concluded that these sources are dippers.  This episode
-suggests that there could be overlap between CRs and dippers.  It is
-also worth emphasizing that our labeling of e.g.~TIC~57830249 was
-based on a single sector of TESS data (Sector~36) when its behavior
-was relatively periodic and it showed dip depths of a few percent.
-However, in other TESS sectors (e.g. Sector~10), this source looks
-completely different, varying in apparent flux by a factor of two,
-with no discernible periodicity at all.
-
-Assessing these results against the backdrop of our increasing
-understanding of dippers
-\citep[e.g.][]{2014AJ....147...82C,2016ApJ...816...69A,2021ApJ...908...16R,2022ApJS..263...14C,2022MNRAS.514.1386G},
-it is clear that the loss of an infrared excess is associated with
-strong changes in a star's optical variability.  It is reasonable to
-imagine connections between CRs and dippers: both classes of object
-can show transient flux dips that are relatively narrow in duration.
-The dips in both are probably associated with clumps of dust or gas.
-However the CR dips are generally more periodic and less deep than
-those of dippers; they also display far less transience over
-timescales of a few to tens of cycles.  The CRs also have
-demonstrably less dust than (most) dipper stars.  At a population
-level, the CR stars are also older.  A common mystery between the
-CRs and dippers, in our own estimation, is how exactly the {\it
-narrowness} of the dust clumps is produced.  It is not unreasonable to
-imagine a similar mechanism operating for both types of object, tied
-perhaps to a shared magnetic topology, or perhaps to a preference for
-dust to inspiral to the star in clumped structures.
+suggests that there could be overlap between CRs and dippers.  Taking
+TIC~57830249 as one example, the Sector~36 TESS data are suggestive of
+a CR, with relatively periodic, sharp dips with depths of a few
+percent.  The Sector~10 data are completely different, varying in
+apparent flux by a factor of two, with no discernible periodicity at
+all.  Perhaps this source becomes a ``dipper'' when an inflow of dust
+reaches the inner disk wall, and is otherwise a ``CR'' when the inner
+disk is starved of dust.
+
+Although this outlier is intriguing, stars without infrared excessess
+typically have more stable optical light curves than those with
+infrared excesses.  While some dippers may evolve into CRs after the
+disk is mostly gone, this would be generically expected based on the
+population statistics: young stars become older.  There may be no
+other causal connection between the two evolutionary stages.  With
+that said, a common mystery between the CRs and dippers is how exactly
+the {\it narrowness} of the dust-induced dimmings is produced.  It is
+not unreasonable to imagine a similar mechanism operating for both
+types of object, tied perhaps to a shared magnetic topology, or
+perhaps to a preference for dust to inspiral to the star in clumped
+structures.
 
 %\subsection{Are half-cycles important?}
+%
+% NOTE to arxis readers: the answer was: "maybe in a few cases, but
+% this manuscript was already too long!".
 %
@@
 
-We can estimate the mass of a transiting cloud by first converting the
-transit depth to an effective cloud radius, $R_{\rm cloud}$.  For most
-CRs in Figure~\ref{fig:cqvs}, this yields $\approx$2-20\,$R_\oplus$.
-A minimum constraint on the number density follows by requiring the
-cloud to be optically thick.  For cases like LP 12-502, this is
-reasonable because the transit duration of the shortest dips implies
-$R_{\rm cloud}\ll R_\star$.  Carrying out the relevant calculation
-assuming the occulting material is dust grains 1\,$\mu$m in size,
+Assuming for the moment that the obscuring material is dust, we can
+estimate the mass of a transiting clump. First, we convert the transit
+depth into an effective cloud radius, $R_{\rm cloud}$.  For most CRs
+in Figure~\ref{fig:cqvs}, this yields $\approx$2-20\,$R_\oplus$.  A
+minimum constraint on the number density of dust particles is obtained
+by requiring the cloud to be optically thick.  For cases like LP
+12-502, this is reasonable because the transit duration of the
+shortest dips implies $R_{\rm cloud}\ll R_\star$.  Carrying out the
+relevant calculation assuming the dust grains are 1\,$\mu$m in size,
 \citet{2023MNRAS.518.4734S} reported minimum cloud masses of order
@@
 asteroid; the asteroid belt itself has a mass of order
-$\approx$10$^{21}$\,kg \citep{2019Icar..319..812P}.  If the material
-were cool gas prominences rather than dust, the mass would need to be
-of order $10^{14}$\,kg \citep{1990MNRAS.247..415C}, about 100$\times$
-larger than the requisite dust mass.
-
-Our observations provide a direct measurement of how often dips appear
-and disappear, both due to sudden state-switches, and due to more
-gradual, secular evolution.  For instance, LP~12-502 showed three
-``state-switch'' events over the six months of available TESS
-observations, during cycles 248-264, 299-315, and 1233-1247.  In each
-case, a dip ``turned off''.  It is plausible to imagine that these
-events correspond to either mass being ejected from the corotating
-clumps, or else perhaps being accreted onto the star.  In either case,
-the corresponding $\dot{M} \equiv M\cdot {\rm d}N/{\rm d}t$
-time-averaged over six months is $\approx$3$\times$$10^{-18}
-M_\odot\,{\rm yr}^{-1} \approx 1\times10^{-12} M_\oplus\,{\rm
-yr}^{-1}$.  Considered cumulatively over the $\approx$$10^8$ years for
-which the CR phenomenon is observed, this yields a cumulative moved
-dust mass of $10^{-4}\,M_\oplus$, of order the Solar System's asteroid
-belt.  If the occulting material is gas, the masses involved would be
-of order 100 times larger.  For cases in which we observe the {\it
-growth} of dips, such as the Sector~29 data for TIC~224283342, or
-Sector~5 of TIC~294328885, the dip depths typically increase by of
-order a few percent over ten to twenty days.  This growth rate yields
-a mass flux one order of magnitude larger than the earlier estimate.
+$\approx$10$^{21}$\,kg \citep{2019Icar..319..812P}.  A similar
+calculation that assumed occulting clupms of hydrogen, rather than
+dust, derived gas prominence masses of at least $10^{14}$\,kg
+\citep{1990MNRAS.247..415C}, about 100$\times$ larger than the lower
+limit on the dust mass.
+
+If the disappearance of a dip represents the permanent loss of the
+obscuring material -- for example, if it is the result of a dust clump
+being accreted or ejected -- then we can also estimate the rate at
+which mass is flowing through the structures that lead to dips.  For
+instance, LP~12-502 showed three ``state-switch'' events over the six
+months of available TESS observations, during cycles 261, 309, and
+1241 (Figure~\ref{fig:lpriver0}).  The other source for which we
+performed a comparable analysis, TIC~300651846
+(Appendix~\ref{app:tic3006}), showed two state-switches over 11
+months.  In all such cases, at least one dip turned off.  For purposes
+of estimation, we will take LP 12-502 as our prototype.  Assuming the
+occulting material is dust, the corresponding $\dot{M} \equiv M\cdot
+{\rm d}N/{\rm d}t$ time-averaged over six months is
+$\approx$3$\times$$10^{-18} M_\odot\,{\rm yr}^{-1} \approx
+1\times10^{-12} M_\oplus\,{\rm yr}^{-1}$.  Considered cumulatively
+over the $\approx$$10^8$ years for which the CR phenomenon is
+observed, this yields a cumulative moved dust mass of
+$10^{-4}\,M_\oplus$, of order the Solar System's asteroid belt.  If
+the occulting material is gas, the masses involved would be of order
+100 times larger.  For cases in which we observe the {\it growth} of
+dips, such as the Sector~29 data for TIC~224283342, or Sector~5 of
+TIC~294328885, the dip depths typically increase by of order a few
+percent over ten to twenty days.  This growth rate yields a mass flux
+one order of magnitude larger than the earlier estimate.
 
@@
 An argument against the connection between CRs and the $\sigma$~Ori~E
-analogs is that the light curve of $\sigma$~Ori~E is much simpler than
+analogs is that the light curve of $\sigma$~Ori~E is simpler than
 those in Figure~\ref{fig:cqvs}, with only two broad local minima, and
@@
 \citealt{2022ApJ...924L..10J}).  Within the model proposed by
-\citeauthor{2005ApJ...630L..81T}, this is explained by the simplicity
-of the star's magnetic field, which is well-approximated by a dipole,
-similar to most other magnetic B stars
-\citep{2007A&A...475.1053A,2009ARA&A..47..333D}.  The magnetic axis
-needs to be tilted relative to the stellar spin axis in order to match
-the qualitative behavior of both the broadband light curves, and the
-line-profile variations seen in hydrogen, helium, and carbon
-\citep{2012MNRAS.419..959O}.
-
-Two exceptions to the rule of ``simple field topologies for magnetic B
-stars'' are HD~37776 and HD~64740, which are B stars that were
-previously known from spectropolarimetry to have field geometries
+\citeauthor{2005ApJ...630L..81T}, the simplicity of the light curve is
+the result of a simple dipolar magnetic field, which is typical of
+magnetic B stars \citep{2007A&A...475.1053A,2009ARA&A..47..333D}.  The
+magnetic axis needs to be tilted relative to the stellar spin axis in
+order to match the qualitative behavior of both the broadband light
+curves, and the line-profile variations seen in hydrogen, helium, and
+carbon \citep{2012MNRAS.419..959O}.
+
+Two interesting and possibly telling exceptions to the rule that
+magnetic B stars have simple light curves are HD~37776 and HD~64740.
+Both stars are known from spectropolarimetry to have field geometries
 dominated by high order multipoles \citep{2011ApJ...726...24K}.
-Reviewing the literature, we learned that recent TESS light curves of
-these two B stars appear surprisingly similar to the CR light curves
-\citep{2020pase.conf...46M}.  The middle row of Figure~\ref{fig:bstar}
-shows the phased TESS light curves for these two outlying magnetic B
-stars, with by-eye ``best matching'' CRs shown underneath for comparison.  The
-number of dips per cycle, the shapes of the dips, and the dip depths
-relative to the sinusoidal envelope all appear to be similar.  This surprising connection 
-suggests that the
-highly-structured M dwarf light curves may imply multipolar magnetic
-fields -- since it is the complex fields which are the defining
-characteristic of these two B stars, relative to other known magnetic
-B stars like $\sigma$~Ori~E.  This is consistent with the
-non-axisymmetric topologies that have been reported in a small number
-of M dwarfs for which Zeeman Doppler Imaging is technically feasible
+And, recent TESS light curves of these two B stars appear surprisingly
+similar to the CR light curves \citep{2020pase.conf...46M}.  The
+middle row of Figure~\ref{fig:bstar} shows the phased TESS light
+curves for these two stars, with by-eye best-matching CRs shown
+underneath for comparison.  The number of dips per cycle, the shapes
+of the dips, and the dip depths relative to the sinusoidal envelope
+are all similar.  This connection suggests that the highly structured
+light curves of both the M dwarfs and the B stars are associated with
+(and perhaps caused by) strong non-dipolar magnetic fields.
+Non-dipolar fields for M dwarfs are plausible, given that Zeeman
+Doppler Imaging has revealed non-axisymmetric magnetic field patterns
+for the few M dwarfs for which this technique is technically feasible
 \citep[see][and references therein]{2021A&ARv..29....1K}.
@@
 magnetosphere'' \citep[see][]{2013MNRAS.429..398P}.  In other words,
-both classes of objects probably satisfy the condition $R_{\rm M} >
-R_{\rm c}$, for $R_{\rm M}$ the magnetospheric radius (sometimes
-referred to as the Alfv\'en radius).  When this condition
-holds, stable points exist wherever the outward centrifugal force is
-balanced by the combined effect of gravity and magnetic tension along
-closed field loops \citep{1985Ap&SS.116..285N}.  In the converse
-``dynamical'' case, when  $R_{\rm M} < R_{\rm c}$, material
-interior to the magnetospheric radius returns to the stellar surface
-over the free-fall timescale.  A simple estimate assuming a dipole
-field with $B_0\approx1\,{\rm kG}$ at the star's surface, a local
-plasma number density $n\approx10^9\,{\rm cm^{-3}}$, and a plasma
-temperature $10^6\,{\rm K}$ gives magnetospheric radii of order a few
-times the corotation radii, $R_{\rm c}$.  This suggests that the
-existence of a centrifugal magnetosphere is plausible in young,
-rapidly rotating M dwarfs.
+both classes of objects probably satisfy the condition $R_{\rm m} >
+R_{\rm c}$, for $R_{\rm m}$ the magnetosphere radius (sometimes called
+the Alfv\'en radius).  Provided that charged particles are confined to
+move along magnetic field lines, stable points that balance the
+centrifugal force and gravity can then exist at the corotation radius
+\citep[e.g.][]{2005MNRAS.357..251T}.  In the converse ``dynamical''
+case, when $R_{\rm m} < R_{\rm c}$, material interior to the
+magnetospheric radius returns to the stellar surface over the
+free-fall timescale.  A simple estimate assuming a dipole field with
+$B_0\approx1\,{\rm kG}$ at the star's surface, a local plasma number
+density $n\approx10^9\,{\rm cm^{-3}}$, and a plasma temperature
+$10^6\,{\rm K}$ gives magnetospheric radii of order a few times the
+corotation radii, $R_{\rm c}$.  This suggests that the existence of a
+centrifugal magnetosphere is plausible for young, rapidly rotating M
+dwarfs.
 
 % NOTE to the arxiv crawlers:
-
+%
 % While there are some qualitative connections to Jupiter-Io, it's not
-% perfect.  In that system, R_A>R_cr...  But the plasma torus exists
+% perfect.  In that system, R_m>R_c...  But the plasma torus exists
 % near Io's 42 hour orbit ...and is nonetheless STILL FORCED into
@@
 % type of structure is very different, because here we actually see
-% the plasma at corotation!
+% the plasma at the corotation radius itself!
 
@@
 In this work, we searched 120-second cadence TESS data collected from
-2018 July to 2022 September for complex rotators
-(CRs).  The target stars were \nstarssearched\ K and M dwarfs within
-150\,pc.  The selection function was $>$$80\%$ complete within 30\,pc,
-and $<$$10\%$ complete at distances exceeding 100\,pc.
+2018 July to 2022 September for complex rotators (CRs).  The target
+stars were \nstarssearched\ K and M dwarfs within 150\,pc.  The
+selection function was $>$$80\%$ complete within 30\,pc, and $<$$10\%$
+complete at distances exceeding 100\,pc.
 
@@
 bona fide CRs are listed in Table~\ref{tab:thetable}.  This table also
-includes an additional \nmaybes\ ambiguous CRs, whose designation is
+includes \nmaybes\ ambiguous CRs, whose designation is
 less certain, and \ndebunked\ impostors.  We inferred ages for all but
-two of the \nallcands\ objects based on association memberships; we
-also derived temperatures and radii using SED fitting, and then
+two of the \nallcands\ objects based on memberships in young stellar assocations; we
+also derived temperatures and radii using SED fitting, and 
 inferred stellar masses by interpolating against stellar evolutionary
-models.  We caution that our selection function was not
-volume-limited: the TESS 120-second stellar sample had a heterogeneous
+models.  We caution that our sample is far from being
+volume-limited and is not even magnitude-limited:
+the TESS 120-second stellar sample had a heterogeneous
 selection function which may have been biased in favor of young stars
@@
 %
-    \item CRs are quasiperiodic.  The mean periods remain fixed over
-      the $>$1{,}000-cycle baseline of available observations; but the
-      light curve shapes always evolve (Figure~\ref{fig:evoln}).
-  %
-    \item The same CR can show multiple periods simultaneously.  LP
-      12-502, for instance, showed dips with four distinct periods
-      within $\pm 0.3\%$ of its fundamental period, sometimes
-      simultaneously, and each lasting for up to 50 cycles
+    \item The sharpest CR dips have durations of $\approx$0.05\,$P$
+      and depths of $\approx$1-3\% (Figures~\ref{fig:cqvs}
+      and~\ref{fig:evoln}).  Explaining dips this sharp requires
+      material extrinsic to the stellar surface (see
+      Section~\ref{sec:intro}).
+%
+    \item The shortest CR dips, also with durations of
+      $\approx$0.05\,$P$, match the expected transit duration of a
+      small body at the corotation radius, $T_{\rm dur} \equiv R_\star
+      P_{\rm rot} / (\pi a)$ (see Section~\ref{subsec:lplessons}).
+      Such dips may therefore be produced by transits of bodies or
+      distributions of optically-thick material that are smaller than
+      the star.
+%
+    \item Most CR dips have durations a few times longer than $T_{\rm
+      dur}$ (Figure~\ref{fig:cqvs}).  Such dips are often superposed
+      on a quasi-sinusoidal signal that presumably comes from
+      starspots and faculae that produce inhomogeneities in the
+      longitudinal flux distribution across the stellar surface.  The
+      only viable explanation for the sharp dips being superposed on
+      the quasi-sinusoidal signals is that clumps of circumstellar
+      material are corotating with the star.  Assuming that the longer
+      dips have the same physical origin as the shortest dips, the
+      transiting material must therefore also be capable of having
+      effective sizes comparable to the star.
+%
+    \item The mean periods of CRs remain fixed to within a relative
+      precision $\lesssim$0.1\% over the two-year ($\approx$1{,}000
+      cycle) baseline of available observations.  The light curve
+      shapes always evolve over this timescale
+      (Figure~\ref{fig:evoln}).
+%
+    \item The dips in CR light curves can have slightly different
+      periods.  LP 12-502, for instance, showed dips with four
+      distinct periods within $\pm 0.3\%$ of its fundamental period,
+      sometimes simultaneously, and each lasting for up to 50 cycles
       (Figure~\ref{fig:lpriver0}).
 %
-    \item CRs evolve over timescales that are both secular
-      ($>$100\,cycles) and impulsive ($<$1 cycle).  Dip growth seems
+    \item The CR peaks and dips evolve over timescales that are both secular
+      ($\approx$100\,cycles) and impulsive ($<$1 cycle).  Dip growth seems
       to happen over durations of at least ten cycles, and slow dip
@@
       collapsing instantaneously, and are almost always linked with
-      observed optical flares.  This suggests that the occulting
-      material is sensitive to sudden changes in the magnetic field.
-  %
-    \item The rate of dip evolution can be used to place a
-      model-dependent constraint on how much material is either being
-      accreted or ejected during the state changes
-      (Section~\ref{subsec:massflux}).  Order of magnitude estimates
-      require at least an asteroid belt's worth of dust
-      ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or
-      $\approx$$10^{-2}$\,$M_\oplus$ if the occulting material is gas.
+      observed optical flares.  Such switches are suggestive of
+      magnetic reconnection opening the ``magnetic cage'' that traps
+      the dust.
+%
+    \item The on-off duty cycle for CRs seems to be $\approx$$75$\%, based
+      on the fraction of bona fide CRs that either turned on or turned
+      off during TESS re-observations, two years after the initial
+      observation (Figure~\ref{fig:evoln}).
 %
@@
 %
-    \item The on-off duty cycle for CRs seems to be $\approx$$75$\%, based
-      on the fraction of bona fide CRs that either turned on or turned
-      off during TESS re-observations, two years after the initial
-      observation (Figure~\ref{fig:evoln}).
-  %
     \item Most CRs are M dwarfs with masses
@@
       scrutiny of these objects in future work.
-  %
-    \item Surprising analogs to the CRs exist in magnetic B stars,
-      but only those with multipolar field topologies.  Since most
-      magnetic B stars have dipolar magnetic fields, this suggests
-      that the CR dips and warps are similarly being sculpted by the
-      stellar magnetic fields, and that the magnetic fields themselves
-      are probably also multipolar.
 %
@@
       two within 50\,pc, and by a factor of ten within 100\,pc.
+%
+    \item Surprising analogs to the CRs exist in two magnetic B stars
+      with multipolar field topologies.  Since most magnetic B stars
+      have dipolar magnetic fields, this suggests that the CR dips and
+      warps are similarly being sculpted by the stellar magnetic
+      fields, and that the magnetic fields themselves are potentially
+      also multipolar.
+%
+    \item The rate of dip evolution can be used to place a
+      model-dependent lower bound on how much material is either being
+      accreted or ejected during the state changes
+      (Section~\ref{subsec:massflux}).  Order of magnitude estimates
+      require at least an asteroid belt's worth of dust
+      ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or at least
+      $\approx$$10^{-2}$\,$M_\oplus$ if the occulting material is gas.
 \end{enumerate}
@@
 preferentially show transiting planets at larger distances than the
-corotating material, though this may be dependent on whether the
+corotating material, though this conclusion would be dependent on whether the
 magnetic and stellar spin axes tend to be aligned.  Given these
@@
 close-in rocky planets that are expected to be present around most of
-these stars.  The challenges intrinsic to both the observational and
-theoretical work seem worth the effort.
+these stars.
 
@@
 Fellowship, and for helpful conversations with G.~Laughlin, A.~Mann,
-and J.~Spake.  This paper relied on data collected by the TESS
-mission, which are publicly available from the Mikulski Archive for
+and J.~Spake.  
+This paper relied on data collected by the TESS
+mission, which are available from the Mikulski Archive for
 Space Telescopes (MAST).  The specific 120-second cadence observations
-can be accessed via DOI\!\!\!~\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.  Funding for the
+can be accessed via DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.  Funding for the
 TESS mission is provided by NASA’s Science Mission Directorate.  TIC
@@
 Sectors 18, 19, 25, 26) and G04168 (PI: R.~Jayaraman; Sector 53).
+LGB is also grateful for the assistance of 
+S.~Yee, L.~Weiss, H.~Isaacson, and A.~Howard in
+acquiring and analyzing the HIRES spectra.
 
@@
 LAH contributed to project design and to the interpretation of the light curves.
-JNW significantly improved the clarity of the manuscript.
+JNW and SR significantly improved the clarity of the manuscript.
 G\'AB acquired and maintained the servers used to run the dip-finding pipeline.
@@
 %HI and AH designed and maintain the architecture used to acquire and process the HIRES spectra.
-All authors assisted in manuscript writing and revision.
+All authors assisted in manuscript revision.
 
@@
 One hypothesis for the CRs, presented by \citet{2019ApJ...876..127Z},
-is that the star might be ``{\it orbited by one or more rings composed of
-dust-size or somewhat larger particles\ldots The ring particles would
-move in Keplerian orbits at relatively large distances from the star,
-and therefore the sublimation lifetime would not be an issue even if
-the particles are dust-like in size.}'' A sketch of this scenario was
-presented by \citet{2019ApJ...876..127Z}, in their Figure~11.
-An example set of proposed parameters involved a ring inclined with
-respect to the stellar spin axis by a few degrees, and with inner and
-outer radii of 10 and 15 stellar radii.
+is that the star might be ``{\it orbited by one or more rings composed
+of dust-size or somewhat larger particles\ldots The ring particles
+would move in Keplerian orbits at relatively large distances from the
+star, and therefore the sublimation lifetime would not be an issue
+even if the particles are dust-like in size.}'' A sketch of this
+scenario was presented by \citet{2019ApJ...876..127Z}, in their
+Figure~11.  An example set of proposed parameters involved a ring
+inclined with respect to the stellar spin axis by a few degrees, and
+with inner and outer radii of 10 and 15 stellar radii.
 
@@
 transit behind the ring, it would produce a brightening, not a
-dimming.   Most CRs show dimmings.   The ring scenario would
-therefore imply that large hot spots are common in the photospheres of
+dimming.   Most CRs show dimmings.   The ring scenario would therefore
+imply that large hot spots are common in the photospheres of
 pre-main-sequence M dwarfs.  Empirical evidence however suggests that
-cool spots dominate the
-the optical variability of disk-free pre-main-sequence stars.
-This evidence includes flux excursions
+cool spots dominate the the optical variability of disk-free
+pre-main-sequence stars.  This evidence includes flux excursions
 caused by spot-crossings during planetary transits
@@
 
-An independent  concern with the ring hypothesis is that it is fine-tuned.
-The model requires specific locations for the inner edge and the outer
-edge of the ring, an inclination that yields a band with a specific
-apparent size, and material in the ring that must be optically thick
-while also being homogeneous enough to not induce any apparent
-photometric variability.
-It is challenging to ascribe specific probabilities to any one
-of these factors.
-However the requirement that they all be simultaneously met seems sufficiently
+An independent  concern with the ring hypothesis is that it is
+fine-tuned.  The model requires specific locations for the inner edge
+and the outer edge of the ring, an inclination that yields a band with
+a specific apparent size, and material in the ring that must be
+optically thick while also being homogeneous enough to not induce any
+apparent photometric variability.  It is challenging to ascribe
+specific probabilities to any one of these factors.  However the
+requirement that they all be simultaneously met seems sufficiently
 severe to disfavor this scenario.
@@
 continuous viewing zone.  If it were not for the existence of
-TIC~402980664, this source would probably have received greater
+TIC~402980664, this source would have received greater
 attention.  With the exception of a few sectors, TESS data will exist
@@
 minima per cycle.  During the early portions of Sectors 61-65, it is
-somewhat more complex, with at least five clear local minima per
-cycle.  As the source evolves, this complexity decreases, while the
-sharpness of one of the minima appears to increase.  We did not find
-evidence for any obvious ``state-switches'' analogous to those that we
-observed in LP 12-502; gradual evolution over timescales of
-$\approx$50-100 cycles seem to be the norm for TIC~300651846.  Unlike
-the TIC~402980664 river plots (Figure~\ref{fig:lpriver0}), we did not
-subtract any ``continuum sinusoid'' for this source, because the
-continuum is not as obviously defined.
+more complex, with at least five clear local minima per
+cycle.  As the source evolves, its shape becomes simpler, and the
+sharpness of one global minimum appears to increase.
+
+State-switches analogous to those observed in LP 12-502 occur at
+cycles 498 and 2554.  During the cycle 498 switch, two narrow dips at
+$\phi$$\approx$$-0.4$ and $\phi$$\approx$0.0 collapse.  For the cycle
+2554 switch, a longer dip collapses.  This is visible as a change in
+curvature in Figure~\ref{fig:tic3006timegroups} between $\phi \in
+[-0.25, -0.05]$ across cycles 2520-2561.  The  more typical dip
+evolution timescales for TIC~300651846 seem to be $\approx$50-100
+cycles.  Unlike the TIC~402980664 river plots
+(Figure~\ref{fig:lpriver0}), we did not subtract any ``continuum
+sinusoid'' for this source, because the continuum is not as obviously
+defined.
 
@@
 one minute.  Between 2020 and 2021, we observed 10 CRs at 20-second
-cadence with TESS in order to explore this question (TESS DDT029).
+cadence with TESS in order to explore this question (TESS DDT029; PI L.~Bouma).
 The stars were TICs 142173958, 146539195, 24518895, 276453848,
@@
 	\subfloat{
-			\includegraphics[width=0.9\textwidth]{f13a.pdf}
-    }
-
-	\vspace{-1.1cm}
+			\includegraphics[width=0.7\textwidth]{f13a.pdf}
+    }
+
+	\vspace{-1.cm}
 	\subfloat{
-			\includegraphics[width=0.9\textwidth]{f13b.pdf}
-    }
-
-	\vspace{-1.1cm}
+			\includegraphics[width=0.7\textwidth]{f13b.pdf}
+    }
+
+	\vspace{-1.cm}
 	\subfloat{
-			\includegraphics[width=0.9\textwidth]{f13c.pdf}
+			\includegraphics[width=0.7\textwidth]{f13c.pdf}
     }

### 2023-08-31 paper/ms.tex
update ms

@@
 is that there is a local minimum in the effective potential of the
-corotating frame; given a flow from the either the star or from a
+corotating frame; given a flow from either the star or from a
 tenuous accretion disk, this local potential minimum enables material
@@
 short-term mechanical stability of such gas configurations is
-theoretically plausible for such stars
+theoretically plausible for rapidly rotating stars
 \citep{2000MNRAS.316..647F,2022MNRAS.514.5465W}.   To our best
@@
     \item Most CR dips have durations a few times longer than $T_{\rm
-      dur}$ (Figure~\ref{fig:cqvs}).  Such dips are often superposed
+      dur}$ (Figure~\ref{fig:cqvs}).  The dips are often superposed
       on a quasi-sinusoidal signal that presumably comes from
@@
       longitudinal flux distribution across the stellar surface.  The
-      only viable explanation for the sharp dips being superposed on
-      the quasi-sinusoidal signals is that clumps of circumstellar
-      material are corotating with the star.  Assuming that the longer
-      dips have the same physical origin as the shortest dips, the
-      transiting material must therefore also be capable of having
-      effective sizes comparable to the star.
+      only viable explanation currently known for the sharp dips being superposed on
+      the quasi-sinusoidal signals is that concentrations (``clumps'')
+      of circumstellar material are corotating with the star.
+      Assuming that the longer dips have the same physical origin as
+      the shortest dips, the transiting material must therefore also
+      be capable of having effective sizes comparable to the star.
 %

### 2023-08-31 paper/ms.tex
update ms

@@
 CRs, while also being able to consistently reject common false
-positives such as rapidly rotating spot-induced variability and
-typical eclipsing binaries.
+positives such as spot-induced variability and
+eclipsing binaries.
 
@@
 with a combination of radiative cores and convective envelopes, with
-the dividing line at around $M_\star = 0.25\,M_\odot$
+the dividing line for these ages at around $M_\star = 0.25\,M_\odot$
 \citep{2018A&A...619A.177B}.  We found no obvious differences in light
@@
 above the Gaia single-source astrometric model is common
-(\ngoodhighruwe/\ngoods\ high-quality CRs with RUWE$_{\rm DR3}$$>$2),
+(\ngoodhighruwe/\ngoods\ high-quality CRs have RUWE$_{\rm DR3}$$>$2),
 as is the presence of multiple periods in the TESS light curves
-(\ngoodmultperiodflag/\ngoods).  Elevated astrometric noise is almost
-always accompanied by multiple detectable TESS periods
+(\ngoodmultperiodflag/\ngoods).  Elevated astrometric noise almost
+always implies multiple detectable TESS periods
 (\ngoodruweandmultperiod/\ngoodhighruwe\ high-quality CRs).  The
@@
 rotating stars, we would expect a sample of CRs to have a larger
-binary fraction than the field.  We do not see clear evidence for such
+binary fraction than the field.  We see marginal, if any, evidence for such
 an effect.  The multiplicity rate of M dwarfs near the Sun is
@@
 $0.15$-$0.30$\,$M_\odot$ M dwarfs.  The multiplicity fraction in our
-CR sample seems approximately consistent with this field fraction.
+CR sample (32\% from RUWE$_{\rm DR3}$) seems approximately consistent
+with this field fraction.
 
@@
 P_1^{-1})^{-1}$ of 10.8\,hr.  This is a novel false positive scenario
-for CRs: two rapidly-rotating stars with near-integer ratios of
-rotation periods.  The beat between the two rotation signals produces
-the apparent CR signal.  Such false positives can be excluded through
-careful accounting of all peaks in a periodogram.  For instance,
-TIC~435903839 shows a peak at 16.27\,hr, which is not an integer
-multiple of the dispersion-minimizing 10.82\,hr period.
+for CRs: two rapid rotators near the 3:2 period commensurability.
+The beat between the two rotation signals produces the apparent CR
+signal.  Such false positives can be excluded through careful
+accounting of all peaks in a periodogram.  For instance, TIC~435903839
+shows a peak at 16.27\,hr, which is not an integer multiple of the
+dispersion-minimizing 10.82\,hr period.
 
@@
 Figures~\ref{fig:evoln} and~\ref{fig:lpriver0}).  The CRs are
-therefore quasiperiodic, with a characteristic dip longevity of
-$\approx$100 cycles.  While this observation is consistent with the
-analyses by \citet{2022AJ....163..144G} and
-\citet{2023ApJ...945..114P}, it marks a qualitative departure from the
-``persistent'' {\it vs.} ``transient'' flux dip distinction described
-by \citet{2017AJ....153..152S}, since all CR dips seem to be transient
-over timescales of more than 1{,}000 cycles (Figure~\ref{fig:evoln}).
+therefore quasiperiodic, with quality factors of $Q$$\approx$100.
+While this observation is consistent with the analyses by
+\citet{2022AJ....163..144G} and \citet{2023ApJ...945..114P}, the fact
+that all CR dips seem to be transient over timescales of more than
+1{,}000 cycles (Figure~\ref{fig:evoln}) marks a qualitative departure
+from the ``persistent'' {\it vs.} ``transient'' flux dip distinction
+previously described by \citet{2017AJ....153..152S}.
 
@@
 \subsubsection{What is a prominence?}
-The prominence idea is based on an analogy with quiescent
+The prominence idea is based on a loose analogy with quiescent
 prominences/filaments in the solar corona that last as long as a few
@@
 short-term mechanical stability of such gas configurations is
-theoretically plausible for rapidly rotating stars
+theoretically plausible for rapid rotators
 \citep{2000MNRAS.316..647F,2022MNRAS.514.5465W}.   To our best
@@
 \citet{2019MNRAS.482.2853J}--AB~Dor, Speedy~Mic, LQ Lup, HK Aqr, and
-V374 Peg--and detected no CR behavior.  Assuming that
-spectroscopically observable prominence systems do not turn off, this would
-imply that they are not always accompanied by photometric CR-like
-dips: a link between the spectroscopic prominences
-that may exist around rapidly rotating low-mass stars and the CR
-phenomenon has yet to be made.
+V374 Peg--and detected no CR behavior.  While individual prominences
+may only last one to tens of rotation cycles, the prominence system
+itself is thought to always be ``on'', due to the repeatable
+detectability of spectroscopic transients \citep[e.g.][and references
+therein]{1990MNRAS.247..415C}.  Assuming that spectroscopically
+observable prominence systems indeed do not turn off, this would imply
+that they are not always accompanied by photometric CR-like dips: a
+link between the spectroscopic prominences that may exist around
+rapidly rotating low-mass stars and the CR phenomenon has yet to be
+made.
 
@@
 absorption can be excluded, since it provides opacity only at narrow
-resonant lines, the (neutral) hydrogen opacity due to bound-free
+resonant lines, the hydrogen opacity due to bound-free
 absorption is ``jagged'' \citep[see][Figure 8.5 and
@@
 scenario, because pre-main-sequence M dwarfs spin up over the first
-100\,Myr; prominences might therefore even be expected to be {\it
+100\,Myr; prominences might therefore be expected to be {\it
 more} common at 100\,Myr than at 10\,Myr, under the assumption that the
@@
 of rapidly rotating M dwarfs may depend on factors other than the
-rotation rate (e.g. the age), which might affect the production of prominences.
+rotation rate (e.g.\ the age), which might alter the production of prominences.
 
@@
 corotation radius for low accretion rates
-\citep{2016ARA&A..54..135H,2022MNRAS.510.5246L}.  These considerations
+\citep[e.g.][]{2016ARA&A..54..135H,2022MNRAS.510.5246L}.  These considerations
 invite us to imagine one or more planets migrating inward due to gas
@@
 With this picture in mind, it is tempting to attribute features of the
-CR light curves as transits of material ejected by planets or
+CR light curves to transits of material ejected by planets or
 planetesimals.  Young rocky bodies are expected to be hot, and they
@@
 to explain the observed phases of the observed dips.  The azimuthal
-angle of the eventual entrainment would be entirely determined by the
+angle of the eventual entrainment could be entirely determined by the
 stellar magnetic field.  In this scenario, the obscuring material
@@
 
-Although this outlier is intriguing, stars without infrared excessess
-typically have more stable optical light curves than those with
+Although this outlier is intriguing, stars without infrared excesses
+generally have more stable optical light curves than those with
 infrared excesses.  While some dippers may evolve into CRs after the
 disk is mostly gone, this would be generically expected based on the
-population statistics: young stars become older.  There may be no
+population statistics: young objects become old.  There may be no
 other causal connection between the two evolutionary stages.  With
@@
 {\rm d}N/{\rm d}t$ time-averaged over six months is
-$\approx$3$\times$$10^{-18} M_\odot\,{\rm yr}^{-1} \approx
+%$\approx$3$\times$$10^{-18} M_\odot\,{\rm yr}^{-1}
+$\approx
 1\times10^{-12} M_\oplus\,{\rm yr}^{-1}$.  Considered cumulatively
@@
 $10^{-4}\,M_\oplus$, of order the Solar System's asteroid belt.  If
-the occulting material is gas, the masses involved would be of order
+the occulting material is gas, the lower mass bounds would be of order
 100 times larger.  For cases in which we observe the {\it growth} of
@@
 2018 July to 2022 September for complex rotators (CRs).  The target
-stars were \nstarssearched\ K and M dwarfs within 150\,pc.  The
-selection function was $>$$80\%$ complete within 30\,pc, and $<$$10\%$
-complete at distances exceeding 100\,pc.
-
-In our target sample, we found \ngoods\ objects that showed complex
+stars were \nstarssearched\ late-K and early-to-mid M dwarfs within 150\,pc
+and with TESS magnitudes $T$<16. 
+The selection function included $>$$80\%$ of such stars within 30\,pc, and $<$$10\%$ of such stars at distances exceeding 100\,pc (Figure~\ref{fig:completeness}).
+
+We found \ngoods\ objects that showed complex
 quasiperiodic behavior over at least one TESS sector.  These \ngoods\
@@
       dur}$ (Figure~\ref{fig:cqvs}).  The dips are often superposed
-      on a quasi-sinusoidal signal that presumably comes from
-      starspots and faculae that produce inhomogeneities in the
-      longitudinal flux distribution across the stellar surface.  The
-      only viable explanation currently known for the sharp dips being superposed on
-      the quasi-sinusoidal signals is that concentrations (``clumps'')
-      of circumstellar material are corotating with the star.
+      on a quasi-sinusoidal signal that presumably originates from
+      inhomogeneities in the stellar surface brightness
+      distribution (starspots and faculae).  The
+      only viable explanation currently known for sharp dips being superposed on
+      the starspot signals is that concentrations (``clumps'')
+      of circumstellar material corotate with the star.
       Assuming that the longer dips have the same physical origin as
-      the shortest dips, the transiting material must therefore also
-      be capable of having effective sizes comparable to the star.
+      the shortest dips, the clumps must also
+      be capable of having sizes comparable to the star.
 %
@@
 %{\bf AUTHOR CONTRIBUTION STATEMENTS: PLEASE REVISE IF APPROPRIATE)}
-LGB conceived the project and performed the dip-counting search, light curve classification, cluster membership, SED, variability, and secondary-period analyses.
+LGB conceived the project, performed the dip-counting search, light curve classification, cluster membership, SED, variability, and secondary-period analyses, and wrote the manuscript.
 RJ and SR performed the Fourier-based analysis and contributed to light curve classification.

### 2023-09-01 paper/ms.tex
Update ms (LR suggestions)
Co-authored-by: Luisa Rebull <rebull@ipac.caltech.edu>

@@
 reported to date
-\citep{2016AJ....152..114R,2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2020AJ....160...86B,2022AJ....163..144G,2023ApJ...945..114P}.
+\citep{2016AJ....152..114R,2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2020AJ....160...86B,2021AJ....161...60S,2022AJ....163..144G,2023ApJ...945..114P}.
 They have been hard to characterize because many of the known CRs are
-relatively faint; the initial K2 discoveries
+faint; the initial K2 discoveries
 \citep{2016AJ....152..114R,2017AJ....153..152S} were M2-M6 dwarfs at
@@
 ``complex rotator'' correctly draws attention to the fact that
-rotation will play a fundamental role in explaining these objects, and
-that their key defining feature is the complexity of their optical
-light curves relative to the quasi-sinusoidal modulations of
-starspots.
+{\it complexity} relative to quasi-sinusoidal starspots is the
+defining phenomenological feature of these objects, while also highlighting the expectation that {\it
+rotation} will play a central role in explaining their physical
+behavior.
 
@@
 below 1$''$, and projected physical separations $\lesssim$50\,AU.
+These observations are also in agreement with previous analyses of
+multi-periodic low-mass discovered by K2, which found that such
+systems are almost always binaries
+\citep{2018AJ....156..138T,2018AJ....156..275S}.
 
@@
 have periods of 11.76\,hr and 12.84\,hr.  For TIC~425937691, the two
-periods are 4.82\,hr and 3.22\,hr, near the 3:2 commensurability.
+periods are 4.82\,hr and 3.22\,hr, near the 3:2 period commensurability.
 Given that both sources have two photometric signals and elevated
 RUWEs, each source is probably an unresolved binary consisting of two
-CRs.
+CRs.  To our knowledge, these are the third and fourth such systems
+known: EPIC~204060981 has two CRs with periods of 9.59\,hr and
+9.12\,hr \citep{2018AJ....155...63S}, and TIC~242407571 has two CRs
+with periods of 11.33\,hr and 13.63\,hr, near the 6:5 period commensurability
+\citep{2021AJ....161...60S}.\footnote{TIC~242407571, although within
+our nominal distance and brightness limits, was not observed by TESS
+in the 120-second cadence mode between 2018~July and 2022~September, and is therefore not in our sample.}
 
@@
 correct, it would not provide an immediate explanation for the
-near-commensurability of the two periods of TIC~425937691 (the ratio
-is within 1\% of 3:2).
+near-commensurability of the two periods of either TIC~425937691 
+or TIC~242407571.
 

### 2023-09-01 paper/ms.tex
update ms

@@
       circumstellar plasma tori.  HD~37776 and HD~64740 (middle row)
-      are analogous magnetic B stars with field topologies dominated by
+      are analogous magnetic B stars with field topologies potentially dominated by
       high order multipoles.  The bottom row compares the latter
@@
 magnetic B stars have simple light curves are HD~37776 and HD~64740.
-Both stars are known from spectropolarimetry to have field geometries
-dominated by high order multipoles \citep{2011ApJ...726...24K}.
-And, recent TESS light curves of these two B stars appear surprisingly
-similar to the CR light curves \citep{2020pase.conf...46M}.  The
-middle row of Figure~\ref{fig:bstar} shows the phased TESS light
-curves for these two stars, with by-eye best-matching CRs shown
-underneath for comparison.  The number of dips per cycle, the shapes
-of the dips, and the dip depths relative to the sinusoidal envelope
-are all similar.  This connection suggests that the highly structured
-light curves of both the M dwarfs and the B stars are associated with
-(and perhaps caused by) strong non-dipolar magnetic fields.
-Non-dipolar fields for M dwarfs are plausible, given that Zeeman
-Doppler Imaging has revealed non-axisymmetric magnetic field patterns
-for the few M dwarfs for which this technique is technically feasible
-\citep[see][and references therein]{2021A&ARv..29....1K}.
+HD~37776 is known from spectropolarimetry to have an extreme field
+geometry dominated by high order multipoles
+\citep{2011ApJ...726...24K}.  The field geometry of HD~64740, while
+potentially less extreme, is also less well-studied
+\citep[see][Ch.~4]{1988PhDT........53B}.  Recent TESS light curves
+of these two B stars appear surprisingly similar to the CR light
+curves \citep{2020pase.conf...46M}.  The middle row of
+Figure~\ref{fig:bstar} shows the phased TESS light curves for these
+two stars, with by-eye best-matching CRs shown underneath for
+comparison.  The number of dips per cycle, the shapes of the dips, and
+the dip depths relative to the sinusoidal envelope are all similar.
+This connection suggests that the highly structured light curves of
+both the M dwarfs and the B stars are associated with (and perhaps
+caused by) strong non-dipolar magnetic fields.  Non-dipolar fields for
+M dwarfs are plausible, given that Zeeman Doppler Imaging has revealed
+non-axisymmetric magnetic field patterns for the few M dwarfs for
+which this technique is technically feasible \citep[see][and
+references therein]{2021A&ARv..29....1K}.
 

### 2023-09-02 paper/ms.tex
update ms

@@
   most viable explanation for CRs. The gas or dust is probably
-  entrained by the star's magnetic field, and the sharp features may
+  entrained by the star's magnetic field, and the sharp features could
   result from a multipolar field topology, a hypothesis supported by
   correspondences between the light curves of CRs and of B stars
-  known to have strong multipolar magnetic fields.
+  that may have strong multipolar magnetic fields.
 \end{abstract}
@@
 %
-    \item Surprising analogs to the CRs exist in two magnetic B stars
-      with multipolar field topologies.  Since most magnetic B stars
-      have dipolar magnetic fields, this suggests that the CR dips and
-      warps are similarly being sculpted by the stellar magnetic
-      fields, and that the magnetic fields themselves are potentially
-      also multipolar.
+    \item Surprising analogs to the CRs exist in two magnetic B stars,
+      one of which is known to have an extreme multipolar field
+      topology.  Since most magnetic B stars have dipolar magnetic
+      fields \citep{2009ARA&A..47..333D}, this suggests that the CR
+      dips and warps are similarly being sculpted by the stellar
+      magnetic fields, and that the magnetic fields themselves are
+      potentially also multipolar.
 %

### 2023-09-04 paper/ms.tex
update ms

@@
 
-%\title{Transient Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Rotators from TESS}
 \title{Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS}
@@
 
-% PENDING DISCUSSION!
-%\author[0000-0002-0531-1073]{H. Isaacson}
-%\affiliation{\berkeley}
-%
-%\author[0000-0001-8638-0320]{A. W. Howard}
-%\affiliation{\caltech}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{abstract}
-  We study a set of pre-main-sequence stars
+  We explore a set of pre-main-sequence stars
   with sub-solar masses, rotation periods of 0.2--2 days, optical variability amplitudes
@@
   12-502, stands out for the complexity of its light curve --- with as
-  many as eight flux dips per cycle --- and the detail with which the
+  many as eight flux dips per cycle --- and for the detail with which the
   evolution in each dip's amplitude and phase can be tracked over
@@
   correspondences between the light curves of CRs and of B stars
-  that may have strong multipolar magnetic fields.
+  that may have multipolar magnetic fields.
 \end{abstract}
@@
 Likewise, Thomson scattering is too gray to be the dominant opacity
-source.
+source.  From hydrogen alone, bound-free absorption therefore seems
+like the most plausible opacity source.  However it remains to be
+demonstrated whether a sufficient population of excited states could
+be maintained, particularly given the short ($\approx$microsecond)
+radiative decay timescales.
 
@@
 of M dwarfs younger than $\approx$100\,Myr show the CR phenomenon
-\citep{2016AJ....152..114R,2022AJ....163..144G}.
+\citep{2016AJ....152..114R,2022AJ....163..144G,2022AJ....164...80R}.
 
@@
     \item The shortest CR dips, also with durations of
-      $\approx$0.05\,$P$, match the expected transit duration of a
+      $\approx$0.05\,$P$, match the expected transit duration for a
       small body at the corotation radius, $T_{\rm dur} \equiv R_\star
@@
 %
-    \item Most CR dips have durations a few times longer than $T_{\rm
+    \item Many CR dips have durations a few times longer than $T_{\rm
       dur}$ (Figure~\ref{fig:cqvs}).  The dips are often superposed
@@
       Assuming that the longer dips have the same physical origin as
-      the shortest dips, the clumps must also
+      the shortest dips, the corotating clumps must also
       be capable of having sizes comparable to the star.
@@
 
-The distinction between gas or dust is important because it will
+The distinction between gas or dust is important because it could
 clarify whether the CR phenomenon is intrinsic, so that material
@@
 LGB is grateful for support from the Heising-Simons 51~Pegasi~b
-Fellowship, and for helpful conversations with G.~Laughlin, A.~Mann,
-and J.~Spake.  
-This paper relied on data collected by the TESS
-mission, which are available from the Mikulski Archive for
-Space Telescopes (MAST).  The specific 120-second cadence observations
-can be accessed via DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.  Funding for the
-TESS mission is provided by NASA’s Science Mission Directorate.  TIC
-402980664 in particular was observed at 120-second cadence thanks to
-the TESS Guest Investigator programs G022252 (PI: J.~Schlieder;
-Sectors 18, 19, 25, 26) and G04168 (PI: R.~Jayaraman; Sector 53).
-LGB is also grateful for the assistance of 
-S.~Yee, L.~Weiss, H.~Isaacson, and A.~Howard in
-acquiring and analyzing the HIRES spectra.
+Fellowship.  This paper benefited from conversations between the
+authors and G.~Laughlin, A.~Mann, J.~Spake, and B.~Draine.  The paper
+also relied on data collected by the TESS mission, which are available
+from the Mikulski Archive for Space Telescopes (MAST).  The specific
+120-second cadence observations can be accessed via
+DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.
+Funding for the TESS mission is provided by NASA’s Science Mission
+Directorate.  TIC 402980664 in particular was observed at 120-second
+cadence thanks to the TESS Guest Investigator programs G022252 (PI:
+J.~Schlieder; Sectors 18, 19, 25, 26) and G04168 (PI: R.~Jayaraman;
+Sector 53).  LGB is also grateful for the assistance of S.~Yee,
+L.~Weiss, H.~Isaacson, and A.~Howard in acquiring and analyzing the
+HIRES spectra.
 

### 2023-09-04 paper/ms.tex
update ms: we are back to CPV

@@
 %%%%%%%%
-% CRS %
+% CPVS %
 %%%%%%%%
@@
 \accepted{---}
-\shorttitle{Four Years of Complex Rotators}
+\shorttitle{Four Years of Complex Periodic Variables}
 
@@
   eclipsing clumps of dust or gas orbiting at the corotation radius.
-  We refer to this class of variable star as ``complex rotators'' (CRs).
+  We refer to this class of star as ``complex periodic variables'' (CPVs).
   To improve our understanding of these
-  enigmatic objects, we conducted a survey for CRs using TESS
+  enigmatic objects, we conducted a survey for CPVs using TESS
   short-cadence data collected between 2018~July and 2022~September.
   Our search of \nstarssearched\ K and M dwarfs with $T$$<$16 and
-  $d$$<$150\,pc yielded \ngoods\ high-quality CRs, most of which are
+  $d$$<$150\,pc yielded \ngoods\ high-quality CPVs, most of which are
   new discoveries.  Our sample includes the brightest
   ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and oldest
-  ($\approx$200\,Myr) known CRs.  One of the new discoveries, LP
+  ($\approx$200\,Myr) known CPVs.  One of the new discoveries, LP
   12-502, stands out for the complexity of its light curve --- with as
@@
   1{,}500 cycles.  We argue that corotating gas or dust remains the
-  most viable explanation for CRs. The gas or dust is probably
+  most viable explanation for CPVs. The gas or dust is probably
   entrained by the star's magnetic field, and the sharp features could
   result from a multipolar field topology, a hypothesis supported by
-  correspondences between the light curves of CRs and of B stars
+  correspondences between the light curves of CPVs and of B stars
   that may have multipolar magnetic fields.
@@
 	\caption{
-		{\bf Complex rotators (CRs)}:
-		{\it Top:} Phase-folded TESS light curves for three CRs.  Each
+		{\bf Complex periodic variables (CPVs)}:
+		{\it Top:} Phase-folded TESS light curves for three CPVs.  Each
 		panel shows the average of the data accumulated over one month,
@@
 for which the root cause of variability is only beginning to become
-clear: complex rotators (CRs).  These objects are identified from
+clear: complex periodic variables (CPVs).  These objects are identified from
 their optical light curves, which show nearly periodic troughs that
@@
 \citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z}.
-Some CRs show up to eight dips per cycle.  Most CRs are
+Some CPVs show up to eight dips per cycle.  Most CPVs are
 pre-main-sequence M dwarfs with ages of $\approx$5-150 million years
@@
 not show near-infrared excesses indicative of dusty disks, but the
-wavelength-dependent dip amplitudes of some CRs is consistent with
+wavelength-dependent dip amplitudes of some CPVs is consistent with
 reddening by dust
@@
 
-The sharp features of CR light curves can have durations as short as
+The sharp features of CPV light curves can have durations as short as
 5\% of the rotation period ($P_{\rm rot}$), which is too short to be
@@
 \citealt{2017AJ....153..152S}, Figures 37-41).  Thus, a
-``starspot-only'' scenario can be ruled out for many CRs
+``starspot-only'' scenario can be ruled out for many CPVs
 \citep{2017AJ....153..152S,2019ApJ...876..127Z,2021MNRAS.500.1366K}.
-Given that many CRs cannot be explained by starspots alone, and
-working under the assumption that all CRs share the same basic
+Given that many CPVs cannot be explained by starspots alone, and
+working under the assumption that all CPVs share the same basic
 physical scenario, we discard the ``starspot-only'' scenario.
@@
 concentrates.  The empirical basis for this is that
-the sharp CR features are superposed over smooth, quasi-sinusoidal
+the sharp CPV features are superposed over smooth, quasi-sinusoidal
 starspot profiles.  The theoretical importance of the corotation
@@
 Although theoretical heritage for understanding rapid magnetic
-rotators exists, CRs have remained mysterious because they have been both
-hard to discover and hard to characterize.   They are hard to discover
-because they are rare: CRs comprise $\approx$1\% of the youngest
+rotators exists, CPVs have remained mysterious because they have been both
+hard to discover and hard to characterize.   They have been hard to discover
+because they are rare: CPVs comprise $\approx$1\% of the youngest
 $\approx$1\% of M dwarfs \citep{2018AJ....155..196R}.  Out of the
-millions of stars monitored by K2 and TESS, about 50 CRs have been
+millions of stars monitored by K2 and TESS, about 50 CPVs have been
 reported to date
 \citep{2016AJ....152..114R,2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2020AJ....160...86B,2021AJ....161...60S,2022AJ....163..144G,2023ApJ...945..114P}.
-They have been hard to characterize because many of the known CRs are
+They have been hard to characterize because many of the known CPVs are
 faint; the initial K2 discoveries
 \citep{2016AJ....152..114R,2017AJ....153..152S} were M2-M6 dwarfs at
-distances $\gtrsim$100\,pc, yielding optical brightnesses of
+distances $\gtrsim$100\,pc, with optical brightnesses of
 $V$$\approx$15.5 to $V$$>$20.  At such magnitudes, high-resolution
@@
 
-In this work, we aim to find bright and nearby CRs, since these
+In this work, we aim to find bright and nearby CPVs, since these
 objects will be the most amenable to detailed photometric and
@@
 Cycles 1-4).  We present our search methods in
-Section~\ref{sec:methods}, and the resulting CR catalog in
-Section~\ref{sec:results}.  The observed evolution of many CRs over a
+Section~\ref{sec:methods}, and the resulting CPV catalog in
+Section~\ref{sec:results}.  The observed evolution of many CPVs over a
 two-year baseline is described in Section~\ref{sec:evoln}, including a
@@
 Some comments on nomenclature are needed.  What we are calling
-``complex rotators''
-\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
-have also been called ``transient flux dips'', ``persistent flux
-dips'', and ``scallop shells'' by \citet{2017AJ....153..152S}, or more
-generally ``complex periodic variables'' by
-\citet{2023MNRAS.518.2921K}.  The CRs should not be conflated with
-``dippers'', which are classical T Tauri stars with infrared excesses,
-and which show large-amplitude variability linked to obscuring inner
-disk structures and accretion hot spots
+``complex periodic variables'' \citep{2023MNRAS.518.2921K} have also
+been called ``complex rotators''
+\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P},
+``transient flux dips'', ``persistent flux dips'', and ``scallop
+shells'' \citep{2017AJ....153..152S}.  The CPVs should not be conflated
+with ``dippers'', which are classical T Tauri stars with infrared
+excesses, and which show large-amplitude variability linked to
+obscuring inner disk structures and accretion hot spots
 \citep{2014AJ....147...82C,2021ApJ...908...16R}.  The phenomenology
-and stellar properties of CRs and dippers are quite different (though
-see Sections~\ref{subsec:irexcess} and~\ref{subsec:discdippers}).
-While we considered other possibilities, we ultimately concluded that
-``complex rotator'' correctly draws attention to the fact that
-{\it complexity} relative to quasi-sinusoidal starspots is the
-defining phenomenological feature of these objects, while also highlighting the expectation that {\it
-rotation} will play a central role in explaining their physical
-behavior.
+and stellar properties of CPVs and dippers are quite different (though
+see Sections~\ref{subsec:irexcess} and~\ref{subsec:discdippers}).  The
+defining phenomenological features of the CPVs are that their
+light curves are {\it complex}, relative to quasi-sinusoidal
+starspots, and the complex features are {\it periodic}, over
+timescales of order one hundred cycles.  While rotation likely
+does play a central role in explaining their physical behavior, the
+acronym for ``complex rotator'' is already widely used in the astrophysical
+literature for cosmic rays.  Given these
+considerations, we refer to the stars as complex periodic variables
+(CPVs); our preferred explanation for their behavior is that transient
+clumps of gas or dust orbit at the corotation radius.
 
@@
 
-To construct our sample, we analyzed the short-cadence data acquired
+We searched for CPVs by analyzing the short-cadence data acquired
 by TESS between 2018 July 25 and 2022 September 1 (Sectors 1-55).
@@
 
-To further simplify our search, we defined our target sample as
+To simplify our search, we defined our target sample as
 stars with 120-second cadence TESS light curves satisfying the
@@
 For stars with multiple sectors of TESS data available, we searched
-for CR signals independently.
+for CPV signals independently.
 In total, our \nstarssearched\ star target list included \nlcssearched\ month-long light
@@
 
-\subsection{CR discovery}
+\subsection{CPV discovery}
 \label{subsec:discoverymethods}
 
-Prior to this study, most CRs have been found by visually examining
+Prior to this study, most CPVs have been found by visually examining
 all the light curves of stars in young clusters
@@
 The dip counting technique aims to count sharp local minima in
-phase-folded light curves.  The most remarkable CRs often show three
+phase-folded light curves.  The most remarkable CPVs often show three
 or more dips per cycle, which distinguishes them from other types of
@@
 correctly re-identify a large fraction ($>$90\%) of previously known
-CRs, while also being able to consistently reject common false
+CPVs, while also being able to consistently reject common false
 positives such as spot-induced variability and
@@
 
-In short, CR candidates were identified by requiring a peak PDM period
+In short, CPV candidates were identified by requiring a peak PDM period
 below two days and the presence of at least three sharp local minima,
@@
 light curve based on visual inspection of its morphology (with
-categories including eclipsing binary, CR, RS CVn, and cataclysmic
-variable). Whenever a CR was identified, the light curves from
+categories including eclipsing binary, CPV, RS CVn, and cataclysmic
+variable). Whenever a CPV was identified, the light curves from
 multiple sectors were stitched together and analyzed jointly, for a
@@
 		\caption{
-      {\bf Validation plots used to classify CRs}.  The complete figure
+      {\bf Validation plots used to classify CPVs}.  The complete figure
       set, with one image per sector for each of the \nallcands\
@@
 (Section~\ref{subsec:fourier}) techniques were consistent with
-expectations for CRs by assembling the data shown in
-Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CR if it met
+expectations for CPVs by assembling the data shown in
+Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CPV if it met
 all of the following criteria for at least one TESS sector:
@@
   %
-  \item Dip phases (mostly) repeat over $\approx$30\,day sector duration.
+  \item Dip phases mostly repeat over $\approx$30\,day sector duration.
 \end{itemize}
 \vspace{-2pt}
-We also noted ''possible'' CRs for which the classification was more
-ambiguous, and ``false positives'' that are definitely not CRs.  The
+We also noted ''possible'' CPVs for which the classification was more
+ambiguous, and ``false positives'' that are definitely not CPVs.  The
 most common false positives for both the Fourier and dip-counting
@@
 \nuniqdipflagged\ unique stars for visual inspection; about 20\% were
-subsequently labeled either good or possible CRs.  From the Fourier
+subsequently labeled either good or possible CPVs.  From the Fourier
 pipeline, $\approx$0.5\% of stars that passed the 12-$\sigma$ peak
-threshold were eventually classified as CRs.  This is because the
+threshold were eventually classified as CPVs.  This is because the
 Fourier pipeline was implemented as a general variability search; its
-results are also being used for analyses on topics other than CRs.
+results are also being used for analyses on topics other than CPVs.
 
@@
 We estimated the stellar ages by making probabilistic spatial and
-kinematic associations between the CRs and known clusters in the solar
+kinematic associations between the CPVs and known clusters in the solar
 neighborhood.  For most stars in our sample, we did this using
@@
 		\caption{
-      {\bf CRs found in the TESS 2-minute data.}
+      {\bf CPVs found in the TESS 2-minute data.}
       Phased TESS light curves over one month are shown for \ngoods\
-      CRs in the high quality sample.  Gray are raw 2-minute data;
+      CPVs in the high quality sample.  Gray are raw 2-minute data;
       black bins to 300 points per cycle.  Objects are ordered such
@@
 
-\subsection{CR catalog}
+\subsection{CPV catalog}
 \label{sec:catalog}
@@
 our search.  The \ngoods\ stars in the ``good'' sample demonstrated
-what we deemed to be the key characteristics of the CR phenomenon in
-at least one TESS sector.  The classification of \nmaybes\ CR
+what we deemed to be the key characteristics of the CPV phenomenon in
+at least one TESS sector.  The classification of \nmaybes\ CPV
 candidates was ambiguous, and the \ndebunked\ remaining objects were
@@
 TESS or other instruments could help resolve the classification of the
-ambiguous cases.   Of the \ncqvsnodebunked\ CRs and candidate CRs,
+ambiguous cases.   Of the \ncqvsnodebunked\ CPVs and candidate CPVs,
 \nbothdipfourier\ were found using both the dip-counting and Fourier
@@
 Figure~\ref{fig:cqvs} is a mosaic of phased light curves for the
-\ngoods\ CRs.  The objects are sorted first in order of the number of
+\ngoods\ CPVs.  The objects are sorted first in order of the number of
 TESS 120-second cadence sectors in which they clearly demonstrated the
-CR phenomenon, and secondarily by descending brightness.  The top
+CPV phenomenon, and secondarily by descending brightness.  The top
 five objects by this metric are TIC~300651846 ($T$$=$13.5, 12
@@
 ($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5 sectors); and
-TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest five CRs span
+TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest five CPVs span
 9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
@@
 
-Of our \ncqvsnodebunked\ confirmed and candidate CRs,
+Of our \ncqvsnodebunked\ confirmed and candidate CPVs,
 \nnotfieldbanyan\ were associated with a nearby moving group or open
@@
 $\approx$5-200\,Myr.  The groups that contain the largest number of
-CRs in our catalog are Sco-Cen, Tuc-Hor, and Columba.  Six CRs were
+CPVs in our catalog are Sco-Cen, Tuc-Hor, and Columba.  Six CPVs were
 also identified in the Argus association \citep{2019ApJ...870...27Z},
@@
 Given the $\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there
-may be many more CRs in Sco-Cen that remain to be discovered.
+may be many more CPVs in Sco-Cen that remain to be discovered.
 
@@
 literature search led to a confident association with any young group.
-Both stars display CR signals over multiple TESS sectors. Both are
+Both stars display CPV signals over multiple TESS sectors. Both are
 photometrically elevated relative to the main sequence, an indication
@@
 
-Our search confirms that the CR phenomenon persists for at least
+Our search confirms that the CPV phenomenon persists for at least
 $\approx$150\,Myr.  Table~\ref{tab:thetable} includes three
-$\approx$150\,Myr CRs in AB~Dor \citep{2015MNRAS.454..593B}, a
-$\approx$112\,Myr old Pleiades CR \citep{2015ApJ...813..108D}, and a
+$\approx$150\,Myr CPVs in AB~Dor \citep{2015MNRAS.454..593B}, a
+$\approx$112\,Myr old Pleiades CPV \citep{2015ApJ...813..108D}, and a
 similarly-aged Psc-Eri member \citep{2020A&A...639A..64R}.  To our
@@
 \citealt{2015MNRAS.454..593B}) was the previous record-holder for the
-oldest-known CR \citep{2019ApJ...876..127Z,2022AJ....163..144G}; at
-least one unambiguous CR (EPIC~211070495) and a few other candidates
+oldest-known CPV \citep{2019ApJ...876..127Z,2022AJ....163..144G}; at
+least one unambiguous CPV (EPIC~211070495) and a few other candidates
 were also previously known in the Pleiades
@@
 
-The maximum age of CRs might even exceed 200\,Myr, based on the
+The maximum age of CPVs might even exceed 200\,Myr, based on the
 candidate membership of TIC~294328887 in the Carina Near moving group
@@
 
-Most CRs in our catalog did not show infrared excesses in the
+Most CPVs in our catalog did not show infrared excesses in the
 $W1$-$W4$ bands, which is typical for this class of object
@@
 respectively.  In our initial labeling, we labeled both as
-``ambiguous'' CRs because the dips in their Sector~36 light curves
+``ambiguous'' CPVs because the dips in their Sector~36 light curves
 seemed to stochastically evolve over only one or a few cycles, which
-is not typical of CRs; their periods were also long in comparison with
-most of the other CRs.  Inspection of additional sectors clarified
-that both sources are dippers, not CRs (see the online plots in
+is not typical of CPVs; their periods were also long in comparison with
+most of the other CPVs.  Inspection of additional sectors clarified
+that both sources are dippers, not CPVs (see the online plots in
 Figure~\ref{fig:vet}).  For TIC~57830249, the Sector~10 light curve of
@@
 appearing and disappearing within the span of one cycle.  None of the
-CRs in our sample exhibit this property.  Independently, TIC~193136669
+CPVs in our sample exhibit this property.  Independently, TIC~193136669
 is known to have a cold disk of dust and molecular gas, based on
@@
 \citet{2022ApJS..263...14C}; we agree with their designation, and
-label it an ``impostor'' CR in Table~\ref{tab:thetable}.
+label it an ``impostor'' CPV in Table~\ref{tab:thetable}.
 Section~\ref{subsec:discdippers} highlights plausible evolutionary
-connections between CRs and dippers in light of these
+connections between CPVs and dippers in light of these
 ``misclassifications''.
@@
 % a $P$=38\,hr singly-eclipsing binary, except with additional
-% substructure during each eclipse that resembles the CR phenomenon
+% substructure during each eclipse that resembles the CPV phenomenon
 % more than any other variability of which we are aware.  TIC~289840926
 % ($\beta$~Pic moving group, $P$=4.8\,hr), shows what we believe is a
-% clear CR signal, but has no definitive evidence for a large, dusty
+% clear CPV signal, but has no definitive evidence for a large, dusty
 % disk.  TIC~244161191 (TOI-278), in Columba, also has no definitive
 % evidence for a large disk.  It is however ``multi-periodic''---in
-% addition to the 7.17\,hr CR signal, this source shows a superposed
+% addition to the 7.17\,hr CPV signal, this source shows a superposed
 % 8.39\,hr sinusoidal signal, probably from an unresolved neighboring
@@
 		\caption{
-			{\bf Properties of CRs identified by our search}.
-      CRs are mostly pre-main-sequence M dwarfs, younger than
+			{\bf Properties of CPVs identified by our search}.
+      CPVs are mostly pre-main-sequence M dwarfs, younger than
       $\approx$150 Myr, with rotation periods faster than
-      $\approx$1\,day.  The \ngoods\ bona fide CRs in
+      $\approx$1\,day.  The \ngoods\ bona fide CPVs in
       Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
-      ambiguous CR candidates are light blue circles.  Unresolved
+      ambiguous CPV candidates are light blue circles.  Unresolved
       binaries (red circles) are objects for which the Gaia DR3 radial velocity
@@
       searched stars.  The lower-left panel compares the
-      rotation--color distribution of CRs against the rotation
+      rotation--color distribution of CPVs against the rotation
       periods of K and M dwarfs in the Pleiades from
@@
       derived corotation radii $R_{\rm c} = (GM/\Omega^2)^{1/3}$ in
-      units of stellar radii against the measured CR periods, in
+      units of stellar radii against the measured CPV periods, in
       units of hours.  Ages in the final panel are known from cluster
@@
 signals and hinder our ability to correctly identify the star hosting
-the CR signal.  Unresolved binaries could also bias photometric magnitude
+the CPV signal.  Unresolved binaries could also bias photometric magnitude
 and color measurements, which would affect our stellar parameter
@@
 ``radial velocity error'' as a function of stellar color for all
-\ncqvsnodebunked\ CRs and candidate CRs.  Since this quantity
+\ncqvsnodebunked\ CPVs and candidate CPVs.  Since this quantity
 represents the standard deviation of the non-published Gaia RV time
@@
 flag sources with excess astrometric noise.  This threshold was met
-by \ngoodhighruwe/\ngoods\ high-quality CRs and by
-\nmaybehighruwe/\nmaybes\ of the ambiguous CRs.  The choice of the threshold RUWE
+by \ngoodhighruwe/\ngoods\ high-quality CPVs and by
+\nmaybehighruwe/\nmaybes\ of the ambiguous CPVs.  The choice of the threshold RUWE
 is somewhat subjective, since the RUWE distribution has an extended tail
 \citep[e.g.][]{2022MNRAS.513.5270P}.  If we had instead required
-RUWE$_{\rm DR3}$ $>$ 1.4, \ngoodweakruwe/\ngoods\ high-quality CRs
+RUWE$_{\rm DR3}$ $>$ 1.4, \ngoodweakruwe/\ngoods\ high-quality CPVs
 and \nmaybeweakruwe/\nmaybes\ of the ambiguous sample would have been
@@
 non\_single\_star} column that flagged eclipsing, astrometric, and
-spectroscopic binaries.  None of the stars in our CR sample were
+spectroscopic binaries.  None of the stars in our CPV sample were
 identified as possible binaries in this column.
@@
 periods.  We also attempted to disentangle the two signals by
-subtracting the mean CR signal over each sector, and then repeating
+subtracting the mean CPV signal over each sector, and then repeating
 the phase-dispersion minimization analysis.  The results of this effort
@@
 different from the primary period.  This process yielded
-\ngoodmultperiodflag/\ngoods\ high-quality CRs with secondary
+\ngoodmultperiodflag/\ngoods\ high-quality CPVs with secondary
 periods; \nmaybemultperiodflag/\nmaybes\ of the ambiguous sample met
-the same criterion.  Of the \ngoodhighruwe\ good CRs with RUWE$_{\rm
+the same criterion.  Of the \ngoodhighruwe\ good CPVs with RUWE$_{\rm
 DR3}$ $>$ 2, \ngoodruweandmultperiod\ also showed secondary periods in
 the TESS light curves.  Considering the weaker threshold of RUWE$_{\rm
-DR3}$ $>$ 1.4, \ngoodweakruweandmultperiod/\ngoodweakruwe\ such CRs
+DR3}$ $>$ 1.4, \ngoodweakruweandmultperiod/\ngoodweakruwe\ such CPVs
 showed secondary TESS periods.
@@
 information into a single bitwise column.  We discuss possible
-connections between binarity and the CR phenomenon in
+connections between binarity and the CPV phenomenon in
 Section~\ref{subsec:discbinary}.
 
-\section{CR evolution}
+\section{CPV evolution}
 \label{sec:evoln}
@@
 		\caption{
-			{\bf Evolution of CR light curves over two years.}
-			Out of the \ngoods\ CRs in Figure~\ref{fig:cqvs}, 32 had
+			{\bf Evolution of CPV light curves over two years.}
+			Out of the \ngoods\ CPVs in Figure~\ref{fig:cqvs}, 32 had
 			120-second cadence TESS data available for a baseline of at
@@
 
-Figure~\ref{fig:evoln} shows ``before'' and ``after'' views of 27 CRs
+Figure~\ref{fig:evoln} shows ``before'' and ``after'' views of 27 CPVs
 for which TESS 120-second cadence observations were available at least
 two years apart.  Such a baseline was available for 32 of the
-confirmed \ngoods\ CRs in our catalog; for plotting purposes we show
+confirmed \ngoods\ CPVs in our catalog; for plotting purposes we show
 the brightest 27.  
@@
 
-A few objects in Figure~\ref{fig:evoln} show the CR phenomenon in one
-sector, and only marginal signs or no sign of CR behavior in the other
+A few objects in Figure~\ref{fig:evoln} show the CPV phenomenon in one
+sector, and only marginal signs or no sign of CPV behavior in the other
 sector.  In our subjective assessment, cases for which at least one
@@
 already gave this source such a label.  However, based on the shape
-evolution between Sectors 13 and 39, it is a CR.  Based on the
+evolution between Sectors 13 and 39, it is a CPV.  Based on the
 fraction of sources overall that ``turned off'', the observed shape
-evolution implies that CRs have an on-off duty cycle of $\approx$75\%.
+evolution implies that CPVs have an on-off duty cycle of $\approx$75\%.
 Correcting for the duty cycle might be important in population-level
-estimates of the intrinsic frequency of the CR phenomenon
+estimates of the intrinsic frequency of the CPV phenomenon
 \citep[e.g.][]{2022AJ....163..144G}.
@@
 
-A few of our complex rotators were near the TESS continuous viewing
+A few of our complex periodic variables were near the TESS continuous viewing
 zones (Figure~\ref{fig:catalogscatter}, top right).  Out of this
@@
 
-\subsection{Typical and extreme CRs}
+\subsection{Typical and extreme CPVs}
 \label{subsec:extreme}
@@
 Referring back to Figure~\ref{fig:catalogscatter}, which compares the
-properties of CRs with those of the search sample (top panels) and the
-Pleiades \citep{2016AJ....152..114R}, we see that the typical CR
+properties of CPVs with those of the search sample (top panels) and the
+Pleiades \citep{2016AJ....152..114R}, we see that the typical CPV
 masses span 0.1-0.4\,$M_\odot$, and the typical ages span 2-150\,Myr.
@@
 \citep{2018A&A...619A.177B}.  We found no obvious differences in light
-curve morphology between CRs above and below the boundary of
+curve morphology between CPVs above and below the boundary of
 0.25\,$M_\odot$.  In terms of their rotation rates relative to the
-Pleiades, the CRs are among the more rapidly rotating half of M
+Pleiades, the CPVs are among the more rapidly rotating half of M
 dwarfs.
 
-The closest CR in our catalog is DG~CVn (TIC~368129164; $d$$=$18\,pc),
+The closest CPV in our catalog is DG~CVn (TIC~368129164; $d$$=$18\,pc),
 a member of AB Dor.  To our knowledge, this star had not previously
-been recognized as a CR.  The three brightest CRs are DG~CVn
+been recognized as a CPV.  The three brightest CPVs are DG~CVn
 ($T$=9.3), TIC~405754448 ($T$=9.6), and TIC~167664935 ($T$=10.3).  The
@@
 period, 37.9\,hr, belongs to TIC~405910546.  If the latter source
-turns out to be an eclipsing binary, the longest-period CR in the
+turns out to be an eclipsing binary, the longest-period CPV in the
 catalog would be TIC~193831684 (31.0\,hr).  By definition, we required
@@
 The catalog contains a few other stars with similar mass.  We cannot
-rule out the possibility that CRs exist with even lower masses, given
+rule out the possibility that CPVs exist with even lower masses, given
 the small number of such low-mass stars in our target sample.  Perhaps
-even brown dwarfs can be CRs, although it might be difficult to
-distinguish the type of variability we associate with CRs from the
+even brown dwarfs can be CPVs, although it might be difficult to
+distinguish the type of variability we associate with CPVs from the
 usual variability of brown dwarfs caused by clouds and latitudinal
@@
 
-\subsection{CRs and binarity}
+\subsection{CPVs and binarity}
 \label{subsec:discbinary}
@@
 In Section~\ref{subsec:binarity}, we found that a significant fraction
-of the CRs show indications of unresolved binarity.  Excess noise
+of the CPVs show indications of unresolved binarity.  Excess noise
 above the Gaia single-source astrometric model is common
-(\ngoodhighruwe/\ngoods\ high-quality CRs have RUWE$_{\rm DR3}$$>$2),
+(\ngoodhighruwe/\ngoods\ high-quality CPVs have RUWE$_{\rm DR3}$$>$2),
 as is the presence of multiple periods in the TESS light curves
@@
 always implies multiple detectable TESS periods
-(\ngoodruweandmultperiod/\ngoodhighruwe\ high-quality CRs).  The
+(\ngoodruweandmultperiod/\ngoodhighruwe\ high-quality CPVs).  The
 latter observation corroborates the claim that most sources with
@@
 
-One possible relation between binarity and CRs is that the presence of
+One possible relation between binarity and CPVs is that the presence of
 an intermediate-separation binary could cause early disk dispersal,
-freeing the star to contract.  The CR phenomenon seems to require
+freeing the star to contract.  The CPV phenomenon seems to require
 rapid rotation; thus if binary systems tend to produce more rapidly
-rotating stars, we would expect a sample of CRs to have a larger
+rotating stars, we would expect a sample of CPVs to have a larger
 binary fraction than the field.  We see marginal, if any, evidence for such
@@
 $0.15$-$0.30$\,$M_\odot$ M dwarfs.  The multiplicity fraction in our
-CR sample (32\% from RUWE$_{\rm DR3}$) seems approximately consistent
+CPV sample (32\% from RUWE$_{\rm DR3}$) seems approximately consistent
 with this field fraction.
 
-\subsubsection{Do K dwarf CRs exist?}
+\subsubsection{Do K dwarf CPVs exist?}
 \label{subsec:massive}
 
-To date, the only stars reported to show the CR phenomenon are M
+To date, the only stars reported to show the CPV phenomenon are M
 dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
 \citep{2017AJ....153..152S,2022AJ....163..144G}.  However the two most
-massive CRs in our sample, TIC~405754448 and TIC~405910546, were
+massive CPVs in our sample, TIC~405754448 and TIC~405910546, were
 assigned masses of $\approx$0.82\,$M_\odot$ and
@@
 suggestive of an eclipsing binary.  Independently, TIC~405910546 was
-one of only \nrvscatterflag\ CRs flagged with a Gaia DR3 radial
+one of only \nrvscatterflag\ CPVs flagged with a Gaia DR3 radial
 velocity scatter exceeding 20\,\kms.  Combined, these factors suggest
@@
 stronger.  The RUWE$_{\rm DR3}$ statistic is 6.8, and the raw light
-curves in Sectors 11, 37, and 38 show both the CR signal with period
+curves in Sectors 11, 37, and 38 show both the CPV signal with period
 12.9\,hr and amplitude $\approx$1\% and an additional sinusoidal
@@
 flux ratio between the primary and secondary would be expected to be
-$\approx$10:1.  Thus, if the K star were the source of the CR signal,
+$\approx$10:1.  Thus, if the K star were the source of the CPV signal,
 its intrinsic variability amplitude would be $\approx$1\%, while if
@@
 
-In short, these two objects suggest that the CR phenomenon may extend
+In short, these two objects suggest that the CPV phenomenon may extend
 up in mass to pre-main-sequence K dwarfs, but more data are needed to
@@
 
-\subsubsection{An astrophysical CR false positive: TIC~435903839}
+\subsubsection{An astrophysical CPV false positive: TIC~435903839}
 
 We originally classified TIC~435903839, with RUWE$_{\rm DR3}$=17.7, as
-an ``ambiguous'' CR with a 10.8\,hr period, because this period
+an ``ambiguous'' CPV with a 10.8\,hr period, because this period
 minimized the dispersion in the phase-folded light curve.  More
@@
 P_1^{-1})^{-1}$ of 10.8\,hr.  This is a novel false positive scenario
-for CRs: two rapid rotators near the 3:2 period commensurability.
-The beat between the two rotation signals produces the apparent CR
+for CPVs: two rapid rotators near the 3:2 period commensurability.
+The beat between the two rotation signals produces the apparent CPV
 signal.  Such false positives can be excluded through careful
@@
 
-\subsubsection{Multiple CRs in the same system: TIC~425937691 and TIC~142173958}
-
-TIC~142173958 and TIC~425937691 both show evidence for two separate CR
+\subsubsection{Multiple CPVs in the same system: TIC~425937691 and TIC~142173958}
+
+TIC~142173958 and TIC~425937691 both show evidence for two separate CPV
 signals in their TESS light curves.  For TIC~142173958, the signals
@@
 RUWEs, each source is probably an unresolved binary consisting of two
-CRs.  To our knowledge, these are the third and fourth such systems
-known: EPIC~204060981 has two CRs with periods of 9.59\,hr and
-9.12\,hr \citep{2018AJ....155...63S}, and TIC~242407571 has two CRs
+CPVs.  To our knowledge, these are the third and fourth such systems
+known: EPIC~204060981 has two CPVs with periods of 9.59\,hr and
+9.12\,hr \citep{2018AJ....155...63S}, and TIC~242407571 has two CPVs
 with periods of 11.33\,hr and 13.63\,hr, near the 6:5 period commensurability
@@
 $\lesssim$700 AU tend to be aligned with their planetary systems
-\citep[e.g.][]{2022AJ....163..207C}.  If we assume that observing CR
+\citep[e.g.][]{2022AJ....163..207C}.  If we assume that observing CPV
 variability requires high inclinations relative to the line of sight,
 and that the inclinations in binaries are correlated, then we would
-expect the detection of one CR in a binary system to raise the
-probability that the other star is a CR.  The limitations of the
+expect the detection of one CPV in a binary system to raise the
+probability that the other star is a CPV.  The limitations of the
 current catalog prevent further exploration of this issue, but it
@@
 
-\subsection{Transience \& special phases of CR dips}
-
-While CR periods appear to remain constant to within measurement
+\subsection{Transience \& special phases of CPV dips}
+
+While CPV periods appear to remain constant to within measurement
 precision over thousands of cycles, the light curve shapes evolve over
 typical timescales of 10 to 1{,}000 cycles (e.g.
-Figures~\ref{fig:evoln} and~\ref{fig:lpriver0}).  The CRs are
+Figures~\ref{fig:evoln} and~\ref{fig:lpriver0}).  The CPVs are
 therefore quasiperiodic, with quality factors of $Q$$\approx$100.
@@
 \citet{2022AJ....163..144G} and \citet{2023ApJ...945..114P}, the fact
-that all CR dips seem to be transient over timescales of more than
+that all CPV dips seem to be transient over timescales of more than
 1{,}000 cycles (Figure~\ref{fig:evoln}) marks a qualitative departure
@@
 
-One peculiarity of CR evolution however is that the dips do not
-explore all phase angles with equal weight.  LP 12-502, and other CRs,
+One peculiarity of CPV evolution however is that the dips do not
+explore all phase angles with equal weight.  LP 12-502, and other CPVs,
 have preferred phases lasting for at least two years.  For LP 12-502,
@@
 
-Examining Figure~\ref{fig:cqvs}, it is clear that CR dips can be
+Examining Figure~\ref{fig:cqvs}, it is clear that CPV dips can be
 asymmetric but it is not obvious whether there is a preference for
@@
 \citet{2019MNRAS.482.2853J}--AB~Dor, Speedy~Mic, LQ Lup, HK Aqr, and
-V374 Peg--and detected no CR behavior.  While individual prominences
+V374 Peg--and detected no CPV behavior.  While individual prominences
 may only last one to tens of rotation cycles, the prominence system
@@
 observable prominence systems indeed do not turn off, this would imply
-that they are not always accompanied by photometric CR-like dips: a
+that they are not always accompanied by photometric CPV-like dips: a
 link between the spectroscopic prominences that may exist around
-rapidly rotating low-mass stars and the CR phenomenon has yet to be
+rapidly rotating low-mass stars and the CPV phenomenon has yet to be
 made.
@@
 
-CRs show broadband flux variations that can be 1-2$\times$ deeper in
+CPVs show broadband flux variations that can be 1-2$\times$ deeper in
 the blue than in the red
@@
 star.\footnote{\citet{2019ApJ...876..127Z} explored the sublimation
-timescales for a canonical CR with $M_\star=0.2\,M_\odot$,
+timescales for a canonical CPV with $M_\star=0.2\,M_\odot$,
 $R_\star=0.3\,R_\odot$, and $T_{\rm eff}=3200\,{\rm K}$.  They found
@@
 temperature at $\approx$3\,$R_\star$.  This suggests that dust
-sublimation could be an important effect even for CRs. }  The opacity
+sublimation could be an important effect even for CPVs. }  The opacity
 source for $\sigma$~Ori~E and its analogs is instead thought to be
@@
 study to be conducted to determine to what degree the observed
-chromaticities in CRs match, or do not match, expectations from
+chromaticities in CPVs match, or do not match, expectations from
 radiative transfer.  This issue has a key ability to resolve the
-question of whether the CRs are explained by dust or by gas, which has
+question of whether the CPVs are explained by dust or by gas, which has
 bearing on whether the material producing the dips is coming from the
@@
 
-The observed lifetime of the CR phenomenon could provide another way
+The observed lifetime of the CPV phenomenon could provide another way
 to discern between the gas and dust clump scenarios.  Based on the
 available statistics from e.g.  \citet{2022AJ....164...80R} and
-references therein, it seems plausible that CR occurrence decreases
+references therein, it seems plausible that CPV occurrence decreases
 with stellar age from $\approx$3\% at 10\,Myr (Sco-Cen),
@@
 production of prominences depends only on the stellar rotation rate. 
-The dust clump scenario would hold a natural explanation: the lower occurrence of CRs around older stars would
+The dust clump scenario would hold a natural explanation: the lower occurrence of CPVs around older stars would
 simply reflect a finite supply of dust.
@@
 for the innermost planet is set by the location of the protoplanetary
-disk's truncation radius \citep{2018haex.bookE.142I}.  The 
+disk's truncation radius \citep[e.g.][and references therein]{2018haex.bookE.142I}.  The 
 truncation radius is traditionally calculated by equating the magnetic
@@
 With this picture in mind, it is tempting to attribute features of the
-CR light curves to transits of material ejected by planets or
+CPV light curves to transits of material ejected by planets or
 planetesimals.  Young rocky bodies are expected to be hot, and they
@@
 system \citep[e.g.][]{2004jpsm.book..537S} is analogous, in that a small rocky
-body similarly feeds the construction of a plasma torus.  We emphasize
-that while this type of configuration seems a priori plausible, no
+body feeds the construction of a plasma torus.  We emphasize
+that although this type of configuration seems a priori plausible, no
 direct evidence currently supports it.
@@
 to explain the observed phases of the observed dips.  The azimuthal
-angle of the eventual entrainment could be entirely determined by the
+angle of the eventual entrainment could be entirely dictated by the
 stellar magnetic field.  In this scenario, the obscuring material
@@
 and KOI-2700 \citep{2014ApJ...784...40R}, though the obscuring
-material in the CRs would need to be observed much further from the
+material in the CPVs would need to be observed much further from the
 emitting planet than for those two examples.
@@
 be massive enough to remain in orbit, while stochastically ejecting
-material.  For most CRs (Figure~\ref{fig:evoln}), the data seem to be
+material.  For most CPVs (Figure~\ref{fig:evoln}), the data seem to be
 in tension with this expectation because the relative spacing between
@@
 seems to be associated with the presence of infrared excesses.
-Phenomenologically, dippers are different from CRs in that their dips
+Phenomenologically, dippers are different from CPVs in that their dips
 are usually deeper, less periodic, and more variable in depth over
@@
 
-In identifying the two candidate CRs with outlying SEDs
+In identifying the two candidate CPVs with outlying SEDs
 (TICs~193136669 and TIC~57830249; Section~\ref{subsec:irexcess}), we
@@
 ultimately concluded that these sources are dippers.  This episode
-suggests that there could be overlap between CRs and dippers.  Taking
+suggests that there could be overlap between CPVs and dippers.  Taking
 TIC~57830249 as one example, the Sector~36 TESS data are suggestive of
-a CR, with relatively periodic, sharp dips with depths of a few
+a CPV, with relatively periodic, sharp dips with depths of a few
 percent.  The Sector~10 data are completely different, varying in
@@
 all.  Perhaps this source becomes a ``dipper'' when an inflow of dust
-reaches the inner disk wall, and is otherwise a ``CR'' when the inner
+reaches the inner disk wall, and is otherwise a ``CPV'' when the inner
 disk is starved of dust.
 
-Although this outlier is intriguing, stars without infrared excesses
-generally have more stable optical light curves than those with
-infrared excesses.  While some dippers may evolve into CRs after the
-disk is mostly gone, this would be generically expected based on the
-population statistics: young objects become old.  There may be no
+Although TIC~57830249 is an intriguing outlier, the general picture is that
+stars without infrared excesses have more stable optical light curves
+than those with infrared excesses.  While some dippers may evolve into CPVs after the
+disk is mostly gone, this would be generically expected based on population
+statistics: young objects become old.  There may be no
 other causal connection between the two evolutionary stages.  With
-that said, a common mystery between the CRs and dippers is how exactly
-the {\it narrowness} of the dust-induced dimmings is produced.  It is
-not unreasonable to imagine a similar mechanism operating for both
+that said, a common mystery between the CPVs and dippers is how exactly
+the {\it narrowness} of their flux dimmings is produced.  
+A similar mechanism may operate for both
 types of object, tied perhaps to a shared magnetic topology, or
@@
 %The interval of half a cycle period could be significant in the
-%context of CRs for two reasons.  The first is that for material on a
+%context of CPVs for two reasons.  The first is that for material on a
 %circular orbit viewed edge-on, a half-cycle corresponds to the
@@
 %the half-cycle also corresponds to the interval over which half of the
-%star's surface is visible.  Of the CRs in Figures~\ref{fig:cqvs}
+%star's surface is visible.  Of the CPVs in Figures~\ref{fig:cqvs}
 %and~\ref{fig:evoln}, a fraction that seems greater than random might
@@
 %
-%One set of CRs shows ``CR behavior'' (some form of dip complex), but
+%One set of CPVs shows ``CPV behavior'' (some form of dip complex), but
 %which only lasts for half of any given cycle.  TIC~206544316 (Sector
@@
 %
-%An independent set of CRs exhibits small dips roughly half a cycle
+%An independent set of CPVs exhibits small dips roughly half a cycle
 %after large dips; it is tempting to label the small dips secondary
@@
 %In general however, it is challenging to interpret the significance of
-%the potential ``half-period regularities'';  the CRs exhibit such a
+%the potential ``half-period regularities'';  the CPVs exhibit such a
 %wide range of variability that for seemingly any regularity one might
 %posit, it is easy to come up with counter-example objects which do not
-%follow the trend.  In other words, these half-cycle CRs could simply
+%follow the trend.  In other words, these half-cycle CPVs could simply
 %be a product of the human tendency to pattern match.
@@
       high order multipoles.  The bottom row compares the latter
-      systems against the ``best-matching'' CR light curves, selected
-      by eye from Figure~\ref{fig:cqvs}.  CRs have light curves that
+      systems against the ``best-matching'' CPV light curves, selected
+      by eye from Figure~\ref{fig:cqvs}.  CPVs have light curves that
       are visually similar to the topologically complex magnetic B
@@
 estimate the mass of a transiting clump. First, we convert the transit
-depth into an effective cloud radius, $R_{\rm cloud}$.  For most CRs
+depth into an effective cloud radius, $R_{\rm cloud}$.  For most CPVs
 in Figure~\ref{fig:cqvs}, this yields $\approx$2-20\,$R_\oplus$.  A
@@
 1\times10^{-12} M_\oplus\,{\rm yr}^{-1}$.  Considered cumulatively
-over the $\approx$$10^8$ years for which the CR phenomenon is
+over the $\approx$$10^8$ years for which the CPV phenomenon is
 observed, this yields a cumulative moved dust mass of
@@
 \citet{2017AJ....153..152S} previously noted a possible connection
-between the CRs and rapidly rotating magnetic B stars such as
+between the CPVs and rapidly rotating magnetic B stars such as
 $\sigma$~Ori~E, which can have circumstellar gas clouds trapped in
@@
 
-An argument against the connection between CRs and the $\sigma$~Ori~E
+An argument against the connection between CPVs and the $\sigma$~Ori~E
 analogs is that the light curve of $\sigma$~Ori~E is simpler than
@@
 \citep[see][Ch.~4]{1988PhDT........53B}.  Recent TESS light curves
-of these two B stars appear surprisingly similar to the CR light
+of these two B stars appear surprisingly similar to the CPV light
 curves \citep{2020pase.conf...46M}.  The middle row of
 Figure~\ref{fig:bstar} shows the phased TESS light curves for these
-two stars, with by-eye best-matching CRs shown underneath for
+two stars, with by-eye best-matching CPVs shown underneath for
 comparison.  The number of dips per cycle, the shapes of the dips, and
@@
 In this work, we searched 120-second cadence TESS data collected from
-2018 July to 2022 September for complex rotators (CRs).  The target
+2018 July to 2022 September for complex periodic variables (CPVs).  The target
 stars were \nstarssearched\ late-K and early-to-mid M dwarfs within 150\,pc
@@
 quasiperiodic behavior over at least one TESS sector.  These \ngoods\
-bona fide CRs are listed in Table~\ref{tab:thetable}.  This table also
-includes \nmaybes\ ambiguous CRs, whose designation is
+bona fide CPVs are listed in Table~\ref{tab:thetable}.  This table also
+includes \nmaybes\ ambiguous CPVs, whose designation is
 less certain, and \ndebunked\ impostors.  We inferred ages for all but
@@
 over field stars.  Previous work however has shown that $\approx$1-3\%
-of M dwarfs younger than $\approx$100\,Myr show the CR phenomenon
+of M dwarfs younger than $\approx$100\,Myr show the CPV phenomenon
 \citep{2016AJ....152..114R,2022AJ....163..144G,2022AJ....164...80R}.
 
-Analyzing the TESS light curves and stellar properties of our CRs, we
+Analyzing the TESS light curves and stellar properties of our CPVs, we
 draw the following conclusions.
@@
 %
-    \item The sharpest CR dips have durations of $\approx$0.05\,$P$
+    \item The sharpest CPV dips have durations of $\approx$0.05\,$P$
       and depths of $\approx$1-3\% (Figures~\ref{fig:cqvs}
@@
 %
-    \item The shortest CR dips, also with durations of
+    \item The shortest CPV dips, also with durations of
       $\approx$0.05\,$P$, match the expected transit duration for a
@@
 %
-    \item Many CR dips have durations a few times longer than $T_{\rm
+    \item Many CPV dips have durations a few times longer than $T_{\rm
       dur}$ (Figure~\ref{fig:cqvs}).  The dips are often superposed
@@
 %
-    \item The mean periods of CRs remain fixed to within a relative
+    \item The mean periods of CPVs remain fixed to within a relative
       precision $\lesssim$0.1\% over the two-year ($\approx$1{,}000
@@
 %
-    \item The dips in CR light curves can have slightly different
+    \item The dips in CPV light curves can have slightly different
       periods.  LP 12-502, for instance, showed dips with four
@@
 %
-    \item The CR peaks and dips evolve over timescales that are both secular
+    \item The CPV peaks and dips evolve over timescales that are both secular
       ($\approx$100\,cycles) and impulsive ($<$1 cycle).  Dip growth seems
@@
 %
-    \item The on-off duty cycle for CRs seems to be $\approx$$75$\%, based
-      on the fraction of bona fide CRs that either turned on or turned
+    \item The on-off duty cycle for CPVs seems to be $\approx$$75$\%, based
+      on the fraction of bona fide CPVs that either turned on or turned
       off during TESS re-observations, two years after the initial
@@
 %
-    \item The CR phenomenon persists for $\gtrsim$150\,Myr, based on
-      the existence of multiple CRs in AB Dor, the Pleiades, and
+    \item The CPV phenomenon persists for $\gtrsim$150\,Myr, based on
+      the existence of multiple CPVs in AB Dor, the Pleiades, and
       Psc-Eri (Section~\ref{subsec:starprops}).  It may even extend to
-      200\,Myr, based on the one CR we found in the Carina Near
+      200\,Myr, based on the one CPV we found in the Carina Near
       moving group (TIC~294328887; $\approx$200\,Myr).  However the
-      lack of detected CRs in the Hyades and Praesepe suggests that
+      lack of detected CPVs in the Hyades and Praesepe suggests that
       the lifetime of the phenomenon is limited to the first few
@@
 %
-    \item Most CRs are M dwarfs with masses
+    \item Most CPVs are M dwarfs with masses
       0.1-0.5\,$M_\odot$.  Two sources, TIC~405754448 and
@@
       limit.  However both are potentially binaries, and this may
-      confuse our ability to accurate identify the source of the CR
+      confuse our ability to accurate identify the source of the CPV
       signal (Section~\ref{subsec:massive}).  We encourage additional
@@
 %
-    \item The closest CRs to the Sun are at distances of 15-20\,pc,
+    \item The closest CPVs to the Sun are at distances of 15-20\,pc,
       and the brightest have $V$$\approx$12 ($J$$\approx$7.5).  We
-      have found most of them in this work, since our CR sample was
-      $\gtrsim$80\% complete within 30\,pc.  The lack of CRs in the
+      have found most of them in this work, since our CPV sample was
+      $\gtrsim$80\% complete within 30\,pc.  The lack of CPVs in the
       volume-complete $<$15\,pc sample of 0.1-0.3\,$M_\odot$ stars
@@
       frame images would yield a truly volume-limited selection
-      function, and would expand the CR census by about a factor of
+      function, and would expand the CPV census by about a factor of
       two within 50\,pc, and by a factor of ten within 100\,pc.
 %
-    \item Surprising analogs to the CRs exist in two magnetic B stars,
+    \item Surprising analogs to the CPVs exist in two magnetic B stars,
       one of which is known to have an extreme multipolar field
       topology.  Since most magnetic B stars have dipolar magnetic
-      fields \citep{2009ARA&A..47..333D}, this suggests that the CR
+      fields \citep{2009ARA&A..47..333D}, this suggests that the CPV
       dips and warps are similarly being sculpted by the stellar
@@
 The distinction between gas or dust is important because it could
-clarify whether the CR phenomenon is intrinsic, so that material
+clarify whether the CPV phenomenon is intrinsic, so that material
 comes from the star, or extrinsic, so that it is sourced through some
@@
 
-In both the gas and dust scenarios, CRs are preferentially viewed
+In both the gas and dust scenarios, CPVs are preferentially viewed
 edge-on.  This implies that after correcting for the line-of-sight
@@
 rotate rapidly enough;][]{2022AJ....163..144G} could trap circumstellar
-material in the same way.  It also suggests that CRs may
+material in the same way.  It also suggests that CPVs may
 preferentially show transiting planets at larger distances than the
@@
 %\tabletypesize{\scriptsize}
-\tablecaption{Bona fide, candidate, and debunked complex rotators from
+\tablecaption{Bona fide, candidate, and debunked complex periodic
+  variables from
   the TESS 2-minute data. {\bf For internal review, full versions are
@@
 \enddata
-\tablecomments{This table includes \ngoods\ good CRs (\texttt{Quality}
-  flag 1), \nmaybes\ ambiguous CRs (\texttt{Quality} flag 0), and
+\tablecomments{This table includes \ngoods\ good CPVs (\texttt{Quality}
+  flag 1), \nmaybes\ ambiguous CPVs (\texttt{Quality} flag 0), and
   \ndebunked\ impostors (\texttt{Quality} flag -1).  The three-bit
@@
 
-One hypothesis for the CRs, presented by \citet{2019ApJ...876..127Z},
+One hypothesis for the CPVs, presented by \citet{2019ApJ...876..127Z},
 is that the star might be ``{\it orbited by one or more rings composed
@@
 transit behind the ring, it would produce a brightening, not a
-dimming.   Most CRs show dimmings.   The ring scenario would therefore
+dimming.   Most CPVs show dimmings.   The ring scenario would therefore
 imply that large hot spots are common in the photospheres of
@@
 Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river} show
-120-second cadence data for TIC~300651846, a CR in the TESS
+120-second cadence data for TIC~300651846, a CPV in the TESS
 continuous viewing zone.  If it were not for the existence of
@@
 
-TESS was the first instrument to show that CR light curves contain
+TESS was the first instrument to show that CPV light curves contain
 power at timescales of a few minutes
@@
 relative to K2.  A logical follow-up is to ask whether the periodic
-components of the CR light curves contain power at timescales below
-one minute.  Between 2020 and 2021, we observed 10 CRs at 20-second
+components of the CPV light curves contain power at timescales below
+one minute.  Between 2020 and 2021, we observed 10 CPVs at 20-second
 cadence with TESS in order to explore this question (TESS DDT029; PI L.~Bouma).
@@
 264599508, 363963079, 144486786, 408188366, 300651846, 262400835.
-These sources were selected from CRs known at the time to have short
+These sources were selected from CPVs known at the time to have short
 periods and sharp features when observed at 2-minute cadence.
 Comparing the 20-second to 120-second data for these stars (data
-available on MAST), we concluded that these CRs did not contain
+available on MAST), we concluded that these CPVs did not contain
 appreciable power at timescales shorter than a few minutes.
 
-\section{The CRs are not obviously accreting}
+\section{The CPVs are not obviously accreting}
 
 We acquired iodine-free reconnaissance spectra using Keck/HIRES for
-three CRs.  The goals were to determine the chromospheric activity
+three CPVs.  The goals were to determine the chromospheric activity
 levels, and to check for indications of either accretion or
@@
 blue excess in TIC~264599508 could be explained by a second unresolved
-star; the TESS light curve for this source shows both the 7.90\,hr CR
+star; the TESS light curve for this source shows both the 7.90\,hr CPV
 signal, and a 9.00\,hr rotation signal with comparable amplitude.
@@
 	\caption{
-		{\bf Spectral age and activity diagnostics for three CRs}.
+		{\bf Spectral age and activity diagnostics for three CPVs}.
 		Wavelengths are in air;
@@
 % TIC~262400835 ($d$=174\,pc) is formally outside the scope of the
-% current work.  However, this CR was observed using MuSCAT2 on 2020
+% current work.  However, this CPV was observed using MuSCAT2 on 2020
 % December 12, 13, and 16, and the results might be worth including in

### 2023-09-05 paper/ms.tex
update ms

@@
   with sub-solar masses, rotation periods of 0.2--2 days, optical variability amplitudes
-  of a few percent, and sharp recurring light curve features that last for
-  hundreds of cycles.  The sharp features are probably caused by
+  of a few percent, and sharp light curve features that repeat for
+  hundreds of rotation cycles.  The sharp features are probably caused by
   eclipsing clumps of dust or gas orbiting at the corotation radius.
@@
   12-502, stands out for the complexity of its light curve --- with as
-  many as eight flux dips per cycle --- and for the detail with which the
-  evolution in each dip's amplitude and phase can be tracked over
+  many as eight flux dips per cycle --- and for the detail with which 
+  each dip's evolving amplitude and phase can be tracked over
   1{,}500 cycles.  We argue that corotating gas or dust remains the
@@
 physical scenario, we discard the ``starspot-only'' scenario.
-Instead, the correct explanation probably involves material above the
-stellar surface that is spatially confined with sharp boundaries
+Instead, the correct explanation probably involves spatially concentrated
+circumstellar material
 \citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.
@@
 periodically transit the star
-\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The second scenario
+\citep[e.g.][]{2017AJ....153..152S,2017MNRAS.471L.145F,2023MNRAS.518.4734S}.  The second scenario
 invokes ``prominences'', long-lived condensations of cool, dense,
@@
 optically-thick ring obscures a narrow band of the stellar
-photosphere \citep{2019ApJ...876..127Z}.  Hot spots passing behind
-such a ring could produce sudden dips.  We do not favor this scenario
-(see Appendix~\ref{app:ring}).
-
-The dust clump and gas prominence hypotheses are geometrically
+photosphere \citep{2019ApJ...876..127Z}; hot spots passing behind
+such a ring could produce sudden dips.  We disfavor this scenario
+for reasons described in Appendix~\ref{app:ring}.
+
+The dust clump and gas prominence hypotheses are conceptually
 similar; one could imagine dust or gas accumulating in
@@
 starspot profiles.  The theoretical importance of the corotation
-radius has been discussed in studies of magnetic rotators
-\citep[e.g.][]{1973ApJ...184..271L,1985Ap&SS.116..285N,2005ApJ...634.1214L}.
+radius has been noted in previous studies of magnetic rotators
+\citep[e.g.][]{1973ApJ...184..271L,1985Ap&SS.116..285N,1991ApJ...370L..39K,2005ApJ...634.1214L}.
 %
@@
 In regions where the magnetic field dominates the flow (i.e.~$B^2/8\pi
-> \rho v^2 /2$), matter is dragged along with the field lines.  The
-tendency for charged gas or dust to become trapped at corotation is
-then tied to how of the four relevant forces -- gravity, Lorentz,
-inertial Coriolis, and inertial centrifugal -- the Lorentz and
-Coriolis only act perpendicular to field lines, while gravity and the
-centrifugal force are in balance at $R_{\rm c}$ \citep[e.g.][their
+> \rho v^2 /2$), matter is dragged along with the field lines.  
+Within such regions, charged gas or dust can become trapped at corotation because
+of the four relevant forces -- gravity, Lorentz, inertial
+Coriolis, and inertial centrifugal -- the Lorentz and Coriolis only
+act perpendicular to field lines, while gravity and the centrifugal
+force are in balance at $R_{\rm c}$ \citep[e.g.][their
 Section~2]{2005MNRAS.357..251T}.  Another way to phrase this statement
-is that there is a local minimum in the effective potential of the
-corotating frame; given a flow from either the star or from a
-tenuous accretion disk, this local potential minimum enables material
-to build up \citep{2005MNRAS.357..251T}.
-
-Although theoretical heritage for understanding rapid magnetic
+is that, in the corotating frame, the effective potential experienced
+by charged particles tends to have local minima at $R_{\rm c}$; given
+a flow from either the star or from a tenuous accretion disk, this
+local potential minimum enables material to build up
+\citep{2005MNRAS.357..251T}.
+
+While theoretical heritage for understanding magnetic
 rotators exists, CPVs have remained mysterious because they have been both
@@
 does play a central role in explaining their physical behavior, the
-acronym for ``complex rotator'' is already widely used in the astrophysical
+acronym for ``complex rotator'' is already used in the astrophysical
 literature for cosmic rays.  Given these
@@
 (CPVs); our preferred explanation for their behavior is that transient
-clumps of gas or dust orbit at the corotation radius.
+clumps of gas or dust orbit at their corotation radii.
 
@@
 		\subfloat{
-			\includegraphics[width=0.46\textwidth]{f7a.pdf}
-			\includegraphics[width=0.46\textwidth]{f7b.pdf}
+			\includegraphics[width=0.48\textwidth]{f7a.pdf}
+			\includegraphics[width=0.48\textwidth]{f7b.pdf}
 		}
@@
 		\subfloat{
-			\includegraphics[width=0.46\textwidth]{f7d.pdf}
-			\includegraphics[width=0.46\textwidth]{f7c.pdf}
+			\includegraphics[width=0.48\textwidth]{f7d.pdf}
+			\includegraphics[width=0.48\textwidth]{f7c.pdf}
 		}
@@
     chunks denote missing data.
-    The state changes noted in red in Figure~\ref{fig:lplc} occur in
+    The state changes noted with red markers in Figure~\ref{fig:lplc} occur in
     cycles 261, 309, and 1241.

### 2023-09-05 paper/ms.tex
update ms
fix arxiv bibliography references

fix figure numbering

@@
 		\centering
-		\includegraphics[width=0.43\textwidth]{f2completeness.pdf}
+		\includegraphics[width=0.43\textwidth]{f2.pdf}
 		\vspace{-0.2cm}
@@
 		\centering
-		\includegraphics[width=0.96\textwidth]{f2.pdf}
+		\includegraphics[width=0.96\textwidth]{f3.pdf}
 		\vspace{-0.3cm}
@@
 		\centering
-		\includegraphics[width=0.98\textwidth]{f3.pdf}
+		\includegraphics[width=0.98\textwidth]{f4.pdf}
     \vspace{-0.3cm}
@@
 		\centering
-		\includegraphics[width=0.95\textwidth]{f8.pdf}
+		\includegraphics[width=0.95\textwidth]{f5.pdf}
 		\vspace{-0.1cm}
@@
 		\centering
-		\includegraphics[width=\textwidth]{f4.pdf}
+		\includegraphics[width=\textwidth]{f6.pdf}
 		\vspace{-0.6cm}
@@
 		\centering
-		\includegraphics[width=0.98\textwidth]{f5.pdf}
+		\includegraphics[width=0.98\textwidth]{f7.pdf}
 		\vspace{-0.3cm}
@@
 		\centering
-		\includegraphics[width=0.98\textwidth]{f6.pdf}
+		\includegraphics[width=0.98\textwidth]{f8.pdf}
 		\vspace{-0.3cm}
@@
 		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f7a.pdf}
-			\includegraphics[width=0.48\textwidth]{f7b.pdf}
+			\includegraphics[width=0.48\textwidth]{f9a.pdf}
+			\includegraphics[width=0.48\textwidth]{f9b.pdf}
 		}
@@
 		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f7d.pdf}
-			\includegraphics[width=0.48\textwidth]{f7c.pdf}
+			\includegraphics[width=0.48\textwidth]{f9d.pdf}
+			\includegraphics[width=0.48\textwidth]{f9c.pdf}
 		}
@@
 		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f9a.pdf}
+			\includegraphics[width=0.48\textwidth]{f10a.pdf}
 		}
@@
 		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f9b.pdf}
+			\includegraphics[width=0.48\textwidth]{f10b.pdf}
 		}
@@
 		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f9c.pdf}
+			\includegraphics[width=0.48\textwidth]{f10c.pdf}
 		}
@@
 LGB is grateful for support from the Heising-Simons 51~Pegasi~b
-Fellowship.  This paper benefited from conversations between the
-authors and G.~Laughlin, A.~Mann, J.~Spake, and B.~Draine.  The paper
-also relied on data collected by the TESS mission, which are available
-from the Mikulski Archive for Space Telescopes (MAST).  The specific
+Fellowship, and for helpful conversations with
+J.~Spake, A.~Mann, G.~Laughlin, and B.~Draine.  
+We are also grateful for the assistance of S.~Yee,
+L.~Weiss, H.~Isaacson, and A.~Howard in acquiring and reducing the
+HIRES spectra.
+This paper relied primarily on data collected by the TESS mission; the specific
 120-second cadence observations can be accessed via
@@
 Funding for the TESS mission is provided by NASA’s Science Mission
-Directorate.  TIC 402980664 in particular was observed at 120-second
+Directorate.  
+We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham, S.~Seager, and J.~Jenkins) and the many TESS team members for their efforts to make the mission a continued success. 
+TIC 402980664 in particular was observed at 120-second
 cadence thanks to the TESS Guest Investigator programs G022252 (PI:
 J.~Schlieder; Sectors 18, 19, 25, 26) and G04168 (PI: R.~Jayaraman;
-Sector 53).  LGB is also grateful for the assistance of S.~Yee,
-L.~Weiss, H.~Isaacson, and A.~Howard in acquiring and analyzing the
-HIRES spectra.
+Sector 53).
 
@@
   %\texttt{webplotdigitzer} \citep{rohatgi_2019},
-  \texttt{wotan} \citep{hippke_wotan_2019}.
+  \texttt{wotan} \citep{2019AJ....158..143H}.
 }
@@
  	{\it Astrometry}:
-		Gaia \citep{2018A&A...616A...1G,2022arXiv220800211G}.
+		Gaia \citep{2018A&A...616A...1G,2023A&A...674A...1G}.
  	{\it Imaging}:
@@
     APASS \citep{2016yCat.2336....0H},
-		Gaia \citep{2018A&A...616A...1G,2022arXiv220800211G},
+		Gaia \citep{2018A&A...616A...1G,2023A&A...674A...1G},
     SDSS \citep{2000AJ....120.1579Y},
@@
 
-%\clearpage
-
+\clearpage
+
+\def\bibfont{\footnotesize}
 \bibliographystyle{yahapj}                           
-\bibliography{bibliography}
+\renewcommand*{\bibfont}{\footnotesize} 
+{\footnotesize \bibliography{bibliography} }
 

### 2023-09-05 paper/collect.sh

@@ -2,47 +2,51 @@ resultsdir="/Users/luke/Dropbox/proj/cpv/results"
 artdir="/Users/luke/Dropbox/proj/cpv/art"
 addir="/Users/luke/Dropbox/Documents/proposals/2023_05_ADAP/latex/figs/"
 
-# fig1
+# 3-panel mosaic and cartoons
 cp $resultsdir/lc_mosaic/lc_mosaic_fav3.pdf f1a.pdf
 cp $artdir/twomodels.pdf f1b.pdf
 
-# fig2 is annotated_lp12502.key exported
+# completeness
+cp $resultsdir/fraction_coverage/fraction_coverage.pdf f2.pdf
 
-# fig2 completeness
-cp $resultsdir/fraction_coverage/fraction_coverage.pdf f2completeness.pdf
+# fig3 is annotated_lp12502.key exported
 
-# fig3
-cp $resultsdir/full_lcmosaic/full_lcmosaic_showtitles_binarytitle_Ngoodsectors_tic8_Tmag.pdf f3.pdf
+# full LC mosaic (50 panel)
+cp $resultsdir/full_lcmosaic/full_lcmosaic_showtitles_binarytitle_Ngoodsectors_tic8_Tmag.pdf f4.pdf
 
-# fig4
-cp $resultsdir/beforeafter_mosaic/beforeafter_mosaic_showtitles_tic8_Tmag.pdf f4.pdf
+# catalog properties
+cp $resultsdir/catalogscatter/catalogscatter_showmaybe_emphruwe.pdf f5.pdf
 
-# fig5
-cp $resultsdir/tic4029_segments/tic4029_segments.pdf f5.pdf
+# LC evolution
+cp $resultsdir/beforeafter_mosaic/beforeafter_mosaic_showtitles_tic8_Tmag.pdf f6.pdf
 
-# fig6
-cp $resultsdir/phase_timegroups_mosaic/TIC_402980664/TIC_402980664_P18.5611_2min_phase_timegroups_mosaic_ymin-4.8_ymax3.pdf f6.pdf
+# TIC4029 segments
+cp $resultsdir/tic4029_segments/tic4029_segments.pdf f7.pdf
 
-# fig7
-cp $resultsdir/river/TIC_402980664/TIC402980664_river_gist_stern_truncated_-1_64_manual_20230617_mask_v0_nterms2_vmin-4.00000_vmax1.00000.pdf f7a.pdf
[…]

### 2023-09-06 paper/ms.tex
update ms

@@
   correspondences between the light curves of CPVs and of B stars
-  that may have multipolar magnetic fields.
+  known to have multipolar magnetic fields.
 \end{abstract}
@@
 
+\begin{figure*}[!t]
+	\begin{center}
+		\subfloat{
+			\includegraphics[width=0.48\textwidth]{f11a.pdf}
+			\includegraphics[width=0.48\textwidth]{f11b.pdf}
+		}
+	\end{center}
+	\vspace{-0.4cm}
+	\caption{
+		{\bf Light curve evolution of TIC 300651846}.
+		All available 120-second cadence data as of 2023 Aug 11 are shown.
+		Cycles 0 to 622 span TESS Sectors 32-39 (Nov 2020--June 2021);
+		cycles 2296-2676 span Sectors 61-65 (Jan--June 2023).  We assumed
+		a 8.254\,hr period and a fixed reference epoch (BTJD 2174.127) for
+		both panels.  Light curve segments are split based on the presence
+		of gaps longer than three hours.  Cycle numbers are listed in the
+		lower-right of each light curve segment.
+	}
+	\label{fig:tic3006timegroups}
+\end{figure*}
+
+\begin{figure*}[!t]
+	\begin{center}
+		\subfloat{
+			\includegraphics[width=0.48\textwidth]{f12a.pdf}
+			\includegraphics[width=0.48\textwidth]{f12b.pdf}
+		}
+	\end{center}
+	\vspace{-0.4cm}
+	\caption{
+		{\bf River plots of TIC 300651846}.
+		This is an alternative visualization of the data in
+		Figure~\ref{fig:tic3006timegroups}.  All available 120-second
+		cadence data as of 2023 Aug 11 are shown.  Cycles 0 to 622 span
+		TESS Sectors 32-39 (Nov 2020--June 2021); cycles 2296-2676 span
+		Sectors 61-65 (Jan--June 2023).  We assumed $P$$=$8.254\,hr and
+		$t_0$=2174.127 [BTJD].  Note that the two panels have slightly
+		different color scales.
+	}
+	\label{fig:tic3006river}
+\end{figure*}
+
 \section{TIC~300651846}
@@
 
-\begin{figure*}[!t]
+\section{Literature comparison}
+\label{sec:litcomp}
+
+We compared our CPV search results against previous work by
+compiling a list of CPVs from both K2
+\citep{2017AJ....153..152S,2018AJ....155...63S} and TESS
+\citep{2019ApJ...876..127Z,2020AJ....160...86B,2021AJ....161...60S,2022AJ....163..144G,2023ApJ...945..114P}.
+We counted PTFO 8-8695 as a TESS-detected CPV \citep[but see][and
+references therein]{2020AJ....160...86B}.  This effort resulted in a
+list of 74 unique objects that had been reported to be CPVs.  We made
+no attempt to reclassify these sources based on our subjective grading
+scheme.  TESS contributed 41 of the 74 objects; the remaining 33 were
+from K2.
+
+{\it How many known CPVs did we miss?}---A minority of the literature
+CPVs, 19/74, were stars with 120-second TESS data acquired between
+Sectors 1-55 that also met conditions~\ref{eq:one}--\ref{eq:four}.
+Our blind search (Table~\ref{tab:thetable}) recovered all but two of
+these 19 sources: TIC~65347864 in Tuc-Hor \citep{2023ApJ...945..114P},
+and TIC~243499565 in Sco-Cen \citep{2021AJ....161...60S}.  During our
+blind vetting, we manually labelled both sources as eclipsing
+binaries.  Reconsidering with the knowledge of previous literature, we
+believe that TIC~65347864 remains ambiguous: this source shows one
+persistent broad local minimum superposed over sinusoidal spot
+modulation; it could be an eclipsing binary, an RS CVn, or a CPV.
+
+TIC~243499565 however is a bona fide CPV; our blind labeling for this
+source was incorrect.  \citet{2021AJ....161...60S} made the
+classification based on Sector~11 full-frame image data.  During
+Sector~38, the dip phases were different, and the source
+resembled an eccentric eclipsing binary (similar to TIC~193831684).  Sector~64 recently showed
+the development of additional local minima in the light curve so that
+it shows three dips per cycle; its CPV classification is secure.  Our
+search therefore missed one star that had previously been classified
+as a CPV.
+
+{\it How many of our CPVs are new?}---Considering only our ``good''
+CPVs, 35 of these 50 sources have not yet been reported in the
+literature.  Considering only the 13 ``ambiguous'' CPVs, 11 are new to
+the literature.  Two sources, TIC~67897871 (EPIC~202724025; RIK-90;
+\citealt{2017AJ....153..152S}) and TIC~118769116 (EPIC~247343526;
+\citealt{2017AJ....153..152S}), were previously only known to be CPVs
+due to K2 observations.  Both periods appear to have remained
+identical, within measurement precision.  The shapes have of course changed.
+These two objects, combined with PTFO 8-8695, provide evidence
+that CPV variability persists for at least decade timescales.
+
+\begin{figure}[!t]
 	\begin{center}
-		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f11a.pdf}
-			\includegraphics[width=0.48\textwidth]{f11b.pdf}
-		}
+		\centering
+		\includegraphics[width=0.55\textwidth]{f13.pdf}
+		\vspace{-0.2cm}
+		\caption{
+			{\bf Brightnesses and distances of our CPVs compared
+      against previous work.}  
+      ``K2 literature'' corresponds to \citet{2017AJ....153..152S} and
+      \citet{2018AJ....155...63S}.  ``TESS literature'' corresponds to
+      \citet{2019ApJ...876..127Z,2021AJ....161...60S,2022AJ....163..144G}, and \citet{2023ApJ...945..114P}.
+      ``CQVs'' and ``candidates'' are as in
+      Figure~\ref{fig:catalogscatter}, though for visual clarity
+      unresolved binaries are not highlighted.  PTFO 8-8695, a CPV at
+      a distance of $\approx$350\,pc, is not shown.
+		}
+			\vspace{-0.5cm}
+		\label{fig:tmagvsdist}
 	\end{center}
-	\vspace{-0.4cm}
-	\caption{
-		{\bf Light curve evolution of TIC 300651846}.
-    All available 120-second cadence data as of 2023 Aug 11 are shown.
-    Cycles 0 to 622 span TESS Sectors 32-39 (Nov 2020--June 2021);
-    cycles 2296-2676 span Sectors 61-65 (Jan--June 2023).  We assumed
-    a 8.254\,hr period and a fixed reference epoch (BTJD 2174.127) for
-    both panels.  Light curve segments are split based on the presence
-    of gaps longer than three hours.  Cycle numbers are listed in the
-    lower-right of each light curve segment.
-	}
-	\label{fig:tic3006timegroups}
-\end{figure*}
-
-\begin{figure*}[!t]
-	\begin{center}
-		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f12a.pdf}
-			\includegraphics[width=0.48\textwidth]{f12b.pdf}
-		}
-	\end{center}
-	\vspace{-0.4cm}
-	\caption{
-		{\bf River plots of TIC 300651846}.
-    This is an alternative visualization of the data in
-    Figure~\ref{fig:tic3006timegroups}.  All available 120-second
-    cadence data as of 2023 Aug 11 are shown.  Cycles 0 to 622 span
-    TESS Sectors 32-39 (Nov 2020--June 2021); cycles 2296-2676 span
-    Sectors 61-65 (Jan--June 2023).  We assumed $P$$=$8.254\,hr and
-    $t_0$=2174.127 [BTJD].  Note that the two panels have slightly
-    different color scales.
-	}
-	\label{fig:tic3006river}
-\end{figure*}
+\end{figure}
+
+{\it How do the brightness and distance distributions
+compare?}---Figure~\ref{fig:tmagvsdist} compares the TESS magnitudes
+and distances for the CPVs in Table~\ref{tab:thetable} against the
+previously known literature CPVs.  At the extremes, our new sources
+include the closest and brightest CPVs currently known. 
+All K2 CPVs are in Sco-Cen,
+$\approx$100-180\,pc from the Sun.  The large gap in the TESS literature CPV
+distance distribution was because the studies by
+\citep{2019ApJ...876..127Z} and \citet{2023ApJ...945..114P} both
+favored Tuc-Hor; many of our new CQVs are within this 40-100\,pc gap.
 
 \section{No significant power at 20~second cadence}
+\label{sec:twentysec}
 
@@
 \section{The CPVs are not obviously accreting}
+\label{sec:accretion}
 
@@
 	\subfloat{
-			\includegraphics[width=0.7\textwidth]{f13a.pdf}
+			\includegraphics[width=0.7\textwidth]{f14a.pdf}
     }
@@
 	\subfloat{
-			\includegraphics[width=0.7\textwidth]{f13b.pdf}
+			\includegraphics[width=0.7\textwidth]{f14b.pdf}
     }
@@
 	\subfloat{
-			\includegraphics[width=0.7\textwidth]{f13c.pdf}
+			\includegraphics[width=0.7\textwidth]{f14c.pdf}
     }

### 2023-09-06 drivers/plot_literature_Tmag_vs_dist.py

@@ -1,0 +1,224 @@
+import numpy as np, pandas as pd, matplotlib.pyplot as plt
+from os.path import join
+import os
+from complexrotators.paths import LOCALDIR, DATADIR, TABLEDIR
+from aesthetic.plot import set_style, savefig
+from numpy import array as nparr
+
+def get_detection_df():
+    # good, maybe, and omit impostors
+    csvpath = join(
+        TABLEDIR,
+        '2023_catalog_table',
+        '20230613_LGB_RJ_CPV_TABLE_supplemental_selfnapplied.csv'
+    )
+    df = pd.read_csv(csvpath, sep="|")
+
+    df = df[(df.quality == 0) | (df.quality == 1)]
+
+    # all dr2...
+    Tmag_pred = (
+            df['phot_g_mean_mag']
+            - 0.00522555 * (df['phot_bp_mean_mag'] - df['phot_rp_mean_mag'])**3
+            + 0.0891337 * (df['phot_bp_mean_mag'] - df['phot_rp_mean_mag'])**2
+            - 0.633923 * (df['phot_bp_mean_mag'] - df['phot_rp_mean_mag'])
+            + 0.0324473
+    )
+    df['TESSMAG_pred'] = Tmag_pred
+
+    return df
+
+
+def get_literature_cpv_df():
+
+    indir = join(DATADIR, 'interim')
+    inpath = join(indir, "Stauffer2017_k2_class1class2_supplemented.csv")
+    s17_df = pd.read_csv(inpath)
+    s17_df['telescope'] = 'K2'
+    s17_df['provenance'] = 'Stauffer2017'
+
+    inpath = join(indir, "Stauffer2018_k2_class1_supplemented.csv")
+    s18_df = pd.read_csv(inpath)
+    s18_df['telescope'] = 'K2'
+    s18_df['provenance'] = 'Stauffer2018'
+
+    inpath = join(indir, "Stauffer2021_tess_class1class2_supplemented.csv")
+    s21_df = pd.read_csv(inpath)
+    s21_df['telescope'] = 'TESS'
+    s21_df['provenance'] = 'Stauffer2021'
+
+    inpath = join(indir, "Gunther_2022_tess_supplemented.csv")
+    g22_df = pd.read_csv(inpath)
+    g22_df['telescope'] = 'TESS'
+    g22_df['provenance'] = 'Zhan2019/Gunther2022'
+
+    # latter source is not a CPV...
+    p23_df = pd.DataFrame({
[…]

### 2023-09-06 paper/collect.sh

@@ -46,7 +46,10 @@ cp $resultsdir/phase_timegroups/TIC_300651846/cycle2290_to_2680TIC_300651846_P8.
 cp $resultsdir/river/tic_300651846/TIC300651846_river_seismic_-1_630_vmin-6.00000_vmax6.00000.pdf f12a.pdf
 cp $resultsdir/river/tic_300651846/TIC300651846_river_seismic_2290_2680_vmin-8.00000_vmax8.00000.pdf f12b.pdf
 
-# TIC3006 phase timegroup
-cp $resultsdir/spectrum_windows/*402980664*pdf f13a.pdf
-cp $resultsdir/spectrum_windows/*146539195*pdf f13b.pdf
-cp $resultsdir/spectrum_windows/*264599508*pdf f13c.pdf
+# brightness/dist comp
+cp $resultsdir/literaturecomp/gmag_vs_distance_CPVs_showlit.pdf f13.pdf
+
+# specturm windows
+cp $resultsdir/spectrum_windows/*402980664*pdf f14a.pdf
+cp $resultsdir/spectrum_windows/*146539195*pdf f14b.pdf
+cp $resultsdir/spectrum_windows/*264599508*pdf f14c.pdf

### 2023-09-06 paper/ms.tex
Rewrote abstract
Co-authored-by: Lynne Hillenbrand <lah@astro.caltech.edu>

@@
 
+\author{Lynne~A.~Hillenbrand}
+\affiliation{\caltech}
+
+\author[0000-0002-4265-047X]{Joshua N. Winn}
+\affiliation{\princeton}
+
 \author[0000-0003-4062-0776]{Alexandre David-Uraz}
@@
 
-\author{Lynne~A.~Hillenbrand}
-\affiliation{\caltech}
-
-\author[0000-0002-4265-047X]{Joshua N. Winn}
-\affiliation{\princeton}
-
 \author[0000-0001-7204-6727]{G\'asp\'ar \'A. Bakos}
@@
 \begin{abstract}
-  We explore a set of pre-main-sequence stars
-  with sub-solar masses, rotation periods of 0.2--2 days, optical variability amplitudes
-  of a few percent, and sharp light curve features that repeat for
-  hundreds of rotation cycles.  The sharp features are probably caused by
-  eclipsing clumps of dust or gas orbiting at the corotation radius.
-  We refer to this class of star as ``complex periodic variables'' (CPVs).
-  To improve our understanding of these
-  enigmatic objects, we conducted a survey for CPVs using TESS
-  short-cadence data collected between 2018~July and 2022~September.
-  Our search of \nstarssearched\ K and M dwarfs with $T$$<$16 and
-  $d$$<$150\,pc yielded \ngoods\ high-quality CPVs, most of which are
-  new discoveries.  Our sample includes the brightest
-  ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and oldest
-  ($\approx$200\,Myr) known CPVs.  One of the new discoveries, LP
-  12-502, stands out for the complexity of its light curve --- with as
-  many as eight flux dips per cycle --- and for the detail with which 
-  each dip's evolving amplitude and phase can be tracked over
-  1{,}500 cycles.  We argue that corotating gas or dust remains the
-  most viable explanation for CPVs. The gas or dust is probably
-  entrained by the star's magnetic field, and the sharp features could
-  result from a multipolar field topology, a hypothesis supported by
-  correspondences between the light curves of CPVs and of B stars
-  known to have multipolar magnetic fields.
+  %
+  Complex periodic variables (CPVs) are stars that exhibit sharp and
+  periodic optical light curves.  Previous work has shown that such
+  stars tend to be disk-free pre-main-sequence M dwarfs with rotation
+  periods of 0.2--2 days.  To advance understanding of these enigmatic
+  objects, we performed a blind CPV search using TESS 2-minute data of
+  \nstarssearched\ K and M dwarfs with $T$$<$16 and $d$$<$150\,pc.  We
+  found \ngoods\ high-quality CPVs.  The new objects include the
+  brightest ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and
+  oldest ($\approx$200\,Myr) CPVs known.  All objects but one turned
+  out to be likely members of stellar associations, which enabled
+  age-dating.  One exceptional new object, LP 12-502, showed up to
+  eight dips per cycle; the dips at times coexisted with slightly
+  different periods, and the variability of the dips suggests that
+  they are additive and independent.  Broadly, our search confirms
+  that CPVs are mostly young ($\lesssim$150\,Myr) and low-mass
+  ($\lesssim$0.4\,$M_\odot$).  The flux dips that embody the class
+  have lifetimes of $\approx$100 cycles, and the dips collapse in
+  response to stellar flares once every few months.  Corotating gas or
+  dust clumps remain the only viable explanation.  The gas or dust is
+  probably entrained by the star's magnetic field, and the sharp
+  features could result from a multipolar field topology, a hypothesis
+  supported by correspondences between the light curves of CPVs and of
+  B stars known to have multipolar magnetic fields.
+  %
 \end{abstract}
@@
 $\approx$1\% of M dwarfs \citep{2018AJ....155..196R}.  Out of the
-millions of stars monitored by K2 and TESS, about 50 CPVs have been
+millions of stars monitored by K2 and TESS, about 70 CPVs have been
 reported to date
@@
 {\sc State-changes reveal dip independence}---The state-changes seen
-in cycles 1233-1247 and 299-315 confirm that dips can disappear in
+in cycles 261, 309, and 1241 confirm that dips can disappear in
 less than one cycle. While such behavior was also noted by
@@
 for one dip can vary independently of the materials or processes
-responsible for other dips.  The state changes during cycles 248-264
-and 299-315 support the same conclusion, while also hinting that the
+responsible for other dips.  The state changes during cycles 261
+and 309 support the same conclusion, while also hinting that the
 {\it leading} dip of a complex is most prone to disappearing, leaving
@@
 LAH contributed to project design and to the interpretation of the light curves.
-JNW and SR significantly improved the clarity of the manuscript.
+JNW, SR, and LAH significantly improved the clarity of the manuscript.
 G\'AB acquired and maintained the servers used to run the dip-finding pipeline.
@@
 These two objects, combined with PTFO 8-8695, provide evidence
-that CPV variability persists for at least decade timescales.
+that CPV variability persists over timescales of at least decades.
 

### 2023-09-06 paper/ms.tex
[WIP] update ms for clarity (LAH suggestions)
Co-authored-by: Lynne Hillenbrand <lah@astro.caltech.edu>

@@
   Complex periodic variables (CPVs) are stars that exhibit sharp and
-  periodic optical light curves.  Previous work has shown that such
-  stars tend to be disk-free pre-main-sequence M dwarfs with rotation
+  periodic optical light curves.  Previous work has indicated that such stars
+  tend to be disk-free pre-main-sequence M dwarfs with rotation
   periods of 0.2--2 days.  To advance understanding of these enigmatic
-  objects, we performed a blind CPV search using TESS 2-minute data of
+  objects, we performed a blind search using TESS 2-minute data of
   \nstarssearched\ K and M dwarfs with $T$$<$16 and $d$$<$150\,pc.  We
@@
   out to be likely members of stellar associations, which enabled
-  age-dating.  One exceptional new object, LP 12-502, showed up to
-  eight dips per cycle; the dips at times coexisted with slightly
-  different periods, and the variability of the dips suggests that
-  they are additive and independent.  Broadly, our search confirms
+  age-dating.  An exceptional new object, LP 12-502, showed up to
+  eight flux dips per cycle; some of the LP 12-502 dips coexisted with slightly
+  different periods, and the shortest-duration LP 12-502 dips matched the expected
+  timescale for transiting small bodies at the corotation radius.
+  Broadly, our search confirms
   that CPVs are mostly young ($\lesssim$150\,Myr) and low-mass
@@
   have lifetimes of $\approx$100 cycles, and the dips collapse in
-  response to stellar flares once every few months.  Corotating gas or
-  dust clumps remain the only viable explanation.  The gas or dust is
-  probably entrained by the star's magnetic field, and the sharp
-  features could result from a multipolar field topology, a hypothesis
-  supported by correspondences between the light curves of CPVs and of
-  B stars known to have multipolar magnetic fields.
+  response to stellar flares once every few months.  Corotating
+  concentrations of gas or dust remains the only plausible explanation
+  known.  The gas or dust is probably entrained by the star's magnetic
+  field, and the sharp features could result from a multipolar field
+  topology, a hypothesis supported by correspondences between the
+  light curves of CPVs and of B stars known to have multipolar
+  magnetic fields.
   %
@@
 		bottom right corner.  Left-to-right, the objects are LP 12-502
-		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
-		425933644 (Sector~28).
+    (TIC~402980664; Sector~19), TIC~94088626 (Sector 10), and
+    TIC~425933644 (Sector~28).
 		{\it Bottom:} Cartoon explanations for the phenomenon.  The dust
@@
 objects will be the most amenable to detailed photometric and
-spectroscopic analyses.  To do this, we use 120-second cadence data
+spectroscopic analyses.  To do this, we use 2-minute cadence data
 acquired by TESS between 2018 July and 2022 September (Sectors 1-55;
@@
 by TESS between 2018 July 25 and 2022 September 1 (Sectors 1-55).
-Specifically, we used the 120-second cadence light curves produced by
+Specifically, we used the 2-minute cadence light curves produced by
 the Science Processing and Operations Center at the NASA Ames Research
 Center \citep{2016SPIE.9913E..3EJ}.  While the TESS data products from
-these sectors also included full frame images with cadences of 600 and
-1800 seconds for a larger number of sources, we restricted our
-attention to the 120-second data for the sake of uniformity and
+these sectors also included full frame images with cadences of 10 and
+30 minutes for a larger number of sources, we restricted our
+attention to the 2-minute data for the sake of uniformity and
 simplicity in data handling.  In exchange, we sacrificed both
@@
 cumulatively observed $\approx$90\% of the sky for at least one lunar
-month between 2018 July and 2022 September, the 120-second cadence
+month between 2018 July and 2022 September, the 2-minute cadence
 data were collected for only a subset of observable stars that were
 preferentially nearby and bright \citep[see][]{2021PASP..133i5002F}.
-The total 120-second data volume
+The total 2-minute data volume
 from Sectors 1-55 included 1{,}087{,}475 short-cadence light curves, which were
@@
 To simplify our search, we defined our target sample as
-stars with 120-second cadence TESS light curves satisfying the
+stars with 2-minute cadence TESS light curves satisfying the
 following four conditions:
@@
       radial shells, each with a width of 10\,pc.  To be part of our selection function,
-      these stars must meet the listed conditions: they must be red dwarf
+      these stars must meet the following conditions: they must be red dwarf
       stars
@@
 \citep{2016AJ....152..114R,2017AJ....153..152S,2023ApJ...945..114P},
-or by flagging light curves with short periods and a large number of
+or by flagging light curves with short periods and 
 strong Fourier harmonics for visual inspection
@@
 phase-folded light curves, while also using the Fourier approach.  We
-applied these two search techniques independently.
+applied these two search techniques independently to our
+\nstarssearched\ targets.
 
@@
 For our dip-counting pipeline, we began with the {\tt PDC\_SAP} light
-curves for each sector, removed non-zero quality flags, and normalized
+curves for each sector \citep{2017ksci.rept....8S}, removed non-zero quality flags, and normalized
 the light curve by dividing out its median value.  We then flattened
@@
 below two days and the presence of at least three sharp local minima,
-based on at least one sector of the TESS 120-second data. Candidates
+based on at least one sector of the TESS 2-minute data. Candidates
 were then inspected visually as described in
@@
 light curves, we normalized each light curve, and then re-binned it
-into equal width 120-second bins to account for the uneven spacing in
+into equal width 2-minute bins to account for the uneven spacing in
 the TESS data, as well as the data gap caused by satellite downlink
@@
 
-If a peak of such significance was found, we generated a ``summary
-sheet'' with information about the star, its full and folded light
-curves, Fourier transform, potential contaminating stars, and
-information about these contaminating stars.  Summary sheets were
-generated for $\approx$10\% of the 20{,}000 120-second targets in each
-sector.  We reviewed each summary sheet and tried to classify each
-light curve based on visual inspection of its morphology (with
-categories including eclipsing binary, CPV, RS CVn, and cataclysmic
-variable). Whenever a CPV was identified, the light curves from
-multiple sectors were stitched together and analyzed jointly, for a
-more accurate period determination.
+Peaks of significance were found for $\approx$10\% of the searched
+stars.  For all such cases, we generated an interim ``summary sheet''
+with information about the star, its full and folded light curves,
+Fourier transform, potential contaminating stars, and information
+about these contaminating stars.  We then reviewed each summary sheet,
+and tentatively classified each light curve based on visual inspection
+of its morphology (with common categories including eclipsing binary,
+CPV, RS CVn, and cataclysmic variable).
+%Whenever a CPV was identified, the light curves from
+%multiple sectors were stitched together and analyzed jointly, for a
+%more accurate period determination.
 
@@
       if $\Delta T$$<$2.5.
-      {\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities,
+      {\it m)}: BANYAN\,$\Sigma$ v1.2 association probabilities,
       calculated using positions, proper motions, and the parallax.
@@
 
-We assessed whether the objects found using the dip-counting
-(Section~\ref{subsec:counting}) and Fourier
-(Section~\ref{subsec:fourier}) techniques were consistent with
+We homogeneously assessed whether the objects identified using the
+dip-counting (Section~\ref{subsec:counting}) and Fourier
+(Section~\ref{subsec:fourier}) approaches were consistent with
 expectations for CPVs by assembling the data shown in
@@
 techniques were eclipsing binaries, ordinary spotted rapid rotators,
-and complex light curves due to multiple stars contributing to the
-photometric aperture.  Our dip-counting pipeline flagged
+and light curves that were complex due to multiple stars contributing to the
+photometric aperture.  Our specialized dip-counting pipeline flagged
 \nuniqdipflagged\ unique stars for visual inspection; about 20\% were
-subsequently labeled either good or possible CPVs.  From the Fourier
-pipeline, $\approx$0.5\% of stars that passed the 12-$\sigma$ peak
-threshold were eventually classified as CPVs.  This is because the
-Fourier pipeline was implemented as a general variability search; its
-results are also being used for analyses on topics other than CPVs.
+subsequently labeled either good or possible CPVs.  From the more
+general Fourier pipeline, $\approx$0.5\% of stars that passed the
+12-$\sigma$ peak threshold were eventually classified as CPVs.
 
@@
 
-\paragraph{Ages}
-We estimated the stellar ages by making probabilistic spatial and
-kinematic associations between the CPVs and known clusters in the solar
-neighborhood.  For most stars in our sample, we did this using
+\subsubsection{Ages}
+While most of our target stars were field stars, color--absolute
+magnitude diagrams suggested that most CPVs tended to be on the
+pre-main-sequence (e.g.\ panel {\it (k) of Figure~\ref{fig:vet}}).  We
+therefore estimated stellar ages by checking for probabilistic spatial
+and kinematic associations between the CPVs and known clusters in the
+solar neighborhood.  For most stars in our sample, we did this using
 BANYAN\,$\Sigma$
@@
 git commit \texttt{394b486}} This algorithm calculates the probability
-that a given star belongs to one of 27 young clusters (or
-``associations'') within 150\,pc of the Sun, by modeling the clusters
-as multivariate Gaussian distributions in 3-D position and 3-D
-velocity space.  We used the Gaia DR2 sky positions, proper motions,
-and distances to calculate the membership probabilities.
-BANYAN\,$\Sigma$ in turn analytically marginalizes over the radial
-velocity dimension.  The probabilities returned by this procedure are
-qualitatively useful, but should be interpreted with caution because
-the assumption of Gaussian distributions is questionable for most
-groups within the solar neighborhood \citep[see
-e.g.][Figure~10]{2021ApJ...917...23K}.
+that a given star belongs to either the field, or to any of 27 young
+clusters (``associations'') within 150\,pc of the Sun.  This is
+achieved by modeling the field and cluster populations as multivariate
+Gaussian distributions in 3-D position and 3-D velocity space.  We
+used the Gaia DR2 sky positions, proper motions, and distances to
+calculate the membership probabilities.  BANYAN\,$\Sigma$ in turn
+analytically marginalizes over the radial velocity dimension.  The
+probabilities returned by this procedure are qualitatively helpful, but
+should be interpreted with caution because the assumption of Gaussian
+distributions is questionable for most groups within the solar
+neighborhood \citep[see e.g.][Figure~10]{2021ApJ...917...23K}.
 
@@
 commit \texttt{278b372}}
-
-\paragraph{Effective temperatures, radii, and masses}
-
-We determined the stellar effective temperature and radii by fitting
-the broadband spectral energy distributions (SEDs); we then estimated
-the masses by interpolating against the sizes, temperatures, and ages
-of the PARSEC v1.2S models
+Finally, to provide a base for comparison, we also ran the
+BANYAN\,$\Sigma$ membership analysis on our entire \nstarssearched\
+target star sample.
+
+\subsubsection{Effective temperatures, radii, and masses}
+
+We determined the stellar effective temperature and radii for the CPVs
+by fitting the broadband spectral energy distributions (SEDs); we then
+estimated the masses by interpolating against the sizes, temperatures,
+and ages of the PARSEC v1.2S models
 \citep{2012MNRAS.427..127B,2014MNRAS.444.2525C}.
@@
 
+\subsubsection{Binarity}
+
+The main types of binaries of interest in this work are those that
+are unresolved, because they can lead to misinterpretations of the data.
+For instance, unresolved binaries might produce multiple photometric
+signals and hinder our ability to correctly identify the star hosting
+the CPV signal.  Unresolved binaries could also bias photometric magnitude
+and color measurements, which would affect our stellar parameter
+estimates.  To attempt to identify binaries, we considered the
+following lines of information.
+
+{\it Radial velocity scatter}---We examined diagrams of the Gaia DR3
+``radial velocity error'' as a function of stellar color for all
+\ncqvsnodebunked\ CPVs and candidate CPVs.  Since this quantity
+represents the standard deviation of the non-published Gaia RV time
+series, outliers can suggest single-lined spectroscopic binarity.
+These plots showed two clusters of stars, at $\lesssim$10\,\kms and
+20-25\,\kms.  We therefore adopted a threshold of $20$\,km\,s$^{-1}$ to
+flag possible single-lined spectroscopic binaries, which selected
+\nrvscatterflag\ stars: TIC~405910546, TIC~224283342, and
+TIC~280945693.
+
+{\it RUWE}---We examined plots of Gaia DR3 RUWE as a function of
+color.\footnote{For an explanation of the renormalized unit weight
+error (RUWE), see the GAIA DPAC technical note
+\url{http://www.rssd.esa.int/doc_fetch.php?  id=3757412}.}  Elevated
+RUWEs imply excess astrometric noise relative to a single-source
+model.  This can be caused by marginally resolved binaries,  intrinsic
+photometric variability, or intrinsic astrometric motion.  Based on
+this exercise, we adopted a threshold of RUWE$_{\rm DR3}>2$ to
+flag sources with excess astrometric noise.  This threshold was met
+by \ngoodhighruwe/\ngoods\ high-quality CPVs and by
+\nmaybehighruwe/\nmaybes\ of the ambiguous CPVs.  The choice of the threshold RUWE
+is somewhat subjective, since the RUWE distribution has an extended tail
+\citep[e.g.][]{2022MNRAS.513.5270P}.  If we had instead required
+RUWE$_{\rm DR3}>1.4$, \ngoodweakruwe/\ngoods\ high-quality CPVs
+and \nmaybeweakruwe/\nmaybes\ of the ambiguous sample would have been
+flagged.
+
+{\it Gaia DR3 non-single stars}---Gaia DR3 included a {\tt
+non\_single\_star} column that flagged eclipsing, astrometric, and
+spectroscopic binaries.  None of the stars in our CPV sample were
+identified as possible binaries in this column.
+
+{\it Multiple periodic TESS signals}---During our visual analysis of
+the TESS light curves and PDM periodograms, we flagged sources with
+beating light curves, and with PDM periodograms that showed multiple
+periods.  We also attempted to disentangle the two signals by
+subtracting the mean CPV signal over each sector, and then repeating
+the phase-dispersion minimization analysis.  The results of this effort
+are summarized in the secondary periods, $P_{\rm sec}$, listed in
+Table~\ref{tab:thetable}, which we required to be at least 5\%
+different from the primary period.  This process yielded
+\ngoodmultperiodflag/\ngoods\ high-quality CPVs with secondary
+periods; \nmaybemultperiodflag/\nmaybes\ of the ambiguous sample met
+the same criterion.  Of the \ngoodhighruwe\ good CPVs with ${\rm
+RUWE}_{\rm DR3}> 2$, \ngoodruweandmultperiod\ also showed secondary
+periods in the TESS light curves.  Considering the weaker threshold of
+${\rm RUWE}_{\rm DR3}> 1.4$,
+\ngoodweakruweandmultperiod/\ngoodweakruwe\ such CPVs showed secondary
+TESS periods.
+
+Table~\ref{tab:thetable} summarizes each of the sources of
+binarity information into a single bitwise column.  
+We present the detailed results concerning binarity in
+Section~\ref{subsec:resultsbinarity}, and a summary discussion in
+Section~\ref{subsec:discbinary}.
+
 \begin{figure*}[!tp]
@@
 sample, irrespective of discovery method.  We will often refer to
-stars by their TIC identifiers; the easiest way to reference these
-against the figures in most document readers is to use a
-``find'' ({\tt Ctrl+F}) utility.
+stars by their TIC identifiers; these can be referenced against the
+figures in most digital document readers using a ``find'' ({\tt
+Ctrl+F}) utility.
 
@@
 \ngoods\ CPVs.  The objects are sorted first in order of the number of
-TESS 120-second cadence sectors in which they clearly demonstrated the
+TESS 2-minute cadence sectors in which they clearly demonstrated the
 CPV phenomenon, and secondarily by descending brightness.  The top
-five objects by this metric are TIC~300651846 ($T$$=$13.5, 12
-sectors); TIC~402980664 ($T$$=$11.1, 7 sectors); TIC~89463560
-($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5 sectors); and
-TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest five CPVs span
+five objects by this metric are TIC~300651846 (12 sectors);
+TIC~402980664 (7 sectors); TIC~89463560
+(5 sectors); TIC~363963079 (5 sectors); and
+TIC~294328887 (4 sectors).  The brightest five CPVs span
 9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
@@
 
-\subsection{Ages}
+\subsection{Ages of CPVs}
+\label{subsec:ageresults}
 
@@
 \nnotfieldbanyan\ were associated with a nearby moving group or open
-cluster, primarily using BANYAN\,$\Sigma$.\footnote{Two of the
+cluster, primarily using BANYAN\,$\Sigma$ as described in
+Section~\ref{subsec:starprops}.\footnote{Two of the
 \nnotfieldbanyan\ memberships were made with low confidence and are
@@
 groups are listed in Table~\ref{tab:thetable}; their ages span
-$\approx$5-200\,Myr.  The groups that contain the largest number of
-CPVs in our catalog are Sco-Cen, Tuc-Hor, and Columba.  Six CPVs were
-also identified in the Argus association \citep{2019ApJ...870...27Z},
-which serves as an indirect line of evidence supporting the reality
-and youth of that group.  The large contribution from Sco-Cen is not
-surprising since Sco-Cen contains the majority of pre-main-sequence
-stars in the solar neighborhood, and many of its stars were selected
-for TESS 120-second cadence observations by guest investigators.
-Given the $\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there
-may be many more CPVs in Sco-Cen that remain to be discovered.
+$\approx$5-200\,Myr.  For comparison, BANYAN\,$\Sigma$ assigned high-probability
+($>$95\%)
+field membership to 59{,}361 out of the
+\nstarssearched\ target stars.  Most stars in our target sample are old;
+the CPVs returned by our blind search are young.
+
+The groups that contain the largest number of CPVs in our catalog are
+Sco-Cen, Tuc-Hor, and Columba.  Six CPVs were also identified in the
+Argus association \citep{2019ApJ...870...27Z}, which serves as an
+indirect line of evidence supporting the reality and youth of that
+group.  The large contribution from Sco-Cen is not surprising since
+Sco-Cen contains the majority of pre-main-sequence stars in the solar
+neighborhood, and many of its stars were selected for TESS 2-minute
+cadence observations by guest investigators.  Given the
+$\lesssim$$10\%$ completeness of TESS beyond 100\,pc
+(Figure~\ref{fig:completeness}), there may be
+many more CPVs in Sco-Cen that remain to be discovered.
 
@@
 similarly-aged Psc-Eri member \citep{2020A&A...639A..64R}.  To our
-knowledge, TIC~332517282 in AB~Dor ($t$$=$$149^{51}_{-19}$\,Myr;
+knowledge, TIC~332517282 in AB~Dor ($t$$=$$149^{+51}_{-19}$\,Myr;
 \citealt{2015MNRAS.454..593B}) was the previous record-holder for the
@@
 older than the Pleiades and younger than the 400\,Myr Ursa Major
-moving group.  However, the formal BANYAN-$\Sigma$ membership
+moving group.  However, the formal BANYAN\,$\Sigma$ membership
 probability is somewhat low (only 6\%), perhaps due to the missing
@@
 
-\subsection{Infrared excesses}
+\subsection{Infrared excesses of CPVs}
 \label{subsec:irexcess}
@@
 prediction): TIC~193136669 (TWA~34) and TIC~57830249 (TWA~33).
-
-Both of these stars with IR exceses are in the TW Hydrae association
+However, neither is considered a ``good'' CPV for the reasons
+that follow.
+
+Both of the stars with IR exceses are in the TW Hydrae association
 ($\approx$10\,Myr).  They have periods of 38\,hr and 44\,hr,
@@
 seemed to stochastically evolve over only one or a few cycles, which
-is not typical of CPVs; their periods were also long in comparison with
+is atypical for CPVs; their periods were also long in comparison with
 most of the other CPVs.  Inspection of additional sectors clarified
@@
 shows completely different behavior from Sector~36, with variability
-amplitudes of $\pm 50\%$ and no obvious periodicity.  TIC 57830249
+amplitudes of $\pm 50\%$ and no obvious periodicity.  TIC~57830249
 also shows continuum emission at 1.3\,mm \citep{2015A&A...582L...5R},
@@
       curve.  The top panels show the \nstarssearched\ target stars
-      with 120-second cadence TESS data as the shaded gray background;
+      with 2-minute cadence TESS data as the shaded gray background;
       darker regions correspond to a larger relative number of
@@
 
-\subsection{Binarity}
-\label{subsec:binarity}
-
-The main types of binaries of interest in this work were those that
-were unresolved, because they can lead to misinterpretations of the data.
-For instance, unresolved binaries might produce multiple photometric
-signals and hinder our ability to correctly identify the star hosting
-the CPV signal.  Unresolved binaries could also bias photometric magnitude
-and color measurements, which would affect our stellar parameter
-estimates.  To attempt to identify binaries, we considered the
-following lines of information.
-
-{\it Radial velocity scatter}---We examined diagrams of the Gaia DR3
-``radial velocity error'' as a function of stellar color for all
-\ncqvsnodebunked\ CPVs and candidate CPVs.  Since this quantity
-represents the standard deviation of the non-published Gaia RV time
-series, outliers can suggest single-lined spectroscopic binarity.
-These plots showed two clusters of stars, at $\lesssim$10\,\kms and
-20-25\,\kms.  We therefore adopted a threshold of $20$\,km\,s$^{-1}$ to
-flag possible single-lined spectroscopic binaries, which selected
-\nrvscatterflag\ stars: TIC~405910546, TIC~224283342, and
-TIC~280945693.
-
-{\it RUWE}---We examined plots of Gaia DR3 RUWE as a function of
-color.\footnote{For an explanation of the renormalized unit weight
-error (RUWE), see the GAIA DPAC technical note
-\url{http://www.rssd.esa.int/doc_fetch.php?  id=3757412}.}  Elevated
-RUWEs imply excess astrometric noise relative to a single-source
-model.  This can be caused by marginally resolved binaries,  intrinsic
-photometric variability, or intrinsic astrometric motion.  Based on
-this exercise, we adopted a threshold of RUWE$_{\rm DR3}$ $>$ 2 to
-flag sources with excess astrometric noise.  This threshold was met
-by \ngoodhighruwe/\ngoods\ high-quality CPVs and by
-\nmaybehighruwe/\nmaybes\ of the ambiguous CPVs.  The choice of the threshold RUWE
-is somewhat subjective, since the RUWE distribution has an extended tail
-\citep[e.g.][]{2022MNRAS.513.5270P}.  If we had instead required
-RUWE$_{\rm DR3}$ $>$ 1.4, \ngoodweakruwe/\ngoods\ high-quality CPVs
-and \nmaybeweakruwe/\nmaybes\ of the ambiguous sample would have been
-flagged.
-
-{\it Gaia DR3 non-single stars}---Gaia DR3 included a {\tt
-non\_single\_star} column that flagged eclipsing, astrometric, and
-spectroscopic binaries.  None of the stars in our CPV sample were
-identified as possible binaries in this column.
-
-{\it Multiple periodic TESS signals}---During our visual analysis of
-the TESS light curves and PDM periodograms, we flagged sources with
-beating light curves, and with PDM periodograms that showed multiple
-periods.  We also attempted to disentangle the two signals by
-subtracting the mean CPV signal over each sector, and then repeating
-the phase-dispersion minimization analysis.  The results of this effort
-are summarized in the secondary periods, $P_{\rm sec}$, listed in
-Table~\ref{tab:thetable}, which we required to be at least 5\%
-different from the primary period.  This process yielded
-\ngoodmultperiodflag/\ngoods\ high-quality CPVs with secondary
-periods; \nmaybemultperiodflag/\nmaybes\ of the ambiguous sample met
-the same criterion.  Of the \ngoodhighruwe\ good CPVs with RUWE$_{\rm
-DR3}$ $>$ 2, \ngoodruweandmultperiod\ also showed secondary periods in
-the TESS light curves.  Considering the weaker threshold of RUWE$_{\rm
-DR3}$ $>$ 1.4, \ngoodweakruweandmultperiod/\ngoodweakruwe\ such CPVs
-showed secondary TESS periods.
-
-Table~\ref{tab:thetable} summarizes each of the above sources of
-information into a single bitwise column.  We discuss possible
-connections between binarity and the CPV phenomenon in
-Section~\ref{subsec:discbinary}.
-
-\section{CPV evolution}
+\subsection{Binarity of CPVs}
+\label{subsec:resultsbinarity}
+
+\subsubsection{Binary statistics}
+
+A significant fraction of the CPVs show indications of unresolved
+binarity.  Excess noise above the Gaia single-source astrometric model
+is common (\ngoodhighruwe/\ngoods\ high-quality CPVs have RUWE$_{\rm
+DR3}$$>$2), as is the presence of multiple periods in the TESS light
+curves (\ngoodmultperiodflag/\ngoods).  Elevated astrometric noise
+almost always implies multiple detectable TESS periods
+(\ngoodruweandmultperiod/\ngoodhighruwe\ high-quality CPVs).  The
+latter observation corroborates the claim that most sources with
+RUWE$_{\rm DR3}$$>$2 are binaries with projected apparent separations
+below 1$''$, and projected physical separations $\lesssim$50\,AU.
+These observations are also in agreement with previous analyses of
+multi-periodic low-mass discovered by K2, which found that such
+systems are almost always binaries
+\citep{2018AJ....156..138T,2018AJ....156..275S}.
+
+\subsubsection{Do K dwarf CPVs exist?}
+\label{subsec:massive}
+
+To date, the only stars reported to show the CPV phenomenon are M
+dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
+\citep{2017AJ....153..152S,2022AJ....163..144G}.  However the two most
+massive CPVs in our sample, TIC~405754448 and TIC~405910546, were
+assigned masses of $\approx$0.82\,$M_\odot$ and
+$\approx$0.60\,$M_\odot$ respectively.  The next-highest masses in our
+sample are $\approx$0.40\,$M_\odot$.
+
+These stars' locations in color--absolute magnitude diagrams and their
+probable membership in Lower Centaurus Crux both support the
+conclusion that they have relatively high masses.  However in detail,
+both are subject to ambiguities in interpretation.  The TIC~405910546
+light curve has a unique shape, suggestive of an eclipsing binary.
+Independently, TIC~405910546 was one of only \nrvscatterflag\ CPVs
+flagged with a Gaia DR3 radial velocity scatter exceeding 20\,\kms.
+Combined, these factors suggest that TIC~405910546 could be a
+pre-main-sequence eclipsing binary; it should be studied further to
+clarify this classification.
+
+For the other object, TIC~405754448, the evidence for binarity is
+stronger.  The RUWE$_{\rm DR3}$ statistic is 6.8, and the raw light
+curves in Sectors 11, 37, and 38 show both the CPV signal with period
+12.9\,hr and amplitude $\approx$1\% and an additional sinusoidal
+signal with a period $\approx$6.5\,days and amplitude $\approx$0.3\%,
+likely from a second star.  If TIC~405754448 is a K+M binary, then the
+flux ratio between the primary and secondary would be expected to be
+$\approx$10:1.  Thus, if the K star were the source of the CPV signal,
+its intrinsic variability amplitude would be $\approx$1\%, while if
+the M star were responsible its intrinsic variability amplitude would
+be $\approx$10\%.
+
+In short, these two objects suggest that the CPV phenomenon may extend
+up in mass to pre-main-sequence K dwarfs, but more data are needed to
+substantiate this claim.
+
+\subsubsection{An astrophysical CPV false positive: TIC~435903839}
+
+We originally classified TIC~435903839, with RUWE$_{\rm DR3}$=17.7, as
+an ``ambiguous'' CPV with a 10.8\,hr period, because this period
+minimized the dispersion in the phase-folded light curve.  More
+careful inspection revealed an impostor: this source is a photometric
+blend of two ordinary rotating stars with $P_0$=3.60\,hr, and
+$P_1$=5.41\,hr, giving a beat period $(P_0^{-1} - P_1^{-1})^{-1}$ of
+10.8\,hr.  This is a novel false positive scenario for CPVs: two rapid
+rotators near the 3:2 period commensurability.  The beat between the
+two rotation signals produces the apparent CPV signal.  Such false
+positives can be excluded through careful accounting of all peaks in a
+periodogram.  For instance, TIC~435903839 shows a peak at 16.27\,hr,
+which is not an integer multiple of the dispersion-minimizing
+10.82\,hr period.
+
+\subsubsection{Multiple CPVs in the same system: TIC~425937691 and TIC~142173958}
+
+TIC~142173958 and TIC~425937691 both show evidence for two separate CPV
+signals in their TESS light curves.  For TIC~142173958, the signals
+have periods of 11.76\,hr and 12.84\,hr.  For TIC~425937691, the two
+periods are 4.82\,hr and 3.22\,hr, near the 3:2 period commensurability.
+Given that both sources have two photometric signals and elevated
+RUWEs, each source is probably an unresolved binary consisting of two
+CPVs.  To our knowledge, these are the third and fourth such systems
+known: EPIC~204060981 has two CPVs with periods of 9.59\,hr and
+9.12\,hr \citep{2018AJ....155...63S}, and TIC~242407571 has two CPVs
+with periods of 11.33\,hr and 13.63\,hr, near the 6:5 period commensurability
+\citep{2021AJ....161...60S}.
+%\footnote{TIC~242407571, although within
+%our nominal distance and brightness limits, was not observed by TESS
+%in the 2-minute cadence mode between 2018~July and 2022~September, and
+%is therefore not in our sample.}
+
+\section{Evolution of CPV Behavior}
 \label{sec:evoln}
@@
 			Out of the \ngoods\ CPVs in Figure~\ref{fig:cqvs}, 32 had
-			120-second cadence TESS data available for a baseline of at
+			2-minute cadence TESS data available for a baseline of at
 			least two years; the 27 brightest are shown here due to space
@@
 Figure~\ref{fig:evoln} shows ``before'' and ``after'' views of 27 CPVs
-for which TESS 120-second cadence observations were available at least
+for which TESS 2-minute cadence observations were available at least
 two years apart.  Such a baseline was available for 32 of the
@@
 already gave this source such a label.  However, based on the shape
-evolution between Sectors 13 and 39, it is a CPV.  Based on the
+evolution between Sectors 13 and 39, it is a CPV.
+
+Based on the
 fraction of sources overall that ``turned off'', the observed shape
@@
 		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f9a.pdf}
-			\includegraphics[width=0.48\textwidth]{f9b.pdf}
+			\includegraphics[width=0.49\textwidth]{f9a.pdf}
+			\includegraphics[width=0.49\textwidth]{f9b.pdf}
 		}
@@
 		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f9d.pdf}
-			\includegraphics[width=0.48\textwidth]{f9c.pdf}
+			\includegraphics[width=0.49\textwidth]{f9d.pdf}
+			\includegraphics[width=0.49\textwidth]{f9c.pdf}
 		}
@@
 zones (Figure~\ref{fig:catalogscatter}, top right).  Out of this
-already small sample, LP 12-502 (TIC 402980664; $d$=21\,pc, $J$=9.4,
+already small sample, LP 12-502 (TIC~402980664; $d$=21\,pc, $J$=9.4,
 $T$=11.1) stood out due to the quality and content of its data.  We
@@
 Whenever LP 12-502 was located within a TESS sector, it was observed
-at 120-second cadence.  Figure~\ref{fig:lplc} shows all the available
+at 2-minute cadence.  Figure~\ref{fig:lplc} shows all the available
 data, from Sectors 18, 19, 25, 26, 53, 58, and 59. Vertical offsets
@@
 
-Referring back to Figure~\ref{fig:catalogscatter}, which compares the
-properties of CPVs with those of the search sample (top panels) and the
-Pleiades \citep{2016AJ....152..114R}, we see that the typical CPV
-masses span 0.1-0.4\,$M_\odot$, and the typical ages span 2-150\,Myr.
-This mass and age range includes both fully convective stars and stars
-with a combination of radiative cores and convective envelopes, with
-the dividing line for these ages at around $M_\star = 0.25\,M_\odot$
-\citep{2018A&A...619A.177B}.  We found no obvious differences in light
-curve morphology between CPVs above and below the boundary of
-0.25\,$M_\odot$.  In terms of their rotation rates relative to the
+Referring back to Figure~\ref{fig:catalogscatter},  typical CPV
+masses span 0.1-0.4\,$M_\odot$, typical ages span 2-150\,Myr,
+and
+relative to the
 Pleiades, the CPVs are among the more rapidly rotating half of M
 dwarfs. 
-
-The closest CPV in our catalog is DG~CVn (TIC~368129164; $d$$=$18\,pc),
-a member of AB Dor.  To our knowledge, this star had not previously
-been recognized as a CPV.  The three brightest CPVs are DG~CVn
+The CPV mass and age range includes both fully convective stars and stars
+with a combination of radiative cores and convective envelopes; 
+the dividing line for these ages is at around $M_\star = 0.25\,M_\odot$
+\citep{2018A&A...619A.177B}.  We found no obvious differences in light
+curve morphology for CPVs above and below this fully-convective pre-main-sequence boundary.
+
+The closest newly-recognized CPV in our catalog is DG~CVn (TIC~368129164),
+a member of AB Dor at $d$$=$18\,pc.  
+The three brightest CPVs are DG~CVn
 ($T$=9.3), TIC~405754448 ($T$=9.6), and TIC~167664935 ($T$=10.3).  The
 shortest period, 3.64\,hr, belongs to TIC~201789285.  The longest
-period, 37.9\,hr, belongs to TIC~405910546.  If the latter source
-turns out to be an eclipsing binary, the longest-period CPV in the
+period, 37.9\,hr, belongs to TIC~405910546.  Based on the Gaia$_{\rm DR3}$ RV
+scatter, the latter source may
+turn out to be an eclipsing binary; if so, the longest-period CPV in our
 catalog would be TIC~193831684 (31.0\,hr).  By definition, we required
@@
 
-\subsection{CPVs and binarity}
+\subsection{Is binarity important for CPVs?}
 \label{subsec:discbinary}
 
-\subsubsection{Binary statistics}
-
-In Section~\ref{subsec:binarity}, we found that a significant fraction
-of the CPVs show indications of unresolved binarity.  Excess noise
-above the Gaia single-source astrometric model is common
-(\ngoodhighruwe/\ngoods\ high-quality CPVs have RUWE$_{\rm DR3}$$>$2),
-as is the presence of multiple periods in the TESS light curves
-(\ngoodmultperiodflag/\ngoods).  Elevated astrometric noise almost
-always implies multiple detectable TESS periods
-(\ngoodruweandmultperiod/\ngoodhighruwe\ high-quality CPVs).  The
-latter observation corroborates the claim that most sources with
-RUWE$_{\rm DR3}$$>$2 are binaries with projected apparent separations
-below 1$''$, and projected physical separations $\lesssim$50\,AU.
-These observations are also in agreement with previous analyses of
-multi-periodic low-mass discovered by K2, which found that such
-systems are almost always binaries
-\citep{2018AJ....156..138T,2018AJ....156..275S}.
-
-One possible relation between binarity and CPVs is that the presence of
-an intermediate-separation binary could cause early disk dispersal,
-freeing the star to contract.  The CPV phenomenon seems to require
-rapid rotation; thus if binary systems tend to produce more rapidly
-rotating stars, we would expect a sample of CPVs to have a larger
-binary fraction than the field.  We see marginal, if any, evidence for such
-an effect.  The multiplicity rate of M dwarfs near the Sun is
-26.8$\pm$1.4\% \citep{2019AJ....157..216W}.  Based on the same study,
-the peak of the separation distribution decreases from $\approx$49\,AU
-for $0.30$-$0.60$\,$M_\odot$ stars, to $\approx$11\,AU for
-$0.15$-$0.30$\,$M_\odot$ M dwarfs.  The multiplicity fraction in our
-CPV sample (32\% from RUWE$_{\rm DR3}$) seems approximately consistent
-with this field fraction.
-
-\subsubsection{Do K dwarf CPVs exist?}
-\label{subsec:massive}
-
-To date, the only stars reported to show the CPV phenomenon are M
-dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
-\citep{2017AJ....153..152S,2022AJ....163..144G}.  However the two most
-massive CPVs in our sample, TIC~405754448 and TIC~405910546, were
-assigned masses of $\approx$0.82\,$M_\odot$ and
-$\approx$0.60\,$M_\odot$ respectively.  The next-highest masses in our
-sample are $\approx$0.40\,$M_\odot$.
-
-These stars' locations in color--absolute magnitude diagrams and
-their probable membership in Lower Centaurus Crux both support the
-conclusion that they have relatively high masses.
-However in detail, both are subject to ambiguities
-in interpretation.  The TIC~405910546 light curve has a unique shape,
-suggestive of an eclipsing binary.  Independently, TIC~405910546 was
-one of only \nrvscatterflag\ CPVs flagged with a Gaia DR3 radial
-velocity scatter exceeding 20\,\kms.  Combined, these factors suggest
-that TIC~405910546 could be a pre-main-sequence eclipsing binary; it
-should be studied further to clarify this classification.
-
-For the other object, TIC~405754448, the evidence for binarity is
-stronger.  The RUWE$_{\rm DR3}$ statistic is 6.8, and the raw light
-curves in Sectors 11, 37, and 38 show both the CPV signal with period
-12.9\,hr and amplitude $\approx$1\% and an additional sinusoidal
-signal with a period $\approx$6.5\,days and amplitude $\approx$0.3\%,
-likely from a second star.  If TIC~405754448 is a K+M binary, then the
-flux ratio between the primary and secondary would be expected to be
-$\approx$10:1.  Thus, if the K star were the source of the CPV signal,
-its intrinsic variability amplitude would be $\approx$1\%, while if
-the M star were responsible its intrinsic variability amplitude would
-be $\approx$10\%.
-
-In short, these two objects suggest that the CPV phenomenon may extend
-up in mass to pre-main-sequence K dwarfs, but more data are needed to
-substantiate this claim.
-
-\subsubsection{An astrophysical CPV false positive: TIC~435903839}
-
-We originally classified TIC~435903839, with RUWE$_{\rm DR3}$=17.7, as
-an ``ambiguous'' CPV with a 10.8\,hr period, because this period
-minimized the dispersion in the phase-folded light curve.  More
-careful inspection revealed an impostor:
-this source is a photometric blend of two ordinary rotating stars with
-$P_0$=3.60\,hr, and $P_1$=5.41\,hr, giving a beat period $(P_0^{-1} -
-P_1^{-1})^{-1}$ of 10.8\,hr.  This is a novel false positive scenario
-for CPVs: two rapid rotators near the 3:2 period commensurability.
-The beat between the two rotation signals produces the apparent CPV
-signal.  Such false positives can be excluded through careful
-accounting of all peaks in a periodogram.  For instance, TIC~435903839
-shows a peak at 16.27\,hr, which is not an integer multiple of the
-dispersion-minimizing 10.82\,hr period.
-
-\subsubsection{Multiple CPVs in the same system: TIC~425937691 and TIC~142173958}
-
-TIC~142173958 and TIC~425937691 both show evidence for two separate CPV
-signals in their TESS light curves.  For TIC~142173958, the signals
-have periods of 11.76\,hr and 12.84\,hr.  For TIC~425937691, the two
-periods are 4.82\,hr and 3.22\,hr, near the 3:2 period commensurability.
-Given that both sources have two photometric signals and elevated
-RUWEs, each source is probably an unresolved binary consisting of two
-CPVs.  To our knowledge, these are the third and fourth such systems
-known: EPIC~204060981 has two CPVs with periods of 9.59\,hr and
-9.12\,hr \citep{2018AJ....155...63S}, and TIC~242407571 has two CPVs
-with periods of 11.33\,hr and 13.63\,hr, near the 6:5 period commensurability
-\citep{2021AJ....161...60S}.\footnote{TIC~242407571, although within
-our nominal distance and brightness limits, was not observed by TESS
-in the 120-second cadence mode between 2018~July and 2022~September, and is therefore not in our sample.}
-
-Recent work has shown that the orbits of binaries closer than
+For CPVs, binarity seems to mostly provide a mix of
+observational nuisances and curiosities.  The
+nuisances include
+astrophysical false positives with two beating rapidly
+rotating stars, as well as uncertainty about which
+star is producing the CPV signal in binary systems.  Our two candidate K dwarf CPVs 
+suffer from the latter concern (see Section~\ref{subsec:resultsbinarity}).
+
+Curiosities include the four binary systems that are now known to each host
+two separate CQVs.
+CQVs are sufficiently rare that such systems may have 
+physical implications.
+For instance, recent work has shown that the orbits of binaries closer than
 $\lesssim$700 AU tend to be aligned with their planetary systems
@@
 current catalog prevent further exploration of this issue, but it
-might be interesting for future study.  Even if this scenario is
-correct, it would not provide an immediate explanation for the
-near-commensurability of the two periods of either TIC~425937691 
-or TIC~242407571.
+might be interesting for future study.
+
+A separate possible relation between binarity and CPVs is that the presence
+of an intermediate-separation binary could cause early disk dispersal,
+freeing the star to contract.  The CPV phenomenon seems to require
+rapid rotation; thus if binary systems tend to produce more rapidly
+rotating stars, we would expect a sample of CPVs to have a larger
+binary fraction than the field.  However, we see minimal evidence for
+such an effect (Section~\ref{subsec:resultsbinarity}).  The
+multiplicity rate of M dwarfs near the Sun is 26.8$\pm$1.4\%
+\citep{2019AJ....157..216W}.  Based on the same study, the peak of the
+separation distribution decreases from $\approx$49\,AU for
+$0.30$-$0.60$\,$M_\odot$ stars, to $\approx$11\,AU for
+$0.15$-$0.30$\,$M_\odot$ M dwarfs.  The multiplicity fraction in our
+CPV sample ($\approx$32\% from RUWE$_{\rm DR3}$) seems approximately
+consistent with this field fraction.
 
@@
 
-In this work, we searched 120-second cadence TESS data collected from
+In this work, we searched 2-minute cadence TESS data collected from
 2018 July to 2022 September for complex periodic variables (CPVs).  The target
@@
 volume-limited and is not even magnitude-limited:
-the TESS 120-second stellar sample had a heterogeneous
+the TESS 2-minute stellar sample had a heterogeneous
 selection function which may have been biased in favor of young stars
@@
 This paper relied primarily on data collected by the TESS mission; the specific
-120-second cadence observations can be accessed via
+2-minute cadence observations can be accessed via
 DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.
@@
 We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham, S.~Seager, and J.~Jenkins) and the many TESS team members for their efforts to make the mission a continued success. 
-TIC 402980664 in particular was observed at 120-second
+LP 12-502 in particular was observed at 2-minute
 cadence thanks to the TESS Guest Investigator programs G022252 (PI:
@@
   Oct~2024.  This number is generally greater than the number of
-  sectors for which 120-second cadence data exist.   Association names
+  sectors for which 2-minute cadence data exist.   Association names
   and provenance follow conventions adopted by
@@
 		{\bf Light curve evolution of TIC 300651846}.
-		All available 120-second cadence data as of 2023 Aug 11 are shown.
+		All available 2-minute cadence data as of 2023 Aug 11 are shown.
 		Cycles 0 to 622 span TESS Sectors 32-39 (Nov 2020--June 2021);
@@
 		This is an alternative visualization of the data in
-		Figure~\ref{fig:tic3006timegroups}.  All available 120-second
+		Figure~\ref{fig:tic3006timegroups}.  All available 2-minute
 		cadence data as of 2023 Aug 11 are shown.  Cycles 0 to 622 span
@@
 Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river} show
-120-second cadence data for TIC~300651846, a CPV in the TESS
+2-minute cadence data for TIC~300651846, a CPV in the TESS
 continuous viewing zone.  If it were not for the existence of
-TIC~402980664, this source would have received greater
+LP~12-502, this source would have received greater
 attention.  With the exception of a few sectors, TESS data will exist
@@
 Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river} focus
-only on the currently available 120-second cadence data.
+only on the currently available 2-minute cadence data.
 
@@
 evolution timescales for TIC~300651846 seem to be $\approx$50-100
-cycles.  Unlike the TIC~402980664 river plots
+cycles.  Unlike the LP~12-502 river plots
 (Figure~\ref{fig:lpriver0}), we did not subtract any ``continuum
@@
 {\it How many known CPVs did we miss?}---A minority of the literature
-CPVs, 19/74, were stars with 120-second TESS data acquired between
+CPVs, 19/74, were stars with 2-minute TESS data acquired between
 Sectors 1-55 that also met conditions~\ref{eq:one}--\ref{eq:four}.
@@
 periods and sharp features when observed at 2-minute cadence.
-Comparing the 20-second to 120-second data for these stars (data
+Comparing the 20-second to 2-minute data for these stars (data
 available on MAST), we concluded that these CPVs did not contain
@@
 TIC~146539195 on 2023 January 3, a 15 minute exposure of TIC~264599508
-on 2023 January 9, and a 30 minute exposure of TIC~402980664 on 2023
+on 2023 January 9, and a 30 minute exposure of LP~12-502 (TIC~402980664) on 2023
 July 10.  The acquisition and analysis followed the usual techniques
@@
 		mass and $\beta$~Pic membership;
-		the non-detections for TIC~402980664 and TIC~264599508
+		the non-detections for LP~12-502 (TIC~402980664) and TIC~264599508
 		are consistent with the $\approx$42\,Myr age implied by their membership

### 2023-09-07 paper/ms.tex
update ms
Co-authored-by: Lynne Hillenbrand <lah@astro.caltech.edu>

@@
   ($\lesssim$0.4\,$M_\odot$).  The flux dips that embody the class
-  have lifetimes of $\approx$100 cycles, and the dips collapse in
-  response to stellar flares once every few months.  Corotating
+  have lifetimes of $\approx$100 cycles, and the dips collapse following
+  stellar flares once every few months.  Corotating
   concentrations of gas or dust remains the only plausible explanation
@@
 binarity information into a single bitwise column.  
-We present the detailed results concerning binarity in
+We present detailed results concerning binarity in
 Section~\ref{subsec:resultsbinarity}, and a summary discussion in
@@
 		\centering
-		\includegraphics[width=0.98\textwidth]{f8.pdf}
+		\includegraphics[width=0.99\textwidth]{f8.pdf}
 		\vspace{-0.3cm}
@@
 
-The closest newly-recognized CPV in our catalog is DG~CVn (TIC~368129164),
+The closest CPV in our catalog is DG~CVn (TIC~368129164),
 a member of AB Dor at $d$$=$18\,pc.  
@@
 For CPVs, binarity seems to mostly provide a mix of
-observational nuisances and curiosities.  The
+nuisances and curiosities.  The
 nuisances include
@@
 rotating stars, as well as uncertainty about which
-star is producing the CPV signal in binary systems.  Our two candidate K dwarf CPVs 
-suffer from the latter concern (see Section~\ref{subsec:resultsbinarity}).
+star produces the CPV signal in binary systems.  Our two candidate K dwarf CPVs 
+suffer from this latter concern (see Section~\ref{subsec:resultsbinarity}).
 
@@
 physical implications.
-For instance, recent work has shown that the orbits of binaries closer than
+Recent work has shown that the orbits of binaries closer than
 $\lesssim$700 AU tend to be aligned with their planetary systems
 \citep[e.g.][]{2022AJ....163..207C}.  If we assume that observing CPV
-variability requires high inclinations relative to the line of sight,
+variability requires high line-of-sight inclinations,
 and that the inclinations in binaries are correlated, then we would
@@
 
-While CPV periods appear to remain constant to within measurement
-precision over thousands of cycles, the light curve shapes evolve over
+While CPV periods appear to remain fixed over thousands of cycles, the light curve shapes evolve over
 typical timescales of 10 to 1{,}000 cycles (e.g.
-Figures~\ref{fig:evoln} and~\ref{fig:lpriver0}).  The CPVs are
-therefore quasiperiodic, with quality factors of $Q$$\approx$100.
+Figures~\ref{fig:evoln} and~\ref{fig:lpriver0}).  Although we refer
+to them as ``periodic'', the CPVs are
+therefore actually quasiperiodic, with quality factors of $Q$$\approx$100.
 While this observation is consistent with the analyses by
@@
 
-\subsection{Dip asymmetries and dust geometries}
+\subsection{Dip asymmetries?}
 
@@
 
-\subsection{Dust vs. gas}
-
-Both the dust clump and the gas prominence scenario invoke clumps
+\subsection{What causes the CPV phenomenon: dust vs.\ gas}
+
+Both the dust clump and the gas prominence scenarios (Figure~\ref{fig:f1} and Section~\ref{sec:intro})
+invoke clumps
 of material at the corotation radius;
@@
 that non-shielded, generic silicate dust mixture \citep{1985ApJS...57..587D} with a
-single size of 0.1\,$\mu$m reached the $\approx$1500\,K sublimination
+single size of 0.1\,$\mu$m reached the $\approx$1500\,K sublimation
 temperature at $\approx$3\,$R_\star$.  This suggests that dust
@@
 corotation radius for low accretion rates
-\citep[e.g.][]{2016ARA&A..54..135H,2022MNRAS.510.5246L}.  These considerations
+\citep[e.g.][]{2015SSRv..191..339R,2022MNRAS.510.5246L}.  These considerations
 invite us to imagine one or more planets migrating inward due to gas
@@
 
-		\vspace{-0.35cm}
+		\vspace{-0.34cm}
 		\subfloat{
@@
       decay can also occur.  ``State-switches'' correspond to dips 
-      collapsing instantaneously, and are almost always linked with
+      collapsing instantaneously, and
+      occur once every few months for
+      both LP~12-502 and TIC~300651846.
+      They are almost always linked with
       observed optical flares.  Such switches are suggestive of

### 2023-09-07 paper/ms.tex
improve abstract

@@
   Complex periodic variables (CPVs) are stars that exhibit sharp and
-  periodic optical light curves.  Previous work has indicated that such stars
-  tend to be disk-free pre-main-sequence M dwarfs with rotation
-  periods of 0.2--2 days.  To advance understanding of these enigmatic
-  objects, we performed a blind search using TESS 2-minute data of
-  \nstarssearched\ K and M dwarfs with $T$$<$16 and $d$$<$150\,pc.  We
-  found \ngoods\ high-quality CPVs.  The new objects include the
+  periodic optical light curves.  Previous studies have indicated that
+  these stars are typically disk-free pre-main-sequence M dwarfs with
+  rotation periods ranging from 0.2 to 2 days.  To advance our
+  understanding of these enigmatic objects, we conducted a blind
+  search using TESS 2-minute data of \nstarssearched\ K and M dwarfs
+  with $T$$<$16 and $d$$<$150\,pc.  We found \ngoods\ high-quality
+  CPVs, and subsequently determined that most are members
+  of stellar associations.  Among the new discoveries are the
   brightest ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and
-  oldest ($\approx$200\,Myr) CPVs known.  All objects but one turned
-  out to be likely members of stellar associations, which enabled
-  age-dating.  An exceptional new object, LP 12-502, showed up to
-  eight flux dips per cycle; some of the LP 12-502 dips coexisted with slightly
-  different periods, and the shortest-duration LP 12-502 dips matched the expected
+  oldest ($\approx$200\,Myr) CPVs known.  One exceptional object, LP
+  12-502, exhibited up to eight flux dips per cycle. Some of these
+  dips coexisted with slightly different periods, and the
+  shortest-duration LP 12-502 dips precisely matched the expected
   timescale for transiting small bodies at the corotation radius.
-  Broadly, our search confirms
-  that CPVs are mostly young ($\lesssim$150\,Myr) and low-mass
-  ($\lesssim$0.4\,$M_\odot$).  The flux dips that embody the class
-  have lifetimes of $\approx$100 cycles, and the dips collapse following
-  stellar flares once every few months.  Corotating
-  concentrations of gas or dust remains the only plausible explanation
-  known.  The gas or dust is probably entrained by the star's magnetic
-  field, and the sharp features could result from a multipolar field
-  topology, a hypothesis supported by correspondences between the
-  light curves of CPVs and of B stars known to have multipolar
-  magnetic fields.
+  Broadly, our search confirms that CPVs are mostly young
+  ($\lesssim$150\,Myr) and low-mass ($\lesssim$0.4\,$M_\odot$).  The
+  flux dips characteristic of the class have lifetimes of $\approx$100
+  cycles, although stellar flares seem to induce sudden dip collapse
+  once every few months.  The most plausible explanation for these
+  phenomena remains corotating concentrations of gas or dust.  The gas
+  or dust is probably entrained by the star's magnetic field, and the
+  sharp features could result from a multipolar field topology, a
+  hypothesis supported by correspondences between the light curves of
+  CPVs and of B stars known to have multipolar magnetic fields.
   %

### 2023-09-07 paper/ms.tex
update ms
Co-authored-by: Lynne Hillenbrand <lah@astro.caltech.edu>

@@
 ``transient flux dips'', ``persistent flux dips'', and ``scallop
-shells'' \citep{2017AJ....153..152S}.  The CPVs should not be conflated
-with ``dippers'', which are classical T Tauri stars with infrared
-excesses, and which show large-amplitude variability linked to
-obscuring inner disk structures and accretion hot spots
+shells'' \citep{2017AJ....153..152S}.  The CPVs should not be
+conflated with ``dippers'', which are classical T Tauri stars with
+infrared excesses, and which show large-amplitude variability linked
+to obscuring inner disk structures and accretion hot spots
 \citep{2014AJ....147...82C,2021ApJ...908...16R}.  The phenomenology
@@
 see Sections~\ref{subsec:irexcess} and~\ref{subsec:discdippers}).  The
-defining phenomenological features of the CPVs are that their
-light curves are {\it complex}, relative to quasi-sinusoidal
-starspots, and the complex features are {\it periodic}, over
-timescales of order one hundred cycles.  While rotation likely
-does play a central role in explaining their physical behavior, the
-acronym for ``complex rotator'' is already used in the astrophysical
-literature for cosmic rays.  Given these
-considerations, we refer to the stars as complex periodic variables
-(CPVs); our preferred explanation for their behavior is that transient
-clumps of gas or dust orbit at their corotation radii.
+defining phenomenological features of the CPVs are that their light
+curves are {\it complex}, relative to quasi-sinusoidal starspots, and
+the complex features are {\it periodic}, meaning they typically repeat
+for at least tens of days.  While rotation likely does play a central
+role in explaining their physical behavior, the acronym for ``complex
+rotator'' is already used in the astrophysical literature for cosmic
+rays.  Given these considerations, we refer to the stars as complex
+periodic variables (CPVs); our preferred explanation for their
+behavior is that transient clumps of gas or dust orbit at their
+corotation radii.
 
@@
 
-For CPVs, binarity seems to mostly provide a mix of
-nuisances and curiosities.  The
+For CPVs, binarity seems to provide either nuisances or curiosities.  The
 nuisances include
@@
 CQVs are sufficiently rare that such systems may have 
-physical implications.
+physical import.
 Recent work has shown that the orbits of binaries closer than
@@
 A separate possible relation between binarity and CPVs is that the presence
-of an intermediate-separation binary could cause early disk dispersal,
+of a binary companion could cause early disk dispersal,
 freeing the star to contract.  The CPV phenomenon seems to require
@@
 multiplicity rate of M dwarfs near the Sun is 26.8$\pm$1.4\%
-\citep{2019AJ....157..216W}.  Based on the same study, the peak of the
-separation distribution decreases from $\approx$49\,AU for
-$0.30$-$0.60$\,$M_\odot$ stars, to $\approx$11\,AU for
-$0.15$-$0.30$\,$M_\odot$ M dwarfs.  The multiplicity fraction in our
-CPV sample ($\approx$32\% from RUWE$_{\rm DR3}$) seems approximately
+\citep{2019AJ....157..216W}.  
+%Based on the same study, the peak of the
+%separation distribution decreases from $\approx$49\,AU for
+%$0.30$-$0.60$\,$M_\odot$ stars, to $\approx$11\,AU for
+%$0.15$-$0.30$\,$M_\odot$ M dwarfs.
+The $\approx$32\% multiplicity fraction in our
+CPV sample (from RUWE$_{\rm DR3}$; see Section~\ref{subsec:resultsbinarity})
+seems approximately
 consistent with this field fraction.
 
-\subsection{Transience \& special phases of CPV dips}
+\subsection{Transience of CPV dips}
 
 While CPV periods appear to remain fixed over thousands of cycles, the light curve shapes evolve over
-typical timescales of 10 to 1{,}000 cycles (e.g.
-Figures~\ref{fig:evoln} and~\ref{fig:lpriver0}).  Although we refer
+typical timescales of 10 to 1{,}000 cycles (e.g.\ Figures~\ref{fig:evoln} and~\ref{fig:lpriver0}).  Although we refer
 to them as ``periodic'', the CPVs are
-therefore actually quasiperiodic, with quality factors of $Q$$\approx$100.
-While this observation is consistent with the analyses by
-\citet{2022AJ....163..144G} and \citet{2023ApJ...945..114P}, the fact
-that all CPV dips seem to be transient over timescales of more than
-1{,}000 cycles (Figure~\ref{fig:evoln}) marks a qualitative departure
+therefore actually quasiperiodic, with coherence timescales of $\approx$100 cycles.
+This marks a qualitative departure
 from the ``persistent'' {\it vs.} ``transient'' flux dip distinction
-previously described by \citet{2017AJ....153..152S}.
-
-One peculiarity of CPV evolution however is that the dips do not
+previously described by \citet{2017AJ....153..152S}, which was based on
+$\lesssim$100\,cycle K2 baselines.
+The observation that CPVs have a population-averaged on-off duty cycle of $\approx$75\%
+(Figure~\ref{fig:evoln}) is also new.
+Appendix~\ref{app:tic3006} for instance shows $\approx$1{,}000 cycles of a source, TIC~300651846, with between zero and five sharp local minima per cycle.
+During the ``zero'' epochs (cycles $\approx$503-542), the source would likely be labeled an ordinary rotating star.
+
+\subsection{Special phases of CPV dips}
+
+An independent peculiarity of CPV evolution is that the dips do not
 explore all phase angles with equal weight.  LP 12-502, and other CPVs,
-have preferred phases lasting for at least two years.  For LP 12-502,
+exhibit preferred phases lasting for at least two years.  For LP 12-502,
 all of the dips happen over phases corresponding to only two thirds of
@@
 of exocomet \citep[e.g.][]{2018MNRAS.474.1453R,2019A&A...625L..13Z},
-or the outflowing exospheres of certain transiting planets
+and the outflowing exospheres of some transiting planets
 \citep[e.g.][]{2019ApJ...873...89M,2022ApJ...926..226M}.
@@
 In the context of disk-driven planet migration, the stopping location
-for the innermost planet is set by the location of the protoplanetary
+for the innermost planet is set by the protoplanetary
 disk's truncation radius \citep[e.g.][and references therein]{2018haex.bookE.142I}.  The 
-truncation radius is traditionally calculated by equating the magnetic
+truncation radius is often calculated by equating the magnetic
 pressure from the stellar magnetosphere with the ram pressure of the

### 2023-09-07 paper/ms.tex
update ms

@@
 
-\subsection{Planets or planetesimal swarms near corotation?}
+\subsection{Planets or planetesimals near corotation?}
 
@@
 
-\subsection{From dippers to debris disks}
-\label{subsec:discdippers}
-
-About one in three young stars with infrared-detected inner dusty
-disks show quasiperiodic or stochastic dimming over timescales of
-roughly one day \citep[e.g.][]{2010A&A...519A..88A}.  The dimming
-amplitudes can reach a few tenths of the stellar brightness, and dips
-with identical depths and phases rarely recur.  These ``dipper'' stars
-are probably explained by occulting circumstellar dust in the inner
-disk
-\citep[e.g.][]{2014AJ....147...82C,2016ApJ...816...69A,2021ApJ...908...16R,2022ApJS..263...14C}.
-While the phenomenon can persist beyond $\approx$10\,Myr
-\citep{2019MNRAS.488.4465G,2022MNRAS.514.1386G}, in all such cases it
-seems to be associated with the presence of infrared excesses.
-Phenomenologically, dippers are different from CPVs in that their dips
-are usually deeper, less periodic, and more variable in depth over
-timescales of only one or a few cycles.  Dipper stars also tend to be
-younger, since they tend to be classical T Tauri stars with infrared
-excesses.
-
-In identifying the two candidate CPVs with outlying SEDs
-(TICs~193136669 and TIC~57830249; Section~\ref{subsec:irexcess}), we
-were prompted to reconsider our light curve-based labeling, and
-ultimately concluded that these sources are dippers.  This episode
-suggests that there could be overlap between CPVs and dippers.  Taking
-TIC~57830249 as one example, the Sector~36 TESS data are suggestive of
-a CPV, with relatively periodic, sharp dips with depths of a few
-percent.  The Sector~10 data are completely different, varying in
-apparent flux by a factor of two, with no discernible periodicity at
-all.  Perhaps this source becomes a ``dipper'' when an inflow of dust
-reaches the inner disk wall, and is otherwise a ``CPV'' when the inner
-disk is starved of dust.
-
-Although TIC~57830249 is an intriguing outlier, the general picture is that
-stars without infrared excesses have more stable optical light curves
-than those with infrared excesses.  While some dippers may evolve into CPVs after the
-disk is mostly gone, this would be generically expected based on population
-statistics: young objects become old.  There may be no
-other causal connection between the two evolutionary stages.  With
-that said, a common mystery between the CPVs and dippers is how exactly
-the {\it narrowness} of their flux dimmings is produced.  
-A similar mechanism may operate for both
-types of object, tied perhaps to a shared magnetic topology, or
-perhaps to a preference for dust to inspiral to the star in clumped
-structures.
-
-%\subsection{Are half-cycles important?}
-%
-% NOTE to arxis readers: the answer was: "maybe in a few cases, but
-% this manuscript was already too long!".
-%
-%The interval of half a cycle period could be significant in the
-%context of CPVs for two reasons.  The first is that for material on a
-%circular orbit viewed edge-on, a half-cycle corresponds to the
-%interval between transit and secondary eclipse.  The second is that
-%the half-cycle also corresponds to the interval over which half of the
-%star's surface is visible.  Of the CPVs in Figures~\ref{fig:cqvs}
-%and~\ref{fig:evoln}, a fraction that seems greater than random might
-%exhibit a preference for showing dips or peaks that correspond to the
-%half-cycle interval.
-%
-%One set of CPVs shows ``CPV behavior'' (some form of dip complex), but
-%which only lasts for half of any given cycle.  TIC~206544316 (Sector
-%2) is a canonical example; TIC~405910546 (Sector 38), TIC~167664935
-%(Sector 38), TIC~146539195 (Sector 5), TIC~118449916 (Sector 44), and
-%TIC~312410638 (Sector 38) seem to show the same tendency.
-%
-%An independent set of CPVs exhibits small dips roughly half a cycle
-%after large dips; it is tempting to label the small dips secondary
-%eclipses.  Such sources include TIC~402980664 (Sector 25; relative to
-%the sharpest, deepest minimum), TIC~89463560 (Sector 36),
-%TIC~224283342 (Sector 2), and TIC~442571495 (Sector 12).  For the
-%particular case of TIC~224283342, this observation, coupled with Gaia
-%DR3 radial velocities suggesting a radial velocity scatter exceeding
-%20\,\kms, suggests that the system could be a low-mass eclipsing
-%binary transiting a giant polar spot, analogous to TOI-3884
-%\citep{2022A&A...667L..11A}.
-%
-%In general however, it is challenging to interpret the significance of
-%the potential ``half-period regularities'';  the CPVs exhibit such a
-%wide range of variability that for seemingly any regularity one might
-%posit, it is easy to come up with counter-example objects which do not
-%follow the trend.  In other words, these half-cycle CPVs could simply
-%be a product of the human tendency to pattern match.
-
-\begin{figure}[!th]
-	\begin{center}
-		\centering
-		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f10a.pdf}
-		}
-
-		\vspace{-0.34cm}
-		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f10b.pdf}
-		}
-
-		\vspace{-0.34cm}
-		\subfloat{
-			\includegraphics[width=0.48\textwidth]{f10c.pdf}
-		}
-
-		\vspace{-0.1cm}
-		\caption{
-      {\bf The magnetic B star connection.}
-      $\sigma$~Ori~E and HD~345439 (top row) are magnetic B stars with
-      predominantly dipolar magnetic fields known to host
-      circumstellar plasma tori.  HD~37776 and HD~64740 (middle row)
-      are analogous magnetic B stars with field topologies potentially dominated by
-      high order multipoles.  The bottom row compares the latter
-      systems against the ``best-matching'' CPV light curves, selected
-      by eye from Figure~\ref{fig:cqvs}.  CPVs have light curves that
-      are visually similar to the topologically complex magnetic B
-      stars.  Stellar masses rounded to one significant figure are
-      given in the lower right of each panel; the star, TESS sector,
-      and period are listed in each subtitle.
-		}
-		\label{fig:bstar}
-	\end{center}
-\end{figure}
-
 \subsection{Mass flux estimate}
@@
 $\approx$10$^{21}$\,kg \citep{2019Icar..319..812P}.  A similar
-calculation that assumed occulting clupms of hydrogen, rather than
+calculation that assumed occulting clumps of hydrogen, rather than
 dust, derived gas prominence masses of at least $10^{14}$\,kg
@@
 one order of magnitude larger than the earlier estimate.
+
+\subsection{From dippers to debris disks}
+\label{subsec:discdippers}
+
+About one in three young stars with infrared-detected inner dusty
+disks show quasiperiodic or stochastic dimming over timescales of
+roughly one day \citep[e.g.][]{2010A&A...519A..88A,2010ApJS..191..389C}.  The dimming
+amplitudes can reach a few tenths of the stellar brightness, and dips
+with identical depths and phases rarely recur.  These ``dipper'' stars
+are probably explained by occulting circumstellar dust in the inner
+disk
+\citep[e.g.][]{2014AJ....147...82C,2016ApJ...816...69A,2021ApJ...908...16R,2022ApJS..263...14C}.
+While the phenomenon can persist beyond $\approx$10\,Myr
+\citep{2019MNRAS.488.4465G,2022MNRAS.514.1386G}, in all such cases it
+seems to be associated with the presence of infrared excesses.
+Phenomenologically, dippers are different from CPVs in that their dips
+are usually deeper, less periodic, and more variable in depth over
+timescales of only one or a few cycles.  Dipper stars also tend to be
+younger, since they tend to be classical T Tauri stars with infrared
+excesses.
+
+In identifying the two candidate CPVs with outlying SEDs
+(TICs~193136669 and TIC~57830249; Section~\ref{subsec:irexcess}), we
+were prompted to reconsider our light curve-based labeling, and
+ultimately concluded that these sources are dippers.  This episode
+suggests that there could be overlap between CPVs and dippers.  Taking
+TIC~57830249 as one example, the Sector~36 TESS data are suggestive of
+a CPV, with relatively periodic, sharp dips with depths of a few
+percent.  The Sector~10 data are completely different, varying in
+apparent flux by a factor of two, with no discernible periodicity at
+all.  Perhaps this source becomes a ``dipper'' when an inflow of dust
+reaches the inner disk wall, and is otherwise a ``CPV'' when the inner
+disk is starved of dust.
+
+Although TIC~57830249 is an intriguing outlier, the general picture is that
+stars without infrared excesses have more stable optical light curves
+than those with infrared excesses.  While some dippers may evolve into CPVs after the
+disk is mostly gone, this would be generically expected based on population
+statistics: young objects become old.  There may be no
+other causal connection between the two evolutionary stages.  With
+that said, a common mystery between the CPVs and dippers is how exactly
+the {\it narrowness} of their flux dimmings is produced.  
+A similar mechanism may operate for both
+types of object, tied perhaps to a shared magnetic topology, or
+perhaps to a preference for dust to inspiral to the star in clumped
+structures.
+
+%\subsection{Are half-cycles important?}
+%
+% NOTE to arxis readers: the answer was: "maybe in a few cases, but
+% this manuscript was already too long!".
+%
+%The interval of half a cycle period could be significant in the
+%context of CPVs for two reasons.  The first is that for material on a
+%circular orbit viewed edge-on, a half-cycle corresponds to the
+%interval between transit and secondary eclipse.  The second is that
+%the half-cycle also corresponds to the interval over which half of the
+%star's surface is visible.  Of the CPVs in Figures~\ref{fig:cqvs}
+%and~\ref{fig:evoln}, a fraction that seems greater than random might
+%exhibit a preference for showing dips or peaks that correspond to the
+%half-cycle interval.
+%
+%One set of CPVs shows ``CPV behavior'' (some form of dip complex), but
+%which only lasts for half of any given cycle.  TIC~206544316 (Sector
+%2) is a canonical example; TIC~405910546 (Sector 38), TIC~167664935
+%(Sector 38), TIC~146539195 (Sector 5), TIC~118449916 (Sector 44), and
+%TIC~312410638 (Sector 38) seem to show the same tendency.
+%
+%An independent set of CPVs exhibits small dips roughly half a cycle
+%after large dips; it is tempting to label the small dips secondary
+%eclipses.  Such sources include TIC~402980664 (Sector 25; relative to
+%the sharpest, deepest minimum), TIC~89463560 (Sector 36),
+%TIC~224283342 (Sector 2), and TIC~442571495 (Sector 12).  For the
+%particular case of TIC~224283342, this observation, coupled with Gaia
+%DR3 radial velocities suggesting a radial velocity scatter exceeding
+%20\,\kms, suggests that the system could be a low-mass eclipsing
+%binary transiting a giant polar spot, analogous to TOI-3884
+%\citep{2022A&A...667L..11A}.
+%
+%In general however, it is challenging to interpret the significance of
+%the potential ``half-period regularities'';  the CPVs exhibit such a
+%wide range of variability that for seemingly any regularity one might
+%posit, it is easy to come up with counter-example objects which do not
+%follow the trend.  In other words, these half-cycle CPVs could simply
+%be a product of the human tendency to pattern match.
+
+\begin{figure}[!th]
+	\begin{center}
+		\centering
+		\subfloat{
+			\includegraphics[width=0.48\textwidth]{f10a.pdf}
+		}
+
+		\vspace{-0.34cm}
+		\subfloat{
+			\includegraphics[width=0.48\textwidth]{f10b.pdf}
+		}
+
+		\vspace{-0.34cm}
+		\subfloat{
+			\includegraphics[width=0.48\textwidth]{f10c.pdf}
+		}
+
+		\vspace{-0.1cm}
+		\caption{
+      {\bf The magnetic B star connection.}
+      $\sigma$~Ori~E and HD~345439 (top row) are magnetic B stars with
+      predominantly dipolar magnetic fields known to host
+      circumstellar plasma tori.  HD~37776 and HD~64740 (middle row)
+      are analogous magnetic B stars with field topologies potentially dominated by
+      high order multipoles.  The bottom row compares the latter
+      systems against the ``best-matching'' CPV light curves, selected
+      by eye from Figure~\ref{fig:cqvs}.  CPVs have light curves that
+      are visually similar to the topologically complex magnetic B
+      stars.  Stellar masses rounded to one significant figure are
+      given in the lower right of each panel; the star, TESS sector,
+      and period are listed in each subtitle.
+		}
+		\label{fig:bstar}
+	\end{center}
+\end{figure}
 

### 2023-09-07 paper/ms.tex
update ms (ADU sugggestions)
Co-authored-by: Alexandre David-Uraz <adu@udel.edu>

@@
   hypothesis supported by correspondences between the light curves of
-  CPVs and of B stars known to have multipolar magnetic fields.
+  CPVs and of rapidly-rotating B stars known to have multipolar magnetic fields.
   %
@@
 
-The dust clump and gas prominence hypotheses are conceptually
-similar; one could imagine dust or gas accumulating in
-either of the geometries shown in Figure~\ref{fig:f1}.  The main
-distinguishing factor between the two models is the composition of the
-occulting material.   ``Dust clumps'' invoke opacity from dust, which
-would need to be collisionally charged \citep{2023MNRAS.518.4734S}.
-``Gas prominences'' invoke opacity from partially-ionized gas, likely
-bound-free transitions in hydrogen or perhaps a molecular opacity.
+While the dust clump and gas prominence hypotheses both invoke
+magnetically-entrained material, the two pictures differ in the origin
+and the composition of the occulting material.   ``Dust clumps''
+invoke opacity from dust, which would need to be collisionally charged
+\citep{2023MNRAS.518.4734S}; such dust might be sourced from a
+low-mass debris disk.  ``Gas prominences'' invoke opacity from
+partially-ionized gas, perhaps bound-free transitions in hydrogen or a
+molecular opacity.  The gas might be sourced from a stellar wind.
 Unambiguous evidence in support of either scenario has yet to be
@@
   \item At least three dips per cycle, or else otherwise
-    oddly-shaped dips.
-  %
-  \item Dip phases mostly repeat over $\approx$30\,day sector duration.
+    oddly-shaped dips relative to expectations for quasi-sinusoidal
+    starspot-induced modulation.
+  %
+  \item Persistent dips over multiple consecutive rotation cycles.
 \end{itemize}
@@
 for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
-distributions, and $\mathcal{T}(\mu, \sigma, a, b)$ a truncated normal
+distributions, and $\mathcal{T}_{\rm N}(\mu, \sigma, a, b)$ a truncated normal
 distribution with mean $\mu$, standard deviation $\sigma$, and lower
@@
 beating light curves, and with PDM periodograms that showed multiple
-periods.  We also attempted to disentangle the two signals by
-subtracting the mean CPV signal over each sector, and then repeating
-the phase-dispersion minimization analysis.  The results of this effort
-are summarized in the secondary periods, $P_{\rm sec}$, listed in
-Table~\ref{tab:thetable}, which we required to be at least 5\%
-different from the primary period.  This process yielded
-\ngoodmultperiodflag/\ngoods\ high-quality CPVs with secondary
-periods; \nmaybemultperiodflag/\nmaybes\ of the ambiguous sample met
-the same criterion.  Of the \ngoodhighruwe\ good CPVs with ${\rm
-RUWE}_{\rm DR3}> 2$, \ngoodruweandmultperiod\ also showed secondary
-periods in the TESS light curves.  Considering the weaker threshold of
-${\rm RUWE}_{\rm DR3}> 1.4$,
+periods.  In such cases, we attempted to disentangle the two signals
+by subtracting the mean CPV signal over each sector, and we then
+repeated the phase-dispersion minimization analysis.  The resulting
+secondary periods, $P_{\rm sec}$, are listed in
+Table~\ref{tab:thetable}; we required these to be at least 5\%
+different from the primary period, and for the majority of secondary
+signals the morphologies corresponded to starspot modulation.  This
+process yielded \ngoodmultperiodflag/\ngoods\ high-quality CPVs with
+secondary periods; \nmaybemultperiodflag/\nmaybes\ of the ambiguous
+sample met the same criterion.  Of the \ngoodhighruwe\ good CPVs with
+${\rm RUWE}_{\rm DR3}> 2$, \ngoodruweandmultperiod\ also showed
+secondary periods in the TESS light curves.  Considering the weaker
+threshold of ${\rm RUWE}_{\rm DR3}> 1.4$,
 \ngoodweakruweandmultperiod/\ngoodweakruwe\ such CPVs showed secondary
-TESS periods.
+TESS periods.  These results broadly suggest that the secondary
+periods are associated with physically-bound binary companions.
 
@@
 
-Both of the stars with IR exceses are in the TW Hydrae association
+Both of the stars with IR excesses are in the TW Hydrae association
 ($\approx$10\,Myr).  They have periods of 38\,hr and 44\,hr,
@@
 that both sources are dippers, not CPVs (see the online plots in
-Figure~\ref{fig:vet}).  For TIC~57830249, the Sector~10 light curve of
+Figure~\ref{fig:vet}).  For TIC~57830249, the Sector~10 light curve 
 shows completely different behavior from Sector~36, with variability
@@
       $\approx$1\,day.  The \ngoods\ bona fide CPVs in
-      Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
-      ambiguous CPV candidates are light blue circles.  Unresolved
-      binaries (red circles) are objects for which the Gaia DR3 radial velocity
+      Table~\ref{tab:thetable} are the dark blue dots; \nmaybes\
+      ambiguous CPV candidates are light blue dots.  Unresolved
+      binaries (red rings) are objects for which the Gaia DR3 radial velocity
       scatter exceeded 20\,\kms, or if Gaia ${\rm RUWE}_{\rm DR3}$$>$2
@@
 These observations are also in agreement with previous analyses of
-multi-periodic low-mass discovered by K2, which found that such
+multi-periodic low-mass objects discovered by K2, which found that such
 systems are almost always binaries
@@
 two years apart.  Such a baseline was available for 32 of the
-confirmed \ngoods\ CPVs in our catalog; for plotting purposes we show
+\ngoods\ confirmed CPVs in our catalog; for plotting purposes we show
 the brightest 27.  
@@
 duration over this five-month interval.  Other dips grow, like the one
-at $\phi = +0.06$ between cycles 1499 and 1481.  Other dips, such as
+at $\phi = +0.06$ between cycles 1458 and 1481.  Other dips, such as
 the one at $\phi = +0.12$ in cycles 1233-1264, disappear entirely.
@@
 an exponential return to the baseline flux, resembling the signatures
-of exocomet \citep[e.g.][]{2018MNRAS.474.1453R,2019A&A...625L..13Z},
+of exocomets \citep[e.g.][]{2018MNRAS.474.1453R,2019A&A...625L..13Z},
 and the outflowing exospheres of some transiting planets
@@
 corotation \citep{2005ApJ...630L..81T}.  The $\sigma$~Ori class is
-distinct from Be-star decretion disks, which do not have any obvious
-connection to the stellar magnetic field \citep{2013A&ARv..21...69R}.
+distinct from Be-star decretion disks, which are found to
+systematically not host detectable magnetic fields
+\citep{2013A&ARv..21...69R,2016ASPC..506..207W}.
 
@@
 \citep{2011ApJ...726...24K}.  The field geometry of HD~64740, while
-potentially less extreme, is also less well-studied
-\citep[see][Ch.~4]{1988PhDT........53B}.  Recent TESS light curves
+potentially less extreme, also shows evidence for a non-dipolar contribution
+\citep{2018MNRAS.475.5144S}.
+Recent TESS light curves
 of these two B stars appear surprisingly similar to the CPV light
@@
 
-The physical similarity between the B stars and the M dwarfs
-presumably has its origin in the existence of a ``centrifugal
-magnetosphere'' \citep[see][]{2013MNRAS.429..398P}.  In other words,
-both classes of objects probably satisfy the condition $R_{\rm m} >
-R_{\rm c}$, for $R_{\rm m}$ the magnetosphere radius (sometimes called
-the Alfv\'en radius).  Provided that charged particles are confined to
-move along magnetic field lines, stable points that balance the
-centrifugal force and gravity can then exist at the corotation radius
-\citep[e.g.][]{2005MNRAS.357..251T}.  In the converse ``dynamical''
-case, when $R_{\rm m} < R_{\rm c}$, material interior to the
-magnetospheric radius returns to the stellar surface over the
-free-fall timescale.  A simple estimate assuming a dipole field with
-$B_0\approx1\,{\rm kG}$ at the star's surface, a local plasma number
-density $n\approx10^9\,{\rm cm^{-3}}$, and a plasma temperature
-$10^6\,{\rm K}$ gives magnetospheric radii of order a few times the
-corotation radii, $R_{\rm c}$.  This suggests that the existence of a
-centrifugal magnetosphere is plausible for young, rapidly rotating M
-dwarfs.
+The physical similarity between the B stars and the M dwarfs could
+have its origin in the existence of a ``centrifugal magnetosphere''
+\citep[see][]{2013MNRAS.429..398P}.  In other words, both classes of
+objects might satisfy the condition $R_{\rm m} > R_{\rm c}$, for
+$R_{\rm m}$ the magnetosphere radius (sometimes called the Alfv\'en
+radius).  Provided that charged particles are confined to move along
+magnetic field lines, material can then build up at the corotation
+radius \citep[see][Sec.~4, and references
+therein]{2015SSRv..191..339R}.  In the converse ``dynamical'' case,
+when $R_{\rm m} < R_{\rm c}$, material interior to the magnetospheric
+radius returns to the stellar surface over the free-fall timescale.  A
+simple estimate assuming a dipole field with $B_0\approx1\,{\rm kG}$
+at the star's surface, a local plasma number density
+$n\approx10^9\,{\rm cm^{-3}}$, and a plasma temperature $10^6\,{\rm
+K}$ gives magnetospheric radii of order a few times the corotation
+radii, $R_{\rm c}$.  This suggests that the existence of a centrifugal
+magnetosphere is plausible for young, rapidly rotating M dwarfs.
 
@@
 
+\vspace{-2pt}
 \begin{enumerate}[leftmargin=*]
+	  \setlength\itemsep{-2pt}
 %
@@
 %
-    \item The CPV peaks and dips evolve over timescales that are both secular
-      ($\approx$100\,cycles) and impulsive ($<$1 cycle).  Dip growth seems
-      to happen over durations of at least ten cycles, and slow dip
-      decay can also occur.  ``State-switches'' correspond to dips 
-      collapsing instantaneously, and
-      occur once every few months for
-      both LP~12-502 and TIC~300651846.
-      They are almost always linked with
-      observed optical flares.  Such switches are suggestive of
-      magnetic reconnection opening the ``magnetic cage'' that traps
-      the dust.
+    \item The CPV peaks and dips evolve over timescales that are both
+      secular ($\approx$100\,cycles) and impulsive ($<$1 cycle).  Dip
+      growth seems to happen over durations of at least ten cycles,
+      and slow dip decay can also occur.  ``State-switches''
+      correspond to dips collapsing instantaneously, and occur once
+      every few months for both LP~12-502 and TIC~300651846.  They are
+      almost always linked with observed optical flares.  Such
+      switches are suggestive of magnetic reconnection opening the
+      ``magnetic cage'' that traps the dust.
+%
+	\item The detailed morphology changes exhibited by LP~12-502
+	during its state-switches (e.g.\ Figure~\ref{fig:lp}, cycles 1233-1264)
+	imply that the flux dips are additive and independent.
 %
@@
 
-On the theoretical front, building a physical understanding what sets
+On the theoretical front, building a physical understanding of what sets
 the characteristic size scale of the clumping material would help
@@
 Sector 53). 
+ADU acknowledges support by NASA under award number 80GSFC21M0002, as
+well as ROSES award 22-ADAP22-0070.
 
@@
 LR cross-examined the light curve classification, and contributed an independent SED analysis.
-AD identified the magnetic B star connection.
+ADU identified the magnetic B star connection.
 LAH contributed to project design and to the interpretation of the light curves.
@@
 pre-main-sequence M dwarfs.  Empirical evidence however suggests that
-cool spots dominate the the optical variability of disk-free
+cool spots dominate the optical variability of disk-free
 pre-main-sequence stars.  This evidence includes flux excursions
@@
 one minute.  Between 2020 and 2021, we observed 10 CPVs at 20-second
-cadence with TESS in order to explore this question (TESS DDT029; PI L.~Bouma).
-The stars were TICs 142173958, 146539195, 24518895, 276453848,
-264599508, 363963079, 144486786, 408188366, 300651846, 262400835.
-These sources were selected from CPVs known at the time to have short
-periods and sharp features when observed at 2-minute cadence.
-Comparing the 20-second to 2-minute data for these stars (data
-available on MAST), we concluded that these CPVs did not contain
-appreciable power at timescales shorter than a few minutes.
+cadence with TESS in order to explore this question (TESS DDT029; PI
+L.~Bouma).  The stars were TICs 142173958, 146539195, 24518895,
+276453848, 264599508, 363963079, 144486786, 408188366, 300651846,
+262400835.  These sources were selected from CPVs known at the time to
+have short periods and sharp features when observed at 2-minute
+cadence.  Comparing the 20-second to 2-minute data for these stars
+(data available on MAST), we concluded that these CPVs did not contain
+appreciable power at timescales shorter than a few minutes, other than
+the usual flaring.  This is consistent with the expected few-minute
+ingress and egress timescales for transiting circumstellar material.
 

### 2023-09-07 paper/ms.tex
update ms

@@
   hypothesis supported by correspondences between the light curves of
-  CPVs and of rapidly-rotating B stars known to have multipolar magnetic fields.
+  CPVs and of rapidly rotating B stars known to have multipolar magnetic fields.
   %
@@
 Section~\ref{subsec:starprops}.  Thus, the shortest-duration dips
-could be produced by transits of bodies or distributions of material
+are likely produced by transits of bodies or distributions of material
 that are smaller than the star.  The corotation radius corresponds to
@@
 \subsection{Strengthening the magnetic B star connection}
+\label{subsec:bstardisc}
 
@@
 magnetic field lines, material can then build up at the corotation
-radius \citep[see][Sec.~4, and references
+radius \citep[e.g.][Sec.\ 4, and references
 therein]{2015SSRv..191..339R}.  In the converse ``dynamical'' case,
@@
 less certain, and \ndebunked\ impostors.  We inferred ages for all but
-two of the \nallcands\ objects based on memberships in young stellar assocations; we
+two of the \nallcands\ objects based on memberships in young stellar associations; we
 also derived temperatures and radii using SED fitting, and 
@@
       P_{\rm rot} / (\pi a)$ (see Section~\ref{subsec:lplessons}).
-      Such dips may therefore be produced by transits of bodies or
+      Such dips are therefore likely produced by transits of bodies or
       distributions of optically-thick material that are smaller than
@@
       on a quasi-sinusoidal signal that presumably originates from
-      inhomogeneities in the stellar surface brightness
-      distribution (starspots and faculae).  The
+      starspots and faculae on the stellar surface.  The
       only viable explanation currently known for sharp dips being superposed on
@@
       and slow dip decay can also occur.  ``State-switches''
-      correspond to dips collapsing instantaneously, and occur once
-      every few months for both LP~12-502 and TIC~300651846.  They are
-      almost always linked with observed optical flares.  Such
-      switches are suggestive of magnetic reconnection opening the
-      ``magnetic cage'' that traps the dust.
+      correspond to dips collapsing instantaneously;  they occur once
+      every few months for both LP~12-502 and TIC~300651846.
+      State-switches are almost always linked with observed optical
+      flares.  Such switches are suggestive of magnetic reconnection
+      opening the ``magnetic cage'' that traps the dust.
 %
@@
 %
-    \item The on-off duty cycle for CPVs seems to be $\approx$$75$\%, based
+    \item The on-off duty cycle for CPVs is $\approx$$75$\%, based
       on the fraction of bona fide CPVs that either turned on or turned
@@
       200\,Myr, based on the one CPV we found in the Carina Near
-      moving group (TIC~294328887; $\approx$200\,Myr).  However the
+      moving group (TIC~294328887; $\approx$200\,Myr).  The
       lack of detected CPVs in the Hyades and Praesepe suggests that
@@
       TIC~405910546, have masses that appear to exceed the M dwarf
-      limit.  However both are potentially binaries, and this may
+      limit.  Both are potentially binaries, and this may
       confuse our ability to accurate identify the source of the CPV
@@
 %
-    \item The closest CPVs to the Sun are at distances of 15-20\,pc,
-      and the brightest have $V$$\approx$12 ($J$$\approx$7.5).  We
-      have found most of them in this work, since our CPV sample was
+    \item The closest CPVs to the Sun are at distances of 15-20\,pc;
+      the brightest have $V$$\approx$12 ($J$$\approx$7.5).  We
+      have found most of the close exemplars in this work, since our CPV sample was
       $\gtrsim$80\% complete within 30\,pc.  The lack of CPVs in the
@@
 %
-    \item Surprising analogs to the CPVs exist in two magnetic B stars,
+    \item Surprising analogs to CPVs exist in two magnetic B stars,
       one of which is known to have an extreme multipolar field
-      topology.  Since most magnetic B stars have dipolar magnetic
-      fields \citep{2009ARA&A..47..333D}, this suggests that the CPV
+      topology (Section~\ref{subsec:bstardisc}).  Since most magnetic
+      B stars have dipolar magnetic fields, this suggests that the CPV
       dips and warps are similarly being sculpted by the stellar

### 2023-09-07 paper/ms.tex
update ms

@@
   %
-  Complex periodic variables (CPVs) are stars that exhibit sharp and
-  periodic optical light curves.  Previous studies have indicated that
-  these stars are typically disk-free pre-main-sequence M dwarfs with
-  rotation periods ranging from 0.2 to 2 days.  To advance our
-  understanding of these enigmatic objects, we conducted a blind
-  search using TESS 2-minute data of \nstarssearched\ K and M dwarfs
-  with $T$$<$16 and $d$$<$150\,pc.  We found \ngoods\ high-quality
-  CPVs, and subsequently determined that most are members
-  of stellar associations.  Among the new discoveries are the
-  brightest ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and
-  oldest ($\approx$200\,Myr) CPVs known.  One exceptional object, LP
-  12-502, exhibited up to eight flux dips per cycle. Some of these
+  Complex periodic variables (CPVs) are stars that exhibit 
+  highly structured and periodic optical light curves.  Previous
+  studies have indicated that these stars are typically disk-free
+  pre-main-sequence M dwarfs with rotation periods ranging from 0.2 to
+  2 days.  To advance our understanding of these enigmatic objects, we
+  conducted a blind search using TESS 2-minute data of
+  \nstarssearched\ K and M dwarfs with $T$$<$16 and $d$$<$150\,pc.  We
+  found \ngoods\ high-quality CPVs, and subsequently determined that
+  most are members of stellar associations.  Among the new discoveries
+  are the brightest ($T$$\approx$9.5), closest ($d$$\approx$20\,pc),
+  and oldest ($\approx$200\,Myr) CPVs known.  One exceptional object,
+  LP 12-502, exhibited up to eight flux dips per cycle. Some of these
   dips coexisted with slightly different periods, and the
-  shortest-duration LP 12-502 dips precisely matched the expected
+  shortest-duration dips precisely matched the expected
   timescale for transiting small bodies at the corotation radius.
@@
   hypothesis supported by correspondences between the light curves of
-  CPVs and of rapidly rotating B stars known to have multipolar magnetic fields.
+  CPVs and of rapidly rotating B stars known to have multipolar
+  magnetic fields.
   %
@@
 beating light curves, and with PDM periodograms that showed multiple
-periods.  In such cases, we attempted to disentangle the two signals
-by subtracting the mean CPV signal over each sector, and we then
+periods.  For such cases, we then
+subtracted the mean CPV signal over each sector, and 
 repeated the phase-dispersion minimization analysis.  The resulting
@@
 Table~\ref{tab:thetable}; we required these to be at least 5\%
-different from the primary period, and for the majority of secondary
-signals the morphologies corresponded to starspot modulation.  This
+different from the primary period.  The majority of secondary
+signals showed morphologies corresponding to starspot modulation.  This
 process yielded \ngoodmultperiodflag/\ngoods\ high-quality CPVs with
@@
 \ngoodweakruweandmultperiod/\ngoodweakruwe\ such CPVs showed secondary
-TESS periods.  These results broadly suggest that the secondary
-periods are associated with physically-bound binary companions.
+TESS periods.  The latter results strongly suggest that the secondary
+periods are associated with bound binary companions.
 
@@
 binarity information into a single bitwise column.  
-We present detailed results concerning binarity in
-Section~\ref{subsec:resultsbinarity}, and a summary discussion in
+We describe detailed results concerning binarity in
+Section~\ref{subsec:resultsbinarity}, and summarize those results
 Section~\ref{subsec:discbinary}.
@@
 assigned masses of $\approx$0.82\,$M_\odot$ and
-$\approx$0.60\,$M_\odot$ respectively.  The next-highest masses in our
-sample are $\approx$0.40\,$M_\odot$.
-
-These stars' locations in color--absolute magnitude diagrams and their
-probable membership in Lower Centaurus Crux both support the
-conclusion that they have relatively high masses.  However in detail,
-both are subject to ambiguities in interpretation.  The TIC~405910546
-light curve has a unique shape, suggestive of an eclipsing binary.
-Independently, TIC~405910546 was one of only \nrvscatterflag\ CPVs
-flagged with a Gaia DR3 radial velocity scatter exceeding 20\,\kms.
-Combined, these factors suggest that TIC~405910546 could be a
-pre-main-sequence eclipsing binary; it should be studied further to
-clarify this classification.
+$\approx$0.60\,$M_\odot$ respectively.  The next-highest mass in our
+sample belongs to TIC~59836633 ($\approx$0.48\,$M_\odot$), with all
+remaining CPVs having masses $\lesssim$0.40\,$M_\odot$.
+
+The locations of TIC~405754448 and TIC~405910546 in color--absolute
+magnitude diagrams, combined with their probable membership in Lower
+Centaurus Crux, support the conclusion that these stars have
+relatively high masses.  However in detail, both objects are subject
+to ambiguities in interpretation.  The TIC~405910546 light curve has a
+unique shape, suggestive of an eclipsing binary.  Independently,
+TIC~405910546 was one of only \nrvscatterflag\ CPVs flagged with a
+Gaia DR3 radial velocity scatter exceeding 20\,\kms.  Combined, these
+factors suggest that TIC~405910546 could be a pre-main-sequence
+eclipsing binary; it should be studied further to clarify this
+classification.
 
@@
     \item The detailed morphology changes exhibited by LP~12-502
-	during its state-switches (e.g.\ Figure~\ref{fig:lp}, cycles 1233-1264)
-	imply that the flux dips are additive and independent.
+      during its state-switches (e.g.\ Figure~\ref{fig:lp}, cycles
+      1233-1264) imply that the flux dips are additive and
+      independent.
 %
@@
       200\,Myr, based on the one CPV we found in the Carina Near
-      moving group (TIC~294328887; $\approx$200\,Myr).  The
-      lack of detected CPVs in the Hyades and Praesepe suggests that
-      the lifetime of the phenomenon is limited to the first few
-      hundred million years.
-%
-    \item Most CPVs are M dwarfs with masses
-      0.1-0.5\,$M_\odot$.  Two sources, TIC~405754448 and
-      TIC~405910546, have masses that appear to exceed the M dwarf
-      limit.  Both are potentially binaries, and this may
-      confuse our ability to accurate identify the source of the CPV
-      signal (Section~\ref{subsec:massive}).  We encourage additional
+      moving group (TIC~294328887; $\approx$200\,Myr).  The lack of
+      detected CPVs in the Hyades and Praesepe suggests that the
+      lifetime of the phenomenon is limited to the first few hundred
+      million years.
+%
+    \item Most CPVs are M dwarfs with masses 0.1-0.4\,$M_\odot$.
+    Two sources, TIC~405754448 and
+      TIC~405910546, have masses that appear to exceed 0.5\,$M_\odot$.
+      Both are potentially binaries, and this may confuse our ability
+      to accurate identify the source of the CPV signal
+      (Section~\ref{subsec:massive}).  We encourage additional
       scrutiny of these objects in future work.

### 2023-09-08 paper/ms.tex
clean up latex; stage table CSV files and readme

@@
 \affiliation{\princeton}
-%
-%\author{-----SUGGESTED CONTRIBUTORS, PENDING DISCUSSION, COMMENTS, ANALYSES, ETC-----}
-%%
-%
-%\author[0000-0002-3164-9086]{Maximilian N. G\"unther}
-%\affiliation{\esa}
-%
-%\author[0000-0003-2058-6662]{George~R.~Ricker}
-%\affiliation{\mitkavli}
 
@@
   %
-  Complex periodic variables (CPVs) are stars that exhibit 
-  highly structured and periodic optical light curves.  Previous
-  studies have indicated that these stars are typically disk-free
-  pre-main-sequence M dwarfs with rotation periods ranging from 0.2 to
-  2 days.  To advance our understanding of these enigmatic objects, we
-  conducted a blind search using TESS 2-minute data of
-  \nstarssearched\ K and M dwarfs with $T$$<$16 and $d$$<$150\,pc.  We
-  found \ngoods\ high-quality CPVs, and subsequently determined that
-  most are members of stellar associations.  Among the new discoveries
-  are the brightest ($T$$\approx$9.5), closest ($d$$\approx$20\,pc),
-  and oldest ($\approx$200\,Myr) CPVs known.  One exceptional object,
-  LP 12-502, exhibited up to eight flux dips per cycle. Some of these
+  Complex periodic variables (CPVs) are stars that exhibit highly
+  structured and periodic optical light curves.  Previous studies have
+  indicated that these stars are typically disk-free pre-main-sequence
+  M dwarfs with rotation periods ranging from 0.2 to 2 days.  To
+  advance our understanding of these enigmatic objects, we conducted a
+  blind search using TESS 2-minute data of \nstarssearched\ K and M
+  dwarfs with $T$$<$16 and $d$$<$150\,pc.  We found \ngoods\
+  high-quality CPVs, and subsequently determined that most are members
+  of stellar associations.  Among the new discoveries are the
+  brightest ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and
+  oldest ($\approx$200\,Myr) CPVs known.  One exceptional object, LP
+  12-502, exhibited up to eight flux dips per cycle. Some of these
   dips coexisted with slightly different periods, and the
-  shortest-duration dips precisely matched the expected
-  timescale for transiting small bodies at the corotation radius.
-  Broadly, our search confirms that CPVs are mostly young
-  ($\lesssim$150\,Myr) and low-mass ($\lesssim$0.4\,$M_\odot$).  The
-  flux dips characteristic of the class have lifetimes of $\approx$100
-  cycles, although stellar flares seem to induce sudden dip collapse
-  once every few months.  The most plausible explanation for these
-  phenomena remains corotating concentrations of gas or dust.  The gas
-  or dust is probably entrained by the star's magnetic field, and the
-  sharp features could result from a multipolar field topology, a
-  hypothesis supported by correspondences between the light curves of
-  CPVs and of rapidly rotating B stars known to have multipolar
-  magnetic fields.
+  shortest-duration dips precisely matched the expected timescale for
+  transiting small bodies at the corotation radius.  Broadly, our
+  search confirms that CPVs are mostly young ($\lesssim$150\,Myr) and
+  low-mass ($\lesssim$0.4\,$M_\odot$).  The flux dips characteristic
+  of the class have lifetimes of $\approx$100 cycles, although stellar
+  flares seem to induce sudden dip collapse once every few months.
+  The most plausible explanation for these phenomena remains
+  corotating concentrations of gas or dust.  The gas or dust is
+  probably entrained by the star's magnetic field, and the sharp
+  features could result from a multipolar field topology, a hypothesis
+  supported by correspondences between the light curves of CPVs and of
+  rapidly rotating B stars known to have multipolar magnetic fields.
   %
@@
 for which the root cause of variability is only beginning to become
-clear: complex periodic variables (CPVs).  These objects are identified from
-their optical light curves, which show nearly periodic troughs that
-are either sharp or broad; these troughs are often superposed on
-quasi-sinusoidal spot-like modulation
+clear: complex periodic variables (CPVs).  These objects are
+identified from their optical light curves, which show nearly periodic
+troughs that are either sharp or broad; these troughs are often
+superposed on quasi-sinusoidal spot-like modulation
 \citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z}.
@@
 physical scenario, we discard the ``starspot-only'' scenario.
-Instead, the correct explanation probably involves spatially concentrated
-circumstellar material
+Instead, the correct explanation probably involves spatially
+concentrated circumstellar material
 \citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.
@@
 periodically transit the star
-\citep[e.g.][]{2017AJ....153..152S,2017MNRAS.471L.145F,2023MNRAS.518.4734S}.  The second scenario
-invokes ``prominences'', long-lived condensations of cool, dense,
-marginally-ionized gas that are embedded within the hotter corona and
-that corotate with the star
+\citep[e.g.][]{2017AJ....153..152S,2017MNRAS.471L.145F,2023MNRAS.518.4734S}.
+The second scenario invokes ``prominences'', long-lived condensations
+of cool, dense, marginally-ionized gas that are embedded within the
+hotter corona and that corotate with the star
 \citep{1989MNRAS.238..657C,2019MNRAS.482.2853J,2022MNRAS.514.5465W}.
@@
 at distances of a few stellar radii.  A final possibility is that an
-optically-thick ring obscures a narrow band of the stellar
-photosphere \citep{2019ApJ...876..127Z}; hot spots passing behind
-such a ring could produce sudden dips.  We disfavor this scenario
-for reasons described in Appendix~\ref{app:ring}.
+optically-thick ring obscures a narrow band of the stellar photosphere
+\citep{2019ApJ...876..127Z}; hot spots passing behind such a ring
+could produce sudden dips.  We disfavor this scenario for reasons
+described in Appendix~\ref{app:ring}.
 
@@
 In both models, the corotation radius is the location at which matter
-concentrates.  The empirical basis for this is that
-the sharp CPV features are superposed over smooth, quasi-sinusoidal
-starspot profiles.  The theoretical importance of the corotation
-radius has been noted in previous studies of magnetic rotators
+concentrates.  The empirical basis for this is that the sharp CPV
+features are superposed over smooth, quasi-sinusoidal starspot
+profiles.  The theoretical importance of the corotation radius has
+been noted in previous studies of magnetic rotators
 \citep[e.g.][]{1973ApJ...184..271L,1985Ap&SS.116..285N,1991ApJ...370L..39K,2005ApJ...634.1214L}.
-%
-%including neutron stars \citep[e.g.]{1973ApJ...184..271L}, magnetic
-%massive stars \citep[e.g.][]{1985Ap&SS.116..285N}, and accreting T
-%Tauri stars \citep[e.g.][]{2005ApJ...634.1214L}.  
-%
 In regions where the magnetic field dominates the flow (i.e.~$B^2/8\pi
-> \rho v^2 /2$), matter is dragged along with the field lines.  
-Within such regions, charged gas or dust can become trapped at corotation because
-of the four relevant forces -- gravity, Lorentz, inertial
+> \rho v^2 /2$), matter is dragged along with the field lines.  Within
+such regions, charged gas or dust can become trapped at corotation
+because of the four relevant forces -- gravity, Lorentz, inertial
 Coriolis, and inertial centrifugal -- the Lorentz and Coriolis only
@@
 
-While theoretical heritage for understanding magnetic
-rotators exists, CPVs have remained mysterious because they have been both
-hard to discover and hard to characterize.   They have been hard to discover
+While theoretical heritage for understanding magnetic rotators exists,
+CPVs have remained mysterious because they have been both hard to
+discover and hard to characterize.   They have been hard to discover
 because they are rare: CPVs comprise $\approx$1\% of the youngest
@@
 
-We searched for CPVs by analyzing the short-cadence data acquired
-by TESS between 2018 July 25 and 2022 September 1 (Sectors 1-55).
+We searched for CPVs by analyzing the short-cadence data acquired by
+TESS between 2018 July 25 and 2022 September 1 (Sectors 1-55).
 Specifically, we used the 2-minute cadence light curves produced by
@@
 these sectors also included full frame images with cadences of 10 and
-30 minutes for a larger number of sources, we restricted our
-attention to the 2-minute data for the sake of uniformity and
-simplicity in data handling.  In exchange, we sacrificed both
-completeness and homogeneity of the selection function.  While TESS
-cumulatively observed $\approx$90\% of the sky for at least one lunar
-month between 2018 July and 2022 September, the 2-minute cadence
-data were collected for only a subset of observable stars that were
-preferentially nearby and bright \citep[see][]{2021PASP..133i5002F}.
-The total 2-minute data volume
-from Sectors 1-55 included 1{,}087{,}475 short-cadence light curves, which were
-available for 428{,}121 unique stars.
+30 minutes for a larger number of sources, we restricted our attention
+to the 2-minute data for the sake of uniformity and simplicity in data
+handling.  In exchange, we sacrificed both completeness and
+homogeneity of the selection function.  While TESS cumulatively
+observed $\approx$90\% of the sky for at least one lunar month between
+2018 July and 2022 September, the 2-minute cadence data were collected
+for only a subset of observable stars that were preferentially nearby
+and bright \citep[see][]{2021PASP..133i5002F}.  The total 2-minute
+data volume from Sectors 1-55 included 1{,}087{,}475 short-cadence
+light curves, which were available for 428{,}121 unique stars.
+
 % latter stats from MERGED_spoc2min_sector1_to_sector58.csv
 
-To simplify our search, we defined our target sample as
-stars with 2-minute cadence TESS light curves satisfying the
-following four conditions:
+To simplify our search, we defined our target sample as stars with
+2-minute cadence TESS light curves satisfying the following four
+conditions:
 \begin{align}
@@
 For stars with multiple sectors of TESS data available, we searched
-for CPV signals independently.
-In total, our \nstarssearched\ star target list included \nlcssearched\ month-long light
-curves.
+for CPV signals independently.  In total, our \nstarssearched\ star
+target list included \nlcssearched\ month-long light curves.
 
@@
 the number of stars with TESS Sector 1-55 short-cadence data against
-the number of Gaia DR2 point sources.
-We required all stars to meet conditions~\ref{eq:one}--\ref{eq:four}.
-The results are shown in Figure~\ref{fig:completeness}.
-TESS 2-minute data exist for $\approx$50\%
-of $T$$<$16 M and late-K dwarfs at $\approx$50\,pc.
+the number of Gaia DR2 point sources.  We required all stars to meet
+conditions~\ref{eq:one}--\ref{eq:four}.  The results are shown in
+Figure~\ref{fig:completeness}.  TESS 2-minute data exist for
+$\approx$50\% of $T$$<$16 M and late-K dwarfs at $\approx$50\,pc.
 Within 20\,pc, $\gtrsim$80\% of the $T$$<$16 M and late-K dwarfs have
-at least one sector of short-cadence data.
-Beyond 100\,pc, $\lesssim$10\% of such stars have any short-cadence
-data available.
+at least one sector of short-cadence data.  Beyond 100\,pc,
+$\lesssim$10\% of such stars have any short-cadence data available.
 This can be translated into our sensitivity for the lowest mass stars
@@
 		\caption{
-			{\bf Completeness of the TESS 2-minute data for late-K
-      and early M dwarfs near the Sun, from Sectors 1-55.}  
-      The orange dotted curve shows the number of stars in successive
-      radial shells, each with a width of 10\,pc.  To be part of our selection function,
-      these stars must meet the following conditions: they must be red dwarf
-      stars
-      ($\bprp$>$1.5$; $M_{\rm G}$>4) amenable for TESS
-      observations ($T$<16).  The blue solid curve shows the fraction
-      of such stars with at least one sector of TESS 2-minute cadence
-      data acquired between Sectors 1-55.
+      {\bf Completeness of the TESS 2-minute data for late-K and early
+      M dwarfs near the Sun, from Sectors 1-55.}  The orange dotted
+      curve shows the number of stars in successive radial shells,
+      each with a width of 10\,pc.  To be part of our selection
+      function, these stars must meet the following conditions: they
+      must be red dwarf stars ($\bprp$>$1.5$; $M_{\rm G}$>4) amenable
+      for TESS observations ($T$<16).  The blue solid curve shows the
+      fraction of such stars with at least one sector of TESS 2-minute
+      cadence data acquired between Sectors 1-55.
 		}
@@
 \citep{2016AJ....152..114R,2017AJ....153..152S,2023ApJ...945..114P},
-or by flagging light curves with short periods and 
-strong Fourier harmonics for visual inspection
-\citep{2019ApJ...876..127Z}.  In this work, we implemented a new
-search approach based on counting the number of sharp local minima in
-phase-folded light curves, while also using the Fourier approach.  We
-applied these two search techniques independently to our
-\nstarssearched\ targets.
+or by flagging light curves with short periods and strong Fourier
+harmonics for visual inspection \citep{2019ApJ...876..127Z}.  In this
+work, we implemented a new search approach based on counting the
+number of sharp local minima in phase-folded light curves, while also
+using the Fourier approach.  We applied these two search techniques
+independently to our \nstarssearched\ targets.
 
@@
 For our dip-counting pipeline, we began with the {\tt PDC\_SAP} light
-curves for each sector \citep{2017ksci.rept....8S}, removed non-zero quality flags, and normalized
-the light curve by dividing out its median value.  We then flattened
-the light curve using a 5-day sliding median filter, as implemented in
-\texttt{wotan} \citep{2019AJ....158..143H}.  We computed a periodogram
-of the resulting cleaned and flattened light curve, opting for the
+curves for each sector \citep{2017ksci.rept....8S}, removed non-zero
+quality flags, and normalized the light curve by dividing out its
+median value.  We then flattened the light curve using a 5-day sliding
+median filter, as implemented in \texttt{wotan}
+\citep{2019AJ....158..143H}.  We computed a periodogram of the
+resulting cleaned and flattened light curve, opting for the
 \citet{1978ApJ...224..953S} phase dispersion minimization (PDM)
@@
 required it to have a width of at least $0.02\,P$, and a height of at
-least twice the noise level.  The noise level was defined
-as the 68$^{\rm th}$ percentile of the distribution of the residuals
-from the median value of $\delta f_i \equiv f_i - f_{i+1}$, where $f$
-is the flux and $i$ is an index over time.
-In panel {\it (e)} of Figure~\ref{fig:vet}, automatically-identified
-local minima are shown with the gray triangles.
+least twice the noise level.  The noise level was defined as the
+68$^{\rm th}$ percentile of the distribution of the residuals from the
+median value of $\delta f_i \equiv f_i - f_{i+1}$, where $f$ is the
+flux and $i$ is an index over time.  In panel {\it (e)} of
+Figure~\ref{fig:vet}, automatically-identified local minima are shown
+with the gray triangles.
 
@@
 CPVs, while also being able to consistently reject common false
-positives such as spot-induced variability and
-eclipsing binaries.
-
-In short, CPV candidates were identified by requiring a peak PDM period
-below two days and the presence of at least three sharp local minima,
-based on at least one sector of the TESS 2-minute data. Candidates
-were then inspected visually as described in
+positives such as spot-induced variability and eclipsing binaries.
+
+In short, CPV candidates were identified by requiring a peak PDM
+period below two days and the presence of at least three sharp local
+minima, based on at least one sector of the TESS 2-minute data.
+Candidates were then inspected visually as described in
 Section~\ref{subsec:visual}.
@@
 CPV, RS CVn, and cataclysmic variable).
-%Whenever a CPV was identified, the light curves from
-%multiple sectors were stitched together and analyzed jointly, for a
-%more accurate period determination.
 
@@
       {\bf Validation plots used to classify CPVs}.  The complete figure
-      set, with one image per sector for each of the \nallcands\
-      objects in Table~\ref{tab:thetable} is available in the online
-      journal. {\bf For internal collaboration review:
+      set  is available in the online journal and contains one image per sector for each of the \nallcands\
+      objects in Table~\ref{tab:thetable}.
+      {\bf For internal collaboration review:
       \url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
@@
   %
-  \item At least three dips per cycle, or else otherwise
-    oddly-shaped dips relative to expectations for quasi-sinusoidal
+  \item At least three dips per cycle, or else otherwise oddly-shaped
+    dips relative to expectations for quasi-sinusoidal
     starspot-induced modulation.
@@
 techniques were eclipsing binaries, ordinary spotted rapid rotators,
-and light curves that were complex due to multiple stars contributing to the
-photometric aperture.  Our specialized dip-counting pipeline flagged
-\nuniqdipflagged\ unique stars for visual inspection; about 20\% were
-subsequently labeled either good or possible CPVs.  From the more
-general Fourier pipeline, $\approx$0.5\% of stars that passed the
+and light curves that were complex due to multiple stars contributing
+to the photometric aperture.  Our specialized dip-counting pipeline
+flagged \nuniqdipflagged\ unique stars for visual inspection; about
+20\% were subsequently labeled either good or possible CPVs.  From the
+more general Fourier pipeline, $\approx$0.5\% of stars that passed the
 12-$\sigma$ peak threshold were eventually classified as CPVs.
@@
 analytically marginalizes over the radial velocity dimension.  The
-probabilities returned by this procedure are qualitatively helpful, but
-should be interpreted with caution because the assumption of Gaussian
-distributions is questionable for most groups within the solar
-neighborhood \citep[see e.g.][Figure~10]{2021ApJ...917...23K}.
+probabilities returned by this procedure are qualitatively helpful,
+but should be interpreted with caution because the assumption of
+Gaussian distributions is questionable for most groups within the
+solar neighborhood \citep[see e.g.][Figure~10]{2021ApJ...917...23K}.
 
@@
 companions.\footnote{\url{https://github.com/adamkraus/Comove}, git
-commit \texttt{278b372}}
-Finally, to provide a base for comparison, we also ran the
-BANYAN\,$\Sigma$ membership analysis on our entire \nstarssearched\
-target star sample.
+commit \texttt{278b372}} Finally, to provide a base for comparison, we
+also ran the BANYAN\,$\Sigma$ membership analysis on our entire
+\nstarssearched\ target star sample.
 
@@
 for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
-distributions, and $\mathcal{T}_{\rm N}(\mu, \sigma, a, b)$ a truncated normal
-distribution with mean $\mu$, standard deviation $\sigma$, and lower
-and upper bounds $a$ and $b$.  We validated our chosen upper bound on
-$A_{\rm V}$ using a 2MASS color-color diagram.  Finally, using
-\texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we sampled
-the posterior probability assuming the default Gaussian likelihood,
-and set a stopping threshold of ${\rm d}\log \mathcal{Z} < 0.01$,
-where $\mathcal{Z}$ denotes the evidence.
+distributions, and $\mathcal{T}_{\rm N}(\mu, \sigma, a, b)$ a
+truncated normal distribution with mean $\mu$, standard deviation
+$\sigma$, and lower and upper bounds $a$ and $b$.  We validated our
+chosen upper bound on $A_{\rm V}$ using a 2MASS color-color diagram.
+Finally, using \texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we
+sampled the posterior probability assuming the default Gaussian
+likelihood, and set a stopping threshold of ${\rm d}\log \mathcal{Z} <
+0.01$, where $\mathcal{Z}$ denotes the evidence.
 
@@
 
-The main types of binaries of interest in this work are those that
-are unresolved, because they can lead to misinterpretations of the data.
+The main types of binaries of interest in this work are those that are
+unresolved, because they can lead to misinterpretations of the data.
 For instance, unresolved binaries might produce multiple photometric
 signals and hinder our ability to correctly identify the star hosting
-the CPV signal.  Unresolved binaries could also bias photometric magnitude
-and color measurements, which would affect our stellar parameter
-estimates.  To attempt to identify binaries, we considered the
-following lines of information.
+the CPV signal.  Unresolved binaries could also bias photometric
+magnitude and color measurements, which would affect our stellar
+parameter estimates.  To attempt to identify binaries, we considered
+the following lines of information.
 
@@
 These plots showed two clusters of stars, at $\lesssim$10\,\kms and
-20-25\,\kms.  We therefore adopted a threshold of $20$\,km\,s$^{-1}$ to
-flag possible single-lined spectroscopic binaries, which selected
+20-25\,\kms.  We therefore adopted a threshold of $20$\,km\,s$^{-1}$
+to flag possible single-lined spectroscopic binaries, which selected
 \nrvscatterflag\ stars: TIC~405910546, TIC~224283342, and
@@
 photometric variability, or intrinsic astrometric motion.  Based on
-this exercise, we adopted a threshold of RUWE$_{\rm DR3}>2$ to
-flag sources with excess astrometric noise.  This threshold was met
-by \ngoodhighruwe/\ngoods\ high-quality CPVs and by
-\nmaybehighruwe/\nmaybes\ of the ambiguous CPVs.  The choice of the threshold RUWE
-is somewhat subjective, since the RUWE distribution has an extended tail
-\citep[e.g.][]{2022MNRAS.513.5270P}.  If we had instead required
-RUWE$_{\rm DR3}>1.4$, \ngoodweakruwe/\ngoods\ high-quality CPVs
-and \nmaybeweakruwe/\nmaybes\ of the ambiguous sample would have been
-flagged.
+this exercise, we adopted a threshold of RUWE$_{\rm DR3}>2$ to flag
+sources with excess astrometric noise.  This threshold was met by
+\ngoodhighruwe/\ngoods\ high-quality CPVs and by
+\nmaybehighruwe/\nmaybes\ of the ambiguous CPVs.  The choice of the
+threshold RUWE is somewhat subjective, since the RUWE distribution has
+an extended tail \citep[e.g.][]{2022MNRAS.513.5270P}.  If we had
+instead required RUWE$_{\rm DR3}>1.4$, \ngoodweakruwe/\ngoods\
+high-quality CPVs and \nmaybeweakruwe/\nmaybes\ of the ambiguous
+sample would have been flagged.
 
@@
 beating light curves, and with PDM periodograms that showed multiple
-periods.  For such cases, we then
-subtracted the mean CPV signal over each sector, and 
-repeated the phase-dispersion minimization analysis.  The resulting
-secondary periods, $P_{\rm sec}$, are listed in
+periods.  For such cases, we then subtracted the mean CPV signal over
+each sector, and repeated the phase-dispersion minimization analysis.
+The resulting secondary periods, $P_{\rm sec}$, are listed in
 Table~\ref{tab:thetable}; we required these to be at least 5\%
-different from the primary period.  The majority of secondary
-signals showed morphologies corresponding to starspot modulation.  This
+different from the primary period.  The majority of secondary signals
+showed morphologies corresponding to starspot modulation.  This
 process yielded \ngoodmultperiodflag/\ngoods\ high-quality CPVs with
@@
 
-Table~\ref{tab:thetable} summarizes each of the sources of
-binarity information into a single bitwise column.  
-We describe detailed results concerning binarity in
-Section~\ref{subsec:resultsbinarity}, and summarize those results
-Section~\ref{subsec:discbinary}.
+Table~\ref{tab:thetable} summarizes each of the sources of binarity
+information into a single bitwise column.  We describe detailed
+results concerning binarity in Section~\ref{subsec:resultsbinarity},
+and summarize those results Section~\ref{subsec:discbinary}.
 
@@
 		}
-		\label{fig:cqvs}
+		\label{fig:cpvs}
 	\end{center}
@@
 
-Figure~\ref{fig:cqvs} is a mosaic of phased light curves for the
+Figure~\ref{fig:cpvs} is a mosaic of phased light curves for the
 \ngoods\ CPVs.  The objects are sorted first in order of the number of
@@
 five objects by this metric are TIC~300651846 (12 sectors);
-TIC~402980664 (7 sectors); TIC~89463560
-(5 sectors); TIC~363963079 (5 sectors); and
-TIC~294328887 (4 sectors).  The brightest five CPVs span
+TIC~402980664 (7 sectors); TIC~89463560 (5 sectors); TIC~363963079 (5
+sectors); and TIC~294328887 (4 sectors).  The brightest five CPVs span
 9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
@@
 cluster, primarily using BANYAN\,$\Sigma$ as described in
-Section~\ref{subsec:starprops}.\footnote{Two of the
-\nnotfieldbanyan\ memberships were made with low confidence and are
-flagged in Table~\ref{tab:thetable}.  The assignment of TIC~397791443
-to IC\,2602 was based not on BANYAN\,$\Sigma$ but instead on a
-literature search \citep[e.g.][]{2020A&A...633A..99C}.}  The relevant
-groups are listed in Table~\ref{tab:thetable}; their ages span
-$\approx$5-200\,Myr.  For comparison, BANYAN\,$\Sigma$ assigned high-probability
-($>$95\%)
-field membership to 59{,}361 out of the
-\nstarssearched\ target stars.  Most stars in our target sample are old;
-the CPVs returned by our blind search are young.
+Section~\ref{subsec:starprops}.\footnote{Two of the \nnotfieldbanyan\
+memberships were made with low confidence and are flagged in
+Table~\ref{tab:thetable}.  The assignment of TIC~397791443 to IC\,2602
+was based not on BANYAN\,$\Sigma$ but instead on a literature search
+\citep[e.g.][]{2020A&A...633A..99C}.}  The relevant groups are listed
+in Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  For
+comparison, BANYAN\,$\Sigma$ assigned high-probability ($>$95\%) field
+membership to 59{,}361 out of the \nstarssearched\ target stars.  Most
+stars in our target sample are old; the CPVs returned by our blind
+search are young.
 
@@
 $\lesssim$$10\%$ completeness of TESS beyond 100\,pc
-(Figure~\ref{fig:completeness}), there may be
-many more CPVs in Sco-Cen that remain to be discovered.
+(Figure~\ref{fig:completeness}), there may be many more CPVs in
+Sco-Cen that remain to be discovered.
 
@@
 prediction): TIC~193136669 (TWA~34) and TIC~57830249 (TWA~33).
-However, neither is considered a ``good'' CPV for the reasons
-that follow.
+However, neither is considered a ``good'' CPV for the reasons that
+follow.
 
@@
 appearing and disappearing within the span of one cycle.  None of the
-CPVs in our sample exhibit this property.  Independently, TIC~193136669
-is known to have a cold disk of dust and molecular gas, based on
-1.3\,mm continuum emission and resolved $^{12}{\rm CO}(2-1)$ emission
-\citep{2015A&A...582L...5R}.  It was labeled a dipper by
+CPVs in our sample exhibit this property.  Independently,
+TIC~193136669 is known to have a cold disk of dust and molecular gas,
+based on 1.3\,mm continuum emission and resolved $^{12}{\rm CO}(2-1)$
+emission \citep{2015A&A...582L...5R}.  It was labeled a dipper by
 \citet{2022ApJS..263...14C}; we agree with their designation, and
@@
 ``misclassifications''.
-
-% Our three ``possible'' infrared excesses were TIC~405910546,
-% 289840926, and 244161191.  After a literature search, we concluded
-% that none have clear evidence for the presence of a disk.
-% TIC~405910546, in LCC, shows a unique TESS light curve, reminiscent of
-% a $P$=38\,hr singly-eclipsing binary, except with additional
-% substructure during each eclipse that resembles the CPV phenomenon
-% more than any other variability of which we are aware.  TIC~289840926
-% ($\beta$~Pic moving group, $P$=4.8\,hr), shows what we believe is a
-% clear CPV signal, but has no definitive evidence for a large, dusty
-% disk.  TIC~244161191 (TOI-278), in Columba, also has no definitive
-% evidence for a large disk.  It is however ``multi-periodic''---in
-% addition to the 7.17\,hr CPV signal, this source shows a superposed
-% 8.39\,hr sinusoidal signal, probably from an unresolved neighboring
-% star or binary companion.
 
@@
       ambiguous CPV candidates are light blue dots.  Unresolved
-      binaries (red rings) are objects for which the Gaia DR3 radial velocity
-      scatter exceeded 20\,\kms, or if Gaia ${\rm RUWE}_{\rm DR3}$$>$2
-      and multiple photometric signals were present in the TESS light
-      curve.  The top panels show the \nstarssearched\ target stars
-      with 2-minute cadence TESS data as the shaded gray background;
-      darker regions correspond to a larger relative number of
-      searched stars.  The lower-left panel compares the
+      binaries (red rings) are objects for which the Gaia DR3 radial
+      velocity scatter exceeded 20\,\kms, or if Gaia ${\rm RUWE}_{\rm
+      DR3}$$>$2 and multiple photometric signals were present in the
+      TESS light curve.  The top panels show the \nstarssearched\
+      target stars with 2-minute cadence TESS data as the shaded gray
+      background; darker regions correspond to a larger relative
+      number of searched stars.  The lower-left panel compares the
       rotation--color distribution of CPVs against the rotation
@@
 These observations are also in agreement with previous analyses of
-multi-periodic low-mass objects discovered by K2, which found that such
-systems are almost always binaries
+multi-periodic low-mass objects discovered by K2, which found that
+such systems are almost always binaries
 \citep{2018AJ....156..138T,2018AJ....156..275S}.
@@
 
-TIC~142173958 and TIC~425937691 both show evidence for two separate CPV
-signals in their TESS light curves.  For TIC~142173958, the signals
-have periods of 11.76\,hr and 12.84\,hr.  For TIC~425937691, the two
-periods are 4.82\,hr and 3.22\,hr, near the 3:2 period commensurability.
-Given that both sources have two photometric signals and elevated
-RUWEs, each source is probably an unresolved binary consisting of two
-CPVs.  To our knowledge, these are the third and fourth such systems
-known: EPIC~204060981 has two CPVs with periods of 9.59\,hr and
-9.12\,hr \citep{2018AJ....155...63S}, and TIC~242407571 has two CPVs
-with periods of 11.33\,hr and 13.63\,hr, near the 6:5 period commensurability
-\citep{2021AJ....161...60S}.
+TIC~142173958 and TIC~425937691 both show evidence for two separate
+CPV signals in their TESS light curves.  For TIC~142173958, the
+signals have periods of 11.76\,hr and 12.84\,hr.  For TIC~425937691,
+the two periods are 4.82\,hr and 3.22\,hr, near the 3:2 period
+commensurability.  Given that both sources have two photometric
+signals and elevated RUWEs, each source is probably an unresolved
+binary consisting of two CPVs.  To our knowledge, these are the third
+and fourth such systems known: EPIC~204060981 has two CPVs with
+periods of 9.59\,hr and 9.12\,hr \citep{2018AJ....155...63S}, and
+TIC~242407571 has two CPVs with periods of 11.33\,hr and 13.63\,hr,
+near the 6:5 period commensurability \citep{2021AJ....161...60S}.
+
 %\footnote{TIC~242407571, although within
@@
 			{\bf Evolution of CPV light curves over two years.}
-			Out of the \ngoods\ CPVs in Figure~\ref{fig:cqvs}, 32 had
+			Out of the \ngoods\ CPVs in Figure~\ref{fig:cpvs}, 32 had
 			2-minute cadence TESS data available for a baseline of at
@@
 for which TESS 2-minute cadence observations were available at least
-two years apart.  Such a baseline was available for 32 of the
-\ngoods\ confirmed CPVs in our catalog; for plotting purposes we show
-the brightest 27.  
-We have defined $\phi=0$ for each sector to be the time of minimum
-light observed in that sector, rather than using a consistent phase
-definition across multiple sectors.
-This is because for most of the sources we do not know the period at the
-precision necessary to be able to accurately propagate an ephemeris
-over two years.  The achievable period precision, $\sigma_P$, can be
-estimated as
+two years apart.  Such a baseline was available for 32 of the \ngoods\
+confirmed CPVs in our catalog; for plotting purposes we show the
+brightest 27.  We have defined $\phi=0$ for each sector to be the time
+of minimum light observed in that sector, rather than using a
+consistent phase definition across multiple sectors.  This is because
+for most of the sources we do not know the period at the precision
+necessary to be able to accurately propagate an ephemeris over two
+years.  The achievable period precision, $\sigma_P$, can be estimated
+as
 \begin{equation}
@@
 Measuring the period independently for each sector did not reveal
-evidence for significant ($>$3$\sigma$) changes in period, implying
-a period stability of $\lesssim$0.1\% over two years.
+evidence for significant ($>$3$\sigma$) changes in period, implying a
+period stability of $\lesssim$0.1\% over two years.
 
 A few objects in Figure~\ref{fig:evoln} show the CPV phenomenon in one
-sector, and only marginal signs or no sign of CPV behavior in the other
-sector.  In our subjective assessment, cases for which at least one
-sector would be flagged as ``ambiguous'' include
+sector, and only marginal signs or no sign of CPV behavior in the
+other sector.  In our subjective assessment, cases for which at least
+one sector would be flagged as ``ambiguous'' include
 TIC~368129164 (Sector 23 might be labeled an EB),
@@
 
-Based on the
-fraction of sources overall that ``turned off'', the observed shape
-evolution implies that CPVs have an on-off duty cycle of $\approx$75\%.
-Correcting for the duty cycle might be important in population-level
-estimates of the intrinsic frequency of the CPV phenomenon
-\citep[e.g.][]{2022AJ....163..144G}.
+Based on the fraction of sources that ``turned off'', the
+observed shape evolution implies that CPVs have an on-off duty cycle
+of $\approx$75\%.  Correcting for the duty cycle might be important in
+population-level estimates of the intrinsic frequency of the CPV
+phenomenon \citep[e.g.][]{2022AJ....163..144G}.
 
@@
     two-harmonic sinusoid has been subtracted to highlight the sharp
-    dips.  
-    A fixed period and phase are adopted for all sectors; the dips
-    across all observations are bounded by $\phi \in [-0.35,0.35]$.
-    In Sectors 25-26 (cycles 248-315), periods are visible at
-    the fundamental period of 18.5611\,hr, as well as at faster
-    ($\phi$$\approx$0-0.07) and slower ($\phi$$\approx$0.25-0.27)
-    relative periods based on the presence of blue dips with distinct
-    slopes.  Multiple simultaneous periods are also visible in Sector
-    53 (cycles 1234-1263) and Sectors 58-59 (cycles 1411-1479).  White
-    chunks denote missing data.
-    The state changes noted with red markers in Figure~\ref{fig:lplc} occur in
+    dips.  A fixed period and phase are adopted for all sectors; the
+    dips across all observations are bounded by $\phi \in
+    [-0.35,0.35]$.  In Sectors 25-26 (cycles 248-315), periods are
+    visible at the fundamental period of 18.5611\,hr, as well as at
+    faster ($\phi$$\approx$0-0.07) and slower
+    ($\phi$$\approx$0.25-0.27) relative periods based on the presence
+    of blue dips with distinct slopes.  Multiple simultaneous periods
+    are also visible in Sector 53 (cycles 1234-1263) and Sectors 58-59
+    (cycles 1411-1479).  White chunks denote missing data.  The state
+    changes noted with red markers in Figure~\ref{fig:lplc} occur in
     cycles 261, 309, and 1241.
@@
 
-A few of our complex periodic variables were near the TESS continuous viewing
-zones (Figure~\ref{fig:catalogscatter}, top right).  Out of this
-already small sample, LP 12-502 (TIC~402980664; $d$=21\,pc, $J$=9.4,
-$T$=11.1) stood out due to the quality and content of its data.  We
-discuss another interesting source, TIC~300651846, in
+A few of our complex periodic variables were near the TESS continuous
+viewing zones (Figure~\ref{fig:catalogscatter}, top right).  Out of
+this already small sample, LP 12-502 (TIC~402980664; $d$=21\,pc,
+$J$=9.4, $T$=11.1) stood out due to the quality and content of its
+data.  We discuss another interesting source, TIC~300651846, in
 Appendix~\ref{app:tic3006}.  In this section, we describe the LP
@@
 
-The behavior during Sectors 53--58 (cycles 1233-1481) is comparatively tame; the light curve shows
-only four to six dips per cycle.  Some dips remain stable in depth and
-duration over this five-month interval.  Other dips grow, like the one
-at $\phi = +0.06$ between cycles 1458 and 1481.  Other dips, such as
-the one at $\phi = +0.12$ in cycles 1233-1264, disappear entirely.
-The most dramatic state change occurs during cycle 1241, when a large
-dip switches from a depth of 3\% and a duration of 3 hours to a depth
-of 0.3\% and a duration of 1 hour.
+The behavior during Sectors 53--58 (cycles 1233-1481) is comparatively
+tame; the light curve shows only four to six dips per cycle.  Some
+dips remain stable in depth and duration over this five-month
+interval.  Other dips grow, like the one at $\phi = +0.06$ between
+cycles 1458 and 1481.  Other dips, such as the one at $\phi = +0.12$
+in cycles 1233-1264, disappear entirely.  The most dramatic state
+change occurs during cycle 1241, when a large dip switches from a
+depth of 3\% and a duration of 3 hours to a depth of 0.3\% and a
+duration of 1 hour.
 
@@
 {\sc State-changes reveal dip independence}---The state-changes seen
-in cycles 261, 309, and 1241 confirm that dips can disappear in
-less than one cycle. While such behavior was also noted by
+in cycles 261, 309, and 1241 confirm that dips can disappear in less
+than one cycle. While such behavior was also noted by
 \cite{2017AJ....153..152S}, the data presented here show further that
@@
 for one dip can vary independently of the materials or processes
-responsible for other dips.  The state changes during cycles 261
-and 309 support the same conclusion, while also hinting that the
-{\it leading} dip of a complex is most prone to disappearing, leaving
-the trailing dips unchanged in its wake.
+responsible for other dips.  The state changes during cycles 261 and
+309 support the same conclusion, while also hinting that the {\it
+leading} dip of a complex is most prone to disappearing, leaving the
+trailing dips unchanged in its wake.
 
@@
 
-% 16 px vs 310 px for a full phase
-% Based on our SED fitting $R_\star=0.369\,R_\odot$ star, and from the
-% isochrone mass, $M_\star=0.215\,M_\odot$
-
 {\sc Dip durations}---The shortest dip duration for any of the
@@
 where we have inserted the stellar radius and mass derived in
-Section~\ref{subsec:starprops}.  Thus, the shortest-duration dips
-are likely produced by transits of bodies or distributions of material
+Section~\ref{subsec:starprops}.  Thus, the shortest-duration dips are
+likely produced by transits of bodies or distributions of material
 that are smaller than the star.  The corotation radius corresponds to
@@
 
-Referring back to Figure~\ref{fig:catalogscatter},  typical CPV
-masses span 0.1-0.4\,$M_\odot$, typical ages span 2-150\,Myr,
-and
-relative to the
-Pleiades, the CPVs are among the more rapidly rotating half of M
-dwarfs. 
-The CPV mass and age range includes both fully convective stars and stars
-with a combination of radiative cores and convective envelopes; 
-the dividing line for these ages is at around $M_\star = 0.25\,M_\odot$
-\citep{2018A&A...619A.177B}.  We found no obvious differences in light
-curve morphology for CPVs above and below this fully-convective pre-main-sequence boundary.
-
-The closest CPV in our catalog is DG~CVn (TIC~368129164),
-a member of AB Dor at $d$$=$18\,pc.  
-The three brightest CPVs are DG~CVn
+Referring back to Figure~\ref{fig:catalogscatter},  typical CPV masses
+span 0.1-0.4\,$M_\odot$, typical ages span 2-150\,Myr, and relative to
+the Pleiades, the CPVs are among the more rapidly rotating half of M
+dwarfs.  The CPV mass and age range includes both fully convective
+stars and stars with a combination of radiative cores and convective
+envelopes; the dividing line for these ages is at around $M_\star =
+0.25\,M_\odot$ \citep{2018A&A...619A.177B}.  We found no obvious
+differences in light curve morphology for CPVs above and below this
+fully-convective pre-main-sequence boundary.
+
+The closest CPV in our catalog is DG~CVn (TIC~368129164), a member of
+AB Dor at $d$$=$18\,pc.  The three brightest CPVs are DG~CVn
 ($T$=9.3), TIC~405754448 ($T$=9.6), and TIC~167664935 ($T$=10.3).  The
 shortest period, 3.64\,hr, belongs to TIC~201789285.  The longest
-period, 37.9\,hr, belongs to TIC~405910546.  Based on the Gaia$_{\rm DR3}$ RV
-scatter, the latter source may
-turn out to be an eclipsing binary; if so, the longest-period CPV in our
-catalog would be TIC~193831684 (31.0\,hr).  By definition, we required
-the periods to be below 48\,hr.
+period, 37.9\,hr, belongs to TIC~405910546.  Based on the Gaia$_{\rm
+DR3}$ RV scatter, the latter source may turn out to be an eclipsing
+binary; if so, the longest-period CPV in our catalog would be
+TIC~193831684 (31.0\,hr).  By definition, we required the periods to
+be below 48\,hr.
 
@@
 
-For CPVs, binarity seems to provide either nuisances or curiosities.  The
-nuisances include
-astrophysical false positives with two beating rapidly
-rotating stars, as well as uncertainty about which
-star produces the CPV signal in binary systems.  Our two candidate K dwarf CPVs 
-suffer from this latter concern (see Section~\ref{subsec:resultsbinarity}).
-
-Curiosities include the four binary systems that are now known to each host
-two separate CQVs.
-CQVs are sufficiently rare that such systems may have 
-physical import.
-Recent work has shown that the orbits of binaries closer than
-$\lesssim$700 AU tend to be aligned with their planetary systems
-\citep[e.g.][]{2022AJ....163..207C}.  If we assume that observing CPV
-variability requires high line-of-sight inclinations,
-and that the inclinations in binaries are correlated, then we would
-expect the detection of one CPV in a binary system to raise the
-probability that the other star is a CPV.  The limitations of the
-current catalog prevent further exploration of this issue, but it
-might be interesting for future study.
-
-A separate possible relation between binarity and CPVs is that the presence
-of a binary companion could cause early disk dispersal,
+For CPVs, binarity seems to provide either nuisances or curiosities.
+The nuisances include astrophysical false positives with two beating
+rapidly rotating stars, as well as uncertainty about which star
+produces the CPV signal in binary systems.  Our two candidate K dwarf
+CPVs suffer from this latter concern (see
+Section~\ref{subsec:resultsbinarity}).
+
+Curiosities include the four binary systems that are now known to each
+host two separate CPVs.  CPVs are sufficiently rare that such systems
+may have physical import.  Recent work has shown that the orbits of
+binaries closer than $\lesssim$700 AU tend to be aligned with their
+planetary systems \citep[e.g.][]{2022AJ....163..207C}.  If we assume
+that observing CPV variability requires high line-of-sight
+inclinations, and that the inclinations in binaries are correlated,
+then we would expect the detection of one CPV in a binary system to
+raise the probability that the other star is a CPV.  The limitations
+of the current catalog prevent further exploration of this issue, but
+it might be interesting for future study.
+
+A separate possible relation between binarity and CPVs is that the
+presence of a binary companion could cause early disk dispersal,
 freeing the star to contract.  The CPV phenomenon seems to require
@@
 multiplicity rate of M dwarfs near the Sun is 26.8$\pm$1.4\%
-\citep{2019AJ....157..216W}.  
-%Based on the same study, the peak of the
-%separation distribution decreases from $\approx$49\,AU for
-%$0.30$-$0.60$\,$M_\odot$ stars, to $\approx$11\,AU for
-%$0.15$-$0.30$\,$M_\odot$ M dwarfs.
-The $\approx$32\% multiplicity fraction in our
-CPV sample (from RUWE$_{\rm DR3}$; see Section~\ref{subsec:resultsbinarity})
-seems approximately
-consistent with this field fraction.
+\citep{2019AJ....157..216W}.  The $\approx$32\% multiplicity fraction
+in our CPV sample (from RUWE$_{\rm DR3}$; see
+Section~\ref{subsec:resultsbinarity}) seems approximately consistent
+with this field fraction.
 
@@
 
-While CPV periods appear to remain fixed over thousands of cycles, the light curve shapes evolve over
-typical timescales of 10 to 1{,}000 cycles (e.g.\ Figures~\ref{fig:evoln} and~\ref{fig:lpriver0}).  Although we refer
-to them as ``periodic'', the CPVs are
-therefore actually quasiperiodic, with coherence timescales of $\approx$100 cycles.
-This marks a qualitative departure
-from the ``persistent'' {\it vs.} ``transient'' flux dip distinction
-previously described by \citet{2017AJ....153..152S}, which was based on
-$\lesssim$100\,cycle K2 baselines.
-The observation that CPVs have a population-averaged on-off duty cycle of $\approx$75\%
-(Figure~\ref{fig:evoln}) is also new.
-Appendix~\ref{app:tic3006} for instance shows $\approx$1{,}000 cycles of a source, TIC~300651846, with between zero and five sharp local minima per cycle.
-During the ``zero'' epochs (cycles $\approx$503-542), the source would likely be labeled an ordinary rotating star.
+While CPV periods appear to remain fixed over thousands of cycles, the
+light curve shapes evolve over typical timescales of 10 to 1{,}000
+cycles (e.g.\ Figures~\ref{fig:evoln} and~\ref{fig:lpriver0}).
+Although we refer to them as ``periodic'', the CPVs are therefore
+actually quasiperiodic, with coherence timescales of $\approx$100
+cycles.  This marks a qualitative departure from the ``persistent''
+{\it vs.} ``transient'' flux dip distinction previously described by
+\citet{2017AJ....153..152S}, which was based on $\lesssim$100\,cycle
+K2 baselines.  The observation that CPVs have a population-averaged
+on-off duty cycle of $\approx$75\% (Figure~\ref{fig:evoln}) is also
+new.  Appendix~\ref{app:tic3006} for instance shows $\approx$1{,}000
+cycles of a source, TIC~300651846, with between zero and five sharp
+local minima per cycle.  During the ``zero'' epochs (cycles
+$\approx$503-542), the source would likely be labeled an ordinary
+rotating star.
 
@@
 An independent peculiarity of CPV evolution is that the dips do not
-explore all phase angles with equal weight.  LP 12-502, and other CPVs,
-exhibit preferred phases lasting for at least two years.  For LP 12-502,
-all of the dips happen over phases corresponding to only two thirds of
-the period (Figures~\ref{fig:lp} and~\ref{fig:lpriver0}).  The
-remaining third seems to be ``out of limits'' for dips over the
+explore all phase angles with equal weight.  LP 12-502, and other
+CPVs, exhibit preferred phases lasting for at least two years.  For LP
+12-502, all of the dips happen over phases corresponding to only two
+thirds of the period (Figures~\ref{fig:lp} and~\ref{fig:lpriver0}).
+The remaining third seems to be ``out of limits'' for dips over the
 timespan of observations.  This could be evidence that the stellar
@@
 
-Examining Figure~\ref{fig:cqvs}, it is clear that CPV dips can be
+Examining Figure~\ref{fig:cpvs}, it is clear that CPV dips can be
 asymmetric but it is not obvious whether there is a preference for
@@
 
-Both the dust clump and the gas prominence scenarios (Figure~\ref{fig:f1} and Section~\ref{sec:intro})
-invoke clumps
-of material at the corotation radius;
-the main property that we believe distinguishes the two ideas is 
-the composition of the material.
+Both the dust clump and the gas prominence scenarios
+(Figure~\ref{fig:f1} and Section~\ref{sec:intro}) invoke clumps of
+material at the corotation radius; one property that distinguishes the
+two ideas is the composition of the material.
 
@@
 absorption cross-section in the blue than the red
-\citep[e.g.][]{1989ApJ...345..245C}.  Gas might also explain the observed
-chromaticities \citep{1992oasp.book.....G}.  While bound-bound
-absorption can be excluded, since it provides opacity only at narrow
-resonant lines, the hydrogen opacity due to bound-free
+\citep[e.g.][]{1989ApJ...345..245C}.  Gas might also explain the
+observed chromaticities \citep{1992oasp.book.....G}.  While
+bound-bound absorption can be excluded, since it provides opacity only
+at narrow resonant lines, the hydrogen opacity due to bound-free
 absorption is ``jagged'' \citep[see][Figure 8.5 and
@@
 $R_\star=0.3\,R_\odot$, and $T_{\rm eff}=3200\,{\rm K}$.  They found
-that non-shielded, generic silicate dust mixture \citep{1985ApJS...57..587D} with a
-single size of 0.1\,$\mu$m reached the $\approx$1500\,K sublimation
-temperature at $\approx$3\,$R_\star$.  This suggests that dust
-sublimation could be an important effect even for CPVs. }  The opacity
-source for $\sigma$~Ori~E and its analogs is instead thought to be
-bound-free absorption by neutral hydrogen \citep{1985Ap&SS.116..285N},
-although to our best knowledge direct evidence for this conclusion has
-yet to be acquired.  Separate and smaller-amplitude continuum flux
-brightenings in $\sigma$~Ori~E may also come from electrons scattering
-photospheric light toward the observer when the clouds are not
-transiting \citep{2022MNRAS.511.4815B}.
+that non-shielded, generic silicate dust mixture
+\citep{1985ApJS...57..587D} with a single size of 0.1\,$\mu$m reached
+the $\approx$1500\,K sublimation temperature at $\approx$3\,$R_\star$.
+This suggests that dust sublimation could be an important effect even
+for CPVs. }  The opacity source for $\sigma$~Ori~E and its analogs is
+instead thought to be bound-free absorption by neutral hydrogen
+\citep{1985Ap&SS.116..285N}, although to our best knowledge direct
+evidence for this conclusion has yet to be acquired.  Separate and
+smaller-amplitude continuum flux brightenings in $\sigma$~Ori~E may
+also come from electrons scattering photospheric light toward the
+observer when the clouds are not transiting
+\citep{2022MNRAS.511.4815B}.
 
@@
 radiative transfer.  This issue has a key ability to resolve the
-question of whether the CPVs are explained by dust or by gas, which has
-bearing on whether the material producing the dips is coming from the
-star, or whether it is a byproduct of the protoplanetary disk.
+question of whether the CPVs are explained by dust or by gas, which
+has bearing on whether the material producing the dips is coming from
+the star, or whether it is a byproduct of the protoplanetary disk.
 
@@
 references therein, it seems plausible that CPV occurrence decreases
-with stellar age from $\approx$3\% at 10\,Myr (Sco-Cen),
-to $\approx$1\% at 100\,Myr (Pleiades),
-down to 0\% by the $\approx$700\,Myr
-age of Praesepe.  This is odd in the context of the prominence
-scenario, because pre-main-sequence M dwarfs spin up over the first
-100\,Myr; prominences might therefore be expected to be {\it
-more} common at 100\,Myr than at 10\,Myr, under the assumption that the
-production of prominences depends only on the stellar rotation rate. 
-The dust clump scenario would hold a natural explanation: the lower occurrence of CPVs around older stars would
-simply reflect a finite supply of dust.
-One possible complication however is that the magnetic field topology
-of rapidly rotating M dwarfs may depend on factors other than the
-rotation rate (e.g.\ the age), which might alter the production of prominences.
+with stellar age from $\approx$3\% at 10\,Myr (Sco-Cen), to
+$\approx$1\% at 100\,Myr (Pleiades), down to 0\% by the
+$\approx$700\,Myr age of Praesepe.  This is odd in the context of the
+prominence scenario, because pre-main-sequence M dwarfs spin up over
+the first 100\,Myr; prominences might therefore be expected to be {\it
+more} common at 100\,Myr than at 10\,Myr, under the assumption that
+the production of prominences depends only on the stellar rotation
+rate.  The dust clump scenario would hold a natural explanation: the
+lower occurrence of CPVs around older stars would simply reflect a
+finite supply of dust.  One possible complication however is that the
+magnetic field topology of rapidly rotating M dwarfs may depend on
+factors other than the rotation rate (e.g.\ the age), which might
+alter the production of prominences.
 
@@
 increases to $\approx$0.7 when considering periods as long as
-10\,days.  Extrapolating to all small (0.1-4\,$R_\oplus$) planets within
-10 days, it is reasonable to expect
-nearly all M dwarfs to have at least one planet.
+10\,days.  Extrapolating to all small (0.1-4\,$R_\oplus$) planets
+within 10 days, it is reasonable to expect nearly all M dwarfs to have
+at least one planet.
 
 In the context of disk-driven planet migration, the stopping location
-for the innermost planet is set by the protoplanetary
-disk's truncation radius \citep[e.g.][and references therein]{2018haex.bookE.142I}.  The 
-truncation radius is often calculated by equating the magnetic
-pressure from the stellar magnetosphere with the ram pressure of the
-inflowing gas.  As it happens, the truncation radius is close to the
-corotation radius for low accretion rates
-\citep[e.g.][]{2015SSRv..191..339R,2022MNRAS.510.5246L}.  These considerations
-invite us to imagine one or more planets migrating inward due to gas
-drag, and arriving at $\approx$5-10 stellar
-radii before the disk is depleted.
+for the innermost planet is set by the protoplanetary disk's
+truncation radius \citep[e.g.][and references
+therein]{2018haex.bookE.142I}.  The truncation radius is often
+calculated by equating the magnetic pressure from the stellar
+magnetosphere with the ram pressure of the inflowing gas.  As it
+happens, the truncation radius is close to the corotation radius for
+low accretion rates
+\citep[e.g.][]{2015SSRv..191..339R,2022MNRAS.510.5246L}.  These
+considerations invite us to imagine one or more planets migrating
+inward due to gas drag, and arriving at $\approx$5-10 stellar radii
+before the disk is depleted.
 
@@
 planetesimals.  Young rocky bodies are expected to be hot, and they
-might expel either gas or dust.  The Jupiter-Io
-system \citep[e.g.][]{2004jpsm.book..537S} is analogous, in that a small rocky
-body feeds the construction of a plasma torus.  We emphasize
+might expel either gas or dust.  The Jupiter-Io system
+\citep[e.g.][]{2004jpsm.book..537S} is analogous, in that a small
+rocky body feeds the construction of a plasma torus.  We emphasize
 that although this type of configuration seems a priori plausible, no
@@
 depth into an effective cloud radius, $R_{\rm cloud}$.  For most CPVs
-in Figure~\ref{fig:cqvs}, this yields $\approx$2-20\,$R_\oplus$.  A
+in Figure~\ref{fig:cpvs}, this yields $\approx$2-20\,$R_\oplus$.  A
 minimum constraint on the number density of dust particles is obtained
@@
 {\rm d}N/{\rm d}t$ time-averaged over six months is
-%$\approx$3$\times$$10^{-18} M_\odot\,{\rm yr}^{-1}
-$\approx
-1\times10^{-12} M_\oplus\,{\rm yr}^{-1}$.  Considered cumulatively
-over the $\approx$$10^8$ years for which the CPV phenomenon is
-observed, this yields a cumulative moved dust mass of
+$\approx$$1\times10^{-12} M_\oplus\,{\rm yr}^{-1}$.  Considered
+cumulatively over the $\approx$$10^8$ years for which the CPV
+phenomenon is observed, this yields a cumulative moved dust mass of
 $10^{-4}\,M_\oplus$, of order the Solar System's asteroid belt.  If
@@
 disks show quasiperiodic or stochastic dimming over timescales of
-roughly one day \citep[e.g.][]{2010A&A...519A..88A,2010ApJS..191..389C}.  The dimming
+roughly one day
+\citep[e.g.][]{2010A&A...519A..88A,2010ApJS..191..389C}.  The dimming
 amplitudes can reach a few tenths of the stellar brightness, and dips
@@
 
-Although TIC~57830249 is an intriguing outlier, the general picture is that
-stars without infrared excesses have more stable optical light curves
-than those with infrared excesses.  While some dippers may evolve into CPVs after the
-disk is mostly gone, this would be generically expected based on population
-statistics: young objects become old.  There may be no
-other causal connection between the two evolutionary stages.  With
-that said, a common mystery between the CPVs and dippers is how exactly
-the {\it narrowness} of their flux dimmings is produced.  
-A similar mechanism may operate for both
-types of object, tied perhaps to a shared magnetic topology, or
-perhaps to a preference for dust to inspiral to the star in clumped
-structures.
+Although TIC~57830249 is an intriguing outlier, the general picture is
+that stars without infrared excesses have more stable optical light
+curves than those with infrared excesses.  While some dippers may
+evolve into CPVs after the disk is mostly gone, this would be
+generically expected based on population statistics: young objects
+become old.  There may be no other causal connection between the two
+evolutionary stages.  With that said, a common mystery between the
+CPVs and dippers is how exactly the {\it narrowness} of their flux
+dimmings is produced.  A similar mechanism may operate for both types
+of object, tied perhaps to a shared magnetic topology, or perhaps to a
+preference for dust to inspiral to the star in clumped structures.
 
@@
 %the half-cycle also corresponds to the interval over which half of the
-%star's surface is visible.  Of the CPVs in Figures~\ref{fig:cqvs}
+%star's surface is visible.  Of the CPVs in Figures~\ref{fig:cpvs}
 %and~\ref{fig:evoln}, a fraction that seems greater than random might
@@
       circumstellar plasma tori.  HD~37776 and HD~64740 (middle row)
-      are analogous magnetic B stars with field topologies potentially dominated by
-      high order multipoles.  The bottom row compares the latter
-      systems against the ``best-matching'' CPV light curves, selected
-      by eye from Figure~\ref{fig:cqvs}.  CPVs have light curves that
-      are visually similar to the topologically complex magnetic B
-      stars.  Stellar masses rounded to one significant figure are
-      given in the lower right of each panel; the star, TESS sector,
-      and period are listed in each subtitle.
+      are analogous magnetic B stars with field topologies potentially
+      dominated by high order multipoles.  The bottom row compares the
+      latter systems against the ``best-matching'' CPV light curves,
+      selected by eye from Figure~\ref{fig:cpvs}.  CPVs have light
+      curves that are visually similar to the topologically complex
+      magnetic B stars.  Stellar masses rounded to one significant
+      figure are given in the lower right of each panel; the star,
+      TESS sector, and period are listed in each subtitle.
 		}
@@
 analogs is that the light curve of $\sigma$~Ori~E is simpler than
-those in Figure~\ref{fig:cqvs}, with only two broad local minima, and
+those in Figure~\ref{fig:cpvs}, with only two broad local minima, and
 one ``hump'' (Figure~\ref{fig:bstar}; see also
@@
 \citep{2011ApJ...726...24K}.  The field geometry of HD~64740, while
-potentially less extreme, also shows evidence for a non-dipolar contribution
-\citep{2018MNRAS.475.5144S}.
-Recent TESS light curves
-of these two B stars appear surprisingly similar to the CPV light
-curves \citep{2020pase.conf...46M}.  The middle row of
-Figure~\ref{fig:bstar} shows the phased TESS light curves for these
-two stars, with by-eye best-matching CPVs shown underneath for
-comparison.  The number of dips per cycle, the shapes of the dips, and
-the dip depths relative to the sinusoidal envelope are all similar.
-This connection suggests that the highly structured light curves of
-both the M dwarfs and the B stars are associated with (and perhaps
-caused by) strong non-dipolar magnetic fields.  Non-dipolar fields for
-M dwarfs are plausible, given that Zeeman Doppler Imaging has revealed
-non-axisymmetric magnetic field patterns for the few M dwarfs for
-which this technique is technically feasible \citep[see][and
-references therein]{2021A&ARv..29....1K}.
+potentially less extreme, also shows evidence for a non-dipolar
+contribution \citep{2018MNRAS.475.5144S}.  Recent TESS light curves of
+these two B stars appear surprisingly similar to the CPV light curves
+\citep{2020pase.conf...46M}.  The middle row of Figure~\ref{fig:bstar}
+shows the phased TESS light curves for these two stars, with by-eye
+best-matching CPVs shown underneath for comparison.  The number of
+dips per cycle, the shapes of the dips, and the dip depths relative to
+the sinusoidal envelope are all similar.  This connection suggests
+that the highly structured light curves of both the M dwarfs and the B
+stars are associated with (and perhaps caused by) strong non-dipolar
+magnetic fields.  Non-dipolar fields for M dwarfs are plausible, given
+that Zeeman Doppler Imaging has revealed non-axisymmetric magnetic
+field patterns for the few M dwarfs for which this technique is
+technically feasible \citep[see][and references
+therein]{2021A&ARv..29....1K}.
 
@@
 In this work, we searched 2-minute cadence TESS data collected from
-2018 July to 2022 September for complex periodic variables (CPVs).  The target
-stars were \nstarssearched\ late-K and early-to-mid M dwarfs within 150\,pc
-and with TESS magnitudes $T$<16. 
-The selection function included $>$$80\%$ of such stars within 30\,pc, and $<$$10\%$ of such stars at distances exceeding 100\,pc (Figure~\ref{fig:completeness}).
-
-We found \ngoods\ objects that showed complex
-quasiperiodic behavior over at least one TESS sector.  These \ngoods\
-bona fide CPVs are listed in Table~\ref{tab:thetable}.  This table also
-includes \nmaybes\ ambiguous CPVs, whose designation is
-less certain, and \ndebunked\ impostors.  We inferred ages for all but
-two of the \nallcands\ objects based on memberships in young stellar associations; we
-also derived temperatures and radii using SED fitting, and 
-inferred stellar masses by interpolating against stellar evolutionary
-models.  We caution that our sample is far from being
-volume-limited and is not even magnitude-limited:
-the TESS 2-minute stellar sample had a heterogeneous
-selection function which may have been biased in favor of young stars
-over field stars.  Previous work however has shown that $\approx$1-3\%
-of M dwarfs younger than $\approx$100\,Myr show the CPV phenomenon
+2018 July to 2022 September for complex periodic variables (CPVs).
+The target stars were \nstarssearched\ late-K and early-to-mid M
+dwarfs within 150\,pc and with TESS magnitudes $T$<16.  The selection
+function included $>$$80\%$ of such stars within 30\,pc, and $<$$10\%$
+of such stars at distances exceeding 100\,pc
+(Figure~\ref{fig:completeness}).
+
+We found \ngoods\ objects that showed complex quasiperiodic behavior
+over at least one TESS sector.  These \ngoods\ bona fide CPVs are
+listed in Table~\ref{tab:thetable}.  This table also includes
+\nmaybes\ ambiguous CPVs, whose designation is less certain, and
+\ndebunked\ impostors.  We inferred ages for all but two of the
+\nallcands\ objects based on memberships in young stellar
+associations; we also derived temperatures and radii using SED
+fitting, and inferred stellar masses by interpolating against stellar
+evolutionary models.  We caution that our sample is far from being
+volume-limited and is not even magnitude-limited: the TESS 2-minute
+stellar sample had a heterogeneous selection function which may have
+been biased in favor of young stars over field stars.  Previous work
+however has shown that $\approx$1-3\% of M dwarfs younger than
+$\approx$100\,Myr show the CPV phenomenon
 \citep{2016AJ....152..114R,2022AJ....163..144G,2022AJ....164...80R}.
@@
     \item The sharpest CPV dips have durations of $\approx$0.05\,$P$
-      and depths of $\approx$1-3\% (Figures~\ref{fig:cqvs}
+      and depths of $\approx$1-3\% (Figures~\ref{fig:cpvs}
       and~\ref{fig:evoln}).  Explaining dips this sharp requires
@@
     \item Many CPV dips have durations a few times longer than $T_{\rm
-      dur}$ (Figure~\ref{fig:cqvs}).  The dips are often superposed
-      on a quasi-sinusoidal signal that presumably originates from
-      starspots and faculae on the stellar surface.  The
-      only viable explanation currently known for sharp dips being superposed on
-      the starspot signals is that concentrations (``clumps'')
-      of circumstellar material corotate with the star.
-      Assuming that the longer dips have the same physical origin as
-      the shortest dips, the corotating clumps must also
-      be capable of having sizes comparable to the star.
+      dur}$ (Figure~\ref{fig:cpvs}).  The dips are often superposed on
+      a quasi-sinusoidal signal that presumably originates from
+      starspots and faculae on the stellar surface.  The only viable
+      explanation currently known for sharp dips being superposed on
+      the starspot signals is that concentrations (``clumps'') of
+      circumstellar material corotate with the star.  Assuming that
+      the longer dips have the same physical origin as the shortest
+      dips, the corotating clumps must also be capable of having sizes
+      comparable to the star.
 %
@@
 %
-    \item Most CPVs are M dwarfs with masses 0.1-0.4\,$M_\odot$.
-    Two sources, TIC~405754448 and
-      TIC~405910546, have masses that appear to exceed 0.5\,$M_\odot$.
-      Both are potentially binaries, and this may confuse our ability
-      to accurate identify the source of the CPV signal
-      (Section~\ref{subsec:massive}).  We encourage additional
-      scrutiny of these objects in future work.
+    \item Most CPVs are M dwarfs with masses 0.1-0.4\,$M_\odot$.  Two
+      sources, TIC~405754448 and TIC~405910546, have masses that
+      appear to exceed 0.5\,$M_\odot$.  Both are potentially binaries,
+      and this may confuse our ability to accurate identify the source
+      of the CPV signal (Section~\ref{subsec:massive}).  We encourage
+      additional scrutiny of these objects in future work.
 %
     \item The closest CPVs to the Sun are at distances of 15-20\,pc;
-      the brightest have $V$$\approx$12 ($J$$\approx$7.5).  We
-      have found most of the close exemplars in this work, since our CPV sample was
-      $\gtrsim$80\% complete within 30\,pc.  The lack of CPVs in the
-      volume-complete $<$15\,pc sample of 0.1-0.3\,$M_\odot$ stars
-      analyzed by \citet{2021AJ....161...63W} is consistent with this
-      estimate.  Expanding our analysis of the TESS data to the full
-      frame images would yield a truly volume-limited selection
-      function, and would expand the CPV census by about a factor of
-      two within 50\,pc, and by a factor of ten within 100\,pc.
+      the brightest have $V$$\approx$12 ($J$$\approx$7.5).  We have
+      found most of the close exemplars in this work, since our CPV
+      sample was $\gtrsim$80\% complete within 30\,pc.  The lack of
+      CPVs in the volume-complete $<$15\,pc sample of
+      0.1-0.3\,$M_\odot$ stars analyzed by \citet{2021AJ....161...63W}
+      is consistent with this estimate.  Expanding our analysis of the
+      TESS data to the full frame images would yield a truly
+      volume-limited selection function, and would expand the CPV
+      census by about a factor of two within 50\,pc, and by a factor
+      of ten within 100\,pc.
 %
@@
 inclination, roughly one third of low mass stars \citep[those that
-rotate rapidly enough;][]{2022AJ....163..144G} could trap circumstellar
-material in the same way.  It also suggests that CPVs may
-preferentially show transiting planets at larger distances than the
-corotating material, though this conclusion would be dependent on whether the
-magnetic and stellar spin axes tend to be aligned.  Given these
-points, observational follow-up work should include searching for
-outer transiting planets, and measuring equatorial velocities in order
-to test whether the stellar inclination angles are indeed
+rotate rapidly enough;][]{2022AJ....163..144G} could trap
+circumstellar material in the same way.  It also suggests that CPVs
+may preferentially show transiting planets at larger distances than
+the corotating material, though this conclusion would be dependent on
+whether the magnetic and stellar spin axes tend to be aligned.  Given
+these points, observational follow-up work should include searching
+for outer transiting planets, and measuring equatorial velocities in
+order to test whether the stellar inclination angles are indeed
 preferentially edge-on.  Any source of empirical information on the
@@
 
-On the theoretical front, building a physical understanding of what sets
-the characteristic size scale of the clumping material would help
+On the theoretical front, building a physical understanding of what
+sets the characteristic size scale of the clumping material would help
 clarify why the light curves have the bizarre shapes that are
@@
 LGB is grateful for support from the Heising-Simons 51~Pegasi~b
-Fellowship, and for helpful conversations with
-J.~Spake, A.~Mann, G.~Laughlin, and B.~Draine.  
-We are also grateful for the assistance of S.~Yee,
-L.~Weiss, H.~Isaacson, and A.~Howard in acquiring and reducing the
-HIRES spectra.
-This paper relied primarily on data collected by the TESS mission; the specific
-2-minute cadence observations can be accessed via
+Fellowship, and for helpful conversations with J.~Spake, A.~Mann,
+G.~Laughlin, and B.~Draine.  
+We are also grateful for the assistance of S.~Yee, L.~Weiss,
+H.~Isaacson, and A.~Howard in acquiring and reducing the HIRES
+spectra.
+This paper relied primarily on data collected by the TESS mission; the
+specific 2-minute cadence observations can be accessed via
 DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.
@@
 Directorate.  
-We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham, S.~Seager, and J.~Jenkins) and the many TESS team members for their efforts to make the mission a continued success. 
-LP 12-502 in particular was observed at 2-minute
-cadence thanks to the TESS Guest Investigator programs G022252 (PI:
-J.~Schlieder; Sectors 18, 19, 25, 26) and G04168 (PI: R.~Jayaraman;
-Sector 53). 
+We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
+S.~Seager, and J.~Jenkins) and the many TESS team members for their
+efforts to make the mission a continued success. 
+LP 12-502 in particular was observed at 2-minute cadence thanks to the
+TESS Guest Investigator programs G022252 (PI: J.~Schlieder; Sectors
+18, 19, 25, 26) and G04168 (PI: R.~Jayaraman; Sector 53). 
 ADU acknowledges support by NASA under award number 80GSFC21M0002, as
@@
 
-%{\bf AUTHOR CONTRIBUTION STATEMENTS: PLEASE REVISE IF APPROPRIATE)}
+% Author contributions statements
 LGB conceived the project, performed the dip-counting search, light curve classification, cluster membership, SED, variability, and secondary-period analyses, and wrote the manuscript.
@@
 G\'AB acquired and maintained the servers used to run the dip-finding pipeline.
-%-----
-%{\bf JNW, MNG, GRR to confirm coauthorship \&/or to help out on interpretation!}
-% Pending!
-%HI and AH designed and maintain the architecture used to acquire and process the HIRES spectra.
-All authors assisted in manuscript revision.
 
@@
 \tablecaption{Bona fide, candidate, and debunked complex periodic
-  variables from
-  the TESS 2-minute data. {\bf For internal review, full versions are
-  available here
+  variables from the TESS 2-minute data. {\bf For internal review,
+  full versions are available here
   \url{https://www.dropbox.com/scl/fo/twn4s9ckbevf75jqhtoy1/h?rlkey=t5cn8cx2uoc2ptdm9e570kp1b&dl=0}}
@@
 \enddata
-\tablecomments{This table includes \ngoods\ good CPVs (\texttt{Quality}
-  flag 1), \nmaybes\ ambiguous CPVs (\texttt{Quality} flag 0), and
-  \ndebunked\ impostors (\texttt{Quality} flag -1).  The three-bit
-  binarity flag ``Bin'' is for Gaia DR3
-  \texttt{radial\_velocity\_error} outliers (bit 1), Gaia DR3
-  \texttt{ruwe} outliers (bit 2), and stars with multiple TESS periods
-  (bit 3).  The machine-readable version, available online, includes
-  additional columns for the Gaia DR2 and DR3 source identifiers, as
-  well as the stellar parameter uncertainties.  The age uncertainties
-  are typically $\approx \pm 10\%$, but can be asymmetric.  The median
-  statistical uncertainties on the temperature, radius, and mass are
-  $\pm$50\,K, $\pm$4\% and $\pm$9\% respectively.
-  $N_{\rm sector}$ denotes the number of TESS sectors for which {\it
-  any} data are expected to be acquired between July~2018 and
-  Oct~2024.  This number is generally greater than the number of
-  sectors for which 2-minute cadence data exist.   Association names
-  and provenance follow conventions adopted by
+\tablecomments{This table includes \ngoods\ good CPVs
+  (\texttt{Quality} flag 1), \nmaybes\ ambiguous CPVs
+  (\texttt{Quality} flag 0), and \ndebunked\ impostors
+  (\texttt{Quality} flag -1).  The three-bit binarity flag ``Bin'' is
+  for Gaia DR3 \texttt{radial\_velocity\_error} outliers (bit 1), Gaia
+  DR3 \texttt{ruwe} outliers (bit 2), and stars with multiple TESS
+  periods (bit 3).  The machine-readable version, available online,
+  includes additional columns for the Gaia DR2 and DR3 source
+  identifiers, as well as the stellar parameter uncertainties.  The
+  age uncertainties are typically $\approx \pm 10\%$, but can be
+  asymmetric.  The median statistical uncertainties on the
+  temperature, radius, and mass are $\pm$50\,K, $\pm$4\% and $\pm$9\%
+  respectively.  $N_{\rm sector}$ denotes the number of TESS sectors
+  for which {\it any} data are expected to be acquired between
+  2018~July and 2024~Oct.  This number is generally greater than the
+  number of sectors for which 2-minute cadence data exist.
+  Association names and provenance follow conventions adopted by
   \citet{2018ApJ...856...23G}: 
@@
 TIC~146539195 on 2023 January 3, a 15 minute exposure of TIC~264599508
-on 2023 January 9, and a 30 minute exposure of LP~12-502 (TIC~402980664) on 2023
-July 10.  The acquisition and analysis followed the usual techniques
-of the California Planet Survey \citep{2010ApJ...721.1467H}.
-Figure~\ref{fig:speccutouts} shows cutouts from the resulting spectra,
-centered on the \ion{Ca}{2} HK windows, H$\alpha$, and the \ion{Li}{1}
-6708\,\AA\ doublet.  The \ion{Ca}{2} H emission line is blended with
-H$\epsilon$.  While a more detailed analysis will be left for future
-work, these spectra confirm previous understanding established by
-\citet{2017AJ....153..152S} that the stars are chromospherically
-active M dwarfs in the ``weak-lined'' T Tauri regime
-\citep[e.g.][Figure~15]{2019AJ....157...85B}.  Their H$\alpha$
-equivalent widths, at $\approx$14\,\AA, $\approx$3\AA, and
+on 2023 January 9, and a 30 minute exposure of LP~12-502
+(TIC~402980664) on 2023 July 10.  The acquisition and analysis
+followed the usual techniques of the California Planet Survey
+\citep{2010ApJ...721.1467H}.  Figure~\ref{fig:speccutouts} shows
+cutouts from the resulting spectra, centered on the \ion{Ca}{2} HK
+windows, H$\alpha$, and the \ion{Li}{1} 6708\,\AA\ doublet.  The
+\ion{Ca}{2} H emission line is blended with H$\epsilon$.  While a more
+detailed analysis will be left for future work, these spectra confirm
+previous understanding established by \citet{2017AJ....153..152S} that
+the stars are chromospherically active M dwarfs in the ``weak-lined''
+T Tauri regime \citep[e.g.][Figure~15]{2019AJ....157...85B}.  Their
+H$\alpha$ equivalent widths, at $\approx$14\,\AA, $\approx$3\AA, and
 $\approx$8\,\AA\ (for TIC~264599508, 146539195, and 402980664
@@
 		{\bf Spectral age and activity diagnostics for three CPVs}.
-		Wavelengths are in air;
-		the continuum normalization is relative to the entire order.
-		The H$\alpha$ emission strength classifies the stars as weak-lined
-		T Tauris.
-		The lithium detection for TIC~146539195 is consistent with its
-		mass and $\beta$~Pic membership;
-		the non-detections for LP~12-502 (TIC~402980664) and TIC~264599508
-		are consistent with the $\approx$42\,Myr age implied by their membership
-		in the Columba moving group.
+    Wavelengths are in air; the continuum normalization is relative to
+    the entire order.  The H$\alpha$ emission strength classifies the
+    stars as weak-lined T Tauris.  The lithium detection for
+    TIC~146539195 is consistent with its mass and $\beta$~Pic
+    membership; the non-detections for LP~12-502 (TIC~402980664) and
+    TIC~264599508 are consistent with the $\approx$42\,Myr age implied
+    by their membership in the Columba moving group.
 	}
@@
 
-% \section{Chromaticity in TIC 262400835}
-% 
-% TIC~262400835 ($d$=174\,pc) is formally outside the scope of the
-% current work.  However, this CPV was observed using MuSCAT2 on 2020
-% December 12, 13, and 16, and the results might be worth including in
-% this study.
-% {\bf todo: describe observations / decide whether to include!}.
-% 
-% We include {\bf a table of the photometry} here to enable potential
-% future deeper analyses of the chromaticity of this object class.
-% 
-% Generally, these data serve as a minor addition beyond the
-% observations that have been acquired by
-% \citet[e.g.][]{2017PASJ...69L...2O,2020PASJ...72...23T,2022AJ....163..144G,2023MNRAS.518.2921K}
-% on this topic.  \citet{2023MNRAS.518.2921K} provides what we find to
-% be the most lucid summary, and we quote: ``amplitudes are almost
-% always larger, the shorter the wavelength of the filter, but the
-% relationship can be weak or non-monotonic.''
-% 
-% \begin{figure*}[!t]
-% 	\begin{center}
-%     \includegraphics[width=0.45\textwidth]{TIC262400835_multicolor_phase_stacked.pdf}
-%     	\end{center}
-%     \vspace{-0.4cm}
-% 		\caption{
-% 	      {\bf Chromaticity in TIC~262400835}.
-% 		}
-% 		\label{fig:muscat}
-% \end{figure*}
-
 \clearpage

### 2023-09-08 paper/collect.sh

@@ -2,6 +2,10 @@ resultsdir="/Users/luke/Dropbox/proj/cpv/results"
 artdir="/Users/luke/Dropbox/proj/cpv/art"
 addir="/Users/luke/Dropbox/Documents/proposals/2023_05_ADAP/latex/figs/"
 
+# tables
+cp $resultsdir/tables/2023_catalog_table/20230613_LGB_RJ_CPV_TABLE_selfnapplied_rounded.csv table1_short.csv
+cp $resultsdir/tables/2023_catalog_table/20230613_LGB_RJ_CPV_TABLE_selfnapplied_rounded_longMRT.csv table1_MRT.csv
+
 # 3-panel mosaic and cartoons
 cp $resultsdir/lc_mosaic/lc_mosaic_fav3.pdf f1a.pdf
 cp $artdir/twomodels.pdf f1b.pdf

### 2023-09-08 paper/ms.tex
update ms (zenodo)

@@
 		\caption{
-      {\bf Validation plots used to classify CPVs}.  The complete figure
-      set  is available in the online journal and contains one image per sector for each of the \nallcands\
-      objects in Table~\ref{tab:thetable}.
-      {\bf For internal collaboration review:
-      \url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
-      Panels are as follows.
+      {\bf Validation plots used to classify CPVs}.  The complete
+      figure set contains one image
+      per sector for each of the \nallcands\ objects in
+      Table~\ref{tab:thetable}, and
+      is accessible both through the online journal and via
+      \url{https://zenodo.org/record/8327508}. Panels are as follows.
 			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
@@
 \tablecaption{Bona fide, candidate, and debunked complex periodic
-  variables from the TESS 2-minute data. {\bf For internal review,
-  full versions are available here
-  \url{https://www.dropbox.com/scl/fo/twn4s9ckbevf75jqhtoy1/h?rlkey=t5cn8cx2uoc2ptdm9e570kp1b&dl=0}}
-  \label{tab:thetable}}
+  variables from the TESS 2-minute data.  The non-truncated machine readable versions
+  are accessible both through the online journal, and at \url{https://zenodo.org/record/8327508}. \label{tab:thetable}}
 %\toprule

### 2023-09-08 paper/ms.tex
add rasterization option...
because google chrome is bad at rendering things

(literally firefox does it.  adobe acrobat reader is fine.  preview is
fine.  just chrome)

@@
 
-\newcommand{\mstype}{letter}
+\newcommand{\mstype}{article}
 
@@
 
-% dip-counting pipeline
 \newcommand{\nuniqdipflagged}{{368}} % up-to-date; get_lgb_list_count.py
-
 \input{vals_cqv_table_statistics}
@@
 
-\received{---}
+\received{2023 September 8}
 \revised{---}
@@
 
-% primary authors
 \author[0000-0002-0514-5538]{Luke~G.~Bouma}
@@
 working under the assumption that all CPVs share the same basic
-physical scenario, we discard the ``starspot-only'' scenario.
+physical scenario, we discard the ``starspot-only'' model.
 Instead, the correct explanation probably involves spatially
@@
 
-Figure~\ref{fig:f1} illustrates two proposed models for the extrinsic
+Figure~\ref{fig:f1} illustrates two proposed configurations for the extrinsic
 material.  The first scenario invokes opaque dust ``clumps'' that
@@
 invoke opacity from dust, which would need to be collisionally charged
-\citep{2023MNRAS.518.4734S}; such dust might be sourced from a
+\citep{2023MNRAS.518.4734S}, and which might be sourced from a
 low-mass debris disk.  ``Gas prominences'' invoke opacity from
@@
 and we have observed 1500 cycles.  By folding with a fine grid of
-trial periods, we found that the choice $P=18.5611 \pm 0.0001$ causes
+trial periods, we found that the choice $P=18.5611 \pm 0.0001$\,hr causes
 more of the features in the LP 12-502 light curve to maintain constant
@@
 ADU identified the magnetic B star connection.
-LAH contributed to project design and to the interpretation of the light curves.
+LAH contributed to project design.
 JNW, SR, and LAH significantly improved the clarity of the manuscript.

### 2023-09-08 complexrotators/plotting.py

@@ -509,7 +509,8 @@ def plot_phase_timegroups(
     figsize_y=7,
     do4029_resid=0,
     cyclewindow=None,
-    mingap=3/24  # days
+    mingap=3/24,  # days
+    rasterized=False
     ):
     """
     As in plot_phase
@@ -618,7 +619,7 @@ def plot_phase_timegroups(
             fig=fig, ax=ax,
             titlestr=None, binsize_phase=binsize_phase,
             xlim=xlim, yoffset=ix, showtext=txt, savethefigure=False,
-            dy=yoffset
+            dy=yoffset, rasterized=rasterized
         )
 
         ix -= yoffset
@@ -651,10 +652,13 @@ def plot_phase_timegroups(
         s += 'resid_'
     if isinstance(cyclewindow, (tuple, list)):
         s += f'cycle{cyclewindow[0]}_to_{cyclewindow[1]}'
+    _r = ''
+    if rasterized:
+        _r = '_rasterized'
 
-    outpath = join(outdir, f"{s}{ticid}_P{plot_period*24:.4f}_{lc_cadences}_phase_timegroups.png")
+    outpath = join(outdir, f"{s}{ticid}_P{plot_period*24:.4f}_{lc_cadences}_phase_timegroups{_r}.png")
     #fig.savefig(outpath, dpi=300)
-    savefig(fig, outpath, dpi=450)
+    savefig(fig, outpath, dpi=600)
 
 
 def plot_phase_timegroups_mosaic(
@@ -669,7 +673,8 @@ def plot_phase_timegroups_mosaic(
     yoffset=5,
     showtitle=1,
     figsize_y=7,
-    model_id=None
+    model_id=None,
+    rasterized=False
     ):
     """
     As in plot_phase
@@ -782,7 +787,8 @@ def plot_phase_timegroups_mosaic(
             titlepad=0.1,
             showtext=False,
             savethefigure=False,
-            titlefontsize='x-small'
+            titlefontsize='x-small',
+            rasterized=rasterized
         )
         if isinstance(ylim, (list, tuple)):
             ax.set_ylim(ylim)
@@ -834,6 +840,8 @@ def plot_phase_timegroups_mosaic(
         s += f'_{model_id}'
     if isinstance(ylim, (list, tuple)):
         s += f'_ymin{ylim[0]}_ymax{ylim[1]}'
+    if rasterized:
+        s += "_rasterized"
 
     outpath = join(
         outdir,
@@ -844,7 +852,7 @@ def plot_phase_timegroups_mosaic(
[…]

### 2023-09-08 drivers/plot_beforeafter_mosaic.py

@@ -6,7 +6,8 @@ PLOTDIR = os.path.join(RESULTSDIR, 'beforeafter_mosaic')
 if not os.path.exists(PLOTDIR):
     os.mkdir(PLOTDIR)
 
-rp.plot_beforeafter_mosaic(PLOTDIR, sortby='tic8_Tmag')
+for r in [0,1]:
+    rp.plot_beforeafter_mosaic(PLOTDIR, sortby='tic8_Tmag', rasterized=r)
 assert 0
 rp.plot_beforeafter_mosaic(PLOTDIR, sortby='Ngoodsectors_tic8_Tmag')
 rp.plot_beforeafter_mosaic(PLOTDIR, sortby='tlc_mean_period')

### 2023-09-08 drivers/plot_full_mosaic.py

@@ -6,7 +6,9 @@ PLOTDIR = os.path.join(RESULTSDIR, 'full_lcmosaic')
 if not os.path.exists(PLOTDIR):
     os.mkdir(PLOTDIR)
 
-rp.plot_full_lcmosaic(PLOTDIR, sortby='Ngoodsectors_tic8_Tmag', binarytitle=1)
+for r in [0,1]:
+    rp.plot_full_lcmosaic(PLOTDIR, sortby='Ngoodsectors_tic8_Tmag',
+                          binarytitle=1, rasterized=r)
 rp.plot_full_lcmosaic(PLOTDIR, sortby='Rcr_over_Rstar')
 rp.plot_full_lcmosaic(PLOTDIR, sortby='Ngoodsectors_tic8_Tmag')
 rp.plot_full_lcmosaic(PLOTDIR, sortby='tlc_mean_period')

### 2023-09-08 drivers/plot_phase_timegroups.py

@@ -42,10 +42,11 @@ def main():
             #cyclewindow = [-1,630]
             #ylim = [-105,5]
 
-            # for 2min secondthalf
+            ## for 2min secondthalf
             lc_cadences = '2min'
             cyclewindow = [2290,2680]
             ylim = [-133,5]
+
             mingap = 3/24
 
             ## for all available 2min
@@ -72,21 +73,14 @@ def main():
 
             do4029_resid = 0
 
-        cp.plot_phase_timegroups(
-            outdir,
-            ticid=f'TIC_{ticid}',
-            lc_cadences='2min',
-            binsize_phase=0.005,
-            t0=t0,
-            ylim=ylim,
-            yoffset=yoffset,
-            manual_period=manual_period,
-            showtitle=0,
-            do4029_resid=do4029_resid,
-            figsize_y=figsize_y,
-            cyclewindow=cyclewindow,
-            mingap=mingap
-        )
+        for r in [1,0]:
+            cp.plot_phase_timegroups(
+                outdir, ticid=f'TIC_{ticid}', lc_cadences='2min',
+                binsize_phase=0.005, t0=t0, ylim=ylim, yoffset=yoffset,
+                manual_period=manual_period, showtitle=0,
+                do4029_resid=do4029_resid, figsize_y=figsize_y,
+                cyclewindow=cyclewindow, mingap=mingap, rasterized=r
+            )
 
 if __name__ == "__main__":
     main()

### 2023-09-08 drivers/plot_phase_timegroups_mosaic.py

@@ -22,22 +22,24 @@ def main():
         #for manual_period in np.arange(18.5600, 18.5620+0.0001, 0.0001):
         #for manual_period in [18.5611,18.5604]:
         for manual_period in [18.5611]:
-            #for ylim in ([0.2,1.6], [-4.8,3]):
-            cp.plot_phase_timegroups_mosaic(
-                outdir,
-                ticid=f'TIC_{ticid}',
-                lc_cadences='2min',
-                binsize_phase=0.005,
-                #t0=1791.15, # NOTE default
-                t0=1791.12,
-                #t0=1791.19,
-                #manual_period=18.559/24,
-                manual_period=manual_period/24,
-                ylim=[-4.8,3],
-                #showtitle=1
-                showtitle=0,
-                #model_id=f"manual_20230617_mask_v0_nterms2" # NOTE can be None
-            )
+            for r in [0, 1]:
+                #for ylim in ([0.2,1.6], [-4.8,3]):
+                cp.plot_phase_timegroups_mosaic(
+                    outdir,
+                    ticid=f'TIC_{ticid}',
+                    lc_cadences='2min',
+                    binsize_phase=0.005,
+                    #t0=1791.15, # NOTE default
+                    t0=1791.12,
+                    #t0=1791.19,
+                    #manual_period=18.559/24,
+                    manual_period=manual_period/24,
+                    ylim=[-4.8,3],
+                    #showtitle=1
+                    showtitle=0,
+                    #model_id=f"manual_20230617_mask_v0_nterms2", # NOTE can be None
+                    rasterized=r
+                )
 
 if __name__ == "__main__":
     main()

### 2023-09-08 paper/collect.sh

@@ -2,33 +2,54 @@ resultsdir="/Users/luke/Dropbox/proj/cpv/results"
 artdir="/Users/luke/Dropbox/proj/cpv/art"
 addir="/Users/luke/Dropbox/Documents/proposals/2023_05_ADAP/latex/figs/"
 
+################################
+# RASTERIZED FIGURES FOR ARXIV 
+# ...generally might prefer not, but this is a requirement for google chrome to render the figures correctly :-(
+################################
+echo -n "Enter 1 for arxiv (rasterized mosaics), 0 for anything else (e.g. AAS journals): "
+read VAR
+if [[ $VAR -eq 1 ]]
+then
+  # full LC mosaic (50 panel)
+  cp $resultsdir/full_lcmosaic/full_lcmosaic_showtitles_binarytitle_Ngoodsectors_tic8_Tmag_rasterized.pdf f4.pdf
+  # LC evolution
+  cp $resultsdir/beforeafter_mosaic/beforeafter_mosaic_showtitles_tic8_Tmag_rasterized.pdf f6.pdf
+  # TIC4029 phase timegroups one orbit per panel
+  cp $resultsdir/phase_timegroups_mosaic/TIC_402980664/TIC_402980664_P18.5611_2min_phase_timegroups_mosaic_ymin-4.8_ymax3_rasterized.pdf f8.pdf
+  # TIC3006 phase timegroup
+  cp $resultsdir/phase_timegroups/TIC_300651846/cycle-1_to_630TIC_300651846_P8.2540_2min_phase_timegroups_rasterized.pdf f11a.pdf
+  cp $resultsdir/phase_timegroups/TIC_300651846/cycle2290_to_2680TIC_300651846_P8.2540_2min_phase_timegroups_rasterized.pdf f11b.pdf
+else
+  # full LC mosaic (50 panel)
+  cp $resultsdir/full_lcmosaic/full_lcmosaic_showtitles_binarytitle_Ngoodsectors_tic8_Tmag.pdf f4.pdf
+  # LC evolution
+  cp $resultsdir/beforeafter_mosaic/beforeafter_mosaic_showtitles_tic8_Tmag.pdf f6.pdf
+  # TIC4029 phase timegroups one orbit per panel
[…]

### 2023-09-08 paper/ms.tex
update ms

@@
 % drafting / arxiv
-\documentclass[11pt,twocolumn,tighten]{aastex63}
+\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex63}
 \turnoffedit
@@
     TIC~425933644 (Sector~28).
-		{\it Bottom:} Cartoon explanations for the phenomenon.  The dust
-		clump scenario (left) and gas prominence scenario (right) both invoke
-		magnetically-entrained corotating material.
+    {\it Bottom:} Cartoon configurations for magnetically-entrained
+    corotating material.  The dust clump scenario (left) and gas
+    prominence scenario (right) propose different opacity sources, and
+    different occultation geometries.
 	}

### 2023-09-22 paper/ms.tex
update ms

@@
 % drafting / arxiv
-\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex63}
+\documentclass[11pt,twocolumn,tighten]{aastex63}
 \turnoffedit
@@
 
-		\vspace{-0.65cm}
+		\vspace{-0.62cm}
 		\subfloat{
@@
 curve had a length that was a power of two, as described by
-\citeauthor{2019ApJ...876..127Z}.  After taking the Fourier transform
+\citeauthor{2019ApJ...876..127Z}\ After taking the Fourier transform
 of the padded light curve using {\tt numpy.fft}, we searched for peaks
@@
 magnitude diagrams suggested that most CPVs tended to be on the
-pre-main-sequence (e.g.\ panel {\it (k) of Figure~\ref{fig:vet}}).  We
+pre-main-sequence (e.g.\ panel {\it (k)} of Figure~\ref{fig:vet}).  We
 therefore estimated stellar ages by checking for probabilistic spatial
@@
 spectroscopic binaries.  None of the stars in our CPV sample were
-identified as possible binaries in this column.
+identified as \deleted{possible }binaries in this column.
 
@@
 cadence observations by guest investigators.  Given the
-$\lesssim$$10\%$ completeness of TESS beyond 100\,pc
+$\lesssim$$10\%$ completeness of \replaced{TESS}{our data} beyond 100\,pc
 (Figure~\ref{fig:completeness}), there may be many more CPVs in
@@
 population shown in Figure~\ref{fig:evoln}; propagated forward 1{,}000
-cycles yields a typical ephemeris uncertainty range of 2-11\,hours.
+cycles yields a typical ephemeris uncertainty range of 2 to 11\,hours.
 Measuring the period independently for each sector did not reveal
@@
 to discern between the gas and dust clump scenarios.  Based on the
-available statistics from e.g.  \citet{2022AJ....164...80R} and
+available statistics from \deleted{e.g. }\citet{2022AJ....164...80R} and
 references therein, it seems plausible that CPV occurrence decreases

### 2023-09-22 paper/ms.tex
update ms; fix fig13 typo

@@
       \citet{2019ApJ...876..127Z,2021AJ....161...60S,2022AJ....163..144G}, and \citet{2023ApJ...945..114P}.
-      ``CQVs'' and ``candidates'' are as in
+      ``\replaced{CQVs}{CPVs}'' and ``candidates'' are as in
       Figure~\ref{fig:catalogscatter}, though for visual clarity
@@
 \citep{2019ApJ...876..127Z} and \citet{2023ApJ...945..114P} both
-favored Tuc-Hor; many of our new CQVs are within this 40-100\,pc gap.
+favored Tuc-Hor; many of our new \replaced{CQVs}{CPVs} are within this 40-100\,pc gap.
 

### 2023-09-22 drivers/plot_literature_Tmag_vs_dist.py

@@ -171,7 +171,7 @@ def plot_tessmag_vs_distance(showliterature=1, show120seccands=1, basems=9,
     sel = (df.quality == 1)
     ax.scatter(
         df[sel].dist_pc, df[sel].TESSMAG,
-        c='C0', s=f*basems, zorder=5, label='CQVs B23', linewidths=0
+        c='C0', s=f*basems, zorder=5, label='CPVs B23', linewidths=0
     )
 
     # 120second candidates
@@ -190,7 +190,7 @@ def plot_tessmag_vs_distance(showliterature=1, show120seccands=1, basems=9,
         ax.scatter(
             ldf[sel].distance_pc, ldf[sel].TESSMAG,
             c='gray', marker='D', s=f*basems, linewidth=0.1, zorder=4,
-            label='K2 literature'
+            label='K2 literature', alpha=0.7
         )
 
         sel = ldf.telescope == 'TESS'
@@ -234,7 +234,7 @@ def plot_tessmag_vs_distance(showliterature=1, show120seccands=1, basems=9,
 if __name__ == "__main__":
 
     # sales plots
-    plot_tessmag_vs_distance(showliterature=1, basems=12, f=1.2)
+    plot_tessmag_vs_distance(showliterature=1, basems=12, f=1.)
 
     # manuscript
     plot_tessmag_vs_distance(showliterature=1)

### 2023-10-31 paper/ms.tex
update ms (reviewer report)

@@
 % upon AAS submission
-%\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
-%\documentclass[12pt,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
+%\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex63}
+\documentclass[11pt,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
 % drafting / arxiv
-\documentclass[11pt,twocolumn,tighten]{aastex63}
-\turnoffedit
+%\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex63}
+%\turnoffedit
 
@@
   blind search using TESS 2-minute data of \nstarssearched\ K and M
-  dwarfs with $T$$<$16 and $d$$<$150\,pc.  We found \ngoods\
+  dwarfs with $T$$<$16\added{\,mag} and $d$$<$150\,pc.  We found \ngoods\
   high-quality CPVs, and subsequently determined that most are members
   of stellar associations.  Among the new discoveries are the
-  brightest ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and
+  brightest ($T$$\approx$9.5\added{\,mag}), closest ($d$$\approx$20\,pc), and
   oldest ($\approx$200\,Myr) CPVs known.  One exceptional object, LP
@@
 \vspace{-2pt}
-We also noted ''possible'' CPVs for which the classification was more
-ambiguous, and ``false positives'' that are definitely not CPVs.  The
-most common false positives for both the Fourier and dip-counting
-techniques were eclipsing binaries, ordinary spotted rapid rotators,
-and light curves that were complex due to multiple stars contributing
-to the photometric aperture.  Our specialized dip-counting pipeline
-flagged \nuniqdipflagged\ unique stars for visual inspection; about
-20\% were subsequently labeled either good or possible CPVs.  From the
-more general Fourier pipeline, $\approx$0.5\% of stars that passed the
+We also noted \replaced{''possible'' CPVs for which the classification
+was more ambiguous, and}{a few stars with potentially oddly-shaped dips
+as ``ambiguous'' CPVs, and a few interesting} ``false
+positives'' that are definitely not CPVs.  The most common false
+positives for both the Fourier and dip-counting techniques were
+eclipsing binaries, ordinary spotted rapid rotators, and light curves
+that were complex due to multiple stars contributing to the
+photometric aperture.  Our specialized dip-counting pipeline flagged
+\nuniqdipflagged\ unique stars for visual inspection; about 20\% were
+subsequently labeled either good or \replaced{possible}{ambiguous} CPVs.  From the more
+general Fourier pipeline, $\approx$0.5\% of stars that passed the
 12-$\sigma$ peak threshold were eventually classified as CPVs.
@@
 consulted the meta-catalog of young, age-dated, and age-dateable stars
-provided by \citet{2022AJ....163..121B}, and also searched the local
+\replaced{provided}{assembled} by \citet{2022AJ....163..121B}, and also searched the local
 volume around each star for co-moving
 companions.\footnote{\url{https://github.com/adamkraus/Comove}, git
-commit \texttt{278b372}} Finally, to provide a base for comparison, we
+commit \texttt{278b372}\added{; see also \citet{2021AJ....161..171T}.}}\added{ A few important sources in the former meta-catalog included the
+Theia groups from \citet{KounkelCovey2019} and \citet{2020AJ....160..279K}, and the SPYGLASS stars from Table~1 of \citet{2021ApJ...917...23K}.} Finally, to provide a base for comparison, we
 also ran the BANYAN\,$\Sigma$ membership analysis on our entire
@@
 estimated the stellar masses by interpolating against the PARSEC
-isochrones \citep[v1.2S][]{2014MNRAS.444.2525C}.  The need for models
-that incorporate some form of correction for young, active M dwarfs is
-well-documented
-\citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2020ApJ...891...29S}.
+isochrones \citep[v1.2S;][]{2014MNRAS.444.2525C}.  The need for models
+that incorporate some form of correction for \deleted{young, active }M dwarfs is
+well-documented \citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2018AJ....155..225K,2019MNRAS.489.2615M,2020ApJ...891...29S}.
 Plausible explanations for the disagreement between observed and
 theoretical M dwarf colors and sizes include starspot coverage
-\citep[e.g.][]{2017ApJ...836..200G} and potentially incomplete line
+\citep[e.g.][]{2017ApJ...836..200G} and \deleted{potentially }incomplete line
 lists \citep[e.g.][]{2013A&A...556A..15R}.  In the PARSEC models,
@@
 stellar masses.  Given our estimates of $\{ \tilde{T}_{\rm eff},
-\tilde{M}_\star, \tilde{t} \}$, and approximating their uncertainties
-as Gaussian $\sigma_{\tilde{T}_{\rm eff}}$, $\sigma_{\tilde{M}_\star}$
+\tilde{R}_\star, \tilde{t} \}$, and approximating their uncertainties
+as Gaussian $\sigma_{\tilde{T}_{\rm eff}}$, $\sigma_{\tilde{R}_\star}$
 and $\sigma_{\tilde{t}}$, we define a distance metric $\Delta$ to each
-model PARSEC grid-point $\{ T_{\rm eff}, M_\star, t \}$ via
+model PARSEC grid-point $\{ T_{\rm eff}, R_\star, t \}$ via
 \begin{equation}
@@
   +
-  \left( \frac{\tilde{M}_{\star} - M_{\star}}{\sigma_{\tilde{M}_{\star}}} \right)^2
+  \left( \frac{\tilde{R}_{\star} - R_{\star}}{\sigma_{\tilde{R}_{\star}}} \right)^2
   +
@@
 represents the standard deviation of the non-published Gaia RV time
-series, outliers can suggest single-lined spectroscopic binarity.
-These plots showed two clusters of stars, at $\lesssim$10\,\kms and
+series, outliers can suggest single-lined spectroscopic binarity\added{ \citep[e.g.][]{2022arXiv220611275C}}.  These plots showed two
+clusters of stars, at $\lesssim$10\,\kms and
 20-25\,\kms.  We therefore adopted a threshold of $20$\,km\,s$^{-1}$
@@
 model.  This can be caused by marginally resolved binaries,  intrinsic
-photometric variability, or intrinsic astrometric motion.  Based on
-this exercise, we adopted a threshold of RUWE$_{\rm DR3}>2$ to flag
+photometric variability, or intrinsic astrometric motion\added{
+\citep[e.g.][]{2021AJ....162..128W}}.  Based on this exercise, we
+adopted a threshold of RUWE$_{\rm DR3}>2$ to flag
 sources with excess astrometric noise.  This threshold was met by
@@
 $W1$-$W4$ bands, which is typical for this class of object
-\citep{2017AJ....153..152S}.  Visually inspecting the SEDs of our
+\citep{2017AJ....153..152S}.  \replaced{Visually inspecting}{Inspecting} the SEDs of our
 \nallcands\ star sample and the WISE images available through IRSA, we
@@
 \subsubsection{Multiple CPVs in the same system: TIC~425937691 and TIC~142173958}
+\label{subsec:multis}
 
@@
 CPVs suffer from this latter concern (see
-Section~\ref{subsec:resultsbinarity}).
+Section~\ref{subsec:massive}).
 
 Curiosities include the four binary systems that are now known to each
-host two separate CPVs.  CPVs are sufficiently rare that such systems
+host two separate CPVs \added{(see Section~\ref{subsec:multis})}.  CPVs are sufficiently rare that such systems
 may have physical import.  Recent work has shown that the orbits of
@@
 
-A separate possible relation between binarity and CPVs is that the
+\deleted{A separate possible relation between binarity and CPVs is that the
 presence of a binary companion could cause early disk dispersal,
@@
 Section~\ref{subsec:resultsbinarity}) seems approximately consistent
-with this field fraction.
+with this field fraction.}
 
@@
 lower occurrence of CPVs around older stars would simply reflect a
-finite supply of dust.  One possible complication however is that the
+finite supply of dust.  One \replaced{possible}{potential} complication however is that the
 magnetic field topology of rapidly rotating M dwarfs may depend on
@@
 alter the production of prominences.
+
+\added{\subsection{Why are the dip and spot periods nearly equal?}}
+
+\added{The CPV dips are usually superposed on nearly sinusoidal modulation.
+The sinusoidal modulation
+is probably induced by brightness inhomogeneities on the stellar surface.  If
+the dips are explained by material orbiting the star, then the proximity
+of the spot and dip periods is surprising.
+For instance, the dust clumps modeled by \citet{2023MNRAS.518.4734S} tend to
+accumulate near -- but not exactly at -- corotation.}
+
+\added{To explore the proximity of the dip and spot periods, we
+generated synthetic light curves that superposed a sinusoid and a single
+eclipse.  We imposed periods, amplitudes, sampling, and noise properties
+similar to typical CPVs in Figure~\ref{fig:cpvs}.  We then tuned
+the period of the eclipse signal to differ slightly from the
+sinusoidal period, and processed the resulting synthetic signals
+through the same period-finding routine to which we subjected the real data.
+Provided the dip and sinusoid periods agreed to within $\approx$0.1\%, we found that
+phase-folding on the dominant period (that of the larger-amplitude starspots)
+yielded dip signals analogous to those in Figure~\ref{fig:cpvs}.  However
+increasing the period difference beyond $\gtrsim$0.3\%, the dip signal quickly becomes
+``smeared'' out and unidentifiable when phase-folding.  This
+exercise highlights that our search was sensitive only to stars with dip
+and spot periods that agreed to within a few parts per thousand.  
+Some CPVs may exceed this threshold; we encourage
+future work aimed at determining whether such stars exist.}
 
@@
 H.~Isaacson, and A.~Howard in acquiring and reducing the HIRES
-spectra.
+spectra\added{, and for the reviewer's suggestion to consider
+the proximity of the dip and spot periods}.
 This paper relied primarily on data collected by the TESS mission; the
@@
     SDSS \citep{2000AJ....120.1579Y},
-    WISE \citep{2010AJ....140.1868W}.
+    WISE \citep{2010AJ....140.1868W,2014yCat.2328....0C}.
 }

### 2023-11-01 complexrotators/sedfit.py
sedfit: uniform prior option

@@ -11,7 +11,7 @@ import os
 from os.path import join
 import pandas as pd, numpy as np
 
-from complexrotators.observability import get_gaia_rows
+from complexrotators.observability import get_gaia_dr2_rows
 from complexrotators.paths import RESULTSDIR
 
 from astropy.coordinates import SkyCoord
@@ -79,7 +79,7 @@ def run_SED_analysis(ticid, trimlist=None, uniformpriors=0):
     ##################
     # query the star #
     ##################
-    gdr2_df = get_gaia_rows(ticid, allcols=1)
+    gdr2_df = get_gaia_dr2_rows(ticid, allcols=1)
 
     ra = float(gdr2_df.ra)
     dec = float(gdr2_df.dec)
@@ -295,7 +295,10 @@ def run_SED_analysis(ticid, trimlist=None, uniformpriors=0):
     ##############
     # make plots #
     ##############
-    out_folder = join(RESULTSDIR, 'ariadne_sed_fitting', f'{starname}')
+    if uniformpriors:
+        out_folder = join(RESULTSDIR, 'ariadne_sed_fitting_UNIFORM', f'{starname}')
+    else:
+        out_folder = join(RESULTSDIR, 'ariadne_sed_fitting', f'{starname}')
 
     plots_out_folder = join(out_folder, 'plots')
     if not os.path.exists(plots_out_folder): os.mkdir(plots_out_folder)

### 2023-11-01 paper/ms.tex
update ms

@@
 that incorporate some form of correction for \deleted{young, active }M dwarfs is
-well-documented \citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2018AJ....155..225K,2019MNRAS.489.2615M,2020ApJ...891...29S}.
+well-documented \citep[e.g.][]{2012ApJ...757..112B,2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2018AJ....155..225K,2019MNRAS.489.2615M,2020ApJ...891...29S}.
 Plausible explanations for the disagreement between observed and
@@
 phase-folding on the dominant period (that of the larger-amplitude starspots)
-yielded dip signals analogous to those in Figure~\ref{fig:cpvs}.  However
+yielded dip signals analogous to those in Figure~\ref{fig:cpvs}.  However,
 increasing the period difference beyond $\gtrsim$0.3\%, the dip signal quickly becomes

### 2023-11-01 paper/ms.tex
propagate updated SED prior change into ms
per reviewer's suggestion

@@
 \begin{align}
-  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
-  R_\star / R_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
+  T_{\rm eff} / {\rm K}    &\sim \mathcal{U}(2000, 8000), \\
+  R_\star / R_\odot  &\sim \mathcal{U}(0.1, 1.5), \\
   A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
@@
 $\approx$0.60\,$M_\odot$ respectively.  The next-highest mass in our
-sample belongs to TIC~59836633 ($\approx$0.48\,$M_\odot$), with all
+sample belongs to TIC~59836633 ($\approx$\replaced{0.48}{0.45}\,$M_\odot$), with all
 remaining CPVs having masses $\lesssim$0.40\,$M_\odot$.

### 2023-11-01 paper/ms.tex
update ms

@@
 % upon AAS submission
-%\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex63}
-\documentclass[11pt,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
+\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex63}
+%\documentclass[11pt,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
 % drafting / arxiv
@@
 \received{2023 September 8}
-\revised{---}
+\revised{2023 November 3}
 \accepted{---}
@@
 \end{align}
-for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
-distributions, and $\mathcal{T}_{\rm N}(\mu, \sigma, a, b)$ a
+for \deleted{$\mathcal{N}$ the Gaussian and }$\mathcal{U}$ the uniform
+distribution\deleted{s, and $\mathcal{T}_{\rm N}(\mu, \sigma, a, b)$ a
 truncated normal distribution with mean $\mu$, standard deviation
-$\sigma$, and lower and upper bounds $a$ and $b$.  We validated our
+$\sigma$, and lower and upper bounds $a$ and $b$}.  We validated our
 chosen upper bound on $A_{\rm V}$ using a 2MASS color-color diagram.
@@
 Some CPVs may exceed this threshold; we encourage
-future work aimed at determining whether such stars exist.}
+future work aimed at determining whether such systems exist.}
 
